### 2023-12-13 manuscript.Rmd
Upload files

---
title: 'Chapter 4: Binocular combination in the Autonomic Nervous System'
author: |
 | Federico G. Segala$^1$, Joel T. Martin$^1$, Alex R. Wade$^1,2$ & Daniel H. Baker$^1,2$
output:
  bookdown::pdf_document2:
    fig_caption: yes
    toc: no
  html_document: default
bibliography: references.bib
link-citations: yes
linkcolor: black
csl: elife.csl
header-includes:
- \usepackage{caption}
---

```{r setup, include=FALSE}

processdata <- 0  # this flag determines the amount of processing, with 4 levels:
# 0 - do no processing, generate the pdf using existing versions of all figures
# 1 - generate figures using the processed group data
# 2 - average data across participants, do bootstrapping
# 3 - download all raw data and analyse (requires 48GB of storage)
cleanupraw <- 0  # if downloading raw data, delete once processed to save space

domodelling <- 0    # if set to 1, run the Stan models (takes ~24 hours)

localdir <- 'local/'    # all files are stored in the project directory /local/ which git is told to ignore
if (!file.exists(localdir)){dir.create(localdir)}   # create a local directory to store data and outputs
rawdir <- 'local/rawdata/'
if (!file.exists(rawdir)){dir.create(rawdir)}   # create a local directory to store raw data
figdir <- 'Figures/'
if (!file.exists(figdir)){dir.create(figdir)}   # create a local directory to store figures
datadir <- 'local/processeddata/'
if (!file.exists(datadir)){dir.create(datadir)}   # create a local directory to store processed data

# cut off for data inclusion (Mahalanobis distance for complex data)
SDthresh <<- 3
SDthreshcond <- 1.85
nbootstraps <<- 1000
legaltriggers <- 1:55
targetelectrodes1 <- c('POz','POz')

# check which packages are installed, install the missing ones, and activate
packagelist <- c('knitr','remotes','tictoc','R.matlab','bookdown','grImport','png','tiff','pals','ez','gtools','signal','boot','quickpsy','rstan','rstatix','coda','parallel','utils','osfr','ggplot2','grid','gridExtra','cowplot','ggsignif') # list of CRAN packages

missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
if (length(missingpackages)>0){install.packages(missingpackages,repos = "http://cran.us.r-project.org")}
if (!'FourierStats' %in% installed.packages()[,1]){remotes::install_github("bakerdh/FourierStats")}
packagelist <- c(packagelist,'FourierStats')
toinstall <- packagelist[which(!packagelist %in% (.packages()))]
invisible(lapply(toinstall,library,character.only=TRUE))

devtools::install_github("kupietz/kableExtra")
library(kableExtra)

knitr::opts_chunk$set(echo = TRUE)

# settings for sampler 
numSavedSteps <- 100000    # total number of MCMC steps
adaptSteps <- 1000  # Number of steps to "tune" the samplers
burnInSteps <- 2000 
thinSteps <- 10
nChains <- 16
ncores <- 8  # because of multi-threading, this is usually double the true number of physical cores, so we halve the number as Stan can only use physical cores
options(mc.cores=ncores)

# helper function to make colours transparent
addalpha <- function(col, alpha=1){apply(sapply(col, col2rgb)/255, 2, function(x) rgb(x[1], x[2], x[3], alpha=alpha))}

v4Interp <- function(df, xo, yo, rmax = .75, gridRes = 67) {
  ## Create a function to perform Matlab's v4 interpolation.
  ## Takes as input a data-frame with columns x, y, and z (x co-ordinates, y co-ordinates, and amplitude)
  ## and variables xo and yo, the co-ordinates which will be use to create a grid for interpolation
  xo <- matrix(rep(xo,length(yo)),nrow = length(xo),ncol = length(yo))
  yo <- t(matrix(rep(yo,length(xo)),nrow = length(yo),ncol = length(xo)))
  xy <- df$x + df$y*sqrt(as.complex(-1))
  d <- matrix(rep(xy,length(xy)),nrow = length(xy), ncol = length(xy))
  d <- abs(d - t(d))
  diag(d) <- 1
  g <- (d^2) * (log(d)-1)   # Green's function.
  diag(g) <- 0
  weights <- qr.solve(g,df$z)
  xy <- t(xy)
  outmat <- matrix(nrow = gridRes,ncol = gridRes)
  for (i in 1:gridRes){
    for (j in 1:gridRes) {
      test4 <- abs((xo[i,j] + sqrt(as.complex(-1))*yo[i,j]) - xy)
      g <- (test4^2) * (log(test4)-1)
      outmat[i,j] <- g %*% weights}}
  outDf <- data.frame(x = xo[,1],outmat)
  names(outDf)[1:length(yo[1,])+1] <- yo[1,]
  return(outDf)}

anovacirc2way <- function(data, groupA=NULL, groupB=NULL, participant=NULL){

  grouplabelsA <- groupA
  grouplabelsB <- groupB
  participantlabels <- participant
  datavals <- data

  grouplabelsA <- as.factor(grouplabelsA)
  factorlistA <- levels(grouplabelsA)
  grouplabelsB <- as.factor(grouplabelsB)
  factorlistB <- levels(grouplabelsB)
  participantlabels <- as.factor(participantlabels)
  participantlist <- levels(participantlabels)

  grandmean <- mean(datavals)
  grandvar <- sum(abs(datavals - grandmean)^2)/(length(datavals)-1)

    SST <- grandvar*(length(datavals) - 1)

    SSW <- 0
    for (n in 1:nlevels(participantlabels)){SSW <- SSW + sum(abs(datavals[which(participantlabels==participantlist[n])] - mean(datavals[which(participantlabels==participantlist[n])]))^2)}
    dfW <- 2*(nlevels(participantlabels)*(nlevels(grouplabelsA)*nlevels(grouplabelsB)-1))

    SSBet <- SST - SSW  # between subjects SS - not actually used
    SSM <- 0
    for (a in 1:nlevels(grouplabelsA)){
      for (b in 1:nlevels(grouplabelsB)){
        i <- as.numeric(((grouplabelsA==grouplabelsA[a])))
        j <- as.numeric(((grouplabelsB==grouplabelsB[b])))
        indices <- which((i*j)>0)
        SSM <- SSM + (nlevels(participantlabels)*sum(abs(datavals[indices] - grandmean)^2))
      }
    }
    dfM <- 2*((nlevels(grouplabelsA)*nlevels(grouplabelsB))-1)

    SSR <- 0
    for (a in 1:nlevels(grouplabelsA)){
      for (b in 1:nlevels(grouplabelsB)){
        i <- as.numeric(((grouplabelsA==grouplabelsA[a])))
        j <- as.numeric(((grouplabelsB==grouplabelsB[b])))
        indices <- which((i*j)>0)
        condvar <- sum(abs(datavals[indices] - mean(datavals[indices]))^2)/(length(indices)-1)
        SSR <- SSR + (nlevels(participantlabels)-1)*condvar
      }
    }    
    dfR <- 2*(nlevels(participantlabels)-1)*(nlevels(grouplabelsA)*nlevels(grouplabelsB))

    groupmeansA <- NULL
    for (n in 1:nlevels(grouplabelsA)){groupmeansA[n] <- mean(datavals[which(grouplabelsA==factorlistA[n])])}
    SSA <- 0
    for (n in 1:nlevels(grouplabelsA)){SSA <- SSA + length(which(grouplabelsA==factorlistA[n]))*abs(groupmeansA[n]-grandmean)^2}
    dfA <- 2*(nlevels(grouplabelsA)-1)

    groupmeansB <- NULL
    for (n in 1:nlevels(grouplabelsB)){groupmeansB[n] <- mean(datavals[which(grouplabelsB==factorlistB[n])])}
    SSB <- 0
    for (n in 1:nlevels(grouplabelsB)){SSB <- SSB + length(which(grouplabelsB==factorlistB[n]))*abs(groupmeansB[n]-grandmean)^2}
    dfB <- 2*(nlevels(grouplabelsB)-1)

    SSAB <- SSW - (SSA + SSB)
    dfAB <- 2 * (nlevels(grouplabelsA)-1) * (nlevels(grouplabelsB)-1)

    MSA <- SSA/dfA
    MSB <- SSB/dfB
    MSAB <- SSAB/dfAB
    MSR <- SSR/dfR

    FratioA <- MSA/MSR
    pvalA <- pf(FratioA,df1=dfA,df2=dfR,lower.tail=FALSE)
    FratioB <- MSB/MSR
    pvalB <- pf(FratioB,df1=dfB,df2=dfR,lower.tail=FALSE)
    FratioAB <- MSAB/MSR
    pvalAB <- pf(FratioAB,df1=dfAB,df2=dfR,lower.tail=FALSE)

    method <- 'Factorial repeated measures ANOVA^2-circ'
    output <- data.frame(FratioA,pvalA,FratioB,pvalB,FratioAB,pvalAB,dfA,dfB,dfAB,dfR,method)

  return(output)
}

cleanup2D <- function(data){
  # helper function to clean up complex data by removing any data points more than 
  # SDthresh standard deviations from the mean (in Mahalanobis distance units)
  cartdata <- data.frame(Re(data),Im(data))
  output <- 0
  if (sum(cartdata)!=0){
    D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
    i <- which(D<SDthresh) 
    output <- mean(temp[i])}
return(output)}

bootstrap2D <- function(data){
  mbs <- data.frame(meanamp=0,lowerCI=0,upperCI=0)
    cartdata <- data.frame(Re(data),Im(data))
    if (sum(cartdata)!=0){
      D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
      i <- which(D<SDthresh) 
    mbs <- amperrors(data[i],method='boot',quantiles=68,nresamples=nbootstraps)}
return(mbs)}

contrastsdB <- 20*log10(c(6,12,24,48,96))
colpal <- c('#FE5000','#8783CF','#228B22','#808080','#6d008b','#8B8000')
colpalmod <- c('#808080','#8B8000','#FE5000','#8783CF')
targetelectrodes <- c('Oz','POz','O1','O2')

if (processdata==2){
# if we're going to need the pre-processed files, extract from zip file
  if (!file.exists(paste0(datadir,'P101summary.RData'))){
   if (file.exists('resources/allprocessed.zip')){file.copy('resources/allprocessed.zip',localdir)}
   if (!file.exists('resources/allprocessed.zip')){ 
          osfnode <- '2qu6y'
          osfproject <- osf_retrieve_node(osfnode)
          osffiles <- osf_ls_files(osfproject,n_max=300)
          fid <- which(osffiles$name=='allprocessed.zip')
          osf_download(osffiles[fid,],localdir,progress=TRUE)
   }
          unzip(paste0(localdir,'allprocessed.zip'),exdir=localdir)
          d <- dir(paste0(localdir,'allprocessed'),full.names=TRUE)
          file.copy(d,datadir)
  }
}

```

$^1$Department of Psychology, University of York, York, UK. YO10 5DD  
$^2$York Biomedical Research Institute, University of York, York, United Kingdom

Address for correspondence: Federico G. Segala, [federico.segala\@york.ac.uk](federico.segala@york.ac.uk)

# Abstract

The size of the pupils changes in response to levels of ambient light and is regulated by the autonomic nervous system. The role of the retinal photoreceptors in determining pupil size has been investigated using silent substitution. They have been shown to be directly involved in controlling and maintaining the size of the pupils, with the cones and rods driving the initial constriction and the intrinsically photosensitive retinal ganglion cells maintaining the size over prolonged time periods. Here, we used silent substitution and pupillometry to investigate binocular combination while targeting the intrinsically-photoreceptive retinal ganglion cells, the L-M pathway and the S-(L+M) pathway. We found that the signals between the two pupils are combined in a non-linear manner when targeting all the different photoreceptor classes and that the non-linear combination was different between each class, as reflected by the different magnitudes of interocular suppression measured for each pathway.

# Introduction

The autonomic nervous system regulates many involuntary bodily processes, including the constriction and dilation of the pupils in response to light [@McDougal2015]. The anatomical pathway from the retina to the subcortical nuclei controlling the pupillary light response (PLR) is well established: it includes the Pretectal Olivary nucleus (PON), the Superior Cervical ganglion and the Edinger-Westphal nucleus, which project to the iris sphincter muscles that directly control the pupil size [@McDougal2008; @McDougal2015; @Wang2015]. Additionally, the retinal photoreceptors (cones, rods and the recently discovered melanopsin-containing intrinsically photosensitive retinal ganglion cells, ipRGCs) have been shown to be directly involved in controlling and maintaining the size of the pupils [@Barrionuevo2014; @Barrionuevo2018; @Dacey2005; @Murray2018; @Spitschan2014; @Spitschan2019; @Woelders2018]. The cones have been shown to drive the initial rapid constriction of the pupils [@Mathot2018], while the slower and longer activation of the ipRGCs shows their role in maintaining the constriction over a prolonged period of time and in regulating the post-illumination pupillary response [@Markwell2010; @McDougal2010].

The ipRGCs are a unique photoreceptor class that has been discovered recently [@Provencio2000]. They express the photopigment melanopsin, which is involved in the regulation of the circadian rhythm [@Provencio2000; @Panda2002; @Ruby2002], and form a major input to the PON [@Dacey2003]. The first direct evidence of the involvement of the ipRGCs in the PLR was shown in rats by @Lucas2003 who genetically deleted the melanopsin gene from rats, resulting in the loss of the intrinsic photosensitivity of the cells and a reduced pupil constriction. This same behaviour was later also observed in primates and humans [@Gamlin2007], where it was demonstrated that the PLR continues during light presentation even when cone and rod signalling is blocked. This also demonstrates the primary role of the ipRGCs in maintaining pupil constriction over a prolonged time. It has also been shown that the ipRGCs receive inputs from the other photoreceptors (cones and rods) and are activated by them [@Dacey2005].

To investigate how specific photoreceptor classes control the size of the pupils, a technique known as silent substitution is used. Silent substitution exploits the fact that each photoreceptor class has a distinct spectral tuning that overlaps with the others. Using a multiprimary system, in which the primaries have different spectra, it is possible to target one class of photoreceptors while maintaining the others at a constant activity level, effectively silencing them [@Shapiro1996; @Spitschan2018, this paper also offers a clear explanation of how to implement silent substitution]. Studies using silent substitution have shown that the pupils behave differently depending on which photoreceptor or pathway is being stimulated. For example, pupil responses have been shown to be out of phase when the S cones are stimulated, relative to when the ipRGCs or the L+M cones are stimulated [@Spitschan2014; @Cao2015]. Additionally, when L and M cones are stimulated individually, there appears to be a paradoxical pupil response: increments in L cone stimulation cause a constriction of the pupil, while increments in M cone stimulation lead to a dilation of the pupil [@Woelders2018; @Murray2018].

Interaction between the two eyes and the rules of binocular combination have been extensively studied. For pattern vision in the visual cortex, at low contrast, binocular summation occurs [binocular presentation confers higher sensitivity than monocular presentation, @Baker2018; @Campbell1965; @Legge1984], while, at high contrast, ocularity invariance is implemented [the response to monocularly- and binocularly-presented patterns is equalised, @Baker2007; @Ding2006; @Meese2006]. Additionally, evidence of a binocular component to the PLR is shown by the existence of a consensual response of the pupil [the stimulation of one eye will cause constriction of the other eye, @Wyatt1981] and the rules of binocular combination between the pupils have also been recently investigated [@Segala2023], finding that combination happens non-linearly with evidence of interocular suppression.

Most of the studies that use silent substitution and that investigate the PLR stimulate only one eye. If the stimulated eye is pharmacologically dilated to control pupil size, the response from the unstimulated eye (known as the consensual response) can be recorded [e.g. @McDougal2010; @Spitschan2014]. While this approach controls the total amount of light incident at the retina, it does not permit investigation of binocular combination for specific photoreceptor pathways. Seeing that it is possible to directly investigate binocular combination of signals between the pupils, we decided to investigate this by designing an experiment that allowed us to binocularly target the ipRGCs, the L-M pathway and the S-(L+M) pathway individually while recording binocular pupillometric measures. We chose a primary flicker frequency of 0.5 Hz, which has been shown to elicit pupil responses from all three pathways [@Spitschan2014]. The final results are interpreted using a hierarchical Bayesian computational model of binocular vision.

# Methods

## Participants

Twenty-four participants were recruited for each of the four experiments for a total of ninety-six (68 females) adult participants, whose age ranged from 18 to 41. All participants had normal or corrected to normal binocular vision and normal colour vision, and gave written informed consent. Our procedures were approved by the Ethics Committee of the Department of Psychology at the University of York (identification number 184).

## Apparatus & stimuli

To present synchronised silent substitution contrast modulations independently to each eye, two light engines, each with 10 independently addressable LED colour channels (SpectraTuneLAB: LEDMOTIVE Technologies, LLC, Barcelona, Spain), were integrated into a customised viewing system. The light engines were operated via a Python interface to their REST API [@Martin2022], which supports synchronous launch and playback of spectral sequences prepared in advance and stored in JSON format. When preparing the spectral sequences, the age of participants was recorded to account for the yellowing of the lenses.

```{r allcons, fig.cap="Summary of the spectral power distributions and alpha-opic irradiances for the background and each experiment. Panel (a) shows a schematic of the binocular stimulation system for presenting spectrally tuned modulations independently to each eye. The VR headset was attached to a clamp stand that the experimenters could use to adjust the height and align the headset with the eyes of the participant. The participant's head was positioned on a chin rest to keep it in position throughout the entire experiment. Panels (b) and (c) show the spectral power distributions and the alpha-opic irradiances of the background spectra used for both eyes. Panels (d-k) show the power distributions and the alpha-opic irradiances relative to the background for the four experiments: luminance (d, e), melanopsin (f, g), L-M pathway (h, i) and S-(L+M) pathway (j, k). A positive difference power shows a positive modulation (white disc for the luminance experiment, magenta for the L-M pathway experiment and purple for the S-(L+M) experiment) and a negative difference power shows a negative modulation (black disc for the luminance experiment, cyan for the L-M pathway experiment and lime for the S-(L+M) experiment).", fig.align="center", out.width = '80%', echo=FALSE}

knitr::include_graphics(paste0(figdir,'allcons.pdf'))

```

The output from the light engines was directed through liquid light guides (LLG3-8H: Thorlabs Ltd, Cambridgeshire, UK) and diffused onto semi-opaque and highly diffusive white glass discs with a diameter of 50 mm for even illumination (34-473: Edmund Optics, York, UK). The light guide gaskets were butt-coupled to the light engine diffusers with threaded adapters (SM1A9, AD3LLG: Thorlabs Ltd, Cambridgeshire, UK) and the exiting ends of the light guides were mated with 51 mm depth optical cylinders (SM2L20: Thorlabs Ltd, Cambridgeshire, UK) via appropriately threaded adapters (AD3LLG, SM2A6: Thorlabs Ltd, Cambridgeshire, UK). The stimulus diffuser discs were retained at the front end of the optical cylinders approximately 51 mm from the light source, at which distance the output beam was sufficiently dispersed to afford even illumination of the diffuser when viewed from the front. To guarantee safe illumination levels, a circular neutral-density filter with the same diameter of the white glass discs (50 mm) and an optical density of 0.6 log units was placed in the optical path between the light source and the diffusers. A small circular piece of blackout material with a diameter of approximately 8 degrees (10 mm) was positioned centrally on the front of each diffuser disc to aid as a fusion lock, as a fixation point and to occlude the fovea.

The diffuser discs were positioned in the objective planes of the lenses of a modified VR headset (SHINECON SC-G01, Dongguan Shinecon Industrial Co. Ltd), which was used by the participants to view the stimuli. The stimuli were two discs of flickering light with a diameter of approximately 30 degrees, which were fused together into a cyclopean percept resembling a donut-shaped ring of light, similar to that used in other studies [e.g., @Barrionuevo2016; @Murray2018; @Spitschan2014; @Zele2018]. The VR headset modifications allowed for small adjustments to account for individual differences in interpupillary distance and focal length. The use of this set up allowed us to modulate the stimuli in three different ocular configurations, similar to the ones we used in our previous experiment [@Segala2023]: monocular, binocular and dichoptic. In the monocular configuration, the unstimulated eye still saw a non-flickering disc of mean luminance. A schematic of the stimulation system is shown in Figure \@ref(fig:allcons)a. Pupillometry data were collected using a binocular Pupil Core eye-tracker headset [Pupil Labs GmbH, Berlin, Germany, @Kassner2014] running at 120 Hz, and the signals were recorded with the Pupil Capture software.

## Procedure

Before the start of each experiment, participants adjusted the objective planes of the lenses with the help of the experimenter until the stimulus was in focus and they perceived the two pieces of blackout material as one fused piece.

```{r ExampleStims, fig.cap="Example of the different experimental conditions. Panel (a) shows one cycle of flicker in the achromatic luminance experiment. In this experiment, the stimulus flickers between black and white. At the beginning of the cycle (0s), the stimulus appears at half the intesity and appears grey to the viewer. At 0.5s, the stimulus reaches the maximum intensity of the flicker and appears white to the viewer. At 1s, the stimulus appears again at half maximum and once again appears to be grey to the viewer. At 1.5s, the stimulus reaches the minimum intensity of the flicker and appears black to the viewer. Panel (b) shows one cycle of the flickering in the L-M pathway experiment. In this experiment, the stimulus flickers between magenta (+L-M) and cyan (-L+M). At the beginning of the cycle (0s), the stimulus appears at zero cone contrast and appears to be grey to the viewer. At 0.5s, the stimulus reaches the maximum L-cone contrast and appears magenta to the viewer. At 1s, the stimulus appears again at zero cone contrast and switches colour, once again appearing to be grey to the viewer. At 1.5s, the stimulus reaches the minimum L-cone contrast and appears cyan to the viewer. Panel (c) shows one cycle of the flickering in the S-(L+M) pathway experiment. In this experiment, the stimulus flickers between purple (+S-(L+M)) and lime (-S+(L+M)). At the beginning of the cycle (0s), the stimulus appears at zero cone contrast and appears to be grey to the viewer. At 0.5s, the stimulus reaches the maximum S-cone contrast and appears purple to the viewer. At 1s, the stimulus appears again at zero cone contrast and switches colour, once again appearing to be grey to the viewer. At 1.5s, the stimulus reaches the minimum S-cone contrast and appears lime to the viewer.", fig.align="center", out.width = '95%', echo=FALSE}

knitr::include_graphics(paste0(figdir,'ExampleStims.pdf'))

```

We initially planned to examine pupil responses and EEG responses simultaneously to temporal modulations flickering at 2 Hz and 1.6 Hz while stimulating the periphery of the retina. While the experiment produced clear responses when presenting an achromatic light (see Figures \@ref(fig:appendixfig1) and \@ref(fig:appendixfig2) in Appendix 1), the responses were very noisy for the targeted photoreceptor class experiments (see Figures \@ref(fig:pupildataMel2Hz)-\@ref(fig:EEGdataS2Hz) in Appendix 2) for both the pupillometry and the EEG data. Therefore, we decided to lower the main frequency to 0.5 Hz as previous literature showed that it was slow enough to elicit a pupil response from all photoreceptor classes [@Spitschan2014] and we focussed on only recording pupillometry data as this frequency would be well below the minimum threshold to elicit EEG responses [@Norcia2015].

Pupil responses to binocular temporal contrast modulations were examined in a factorial design that combined six ocular conditions, two temporal frequencies (0.4 and 0.5 Hz) and five temporal contrast levels relative to the mean illuminance (6, 12, 24, 48 and 96%). This design, similar to what we used in our previous study [@Segala2023], was applied in four separate experiments, each with a different mode of photoreceptor stimulation. In the first three conditions, the discs flickered at 0.5 Hz, in either a monocular, binocular or dichoptic arrangement. In the dichoptic condition the non-target eye saw a flickering fixed contrast of 48%. In the remaining three conditions (the cross-frequency conditions) one eye’s disc flickered at 0.4 Hz, and the other eye’s disc flickered at 0.5 Hz. We also tested monocular responses at 0.4 Hz, as well as binocular (one eye sees each frequency at the target contrast) and dichoptic (target stimulus flickering at 0.5 Hz, mask contrast of 48% at 0.4 Hz in the other eye) arrangements. We counterbalanced presentation of the target stimulus across the left and right eyes.

For all experiments, sinusoidal contrast modulations were presented against the same background spectrum (matched between the eyes), which was used to achieve silent substitution in the three photoreceptor modulation experiments. The background spectra were defined by setting all channels to half maximum output for the brighter of the two devices (STLab 1, left eye) and then using the STLab 1/STLab 2 calibration ratio to find the equivalent settings for the companion device (STLab 2, right eye). The background spectrum illuminance was approximately 74 lux. The spectral power distributions and alpha-opic irradiances of the background spectra for both eyes are shown in Figures \@ref(fig:allcons)b-c.

### Experiment 1: luminance

The experiment was conducted in a windowless room, in which the only source of light was the modified VR headset. The participants sat as close as possible to the VR headset, leaving enough space for the eye-tracker to record the eyes. The experiment was carried out in a single session of 45 minutes, divided into three blocks of 15 minutes each. In each block, there were a total of 60 trials lasting 15 seconds each (12s of stimulus presentation, followed by 3s of interstimulus interval). The participants were given no task other than look at the black fixation dot while trying to minimise their blinking during the presentation period.

In this experiment, the participants saw a disc of achromatic flickering light (average illuminance of approximately 74 lux), flickering between black and white, at the different contrast levels defined earlier. An example of one cycle of flickering for the luminance experiment is shown in Figure \@ref(fig:ExampleStims)a. The spectral power distributions and alpha-opic irradiances relative to the background for the luminance experiment are shown in Figures \@ref(fig:allcons)d-e.

### Experiment 2: melanopsin

The experiment used the same equipment set-up and the same experimental conditions as Experiment 5. The procedure was also the same. However, at the beginning of each block, participants habituated for 2 minutes to the background that would be present throughout the entire experiment. During this adaptation period, participants were asked to fixate on the same black fixation dot positioned in the middle of the stimulus and were told that they could blink normally. At the end of the adaptation period, the experiment started immediately and the participants followed the same instructions given in Experiment 1.

In this experiment, the participants experienced contrast modulations that targeted the melanopsin-containing intrinsically photosensitive Retinal Ganglion cells, while ignoring rods and nominally silencing the cones. Michelson contrast levels represented a percentage of the maximum melanopic contrast available, which was predetermined to be approximately 22 \%. Under perfect silent substitution conditions, these modulations do not entail any changes in brightness or chromaticity: it is therefore very difficult to include an example to visualise the stimulus. However, silent substitution is never perfect, so participants reported small fluctuations in reddishness, greenishness and brightness due to open-field cone contrast artefacts. These fluctuations were especially present at higher contrasts. This can be observed in the alpha-opic irradiances relative to the background for the melanopsin experiment shown in Figure \@ref(fig:allcons)g, where a small activation of the S, L and M cones is observable. The spectral power distributions relative to the background for the melanopsin experiment is also shown in Figure \@ref(fig:allcons)f.

### Experiment 3: L-M postreceptoral ‘parvocellular’ pathway

The experiment used the same equipment set-up and the same experimental conditions as Experiment 5. The procedure was the same as Experiment 6, including the presence of a 2-minute adaptation period at the beginning of each block. Additionally, before the start of the experiment, participants completed a luminance nulling perceptual calibration procedure in L-M cone space on an Iiyama $\textrm{VisionMaster}^{\textrm{TM}}$ Pro 510 display (800 x 600 pixels, 60 Hz refresh rate). During the task, participants were presented with a disc flickering within the L-M cone space (between magenta and cyan). Using a trackball, participants adjusted the angle in cone space to find their subjective isoluminant point, which resulted in changing the flickering intensity of the stimulus until the amplitude of the flicker appeared to be minimised. The result was used to modify the requested contrasts during stimulus preparation so as to account for individual differences affecting perceived illuminance, principally the L:M cone ratio [@Carroll2002; @Hofer2005].

In this experiment, the participants experienced contrast modulations that targeted the L-M postreceptoral ‘parvocellular’ pathway while ignoring rods and nominally silencing S-cones and melanopsin. Michelson contrast levels represented a percentage of the maximum L-M contrast available for the background spectrum, which was determined in advance to be approximately 10 \%. As shown in Figure \@ref(fig:ExampleStims)b, participants experienced an isoluminant chromatic modulation between magenta (+L-M) and cyan (-L+M). The spectral power distributions and alpha-opic irradiances relative to the background for the L-M pathway experiment are shown in Figures \@ref(fig:allcons)h-i.

### Experiment 4: S-(L+M) ‘koniocelluar’ pathway

The experiment used the same equipment set-up and the same experimental conditions as Experiment 5. The procedure was the same as Experiment 6, including the presence of a 2-minute adaptation period at the beginning of each block.

In this experiment, the participants experienced contrast modulations that targeted the S-(L+M) ‘koniocelluar’ pathway while ignoring rods and nominally silencing L/M cones and melanopsin. Michelson contrast levels represented a percentage of the maximum S-cone contrast available for the background spectrum, which was predetermined to be approximately 45 \%. As shown in Figure \@ref(fig:ExampleStims)c, participants experienced an isoluminant chromatic modulation between purple (+S-(L+M)) and lime (-S+(L+M)). The spectral power distributions and alpha-opic irradiances relative to the background for the S-(L+M) pathway experiment are shown in Figures \@ref(fig:allcons)j-k.

## Data analysis

The pupillometry data were analysed using the same method we used in our previous study [@Segala2023]. The data were converted from mp4 videos to a csv text file using the Pupil Player software [@Kassner2014], which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball. The individual data were then loaded into R for analysis, where a ten-second waveform for each trial in each eye was extracted (excluding the first two seconds after stimulus onset). We interpolated across any dropped or missing frames to ensure regular and continuous sampling over time. The Fourier transform was calculated for each waveform, and all repetitions of each condition were pooled across eye and then averaged. Finally, data were averaged across all participants to obtain the group results. We used coherent averaging and at each stage we excluded data points with a Mahalanobis distance exceeding $D$ = `r SDthresh` from the complex-valued mean. The consensual response was also analysed (see Appendix 3 for more details and the results).

For all experiments, we used a bootstrapping procedure with `r nbootstraps` iterations to estimate standard errors across participants. All analysis and figure construction was conducted using a single R-script, available online, making this study fully computationally reproducible: https://osf.io/gdvt4/.

## Computational model and parameter estimation

To describe our data, we chose the same model described in our previous study [@Segala2023]. The model has the same general form as the first stage of the contrast gain control model proposed by @Meese2006 and omits the second stage. For the previous model that we used [@Segala2023], the exponent of the numerator had a fixed value of 2. Here, we allow this parameter (called _p_) to be free, in order to permit different shapes of contrast response function, e.g. saturating or super-saturating. The responses of the left eye and right eye channels are as follows:

\begin{equation}
\label{eq:respLchap4}
Resp_L = \frac{L^p}{Z + L^q + wR^q},
\end{equation}

\begin{equation}
\label{eq:respRchap4}
Resp_R = \frac{R^p}{Z + R^q + wL^q},
\end{equation}

\noindent where _L_ and _R_ are the contrast signals from the left and right eyes, _p_ and _q_ are exponents, _Z_ is a saturation constant that shifts the contrast-response function laterally, and _w_ is the weight of suppression from the other eye.

The responses from the two eyes are then summed binocularly:

\begin{equation}
\label{eq:respBchap4}
Resp_B = R_{max}(Resp_L + Resp_R) + k,
\end{equation}

\noindent where _n_ is a noise parameter, and $R_{max}$ scales the overall response amplitude.

We performed model fitting on the normalised amplitudes to account for amplitude differences between the experiments.

# Results

## Experiment 1

```{r luminance individual, include=FALSE, results='hide'}

# (download and) analyse individual participant data for the luminance condition
if (processdata > 2){

  for(p in 601:612){
    participant <- paste0('P',p)

    tic()

    pupiltargets <- array(0,dim=c(3,2,60))
    pupilmasks <- pupiltargets
    pupiltargets2 <- pupiltargets
    pupilmasks2 <- pupiltargets
    pupilwaveforms <- array(0,dim=c(3,2,60,120*14))
    pupilspectra <- array(0,dim=c(3,2,60,300))
    timeseq <- seq(1/120,10,length.out=120*10)
    timeseq2 <- seq(1/120,14,length.out=120*14)
    targetindex <- (0.5*10)+1
    maskindex <- (0.4*10)+1
    targetindex2 <- (0.5*2*10)+1
    maskindex2 <- (2*0.4*10)+1

    repcounterP <- (1:60)*0
    d <- dir(paste0(rawdir,participant),pattern='*annotations.csv',full.names=TRUE)

    for (block in 1:length(d)){
        tic()
        adata <- read.csv(paste0(rawdir,participant,'/',paste0(participant,'_S',block),'_annotations.csv'))

        trialtimes <- NULL
        trialtypes <- NULL
        for (t in 1:(nrow(adata)/2)){
          trialtimes[t] <- mean(adata$timestamp[(t*2 - 1):(t*2)])
          trialtypes[t] <- adata$condition_code[t*2]
        }

        trialtypes[which(trialtypes>15)] <- trialtypes[which(trialtypes>15)] + 5
        inclist <- NULL
        for (t in 11:15){
          i <- which(trialtypes==t)
          inclist[t-10] <- i[2]
        }
        inclist <- inclist[which(!is.na(inclist))]
        trialtypes[inclist] <- trialtypes[inclist] + 5

        pdata <- read.csv(paste(rawdir,participant,'/',paste0(participant,'_S',block),'_pupil_positions.csv',sep=''))
        pdata2 <- pdata[,c(1,3,4,14)]
        pdata2 <- pdata2[which(pdata2[,3]>0.2),]

        for (trialno in 1:length(trialtypes)){
          repcounterP[trialtypes[trialno]] <- repcounterP[trialtypes[trialno]] + 1
          for (eye in 1:2){
            eyedata <- pdata2[which(pdata2[,2]==(2-eye)),]      
            a <- which(eyedata[,1]>trialtimes[trialno]+2)
            b <- which(eyedata[,1]<(trialtimes[trialno]+12))
            i <- intersect(a,b)
            trial <- eyedata[i,]
            trial <- trial[which(!is.na(trial[,4])),]
            trial[,1] <- trial[,1] - trial[1,1]
            if (nrow(trial)>3){
              resampled <- interp1(trial[,1],trial[,4],timeseq,method='linear',extrap=TRUE)
              fspec <- (fft(resampled)/length(resampled))
              pupiltargets[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno]] <- fspec[targetindex]
              pupilmasks[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno]] <- fspec[maskindex]
              pupiltargets2[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno]] <- fspec[targetindex2]
              pupilmasks2[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno]] <- fspec[maskindex2]
              pupilspectra[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno],1:300] <- fspec[1:300]
            }

            a <- which(eyedata[,1]>(trialtimes[trialno]-1))
            b <- which(eyedata[,1]<(trialtimes[trialno]+13))
            i <- intersect(a,b)
            trial <- eyedata[i,]
            trial[,1] <- trial[,1] - trial[1,1]
            if (nrow(trial)>3){
              trial <- trial[which(!is.na(trial[,4])),]
              resampled <- interp1(trial[,1],trial[,4],timeseq2,method='linear',extrap=TRUE)
              pupilwaveforms[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno],] <- resampled - mean(resampled[1:120])
            }
          }
        }
    }

    cleanmeansP <- matrix(0,nrow=6,ncol=5)
    cleanmasksP <- matrix(0,nrow=6,ncol=5)
    cleanmeansP2 <- matrix(0,nrow=6,ncol=5)
    cleanmasksP2 <- matrix(0,nrow=6,ncol=5)

    for (cond in 1:6){
        startindex <- (10*(cond-1))
        for (level in 1:5){
          temp <- c(pupiltargets[,,startindex+level],pupiltargets[,,startindex+level+5])
          cartdata <- data.frame(Re(temp),Im(temp))
          if (sum(cartdata)!=0){
            D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
            i <- which(D<SDthresh)
            cleanmeansP[cond,level] <- mean(temp[i])}

          temp <- c(pupiltargets2[,,startindex+level],pupiltargets2[,,startindex+level+5])
          cartdata <- data.frame(Re(temp),Im(temp))
          if (sum(cartdata)!=0){
            D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
            i <- which(D<SDthresh)
            cleanmeansP2[cond,level] <- mean(temp[i])}

          temp <- c(pupilmasks[,,startindex+level],pupilmasks[,,startindex+level+5])
          cartdata <- data.frame(Re(temp),Im(temp))
          if (sum(cartdata)!=0){
            D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
            i <- which(D<SDthresh)
            cleanmasksP[cond,level] <- mean(temp[i])}

          temp <- c(pupilmasks2[,,startindex+level],pupilmasks2[,,startindex+level+5])
          cartdata <- data.frame(Re(temp),Im(temp))
          if (sum(cartdata)!=0){
            D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
            i <- which(D<SDthresh)
            cleanmasksP2[cond,level] <- mean(temp[i])}
        }
    }

    meanwavesP <- apply(pupilwaveforms[,,c(15,20),],4,mean,na.rm=TRUE)
    meanspectraP <- apply(pupilspectra[,,c(15,20),],4,mean,na.rm=TRUE)
    save(file=paste(datadir,participant,'_summaryLum.RData',sep=''),list=c('cleanmeansP','cleanmasksP','cleanmeansP2','cleanmasksP2','meanspectraP','meanwavesP'))
  }

  }
```

```{r luminance group, include=FALSE, results='hide'}

# load in individual participant data and average, save group data
if (processdata > 1){

  d <- dir(datadir,pattern='summaryLum.RData', full.names = TRUE)

  tempmasksP <- array(0,dim=c(length(d),6,5))
  tempmeansP <- tempmasksP
  tempmeansP2 <- tempmasksP
  tempmasksP2 <- tempmasksP
  tempspectraP <- array(0,dim=c(length(d),300))
  tempwavesP <- array(0,dim=c(length(d),1680))

  for (s in 1:length(d)){

    load(d[s])

    tempmasksP[s,,] <- cleanmasksP
    tempmeansP[s,,] <- cleanmeansP
    tempmasksP2[s,,] <- cleanmasksP2
    tempmeansP2[s,,] <- cleanmeansP2
    tempspectraP[s,] <- meanspectraP
    tempwavesP[s,] <- meanwavesP
  }

  tempspectraP <- tempspectraP[-c(2,4,13,20,26),]

  cleanmeansP <- matrix(0,nrow=6,ncol=5)
  cleanmeansPCI <- array(0,c(2,6,5))
  cleanmasksP <- matrix(0,nrow=6,ncol=5)
  cleanmasksPCI <- array(0,c(2,6,5))
  cleanmeansP2 <- matrix(0,nrow=6,ncol=5)
  cleanmeansP2CI <- array(0,c(2,6,5))
  cleanmasksP2 <- matrix(0,nrow=6,ncol=5)
  cleanmasksP2CI <- array(0,c(2,6,5))

  for (cond in 1:6){
    for (level in 1:5){

      temp <- tempmeansP[,cond,level]
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh)
        mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
        cleanmeansP[cond,level] <- mean(temp[i])
        cleanmeansPCI[1,cond,level] <- mbs$lowerCI
        cleanmeansPCI[2,cond,level] <- mbs$upperCI
      }

      temp <- tempmasksP[,cond,level]
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh)
        mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
        cleanmasksP[cond,level] <- mean(temp[i])
        cleanmasksPCI[1,cond,level] <- mbs$lowerCI
        cleanmasksPCI[2,cond,level] <- mbs$upperCI
      }

      temp <- tempmeansP2[,cond,level]
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh)
        mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
        cleanmeansP2[cond,level] <- mean(temp[i])
        cleanmeansP2CI[1,cond,level] <- mbs$lowerCI
        cleanmeansP2CI[2,cond,level] <- mbs$upperCI
      }

      temp <- tempmasksP2[,cond,level]
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh)
        mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
        cleanmasksP2[cond,level] <- mean(temp[i])
        cleanmasksP2CI[1,cond,level] <- mbs$lowerCI
        cleanmasksP2CI[2,cond,level] <- mbs$upperCI
      }
    }
  }

  meanspectraP <- (1:300)*0
  meanspectraPCI <- array(0,c(2,300))

  for (f in 2:300){
    temp <- tempspectraP[,f]
    cartdata <- data.frame(Re(temp),Im(temp))
    if (sum(cartdata)!=0){
      D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
      i <- which(D<SDthresh) 
      mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
      meanspectraP[f] <- mbs$meanamp
      meanspectraPCI[1,f] <- mbs$lowerCI
      meanspectraPCI[2,f] <- mbs$upperCI
    }
  }

  meanwavesP <- NULL
  meanwavesPCI <- array(0,dim=c(2,dim(tempwavesP)[2]))

  nsubjs <- dim(tempwavesP)[1]
  for (t in 1:dim(tempwavesP)[2]){
    temp <- tempwavesP[,t]
    i <- which(abs(temp-mean(temp))<(SDthresh*sd(temp)))
    meanwavesP[t] <- mean(temp[i])
    bspop <- NULL
    for (s in 1:nbootstraps){bspop[s] <- mean(sample(temp[i],length(i),replace=TRUE))}
    meanwavesPCI[,t] <- quantile(bspop,c(0.16,0.84),na.rm=TRUE)
  }

  save(file=paste0(datadir,'AveragedataLum.RData'),list=c('meanwavesP','meanwavesPCI','cleanmeansP','cleanmeansPCI','cleanmasksP','cleanmasksPCI','cleanmeansP2','cleanmeansP2CI','cleanmasksP2','cleanmasksP2CI','meanspectraP','meanspectraPCI','tempmeansP','tempmeansP2','tempmasksP','tempmasksP2'))

  }
```

```{r luminance plot, include=FALSE, results='hide'}

load(file=paste0(datadir,'AveragedataLum.RData'))

# generate plot showing the group pupillometry data for the luminance condition
if (processdata > 0){

allPLumratios <- abs(cleanmeansP[2,])/abs(cleanmeansP[1,])
allPLum2ratios <- abs(cleanmeansP2[2,])/abs(cleanmeansP2[1,])

# plot figure  
plotlims <- c(15,40,0,3)  
ticklocsx <- contrastsdB
ticklabelsx <-c(6,12,24,48,96) 
ticklocsy <- seq(0,3,0.5)    # locations of tick marks on y axis
ticklabelsy <- ticklocsy

postscript("SumLum.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx)     
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  
title(ylab="Bin:Mon ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)

lines(contrastsdB,allPLumratios, col=colpal[1], lwd=3, cex=0.5)
lines(contrastsdB,allPLum2ratios, col=colpal[2], lwd=3, cex=0.5)
points(contrastsdB,allPLumratios, pch = 21, col='black', bg=colpal[1], cex=1.6, lwd=3)
points(contrastsdB,allPLum2ratios, pch = 22, col='black', bg=colpal[2], cex=1.6, lwd=3)

legend(contrastsdB[4],3,c('Lum 1F','Lum 2F'), pch=21:24, pt.bg=colpal[1:2],box.lwd=2,pt.cex=1.6,pt.lwd=3)
text(17,2.8,'(c)',adj=0.5,cex=2.5)

dev.off()

plotlims <- c(15,40,0,0.15)
plotlims2 <- c(15,40,0,0.015) 
ticklocsx <- contrastsdB    # locations of tick marks on x axis
ticklocsy <- seq(0,0.15,0.05)
ticklocsy2 <- seq(0,0.015,0.005)    # locations of tick marks on y axis
ticklabelsx <-c(6,12,24,48,96)        # set labels for x ticks
ticklabelsy <- ticklocsy
ticklabelsy2 <- ticklocsy2     # set labels for y ticks

postscript("CRF1p.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
title(ylab="Amplitude at 0.5Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)

for (cond in 1:3){
  lines(contrastsdB,abs(cleanmeansP[cond,]), col=colpal[cond], lwd=3, cex=0.5)
  arrows(contrastsdB,abs(cleanmeansP[cond,]),contrastsdB,cleanmeansPCI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
  arrows(contrastsdB,abs(cleanmeansP[cond,]),contrastsdB,cleanmeansPCI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
  points(contrastsdB,abs(cleanmeansP[cond,]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
}  
legend(22,0.15,c('Monocular','Binocular','Dichoptic'),pch=21:23,pt.bg=colpal[1:3],pt.lwd=3,pt.cex=1.6,box.lwd=2)
text(17,0.14,'(d)',adj=0.5,cex=2.5)

dev.off()

postscript("CRF2p.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
title(ylab="Amplitude at 0.5Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)

condlist <- c(1,5,6)
pointlist <- c(21,24,25)
for (cond in 1:3){
  lines(contrastsdB,abs(cleanmeansP[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)  
  arrows(contrastsdB,abs(cleanmeansP[condlist[cond],]),contrastsdB,cleanmeansPCI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
  arrows(contrastsdB,abs(cleanmeansP[condlist[cond],]),contrastsdB,cleanmeansPCI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)  
  points(contrastsdB,abs(cleanmeansP[condlist[cond],]), pch = pointlist[cond], col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
}  
legend(22,0.15,c('Monocular','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[condlist],pt.lwd=3,pt.cex=1.6,box.lwd=2)
text(17,0.14,'(e)',adj=0.5,cex=2.5)

dev.off()

postscript("CRF3p.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
title(ylab="Amplitude at 0.4Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)

for (cond in 4:6){
  lines(contrastsdB,abs(cleanmasksP[cond,]), col=colpal[cond], lwd=3, cex=0.5)   
  arrows(contrastsdB,abs(cleanmasksP[cond,]),contrastsdB,cleanmasksPCI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
  arrows(contrastsdB,abs(cleanmasksP[cond,]),contrastsdB,cleanmasksPCI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)    
  points(contrastsdB,abs(cleanmasksP[cond,]), pch = pointlist[cond-3], col='black', bg=colpal[cond], cex=1.6, lwd=3) 
}
legend(22,0.15,c('Monocular 0.4Hz','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[4:6],pt.lwd=3,pt.cex=1.6,box.lwd=2)
text(17,0.14,'(f)',adj=0.5,cex=2.5)

dev.off()

postscript("CRF1p2.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims2[3:4])   # create an empty axis of the correct dimensions
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy2, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
mtext(text = ticklabelsy2, side = 2, at=ticklocsy2, line=0.2, las=1) 
title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
title(ylab="Amplitude at 1Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)

for (cond in 1:3){
  lines(contrastsdB,abs(cleanmeansP2[cond,]), col=colpal[cond], lwd=3, cex=0.5)
  arrows(contrastsdB,abs(cleanmeansP2[cond,]),contrastsdB,cleanmeansP2CI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
  arrows(contrastsdB,abs(cleanmeansP2[cond,]),contrastsdB,cleanmeansP2CI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
  points(contrastsdB,abs(cleanmeansP2[cond,]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
}  
legend(22,0.015,c('Monocular','Binocular','Dichoptic'),pch=21:23,pt.bg=colpal[1:3],pt.lwd=3,pt.cex=1.6,box.lwd=2)
text(17,0.014,'(g)',adj=0.5,cex=2.5)

dev.off()

postscript("CRF2p2.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims2[3:4])   # create an empty axis of the correct dimensions
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy2, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
mtext(text = ticklabelsy2, side = 2, at=ticklocsy2, line=0.2, las=1)
title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
title(ylab="Amplitude at 1Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)

condlist <- c(1,5,6)
pointlist <- c(21,24,25)
for (cond in 1:3){
  lines(contrastsdB,abs(cleanmeansP2[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)  
  arrows(contrastsdB,abs(cleanmeansP2[condlist[cond],]),contrastsdB,cleanmeansP2CI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
  arrows(contrastsdB,abs(cleanmeansP2[condlist[cond],]),contrastsdB,cleanmeansP2CI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)  
  points(contrastsdB,abs(cleanmeansP2[condlist[cond],]), pch = pointlist[cond], col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
}  
legend(22,0.015,c('Monocular','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[condlist],pt.lwd=3,pt.cex=1.6,box.lwd=2)
text(17,0.014,'(h)',adj=0.5,cex=2.5)

dev.off()

postscript("CRF3p2.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims2[3:4])   # create an empty axis of the correct dimensions
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy2, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
mtext(text = ticklabelsy2, side = 2, at=ticklocsy2, line=0.2, las=1)
title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
title(ylab="Amplitude at 0.8Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)

for (cond in 4:6){
  lines(contrastsdB,abs(cleanmasksP2[cond,]), col=colpal[cond], lwd=3, cex=0.5)   
  arrows(contrastsdB,abs(cleanmasksP2[cond,]),contrastsdB,cleanmasksP2CI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
  arrows(contrastsdB,abs(cleanmasksP2[cond,]),contrastsdB,cleanmasksP2CI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)    
  points(contrastsdB,abs(cleanmasksP2[cond,]), pch = pointlist[cond-3], col='black', bg=colpal[cond], cex=1.6, lwd=3) 
}
legend(22,0.015,c('Monocular 0.4Hz','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[4:6],pt.lwd=3,pt.cex=1.6,box.lwd=2)
text(17,0.014,'(i)',adj=0.5,cex=2.5)

dev.off()

postscript("SpecP.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 8)

frequencies <- (0:299)/10

plotlims <- c(0,2,0,0.15) 
ticklocsx <- seq(0,2,0.25)    # locations of tick marks on x axis
ticklocsy <- seq(0,0.15,0.05)    # locations of tick marks on y axis
ticklabelsx <-ticklocsx        # set labels for x ticks
ticklabelsy <- ticklocsy    # set labels for y ticks

plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
title(xlab="Frequency (Hz)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  
title(ylab="Amplitude (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)

polygon(frequencies[c(3:21,21:3)],c(meanspectraPCI[1,3:21],meanspectraPCI[2,21:3]),col=colpal[2],border=NA)

lines(frequencies[3:21],abs(meanspectraP[3:21]), col=colpal[2], lwd=3, cex=0.5)

text(0.1,0.14,'(a)',adj=0.5,cex=2.5)

dev.off()

postscript("timecourseP.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 8)

times <- seq((1/120)-1,13,1/120)
sinewave <- sin(0.5*times * 2*pi)
sinewave[1:120] <- 0
sinewave[1560:1680] <- 0

plotlims <- c(-1,13,-1,0.5)
ticklocsx <- seq(-1,13,1)    # locations of tick marks on x axis
ticklocsy <- seq(-1,0.5,0.5)    # locations of tick marks on y axis
ticklabelsx <- ticklocsx        # set labels for x ticks
ticklabelsy <- ticklocsy    # set labels for y ticks

plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)
title(ylab="Amplitude (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)

filt <- butter(3,0.083)
filtwaveP <- signal::filter(filt, meanwavesP)
filtU <- signal::filter(filt,meanwavesPCI[1,])
filtL <- signal::filter(filt,meanwavesPCI[2,])
polygon(times[c(1:length(times),length(times):1)],c(filtL,filtU[length(filtU):1]),col=colpal[2],border=NA)
lines(times, filtwaveP, col=colpal[2], lwd=1.5)
lines(times, (sinewave/10)-0.9, col='black', lwd=3)

text(-0.7,0.4,'(b)',adj=0.5,cex=2.5)

dev.off()

PostScriptTrace('CRF1p.ps')
p1 <- readPicture('CRF1p.ps.xml')
PostScriptTrace('CRF2p.ps')
p2 <- readPicture('CRF2p.ps.xml')
PostScriptTrace('CRF3p.ps')
p3 <- readPicture('CRF3p.ps.xml')
PostScriptTrace('CRF1p2.ps')
p4 <- readPicture('CRF1p2.ps.xml')
PostScriptTrace('CRF2p2.ps')
p5 <- readPicture('CRF2p2.ps.xml')
PostScriptTrace('CRF3p2.ps')
p6 <- readPicture('CRF3p2.ps.xml')
PostScriptTrace('SpecP.ps')
p7 <- readPicture('SpecP.ps.xml')
PostScriptTrace('timecourseP.ps')
p8 <- readPicture('timecourseP.ps.xml')
PostScriptTrace('SumLum.ps')
p9 <- readPicture('SumLum.ps.xml')

for (n in 1:length(p7@paths)){
  temp <- class(p7@paths[n]$path)[1]
  if (pmatch(temp,"PictureFill",nomatch=0)){
    if (sum(col2rgb(p7@paths[n]$path@rgb))<765){p7@paths[n]$path@rgb <- addalpha(p7@paths[n]$path@rgb,alpha=0.2)}}}

for (n in 1:length(p8@paths)){
  temp <- class(p8@paths[n]$path)[1]
  if (pmatch(temp,"PictureFill",nomatch=0)){
    if (sum(col2rgb(p8@paths[n]$path@rgb))<765){p8@paths[n]$path@rgb <- addalpha(p8@paths[n]$path@rgb,alpha=0.2)}}}

pdf(paste0(figdir,"pupildataLum.pdf"), bg="transparent", height = 20, width = 15)

par(mar=c(0.1,0.1,0.1,0.1))
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(0,1), ylim=c(0,1))

grid.picture(p1,x=0.17,y=0.4,width=0.32,height=1)
grid.picture(p2,x=0.5,y=0.4,width=0.32,height=1)
grid.picture(p3,x=0.83,y=0.4,width=0.32,height=1)
grid.picture(p4,x=0.17,y=0.15,width=0.32,height=1)
grid.picture(p5,x=0.5,y=0.15,width=0.32,height=1)
grid.picture(p6,x=0.83,y=0.15,width=0.32,height=1)
grid.picture(p7,x=0.25,y=0.83,width=0.5,height=1)
grid.picture(p8,x=0.25,y=0.63,width=0.5,height=1)
grid.picture(p9,x=0.75,y=0.71,width=0.5,height=1)

text(0.5,0.98,'Luminance',cex=4)

dev.off()

file.remove(c('CRF1p.ps','CRF2p.ps','CRF3p.ps','CRF1p2.ps','CRF2p2.ps','CRF3p2.ps','SpecP.ps','timecourseP.ps','SumLum.ps'))
file.remove(c('CRF1p.ps.xml','CRF2p.ps.xml','CRF3p.ps.xml','CRF1p2.ps.xml','CRF2p2.ps.xml','CRF3p2.ps.xml','SpecP.ps.xml','timecourseP.ps.xml','SumLum.ps.xml'))

  }
```

```{r luminance statistics, include=FALSE, results='hide'}

# do statistics on the luminance data
alldata <- NULL
groupID <- NULL
allP <- NULL
counter <- 0
for (cont in 1:dim(tempmeansP)[3]){
  for (p in 1:dim(tempmeansP)[1]){
    counter <- counter + 1
    alldata[counter] <- tempmeansP[p,3,cont]
    groupID[counter] <- cont
    allP[counter] <- p
  }
}

# stats for the dichoptic (green line) condition (fig. 1c)
dichA2c <- anovacirc.test(alldata,group=groupID,participant=allP)

alldata <- NULL
allgroupA <- NULL
allgroupB <- NULL
allP <- NULL
counter <- 0
for (p in 1:12){
  for (lev in 1:5){
    for (cond in 1:2){
    counter <- counter + 1
    alldata[counter] <- tempmeansP[p,cond,lev]
    allgroupA[counter] <- lev
    allgroupB[counter] <- cond
    allP[counter] <- p
    }
  }
}

# stats for the mon and bin conditions (fig. 1c)
monbinPstats <- anovacirc2way(alldata,allgroupA,allgroupB,allP)

alldata <- NULL
allgroupA <- NULL
allgroupB <- NULL
allP <- NULL
counter <- 0
for (p in 1:12){
  for (lev in 1:5){
    counter <- counter + 1
    alldata[counter] <- tempmeansP[p,1,lev]
    allgroupA[counter] <- lev
    allgroupB[counter] <- 1
    allP[counter] <- p

    counter <- counter + 1
    alldata[counter] <- tempmeansP[p,3,lev]
    allgroupA[counter] <- lev
    allgroupB[counter] <- 2
    allP[counter] <- p
  }
}

# stats for the mon and dich conditions (fig. 1c)
mondichPstats <- anovacirc2way(alldata,allgroupA,allgroupB,allP)

alldata <- NULL
allgroupA <- NULL
allgroupB <- NULL
allP <- NULL
counter <- 0
for (p in 1:12){
  for (lev in 1:5){
    counter <- counter + 1
    alldata[counter] <- tempmeansP[p,1,lev]
    allgroupA[counter] <- lev
    allgroupB[counter] <- 1
    allP[counter] <- p

    counter <- counter + 1
    alldata[counter] <- tempmeansP[p,5,lev]
    allgroupA[counter] <- lev
    allgroupB[counter] <- 2
    allP[counter] <- p
  }
}

# stats for the mon and binX conditions (fig. 1d)
monbinPstatsX <- anovacirc2way(alldata,allgroupA,allgroupB,allP)

alldata <- NULL
allgroupA <- NULL
allgroupB <- NULL
allP <- NULL
counter <- 0
for (p in 1:12){
  for (lev in 1:5){
    counter <- counter + 1
    alldata[counter] <- tempmeansP[p,1,lev]
    allgroupA[counter] <- lev
    allgroupB[counter] <- 1
    allP[counter] <- p

    counter <- counter + 1
    alldata[counter] <- tempmeansP[p,6,lev]
    allgroupA[counter] <- lev
    allgroupB[counter] <- 2
    allP[counter] <- p
  }
}

# stats for the mon and dichX conditions (fig. 1d)
mondichPstatsX <- anovacirc2way(alldata,allgroupA,allgroupB,allP)

```

The results of the luminance experiment are summarised in Figure \@ref(fig:pupildataLum). The average Fourier spectrum is displayed in Figure \@ref(fig:pupildataLum)a, and shows a strong response at the first harmonic frequency (0.5 Hz) and a weaker but still clear response at the second harmonic frequency (1 Hz). These results demonstrate that we can evoke measurable steady-state pupil responses at 0.5 Hz by stimulating the periphery of the retina. The group average waveform for binocular presentation is shown in Figure \@ref(fig:pupildataLum)b. There is a substantial pupil constriction at stimulus onset, followed by very visible oscillations at the flicker frequency (0.5 Hz, see waveform at foot).

Figure \@ref(fig:pupildataLum)d shows contrast response functions in response to stimuli flickering only at 0.5 Hz. The amplitude of the binocular condition (blue squares) is consistently greater than that of the monocular condition (red circles) across all target contrasts. A $2\times5$ repeated measures $ANOVA^2_{circ}$ [@Baker2021] comparing these conditions revealed a significant main effect of target contrast (F(`r monbinPstats$dfA`,`r monbinPstats$dfR`) = `r round(monbinPstats$FratioA,digits=2)`, $p$ < 0.001), a significant effect of condition (F(`r monbinPstats$dfB`,`r monbinPstats$dfR`) = `r round(monbinPstats$FratioB,digits=2)`, $p$ < 0.001), and a significant interaction (F(`r monbinPstats$dfAB`,`r monbinPstats$dfR`) = `r round(monbinPstats$FratioAB,digits=2)`, $p$ < 0.001). The dichoptic condition (green diamonds) begins at a much higher amplitude, owing to binocular combination of the target and high (48%) contrast mask, and then increases with increasing target contrast (main effect of target contrast: F(`r dichA2c$dfM`,`r dichA2c$dfR`) = `r round(dichA2c$Fratio,digits=2)`, $p$ < 0.001). Similar results can be observed at the second harmonic in Figure \@ref(fig:pupildataLum)g (see Tables \@ref(tab:TableStatsFig3g) and \@ref(tab:TableStatsMonDichFig3g) for summary of statistical results).

In Figure \@ref(fig:pupildataLum)e, we plot responses to monocular target stimuli flickering at 0.5 Hz, when the other eye viewed stimuli flickering at 0.4 Hz (the red monocular-only data are replotted from Figure \@ref(fig:pupildataLum)d for comparison). When the 0.4 Hz component had the same contrast as the target (the binocular cross condition, shown in purple) responses were suppressed slightly across all target contrasts (interaction between contrast and condition: F(`r monbinPstatsX$dfAB`,`r monbinPstatsX$dfR`) = `r round(monbinPstatsX$FratioAB,digits=2)`, $p$ < 0.001). When the 0.4 Hz component had a fixed contrast of 48 % (the dichoptic cross condition, shown in yellow), responses were also suppressed slightly across the contrast range (interaction between contrast and condition: F(`r mondichPstatsX$dfAB`,`r mondichPstatsX$dfR`) = `r round(mondichPstatsX$FratioAB,digits=2)`, $p$ < 0.001). The same pattern of results was generally observed at the second harmonic (Figure \@ref(fig:pupildataLum)h, see Tables \@ref(tab:TableStatsMonBinXFig3h) and \@ref(tab:TableStatsMonDichXFig3h) for summary of statistical results).

```{r pupildataLum, fig.cap="Summary of pupillometry results for the luminance experiment for N=12 participants. Panel (a) shows the average Fourier spectrum. Panel (b) shows a group average waveform for binocular presentation (low pass filtered at 5 Hz), with the driving signal plotted at the foot. Panel (c) shows the ratio of binocular to monocular response. The red circles show the ratios at the first harmonic (0.5 Hz) and the blue squares show the ratios at the second harmonic (1 Hz). Panels (d,e) show contrast response functions at 0.5 Hz for different conditions. Panel (f) shows contrast response functions at 0.4 Hz for three conditions. Panels (g-i) are in the same format but for the second harmonic responses. Shaded regions and error bars indicate bootstrapped standard errors.", fig.align="center", out.width = '85%', echo=FALSE}

knitr::include_graphics(paste0(figdir,'pupildataLum.pdf'))
```

Figure \@ref(fig:pupildataLum)f shows responses at 0.4 Hz, for the same conditions, as well as for a condition in which a monocular stimulus flickered at 0.4 Hz (grey circles). Again there was evidence of weak suppression between the eyes, as the purple triangles fall below the grey circles (see Table \@ref(tab:TableStatsMonXBinXFig3f) for summary of statistical results). The dichoptic cross condition also shows evidence of suppressive modulation with target contrast (see Table \@ref(tab:TableStatsMonXDichXFig3f) for summary of statistical results). The same pattern is also observed at the second harmonic (Figure \@ref(fig:pupildataLum)i, see Tables \@ref(tab:TableStatsMonXBinXFig3i) and \@ref(tab:TableStatsMonXDichXFig3i) for summary of statistical results).

Finally, we calculated the binocular to monocular ratio at the first and second harmonic frequencies. Figure \@ref(fig:pupildataLum)c shows that these ratios are generally below 2 at both frequencies, suggesting that there is summation happening between the eyes but also interocular suppression, therefore suggesting that the signals between the eyes are combined non-linearly. At the highest contrast at the second harmonic, the ratio is close to 2, perhaps indicating that a more linear combination is happening for higher contrasts.

## Experiment 2

```{r melanopsin individual, include=FALSE, results='hide'}

# (download and) analyse individual participant data for the melanopsin condition
if (processdata > 2){

  for(p in 501:512){
    participant <- paste0('P',p)

    tic()

    pupiltargets <- array(0,dim=c(3,2,60))
    pupilmasks <- pupiltargets
    pupiltargets2 <- pupiltargets
    pupilmasks2 <- pupiltargets
    pupilwaveforms <- array(0,dim=c(3,2,60,120*14))
    pupilspectra <- array(0,dim=c(3,2,60,300))
    timeseq <- seq(1/120,10,length.out=120*10)
    timeseq2 <- seq(1/120,14,length.out=120*14)
    targetindex <- (0.5*10)+1
    maskindex <- (0.4*10)+1
    targetindex2 <- (0.5*2*10)+1
    maskindex2 <- (2*0.4*10)+1

    repcounterP <- (1:60)*0
    d <- dir(paste0(rawdir,participant),pattern='*annotations.csv',full.names=TRUE)

    for (block in 1:length(d)){
        tic()
        adata <- read.csv(paste0(rawdir,participant,'/',paste0(participant,'_S',block),'_annotations.csv'))

        trialtimes <- NULL
        trialtypes <- NULL
        for (t in 1:(nrow(adata)/2)){
          trialtimes[t] <- mean(adata$timestamp[(t*2 - 1):(t*2)])
          trialtypes[t] <- adata$condition_code[t*2]
        }

        trialtypes[which(trialtypes>15)] <- trialtypes[which(trialtypes>15)] + 5
        inclist <- NULL
        for (t in 11:15){
          i <- which(trialtypes==t)
          inclist[t-10] <- i[2]
        }
        inclist <- inclist[which(!is.na(inclist))]
        trialtypes[inclist] <- trialtypes[inclist] + 5

        pdata <- read.csv(paste(rawdir,participant,'/',paste0(participant,'_S',block),'_pupil_positions.csv',sep=''))
        pdata2 <- pdata[,c(1,3,4,14)]
        pdata2 <- pdata2[which(pdata2[,3]>0.2),]

        for (trialno in 1:length(trialtypes)){
          repcounterP[trialtypes[trialno]] <- repcounterP[trialtypes[trialno]] + 1
          for (eye in 1:2){
            eyedata <- pdata2[which(pdata2[,2]==(2-eye)),]      
            a <- which(eyedata[,1]>trialtimes[trialno]+2)
            b <- which(eyedata[,1]<(trialtimes[trialno]+12))
            i <- intersect(a,b)
            trial <- eyedata[i,]
            trial <- trial[which(!is.na(trial[,4])),]
            trial[,1] <- trial[,1] - trial[1,1]
            if (nrow(trial)>3){
              resampled <- interp1(trial[,1],trial[,4],timeseq,method='linear',extrap=TRUE)
              fspec <- (fft(resampled)/length(resampled))
              pupiltargets[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno]] <- fspec[targetindex]
              pupilmasks[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno]] <- fspec[maskindex]
              pupiltargets2[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno]] <- fspec[targetindex2]
              pupilmasks2[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno]] <- fspec[maskindex2]
              pupilspectra[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno],1:300] <- fspec[1:300]
            }

            a <- which(eyedata[,1]>(trialtimes[trialno]-1))
            b <- which(eyedata[,1]<(trialtimes[trialno]+13))
            i <- intersect(a,b)
            trial <- eyedata[i,]
            trial[,1] <- trial[,1] - trial[1,1]
            if (nrow(trial)>3){
              trial <- trial[which(!is.na(trial[,4])),]
              resampled <- interp1(trial[,1],trial[,4],timeseq2,method='linear',extrap=TRUE)
              pupilwaveforms[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno],] <- resampled - mean(resampled[1:120])
            }
          }
        }
    }

    cleanmeansP <- matrix(0,nrow=6,ncol=5)
    cleanmasksP <- matrix(0,nrow=6,ncol=5)
    cleanmeansP2 <- matrix(0,nrow=6,ncol=5)
    cleanmasksP2 <- matrix(0,nrow=6,ncol=5)

    for (cond in 1:6){
        startindex <- (10*(cond-1))
        for (level in 1:5){
          temp <- c(pupiltargets[,,startindex+level],pupiltargets[,,startindex+level+5])
          cartdata <- data.frame(Re(temp),Im(temp))
          if (sum(cartdata)!=0){
            D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
            i <- which(D<SDthresh)
            cleanmeansP[cond,level] <- mean(temp[i])}

          temp <- c(pupiltargets2[,,startindex+level],pupiltargets2[,,startindex+level+5])
          cartdata <- data.frame(Re(temp),Im(temp))
          if (sum(cartdata)!=0){
            D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
            i <- which(D<SDthresh)
            cleanmeansP2[cond,level] <- mean(temp[i])}

          temp <- c(pupilmasks[,,startindex+level],pupilmasks[,,startindex+level+5])
          cartdata <- data.frame(Re(temp),Im(temp))
          if (sum(cartdata)!=0){
            D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
            i <- which(D<SDthresh)
            cleanmasksP[cond,level] <- mean(temp[i])}

          temp <- c(pupilmasks2[,,startindex+level],pupilmasks2[,,startindex+level+5])
          cartdata <- data.frame(Re(temp),Im(temp))
          if (sum(cartdata)!=0){
            D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
            i <- which(D<SDthresh)
            cleanmasksP2[cond,level] <- mean(temp[i])}
        }
    }

    meanwavesP <- apply(pupilwaveforms[,,c(15,20),],4,mean,na.rm=TRUE)
    meanspectraP <- apply(pupilspectra[,,c(15,20),],4,mean,na.rm=TRUE)
    save(file=paste(datadir,participant,'_summaryMel.RData',sep=''),list=c('cleanmeansP','cleanmasksP','cleanmeansP2','cleanmasksP2','meanspectraP','meanwavesP'))
    }
  }
```

```{r melanopsin group, include=FALSE, results='hide'}

# load in individual participant data and average, save group data
if (processdata > 1){

  d <- dir(datadir,pattern='summaryMel.RData', full.names = TRUE)

  tempmasksP <- array(0,dim=c(length(d),6,5))
  tempmeansP <- tempmasksP
  tempmeansP2 <- tempmasksP
  tempmasksP2 <- tempmasksP
  tempspectraP <- array(0,dim=c(length(d),300))
  tempwavesP <- array(0,dim=c(length(d),1680))

  for (s in 1:length(d)){

    load(d[s])

    tempmasksP[s,,] <- cleanmasksP
    tempmeansP[s,,] <- cleanmeansP
    tempmasksP2[s,,] <- cleanmasksP2
    tempmeansP2[s,,] <- cleanmeansP2
    tempspectraP[s,] <- meanspectraP
    tempwavesP[s,] <- meanwavesP
  }

  tempspectraP <- tempspectraP[-c(2,4,13,20,26),]

  cleanmeansP <- matrix(0,nrow=6,ncol=5)
  cleanmeansPCI <- array(0,c(2,6,5))
  cleanmasksP <- matrix(0,nrow=6,ncol=5)
  cleanmasksPCI <- array(0,c(2,6,5))
  cleanmeansP2 <- matrix(0,nrow=6,ncol=5)
  cleanmeansP2CI <- array(0,c(2,6,5))
  cleanmasksP2 <- matrix(0,nrow=6,ncol=5)
  cleanmasksP2CI <- array(0,c(2,6,5))

  for (cond in 1:6){
    for (level in 1:5){

      temp <- tempmeansP[,cond,level]
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh)
        mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
        cleanmeansP[cond,level] <- mean(temp[i])
        cleanmeansPCI[1,cond,level] <- mbs$lowerCI
        cleanmeansPCI[2,cond,level] <- mbs$upperCI
      }

      temp <- tempmasksP[,cond,level]
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh)
        mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
        cleanmasksP[cond,level] <- mean(temp[i])
        cleanmasksPCI[1,cond,level] <- mbs$lowerCI
        cleanmasksPCI[2,cond,level] <- mbs$upperCI
      }

      temp <- tempmeansP2[,cond,level]
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh)
        mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
        cleanmeansP2[cond,level] <- mean(temp[i])
        cleanmeansP2CI[1,cond,level] <- mbs$lowerCI
        cleanmeansP2CI[2,cond,level] <- mbs$upperCI
      }

      temp <- tempmasksP2[,cond,level]
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh)
        mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
        cleanmasksP2[cond,level] <- mean(temp[i])
        cleanmasksP2CI[1,cond,level] <- mbs$lowerCI
        cleanmasksP2CI[2,cond,level] <- mbs$upperCI
      }
    }
  }

  meanspectraP <- (1:300)*0
  meanspectraPCI <- array(0,c(2,300))

  for (f in 2:300){
    temp <- tempspectraP[,f]
    cartdata <- data.frame(Re(temp),Im(temp))
    if (sum(cartdata)!=0){
      D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
      i <- which(D<SDthresh) 
      mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
      meanspectraP[f] <- mbs$meanamp
      meanspectraPCI[1,f] <- mbs$lowerCI
      meanspectraPCI[2,f] <- mbs$upperCI
    }
  }

  meanwavesP <- NULL
  meanwavesPCI <- array(0,dim=c(2,dim(tempwavesP)[2]))

  nsubjs <- dim(tempwavesP)[1]
  for (t in 1:dim(tempwavesP)[2]){
    temp <- tempwavesP[,t]
    i <- which(abs(temp-mean(temp))<(SDthresh*sd(temp)))
    meanwavesP[t] <- mean(temp[i])
    bspop <- NULL
    for (s in 1:nbootstraps){bspop[s] <- mean(sample(temp[i],length(i),replace=TRUE))}
    meanwavesPCI[,t] <- quantile(bspop,c(0.16,0.84),na.rm=TRUE)
  }

  save(file=paste0(datadir,'AveragedataMel.RData'),list=c('meanwavesP','meanwavesPCI','cleanmeansP','cleanmeansPCI','cleanmasksP','cleanmasksPCI','cleanmeansP2','cleanmeansP2CI','cleanmasksP2','cleanmasksP2CI','meanspectraP','meanspectraPCI','tempmeansP','tempmeansP2','tempmasksP','tempmasksP2'))

  }
```

```{r melanopsin plot, include=FALSE, results='hide'}

load(file=paste0(datadir,'AveragedataMel.RData'))

# generate plot showing the group pupillometry data for the melanopsin experiment
if (processdata > 0){

allPMelratios <- abs(cleanmeansP[2,])/abs(cleanmeansP[1,])
allPMel2ratios <- abs(cleanmeansP2[2,])/abs(cleanmeansP2[1,])

# plot figure  
plotlims <- c(15,40,0,5)  
ticklocsx <- contrastsdB
ticklabelsx <-c(6,12,24,48,96) 
ticklocsy <- seq(0,5,0.5)    # locations of tick marks on y axis
ticklabelsy <- ticklocsy

postscript("SumMel.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx)     
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
title(xlab="Target contrast (% of max)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  
title(ylab="Bin:Mon ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)

lines(contrastsdB,allPMelratios, col=colpal[1], lwd=3, cex=0.5)
lines(contrastsdB,allPMel2ratios, col=colpal[2], lwd=3, cex=0.5)
points(contrastsdB,allPMelratios, pch = 21, col='black', bg=colpal[1], cex=1.6, lwd=3)
points(contrastsdB,allPMel2ratios, pch = 22, col='black', bg=colpal[2], cex=1.6, lwd=3)

legend(contrastsdB[2],5,c('Mel 1F','Mel 2F'), pch=21:24, pt.bg=colpal[1:2],box.lwd=2,pt.cex=1.6,pt.lwd=3)
text(17,4.8,'(c)',adj=0.5,cex=2.5)

dev.off()

plotlims <- c(15,40,0,0.02)
plotlims2 <- c(15,40,0,0.015) 
ticklocsx <- contrastsdB    # locations of tick marks on x axis
ticklocsy <- seq(0,0.02,0.005)
ticklocsy2 <- seq(0,0.015,0.005)    # locations of tick marks on y axis
ticklabelsx <-c(6,12,24,48,96)        # set labels for x ticks
ticklabelsy <- ticklocsy
ticklabelsy2 <- ticklocsy2     # set labels for y ticks

postscript("CRF1p.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
title(xlab="Target contrast (% of max)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
title(ylab="Amplitude at 0.5Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)

for (cond in 1:3){
  lines(contrastsdB,abs(cleanmeansP[cond,]), col=colpal[cond], lwd=3, cex=0.5)
  arrows(contrastsdB,abs(cleanmeansP[cond,]),contrastsdB,cleanmeansPCI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
  arrows(contrastsdB,abs(cleanmeansP[cond,]),contrastsdB,cleanmeansPCI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
  points(contrastsdB,abs(cleanmeansP[cond,]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
}  
legend(22,0.02,c('Monocular','Binocular','Dichoptic'),pch=21:23,pt.bg=colpal[1:3],pt.lwd=3,pt.cex=1.6,box.lwd=2)
text(17,0.019,'(d)',adj=0.5,cex=2.5)

dev.off()

postscript("CRF2p.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Target contrast (% of max)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
title(ylab="Amplitude at 0.5Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)

condlist <- c(1,5,6)
pointlist <- c(21,24,25)
for (cond in 1:3){
  lines(contrastsdB,abs(cleanmeansP[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)  
  arrows(contrastsdB,abs(cleanmeansP[condlist[cond],]),contrastsdB,cleanmeansPCI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
  arrows(contrastsdB,abs(cleanmeansP[condlist[cond],]),contrastsdB,cleanmeansPCI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)  
  points(contrastsdB,abs(cleanmeansP[condlist[cond],]), pch = pointlist[cond], col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
}  
legend(22,0.02,c('Monocular','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[condlist],pt.lwd=3,pt.cex=1.6,box.lwd=2)
text(17,0.019,'(e)',adj=0.5,cex=2.5)

dev.off()

postscript("CRF3p.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Target contrast (% of max)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
title(ylab="Amplitude at 0.4Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)

for (cond in 4:6){
  lines(contrastsdB,abs(cleanmasksP[cond,]), col=colpal[cond], lwd=3, cex=0.5)   
  arrows(contrastsdB,abs(cleanmasksP[cond,]),contrastsdB,cleanmasksPCI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
  arrows(contrastsdB,abs(cleanmasksP[cond,]),contrastsdB,cleanmasksPCI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)    
  points(contrastsdB,abs(cleanmasksP[cond,]), pch = pointlist[cond-3], col='black', bg=colpal[cond], cex=1.6, lwd=3) 
}
legend(22,0.02,c('Monocular 0.4Hz','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[4:6],pt.lwd=3,pt.cex=1.6,box.lwd=2)
text(17,0.019,'(f)',adj=0.5,cex=2.5)

dev.off()

postscript("CRF1p2.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims2[3:4])   # create an empty axis of the correct dimensions
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy2, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
mtext(text = ticklabelsy2, side = 2, at=ticklocsy2, line=0.2, las=1) 
title(xlab="Target contrast (% of max)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
title(ylab="Amplitude at 1Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)

for (cond in 1:3){
  lines(contrastsdB,abs(cleanmeansP2[cond,]), col=colpal[cond], lwd=3, cex=0.5)
  arrows(contrastsdB,abs(cleanmeansP2[cond,]),contrastsdB,cleanmeansP2CI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
  arrows(contrastsdB,abs(cleanmeansP2[cond,]),contrastsdB,cleanmeansP2CI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
  points(contrastsdB,abs(cleanmeansP2[cond,]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
}  
legend(22,0.015,c('Monocular','Binocular','Dichoptic'),pch=21:23,pt.bg=colpal[1:3],pt.lwd=3,pt.cex=1.6,box.lwd=2)
text(17,0.014,'(g)',adj=0.5,cex=2.5)

dev.off()

postscript("CRF2p2.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims2[3:4])   # create an empty axis of the correct dimensions
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy2, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
mtext(text = ticklabelsy2, side = 2, at=ticklocsy2, line=0.2, las=1)
title(xlab="Target contrast (% of max)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
title(ylab="Amplitude at 1Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)

condlist <- c(1,5,6)
pointlist <- c(21,24,25)
for (cond in 1:3){
  lines(contrastsdB,abs(cleanmeansP2[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)  
  arrows(contrastsdB,abs(cleanmeansP2[condlist[cond],]),contrastsdB,cleanmeansP2CI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
  arrows(contrastsdB,abs(cleanmeansP2[condlist[cond],]),contrastsdB,cleanmeansP2CI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)  
  points(contrastsdB,abs(cleanmeansP2[condlist[cond],]), pch = pointlist[cond], col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
}  
legend(22,0.015,c('Monocular','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[condlist],pt.lwd=3,pt.cex=1.6,box.lwd=2)
text(17,0.014,'(h)',adj=0.5,cex=2.5)

dev.off()

postscript("CRF3p2.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims2[3:4])   # create an empty axis of the correct dimensions
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy2, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
mtext(text = ticklabelsy2, side = 2, at=ticklocsy2, line=0.2, las=1)
title(xlab="Target contrast (% of max)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
title(ylab="Amplitude at 0.8Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)

for (cond in 4:6){
  lines(contrastsdB,abs(cleanmasksP2[cond,]), col=colpal[cond], lwd=3, cex=0.5)   
  arrows(contrastsdB,abs(cleanmasksP2[cond,]),contrastsdB,cleanmasksP2CI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
  arrows(contrastsdB,abs(cleanmasksP2[cond,]),contrastsdB,cleanmasksP2CI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)    
  points(contrastsdB,abs(cleanmasksP2[cond,]), pch = pointlist[cond-3], col='black', bg=colpal[cond], cex=1.6, lwd=3) 
}
legend(22,0.015,c('Monocular 0.4Hz','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[4:6],pt.lwd=3,pt.cex=1.6,box.lwd=2)
text(17,0.014,'(i)',adj=0.5,cex=2.5)

dev.off()

postscript("SpecP.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 8)

frequencies <- (0:299)/10

plotlims <- c(0,2,0,0.015) 
ticklocsx <- seq(0,2,0.25)    # locations of tick marks on x axis
ticklocsy <- seq(0,0.015,0.005)    # locations of tick marks on y axis
ticklabelsx <-ticklocsx        # set labels for x ticks
ticklabelsy <- ticklocsy    # set labels for y ticks

plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
title(xlab="Frequency (Hz)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  
title(ylab="Amplitude (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)

polygon(frequencies[c(3:21,21:3)],c(meanspectraPCI[1,3:21],meanspectraPCI[2,21:3]),col=colpal[2],border=NA)

lines(frequencies[3:21],abs(meanspectraP[3:21]), col=colpal[2], lwd=3, cex=0.5)

text(0.1,0.014,'(a)',adj=0.5,cex=2.5)

dev.off()

postscript("timecourseP.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 8)

times <- seq((1/120)-1,13,1/120)
sinewave <- sin(0.5*times * 2*pi)
sinewave[1:120] <- 0
sinewave[1560:1680] <- 0

plotlims <- c(-1,13,-0.5,0.5)
ticklocsx <- seq(-1,13,1)    # locations of tick marks on x axis
ticklocsy <- seq(-0.5,0.5,0.5)    # locations of tick marks on y axis
ticklabelsx <- ticklocsx        # set labels for x ticks
ticklabelsy <- ticklocsy    # set labels for y ticks

plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)
title(ylab="Amplitude (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)

filt <- butter(3,0.083)
filtwaveP <- signal::filter(filt, meanwavesP)
filtU <- signal::filter(filt,meanwavesPCI[1,])
filtL <- signal::filter(filt,meanwavesPCI[2,])
polygon(times[c(1:length(times),length(times):1)],c(filtL,filtU[length(filtU):1]),col=colpal[2],border=NA)
lines(times, filtwaveP, col=colpal[2], lwd=1.5)
lines(times, (sinewave/10)-0.4, col='black', lwd=3)

text(-0.7,0.4,'(b)',adj=0.5,cex=2.5)

dev.off()

PostScriptTrace('CRF1p.ps')
p1 <- readPicture('CRF1p.ps.xml')
PostScriptTrace('CRF2p.ps')
p2 <- readPicture('CRF2p.ps.xml')
PostScriptTrace('CRF3p.ps')
p3 <- readPicture('CRF3p.ps.xml')
PostScriptTrace('CRF1p2.ps')
p4 <- readPicture('CRF1p2.ps.xml')
PostScriptTrace('CRF2p2.ps')
p5 <- readPicture('CRF2p2.ps.xml')
PostScriptTrace('CRF3p2.ps')
p6 <- readPicture('CRF3p2.ps.xml')
PostScriptTrace('SpecP.ps')
p7 <- readPicture('SpecP.ps.xml')
PostScriptTrace('timecourseP.ps')
p8 <- readPicture('timecourseP.ps.xml')
PostScriptTrace('SumMel.ps')
p9 <- readPicture('SumMel.ps.xml')

for (n in 1:length(p7@paths)){
  temp <- class(p7@paths[n]$path)[1]
  if (pmatch(temp,"PictureFill",nomatch=0)){
    if (sum(col2rgb(p7@paths[n]$path@rgb))<765){p7@paths[n]$path@rgb <- addalpha(p7@paths[n]$path@rgb,alpha=0.2)}}}

for (n in 1:length(p8@paths)){
  temp <- class(p8@paths[n]$path)[1]
  if (pmatch(temp,"PictureFill",nomatch=0)){
    if (sum(col2rgb(p8@paths[n]$path@rgb))<765){p8@paths[n]$path@rgb <- addalpha(p8@paths[n]$path@rgb,alpha=0.2)}}}

pdf(paste0(figdir,"pupildataMel.pdf"), bg="transparent", height = 20, width = 15)

par(mar=c(0.1,0.1,0.1,0.1))
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(0,1), ylim=c(0,1))

grid.picture(p1,x=0.17,y=0.4,width=0.32,height=1)
grid.picture(p2,x=0.5,y=0.4,width=0.32,height=1)
grid.picture(p3,x=0.83,y=0.4,width=0.32,height=1)
grid.picture(p4,x=0.17,y=0.15,width=0.32,height=1)
grid.picture(p5,x=0.5,y=0.15,width=0.32,height=1)
grid.picture(p6,x=0.83,y=0.15,width=0.32,height=1)
grid.picture(p7,x=0.25,y=0.85,width=0.5,height=1)
grid.picture(p8,x=0.25,y=0.63,width=0.5,height=1)
grid.picture(p9,x=0.75,y=0.73,width=0.5,height=1)

text(0.5,0.98,'Melanopsin',cex=4)

dev.off()

file.remove(c('CRF1p.ps','CRF2p.ps','CRF3p.ps','CRF1p2.ps','CRF2p2.ps','CRF3p2.ps','SpecP.ps','timecourseP.ps','SumMel.ps'))
file.remove(c('CRF1p.ps.xml','CRF2p.ps.xml','CRF3p.ps.xml','CRF1p2.ps.xml','CRF2p2.ps.xml','CRF3p2.ps.xml','SpecP.ps.xml','timecourseP.ps.xml','SumMel.ps.xml'))

  }
```

```{r melanopsin statistics, include=FALSE, results='hide'}

# do statistics on the melanopsin data
alldata <- NULL
groupID <- NULL
allP <- NULL
counter <- 0
for (cont in 1:dim(tempmeansP)[3]){
  for (p in 1:dim(tempmeansP)[1]){
    counter <- counter + 1
    alldata[counter] <- tempmeansP[p,3,cont]
    groupID[counter] <- cont
    allP[counter] <- p
  }
}
dichA2c <- anovacirc.test(alldata,group=groupID,participant=allP)

alldata <- NULL
allgroupA <- NULL
allgroupB <- NULL
allP <- NULL
counter <- 0
for (p in 1:12){
  for (lev in 1:5){
    for (cond in 1:2){
    counter <- counter + 1
    alldata[counter] <- tempmeansP[p,cond,lev]
    allgroupA[counter] <- lev
    allgroupB[counter] <- cond
    allP[counter] <- p
    }
  }
}
monbinPstats <- anovacirc2way(alldata,allgroupA,allgroupB,allP)

alldata <- NULL
allgroupA <- NULL
allgroupB <- NULL
allP <- NULL
counter <- 0
for (p in 1:12){
  for (lev in 1:5){
    counter <- counter + 1
    alldata[counter] <- tempmeansP[p,1,lev]
    allgroupA[counter] <- lev
    allgroupB[counter] <- 1
    allP[counter] <- p

    counter <- counter + 1
    alldata[counter] <- tempmeansP[p,3,lev]
    allgroupA[counter] <- lev
    allgroupB[counter] <- 2
    allP[counter] <- p
  }
}

mondichPstats <- anovacirc2way(alldata,allgroupA,allgroupB,allP)

alldata <- NULL
allgroupA <- NULL
allgroupB <- NULL
allP <- NULL
counter <- 0
for (p in 1:12){
  for (lev in 1:5){
    counter <- counter + 1
    alldata[counter] <- tempmeansP[p,1,lev]
    allgroupA[counter] <- lev
    allgroupB[counter] <- 1
    allP[counter] <- p

    counter <- counter + 1
    alldata[counter] <- tempmeansP[p,5,lev]
    allgroupA[counter] <- lev
    allgroupB[counter] <- 2
    allP[counter] <- p
  }
}

monbinPstatsX <- anovacirc2way(alldata,allgroupA,allgroupB,allP)

alldata <- NULL
allgroupA <- NULL
allgroupB <- NULL
allP <- NULL
counter <- 0
for (p in 1:12){
  for (lev in 1:5){
    counter <- counter + 1
    alldata[counter] <- tempmeansP[p,1,lev]
    allgroupA[counter] <- lev
    allgroupB[counter] <- 1
    allP[counter] <- p

    counter <- counter + 1
    alldata[counter] <- tempmeansP[p,6,lev]
    allgroupA[counter] <- lev
    allgroupB[counter] <- 2
    allP[counter] <- p
  }
}

mondichPstatsX <- anovacirc2way(alldata,allgroupA,allgroupB,allP)

```

The results of the melanopsin experiment are summarised in Figure \@ref(fig:pupildataMel). The average Fourier spectrum is displayed in Figure \@ref(fig:pupildataMel)a, and also shows clear responses at both the first harmonic frequency (0.5 Hz) and the second harmonic frequency (1 Hz) of approximately equal amplitude. These results demonstrate that we can evoke measurable steady-state pupil responses at 0.5 Hz by selectively stimulating the melanopsin-containing retinal ganglion cells whilst ignoring rods and nominally silencing all three cone classes. The group average waveform for binocular presentation is shown in Figure \@ref(fig:pupildataMel)b and shows a substantial pupil constriction at stimulus onset, followed by visible oscillations at approximately the flicker frequency (0.5 Hz, see waveform at foot).

Figure \@ref(fig:pupildataMel)d shows contrast response functions for melanopsin-directed stimuli flickering at 0.5 Hz. The amplitude of the binocular condition (blue squares) is similar to that of the monocular condition (red circles) across all target contrasts (all error bars overlap, see Table \@ref(tab:TableStatsFig4d) for summary of statistical results). At the second harmonic the binocular response is substantially greater than the monocular response at higher contrasts where the response is above baseline (Figure \@ref(fig:pupildataMel)g, see Table \@ref(tab:TableStatsFig4g) for summary of statistical results).

```{r pupildataMel, fig.cap="Summary of pupillometry results for the melanopsin experiment for N=12 participants. Panel (a) shows the average Fourier spectrum. Panel (b) shows a group average waveform for binocular presentation (low pass filtered at 5 Hz), with the driving signal plotted at the foot. Panel (c) shows the ratio of binocular to monocular response. The red circles show the ratios at the first harmonic (0.5 Hz) and the blue squares show the ratios at the second harmonic (1 Hz). Panels (d,e) show contrast response functions at 0.5 Hz for different conditions. Panel (f) shows contrast response functions at 0.4 Hz for three conditions. Panels (g-i) are in the same format but for the second harmonic responses. Shaded regions and error bars indicate bootstrapped standard errors.", fig.align="center", out.width = '85%', echo=FALSE}

knitr::include_graphics(paste0(figdir,'pupildataMel.pdf'))
```

In Figure \@ref(fig:pupildataMel)e, we again plot responses to monocular target stimuli flickering at 0.5 Hz, when the other eye viewed stimuli flickering at 0.4 Hz (here too, the red monocular-only data are replotted from Figure \@ref(fig:pupildataMel)d for comparison). For the binocular cross condition (shown in purple), responses were slightly suppressed across all target contrasts (see Table \@ref(tab:TableStatsMonBinXFig4e) for summary of statistical results). For the dichoptic cross condition (shown in yellow), responses were also slightly suppressed across the contrast range (see Table \@ref(tab:TableStatsMonDichXFig4e) for summary of statistical results). This pattern is also observed at the second harmonic (Figure \@ref(fig:pupildataMel)h, see Tables \@ref(tab:TableStatsMonBinXFig4h) and \@ref(tab:TableStatsMonDichXFig4h) for summary of statistical results).

Figure \@ref(fig:pupildataMel)f shows responses at 0.4 Hz, for the same conditions, as well as for a condition in which a monocular stimulus flickered at 0.4 Hz (grey circles). These data are perhaps too noisy to interpret, though we note that the binocular cross data (purple triangles) are generally below the monocular data (grey circles), perhaps indicating suppression (see Table \@ref(tab:TableStatsMonXBinXFig4f) for summary of statistical results). The same pattern is generally also observed at the second harmonic (Figure \@ref(fig:pupildataMel)i, see Table \@ref(tab:TableStatsMonXBinXFig4i) for summary of statistical results).

Finally, we calculated the binocular to monocular ratio at the first and second harmonic frequencies. Figure \@ref(fig:pupildataMel)c shows that these ratios are around 1 at the first harmonic, suggesting that there is strong interocular suppression between the eyes, and binocular signal combination is therefore strongly non-linear.

## Experiment 3

```{r L-M individual, include=FALSE, results='hide'}

# (download and) analyse individual participant data for the L-M condition
if (processdata > 2){

  for(p in 701:712){
    participant <- paste0('P',p)

    tic()

    pupiltargets <- array(0,dim=c(3,2,60))
    pupilmasks <- pupiltargets
    pupiltargets2 <- pupiltargets
    pupilmasks2 <- pupiltargets
    pupilwaveforms <- array(0,dim=c(3,2,60,120*14))
    pupilspectra <- array(0,dim=c(3,2,60,300))
    timeseq <- seq(1/120,10,length.out=120*10)
    timeseq2 <- seq(1/120,14,length.out=120*14)
    targetindex <- (0.5*10)+1
    maskindex <- (0.4*10)+1
    targetindex2 <- (0.5*2*10)+1
    maskindex2 <- (2*0.4*10)+1

    repcounterP <- (1:60)*0
    d <- dir(paste0(rawdir,participant),pattern='*annotations.csv',full.names=TRUE)

    for (block in 1:length(d)){
        tic()
        adata <- read.csv(paste0(rawdir,participant,'/',paste0(participant,'_S',block),'_annotations.csv'))

        trialtimes <- NULL
        trialtypes <- NULL
        for (t in 1:(nrow(adata)/2)){
          trialtimes[t] <- mean(adata$timestamp[(t*2 - 1):(t*2)])
          trialtypes[t] <- adata$condition_code[t*2]
        }

        trialtypes[which(trialtypes>15)] <- trialtypes[which(trialtypes>15)] + 5
        inclist <- NULL
        for (t in 11:15){
          i <- which(trialtypes==t)
          inclist[t-10] <- i[2]
        }
        inclist <- inclist[which(!is.na(inclist))]
        trialtypes[inclist] <- trialtypes[inclist] + 5

        pdata <- read.csv(paste(rawdir,participant,'/',paste0(participant,'_S',block),'_pupil_positions.csv',sep=''))
        pdata2 <- pdata[,c(1,3,4,14)]
        pdata2 <- pdata2[which(pdata2[,3]>0.2),]

        for (trialno in 1:length(trialtypes)){
          repcounterP[trialtypes[trialno]] <- repcounterP[trialtypes[trialno]] + 1
          for (eye in 1:2){
            eyedata <- pdata2[which(pdata2[,2]==(2-eye)),]      
            a <- which(eyedata[,1]>trialtimes[trialno]+2)
            b <- which(eyedata[,1]<(trialtimes[trialno]+12))
            i <- intersect(a,b)
            trial <- eyedata[i,]
            trial <- trial[which(!is.na(trial[,4])),]
            trial[,1] <- trial[,1] - trial[1,1]
            if (nrow(trial)>3){
              resampled <- interp1(trial[,1],trial[,4],timeseq,method='linear',extrap=TRUE)
              fspec <- (fft(resampled)/length(resampled))
              pupiltargets[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno]] <- fspec[targetindex]
              pupilmasks[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno]] <- fspec[maskindex]
              pupiltargets2[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno]] <- fspec[targetindex2]
              pupilmasks2[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno]] <- fspec[maskindex2]
              pupilspectra[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno],1:300] <- fspec[1:300]
            }

            a <- which(eyedata[,1]>(trialtimes[trialno]-1))
            b <- which(eyedata[,1]<(trialtimes[trialno]+13))
            i <- intersect(a,b)
            trial <- eyedata[i,]
            trial[,1] <- trial[,1] - trial[1,1]
            if (nrow(trial)>3){
              trial <- trial[which(!is.na(trial[,4])),]
              resampled <- interp1(trial[,1],trial[,4],timeseq2,method='linear',extrap=TRUE)
              pupilwaveforms[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno],] <- resampled - mean(resampled[1:120])
            }
          }
        }
    }

    cleanmeansP <- matrix(0,nrow=6,ncol=5)
    cleanmasksP <- matrix(0,nrow=6,ncol=5)
    cleanmeansP2 <- matrix(0,nrow=6,ncol=5)
    cleanmasksP2 <- matrix(0,nrow=6,ncol=5)

    for (cond in 1:6){
        startindex <- (10*(cond-1))
        for (level in 1:5){
          temp <- c(pupiltargets[,,startindex+level],pupiltargets[,,startindex+level+5])
          cartdata <- data.frame(Re(temp),Im(temp))
          if (sum(cartdata)!=0){
            D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
            i <- which(D<SDthresh)
            cleanmeansP[cond,level] <- mean(temp[i])}

          temp <- c(pupiltargets2[,,startindex+level],pupiltargets2[,,startindex+level+5])
          cartdata <- data.frame(Re(temp),Im(temp))
          if (sum(cartdata)!=0){
            D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
            i <- which(D<SDthresh)
            cleanmeansP2[cond,level] <- mean(temp[i])}

          temp <- c(pupilmasks[,,startindex+level],pupilmasks[,,startindex+level+5])
          cartdata <- data.frame(Re(temp),Im(temp))
          if (sum(cartdata)!=0){
            D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
            i <- which(D<SDthresh)
            cleanmasksP[cond,level] <- mean(temp[i])}

          temp <- c(pupilmasks2[,,startindex+level],pupilmasks2[,,startindex+level+5])
          cartdata <- data.frame(Re(temp),Im(temp))
          if (sum(cartdata)!=0){
            D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
            i <- which(D<SDthresh)
            cleanmasksP2[cond,level] <- mean(temp[i])}
        }
    }

    meanwavesP <- apply(pupilwaveforms[,,c(15,20),],4,mean,na.rm=TRUE)
    meanspectraP <- apply(pupilspectra[,,c(15,20),],4,mean,na.rm=TRUE)
    save(file=paste(datadir,participant,'_summaryLM.RData',sep=''),list=c('cleanmeansP','cleanmasksP','cleanmeansP2','cleanmasksP2','meanspectraP','meanwavesP'))
  }

  }
```

```{r L-M group, include=FALSE, results='hide'}

# load in individual participant data and average, save group data
if (processdata > 1){

  d <- dir(datadir,pattern='summaryLM.RData', full.names = TRUE)

  tempmasksP <- array(0,dim=c(length(d),6,5))
  tempmeansP <- tempmasksP
  tempmeansP2 <- tempmasksP
  tempmasksP2 <- tempmasksP
  tempspectraP <- array(0,dim=c(length(d),300))
  tempwavesP <- array(0,dim=c(length(d),1680))

  for (s in 1:length(d)){

    load(d[s])

    tempmasksP[s,,] <- cleanmasksP
    tempmeansP[s,,] <- cleanmeansP
    tempmasksP2[s,,] <- cleanmasksP2
    tempmeansP2[s,,] <- cleanmeansP2
    tempspectraP[s,] <- meanspectraP
    tempwavesP[s,] <- meanwavesP
  }

  tempspectraP <- tempspectraP[-c(2,4,13,20,26),]

  cleanmeansP <- matrix(0,nrow=6,ncol=5)
  cleanmeansPCI <- array(0,c(2,6,5))
  cleanmasksP <- matrix(0,nrow=6,ncol=5)
  cleanmasksPCI <- array(0,c(2,6,5))
  cleanmeansP2 <- matrix(0,nrow=6,ncol=5)
  cleanmeansP2CI <- array(0,c(2,6,5))
  cleanmasksP2 <- matrix(0,nrow=6,ncol=5)
  cleanmasksP2CI <- array(0,c(2,6,5))

  for (cond in 1:6){
    for (level in 1:5){

      temp <- tempmeansP[,cond,level]
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh)
        mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
        cleanmeansP[cond,level] <- mean(temp[i])
        cleanmeansPCI[1,cond,level] <- mbs$lowerCI
        cleanmeansPCI[2,cond,level] <- mbs$upperCI
      }

      temp <- tempmasksP[,cond,level]
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh)
        mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
        cleanmasksP[cond,level] <- mean(temp[i])
        cleanmasksPCI[1,cond,level] <- mbs$lowerCI
        cleanmasksPCI[2,cond,level] <- mbs$upperCI
      }

      temp <- tempmeansP2[,cond,level]
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh)
        mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
        cleanmeansP2[cond,level] <- mean(temp[i])
        cleanmeansP2CI[1,cond,level] <- mbs$lowerCI
        cleanmeansP2CI[2,cond,level] <- mbs$upperCI
      }

      temp <- tempmasksP2[,cond,level]
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh)
        mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
        cleanmasksP2[cond,level] <- mean(temp[i])
        cleanmasksP2CI[1,cond,level] <- mbs$lowerCI
        cleanmasksP2CI[2,cond,level] <- mbs$upperCI
      }
    }
  }

  meanspectraP <- (1:300)*0
  meanspectraPCI <- array(0,c(2,300))

  for (f in 2:300){
    temp <- tempspectraP[,f]
    cartdata <- data.frame(Re(temp),Im(temp))
    if (sum(cartdata)!=0){
      D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
      i <- which(D<SDthresh) 
      mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
      meanspectraP[f] <- mbs$meanamp
      meanspectraPCI[1,f] <- mbs$lowerCI
      meanspectraPCI[2,f] <- mbs$upperCI
    }
  }

  meanwavesP <- NULL
  meanwavesPCI <- array(0,dim=c(2,dim(tempwavesP)[2]))

  nsubjs <- dim(tempwavesP)[1]
  for (t in 1:dim(tempwavesP)[2]){
    temp <- tempwavesP[,t]
    i <- which(abs(temp-mean(temp))<(SDthresh*sd(temp)))
    meanwavesP[t] <- mean(temp[i])
    bspop <- NULL
    for (s in 1:nbootstraps){bspop[s] <- mean(sample(temp[i],length(i),replace=TRUE))}
    meanwavesPCI[,t] <- quantile(bspop,c(0.16,0.84),na.rm=TRUE)
  }

  save(file=paste0(datadir,'AveragedataLM.RData'),list=c('meanwavesP','meanwavesPCI','cleanmeansP','cleanmeansPCI','cleanmasksP','cleanmasksPCI','cleanmeansP2','cleanmeansP2CI','cleanmasksP2','cleanmasksP2CI','meanspectraP','meanspectraPCI','tempmeansP','tempmeansP2','tempmasksP','tempmasksP2'))

  }
```

```{r L-M plot, include=FALSE, results='hide'}

load(file=paste0(datadir,'AveragedataLM.RData'))

# generate plot showing the group pupillometry data for the L-M experiment
if (processdata > 0){

allPLMratios <- abs(cleanmeansP[2,])/abs(cleanmeansP[1,])
allPLM2ratios <- abs(cleanmeansP2[2,])/abs(cleanmeansP2[1,])

# plot figure  
plotlims <- c(15,40,0,4)  
ticklocsx <- contrastsdB
ticklabelsx <-c(6,12,24,48,96) 
ticklocsy <- seq(0,4,0.5)    # locations of tick marks on y axis
ticklabelsy <- ticklocsy

postscript("SumLM.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx)     
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
title(xlab="Target contrast (% of max)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  
title(ylab="Bin:Mon ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)

lines(contrastsdB,allPLMratios, col=colpal[1], lwd=3, cex=0.5)
lines(contrastsdB,allPLM2ratios, col=colpal[2], lwd=3, cex=0.5)
points(contrastsdB,allPLMratios, pch = 21, col='black', bg=colpal[1], cex=1.6, lwd=3)
points(contrastsdB,allPLM2ratios, pch = 22, col='black', bg=colpal[2], cex=1.6, lwd=3)

legend(contrastsdB[4],4,c('L-M 1F','L-M 2F'), pch=21:24, pt.bg=colpal[1:2],box.lwd=2,pt.cex=1.6,pt.lwd=3)
text(17,3.8,'(c)',adj=0.5,cex=2.5)

dev.off()

plotlims <- c(15,40,0,0.02)
plotlims2 <- c(15,40,0,0.015) 
ticklocsx <- contrastsdB    # locations of tick marks on x axis
ticklocsy <- seq(0,0.02,0.005)
ticklocsy2 <- seq(0,0.015,0.005)    # locations of tick marks on y axis
ticklabelsx <-c(6,12,24,48,96)        # set labels for x ticks
ticklabelsy <- ticklocsy
ticklabelsy2 <- ticklocsy2     # set labels for y ticks

postscript("CRF1p.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
title(xlab="Target contrast (% of max)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
title(ylab="Amplitude at 0.5Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)

for (cond in 1:3){
  lines(contrastsdB,abs(cleanmeansP[cond,]), col=colpal[cond], lwd=3, cex=0.5)
  arrows(contrastsdB,abs(cleanmeansP[cond,]),contrastsdB,cleanmeansPCI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
  arrows(contrastsdB,abs(cleanmeansP[cond,]),contrastsdB,cleanmeansPCI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
  points(contrastsdB,abs(cleanmeansP[cond,]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
}  
legend(22,0.02,c('Monocular','Binocular','Dichoptic'),pch=21:23,pt.bg=colpal[1:3],pt.lwd=3,pt.cex=1.6,box.lwd=2)
text(17,0.019,'(d)',adj=0.5,cex=2.5)

dev.off()

postscript("CRF2p.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Target contrast (% of max)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
title(ylab="Amplitude at 0.5Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)

condlist <- c(1,5,6)
pointlist <- c(21,24,25)
for (cond in 1:3){
  lines(contrastsdB,abs(cleanmeansP[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)  
  arrows(contrastsdB,abs(cleanmeansP[condlist[cond],]),contrastsdB,cleanmeansPCI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
  arrows(contrastsdB,abs(cleanmeansP[condlist[cond],]),contrastsdB,cleanmeansPCI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)  
  points(contrastsdB,abs(cleanmeansP[condlist[cond],]), pch = pointlist[cond], col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
}  
legend(22,0.02,c('Monocular','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[condlist],pt.lwd=3,pt.cex=1.6,box.lwd=2)
text(17,0.019,'(e)',adj=0.5,cex=2.5)

dev.off()

postscript("CRF3p.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Target contrast (% of max)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
title(ylab="Amplitude at 0.4Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)

for (cond in 4:6){
  lines(contrastsdB,abs(cleanmasksP[cond,]), col=colpal[cond], lwd=3, cex=0.5)   
  arrows(contrastsdB,abs(cleanmasksP[cond,]),contrastsdB,cleanmasksPCI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
  arrows(contrastsdB,abs(cleanmasksP[cond,]),contrastsdB,cleanmasksPCI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)    
  points(contrastsdB,abs(cleanmasksP[cond,]), pch = pointlist[cond-3], col='black', bg=colpal[cond], cex=1.6, lwd=3) 
}
legend(22,0.02,c('Monocular 0.4Hz','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[4:6],pt.lwd=3,pt.cex=1.6,box.lwd=2)
text(17,0.019,'(f)',adj=0.5,cex=2.5)

dev.off()

postscript("CRF1p2.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims2[3:4])   # create an empty axis of the correct dimensions
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy2, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
mtext(text = ticklabelsy2, side = 2, at=ticklocsy2, line=0.2, las=1) 
title(xlab="Target contrast (% of max)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
title(ylab="Amplitude at 1Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)

for (cond in 1:3){
  lines(contrastsdB,abs(cleanmeansP2[cond,]), col=colpal[cond], lwd=3, cex=0.5)
  arrows(contrastsdB,abs(cleanmeansP2[cond,]),contrastsdB,cleanmeansP2CI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
  arrows(contrastsdB,abs(cleanmeansP2[cond,]),contrastsdB,cleanmeansP2CI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
  points(contrastsdB,abs(cleanmeansP2[cond,]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
}  
legend(22,0.015,c('Monocular','Binocular','Dichoptic'),pch=21:23,pt.bg=colpal[1:3],pt.lwd=3,pt.cex=1.6,box.lwd=2)
text(17,0.014,'(g)',adj=0.5,cex=2.5)

dev.off()

postscript("CRF2p2.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims2[3:4])   # create an empty axis of the correct dimensions
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy2, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
mtext(text = ticklabelsy2, side = 2, at=ticklocsy2, line=0.2, las=1)
title(xlab="Target contrast (% of max)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
title(ylab="Amplitude at 1Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)

condlist <- c(1,5,6)
pointlist <- c(21,24,25)
for (cond in 1:3){
  lines(contrastsdB,abs(cleanmeansP2[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)  
  arrows(contrastsdB,abs(cleanmeansP2[condlist[cond],]),contrastsdB,cleanmeansP2CI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
  arrows(contrastsdB,abs(cleanmeansP2[condlist[cond],]),contrastsdB,cleanmeansP2CI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)  
  points(contrastsdB,abs(cleanmeansP2[condlist[cond],]), pch = pointlist[cond], col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
}  
legend(22,0.015,c('Monocular','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[condlist],pt.lwd=3,pt.cex=1.6,box.lwd=2)
text(17,0.014,'(h)',adj=0.5,cex=2.5)

dev.off()

postscript("CRF3p2.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims2[3:4])   # create an empty axis of the correct dimensions
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy2, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
mtext(text = ticklabelsy2, side = 2, at=ticklocsy2, line=0.2, las=1)
title(xlab="Target contrast (% of max)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
title(ylab="Amplitude at 0.8Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)

for (cond in 4:6){
  lines(contrastsdB,abs(cleanmasksP2[cond,]), col=colpal[cond], lwd=3, cex=0.5)   
  arrows(contrastsdB,abs(cleanmasksP2[cond,]),contrastsdB,cleanmasksP2CI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
  arrows(contrastsdB,abs(cleanmasksP2[cond,]),contrastsdB,cleanmasksP2CI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)    
  points(contrastsdB,abs(cleanmasksP2[cond,]), pch = pointlist[cond-3], col='black', bg=colpal[cond], cex=1.6, lwd=3) 
}
legend(22,0.015,c('Monocular 0.4Hz','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[4:6],pt.lwd=3,pt.cex=1.6,box.lwd=2)
text(17,0.014,'(i)',adj=0.5,cex=2.5)

dev.off()

postscript("SpecP.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 8)

frequencies <- (0:299)/10

plotlims <- c(0,2,0,0.015) 
ticklocsx <- seq(0,2,0.25)    # locations of tick marks on x axis
ticklocsy <- seq(0,0.015,0.005)    # locations of tick marks on y axis
ticklabelsx <-ticklocsx        # set labels for x ticks
ticklabelsy <- ticklocsy    # set labels for y ticks

plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
title(xlab="Frequency (Hz)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  
title(ylab="Amplitude (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)

polygon(frequencies[c(3:21,21:3)],c(meanspectraPCI[1,3:21],meanspectraPCI[2,21:3]),col=colpal[2],border=NA)

lines(frequencies[3:21],abs(meanspectraP[3:21]), col=colpal[2], lwd=3, cex=0.5)

text(0.1,0.014,'(a)',adj=0.5,cex=2.5)

dev.off()

postscript("timecourseP.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 8)

times <- seq((1/120)-1,13,1/120)
sinewave <- sin(0.5*times * 2*pi)
sinewave[1:120] <- 0
sinewave[1560:1680] <- 0

plotlims <- c(-1,13,-0.5,0.5)
ticklocsx <- seq(-1,13,1)    # locations of tick marks on x axis
ticklocsy <- seq(-0.5,0.5,0.5)    # locations of tick marks on y axis
ticklabelsx <- ticklocsx        # set labels for x ticks
ticklabelsy <- ticklocsy    # set labels for y ticks

plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)
title(ylab="Amplitude (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)

filt <- butter(3,0.083)
filtwaveP <- signal::filter(filt, meanwavesP)
filtU <- signal::filter(filt,meanwavesPCI[1,])
filtL <- signal::filter(filt,meanwavesPCI[2,])
polygon(times[c(1:length(times),length(times):1)],c(filtL,filtU[length(filtU):1]),col=colpal[2],border=NA)
lines(times, filtwaveP, col=colpal[2], lwd=1.5)
lines(times, (sinewave/10)-0.4, col='black', lwd=3)

text(-0.7,0.4,'(b)',adj=0.5,cex=2.5)

dev.off()

PostScriptTrace('CRF1p.ps')
p1 <- readPicture('CRF1p.ps.xml')
PostScriptTrace('CRF2p.ps')
p2 <- readPicture('CRF2p.ps.xml')
PostScriptTrace('CRF3p.ps')
p3 <- readPicture('CRF3p.ps.xml')
PostScriptTrace('CRF1p2.ps')
p4 <- readPicture('CRF1p2.ps.xml')
PostScriptTrace('CRF2p2.ps')
p5 <- readPicture('CRF2p2.ps.xml')
PostScriptTrace('CRF3p2.ps')
p6 <- readPicture('CRF3p2.ps.xml')
PostScriptTrace('SpecP.ps')
p7 <- readPicture('SpecP.ps.xml')
PostScriptTrace('timecourseP.ps')
p8 <- readPicture('timecourseP.ps.xml')
PostScriptTrace('SumLM.ps')
p9 <- readPicture('SumLM.ps.xml')

for (n in 1:length(p7@paths)){
  temp <- class(p7@paths[n]$path)[1]
  if (pmatch(temp,"PictureFill",nomatch=0)){
    if (sum(col2rgb(p7@paths[n]$path@rgb))<765){p7@paths[n]$path@rgb <- addalpha(p7@paths[n]$path@rgb,alpha=0.2)}}}

for (n in 1:length(p8@paths)){
  temp <- class(p8@paths[n]$path)[1]
  if (pmatch(temp,"PictureFill",nomatch=0)){
    if (sum(col2rgb(p8@paths[n]$path@rgb))<765){p8@paths[n]$path@rgb <- addalpha(p8@paths[n]$path@rgb,alpha=0.2)}}}

pdf(paste0(figdir,"pupildataLM.pdf"), bg="transparent", height = 20, width = 15)

par(mar=c(0.1,0.1,0.1,0.1))
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(0,1), ylim=c(0,1))

grid.picture(p1,x=0.17,y=0.4,width=0.32,height=1)
grid.picture(p2,x=0.5,y=0.4,width=0.32,height=1)
grid.picture(p3,x=0.83,y=0.4,width=0.32,height=1)
grid.picture(p4,x=0.17,y=0.15,width=0.32,height=1)
grid.picture(p5,x=0.5,y=0.15,width=0.32,height=1)
grid.picture(p6,x=0.83,y=0.15,width=0.32,height=1)
grid.picture(p7,x=0.25,y=0.83,width=0.5,height=1)
grid.picture(p8,x=0.25,y=0.63,width=0.5,height=1)
grid.picture(p9,x=0.75,y=0.71,width=0.5,height=1)

text(0.5,0.98,'L-M',cex=4)

dev.off()

file.remove(c('CRF1p.ps','CRF2p.ps','CRF3p.ps','CRF1p2.ps','CRF2p2.ps','CRF3p2.ps','SpecP.ps','timecourseP.ps','SumLM.ps'))
file.remove(c('CRF1p.ps.xml','CRF2p.ps.xml','CRF3p.ps.xml','CRF1p2.ps.xml','CRF2p2.ps.xml','CRF3p2.ps.xml','SpecP.ps.xml','timecourseP.ps.xml','SumLM.ps.xml'))

  }
```

```{r L-M statistics, include=FALSE, results='hide'}

# do statistics on the L-M data
alldata <- NULL
groupID <- NULL
allP <- NULL
counter <- 0
for (cont in 1:dim(tempmeansP)[3]){
  for (p in 1:dim(tempmeansP)[1]){
    counter <- counter + 1
    alldata[counter] <- tempmeansP[p,3,cont]
    groupID[counter] <- cont
    allP[counter] <- p
  }
}
dichA2c <- anovacirc.test(alldata,group=groupID,participant=allP)

alldata <- NULL
allgroupA <- NULL
allgroupB <- NULL
allP <- NULL
counter <- 0
for (p in 1:12){
  for (lev in 1:5){
    for (cond in 1:2){
    counter <- counter + 1
    alldata[counter] <- tempmeansP[p,cond,lev]
    allgroupA[counter] <- lev
    allgroupB[counter] <- cond
    allP[counter] <- p
    }
  }
}
monbinPstats <- anovacirc2way(alldata,allgroupA,allgroupB,allP)

alldata <- NULL
allgroupA <- NULL
allgroupB <- NULL
allP <- NULL
counter <- 0
for (p in 1:12){
  for (lev in 1:5){
    counter <- counter + 1
    alldata[counter] <- tempmeansP[p,1,lev]
    allgroupA[counter] <- lev
    allgroupB[counter] <- 1
    allP[counter] <- p

    counter <- counter + 1
    alldata[counter] <- tempmeansP[p,3,lev]
    allgroupA[counter] <- lev
    allgroupB[counter] <- 2
    allP[counter] <- p
  }
}

mondichPstats <- anovacirc2way(alldata,allgroupA,allgroupB,allP)

alldata <- NULL
allgroupA <- NULL
allgroupB <- NULL
allP <- NULL
counter <- 0
for (p in 1:12){
  for (lev in 1:5){
    counter <- counter + 1
    alldata[counter] <- tempmeansP[p,1,lev]
    allgroupA[counter] <- lev
    allgroupB[counter] <- 1
    allP[counter] <- p

    counter <- counter + 1
    alldata[counter] <- tempmeansP[p,5,lev]
    allgroupA[counter] <- lev
    allgroupB[counter] <- 2
    allP[counter] <- p
  }
}

monbinPstatsX <- anovacirc2way(alldata,allgroupA,allgroupB,allP)

alldata <- NULL
allgroupA <- NULL
allgroupB <- NULL
allP <- NULL
counter <- 0
for (p in 1:12){
  for (lev in 1:5){
    counter <- counter + 1
    alldata[counter] <- tempmeansP[p,1,lev]
    allgroupA[counter] <- lev
    allgroupB[counter] <- 1
    allP[counter] <- p

    counter <- counter + 1
    alldata[counter] <- tempmeansP[p,6,lev]
    allgroupA[counter] <- lev
    allgroupB[counter] <- 2
    allP[counter] <- p
  }
}

mondichPstatsX <- anovacirc2way(alldata,allgroupA,allgroupB,allP)

```

The results of the L-M pathway experiment are summarised in Figure \@ref(fig:pupildataLM). The average Fourier spectrum is displayed in Figure \@ref(fig:pupildataLM)a, and shows clear responses at both the first harmonic frequency (0.5 Hz) and the second harmonic frequency (1 Hz) of approximately equal amplitude. These results demonstrate that we can evoke measurable steady-state pupil responses at 0.5 Hz by selectively stimulating the L-M postreceptoral ‘parvocellular’ pathway whilst ignoring rods and nominally silencing S-cones and melanopsin. The group average waveform for binocular presentation is shown in Figure \@ref(fig:pupildataLM)b and, as observed in the previous experiments, there is a substantial pupil constriction at stimulus onset, followed by visible oscillations at the flicker frequency (0.5 Hz, see waveform at foot) and its second harmonic (i.e. there are two peaks in the data for every one peak in the driving waveform).

```{r pupildataLM, fig.cap="Summary of pupillometry results for the L-M pathway experiment for N=12 participants. Panel (a) shows the average Fourier spectrum. Panel (b) shows a group average waveform for binocular presentation (low pass filtered at 5 Hz), with the driving signal plotted at the foot. Panel (c) shows the ratio of binocular to monocular response. The red circles show the ratios at the first harmonic (0.5 Hz) and the blue squares show the ratios at the second harmonic (1 Hz). Panels (d,e) show contrast response functions at 0.5 Hz for different conditions. Panel (f) shows contrast response functions at 0.4 Hz for three conditions. Panels (g-i) are in the same format but for the second harmonic responses. Shaded regions and error bars indicate bootstrapped standard errors.", fig.align="center", out.width = '85%', echo=FALSE}

knitr::include_graphics(paste0(figdir,'pupildataLM.pdf'))
```

Figure \@ref(fig:pupildataLM)d shows contrast response functions in response to stimuli flickering only at 0.5 Hz. The amplitude of the binocular condition (blue squares) is substantially smaller than that of the monocular condition (red circles) across the range of target contrasts, indicating a process of binocular suppression (see Table \@ref(tab:TableStatsFig5d) for summary of statistical results). At the second harmonic, the pattern is reversed, with the binocular responses being larger than the monocular responses (Figure \@ref(fig:pupildataLM)g, see Table \@ref(tab:TableStatsFig5g) for summary of statistical results).

In Figure \@ref(fig:pupildataLM)e, we plot responses to monocular target stimuli flickering at 0.5 Hz, when the other eye viewed stimuli flickering at 0.4 Hz (the red monocular-only data are replotted from Figure \@ref(fig:pupildataLM)d for comparison). For the binocular cross (purple triangles) and dichoptic cross (yellow triangles) conditions, we again observed a very strong suppression of the responses across all target contrasts (see Tables \@ref(tab:TableStatsMonBinXFig5e) and \@ref(tab:TableStatsMonDichXFig5e) for summary of statistical results). This was not observed at the second harmonic (Figure \@ref(fig:pupildataLM)h), where monocular and binocular responses appeared to be quite similar (see Tables \@ref(tab:TableStatsMonBinXFig5h) and \@ref(tab:TableStatsMonDichXFig5h) for summary of statistical results).

Figure \@ref(fig:pupildataLM)f shows responses at 0.4 Hz, for the same conditions, as well as for a condition in which a monocular stimulus flickered at 0.4 Hz (grey circles). Again, strong suppression can be observed across the contrast range (see Table \@ref(tab:TableStatsMonXBinXFig5f) for summary of statistical results). The dichoptic cross condition shows a clear modulation with target contrast, as we can see by the decrease of the response as the contrast increases (see Table \@ref(tab:TableStatsMonXDichXFig5f) for summary of statistical results). The same pattern is also observed at the second harmonic (Figure \@ref(fig:pupildataLM)i), though the suppression in the binocular cross condition is less extreme at the second harmonic (see Tables \@ref(tab:TableStatsMonXBinXFig5i) and \@ref(tab:TableStatsMonXDichXFig5i) for summary of statistical results).

Finally, we calculated the binocular to monocular ratio at the first and second harmonics. Figure \@ref(fig:pupildataLM)c shows that these ratios are generally below 1 at the first harmonic, again indicating very strong interocular suppression, and suggesting that the combination of the signals between the eyes is strongly non-linear. At the second harmonic, the ratios are generally between 1 and 2, suggesting that suppression between the eyes is weaker, but overall the combination remains non-linear.

## Experiment 4

```{r S individual, include=FALSE, results='hide'}

# (download and) analyse individual participant data for the S condition
if (processdata > 2){

  for(p in 301:312){
    participant <- paste0('P',p)

    tic()

    pupiltargets <- array(0,dim=c(3,2,60))
    pupilmasks <- pupiltargets
    pupiltargets2 <- pupiltargets
    pupilmasks2 <- pupiltargets
    pupilwaveforms <- array(0,dim=c(3,2,60,120*14))
    pupilspectra <- array(0,dim=c(3,2,60,300))
    timeseq <- seq(1/120,10,length.out=120*10)
    timeseq2 <- seq(1/120,14,length.out=120*14)
    targetindex <- (0.5*10)+1
    maskindex <- (0.4*10)+1
    targetindex2 <- (0.5*2*10)+1
    maskindex2 <- (2*0.4*10)+1

    repcounterP <- (1:60)*0
    d <- dir(paste0(rawdir,participant),pattern='*annotations.csv',full.names=TRUE)

    for (block in 1:length(d)){
        tic()
        adata <- read.csv(paste0(rawdir,participant,'/',paste0(participant,'_S',block),'_annotations.csv'))

        trialtimes <- NULL
        trialtypes <- NULL
        for (t in 1:(nrow(adata)/2)){
          trialtimes[t] <- mean(adata$timestamp[(t*2 - 1):(t*2)])
          trialtypes[t] <- adata$condition_code[t*2]
        }

        trialtypes[which(trialtypes>15)] <- trialtypes[which(trialtypes>15)] + 5
        inclist <- NULL
        for (t in 11:15){
          i <- which(trialtypes==t)
          inclist[t-10] <- i[2]
        }
        inclist <- inclist[which(!is.na(inclist))]
        trialtypes[inclist] <- trialtypes[inclist] + 5

        pdata <- read.csv(paste(rawdir,participant,'/',paste0(participant,'_S',block),'_pupil_positions.csv',sep=''))
        pdata2 <- pdata[,c(1,3,4,14)]
        pdata2 <- pdata2[which(pdata2[,3]>0.2),]

        for (trialno in 1:length(trialtypes)){
          repcounterP[trialtypes[trialno]] <- repcounterP[trialtypes[trialno]] + 1
          for (eye in 1:2){
            eyedata <- pdata2[which(pdata2[,2]==(2-eye)),]      
            a <- which(eyedata[,1]>trialtimes[trialno]+2)
            b <- which(eyedata[,1]<(trialtimes[trialno]+12))
            i <- intersect(a,b)
            trial <- eyedata[i,]
            trial <- trial[which(!is.na(trial[,4])),]
            trial[,1] <- trial[,1] - trial[1,1]
            if (nrow(trial)>3){
              resampled <- interp1(trial[,1],trial[,4],timeseq,method='linear',extrap=TRUE)
              fspec <- (fft(resampled)/length(resampled))
              pupiltargets[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno]] <- fspec[targetindex]
              pupilmasks[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno]] <- fspec[maskindex]
              pupiltargets2[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno]] <- fspec[targetindex2]
              pupilmasks2[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno]] <- fspec[maskindex2]
              pupilspectra[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno],1:300] <- fspec[1:300]
            }

            a <- which(eyedata[,1]>(trialtimes[trialno]-1))
            b <- which(eyedata[,1]<(trialtimes[trialno]+13))
            i <- intersect(a,b)
            trial <- eyedata[i,]
            trial[,1] <- trial[,1] - trial[1,1]
            if (nrow(trial)>3){
              trial <- trial[which(!is.na(trial[,4])),]
              resampled <- interp1(trial[,1],trial[,4],timeseq2,method='linear',extrap=TRUE)
              pupilwaveforms[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno],] <- resampled - mean(resampled[1:120])
            }
          }
        }
    }

    cleanmeansP <- matrix(0,nrow=6,ncol=5)
    cleanmasksP <- matrix(0,nrow=6,ncol=5)
    cleanmeansP2 <- matrix(0,nrow=6,ncol=5)
    cleanmasksP2 <- matrix(0,nrow=6,ncol=5)

    for (cond in 1:6){
        startindex <- (10*(cond-1))
        for (level in 1:5){
          temp <- c(pupiltargets[,,startindex+level],pupiltargets[,,startindex+level+5])
          cartdata <- data.frame(Re(temp),Im(temp))
          if (sum(cartdata)!=0){
            D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
            i <- which(D<SDthresh)
            cleanmeansP[cond,level] <- mean(temp[i])}

          temp <- c(pupiltargets2[,,startindex+level],pupiltargets2[,,startindex+level+5])
          cartdata <- data.frame(Re(temp),Im(temp))
          if (sum(cartdata)!=0){
            D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
            i <- which(D<SDthresh)
            cleanmeansP2[cond,level] <- mean(temp[i])}

          temp <- c(pupilmasks[,,startindex+level],pupilmasks[,,startindex+level+5])
          cartdata <- data.frame(Re(temp),Im(temp))
          if (sum(cartdata)!=0){
            D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
            i <- which(D<SDthresh)
            cleanmasksP[cond,level] <- mean(temp[i])}

          temp <- c(pupilmasks2[,,startindex+level],pupilmasks2[,,startindex+level+5])
          cartdata <- data.frame(Re(temp),Im(temp))
          if (sum(cartdata)!=0){
            D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
            i <- which(D<SDthresh)
            cleanmasksP2[cond,level] <- mean(temp[i])}
        }
    }

    meanwavesP <- apply(pupilwaveforms[,,c(15,20),],4,mean,na.rm=TRUE)
    meanspectraP <- apply(pupilspectra[,,c(15,20),],4,mean,na.rm=TRUE)
    save(file=paste(datadir,participant,'_summaryS.RData',sep=''),list=c('cleanmeansP','cleanmasksP','cleanmeansP2','cleanmasksP2','meanspectraP','meanwavesP'))
  }

  }
```

```{r S group, include=FALSE, results='hide'}

# load in individual participant data and average, save group data
if (processdata > 1){

  d <- dir(datadir,pattern='summaryS.RData', full.names = TRUE)

  tempmasksP <- array(0,dim=c(length(d),6,5))
  tempmeansP <- tempmasksP
  tempmeansP2 <- tempmasksP
  tempmasksP2 <- tempmasksP
  tempspectraP <- array(0,dim=c(length(d),300))
  tempwavesP <- array(0,dim=c(length(d),1680))

  for (s in 1:length(d)){

    load(d[s])

    tempmasksP[s,,] <- cleanmasksP
    tempmeansP[s,,] <- cleanmeansP
    tempmasksP2[s,,] <- cleanmasksP2
    tempmeansP2[s,,] <- cleanmeansP2
    tempspectraP[s,] <- meanspectraP
    tempwavesP[s,] <- meanwavesP
  }

  tempspectraP <- tempspectraP[-c(2,4,13,20,26),]

  cleanmeansP <- matrix(0,nrow=6,ncol=5)
  cleanmeansPCI <- array(0,c(2,6,5))
  cleanmasksP <- matrix(0,nrow=6,ncol=5)
  cleanmasksPCI <- array(0,c(2,6,5))
  cleanmeansP2 <- matrix(0,nrow=6,ncol=5)
  cleanmeansP2CI <- array(0,c(2,6,5))
  cleanmasksP2 <- matrix(0,nrow=6,ncol=5)
  cleanmasksP2CI <- array(0,c(2,6,5))

  for (cond in 1:6){
    for (level in 1:5){

      temp <- tempmeansP[,cond,level]
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh)
        mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
        cleanmeansP[cond,level] <- mean(temp[i])
        cleanmeansPCI[1,cond,level] <- mbs$lowerCI
        cleanmeansPCI[2,cond,level] <- mbs$upperCI
      }

      temp <- tempmasksP[,cond,level]
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh)
        mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
        cleanmasksP[cond,level] <- mean(temp[i])
        cleanmasksPCI[1,cond,level] <- mbs$lowerCI
        cleanmasksPCI[2,cond,level] <- mbs$upperCI
      }

      temp <- tempmeansP2[,cond,level]
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh)
        mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
        cleanmeansP2[cond,level] <- mean(temp[i])
        cleanmeansP2CI[1,cond,level] <- mbs$lowerCI
        cleanmeansP2CI[2,cond,level] <- mbs$upperCI
      }

      temp <- tempmasksP2[,cond,level]
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh)
        mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
        cleanmasksP2[cond,level] <- mean(temp[i])
        cleanmasksP2CI[1,cond,level] <- mbs$lowerCI
        cleanmasksP2CI[2,cond,level] <- mbs$upperCI
      }
    }
  }

  meanspectraP <- (1:300)*0
  meanspectraPCI <- array(0,c(2,300))

  for (f in 2:300){
    temp <- tempspectraP[,f]
    cartdata <- data.frame(Re(temp),Im(temp))
    if (sum(cartdata)!=0){
      D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
      i <- which(D<SDthresh) 
      mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
      meanspectraP[f] <- mbs$meanamp
      meanspectraPCI[1,f] <- mbs$lowerCI
      meanspectraPCI[2,f] <- mbs$upperCI
    }
  }

  meanwavesP <- NULL
  meanwavesPCI <- array(0,dim=c(2,dim(tempwavesP)[2]))

  nsubjs <- dim(tempwavesP)[1]
  for (t in 1:dim(tempwavesP)[2]){
    temp <- tempwavesP[,t]
    i <- which(abs(temp-mean(temp))<(SDthresh*sd(temp)))
    meanwavesP[t] <- mean(temp[i])
    bspop <- NULL
    for (s in 1:nbootstraps){bspop[s] <- mean(sample(temp[i],length(i),replace=TRUE))}
    meanwavesPCI[,t] <- quantile(bspop,c(0.16,0.84),na.rm=TRUE)
  }

  save(file=paste0(datadir,'AveragedataS.RData'),list=c('meanwavesP','meanwavesPCI','cleanmeansP','cleanmeansPCI','cleanmasksP','cleanmasksPCI','cleanmeansP2','cleanmeansP2CI','cleanmasksP2','cleanmasksP2CI','meanspectraP','meanspectraPCI','tempmeansP','tempmeansP2','tempmasksP','tempmasksP2'))

  }
```

```{r S plot, include=FALSE, results='hide'}

load(file=paste0(datadir,'AveragedataS.RData'))

# generate plot showing the group pupillometry data for the S experiment
if (processdata > 0){

allPSratios <- abs(cleanmeansP[2,])/abs(cleanmeansP[1,])
allPS2ratios <- abs(cleanmeansP2[2,])/abs(cleanmeansP2[1,])

# plot figure  
plotlims <- c(15,40,0,3)  
ticklocsx <- contrastsdB
ticklabelsx <-c(6,12,24,48,96) 
ticklocsy <- seq(0,3,0.5)    # locations of tick marks on y axis
ticklabelsy <- ticklocsy

postscript("SumS.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx)     
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
title(xlab="Target contrast (% of max)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  
title(ylab="Bin:Mon ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)

lines(contrastsdB,allPSratios, col=colpal[1], lwd=3, cex=0.5)
lines(contrastsdB,allPS2ratios, col=colpal[2], lwd=3, cex=0.5)
points(contrastsdB,allPSratios, pch = 21, col='black', bg=colpal[1], cex=1.6, lwd=3)
points(contrastsdB,allPS2ratios, pch = 22, col='black', bg=colpal[2], cex=1.6, lwd=3)

legend(contrastsdB[4],3,c('S 1F','S 2F'), pch=21:24, pt.bg=colpal[1:2],box.lwd=2,pt.cex=1.6,pt.lwd=3)
text(17,2.8,'(c)',adj=0.5,cex=2.5)

dev.off()

plotlims <- c(15,40,0,0.02)
plotlims2 <- c(15,40,0,0.015) 
ticklocsx <- contrastsdB    # locations of tick marks on x axis
ticklocsy <- seq(0,0.02,0.005)
ticklocsy2 <- seq(0,0.015,0.005)    # locations of tick marks on y axis
ticklabelsx <-c(6,12,24,48,96)        # set labels for x ticks
ticklabelsy <- ticklocsy
ticklabelsy2 <- ticklocsy2     # set labels for y ticks

postscript("CRF1p.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
title(xlab="Target contrast (% of max)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
title(ylab="Amplitude at 0.5Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)

for (cond in 1:3){
  lines(contrastsdB,abs(cleanmeansP[cond,]), col=colpal[cond], lwd=3, cex=0.5)
  arrows(contrastsdB,abs(cleanmeansP[cond,]),contrastsdB,cleanmeansPCI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
  arrows(contrastsdB,abs(cleanmeansP[cond,]),contrastsdB,cleanmeansPCI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
  points(contrastsdB,abs(cleanmeansP[cond,]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
}  
legend(22,0.02,c('Monocular','Binocular','Dichoptic'),pch=21:23,pt.bg=colpal[1:3],pt.lwd=3,pt.cex=1.6,box.lwd=2)
text(17,0.019,'(d)',adj=0.5,cex=2.5)

dev.off()

postscript("CRF2p.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Target contrast (% of max)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
title(ylab="Amplitude at 0.5Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)

condlist <- c(1,5,6)
pointlist <- c(21,24,25)
for (cond in 1:3){
  lines(contrastsdB,abs(cleanmeansP[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)  
  arrows(contrastsdB,abs(cleanmeansP[condlist[cond],]),contrastsdB,cleanmeansPCI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
  arrows(contrastsdB,abs(cleanmeansP[condlist[cond],]),contrastsdB,cleanmeansPCI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)  
  points(contrastsdB,abs(cleanmeansP[condlist[cond],]), pch = pointlist[cond], col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
}  
legend(22,0.02,c('Monocular','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[condlist],pt.lwd=3,pt.cex=1.6,box.lwd=2)
text(17,0.019,'(e)',adj=0.5,cex=2.5)

dev.off()

postscript("CRF3p.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Target contrast (% of max)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
title(ylab="Amplitude at 0.4Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)

for (cond in 4:6){
  lines(contrastsdB,abs(cleanmasksP[cond,]), col=colpal[cond], lwd=3, cex=0.5)   
  arrows(contrastsdB,abs(cleanmasksP[cond,]),contrastsdB,cleanmasksPCI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
  arrows(contrastsdB,abs(cleanmasksP[cond,]),contrastsdB,cleanmasksPCI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)    
  points(contrastsdB,abs(cleanmasksP[cond,]), pch = pointlist[cond-3], col='black', bg=colpal[cond], cex=1.6, lwd=3) 
}
legend(22,0.02,c('Monocular 0.4Hz','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[4:6],pt.lwd=3,pt.cex=1.6,box.lwd=2)
text(17,0.019,'(f)',adj=0.5,cex=2.5)

dev.off()

postscript("CRF1p2.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
title(xlab="Target contrast (% of max)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
title(ylab="Amplitude at 1Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)

for (cond in 1:3){
  lines(contrastsdB,abs(cleanmeansP2[cond,]), col=colpal[cond], lwd=3, cex=0.5)
  arrows(contrastsdB,abs(cleanmeansP2[cond,]),contrastsdB,cleanmeansP2CI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
  arrows(contrastsdB,abs(cleanmeansP2[cond,]),contrastsdB,cleanmeansP2CI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
  points(contrastsdB,abs(cleanmeansP2[cond,]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
}  
legend(22,0.02,c('Monocular','Binocular','Dichoptic'),pch=21:23,pt.bg=colpal[1:3],pt.lwd=3,pt.cex=1.6,box.lwd=2)
text(17,0.019,'(g)',adj=0.5,cex=2.5)

dev.off()

postscript("CRF2p2.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Target contrast (% of max)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
title(ylab="Amplitude at 1Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)

condlist <- c(1,5,6)
pointlist <- c(21,24,25)
for (cond in 1:3){
  lines(contrastsdB,abs(cleanmeansP2[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)  
  arrows(contrastsdB,abs(cleanmeansP2[condlist[cond],]),contrastsdB,cleanmeansP2CI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
  arrows(contrastsdB,abs(cleanmeansP2[condlist[cond],]),contrastsdB,cleanmeansP2CI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)  
  points(contrastsdB,abs(cleanmeansP2[condlist[cond],]), pch = pointlist[cond], col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
}  
legend(22,0.02,c('Monocular','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[condlist],pt.lwd=3,pt.cex=1.6,box.lwd=2)
text(17,0.019,'(h)',adj=0.5,cex=2.5)

dev.off()

postscript("CRF3p2.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Target contrast (% of max)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
title(ylab="Amplitude at 0.8Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)

for (cond in 4:6){
  lines(contrastsdB,abs(cleanmasksP2[cond,]), col=colpal[cond], lwd=3, cex=0.5)   
  arrows(contrastsdB,abs(cleanmasksP2[cond,]),contrastsdB,cleanmasksP2CI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
  arrows(contrastsdB,abs(cleanmasksP2[cond,]),contrastsdB,cleanmasksP2CI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)    
  points(contrastsdB,abs(cleanmasksP2[cond,]), pch = pointlist[cond-3], col='black', bg=colpal[cond], cex=1.6, lwd=3) 
}
legend(22,0.02,c('Monocular 0.4Hz','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[4:6],pt.lwd=3,pt.cex=1.6,box.lwd=2)
text(17,0.019,'(i)',adj=0.5,cex=2.5)

dev.off()

postscript("SpecP.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 8)

frequencies <- (0:299)/10

plotlims <- c(0,2,0,0.015) 
ticklocsx <- seq(0,2,0.25)    # locations of tick marks on x axis
ticklocsy <- seq(0,0.015,0.005)    # locations of tick marks on y axis
ticklabelsx <-ticklocsx        # set labels for x ticks
ticklabelsy <- ticklocsy    # set labels for y ticks

plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
title(xlab="Frequency (Hz)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  
title(ylab="Amplitude (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)

polygon(frequencies[c(3:21,21:3)],c(meanspectraPCI[1,3:21],meanspectraPCI[2,21:3]),col=colpal[2],border=NA)

lines(frequencies[3:21],abs(meanspectraP[3:21]), col=colpal[2], lwd=3, cex=0.5)

text(0.1,0.014,'(a)',adj=0.5,cex=2.5)

dev.off()

postscript("timecourseP.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 8)

times <- seq((1/120)-1,13,1/120)
sinewave <- sin(0.5*times * 2*pi)
sinewave[1:120] <- 0
sinewave[1560:1680] <- 0

plotlims <- c(-1,13,-0.5,0.5)
ticklocsx <- seq(-1,13,1)    # locations of tick marks on x axis
ticklocsy <- seq(-0.5,0.5,0.5)    # locations of tick marks on y axis
ticklabelsx <- ticklocsx        # set labels for x ticks
ticklabelsy <- ticklocsy    # set labels for y ticks

plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)
title(ylab="Amplitude (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)

filt <- butter(3,0.083)
filtwaveP <- signal::filter(filt, meanwavesP)
filtU <- signal::filter(filt,meanwavesPCI[1,])
filtL <- signal::filter(filt,meanwavesPCI[2,])
polygon(times[c(1:length(times),length(times):1)],c(filtL,filtU[length(filtU):1]),col=colpal[2],border=NA)
lines(times, filtwaveP, col=colpal[2], lwd=1.5)
lines(times, (sinewave/10)-0.4, col='black', lwd=3)

text(-0.7,0.4,'(b)',adj=0.5,cex=2.5)

dev.off()

PostScriptTrace('CRF1p.ps')
p1 <- readPicture('CRF1p.ps.xml')
PostScriptTrace('CRF2p.ps')
p2 <- readPicture('CRF2p.ps.xml')
PostScriptTrace('CRF3p.ps')
p3 <- readPicture('CRF3p.ps.xml')
PostScriptTrace('CRF1p2.ps')
p4 <- readPicture('CRF1p2.ps.xml')
PostScriptTrace('CRF2p2.ps')
p5 <- readPicture('CRF2p2.ps.xml')
PostScriptTrace('CRF3p2.ps')
p6 <- readPicture('CRF3p2.ps.xml')
PostScriptTrace('SpecP.ps')
p7 <- readPicture('SpecP.ps.xml')
PostScriptTrace('timecourseP.ps')
p8 <- readPicture('timecourseP.ps.xml')
PostScriptTrace('SumS.ps')
p9 <- readPicture('SumS.ps.xml')

for (n in 1:length(p7@paths)){
  temp <- class(p7@paths[n]$path)[1]
  if (pmatch(temp,"PictureFill",nomatch=0)){
    if (sum(col2rgb(p7@paths[n]$path@rgb))<765){p7@paths[n]$path@rgb <- addalpha(p7@paths[n]$path@rgb,alpha=0.2)}}}

for (n in 1:length(p8@paths)){
  temp <- class(p8@paths[n]$path)[1]
  if (pmatch(temp,"PictureFill",nomatch=0)){
    if (sum(col2rgb(p8@paths[n]$path@rgb))<765){p8@paths[n]$path@rgb <- addalpha(p8@paths[n]$path@rgb,alpha=0.2)}}}

pdf(paste0(figdir,"pupildataS.pdf"), bg="transparent", height = 20, width = 15)

par(mar=c(0.1,0.1,0.1,0.1))
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(0,1), ylim=c(0,1))

grid.picture(p1,x=0.17,y=0.4,width=0.32,height=1)
grid.picture(p2,x=0.5,y=0.4,width=0.32,height=1)
grid.picture(p3,x=0.83,y=0.4,width=0.32,height=1)
grid.picture(p4,x=0.17,y=0.15,width=0.32,height=1)
grid.picture(p5,x=0.5,y=0.15,width=0.32,height=1)
grid.picture(p6,x=0.83,y=0.15,width=0.32,height=1)
grid.picture(p7,x=0.25,y=0.83,width=0.5,height=1)
grid.picture(p8,x=0.25,y=0.63,width=0.5,height=1)
grid.picture(p9,x=0.75,y=0.71,width=0.5,height=1)

text(0.5,0.98,'S-(L+M)',cex=4)

dev.off()

file.remove(c('CRF1p.ps','CRF2p.ps','CRF3p.ps','CRF1p2.ps','CRF2p2.ps','CRF3p2.ps','SpecP.ps','timecourseP.ps','SumS.ps'))
file.remove(c('CRF1p.ps.xml','CRF2p.ps.xml','CRF3p.ps.xml','CRF1p2.ps.xml','CRF2p2.ps.xml','CRF3p2.ps.xml','SpecP.ps.xml','timecourseP.ps.xml','SumS.ps.xml'))

  }
```

```{r S statistics, include=FALSE, results='hide'}

# do statistics on the S data
alldata <- NULL
groupID <- NULL
allP <- NULL
counter <- 0
for (cont in 1:dim(tempmeansP)[3]){
  for (p in 1:dim(tempmeansP)[1]){
    counter <- counter + 1
    alldata[counter] <- tempmeansP[p,3,cont]
    groupID[counter] <- cont
    allP[counter] <- p
  }
}
dichA2c <- anovacirc.test(alldata,group=groupID,participant=allP)

alldata <- NULL
allgroupA <- NULL
allgroupB <- NULL
allP <- NULL
counter <- 0
for (p in 1:12){
  for (lev in 1:5){
    for (cond in 1:2){
    counter <- counter + 1
    alldata[counter] <- tempmeansP[p,cond,lev]
    allgroupA[counter] <- lev
    allgroupB[counter] <- cond
    allP[counter] <- p
    }
  }
}
monbinPstats <- anovacirc2way(alldata,allgroupA,allgroupB,allP)

alldata <- NULL
allgroupA <- NULL
allgroupB <- NULL
allP <- NULL
counter <- 0
for (p in 1:12){
  for (lev in 1:5){
    counter <- counter + 1
    alldata[counter] <- tempmeansP[p,1,lev]
    allgroupA[counter] <- lev
    allgroupB[counter] <- 1
    allP[counter] <- p

    counter <- counter + 1
    alldata[counter] <- tempmeansP[p,3,lev]
    allgroupA[counter] <- lev
    allgroupB[counter] <- 2
    allP[counter] <- p
  }
}

mondichPstats <- anovacirc2way(alldata,allgroupA,allgroupB,allP)

alldata <- NULL
allgroupA <- NULL
allgroupB <- NULL
allP <- NULL
counter <- 0
for (p in 1:12){
  for (lev in 1:5){
    counter <- counter + 1
    alldata[counter] <- tempmeansP[p,1,lev]
    allgroupA[counter] <- lev
    allgroupB[counter] <- 1
    allP[counter] <- p

    counter <- counter + 1
    alldata[counter] <- tempmeansP[p,5,lev]
    allgroupA[counter] <- lev
    allgroupB[counter] <- 2
    allP[counter] <- p
  }
}

monbinPstatsX <- anovacirc2way(alldata,allgroupA,allgroupB,allP)

alldata <- NULL
allgroupA <- NULL
allgroupB <- NULL
allP <- NULL
counter <- 0
for (p in 1:12){
  for (lev in 1:5){
    counter <- counter + 1
    alldata[counter] <- tempmeansP[p,1,lev]
    allgroupA[counter] <- lev
    allgroupB[counter] <- 1
    allP[counter] <- p

    counter <- counter + 1
    alldata[counter] <- tempmeansP[p,6,lev]
    allgroupA[counter] <- lev
    allgroupB[counter] <- 2
    allP[counter] <- p
  }
}

mondichPstatsX <- anovacirc2way(alldata,allgroupA,allgroupB,allP)

```

The results of the S-(L+M) pathway experiment are summarised in Figure \@ref(fig:pupildataS). The average Fourier spectrum is displayed in Figure \@ref(fig:pupildataS)a, and shows a clear response at both the first harmonic frequency (0.5 Hz) and a stronger response (by around 50%) at the second harmonic frequency (1 Hz). These results demonstrate that we can evoke measurable steady-state pupil responses at 0.5 Hz by selectively stimulating the S-(L+M) ‘koniocelluar’ pathway whilst ignoring rods and nominally silencing L/M cones and melanopsin. The group average waveform for binocular presentation is shown in Figure \@ref(fig:pupildataS)b. There is a substantial pupil constriction at stimulus onset, followed by very visible oscillations at the flicker frequency (0.5 Hz, see waveform at foot) and its second harmonic.

Figure \@ref(fig:pupildataS)d shows contrast response functions in response to stimuli flickering only at 0.5 Hz. For the first 3 target contrasts, response amplitudes increased monotonically with target contrast. At the higher contrasts, we observe a roll-over of the pupil response shown by the drop in the signals. This suggests that the S cones saturate at higher contrasts, and so are not able to drive larger pupil modulations. The amplitude of the binocular condition (blue squares) is consistently greater than that of the monocular condition (red circles) across the range of target contrasts (see Table \@ref(tab:TableStatsFig6d) for summary of statistical results). At the second harmonic, we observe quite different results, with the binocular and monocular conditions having the same amplitudes across the contrast range (Figure \@ref(fig:pupildataS)g), and no evidence of saturation (see Table \@ref(tab:TableStatsFig6g) for summary of statistical results).

In Figure \@ref(fig:pupildataS)e, we plot responses to monocular target stimuli flickering at 0.5 Hz, when the other eye viewed stimuli flickering at 0.4 Hz (the red monocular data are replotted from Figure \@ref(fig:pupildataS)d for comparison). There was very little evidence of suppression in the binocular cross (purple triangles) or dichoptic cross (yellow triangles) conditions at the first harmonic (see Tables \@ref(tab:TableStatsMonBinXFig6e) and \@ref(tab:TableStatsMonDichXFig6e) for summary of statistical results). However at the second harmonic (Figure \@ref(fig:pupildataS)h), strong suppression was apparent at the higher target contrasts (see Tables \@ref(tab:TableStatsMonBinXFig6h) and \@ref(tab:TableStatsMonDichXFig6h) for summary of statistical results).

Figure \@ref(fig:pupildataS)f shows responses at 0.4 Hz, for the same conditions, as well as for a condition in which a monocular stimulus flickered at 0.4 Hz (grey circles). At this frequency there was some evidence of suppression at the higher target contrasts (purple triangles below grey circles, see Table \@ref(tab:TableStatsMonXBinXFig6f) for summary of statistical results). At the second harmonic (Figure \@ref(fig:pupildataS)i), the binocular cross condition (purple triangles) shows a very strong suppression and the dichoptic cross condition shows a clear modulation with target contrast (yellow triangles), visible as a decrease of the response as the target contrast increases (see Tables \@ref(tab:TableStatsMonXBinXFig6i) and \@ref(tab:TableStatsMonXDichXFig6i) for summary of statistical results).

Finally, we calculated the binocular to monocular ratio at the first and second harmonics. Figure \@ref(fig:pupildataS)c shows that these ratios are generally between 1 and 2 at the first harmonic, indicating summation between the eyes with intermediate levels of interocular suppression. At the second harmonic, the ratios were around 1 for the three highest target contrasts, again consistent with strong interocular suppression.

```{r pupildataS, fig.cap="Summary of pupillometry results for the S-(L+M) pathway experiment for N=12 participants. Panel (a) shows the average Fourier spectrum. Panel (b) shows a group average waveform for binocular presentation (low pass filtered at 5 Hz), with the driving signal plotted at the foot. Panel (c) shows the ratio of binocular to monocular response. The red circles show the ratios at the first harmonic (0.5 Hz) and the blue squares show the ratios at the second harmonic (1 Hz). Panels (d,e) show contrast response functions at 0.5 Hz for different conditions. Panel (f) shows contrast response functions at 0.4 Hz for three conditions. Panels (g-i) are in the same format but for the second harmonic responses. Shaded regions and error bars indicate bootstrapped standard errors.", fig.align="center", out.width = '85%', echo=FALSE}

knitr::include_graphics(paste0(figdir,'pupildataS.pdf'))
```

## Computational modelling

```{r makestanmodels, include=FALSE, results='hide'}

# create text objects for Stan models

if (domodelling > 0){

CRFmodelstring = "
  data {
    int<lower=1> Nsubj ;
    int<lower=1> Ntotal ;
    real y[Ntotal] ;
    real x[Ntotal] ;
    real<lower=0> w[Ntotal] ;
    int<lower=1> c[Ntotal] ;
    int<lower=1> s[Ntotal] ;
  }
  parameters {
    real<lower=1> Z[Nsubj] ;
    real<lower=0> Rmax[Nsubj] ;
    real<lower=0> wt[Nsubj] ;
    real<lower=0> k[Nsubj] ;
    real<lower=0> p[Nsubj] ;    
    real<lower=0> q[Nsubj] ;    
    real<lower=0> sigma ;
    real<lower=1> Zmu ; 
    real<lower=0> Rmaxmu ; 
    real<lower=0> wtmu ; 
    real<lower=0> kmu ; 
    real<lower=0> pmu ;     
    real<lower=0> qmu ;     
    real<lower=0> Zsigma ;
    real<lower=0> Rmaxsigma ;
    real<lower=0> wtsigma ;
    real<lower=0> ksigma ;
    real<lower=0> psigma ;
    real<lower=0> qsigma ;
    real<lower=0> nu ;
  }
  model {
    Zmu ~ normal( 20 , 5 ) ;
    Rmaxmu ~ normal( 0.1 , 0.05 ) ;
    wtmu ~ normal( 1 , 0.5 ) ;
    kmu ~ normal( 0.1 , 0.05 ) ;
    pmu ~ normal( 2 , 0.1 ) ;
    qmu ~ normal( 1 , 0.5 ) ;
    sigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    Zsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    Rmaxsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    wtsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    ksigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    psigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    qsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    nu ~ exponential(1/30.0) ;
    Z ~ normal( Zmu , Zsigma ) ; // vectorized
    Rmax ~ normal( Rmaxmu , Rmaxsigma ) ; // vectorized
    wt ~ normal( wtmu , wtsigma ) ; // vectorized
    k ~ normal( kmu , ksigma ) ; // vectorized
    p ~ normal( pmu, psigma ) ;
    q ~ normal( qmu, qsigma ) ;
    for ( i in 1:Ntotal ) {

    if (c[i]==1)  // monocular condition
       y[i] ~ student_t( 
                nu ,
                k[s[i]] + (Rmax[s[i]]*(pow(x[i],p[s[i]]))/(Z[s[i]] + (pow(x[i],q[s[i]])))) ,
                w[i]*sigma ) ;

     else if (c[i]==2)  // binocular condition 
       y[i] ~ student_t( 
                nu ,
                k[s[i]] + (Rmax[s[i]]*((pow(x[i],p[s[i]]))/(Z[s[i]] + (pow(x[i],q[s[i]])) + wt[s[i]]*(pow(x[i],q[s[i]]))) + (pow(x[i],p[s[i]]))/(Z[s[i]] + (pow(x[i],q[s[i]])) + wt[s[i]]*(pow(x[i],q[s[i]]))))),
                w[i]*sigma ) ;

     else if (c[i]==3)  // dichoptic condition
       y[i] ~ student_t( 
                nu ,
                k[s[i]] + (Rmax[s[i]]*((pow(x[i],p[s[i]]))/(Z[s[i]] + (pow(x[i],q[s[i]])) + wt[s[i]]*(pow(48,q[s[i]]))) + (pow(48,p[s[i]]))/(Z[s[i]] + (pow(48,q[s[i]])) + wt[s[i]]*(pow(x[i],q[s[i]]))))),
                w[i]*sigma ) ;

     else if (c[i]==4)  // binocular cross condition 
       y[i] ~ student_t( 
                nu ,
                k[s[i]] + (Rmax[s[i]]*(pow(x[i],p[s[i]]))/(Z[s[i]] + (pow(x[i],q[s[i]])) + wt[s[i]]*(pow(x[i],q[s[i]])))) ,
                w[i]*sigma ) ;

     else if (c[i]==5)  // dichoptic cross condition
       y[i] ~ student_t( 
                nu ,
                k[s[i]] + (Rmax[s[i]]*(pow(x[i],p[s[i]]))/(Z[s[i]] + (pow(x[i],q[s[i]])) + wt[s[i]]*(pow(48,q[s[i]])))) ,
                w[i]*sigma ) ;       
    }
  }

  " # close quote for CRFmodelstring

# Translate Stan models to C++ and compile to DSO:
CRFmodel <- stan_model(model_code=CRFmodelstring)  
}

```

```{r runstanmodelLum, include=FALSE, results='hide'}

# do computational modelling for luminance experiment

if (domodelling > 0){

# Luminance experiment
d <- paste0('P',601:612,'_summaryLum.RData')

allmasksP <- array(0,dim=c(length(d),6,5))
allmeansP <- allmasksP
allmasksP2 <- array(0,dim=c(length(d),6,5))
allmeansP2 <- allmasksP

  for (s in 1:length(d)){

    load(paste0(datadir,d[s]))

  allmasksP[s,,] <- cleanmasksP/cleanmasksP[2,5]
  allmeansP[s,,] <- cleanmeansP/cleanmeansP[2,5]
  allmasksP2[s,,] <- cleanmasksP2/cleanmasksP2[2,5]
  allmeansP2[s,,] <- cleanmeansP2/cleanmeansP2[2,5]

  }

  # 1st harmonic
  condlist <- c(1,2,3,5,6)
  contlist <- c(6,12,24,48,96)
  y <- NULL
  x <- NULL
  c <- NULL
  s <- NULL
  w <- NULL
  i <- 0
  for (subj in 1:dim(allmeansP)[1]){
    for (cond in 1:length(condlist)){
      for (cont in 1:length(contlist)){
        dp <- abs(allmeansP[subj,condlist[cond],cont])
        if (is.na(dp)==0){
          if (is.infinite(dp)==0){
          i <- i + 1
          x[i] <- contlist[cont]
          y[i] <- dp
          c[i] <- cond
          s[i] <- subj
          w[i] <- 1
          }
        }
      }
    }
  }

pupildatalist = list(x = x, y = y, s = s, w = w, c = c, Nsubj = max(s), Ntotal = length(y))

# Get MC sample of posterior:
pupilsamplesLum <- sampling(object=CRFmodel, 
                    data = pupildatalist, 
                    chains = nChains,
                    iter = (ceiling(numSavedSteps/nChains)*thinSteps+burnInSteps), 
                    warmup = burnInSteps, 
                    thin = thinSteps,
                    cores = getOption("mc.cores", 1L))

  # 2nd harmonic
  condlist <- c(1,2,3,5,6)
  contlist <- c(6,12,24,48,96)
  y <- NULL
  x <- NULL
  c <- NULL
  s <- NULL
  w <- NULL
  i <- 0
  for (subj in 1:dim(allmeansP2)[1]){
    for (cond in 1:length(condlist)){
      for (cont in 1:length(contlist)){
        dp <- abs(allmeansP2[subj,condlist[cond],cont])
        if (is.na(dp)==0){
          if (is.infinite(dp)==0){
          i <- i + 1
          x[i] <- contlist[cont]
          y[i] <- dp
          c[i] <- cond
          s[i] <- subj
          w[i] <- 1
          }
        }
      }
    }
  }

pupildatalist = list(x = x, y = y, s = s, w = w, c = c, Nsubj = max(s), Ntotal = length(y))

# Get MC sample of posterior:
pupilsamplesLum2 <- sampling(object=CRFmodel, 
                    data = pupildatalist, 
                    chains = nChains,
                    iter = (ceiling(numSavedSteps/nChains)*thinSteps+burnInSteps), 
                    warmup = burnInSteps, 
                    thin = thinSteps,
                    cores = getOption("mc.cores", 1L))

save(file=paste0(datadir,'modeloutputLum.RData'),list=c('pupilsamplesLum','pupilsamplesLum2'))

}

```

```{r runstanmodelMel, include=FALSE, results='hide'}

# do computational modelling for melanopsin experiment

if (domodelling > 0){

# Melanopsin experiment
d <- paste0('P',501:512,'_summaryMel.RData')

allmasksP <- array(0,dim=c(length(d),6,5))
allmeansP <- allmasksP
allmasksP2 <- array(0,dim=c(length(d),6,5))
allmeansP2 <- allmasksP

  for (s in 1:length(d)){

    load(paste0(datadir,d[s]))

  allmasksP[s,,] <- cleanmasksP/cleanmasksP[2,5]
  allmeansP[s,,] <- cleanmeansP/cleanmeansP[2,5]
  allmasksP2[s,,] <- cleanmasksP2/cleanmasksP2[2,5]
  allmeansP2[s,,] <- cleanmeansP2/cleanmeansP2[2,5]

  }

  # 1st harmonic
  condlist <- c(1,2,3,5,6)
  contlist <- c(6,12,24,48,96)
  y <- NULL
  x <- NULL
  c <- NULL
  s <- NULL
  w <- NULL
  i <- 0
  for (subj in 1:dim(allmeansP)[1]){
    for (cond in 1:length(condlist)){
      for (cont in 1:length(contlist)){
        dp <- abs(allmeansP[subj,condlist[cond],cont])
        if (is.na(dp)==0){
          if (is.infinite(dp)==0){
          i <- i + 1
          x[i] <- contlist[cont]
          y[i] <- dp
          c[i] <- cond
          s[i] <- subj
          w[i] <- 1
          }
        }
      }
    }
  }

pupildatalist = list(x = x, y = y, s = s, w = w, c = c, Nsubj = max(s), Ntotal = length(y))

# Get MC sample of posterior:
pupilsamplesMel <- sampling(object=CRFmodel, 
                    data = pupildatalist, 
                    chains = nChains,
                    iter = (ceiling(numSavedSteps/nChains)*thinSteps+burnInSteps), 
                    warmup = burnInSteps, 
                    thin = thinSteps,
                    cores = getOption("mc.cores", 1L))

  # 2nd harmonic
  condlist <- c(1,2,3,5,6)
  contlist <- c(6,12,24,48,96)
  y <- NULL
  x <- NULL
  c <- NULL
  s <- NULL
  w <- NULL
  i <- 0
  for (subj in 1:dim(allmeansP2)[1]){
    for (cond in 1:length(condlist)){
      for (cont in 1:length(contlist)){
        dp <- abs(allmeansP2[subj,condlist[cond],cont])
        if (is.na(dp)==0){
          if (is.infinite(dp)==0){
          i <- i + 1
          x[i] <- contlist[cont]
          y[i] <- dp
          c[i] <- cond
          s[i] <- subj
          w[i] <- 1
          }
        }
      }
    }
  }

pupildatalist = list(x = x, y = y, s = s, w = w, c = c, Nsubj = max(s), Ntotal = length(y))

# Get MC sample of posterior:
pupilsamplesMel2 <- sampling(object=CRFmodel, 
                    data = pupildatalist, 
                    chains = nChains,
                    iter = (ceiling(numSavedSteps/nChains)*thinSteps+burnInSteps), 
                    warmup = burnInSteps, 
                    thin = thinSteps,
                    cores = getOption("mc.cores", 1L))

save(file=paste0(datadir,'modeloutputMel.RData'),list=c('pupilsamplesMel','pupilsamplesMel2'))
}

```

```{r runstanmodelLM, include=FALSE, results='hide'}

# do computational modelling for LM experiment

if (domodelling > 0){

# L-M experiment
d <- paste0('P',701:712,'_summaryLM.RData')

allmasksP <- array(0,dim=c(length(d),6,5))
allmeansP <- allmasksP
allmasksP2 <- array(0,dim=c(length(d),6,5))
allmeansP2 <- allmasksP

  for (s in 1:length(d)){

    load(paste0(datadir,d[s]))

  allmasksP[s,,] <- cleanmasksP/cleanmasksP[2,5]
  allmeansP[s,,] <- cleanmeansP/cleanmeansP[2,5]
  allmasksP2[s,,] <- cleanmasksP2/cleanmasksP2[2,5]
  allmeansP2[s,,] <- cleanmeansP2/cleanmeansP2[2,5]

  }

  # 1st harmonic
  condlist <- c(1,2,3,5,6)
  contlist <- c(6,12,24,48,96)
  y <- NULL
  x <- NULL
  c <- NULL
  s <- NULL
  w <- NULL
  i <- 0
  for (subj in 1:dim(allmeansP)[1]){
    for (cond in 1:length(condlist)){
      for (cont in 1:length(contlist)){
        dp <- abs(allmeansP[subj,condlist[cond],cont])
        if (is.na(dp)==0){
          if (is.infinite(dp)==0){
          i <- i + 1
          x[i] <- contlist[cont]
          y[i] <- dp
          c[i] <- cond
          s[i] <- subj
          w[i] <- 1
          }
        }
      }
    }
  }

pupildatalist = list(x = x, y = y, s = s, w = w, c = c, Nsubj = max(s), Ntotal = length(y))

# Get MC sample of posterior:
pupilsamplesLM <- sampling(object=CRFmodel, 
                    data = pupildatalist, 
                    chains = nChains,
                    iter = (ceiling(numSavedSteps/nChains)*thinSteps+burnInSteps), 
                    warmup = burnInSteps, 
                    thin = thinSteps,
                    cores = getOption("mc.cores", 1L))

  # 2nd harmonic
  condlist <- c(1,2,3,5,6)
  contlist <- c(6,12,24,48,96)
  y <- NULL
  x <- NULL
  c <- NULL
  s <- NULL
  w <- NULL
  i <- 0
  for (subj in 1:dim(allmeansP2)[1]){
    for (cond in 1:length(condlist)){
      for (cont in 1:length(contlist)){
        dp <- abs(allmeansP2[subj,condlist[cond],cont])
        if (is.na(dp)==0){
          if (is.infinite(dp)==0){
          i <- i + 1
          x[i] <- contlist[cont]
          y[i] <- dp
          c[i] <- cond
          s[i] <- subj
          w[i] <- 1
          }
        }
      }
    }
  }

pupildatalist = list(x = x, y = y, s = s, w = w, c = c, Nsubj = max(s), Ntotal = length(y))

# Get MC sample of posterior:
pupilsamplesLM2 <- sampling(object=CRFmodel, 
                    data = pupildatalist, 
                    chains = nChains,
                    iter = (ceiling(numSavedSteps/nChains)*thinSteps+burnInSteps), 
                    warmup = burnInSteps, 
                    thin = thinSteps,
                    cores = getOption("mc.cores", 1L))

save(file=paste0(datadir,'modeloutputLM.RData'),list=c('pupilsamplesLM','pupilsamplesLM2'))

}

```

```{r runstanmodelS, include=FALSE, results='hide'}

# do computational modelling for S-cone experiment

if (domodelling > 0){

# S experiment
d <- paste0('P',301:312,'_summaryS.RData')

allmasksP <- array(0,dim=c(length(d),6,5))
allmeansP <- allmasksP
allmasksP2 <- array(0,dim=c(length(d),6,5))
allmeansP2 <- allmasksP

  for (s in 1:length(d)){

    load(paste0(datadir,d[s]))

  allmasksP[s,,] <- cleanmasksP/cleanmasksP[2,5]
  allmeansP[s,,] <- cleanmeansP/cleanmeansP[2,5]
  allmasksP2[s,,] <- cleanmasksP2/cleanmasksP2[2,5]
  allmeansP2[s,,] <- cleanmeansP2/cleanmeansP2[2,5]

  }

  # 1st harmonic
  condlist <- c(1,2,3,5,6)
  contlist <- c(6,12,24,48,96)
  y <- NULL
  x <- NULL
  c <- NULL
  s <- NULL
  w <- NULL
  i <- 0
  for (subj in 1:dim(allmeansP)[1]){
    for (cond in 1:length(condlist)){
      for (cont in 1:length(contlist)){
        dp <- abs(allmeansP[subj,condlist[cond],cont])
        if (is.na(dp)==0){
          if (is.infinite(dp)==0){
          i <- i + 1
          x[i] <- contlist[cont]
          y[i] <- dp
          c[i] <- cond
          s[i] <- subj
          w[i] <- 1
          }
        }
      }
    }
  }

pupildatalist = list(x = x, y = y, s = s, w = w, c = c, Nsubj = max(s), Ntotal = length(y))

# Get MC sample of posterior:
pupilsamplesS <- sampling(object=CRFmodel, 
                    data = pupildatalist, 
                    chains = nChains,
                    iter = (ceiling(numSavedSteps/nChains)*thinSteps+burnInSteps), 
                    warmup = burnInSteps, 
                    thin = thinSteps,
                    cores = getOption("mc.cores", 1L))

  # 2nd harmonic
  condlist <- c(1,2,3,5,6)
  contlist <- c(6,12,24,48,96)
  y <- NULL
  x <- NULL
  c <- NULL
  s <- NULL
  w <- NULL
  i <- 0
  for (subj in 1:dim(allmeansP2)[1]){
    for (cond in 1:length(condlist)){
      for (cont in 1:length(contlist)){
        dp <- abs(allmeansP2[subj,condlist[cond],cont])
        if (is.na(dp)==0){
          if (is.infinite(dp)==0){
          i <- i + 1
          x[i] <- contlist[cont]
          y[i] <- dp
          c[i] <- cond
          s[i] <- subj
          w[i] <- 1
          }
        }
      }
    }
  }

pupildatalist = list(x = x, y = y, s = s, w = w, c = c, Nsubj = max(s), Ntotal = length(y))

# Get MC sample of posterior:
pupilsamplesS2 <- sampling(object=CRFmodel, 
                    data = pupildatalist, 
                    chains = nChains,
                    iter = (ceiling(numSavedSteps/nChains)*thinSteps+burnInSteps), 
                    warmup = burnInSteps, 
                    thin = thinSteps,
                    cores = getOption("mc.cores", 1L))

save(file=paste0(datadir,'modeloutputS.RData'),list=c('pupilsamplesS','pupilsamplesS2'))

}

```

```{r makemodelfigurechap4, include=FALSE, results='hide'}

# create figure containing modelling results

  load(paste0(datadir,'modeloutputLum.RData'))
  load(paste0(datadir,'modeloutputMel.RData'))
  load(paste0(datadir,'modeloutputLM.RData'))
  load(paste0(datadir,'modeloutputS.RData'))

  nchains <- dim(pupilsamplesLum)[2]
  pupilweightpopLum <- NULL
  pupilZpopLum <- NULL
  pupilKpopLum <- NULL
  pupilPpopLum <- NULL
  pupilQpopLum <- NULL
  pupilRpopLum <- NULL

  for (n in 1:nchains){
    pupilweightpopLum <- c(pupilweightpopLum,pupilsamplesLum@sim$samples[[n]]$wtmu)
    pupilZpopLum <- c(pupilZpopLum,pupilsamplesLum@sim$samples[[n]]$Zmu)
    pupilKpopLum <- c(pupilKpopLum,pupilsamplesLum@sim$samples[[n]]$kmu)
    pupilPpopLum <- c(pupilPpopLum,pupilsamplesLum@sim$samples[[n]]$pmu)
    pupilQpopLum <- c(pupilQpopLum,pupilsamplesLum@sim$samples[[n]]$qmu)
    pupilRpopLum <- c(pupilRpopLum,pupilsamplesLum@sim$samples[[n]]$Rmaxmu)
  }

  pupilWLum <- median(pupilweightpopLum)
  pupilZLum <- median(pupilZpopLum)
  pupilKLum <- median(pupilKpopLum)/sqrt(12)
  pupilPLum <- median(pupilPpopLum)
  pupilQLum <- median(pupilQpopLum)
  pupilRmaxLum <- median(pupilRpopLum)

  nchains <- dim(pupilsamplesMel)[2]
  pupilweightpopMel <- NULL
  pupilZpopMel <- NULL
  pupilKpopMel <- NULL
  pupilPpopMel <- NULL
  pupilQpopMel <- NULL
  pupilRpopMel <- NULL

  for (n in 1:nchains){
    pupilweightpopMel <- c(pupilweightpopMel,pupilsamplesMel@sim$samples[[n]]$wtmu)
    pupilZpopMel <- c(pupilZpopMel,pupilsamplesMel@sim$samples[[n]]$Zmu)
    pupilKpopMel <- c(pupilKpopMel,pupilsamplesMel@sim$samples[[n]]$kmu)
    pupilPpopMel <- c(pupilPpopMel,pupilsamplesMel@sim$samples[[n]]$pmu)
    pupilQpopMel <- c(pupilQpopMel,pupilsamplesMel@sim$samples[[n]]$qmu)
    pupilRpopMel <- c(pupilRpopMel,pupilsamplesMel@sim$samples[[n]]$Rmaxmu)
  }

  pupilWMel <- median(pupilweightpopMel)
  pupilZMel <- median(pupilZpopMel)
  pupilKMel <- median(pupilKpopMel)/sqrt(12)
  pupilPMel <- median(pupilPpopMel)
  pupilQMel <- median(pupilQpopMel)
  pupilRmaxMel <- median(pupilRpopMel)

  nchains <- dim(pupilsamplesLM)[2]
  pupilweightpopLM <- NULL
  pupilZpopLM <- NULL
  pupilKpopLM <- NULL
  pupilPpopLM <- NULL
  pupilQpopLM <- NULL
  pupilRpopLM <- NULL

  for (n in 1:nchains){
    pupilweightpopLM <- c(pupilweightpopLM,pupilsamplesLM@sim$samples[[n]]$wtmu)
    pupilZpopLM <- c(pupilZpopLM,pupilsamplesLM@sim$samples[[n]]$Zmu)
    pupilKpopLM <- c(pupilKpopLM,pupilsamplesLM@sim$samples[[n]]$kmu)
    pupilPpopLM <- c(pupilPpopLM,pupilsamplesLM@sim$samples[[n]]$pmu)
    pupilQpopLM <- c(pupilQpopLM,pupilsamplesLM@sim$samples[[n]]$qmu)
    pupilRpopLM <- c(pupilRpopLM,pupilsamplesLM@sim$samples[[n]]$Rmaxmu)
  }

  pupilWLM <- median(pupilweightpopLM)
  pupilZLM <- median(pupilZpopLM)
  pupilKLM <- median(pupilKpopLM)/sqrt(12)
  pupilPLM <- median(pupilPpopLM)
  pupilQLM <- median(pupilQpopLM)
  pupilRmaxLM <- median(pupilRpopLM)

  nchains <- dim(pupilsamplesS)[2]
  pupilweightpopS <- NULL
  pupilZpopS <- NULL
  pupilKpopS <- NULL
  pupilPpopS <- NULL
  pupilQpopS <- NULL
  pupilRpopS <- NULL

  for (n in 1:nchains){
    pupilweightpopS <- c(pupilweightpopS,pupilsamplesS@sim$samples[[n]]$wtmu)
    pupilZpopS <- c(pupilZpopS,pupilsamplesS@sim$samples[[n]]$Zmu)
    pupilKpopS <- c(pupilKpopS,pupilsamplesS@sim$samples[[n]]$kmu)
    pupilPpopS <- c(pupilPpopS,pupilsamplesS@sim$samples[[n]]$pmu)
    pupilQpopS <- c(pupilQpopS,pupilsamplesS@sim$samples[[n]]$qmu)
    pupilRpopS <- c(pupilRpopS,pupilsamplesS@sim$samples[[n]]$Rmaxmu)
  }

  pupilWS <- median(pupilweightpopS)
  pupilZS <- median(pupilZpopS)
  pupilKS <- median(pupilKpopS)/sqrt(12)
  pupilPS <- median(pupilPpopS)
  pupilQS <- median(pupilQpopS)
  pupilRmaxS <- median(pupilRpopS)

  nchains <- dim(pupilsamplesLum2)[2]
  pupilweightpopLum2 <- NULL
  pupilZpopLum2 <- NULL
  pupilKpopLum2 <- NULL
  pupilPpopLum2 <- NULL
  pupilQpopLum2 <- NULL
  pupilRpopLum2 <- NULL

  for (n in 1:nchains){
    pupilweightpopLum2 <- c(pupilweightpopLum2,pupilsamplesLum2@sim$samples[[n]]$wtmu)
    pupilZpopLum2 <- c(pupilZpopLum2,pupilsamplesLum2@sim$samples[[n]]$Zmu)
    pupilKpopLum2 <- c(pupilKpopLum2,pupilsamplesLum2@sim$samples[[n]]$kmu)
    pupilPpopLum2 <- c(pupilPpopLum2,pupilsamplesLum2@sim$samples[[n]]$pmu)
    pupilQpopLum2 <- c(pupilQpopLum2,pupilsamplesLum2@sim$samples[[n]]$qmu)
    pupilRpopLum2 <- c(pupilRpopLum2,pupilsamplesLum2@sim$samples[[n]]$Rmaxmu)
  }

  pupilWLum2 <- median(pupilweightpopLum2)
  pupilZLum2 <- median(pupilZpopLum2)
  pupilKLum2 <- median(pupilKpopLum2)/sqrt(12)
  pupilPLum2 <- median(pupilPpopLum2)
  pupilQLum2 <- median(pupilQpopLum2)
  pupilRmaxLum2 <- median(pupilRpopLum2)

  nchains <- dim(pupilsamplesMel2)[2]
  pupilweightpopMel2 <- NULL
  pupilZpopMel2 <- NULL
  pupilKpopMel2 <- NULL
  pupilPpopMel2 <- NULL
  pupilQpopMel2 <- NULL
  pupilRpopMel2 <- NULL

  for (n in 1:nchains){
    pupilweightpopMel2 <- c(pupilweightpopMel2,pupilsamplesMel2@sim$samples[[n]]$wtmu)
    pupilZpopMel2 <- c(pupilZpopMel2,pupilsamplesMel2@sim$samples[[n]]$Zmu)
    pupilKpopMel2 <- c(pupilKpopMel2,pupilsamplesMel2@sim$samples[[n]]$kmu)
    pupilPpopMel2 <- c(pupilPpopMel2,pupilsamplesMel2@sim$samples[[n]]$pmu)
    pupilQpopMel2 <- c(pupilQpopMel2,pupilsamplesMel2@sim$samples[[n]]$qmu)
    pupilRpopMel2 <- c(pupilRpopMel2,pupilsamplesMel2@sim$samples[[n]]$Rmaxmu)
  }

  pupilWMel2 <- median(pupilweightpopMel2)
  pupilZMel2 <- median(pupilZpopMel2)
  pupilKMel2 <- median(pupilKpopMel2)/sqrt(12)
  pupilPMel2 <- median(pupilPpopMel2)
  pupilQMel2 <- median(pupilQpopMel2)
  pupilRmaxMel2 <- median(pupilRpopMel2)

  nchains <- dim(pupilsamplesLM2)[2]
  pupilweightpopLM2 <- NULL
  pupilZpopLM2 <- NULL
  pupilKpopLM2 <- NULL
  pupilPpopLM2 <- NULL
  pupilQpopLM2 <- NULL
  pupilRpopLM2 <- NULL

  for (n in 1:nchains){
    pupilweightpopLM2 <- c(pupilweightpopLM2,pupilsamplesLM2@sim$samples[[n]]$wtmu)
    pupilZpopLM2 <- c(pupilZpopLM2,pupilsamplesLM2@sim$samples[[n]]$Zmu)
    pupilKpopLM2 <- c(pupilKpopLM2,pupilsamplesLM2@sim$samples[[n]]$kmu)
    pupilPpopLM2 <- c(pupilPpopLM2,pupilsamplesLM2@sim$samples[[n]]$pmu)
    pupilQpopLM2 <- c(pupilQpopLM2,pupilsamplesLM2@sim$samples[[n]]$qmu)
    pupilRpopLM2 <- c(pupilRpopLM2,pupilsamplesLM2@sim$samples[[n]]$Rmaxmu)
  }

  pupilWLM2 <- median(pupilweightpopLM2)
  pupilZLM2 <- median(pupilZpopLM2)
  pupilKLM2 <- median(pupilKpopLM2)/sqrt(12)
  pupilPLM2 <- median(pupilPpopLM2)
  pupilQLM2 <- median(pupilQpopLM2)
  pupilRmaxLM2 <- median(pupilRpopLM2)

  nchains <- dim(pupilsamplesS2)[2]
  pupilweightpopS2 <- NULL
  pupilZpopS2 <- NULL
  pupilKpopS2 <- NULL
  pupilPpopS2 <- NULL
  pupilQpopS2 <- NULL
  pupilRpopS2 <- NULL

  for (n in 1:nchains){
    pupilweightpopS2 <- c(pupilweightpopS2,pupilsamplesS2@sim$samples[[n]]$wtmu)
    pupilZpopS2 <- c(pupilZpopS2,pupilsamplesS2@sim$samples[[n]]$Zmu)
    pupilKpopS2 <- c(pupilKpopS2,pupilsamplesS2@sim$samples[[n]]$kmu)
    pupilPpopS2 <- c(pupilPpopS2,pupilsamplesS2@sim$samples[[n]]$pmu)
    pupilQpopS2 <- c(pupilQpopS2,pupilsamplesS2@sim$samples[[n]]$qmu)
    pupilRpopS2 <- c(pupilRpopS2,pupilsamplesS2@sim$samples[[n]]$Rmaxmu)
  }

  pupilWS2 <- median(pupilweightpopS2)
  pupilZS2 <- median(pupilZpopS2)
  pupilKS2 <- median(pupilKpopS2)/sqrt(12)
  pupilPS2 <- median(pupilPpopS2)
  pupilQS2 <- median(pupilQpopS2)
  pupilRmaxS2 <- median(pupilRpopS2)

getmodresps <- function(params){
contrastsfinedB <- 2:40
contrastsfine <- 10^(contrastsfinedB/20)

modresps <- matrix(0,nrow=4,ncol=length(contrastsfine))
modresps[1,] <- params[1]*(contrastsfine^params[2])/(params[3] + contrastsfine^params[6]) + params[5]

binresp <- 2*((contrastsfine^params[2])/(params[3] + contrastsfine^params[6] + params[4]*contrastsfine^params[6]))
modresps[2,] <- params[1]*binresp + params[5]

dichresp <- ((contrastsfine^params[2])/(params[3] + contrastsfine^params[6] + params[4]*48^params[6])) + ((48^params[2])/(params[3] + 48^params[6] + params[4]*contrastsfine^params[6]))
modresps[3,] <- params[1]*dichresp + params[5]

dichresp2 <- ((contrastsfine^params[2])/(params[3] + contrastsfine^params[6] + params[4]*48^params[6]))
modresps[4,] <- params[1]*dichresp2 + params[5]

return(modresps)}

if (processdata > 0){

pdf(paste(figdir,"modelfigurechap4.pdf",sep=''), bg="transparent", height = 10, width = 25)

par(mfrow=c(2,5))

load(file=paste0(datadir,'AveragedataLum.RData'))

contrastsfinedB <- 2:40

params <- c(pupilRmaxLum,pupilPLum,pupilZLum,pupilWLum,pupilKLum,pupilQLum)
modresps <- getmodresps(params)

plotlims <- c(15,40,0,1)
ticklocsx <- contrastsdB    # locations of tick marks on x axis
ticklocsy <- seq(0,1,0.2)
ticklabelsx <-c(6,12,24,48,96)        # set labels for x ticks
ticklabelsy <- ticklocsy

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2)     # add the tick labels
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
title(ylab="Relative amplitude at 0.5Hz", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
title(main='Luminance 1F',cex.main=2)

for (cond in 1:3){
  lines(contrastsfinedB,modresps[cond,], col=colpal[cond], lwd=3, cex=0.5)
  points(contrastsdB,abs(cleanmeansP[cond,])/abs(cleanmeansP[2,5]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
}  
  lines(contrastsfinedB,modresps[4,], col=colpal[6], lwd=3, cex=0.5)
  points(contrastsdB,abs(cleanmeansP[6,])/abs(cleanmeansP[2,5]), pch = 25, col='black', bg=colpal[6], cex=1.6, lwd=3)   # draw the data points themselves

legend(22,1,c('Monocular','Binocular','Dichoptic','Dichoptic cross'),pch=c(21:23,25),pt.bg=colpal[c(1:3,6)],pt.lwd=3,cex=1.5,pt.cex=1.6,box.lwd=2)
text(17,0.95,'(a)',adj=0.5,cex=2.5)

load(file=paste0(datadir,'AveragedataMel.RData'))

params <- c(pupilRmaxMel,pupilPMel,pupilZMel,pupilWMel,pupilKMel,pupilQMel)
modresps <- getmodresps(params)

plotlims <- c(15,40,0,1)
ticklocsx <- contrastsdB    # locations of tick marks on x axis
ticklocsy <- seq(0,1,0.2)
ticklabelsx <-c(6,12,24,48,96)        # set labels for x ticks
ticklabelsy <- ticklocsy

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2)     # add the tick labels
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
title(ylab="Relative amplitude at 0.5Hz", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
title(main='Melanopsin 1F',cex.main=2)

for (cond in 1:3){
  lines(contrastsfinedB,modresps[cond,], col=colpal[cond], lwd=3, cex=0.5)
  points(contrastsdB,abs(cleanmeansP[cond,])/abs(cleanmeansP[2,5]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
}  
  lines(contrastsfinedB,modresps[4,], col=colpal[6], lwd=3, cex=0.5)
  points(contrastsdB,abs(cleanmeansP[6,])/abs(cleanmeansP[2,5]), pch = 25, col='black', bg=colpal[6], cex=1.6, lwd=3)   # draw the data points themselves

text(17,0.95,'(b)',adj=0.5,cex=2.5)

load(file=paste0(datadir,'AveragedataLM.RData'))

params <- c(pupilRmaxLM,pupilPLM,pupilZLM,pupilWLM,pupilKLM,pupilQLM)
modresps <- getmodresps(params)

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2)     # add the tick labels
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
title(ylab="Relative amplitude at 0.5Hz", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
title(main='L-M cones 1F',cex.main=2)

for (cond in 1:3){
  lines(contrastsfinedB,modresps[cond,], col=colpal[cond], lwd=3, cex=0.5)
  points(contrastsdB,abs(cleanmeansP[cond,])/abs(cleanmeansP[2,5]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
}  
  lines(contrastsfinedB,modresps[4,], col=colpal[6], lwd=3, cex=0.5)
  points(contrastsdB,abs(cleanmeansP[6,])/abs(cleanmeansP[2,5]), pch = 25, col='black', bg=colpal[6], cex=1.6, lwd=3)   # draw the data points themselves

text(17,0.95,'(c)',adj=0.5,cex=2.5)

load(file=paste0(datadir,'AveragedataS.RData'))

params <- c(pupilRmaxS,pupilPS,pupilZS,pupilWS,pupilKS,pupilQS)
modresps <- getmodresps(params)

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2)     # add the tick labels
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
title(ylab="Relative amplitude at 0.5Hz", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
title(main='S cones 1F',cex.main=2)

for (cond in 1:3){
  lines(contrastsfinedB,modresps[cond,], col=colpal[cond], lwd=3, cex=0.5)
  points(contrastsdB,abs(cleanmeansP[cond,])/abs(cleanmeansP[2,5]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
}  
  lines(contrastsfinedB,modresps[4,], col=colpal[6], lwd=3, cex=0.5)
  points(contrastsdB,abs(cleanmeansP[6,])/abs(cleanmeansP[2,5]), pch = 25, col='black', bg=colpal[6], cex=1.6, lwd=3)   # draw the data points themselves

text(17,0.95,'(d)',adj=0.5,cex=2.5)

# pdf(paste(figdir,"posteriors1F.pdf",sep=''), bg="transparent", height = 5.5, width = 5.5)

plotlims <- c(-24,12,0,0.6) 
ticklocsx <- seq(-24,12,12)    
ticklocsy <- seq(0,0.6,0.1)    
ticklabelsx <- c('1/16','1/4','1','4')        
ticklabelsy <- ticklocsy    # set labels for y ticks

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2)    
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)

title(xlab="w", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
title(ylab="Probability", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
title(main='Suppression 1F',cex.main=2)

a <- density(20*log10(pupilweightpopLum),from=-48,to=12)   
polygon(c(-48,a$x,12), c(0,a$y,0), col=addalpha(colpalmod[1],0.5),border=NA)

a <- density(20*log10(pupilweightpopMel),from=-48,to=12)   
polygon(c(-48,a$x,12), c(0,a$y,0), col=addalpha(colpalmod[2],0.5),border=NA)

a<- density(20*log10(pupilweightpopLM),from=-48,to=12)   
polygon(c(-48,a$x,12), c(0,a$y,0), col=addalpha(colpalmod[3],0.5),border=NA)

a <- density(20*log10(pupilweightpopS),from=-48,to=12)   
polygon(c(-48,a$x,12), c(0,a$y,0), col=addalpha(colpalmod[4],0.5),border=NA)

prior <- dnorm(10^((-48:12)/20),1,0.5)
prior <- 0.5*prior/max(prior)
lines(-48:12,prior)

lines(20*log10(c(mean(pupilWLum),mean(pupilWLum))),c(0,0.6),lwd=3,col=colpalmod[1])
lines(20*log10(c(mean(pupilWMel),mean(pupilWMel))),c(0,0.6),lwd=3,col=colpalmod[2])
lines(20*log10(c(mean(pupilWLM),mean(pupilWLM))),c(0,0.6),lwd=3,col=colpalmod[3])
lines(20*log10(c(mean(pupilWS),mean(pupilWS))),c(0,0.6),lwd=3,col=colpalmod[4])

legend(-24,0.6,c('Prior','Lum 1F', 'Mel 1F', 'LM 1F', 'S 1F'),col=c('black',colpalmod[1:4]),lwd=c(1,3,3,3,3),lty=1, cex=1.5, box.lwd=2, bg='white')

text(10,0.58,'(e)',adj=0.5,cex=2.5)

# dev.off()
# 
# pdf(paste(figdir,"posteriors2F.pdf",sep=''), bg="transparent", height = 5.5, width = 5.5)

load(file=paste0(datadir,'AveragedataLum.RData'))

contrastsfinedB <- 2:40

params <- c(pupilRmaxLum2,pupilPLum2,pupilZLum2,pupilWLum2,pupilKLum2,pupilQLum2)
modresps <- getmodresps(params)

plotlims <- c(15,40,0,1)
ticklocsx <- contrastsdB    # locations of tick marks on x axis
ticklocsy <- seq(0,1,0.2)
ticklabelsx <-c(6,12,24,48,96)        # set labels for x ticks
ticklabelsy <- ticklocsy

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2)     # add the tick labels
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
title(ylab="Relative amplitude at 1Hz", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
title(main='Luminance 2F',cex.main=2)

for (cond in 1:3){
  lines(contrastsfinedB,modresps[cond,], col=colpal[cond], lwd=3, cex=0.5)
  points(contrastsdB,abs(cleanmeansP2[cond,])/abs(cleanmeansP2[2,5]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
}  
  lines(contrastsfinedB,modresps[4,], col=colpal[6], lwd=3, cex=0.5)
  points(contrastsdB,abs(cleanmeansP2[6,])/abs(cleanmeansP2[2,5]), pch = 25, col='black', bg=colpal[6], cex=1.6, lwd=3)   # draw the data points themselves

text(17,0.95,'(f)',adj=0.5,cex=2.5)

load(file=paste0(datadir,'AveragedataMel.RData'))

params <- c(pupilRmaxMel2,pupilPMel2,pupilZMel2,pupilWMel2,pupilKMel2,pupilQMel2)
modresps <- getmodresps(params)

plotlims <- c(15,40,0,1)
ticklocsx <- contrastsdB    # locations of tick marks on x axis
ticklocsy <- seq(0,1,0.2)
ticklabelsx <-c(6,12,24,48,96)        # set labels for x ticks
ticklabelsy <- ticklocsy

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2)     # add the tick labels
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
title(ylab="Relative amplitude at 1Hz", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
title(main='Melanopsin 2F',cex.main=2)

for (cond in 1:3){
  lines(contrastsfinedB,modresps[cond,], col=colpal[cond], lwd=3, cex=0.5)
  points(contrastsdB,abs(cleanmeansP2[cond,])/abs(cleanmeansP2[2,5]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
}  
  lines(contrastsfinedB,modresps[4,], col=colpal[6], lwd=3, cex=0.5)
  points(contrastsdB,abs(cleanmeansP2[6,])/abs(cleanmeansP2[2,5]), pch = 25, col='black', bg=colpal[6], cex=1.6, lwd=3)   # draw the data points themselves

text(17,0.95,'(g)',adj=0.5,cex=2.5)

load(file=paste0(datadir,'AveragedataLM.RData'))

params <- c(pupilRmaxLM2,pupilPLM2,pupilZLM2,pupilWLM2,pupilKLM2,pupilQLM2)
modresps <- getmodresps(params)

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2)     # add the tick labels
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
title(ylab="Relative amplitude at 1Hz", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
title(main='L-M cones 2F',cex.main=2)

for (cond in 1:3){
  lines(contrastsfinedB,modresps[cond,], col=colpal[cond], lwd=3, cex=0.5)
  points(contrastsdB,abs(cleanmeansP2[cond,])/abs(cleanmeansP2[2,5]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
}  
  lines(contrastsfinedB,modresps[4,], col=colpal[6], lwd=3, cex=0.5)
  points(contrastsdB,abs(cleanmeansP2[6,])/abs(cleanmeansP2[2,5]), pch = 25, col='black', bg=colpal[6], cex=1.6, lwd=3)   # draw the data points themselves

text(17,0.95,'(h)',adj=0.5,cex=2.5)

load(file=paste0(datadir,'AveragedataS.RData'))

params <- c(pupilRmaxS2,pupilPS2,pupilZS2,pupilWS2,pupilKS2,pupilQS2)
modresps <- getmodresps(params)

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2)     # add the tick labels
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
title(ylab="Relative amplitude at 1Hz", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
title(main='S cones 2F',cex.main=2)

for (cond in 1:3){
  lines(contrastsfinedB,modresps[cond,], col=colpal[cond], lwd=3, cex=0.5)
  points(contrastsdB,abs(cleanmeansP2[cond,])/abs(cleanmeansP2[2,5]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
}  
  lines(contrastsfinedB,modresps[4,], col=colpal[6], lwd=3, cex=0.5)
  points(contrastsdB,abs(cleanmeansP2[6,])/abs(cleanmeansP2[2,5]), pch = 25, col='black', bg=colpal[6], cex=1.6, lwd=3)   # draw the data points themselves

text(17,0.95,'(i)',adj=0.5,cex=2.5)

plotlims <- c(-24,12,0,0.6) 
ticklocsx <- seq(-24,12,12)    
ticklocsy <- seq(0,0.6,0.1)    
ticklabelsx <- c('1/16','1/4','1','4')        
ticklabelsy <- ticklocsy    # set labels for y ticks

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2)    
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)

title(xlab="w", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
title(ylab="Probability", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
title(main='Suppression 2F',cex.main=2)

a <- density(20*log10(pupilweightpopLum2),from=-48,to=12)   
polygon(c(-48,a$x,12), c(0,a$y,0), col=addalpha(colpalmod[1],0.5),border=NA)

a <- density(20*log10(pupilweightpopMel2),from=-48,to=12)   
polygon(c(-48,a$x,12), c(0,a$y,0), col=addalpha(colpalmod[2],0.5),border=NA)

a <- density(20*log10(pupilweightpopLM2),from=-48,to=12)   
polygon(c(-48,a$x,12), c(0,a$y,0), col=addalpha(colpalmod[3],0.5),border=NA)

a <- density(20*log10(pupilweightpopS2),from=-48,to=12)   
polygon(c(-48,a$x,12), c(0,a$y,0), col=addalpha(colpalmod[4],0.5),border=NA)

prior <- dnorm(10^((-48:12)/20),1,0.5)
prior <- 0.5*prior/max(prior)
lines(-48:12,prior)

lines(20*log10(c(mean(pupilWLum2),mean(pupilWLum2))),c(0,0.6),lwd=3,col=colpalmod[1])
lines(20*log10(c(mean(pupilWMel2),mean(pupilWMel2))),c(0,0.6),lwd=3,col=colpalmod[2])
lines(20*log10(c(mean(pupilWLM2),mean(pupilWLM2))),c(0,0.6),lwd=3,col=colpalmod[3])
lines(20*log10(c(mean(pupilWS2),mean(pupilWS2))),c(0,0.6),lwd=3,col=colpalmod[4])

legend(-24,0.6,c('Prior','Lum 2F', 'Mel 2F', 'LM 2F', 'S 2F'),col=c('black',colpalmod[1:4]),lwd=c(1,3,3,3,3),lty=1, cex=1.5, box.lwd=2, bg='white')

text(10,0.58,'(j)',adj=0.5,cex=2.5)

dev.off()

}

```

We fitted a computational model to the data from Experiments 1, 2, 3 and 4 using a hierarchical Bayesian approach. The model behaviour is displayed in Figure \@ref(fig:modfig)a-d for the first harmonic frequency and in Figure \@ref(fig:modfig)f-i for the second harmonic frequency. The empirical data is superimposed for comparison. In general, the model captures the key characteristics of the empirical data, with group-level parameter estimates provided in Tables \@ref(tab:paramtable1F) and \@ref(tab:paramtable2F) for the first and second harmonic frequencies respectively. We were particularly interested in comparing the weight of interocular suppression across data sets. We therefore plot the posterior distributions for this parameter for all four data sets (see Figure \@ref(fig:modfig)e for the distributions at the first harmonic and Figure \@ref(fig:modfig)j for the distributions at the second harmonic).

```{r modfig, fig.cap="Summary of computational modelling. Panels (a-d) and (f-i) show empirical data from key conditions at the first and the second harmonic frequencies respectively. The data are replotted from earlier figures for the luminance experiment at the first (a) and the second (f) harmonic frequencies, the melanopsin experiment at the first (b) and the second (g) harmonic frequencies, the L-M pathway experiment at the first (c) and the second (h) harmonic frequencies, and the S-(L+M) pathway experiment at the first (d) and the second (i) harmonic frequencies. The curves show model behaviour generated using the median group-level parameter values. Panels (e) and (j) show the posterior probability distributions of the interocular suppression parameter for each of the four model fits at the first and the second harmonic frequencies respectively. In panel (e), the luminance distribution (grey) is centred about a substantially lower suppressive weight than for the other data types (note the logarithmic x-axis), while the L-M distribution (red) is centred about a higher suppressive weight than for the other data types. On the other hand, in panel (j), the L-M distribution is centred about a substantially lower suppressive weight than for the other data types, while it is the S-(L+M) distribution (blue) that is centred about a higher suppressive weight than for the other data types. The black curves show the (scaled) prior distribution for the weight parameter.", fig.align="center", echo=FALSE}

knitr::include_graphics(paste0(figdir,'modelfigurechap4.pdf'))

```

At the first harmonic, the key finding is that the luminance results (grey distribution) display a much smaller weight of interocular suppression than the other data sets. The melanopsin and S-(L+M) results (gold and blue distributions) display a similar weight of interocular suppression. The L-M results (red distribution) display the greatest weight of interocular suppression of all data sets. There is minimal overlap between the luminance distribution and the other three distributions. For the luminance, the distribution is meaningfully below a weight of 1, while it is well above a weight of 1 for the L-M results. The distributions of melanopsin and S-(L+M) are around a weight of 1. These results offer an explanation of the empirical data: the weaker suppression for the luminance experiment is consistent with the weaker suppression effects and the weaker dichoptic masking, while the stronger suppression for the L-M experiment is consistent with the stronger suppression observed at the first harmonic and the stronger dichoptic masking.

At the second harmonic, the key finding is that the S-(L+M) results display a greater weight of interocular suppression compared to the other data sets. On the other hand, the L-M results display the smallest weight of interocular suppression. The luminance and melanopsin results display weights of interocular suppression that are quite close to each other. For the L-M results, the distribution is meaningfully below a weight of 1, while it is well above a weight of 1 for the S-(L+M) results. The distributions of luminance and melanospin are around a weight of 1, with the former being slightly below and the latter being slightly above. These results offer an explanation of the empirical data: the weaker suppression for the L-M experiment is consistent with the weaker suppression effects and the weaker dichoptic masking observed at the second harmonic, while the stronger suppression for the S-(L+M) experiment is consistent with the stronger suppression observed at the second harmonic and the stronger dichoptic masking.

```{r paramtable1F, echo=FALSE}

condnames <- c('Luminance 1F', 'Melanopsin 1F', 'L-M 1F', 'S 1F')
zlist <- c(pupilZLum, pupilZMel, pupilZLM, pupilZS)
klist <- c(pupilKLum, pupilKMel, pupilKLM, pupilKS)
wlist <- c(pupilWLum, pupilWMel, pupilWLM, pupilWS)
plist <- c(pupilPLum, pupilPMel, pupilPLM, pupilPS)
qlist <- c(pupilQLum, pupilQMel, pupilQLM, pupilQS)
Rlist <- c(round(c(pupilRmaxLum, pupilRmaxMel, pupilRmaxLM, pupilRmaxS),5))
tabledata <- data.frame(condnames,round(zlist,digits=2),round(klist,digits=2),round(wlist,digits=2),round(plist,digits=2),round(qlist,digits=2),Rlist)

colnames(tabledata) <- c('Experiment','Z','k','w','p','q','Rmax')
kable(tabledata, align='lcccccc',caption = 'Summary of median parameter values at the first harmonic frequency.')

```

```{r paramtable2F, echo=FALSE}

condnames <- c('Luminance 2F', 'Melanopsin 2F', 'L-M 2F', 'S 2F')
zlist <- c(pupilZLum2, pupilZMel2, pupilZLM2, pupilZS2)
klist <- c(pupilKLum2, pupilKMel2, pupilKLM2, pupilKS2)
wlist <- c(pupilWLum2, pupilWMel2, pupilWLM2, pupilWS2)
plist <- c(pupilPLum2, pupilPMel2, pupilPLM2, pupilPS2)
qlist <- c(pupilQLum2, pupilQMel2, pupilQLM2, pupilQS2)
Rlist <- c(round(c(pupilRmaxLum2, pupilRmaxMel2, pupilRmaxLM2, pupilRmaxS2),5))
tabledata <- data.frame(condnames,round(zlist,digits=2),round(klist,digits=2),round(wlist,digits=2),round(plist,digits=2),round(qlist,digits=2),Rlist)

colnames(tabledata) <- c('Experiment','Z','k','w','p','q','Rmax')
kable(tabledata, align='lcccccc',caption = 'Summary of median parameter values at the second harmonic frequency.')

```

## Phase analysis

```{r makephaseplots, include=FALSE, results='hide'}

# generate plots showing the phase angles
if (processdata > 0){

load(file=paste0(datadir,'AveragedataLum.RData'))
xlum <- Re(cleanmeansP)
ylum <- Im(cleanmeansP)
xlum2 <- Re(cleanmeansP2)
ylum2 <- Im(cleanmeansP2)
load(file=paste0(datadir,'AveragedataMel.RData'))
xmel <- Re(cleanmeansP)
ymel <- Im(cleanmeansP)
xmel2 <- Re(cleanmeansP2)
ymel2 <- Im(cleanmeansP2)
load(file=paste0(datadir,'AveragedataLM.RData'))
xlm <- Re(cleanmeansP)
ylm <- Im(cleanmeansP)
xlm2 <- Re(cleanmeansP2)
ylm2 <- Im(cleanmeansP2)
load(file=paste0(datadir,'AveragedataS.RData'))
xs <- Re(cleanmeansP)
ys <- Im(cleanmeansP)
xs2 <- Re(cleanmeansP2)
ys2 <- Im(cleanmeansP2)

pdf(paste(figdir,"phaseplots.pdf",sep=''), bg="transparent", height = 10, width = 10)

par(mfrow=c(2,2),mar=c(1,1,1,1))

plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-0.02,0.02), ylim=c(-0.02,0.02))

rangles <- seq(0,360)*(pi/180)
r <- seq(0.005,0.02,0.005)
for (n in 1:length(r)){
  lines(r[n]*cos(rangles),r[n]*sin(rangles),col='gray')
}
lines(c(0,0),c(-0.02,0.02),lwd=2)
lines(c(-0.02,0.02),c(0,0),lwd=2)

text(0.015,0.001,'Amplitude',cex=1.25,adj=0.5)
text(0.021,0,'Phase',cex=1.25,adj=0.5,srt=-90)

lines(xlum[1,]/10,ylum[1,]/10,col='black',lwd=3)
points(xlum[1,]/10,ylum[1,]/10,pch=21,col='black',bg='white',cex=2,lwd=3)

lines(xmel[1,],ymel[1,],col='grey',lwd=3)
points(xmel[1,],ymel[1,],pch=21,col='grey',bg='cornflowerblue',cex=2,lwd=3)

lines(xlm[1,],ylm[1,],col='darkgreen',lwd=3)
points(xlm[1,],ylm[1,],pch=21,col='darkgreen',bg='red',cex=2,lwd=3)

lines(xs[1,],ys[1,],col='blue',lwd=3)
points(xs[1,],ys[1,],pch=21,col='blue',bg='gold',cex=2,lwd=3)

legend(-0.0175,0.0155,c('Luminance','Melanopsin','L-M','S'),lty=1,col=c('black','grey','darkgreen','blue'),lwd=3,pch=21,pt.cex=2,pt.bg=c('white','cornflowerblue','red','gold'),cex=1.4,box.lwd=3,bg='white')

text(-0.019,0.019,'(a)',cex=3)
text(0.016,0.019,'Mon 1F',cex=2.5)

plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-0.02,0.02), ylim=c(-0.02,0.02))

rangles <- seq(0,360)*(pi/180)
r <- seq(0.005,0.02,0.005)
for (n in 1:length(r)){
  lines(r[n]*cos(rangles),r[n]*sin(rangles),col='gray')
}
lines(c(0,0),c(-0.02,0.02),lwd=2)
lines(c(-0.02,0.02),c(0,0),lwd=2)

text(0.015,0.001,'Amplitude',cex=1.25,adj=0.5)
text(0.021,0,'Phase',cex=1.25,adj=0.5,srt=-90)

lines(xlum[2,]/10,ylum[2,]/10,col='black',lwd=3)
points(xlum[2,]/10,ylum[2,]/10,pch=22,col='black',bg='white',cex=2,lwd=3)

lines(xmel[2,],ymel[2,],col='grey',lwd=3)
points(xmel[2,],ymel[2,],pch=22,col='grey',bg='cornflowerblue',cex=2,lwd=3)

lines(xlm[2,],ylm[2,],col='darkgreen',lwd=3)
points(xlm[2,],ylm[2,],pch=22,col='darkgreen',bg='red',cex=2,lwd=3)

lines(xs[2,],ys[2,],col='blue',lwd=3)
points(xs[2,],ys[2,],pch=22,col='blue',bg='gold',cex=2,lwd=3)

text(-0.019,0.019,'(b)',cex=3)
text(0.016,0.019,'Bin 1F',cex=2.5)

plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-0.02,0.02), ylim=c(-0.02,0.02))

rangles <- seq(0,360)*(pi/180)
r <- seq(0.005,0.02,0.005)
for (n in 1:length(r)){
  lines(r[n]*cos(rangles),r[n]*sin(rangles),col='gray')
}
lines(c(0,0),c(-0.02,0.02),lwd=2)
lines(c(-0.02,0.02),c(0,0),lwd=2)

text(0.015,0.001,'Amplitude',cex=1.25,adj=0.5)
text(0.021,0,'Phase',cex=1.25,adj=0.5,srt=-90)

lines(xlum2[1,],ylum2[1,],col='black',lwd=3)
points(xlum2[1,],ylum2[1,],pch=21,col='black',bg='white',cex=2,lwd=3)

lines(xmel2[1,],ymel2[1,],col='grey',lwd=3)
points(xmel2[1,],ymel2[1,],pch=21,col='grey',bg='cornflowerblue',cex=2,lwd=3)

lines(xlm2[1,],ylm2[1,],col='darkgreen',lwd=3)
points(xlm2[1,],ylm2[1,],pch=21,col='darkgreen',bg='red',cex=2,lwd=3)

lines(xs2[1,],ys2[1,],col='blue',lwd=3)
points(xs2[1,],ys2[1,],pch=21,col='blue',bg='gold',cex=2,lwd=3)

text(-0.019,0.019,'(c)',cex=3)
text(0.016,0.019,'Mon 2F',cex=2.5)

plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-0.02,0.02), ylim=c(-0.02,0.02))

rangles <- seq(0,360)*(pi/180)
r <- seq(0.005,0.02,0.005)
for (n in 1:length(r)){
  lines(r[n]*cos(rangles),r[n]*sin(rangles),col='gray')
}
lines(c(0,0),c(-0.02,0.02),lwd=2)
lines(c(-0.02,0.02),c(0,0),lwd=2)

text(0.015,0.001,'Amplitude',cex=1.25,adj=0.5)
text(0.021,0,'Phase',cex=1.25,adj=0.5,srt=-90)

lines(xlum2[2,],ylum2[2,],col='black',lwd=3)
points(xlum2[2,],ylum2[2,],pch=22,col='black',bg='white',cex=2,lwd=3)

lines(xmel2[2,],ymel2[2,],col='grey',lwd=3)
points(xmel2[2,],ymel2[2,],pch=22,col='grey',bg='cornflowerblue',cex=2,lwd=3)

lines(xlm2[2,],ylm2[2,],col='darkgreen',lwd=3)
points(xlm2[2,],ylm2[2,],pch=22,col='darkgreen',bg='red',cex=2,lwd=3)

lines(xs2[2,],ys2[2,],col='blue',lwd=3)
points(xs2[2,],ys2[2,],pch=22,col='blue',bg='gold',cex=2,lwd=3)

text(-0.019,0.019,'(d)',cex=3)
text(0.016,0.019,'Bin 2F',cex=2.5)

dev.off()

}

```

```{r phaseplots, fig.cap="Pupil phase plots at the first and second harmonic frequencies for the luminance, melanopsin, L-M pathway and the S-(L+M) pathway experiments. Panel (a) shows the pupil response during monocular stimulation at the first harmonic frequency. Panel (b) shows the pupil response during binocular stimulation at the first harmonic frequency. Panel (c) shows the pupil response during monocular stimulation at the second harmonic frequency. Panel (d) shows the pupil response during binocular stimulation at the second harmonic frequency. In panels (a) and (b), the luminance amplitudes have been scaled down by a factor of 10 to be compared with the other experiments' results.", fig.align="center", echo=FALSE}

knitr::include_graphics(paste0(figdir,'phaseplots.pdf'))

```

In a previous study, @Spitschan2014 analysed the phase of the pupil response and compared it between L+M-cone stimulation, S-cone stimulation, melanopsin stimulation and brightness stimulation. In their study, they found that, at a flicker frequency of 0.5 Hz, L+M and melanopsin responses were in phase, while brightness and S-cone responses were in anti-phase. Additionally, they found that, at the second harmonic frequency, S-cone and melanospin responses seem to be in phase with each other and in anti-phase to L+M-cone responses. We reproduced this analysis with our data and the results are summarised in Figure \@ref(fig:phaseplots). At the first harmonic frequency, the amplitudes from the luminance experiment have been scaled down by a factor of 10 to make it possible to compare them directly with the results from the other experiments.

Figure \@ref(fig:phaseplots)a shows the results to monocular responses at the first harmonic frequency. The L-M pathway stimulation produces an anti-phase pupil response relative to luminance stimulation. The S-(L+M) pathway and luminance results are desynchronised in quadrature phase. This same pattern of results is also observable in Figure \@ref(fig:phaseplots)b, which summarises the results to binocular responses at the first harmonic frequency.

Figure \@ref(fig:phaseplots)c shows the results to monocular responses at the second harmonic frequency. Here, results are noisier compare to the first harmonic results, but a pattern is still observable. In general, it seems that melanopsin and S-(L+M) stimulations produce in-phase responses to each other, but produce anti-phase responses to luminance stimulation. On the other hand, L-M pathway responses seem to be desynchronised in quadrature phase from the the results of the other experiments. The same pattern of results is also observable in Figure \@ref(fig:phaseplots)d, which summarises the results to binocular responses at the second harmonic frequency.

# Discussion

We used pupillometry and silent substitution to measure monocular and binocular responses of the pupils to flickering stimuli when stimulating specific photoreceptor pathways. In our luminance experiment, we found that peripheral stimulation of the retina can elicit a pupillary response and we were also able to record a response at the second harmonic, which was not seen when we stimulated the fovea [@Segala2023]. In all four experiments, we were able to record contrast response functions at both the first and the second harmonics. All experiments showed that binocular combination in the autonomic nervous system happens in a non-linear manner, with evidence of different magnitudes of interocular suppression depending on the photoreceptor pathway. This pattern of results was confirmed by a computational model, which allowed us to compare the weight of interocular suppression for each pathway. We found that, at the first harmonic frequency, the L-M pathway had a bigger suppression weight than the other pathways, while, at the second harmonic frequency, the S-(L+M) pathway had a bigger suppression weight. Finally, we looked at the pupil phases and observed different behaviours for the different pathways at the first and second harmonic frequencies. While the patterns differed between the first and second harmonics, within the same harmonic, whether the stimuli were presented monocularly or binocularly, the patterns were similar.

Our four experiments produced results that we were expecting based on our previous pupillometry findings [@Segala2023]: the signals between the 2 pupils are combined non-linearly regardless of which photoreceptor pathway is being stimulated and whether the fovea or the periphery of the retina is being stimulated. We also observed responses at both the first and the second harmonic frequencies, which were expected based on previous literature [@Spitschan2014; @Stark1957; @Verdon1988]. There was, however, one aspect of our results that we were surprised to observe: the amplitude of this second harmonic response in the different photoreceptor pathways. It is true that we had already observed second harmonic responses when stimulating the periphery of the retina with achromatic luminance modulations flickering at 2 Hz (see Figure \@ref(fig:appendixfig1)b), but the peak was very small when compared to the first harmonic peak, which is similar to what we observed in the luminance experiment here. On the other hand, in the melanopsin and L-M pathway experiments, the first and second harmonics are similar in amplitudes, and in the S-(L+M) pathway experiment, the peak of the second harmonic is even bigger than the peak of the first harmonic. One reason for why this might be happening may be because the driving signal is stronger when using a lower flicker frequency [indeed, pupillometry is more responsive to slow flicker frequencies of less than 1 Hz, @Spitschan2014] and when stimulating the periphery of the retina (we have a very clear waveform for the luminance experiment in Figure \@ref(fig:pupildataLum)b). However, this explanation is not entirely satisfactory: we observed a second harmonic when stimulating the periphery using a higher flicker frequency and the pupil waveforms from the other three experiments are not as clear as the one from the luminance experiment. The presence of a second harmonic might indicate the existence of non-linearities that are not observable in the fovea: indeed, steady-state visual responses can contain activity beyond the first harmonic and these harmonics reflect non-linearities (e.g. squaring, exponentiation, rectification) in the visual response [@Norcia2015]. Additionally, it can be the case that, when these non-linearities are strong, then the higher harmonics can have equal or even higher peaks than the first harmonic. Here, we did observe strong non-linearities in our photoreceptor pathways, as reflected by the interocular suppression weights that were output by our computational model. For the S-(L+M) pathway specifically, it seems that the higher peak of the second harmonic is a behaviour intrinsic to S cones, as this was observed previously [@Spitschan2014].

The pupil phases shown in Figure \@ref(fig:phaseplots) give us more information about the pathways controlling the pupil response. The first thing that we  notice is that the luminance and L-M pathway responses are in anti-phase. It is important to note that, for our L-M pathway stimulation, the stimulus flickered between magenta (first half of the cycle) and cyan (second half of the cycle), which means that the pupil was dilating during the magenta stimulation and then constricting during the cyan presentation. This seems to suggest that increments in magenta would correspond to decrements in brightness and increments in cyan would correspond to increments in brightness. It is possible that, if we had reversed the presentation cycle for the L-M pathway, the pupil response would have been in phase with the luminance responses. It has been recently shown that L-cone and melanopsin stimulation induce an opponent pupillary response to M- and S-cone stimulation [@Murray2018; @Woelders2018]. Our melanopsin and S-(L+M) results show a similar behaviour both for monocular and binocular responses. The L-M pathways results are desynchronised approximately in quadrature phase from the melanopsin and S-(L+M) results. These results also seem to align with what was previously found: combining L and M responses should display results that are between the opponency shown by the isolated cone stimulation. Additionally, this could explain the very strong suppression that binocular (L-M) stimulation displays compared to the monocular stimulation: if L and M produce pupil responses that are in anti-phase with each other, then combining the two together should elicit smaller responses. Finally, since the results from our experiments are not in phase, it would suggest that the photoreceptors control the pupil diameter through different pathways.

# Conclusions

We have demonstrated that binocular combination of temporal flickering light in the autonomic nervous system depends on the photoreceptor pathway. We were able to elicit pupil responses by stimulating only the periphery of the retina and we were able to record contrast response functions for all photoreceptor pathways. While all pathways showed non-linear combination, they showed a variation in how the signals are combined, particularly in the weight of interocular suppression.

# Acknowledgements

Supported by Biotechnology and Biological Sciences Research Council grant BB/V007580/1 awarded to DHB and ARW.

# References

### 2024-01-11 manuscript.Rmd
Added osf download commands

@@
 colpalmod <- c('#808080','#8B8000','#FE5000','#8783CF')
-targetelectrodes <- c('Oz','POz','O1','O2')
 
@@
 
-# (download and) analyse individual participant data for the luminance condition
+# (download and) analyse individual participant data for the luminance experiment
 if (processdata > 2){
 
-  for(p in 601:612){
-    participant <- paste0('P',p)
+  for(participant in 1:24){
+
+    # only download and process data if this has not been done already for this participant
+    if (!file.exists(paste0(datadir,'P',600+participant,'summary.RData'))){
+
+      # if there is no directory for this participant's data
+      if (!file.exists(paste0(rawdir,'P',600+participant))){
+        dir.create(paste0(rawdir,'P',600+participant))
+
+       d <- dir(paste0(rawdir,'P',600+participant))
+
+       if (length(d)==0){
+
+         # if the tar file of this participant's data doesn't exist
+         if (!file.exists(paste0(rawdir,'P',600+participant,'.zip'))){
+           # download it from OSF
+           if (!exists('osffiles')){
+           osfnode <- '6u7db'
+           osfproject <- osf_retrieve_node(osfnode)
+          osffiles <- osf_ls_files(osfproject,n_max=300)}
+          fid <- which(osffiles$name==paste0('P',600+participant,'.zip'))
+          osf_download(osffiles[fid,],rawdir,progress=TRUE)
+         }
+
+         # then unzip the tar file
+         unzip(paste0(rawdir,'P',600+participant,'.zip'),exdir=paste0(rawdir))
+
+         # and delete the tar file to save storage space
+         file.remove(paste0(rawdir,'P',600+participant,'.zip'))
+       }
+      }
+
+      d <- dir(paste0(rawdir,'P',600+participant),full.names=TRUE)
 
@@
     repcounterP <- (1:60)*0
-    d <- dir(paste0(rawdir,participant),pattern='*annotations.csv',full.names=TRUE)
-
-    for (block in 1:length(d)){
+    afiles <- dir(path=paste0(rawdir,'P',600+participant),pattern='*annotations.csv',full.names=TRUE)
+
+    for (block in 1:length(afiles)){
         tic()
-        adata <- read.csv(paste0(rawdir,participant,'/',paste0(participant,'_S',block),'_annotations.csv'))
+        adata <- read.csv(paste0(rawdir,'P',600+participant,'/',paste0('P',600+participant,'_S',block),'_annotations.csv'))
 
@@
 
-        pdata <- read.csv(paste(rawdir,participant,'/',paste0(participant,'_S',block),'_pupil_positions.csv',sep=''))
+        pdata <- read.csv(paste(rawdir,'P',600+participant,'/',paste0('P',600+participant,'_S',block),'_pupil_positions.csv',sep=''))
         pdata2 <- pdata[,c(1,3,4,14)]
@@
     meanspectraP <- apply(pupilspectra[,,c(15,20),],4,mean,na.rm=TRUE)
-    save(file=paste(datadir,participant,'_summaryLum.RData',sep=''),list=c('cleanmeansP','cleanmasksP','cleanmeansP2','cleanmasksP2','meanspectraP','meanwavesP'))
-  }
-
-  }
+    save(file=paste(datadir,'P',600+participant,'_summaryLum.RData',sep=''),list=c('cleanmeansP','cleanmasksP','cleanmeansP2','cleanmasksP2','meanspectraP','meanwavesP'))
+
+    if (cleanupraw==1){file.remove(d)} # delete raw data files to save space
+  }
+
+  }}
 ```
@@
 if (processdata > 1){
+  for (participant in 1:24){
+         # if the summary file of this participant's data doesn't exist
+         if (!file.exists(paste0(datadir,'P',600+participant,'summaryLum.RData'))){
+           # download it from OSF
+           if (!exists('osffilesP')){
+           osfnode <- '9ebtd'
+           osfproject <- osf_retrieve_node(osfnode)
+          osffilesP <- osf_ls_files(osfproject,n_max=300)}
+          fid <- which(osffilesP$name==paste0('P',600+participant,'summaryLum.RData'))
+          osf_download(osffilesP[fid,],datadir,progress=TRUE)
+         }
+}
 
@@
 
+# generate plot showing the group pupillometry data for the luminance experiment
+
+         if (!file.exists(paste0(datadir,'AveragedataLum.RData'))){
+           # download it from OSF
+           if (!exists('osffilesP')){
+           osfnode <- '9ebtd'
+           osfproject <- osf_retrieve_node(osfnode)
+          osffilesP <- osf_ls_files(osfproject,n_max=300)}
+          fid <- which(osffilesP$name=='AveragedataLum.RData')
+          osf_download(osffilesP[fid,],datadir,progress=TRUE)
+         }
+
 load(file=paste0(datadir,'AveragedataLum.RData'))
 
-# generate plot showing the group pupillometry data for the luminance condition
 if (processdata > 0){
@@
 
-# (download and) analyse individual participant data for the melanopsin condition
+# (download and) analyse individual participant data for the melanopsin experiment
 if (processdata > 2){
 
-  for(p in 501:512){
-    participant <- paste0('P',p)
+  for(participant in 1:24){
+
+    # only download and process data if this has not been done already for this participant
+    if (!file.exists(paste0(datadir,'P',500+participant,'summary.RData'))){
+
+      # if there is no directory for this participant's data
+      if (!file.exists(paste0(rawdir,'P',500+participant))){
+        dir.create(paste0(rawdir,'P',500+participant))
+
+       d <- dir(paste0(rawdir,'P',500+participant))
+
+       if (length(d)==0){
+
+         # if the tar file of this participant's data doesn't exist
+         if (!file.exists(paste0(rawdir,'P',500+participant,'.zip'))){
+           # download it from OSF
+           if (!exists('osffiles')){
+           osfnode <- 'xkgd9'
+           osfproject <- osf_retrieve_node(osfnode)
+          osffiles <- osf_ls_files(osfproject,n_max=300)}
+          fid <- which(osffiles$name==paste0('P',500+participant,'.zip'))
+          osf_download(osffiles[fid,],rawdir,progress=TRUE)
+         }
+
+         # then unzip the tar file
+         unzip(paste0(rawdir,'P',500+participant,'.zip'),exdir=paste0(rawdir))
+
+         # and delete the tar file to save storage space
+         file.remove(paste0(rawdir,'P',500+participant,'.zip'))
+       }
+      }
+
+      d <- dir(paste0(rawdir,'P',500+participant),full.names=TRUE)
 
@@
     repcounterP <- (1:60)*0
-    d <- dir(paste0(rawdir,participant),pattern='*annotations.csv',full.names=TRUE)
-
-    for (block in 1:length(d)){
+    afiles <- dir(path=paste0(rawdir,'P',500+participant),pattern='*annotations.csv',full.names=TRUE)
+
+    for (block in 1:length(afiles)){
         tic()
-        adata <- read.csv(paste0(rawdir,participant,'/',paste0(participant,'_S',block),'_annotations.csv'))
+        adata <- read.csv(paste0(rawdir,'P',500+participant,'/',paste0('P',500+participant,'_S',block),'_annotations.csv'))
 
@@
 
-        pdata <- read.csv(paste(rawdir,participant,'/',paste0(participant,'_S',block),'_pupil_positions.csv',sep=''))
+        pdata <- read.csv(paste(rawdir,'P',500+participant,'/',paste0('P',500+participant,'_S',block),'_pupil_positions.csv',sep=''))
         pdata2 <- pdata[,c(1,3,4,14)]
@@
     meanspectraP <- apply(pupilspectra[,,c(15,20),],4,mean,na.rm=TRUE)
-    save(file=paste(datadir,participant,'_summaryMel.RData',sep=''),list=c('cleanmeansP','cleanmasksP','cleanmeansP2','cleanmasksP2','meanspectraP','meanwavesP'))
-    }
-  }
+    save(file=paste(datadir,'P',500+participant,'_summaryMel.RData',sep=''),list=c('cleanmeansP','cleanmasksP','cleanmeansP2','cleanmasksP2','meanspectraP','meanwavesP'))
+
+    if (cleanupraw==1){file.remove(d)} # delete raw data files to save space
+    }
+  }}
 ```
@@
 if (processdata > 1){
+  for (participant in 1:24){
+         # if the summary file of this participant's data doesn't exist
+         if (!file.exists(paste0(datadir,'P',500+participant,'summaryMel.RData'))){
+           # download it from OSF
+           if (!exists('osffilesP')){
+           osfnode <- '9ebtd'
+           osfproject <- osf_retrieve_node(osfnode)
+          osffilesP <- osf_ls_files(osfproject,n_max=300)}
+          fid <- which(osffilesP$name==paste0('P',500+participant,'summaryMel.RData'))
+          osf_download(osffilesP[fid,],datadir,progress=TRUE)
+         }
+}
 
@@
 
+# generate plot showing the group pupillometry data for the melanopsin experiment 
+if (!file.exists(paste0(datadir,'AveragedataMel.RData'))){
+           # download it from OSF
+           if (!exists('osffilesP')){
+           osfnode <- '9ebtd'
+           osfproject <- osf_retrieve_node(osfnode)
+          osffilesP <- osf_ls_files(osfproject,n_max=300)}
+          fid <- which(osffilesP$name=='AveragedataMel.RData')
+          osf_download(osffilesP[fid,],datadir,progress=TRUE)
+         }
+
 load(file=paste0(datadir,'AveragedataMel.RData'))
 
-# generate plot showing the group pupillometry data for the melanopsin experiment
 if (processdata > 0){
@@
 
-# (download and) analyse individual participant data for the L-M condition
+# (download and) analyse individual participant data for the L-M experiment
 if (processdata > 2){
 
-  for(p in 701:712){
-    participant <- paste0('P',p)
+  for(participant in 1:24){
+
+    # only download and process data if this has not been done already for this participant
+    if (!file.exists(paste0(datadir,'P',700+participant,'summary.RData'))){
+
+      # if there is no directory for this participant's data
+      if (!file.exists(paste0(rawdir,'P',700+participant))){
+        dir.create(paste0(rawdir,'P',700+participant))
+
+       d <- dir(paste0(rawdir,'P',700+participant))
+
+       if (length(d)==0){
+
+         # if the tar file of this participant's data doesn't exist
+         if (!file.exists(paste0(rawdir,'P',700+participant,'.zip'))){
+           # download it from OSF
+           if (!exists('osffiles')){
+           osfnode <- 'pexyk'
+           osfproject <- osf_retrieve_node(osfnode)
+          osffiles <- osf_ls_files(osfproject,n_max=300)}
+          fid <- which(osffiles$name==paste0('P',700+participant,'.zip'))
+          osf_download(osffiles[fid,],rawdir,progress=TRUE)
+         }
+
+         # then unzip the tar file
+         unzip(paste0(rawdir,'P',700+participant,'.zip'),exdir=paste0(rawdir))
+
+         # and delete the tar file to save storage space
+         file.remove(paste0(rawdir,'P',700+participant,'.zip'))
+       }
+      }
+
+      d <- dir(paste0(rawdir,'P',700+participant),full.names=TRUE)
 
@@
     repcounterP <- (1:60)*0
-    d <- dir(paste0(rawdir,participant),pattern='*annotations.csv',full.names=TRUE)
-
-    for (block in 1:length(d)){
+    afiles <- dir(path=paste0(rawdir,'P',700+participant),pattern='*annotations.csv',full.names=TRUE)
+
+    for (block in 1:length(afiles)){
         tic()
-        adata <- read.csv(paste0(rawdir,participant,'/',paste0(participant,'_S',block),'_annotations.csv'))
+        adata <- read.csv(paste0(rawdir,'P',700+participant,'/',paste0('P',700+participant,'_S',block),'_annotations.csv'))
 
@@
 
-        pdata <- read.csv(paste(rawdir,participant,'/',paste0(participant,'_S',block),'_pupil_positions.csv',sep=''))
+        pdata <- read.csv(paste(rawdir,'P',700+participant,'/',paste0('P',700+participant,'_S',block),'_pupil_positions.csv',sep=''))
         pdata2 <- pdata[,c(1,3,4,14)]
@@
     meanspectraP <- apply(pupilspectra[,,c(15,20),],4,mean,na.rm=TRUE)
-    save(file=paste(datadir,participant,'_summaryLM.RData',sep=''),list=c('cleanmeansP','cleanmasksP','cleanmeansP2','cleanmasksP2','meanspectraP','meanwavesP'))
-  }
-
-  }
+    save(file=paste(datadir,'P',700+participant,'_summaryLM.RData',sep=''),list=c('cleanmeansP','cleanmasksP','cleanmeansP2','cleanmasksP2','meanspectraP','meanwavesP'))
+
+    if (cleanupraw==1){file.remove(d)} # delete raw data files to save space
+  }
+
+  }}
 ```
@@
 if (processdata > 1){
+  for (participant in 1:24){
+         # if the summary file of this participant's data doesn't exist
+         if (!file.exists(paste0(datadir,'P',700+participant,'summaryLM.RData'))){
+           # download it from OSF
+           if (!exists('osffilesP')){
+           osfnode <- '9ebtd'
+           osfproject <- osf_retrieve_node(osfnode)
+          osffilesP <- osf_ls_files(osfproject,n_max=300)}
+          fid <- which(osffilesP$name==paste0('P',700+participant,'summaryLM.RData'))
+          osf_download(osffilesP[fid,],datadir,progress=TRUE)
+         }
+}
 
@@
 
+# generate plot showing the group pupillometry data for the L-M experiment
+if (!file.exists(paste0(datadir,'AveragedataLM.RData'))){
+           # download it from OSF
+           if (!exists('osffilesP')){
+           osfnode <- '9ebtd'
+           osfproject <- osf_retrieve_node(osfnode)
+          osffilesP <- osf_ls_files(osfproject,n_max=300)}
+          fid <- which(osffilesP$name=='AveragedataLM.RData')
+          osf_download(osffilesP[fid,],datadir,progress=TRUE)
+         }
+
 load(file=paste0(datadir,'AveragedataLM.RData'))
 
-# generate plot showing the group pupillometry data for the L-M experiment
 if (processdata > 0){
@@
 
-  for(p in 301:312){
-    participant <- paste0('P',p)
+  for(participant in 1:24){
+
+    # only download and process data if this has not been done already for this participant
+    if (!file.exists(paste0(datadir,'P',300+participant,'summary.RData'))){
+
+      # if there is no directory for this participant's data
+      if (!file.exists(paste0(rawdir,'P',300+participant))){
+        dir.create(paste0(rawdir,'P',300+participant))
+
+       d <- dir(paste0(rawdir,'P',300+participant))
+
+       if (length(d)==0){
+
+         # if the tar file of this participant's data doesn't exist
+         if (!file.exists(paste0(rawdir,'P',300+participant,'.zip'))){
+           # download it from OSF
+           if (!exists('osffiles')){
+           osfnode <- 'k9mdq'
+           osfproject <- osf_retrieve_node(osfnode)
+          osffiles <- osf_ls_files(osfproject,n_max=300)}
+          fid <- which(osffiles$name==paste0('P',300+participant,'.zip'))
+          osf_download(osffiles[fid,],rawdir,progress=TRUE)
+         }
+
+         # then unzip the tar file
+         unzip(paste0(rawdir,'P',300+participant,'.zip'),exdir=paste0(rawdir))
+
+         # and delete the tar file to save storage space
+         file.remove(paste0(rawdir,'P',300+participant,'.zip'))
+       }
+      }
+
+      d <- dir(paste0(rawdir,'P',300+participant),full.names=TRUE)
 
@@
     repcounterP <- (1:60)*0
-    d <- dir(paste0(rawdir,participant),pattern='*annotations.csv',full.names=TRUE)
-
-    for (block in 1:length(d)){
+    afiles <- dir(path=paste0(rawdir,'P',300+participant),pattern='*annotations.csv',full.names=TRUE)
+
+    for (block in 1:length(afiles)){
         tic()
-        adata <- read.csv(paste0(rawdir,participant,'/',paste0(participant,'_S',block),'_annotations.csv'))
+        adata <- read.csv(paste0(rawdir,'P',300+participant,'/',paste0('P',300+participant,'_S',block),'_annotations.csv'))
 
@@
 
-        pdata <- read.csv(paste(rawdir,participant,'/',paste0(participant,'_S',block),'_pupil_positions.csv',sep=''))
+        pdata <- read.csv(paste(rawdir,'P',300+participant,'/',paste0('P',300+participant,'_S',block),'_pupil_positions.csv',sep=''))
         pdata2 <- pdata[,c(1,3,4,14)]
@@
     meanspectraP <- apply(pupilspectra[,,c(15,20),],4,mean,na.rm=TRUE)
-    save(file=paste(datadir,participant,'_summaryS.RData',sep=''),list=c('cleanmeansP','cleanmasksP','cleanmeansP2','cleanmasksP2','meanspectraP','meanwavesP'))
-  }
-
-  }
+    save(file=paste(datadir,'P',300+participant,'_summaryS.RData',sep=''),list=c('cleanmeansP','cleanmasksP','cleanmeansP2','cleanmasksP2','meanspectraP','meanwavesP'))
+
+    if (cleanupraw==1){file.remove(d)} # delete raw data files to save space
+  }
+
+  }}
 ```
@@
 if (processdata > 1){
+  for (participant in 1:24){
+         # if the summary file of this participant's data doesn't exist
+         if (!file.exists(paste0(datadir,'P',300+participant,'summaryS.RData'))){
+           # download it from OSF
+           if (!exists('osffilesP')){
+           osfnode <- '9ebtd'
+           osfproject <- osf_retrieve_node(osfnode)
+          osffilesP <- osf_ls_files(osfproject,n_max=300)}
+          fid <- which(osffilesP$name==paste0('P',300+participant,'summaryS.RData'))
+          osf_download(osffilesP[fid,],datadir,progress=TRUE)
+         }
+}
 
@@
 
+# generate plot showing the group pupillometry data for the S experiment
+if (!file.exists(paste0(datadir,'AveragedataS.RData'))){
+           # download it from OSF
+           if (!exists('osffilesP')){
+           osfnode <- '9ebtd'
+           osfproject <- osf_retrieve_node(osfnode)
+          osffilesP <- osf_ls_files(osfproject,n_max=300)}
+          fid <- which(osffilesP$name=='AveragedataS.RData')
+          osf_download(osffilesP[fid,],datadir,progress=TRUE)
+         }
+
 load(file=paste0(datadir,'AveragedataS.RData'))
 
-# generate plot showing the group pupillometry data for the S experiment
 if (processdata > 0){

### 2024-01-12 manuscript.Rmd
Modified unzipping command

@@
          # then unzip the tar file
-         unzip(paste0(rawdir,'P',600+participant,'.zip'),exdir=paste0(rawdir))
+         unzip(paste0(rawdir,'P',600+participant,'.zip'),exdir=paste0(rawdir,'P',600+participant))
 
@@
          # then unzip the tar file
-         unzip(paste0(rawdir,'P',500+participant,'.zip'),exdir=paste0(rawdir))
+         unzip(paste0(rawdir,'P',500+participant,'.zip'),exdir=paste0(rawdir,'P',500+participant))
 
@@
          # then unzip the tar file
-         unzip(paste0(rawdir,'P',700+participant,'.zip'),exdir=paste0(rawdir))
+         unzip(paste0(rawdir,'P',700+participant,'.zip'),exdir=paste0(rawdir,'P',700+participant))
 
@@
          # then unzip the tar file
-         unzip(paste0(rawdir,'P',300+participant,'.zip'),exdir=paste0(rawdir))
+         unzip(paste0(rawdir,'P',300+participant,'.zip'),exdir=paste0(rawdir,'P',300+participant))
 

### 2024-01-12 manuscript.Rmd
Modified command to download individual summary.RData files as it was not working properly. Now works as it should.

@@
          # if the summary file of this participant's data doesn't exist
-         if (!file.exists(paste0(datadir,'P',600+participant,'summaryLum.RData'))){
+         if (!file.exists(paste0(datadir,'P',600+participant,'_summaryLum.RData'))){
            # download it from OSF
@@
           osffilesP <- osf_ls_files(osfproject,n_max=300)}
-          fid <- which(osffilesP$name==paste0('P',600+participant,'summaryLum.RData'))
+          fid <- which(osffilesP$name==paste0('P',600+participant,'_summaryLum.RData'))
           osf_download(osffilesP[fid,],datadir,progress=TRUE)
@@
          # if the summary file of this participant's data doesn't exist
-         if (!file.exists(paste0(datadir,'P',500+participant,'summaryMel.RData'))){
+         if (!file.exists(paste0(datadir,'P',500+participant,'_summaryMel.RData'))){
            # download it from OSF
@@
           osffilesP <- osf_ls_files(osfproject,n_max=300)}
-          fid <- which(osffilesP$name==paste0('P',500+participant,'summaryMel.RData'))
+          fid <- which(osffilesP$name==paste0('P',500+participant,'_summaryMel.RData'))
           osf_download(osffilesP[fid,],datadir,progress=TRUE)
@@
          # if the summary file of this participant's data doesn't exist
-         if (!file.exists(paste0(datadir,'P',700+participant,'summaryLM.RData'))){
+         if (!file.exists(paste0(datadir,'P',700+participant,'_summaryLM.RData'))){
            # download it from OSF
@@
           osffilesP <- osf_ls_files(osfproject,n_max=300)}
-          fid <- which(osffilesP$name==paste0('P',700+participant,'summaryLM.RData'))
+          fid <- which(osffilesP$name==paste0('P',700+participant,'_summaryLM.RData'))
           osf_download(osffilesP[fid,],datadir,progress=TRUE)
@@
          # if the summary file of this participant's data doesn't exist
-         if (!file.exists(paste0(datadir,'P',300+participant,'summaryS.RData'))){
+         if (!file.exists(paste0(datadir,'P',300+participant,'_summaryS.RData'))){
            # download it from OSF
@@
           osffilesP <- osf_ls_files(osfproject,n_max=300)}
-          fid <- which(osffilesP$name==paste0('P',300+participant,'summaryS.RData'))
+          fid <- which(osffilesP$name==paste0('P',300+participant,'_summaryS.RData'))
           osf_download(osffilesP[fid,],datadir,progress=TRUE)

### 2024-01-15 manuscript.Rmd
Updates to text and code

--- 2024-01-11 manuscript.Rmd
@@
 ---
-title: 'Chapter 4: Binocular combination in the Autonomic Nervous System'
+title: 'Binocular combination in the autonomic nervous system'
 author: |
- | Federico G. Segala$^1$, Joel T. Martin$^1$, Alex R. Wade$^1,2$ & Daniel H. Baker$^1,2$
+ | Federico G. Segala$^1$, Joel T. Martin$^1$, Annie Y. Morsi$^1$, Alex R. Wade$^{1,2}$ & Daniel H. Baker$^{1,2}$
 output:
@@
     toc: no
+    keep_tex: true
   html_document: default
@@
 
-processdata <- 0  # this flag determines the amount of processing, with 4 levels:
+processdata <- 1  # this flag determines the amount of processing, with 4 levels:
 # 0 - do no processing, generate the pdf using existing versions of all figures
@@
 # 2 - average data across participants, do bootstrapping
-# 3 - download all raw data and analyse (requires 48GB of storage)
-cleanupraw <- 0  # if downloading raw data, delete once processed to save space
+# 3 - download all raw data and analyse (requires 56GB of storage)
 
@@
 SDthresh <<- 3
-SDthreshcond <- 1.85
 nbootstraps <<- 1000
-legaltriggers <- 1:55
-targetelectrodes1 <- c('POz','POz')
 
 # check which packages are installed, install the missing ones, and activate
-packagelist <- c('knitr','remotes','tictoc','R.matlab','bookdown','grImport','png','tiff','pals','ez','gtools','signal','boot','quickpsy','rstan','rstatix','coda','parallel','utils','osfr','ggplot2','grid','gridExtra','cowplot','ggsignif') # list of CRAN packages
+packagelist <- c('knitr','remotes','tictoc','R.matlab','bookdown','grImport','png','tiff','pals','ez','gtools','signal','boot','quickpsy','rstan','bayestestR','rstatix','coda','parallel','utils','osfr','ggplot2','grid','gridExtra','cowplot','ggsignif','osfr') # list of CRAN packages
 
@@
 # settings for sampler 
-numSavedSteps <- 100000    # total number of MCMC steps
+numSavedSteps <- 10000    # total number of MCMC steps
 adaptSteps <- 1000  # Number of steps to "tune" the samplers
@@
 addalpha <- function(col, alpha=1){apply(sapply(col, col2rgb)/255, 2, function(x) rgb(x[1], x[2], x[3], alpha=alpha))}
-
-v4Interp <- function(df, xo, yo, rmax = .75, gridRes = 67) {
-  ## Create a function to perform Matlab's v4 interpolation.
-  ## Takes as input a data-frame with columns x, y, and z (x co-ordinates, y co-ordinates, and amplitude)
-  ## and variables xo and yo, the co-ordinates which will be use to create a grid for interpolation
-  xo <- matrix(rep(xo,length(yo)),nrow = length(xo),ncol = length(yo))
-  yo <- t(matrix(rep(yo,length(xo)),nrow = length(yo),ncol = length(xo)))
-  xy <- df$x + df$y*sqrt(as.complex(-1))
-  d <- matrix(rep(xy,length(xy)),nrow = length(xy), ncol = length(xy))
-  d <- abs(d - t(d))
-  diag(d) <- 1
-  g <- (d^2) * (log(d)-1)   # Green's function.
-  diag(g) <- 0
-  weights <- qr.solve(g,df$z)
-  xy <- t(xy)
-  outmat <- matrix(nrow = gridRes,ncol = gridRes)
-  for (i in 1:gridRes){
-    for (j in 1:gridRes) {
-      test4 <- abs((xo[i,j] + sqrt(as.complex(-1))*yo[i,j]) - xy)
-      g <- (test4^2) * (log(test4)-1)
-      outmat[i,j] <- g %*% weights}}
-  outDf <- data.frame(x = xo[,1],outmat)
-  names(outDf)[1:length(yo[1,])+1] <- yo[1,]
-  return(outDf)}
 
@@
 
-if (processdata==2){
-# if we're going to need the pre-processed files, extract from zip file
-  if (!file.exists(paste0(datadir,'P101summary.RData'))){
-   if (file.exists('resources/allprocessed.zip')){file.copy('resources/allprocessed.zip',localdir)}
-   if (!file.exists('resources/allprocessed.zip')){ 
-          osfnode <- '2qu6y'
-          osfproject <- osf_retrieve_node(osfnode)
+# these are approximate values for isolumiant red, green, blue and yellow
+stimcolours <- c(rgb(0.02,0.02,0.02),rgb(0.98,0.98,0.98),rgb(0,0.61,0.5),rgb(1,0.39,0.5),rgb(0.35,0.63,0),rgb(0.65,0.37,1),'grey','cornflowerblue')
+
+if (processdata>2){
+  # check if raw data are present locally, and download if not
+  nodelist <- c('6u7db','xkgd9','pexyk','k9mdq')  # list of OSF nodes containing raw data
+  for (expt in 1:4){
+    osfproject <- osf_retrieve_node(nodelist[expt])
     osffiles <- osf_ls_files(osfproject,n_max=300)
-          fid <- which(osffiles$name=='allprocessed.zip')
-          osf_download(osffiles[fid,],localdir,progress=TRUE)
-   }
-          unzip(paste0(localdir,'allprocessed.zip'),exdir=localdir)
-          d <- dir(paste0(localdir,'allprocessed'),full.names=TRUE)
-          file.copy(d,datadir)
-  }
-}
+    for (f in 1:nrow(osffiles)){
+      fname <- osffiles$name[f]
+      foldername <- strsplit(fname,'.',fixed=TRUE)[[1]][1]
+      if (!dir.exists(paste0(rawdir,foldername))){
+        osf_download(osffiles[f,],localdir,progress=TRUE)
+        dir.create(paste0(rawdir,foldername))
+        unzip(paste0(localdir,fname),exdir=paste0(rawdir,foldername))
+        file.remove(paste0(localdir,fname))
+      }
+    }
+  }
+}
+
+# if (processdata==2){
+# # if we're going to need the pre-processed files, extract from zip file
+#   if (!file.exists(paste0(datadir,'P101summary.RData'))){
+#    if (file.exists('resources/allprocessed.zip')){file.copy('resources/allprocessed.zip',localdir)}
+#    if (!file.exists('resources/allprocessed.zip')){ 
+#           osfnode <- '2qu6y'
+#           osfproject <- osf_retrieve_node(osfnode)
+#           osffiles <- osf_ls_files(osfproject,n_max=300)
+#           fid <- which(osffiles$name=='allprocessed.zip')
+#           osf_download(osffiles[fid,],localdir,progress=TRUE)
+#    }
+#           unzip(paste0(localdir,'allprocessed.zip'),exdir=localdir)
+#           d <- dir(paste0(localdir,'allprocessed'),full.names=TRUE)
+#           file.copy(d,datadir)
+#   }
+# }
 
@@
 
-$^1$Department of Psychology, University of York, York, UK. YO10 5DD  
-$^2$York Biomedical Research Institute, University of York, York, United Kingdom
+$^1$Department of Psychology, University of York, Heslington, York, United Kingdom.
+
+$^2$York Biomedical Research Institute, University of York, Heslington, York, United Kingdom.
 
@@
 
-# Abstract
-
-The size of the pupils changes in response to levels of ambient light and is regulated by the autonomic nervous system.
-The role of the retinal photoreceptors in determining pupil size has been investigated using silent substitution.
-They have been shown to be directly involved in controlling and maintaining the size of the pupils, with the cones and rods driving the initial constriction and the intrinsically photosensitive retinal ganglion cells maintaining the size over prolonged time periods.
-Here, we used silent substitution and pupillometry to investigate binocular combination while targeting the intrinsically-photoreceptive retinal ganglion cells, the L-M pathway and the S-(L+M) pathway.
-We found that the signals between the two pupils are combined in a non-linear manner when targeting all the different photoreceptor classes and that the non-linear combination was different between each class, as reflected by the different magnitudes of interocular suppression measured for each pathway.
-
-# Introduction
-
-The autonomic nervous system regulates many involuntary bodily processes, including the constriction and dilation of the pupils in response to light [@McDougal2015].
-The anatomical pathway from the retina to the subcortical nuclei controlling the pupillary light response (PLR) is well established: it includes the Pretectal Olivary nucleus (PON), the Superior Cervical ganglion and the Edinger-Westphal nucleus, which project to the iris sphincter muscles that directly control the pupil size [@McDougal2008; @McDougal2015; @Wang2015].
-Additionally, the retinal photoreceptors (cones, rods and the recently discovered melanopsin-containing intrinsically photosensitive retinal ganglion cells, ipRGCs) have been shown to be directly involved in controlling and maintaining the size of the pupils [@Barrionuevo2014; @Barrionuevo2018; @Dacey2005; @Murray2018; @Spitschan2014; @Spitschan2019; @Woelders2018].
-The cones have been shown to drive the initial rapid constriction of the pupils [@Mathot2018], while the slower and longer activation of the ipRGCs shows their role in maintaining the constriction over a prolonged period of time and in regulating the post-illumination pupillary response [@Markwell2010; @McDougal2010].
-
-The ipRGCs are a unique photoreceptor class that has been discovered recently [@Provencio2000].
-They express the photopigment melanopsin, which is involved in the regulation of the circadian rhythm [@Provencio2000; @Panda2002; @Ruby2002], and form a major input to the PON [@Dacey2003].
-The first direct evidence of the involvement of the ipRGCs in the PLR was shown in rats by @Lucas2003 who genetically deleted the melanopsin gene from rats, resulting in the loss of the intrinsic photosensitivity of the cells and a reduced pupil constriction.
-This same behaviour was later also observed in primates and humans [@Gamlin2007], where it was demonstrated that the PLR continues during light presentation even when cone and rod signalling is blocked.
-This also demonstrates the primary role of the ipRGCs in maintaining pupil constriction over a prolonged time.
-It has also been shown that the ipRGCs receive inputs from the other photoreceptors (cones and rods) and are activated by them [@Dacey2005].
-
-To investigate how specific photoreceptor classes control the size of the pupils, a technique known as silent substitution is used.
-Silent substitution exploits the fact that each photoreceptor class has a distinct spectral tuning that overlaps with the others.
-Using a multiprimary system, in which the primaries have different spectra, it is possible to target one class of photoreceptors while maintaining the others at a constant activity level, effectively silencing them [@Shapiro1996; @Spitschan2018, this paper also offers a clear explanation of how to implement silent substitution].
-Studies using silent substitution have shown that the pupils behave differently depending on which photoreceptor or pathway is being stimulated.
-For example, pupil responses have been shown to be out of phase when the S cones are stimulated, relative to when the ipRGCs or the L+M cones are stimulated [@Spitschan2014; @Cao2015].
-Additionally, when L and M cones are stimulated individually, there appears to be a paradoxical pupil response: increments in L cone stimulation cause a constriction of the pupil, while increments in M cone stimulation lead to a dilation of the pupil [@Woelders2018; @Murray2018].
-
-Interaction between the two eyes and the rules of binocular combination have been extensively studied.
-For pattern vision in the visual cortex, at low contrast, binocular summation occurs [binocular presentation confers higher sensitivity than monocular presentation, @Baker2018; @Campbell1965; @Legge1984], while, at high contrast, ocularity invariance is implemented [the response to monocularly- and binocularly-presented patterns is equalised, @Baker2007; @Ding2006; @Meese2006].
-Additionally, evidence of a binocular component to the PLR is shown by the existence of a consensual response of the pupil [the stimulation of one eye will cause constriction of the other eye, @Wyatt1981] and the rules of binocular combination between the pupils have also been recently investigated [@Segala2023], finding that combination happens non-linearly with evidence of interocular suppression.
-
-Most of the studies that use silent substitution and that investigate the PLR stimulate only one eye.
-If the stimulated eye is pharmacologically dilated to control pupil size, the response from the unstimulated eye (known as the consensual response) can be recorded [e.g.
-@McDougal2010; @Spitschan2014].
-While this approach controls the total amount of light incident at the retina, it does not permit investigation of binocular combination for specific photoreceptor pathways.
-Seeing that it is possible to directly investigate binocular combination of signals between the pupils, we decided to investigate this by designing an experiment that allowed us to binocularly target the ipRGCs, the L-M pathway and the S-(L+M) pathway individually while recording binocular pupillometric measures.
-We chose a primary flicker frequency of 0.5 Hz, which has been shown to elicit pupil responses from all three pathways [@Spitschan2014].
-The final results are interpreted using a hierarchical Bayesian computational model of binocular vision.
-
-# Methods
-
-## Participants
-
-Twenty-four participants were recruited for each of the four experiments for a total of ninety-six (68 females) adult participants, whose age ranged from 18 to 41.
-All participants had normal or corrected to normal binocular vision and normal colour vision, and gave written informed consent.
-Our procedures were approved by the Ethics Committee of the Department of Psychology at the University of York (identification number 184).
-
-## Apparatus & stimuli
-
-To present synchronised silent substitution contrast modulations independently to each eye, two light engines, each with 10 independently addressable LED colour channels (SpectraTuneLAB: LEDMOTIVE Technologies, LLC, Barcelona, Spain), were integrated into a customised viewing system.
-The light engines were operated via a Python interface to their REST API [@Martin2022], which supports synchronous launch and playback of spectral sequences prepared in advance and stored in JSON format.
-When preparing the spectral sequences, the age of participants was recorded to account for the yellowing of the lenses.
-
-```{r allcons, fig.cap="Summary of the spectral power distributions and alpha-opic irradiances for the background and each experiment.
-Panel (a) shows a schematic of the binocular stimulation system for presenting spectrally tuned modulations independently to each eye.
-The VR headset was attached to a clamp stand that the experimenters could use to adjust the height and align the headset with the eyes of the participant.
-The participant's head was positioned on a chin rest to keep it in position throughout the entire experiment.
-Panels (b) and (c) show the spectral power distributions and the alpha-opic irradiances of the background spectra used for both eyes.
-Panels (d-k) show the power distributions and the alpha-opic irradiances relative to the background for the four experiments: luminance (d, e), melanopsin (f, g), L-M pathway (h, i) and S-(L+M) pathway (j, k).
-A positive difference power shows a positive modulation (white disc for the luminance experiment, magenta for the L-M pathway experiment and purple for the S-(L+M) experiment) and a negative difference power shows a negative modulation (black disc for the luminance experiment, cyan for the L-M pathway experiment and lime for the S-(L+M) experiment).", fig.align="center", out.width = '80%', echo=FALSE}
-
-knitr::include_graphics(paste0(figdir,'allcons.pdf'))
-
-```
-
-The output from the light engines was directed through liquid light guides (LLG3-8H: Thorlabs Ltd, Cambridgeshire, UK) and diffused onto semi-opaque and highly diffusive white glass discs with a diameter of 50 mm for even illumination (34-473: Edmund Optics, York, UK).
-The light guide gaskets were butt-coupled to the light engine diffusers with threaded adapters (SM1A9, AD3LLG: Thorlabs Ltd, Cambridgeshire, UK) and the exiting ends of the light guides were mated with 51 mm depth optical cylinders (SM2L20: Thorlabs Ltd, Cambridgeshire, UK) via appropriately threaded adapters (AD3LLG, SM2A6: Thorlabs Ltd, Cambridgeshire, UK).
-The stimulus diffuser discs were retained at the front end of the optical cylinders approximately 51 mm from the light source, at which distance the output beam was sufficiently dispersed to afford even illumination of the diffuser when viewed from the front.
-To guarantee safe illumination levels, a circular neutral-density filter with the same diameter of the white glass discs (50 mm) and an optical density of 0.6 log units was placed in the optical path between the light source and the diffusers.
-A small circular piece of blackout material with a diameter of approximately 8 degrees (10 mm) was positioned centrally on the front of each diffuser disc to aid as a fusion lock, as a fixation point and to occlude the fovea.
-
-The diffuser discs were positioned in the objective planes of the lenses of a modified VR headset (SHINECON SC-G01, Dongguan Shinecon Industrial Co.
-Ltd), which was used by the participants to view the stimuli.
-The stimuli were two discs of flickering light with a diameter of approximately 30 degrees, which were fused together into a cyclopean percept resembling a donut-shaped ring of light, similar to that used in other studies [e.g., @Barrionuevo2016; @Murray2018; @Spitschan2014; @Zele2018].
-The VR headset modifications allowed for small adjustments to account for individual differences in interpupillary distance and focal length.
-The use of this set up allowed us to modulate the stimuli in three different ocular configurations, similar to the ones we used in our previous experiment [@Segala2023]: monocular, binocular and dichoptic.
-In the monocular configuration, the unstimulated eye still saw a non-flickering disc of mean luminance.
-A schematic of the stimulation system is shown in Figure \@ref(fig:allcons)a.
-Pupillometry data were collected using a binocular Pupil Core eye-tracker headset [Pupil Labs GmbH, Berlin, Germany, @Kassner2014] running at 120 Hz, and the signals were recorded with the Pupil Capture software.
-
-## Procedure
-
-Before the start of each experiment, participants adjusted the objective planes of the lenses with the help of the experimenter until the stimulus was in focus and they perceived the two pieces of blackout material as one fused piece.
-
-```{r ExampleStims, fig.cap="Example of the different experimental conditions.
-Panel (a) shows one cycle of flicker in the achromatic luminance experiment.
-In this experiment, the stimulus flickers between black and white.
-At the beginning of the cycle (0s), the stimulus appears at half the intesity and appears grey to the viewer.
-At 0.5s, the stimulus reaches the maximum intensity of the flicker and appears white to the viewer.
-At 1s, the stimulus appears again at half maximum and once again appears to be grey to the viewer.
-At 1.5s, the stimulus reaches the minimum intensity of the flicker and appears black to the viewer.
-Panel (b) shows one cycle of the flickering in the L-M pathway experiment.
-In this experiment, the stimulus flickers between magenta (+L-M) and cyan (-L+M).
-At the beginning of the cycle (0s), the stimulus appears at zero cone contrast and appears to be grey to the viewer.
-At 0.5s, the stimulus reaches the maximum L-cone contrast and appears magenta to the viewer.
-At 1s, the stimulus appears again at zero cone contrast and switches colour, once again appearing to be grey to the viewer.
-At 1.5s, the stimulus reaches the minimum L-cone contrast and appears cyan to the viewer.
-Panel (c) shows one cycle of the flickering in the S-(L+M) pathway experiment.
-In this experiment, the stimulus flickers between purple (+S-(L+M)) and lime (-S+(L+M)).
-At the beginning of the cycle (0s), the stimulus appears at zero cone contrast and appears to be grey to the viewer.
-At 0.5s, the stimulus reaches the maximum S-cone contrast and appears purple to the viewer.
-At 1s, the stimulus appears again at zero cone contrast and switches colour, once again appearing to be grey to the viewer.
-At 1.5s, the stimulus reaches the minimum S-cone contrast and appears lime to the viewer.", fig.align="center", out.width = '95%', echo=FALSE}
-
-knitr::include_graphics(paste0(figdir,'ExampleStims.pdf'))
-
-```
-
-We initially planned to examine pupil responses and EEG responses simultaneously to temporal modulations flickering at 2 Hz and 1.6 Hz while stimulating the periphery of the retina.
-While the experiment produced clear responses when presenting an achromatic light (see Figures \@ref(fig:appendixfig1) and \@ref(fig:appendixfig2) in Appendix 1), the responses were very noisy for the targeted photoreceptor class experiments (see Figures \@ref(fig:pupildataMel2Hz)-\@ref(fig:EEGdataS2Hz) in Appendix 2) for both the pupillometry and the EEG data.
-Therefore, we decided to lower the main frequency to 0.5 Hz as previous literature showed that it was slow enough to elicit a pupil response from all photoreceptor classes [@Spitschan2014] and we focussed on only recording pupillometry data as this frequency would be well below the minimum threshold to elicit EEG responses [@Norcia2015].
-
-Pupil responses to binocular temporal contrast modulations were examined in a factorial design that combined six ocular conditions, two temporal frequencies (0.4 and 0.5 Hz) and five temporal contrast levels relative to the mean illuminance (6, 12, 24, 48 and 96%).
-This design, similar to what we used in our previous study [@Segala2023], was applied in four separate experiments, each with a different mode of photoreceptor stimulation.
-In the first three conditions, the discs flickered at 0.5 Hz, in either a monocular, binocular or dichoptic arrangement.
-In the dichoptic condition the non-target eye saw a flickering fixed contrast of 48%.
-In the remaining three conditions (the cross-frequency conditions) one eye’s disc flickered at 0.4 Hz, and the other eye’s disc flickered at 0.5 Hz.
-We also tested monocular responses at 0.4 Hz, as well as binocular (one eye sees each frequency at the target contrast) and dichoptic (target stimulus flickering at 0.5 Hz, mask contrast of 48% at 0.4 Hz in the other eye) arrangements.
-We counterbalanced presentation of the target stimulus across the left and right eyes.
-
-For all experiments, sinusoidal contrast modulations were presented against the same background spectrum (matched between the eyes), which was used to achieve silent substitution in the three photoreceptor modulation experiments.
-The background spectra were defined by setting all channels to half maximum output for the brighter of the two devices (STLab 1, left eye) and then using the STLab 1/STLab 2 calibration ratio to find the equivalent settings for the companion device (STLab 2, right eye).
-The background spectrum illuminance was approximately 74 lux.
-The spectral power distributions and alpha-opic irradiances of the background spectra for both eyes are shown in Figures \@ref(fig:allcons)b-c.
-
-### Experiment 1: luminance
-
-The experiment was conducted in a windowless room, in which the only source of light was the modified VR headset.
-The participants sat as close as possible to the VR headset, leaving enough space for the eye-tracker to record the eyes.
-The experiment was carried out in a single session of 45 minutes, divided into three blocks of 15 minutes each.
-In each block, there were a total of 60 trials lasting 15 seconds each (12s of stimulus presentation, followed by 3s of interstimulus interval).
-The participants were given no task other than look at the black fixation dot while trying to minimise their blinking during the presentation period.
-
-In this experiment, the participants saw a disc of achromatic flickering light (average illuminance of approximately 74 lux), flickering between black and white, at the different contrast levels defined earlier.
-An example of one cycle of flickering for the luminance experiment is shown in Figure \@ref(fig:ExampleStims)a.
-The spectral power distributions and alpha-opic irradiances relative to the background for the luminance experiment are shown in Figures \@ref(fig:allcons)d-e.
-
-### Experiment 2: melanopsin
-
-The experiment used the same equipment set-up and the same experimental conditions as Experiment 5.
-The procedure was also the same.
-However, at the beginning of each block, participants habituated for 2 minutes to the background that would be present throughout the entire experiment.
-During this adaptation period, participants were asked to fixate on the same black fixation dot positioned in the middle of the stimulus and were told that they could blink normally.
-At the end of the adaptation period, the experiment started immediately and the participants followed the same instructions given in Experiment 1.
-
-In this experiment, the participants experienced contrast modulations that targeted the melanopsin-containing intrinsically photosensitive Retinal Ganglion cells, while ignoring rods and nominally silencing the cones.
-Michelson contrast levels represented a percentage of the maximum melanopic contrast available, which was predetermined to be approximately 22 \%.
-Under perfect silent substitution conditions, these modulations do not entail any changes in brightness or chromaticity: it is therefore very difficult to include an example to visualise the stimulus.
-However, silent substitution is never perfect, so participants reported small fluctuations in reddishness, greenishness and brightness due to open-field cone contrast artefacts.
-These fluctuations were especially present at higher contrasts.
-This can be observed in the alpha-opic irradiances relative to the background for the melanopsin experiment shown in Figure \@ref(fig:allcons)g, where a small activation of the S, L and M cones is observable.
-The spectral power distributions relative to the background for the melanopsin experiment is also shown in Figure \@ref(fig:allcons)f.
-
-### Experiment 3: L-M postreceptoral ‘parvocellular’ pathway
-
-The experiment used the same equipment set-up and the same experimental conditions as Experiment 5.
-The procedure was the same as Experiment 6, including the presence of a 2-minute adaptation period at the beginning of each block.
-Additionally, before the start of the experiment, participants completed a luminance nulling perceptual calibration procedure in L-M cone space on an Iiyama $\textrm{VisionMaster}^{\textrm{TM}}$ Pro 510 display (800 x 600 pixels, 60 Hz refresh rate).
-During the task, participants were presented with a disc flickering within the L-M cone space (between magenta and cyan).
-Using a trackball, participants adjusted the angle in cone space to find their subjective isoluminant point, which resulted in changing the flickering intensity of the stimulus until the amplitude of the flicker appeared to be minimised.
-The result was used to modify the requested contrasts during stimulus preparation so as to account for individual differences affecting perceived illuminance, principally the L:M cone ratio [@Carroll2002; @Hofer2005].
-
-In this experiment, the participants experienced contrast modulations that targeted the L-M postreceptoral ‘parvocellular’ pathway while ignoring rods and nominally silencing S-cones and melanopsin.
-Michelson contrast levels represented a percentage of the maximum L-M contrast available for the background spectrum, which was determined in advance to be approximately 10 \%.
-As shown in Figure \@ref(fig:ExampleStims)b, participants experienced an isoluminant chromatic modulation between magenta (+L-M) and cyan (-L+M).
-The spectral power distributions and alpha-opic irradiances relative to the background for the L-M pathway experiment are shown in Figures \@ref(fig:allcons)h-i.
-
-### Experiment 4: S-(L+M) ‘koniocelluar’ pathway
-
-The experiment used the same equipment set-up and the same experimental conditions as Experiment 5.
-The procedure was the same as Experiment 6, including the presence of a 2-minute adaptation period at the beginning of each block.
-
-In this experiment, the participants experienced contrast modulations that targeted the S-(L+M) ‘koniocelluar’ pathway while ignoring rods and nominally silencing L/M cones and melanopsin.
-Michelson contrast levels represented a percentage of the maximum S-cone contrast available for the background spectrum, which was predetermined to be approximately 45 \%.
-As shown in Figure \@ref(fig:ExampleStims)c, participants experienced an isoluminant chromatic modulation between purple (+S-(L+M)) and lime (-S+(L+M)).
-The spectral power distributions and alpha-opic irradiances relative to the background for the S-(L+M) pathway experiment are shown in Figures \@ref(fig:allcons)j-k.
-
-## Data analysis
-
-The pupillometry data were analysed using the same method we used in our previous study [@Segala2023].
-The data were converted from mp4 videos to a csv text file using the Pupil Player software [@Kassner2014], which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
-The individual data were then loaded into R for analysis, where a ten-second waveform for each trial in each eye was extracted (excluding the first two seconds after stimulus onset).
-We interpolated across any dropped or missing frames to ensure regular and continuous sampling over time.
-The Fourier transform was calculated for each waveform, and all repetitions of each condition were pooled across eye and then averaged.
-Finally, data were averaged across all participants to obtain the group results.
-We used coherent averaging and at each stage we excluded data points with a Mahalanobis distance exceeding $D$ = `r SDthresh` from the complex-valued mean.
-The consensual response was also analysed (see Appendix 3 for more details and the results).
-
-For all experiments, we used a bootstrapping procedure with `r nbootstraps` iterations to estimate standard errors across participants.
-All analysis and figure construction was conducted using a single R-script, available online, making this study fully computationally reproducible: https://osf.io/gdvt4/.
-
-## Computational model and parameter estimation
-
-To describe our data, we chose the same model described in our previous study [@Segala2023].
-The model has the same general form as the first stage of the contrast gain control model proposed by @Meese2006 and omits the second stage.
-For the previous model that we used [@Segala2023], the exponent of the numerator had a fixed value of 2.
-Here, we allow this parameter (called _p_) to be free, in order to permit different shapes of contrast response function, e.g.
-saturating or super-saturating.
-The responses of the left eye and right eye channels are as follows:
-
-\begin{equation}
-\label{eq:respLchap4}
-Resp_L = \frac{L^p}{Z + L^q + wR^q},
-\end{equation}
-
-\begin{equation}
-\label{eq:respRchap4}
-Resp_R = \frac{R^p}{Z + R^q + wL^q},
-\end{equation}
-
-\noindent where _L_ and _R_ are the contrast signals from the left and right eyes, _p_ and _q_ are exponents, _Z_ is a saturation constant that shifts the contrast-response function laterally, and _w_ is the weight of suppression from the other eye.
-
-The responses from the two eyes are then summed binocularly:
-
-\begin{equation}
-\label{eq:respBchap4}
-Resp_B = R_{max}(Resp_L + Resp_R) + k,
-\end{equation}
-
-\noindent where _n_ is a noise parameter, and $R_{max}$ scales the overall response amplitude.
-
-We performed model fitting on the normalised amplitudes to account for amplitude differences between the experiments.
-
-# Results
-
-## Experiment 1
-
-```{r luminance individual, include=FALSE, results='hide'}
-
-# (download and) analyse individual participant data for the luminance experiment
+```{r individualanalyses, include=FALSE, results='hide'}
+
+# analyse individual participant data for all conditions
+
 if (processdata > 2){
 
-  for(participant in 1:24){
-
-    # only download and process data if this has not been done already for this participant
-    if (!file.exists(paste0(datadir,'P',600+participant,'summary.RData'))){
-
-      # if there is no directory for this participant's data
-      if (!file.exists(paste0(rawdir,'P',600+participant))){
-        dir.create(paste0(rawdir,'P',600+participant))
-
-       d <- dir(paste0(rawdir,'P',600+participant))
-
-       if (length(d)==0){
-
-         # if the tar file of this participant's data doesn't exist
-         if (!file.exists(paste0(rawdir,'P',600+participant,'.zip'))){
-           # download it from OSF
-           if (!exists('osffiles')){
-           osfnode <- '6u7db'
-           osfproject <- osf_retrieve_node(osfnode)
-          osffiles <- osf_ls_files(osfproject,n_max=300)}
-          fid <- which(osffiles$name==paste0('P',600+participant,'.zip'))
-          osf_download(osffiles[fid,],rawdir,progress=TRUE)
-         }
-
-         # then unzip the tar file
-         unzip(paste0(rawdir,'P',600+participant,'.zip'),exdir=paste0(rawdir))
-
-         # and delete the tar file to save storage space
-         file.remove(paste0(rawdir,'P',600+participant,'.zip'))
-       }
-      }
-
-      d <- dir(paste0(rawdir,'P',600+participant),full.names=TRUE)
-
-    tic()
+  allsubjects <- dir(rawdir)
+  for (p in 1:length(allsubjects)){
+    participant <- allsubjects[p]
 
@@
     repcounterP <- (1:60)*0
-    afiles <- dir(path=paste0(rawdir,'P',600+participant),pattern='*annotations.csv',full.names=TRUE)
-
-    for (block in 1:length(afiles)){
-        tic()
-        adata <- read.csv(paste0(rawdir,'P',600+participant,'/',paste0('P',600+participant,'_S',block),'_annotations.csv'))
+    annfiles <- dir(paste0(rawdir,participant),pattern='*annotations.csv',full.names=TRUE)
+    pupilfiles <- dir(paste0(rawdir,participant),pattern='*pupil_positions.csv',full.names=TRUE)
+
+    for (block in 1:length(annfiles)){
+
+        adata <- read.csv(annfiles[block])
 
@@
 
-        pdata <- read.csv(paste(rawdir,'P',600+participant,'/',paste0('P',600+participant,'_S',block),'_pupil_positions.csv',sep=''))
+        pdata <- read.csv(pupilfiles[block])
         pdata2 <- pdata[,c(1,3,4,14)]
@@
     meanspectraP <- apply(pupilspectra[,,c(15,20),],4,mean,na.rm=TRUE)
-    save(file=paste(datadir,'P',600+participant,'_summaryLum.RData',sep=''),list=c('cleanmeansP','cleanmasksP','cleanmeansP2','cleanmasksP2','meanspectraP','meanwavesP'))
-
-    if (cleanupraw==1){file.remove(d)} # delete raw data files to save space
-  }
-
-  }}
+    save(file=paste(datadir,participant,'_summary.RData',sep=''),list=c('cleanmeansP','cleanmasksP','cleanmeansP2','cleanmasksP2','meanspectraP','meanwavesP'))
+  }
+
+}
+
 ```
 
-```{r luminance group, include=FALSE, results='hide'}
+```{r groupanalyses, include=FALSE, results='hide'}
+
+# files from P301-P324 are for S-cone stimulation
+# files from P501-P524 are for melanopsin stimulation
+# files from P601-P624 are for luminance stimulation
+# files from P701-P724 are for (L-M) cone stimulation
 
@@
 if (processdata > 1){
-  for (participant in 1:24){
-         # if the summary file of this participant's data doesn't exist
-         if (!file.exists(paste0(datadir,'P',600+participant,'summaryLum.RData'))){
-           # download it from OSF
-           if (!exists('osffilesP')){
-           osfnode <- '9ebtd'
-           osfproject <- osf_retrieve_node(osfnode)
-          osffilesP <- osf_ls_files(osfproject,n_max=300)}
-          fid <- which(osffilesP$name==paste0('P',600+participant,'summaryLum.RData'))
-          osf_download(osffilesP[fid,],datadir,progress=TRUE)
-         }
-}
-
-  d <- dir(datadir,pattern='summaryLum.RData', full.names = TRUE)
+
+  prefixlist <- c('P6','P7','P3','P5')
+  exptnames <- c('AveragedataLum.RData','AveragedataLM.RData','AveragedataS.RData','AveragedataMel.RData')
+
+  includedvalues <- array(0,dim=c(4,24,6,5))
+  includedvalues2 <- array(0,dim=c(4,24,6,5))
+
+  for (expt in 1:4){
+  d <- dir(datadir,pattern=prefixlist[expt], full.names = TRUE)
 
@@
 
-  tempspectraP <- tempspectraP[-c(2,4,13,20,26),]
+  # tempspectraP <- tempspectraP[-c(2,4,13,20,26),]
 
@@
         i <- which(D<SDthresh)
+        includedvalues[expt,i,cond,level] <- 1
         mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
@@
         i <- which(D<SDthresh)
+        includedvalues2[expt,i,cond,level] <- 1
         mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
@@
 
-  save(file=paste0(datadir,'AveragedataLum.RData'),list=c('meanwavesP','meanwavesPCI','cleanmeansP','cleanmeansPCI','cleanmasksP','cleanmasksPCI','cleanmeansP2','cleanmeansP2CI','cleanmasksP2','cleanmasksP2CI','meanspectraP','meanspectraPCI','tempmeansP','tempmeansP2','tempmasksP','tempmasksP2'))
+  save(file=paste0(datadir,exptnames[expt]),list=c('meanwavesP','meanwavesPCI','cleanmeansP','cleanmeansPCI','cleanmasksP','cleanmasksPCI','cleanmeansP2','cleanmeansP2CI','cleanmasksP2','cleanmasksP2CI','meanspectraP','meanspectraPCI','tempmeansP','tempmeansP2','tempmasksP','tempmasksP2'))
+  }
+
+  save(file=paste0(datadir,'included.RData'),list=c('includedvalues','includedvalues2'))
 
@@
 ```
-
-```{r luminance plot, include=FALSE, results='hide'}
-
-# generate plot showing the group pupillometry data for the luminance experiment
-
-         if (!file.exists(paste0(datadir,'AveragedataLum.RData'))){
-           # download it from OSF
-           if (!exists('osffilesP')){
-           osfnode <- '9ebtd'
-           osfproject <- osf_retrieve_node(osfnode)
-          osffilesP <- osf_ls_files(osfproject,n_max=300)}
-          fid <- which(osffilesP$name=='AveragedataLum.RData')
-          osf_download(osffilesP[fid,],datadir,progress=TRUE)
-         }
-
-load(file=paste0(datadir,'AveragedataLum.RData'))
-
-if (processdata > 0){
-
-allPLumratios <- abs(cleanmeansP[2,])/abs(cleanmeansP[1,])
-allPLum2ratios <- abs(cleanmeansP2[2,])/abs(cleanmeansP2[1,])
-
-# plot figure  
-plotlims <- c(15,40,0,3)  
-ticklocsx <- contrastsdB
-ticklabelsx <-c(6,12,24,48,96) 
-ticklocsy <- seq(0,3,0.5)    # locations of tick marks on y axis
-ticklabelsy <- ticklocsy
-
-postscript("SumLum.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
-
-par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx)     
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
-title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  
-title(ylab="Bin:Mon ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-
-lines(contrastsdB,allPLumratios, col=colpal[1], lwd=3, cex=0.5)
-lines(contrastsdB,allPLum2ratios, col=colpal[2], lwd=3, cex=0.5)
-points(contrastsdB,allPLumratios, pch = 21, col='black', bg=colpal[1], cex=1.6, lwd=3)
-points(contrastsdB,allPLum2ratios, pch = 22, col='black', bg=colpal[2], cex=1.6, lwd=3)
-
-legend(contrastsdB[4],3,c('Lum 1F','Lum 2F'), pch=21:24, pt.bg=colpal[1:2],box.lwd=2,pt.cex=1.6,pt.lwd=3)
-text(17,2.8,'(c)',adj=0.5,cex=2.5)
-
-dev.off()
-
-plotlims <- c(15,40,0,0.15)
-plotlims2 <- c(15,40,0,0.015) 
-ticklocsx <- contrastsdB    # locations of tick marks on x axis
-ticklocsy <- seq(0,0.15,0.05)
-ticklocsy2 <- seq(0,0.015,0.005)    # locations of tick marks on y axis
-ticklabelsx <-c(6,12,24,48,96)        # set labels for x ticks
-ticklabelsy <- ticklocsy
-ticklabelsy2 <- ticklocsy2     # set labels for y ticks
-
-postscript("CRF1p.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
-
-par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
-title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
-title(ylab="Amplitude at 0.5Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
-
-for (cond in 1:3){
-  lines(contrastsdB,abs(cleanmeansP[cond,]), col=colpal[cond], lwd=3, cex=0.5)
-  arrows(contrastsdB,abs(cleanmeansP[cond,]),contrastsdB,cleanmeansPCI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
-  arrows(contrastsdB,abs(cleanmeansP[cond,]),contrastsdB,cleanmeansPCI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
-  points(contrastsdB,abs(cleanmeansP[cond,]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
-}  
-legend(22,0.15,c('Monocular','Binocular','Dichoptic'),pch=21:23,pt.bg=colpal[1:3],pt.lwd=3,pt.cex=1.6,box.lwd=2)
-text(17,0.14,'(d)',adj=0.5,cex=2.5)
-
-dev.off()
-
-postscript("CRF2p.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
-
-par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
-title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
-title(ylab="Amplitude at 0.5Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
-
-condlist <- c(1,5,6)
-pointlist <- c(21,24,25)
-for (cond in 1:3){
-  lines(contrastsdB,abs(cleanmeansP[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)  
-  arrows(contrastsdB,abs(cleanmeansP[condlist[cond],]),contrastsdB,cleanmeansPCI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
-  arrows(contrastsdB,abs(cleanmeansP[condlist[cond],]),contrastsdB,cleanmeansPCI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)  
-  points(contrastsdB,abs(cleanmeansP[condlist[cond],]), pch = pointlist[cond], col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
-}  
-legend(22,0.15,c('Monocular','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[condlist],pt.lwd=3,pt.cex=1.6,box.lwd=2)
-text(17,0.14,'(e)',adj=0.5,cex=2.5)
-
-dev.off()
-
-postscript("CRF3p.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
-
-par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
-title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
-title(ylab="Amplitude at 0.4Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
-
-for (cond in 4:6){
-  lines(contrastsdB,abs(cleanmasksP[cond,]), col=colpal[cond], lwd=3, cex=0.5)   
-  arrows(contrastsdB,abs(cleanmasksP[cond,]),contrastsdB,cleanmasksPCI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
-  arrows(contrastsdB,abs(cleanmasksP[cond,]),contrastsdB,cleanmasksPCI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)    
-  points(contrastsdB,abs(cleanmasksP[cond,]), pch = pointlist[cond-3], col='black', bg=colpal[cond], cex=1.6, lwd=3) 
-}
-legend(22,0.15,c('Monocular 0.4Hz','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[4:6],pt.lwd=3,pt.cex=1.6,box.lwd=2)
-text(17,0.14,'(f)',adj=0.5,cex=2.5)
-
-dev.off()
-
-postscript("CRF1p2.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
-
-par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims2[3:4])   # create an empty axis of the correct dimensions
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy2, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
-mtext(text = ticklabelsy2, side = 2, at=ticklocsy2, line=0.2, las=1) 
-title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
-title(ylab="Amplitude at 1Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
-
-for (cond in 1:3){
-  lines(contrastsdB,abs(cleanmeansP2[cond,]), col=colpal[cond], lwd=3, cex=0.5)
-  arrows(contrastsdB,abs(cleanmeansP2[cond,]),contrastsdB,cleanmeansP2CI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
-  arrows(contrastsdB,abs(cleanmeansP2[cond,]),contrastsdB,cleanmeansP2CI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
-  points(contrastsdB,abs(cleanmeansP2[cond,]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
-}  
-legend(22,0.015,c('Monocular','Binocular','Dichoptic'),pch=21:23,pt.bg=colpal[1:3],pt.lwd=3,pt.cex=1.6,box.lwd=2)
-text(17,0.014,'(g)',adj=0.5,cex=2.5)
-
-dev.off()
-
-postscript("CRF2p2.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
-
-par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims2[3:4])   # create an empty axis of the correct dimensions
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy2, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
-mtext(text = ticklabelsy2, side = 2, at=ticklocsy2, line=0.2, las=1)
-title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
-title(ylab="Amplitude at 1Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
-
-condlist <- c(1,5,6)
-pointlist <- c(21,24,25)
-for (cond in 1:3){
-  lines(contrastsdB,abs(cleanmeansP2[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)  
-  arrows(contrastsdB,abs(cleanmeansP2[condlist[cond],]),contrastsdB,cleanmeansP2CI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
-  arrows(contrastsdB,abs(cleanmeansP2[condlist[cond],]),contrastsdB,cleanmeansP2CI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)  
-  points(contrastsdB,abs(cleanmeansP2[condlist[cond],]), pch = pointlist[cond], col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
-}  
-legend(22,0.015,c('Monocular','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[condlist],pt.lwd=3,pt.cex=1.6,box.lwd=2)
-text(17,0.014,'(h)',adj=0.5,cex=2.5)
-
-dev.off()
-
-postscript("CRF3p2.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
-
-par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims2[3:4])   # create an empty axis of the correct dimensions
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy2, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
-mtext(text = ticklabelsy2, side = 2, at=ticklocsy2, line=0.2, las=1)
-title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
-title(ylab="Amplitude at 0.8Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
-
-for (cond in 4:6){
-  lines(contrastsdB,abs(cleanmasksP2[cond,]), col=colpal[cond], lwd=3, cex=0.5)   
-  arrows(contrastsdB,abs(cleanmasksP2[cond,]),contrastsdB,cleanmasksP2CI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
-  arrows(contrastsdB,abs(cleanmasksP2[cond,]),contrastsdB,cleanmasksP2CI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)    
-  points(contrastsdB,abs(cleanmasksP2[cond,]), pch = pointlist[cond-3], col='black', bg=colpal[cond], cex=1.6, lwd=3) 
-}
-legend(22,0.015,c('Monocular 0.4Hz','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[4:6],pt.lwd=3,pt.cex=1.6,box.lwd=2)
-text(17,0.014,'(i)',adj=0.5,cex=2.5)
-
-dev.off()
-
-postscript("SpecP.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 8)
-
-frequencies <- (0:299)/10
-
-plotlims <- c(0,2,0,0.15) 
-ticklocsx <- seq(0,2,0.25)    # locations of tick marks on x axis
-ticklocsy <- seq(0,0.15,0.05)    # locations of tick marks on y axis
-ticklabelsx <-ticklocsx        # set labels for x ticks
-ticklabelsy <- ticklocsy    # set labels for y ticks
-
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
-title(xlab="Frequency (Hz)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  
-title(ylab="Amplitude (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
-
-polygon(frequencies[c(3:21,21:3)],c(meanspectraPCI[1,3:21],meanspectraPCI[2,21:3]),col=colpal[2],border=NA)
-
-lines(frequencies[3:21],abs(meanspectraP[3:21]), col=colpal[2], lwd=3, cex=0.5)
-
-text(0.1,0.14,'(a)',adj=0.5,cex=2.5)
-
-dev.off()
-
-postscript("timecourseP.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 8)
-
-times <- seq((1/120)-1,13,1/120)
-sinewave <- sin(0.5*times * 2*pi)
-sinewave[1:120] <- 0
-sinewave[1560:1680] <- 0
-
-plotlims <- c(-1,13,-1,0.5)
-ticklocsx <- seq(-1,13,1)    # locations of tick marks on x axis
-ticklocsy <- seq(-1,0.5,0.5)    # locations of tick marks on y axis
-ticklabelsx <- ticklocsx        # set labels for x ticks
-ticklabelsy <- ticklocsy    # set labels for y ticks
-
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
-title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)
-title(ylab="Amplitude (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
-
-filt <- butter(3,0.083)
-filtwaveP <- signal::filter(filt, meanwavesP)
-filtU <- signal::filter(filt,meanwavesPCI[1,])
-filtL <- signal::filter(filt,meanwavesPCI[2,])
-polygon(times[c(1:length(times),length(times):1)],c(filtL,filtU[length(filtU):1]),col=colpal[2],border=NA)
-lines(times, filtwaveP, col=colpal[2], lwd=1.5)
-lines(times, (sinewave/10)-0.9, col='black', lwd=3)
-
-text(-0.7,0.4,'(b)',adj=0.5,cex=2.5)
-
-dev.off()
-
-PostScriptTrace('CRF1p.ps')
-p1 <- readPicture('CRF1p.ps.xml')
-PostScriptTrace('CRF2p.ps')
-p2 <- readPicture('CRF2p.ps.xml')
-PostScriptTrace('CRF3p.ps')
-p3 <- readPicture('CRF3p.ps.xml')
-PostScriptTrace('CRF1p2.ps')
-p4 <- readPicture('CRF1p2.ps.xml')
-PostScriptTrace('CRF2p2.ps')
-p5 <- readPicture('CRF2p2.ps.xml')
-PostScriptTrace('CRF3p2.ps')
-p6 <- readPicture('CRF3p2.ps.xml')
-PostScriptTrace('SpecP.ps')
-p7 <- readPicture('SpecP.ps.xml')
-PostScriptTrace('timecourseP.ps')
-p8 <- readPicture('timecourseP.ps.xml')
-PostScriptTrace('SumLum.ps')
-p9 <- readPicture('SumLum.ps.xml')
-
-for (n in 1:length(p7@paths)){
-  temp <- class(p7@paths[n]$path)[1]
-  if (pmatch(temp,"PictureFill",nomatch=0)){
-    if (sum(col2rgb(p7@paths[n]$path@rgb))<765){p7@paths[n]$path@rgb <- addalpha(p7@paths[n]$path@rgb,alpha=0.2)}}}
-
-for (n in 1:length(p8@paths)){
-  temp <- class(p8@paths[n]$path)[1]
-  if (pmatch(temp,"PictureFill",nomatch=0)){
-    if (sum(col2rgb(p8@paths[n]$path@rgb))<765){p8@paths[n]$path@rgb <- addalpha(p8@paths[n]$path@rgb,alpha=0.2)}}}
-
-pdf(paste0(figdir,"pupildataLum.pdf"), bg="transparent", height = 20, width = 15)
-
-par(mar=c(0.1,0.1,0.1,0.1))
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(0,1), ylim=c(0,1))
-
-grid.picture(p1,x=0.17,y=0.4,width=0.32,height=1)
-grid.picture(p2,x=0.5,y=0.4,width=0.32,height=1)
-grid.picture(p3,x=0.83,y=0.4,width=0.32,height=1)
-grid.picture(p4,x=0.17,y=0.15,width=0.32,height=1)
-grid.picture(p5,x=0.5,y=0.15,width=0.32,height=1)
-grid.picture(p6,x=0.83,y=0.15,width=0.32,height=1)
-grid.picture(p7,x=0.25,y=0.83,width=0.5,height=1)
-grid.picture(p8,x=0.25,y=0.63,width=0.5,height=1)
-grid.picture(p9,x=0.75,y=0.71,width=0.5,height=1)
-
-text(0.5,0.98,'Luminance',cex=4)
-
-dev.off()
-
-file.remove(c('CRF1p.ps','CRF2p.ps','CRF3p.ps','CRF1p2.ps','CRF2p2.ps','CRF3p2.ps','SpecP.ps','timecourseP.ps','SumLum.ps'))
-file.remove(c('CRF1p.ps.xml','CRF2p.ps.xml','CRF3p.ps.xml','CRF1p2.ps.xml','CRF2p2.ps.xml','CRF3p2.ps.xml','SpecP.ps.xml','timecourseP.ps.xml','SumLum.ps.xml'))
-
-  }
-```
-
-```{r luminance statistics, include=FALSE, results='hide'}
-
-# do statistics on the luminance data
-alldata <- NULL
-groupID <- NULL
-allP <- NULL
-counter <- 0
-for (cont in 1:dim(tempmeansP)[3]){
-  for (p in 1:dim(tempmeansP)[1]){
-    counter <- counter + 1
-    alldata[counter] <- tempmeansP[p,3,cont]
-    groupID[counter] <- cont
-    allP[counter] <- p
-  }
-}
-
-# stats for the dichoptic (green line) condition (fig. 1c)
-dichA2c <- anovacirc.test(alldata,group=groupID,participant=allP)
-
-alldata <- NULL
-allgroupA <- NULL
-allgroupB <- NULL
-allP <- NULL
-counter <- 0
-for (p in 1:12){
-  for (lev in 1:5){
-    for (cond in 1:2){
-    counter <- counter + 1
-    alldata[counter] <- tempmeansP[p,cond,lev]
-    allgroupA[counter] <- lev
-    allgroupB[counter] <- cond
-    allP[counter] <- p
-    }
-  }
-}
-
-# stats for the mon and bin conditions (fig. 1c)
-monbinPstats <- anovacirc2way(alldata,allgroupA,allgroupB,allP)
-
-alldata <- NULL
-allgroupA <- NULL
-allgroupB <- NULL
-allP <- NULL
-counter <- 0
-for (p in 1:12){
-  for (lev in 1:5){
-    counter <- counter + 1
-    alldata[counter] <- tempmeansP[p,1,lev]
-    allgroupA[counter] <- lev
-    allgroupB[counter] <- 1
-    allP[counter] <- p
-
-    counter <- counter + 1
-    alldata[counter] <- tempmeansP[p,3,lev]
-    allgroupA[counter] <- lev
-    allgroupB[counter] <- 2
-    allP[counter] <- p
-  }
-}
-
-# stats for the mon and dich conditions (fig. 1c)
-mondichPstats <- anovacirc2way(alldata,allgroupA,allgroupB,allP)
-
-alldata <- NULL
-allgroupA <- NULL
-allgroupB <- NULL
-allP <- NULL
-counter <- 0
-for (p in 1:12){
-  for (lev in 1:5){
-    counter <- counter + 1
-    alldata[counter] <- tempmeansP[p,1,lev]
-    allgroupA[counter] <- lev
-    allgroupB[counter] <- 1
-    allP[counter] <- p
-
-    counter <- counter + 1
-    alldata[counter] <- tempmeansP[p,5,lev]
-    allgroupA[counter] <- lev
-    allgroupB[counter] <- 2
-    allP[counter] <- p
-  }
-}
-
-# stats for the mon and binX conditions (fig. 1d)
-monbinPstatsX <- anovacirc2way(alldata,allgroupA,allgroupB,allP)
-
-alldata <- NULL
-allgroupA <- NULL
-allgroupB <- NULL
-allP <- NULL
-counter <- 0
-for (p in 1:12){
-  for (lev in 1:5){
-    counter <- counter + 1
-    alldata[counter] <- tempmeansP[p,1,lev]
-    allgroupA[counter] <- lev
-    allgroupB[counter] <- 1
-    allP[counter] <- p
-
-    counter <- counter + 1
-    alldata[counter] <- tempmeansP[p,6,lev]
-    allgroupA[counter] <- lev
-    allgroupB[counter] <- 2
-    allP[counter] <- p
-  }
-}
-
-# stats for the mon and dichX conditions (fig. 1d)
-mondichPstatsX <- anovacirc2way(alldata,allgroupA,allgroupB,allP)
-
-```
-
-The results of the luminance experiment are summarised in Figure \@ref(fig:pupildataLum).
-The average Fourier spectrum is displayed in Figure \@ref(fig:pupildataLum)a, and shows a strong response at the first harmonic frequency (0.5 Hz) and a weaker but still clear response at the second harmonic frequency (1 Hz).
-These results demonstrate that we can evoke measurable steady-state pupil responses at 0.5 Hz by stimulating the periphery of the retina.
-The group average waveform for binocular presentation is shown in Figure \@ref(fig:pupildataLum)b.
-There is a substantial pupil constriction at stimulus onset, followed by very visible oscillations at the flicker frequency (0.5 Hz, see waveform at foot).
-
-Figure \@ref(fig:pupildataLum)d shows contrast response functions in response to stimuli flickering only at 0.5 Hz.
-The amplitude of the binocular condition (blue squares) is consistently greater than that of the monocular condition (red circles) across all target contrasts.
-A $2\times5$ repeated measures $ANOVA^2_{circ}$ [@Baker2021] comparing these conditions revealed a significant main effect of target contrast (F(`r monbinPstats$dfA`,`r monbinPstats$dfR`) = `r round(monbinPstats$FratioA,digits=2)`, $p$ < 0.001), a significant effect of condition (F(`r monbinPstats$dfB`,`r monbinPstats$dfR`) = `r round(monbinPstats$FratioB,digits=2)`, $p$ < 0.001), and a significant interaction (F(`r monbinPstats$dfAB`,`r monbinPstats$dfR`) = `r round(monbinPstats$FratioAB,digits=2)`, $p$ < 0.001).
-The dichoptic condition (green diamonds) begins at a much higher amplitude, owing to binocular combination of the target and high (48%) contrast mask, and then increases with increasing target contrast (main effect of target contrast: F(`r dichA2c$dfM`,`r dichA2c$dfR`) = `r round(dichA2c$Fratio,digits=2)`, $p$ < 0.001).
-Similar results can be observed at the second harmonic in Figure \@ref(fig:pupildataLum)g (see Tables \@ref(tab:TableStatsFig3g) and \@ref(tab:TableStatsMonDichFig3g) for summary of statistical results).
-
-In Figure \@ref(fig:pupildataLum)e, we plot responses to monocular target stimuli flickering at 0.5 Hz, when the other eye viewed stimuli flickering at 0.4 Hz (the red monocular-only data are replotted from Figure \@ref(fig:pupildataLum)d for comparison).
-When the 0.4 Hz component had the same contrast as the target (the binocular cross condition, shown in purple) responses were suppressed slightly across all target contrasts (interaction between contrast and condition: F(`r monbinPstatsX$dfAB`,`r monbinPstatsX$dfR`) = `r round(monbinPstatsX$FratioAB,digits=2)`, $p$ < 0.001).
-When the 0.4 Hz component had a fixed contrast of 48 % (the dichoptic cross condition, shown in yellow), responses were also suppressed slightly across the contrast range (interaction between contrast and condition: F(`r mondichPstatsX$dfAB`,`r mondichPstatsX$dfR`) = `r round(mondichPstatsX$FratioAB,digits=2)`, $p$ < 0.001).
-The same pattern of results was generally observed at the second harmonic (Figure \@ref(fig:pupildataLum)h, see Tables \@ref(tab:TableStatsMonBinXFig3h) and \@ref(tab:TableStatsMonDichXFig3h) for summary of statistical results).
-
-```{r pupildataLum, fig.cap="Summary of pupillometry results for the luminance experiment for N=12 participants.
-Panel (a) shows the average Fourier spectrum.
-Panel (b) shows a group average waveform for binocular presentation (low pass filtered at 5 Hz), with the driving signal plotted at the foot.
-Panel (c) shows the ratio of binocular to monocular response.
-The red circles show the ratios at the first harmonic (0.5 Hz) and the blue squares show the ratios at the second harmonic (1 Hz).
-Panels (d,e) show contrast response functions at 0.5 Hz for different conditions.
-Panel (f) shows contrast response functions at 0.4 Hz for three conditions.
-Panels (g-i) are in the same format but for the second harmonic responses.
-Shaded regions and error bars indicate bootstrapped standard errors.", fig.align="center", out.width = '85%', echo=FALSE}
-
-knitr::include_graphics(paste0(figdir,'pupildataLum.pdf'))
-```
-
-Figure \@ref(fig:pupildataLum)f shows responses at 0.4 Hz, for the same conditions, as well as for a condition in which a monocular stimulus flickered at 0.4 Hz (grey circles).
-Again there was evidence of weak suppression between the eyes, as the purple triangles fall below the grey circles (see Table \@ref(tab:TableStatsMonXBinXFig3f) for summary of statistical results).
-The dichoptic cross condition also shows evidence of suppressive modulation with target contrast (see Table \@ref(tab:TableStatsMonXDichXFig3f) for summary of statistical results).
-The same pattern is also observed at the second harmonic (Figure \@ref(fig:pupildataLum)i, see Tables \@ref(tab:TableStatsMonXBinXFig3i) and \@ref(tab:TableStatsMonXDichXFig3i) for summary of statistical results).
-
-Finally, we calculated the binocular to monocular ratio at the first and second harmonic frequencies.
-Figure \@ref(fig:pupildataLum)c shows that these ratios are generally below 2 at both frequencies, suggesting that there is summation happening between the eyes but also interocular suppression, therefore suggesting that the signals between the eyes are combined non-linearly.
-At the highest contrast at the second harmonic, the ratio is close to 2, perhaps indicating that a more linear combination is happening for higher contrasts.
-
-## Experiment 2
-
-```{r melanopsin individual, include=FALSE, results='hide'}
-
-# (download and) analyse individual participant data for the melanopsin experiment
-if (processdata > 2){
-
-  for(participant in 1:24){
-
-    # only download and process data if this has not been done already for this participant
-    if (!file.exists(paste0(datadir,'P',500+participant,'summary.RData'))){
-
-      # if there is no directory for this participant's data
-      if (!file.exists(paste0(rawdir,'P',500+participant))){
-        dir.create(paste0(rawdir,'P',500+participant))
-
-       d <- dir(paste0(rawdir,'P',500+participant))
-
-       if (length(d)==0){
-
-         # if the tar file of this participant's data doesn't exist
-         if (!file.exists(paste0(rawdir,'P',500+participant,'.zip'))){
-           # download it from OSF
-           if (!exists('osffiles')){
-           osfnode <- 'xkgd9'
-           osfproject <- osf_retrieve_node(osfnode)
-          osffiles <- osf_ls_files(osfproject,n_max=300)}
-          fid <- which(osffiles$name==paste0('P',500+participant,'.zip'))
-          osf_download(osffiles[fid,],rawdir,progress=TRUE)
-         }
-
-         # then unzip the tar file
-         unzip(paste0(rawdir,'P',500+participant,'.zip'),exdir=paste0(rawdir))
-
-         # and delete the tar file to save storage space
-         file.remove(paste0(rawdir,'P',500+participant,'.zip'))
-       }
-      }
-
-      d <- dir(paste0(rawdir,'P',500+participant),full.names=TRUE)
-
-    tic()
-
-    pupiltargets <- array(0,dim=c(3,2,60))
-    pupilmasks <- pupiltargets
-    pupiltargets2 <- pupiltargets
-    pupilmasks2 <- pupiltargets
-    pupilwaveforms <- array(0,dim=c(3,2,60,120*14))
-    pupilspectra <- array(0,dim=c(3,2,60,300))
-    timeseq <- seq(1/120,10,length.out=120*10)
-    timeseq2 <- seq(1/120,14,length.out=120*14)
-    targetindex <- (0.5*10)+1
-    maskindex <- (0.4*10)+1
-    targetindex2 <- (0.5*2*10)+1
-    maskindex2 <- (2*0.4*10)+1
-
-    repcounterP <- (1:60)*0
-    afiles <- dir(path=paste0(rawdir,'P',500+participant),pattern='*annotations.csv',full.names=TRUE)
-
-    for (block in 1:length(afiles)){
-        tic()
-        adata <- read.csv(paste0(rawdir,'P',500+participant,'/',paste0('P',500+participant,'_S',block),'_annotations.csv'))
-
-        trialtimes <- NULL
-        trialtypes <- NULL
-        for (t in 1:(nrow(adata)/2)){
-          trialtimes[t] <- mean(adata$timestamp[(t*2 - 1):(t*2)])
-          trialtypes[t] <- adata$condition_code[t*2]
-        }
-
-        trialtypes[which(trialtypes>15)] <- trialtypes[which(trialtypes>15)] + 5
-        inclist <- NULL
-        for (t in 11:15){
-          i <- which(trialtypes==t)
-          inclist[t-10] <- i[2]
-        }
-        inclist <- inclist[which(!is.na(inclist))]
-        trialtypes[inclist] <- trialtypes[inclist] + 5
-
-        pdata <- read.csv(paste(rawdir,'P',500+participant,'/',paste0('P',500+participant,'_S',block),'_pupil_positions.csv',sep=''))
-        pdata2 <- pdata[,c(1,3,4,14)]
-        pdata2 <- pdata2[which(pdata2[,3]>0.2),]
-
-        for (trialno in 1:length(trialtypes)){
-          repcounterP[trialtypes[trialno]] <- repcounterP[trialtypes[trialno]] + 1
-          for (eye in 1:2){
-            eyedata <- pdata2[which(pdata2[,2]==(2-eye)),]      
-            a <- which(eyedata[,1]>trialtimes[trialno]+2)
-            b <- which(eyedata[,1]<(trialtimes[trialno]+12))
-            i <- intersect(a,b)
-            trial <- eyedata[i,]
-            trial <- trial[which(!is.na(trial[,4])),]
-            trial[,1] <- trial[,1] - trial[1,1]
-            if (nrow(trial)>3){
-              resampled <- interp1(trial[,1],trial[,4],timeseq,method='linear',extrap=TRUE)
-              fspec <- (fft(resampled)/length(resampled))
-              pupiltargets[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno]] <- fspec[targetindex]
-              pupilmasks[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno]] <- fspec[maskindex]
-              pupiltargets2[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno]] <- fspec[targetindex2]
-              pupilmasks2[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno]] <- fspec[maskindex2]
-              pupilspectra[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno],1:300] <- fspec[1:300]
-            }
-
-            a <- which(eyedata[,1]>(trialtimes[trialno]-1))
-            b <- which(eyedata[,1]<(trialtimes[trialno]+13))
-            i <- intersect(a,b)
-            trial <- eyedata[i,]
-            trial[,1] <- trial[,1] - trial[1,1]
-            if (nrow(trial)>3){
-              trial <- trial[which(!is.na(trial[,4])),]
-              resampled <- interp1(trial[,1],trial[,4],timeseq2,method='linear',extrap=TRUE)
-              pupilwaveforms[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno],] <- resampled - mean(resampled[1:120])
-            }
-          }
-        }
-    }
-
-    cleanmeansP <- matrix(0,nrow=6,ncol=5)
-    cleanmasksP <- matrix(0,nrow=6,ncol=5)
-    cleanmeansP2 <- matrix(0,nrow=6,ncol=5)
-    cleanmasksP2 <- matrix(0,nrow=6,ncol=5)
-
-    for (cond in 1:6){
-        startindex <- (10*(cond-1))
-        for (level in 1:5){
-          temp <- c(pupiltargets[,,startindex+level],pupiltargets[,,startindex+level+5])
-          cartdata <- data.frame(Re(temp),Im(temp))
-          if (sum(cartdata)!=0){
-            D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-            i <- which(D<SDthresh)
-            cleanmeansP[cond,level] <- mean(temp[i])}
-
-          temp <- c(pupiltargets2[,,startindex+level],pupiltargets2[,,startindex+level+5])
-          cartdata <- data.frame(Re(temp),Im(temp))
-          if (sum(cartdata)!=0){
-            D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-            i <- which(D<SDthresh)
-            cleanmeansP2[cond,level] <- mean(temp[i])}
-
-          temp <- c(pupilmasks[,,startindex+level],pupilmasks[,,startindex+level+5])
-          cartdata <- data.frame(Re(temp),Im(temp))
-          if (sum(cartdata)!=0){
-            D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-            i <- which(D<SDthresh)
-            cleanmasksP[cond,level] <- mean(temp[i])}
-
-          temp <- c(pupilmasks2[,,startindex+level],pupilmasks2[,,startindex+level+5])
-          cartdata <- data.frame(Re(temp),Im(temp))
-          if (sum(cartdata)!=0){
-            D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-            i <- which(D<SDthresh)
-            cleanmasksP2[cond,level] <- mean(temp[i])}
-        }
-    }
-
-    meanwavesP <- apply(pupilwaveforms[,,c(15,20),],4,mean,na.rm=TRUE)
-    meanspectraP <- apply(pupilspectra[,,c(15,20),],4,mean,na.rm=TRUE)
-    save(file=paste(datadir,'P',500+participant,'_summaryMel.RData',sep=''),list=c('cleanmeansP','cleanmasksP','cleanmeansP2','cleanmasksP2','meanspectraP','meanwavesP'))
-
-    if (cleanupraw==1){file.remove(d)} # delete raw data files to save space
-    }
-  }}
-```
-
-```{r melanopsin group, include=FALSE, results='hide'}
-
-# load in individual participant data and average, save group data
-if (processdata > 1){
-  for (participant in 1:24){
-         # if the summary file of this participant's data doesn't exist
-         if (!file.exists(paste0(datadir,'P',500+participant,'summaryMel.RData'))){
-           # download it from OSF
-           if (!exists('osffilesP')){
-           osfnode <- '9ebtd'
-           osfproject <- osf_retrieve_node(osfnode)
-          osffilesP <- osf_ls_files(osfproject,n_max=300)}
-          fid <- which(osffilesP$name==paste0('P',500+participant,'summaryMel.RData'))
-          osf_download(osffilesP[fid,],datadir,progress=TRUE)
-         }
-}
-
-  d <- dir(datadir,pattern='summaryMel.RData', full.names = TRUE)
-
-  tempmasksP <- array(0,dim=c(length(d),6,5))
-  tempmeansP <- tempmasksP
-  tempmeansP2 <- tempmasksP
-  tempmasksP2 <- tempmasksP
-  tempspectraP <- array(0,dim=c(length(d),300))
-  tempwavesP <- array(0,dim=c(length(d),1680))
-
-  for (s in 1:length(d)){
-
-    load(d[s])
-
-    tempmasksP[s,,] <- cleanmasksP
-    tempmeansP[s,,] <- cleanmeansP
-    tempmasksP2[s,,] <- cleanmasksP2
-    tempmeansP2[s,,] <- cleanmeansP2
-    tempspectraP[s,] <- meanspectraP
-    tempwavesP[s,] <- meanwavesP
-  }
-
-  tempspectraP <- tempspectraP[-c(2,4,13,20,26),]
-
-  cleanmeansP <- matrix(0,nrow=6,ncol=5)
-  cleanmeansPCI <- array(0,c(2,6,5))
-  cleanmasksP <- matrix(0,nrow=6,ncol=5)
-  cleanmasksPCI <- array(0,c(2,6,5))
-  cleanmeansP2 <- matrix(0,nrow=6,ncol=5)
-  cleanmeansP2CI <- array(0,c(2,6,5))
-  cleanmasksP2 <- matrix(0,nrow=6,ncol=5)
-  cleanmasksP2CI <- array(0,c(2,6,5))
-
-  for (cond in 1:6){
-    for (level in 1:5){
-
-      temp <- tempmeansP[,cond,level]
-      cartdata <- data.frame(Re(temp),Im(temp))
-      if (sum(cartdata)!=0){
-        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-        i <- which(D<SDthresh)
-        mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
-        cleanmeansP[cond,level] <- mean(temp[i])
-        cleanmeansPCI[1,cond,level] <- mbs$lowerCI
-        cleanmeansPCI[2,cond,level] <- mbs$upperCI
-      }
-
-      temp <- tempmasksP[,cond,level]
-      cartdata <- data.frame(Re(temp),Im(temp))
-      if (sum(cartdata)!=0){
-        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-        i <- which(D<SDthresh)
-        mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
-        cleanmasksP[cond,level] <- mean(temp[i])
-        cleanmasksPCI[1,cond,level] <- mbs$lowerCI
-        cleanmasksPCI[2,cond,level] <- mbs$upperCI
-      }
-
-      temp <- tempmeansP2[,cond,level]
-      cartdata <- data.frame(Re(temp),Im(temp))
-      if (sum(cartdata)!=0){
-        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-        i <- which(D<SDthresh)
-        mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
-        cleanmeansP2[cond,level] <- mean(temp[i])
-        cleanmeansP2CI[1,cond,level] <- mbs$lowerCI
-        cleanmeansP2CI[2,cond,level] <- mbs$upperCI
-      }
-
-      temp <- tempmasksP2[,cond,level]
-      cartdata <- data.frame(Re(temp),Im(temp))
-      if (sum(cartdata)!=0){
-        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-        i <- which(D<SDthresh)
-        mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
-        cleanmasksP2[cond,level] <- mean(temp[i])
-        cleanmasksP2CI[1,cond,level] <- mbs$lowerCI
-        cleanmasksP2CI[2,cond,level] <- mbs$upperCI
-      }
-    }
-  }
-
-  meanspectraP <- (1:300)*0
-  meanspectraPCI <- array(0,c(2,300))
-
-  for (f in 2:300){
-    temp <- tempspectraP[,f]
-    cartdata <- data.frame(Re(temp),Im(temp))
-    if (sum(cartdata)!=0){
-      D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-      i <- which(D<SDthresh) 
-      mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
-      meanspectraP[f] <- mbs$meanamp
-      meanspectraPCI[1,f] <- mbs$lowerCI
-      meanspectraPCI[2,f] <- mbs$upperCI
-    }
-  }
-
-  meanwavesP <- NULL
-  meanwavesPCI <- array(0,dim=c(2,dim(tempwavesP)[2]))
-
-  nsubjs <- dim(tempwavesP)[1]
-  for (t in 1:dim(tempwavesP)[2]){
-    temp <- tempwavesP[,t]
-    i <- which(abs(temp-mean(temp))<(SDthresh*sd(temp)))
-    meanwavesP[t] <- mean(temp[i])
-    bspop <- NULL
-    for (s in 1:nbootstraps){bspop[s] <- mean(sample(temp[i],length(i),replace=TRUE))}
-    meanwavesPCI[,t] <- quantile(bspop,c(0.16,0.84),na.rm=TRUE)
-  }
-
-  save(file=paste0(datadir,'AveragedataMel.RData'),list=c('meanwavesP','meanwavesPCI','cleanmeansP','cleanmeansPCI','cleanmasksP','cleanmasksPCI','cleanmeansP2','cleanmeansP2CI','cleanmasksP2','cleanmasksP2CI','meanspectraP','meanspectraPCI','tempmeansP','tempmeansP2','tempmasksP','tempmasksP2'))
-
-  }
-```
-
-```{r melanopsin plot, include=FALSE, results='hide'}
-
-# generate plot showing the group pupillometry data for the melanopsin experiment 
-if (!file.exists(paste0(datadir,'AveragedataMel.RData'))){
-           # download it from OSF
-           if (!exists('osffilesP')){
-           osfnode <- '9ebtd'
-           osfproject <- osf_retrieve_node(osfnode)
-          osffilesP <- osf_ls_files(osfproject,n_max=300)}
-          fid <- which(osffilesP$name=='AveragedataMel.RData')
-          osf_download(osffilesP[fid,],datadir,progress=TRUE)
-         }
-
-load(file=paste0(datadir,'AveragedataMel.RData'))
-
-if (processdata > 0){
-
-allPMelratios <- abs(cleanmeansP[2,])/abs(cleanmeansP[1,])
-allPMel2ratios <- abs(cleanmeansP2[2,])/abs(cleanmeansP2[1,])
-
-# plot figure  
-plotlims <- c(15,40,0,5)  
-ticklocsx <- contrastsdB
-ticklabelsx <-c(6,12,24,48,96) 
-ticklocsy <- seq(0,5,0.5)    # locations of tick marks on y axis
-ticklabelsy <- ticklocsy
-
-postscript("SumMel.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
-
-par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx)     
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
-title(xlab="Target contrast (% of max)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  
-title(ylab="Bin:Mon ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-
-lines(contrastsdB,allPMelratios, col=colpal[1], lwd=3, cex=0.5)
-lines(contrastsdB,allPMel2ratios, col=colpal[2], lwd=3, cex=0.5)
-points(contrastsdB,allPMelratios, pch = 21, col='black', bg=colpal[1], cex=1.6, lwd=3)
-points(contrastsdB,allPMel2ratios, pch = 22, col='black', bg=colpal[2], cex=1.6, lwd=3)
-
-legend(contrastsdB[2],5,c('Mel 1F','Mel 2F'), pch=21:24, pt.bg=colpal[1:2],box.lwd=2,pt.cex=1.6,pt.lwd=3)
-text(17,4.8,'(c)',adj=0.5,cex=2.5)
-
-dev.off()
-
-plotlims <- c(15,40,0,0.02)
-plotlims2 <- c(15,40,0,0.015) 
-ticklocsx <- contrastsdB    # locations of tick marks on x axis
-ticklocsy <- seq(0,0.02,0.005)
-ticklocsy2 <- seq(0,0.015,0.005)    # locations of tick marks on y axis
-ticklabelsx <-c(6,12,24,48,96)        # set labels for x ticks
-ticklabelsy <- ticklocsy
-ticklabelsy2 <- ticklocsy2     # set labels for y ticks
-
-postscript("CRF1p.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
-
-par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
-title(xlab="Target contrast (% of max)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
-title(ylab="Amplitude at 0.5Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
-
-for (cond in 1:3){
-  lines(contrastsdB,abs(cleanmeansP[cond,]), col=colpal[cond], lwd=3, cex=0.5)
-  arrows(contrastsdB,abs(cleanmeansP[cond,]),contrastsdB,cleanmeansPCI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
-  arrows(contrastsdB,abs(cleanmeansP[cond,]),contrastsdB,cleanmeansPCI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
-  points(contrastsdB,abs(cleanmeansP[cond,]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
-}  
-legend(22,0.02,c('Monocular','Binocular','Dichoptic'),pch=21:23,pt.bg=colpal[1:3],pt.lwd=3,pt.cex=1.6,box.lwd=2)
-text(17,0.019,'(d)',adj=0.5,cex=2.5)
-
-dev.off()
-
-postscript("CRF2p.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
-
-par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
-title(xlab="Target contrast (% of max)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
-title(ylab="Amplitude at 0.5Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
-
-condlist <- c(1,5,6)
-pointlist <- c(21,24,25)
-for (cond in 1:3){
-  lines(contrastsdB,abs(cleanmeansP[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)  
-  arrows(contrastsdB,abs(cleanmeansP[condlist[cond],]),contrastsdB,cleanmeansPCI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
-  arrows(contrastsdB,abs(cleanmeansP[condlist[cond],]),contrastsdB,cleanmeansPCI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)  
-  points(contrastsdB,abs(cleanmeansP[condlist[cond],]), pch = pointlist[cond], col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
-}  
-legend(22,0.02,c('Monocular','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[condlist],pt.lwd=3,pt.cex=1.6,box.lwd=2)
-text(17,0.019,'(e)',adj=0.5,cex=2.5)
-
-dev.off()
-
-postscript("CRF3p.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
-
-par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
-title(xlab="Target contrast (% of max)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
-title(ylab="Amplitude at 0.4Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
-
-for (cond in 4:6){
-  lines(contrastsdB,abs(cleanmasksP[cond,]), col=colpal[cond], lwd=3, cex=0.5)   
-  arrows(contrastsdB,abs(cleanmasksP[cond,]),contrastsdB,cleanmasksPCI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
-  arrows(contrastsdB,abs(cleanmasksP[cond,]),contrastsdB,cleanmasksPCI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)    
-  points(contrastsdB,abs(cleanmasksP[cond,]), pch = pointlist[cond-3], col='black', bg=colpal[cond], cex=1.6, lwd=3) 
-}
-legend(22,0.02,c('Monocular 0.4Hz','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[4:6],pt.lwd=3,pt.cex=1.6,box.lwd=2)
-text(17,0.019,'(f)',adj=0.5,cex=2.5)
-
-dev.off()
-
-postscript("CRF1p2.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
-
-par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims2[3:4])   # create an empty axis of the correct dimensions
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy2, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
-mtext(text = ticklabelsy2, side = 2, at=ticklocsy2, line=0.2, las=1) 
-title(xlab="Target contrast (% of max)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
-title(ylab="Amplitude at 1Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
-
-for (cond in 1:3){
-  lines(contrastsdB,abs(cleanmeansP2[cond,]), col=colpal[cond], lwd=3, cex=0.5)
-  arrows(contrastsdB,abs(cleanmeansP2[cond,]),contrastsdB,cleanmeansP2CI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
-  arrows(contrastsdB,abs(cleanmeansP2[cond,]),contrastsdB,cleanmeansP2CI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
-  points(contrastsdB,abs(cleanmeansP2[cond,]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
-}  
-legend(22,0.015,c('Monocular','Binocular','Dichoptic'),pch=21:23,pt.bg=colpal[1:3],pt.lwd=3,pt.cex=1.6,box.lwd=2)
-text(17,0.014,'(g)',adj=0.5,cex=2.5)
-
-dev.off()
-
-postscript("CRF2p2.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
-
-par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims2[3:4])   # create an empty axis of the correct dimensions
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy2, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
-mtext(text = ticklabelsy2, side = 2, at=ticklocsy2, line=0.2, las=1)
-title(xlab="Target contrast (% of max)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
-title(ylab="Amplitude at 1Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
-
-condlist <- c(1,5,6)
-pointlist <- c(21,24,25)
-for (cond in 1:3){
-  lines(contrastsdB,abs(cleanmeansP2[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)  
-  arrows(contrastsdB,abs(cleanmeansP2[condlist[cond],]),contrastsdB,cleanmeansP2CI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
-  arrows(contrastsdB,abs(cleanmeansP2[condlist[cond],]),contrastsdB,cleanmeansP2CI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)  
-  points(contrastsdB,abs(cleanmeansP2[condlist[cond],]), pch = pointlist[cond], col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
-}  
-legend(22,0.015,c('Monocular','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[condlist],pt.lwd=3,pt.cex=1.6,box.lwd=2)
-text(17,0.014,'(h)',adj=0.5,cex=2.5)
-
-dev.off()
-
-postscript("CRF3p2.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
-
-par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims2[3:4])   # create an empty axis of the correct dimensions
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy2, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
-mtext(text = ticklabelsy2, side = 2, at=ticklocsy2, line=0.2, las=1)
-title(xlab="Target contrast (% of max)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
-title(ylab="Amplitude at 0.8Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
-
-for (cond in 4:6){
-  lines(contrastsdB,abs(cleanmasksP2[cond,]), col=colpal[cond], lwd=3, cex=0.5)   
-  arrows(contrastsdB,abs(cleanmasksP2[cond,]),contrastsdB,cleanmasksP2CI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
-  arrows(contrastsdB,abs(cleanmasksP2[cond,]),contrastsdB,cleanmasksP2CI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)    
-  points(contrastsdB,abs(cleanmasksP2[cond,]), pch = pointlist[cond-3], col='black', bg=colpal[cond], cex=1.6, lwd=3) 
-}
-legend(22,0.015,c('Monocular 0.4Hz','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[4:6],pt.lwd=3,pt.cex=1.6,box.lwd=2)
-text(17,0.014,'(i)',adj=0.5,cex=2.5)
-
-dev.off()
-
-postscript("SpecP.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 8)
-
-frequencies <- (0:299)/10
-
-plotlims <- c(0,2,0,0.015) 
-ticklocsx <- seq(0,2,0.25)    # locations of tick marks on x axis
-ticklocsy <- seq(0,0.015,0.005)    # locations of tick marks on y axis
-ticklabelsx <-ticklocsx        # set labels for x ticks
-ticklabelsy <- ticklocsy    # set labels for y ticks
-
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
-title(xlab="Frequency (Hz)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  
-title(ylab="Amplitude (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
-
-polygon(frequencies[c(3:21,21:3)],c(meanspectraPCI[1,3:21],meanspectraPCI[2,21:3]),col=colpal[2],border=NA)
-
-lines(frequencies[3:21],abs(meanspectraP[3:21]), col=colpal[2], lwd=3, cex=0.5)
-
-text(0.1,0.014,'(a)',adj=0.5,cex=2.5)
-
-dev.off()
-
-postscript("timecourseP.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 8)
-
-times <- seq((1/120)-1,13,1/120)
-sinewave <- sin(0.5*times * 2*pi)
-sinewave[1:120] <- 0
-sinewave[1560:1680] <- 0
-
-plotlims <- c(-1,13,-0.5,0.5)
-ticklocsx <- seq(-1,13,1)    # locations of tick marks on x axis
-ticklocsy <- seq(-0.5,0.5,0.5)    # locations of tick marks on y axis
-ticklabelsx <- ticklocsx        # set labels for x ticks
-ticklabelsy <- ticklocsy    # set labels for y ticks
-
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
-title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)
-title(ylab="Amplitude (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
-
-filt <- butter(3,0.083)
-filtwaveP <- signal::filter(filt, meanwavesP)
-filtU <- signal::filter(filt,meanwavesPCI[1,])
-filtL <- signal::filter(filt,meanwavesPCI[2,])
-polygon(times[c(1:length(times),length(times):1)],c(filtL,filtU[length(filtU):1]),col=colpal[2],border=NA)
-lines(times, filtwaveP, col=colpal[2], lwd=1.5)
-lines(times, (sinewave/10)-0.4, col='black', lwd=3)
-
-text(-0.7,0.4,'(b)',adj=0.5,cex=2.5)
-
-dev.off()
-
-PostScriptTrace('CRF1p.ps')
-p1 <- readPicture('CRF1p.ps.xml')
-PostScriptTrace('CRF2p.ps')
-p2 <- readPicture('CRF2p.ps.xml')
-PostScriptTrace('CRF3p.ps')
-p3 <- readPicture('CRF3p.ps.xml')
-PostScriptTrace('CRF1p2.ps')
-p4 <- readPicture('CRF1p2.ps.xml')
-PostScriptTrace('CRF2p2.ps')
-p5 <- readPicture('CRF2p2.ps.xml')
-PostScriptTrace('CRF3p2.ps')
-p6 <- readPicture('CRF3p2.ps.xml')
-PostScriptTrace('SpecP.ps')
-p7 <- readPicture('SpecP.ps.xml')
-PostScriptTrace('timecourseP.ps')
-p8 <- readPicture('timecourseP.ps.xml')
-PostScriptTrace('SumMel.ps')
-p9 <- readPicture('SumMel.ps.xml')
-
-for (n in 1:length(p7@paths)){
-  temp <- class(p7@paths[n]$path)[1]
-  if (pmatch(temp,"PictureFill",nomatch=0)){
-    if (sum(col2rgb(p7@paths[n]$path@rgb))<765){p7@paths[n]$path@rgb <- addalpha(p7@paths[n]$path@rgb,alpha=0.2)}}}
-
-for (n in 1:length(p8@paths)){
-  temp <- class(p8@paths[n]$path)[1]
-  if (pmatch(temp,"PictureFill",nomatch=0)){
-    if (sum(col2rgb(p8@paths[n]$path@rgb))<765){p8@paths[n]$path@rgb <- addalpha(p8@paths[n]$path@rgb,alpha=0.2)}}}
-
-pdf(paste0(figdir,"pupildataMel.pdf"), bg="transparent", height = 20, width = 15)
-
-par(mar=c(0.1,0.1,0.1,0.1))
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(0,1), ylim=c(0,1))
-
-grid.picture(p1,x=0.17,y=0.4,width=0.32,height=1)
-grid.picture(p2,x=0.5,y=0.4,width=0.32,height=1)
-grid.picture(p3,x=0.83,y=0.4,width=0.32,height=1)
-grid.picture(p4,x=0.17,y=0.15,width=0.32,height=1)
-grid.picture(p5,x=0.5,y=0.15,width=0.32,height=1)
-grid.picture(p6,x=0.83,y=0.15,width=0.32,height=1)
-grid.picture(p7,x=0.25,y=0.85,width=0.5,height=1)
-grid.picture(p8,x=0.25,y=0.63,width=0.5,height=1)
-grid.picture(p9,x=0.75,y=0.73,width=0.5,height=1)
-
-text(0.5,0.98,'Melanopsin',cex=4)
-
-dev.off()
-
-file.remove(c('CRF1p.ps','CRF2p.ps','CRF3p.ps','CRF1p2.ps','CRF2p2.ps','CRF3p2.ps','SpecP.ps','timecourseP.ps','SumMel.ps'))
-file.remove(c('CRF1p.ps.xml','CRF2p.ps.xml','CRF3p.ps.xml','CRF1p2.ps.xml','CRF2p2.ps.xml','CRF3p2.ps.xml','SpecP.ps.xml','timecourseP.ps.xml','SumMel.ps.xml'))
-
-  }
-```
-
-```{r melanopsin statistics, include=FALSE, results='hide'}
-
-# do statistics on the melanopsin data
-alldata <- NULL
-groupID <- NULL
-allP <- NULL
-counter <- 0
-for (cont in 1:dim(tempmeansP)[3]){
-  for (p in 1:dim(tempmeansP)[1]){
-    counter <- counter + 1
-    alldata[counter] <- tempmeansP[p,3,cont]
-    groupID[counter] <- cont
-    allP[counter] <- p
-  }
-}
-dichA2c <- anovacirc.test(alldata,group=groupID,participant=allP)
-
-alldata <- NULL
-allgroupA <- NULL
-allgroupB <- NULL
-allP <- NULL
-counter <- 0
-for (p in 1:12){
-  for (lev in 1:5){
-    for (cond in 1:2){
-    counter <- counter + 1
-    alldata[counter] <- tempmeansP[p,cond,lev]
-    allgroupA[counter] <- lev
-    allgroupB[counter] <- cond
-    allP[counter] <- p
-    }
-  }
-}
-monbinPstats <- anovacirc2way(alldata,allgroupA,allgroupB,allP)
-
-alldata <- NULL
-allgroupA <- NULL
-allgroupB <- NULL
-allP <- NULL
-counter <- 0
-for (p in 1:12){
-  for (lev in 1:5){
-    counter <- counter + 1
-    alldata[counter] <- tempmeansP[p,1,lev]
-    allgroupA[counter] <- lev
-    allgroupB[counter] <- 1
-    allP[counter] <- p
-
-    counter <- counter + 1
-    alldata[counter] <- tempmeansP[p,3,lev]
-    allgroupA[counter] <- lev
-    allgroupB[counter] <- 2
-    allP[counter] <- p
-  }
-}
-
-mondichPstats <- anovacirc2way(alldata,allgroupA,allgroupB,allP)
-
-alldata <- NULL
-allgroupA <- NULL
-allgroupB <- NULL
-allP <- NULL
-counter <- 0
-for (p in 1:12){
-  for (lev in 1:5){
-    counter <- counter + 1
-    alldata[counter] <- tempmeansP[p,1,lev]
-    allgroupA[counter] <- lev
-    allgroupB[counter] <- 1
-    allP[counter] <- p
-
-    counter <- counter + 1
-    alldata[counter] <- tempmeansP[p,5,lev]
-    allgroupA[counter] <- lev
-    allgroupB[counter] <- 2
-    allP[counter] <- p
-  }
-}
-
-monbinPstatsX <- anovacirc2way(alldata,allgroupA,allgroupB,allP)
-
-alldata <- NULL
-allgroupA <- NULL
-allgroupB <- NULL
-allP <- NULL
-counter <- 0
-for (p in 1:12){
-  for (lev in 1:5){
-    counter <- counter + 1
-    alldata[counter] <- tempmeansP[p,1,lev]
-    allgroupA[counter] <- lev
-    allgroupB[counter] <- 1
-    allP[counter] <- p
-
-    counter <- counter + 1
-    alldata[counter] <- tempmeansP[p,6,lev]
-    allgroupA[counter] <- lev
-    allgroupB[counter] <- 2
-    allP[counter] <- p
-  }
-}
-
-mondichPstatsX <- anovacirc2way(alldata,allgroupA,allgroupB,allP)
-
-```
-
-The results of the melanopsin experiment are summarised in Figure \@ref(fig:pupildataMel).
-The average Fourier spectrum is displayed in Figure \@ref(fig:pupildataMel)a, and also shows clear responses at both the first harmonic frequency (0.5 Hz) and the second harmonic frequency (1 Hz) of approximately equal amplitude.
-These results demonstrate that we can evoke measurable steady-state pupil responses at 0.5 Hz by selectively stimulating the melanopsin-containing retinal ganglion cells whilst ignoring rods and nominally silencing all three cone classes.
-The group average waveform for binocular presentation is shown in Figure \@ref(fig:pupildataMel)b and shows a substantial pupil constriction at stimulus onset, followed by visible oscillations at approximately the flicker frequency (0.5 Hz, see waveform at foot).
-
-Figure \@ref(fig:pupildataMel)d shows contrast response functions for melanopsin-directed stimuli flickering at 0.5 Hz.
-The amplitude of the binocular condition (blue squares) is similar to that of the monocular condition (red circles) across all target contrasts (all error bars overlap, see Table \@ref(tab:TableStatsFig4d) for summary of statistical results).
-At the second harmonic the binocular response is substantially greater than the monocular response at higher contrasts where the response is above baseline (Figure \@ref(fig:pupildataMel)g, see Table \@ref(tab:TableStatsFig4g) for summary of statistical results).
-
-```{r pupildataMel, fig.cap="Summary of pupillometry results for the melanopsin experiment for N=12 participants.
-Panel (a) shows the average Fourier spectrum.
-Panel (b) shows a group average waveform for binocular presentation (low pass filtered at 5 Hz), with the driving signal plotted at the foot.
-Panel (c) shows the ratio of binocular to monocular response.
-The red circles show the ratios at the first harmonic (0.5 Hz) and the blue squares show the ratios at the second harmonic (1 Hz).
-Panels (d,e) show contrast response functions at 0.5 Hz for different conditions.
-Panel (f) shows contrast response functions at 0.4 Hz for three conditions.
-Panels (g-i) are in the same format but for the second harmonic responses.
-Shaded regions and error bars indicate bootstrapped standard errors.", fig.align="center", out.width = '85%', echo=FALSE}
-
-knitr::include_graphics(paste0(figdir,'pupildataMel.pdf'))
-```
-
-In Figure \@ref(fig:pupildataMel)e, we again plot responses to monocular target stimuli flickering at 0.5 Hz, when the other eye viewed stimuli flickering at 0.4 Hz (here too, the red monocular-only data are replotted from Figure \@ref(fig:pupildataMel)d for comparison).
-For the binocular cross condition (shown in purple), responses were slightly suppressed across all target contrasts (see Table \@ref(tab:TableStatsMonBinXFig4e) for summary of statistical results).
-For the dichoptic cross condition (shown in yellow), responses were also slightly suppressed across the contrast range (see Table \@ref(tab:TableStatsMonDichXFig4e) for summary of statistical results).
-This pattern is also observed at the second harmonic (Figure \@ref(fig:pupildataMel)h, see Tables \@ref(tab:TableStatsMonBinXFig4h) and \@ref(tab:TableStatsMonDichXFig4h) for summary of statistical results).
-
-Figure \@ref(fig:pupildataMel)f shows responses at 0.4 Hz, for the same conditions, as well as for a condition in which a monocular stimulus flickered at 0.4 Hz (grey circles).
-These data are perhaps too noisy to interpret, though we note that the binocular cross data (purple triangles) are generally below the monocular data (grey circles), perhaps indicating suppression (see Table \@ref(tab:TableStatsMonXBinXFig4f) for summary of statistical results).
-The same pattern is generally also observed at the second harmonic (Figure \@ref(fig:pupildataMel)i, see Table \@ref(tab:TableStatsMonXBinXFig4i) for summary of statistical results).
-
-Finally, we calculated the binocular to monocular ratio at the first and second harmonic frequencies.
-Figure \@ref(fig:pupildataMel)c shows that these ratios are around 1 at the first harmonic, suggesting that there is strong interocular suppression between the eyes, and binocular signal combination is therefore strongly non-linear.
-
-## Experiment 3
-
-```{r L-M individual, include=FALSE, results='hide'}
-
-# (download and) analyse individual participant data for the L-M experiment
-if (processdata > 2){
-
-  for(participant in 1:24){
-
-    # only download and process data if this has not been done already for this participant
-    if (!file.exists(paste0(datadir,'P',700+participant,'summary.RData'))){
-
-      # if there is no directory for this participant's data
-      if (!file.exists(paste0(rawdir,'P',700+participant))){
-        dir.create(paste0(rawdir,'P',700+participant))
-
-       d <- dir(paste0(rawdir,'P',700+participant))
-
-       if (length(d)==0){
-
-         # if the tar file of this participant's data doesn't exist
-         if (!file.exists(paste0(rawdir,'P',700+participant,'.zip'))){
-           # download it from OSF
-           if (!exists('osffiles')){
-           osfnode <- 'pexyk'
-           osfproject <- osf_retrieve_node(osfnode)
-          osffiles <- osf_ls_files(osfproject,n_max=300)}
-          fid <- which(osffiles$name==paste0('P',700+participant,'.zip'))
-          osf_download(osffiles[fid,],rawdir,progress=TRUE)
-         }
-
-         # then unzip the tar file
-         unzip(paste0(rawdir,'P',700+participant,'.zip'),exdir=paste0(rawdir))
-
-         # and delete the tar file to save storage space
-         file.remove(paste0(rawdir,'P',700+participant,'.zip'))
-       }
-      }
-
-      d <- dir(paste0(rawdir,'P',700+participant),full.names=TRUE)
-
-    tic()
-
-    pupiltargets <- array(0,dim=c(3,2,60))
-    pupilmasks <- pupiltargets
-    pupiltargets2 <- pupiltargets
-    pupilmasks2 <- pupiltargets
-    pupilwaveforms <- array(0,dim=c(3,2,60,120*14))
-    pupilspectra <- array(0,dim=c(3,2,60,300))
-    timeseq <- seq(1/120,10,length.out=120*10)
-    timeseq2 <- seq(1/120,14,length.out=120*14)
-    targetindex <- (0.5*10)+1
-    maskindex <- (0.4*10)+1
-    targetindex2 <- (0.5*2*10)+1
-    maskindex2 <- (2*0.4*10)+1
-
-    repcounterP <- (1:60)*0
-    afiles <- dir(path=paste0(rawdir,'P',700+participant),pattern='*annotations.csv',full.names=TRUE)
-
-    for (block in 1:length(afiles)){
-        tic()
-        adata <- read.csv(paste0(rawdir,'P',700+participant,'/',paste0('P',700+participant,'_S',block),'_annotations.csv'))
-
-        trialtimes <- NULL
-        trialtypes <- NULL
-        for (t in 1:(nrow(adata)/2)){
-          trialtimes[t] <- mean(adata$timestamp[(t*2 - 1):(t*2)])
-          trialtypes[t] <- adata$condition_code[t*2]
-        }
-
-        trialtypes[which(trialtypes>15)] <- trialtypes[which(trialtypes>15)] + 5
-        inclist <- NULL
-        for (t in 11:15){
-          i <- which(trialtypes==t)
-          inclist[t-10] <- i[2]
-        }
-        inclist <- inclist[which(!is.na(inclist))]
-        trialtypes[inclist] <- trialtypes[inclist] + 5
-
-        pdata <- read.csv(paste(rawdir,'P',700+participant,'/',paste0('P',700+participant,'_S',block),'_pupil_positions.csv',sep=''))
-        pdata2 <- pdata[,c(1,3,4,14)]
-        pdata2 <- pdata2[which(pdata2[,3]>0.2),]
-
-        for (trialno in 1:length(trialtypes)){
-          repcounterP[trialtypes[trialno]] <- repcounterP[trialtypes[trialno]] + 1
-          for (eye in 1:2){
-            eyedata <- pdata2[which(pdata2[,2]==(2-eye)),]      
-            a <- which(eyedata[,1]>trialtimes[trialno]+2)
-            b <- which(eyedata[,1]<(trialtimes[trialno]+12))
-            i <- intersect(a,b)
-            trial <- eyedata[i,]
-            trial <- trial[which(!is.na(trial[,4])),]
-            trial[,1] <- trial[,1] - trial[1,1]
-            if (nrow(trial)>3){
-              resampled <- interp1(trial[,1],trial[,4],timeseq,method='linear',extrap=TRUE)
-              fspec <- (fft(resampled)/length(resampled))
-              pupiltargets[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno]] <- fspec[targetindex]
-              pupilmasks[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno]] <- fspec[maskindex]
-              pupiltargets2[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno]] <- fspec[targetindex2]
-              pupilmasks2[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno]] <- fspec[maskindex2]
-              pupilspectra[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno],1:300] <- fspec[1:300]
-            }
-
-            a <- which(eyedata[,1]>(trialtimes[trialno]-1))
-            b <- which(eyedata[,1]<(trialtimes[trialno]+13))
-            i <- intersect(a,b)
-            trial <- eyedata[i,]
-            trial[,1] <- trial[,1] - trial[1,1]
-            if (nrow(trial)>3){
-              trial <- trial[which(!is.na(trial[,4])),]
-              resampled <- interp1(trial[,1],trial[,4],timeseq2,method='linear',extrap=TRUE)
-              pupilwaveforms[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno],] <- resampled - mean(resampled[1:120])
-            }
-          }
-        }
-    }
-
-    cleanmeansP <- matrix(0,nrow=6,ncol=5)
-    cleanmasksP <- matrix(0,nrow=6,ncol=5)
-    cleanmeansP2 <- matrix(0,nrow=6,ncol=5)
-    cleanmasksP2 <- matrix(0,nrow=6,ncol=5)
-
-    for (cond in 1:6){
-        startindex <- (10*(cond-1))
-        for (level in 1:5){
-          temp <- c(pupiltargets[,,startindex+level],pupiltargets[,,startindex+level+5])
-          cartdata <- data.frame(Re(temp),Im(temp))
-          if (sum(cartdata)!=0){
-            D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-            i <- which(D<SDthresh)
-            cleanmeansP[cond,level] <- mean(temp[i])}
-
-          temp <- c(pupiltargets2[,,startindex+level],pupiltargets2[,,startindex+level+5])
-          cartdata <- data.frame(Re(temp),Im(temp))
-          if (sum(cartdata)!=0){
-            D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-            i <- which(D<SDthresh)
-            cleanmeansP2[cond,level] <- mean(temp[i])}
-
-          temp <- c(pupilmasks[,,startindex+level],pupilmasks[,,startindex+level+5])
-          cartdata <- data.frame(Re(temp),Im(temp))
-          if (sum(cartdata)!=0){
-            D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-            i <- which(D<SDthresh)
-            cleanmasksP[cond,level] <- mean(temp[i])}
-
-          temp <- c(pupilmasks2[,,startindex+level],pupilmasks2[,,startindex+level+5])
-          cartdata <- data.frame(Re(temp),Im(temp))
-          if (sum(cartdata)!=0){
-            D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-            i <- which(D<SDthresh)
-            cleanmasksP2[cond,level] <- mean(temp[i])}
-        }
-    }
-
-    meanwavesP <- apply(pupilwaveforms[,,c(15,20),],4,mean,na.rm=TRUE)
-    meanspectraP <- apply(pupilspectra[,,c(15,20),],4,mean,na.rm=TRUE)
-    save(file=paste(datadir,'P',700+participant,'_summaryLM.RData',sep=''),list=c('cleanmeansP','cleanmasksP','cleanmeansP2','cleanmasksP2','meanspectraP','meanwavesP'))
-
-    if (cleanupraw==1){file.remove(d)} # delete raw data files to save space
-  }
-
-  }}
-```
-
-```{r L-M group, include=FALSE, results='hide'}
-
-# load in individual participant data and average, save group data
-if (processdata > 1){
-  for (participant in 1:24){
-         # if the summary file of this participant's data doesn't exist
-         if (!file.exists(paste0(datadir,'P',700+participant,'summaryLM.RData'))){
-           # download it from OSF
-           if (!exists('osffilesP')){
-           osfnode <- '9ebtd'
-           osfproject <- osf_retrieve_node(osfnode)
-          osffilesP <- osf_ls_files(osfproject,n_max=300)}
-          fid <- which(osffilesP$name==paste0('P',700+participant,'summaryLM.RData'))
-          osf_download(osffilesP[fid,],datadir,progress=TRUE)
-         }
-}
-
-  d <- dir(datadir,pattern='summaryLM.RData', full.names = TRUE)
-
-  tempmasksP <- array(0,dim=c(length(d),6,5))
-  tempmeansP <- tempmasksP
-  tempmeansP2 <- tempmasksP
-  tempmasksP2 <- tempmasksP
-  tempspectraP <- array(0,dim=c(length(d),300))
-  tempwavesP <- array(0,dim=c(length(d),1680))
-
-  for (s in 1:length(d)){
-
-    load(d[s])
-
-    tempmasksP[s,,] <- cleanmasksP
-    tempmeansP[s,,] <- cleanmeansP
-    tempmasksP2[s,,] <- cleanmasksP2
-    tempmeansP2[s,,] <- cleanmeansP2
-    tempspectraP[s,] <- meanspectraP
-    tempwavesP[s,] <- meanwavesP
-  }
-
-  tempspectraP <- tempspectraP[-c(2,4,13,20,26),]
-
-  cleanmeansP <- matrix(0,nrow=6,ncol=5)
-  cleanmeansPCI <- array(0,c(2,6,5))
-  cleanmasksP <- matrix(0,nrow=6,ncol=5)
-  cleanmasksPCI <- array(0,c(2,6,5))
-  cleanmeansP2 <- matrix(0,nrow=6,ncol=5)
-  cleanmeansP2CI <- array(0,c(2,6,5))
-  cleanmasksP2 <- matrix(0,nrow=6,ncol=5)
-  cleanmasksP2CI <- array(0,c(2,6,5))
-
-  for (cond in 1:6){
-    for (level in 1:5){
-
-      temp <- tempmeansP[,cond,level]
-      cartdata <- data.frame(Re(temp),Im(temp))
-      if (sum(cartdata)!=0){
-        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-        i <- which(D<SDthresh)
-        mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
-        cleanmeansP[cond,level] <- mean(temp[i])
-        cleanmeansPCI[1,cond,level] <- mbs$lowerCI
-        cleanmeansPCI[2,cond,level] <- mbs$upperCI
-      }
-
-      temp <- tempmasksP[,cond,level]
-      cartdata <- data.frame(Re(temp),Im(temp))
-      if (sum(cartdata)!=0){
-        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-        i <- which(D<SDthresh)
-        mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
-        cleanmasksP[cond,level] <- mean(temp[i])
-        cleanmasksPCI[1,cond,level] <- mbs$lowerCI
-        cleanmasksPCI[2,cond,level] <- mbs$upperCI
-      }
-
-      temp <- tempmeansP2[,cond,level]
-      cartdata <- data.frame(Re(temp),Im(temp))
-      if (sum(cartdata)!=0){
-        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-        i <- which(D<SDthresh)
-        mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
-        cleanmeansP2[cond,level] <- mean(temp[i])
-        cleanmeansP2CI[1,cond,level] <- mbs$lowerCI
-        cleanmeansP2CI[2,cond,level] <- mbs$upperCI
-      }
-
-      temp <- tempmasksP2[,cond,level]
-      cartdata <- data.frame(Re(temp),Im(temp))
-      if (sum(cartdata)!=0){
-        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-        i <- which(D<SDthresh)
-        mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
-        cleanmasksP2[cond,level] <- mean(temp[i])
-        cleanmasksP2CI[1,cond,level] <- mbs$lowerCI
-        cleanmasksP2CI[2,cond,level] <- mbs$upperCI
-      }
-    }
-  }
-
-  meanspectraP <- (1:300)*0
-  meanspectraPCI <- array(0,c(2,300))
-
-  for (f in 2:300){
-    temp <- tempspectraP[,f]
-    cartdata <- data.frame(Re(temp),Im(temp))
-    if (sum(cartdata)!=0){
-      D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-      i <- which(D<SDthresh) 
-      mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
-      meanspectraP[f] <- mbs$meanamp
-      meanspectraPCI[1,f] <- mbs$lowerCI
-      meanspectraPCI[2,f] <- mbs$upperCI
-    }
-  }
-
-  meanwavesP <- NULL
-  meanwavesPCI <- array(0,dim=c(2,dim(tempwavesP)[2]))
-
-  nsubjs <- dim(tempwavesP)[1]
-  for (t in 1:dim(tempwavesP)[2]){
-    temp <- tempwavesP[,t]
-    i <- which(abs(temp-mean(temp))<(SDthresh*sd(temp)))
-    meanwavesP[t] <- mean(temp[i])
-    bspop <- NULL
-    for (s in 1:nbootstraps){bspop[s] <- mean(sample(temp[i],length(i),replace=TRUE))}
-    meanwavesPCI[,t] <- quantile(bspop,c(0.16,0.84),na.rm=TRUE)
-  }
-
-  save(file=paste0(datadir,'AveragedataLM.RData'),list=c('meanwavesP','meanwavesPCI','cleanmeansP','cleanmeansPCI','cleanmasksP','cleanmasksPCI','cleanmeansP2','cleanmeansP2CI','cleanmasksP2','cleanmasksP2CI','meanspectraP','meanspectraPCI','tempmeansP','tempmeansP2','tempmasksP','tempmasksP2'))
-
-  }
-```
-
-```{r L-M plot, include=FALSE, results='hide'}
-
-# generate plot showing the group pupillometry data for the L-M experiment
-if (!file.exists(paste0(datadir,'AveragedataLM.RData'))){
-           # download it from OSF
-           if (!exists('osffilesP')){
-           osfnode <- '9ebtd'
-           osfproject <- osf_retrieve_node(osfnode)
-          osffilesP <- osf_ls_files(osfproject,n_max=300)}
-          fid <- which(osffilesP$name=='AveragedataLM.RData')
-          osf_download(osffilesP[fid,],datadir,progress=TRUE)
-         }
-
-load(file=paste0(datadir,'AveragedataLM.RData'))
-
-if (processdata > 0){
-
-allPLMratios <- abs(cleanmeansP[2,])/abs(cleanmeansP[1,])
-allPLM2ratios <- abs(cleanmeansP2[2,])/abs(cleanmeansP2[1,])
-
-# plot figure  
-plotlims <- c(15,40,0,4)  
-ticklocsx <- contrastsdB
-ticklabelsx <-c(6,12,24,48,96) 
-ticklocsy <- seq(0,4,0.5)    # locations of tick marks on y axis
-ticklabelsy <- ticklocsy
-
-postscript("SumLM.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
-
-par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx)     
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
-title(xlab="Target contrast (% of max)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  
-title(ylab="Bin:Mon ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-
-lines(contrastsdB,allPLMratios, col=colpal[1], lwd=3, cex=0.5)
-lines(contrastsdB,allPLM2ratios, col=colpal[2], lwd=3, cex=0.5)
-points(contrastsdB,allPLMratios, pch = 21, col='black', bg=colpal[1], cex=1.6, lwd=3)
-points(contrastsdB,allPLM2ratios, pch = 22, col='black', bg=colpal[2], cex=1.6, lwd=3)
-
-legend(contrastsdB[4],4,c('L-M 1F','L-M 2F'), pch=21:24, pt.bg=colpal[1:2],box.lwd=2,pt.cex=1.6,pt.lwd=3)
-text(17,3.8,'(c)',adj=0.5,cex=2.5)
-
-dev.off()
-
-plotlims <- c(15,40,0,0.02)
-plotlims2 <- c(15,40,0,0.015) 
-ticklocsx <- contrastsdB    # locations of tick marks on x axis
-ticklocsy <- seq(0,0.02,0.005)
-ticklocsy2 <- seq(0,0.015,0.005)    # locations of tick marks on y axis
-ticklabelsx <-c(6,12,24,48,96)        # set labels for x ticks
-ticklabelsy <- ticklocsy
-ticklabelsy2 <- ticklocsy2     # set labels for y ticks
-
-postscript("CRF1p.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
-
-par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
-title(xlab="Target contrast (% of max)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
-title(ylab="Amplitude at 0.5Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
-
-for (cond in 1:3){
-  lines(contrastsdB,abs(cleanmeansP[cond,]), col=colpal[cond], lwd=3, cex=0.5)
-  arrows(contrastsdB,abs(cleanmeansP[cond,]),contrastsdB,cleanmeansPCI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
-  arrows(contrastsdB,abs(cleanmeansP[cond,]),contrastsdB,cleanmeansPCI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
-  points(contrastsdB,abs(cleanmeansP[cond,]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
-}  
-legend(22,0.02,c('Monocular','Binocular','Dichoptic'),pch=21:23,pt.bg=colpal[1:3],pt.lwd=3,pt.cex=1.6,box.lwd=2)
-text(17,0.019,'(d)',adj=0.5,cex=2.5)
-
-dev.off()
-
-postscript("CRF2p.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
-
-par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
-title(xlab="Target contrast (% of max)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
-title(ylab="Amplitude at 0.5Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
-
-condlist <- c(1,5,6)
-pointlist <- c(21,24,25)
-for (cond in 1:3){
-  lines(contrastsdB,abs(cleanmeansP[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)  
-  arrows(contrastsdB,abs(cleanmeansP[condlist[cond],]),contrastsdB,cleanmeansPCI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
-  arrows(contrastsdB,abs(cleanmeansP[condlist[cond],]),contrastsdB,cleanmeansPCI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)  
-  points(contrastsdB,abs(cleanmeansP[condlist[cond],]), pch = pointlist[cond], col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
-}  
-legend(22,0.02,c('Monocular','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[condlist],pt.lwd=3,pt.cex=1.6,box.lwd=2)
-text(17,0.019,'(e)',adj=0.5,cex=2.5)
-
-dev.off()
-
-postscript("CRF3p.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
-
-par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
-title(xlab="Target contrast (% of max)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
-title(ylab="Amplitude at 0.4Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
-
-for (cond in 4:6){
-  lines(contrastsdB,abs(cleanmasksP[cond,]), col=colpal[cond], lwd=3, cex=0.5)   
-  arrows(contrastsdB,abs(cleanmasksP[cond,]),contrastsdB,cleanmasksPCI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
-  arrows(contrastsdB,abs(cleanmasksP[cond,]),contrastsdB,cleanmasksPCI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)    
-  points(contrastsdB,abs(cleanmasksP[cond,]), pch = pointlist[cond-3], col='black', bg=colpal[cond], cex=1.6, lwd=3) 
-}
-legend(22,0.02,c('Monocular 0.4Hz','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[4:6],pt.lwd=3,pt.cex=1.6,box.lwd=2)
-text(17,0.019,'(f)',adj=0.5,cex=2.5)
-
-dev.off()
-
-postscript("CRF1p2.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
-
-par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims2[3:4])   # create an empty axis of the correct dimensions
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy2, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
-mtext(text = ticklabelsy2, side = 2, at=ticklocsy2, line=0.2, las=1) 
-title(xlab="Target contrast (% of max)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
-title(ylab="Amplitude at 1Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
-
-for (cond in 1:3){
-  lines(contrastsdB,abs(cleanmeansP2[cond,]), col=colpal[cond], lwd=3, cex=0.5)
-  arrows(contrastsdB,abs(cleanmeansP2[cond,]),contrastsdB,cleanmeansP2CI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
-  arrows(contrastsdB,abs(cleanmeansP2[cond,]),contrastsdB,cleanmeansP2CI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
-  points(contrastsdB,abs(cleanmeansP2[cond,]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
-}  
-legend(22,0.015,c('Monocular','Binocular','Dichoptic'),pch=21:23,pt.bg=colpal[1:3],pt.lwd=3,pt.cex=1.6,box.lwd=2)
-text(17,0.014,'(g)',adj=0.5,cex=2.5)
-
-dev.off()
-
-postscript("CRF2p2.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
-
-par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims2[3:4])   # create an empty axis of the correct dimensions
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy2, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
-mtext(text = ticklabelsy2, side = 2, at=ticklocsy2, line=0.2, las=1)
-title(xlab="Target contrast (% of max)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
-title(ylab="Amplitude at 1Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
-
-condlist <- c(1,5,6)
-pointlist <- c(21,24,25)
-for (cond in 1:3){
-  lines(contrastsdB,abs(cleanmeansP2[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)  
-  arrows(contrastsdB,abs(cleanmeansP2[condlist[cond],]),contrastsdB,cleanmeansP2CI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
-  arrows(contrastsdB,abs(cleanmeansP2[condlist[cond],]),contrastsdB,cleanmeansP2CI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)  
-  points(contrastsdB,abs(cleanmeansP2[condlist[cond],]), pch = pointlist[cond], col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
-}  
-legend(22,0.015,c('Monocular','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[condlist],pt.lwd=3,pt.cex=1.6,box.lwd=2)
-text(17,0.014,'(h)',adj=0.5,cex=2.5)
-
-dev.off()
-
-postscript("CRF3p2.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
-
-par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims2[3:4])   # create an empty axis of the correct dimensions
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy2, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
-mtext(text = ticklabelsy2, side = 2, at=ticklocsy2, line=0.2, las=1)
-title(xlab="Target contrast (% of max)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
-title(ylab="Amplitude at 0.8Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
-
-for (cond in 4:6){
-  lines(contrastsdB,abs(cleanmasksP2[cond,]), col=colpal[cond], lwd=3, cex=0.5)   
-  arrows(contrastsdB,abs(cleanmasksP2[cond,]),contrastsdB,cleanmasksP2CI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
-  arrows(contrastsdB,abs(cleanmasksP2[cond,]),contrastsdB,cleanmasksP2CI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)    
-  points(contrastsdB,abs(cleanmasksP2[cond,]), pch = pointlist[cond-3], col='black', bg=colpal[cond], cex=1.6, lwd=3) 
-}
-legend(22,0.015,c('Monocular 0.4Hz','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[4:6],pt.lwd=3,pt.cex=1.6,box.lwd=2)
-text(17,0.014,'(i)',adj=0.5,cex=2.5)
-
-dev.off()
-
-postscript("SpecP.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 8)
-
-frequencies <- (0:299)/10
-
-plotlims <- c(0,2,0,0.015) 
-ticklocsx <- seq(0,2,0.25)    # locations of tick marks on x axis
-ticklocsy <- seq(0,0.015,0.005)    # locations of tick marks on y axis
-ticklabelsx <-ticklocsx        # set labels for x ticks
-ticklabelsy <- ticklocsy    # set labels for y ticks
-
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
-title(xlab="Frequency (Hz)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  
-title(ylab="Amplitude (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
-
-polygon(frequencies[c(3:21,21:3)],c(meanspectraPCI[1,3:21],meanspectraPCI[2,21:3]),col=colpal[2],border=NA)
-
-lines(frequencies[3:21],abs(meanspectraP[3:21]), col=colpal[2], lwd=3, cex=0.5)
-
-text(0.1,0.014,'(a)',adj=0.5,cex=2.5)
-
-dev.off()
-
-postscript("timecourseP.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 8)
-
-times <- seq((1/120)-1,13,1/120)
-sinewave <- sin(0.5*times * 2*pi)
-sinewave[1:120] <- 0
-sinewave[1560:1680] <- 0
-
-plotlims <- c(-1,13,-0.5,0.5)
-ticklocsx <- seq(-1,13,1)    # locations of tick marks on x axis
-ticklocsy <- seq(-0.5,0.5,0.5)    # locations of tick marks on y axis
-ticklabelsx <- ticklocsx        # set labels for x ticks
-ticklabelsy <- ticklocsy    # set labels for y ticks
-
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
-title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)
-title(ylab="Amplitude (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
-
-filt <- butter(3,0.083)
-filtwaveP <- signal::filter(filt, meanwavesP)
-filtU <- signal::filter(filt,meanwavesPCI[1,])
-filtL <- signal::filter(filt,meanwavesPCI[2,])
-polygon(times[c(1:length(times),length(times):1)],c(filtL,filtU[length(filtU):1]),col=colpal[2],border=NA)
-lines(times, filtwaveP, col=colpal[2], lwd=1.5)
-lines(times, (sinewave/10)-0.4, col='black', lwd=3)
-
-text(-0.7,0.4,'(b)',adj=0.5,cex=2.5)
-
-dev.off()
-
-PostScriptTrace('CRF1p.ps')
-p1 <- readPicture('CRF1p.ps.xml')
-PostScriptTrace('CRF2p.ps')
-p2 <- readPicture('CRF2p.ps.xml')
-PostScriptTrace('CRF3p.ps')
-p3 <- readPicture('CRF3p.ps.xml')
-PostScriptTrace('CRF1p2.ps')
-p4 <- readPicture('CRF1p2.ps.xml')
-PostScriptTrace('CRF2p2.ps')
-p5 <- readPicture('CRF2p2.ps.xml')
-PostScriptTrace('CRF3p2.ps')
-p6 <- readPicture('CRF3p2.ps.xml')
-PostScriptTrace('SpecP.ps')
-p7 <- readPicture('SpecP.ps.xml')
-PostScriptTrace('timecourseP.ps')
-p8 <- readPicture('timecourseP.ps.xml')
-PostScriptTrace('SumLM.ps')
-p9 <- readPicture('SumLM.ps.xml')
-
-for (n in 1:length(p7@paths)){
-  temp <- class(p7@paths[n]$path)[1]
-  if (pmatch(temp,"PictureFill",nomatch=0)){
-    if (sum(col2rgb(p7@paths[n]$path@rgb))<765){p7@paths[n]$path@rgb <- addalpha(p7@paths[n]$path@rgb,alpha=0.2)}}}
-
-for (n in 1:length(p8@paths)){
-  temp <- class(p8@paths[n]$path)[1]
-  if (pmatch(temp,"PictureFill",nomatch=0)){
-    if (sum(col2rgb(p8@paths[n]$path@rgb))<765){p8@paths[n]$path@rgb <- addalpha(p8@paths[n]$path@rgb,alpha=0.2)}}}
-
-pdf(paste0(figdir,"pupildataLM.pdf"), bg="transparent", height = 20, width = 15)
-
-par(mar=c(0.1,0.1,0.1,0.1))
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(0,1), ylim=c(0,1))
-
-grid.picture(p1,x=0.17,y=0.4,width=0.32,height=1)
-grid.picture(p2,x=0.5,y=0.4,width=0.32,height=1)
-grid.picture(p3,x=0.83,y=0.4,width=0.32,height=1)
-grid.picture(p4,x=0.17,y=0.15,width=0.32,height=1)
-grid.picture(p5,x=0.5,y=0.15,width=0.32,height=1)
-grid.picture(p6,x=0.83,y=0.15,width=0.32,height=1)
-grid.picture(p7,x=0.25,y=0.83,width=0.5,height=1)
-grid.picture(p8,x=0.25,y=0.63,width=0.5,height=1)
-grid.picture(p9,x=0.75,y=0.71,width=0.5,height=1)
-
-text(0.5,0.98,'L-M',cex=4)
-
-dev.off()
-
-file.remove(c('CRF1p.ps','CRF2p.ps','CRF3p.ps','CRF1p2.ps','CRF2p2.ps','CRF3p2.ps','SpecP.ps','timecourseP.ps','SumLM.ps'))
-file.remove(c('CRF1p.ps.xml','CRF2p.ps.xml','CRF3p.ps.xml','CRF1p2.ps.xml','CRF2p2.ps.xml','CRF3p2.ps.xml','SpecP.ps.xml','timecourseP.ps.xml','SumLM.ps.xml'))
-
-  }
-```
-
-```{r L-M statistics, include=FALSE, results='hide'}
-
-# do statistics on the L-M data
-alldata <- NULL
-groupID <- NULL
-allP <- NULL
-counter <- 0
-for (cont in 1:dim(tempmeansP)[3]){
-  for (p in 1:dim(tempmeansP)[1]){
-    counter <- counter + 1
-    alldata[counter] <- tempmeansP[p,3,cont]
-    groupID[counter] <- cont
-    allP[counter] <- p
-  }
-}
-dichA2c <- anovacirc.test(alldata,group=groupID,participant=allP)
-
-alldata <- NULL
-allgroupA <- NULL
-allgroupB <- NULL
-allP <- NULL
-counter <- 0
-for (p in 1:12){
-  for (lev in 1:5){
-    for (cond in 1:2){
-    counter <- counter + 1
-    alldata[counter] <- tempmeansP[p,cond,lev]
-    allgroupA[counter] <- lev
-    allgroupB[counter] <- cond
-    allP[counter] <- p
-    }
-  }
-}
-monbinPstats <- anovacirc2way(alldata,allgroupA,allgroupB,allP)
-
-alldata <- NULL
-allgroupA <- NULL
-allgroupB <- NULL
-allP <- NULL
-counter <- 0
-for (p in 1:12){
-  for (lev in 1:5){
-    counter <- counter + 1
-    alldata[counter] <- tempmeansP[p,1,lev]
-    allgroupA[counter] <- lev
-    allgroupB[counter] <- 1
-    allP[counter] <- p
-
-    counter <- counter + 1
-    alldata[counter] <- tempmeansP[p,3,lev]
-    allgroupA[counter] <- lev
-    allgroupB[counter] <- 2
-    allP[counter] <- p
-  }
-}
-
-mondichPstats <- anovacirc2way(alldata,allgroupA,allgroupB,allP)
-
-alldata <- NULL
-allgroupA <- NULL
-allgroupB <- NULL
-allP <- NULL
-counter <- 0
-for (p in 1:12){
-  for (lev in 1:5){
-    counter <- counter + 1
-    alldata[counter] <- tempmeansP[p,1,lev]
-    allgroupA[counter] <- lev
-    allgroupB[counter] <- 1
-    allP[counter] <- p
-
-    counter <- counter + 1
-    alldata[counter] <- tempmeansP[p,5,lev]
-    allgroupA[counter] <- lev
-    allgroupB[counter] <- 2
-    allP[counter] <- p
-  }
-}
-
-monbinPstatsX <- anovacirc2way(alldata,allgroupA,allgroupB,allP)
-
-alldata <- NULL
-allgroupA <- NULL
-allgroupB <- NULL
-allP <- NULL
-counter <- 0
-for (p in 1:12){
-  for (lev in 1:5){
-    counter <- counter + 1
-    alldata[counter] <- tempmeansP[p,1,lev]
-    allgroupA[counter] <- lev
-    allgroupB[counter] <- 1
-    allP[counter] <- p
-
-    counter <- counter + 1
-    alldata[counter] <- tempmeansP[p,6,lev]
-    allgroupA[counter] <- lev
-    allgroupB[counter] <- 2
-    allP[counter] <- p
-  }
-}
-
-mondichPstatsX <- anovacirc2way(alldata,allgroupA,allgroupB,allP)
-
-```
-
-The results of the L-M pathway experiment are summarised in Figure \@ref(fig:pupildataLM).
-The average Fourier spectrum is displayed in Figure \@ref(fig:pupildataLM)a, and shows clear responses at both the first harmonic frequency (0.5 Hz) and the second harmonic frequency (1 Hz) of approximately equal amplitude.
-These results demonstrate that we can evoke measurable steady-state pupil responses at 0.5 Hz by selectively stimulating the L-M postreceptoral ‘parvocellular’ pathway whilst ignoring rods and nominally silencing S-cones and melanopsin.
-The group average waveform for binocular presentation is shown in Figure \@ref(fig:pupildataLM)b and, as observed in the previous experiments, there is a substantial pupil constriction at stimulus onset, followed by visible oscillations at the flicker frequency (0.5 Hz, see waveform at foot) and its second harmonic (i.e.
-there are two peaks in the data for every one peak in the driving waveform).
-
-```{r pupildataLM, fig.cap="Summary of pupillometry results for the L-M pathway experiment for N=12 participants.
-Panel (a) shows the average Fourier spectrum.
-Panel (b) shows a group average waveform for binocular presentation (low pass filtered at 5 Hz), with the driving signal plotted at the foot.
-Panel (c) shows the ratio of binocular to monocular response.
-The red circles show the ratios at the first harmonic (0.5 Hz) and the blue squares show the ratios at the second harmonic (1 Hz).
-Panels (d,e) show contrast response functions at 0.5 Hz for different conditions.
-Panel (f) shows contrast response functions at 0.4 Hz for three conditions.
-Panels (g-i) are in the same format but for the second harmonic responses.
-Shaded regions and error bars indicate bootstrapped standard errors.", fig.align="center", out.width = '85%', echo=FALSE}
-
-knitr::include_graphics(paste0(figdir,'pupildataLM.pdf'))
-```
-
-Figure \@ref(fig:pupildataLM)d shows contrast response functions in response to stimuli flickering only at 0.5 Hz.
-The amplitude of the binocular condition (blue squares) is substantially smaller than that of the monocular condition (red circles) across the range of target contrasts, indicating a process of binocular suppression (see Table \@ref(tab:TableStatsFig5d) for summary of statistical results).
-At the second harmonic, the pattern is reversed, with the binocular responses being larger than the monocular responses (Figure \@ref(fig:pupildataLM)g, see Table \@ref(tab:TableStatsFig5g) for summary of statistical results).
-
-In Figure \@ref(fig:pupildataLM)e, we plot responses to monocular target stimuli flickering at 0.5 Hz, when the other eye viewed stimuli flickering at 0.4 Hz (the red monocular-only data are replotted from Figure \@ref(fig:pupildataLM)d for comparison).
-For the binocular cross (purple triangles) and dichoptic cross (yellow triangles) conditions, we again observed a very strong suppression of the responses across all target contrasts (see Tables \@ref(tab:TableStatsMonBinXFig5e) and \@ref(tab:TableStatsMonDichXFig5e) for summary of statistical results).
-This was not observed at the second harmonic (Figure \@ref(fig:pupildataLM)h), where monocular and binocular responses appeared to be quite similar (see Tables \@ref(tab:TableStatsMonBinXFig5h) and \@ref(tab:TableStatsMonDichXFig5h) for summary of statistical results).
-
-Figure \@ref(fig:pupildataLM)f shows responses at 0.4 Hz, for the same conditions, as well as for a condition in which a monocular stimulus flickered at 0.4 Hz (grey circles).
-Again, strong suppression can be observed across the contrast range (see Table \@ref(tab:TableStatsMonXBinXFig5f) for summary of statistical results).
-The dichoptic cross condition shows a clear modulation with target contrast, as we can see by the decrease of the response as the contrast increases (see Table \@ref(tab:TableStatsMonXDichXFig5f) for summary of statistical results).
-The same pattern is also observed at the second harmonic (Figure \@ref(fig:pupildataLM)i), though the suppression in the binocular cross condition is less extreme at the second harmonic (see Tables \@ref(tab:TableStatsMonXBinXFig5i) and \@ref(tab:TableStatsMonXDichXFig5i) for summary of statistical results).
-
-Finally, we calculated the binocular to monocular ratio at the first and second harmonics.
-Figure \@ref(fig:pupildataLM)c shows that these ratios are generally below 1 at the first harmonic, again indicating very strong interocular suppression, and suggesting that the combination of the signals between the eyes is strongly non-linear.
-At the second harmonic, the ratios are generally between 1 and 2, suggesting that suppression between the eyes is weaker, but overall the combination remains non-linear.
-
-## Experiment 4
-
-```{r S individual, include=FALSE, results='hide'}
-
-# (download and) analyse individual participant data for the S condition
-if (processdata > 2){
-
-  for(participant in 1:24){
-
-    # only download and process data if this has not been done already for this participant
-    if (!file.exists(paste0(datadir,'P',300+participant,'summary.RData'))){
-
-      # if there is no directory for this participant's data
-      if (!file.exists(paste0(rawdir,'P',300+participant))){
-        dir.create(paste0(rawdir,'P',300+participant))
-
-       d <- dir(paste0(rawdir,'P',300+participant))
-
-       if (length(d)==0){
-
-         # if the tar file of this participant's data doesn't exist
-         if (!file.exists(paste0(rawdir,'P',300+participant,'.zip'))){
-           # download it from OSF
-           if (!exists('osffiles')){
-           osfnode <- 'k9mdq'
-           osfproject <- osf_retrieve_node(osfnode)
-          osffiles <- osf_ls_files(osfproject,n_max=300)}
-          fid <- which(osffiles$name==paste0('P',300+participant,'.zip'))
-          osf_download(osffiles[fid,],rawdir,progress=TRUE)
-         }
-
-         # then unzip the tar file
-         unzip(paste0(rawdir,'P',300+participant,'.zip'),exdir=paste0(rawdir))
-
-         # and delete the tar file to save storage space
-         file.remove(paste0(rawdir,'P',300+participant,'.zip'))
-       }
-      }
-
-      d <- dir(paste0(rawdir,'P',300+participant),full.names=TRUE)
-
-    tic()
-
-    pupiltargets <- array(0,dim=c(3,2,60))
-    pupilmasks <- pupiltargets
-    pupiltargets2 <- pupiltargets
-    pupilmasks2 <- pupiltargets
-    pupilwaveforms <- array(0,dim=c(3,2,60,120*14))
-    pupilspectra <- array(0,dim=c(3,2,60,300))
-    timeseq <- seq(1/120,10,length.out=120*10)
-    timeseq2 <- seq(1/120,14,length.out=120*14)
-    targetindex <- (0.5*10)+1
-    maskindex <- (0.4*10)+1
-    targetindex2 <- (0.5*2*10)+1
-    maskindex2 <- (2*0.4*10)+1
-
-    repcounterP <- (1:60)*0
-    afiles <- dir(path=paste0(rawdir,'P',300+participant),pattern='*annotations.csv',full.names=TRUE)
-
-    for (block in 1:length(afiles)){
-        tic()
-        adata <- read.csv(paste0(rawdir,'P',300+participant,'/',paste0('P',300+participant,'_S',block),'_annotations.csv'))
-
-        trialtimes <- NULL
-        trialtypes <- NULL
-        for (t in 1:(nrow(adata)/2)){
-          trialtimes[t] <- mean(adata$timestamp[(t*2 - 1):(t*2)])
-          trialtypes[t] <- adata$condition_code[t*2]
-        }
-
-        trialtypes[which(trialtypes>15)] <- trialtypes[which(trialtypes>15)] + 5
-        inclist <- NULL
-        for (t in 11:15){
-          i <- which(trialtypes==t)
-          inclist[t-10] <- i[2]
-        }
-        inclist <- inclist[which(!is.na(inclist))]
-        trialtypes[inclist] <- trialtypes[inclist] + 5
-
-        pdata <- read.csv(paste(rawdir,'P',300+participant,'/',paste0('P',300+participant,'_S',block),'_pupil_positions.csv',sep=''))
-        pdata2 <- pdata[,c(1,3,4,14)]
-        pdata2 <- pdata2[which(pdata2[,3]>0.2),]
-
-        for (trialno in 1:length(trialtypes)){
-          repcounterP[trialtypes[trialno]] <- repcounterP[trialtypes[trialno]] + 1
-          for (eye in 1:2){
-            eyedata <- pdata2[which(pdata2[,2]==(2-eye)),]      
-            a <- which(eyedata[,1]>trialtimes[trialno]+2)
-            b <- which(eyedata[,1]<(trialtimes[trialno]+12))
-            i <- intersect(a,b)
-            trial <- eyedata[i,]
-            trial <- trial[which(!is.na(trial[,4])),]
-            trial[,1] <- trial[,1] - trial[1,1]
-            if (nrow(trial)>3){
-              resampled <- interp1(trial[,1],trial[,4],timeseq,method='linear',extrap=TRUE)
-              fspec <- (fft(resampled)/length(resampled))
-              pupiltargets[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno]] <- fspec[targetindex]
-              pupilmasks[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno]] <- fspec[maskindex]
-              pupiltargets2[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno]] <- fspec[targetindex2]
-              pupilmasks2[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno]] <- fspec[maskindex2]
-              pupilspectra[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno],1:300] <- fspec[1:300]
-            }
-
-            a <- which(eyedata[,1]>(trialtimes[trialno]-1))
-            b <- which(eyedata[,1]<(trialtimes[trialno]+13))
-            i <- intersect(a,b)
-            trial <- eyedata[i,]
-            trial[,1] <- trial[,1] - trial[1,1]
-            if (nrow(trial)>3){
-              trial <- trial[which(!is.na(trial[,4])),]
-              resampled <- interp1(trial[,1],trial[,4],timeseq2,method='linear',extrap=TRUE)
-              pupilwaveforms[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno],] <- resampled - mean(resampled[1:120])
-            }
-          }
-        }
-    }
-
-    cleanmeansP <- matrix(0,nrow=6,ncol=5)
-    cleanmasksP <- matrix(0,nrow=6,ncol=5)
-    cleanmeansP2 <- matrix(0,nrow=6,ncol=5)
-    cleanmasksP2 <- matrix(0,nrow=6,ncol=5)
-
-    for (cond in 1:6){
-        startindex <- (10*(cond-1))
-        for (level in 1:5){
-          temp <- c(pupiltargets[,,startindex+level],pupiltargets[,,startindex+level+5])
-          cartdata <- data.frame(Re(temp),Im(temp))
-          if (sum(cartdata)!=0){
-            D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-            i <- which(D<SDthresh)
-            cleanmeansP[cond,level] <- mean(temp[i])}
-
-          temp <- c(pupiltargets2[,,startindex+level],pupiltargets2[,,startindex+level+5])
-          cartdata <- data.frame(Re(temp),Im(temp))
-          if (sum(cartdata)!=0){
-            D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-            i <- which(D<SDthresh)
-            cleanmeansP2[cond,level] <- mean(temp[i])}
-
-          temp <- c(pupilmasks[,,startindex+level],pupilmasks[,,startindex+level+5])
-          cartdata <- data.frame(Re(temp),Im(temp))
-          if (sum(cartdata)!=0){
-            D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-            i <- which(D<SDthresh)
-            cleanmasksP[cond,level] <- mean(temp[i])}
-
-          temp <- c(pupilmasks2[,,startindex+level],pupilmasks2[,,startindex+level+5])
-          cartdata <- data.frame(Re(temp),Im(temp))
-          if (sum(cartdata)!=0){
-            D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-            i <- which(D<SDthresh)
-            cleanmasksP2[cond,level] <- mean(temp[i])}
-        }
-    }
-
-    meanwavesP <- apply(pupilwaveforms[,,c(15,20),],4,mean,na.rm=TRUE)
-    meanspectraP <- apply(pupilspectra[,,c(15,20),],4,mean,na.rm=TRUE)
-    save(file=paste(datadir,'P',300+participant,'_summaryS.RData',sep=''),list=c('cleanmeansP','cleanmasksP','cleanmeansP2','cleanmasksP2','meanspectraP','meanwavesP'))
-
-    if (cleanupraw==1){file.remove(d)} # delete raw data files to save space
-  }
-
-  }}
-```
-
-```{r S group, include=FALSE, results='hide'}
-
-# load in individual participant data and average, save group data
-if (processdata > 1){
-  for (participant in 1:24){
-         # if the summary file of this participant's data doesn't exist
-         if (!file.exists(paste0(datadir,'P',300+participant,'summaryS.RData'))){
-           # download it from OSF
-           if (!exists('osffilesP')){
-           osfnode <- '9ebtd'
-           osfproject <- osf_retrieve_node(osfnode)
-          osffilesP <- osf_ls_files(osfproject,n_max=300)}
-          fid <- which(osffilesP$name==paste0('P',300+participant,'summaryS.RData'))
-          osf_download(osffilesP[fid,],datadir,progress=TRUE)
-         }
-}
-
-  d <- dir(datadir,pattern='summaryS.RData', full.names = TRUE)
-
-  tempmasksP <- array(0,dim=c(length(d),6,5))
-  tempmeansP <- tempmasksP
-  tempmeansP2 <- tempmasksP
-  tempmasksP2 <- tempmasksP
-  tempspectraP <- array(0,dim=c(length(d),300))
-  tempwavesP <- array(0,dim=c(length(d),1680))
-
-  for (s in 1:length(d)){
-
-    load(d[s])
-
-    tempmasksP[s,,] <- cleanmasksP
-    tempmeansP[s,,] <- cleanmeansP
-    tempmasksP2[s,,] <- cleanmasksP2
-    tempmeansP2[s,,] <- cleanmeansP2
-    tempspectraP[s,] <- meanspectraP
-    tempwavesP[s,] <- meanwavesP
-  }
-
-  tempspectraP <- tempspectraP[-c(2,4,13,20,26),]
-
-  cleanmeansP <- matrix(0,nrow=6,ncol=5)
-  cleanmeansPCI <- array(0,c(2,6,5))
-  cleanmasksP <- matrix(0,nrow=6,ncol=5)
-  cleanmasksPCI <- array(0,c(2,6,5))
-  cleanmeansP2 <- matrix(0,nrow=6,ncol=5)
-  cleanmeansP2CI <- array(0,c(2,6,5))
-  cleanmasksP2 <- matrix(0,nrow=6,ncol=5)
-  cleanmasksP2CI <- array(0,c(2,6,5))
-
-  for (cond in 1:6){
-    for (level in 1:5){
-
-      temp <- tempmeansP[,cond,level]
-      cartdata <- data.frame(Re(temp),Im(temp))
-      if (sum(cartdata)!=0){
-        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-        i <- which(D<SDthresh)
-        mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
-        cleanmeansP[cond,level] <- mean(temp[i])
-        cleanmeansPCI[1,cond,level] <- mbs$lowerCI
-        cleanmeansPCI[2,cond,level] <- mbs$upperCI
-      }
-
-      temp <- tempmasksP[,cond,level]
-      cartdata <- data.frame(Re(temp),Im(temp))
-      if (sum(cartdata)!=0){
-        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-        i <- which(D<SDthresh)
-        mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
-        cleanmasksP[cond,level] <- mean(temp[i])
-        cleanmasksPCI[1,cond,level] <- mbs$lowerCI
-        cleanmasksPCI[2,cond,level] <- mbs$upperCI
-      }
-
-      temp <- tempmeansP2[,cond,level]
-      cartdata <- data.frame(Re(temp),Im(temp))
-      if (sum(cartdata)!=0){
-        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-        i <- which(D<SDthresh)
-        mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
-        cleanmeansP2[cond,level] <- mean(temp[i])
-        cleanmeansP2CI[1,cond,level] <- mbs$lowerCI
-        cleanmeansP2CI[2,cond,level] <- mbs$upperCI
-      }
-
-      temp <- tempmasksP2[,cond,level]
-      cartdata <- data.frame(Re(temp),Im(temp))
-      if (sum(cartdata)!=0){
-        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-        i <- which(D<SDthresh)
-        mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
-        cleanmasksP2[cond,level] <- mean(temp[i])
-        cleanmasksP2CI[1,cond,level] <- mbs$lowerCI
-        cleanmasksP2CI[2,cond,level] <- mbs$upperCI
-      }
-    }
-  }
-
-  meanspectraP <- (1:300)*0
-  meanspectraPCI <- array(0,c(2,300))
-
-  for (f in 2:300){
-    temp <- tempspectraP[,f]
-    cartdata <- data.frame(Re(temp),Im(temp))
-    if (sum(cartdata)!=0){
-      D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-      i <- which(D<SDthresh) 
-      mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
-      meanspectraP[f] <- mbs$meanamp
-      meanspectraPCI[1,f] <- mbs$lowerCI
-      meanspectraPCI[2,f] <- mbs$upperCI
-    }
-  }
-
-  meanwavesP <- NULL
-  meanwavesPCI <- array(0,dim=c(2,dim(tempwavesP)[2]))
-
-  nsubjs <- dim(tempwavesP)[1]
-  for (t in 1:dim(tempwavesP)[2]){
-    temp <- tempwavesP[,t]
-    i <- which(abs(temp-mean(temp))<(SDthresh*sd(temp)))
-    meanwavesP[t] <- mean(temp[i])
-    bspop <- NULL
-    for (s in 1:nbootstraps){bspop[s] <- mean(sample(temp[i],length(i),replace=TRUE))}
-    meanwavesPCI[,t] <- quantile(bspop,c(0.16,0.84),na.rm=TRUE)
-  }
-
-  save(file=paste0(datadir,'AveragedataS.RData'),list=c('meanwavesP','meanwavesPCI','cleanmeansP','cleanmeansPCI','cleanmasksP','cleanmasksPCI','cleanmeansP2','cleanmeansP2CI','cleanmasksP2','cleanmasksP2CI','meanspectraP','meanspectraPCI','tempmeansP','tempmeansP2','tempmasksP','tempmasksP2'))
-
-  }
-```
-
-```{r S plot, include=FALSE, results='hide'}
-
-# generate plot showing the group pupillometry data for the S experiment
-if (!file.exists(paste0(datadir,'AveragedataS.RData'))){
-           # download it from OSF
-           if (!exists('osffilesP')){
-           osfnode <- '9ebtd'
-           osfproject <- osf_retrieve_node(osfnode)
-          osffilesP <- osf_ls_files(osfproject,n_max=300)}
-          fid <- which(osffilesP$name=='AveragedataS.RData')
-          osf_download(osffilesP[fid,],datadir,progress=TRUE)
-         }
-
-load(file=paste0(datadir,'AveragedataS.RData'))
-
-if (processdata > 0){
-
-allPSratios <- abs(cleanmeansP[2,])/abs(cleanmeansP[1,])
-allPS2ratios <- abs(cleanmeansP2[2,])/abs(cleanmeansP2[1,])
-
-# plot figure  
-plotlims <- c(15,40,0,3)  
-ticklocsx <- contrastsdB
-ticklabelsx <-c(6,12,24,48,96) 
-ticklocsy <- seq(0,3,0.5)    # locations of tick marks on y axis
-ticklabelsy <- ticklocsy
-
-postscript("SumS.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
-
-par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx)     
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
-title(xlab="Target contrast (% of max)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  
-title(ylab="Bin:Mon ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-
-lines(contrastsdB,allPSratios, col=colpal[1], lwd=3, cex=0.5)
-lines(contrastsdB,allPS2ratios, col=colpal[2], lwd=3, cex=0.5)
-points(contrastsdB,allPSratios, pch = 21, col='black', bg=colpal[1], cex=1.6, lwd=3)
-points(contrastsdB,allPS2ratios, pch = 22, col='black', bg=colpal[2], cex=1.6, lwd=3)
-
-legend(contrastsdB[4],3,c('S 1F','S 2F'), pch=21:24, pt.bg=colpal[1:2],box.lwd=2,pt.cex=1.6,pt.lwd=3)
-text(17,2.8,'(c)',adj=0.5,cex=2.5)
-
-dev.off()
-
-plotlims <- c(15,40,0,0.02)
-plotlims2 <- c(15,40,0,0.015) 
-ticklocsx <- contrastsdB    # locations of tick marks on x axis
-ticklocsy <- seq(0,0.02,0.005)
-ticklocsy2 <- seq(0,0.015,0.005)    # locations of tick marks on y axis
-ticklabelsx <-c(6,12,24,48,96)        # set labels for x ticks
-ticklabelsy <- ticklocsy
-ticklabelsy2 <- ticklocsy2     # set labels for y ticks
-
-postscript("CRF1p.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
-
-par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
-title(xlab="Target contrast (% of max)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
-title(ylab="Amplitude at 0.5Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
-
-for (cond in 1:3){
-  lines(contrastsdB,abs(cleanmeansP[cond,]), col=colpal[cond], lwd=3, cex=0.5)
-  arrows(contrastsdB,abs(cleanmeansP[cond,]),contrastsdB,cleanmeansPCI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
-  arrows(contrastsdB,abs(cleanmeansP[cond,]),contrastsdB,cleanmeansPCI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
-  points(contrastsdB,abs(cleanmeansP[cond,]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
-}  
-legend(22,0.02,c('Monocular','Binocular','Dichoptic'),pch=21:23,pt.bg=colpal[1:3],pt.lwd=3,pt.cex=1.6,box.lwd=2)
-text(17,0.019,'(d)',adj=0.5,cex=2.5)
-
-dev.off()
-
-postscript("CRF2p.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
-
-par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
-title(xlab="Target contrast (% of max)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
-title(ylab="Amplitude at 0.5Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
-
-condlist <- c(1,5,6)
-pointlist <- c(21,24,25)
-for (cond in 1:3){
-  lines(contrastsdB,abs(cleanmeansP[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)  
-  arrows(contrastsdB,abs(cleanmeansP[condlist[cond],]),contrastsdB,cleanmeansPCI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
-  arrows(contrastsdB,abs(cleanmeansP[condlist[cond],]),contrastsdB,cleanmeansPCI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)  
-  points(contrastsdB,abs(cleanmeansP[condlist[cond],]), pch = pointlist[cond], col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
-}  
-legend(22,0.02,c('Monocular','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[condlist],pt.lwd=3,pt.cex=1.6,box.lwd=2)
-text(17,0.019,'(e)',adj=0.5,cex=2.5)
-
-dev.off()
-
-postscript("CRF3p.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
-
-par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
-title(xlab="Target contrast (% of max)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
-title(ylab="Amplitude at 0.4Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
-
-for (cond in 4:6){
-  lines(contrastsdB,abs(cleanmasksP[cond,]), col=colpal[cond], lwd=3, cex=0.5)   
-  arrows(contrastsdB,abs(cleanmasksP[cond,]),contrastsdB,cleanmasksPCI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
-  arrows(contrastsdB,abs(cleanmasksP[cond,]),contrastsdB,cleanmasksPCI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)    
-  points(contrastsdB,abs(cleanmasksP[cond,]), pch = pointlist[cond-3], col='black', bg=colpal[cond], cex=1.6, lwd=3) 
-}
-legend(22,0.02,c('Monocular 0.4Hz','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[4:6],pt.lwd=3,pt.cex=1.6,box.lwd=2)
-text(17,0.019,'(f)',adj=0.5,cex=2.5)
-
-dev.off()
-
-postscript("CRF1p2.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
-
-par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
-title(xlab="Target contrast (% of max)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
-title(ylab="Amplitude at 1Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
-
-for (cond in 1:3){
-  lines(contrastsdB,abs(cleanmeansP2[cond,]), col=colpal[cond], lwd=3, cex=0.5)
-  arrows(contrastsdB,abs(cleanmeansP2[cond,]),contrastsdB,cleanmeansP2CI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
-  arrows(contrastsdB,abs(cleanmeansP2[cond,]),contrastsdB,cleanmeansP2CI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
-  points(contrastsdB,abs(cleanmeansP2[cond,]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
-}  
-legend(22,0.02,c('Monocular','Binocular','Dichoptic'),pch=21:23,pt.bg=colpal[1:3],pt.lwd=3,pt.cex=1.6,box.lwd=2)
-text(17,0.019,'(g)',adj=0.5,cex=2.5)
-
-dev.off()
-
-postscript("CRF2p2.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
-
-par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
-title(xlab="Target contrast (% of max)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
-title(ylab="Amplitude at 1Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
-
-condlist <- c(1,5,6)
-pointlist <- c(21,24,25)
-for (cond in 1:3){
-  lines(contrastsdB,abs(cleanmeansP2[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)  
-  arrows(contrastsdB,abs(cleanmeansP2[condlist[cond],]),contrastsdB,cleanmeansP2CI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
-  arrows(contrastsdB,abs(cleanmeansP2[condlist[cond],]),contrastsdB,cleanmeansP2CI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)  
-  points(contrastsdB,abs(cleanmeansP2[condlist[cond],]), pch = pointlist[cond], col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
-}  
-legend(22,0.02,c('Monocular','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[condlist],pt.lwd=3,pt.cex=1.6,box.lwd=2)
-text(17,0.019,'(h)',adj=0.5,cex=2.5)
-
-dev.off()
-
-postscript("CRF3p2.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
-
-par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
-title(xlab="Target contrast (% of max)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
-title(ylab="Amplitude at 0.8Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
-
-for (cond in 4:6){
-  lines(contrastsdB,abs(cleanmasksP2[cond,]), col=colpal[cond], lwd=3, cex=0.5)   
-  arrows(contrastsdB,abs(cleanmasksP2[cond,]),contrastsdB,cleanmasksP2CI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
-  arrows(contrastsdB,abs(cleanmasksP2[cond,]),contrastsdB,cleanmasksP2CI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)    
-  points(contrastsdB,abs(cleanmasksP2[cond,]), pch = pointlist[cond-3], col='black', bg=colpal[cond], cex=1.6, lwd=3) 
-}
-legend(22,0.02,c('Monocular 0.4Hz','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[4:6],pt.lwd=3,pt.cex=1.6,box.lwd=2)
-text(17,0.019,'(i)',adj=0.5,cex=2.5)
-
-dev.off()
-
-postscript("SpecP.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 8)
-
-frequencies <- (0:299)/10
-
-plotlims <- c(0,2,0,0.015) 
-ticklocsx <- seq(0,2,0.25)    # locations of tick marks on x axis
-ticklocsy <- seq(0,0.015,0.005)    # locations of tick marks on y axis
-ticklabelsx <-ticklocsx        # set labels for x ticks
-ticklabelsy <- ticklocsy    # set labels for y ticks
-
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
-title(xlab="Frequency (Hz)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  
-title(ylab="Amplitude (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
-
-polygon(frequencies[c(3:21,21:3)],c(meanspectraPCI[1,3:21],meanspectraPCI[2,21:3]),col=colpal[2],border=NA)
-
-lines(frequencies[3:21],abs(meanspectraP[3:21]), col=colpal[2], lwd=3, cex=0.5)
-
-text(0.1,0.014,'(a)',adj=0.5,cex=2.5)
-
-dev.off()
-
-postscript("timecourseP.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 8)
-
-times <- seq((1/120)-1,13,1/120)
-sinewave <- sin(0.5*times * 2*pi)
-sinewave[1:120] <- 0
-sinewave[1560:1680] <- 0
-
-plotlims <- c(-1,13,-0.5,0.5)
-ticklocsx <- seq(-1,13,1)    # locations of tick marks on x axis
-ticklocsy <- seq(-0.5,0.5,0.5)    # locations of tick marks on y axis
-ticklabelsx <- ticklocsx        # set labels for x ticks
-ticklabelsy <- ticklocsy    # set labels for y ticks
-
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
-title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)
-title(ylab="Amplitude (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
-
-filt <- butter(3,0.083)
-filtwaveP <- signal::filter(filt, meanwavesP)
-filtU <- signal::filter(filt,meanwavesPCI[1,])
-filtL <- signal::filter(filt,meanwavesPCI[2,])
-polygon(times[c(1:length(times),length(times):1)],c(filtL,filtU[length(filtU):1]),col=colpal[2],border=NA)
-lines(times, filtwaveP, col=colpal[2], lwd=1.5)
-lines(times, (sinewave/10)-0.4, col='black', lwd=3)
-
-text(-0.7,0.4,'(b)',adj=0.5,cex=2.5)
-
-dev.off()
-
-PostScriptTrace('CRF1p.ps')
-p1 <- readPicture('CRF1p.ps.xml')
-PostScriptTrace('CRF2p.ps')
-p2 <- readPicture('CRF2p.ps.xml')
-PostScriptTrace('CRF3p.ps')
-p3 <- readPicture('CRF3p.ps.xml')
-PostScriptTrace('CRF1p2.ps')
-p4 <- readPicture('CRF1p2.ps.xml')
-PostScriptTrace('CRF2p2.ps')
-p5 <- readPicture('CRF2p2.ps.xml')
-PostScriptTrace('CRF3p2.ps')
-p6 <- readPicture('CRF3p2.ps.xml')
-PostScriptTrace('SpecP.ps')
-p7 <- readPicture('SpecP.ps.xml')
-PostScriptTrace('timecourseP.ps')
-p8 <- readPicture('timecourseP.ps.xml')
-PostScriptTrace('SumS.ps')
-p9 <- readPicture('SumS.ps.xml')
-
-for (n in 1:length(p7@paths)){
-  temp <- class(p7@paths[n]$path)[1]
-  if (pmatch(temp,"PictureFill",nomatch=0)){
-    if (sum(col2rgb(p7@paths[n]$path@rgb))<765){p7@paths[n]$path@rgb <- addalpha(p7@paths[n]$path@rgb,alpha=0.2)}}}
-
-for (n in 1:length(p8@paths)){
-  temp <- class(p8@paths[n]$path)[1]
-  if (pmatch(temp,"PictureFill",nomatch=0)){
-    if (sum(col2rgb(p8@paths[n]$path@rgb))<765){p8@paths[n]$path@rgb <- addalpha(p8@paths[n]$path@rgb,alpha=0.2)}}}
-
-pdf(paste0(figdir,"pupildataS.pdf"), bg="transparent", height = 20, width = 15)
-
-par(mar=c(0.1,0.1,0.1,0.1))
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(0,1), ylim=c(0,1))
-
-grid.picture(p1,x=0.17,y=0.4,width=0.32,height=1)
-grid.picture(p2,x=0.5,y=0.4,width=0.32,height=1)
-grid.picture(p3,x=0.83,y=0.4,width=0.32,height=1)
-grid.picture(p4,x=0.17,y=0.15,width=0.32,height=1)
-grid.picture(p5,x=0.5,y=0.15,width=0.32,height=1)
-grid.picture(p6,x=0.83,y=0.15,width=0.32,height=1)
-grid.picture(p7,x=0.25,y=0.83,width=0.5,height=1)
-grid.picture(p8,x=0.25,y=0.63,width=0.5,height=1)
-grid.picture(p9,x=0.75,y=0.71,width=0.5,height=1)
-
-text(0.5,0.98,'S-(L+M)',cex=4)
-
-dev.off()
-
-file.remove(c('CRF1p.ps','CRF2p.ps','CRF3p.ps','CRF1p2.ps','CRF2p2.ps','CRF3p2.ps','SpecP.ps','timecourseP.ps','SumS.ps'))
-file.remove(c('CRF1p.ps.xml','CRF2p.ps.xml','CRF3p.ps.xml','CRF1p2.ps.xml','CRF2p2.ps.xml','CRF3p2.ps.xml','SpecP.ps.xml','timecourseP.ps.xml','SumS.ps.xml'))
-
-  }
-```
-
-```{r S statistics, include=FALSE, results='hide'}
-
-# do statistics on the S data
-alldata <- NULL
-groupID <- NULL
-allP <- NULL
-counter <- 0
-for (cont in 1:dim(tempmeansP)[3]){
-  for (p in 1:dim(tempmeansP)[1]){
-    counter <- counter + 1
-    alldata[counter] <- tempmeansP[p,3,cont]
-    groupID[counter] <- cont
-    allP[counter] <- p
-  }
-}
-dichA2c <- anovacirc.test(alldata,group=groupID,participant=allP)
-
-alldata <- NULL
-allgroupA <- NULL
-allgroupB <- NULL
-allP <- NULL
-counter <- 0
-for (p in 1:12){
-  for (lev in 1:5){
-    for (cond in 1:2){
-    counter <- counter + 1
-    alldata[counter] <- tempmeansP[p,cond,lev]
-    allgroupA[counter] <- lev
-    allgroupB[counter] <- cond
-    allP[counter] <- p
-    }
-  }
-}
-monbinPstats <- anovacirc2way(alldata,allgroupA,allgroupB,allP)
-
-alldata <- NULL
-allgroupA <- NULL
-allgroupB <- NULL
-allP <- NULL
-counter <- 0
-for (p in 1:12){
-  for (lev in 1:5){
-    counter <- counter + 1
-    alldata[counter] <- tempmeansP[p,1,lev]
-    allgroupA[counter] <- lev
-    allgroupB[counter] <- 1
-    allP[counter] <- p
-
-    counter <- counter + 1
-    alldata[counter] <- tempmeansP[p,3,lev]
-    allgroupA[counter] <- lev
-    allgroupB[counter] <- 2
-    allP[counter] <- p
-  }
-}
-
-mondichPstats <- anovacirc2way(alldata,allgroupA,allgroupB,allP)
-
-alldata <- NULL
-allgroupA <- NULL
-allgroupB <- NULL
-allP <- NULL
-counter <- 0
-for (p in 1:12){
-  for (lev in 1:5){
-    counter <- counter + 1
-    alldata[counter] <- tempmeansP[p,1,lev]
-    allgroupA[counter] <- lev
-    allgroupB[counter] <- 1
-    allP[counter] <- p
-
-    counter <- counter + 1
-    alldata[counter] <- tempmeansP[p,5,lev]
-    allgroupA[counter] <- lev
-    allgroupB[counter] <- 2
-    allP[counter] <- p
-  }
-}
-
-monbinPstatsX <- anovacirc2way(alldata,allgroupA,allgroupB,allP)
-
-alldata <- NULL
-allgroupA <- NULL
-allgroupB <- NULL
-allP <- NULL
-counter <- 0
-for (p in 1:12){
-  for (lev in 1:5){
-    counter <- counter + 1
-    alldata[counter] <- tempmeansP[p,1,lev]
-    allgroupA[counter] <- lev
-    allgroupB[counter] <- 1
-    allP[counter] <- p
-
-    counter <- counter + 1
-    alldata[counter] <- tempmeansP[p,6,lev]
-    allgroupA[counter] <- lev
-    allgroupB[counter] <- 2
-    allP[counter] <- p
-  }
-}
-
-mondichPstatsX <- anovacirc2way(alldata,allgroupA,allgroupB,allP)
-
-```
-
-The results of the S-(L+M) pathway experiment are summarised in Figure \@ref(fig:pupildataS).
-The average Fourier spectrum is displayed in Figure \@ref(fig:pupildataS)a, and shows a clear response at both the first harmonic frequency (0.5 Hz) and a stronger response (by around 50%) at the second harmonic frequency (1 Hz).
-These results demonstrate that we can evoke measurable steady-state pupil responses at 0.5 Hz by selectively stimulating the S-(L+M) ‘koniocelluar’ pathway whilst ignoring rods and nominally silencing L/M cones and melanopsin.
-The group average waveform for binocular presentation is shown in Figure \@ref(fig:pupildataS)b.
-There is a substantial pupil constriction at stimulus onset, followed by very visible oscillations at the flicker frequency (0.5 Hz, see waveform at foot) and its second harmonic.
-
-Figure \@ref(fig:pupildataS)d shows contrast response functions in response to stimuli flickering only at 0.5 Hz.
-For the first 3 target contrasts, response amplitudes increased monotonically with target contrast.
-At the higher contrasts, we observe a roll-over of the pupil response shown by the drop in the signals.
-This suggests that the S cones saturate at higher contrasts, and so are not able to drive larger pupil modulations.
-The amplitude of the binocular condition (blue squares) is consistently greater than that of the monocular condition (red circles) across the range of target contrasts (see Table \@ref(tab:TableStatsFig6d) for summary of statistical results).
-At the second harmonic, we observe quite different results, with the binocular and monocular conditions having the same amplitudes across the contrast range (Figure \@ref(fig:pupildataS)g), and no evidence of saturation (see Table \@ref(tab:TableStatsFig6g) for summary of statistical results).
-
-In Figure \@ref(fig:pupildataS)e, we plot responses to monocular target stimuli flickering at 0.5 Hz, when the other eye viewed stimuli flickering at 0.4 Hz (the red monocular data are replotted from Figure \@ref(fig:pupildataS)d for comparison).
-There was very little evidence of suppression in the binocular cross (purple triangles) or dichoptic cross (yellow triangles) conditions at the first harmonic (see Tables \@ref(tab:TableStatsMonBinXFig6e) and \@ref(tab:TableStatsMonDichXFig6e) for summary of statistical results).
-However at the second harmonic (Figure \@ref(fig:pupildataS)h), strong suppression was apparent at the higher target contrasts (see Tables \@ref(tab:TableStatsMonBinXFig6h) and \@ref(tab:TableStatsMonDichXFig6h) for summary of statistical results).
-
-Figure \@ref(fig:pupildataS)f shows responses at 0.4 Hz, for the same conditions, as well as for a condition in which a monocular stimulus flickered at 0.4 Hz (grey circles).
-At this frequency there was some evidence of suppression at the higher target contrasts (purple triangles below grey circles, see Table \@ref(tab:TableStatsMonXBinXFig6f) for summary of statistical results).
-At the second harmonic (Figure \@ref(fig:pupildataS)i), the binocular cross condition (purple triangles) shows a very strong suppression and the dichoptic cross condition shows a clear modulation with target contrast (yellow triangles), visible as a decrease of the response as the target contrast increases (see Tables \@ref(tab:TableStatsMonXBinXFig6i) and \@ref(tab:TableStatsMonXDichXFig6i) for summary of statistical results).
-
-Finally, we calculated the binocular to monocular ratio at the first and second harmonics.
-Figure \@ref(fig:pupildataS)c shows that these ratios are generally between 1 and 2 at the first harmonic, indicating summation between the eyes with intermediate levels of interocular suppression.
-At the second harmonic, the ratios were around 1 for the three highest target contrasts, again consistent with strong interocular suppression.
-
-```{r pupildataS, fig.cap="Summary of pupillometry results for the S-(L+M) pathway experiment for N=12 participants.
-Panel (a) shows the average Fourier spectrum.
-Panel (b) shows a group average waveform for binocular presentation (low pass filtered at 5 Hz), with the driving signal plotted at the foot.
-Panel (c) shows the ratio of binocular to monocular response.
-The red circles show the ratios at the first harmonic (0.5 Hz) and the blue squares show the ratios at the second harmonic (1 Hz).
-Panels (d,e) show contrast response functions at 0.5 Hz for different conditions.
-Panel (f) shows contrast response functions at 0.4 Hz for three conditions.
-Panels (g-i) are in the same format but for the second harmonic responses.
-Shaded regions and error bars indicate bootstrapped standard errors.", fig.align="center", out.width = '85%', echo=FALSE}
-
-knitr::include_graphics(paste0(figdir,'pupildataS.pdf'))
-```
-
-## Computational modelling
 
@@
   model {
-    Zmu ~ normal( 20 , 5 ) ;
-    Rmaxmu ~ normal( 0.1 , 0.05 ) ;
+    Zmu ~ normal( 40 , 20 ) ;
+    Rmaxmu ~ normal( 0.5 , 0.3 ) ;
     wtmu ~ normal( 1 , 0.5 ) ;
-    kmu ~ normal( 0.1 , 0.05 ) ;
-    pmu ~ normal( 2 , 0.1 ) ;
-    qmu ~ normal( 1 , 0.5 ) ;
+    kmu ~ normal( 0.2 , 0.05 ) ;
+    pmu ~ normal( 0.4 , 0.2 ) ;
+    qmu ~ normal( 2 , 0.5 ) ;
     sigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
@@
                 nu ,
-                k[s[i]] + (Rmax[s[i]]*(pow(x[i],p[s[i]]))/(Z[s[i]] + (pow(x[i],q[s[i]])))) ,
+                k[s[i]] + (Rmax[s[i]]*(pow(x[i],p[s[i]]+q[s[i]]))/(Z[s[i]] + (pow(x[i],q[s[i]])))) ,
                 w[i]*sigma ) ;
@@
                 nu ,
-                k[s[i]] + (Rmax[s[i]]*((pow(x[i],p[s[i]]))/(Z[s[i]] + (pow(x[i],q[s[i]])) + wt[s[i]]*(pow(x[i],q[s[i]]))) + (pow(x[i],p[s[i]]))/(Z[s[i]] + (pow(x[i],q[s[i]])) + wt[s[i]]*(pow(x[i],q[s[i]]))))),
+                k[s[i]] + (Rmax[s[i]]*((pow(x[i],p[s[i]]+q[s[i]]))/(Z[s[i]] + (pow(x[i],q[s[i]])) + wt[s[i]]*(pow(x[i],q[s[i]]))) + (pow(x[i],p[s[i]]+q[s[i]]))/(Z[s[i]] + (pow(x[i],q[s[i]])) + wt[s[i]]*(pow(x[i],q[s[i]]))))),
                 w[i]*sigma ) ;
@@
                 nu ,
-                k[s[i]] + (Rmax[s[i]]*((pow(x[i],p[s[i]]))/(Z[s[i]] + (pow(x[i],q[s[i]])) + wt[s[i]]*(pow(48,q[s[i]]))) + (pow(48,p[s[i]]))/(Z[s[i]] + (pow(48,q[s[i]])) + wt[s[i]]*(pow(x[i],q[s[i]]))))),
+                k[s[i]] + (Rmax[s[i]]*((pow(x[i],p[s[i]]+q[s[i]]))/(Z[s[i]] + (pow(x[i],q[s[i]])) + wt[s[i]]*(pow(48,q[s[i]]))) + (pow(48,p[s[i]]+q[s[i]]))/(Z[s[i]] + (pow(48,q[s[i]])) + wt[s[i]]*(pow(x[i],q[s[i]]))))),
                 w[i]*sigma ) ;
@@
                 nu ,
-                k[s[i]] + (Rmax[s[i]]*(pow(x[i],p[s[i]]))/(Z[s[i]] + (pow(x[i],q[s[i]])) + wt[s[i]]*(pow(x[i],q[s[i]])))) ,
+                k[s[i]] + (Rmax[s[i]]*(pow(x[i],p[s[i]]+q[s[i]]))/(Z[s[i]] + (pow(x[i],q[s[i]])) + wt[s[i]]*(pow(x[i],q[s[i]])))) ,
                 w[i]*sigma ) ;
@@
                 nu ,
-                k[s[i]] + (Rmax[s[i]]*(pow(x[i],p[s[i]]))/(Z[s[i]] + (pow(x[i],q[s[i]])) + wt[s[i]]*(pow(48,q[s[i]])))) ,
+                k[s[i]] + (Rmax[s[i]]*(pow(x[i],p[s[i]]+q[s[i]]))/(Z[s[i]] + (pow(x[i],q[s[i]])) + wt[s[i]]*(pow(48,q[s[i]])))) ,
                 w[i]*sigma ) ;       
@@
 
-```{r runstanmodelLum, include=FALSE, results='hide'}
-
-# do computational modelling for luminance experiment
+```{r runstanmodels, include=FALSE, results='hide'}
+
+# do computational modelling for all experiments
+
+# files from P301-P324 are for S-cone stimulation
+# files from P501-P524 are for melanopsin stimulation
+# files from P601-P624 are for luminance stimulation
+# files from P701-P724 are for (L-M) cone stimulation
 
@@
 
-# Luminance experiment
-d <- paste0('P',601:612,'_summaryLum.RData')
+  prefixlist <- c('P6','P7','P3','P5')
+  exptnames <- c('modeloutputLum.RData','modeloutputLM.RData','modeloutputS.RData','modeloutputMel.RData')
+  load(paste0(datadir,'included.RData'))
+
+  for (expt in 1:length(prefixlist)){
+
+    d <- dir(datadir,pattern=prefixlist[expt])
 
@@
 
-  allmasksP[s,,] <- cleanmasksP/cleanmasksP[2,5]
-  allmeansP[s,,] <- cleanmeansP/cleanmeansP[2,5]
-  allmasksP2[s,,] <- cleanmasksP2/cleanmasksP2[2,5]
-  allmeansP2[s,,] <- cleanmeansP2/cleanmeansP2[2,5]
+      allmasksP[s,,] <- cleanmasksP  #/cleanmasksP[2,5]
+      allmeansP[s,,] <- cleanmeansP  #/cleanmeansP[2,5]
+      allmasksP2[s,,] <- cleanmasksP2  #/cleanmasksP2[2,5]
+      allmeansP2[s,,] <- cleanmeansP2  #/cleanmeansP2[2,5]
 
@@
           dp <- abs(allmeansP[subj,condlist[cond],cont])
+          if (includedvalues[expt,subj,condlist[cond],cont]==1){
             if (is.na(dp)==0){
@@
       }
+    }
 
@@
     # Get MC sample of posterior:
-pupilsamplesLum <- sampling(object=CRFmodel, 
+    pupilsamples <- sampling(object=CRFmodel, 
                              data = pupildatalist, 
@@
           dp <- abs(allmeansP2[subj,condlist[cond],cont])
+          if (includedvalues2[expt,subj,condlist[cond],cont]==1){
             if (is.na(dp)==0){
@@
     # Get MC sample of posterior:
-pupilsamplesLum2 <- sampling(object=CRFmodel, 
+    pupilsamples2 <- sampling(object=CRFmodel, 
                               data = pupildatalist, 
@@
 
-save(file=paste0(datadir,'modeloutputLum.RData'),list=c('pupilsamplesLum','pupilsamplesLum2'))
+    save(file=paste0(datadir,exptnames[expt]),list=c('pupilsamples','pupilsamples2'))
+  }
 
@@
 
-```{r runstanmodelMel, include=FALSE, results='hide'}
-
-# do computational modelling for melanopsin experiment
-
-if (domodelling > 0){
-
-# Melanopsin experiment
-d <- paste0('P',501:512,'_summaryMel.RData')
-
-allmasksP <- array(0,dim=c(length(d),6,5))
-allmeansP <- allmasksP
-allmasksP2 <- array(0,dim=c(length(d),6,5))
-allmeansP2 <- allmasksP
-
-  for (s in 1:length(d)){
-
-    load(paste0(datadir,d[s]))
-
-  allmasksP[s,,] <- cleanmasksP/cleanmasksP[2,5]
-  allmeansP[s,,] <- cleanmeansP/cleanmeansP[2,5]
-  allmasksP2[s,,] <- cleanmasksP2/cleanmasksP2[2,5]
-  allmeansP2[s,,] <- cleanmeansP2/cleanmeansP2[2,5]
-
-  }
-
-  # 1st harmonic
-  condlist <- c(1,2,3,5,6)
-  contlist <- c(6,12,24,48,96)
-  y <- NULL
-  x <- NULL
-  c <- NULL
-  s <- NULL
-  w <- NULL
-  i <- 0
-  for (subj in 1:dim(allmeansP)[1]){
-    for (cond in 1:length(condlist)){
-      for (cont in 1:length(contlist)){
-        dp <- abs(allmeansP[subj,condlist[cond],cont])
-        if (is.na(dp)==0){
-          if (is.infinite(dp)==0){
-          i <- i + 1
-          x[i] <- contlist[cont]
-          y[i] <- dp
-          c[i] <- cond
-          s[i] <- subj
-          w[i] <- 1
-          }
-        }
-      }
-    }
-  }
-
-pupildatalist = list(x = x, y = y, s = s, w = w, c = c, Nsubj = max(s), Ntotal = length(y))
-
-# Get MC sample of posterior:
-pupilsamplesMel <- sampling(object=CRFmodel, 
-                    data = pupildatalist, 
-                    chains = nChains,
-                    iter = (ceiling(numSavedSteps/nChains)*thinSteps+burnInSteps), 
-                    warmup = burnInSteps, 
-                    thin = thinSteps,
-                    cores = getOption("mc.cores", 1L))
-
-  # 2nd harmonic
-  condlist <- c(1,2,3,5,6)
-  contlist <- c(6,12,24,48,96)
-  y <- NULL
-  x <- NULL
-  c <- NULL
-  s <- NULL
-  w <- NULL
-  i <- 0
-  for (subj in 1:dim(allmeansP2)[1]){
-    for (cond in 1:length(condlist)){
-      for (cont in 1:length(contlist)){
-        dp <- abs(allmeansP2[subj,condlist[cond],cont])
-        if (is.na(dp)==0){
-          if (is.infinite(dp)==0){
-          i <- i + 1
-          x[i] <- contlist[cont]
-          y[i] <- dp
-          c[i] <- cond
-          s[i] <- subj
-          w[i] <- 1
-          }
-        }
-      }
-    }
-  }
-
-pupildatalist = list(x = x, y = y, s = s, w = w, c = c, Nsubj = max(s), Ntotal = length(y))
-
-# Get MC sample of posterior:
-pupilsamplesMel2 <- sampling(object=CRFmodel, 
-                    data = pupildatalist, 
-                    chains = nChains,
-                    iter = (ceiling(numSavedSteps/nChains)*thinSteps+burnInSteps), 
-                    warmup = burnInSteps, 
-                    thin = thinSteps,
-                    cores = getOption("mc.cores", 1L))
-
-save(file=paste0(datadir,'modeloutputMel.RData'),list=c('pupilsamplesMel','pupilsamplesMel2'))
-}
-
-```
-
-```{r runstanmodelLM, include=FALSE, results='hide'}
-
-# do computational modelling for LM experiment
-
-if (domodelling > 0){
-
-# L-M experiment
-d <- paste0('P',701:712,'_summaryLM.RData')
-
-allmasksP <- array(0,dim=c(length(d),6,5))
-allmeansP <- allmasksP
-allmasksP2 <- array(0,dim=c(length(d),6,5))
-allmeansP2 <- allmasksP
-
-  for (s in 1:length(d)){
-
-    load(paste0(datadir,d[s]))
-
-  allmasksP[s,,] <- cleanmasksP/cleanmasksP[2,5]
-  allmeansP[s,,] <- cleanmeansP/cleanmeansP[2,5]
-  allmasksP2[s,,] <- cleanmasksP2/cleanmasksP2[2,5]
-  allmeansP2[s,,] <- cleanmeansP2/cleanmeansP2[2,5]
-
-  }
-
-  # 1st harmonic
-  condlist <- c(1,2,3,5,6)
-  contlist <- c(6,12,24,48,96)
-  y <- NULL
-  x <- NULL
-  c <- NULL
-  s <- NULL
-  w <- NULL
-  i <- 0
-  for (subj in 1:dim(allmeansP)[1]){
-    for (cond in 1:length(condlist)){
-      for (cont in 1:length(contlist)){
-        dp <- abs(allmeansP[subj,condlist[cond],cont])
-        if (is.na(dp)==0){
-          if (is.infinite(dp)==0){
-          i <- i + 1
-          x[i] <- contlist[cont]
-          y[i] <- dp
-          c[i] <- cond
-          s[i] <- subj
-          w[i] <- 1
-          }
-        }
-      }
-    }
-  }
-
-pupildatalist = list(x = x, y = y, s = s, w = w, c = c, Nsubj = max(s), Ntotal = length(y))
-
-# Get MC sample of posterior:
-pupilsamplesLM <- sampling(object=CRFmodel, 
-                    data = pupildatalist, 
-                    chains = nChains,
-                    iter = (ceiling(numSavedSteps/nChains)*thinSteps+burnInSteps), 
-                    warmup = burnInSteps, 
-                    thin = thinSteps,
-                    cores = getOption("mc.cores", 1L))
-
-  # 2nd harmonic
-  condlist <- c(1,2,3,5,6)
-  contlist <- c(6,12,24,48,96)
-  y <- NULL
-  x <- NULL
-  c <- NULL
-  s <- NULL
-  w <- NULL
-  i <- 0
-  for (subj in 1:dim(allmeansP2)[1]){
-    for (cond in 1:length(condlist)){
-      for (cont in 1:length(contlist)){
-        dp <- abs(allmeansP2[subj,condlist[cond],cont])
-        if (is.na(dp)==0){
-          if (is.infinite(dp)==0){
-          i <- i + 1
-          x[i] <- contlist[cont]
-          y[i] <- dp
-          c[i] <- cond
-          s[i] <- subj
-          w[i] <- 1
-          }
-        }
-      }
-    }
-  }
-
-pupildatalist = list(x = x, y = y, s = s, w = w, c = c, Nsubj = max(s), Ntotal = length(y))
-
-# Get MC sample of posterior:
-pupilsamplesLM2 <- sampling(object=CRFmodel, 
-                    data = pupildatalist, 
-                    chains = nChains,
-                    iter = (ceiling(numSavedSteps/nChains)*thinSteps+burnInSteps), 
-                    warmup = burnInSteps, 
-                    thin = thinSteps,
-                    cores = getOption("mc.cores", 1L))
-
-save(file=paste0(datadir,'modeloutputLM.RData'),list=c('pupilsamplesLM','pupilsamplesLM2'))
-
-}
-
-```
-
-```{r runstanmodelS, include=FALSE, results='hide'}
-
-# do computational modelling for S-cone experiment
-
-if (domodelling > 0){
-
-# S experiment
-d <- paste0('P',301:312,'_summaryS.RData')
-
-allmasksP <- array(0,dim=c(length(d),6,5))
-allmeansP <- allmasksP
-allmasksP2 <- array(0,dim=c(length(d),6,5))
-allmeansP2 <- allmasksP
-
-  for (s in 1:length(d)){
-
-    load(paste0(datadir,d[s]))
-
-  allmasksP[s,,] <- cleanmasksP/cleanmasksP[2,5]
-  allmeansP[s,,] <- cleanmeansP/cleanmeansP[2,5]
-  allmasksP2[s,,] <- cleanmasksP2/cleanmasksP2[2,5]
-  allmeansP2[s,,] <- cleanmeansP2/cleanmeansP2[2,5]
-
-  }
-
-  # 1st harmonic
-  condlist <- c(1,2,3,5,6)
-  contlist <- c(6,12,24,48,96)
-  y <- NULL
-  x <- NULL
-  c <- NULL
-  s <- NULL
-  w <- NULL
-  i <- 0
-  for (subj in 1:dim(allmeansP)[1]){
-    for (cond in 1:length(condlist)){
-      for (cont in 1:length(contlist)){
-        dp <- abs(allmeansP[subj,condlist[cond],cont])
-        if (is.na(dp)==0){
-          if (is.infinite(dp)==0){
-          i <- i + 1
-          x[i] <- contlist[cont]
-          y[i] <- dp
-          c[i] <- cond
-          s[i] <- subj
-          w[i] <- 1
-          }
-        }
-      }
-    }
-  }
-
-pupildatalist = list(x = x, y = y, s = s, w = w, c = c, Nsubj = max(s), Ntotal = length(y))
-
-# Get MC sample of posterior:
-pupilsamplesS <- sampling(object=CRFmodel, 
-                    data = pupildatalist, 
-                    chains = nChains,
-                    iter = (ceiling(numSavedSteps/nChains)*thinSteps+burnInSteps), 
-                    warmup = burnInSteps, 
-                    thin = thinSteps,
-                    cores = getOption("mc.cores", 1L))
-
-  # 2nd harmonic
-  condlist <- c(1,2,3,5,6)
-  contlist <- c(6,12,24,48,96)
-  y <- NULL
-  x <- NULL
-  c <- NULL
-  s <- NULL
-  w <- NULL
-  i <- 0
-  for (subj in 1:dim(allmeansP2)[1]){
-    for (cond in 1:length(condlist)){
-      for (cont in 1:length(contlist)){
-        dp <- abs(allmeansP2[subj,condlist[cond],cont])
-        if (is.na(dp)==0){
-          if (is.infinite(dp)==0){
-          i <- i + 1
-          x[i] <- contlist[cont]
-          y[i] <- dp
-          c[i] <- cond
-          s[i] <- subj
-          w[i] <- 1
-          }
-        }
-      }
-    }
-  }
-
-pupildatalist = list(x = x, y = y, s = s, w = w, c = c, Nsubj = max(s), Ntotal = length(y))
-
-# Get MC sample of posterior:
-pupilsamplesS2 <- sampling(object=CRFmodel, 
-                    data = pupildatalist, 
-                    chains = nChains,
-                    iter = (ceiling(numSavedSteps/nChains)*thinSteps+burnInSteps), 
-                    warmup = burnInSteps, 
-                    thin = thinSteps,
-                    cores = getOption("mc.cores", 1L))
-
-save(file=paste0(datadir,'modeloutputS.RData'),list=c('pupilsamplesS','pupilsamplesS2'))
-
-}
-
-```
-
-```{r makemodelfigurechap4, include=FALSE, results='hide'}
+```{r getmodelpredictions, include=FALSE, results='hide'}
 
@@
   load(paste0(datadir,'modeloutputLum.RData'))
-  load(paste0(datadir,'modeloutputMel.RData'))
-  load(paste0(datadir,'modeloutputLM.RData'))
-  load(paste0(datadir,'modeloutputS.RData'))
-
-  nchains <- dim(pupilsamplesLum)[2]
+
+  nchains <- dim(pupilsamples)[2]
   pupilweightpopLum <- NULL
@@
   for (n in 1:nchains){
-    pupilweightpopLum <- c(pupilweightpopLum,pupilsamplesLum@sim$samples[[n]]$wtmu)
-    pupilZpopLum <- c(pupilZpopLum,pupilsamplesLum@sim$samples[[n]]$Zmu)
-    pupilKpopLum <- c(pupilKpopLum,pupilsamplesLum@sim$samples[[n]]$kmu)
-    pupilPpopLum <- c(pupilPpopLum,pupilsamplesLum@sim$samples[[n]]$pmu)
-    pupilQpopLum <- c(pupilQpopLum,pupilsamplesLum@sim$samples[[n]]$qmu)
-    pupilRpopLum <- c(pupilRpopLum,pupilsamplesLum@sim$samples[[n]]$Rmaxmu)
-  }
-
-  pupilWLum <- median(pupilweightpopLum)
-  pupilZLum <- median(pupilZpopLum)
-  pupilKLum <- median(pupilKpopLum)/sqrt(12)
-  pupilPLum <- median(pupilPpopLum)
-  pupilQLum <- median(pupilQpopLum)
-  pupilRmaxLum <- median(pupilRpopLum)
-
-  nchains <- dim(pupilsamplesMel)[2]
+    pupilweightpopLum <- c(pupilweightpopLum,pupilsamples@sim$samples[[n]]$wtmu)
+    pupilZpopLum <- c(pupilZpopLum,pupilsamples@sim$samples[[n]]$Zmu)
+    pupilKpopLum <- c(pupilKpopLum,pupilsamples@sim$samples[[n]]$kmu)
+    pupilPpopLum <- c(pupilPpopLum,pupilsamples@sim$samples[[n]]$pmu)
+    pupilQpopLum <- c(pupilQpopLum,pupilsamples@sim$samples[[n]]$qmu)
+    pupilRpopLum <- c(pupilRpopLum,pupilsamples@sim$samples[[n]]$Rmaxmu)
+  }
+
+  pupilWLum <- 10^(map_estimate(log10(pupilweightpopLum)))
+  pupilZLum <- 10^(map_estimate(log10(pupilZpopLum)))
+  pupilKLum <- 10^(map_estimate(log10(pupilKpopLum)))/sqrt(24)
+  pupilPLum <- 10^(map_estimate(log10(pupilPpopLum+pupilQpopLum)))
+  pupilQLum <- 10^(map_estimate(log10(pupilQpopLum)))
+  pupilRmaxLum <- 10^(map_estimate(log10(pupilRpopLum)))
+
+  load(paste0(datadir,'modeloutputMel.RData'))
+
+  nchains <- dim(pupilsamples)[2]
   pupilweightpopMel <- NULL
@@
   for (n in 1:nchains){
-    pupilweightpopMel <- c(pupilweightpopMel,pupilsamplesMel@sim$samples[[n]]$wtmu)
-    pupilZpopMel <- c(pupilZpopMel,pupilsamplesMel@sim$samples[[n]]$Zmu)
-    pupilKpopMel <- c(pupilKpopMel,pupilsamplesMel@sim$samples[[n]]$kmu)
-    pupilPpopMel <- c(pupilPpopMel,pupilsamplesMel@sim$samples[[n]]$pmu)
-    pupilQpopMel <- c(pupilQpopMel,pupilsamplesMel@sim$samples[[n]]$qmu)
-    pupilRpopMel <- c(pupilRpopMel,pupilsamplesMel@sim$samples[[n]]$Rmaxmu)
-  }
-
-  pupilWMel <- median(pupilweightpopMel)
-  pupilZMel <- median(pupilZpopMel)
-  pupilKMel <- median(pupilKpopMel)/sqrt(12)
-  pupilPMel <- median(pupilPpopMel)
-  pupilQMel <- median(pupilQpopMel)
-  pupilRmaxMel <- median(pupilRpopMel)
-
-  nchains <- dim(pupilsamplesLM)[2]
+    pupilweightpopMel <- c(pupilweightpopMel,pupilsamples@sim$samples[[n]]$wtmu)
+    pupilZpopMel <- c(pupilZpopMel,pupilsamples@sim$samples[[n]]$Zmu)
+    pupilKpopMel <- c(pupilKpopMel,pupilsamples@sim$samples[[n]]$kmu)
+    pupilPpopMel <- c(pupilPpopMel,pupilsamples@sim$samples[[n]]$pmu)
+    pupilQpopMel <- c(pupilQpopMel,pupilsamples@sim$samples[[n]]$qmu)
+    pupilRpopMel <- c(pupilRpopMel,pupilsamples@sim$samples[[n]]$Rmaxmu)
+  }
+
+  pupilWMel <- 10^(map_estimate(log10(pupilweightpopMel)))
+  pupilZMel <- 10^(map_estimate(log10(pupilZpopMel)))
+  pupilKMel <- 10^(map_estimate(log10(pupilKpopMel)))/sqrt(24)
+  pupilPMel <- 10^(map_estimate(log10(pupilPpopMel+pupilQpopMel)))
+  pupilQMel <- 10^(map_estimate(log10(pupilQpopMel)))
+  pupilRmaxMel <- 10^(map_estimate(log10(pupilRpopMel)))
+
+   load(paste0(datadir,'modeloutputLM.RData'))
+
+  nchains <- dim(pupilsamples)[2]
   pupilweightpopLM <- NULL
@@
   for (n in 1:nchains){
-    pupilweightpopLM <- c(pupilweightpopLM,pupilsamplesLM@sim$samples[[n]]$wtmu)
-    pupilZpopLM <- c(pupilZpopLM,pupilsamplesLM@sim$samples[[n]]$Zmu)
-    pupilKpopLM <- c(pupilKpopLM,pupilsamplesLM@sim$samples[[n]]$kmu)
-    pupilPpopLM <- c(pupilPpopLM,pupilsamplesLM@sim$samples[[n]]$pmu)
-    pupilQpopLM <- c(pupilQpopLM,pupilsamplesLM@sim$samples[[n]]$qmu)
-    pupilRpopLM <- c(pupilRpopLM,pupilsamplesLM@sim$samples[[n]]$Rmaxmu)
-  }
-
-  pupilWLM <- median(pupilweightpopLM)
-  pupilZLM <- median(pupilZpopLM)
-  pupilKLM <- median(pupilKpopLM)/sqrt(12)
-  pupilPLM <- median(pupilPpopLM)
-  pupilQLM <- median(pupilQpopLM)
-  pupilRmaxLM <- median(pupilRpopLM)
-
-  nchains <- dim(pupilsamplesS)[2]
+    pupilweightpopLM <- c(pupilweightpopLM,pupilsamples@sim$samples[[n]]$wtmu)
+    pupilZpopLM <- c(pupilZpopLM,pupilsamples@sim$samples[[n]]$Zmu)
+    pupilKpopLM <- c(pupilKpopLM,pupilsamples@sim$samples[[n]]$kmu)
+    pupilPpopLM <- c(pupilPpopLM,pupilsamples@sim$samples[[n]]$pmu)
+    pupilQpopLM <- c(pupilQpopLM,pupilsamples@sim$samples[[n]]$qmu)
+    pupilRpopLM <- c(pupilRpopLM,pupilsamples@sim$samples[[n]]$Rmaxmu)
+  }
+
+  pupilWLM <- 10^(map_estimate(log10(pupilweightpopLM)))
+  pupilZLM <- 10^(map_estimate(log10(pupilZpopLM)))
+  pupilKLM <- 10^(map_estimate(log10(pupilKpopLM)))/sqrt(24)
+  pupilPLM <- 10^(map_estimate(log10(pupilPpopLM+pupilQpopLM)))
+  pupilQLM <- 10^(map_estimate(log10(pupilQpopLM)))
+  pupilRmaxLM <- 10^(map_estimate(log10(pupilRpopLM)))
+
+    load(paste0(datadir,'modeloutputS.RData'))
+
+  nchains <- dim(pupilsamples)[2]
   pupilweightpopS <- NULL
@@
   for (n in 1:nchains){
-    pupilweightpopS <- c(pupilweightpopS,pupilsamplesS@sim$samples[[n]]$wtmu)
-    pupilZpopS <- c(pupilZpopS,pupilsamplesS@sim$samples[[n]]$Zmu)
-    pupilKpopS <- c(pupilKpopS,pupilsamplesS@sim$samples[[n]]$kmu)
-    pupilPpopS <- c(pupilPpopS,pupilsamplesS@sim$samples[[n]]$pmu)
-    pupilQpopS <- c(pupilQpopS,pupilsamplesS@sim$samples[[n]]$qmu)
-    pupilRpopS <- c(pupilRpopS,pupilsamplesS@sim$samples[[n]]$Rmaxmu)
-  }
-
-  pupilWS <- median(pupilweightpopS)
-  pupilZS <- median(pupilZpopS)
-  pupilKS <- median(pupilKpopS)/sqrt(12)
-  pupilPS <- median(pupilPpopS)
-  pupilQS <- median(pupilQpopS)
-  pupilRmaxS <- median(pupilRpopS)
-
-  nchains <- dim(pupilsamplesLum2)[2]
+    pupilweightpopS <- c(pupilweightpopS,pupilsamples@sim$samples[[n]]$wtmu)
+    pupilZpopS <- c(pupilZpopS,pupilsamples@sim$samples[[n]]$Zmu)
+    pupilKpopS <- c(pupilKpopS,pupilsamples@sim$samples[[n]]$kmu)
+    pupilPpopS <- c(pupilPpopS,pupilsamples@sim$samples[[n]]$pmu)
+    pupilQpopS <- c(pupilQpopS,pupilsamples@sim$samples[[n]]$qmu)
+    pupilRpopS <- c(pupilRpopS,pupilsamples@sim$samples[[n]]$Rmaxmu)
+  }
+
+  pupilWS <- 10^(map_estimate(log10(pupilweightpopS)))
+  pupilZS <- 10^(map_estimate(log10(pupilZpopS)))
+  pupilKS <- 10^(map_estimate(log10(pupilKpopS)))/sqrt(24)
+  pupilPS <- 10^(map_estimate(log10(pupilPpopS+pupilQpopS)))
+  pupilQS <- 10^(map_estimate(log10(pupilQpopS)))
+  pupilRmaxS <- 10^(map_estimate(log10(pupilRpopS)))
+
+      load(paste0(datadir,'modeloutputLum.RData'))
+
+  nchains <- dim(pupilsamples2)[2]
   pupilweightpopLum2 <- NULL
@@
   for (n in 1:nchains){
-    pupilweightpopLum2 <- c(pupilweightpopLum2,pupilsamplesLum2@sim$samples[[n]]$wtmu)
-    pupilZpopLum2 <- c(pupilZpopLum2,pupilsamplesLum2@sim$samples[[n]]$Zmu)
-    pupilKpopLum2 <- c(pupilKpopLum2,pupilsamplesLum2@sim$samples[[n]]$kmu)
-    pupilPpopLum2 <- c(pupilPpopLum2,pupilsamplesLum2@sim$samples[[n]]$pmu)
-    pupilQpopLum2 <- c(pupilQpopLum2,pupilsamplesLum2@sim$samples[[n]]$qmu)
-    pupilRpopLum2 <- c(pupilRpopLum2,pupilsamplesLum2@sim$samples[[n]]$Rmaxmu)
-  }
-
-  pupilWLum2 <- median(pupilweightpopLum2)
-  pupilZLum2 <- median(pupilZpopLum2)
-  pupilKLum2 <- median(pupilKpopLum2)/sqrt(12)
-  pupilPLum2 <- median(pupilPpopLum2)
-  pupilQLum2 <- median(pupilQpopLum2)
-  pupilRmaxLum2 <- median(pupilRpopLum2)
-
-  nchains <- dim(pupilsamplesMel2)[2]
+    pupilweightpopLum2 <- c(pupilweightpopLum2,pupilsamples2@sim$samples[[n]]$wtmu)
+    pupilZpopLum2 <- c(pupilZpopLum2,pupilsamples2@sim$samples[[n]]$Zmu)
+    pupilKpopLum2 <- c(pupilKpopLum2,pupilsamples2@sim$samples[[n]]$kmu)
+    pupilPpopLum2 <- c(pupilPpopLum2,pupilsamples2@sim$samples[[n]]$pmu)
+    pupilQpopLum2 <- c(pupilQpopLum2,pupilsamples2@sim$samples[[n]]$qmu)
+    pupilRpopLum2 <- c(pupilRpopLum2,pupilsamples2@sim$samples[[n]]$Rmaxmu)
+  }
+
+  pupilWLum2 <- 10^(map_estimate(log10(pupilweightpopLum2)))
+  pupilZLum2 <- 10^(map_estimate(log10(pupilZpopLum2)))
+  pupilKLum2 <- 10^(map_estimate(log10(pupilKpopLum2)))/sqrt(24)
+  pupilPLum2 <- 10^(map_estimate(log10(pupilPpopLum2+pupilQpopLum2)))
+  pupilQLum2 <- 10^(map_estimate(log10(pupilQpopLum2)))
+  pupilRmaxLum2 <- 10^(map_estimate(log10(pupilRpopLum2)))
+
+    load(paste0(datadir,'modeloutputMel.RData'))
+
+  nchains <- dim(pupilsamples2)[2]
   pupilweightpopMel2 <- NULL
@@
   for (n in 1:nchains){
-    pupilweightpopMel2 <- c(pupilweightpopMel2,pupilsamplesMel2@sim$samples[[n]]$wtmu)
-    pupilZpopMel2 <- c(pupilZpopMel2,pupilsamplesMel2@sim$samples[[n]]$Zmu)
-    pupilKpopMel2 <- c(pupilKpopMel2,pupilsamplesMel2@sim$samples[[n]]$kmu)
-    pupilPpopMel2 <- c(pupilPpopMel2,pupilsamplesMel2@sim$samples[[n]]$pmu)
-    pupilQpopMel2 <- c(pupilQpopMel2,pupilsamplesMel2@sim$samples[[n]]$qmu)
-    pupilRpopMel2 <- c(pupilRpopMel2,pupilsamplesMel2@sim$samples[[n]]$Rmaxmu)
-  }
-
-  pupilWMel2 <- median(pupilweightpopMel2)
-  pupilZMel2 <- median(pupilZpopMel2)
-  pupilKMel2 <- median(pupilKpopMel2)/sqrt(12)
-  pupilPMel2 <- median(pupilPpopMel2)
-  pupilQMel2 <- median(pupilQpopMel2)
-  pupilRmaxMel2 <- median(pupilRpopMel2)
-
-  nchains <- dim(pupilsamplesLM2)[2]
+    pupilweightpopMel2 <- c(pupilweightpopMel2,pupilsamples2@sim$samples[[n]]$wtmu)
+    pupilZpopMel2 <- c(pupilZpopMel2,pupilsamples2@sim$samples[[n]]$Zmu)
+    pupilKpopMel2 <- c(pupilKpopMel2,pupilsamples2@sim$samples[[n]]$kmu)
+    pupilPpopMel2 <- c(pupilPpopMel2,pupilsamples2@sim$samples[[n]]$pmu)
+    pupilQpopMel2 <- c(pupilQpopMel2,pupilsamples2@sim$samples[[n]]$qmu)
+    pupilRpopMel2 <- c(pupilRpopMel2,pupilsamples2@sim$samples[[n]]$Rmaxmu)
+  }
+
+  pupilWMel2 <- 10^(map_estimate(log10(pupilweightpopMel2)))
+  pupilZMel2 <- 10^(map_estimate(log10(pupilZpopMel2)))
+  pupilKMel2 <- 10^(map_estimate(log10(pupilKpopMel2)))/sqrt(24)
+  pupilPMel2 <- 10^(map_estimate(log10(pupilPpopMel2+pupilQpopMel2)))
+  pupilQMel2 <- 10^(map_estimate(log10(pupilQpopMel2)))
+  pupilRmaxMel2 <- 10^(map_estimate(log10(pupilRpopMel2)))
+
+     load(paste0(datadir,'modeloutputLM.RData'))
+
+  nchains <- dim(pupilsamples2)[2]
   pupilweightpopLM2 <- NULL
@@
   for (n in 1:nchains){
-    pupilweightpopLM2 <- c(pupilweightpopLM2,pupilsamplesLM2@sim$samples[[n]]$wtmu)
-    pupilZpopLM2 <- c(pupilZpopLM2,pupilsamplesLM2@sim$samples[[n]]$Zmu)
-    pupilKpopLM2 <- c(pupilKpopLM2,pupilsamplesLM2@sim$samples[[n]]$kmu)
-    pupilPpopLM2 <- c(pupilPpopLM2,pupilsamplesLM2@sim$samples[[n]]$pmu)
-    pupilQpopLM2 <- c(pupilQpopLM2,pupilsamplesLM2@sim$samples[[n]]$qmu)
-    pupilRpopLM2 <- c(pupilRpopLM2,pupilsamplesLM2@sim$samples[[n]]$Rmaxmu)
-  }
-
-  pupilWLM2 <- median(pupilweightpopLM2)
-  pupilZLM2 <- median(pupilZpopLM2)
-  pupilKLM2 <- median(pupilKpopLM2)/sqrt(12)
-  pupilPLM2 <- median(pupilPpopLM2)
-  pupilQLM2 <- median(pupilQpopLM2)
-  pupilRmaxLM2 <- median(pupilRpopLM2)
-
-  nchains <- dim(pupilsamplesS2)[2]
+    pupilweightpopLM2 <- c(pupilweightpopLM2,pupilsamples2@sim$samples[[n]]$wtmu)
+    pupilZpopLM2 <- c(pupilZpopLM2,pupilsamples2@sim$samples[[n]]$Zmu)
+    pupilKpopLM2 <- c(pupilKpopLM2,pupilsamples2@sim$samples[[n]]$kmu)
+    pupilPpopLM2 <- c(pupilPpopLM2,pupilsamples2@sim$samples[[n]]$pmu)
+    pupilQpopLM2 <- c(pupilQpopLM2,pupilsamples2@sim$samples[[n]]$qmu)
+    pupilRpopLM2 <- c(pupilRpopLM2,pupilsamples2@sim$samples[[n]]$Rmaxmu)
+  }
+
+  pupilWLM2 <- 10^(map_estimate(log10(pupilweightpopLM2)))
+  pupilZLM2 <- 10^(map_estimate(log10(pupilZpopLM2)))
+  pupilKLM2 <- 10^(map_estimate(log10(pupilKpopLM2)))/sqrt(24)
+  pupilPLM2 <- 10^(map_estimate(log10(pupilPpopLM2+pupilQpopLM2)))
+  pupilQLM2 <- 10^(map_estimate(log10(pupilQpopLM2)))
+  pupilRmaxLM2 <- 10^(map_estimate(log10(pupilRpopLM2)))
+
+     load(paste0(datadir,'modeloutputS.RData'))
+
+  nchains <- dim(pupilsamples2)[2]
   pupilweightpopS2 <- NULL
@@
   for (n in 1:nchains){
-    pupilweightpopS2 <- c(pupilweightpopS2,pupilsamplesS2@sim$samples[[n]]$wtmu)
-    pupilZpopS2 <- c(pupilZpopS2,pupilsamplesS2@sim$samples[[n]]$Zmu)
-    pupilKpopS2 <- c(pupilKpopS2,pupilsamplesS2@sim$samples[[n]]$kmu)
-    pupilPpopS2 <- c(pupilPpopS2,pupilsamplesS2@sim$samples[[n]]$pmu)
-    pupilQpopS2 <- c(pupilQpopS2,pupilsamplesS2@sim$samples[[n]]$qmu)
-    pupilRpopS2 <- c(pupilRpopS2,pupilsamplesS2@sim$samples[[n]]$Rmaxmu)
-  }
-
-  pupilWS2 <- median(pupilweightpopS2)
-  pupilZS2 <- median(pupilZpopS2)
-  pupilKS2 <- median(pupilKpopS2)/sqrt(12)
-  pupilPS2 <- median(pupilPpopS2)
-  pupilQS2 <- median(pupilQpopS2)
-  pupilRmaxS2 <- median(pupilRpopS2)
+    pupilweightpopS2 <- c(pupilweightpopS2,pupilsamples2@sim$samples[[n]]$wtmu)
+    pupilZpopS2 <- c(pupilZpopS2,pupilsamples2@sim$samples[[n]]$Zmu)
+    pupilKpopS2 <- c(pupilKpopS2,pupilsamples2@sim$samples[[n]]$kmu)
+    pupilPpopS2 <- c(pupilPpopS2,pupilsamples2@sim$samples[[n]]$pmu)
+    pupilQpopS2 <- c(pupilQpopS2,pupilsamples2@sim$samples[[n]]$qmu)
+    pupilRpopS2 <- c(pupilRpopS2,pupilsamples2@sim$samples[[n]]$Rmaxmu)
+  }
+
+  pupilWS2 <- 10^(map_estimate(log10(pupilweightpopS2)))
+  pupilZS2 <- 10^(map_estimate(log10(pupilZpopS2)))
+  pupilKS2 <- 10^(map_estimate(log10(pupilKpopS2)))/sqrt(24)
+  pupilPS2 <- 10^(map_estimate(log10(pupilPpopS2+pupilQpopS2)))
+  pupilQS2 <- 10^(map_estimate(log10(pupilQpopS2)))
+  pupilRmaxS2 <- 10^(map_estimate(log10(pupilRpopS2)))
 
@@
 return(modresps)}
+
+params <- c(pupilRmaxLum,pupilPLum,pupilZLum,pupilWLum,pupilKLum,pupilQLum)
+modrespsLum <- getmodresps(params)
+
+params <- c(pupilRmaxMel,pupilPMel,pupilZMel,pupilWMel,pupilKMel,pupilQMel)
+modrespsMel <- getmodresps(params)
+
+params <- c(pupilRmaxLM,pupilPLM,pupilZLM,pupilWLM,pupilKLM,pupilQLM)
+modrespsLM <- getmodresps(params)
+
+params <- c(pupilRmaxS,pupilPS,pupilZS,pupilWS,pupilKS,pupilQS)
+modrespsS <- getmodresps(params)
+
+params <- c(pupilRmaxLum2,pupilPLum2,pupilZLum2,pupilWLum2,pupilKLum2,pupilQLum2)
+modrespsLum2 <- getmodresps(params)
+
+params <- c(pupilRmaxMel2,pupilPMel2,pupilZMel2,pupilWMel2,pupilKMel2,pupilQMel2)
+modrespsMel2 <- getmodresps(params)
+
+params <- c(pupilRmaxLM2,pupilPLM2,pupilZLM2,pupilWLM2,pupilKLM2,pupilQLM2)
+modrespsLM2 <- getmodresps(params)
+
+params <- c(pupilRmaxS2,pupilPS2,pupilZS2,pupilWS2,pupilKS2,pupilQS2)
+modrespsS2 <- getmodresps(params)
 
@@
 
-We fitted a computational model to the data from Experiments 1, 2, 3 and 4 using a hierarchical Bayesian approach.
-The model behaviour is displayed in Figure \@ref(fig:modfig)a-d for the first harmonic frequency and in Figure \@ref(fig:modfig)f-i for the second harmonic frequency.
-The empirical data is superimposed for comparison.
-In general, the model captures the key characteristics of the empirical data, with group-level parameter estimates provided in Tables \@ref(tab:paramtable1F) and \@ref(tab:paramtable2F) for the first and second harmonic frequencies respectively.
-We were particularly interested in comparing the weight of interocular suppression across data sets.
-We therefore plot the posterior distributions for this parameter for all four data sets (see Figure \@ref(fig:modfig)e for the distributions at the first harmonic and Figure \@ref(fig:modfig)j for the distributions at the second harmonic).
-
-```{r modfig, fig.cap="Summary of computational modelling.
-Panels (a-d) and (f-i) show empirical data from key conditions at the first and the second harmonic frequencies respectively.
-The data are replotted from earlier figures for the luminance experiment at the first (a) and the second (f) harmonic frequencies, the melanopsin experiment at the first (b) and the second (g) harmonic frequencies, the L-M pathway experiment at the first (c) and the second (h) harmonic frequencies, and the S-(L+M) pathway experiment at the first (d) and the second (i) harmonic frequencies.
-The curves show model behaviour generated using the median group-level parameter values.
-Panels (e) and (j) show the posterior probability distributions of the interocular suppression parameter for each of the four model fits at the first and the second harmonic frequencies respectively.
-In panel (e), the luminance distribution (grey) is centred about a substantially lower suppressive weight than for the other data types (note the logarithmic x-axis), while the L-M distribution (red) is centred about a higher suppressive weight than for the other data types.
-On the other hand, in panel (j), the L-M distribution is centred about a substantially lower suppressive weight than for the other data types, while it is the S-(L+M) distribution (blue) that is centred about a higher suppressive weight than for the other data types.
-The black curves show the (scaled) prior distribution for the weight parameter.", fig.align="center", echo=FALSE}
-
-knitr::include_graphics(paste0(figdir,'modelfigurechap4.pdf'))
+```{r makemethodsfig, include=FALSE, results='hide'}
+
+# create plots of spectra, cone absorption, waveforms and Fourier spectra
+if (processdata > 0){
+
+plotcontrasts <- 1 # either plot photoreceptor contrasts (1) or absolute irradiance change (0)
+
+times <- seq((1/120)-1,13,1/120)
+frequencies <- (0:299)/10
+sinewave <- sin(0.5*times * 2*pi)
+sinewave[1:120] <- 0
+sinewave[1560:1680] <- 0
+
+coneab <- read.csv('local/coneabsorptions.csv',header=FALSE)
+spectra <- read.csv('local/spectra.csv',header=FALSE)
+
+# calculate delta photoreceptor contrast
+pcontrast <- coneab
+for (n in 4:11){pcontrast[,n] <- 100*coneab[,n]/coneab[,2]}
+
+  pdf(paste0(figdir,"methodsfig.pdf"), bg="transparent", height = 13, width = 12)
+
+layout(matrix(1:20, 5, 4, byrow = TRUE))
+par(mar=c(1.5,1,0.1,0.1))
+
+  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(0,1), ylim=c(0,1))
+
+  schematic <- readTIFF('local/schematic.tiff')
+  aspratio <- 15/12  # this is the aspect ratio of the output pdf
+  imwidth <- 0.85
+  xstart <- 0
+  ystart <- 0
+  rasterImage(schematic,xstart,ystart,xstart+imwidth*aspratio,ystart+imwidth)
+
+  text(0,0.88,'(a)',pos=4,cex=2)
+
+  par(mar=c(3.5,6,1.5,2))
+
+lspec <- read.csv('local/STLAB_1_oo_irrad_spectra.csv',header=FALSE)
+rspec <- read.csv('local/STLAB_2_oo_irrad_spectra.csv',header=FALSE)
+
+lall <- matrix(0,nrow=11,ncol=401)
+lall[1,] <- unlist(lspec[1,3:403])
+rall <- matrix(0,nrow=11,ncol=401)
+rall[1,] <- unlist(rspec[1,3:403])
+for (primary in 1:10){
+  temp <- subset(lspec,V1==(primary-1) & V2=='4095')
+  lall[primary+1,] <- unlist(temp[1,3:403])
+  temp <- subset(rspec,V1==(primary-1) & V2=='4095')
+  rall[primary+1,] <- unlist(temp[1,3:403])  
+}
+
+primaryrgbvals <- c(rgb(128/255,50/255,218/255),rgb(74/255,104/255,218/255),rgb(0,0,133/255),rgb(0,0,245/255),rgb(117/255,252/255,253/255),rgb(55/255,126/255,33/255),rgb(117/255,252/255,76/255),rgb(242/255,169/255,59/255),rgb(234/255,51/255,35/255),rgb(127/255,23/255,14/255))
+
+plotlims <- c(380,800,0,0.2)
+ticklocsx <- seq(400,800,100)    # locations of tick marks on x axis
+ticklocsy <- seq(0,0.2,0.1)    # locations of tick marks on y axis
+ticklabelsx <- ticklocsx        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Wavelength (nm)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(ylab=expression(paste("Power (",mu,"W/cm"^"2","/nm)")), col.lab=rgb(0,0,0), line=2, cex.lab=1.5)
+
+# for (primary in 1:10){polygon(c(lall[1,],780),c(lall[primary+1,],0),col=addalpha(primaryrgbvals[primary],0.5),border=NA)}
+for (primary in 1:10){polygon(c(rall[1,],780),c(rall[primary+1,],0),col=addalpha(primaryrgbvals[primary],0.5),border=NA)}
+
+legend(680,0.2,1:10,col=primaryrgbvals,lwd=2,box.lwd=2,title='Primary')
+text(380,0.19,'(b)',pos=4,cex=2)
+
+plotlims <- c(380,800,0,0.2)
+ticklocsx <- seq(400,800,100)    # locations of tick marks on x axis
+ticklocsy <- seq(0,0.2,0.1)    # locations of tick marks on y axis
+ticklabelsx <- ticklocsx        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Wavelength (nm)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(ylab=expression(paste("Power (",mu,"W/cm"^"2","/nm)")), col.lab=rgb(0,0,0), line=2, cex.lab=1.5)
+
+lines(spectra[,1],spectra[,2],lwd=2,col=colpal[2])
+lines(spectra[,1],spectra[,3],lwd=2,lty=2)
+
+legend(380,0.2,c('Left eye', 'Right eye'),lty=1:2,lwd=2,col=c(colpal[2],'black'),box.lwd=2)
+
+text(720,0.19,'(c)',pos=4,cex=2)
+
+plotlims <- c(0.5,5.5,0,15)
+ticklocsx <- 1:5    # locations of tick marks on x axis
+ticklocsy <- seq(0,15,5)    # locations of tick marks on y axis
+ticklabelsx <- c('sc','mc','lc','rh','mel')        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Photoreceptor class", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(ylab=expression(paste(alpha,"-opic irradiance")), col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
+
+for (b in 1:5){
+  polygon(c(b-0.3,b,b,b-0.3),c(0,0,coneab[b,2],coneab[b,2]),col=colpal[2],border=NA)
+  polygon(c(b+0.3,b,b,b+0.3),c(0,0,coneab[b,3],coneab[b,3]),col='black',border=NA)
+}
+
+text(4.5,14,'(d)',pos=4,cex=2)
+
+plotlims <- c(380,800,-0.2,0.2)
+ticklocsx <- seq(400,800,100)    # locations of tick marks on x axis
+ticklocsy <- seq(-0.2,0.2,0.1)    # locations of tick marks on y axis
+ticklabelsx <- ticklocsx        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Wavelength (nm)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(ylab="Difference power", col.lab=rgb(0,0,0), line=2.8, cex.lab=1.5)
+title(main='Luminance',cex.main=2)
+
+polygon(c(spectra[,1],spectra[401,1]),c(spectra[,4],0),border=NA,col=stimcolours[1])
+polygon(c(spectra[,1],spectra[401,1]),c(spectra[,5],0),border=NA,col=stimcolours[2])
+
+lines(spectra[,1],spectra[,4],lwd=2)
+lines(spectra[,1],spectra[,5],lwd=2)
+
+lines(c(380,800),c(0,0),lwd=2)
+
+text(720,0.18,'(e)',pos=4,cex=2)
+
+plotlims <- c(380,800,-0.2,0.2)
+ticklocsx <- seq(400,800,100)    # locations of tick marks on x axis
+ticklocsy <- seq(-0.2,0.2,0.1)    # locations of tick marks on y axis
+ticklabelsx <- ticklocsx        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Wavelength (nm)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(ylab="Difference power", col.lab=rgb(0,0,0), line=2.8, cex.lab=1.5)
+title(main='L-M cone',cex.main=2)
+
+polygon(spectra[,1],spectra[,6],border=NA,col=stimcolours[3])
+polygon(spectra[,1],spectra[,7],border=NA,col=stimcolours[4])
+
+lines(spectra[,1],spectra[,6],lwd=2)
+lines(spectra[,1],spectra[,7],lwd=2)
+
+lines(c(380,800),c(0,0),lwd=2)
+
+text(720,0.18,'(f)',pos=4,cex=2)
+
+plotlims <- c(380,800,-0.2,0.2)
+ticklocsx <- seq(400,800,100)    # locations of tick marks on x axis
+ticklocsy <- seq(-0.2,0.2,0.1)    # locations of tick marks on y axis
+ticklabelsx <- ticklocsx        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Wavelength (nm)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(ylab="Difference power", col.lab=rgb(0,0,0), line=2.8, cex.lab=1.5)
+title(main='S-cone',cex.main=2)
+
+polygon(spectra[,1],spectra[,8],border=NA,col=stimcolours[5])
+polygon(spectra[,1],spectra[,9],border=NA,col=stimcolours[6])
+
+lines(spectra[,1],spectra[,8],lwd=2)
+lines(spectra[,1],spectra[,9],lwd=2)
+
+lines(c(380,800),c(0,0),lwd=2)
+
+text(720,0.18,'(g)',pos=4,cex=2)
+
+plotlims <- c(380,800,-0.2,0.2)
+ticklocsx <- seq(400,800,100)    # locations of tick marks on x axis
+ticklocsy <- seq(-0.2,0.2,0.1)    # locations of tick marks on y axis
+ticklabelsx <- ticklocsx        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Wavelength (nm)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(ylab="Difference power", col.lab=rgb(0,0,0), line=2.8, cex.lab=1.5)
+title(main='Melanopsin',cex.main=2)
+
+polygon(spectra[,1],spectra[,10],border=NA,col=stimcolours[7])
+polygon(spectra[,1],spectra[,11],border=NA,col=stimcolours[8])
+
+lines(spectra[,1],spectra[,10],lwd=2)
+lines(spectra[,1],spectra[,11],lwd=2)
+
+lines(c(380,800),c(0,0),lwd=2)
+
+text(720,0.18,'(h)',pos=4,cex=2)
+
+if (plotcontrasts==1){
+
+plotlims <- c(0.5,5.5,-100,100)
+ticklocsx <- 1:5    # locations of tick marks on x axis
+ticklocsy <- seq(-100,100,50)    # locations of tick marks on y axis
+ticklabelsx <- c('sc','mc','lc','rh','mel')        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Photoreceptor class", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(ylab="Contrast (%)", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)
+
+for (b in 1:5){
+  polygon(c(b-0.3,b+0.3,b+0.3,b-0.3),c(0,0,pcontrast[b,4],pcontrast[b,4]),col=stimcolours[1],border='black',lwd=2)
+  polygon(c(b-0.3,b+0.3,b+0.3,b-0.3),c(0,0,pcontrast[b,5],pcontrast[b,5]),col=stimcolours[2],border='black',lwd=2)
+}
+
+lines(c(0.5,5.5),c(0,0),lwd=2)
+
+text(4.55,80,'(i)',pos=4,cex=2)
+
+plotlims <- c(0.5,5.5,-20,20)
+ticklocsx <- 1:5    # locations of tick marks on x axis
+ticklocsy <- seq(-20,20,10)    # locations of tick marks on y axis
+ticklabelsx <- c('sc','mc','lc','rh','mel')        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Photoreceptor class", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(ylab="Contrast (%)", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)
+
+for (b in 1:5){
+  polygon(c(b-0.3,b+0.3,b+0.3,b-0.3),c(0,0,pcontrast[b,6],pcontrast[b,6]),col=stimcolours[3],border='black',lwd=2)
+  polygon(c(b-0.3,b+0.3,b+0.3,b-0.3),c(0,0,pcontrast[b,7],pcontrast[b,7]),col=stimcolours[4],border='black',lwd=2)
+}
+
+lines(c(0.5,5.5),c(0,0),lwd=2)
+
+text(4.6,18,'(j)',pos=4,cex=2)
+
+plotlims <- c(0.5,5.5,-50,50)
+ticklocsx <- 1:5    # locations of tick marks on x axis
+ticklocsy <- seq(-50,50,25)    # locations of tick marks on y axis
+ticklabelsx <- c('sc','mc','lc','rh','mel')        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Photoreceptor class", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(ylab="Contrast (%)", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)
+
+for (b in 1:5){
+  polygon(c(b-0.3,b+0.3,b+0.3,b-0.3),c(0,0,pcontrast[b,8],pcontrast[b,8]),col=stimcolours[5],border='black',lwd=2)
+  polygon(c(b-0.3,b+0.3,b+0.3,b-0.3),c(0,0,pcontrast[b,9],pcontrast[b,9]),col=stimcolours[6],border='black',lwd=2)
+}
+
+lines(c(0.5,5.5),c(0,0),lwd=2)
+
+text(4.6,45,'(k)',pos=4,cex=2)
+
+plotlims <- c(0.5,5.5,-20,20)
+ticklocsx <- 1:5    # locations of tick marks on x axis
+ticklocsy <- seq(-20,20,20)    # locations of tick marks on y axis
+ticklabelsx <- c('sc','mc','lc','rh','mel')        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Photoreceptor class", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(ylab="Contrast (%)", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)
+
+for (b in 1:5){
+  polygon(c(b-0.3,b+0.3,b+0.3,b-0.3),c(0,0,pcontrast[b,10],pcontrast[b,10]),col=stimcolours[7],border='black',lwd=2)
+  polygon(c(b-0.3,b+0.3,b+0.3,b-0.3),c(0,0,pcontrast[b,11],pcontrast[b,11]),col=stimcolours[8],border='black',lwd=2)
+}
+
+lines(c(0.5,5.5),c(0,0),lwd=2)
+
+text(0.5,18,'(l)',pos=4,cex=2)
+}
+
+if (plotcontrasts==0){
+plotlims <- c(0.5,5.5,-15,15)
+ticklocsx <- 1:5    # locations of tick marks on x axis
+ticklocsy <- seq(-15,15,5)    # locations of tick marks on y axis
+ticklabelsx <- c('sc','mc','lc','rh','mel')        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Photoreceptor class", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(ylab="Irradiance change", col.lab=rgb(0,0,0), line=2.8, cex.lab=1.5)
+
+for (b in 1:5){
+  polygon(c(b-0.3,b+0.3,b+0.3,b-0.3),c(0,0,coneab[b,4],coneab[b,4]),col=stimcolours[1],border='black',lwd=2)
+  polygon(c(b-0.3,b+0.3,b+0.3,b-0.3),c(0,0,coneab[b,5],coneab[b,5]),col=stimcolours[2],border='black',lwd=2)
+}
+
+lines(c(0.5,5.5),c(0,0),lwd=2)
+
+text(4.5,14,'(i)',pos=4,cex=2)
+
+plotlims <- c(0.5,5.5,-4,4)
+ticklocsx <- 1:5    # locations of tick marks on x axis
+ticklocsy <- seq(-4,4,2)    # locations of tick marks on y axis
+ticklabelsx <- c('sc','mc','lc','rh','mel')        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Photoreceptor class", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(ylab="Irradiance change", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
+
+for (b in 1:5){
+  polygon(c(b-0.3,b+0.3,b+0.3,b-0.3),c(0,0,coneab[b,6],coneab[b,6]),col=stimcolours[3],border='black',lwd=2)
+  polygon(c(b-0.3,b+0.3,b+0.3,b-0.3),c(0,0,coneab[b,7],coneab[b,7]),col=stimcolours[4],border='black',lwd=2)
+}
+
+lines(c(0.5,5.5),c(0,0),lwd=2)
+
+text(4.5,3.6,'(j)',pos=4,cex=2)
+
+plotlims <- c(0.5,5.5,-4,4)
+ticklocsx <- 1:5    # locations of tick marks on x axis
+ticklocsy <- seq(-4,4,2)    # locations of tick marks on y axis
+ticklabelsx <- c('sc','mc','lc','rh','mel')        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Photoreceptor class", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(ylab="Irradiance change", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
+
+for (b in 1:5){
+  polygon(c(b-0.3,b+0.3,b+0.3,b-0.3),c(0,0,coneab[b,8],coneab[b,8]),col=stimcolours[5],border='black',lwd=2)
+  polygon(c(b-0.3,b+0.3,b+0.3,b-0.3),c(0,0,coneab[b,9],coneab[b,9]),col=stimcolours[6],border='black',lwd=2)
+}
+
+lines(c(0.5,5.5),c(0,0),lwd=2)
+
+text(4.5,3.6,'(k)',pos=4,cex=2)
+
+plotlims <- c(0.5,5.5,-4,4)
+ticklocsx <- 1:5    # locations of tick marks on x axis
+ticklocsy <- seq(-4,4,2)    # locations of tick marks on y axis
+ticklabelsx <- c('sc','mc','lc','rh','mel')        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Photoreceptor class", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(ylab="Irradiance change", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
+
+for (b in 1:5){
+  polygon(c(b-0.3,b+0.3,b+0.3,b-0.3),c(0,0,coneab[b,10],coneab[b,10]),col=stimcolours[7],border='black',lwd=2)
+  polygon(c(b-0.3,b+0.3,b+0.3,b-0.3),c(0,0,coneab[b,11],coneab[b,11]),col=stimcolours[8],border='black',lwd=2)
+}
+
+lines(c(0.5,5.5),c(0,0),lwd=2)
+
+text(4.5,3.6,'(l)',pos=4,cex=2)
+}
+
+  load(file=paste0(datadir,'AveragedataLum.RData'))
+
+plotlims <- c(-1,13,-1,0.5)
+ticklocsx <- c(-1,seq(0,12,2),13)    # locations of tick marks on x axis
+ticklocsy <- seq(-1,0.5,0.5)    # locations of tick marks on y axis
+ticklabelsx <- c('',seq(0,12,2),'')        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(ylab="Diameter change (mm)", col.lab=rgb(0,0,0), line=2.8, cex.lab=1.5)
+
+filt <- butter(3,0.083)
+filtwaveP <- signal::filter(filt, meanwavesP)
+filtU <- signal::filter(filt,meanwavesPCI[1,])
+filtL <- signal::filter(filt,meanwavesPCI[2,])
+polygon(times[c(1:length(times),length(times):1)],c(filtL,filtU[length(filtU):1]),col=addalpha(colpal[2],0.3),border=NA)
+lines(times, filtwaveP, col=colpal[2], lwd=1.5)
+lines(times, (sinewave/10)-0.9, col='black', lwd=2)
+
+text(-1,0.4,'(m)',pos=4,cex=2)
+
+  load(file=paste0(datadir,'AveragedataLM.RData'))
+
+plotlims <- c(-1,13,-1,0.5)
+ticklocsx <- c(-1,seq(0,12,2),13)    # locations of tick marks on x axis
+ticklocsy <- seq(-1,0.5,0.5)    # locations of tick marks on y axis
+ticklabelsx <- c('',seq(0,12,2),'')        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(ylab="Diameter change (mm)", col.lab=rgb(0,0,0), line=2.8, cex.lab=1.5)
+
+filt <- butter(3,0.083)
+filtwaveP <- signal::filter(filt, meanwavesP)
+filtU <- signal::filter(filt,meanwavesPCI[1,])
+filtL <- signal::filter(filt,meanwavesPCI[2,])
+polygon(times[c(1:length(times),length(times):1)],c(filtL,filtU[length(filtU):1]),col=addalpha(colpal[2],0.3),border=NA)
+lines(times, filtwaveP, col=colpal[2], lwd=1.5)
+lines(times, (sinewave/10)-0.9, col='black', lwd=2)
+
+text(-1,0.4,'(n)',pos=4,cex=2)
+
+  load(file=paste0(datadir,'AveragedataS.RData'))
+
+plotlims <- c(-1,13,-1,0.5)
+ticklocsx <- c(-1,seq(0,12,2),13)    # locations of tick marks on x axis
+ticklocsy <- seq(-1,0.5,0.5)    # locations of tick marks on y axis
+ticklabelsx <- c('',seq(0,12,2),'')        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(ylab="Diameter change (mm)", col.lab=rgb(0,0,0), line=2.8, cex.lab=1.5)
+
+filt <- butter(3,0.083)
+filtwaveP <- signal::filter(filt, meanwavesP)
+filtU <- signal::filter(filt,meanwavesPCI[1,])
+filtL <- signal::filter(filt,meanwavesPCI[2,])
+polygon(times[c(1:length(times),length(times):1)],c(filtL,filtU[length(filtU):1]),col=addalpha(colpal[2],0.3),border=NA)
+lines(times, filtwaveP, col=colpal[2], lwd=1.5)
+lines(times, (sinewave/10)-0.9, col='black', lwd=2)
+
+text(-1,0.4,'(o)',pos=4,cex=2)
+
+load(file=paste0(datadir,'AveragedataMel.RData'))
+
+plotlims <- c(-1,13,-1,0.5)
+ticklocsx <- c(-1,seq(0,12,2),13)    # locations of tick marks on x axis
+ticklocsy <- seq(-1,0.5,0.5)    # locations of tick marks on y axis
+ticklabelsx <- c('',seq(0,12,2),'')        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(ylab="Diameter change (mm)", col.lab=rgb(0,0,0), line=2.8, cex.lab=1.5)
+
+filt <- butter(3,0.083)
+filtwaveP <- signal::filter(filt, meanwavesP)
+filtU <- signal::filter(filt,meanwavesPCI[1,])
+filtL <- signal::filter(filt,meanwavesPCI[2,])
+polygon(times[c(1:length(times),length(times):1)],c(filtL,filtU[length(filtU):1]),col=addalpha(colpal[2],0.3),border=NA)
+lines(times, filtwaveP, col=colpal[2], lwd=1.5)
+lines(times, (sinewave/10)-0.9, col='black', lwd=2)
+
+text(-1,0.4,'(p)',pos=4,cex=2)
+
+  load(file=paste0(datadir,'AveragedataLum.RData'))
+
+plotlims <- c(0,2,0,0.15) 
+ticklocsx <- seq(0,2,0.5)    # locations of tick marks on x axis
+ticklocsy <- seq(0,0.15,0.05)    # locations of tick marks on y axis
+ticklabelsx <-ticklocsx        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
+title(xlab="Frequency (Hz)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)  
+title(ylab="Amplitude (mm)", col.lab=rgb(0,0,0), line=3.5, cex.lab=1.5)
+
+polygon(frequencies[c(3:21,21:3)],c(meanspectraPCI[1,3:21],meanspectraPCI[2,21:3]),col=addalpha(colpal[2],0.3),border=NA)
+
+lines(frequencies[3:21],abs(meanspectraP[3:21]), col=colpal[2], lwd=1.5, cex=0.5)
+
+text(0,0.14,'(q)',pos=4,cex=2)
+
+load(file=paste0(datadir,'AveragedataLM.RData'))
+
+plotlims <- c(0,2,0,0.015) 
+ticklocsx <- seq(0,2,0.5)    # locations of tick marks on x axis
+ticklocsy <- seq(0,0.015,0.005)    # locations of tick marks on y axis
+ticklabelsx <-ticklocsx        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
+title(xlab="Frequency (Hz)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)  
+title(ylab="Amplitude (mm)", col.lab=rgb(0,0,0), line=3.5, cex.lab=1.5)
+
+polygon(frequencies[c(3:21,21:3)],c(meanspectraPCI[1,3:21],meanspectraPCI[2,21:3]),col=addalpha(colpal[2],0.3),border=NA)
+
+lines(frequencies[3:21],abs(meanspectraP[3:21]), col=colpal[2], lwd=1.5, cex=0.5)
+
+text(0,0.014,'(r)',pos=4,cex=2)
+
+  load(file=paste0(datadir,'AveragedataS.RData'))
+
+plotlims <- c(0,2,0,0.015) 
+ticklocsx <- seq(0,2,0.5)    # locations of tick marks on x axis
+ticklocsy <- seq(0,0.015,0.005)    # locations of tick marks on y axis
+ticklabelsx <-ticklocsx        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
+title(xlab="Frequency (Hz)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)  
+title(ylab="Amplitude (mm)", col.lab=rgb(0,0,0), line=3.5, cex.lab=1.5)
+
+polygon(frequencies[c(3:21,21:3)],c(meanspectraPCI[1,3:21],meanspectraPCI[2,21:3]),col=addalpha(colpal[2],0.3),border=NA)
+
+lines(frequencies[3:21],abs(meanspectraP[3:21]), col=colpal[2], lwd=1.5, cex=0.5)
+
+text(0,0.014,'(s)',pos=4,cex=2)
+
+load(file=paste0(datadir,'AveragedataMel.RData'))
+
+plotlims <- c(0,2,0,0.015) 
+ticklocsx <- seq(0,2,0.5)    # locations of tick marks on x axis
+ticklocsy <- seq(0,0.015,0.005)    # locations of tick marks on y axis
+ticklabelsx <-ticklocsx        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
+title(xlab="Frequency (Hz)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)  
+title(ylab="Amplitude (mm)", col.lab=rgb(0,0,0), line=3.5, cex.lab=1.5)
+
+polygon(frequencies[c(3:21,21:3)],c(meanspectraPCI[1,3:21],meanspectraPCI[2,21:3]),col=addalpha(colpal[2],0.3),border=NA)
+
+lines(frequencies[3:21],abs(meanspectraP[3:21]), col=colpal[2], lwd=1.5, cex=0.5)
+
+text(0,0.014,'(t)',pos=4,cex=2)
+
+  dev.off()
+
+}
 
@@
 
-At the first harmonic, the key finding is that the luminance results (grey distribution) display a much smaller weight of interocular suppression than the other data sets.
-The melanopsin and S-(L+M) results (gold and blue distributions) display a similar weight of interocular suppression.
-The L-M results (red distribution) display the greatest weight of interocular suppression of all data sets.
-There is minimal overlap between the luminance distribution and the other three distributions.
-For the luminance, the distribution is meaningfully below a weight of 1, while it is well above a weight of 1 for the L-M results.
-The distributions of melanopsin and S-(L+M) are around a weight of 1.
-These results offer an explanation of the empirical data: the weaker suppression for the luminance experiment is consistent with the weaker suppression effects and the weaker dichoptic masking, while the stronger suppression for the L-M experiment is consistent with the stronger suppression observed at the first harmonic and the stronger dichoptic masking.
-
-At the second harmonic, the key finding is that the S-(L+M) results display a greater weight of interocular suppression compared to the other data sets.
-On the other hand, the L-M results display the smallest weight of interocular suppression.
-The luminance and melanopsin results display weights of interocular suppression that are quite close to each other.
-For the L-M results, the distribution is meaningfully below a weight of 1, while it is well above a weight of 1 for the S-(L+M) results.
-The distributions of luminance and melanospin are around a weight of 1, with the former being slightly below and the latter being slightly above.
-These results offer an explanation of the empirical data: the weaker suppression for the L-M experiment is consistent with the weaker suppression effects and the weaker dichoptic masking observed at the second harmonic, while the stronger suppression for the S-(L+M) experiment is consistent with the stronger suppression observed at the second harmonic and the stronger dichoptic masking.
-
-```{r paramtable1F, echo=FALSE}
-
-condnames <- c('Luminance 1F', 'Melanopsin 1F', 'L-M 1F', 'S 1F')
-zlist <- c(pupilZLum, pupilZMel, pupilZLM, pupilZS)
-klist <- c(pupilKLum, pupilKMel, pupilKLM, pupilKS)
-wlist <- c(pupilWLum, pupilWMel, pupilWLM, pupilWS)
-plist <- c(pupilPLum, pupilPMel, pupilPLM, pupilPS)
-qlist <- c(pupilQLum, pupilQMel, pupilQLM, pupilQS)
-Rlist <- c(round(c(pupilRmaxLum, pupilRmaxMel, pupilRmaxLM, pupilRmaxS),5))
-tabledata <- data.frame(condnames,round(zlist,digits=2),round(klist,digits=2),round(wlist,digits=2),round(plist,digits=2),round(qlist,digits=2),Rlist)
-
-colnames(tabledata) <- c('Experiment','Z','k','w','p','q','Rmax')
-kable(tabledata, align='lcccccc',caption = 'Summary of median parameter values at the first harmonic frequency.')
+```{r plotCRFs, include=FALSE, results='hide'}
+
+# create plots of spectra, cone absorption, waveforms and Fourier spectra
+if (processdata > 0){
+
+  contrastsfinedB <- 2:40
+
+condlist <- c(1,2,6)
+condlist2 <- c(1,2,4)
+plotlims <- c(15,40,0,0.15)
+plotlims2 <- c(15,40,0,0.015) 
+ticklocsx <- contrastsdB    # locations of tick marks on x axis
+ticklocsy <- seq(0,0.15,0.05)
+ticklocsy2 <- seq(0,0.015,0.005)    # locations of tick marks on y axis
+ticklabelsx <-c(6,12,24,48,96)        # set labels for x ticks
+ticklabelsy <- ticklocsy
+ticklabelsy2 <- ticklocsy2     # set labels for y ticks
+
+  pdf(paste0(figdir,"CRFs.pdf"), bg="transparent", height = 6, width = 14)
+  par(mfcol=c(2,4), mar=c(3,6,2,2))
+
+load(file=paste0(datadir,'AveragedataLum.RData'))
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)    # titles for axes
+title(ylab="Amplitude at 0.5Hz (mm)", col.lab=rgb(0,0,0), line=3, cex.lab=1.5)
+title(main='Luminance',cex.main=2)
+for (cond in 1:3){
+  lines(contrastsfinedB,modrespsLum[condlist2[cond],], col=colpal[condlist[cond]], lwd=3, cex=0.5)
+  # lines(contrastsfinedB,abs(cleanmeansP[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)
+  arrows(contrastsdB,abs(cleanmeansP[condlist[cond],]),contrastsdB,cleanmeansPCI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  arrows(contrastsdB,abs(cleanmeansP[condlist[cond],]),contrastsdB,cleanmeansPCI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  points(contrastsdB,abs(cleanmeansP[condlist[cond],]), pch = 20+cond, col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
+}  
+legend(15,0.125,c('Monocular','Binocular','Dichoptic cross'),pch=21:23,pt.bg=colpal[condlist],pt.lwd=3,pt.cex=1.6,box.lwd=2,cex=1.2)
+text(17,0.14,'(a)',adj=0.5,cex=2.5)
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims2[1:2], ylim=plotlims2[3:4])   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy2, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
+mtext(text = ticklabelsy2, side = 2, at=ticklocsy2, line=0.2, las=1) 
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)    # titles for axes
+title(ylab="Amplitude at 1Hz (mm)", col.lab=rgb(0,0,0), line=3.5, cex.lab=1.5)
+for (cond in 1:3){
+  lines(contrastsfinedB,modrespsLum2[condlist2[cond],], col=colpal[condlist[cond]], lwd=3, cex=0.5)
+  # lines(contrastsdB,abs(cleanmeansP2[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)
+  arrows(contrastsdB,abs(cleanmeansP2[condlist[cond],]),contrastsdB,cleanmeansP2CI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  arrows(contrastsdB,abs(cleanmeansP2[condlist[cond],]),contrastsdB,cleanmeansP2CI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  points(contrastsdB,abs(cleanmeansP2[condlist[cond],]), pch = 20+cond, col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
+}  
+text(17,0.014,'(e)',adj=0.5,cex=2.5)
+
+load(file=paste0(datadir,'AveragedataLM.RData'))
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims2[1:2], ylim=plotlims2[3:4])   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy2, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
+mtext(text = ticklabelsy2, side = 2, at=ticklocsy2, line=0.2, las=1) 
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)    # titles for axes
+title(ylab="Amplitude at 0.5Hz (mm)", col.lab=rgb(0,0,0), line=3.5, cex.lab=1.5)
+title(main='L-M cone',cex.main=2)
+for (cond in 1:3){
+  lines(contrastsfinedB,modrespsLM[condlist2[cond],], col=colpal[condlist[cond]], lwd=3, cex=0.5)
+  # lines(contrastsdB,abs(cleanmeansP[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)
+  arrows(contrastsdB,abs(cleanmeansP[condlist[cond],]),contrastsdB,cleanmeansPCI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  arrows(contrastsdB,abs(cleanmeansP[condlist[cond],]),contrastsdB,cleanmeansPCI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  points(contrastsdB,abs(cleanmeansP[condlist[cond],]), pch = 20+cond, col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
+}  
+text(17,0.014,'(b)',adj=0.5,cex=2.5)
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims2[1:2], ylim=plotlims2[3:4])   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy2, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
+mtext(text = ticklabelsy2, side = 2, at=ticklocsy2, line=0.2, las=1) 
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)    # titles for axes
+title(ylab="Amplitude at 1Hz (mm)", col.lab=rgb(0,0,0), line=3.5, cex.lab=1.5)
+for (cond in 1:3){
+  lines(contrastsfinedB,modrespsLM2[condlist2[cond],], col=colpal[condlist[cond]], lwd=3, cex=0.5)
+  # lines(contrastsdB,abs(cleanmeansP2[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)
+  arrows(contrastsdB,abs(cleanmeansP2[condlist[cond],]),contrastsdB,cleanmeansP2CI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  arrows(contrastsdB,abs(cleanmeansP2[condlist[cond],]),contrastsdB,cleanmeansP2CI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  points(contrastsdB,abs(cleanmeansP2[condlist[cond],]), pch = 20+cond, col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
+}  
+text(17,0.014,'(f)',adj=0.5,cex=2.5)
+
+load(file=paste0(datadir,'AveragedataS.RData'))
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims2[1:2], ylim=plotlims2[3:4])   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy2, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
+mtext(text = ticklabelsy2, side = 2, at=ticklocsy2, line=0.2, las=1) 
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)    # titles for axes
+title(ylab="Amplitude at 0.5Hz (mm)", col.lab=rgb(0,0,0), line=3.5, cex.lab=1.5)
+title(main='S cone',cex.main=2)
+for (cond in 1:3){
+  lines(contrastsfinedB,modrespsS[condlist2[cond],], col=colpal[condlist[cond]], lwd=3, cex=0.5)
+  # lines(contrastsdB,abs(cleanmeansP[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)
+  arrows(contrastsdB,abs(cleanmeansP[condlist[cond],]),contrastsdB,cleanmeansPCI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  arrows(contrastsdB,abs(cleanmeansP[condlist[cond],]),contrastsdB,cleanmeansPCI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  points(contrastsdB,abs(cleanmeansP[condlist[cond],]), pch = 20+cond, col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
+}  
+text(17,0.014,'(c)',adj=0.5,cex=2.5)
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims2[1:2], ylim=plotlims2[3:4])   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy2, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
+mtext(text = ticklabelsy2, side = 2, at=ticklocsy2, line=0.2, las=1) 
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)    # titles for axes
+title(ylab="Amplitude at 1Hz (mm)", col.lab=rgb(0,0,0), line=3.5, cex.lab=1.5)
+for (cond in 1:3){
+  lines(contrastsfinedB,modrespsS2[condlist2[cond],], col=colpal[condlist[cond]], lwd=3, cex=0.5)
+  # lines(contrastsdB,abs(cleanmeansP2[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)
+  arrows(contrastsdB,abs(cleanmeansP2[condlist[cond],]),contrastsdB,cleanmeansP2CI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  arrows(contrastsdB,abs(cleanmeansP2[condlist[cond],]),contrastsdB,cleanmeansP2CI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  points(contrastsdB,abs(cleanmeansP2[condlist[cond],]), pch = 20+cond, col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
+}  
+text(17,0.014,'(g)',adj=0.5,cex=2.5)
+
+load(file=paste0(datadir,'AveragedataMel.RData'))
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims2[1:2], ylim=plotlims2[3:4])   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy2, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
+mtext(text = ticklabelsy2, side = 2, at=ticklocsy2, line=0.2, las=1) 
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)    # titles for axes
+title(ylab="Amplitude at 0.5Hz (mm)", col.lab=rgb(0,0,0), line=3.5, cex.lab=1.5)
+title(main='Melanopsin',cex.main=2)
+for (cond in 1:3){
+  lines(contrastsfinedB,modrespsMel[condlist2[cond],], col=colpal[condlist[cond]], lwd=3, cex=0.5)
+  # lines(contrastsdB,abs(cleanmeansP[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)
+  arrows(contrastsdB,abs(cleanmeansP[condlist[cond],]),contrastsdB,cleanmeansPCI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  arrows(contrastsdB,abs(cleanmeansP[condlist[cond],]),contrastsdB,cleanmeansPCI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  points(contrastsdB,abs(cleanmeansP[condlist[cond],]), pch = 20+cond, col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
+}  
+text(17,0.014,'(d)',adj=0.5,cex=2.5)
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims2[1:2], ylim=plotlims2[3:4])   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy2, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
+mtext(text = ticklabelsy2, side = 2, at=ticklocsy2, line=0.2, las=1) 
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)    # titles for axes
+title(ylab="Amplitude at 1Hz (mm)", col.lab=rgb(0,0,0), line=3.5, cex.lab=1.5)
+for (cond in 1:3){
+  lines(contrastsfinedB,modrespsMel2[condlist2[cond],], col=colpal[condlist[cond]], lwd=3, cex=0.5)
+  # lines(contrastsdB,abs(cleanmeansP2[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)
+  arrows(contrastsdB,abs(cleanmeansP2[condlist[cond],]),contrastsdB,cleanmeansP2CI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  arrows(contrastsdB,abs(cleanmeansP2[condlist[cond],]),contrastsdB,cleanmeansP2CI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  points(contrastsdB,abs(cleanmeansP2[condlist[cond],]), pch = 20+cond, col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
+}  
+text(17,0.014,'(h)',adj=0.5,cex=2.5)
+
+dev.off()
+
+}
 
@@
 
-```{r paramtable2F, echo=FALSE}
-
-condnames <- c('Luminance 2F', 'Melanopsin 2F', 'L-M 2F', 'S 2F')
-zlist <- c(pupilZLum2, pupilZMel2, pupilZLM2, pupilZS2)
-klist <- c(pupilKLum2, pupilKMel2, pupilKLM2, pupilKS2)
-wlist <- c(pupilWLum2, pupilWMel2, pupilWLM2, pupilWS2)
-plist <- c(pupilPLum2, pupilPMel2, pupilPLM2, pupilPS2)
-qlist <- c(pupilQLum2, pupilQMel2, pupilQLM2, pupilQS2)
-Rlist <- c(round(c(pupilRmaxLum2, pupilRmaxMel2, pupilRmaxLM2, pupilRmaxS2),5))
-tabledata <- data.frame(condnames,round(zlist,digits=2),round(klist,digits=2),round(wlist,digits=2),round(plist,digits=2),round(qlist,digits=2),Rlist)
-
-colnames(tabledata) <- c('Experiment','Z','k','w','p','q','Rmax')
-kable(tabledata, align='lcccccc',caption = 'Summary of median parameter values at the second harmonic frequency.')
+```{r plotsuppression, include=FALSE, results='hide'}
+
+if (processdata > 0){
+
+pdf(paste(figdir,"suppressionfig.pdf",sep=''), bg="transparent", height = 10, width = 10)
+
+par(mfrow=c(2,2))
+
+allbin <- matrix(0,nrow=8,ncol=5)
+alldich <- matrix(0,nrow=8,ncol=5)
+justbin <- matrix(0,nrow=8,ncol=5)
+justdich <- matrix(0,nrow=8,ncol=5)
+
+load(file=paste0(datadir,'AveragedataLum.RData'))
+allbin[1,] <- abs(cleanmeansP[2,])/abs(cleanmeansP[1,])
+allbin[5,] <- abs(cleanmeansP2[2,])/abs(cleanmeansP2[1,])
+alldich[1,] <- abs(cleanmeansP[1,])/abs(cleanmeansP[6,])
+alldich[5,] <- abs(cleanmeansP2[1,])/abs(cleanmeansP2[6,])
+justbin[1,] <- abs(cleanmeansP[2,])
+justbin[5,] <- abs(cleanmeansP2[2,])
+justdich[1,] <- abs(cleanmeansP[6,])
+justdich[5,] <- abs(cleanmeansP2[6,])
+
+load(file=paste0(datadir,'AveragedataLM.RData'))
+allbin[2,] <- abs(cleanmeansP[2,])/abs(cleanmeansP[1,])
+allbin[6,] <- abs(cleanmeansP2[2,])/abs(cleanmeansP2[1,])
+alldich[2,] <- abs(cleanmeansP[1,])/abs(cleanmeansP[6,])
+alldich[6,] <- abs(cleanmeansP2[1,])/abs(cleanmeansP2[6,])
+justbin[2,] <- abs(cleanmeansP[2,])
+justbin[6,] <- abs(cleanmeansP2[2,])
+justdich[2,] <- abs(cleanmeansP[6,])
+justdich[6,] <- abs(cleanmeansP2[6,])
+
+load(file=paste0(datadir,'AveragedataS.RData'))
+allbin[3,] <- abs(cleanmeansP[2,])/abs(cleanmeansP[1,])
+allbin[7,] <- abs(cleanmeansP2[2,])/abs(cleanmeansP2[1,])
+alldich[3,] <- abs(cleanmeansP[1,])/abs(cleanmeansP[6,])
+alldich[7,] <- abs(cleanmeansP2[1,])/abs(cleanmeansP2[6,])
+justbin[3,] <- abs(cleanmeansP[2,])
+justbin[7,] <- abs(cleanmeansP2[2,])
+justdich[3,] <- abs(cleanmeansP[6,])
+justdich[7,] <- abs(cleanmeansP2[6,])
+
+load(file=paste0(datadir,'AveragedataMel.RData'))
+allbin[4,] <- abs(cleanmeansP[2,])/abs(cleanmeansP[1,])
+allbin[8,] <- abs(cleanmeansP2[2,])/abs(cleanmeansP2[1,])
+alldich[4,] <- abs(cleanmeansP[1,])/abs(cleanmeansP[6,])
+alldich[8,] <- abs(cleanmeansP2[1,])/abs(cleanmeansP2[6,])
+justbin[4,] <- abs(cleanmeansP[2,])
+justbin[8,] <- abs(cleanmeansP2[2,])
+justdich[4,] <- abs(cleanmeansP[6,])
+justdich[8,] <- abs(cleanmeansP2[6,])
+
+allbin <- 20*log10(allbin)
+alldich <- 20*log10(alldich)
+
+plotlims <- c(-24,24,-24,24) 
+ticklocsx <- seq(-24,24,12)    
+ticklocsy <- seq(-24,24,12)      
+ticklabelsx <- c('1/16','1/4','1','4','16')        
+ticklabelsy <- ticklabelsx    # set labels for y ticks
+
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2)    
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+
+title(xlab="Binocular facilitation", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
+title(ylab="Dichoptic suppression", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
+
+points(allbin[1:4,5],alldich[1:4,5],pch=21)
+
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2)    
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+
+title(xlab="Binocular facilitation", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
+title(ylab="Dichoptic suppression", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
+
+points(allbin[5:8,5],alldich[5:8,5],pch=21)
+
+plotlims <- c(-24,12,0,0.6) 
+ticklocsx <- seq(-24,12,12)    
+ticklocsy <- seq(0,0.6,0.1)    
+ticklabelsx <- c('1/16','1/4','1','4')        
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2)    
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+
+title(xlab="w", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
+title(ylab="Probability", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
+title(main='Suppressive weight 1F',cex.main=2)
+
+a <- density(20*log10(pupilweightpopLum),from=-48,to=12)   
+polygon(c(-48,a$x,12), c(0,a$y,0), col=addalpha(colpalmod[1],0.5),border=NA)
+
+a <- density(20*log10(pupilweightpopMel),from=-48,to=12)   
+polygon(c(-48,a$x,12), c(0,a$y,0), col=addalpha(colpalmod[2],0.5),border=NA)
+
+a<- density(20*log10(pupilweightpopLM),from=-48,to=12)   
+polygon(c(-48,a$x,12), c(0,a$y,0), col=addalpha(colpalmod[3],0.5),border=NA)
+
+a <- density(20*log10(pupilweightpopS),from=-48,to=12)   
+polygon(c(-48,a$x,12), c(0,a$y,0), col=addalpha(colpalmod[4],0.5),border=NA)
+
+prior <- dnorm(10^((-48:12)/20),1,0.5)
+prior <- 0.5*prior/max(prior)
+lines(-48:12,prior)
+
+lines(20*log10(c(mean(pupilWLum),mean(pupilWLum))),c(0,0.6),lwd=3,col=colpalmod[1])
+lines(20*log10(c(mean(pupilWMel),mean(pupilWMel))),c(0,0.6),lwd=3,col=colpalmod[2])
+lines(20*log10(c(mean(pupilWLM),mean(pupilWLM))),c(0,0.6),lwd=3,col=colpalmod[3])
+lines(20*log10(c(mean(pupilWS),mean(pupilWS))),c(0,0.6),lwd=3,col=colpalmod[4])
+
+legend(-24,0.6,c('Prior','Lum 1F', 'Mel 1F', 'LM 1F', 'S 1F'),col=c('black',colpalmod[1:4]),lwd=c(1,3,3,3,3),lty=1, cex=1.5, box.lwd=2, bg='white')
+
+text(10,0.58,'(c)',adj=0.5,cex=2.5)
+
+plotlims <- c(-24,12,0,0.6) 
+ticklocsx <- seq(-24,12,12)    
+ticklocsy <- seq(0,0.6,0.1)    
+ticklabelsx <- c('1/16','1/4','1','4')        
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2)    
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+
+title(xlab="w", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
+title(ylab="Probability", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
+title(main='Suppressive weight 2F',cex.main=2)
+
+a <- density(20*log10(pupilweightpopLum2),from=-48,to=12)   
+polygon(c(-48,a$x,12), c(0,a$y,0), col=addalpha(colpalmod[1],0.5),border=NA)
+
+a <- density(20*log10(pupilweightpopMel2),from=-48,to=12)   
+polygon(c(-48,a$x,12), c(0,a$y,0), col=addalpha(colpalmod[2],0.5),border=NA)
+
+a <- density(20*log10(pupilweightpopLM2),from=-48,to=12)   
+polygon(c(-48,a$x,12), c(0,a$y,0), col=addalpha(colpalmod[3],0.5),border=NA)
+
+a <- density(20*log10(pupilweightpopS2),from=-48,to=12)   
+polygon(c(-48,a$x,12), c(0,a$y,0), col=addalpha(colpalmod[4],0.5),border=NA)
+
+prior <- dnorm(10^((-48:12)/20),1,0.5)
+prior <- 0.5*prior/max(prior)
+lines(-48:12,prior)
+
+lines(20*log10(c(mean(pupilWLum2),mean(pupilWLum2))),c(0,0.6),lwd=3,col=colpalmod[1])
+lines(20*log10(c(mean(pupilWMel2),mean(pupilWMel2))),c(0,0.6),lwd=3,col=colpalmod[2])
+lines(20*log10(c(mean(pupilWLM2),mean(pupilWLM2))),c(0,0.6),lwd=3,col=colpalmod[3])
+lines(20*log10(c(mean(pupilWS2),mean(pupilWS2))),c(0,0.6),lwd=3,col=colpalmod[4])
+
+legend(-24,0.6,c('Prior','Lum 2F', 'Mel 2F', 'LM 2F', 'S 2F'),col=c('black',colpalmod[1:4]),lwd=c(1,3,3,3,3),lty=1, cex=1.5, box.lwd=2, bg='white')
+
+text(10,0.58,'(d)',adj=0.5,cex=2.5)
+
+dev.off()
+
+}
 
 ```
-
-## Phase analysis
 
@@
 
-pdf(paste(figdir,"phaseplots.pdf",sep=''), bg="transparent", height = 10, width = 10)
-
-par(mfrow=c(2,2),mar=c(1,1,1,1))
-
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-0.02,0.02), ylim=c(-0.02,0.02))
+pdf(paste(figdir,"phaseplots.pdf",sep=''), bg="transparent", height = 5, width = 10)
+
+par(mfrow=c(1,2),mar=c(1,1,1,1))
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-0.022,0.022), ylim=c(-0.022,0.022))
 
@@
 
-text(0.015,0.001,'Amplitude',cex=1.25,adj=0.5)
+text(0.015,-0.001,'Amplitude',cex=1.25,adj=0.5)
 text(0.021,0,'Phase',cex=1.25,adj=0.5,srt=-90)
 
-lines(xlum[1,]/10,ylum[1,]/10,col='black',lwd=3)
-points(xlum[1,]/10,ylum[1,]/10,pch=21,col='black',bg='white',cex=2,lwd=3)
-
-lines(xmel[1,],ymel[1,],col='grey',lwd=3)
-points(xmel[1,],ymel[1,],pch=21,col='grey',bg='cornflowerblue',cex=2,lwd=3)
-
-lines(xlm[1,],ylm[1,],col='darkgreen',lwd=3)
-points(xlm[1,],ylm[1,],pch=21,col='darkgreen',bg='red',cex=2,lwd=3)
-
-lines(xs[1,],ys[1,],col='blue',lwd=3)
-points(xs[1,],ys[1,],pch=21,col='blue',bg='gold',cex=2,lwd=3)
-
-legend(-0.0175,0.0155,c('Luminance','Melanopsin','L-M','S'),lty=1,col=c('black','grey','darkgreen','blue'),lwd=3,pch=21,pt.cex=2,pt.bg=c('white','cornflowerblue','red','gold'),cex=1.4,box.lwd=3,bg='white')
+lines(xlum[2,]/10,ylum[2,]/10,col=stimcolours[1],lwd=3)
+points(xlum[2,]/10,ylum[2,]/10,pch=21,col=stimcolours[1],bg=stimcolours[2],cex=2,lwd=3)
+
+lines(xmel[2,],ymel[2,],col=stimcolours[7],lwd=3)
+points(xmel[2,],ymel[2,],pch=21,col=stimcolours[7],bg=stimcolours[8],cex=2,lwd=3)
+
+lines(xlm[2,],ylm[2,],col=stimcolours[3],lwd=3)
+points(xlm[2,],ylm[2,],pch=21,col=stimcolours[3],bg=stimcolours[4],cex=2,lwd=3)
+
+lines(xs[2,],ys[2,],col=stimcolours[6],lwd=3)
+points(xs[2,],ys[2,],pch=21,col=stimcolours[6],bg=stimcolours[5],cex=2,lwd=3)
 
 text(-0.019,0.019,'(a)',cex=3)
-text(0.016,0.019,'Mon 1F',cex=2.5)
-
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-0.02,0.02), ylim=c(-0.02,0.02))
+text(0.016,0.019,'1F',cex=2.5)
+
+legend(-0.019,0.0155,c('Luminance','L-M','S','Melanopsin'),lty=1,col=stimcolours[c(1,3,6,7)],lwd=3,pch=21,pt.cex=2,pt.bg=stimcolours[c(2,4,5,8)],cex=1.1,box.lwd=3,bg='white')
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-0.022,0.022), ylim=c(-0.022,0.022))
 
@@
 
-text(0.015,0.001,'Amplitude',cex=1.25,adj=0.5)
+text(0.015,-0.001,'Amplitude',cex=1.25,adj=0.5)
 text(0.021,0,'Phase',cex=1.25,adj=0.5,srt=-90)
 
-lines(xlum[2,]/10,ylum[2,]/10,col='black',lwd=3)
-points(xlum[2,]/10,ylum[2,]/10,pch=22,col='black',bg='white',cex=2,lwd=3)
-
-lines(xmel[2,],ymel[2,],col='grey',lwd=3)
-points(xmel[2,],ymel[2,],pch=22,col='grey',bg='cornflowerblue',cex=2,lwd=3)
-
-lines(xlm[2,],ylm[2,],col='darkgreen',lwd=3)
-points(xlm[2,],ylm[2,],pch=22,col='darkgreen',bg='red',cex=2,lwd=3)
-
-lines(xs[2,],ys[2,],col='blue',lwd=3)
-points(xs[2,],ys[2,],pch=22,col='blue',bg='gold',cex=2,lwd=3)
+lines(xlum2[2,],ylum2[2,],col=stimcolours[1],lwd=3)
+points(xlum2[2,],ylum2[2,],pch=21,col=stimcolours[1],bg=stimcolours[2],cex=2,lwd=3)
+
+lines(xmel2[2,],ymel2[2,],col=stimcolours[7],lwd=3)
+points(xmel2[2,],ymel2[2,],pch=21,col=stimcolours[7],bg=stimcolours[8],cex=2,lwd=3)
+
+lines(xlm2[2,],ylm2[2,],col=stimcolours[3],lwd=3)
+points(xlm2[2,],ylm2[2,],pch=21,col=stimcolours[3],bg=stimcolours[4],cex=2,lwd=3)
+
+lines(xs2[2,],ys2[2,],col=stimcolours[6],lwd=3)
+points(xs2[2,],ys2[2,],pch=21,col=stimcolours[6],bg=stimcolours[5],cex=2,lwd=3)
 
 text(-0.019,0.019,'(b)',cex=3)
-text(0.016,0.019,'Bin 1F',cex=2.5)
-
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-0.02,0.02), ylim=c(-0.02,0.02))
-
-rangles <- seq(0,360)*(pi/180)
-r <- seq(0.005,0.02,0.005)
-for (n in 1:length(r)){
-  lines(r[n]*cos(rangles),r[n]*sin(rangles),col='gray')
-}
-lines(c(0,0),c(-0.02,0.02),lwd=2)
-lines(c(-0.02,0.02),c(0,0),lwd=2)
-
-text(0.015,0.001,'Amplitude',cex=1.25,adj=0.5)
-text(0.021,0,'Phase',cex=1.25,adj=0.5,srt=-90)
-
-lines(xlum2[1,],ylum2[1,],col='black',lwd=3)
-points(xlum2[1,],ylum2[1,],pch=21,col='black',bg='white',cex=2,lwd=3)
-
-lines(xmel2[1,],ymel2[1,],col='grey',lwd=3)
-points(xmel2[1,],ymel2[1,],pch=21,col='grey',bg='cornflowerblue',cex=2,lwd=3)
-
-lines(xlm2[1,],ylm2[1,],col='darkgreen',lwd=3)
-points(xlm2[1,],ylm2[1,],pch=21,col='darkgreen',bg='red',cex=2,lwd=3)
-
-lines(xs2[1,],ys2[1,],col='blue',lwd=3)
-points(xs2[1,],ys2[1,],pch=21,col='blue',bg='gold',cex=2,lwd=3)
-
-text(-0.019,0.019,'(c)',cex=3)
-text(0.016,0.019,'Mon 2F',cex=2.5)
-
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-0.02,0.02), ylim=c(-0.02,0.02))
-
-rangles <- seq(0,360)*(pi/180)
-r <- seq(0.005,0.02,0.005)
-for (n in 1:length(r)){
-  lines(r[n]*cos(rangles),r[n]*sin(rangles),col='gray')
-}
-lines(c(0,0),c(-0.02,0.02),lwd=2)
-lines(c(-0.02,0.02),c(0,0),lwd=2)
-
-text(0.015,0.001,'Amplitude',cex=1.25,adj=0.5)
-text(0.021,0,'Phase',cex=1.25,adj=0.5,srt=-90)
-
-lines(xlum2[2,],ylum2[2,],col='black',lwd=3)
-points(xlum2[2,],ylum2[2,],pch=22,col='black',bg='white',cex=2,lwd=3)
-
-lines(xmel2[2,],ymel2[2,],col='grey',lwd=3)
-points(xmel2[2,],ymel2[2,],pch=22,col='grey',bg='cornflowerblue',cex=2,lwd=3)
-
-lines(xlm2[2,],ylm2[2,],col='darkgreen',lwd=3)
-points(xlm2[2,],ylm2[2,],pch=22,col='darkgreen',bg='red',cex=2,lwd=3)
-
-lines(xs2[2,],ys2[2,],col='blue',lwd=3)
-points(xs2[2,],ys2[2,],pch=22,col='blue',bg='gold',cex=2,lwd=3)
-
-text(-0.019,0.019,'(d)',cex=3)
-text(0.016,0.019,'Bin 2F',cex=2.5)
+text(0.016,0.019,'2F',cex=2.5)
 
@@
 
-```{r phaseplots, fig.cap="Pupil phase plots at the first and second harmonic frequencies for the luminance, melanopsin, L-M pathway and the S-(L+M) pathway experiments.
-Panel (a) shows the pupil response during monocular stimulation at the first harmonic frequency.
-Panel (b) shows the pupil response during binocular stimulation at the first harmonic frequency.
-Panel (c) shows the pupil response during monocular stimulation at the second harmonic frequency.
-Panel (d) shows the pupil response during binocular stimulation at the second harmonic frequency.
-In panels (a) and (b), the luminance amplitudes have been scaled down by a factor of 10 to be compared with the other experiments' results.", fig.align="center", echo=FALSE}
+# Abstract (250 words)
+
+The diameter of the pupil fluctuates in response to levels of ambient light and is regulated by the autonomic nervous system.
+Increasing light in one eye causes both pupils to constrict, implying the system must combine signals across the two eyes, a process of binocular integration occuring independently of visual cortex.
+Distinct classes of retinal photoreceptor are involved in controlling and maintaining pupil diameter, with cones and rods driving the initial constriction and intrinsically photosensitive retinal ganglion cells maintaining diameter over prolonged time periods.
+Here, we used silent substitution to investigate binocular combination while targeting different photoreceptor pathways with sinusoidally modulated inputs.
+We find different patterns of binocular response in each pathway, and across the first and second harmonic frequencies.
+At the first harmonic, luminance and S-cone responses showed strong binocular facilitation, and weak interocular suppression.
+Melanopsin responses were invariant to the number of eyes stimulated.
+Notably, the L-M pathway involved binocular inhibition, whereby responses to binocular stimulation were weaker than for monocular stimulation.
+The second harmonic involved greater binocular facilitation in all pathways, and we show that binocular facilitation is negatively correlated with the magnitude of dichoptic masking.
+Our results are consistent with a computational model of binocular signal combination (implemented in a Bayesian hierarchical framework), in which the weight of interocular suppression differs across pathways.
+We also find pathway differences in response phase, consistent with different lag times for phototransduction.
+This work demonstrates for the first time the algorithm governing binocular combination in the autonomic nervous system.
+
+# Significance statement (120 words)
+
+# Introduction
+
+The autonomic nervous system regulates many involuntary bodily processes, including the constriction and dilation of the pupils in response to light [@McDougal2015].
+The anatomical pathway from the retina to the subcortical nuclei controlling the pupillary light response (PLR) is well established: it includes the Pretectal Olivary nucleus (PON), the Superior Cervical ganglion and the Edinger-Westphal nucleus, which project to the iris sphincter muscles that directly control the pupil size [@McDougal2008; @McDougal2015; @Wang2015].
+Evidence of a binocular component to the PLR is shown by the existence of a consensual response of the pupil [the stimulation of one eye will cause constriction of the other eye, @Wyatt1981].
+The anatomical segregation of the subcortical pathway from the rest of the brain means that this binocular combination of signals must occur independently of the cortical processes of binocular integration required for visual perception.
+Our recent work [@Segala2023] has shown that the algorithm underlying binocular combination of light in the pupil pathway differs from that in the cortex.
+Here we extend this paradigm to compare binocular combination in different photoreceptor pathways that feed into the autonomic nervous system.
+
+Different classes of retinal photoreceptors, including cones, rods and the recently discovered melanopsin-containing intrinsically photosensitive retinal ganglion cells (ipRGCs), are directly involved in controlling and maintaining the size of the pupils [@Barrionuevo2014; @Barrionuevo2018; @Dacey2005; @Murray2018; @Spitschan2014; @Spitschan2019; @Woelders2018].
+The cones have been shown to drive the initial rapid constriction of the pupils [@Mathot2018], while the slower and longer activation of the ipRGCs shows their role in maintaining the constriction over a prolonged period of time and in regulating the post-illumination pupillary response [@Markwell2010; @McDougal2010].
+The ipRGCs are a unique photoreceptor class that has been discovered recently [@Provencio2000].
+They express the photopigment melanopsin, and are involved in the regulation of the circadian rhythm [@Provencio2000; @Panda2002; @Ruby2002], forming a major input to the PON [@Dacey2003].
+The first direct evidence of the involvement of the ipRGCs in the PLR was shown in rats by @Lucas2003 who genetically deleted the melanopsin gene from rats, resulting in the loss of the intrinsic photosensitivity of the cells and a reduced pupil constriction.
+This same behaviour was later also observed in primates and humans [@Gamlin2007], where it was demonstrated that the PLR continues during light presentation even when cone and rod signalling is blocked, indicating the primary role of the ipRGCs in maintaining pupil constriction over a prolonged time.
+
+A technique known as silent substitution [@Estevez1982] can be used to selectively stimulate specific photoreceptor classes.
+Silent substitution exploits the fact that each photoreceptor class has a distinct spectral tuning that overlaps with the others.
+Using a multiprimary system, in which the primaries have different spectra, it is possible to target one class of photoreceptors while maintaining the others at a constant activity level, effectively silencing them [@Shapiro1996; @Spitschan2018, this paper also offers a clear explanation of how to implement silent substitution].
+Studies using silent substitution have shown that the pupils behave differently depending on which photoreceptor or pathway is being stimulated.
+For example, pupil responses have been shown to be out of phase when the S cones are stimulated, relative to when the ipRGCs or the L+M cones are stimulated [@Spitschan2014; @Cao2015].
+Additionally, when L and M cones are stimulated individually, there appears to be a paradoxical pupil response: increments in L cone stimulation cause a constriction of the pupil, while increments in M cone stimulation lead to a dilation of the pupil [@Woelders2018; @Murray2018].
+
+Binocular combination has been extensively studied in visual perception, where it is mediated by neurons in primary visual cortex [@Hubel1962; @Moradi2009].
+For pattern vision, binocular summation occurs at threshold, such that less contrast is required to detect a target shown to both eyes than for a target shown to only one eye [@Baker2018; @Campbell1965; @Legge1984].
+At higher contrasts, a process of 'ocularity invariance' is observed, in which the response to monocularly- and binocularly-presented patterns is equal [@Baker2007; @Ding2006; @Meese2006; @Moradi2009].
+This is thought to be due to a process of interocular suppression that compensates for the additional excitatory drive caused by stimulating two eyes.
+Our recent work [@Segala2023] has shown that cortical signal combination for luminance flicker is substantially more linear than for spatial patterns, whereas there is evidence of interocular suppression in the pupil pathway.
+
+Most studies that use silent substitution to investigate the PLR stimulate only one eye.
+If the stimulated eye is pharmacologically dilated to control pupil size, the response from the unstimulated eye (known as the consensual response) can be recorded [e.g.
+@McDougal2010; @Spitschan2014].
+While this approach controls the total amount of light incident at the retina, it does not permit investigation of binocular combination for specific photoreceptor pathways.
+Here we take a different approach, using a custom binocular multiprimary system (see Figure \@ref(fig:spectraplots)a,b) that can modulate each (undilated) eye independently, and a binocular eye tracker to measure the diameter of both pupils.
+We measure the amplitude of pupil modulation (using Fourier analysis) in response to sinusoidal stimulation at 0.5Hz, for stimuli directed at the luminnce pathway, L-M cone pathway, S-cone pathway, and melanopsin pathway.
+Our key comparisons are between monocular and binocular stimulation, and between monocular stimulation and a dichoptic masking condition in which the non-target eye is stimulated by a high contrast mask signal at a different frequency (0.4Hz).
+The results are interpreted using a contemporary model of binocular vision [@Meese2006] implemented within a hierarchical Bayesian framework
+
+# Results
+
+Figure \@ref(fig:spectraplots)m-p shows averaged waveforms of pupil diameter in response to binocular stimulation.
+For luminance stimuli (Figure \@ref(fig:spectraplots)m) a strong modulation is apparent at the stimulation frequency (0.5Hz), which is also clear in the Fourier amplitude spectrum (Figure \@ref(fig:spectraplots)q).
+For binocular stimulation of the L-M pathway, S-cone pathway and melanopsin pathway, pupil modulations were less than 10\% of the amplitude of the luminance modulation (note the change in y-axis scale for the Fourier spectra), but still apparent at 0.5Hz in the Fourier spectra (Figure \@ref(fig:spectraplots)n-p).
+We also observed a second harmonic response (at 1Hz) for all conditions, which was weaker than the first harmonic for luminance and melanopsin stimulation, but stronger for L-M and S-cone stimulation.
+The additional component is also apparent in the pupil waveforms shown in Figure \@ref(fig:spectraplots)n-p.
+Our main analysis therefore focuses on the amplitude of the pupil modulations at both the first and second harmonic frequencies across different stimulus conditions.
+
+```{r spectraplots, fig.cap="Summary of the spectral power distributions and alpha-opic irradiances for the background and each condition, as well as averaged pupil diameters and Fourier spectra.
+Panel (a) shows a schematic of the binocular stimulation system for presenting spectrally tuned modulations independently to each eye.
+The VR headset was attached to a clamp stand that the experimenters could use to adjust the height and align the headset with the eyes of the participant.
+The participant's head was supported by a chin rest to keep it in position throughout the experiment.
+Panel (b) shows the outputs of each LED primary at maximum intensity, and panels (c) and (d) show the overall spectral power distributions and the alpha-opic irradiances of the background spectra used for both eyes.
+The subsequent rows show the power differences (e-h), and photoreceptor contrasts (i-l) relative to the background, averaged pupil diameter waveforms (m-p) and Fourier spectra (q-t) for binocular stimulation.
+Column headings indicate the pathway stimulated, and shaded regions in panels m-t indicate bootstrapped 95\\% confidence intervals.", fig.align="center", out.width = '80%', echo=FALSE}
+
+knitr::include_graphics(paste0(figdir,'methodsfig.pdf'))
+
+```
+
+Figure \@ref(fig:CRFplots) shows contrast response functions across stimulation conditions for responses at the first harmonic (panels a-d) and the second harmonic (panels e-h) frequencies.
+In each plot, the response to monocular stimulation is given by the red circles and typically increases monotonically as a function of stimulus (temporal) contrast (main effects of stimulus contrast are significant for all data sets, see Supplementary Materials).
+Relative to monocular stimulation, binocular stimulation typically led to higher response amplitudes, indicating a binocular facilitation effect (main effects of condition are significant for all data sets, see Supplementary Materials).
+This is strongest for the luminance and S-cone conditions at the first harmonic (Figure \@ref(fig:CRFplots)a,c) and the L-M cone and Melanopsin conditions at the second harmonic (Figure \@ref(fig:CRFplots)f,h).
+One striking exception to this pattern is in the L-M cone condition at the first harmonic (Figure \@ref(fig:CRFplots)b): this condition produced a binocular suppression effect, where the response to binocular stimulation is weaker than the response to monocular stimulation (blue squares below red circles).
+These results indicate that the magnitude of binocular facilitation differs across photoreceptor pathway, suggesting heterogeneity in the underlying neural computation.
+
+```{r CRFplots, fig.cap="Contrast response functions for monocular (red circles), binocular (blue squares) and dichoptic (yellow diamonds) conditions, for stimulation of different pathways (columns) at the first and second harmonic frequencies (rows).
+Error bars indicate bootstrapped 95\\% confidence intervals", fig.align="center", echo=FALSE}
+
+knitr::include_graphics(paste0(figdir,'CRFs.pdf'))
+
+```
+
+In contemporary models of binocular signal combination, the amount of binocular facilitation is determined by the magnitude of interocular suppression, with strong suppression reducing facilitation [@Kingdom2015].
+We can estimate the strength of interocular suppression by measuring how much monocular responses are reduced when a high contrast dichoptic mask is shown to the other eye.
+In our paradigm, this mask flickered at a lower frequency (0.4Hz) so that the two stimulus components remain distinct in the Fourier spectrum [e.g.
+@Busse2009].
+The yellow diamond symbols in Figure \@ref(fig:CRFplots) show the target responses in this condition, and in most cases are weaker than the monocular responses (red circles).
+The strongest dichoptic masking is found in the first harmonic L-M condition, where we also observed the binocular suppression effect.
+We summarise this relationship by calculating an index for each effect, and show that the binocular facilitation effect is negatively correlated with the dichoptic masking effect (see Figure \@ref(fig:suppressionfig)).
+
+```{r suppressionfig, fig.cap="P.", fig.align="center", echo=FALSE}
+
+knitr::include_graphics(paste0(figdir,'suppressionfig.pdf'))
+
+```
+
+Next, we fitted all 8 data sets using a Bayesian hierarchical implementation of a simple binocular combination model [@Meese2006; @Segala2023].
+Our primary interest was to compare posterior distributions of the weight of interocular suppression, which are showin in Figure \@ref(fig:suppressionfig).
+Consistent with our earlier observations, at the first harmonic the strongest suppressive weight corresponds to the L-M condition, and the weakest suppression corresponds to the luminance condition [also consistent with @Segala2023].
+The model fits were of good quality, as shown by the curves in Figure \@ref(fig:CRFplots).
+Further details of fitted parameters, and model behaviour in other empirical conditions are provided in the Supplementary Materials.
+
+Finally, we inspected the response phase of our four stimulation conditions, given previous reports that these differ across pathways [@Spitschan2014], and may be in antiphase for melanopsin and S-cone signals.
+Figure \@ref(fig:phaseplots) shows the phase angles for the first (a) and second (b) harmonic frequencies for binocular stimulation (monocular stimulation produced very similar results).
+At the first harmonic, melanopsin and S-cone signals differed in phase by more than 90 degrees, though they were not fully in antiphase.
+The luminance and L-M responses were more closely in antiphase to each other, however this is likely due to our choice to modulate L+M- in the first half-cycle (corresponding to a luminance increase in the luminance condition), and L-M+ in the second half-cycle (corresponding to a luminance decrease in the luminance condition).
+Had we reversed this phase arrangement, we would likely have seen a close phase correspondence between the L-M and luminance conditions.
+Phase differences between the luminance, S-cone and melanopsin conditions are likely attributable to different lags in phototransduction at the earliest stage (i.e.
+in the retina).
+At the second harmonic frequency (Figure \@ref(fig:phaseplots)b), the luminance condition was again out of phase with the other three, and was approximately in quadrature phase with the L-M condition, and in antiphase with both the S-cone and melanopsin conditions (which were in phase with each other).
+
+```{r phaseplots, fig.cap="Pupil phase plots at the first and second harmonic frequencies for the luminance, melanopsin, L-M pathway and the S-(L+M) pathway conditions Panel (a) shows the pupil response at the first harmonic frequency during binocular stimulation.
+Panel (b) shows the pupil response at the second harmonic frequency during binocular stimulation.
+In panel (a) the luminance amplitudes have been scaled down by a factor of 10 to be compared with the other conditions.", fig.align="center", echo=FALSE}
 
@@
 ```
-
-In a previous study, @Spitschan2014 analysed the phase of the pupil response and compared it between L+M-cone stimulation, S-cone stimulation, melanopsin stimulation and brightness stimulation.
-In their study, they found that, at a flicker frequency of 0.5 Hz, L+M and melanopsin responses were in phase, while brightness and S-cone responses were in anti-phase.
-Additionally, they found that, at the second harmonic frequency, S-cone and melanospin responses seem to be in phase with each other and in anti-phase to L+M-cone responses.
-We reproduced this analysis with our data and the results are summarised in Figure \@ref(fig:phaseplots).
-At the first harmonic frequency, the amplitudes from the luminance experiment have been scaled down by a factor of 10 to make it possible to compare them directly with the results from the other experiments.
-
-Figure \@ref(fig:phaseplots)a shows the results to monocular responses at the first harmonic frequency.
-The L-M pathway stimulation produces an anti-phase pupil response relative to luminance stimulation.
-The S-(L+M) pathway and luminance results are desynchronised in quadrature phase.
-This same pattern of results is also observable in Figure \@ref(fig:phaseplots)b, which summarises the results to binocular responses at the first harmonic frequency.
-
-Figure \@ref(fig:phaseplots)c shows the results to monocular responses at the second harmonic frequency.
-Here, results are noisier compare to the first harmonic results, but a pattern is still observable.
-In general, it seems that melanopsin and S-(L+M) stimulations produce in-phase responses to each other, but produce anti-phase responses to luminance stimulation.
-On the other hand, L-M pathway responses seem to be desynchronised in quadrature phase from the the results of the other experiments.
-The same pattern of results is also observable in Figure \@ref(fig:phaseplots)d, which summarises the results to binocular responses at the second harmonic frequency.
 
@@
 
-# Acknowledgements
+# Materials and methods
+
+## Participants
+
+Twenty-four participants were recruited for each of the four experiments for a total of ninety-six (68 females) adult participants, whose ages ranged from 18 to 41.
+All participants had normal or corrected to normal binocular vision and normal colour vision, and gave written informed consent.
+Our procedures were approved by the Ethics Committee of the Department of Psychology at the University of York (identification number 184).
+
+## Apparatus & stimuli
+
+To present synchronised stimulus modulations independently to each eye, two light engines, each with 10 independently addressable LED colour channels (SpectraTuneLAB: LEDMOTIVE Technologies, LLC, Barcelona, Spain), were integrated into a customised viewing system.
+The light engines were operated via a Python interface to their REST API [@Martin2022], which supports synchronous launch and playback of spectral sequences prepared in advance and stored in JSON format.
+When preparing the spectral sequences, the age of participants was recorded to account for the yellowing of the lenses.
+We calculated silent substitution solutions using the _PySilSub_ toolbox [@Martin2023], using linear algebra.
+The outputs of the two light engines (see Figure \@ref(fig:spectraplots)b,c) were calibrated using an Ocean Optics Jaz spectroradiometer, which was wavelength-calibrated to an Argon lamp and intensity calibrated using a NIST-traceable light source.
+We used the @Stockman2000 10-degree cone fundamentals, and estimates of melanopsin absorbance spectra from CIE S 026 [discussed in @Martin2023] to calculate $\alpha$-opic irradiance.
+
+The output from the light engines was directed through liquid light guides (LLG3-8H: Thorlabs Ltd, Cambridgeshire, UK) and diffused onto semi-opaque and highly diffusive white glass discs with a diameter of 50 mm for even illumination (34-473: Edmund Optics, York, UK).
+The light guide gaskets were butt-coupled to the light engine diffusers with threaded adapters (SM1A9, AD3LLG: Thorlabs Ltd, Cambridgeshire, UK) and the exiting ends of the light guides were mated with 51 mm depth optical cylinders (SM2L20: Thorlabs Ltd, Cambridgeshire, UK) via appropriately threaded adapters (AD3LLG, SM2A6: Thorlabs Ltd, Cambridgeshire, UK).
+The stimulus diffuser discs were retained at the front end of the optical cylinders approximately 51 mm from the light source, at which distance the output beam was sufficiently dispersed to afford even illumination of the diffuser when viewed from the front.
+To guarantee safe illumination levels, a circular neutral-density filter with the same diameter of the white glass discs (50 mm) and an optical density of 0.6 log units was placed in the optical path between the light source and the diffusers.
+A small circular piece of blackout material with a diameter of approximately 8 degrees (10 mm) was positioned centrally on the front of each diffuser disc to aid as a fusion lock, as a fixation point, and to occlude the fovea.
+
+The diffuser discs were positioned in the objective planes of the lenses of a modified VR headset (SHINECON SC-G01, Dongguan Shinecon Industrial Co.
+Ltd., Guangdong, China), which was used by the participants to view the stimuli.
+The stimuli were two discs of flickering light with a diameter of approximately 30 degrees, which were fused together into a cyclopean percept resembling a donut-shaped ring of light, similar to that used in other studies [e.g., @Barrionuevo2016; @Murray2018; @Spitschan2014; @Zele2018].
+The VR headset modifications allowed for small adjustments to account for individual differences in interpupillary distance and focal length.
+The use of this set up allowed us to modulate the stimuli in three different ocular configurations, similar to the ones we used in our previous study [@Segala2023]: monocular, binocular and dichoptic.
+In the monocular configuration, the unstimulated eye still saw a non-flickering disc of mean luminance.
+A schematic of the stimulation system is shown in Figure \@ref(fig:spectraplots)a.
+Pupillometry data were collected using a binocular Pupil Core eye-tracker headset [Pupil Labs GmbH, Berlin, Germany, @Kassner2014] running at 120 Hz, and the signals were recorded with the Pupil Capture software.
+
+Our previous study [@Segala2023] used a temporal frequency of 2Hz for foveal luminance flicker, and recorded EEG data simultaneously with pupillometry.
+Initial pilot experiments indicated that this frequency was too high to elicit measurable responses when stimulating individual photoreceptor pathways.
+For all experiments, we therefore used a primary flicker frequency of 0.5Hz, as previous literature showed that it was slow enough to elicit a pupil response from all photoreceptor classes [@Spitschan2014].
+We also focussed on only recording pupillometry data as this frequency would be well below the minimum threshold to elicit steady-state EEG responses [@Norcia2015].
+
+For all experiments, sinusoidal temporal modulations were presented against the same background spectrum (matched between the eyes), which was used to achieve silent substitution in the three photoreceptor modulation experiments.
+The background spectra were defined by setting all channels to half maximum output for the brighter of the two devices (STLab 1, left eye) and then using the STLab 1/STLab 2 calibration ratio to find the equivalent settings for the companion device (STLab 2, right eye).
+The background spectrum illuminance was approximately 74 lux, or 62 cd/m$^2$.
+The spectral power distributions and $\alpha$-opic irradiances of the background spectra for both eyes are shown in Figure \@ref(fig:spectraplots)c-d.
+
+In the luminance experiment, the stimulus intensity was increased and decreased relative to the background, which we expected to modulate all photoreceptor classes (see Figure \@ref(fig:spectraplots)e,i).
+In the L-M cone modulation experiment, we used silent substution to increase the L-cone activity, and simultaneously decrease the M-cone activity, during the first half-cycle of the sine wave.
+In the second half-cycle the polarity of the modulation reversed (see Figure \@ref(fig:spectraplots)f,j).
+The maximum available L-M contrast was approximately 10\%.
+In the S-cone modulation experiment, we increased and decreased S-cone-directed signals, whilst keeping activity in the other photoreceptors constant (see Figure \@ref(fig:spectraplots)g,k).
+Our system allowed a maximum contrast of 45\%.
+Finally, in the melanopsin experiment, we modulated the activity of the melanopsin-containing intrinsically photoreceptive retinal ganglion cells, whilst keeping cone activity constant (see Figure \@ref(fig:spectraplots)h,l).
+The maximum available melanopsin contrast was 22\%.
+We assume that the activity of rods was constant at the high background luminance intensity used here, and so did not attempt to silence rod activity in any condition, as this would have greatly reduced the available dynamic range.
+Splatter on nominally silenced photoreceptors was very small (see Figure \@ref(fig:spectraplots)j-l), well below the levels that would be expected to generate measureable pupil modulations.
+
+## Procedure
+
+Before the start of each experiment, participants adjusted the objective planes of the lenses with the help of the experimenter until the stimulus was in focus and they perceived the two pieces of blackout material as one fused disc.
+Pupil responses to binocular temporal contrast modulations were examined in a factorial design that combined six ocular conditions and five temporal contrast levels (6, 12, 24, 48 and 96%) of the available dynamic range.
+This design, similar to that used in our previous studies [@Segala2023; @Baker2017; @Baker2020], was applied in four separate experiments, each with a different mode of photoreceptor stimulation.
+In the first three conditions, the discs flickered at 0.5 Hz, in either a monocular, binocular or dichoptic arrangement.
+In the dichoptic condition the non-target eye saw a flickering fixed contrast of 48% of the available dynamic range.
+In the remaining three conditions (the cross-frequency conditions) one eye’s disc flickered at 0.4 Hz, and the other eye’s disc flickered at 0.5 Hz.
+We also tested monocular responses at 0.4 Hz, as well as binocular (one eye sees each frequency at the target contrast) and dichoptic (target stimulus flickering at 0.5 Hz, mask contrast of 48% at 0.4 Hz in the other eye) arrangements.
+We counterbalanced presentation of the target stimulus across the left and right eyes.
+
+The experiments were conducted in a windowless room, in which the only source of light was the modified VR headset.
+The participants sat as close as possible to the VR headset, leaving enough space for the eye-tracker to record the eyes.
+The experiment was carried out in a single session of around 45-60 minutes, divided into three blocks of 15-17 minutes each.
+In each block, there were a total of 60 trials lasting 15 seconds each (12s of stimulus presentation, followed by 3s of interstimulus interval).
+The participants were given no task other than look at the black fixation dot while trying to minimise their blinking during the presentation period.
+For all experiments other than the luminance condition, participants adapted to the mean luminance for two minutes before stimulation began.
+
+Before the start of the L-M experiment, participants completed a luminance nulling perceptual calibration procedure in L-M cone space on an Iiyama $\textrm{VisionMaster}^{\textrm{TM}}$ Pro 510 display (800 x 600 pixels, 60 Hz refresh rate).
+During the task, participants were presented with a disc flickering within the L-M cone space (between magenta and cyan).
+Using a trackball, participants adjusted the angle in cone space to find their subjective isoluminant point, which resulted in changing the flickering intensity of the stimulus until the amplitude of the flicker appeared to be minimised.
+The result was used to modify the requested contrasts during stimulus preparation so as to account for individual differences affecting perceived illuminance, principally the L:M cone ratio [@Carroll2002; @Hofer2005].
+
+## Data analysis
+
+The pupillometry data were analysed using the same method we used in our previous study [@Segala2023].
+The data were converted from mp4 videos to a csv text file using the Pupil Player software [@Kassner2014], which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
+The individual data were then loaded into R for analysis, where a ten-second waveform for each trial in each eye was extracted (excluding the first two seconds after stimulus onset).
+We interpolated across any dropped or missing frames to ensure regular and continuous sampling over time.
+The Fourier transform was calculated for each waveform, and all repetitions of each condition were pooled across eye and then averaged.
+Finally, data were averaged across all participants to obtain the group results.
+We used coherent averaging and at each stage we excluded data points with a Mahalanobis distance exceeding $D$ = `r SDthresh` from the complex-valued mean [@Baker2021].
+For monocular stimulation, we confirmed that the consensual response was equivalent to the response in the stimulated eye.
+
+For all experiments, we used a bootstrapping procedure with `r nbootstraps` iterations to estimate standard errors across participants.
+All analysis and figure construction was conducted using a single R-script, available online, making this study fully computationally reproducible: https://osf.io/gdvt4/.
+
+## Computational model and parameter estimation
+
+To describe our data, we chose the same model described in our previous study [@Segala2023].
+The model has the same general form as the first stage of the contrast gain control model proposed by @Meese2006 and omits the second stage.
+For the previous model that we used [@Segala2023], the exponent of the numerator and denominator had fixed values of 2 and (implicitly) 1.
+Here, we allow these parameters (called _p_ and _q_) to be free, in order to permit different shapes of contrast response function, e.g.
+saturating or super-saturating.
+The responses of the left eye and right eye channels are as follows:
+
+\begin{equation}
+\label{eq:respLchap4}
+Resp_L = \frac{L^p}{Z + L^q + wR^q},
+\end{equation}
+
+\begin{equation}
+\label{eq:respRchap4}
+Resp_R = \frac{R^p}{Z + R^q + wL^q},
+\end{equation}
+
+\noindent where _L_ and _R_ are the contrast signals from the left and right eyes, _p_ and _q_ are exponents, _Z_ is a saturation constant that shifts the contrast-response function laterally, and _w_ is the weight of suppression from the other eye.
+
+The responses from the two eyes are then summed binocularly:
+
+\begin{equation}
+\label{eq:respBchap4}
+Resp_B = R_{max}(Resp_L + Resp_R) + k,
+\end{equation}
+
+\noindent where _k_ is a noise parameter, and $R_{max}$ scales the overall response amplitude.
+
+We performed model fitting on the normalised amplitudes to account for amplitude differences between the experiments.
+The models were fit using a hierarchical Bayesian framework implemented in Stan [@Carpenter2017].
+The data for each photoreceptor type and response frequency was fit separately, for a total of 8 model fits.
+The prior
+
+# Acknowledgements and funding sources
 
@@
 # References
+
+<div id='refs'> </div>
+
+# Supplementary Materials
+
+```{r paramtable1F, echo=FALSE}
+
+condnames <- c('Luminance 1F', 'Melanopsin 1F', 'L-M 1F', 'S 1F')
+zlist <- c(pupilZLum, pupilZMel, pupilZLM, pupilZS)
+klist <- c(pupilKLum, pupilKMel, pupilKLM, pupilKS)
+wlist <- c(pupilWLum, pupilWMel, pupilWLM, pupilWS)
+plist <- c(pupilPLum, pupilPMel, pupilPLM, pupilPS)
+qlist <- c(pupilQLum, pupilQMel, pupilQLM, pupilQS)
+Rlist <- c(round(c(pupilRmaxLum, pupilRmaxMel, pupilRmaxLM, pupilRmaxS),5))
+tabledata <- data.frame(condnames,round(zlist,digits=2),round(klist,digits=2),round(wlist,digits=2),round(plist,digits=2),round(qlist,digits=2),Rlist)
+
+colnames(tabledata) <- c('Experiment','Z','k','w','p','q','Rmax')
+kable(tabledata, align='lcccccc',caption = 'Summary of median parameter values at the first harmonic frequency.')
+
+```
+
+```{r paramtable2F, echo=FALSE}
+
+condnames <- c('Luminance 2F', 'Melanopsin 2F', 'L-M 2F', 'S 2F')
+zlist <- c(pupilZLum2, pupilZMel2, pupilZLM2, pupilZS2)
+klist <- c(pupilKLum2, pupilKMel2, pupilKLM2, pupilKS2)
+wlist <- c(pupilWLum2, pupilWMel2, pupilWLM2, pupilWS2)
+plist <- c(pupilPLum2, pupilPMel2, pupilPLM2, pupilPS2)
+qlist <- c(pupilQLum2, pupilQMel2, pupilQLM2, pupilQS2)
+Rlist <- c(round(c(pupilRmaxLum2, pupilRmaxMel2, pupilRmaxLM2, pupilRmaxS2),5))
+tabledata <- data.frame(condnames,round(zlist,digits=2),round(klist,digits=2),round(wlist,digits=2),round(plist,digits=2),round(qlist,digits=2),Rlist)
+
+colnames(tabledata) <- c('Experiment','Z','k','w','p','q','Rmax')
+kable(tabledata, align='lcccccc',caption = 'Summary of median parameter values at the second harmonic frequency.')
+
+```

### 2024-01-15 manuscript.tex
Updates to text and code

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\usepackage{caption}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Binocular combination in the autonomic nervous system},
  colorlinks=true,
  linkcolor={black},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Binocular combination in the autonomic nervous system}
\author{Federico G. Segala\(^1\), Joel T. Martin\(^1\), Annie Y. Morsi\(^1\), Alex R. Wade\(^{1,2}\) \& Daniel H. Baker\(^{1,2}\)}
\date{}

\begin{document}
\maketitle

\(^1\)Department of Psychology, University of York, Heslington, York, United Kingdom.

\(^2\)York Biomedical Research Institute, University of York, Heslington, York, United Kingdom.

Address for correspondence: Federico G. Segala, \url{federico.segala@york.ac.uk}

\hypertarget{abstract-250-words}{%
\section{Abstract (250 words)}\label{abstract-250-words}}

The diameter of the pupil fluctuates in response to levels of ambient light and is regulated by the autonomic nervous system. Increasing light in one eye causes both pupils to constrict, implying the system must combine signals across the two eyes, a process of binocular integration occuring independently of visual cortex. Distinct classes of retinal photoreceptor are involved in controlling and maintaining pupil diameter, with cones and rods driving the initial constriction and intrinsically photosensitive retinal ganglion cells maintaining diameter over prolonged time periods. Here, we used silent substitution to investigate binocular combination while targeting different photoreceptor pathways with sinusoidally modulated inputs. We find different patterns of binocular response in each pathway, and across the first and second harmonic frequencies. At the first harmonic, luminance and S-cone responses showed strong binocular facilitation, and weak interocular suppression. Melanopsin responses were invariant to the number of eyes stimulated. Notably, the L-M pathway involved binocular inhibition, whereby responses to binocular stimulation were weaker than for monocular stimulation. The second harmonic involved greater binocular facilitation in all pathways, and we show that binocular facilitation is negatively correlated with the magnitude of dichoptic masking. Our results are consistent with a computational model of binocular signal combination (implemented in a Bayesian hierarchical framework), in which the weight of interocular suppression differs across pathways. We also find pathway differences in response phase, consistent with different lag times for phototransduction. This work demonstrates for the first time the algorithm governing binocular combination in the autonomic nervous system.

\hypertarget{significance-statement-120-words}{%
\section{Significance statement (120 words)}\label{significance-statement-120-words}}

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

The autonomic nervous system regulates many involuntary bodily processes, including the constriction and dilation of the pupils in response to light (\protect\hyperlink{ref-McDougal2015}{McDougal and Gamlin, 2015}). The anatomical pathway from the retina to the subcortical nuclei controlling the pupillary light response (PLR) is well established: it includes the Pretectal Olivary nucleus (PON), the Superior Cervical ganglion and the Edinger-Westphal nucleus, which project to the iris sphincter muscles that directly control the pupil size (\protect\hyperlink{ref-McDougal2015}{McDougal and Gamlin, 2015}, \protect\hyperlink{ref-McDougal2008}{2008}; \protect\hyperlink{ref-Wang2015}{Wang and Munoz, 2015}). Evidence of a binocular component to the PLR is shown by the existence of a consensual response of the pupil (the stimulation of one eye will cause constriction of the other eye, \protect\hyperlink{ref-Wyatt1981}{Wyatt and Musselman, 1981}). The anatomical segregation of the subcortical pathway from the rest of the brain means that this binocular combination of signals must occur independently of the cortical processes of binocular integration required for visual perception. Our recent work (\protect\hyperlink{ref-Segala2023}{Segala et al., 2023}) has shown that the algorithm underlying binocular combination of light in the pupil pathway differs from that in the cortex. Here we extend this paradigm to compare binocular combination in different photoreceptor pathways that feed into the autonomic nervous system.

Different classes of retinal photoreceptors, including cones, rods and the recently discovered melanopsin-containing intrinsically photosensitive retinal ganglion cells (ipRGCs), are directly involved in controlling and maintaining the size of the pupils (\protect\hyperlink{ref-Barrionuevo2018}{Barrionuevo et al., 2018}; \protect\hyperlink{ref-Barrionuevo2014}{Barrionuevo et al., 2014}; \protect\hyperlink{ref-Dacey2005}{Dacey et al., 2005}; \protect\hyperlink{ref-Murray2018}{Murray et al., 2018}; \protect\hyperlink{ref-Spitschan2019}{Spitschan, 2019}; \protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}; \protect\hyperlink{ref-Woelders2018}{Woelders et al., 2018}). The cones have been shown to drive the initial rapid constriction of the pupils (\protect\hyperlink{ref-Mathot2018}{Mathôt, 2018}), while the slower and longer activation of the ipRGCs shows their role in maintaining the constriction over a prolonged period of time and in regulating the post-illumination pupillary response (\protect\hyperlink{ref-Markwell2010}{Markwell et al., 2010}; \protect\hyperlink{ref-McDougal2010}{McDougal and Gamlin, 2010}). The ipRGCs are a unique photoreceptor class that has been discovered recently (\protect\hyperlink{ref-Provencio2000}{Provencio et al., 2000}). They express the photopigment melanopsin, and are involved in the regulation of the circadian rhythm (\protect\hyperlink{ref-Panda2002}{Panda et al., 2002}; \protect\hyperlink{ref-Provencio2000}{Provencio et al., 2000}; \protect\hyperlink{ref-Ruby2002}{Ruby et al., 2002}), forming a major input to the PON (\protect\hyperlink{ref-Dacey2003}{Dacey et al., 2003}). The first direct evidence of the involvement of the ipRGCs in the PLR was shown in rats by Lucas et al. (\protect\hyperlink{ref-Lucas2003}{2003}) who genetically deleted the melanopsin gene from rats, resulting in the loss of the intrinsic photosensitivity of the cells and a reduced pupil constriction. This same behaviour was later also observed in primates and humans (\protect\hyperlink{ref-Gamlin2007}{Gamlin et al., 2007}), where it was demonstrated that the PLR continues during light presentation even when cone and rod signalling is blocked, indicating the primary role of the ipRGCs in maintaining pupil constriction over a prolonged time.

A technique known as silent substitution (\protect\hyperlink{ref-Estevez1982}{Estévez and Spekreijse, 1982}) can be used to selectively stimulate specific photoreceptor classes. Silent substitution exploits the fact that each photoreceptor class has a distinct spectral tuning that overlaps with the others. Using a multiprimary system, in which the primaries have different spectra, it is possible to target one class of photoreceptors while maintaining the others at a constant activity level, effectively silencing them (\protect\hyperlink{ref-Shapiro1996}{Shapiro et al., 1996}; \protect\hyperlink{ref-Spitschan2018}{Spitschan and Woelders, 2018}, this paper also offers a clear explanation of how to implement silent substitution). Studies using silent substitution have shown that the pupils behave differently depending on which photoreceptor or pathway is being stimulated. For example, pupil responses have been shown to be out of phase when the S cones are stimulated, relative to when the ipRGCs or the L+M cones are stimulated (\protect\hyperlink{ref-Cao2015}{Cao et al., 2015}; \protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}). Additionally, when L and M cones are stimulated individually, there appears to be a paradoxical pupil response: increments in L cone stimulation cause a constriction of the pupil, while increments in M cone stimulation lead to a dilation of the pupil (\protect\hyperlink{ref-Murray2018}{Murray et al., 2018}; \protect\hyperlink{ref-Woelders2018}{Woelders et al., 2018}).

Binocular combination has been extensively studied in visual perception, where it is mediated by neurons in primary visual cortex (\protect\hyperlink{ref-Hubel1962}{Hubel and Wiesel, 1962}; \protect\hyperlink{ref-Moradi2009}{Moradi and Heeger, 2009}). For pattern vision, binocular summation occurs at threshold, such that less contrast is required to detect a target shown to both eyes than for a target shown to only one eye (\protect\hyperlink{ref-Baker2018}{Baker et al., 2018}; \protect\hyperlink{ref-Campbell1965}{Campbell and Green, 1965}; \protect\hyperlink{ref-Legge1984}{Legge, 1984}). At higher contrasts, a process of `ocularity invariance' is observed, in which the response to monocularly- and binocularly-presented patterns is equal (\protect\hyperlink{ref-Baker2007}{Baker et al., 2007}; \protect\hyperlink{ref-Ding2006}{Ding and Sperling, 2006}; \protect\hyperlink{ref-Meese2006}{Meese et al., 2006}; \protect\hyperlink{ref-Moradi2009}{Moradi and Heeger, 2009}). This is thought to be due to a process of interocular suppression that compensates for the additional excitatory drive caused by stimulating two eyes. Our recent work (\protect\hyperlink{ref-Segala2023}{Segala et al., 2023}) has shown that cortical signal combination for luminance flicker is substantially more linear than for spatial patterns, whereas there is evidence of interocular suppression in the pupil pathway.

Most studies that use silent substitution to investigate the PLR stimulate only one eye. If the stimulated eye is pharmacologically dilated to control pupil size, the response from the unstimulated eye (known as the consensual response) can be recorded (e.g. \protect\hyperlink{ref-McDougal2010}{McDougal and Gamlin, 2010}; \protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}). While this approach controls the total amount of light incident at the retina, it does not permit investigation of binocular combination for specific photoreceptor pathways. Here we take a different approach, using a custom binocular multiprimary system (see Figure \ref{fig:spectraplots}a,b) that can modulate each (undilated) eye independently, and a binocular eye tracker to measure the diameter of both pupils. We measure the amplitude of pupil modulation (using Fourier analysis) in response to sinusoidal stimulation at 0.5Hz, for stimuli directed at the luminnce pathway, L-M cone pathway, S-cone pathway, and melanopsin pathway. Our key comparisons are between monocular and binocular stimulation, and between monocular stimulation and a dichoptic masking condition in which the non-target eye is stimulated by a high contrast mask signal at a different frequency (0.4Hz). The results are interpreted using a contemporary model of binocular vision (\protect\hyperlink{ref-Meese2006}{Meese et al., 2006}) implemented within a hierarchical Bayesian framework

\hypertarget{results}{%
\section{Results}\label{results}}

Figure \ref{fig:spectraplots}m-p shows averaged waveforms of pupil diameter in response to binocular stimulation. For luminance stimuli (Figure \ref{fig:spectraplots}m) a strong modulation is apparent at the stimulation frequency (0.5Hz), which is also clear in the Fourier amplitude spectrum (Figure \ref{fig:spectraplots}q). For binocular stimulation of the L-M pathway, S-cone pathway and melanopsin pathway, pupil modulations were less than 10\% of the amplitude of the luminance modulation (note the change in y-axis scale for the Fourier spectra), but still apparent at 0.5Hz in the Fourier spectra (Figure \ref{fig:spectraplots}n-p). We also observed a second harmonic response (at 1Hz) for all conditions, which was weaker than the first harmonic for luminance and melanopsin stimulation, but stronger for L-M and S-cone stimulation. The additional component is also apparent in the pupil waveforms shown in Figure \ref{fig:spectraplots}n-p.~Our main analysis therefore focuses on the amplitude of the pupil modulations at both the first and second harmonic frequencies across different stimulus conditions.

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{Figures/methodsfig}

}

\caption{Summary of the spectral power distributions and alpha-opic irradiances for the background and each condition, as well as averaged pupil diameters and Fourier spectra. Panel (a) shows a schematic of the binocular stimulation system for presenting spectrally tuned modulations independently to each eye. The VR headset was attached to a clamp stand that the experimenters could use to adjust the height and align the headset with the eyes of the participant. The participant's head was supported by a chin rest to keep it in position throughout the experiment. Panel (b) shows the outputs of each LED primary at maximum intensity, and panels (c) and (d) show the overall spectral power distributions and the alpha-opic irradiances of the background spectra used for both eyes. The subsequent rows show the power differences (e-h), and alpha-opic irradiances (i-l) relative to the background, averaged pupil diameter waveform (m-p) and Fourier spectra (q-t) for binocular stimulation. Column headings indicate the pathway stimulated, and shaded regions in panels m-t indicate bootstrapped 95\% confidence intervals.}\label{fig:spectraplots}
\end{figure}

Figure \ref{fig:CRFplots} shows contrast response functions across stimulation conditions for responses at the first harmonic (panels a-d) and the second harmonic (panels e-h) frequencies. In each plot, the response to monocular stimulation is given by the red circles and typically increases monotonically as a function of stimulus (temporal) contrast (main effects of stimulus contrast are significant for all data sets, see Supplementary Materials). Relative to monocular stimulation, binocular stimulation typically led to higher response amplitudes, indicating a binocular facilitation effect (main effects of condition are significant for all data sets, see Supplementary Materials). This is strongest for the luminance and S-cone conditions at the first harmonic (Figure \ref{fig:CRFplots}a,c) and the L-M cone and Melanopsin conditions at the second harmonic (Figure \ref{fig:CRFplots}f,h). One striking exception to this pattern is in the L-M cone condition at the first harmonic (Figure \ref{fig:CRFplots}b): this condition produced a binocular suppression effect, where the response to binocular stimulation is weaker than the response to monocular stimulation (blue squares below red circles). These results indicate that the magnitude of binocular facilitation differs across photoreceptor pathway, suggesting heterogeneity in the underlying neural computation.

\begin{figure}

{\centering \includegraphics{Figures/CRFs}

}

\caption{Contrast response functions for monocular (red circles), binocular (blue squares) and dichoptic (yellow diamonds) conditions, for stimulation of different pathways (columns) at the first and second harmonic frequencies (rows). Error bars indicate bootstrapped 95\% confidence intervals}\label{fig:CRFplots}
\end{figure}

In contemporary models of binocular signal combination, the amount of binocular facilitation is determined by the magnitude of interocular suppression, with strong suppression reducing facilitation (\protect\hyperlink{ref-Kingdom2015}{Kingdom and Libenson, 2015}). We can estimate the strength of interocular suppression by measuring how much monocular responses are reduced when a high contrast dichoptic mask is shown to the other eye. In our paradigm, this mask flickered at a lower frequency (0.4Hz) so that the two stimulus components remain distinct in the Fourier spectrum (e.g. \protect\hyperlink{ref-Busse2009}{Busse et al., 2009}). The yellow diamond symbols in Figure \ref{fig:CRFplots} show the target responses in this condition, and in most cases are weaker than the monocular responses (red circles). The strongest dichoptic masking is found in the first harmonic L-M condition, where we also observed the binocular suppression effect. We summarise this relationship by calculating an index for each effect, and show that the binocular facilitation effect is negatively correlated with the dichoptic masking effect (see Figure \ref{fig:suppressionfig}).

\begin{figure}

{\centering \includegraphics{Figures/suppressionfig}

}

\caption{P.}\label{fig:suppressionfig}
\end{figure}

Next, we fitted all 8 data sets using a Bayesian hierarchical implementation of a simple binocular combination model (\protect\hyperlink{ref-Meese2006}{Meese et al., 2006}; \protect\hyperlink{ref-Segala2023}{Segala et al., 2023}). Our primary interest was to compare posterior distributions of the weight of interocular suppression, which are showin in Figure \ref{fig:suppressionfig}. Consistent with our earlier observations, at the first harmonic the strongest suppressive weight corresponds to the L-M condition, and the weakest suppression corresponds to the luminance condition (also consistent with \protect\hyperlink{ref-Segala2023}{Segala et al., 2023}). The model fits were of good quality, as shown by the curves in Figure \ref{fig:CRFplots}. Further details of fitted parameters, and model behaviour in other empirical conditions are provided in the Supplementary Materials.

Finally, we inspected the response phase of our four stimulation conditions, given previous reports that these differ across pathways (\protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}), and may be in antiphase for melanopsin and S-cone signals. Figure \ref{fig:phaseplots} shows the phase angles for the first (a) and second (b) harmonic frequencies for binocular stimulation (monocular stimulation produced very similar results). At the first harmonic, melanopsin and S-cone signals differed in phase by more than 90 degrees, though they were not fully in antiphase. The luminance and L-M responses were more closely in antiphase to each other, however this is likely due to our choice to modulate L+M- in the first half-cycle (corresponding to a luminance increase in the luminance condition), and L-M+ in the second half-cycle (corresponding to a luminance decrease in the luminance condition). Had we reversed this phase arrangement, we would likely have seen a close phase correspondence between the L-M and luminance conditions. Phase differences between the luminance, S-cone and melanopsin conditions are likely attributable to different lags in phototransduction at the earliest stage (i.e.~in the retina). At the second harmonic frequency (Figure \ref{fig:phaseplots}b), the luminance condition was again out of phase with the other three, and was approximately in quadrature phase with the L-M condition, and in antiphase with both the S-cone and melanopsin conditions (which were in phase with each other).

\begin{figure}

{\centering \includegraphics{Figures/phaseplots}

}

\caption{Pupil phase plots at the first and second harmonic frequencies for the luminance, melanopsin, L-M pathway and the S-(L+M) pathway conditions Panel (a) shows the pupil response at the first harmonic frequency during binocular stimulation. Panel (b) shows the pupil response at the second harmonic frequency during binocular stimulation. In panel (a) the luminance amplitudes have been scaled down by a factor of 10 to be compared with the other conditions.}\label{fig:phaseplots}
\end{figure}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

We used pupillometry and silent substitution to measure monocular and binocular responses of the pupils to flickering stimuli when stimulating specific photoreceptor pathways. In our luminance experiment, we found that peripheral stimulation of the retina can elicit a pupillary response and we were also able to record a response at the second harmonic, which was not seen when we stimulated the fovea (\protect\hyperlink{ref-Segala2023}{Segala et al., 2023}). In all four experiments, we were able to record contrast response functions at both the first and the second harmonics. All experiments showed that binocular combination in the autonomic nervous system happens in a non-linear manner, with evidence of different magnitudes of interocular suppression depending on the photoreceptor pathway. This pattern of results was confirmed by a computational model, which allowed us to compare the weight of interocular suppression for each pathway. We found that, at the first harmonic frequency, the L-M pathway had a bigger suppression weight than the other pathways, while, at the second harmonic frequency, the S-(L+M) pathway had a bigger suppression weight. Finally, we looked at the pupil phases and observed different behaviours for the different pathways at the first and second harmonic frequencies. While the patterns differed between the first and second harmonics, within the same harmonic, whether the stimuli were presented monocularly or binocularly, the patterns were similar.

Our four experiments produced results that we were expecting based on our previous pupillometry findings (\protect\hyperlink{ref-Segala2023}{Segala et al., 2023}): the signals between the 2 pupils are combined non-linearly regardless of which photoreceptor pathway is being stimulated and whether the fovea or the periphery of the retina is being stimulated. We also observed responses at both the first and the second harmonic frequencies, which were expected based on previous literature (\protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}; \protect\hyperlink{ref-Stark1957}{Stark and Sherman, 1957}; \protect\hyperlink{ref-Verdon1988}{Verdon and Howarth, 1988}). There was, however, one aspect of our results that we were surprised to observe: the amplitude of this second harmonic response in the different photoreceptor pathways. It is true that we had already observed second harmonic responses when stimulating the periphery of the retina with achromatic luminance modulations flickering at 2 Hz (see Figure \ref{fig:appendixfig1}b), but the peak was very small when compared to the first harmonic peak, which is similar to what we observed in the luminance experiment here. On the other hand, in the melanopsin and L-M pathway experiments, the first and second harmonics are similar in amplitudes, and in the S-(L+M) pathway experiment, the peak of the second harmonic is even bigger than the peak of the first harmonic. One reason for why this might be happening may be because the driving signal is stronger when using a lower flicker frequency (indeed, pupillometry is more responsive to slow flicker frequencies of less than 1 Hz, \protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}) and when stimulating the periphery of the retina (we have a very clear waveform for the luminance experiment in Figure \ref{fig:pupildataLum}b). However, this explanation is not entirely satisfactory: we observed a second harmonic when stimulating the periphery using a higher flicker frequency and the pupil waveforms from the other three experiments are not as clear as the one from the luminance experiment. The presence of a second harmonic might indicate the existence of non-linearities that are not observable in the fovea: indeed, steady-state visual responses can contain activity beyond the first harmonic and these harmonics reflect non-linearities (e.g.~squaring, exponentiation, rectification) in the visual response (\protect\hyperlink{ref-Norcia2015}{Norcia et al., 2015}). Additionally, it can be the case that, when these non-linearities are strong, then the higher harmonics can have equal or even higher peaks than the first harmonic. Here, we did observe strong non-linearities in our photoreceptor pathways, as reflected by the interocular suppression weights that were output by our computational model. For the S-(L+M) pathway specifically, it seems that the higher peak of the second harmonic is a behaviour intrinsic to S cones, as this was observed previously (\protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}).

The pupil phases shown in Figure \ref{fig:phaseplots} give us more information about the pathways controlling the pupil response. The first thing that we notice is that the luminance and L-M pathway responses are in anti-phase. It is important to note that, for our L-M pathway stimulation, the stimulus flickered between magenta (first half of the cycle) and cyan (second half of the cycle), which means that the pupil was dilating during the magenta stimulation and then constricting during the cyan presentation. This seems to suggest that increments in magenta would correspond to decrements in brightness and increments in cyan would correspond to increments in brightness. It is possible that, if we had reversed the presentation cycle for the L-M pathway, the pupil response would have been in phase with the luminance responses. It has been recently shown that L-cone and melanopsin stimulation induce an opponent pupillary response to M- and S-cone stimulation (\protect\hyperlink{ref-Murray2018}{Murray et al., 2018}; \protect\hyperlink{ref-Woelders2018}{Woelders et al., 2018}). Our melanopsin and S-(L+M) results show a similar behaviour both for monocular and binocular responses. The L-M pathways results are desynchronised approximately in quadrature phase from the melanopsin and S-(L+M) results. These results also seem to align with what was previously found: combining L and M responses should display results that are between the opponency shown by the isolated cone stimulation. Additionally, this could explain the very strong suppression that binocular (L-M) stimulation displays compared to the monocular stimulation: if L and M produce pupil responses that are in anti-phase with each other, then combining the two together should elicit smaller responses. Finally, since the results from our experiments are not in phase, it would suggest that the photoreceptors control the pupil diameter through different pathways.

\hypertarget{conclusions}{%
\section{Conclusions}\label{conclusions}}

We have demonstrated that binocular combination of temporal flickering light in the autonomic nervous system depends on the photoreceptor pathway. We were able to elicit pupil responses by stimulating only the periphery of the retina and we were able to record contrast response functions for all photoreceptor pathways. While all pathways showed non-linear combination, they showed a variation in how the signals are combined, particularly in the weight of interocular suppression.

\hypertarget{materials-and-methods}{%
\section{Materials and methods}\label{materials-and-methods}}

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

Twenty-four participants were recruited for each of the four experiments for a total of ninety-six (68 females) adult participants, whose ages ranged from 18 to 41. All participants had normal or corrected to normal binocular vision and normal colour vision, and gave written informed consent. Our procedures were approved by the Ethics Committee of the Department of Psychology at the University of York (identification number 184).

\hypertarget{apparatus-stimuli}{%
\subsection{Apparatus \& stimuli}\label{apparatus-stimuli}}

To present synchronised stimulus modulations independently to each eye, two light engines, each with 10 independently addressable LED colour channels (SpectraTuneLAB: LEDMOTIVE Technologies, LLC, Barcelona, Spain), were integrated into a customised viewing system. The light engines were operated via a Python interface to their REST API (\protect\hyperlink{ref-Martin2022}{Martin et al., 2022}), which supports synchronous launch and playback of spectral sequences prepared in advance and stored in JSON format. When preparing the spectral sequences, the age of participants was recorded to account for the yellowing of the lenses. We calculated silent substitution solutions using the \emph{PySilSub} toolbox (\protect\hyperlink{ref-Martin2023}{Martin et al., 2023}), using linear algebra. The outputs of the two light engines (see Figure \ref{fig:spectraplots}b,c) were calibrated using an Ocean Optics Jaz spectroradiometer, which was wavelength-calibrated to an Argon lamp and intensity calibrated using a NIST-traceable light source. We used the Stockman and Sharpe (\protect\hyperlink{ref-Stockman2000}{2000}) 10-degree cone fundamentals, and estimates of melanopsin absorbance spectra from CIE S 026 (discussed in \protect\hyperlink{ref-Martin2023}{Martin et al., 2023}) to calculate \(\alpha\)-opic irradiance.

The output from the light engines was directed through liquid light guides (LLG3-8H: Thorlabs Ltd, Cambridgeshire, UK) and diffused onto semi-opaque and highly diffusive white glass discs with a diameter of 50 mm for even illumination (34-473: Edmund Optics, York, UK). The light guide gaskets were butt-coupled to the light engine diffusers with threaded adapters (SM1A9, AD3LLG: Thorlabs Ltd, Cambridgeshire, UK) and the exiting ends of the light guides were mated with 51 mm depth optical cylinders (SM2L20: Thorlabs Ltd, Cambridgeshire, UK) via appropriately threaded adapters (AD3LLG, SM2A6: Thorlabs Ltd, Cambridgeshire, UK). The stimulus diffuser discs were retained at the front end of the optical cylinders approximately 51 mm from the light source, at which distance the output beam was sufficiently dispersed to afford even illumination of the diffuser when viewed from the front. To guarantee safe illumination levels, a circular neutral-density filter with the same diameter of the white glass discs (50 mm) and an optical density of 0.6 log units was placed in the optical path between the light source and the diffusers. A small circular piece of blackout material with a diameter of approximately 8 degrees (10 mm) was positioned centrally on the front of each diffuser disc to aid as a fusion lock, as a fixation point, and to occlude the fovea.

The diffuser discs were positioned in the objective planes of the lenses of a modified VR headset (SHINECON SC-G01, Dongguan Shinecon Industrial Co.~Ltd., Guangdong, China), which was used by the participants to view the stimuli. The stimuli were two discs of flickering light with a diameter of approximately 30 degrees, which were fused together into a cyclopean percept resembling a donut-shaped ring of light, similar to that used in other studies (e.g., \protect\hyperlink{ref-Barrionuevo2016}{Barrionuevo and Cao, 2016}; \protect\hyperlink{ref-Murray2018}{Murray et al., 2018}; \protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}; \protect\hyperlink{ref-Zele2018}{Zele et al., 2018}). The VR headset modifications allowed for small adjustments to account for individual differences in interpupillary distance and focal length. The use of this set up allowed us to modulate the stimuli in three different ocular configurations, similar to the ones we used in our previous study (\protect\hyperlink{ref-Segala2023}{Segala et al., 2023}): monocular, binocular and dichoptic. In the monocular configuration, the unstimulated eye still saw a non-flickering disc of mean luminance. A schematic of the stimulation system is shown in Figure \ref{fig:spectraplots}a. Pupillometry data were collected using a binocular Pupil Core eye-tracker headset (Pupil Labs GmbH, Berlin, Germany, \protect\hyperlink{ref-Kassner2014}{Kassner et al., 2014}) running at 120 Hz, and the signals were recorded with the Pupil Capture software.

Our previous study (\protect\hyperlink{ref-Segala2023}{Segala et al., 2023}) used a temporal frequency of 2Hz for foveal luminance flicker, and recorded EEG data simultaneously with pupillometry. Initial pilot experiments indicated that this frequency was too high to elicit measurable responses when stimulating individual photoreceptor pathways. For all experiments, we therefore used a primary flicker frequency of 0.5Hz, as previous literature showed that it was slow enough to elicit a pupil response from all photoreceptor classes (\protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}). We also focussed on only recording pupillometry data as this frequency would be well below the minimum threshold to elicit steady-state EEG responses (\protect\hyperlink{ref-Norcia2015}{Norcia et al., 2015}).

For all experiments, sinusoidal temporal modulations were presented against the same background spectrum (matched between the eyes), which was used to achieve silent substitution in the three photoreceptor modulation experiments. The background spectra were defined by setting all channels to half maximum output for the brighter of the two devices (STLab 1, left eye) and then using the STLab 1/STLab 2 calibration ratio to find the equivalent settings for the companion device (STLab 2, right eye). The background spectrum illuminance was approximately 74 lux, or 62 cd/m\(^2\). The spectral power distributions and \(\alpha\)-opic irradiances of the background spectra for both eyes are shown in Figure \ref{fig:spectraplots}c-d.

In the luminance experiment, the stimulus intensity was increased and decreased relative to the background, which we expected to modulate all photoreceptor classes (see Figure \ref{fig:spectraplots}e,i). In the L-M cone modulation experiment, we used silent substution to increase the L-cone activity, and simultaneously decrease the M-cone activity, during the first half-cycle of the sine wave. In the second half-cycle the polarity of the modulation reversed (see Figure \ref{fig:spectraplots}f,j). The maximum available L-M contrast was approximately 10\%. In the S-cone modulation experiment, we increased and decreased S-cone-directed signals, whilst keeping activity in the other photoreceptors constant (see Figure \ref{fig:spectraplots}g,k). Our system allowed a maximum contrast of 45\%. Finally, in the melanopsin experiment, we modulated the activity of the melanopsin-containing intrinsically photoreceptive retinal ganglion cells, whilst keeping cone activity constant (see Figure \ref{fig:spectraplots}h,l). The maximum available melanopsin contrast was 22\%. We assume that the activity of rods was constant at the high background luminance intensity used here, and so did not attempt to silence rod activity in any condition, as this would have greatly reduced the available dynamic range. Splatter on nominally silenced photoreceptors was very small (see Figure \ref{fig:spectraplots}j-l), well below the levels that would be expected to generate measureable pupil modulations.

\hypertarget{procedure}{%
\subsection{Procedure}\label{procedure}}

Before the start of each experiment, participants adjusted the objective planes of the lenses with the help of the experimenter until the stimulus was in focus and they perceived the two pieces of blackout material as one fused disc. Pupil responses to binocular temporal contrast modulations were examined in a factorial design that combined six ocular conditions and five temporal contrast levels (6, 12, 24, 48 and 96\%) of the available dynamic range. This design, similar to that used in our previous studies (\protect\hyperlink{ref-Baker2020}{Baker et al., 2020}; \protect\hyperlink{ref-Baker2017}{Baker and Wade, 2017}; \protect\hyperlink{ref-Segala2023}{Segala et al., 2023}), was applied in four separate experiments, each with a different mode of photoreceptor stimulation. In the first three conditions, the discs flickered at 0.5 Hz, in either a monocular, binocular or dichoptic arrangement. In the dichoptic condition the non-target eye saw a flickering fixed contrast of 48\% of the available dynamic range. In the remaining three conditions (the cross-frequency conditions) one eye's disc flickered at 0.4 Hz, and the other eye's disc flickered at 0.5 Hz. We also tested monocular responses at 0.4 Hz, as well as binocular (one eye sees each frequency at the target contrast) and dichoptic (target stimulus flickering at 0.5 Hz, mask contrast of 48\% at 0.4 Hz in the other eye) arrangements. We counterbalanced presentation of the target stimulus across the left and right eyes.

The experiments were conducted in a windowless room, in which the only source of light was the modified VR headset. The participants sat as close as possible to the VR headset, leaving enough space for the eye-tracker to record the eyes. The experiment was carried out in a single session of around 45-60 minutes, divided into three blocks of 15-17 minutes each. In each block, there were a total of 60 trials lasting 15 seconds each (12s of stimulus presentation, followed by 3s of interstimulus interval). The participants were given no task other than look at the black fixation dot while trying to minimise their blinking during the presentation period. For all experiments other than the luminance condition, participants adapted to the mean luminance for two minutes before stimulation began.

Before the start of the L-M experiment, participants completed a luminance nulling perceptual calibration procedure in L-M cone space on an Iiyama \(\textrm{VisionMaster}^{\textrm{TM}}\) Pro 510 display (800 x 600 pixels, 60 Hz refresh rate). During the task, participants were presented with a disc flickering within the L-M cone space (between magenta and cyan). Using a trackball, participants adjusted the angle in cone space to find their subjective isoluminant point, which resulted in changing the flickering intensity of the stimulus until the amplitude of the flicker appeared to be minimised. The result was used to modify the requested contrasts during stimulus preparation so as to account for individual differences affecting perceived illuminance, principally the L:M cone ratio (\protect\hyperlink{ref-Carroll2002}{Carroll et al., 2002}; \protect\hyperlink{ref-Hofer2005}{Hofer et al., 2005}).

\hypertarget{data-analysis}{%
\subsection{Data analysis}\label{data-analysis}}

The pupillometry data were analysed using the same method we used in our previous study (\protect\hyperlink{ref-Segala2023}{Segala et al., 2023}). The data were converted from mp4 videos to a csv text file using the Pupil Player software (\protect\hyperlink{ref-Kassner2014}{Kassner et al., 2014}), which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball. The individual data were then loaded into R for analysis, where a ten-second waveform for each trial in each eye was extracted (excluding the first two seconds after stimulus onset). We interpolated across any dropped or missing frames to ensure regular and continuous sampling over time. The Fourier transform was calculated for each waveform, and all repetitions of each condition were pooled across eye and then averaged. Finally, data were averaged across all participants to obtain the group results. We used coherent averaging and at each stage we excluded data points with a Mahalanobis distance exceeding \(D\) = 3 from the complex-valued mean (\protect\hyperlink{ref-Baker2021}{Baker, 2021}). For monocular stimulation, we confirmed that the consensual response was equivalent to the response in the stimulated eye.

For all experiments, we used a bootstrapping procedure with 1000 iterations to estimate standard errors across participants. All analysis and figure construction was conducted using a single R-script, available online, making this study fully computationally reproducible: \url{https://osf.io/gdvt4/}.

\hypertarget{computational-model-and-parameter-estimation}{%
\subsection{Computational model and parameter estimation}\label{computational-model-and-parameter-estimation}}

To describe our data, we chose the same model described in our previous study (\protect\hyperlink{ref-Segala2023}{Segala et al., 2023}). The model has the same general form as the first stage of the contrast gain control model proposed by Meese et al. (\protect\hyperlink{ref-Meese2006}{2006}) and omits the second stage. For the previous model that we used (\protect\hyperlink{ref-Segala2023}{Segala et al., 2023}), the exponent of the numerator and denominator had fixed values of 2 and (implicitly) 1. Here, we allow these parameters (called \emph{p} and \emph{q}) to be free, in order to permit different shapes of contrast response function, e.g.~saturating or super-saturating. The responses of the left eye and right eye channels are as follows:

\begin{equation}
\label{eq:respLchap4}
Resp_L = \frac{L^p}{Z + L^q + wR^q},
\end{equation}

\begin{equation}
\label{eq:respRchap4}
Resp_R = \frac{R^p}{Z + R^q + wL^q},
\end{equation}

\noindent where \emph{L} and \emph{R} are the contrast signals from the left and right eyes, \emph{p} and \emph{q} are exponents, \emph{Z} is a saturation constant that shifts the contrast-response function laterally, and \emph{w} is the weight of suppression from the other eye.

The responses from the two eyes are then summed binocularly:

\begin{equation}
\label{eq:respBchap4}
Resp_B = R_{max}(Resp_L + Resp_R) + k,
\end{equation}

\noindent where \emph{k} is a noise parameter, and \(R_{max}\) scales the overall response amplitude.

We performed model fitting on the normalised amplitudes to account for amplitude differences between the experiments. The models were fit using a hierarchical Bayesian framework implemented in Stan (\protect\hyperlink{ref-Carpenter2017}{Carpenter et al., 2017}). The data for each photoreceptor type and response frequency was fit separately, for a total of 8 model fits. The prior

\hypertarget{acknowledgements-and-funding-sources}{%
\section{Acknowledgements and funding sources}\label{acknowledgements-and-funding-sources}}

Supported by Biotechnology and Biological Sciences Research Council grant BB/V007580/1 awarded to DHB and ARW.

\hypertarget{references}{%
\section{References}\label{references}}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-Baker2021}{}}%
Baker DH. 2021. Statistical analysis of periodic data in neuroscience. \emph{Neurons, Behavior, Data analysis, and Theory} \textbf{5}. doi:\href{https://doi.org/10.51628/001c.27680}{10.51628/001c.27680}

\leavevmode\vadjust pre{\hypertarget{ref-Baker2018}{}}%
Baker DH, Lygo FA, Meese TS, Georgeson MA. 2018. Binocular summation revisited: Beyond \(\sqrt{2}\). \emph{Psychol Bull} \textbf{144}:1186--1199. doi:\href{https://doi.org/10.1037/bul0000163}{10.1037/bul0000163}

\leavevmode\vadjust pre{\hypertarget{ref-Baker2007}{}}%
Baker DH, Meese TS, Georgeson MA. 2007. Binocular interaction: Contrast matching and contrast discrimination are predicted by the same model. \emph{Spat Vis} \textbf{20}:397--413. doi:\href{https://doi.org/10.1163/156856807781503622}{10.1163/156856807781503622}

\leavevmode\vadjust pre{\hypertarget{ref-Baker2020}{}}%
Baker DH, Vilidaite G, McClarnon E, Valkova E, Bruno A, Millman RE. 2020. Binaural summation of amplitude modulation involves weak interaural suppression. \emph{Sci Rep} \textbf{10}:3560. doi:\href{https://doi.org/10.1038/s41598-020-60602-5}{10.1038/s41598-020-60602-5}

\leavevmode\vadjust pre{\hypertarget{ref-Baker2017}{}}%
Baker DH, Wade AR. 2017. Evidence for an optimal algorithm underlying signal combination in human visual cortex. \emph{Cereb Cortex} \textbf{27}:254--264. doi:\href{https://doi.org/10.1093/cercor/bhw395}{10.1093/cercor/bhw395}

\leavevmode\vadjust pre{\hypertarget{ref-Barrionuevo2016}{}}%
Barrionuevo PA, Cao D. 2016. Luminance and chromatic signals interact differently with melanopsin activation to control the pupil light response. \emph{Journal of Vision} \textbf{16(11)}:29. doi:\href{https://doi.org/10.1167/16.11.29}{10.1167/16.11.29}

\leavevmode\vadjust pre{\hypertarget{ref-Barrionuevo2018}{}}%
Barrionuevo PA, McAnany JJ, Zele AJ, Cao D. 2018. \href{https://www.frontiersin.org/articles/10.3389/fneur.2018.01140}{Non-linearities in the {Rod} and {Cone} {Photoreceptor} {Inputs} to the {Afferent} {Pupil} {Light} {Response}}. \emph{Frontiers in Neurology} \textbf{9}.

\leavevmode\vadjust pre{\hypertarget{ref-Barrionuevo2014}{}}%
Barrionuevo PA, Nicandro N, McAnany JJ, Zele AJ, Gamlin P, Cao D. 2014. Assessing rod, cone, and melanopsin contributions to human pupil flicker responses. \emph{Investigative Ophthalmology \& Visual Science} \textbf{55}:719--27. doi:\href{https://doi.org/10.1167/iovs.13-13252}{10.1167/iovs.13-13252}

\leavevmode\vadjust pre{\hypertarget{ref-Busse2009}{}}%
Busse L, Wade AR, Carandini M. 2009. Representation of concurrent stimuli by population activity in visual cortex. \emph{Neuron} \textbf{64}:931--42. doi:\href{https://doi.org/10.1016/j.neuron.2009.11.004}{10.1016/j.neuron.2009.11.004}

\leavevmode\vadjust pre{\hypertarget{ref-Campbell1965}{}}%
Campbell FW, Green DG. 1965. Monocular versus binocular visual acuity. \emph{Nature} \textbf{208}:191--2. doi:\href{https://doi.org/10.1038/208191a0}{10.1038/208191a0}

\leavevmode\vadjust pre{\hypertarget{ref-Cao2015}{}}%
Cao D, Nicandro N, Barrionuevo PA. 2015. A five-primary photostimulator suitable for studying intrinsically photosensitive retinal ganglion cell functions in humans. \emph{Journal of Vision} \textbf{15}:27. doi:\href{https://doi.org/10.1167/15.1.27}{10.1167/15.1.27}

\leavevmode\vadjust pre{\hypertarget{ref-Carpenter2017}{}}%
Carpenter B, Gelman A, Hoffman MD, Lee D, Goodrich B, Betancourt M, Brubaker MA, Guo J, Li P, Riddell A. 2017. Stan: A probabilistic programming language. \emph{J Stat Softw} \textbf{76}. doi:\href{https://doi.org/10.18637/jss.v076.i01}{10.18637/jss.v076.i01}

\leavevmode\vadjust pre{\hypertarget{ref-Carroll2002}{}}%
Carroll J, Neitz J, Neitz M. 2002. Estimates of {L}:{M} cone ratio from {ERG} flicker photometry and genetics. \emph{Journal of Vision} \textbf{2}:1. doi:\href{https://doi.org/10.1167/2.8.1}{10.1167/2.8.1}

\leavevmode\vadjust pre{\hypertarget{ref-Dacey2005}{}}%
Dacey DM, Liao H-W, Peterson BB, Robinson FR, Smith VC, Pokorny J, Yau K-W, Gamlin PD. 2005. Melanopsin-expressing ganglion cells in primate retina signal colour and irradiance and project to the {LGN}. \emph{Nature} \textbf{433}:749--754. doi:\href{https://doi.org/10.1038/nature03387}{10.1038/nature03387}

\leavevmode\vadjust pre{\hypertarget{ref-Dacey2003}{}}%
Dacey DM, Peterson BB, Robinson FR, Gamlin PD. 2003. Fireworks in the primate retina: In vitro photodynamics reveals diverse LGN-projecting ganglion cell types. \emph{Neuron} \textbf{37}:15--27. doi:\url{https://doi.org/10.1016/S0896-6273(02)01143-1}

\leavevmode\vadjust pre{\hypertarget{ref-Ding2006}{}}%
Ding J, Sperling G. 2006. A gain-control theory of binocular combination. \emph{Proc Natl Acad Sci U S A} \textbf{103}:1141--6. doi:\href{https://doi.org/10.1073/pnas.0509629103}{10.1073/pnas.0509629103}

\leavevmode\vadjust pre{\hypertarget{ref-Estevez1982}{}}%
Estévez O, Spekreijse H. 1982. The "silent substitution" method in visual research. \emph{Vision Research} \textbf{22}:681--691. doi:\href{https://doi.org/10.1016/0042-6989(82)90104-3}{10.1016/0042-6989(82)90104-3}

\leavevmode\vadjust pre{\hypertarget{ref-Gamlin2007}{}}%
Gamlin PDR, McDougal DH, Pokorny J, Smith VC, Yau K-W, Dacey DM. 2007. Human and macaque pupil responses driven by melanopsin-containing retinal ganglion cells. \emph{Vision Research} \textbf{47}:946--954. doi:\href{https://doi.org/10.1016/j.visres.2006.12.015}{10.1016/j.visres.2006.12.015}

\leavevmode\vadjust pre{\hypertarget{ref-Hofer2005}{}}%
Hofer H, Carroll J, Neitz J, Neitz M, Williams DR. 2005. Organization of the human trichromatic cone mosaic. \emph{The Journal of Neuroscience} \textbf{25}:9669--9679. doi:\href{https://doi.org/10.1523/jneurosci.2414-05.2005}{10.1523/jneurosci.2414-05.2005}

\leavevmode\vadjust pre{\hypertarget{ref-Hubel1962}{}}%
Hubel DH, Wiesel TN. 1962. Receptive fields, binocular interaction and functional architecture in the cat's visual cortex. \emph{J Physiol} \textbf{160}:106--54. doi:\href{https://doi.org/10.1113/jphysiol.1962.sp006837}{10.1113/jphysiol.1962.sp006837}

\leavevmode\vadjust pre{\hypertarget{ref-Kassner2014}{}}%
Kassner M, Patera W, Bulling A. 2014. Pupil: An open source platform for pervasive eye tracking and mobile gaze-based interaction.Proceedings of the 2014 {ACM} International Joint Conference on Pervasive and Ubiquitous Computing: Adjunct Publication. {ACM}. doi:\href{https://doi.org/10.1145/2638728.2641695}{10.1145/2638728.2641695}

\leavevmode\vadjust pre{\hypertarget{ref-Kingdom2015}{}}%
Kingdom FAA, Libenson L. 2015. Dichoptic color saturation mixture: Binocular luminance contrast promotes perceptual averaging. \emph{J Vis} \textbf{15}:2. doi:\href{https://doi.org/10.1167/15.5.2}{10.1167/15.5.2}

\leavevmode\vadjust pre{\hypertarget{ref-Legge1984}{}}%
Legge GE. 1984. Binocular contrast summation--II. Quadratic summation. \emph{Vision Res} \textbf{24}:385--94. doi:\href{https://doi.org/10.1016/0042-6989(84)90064-6}{10.1016/0042-6989(84)90064-6}

\leavevmode\vadjust pre{\hypertarget{ref-Lucas2003}{}}%
Lucas RJ, Hattar S, Takao M, Berson DM, Foster RG, Yau K-W. 2003. Diminished pupillary light reflex at high irradiances in melanopsin-knockout mice. \emph{Science} \textbf{299}:245--247. doi:\href{https://doi.org/10.1126/science.1077293}{10.1126/science.1077293}

\leavevmode\vadjust pre{\hypertarget{ref-Markwell2010}{}}%
Markwell EL, Feigl B, Zele AJ. 2010. Intrinsically photosensitive melanopsin retinal ganglion cell contributions to the pupillary light reflex and circadian rhythm. \emph{Clinical and Experimental Optometry} \textbf{93}:137--149. doi:\href{https://doi.org/10.1111/j.1444-0938.2010.00479.x}{10.1111/j.1444-0938.2010.00479.x}

\leavevmode\vadjust pre{\hypertarget{ref-Martin2023}{}}%
Martin JT, Boynton GM, Baker DH, Wade AR, Spitschan M. 2023. PySilSub: An open-source python toolbox for implementing the method of silent substitution in vision and nonvisual photoreception research. \emph{Journal of Vision} \textbf{23}:10. doi:\href{https://doi.org/10.1167/jov.23.7.10}{10.1167/jov.23.7.10}

\leavevmode\vadjust pre{\hypertarget{ref-Martin2022}{}}%
Martin JT, Pinto J, Bulte D, Spitschan M. 2022. PyPlr: A versatile, integrated system of hardware and software for researching the human pupillary light reflex. \emph{Behavior Research Methods} \textbf{54}:2720--2739. doi:\href{https://doi.org/10.3758/s13428-021-01759-3}{10.3758/s13428-021-01759-3}

\leavevmode\vadjust pre{\hypertarget{ref-Mathot2018}{}}%
Mathôt S. 2018. Pupillometry: Psychology, physiology, and function. \emph{J Cogn} \textbf{1}:16. doi:\href{https://doi.org/10.5334/joc.18}{10.5334/joc.18}

\leavevmode\vadjust pre{\hypertarget{ref-McDougal2015}{}}%
McDougal DH, Gamlin PD. 2015. Autonomic control of the eye. \emph{Comprehensive Physiology} \textbf{5}:439--473. doi:\href{https://doi.org/10.1002/cphy.c140014}{10.1002/cphy.c140014}

\leavevmode\vadjust pre{\hypertarget{ref-McDougal2010}{}}%
McDougal DH, Gamlin PD. 2010. The influence of intrinsically-photosensitive retinal ganglion cells on the spectral sensitivity and response dynamics of the human pupillary light reflex. \emph{Vision Research} \textbf{50}:72--87. doi:\href{https://doi.org/10.1016/j.visres.2009.10.012}{10.1016/j.visres.2009.10.012}

\leavevmode\vadjust pre{\hypertarget{ref-McDougal2008}{}}%
McDougal DH, Gamlin PD. 2008. Pupillary control pathways.The Senses: A Comprehensive Reference. Elsevier. pp. 521--536.

\leavevmode\vadjust pre{\hypertarget{ref-Meese2006}{}}%
Meese TS, Georgeson MA, Baker DH. 2006. Binocular contrast vision at and above threshold. \emph{Journal of Vision} \textbf{6}:1224--43. doi:\href{https://doi.org/10.1167/6.11.7}{10.1167/6.11.7}

\leavevmode\vadjust pre{\hypertarget{ref-Moradi2009}{}}%
Moradi F, Heeger DJ. 2009. Inter-ocular contrast normalization in human visual cortex. \emph{J Vis} \textbf{9}:13.1--22. doi:\href{https://doi.org/10.1167/9.3.13}{10.1167/9.3.13}

\leavevmode\vadjust pre{\hypertarget{ref-Murray2018}{}}%
Murray IJ, Kremers J, McKeefry D, Parry NRA. 2018. Paradoxical pupil responses to isolated {M}-cone increments. \emph{Journal of the Optical Society of America A} \textbf{35}:B66--B71. doi:\href{https://doi.org/10.1364/JOSAA.35.000B66}{10.1364/JOSAA.35.000B66}

\leavevmode\vadjust pre{\hypertarget{ref-Norcia2015}{}}%
Norcia AM, Appelbaum LG, Ales JM, Cottereau BR, Rossion B. 2015. The steady-state visual evoked potential in vision research: A review. \emph{Journal of Vision} \textbf{15(6)}:4. doi:\href{https://doi.org/10.1167/15.6.4}{10.1167/15.6.4}

\leavevmode\vadjust pre{\hypertarget{ref-Panda2002}{}}%
Panda S, Sato TK, Castrucci AM, Rollag MD, DeGrip WJ, Hogenesch JB, Provencio I, Kay SA. 2002. Melanopsin (Opn4) requirement for normal light-induced circadian phase shifting. \emph{Science} \textbf{298}:2213--2216. doi:\href{https://doi.org/10.1126/science.1076848}{10.1126/science.1076848}

\leavevmode\vadjust pre{\hypertarget{ref-Provencio2000}{}}%
Provencio I, Rodriguez IR, Jiang G, Hayes WP, Moreira EF, Rollag MD. 2000. A {Novel} {Human} {Opsin} in the {Inner} {Retina}. \emph{Journal of Neuroscience} \textbf{20}:600--605. doi:\href{https://doi.org/10.1523/JNEUROSCI.20-02-00600.2000}{10.1523/JNEUROSCI.20-02-00600.2000}

\leavevmode\vadjust pre{\hypertarget{ref-Ruby2002}{}}%
Ruby NF, Brennan TJ, Xie X, Cao V, Franken P, Heller HC, O'Hara BF. 2002. Role of melanopsin in circadian responses to light. \emph{Science} \textbf{298}:2211--2213. doi:\href{https://doi.org/10.1126/science.1076701}{10.1126/science.1076701}

\leavevmode\vadjust pre{\hypertarget{ref-Segala2023}{}}%
Segala FG, Bruno A, Martin JT, Aung MT, Wade AR, Baker DH. 2023. Different rules for binocular combination of luminance flicker in cortical and subcortical pathways. \emph{eLife} \textbf{12}. doi:\href{https://doi.org/10.7554/elife.87048}{10.7554/elife.87048}

\leavevmode\vadjust pre{\hypertarget{ref-Shapiro1996}{}}%
Shapiro AG, Pokorny J, Smith VC. 1996. Cone{\textendash}rod receptor spaces with illustrations that use {CRT} phosphor and light-emitting-diode spectra. \emph{Journal of the Optical Society of America A} \textbf{13}:2319. doi:\href{https://doi.org/10.1364/josaa.13.002319}{10.1364/josaa.13.002319}

\leavevmode\vadjust pre{\hypertarget{ref-Spitschan2019}{}}%
Spitschan M. 2019. Photoreceptor inputs to pupil control. \emph{Journal of Vision} \textbf{19}:5. doi:\href{https://doi.org/10.1167/19.9.5}{10.1167/19.9.5}

\leavevmode\vadjust pre{\hypertarget{ref-Spitschan2014}{}}%
Spitschan M, Jain S, Brainard DH, Aguirre GK. 2014. Opponent melanopsin and s-cone signals in the human pupillary light response. \emph{Proceedings of the National Academy of Sciences} \textbf{111}:15568--15572. doi:\href{https://doi.org/10.1073/pnas.1400942111}{10.1073/pnas.1400942111}

\leavevmode\vadjust pre{\hypertarget{ref-Spitschan2018}{}}%
Spitschan M, Woelders T. 2018. \href{https://www.frontiersin.org/articles/10.3389/fneur.2018.00941}{The {Method} of {Silent} {Substitution} for {Examining} {Melanopsin} {Contributions} to {Pupil} {Control}}. \emph{Frontiers in Neurology} \textbf{9}.

\leavevmode\vadjust pre{\hypertarget{ref-Stark1957}{}}%
Stark L, Sherman PM. 1957. A servoanalytic study of consensual pupil reflex to light. \emph{Journal of Neurophysiology} \textbf{20}:17--26. doi:\href{https://doi.org/10.1152/jn.1957.20.1.17}{10.1152/jn.1957.20.1.17}

\leavevmode\vadjust pre{\hypertarget{ref-Stockman2000}{}}%
Stockman A, Sharpe LT. 2000. The spectral sensitivities of the middle- and long-wavelength-sensitive cones derived from measurements in observers of known genotype. \emph{Vision Res} \textbf{40}:1711--37. doi:\href{https://doi.org/10.1016/s0042-6989(00)00021-3}{10.1016/s0042-6989(00)00021-3}

\leavevmode\vadjust pre{\hypertarget{ref-Verdon1988}{}}%
Verdon W, Howarth PA. 1988. The pupil's response to short wavelength cone stimulation. \emph{Vision research} \textbf{28}:1119--1128. doi:\href{https://doi.org/10.1016/0042-6989(88)90138-1}{10.1016/0042-6989(88)90138-1}

\leavevmode\vadjust pre{\hypertarget{ref-Wang2015}{}}%
Wang C-A, Munoz DP. 2015. A circuit for pupil orienting responses: Implications for cognitive modulation of pupil size. \emph{Curr Opin Neurobiol} \textbf{33}:134--40. doi:\href{https://doi.org/10.1016/j.conb.2015.03.018}{10.1016/j.conb.2015.03.018}

\leavevmode\vadjust pre{\hypertarget{ref-Woelders2018}{}}%
Woelders T, Leenheers T, Gordijn MCM, Hut RA, Beersma DGM, Wams EJ. 2018. Melanopsin- and {L}-cone--induced pupil constriction is inhibited by {S}- and {M}-cones in humans. \emph{Proceedings of the National Academy of Sciences} \textbf{115}:792--797. doi:\href{https://doi.org/10.1073/pnas.1716281115}{10.1073/pnas.1716281115}

\leavevmode\vadjust pre{\hypertarget{ref-Wyatt1981}{}}%
Wyatt HJ, Musselman JF. 1981. Pupillary light reflex in humans: Evidence for an unbalanced pathway from nasal retina, and for signal cancellation in brainstem. \emph{Vision Res} \textbf{21}:513--25. doi:\href{https://doi.org/10.1016/0042-6989(81)90097-3}{10.1016/0042-6989(81)90097-3}

\leavevmode\vadjust pre{\hypertarget{ref-Zele2018}{}}%
Zele AJ, Feigl B, Adhikari P, Maynard ML, Cao D. 2018. Melanopsin photoreception contributes to human visual detection, temporal and colour processing. \emph{Scientific Reports} \textbf{8}. doi:\href{https://doi.org/10.1038/s41598-018-22197-w}{10.1038/s41598-018-22197-w}

\end{CSLReferences}

\hypertarget{supplementary-materials}{%
\section{Supplementary Materials}\label{supplementary-materials}}

\begin{table}

\caption{\label{tab:paramtable1F}Summary of median parameter values at the first harmonic frequency.}
\centering
\begin{tabular}[t]{l|c|c|c|c|c|c}
\hline
Experiment & Z & k & w & p & q & Rmax\\
\hline
Luminance 1F & 96.61 & 0 & 0.37 & 1.34 & 1.28 & 0.08258\\
\hline
Melanopsin 1F & 72.80 & 0 & 1.62 & 1.18 & 0.64 & 0.00259\\
\hline
L-M 1F & 62.89 & 0 & 1.52 & 1.54 & 1.28 & 0.00287\\
\hline
S 1F & 61.56 & 0 & 1.40 & 0.41 & 1.08 & 0.04916\\
\hline
\end{tabular}
\end{table}

\begin{table}

\caption{\label{tab:paramtable2F}Summary of median parameter values at the second harmonic frequency.}
\centering
\begin{tabular}[t]{l|c|c|c|c|c|c}
\hline
Experiment & Z & k & w & p & q & Rmax\\
\hline
Luminance 2F & 63.38 & 0 & 1.17 & 1.17 & 0.94 & 0.00652\\
\hline
Melanopsin 2F & 68.76 & 0 & 1.40 & 0.88 & 0.50 & 0.00368\\
\hline
L-M 2F & 74.12 & 0 & 0.85 & 1.19 & 0.85 & 0.00472\\
\hline
S 2F & 77.31 & 0 & 1.91 & 1.36 & 0.77 & 0.00211\\
\hline
\end{tabular}
\end{table}

\end{document}

### 2024-04-28 manuscript.Rmd
Updated the luminance of the background
Synchronising

@@
 
-processdata <- 1  # this flag determines the amount of processing, with 4 levels:
+processdata <- 3  # this flag determines the amount of processing, with 4 levels:
 # 0 - do no processing, generate the pdf using existing versions of all figures
@@
 
-if (processdata > 0){
-
-pdf(paste(figdir,"modelfigurechap4.pdf",sep=''), bg="transparent", height = 10, width = 25)
-
-par(mfrow=c(2,5))
-
-load(file=paste0(datadir,'AveragedataLum.RData'))
-
-contrastsfinedB <- 2:40
-
-params <- c(pupilRmaxLum,pupilPLum,pupilZLum,pupilWLum,pupilKLum,pupilQLum)
-modresps <- getmodresps(params)
-
-plotlims <- c(15,40,0,1)
-ticklocsx <- contrastsdB    # locations of tick marks on x axis
-ticklocsy <- seq(0,1,0.2)
-ticklabelsx <-c(6,12,24,48,96)        # set labels for x ticks
-ticklabelsy <- ticklocsy
-
-par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2)     # add the tick labels
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
-title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
-title(ylab="Relative amplitude at 0.5Hz", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
-title(main='Luminance 1F',cex.main=2)
-
-for (cond in 1:3){
-  lines(contrastsfinedB,modresps[cond,], col=colpal[cond], lwd=3, cex=0.5)
-  points(contrastsdB,abs(cleanmeansP[cond,])/abs(cleanmeansP[2,5]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
-}  
-  lines(contrastsfinedB,modresps[4,], col=colpal[6], lwd=3, cex=0.5)
-  points(contrastsdB,abs(cleanmeansP[6,])/abs(cleanmeansP[2,5]), pch = 25, col='black', bg=colpal[6], cex=1.6, lwd=3)   # draw the data points themselves
-
-legend(22,1,c('Monocular','Binocular','Dichoptic','Dichoptic cross'),pch=c(21:23,25),pt.bg=colpal[c(1:3,6)],pt.lwd=3,cex=1.5,pt.cex=1.6,box.lwd=2)
-text(17,0.95,'(a)',adj=0.5,cex=2.5)
-
-load(file=paste0(datadir,'AveragedataMel.RData'))
-
-params <- c(pupilRmaxMel,pupilPMel,pupilZMel,pupilWMel,pupilKMel,pupilQMel)
-modresps <- getmodresps(params)
-
-plotlims <- c(15,40,0,1)
-ticklocsx <- contrastsdB    # locations of tick marks on x axis
-ticklocsy <- seq(0,1,0.2)
-ticklabelsx <-c(6,12,24,48,96)        # set labels for x ticks
-ticklabelsy <- ticklocsy
-
-par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2)     # add the tick labels
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
-title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
-title(ylab="Relative amplitude at 0.5Hz", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
-title(main='Melanopsin 1F',cex.main=2)
-
-for (cond in 1:3){
-  lines(contrastsfinedB,modresps[cond,], col=colpal[cond], lwd=3, cex=0.5)
-  points(contrastsdB,abs(cleanmeansP[cond,])/abs(cleanmeansP[2,5]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
-}  
-  lines(contrastsfinedB,modresps[4,], col=colpal[6], lwd=3, cex=0.5)
-  points(contrastsdB,abs(cleanmeansP[6,])/abs(cleanmeansP[2,5]), pch = 25, col='black', bg=colpal[6], cex=1.6, lwd=3)   # draw the data points themselves
-
-text(17,0.95,'(b)',adj=0.5,cex=2.5)
-
-load(file=paste0(datadir,'AveragedataLM.RData'))
-
-params <- c(pupilRmaxLM,pupilPLM,pupilZLM,pupilWLM,pupilKLM,pupilQLM)
-modresps <- getmodresps(params)
-
-par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2)     # add the tick labels
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
-title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
-title(ylab="Relative amplitude at 0.5Hz", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
-title(main='L-M cones 1F',cex.main=2)
-
-for (cond in 1:3){
-  lines(contrastsfinedB,modresps[cond,], col=colpal[cond], lwd=3, cex=0.5)
-  points(contrastsdB,abs(cleanmeansP[cond,])/abs(cleanmeansP[2,5]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
-}  
-  lines(contrastsfinedB,modresps[4,], col=colpal[6], lwd=3, cex=0.5)
-  points(contrastsdB,abs(cleanmeansP[6,])/abs(cleanmeansP[2,5]), pch = 25, col='black', bg=colpal[6], cex=1.6, lwd=3)   # draw the data points themselves
-
-text(17,0.95,'(c)',adj=0.5,cex=2.5)
-
-load(file=paste0(datadir,'AveragedataS.RData'))
-
-params <- c(pupilRmaxS,pupilPS,pupilZS,pupilWS,pupilKS,pupilQS)
-modresps <- getmodresps(params)
-
-par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2)     # add the tick labels
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
-title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
-title(ylab="Relative amplitude at 0.5Hz", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
-title(main='S cones 1F',cex.main=2)
-
-for (cond in 1:3){
-  lines(contrastsfinedB,modresps[cond,], col=colpal[cond], lwd=3, cex=0.5)
-  points(contrastsdB,abs(cleanmeansP[cond,])/abs(cleanmeansP[2,5]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
-}  
-  lines(contrastsfinedB,modresps[4,], col=colpal[6], lwd=3, cex=0.5)
-  points(contrastsdB,abs(cleanmeansP[6,])/abs(cleanmeansP[2,5]), pch = 25, col='black', bg=colpal[6], cex=1.6, lwd=3)   # draw the data points themselves
-
-text(17,0.95,'(d)',adj=0.5,cex=2.5)
-
-# pdf(paste(figdir,"posteriors1F.pdf",sep=''), bg="transparent", height = 5.5, width = 5.5)
-
-plotlims <- c(-24,12,0,0.6) 
-ticklocsx <- seq(-24,12,12)    
-ticklocsy <- seq(0,0.6,0.1)    
-ticklabelsx <- c('1/16','1/4','1','4')        
-ticklabelsy <- ticklocsy    # set labels for y ticks
-
-par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2)    
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
-
-title(xlab="w", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
-title(ylab="Probability", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
-title(main='Suppression 1F',cex.main=2)
-
-a <- density(20*log10(pupilweightpopLum),from=-48,to=12)   
-polygon(c(-48,a$x,12), c(0,a$y,0), col=addalpha(colpalmod[1],0.5),border=NA)
-
-a <- density(20*log10(pupilweightpopMel),from=-48,to=12)   
-polygon(c(-48,a$x,12), c(0,a$y,0), col=addalpha(colpalmod[2],0.5),border=NA)
-
-a<- density(20*log10(pupilweightpopLM),from=-48,to=12)   
-polygon(c(-48,a$x,12), c(0,a$y,0), col=addalpha(colpalmod[3],0.5),border=NA)
-
-a <- density(20*log10(pupilweightpopS),from=-48,to=12)   
-polygon(c(-48,a$x,12), c(0,a$y,0), col=addalpha(colpalmod[4],0.5),border=NA)
-
-prior <- dnorm(10^((-48:12)/20),1,0.5)
-prior <- 0.5*prior/max(prior)
-lines(-48:12,prior)
-
-lines(20*log10(c(mean(pupilWLum),mean(pupilWLum))),c(0,0.6),lwd=3,col=colpalmod[1])
-lines(20*log10(c(mean(pupilWMel),mean(pupilWMel))),c(0,0.6),lwd=3,col=colpalmod[2])
-lines(20*log10(c(mean(pupilWLM),mean(pupilWLM))),c(0,0.6),lwd=3,col=colpalmod[3])
-lines(20*log10(c(mean(pupilWS),mean(pupilWS))),c(0,0.6),lwd=3,col=colpalmod[4])
-
-legend(-24,0.6,c('Prior','Lum 1F', 'Mel 1F', 'LM 1F', 'S 1F'),col=c('black',colpalmod[1:4]),lwd=c(1,3,3,3,3),lty=1, cex=1.5, box.lwd=2, bg='white')
-
-text(10,0.58,'(e)',adj=0.5,cex=2.5)
-
-# dev.off()
-# 
-# pdf(paste(figdir,"posteriors2F.pdf",sep=''), bg="transparent", height = 5.5, width = 5.5)
-
-load(file=paste0(datadir,'AveragedataLum.RData'))
-
-contrastsfinedB <- 2:40
-
-params <- c(pupilRmaxLum2,pupilPLum2,pupilZLum2,pupilWLum2,pupilKLum2,pupilQLum2)
-modresps <- getmodresps(params)
-
-plotlims <- c(15,40,0,1)
-ticklocsx <- contrastsdB    # locations of tick marks on x axis
-ticklocsy <- seq(0,1,0.2)
-ticklabelsx <-c(6,12,24,48,96)        # set labels for x ticks
-ticklabelsy <- ticklocsy
-
-par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2)     # add the tick labels
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
-title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
-title(ylab="Relative amplitude at 1Hz", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
-title(main='Luminance 2F',cex.main=2)
-
-for (cond in 1:3){
-  lines(contrastsfinedB,modresps[cond,], col=colpal[cond], lwd=3, cex=0.5)
-  points(contrastsdB,abs(cleanmeansP2[cond,])/abs(cleanmeansP2[2,5]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
-}  
-  lines(contrastsfinedB,modresps[4,], col=colpal[6], lwd=3, cex=0.5)
-  points(contrastsdB,abs(cleanmeansP2[6,])/abs(cleanmeansP2[2,5]), pch = 25, col='black', bg=colpal[6], cex=1.6, lwd=3)   # draw the data points themselves
-
-text(17,0.95,'(f)',adj=0.5,cex=2.5)
-
-load(file=paste0(datadir,'AveragedataMel.RData'))
-
-params <- c(pupilRmaxMel2,pupilPMel2,pupilZMel2,pupilWMel2,pupilKMel2,pupilQMel2)
-modresps <- getmodresps(params)
-
-plotlims <- c(15,40,0,1)
-ticklocsx <- contrastsdB    # locations of tick marks on x axis
-ticklocsy <- seq(0,1,0.2)
-ticklabelsx <-c(6,12,24,48,96)        # set labels for x ticks
-ticklabelsy <- ticklocsy
-
-par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2)     # add the tick labels
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
-title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
-title(ylab="Relative amplitude at 1Hz", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
-title(main='Melanopsin 2F',cex.main=2)
-
-for (cond in 1:3){
-  lines(contrastsfinedB,modresps[cond,], col=colpal[cond], lwd=3, cex=0.5)
-  points(contrastsdB,abs(cleanmeansP2[cond,])/abs(cleanmeansP2[2,5]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
-}  
-  lines(contrastsfinedB,modresps[4,], col=colpal[6], lwd=3, cex=0.5)
-  points(contrastsdB,abs(cleanmeansP2[6,])/abs(cleanmeansP2[2,5]), pch = 25, col='black', bg=colpal[6], cex=1.6, lwd=3)   # draw the data points themselves
-
-text(17,0.95,'(g)',adj=0.5,cex=2.5)
-
-load(file=paste0(datadir,'AveragedataLM.RData'))
-
-params <- c(pupilRmaxLM2,pupilPLM2,pupilZLM2,pupilWLM2,pupilKLM2,pupilQLM2)
-modresps <- getmodresps(params)
-
-par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2)     # add the tick labels
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
-title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
-title(ylab="Relative amplitude at 1Hz", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
-title(main='L-M cones 2F',cex.main=2)
-
-for (cond in 1:3){
-  lines(contrastsfinedB,modresps[cond,], col=colpal[cond], lwd=3, cex=0.5)
-  points(contrastsdB,abs(cleanmeansP2[cond,])/abs(cleanmeansP2[2,5]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
-}  
-  lines(contrastsfinedB,modresps[4,], col=colpal[6], lwd=3, cex=0.5)
-  points(contrastsdB,abs(cleanmeansP2[6,])/abs(cleanmeansP2[2,5]), pch = 25, col='black', bg=colpal[6], cex=1.6, lwd=3)   # draw the data points themselves
-
-text(17,0.95,'(h)',adj=0.5,cex=2.5)
-
-load(file=paste0(datadir,'AveragedataS.RData'))
-
-params <- c(pupilRmaxS2,pupilPS2,pupilZS2,pupilWS2,pupilKS2,pupilQS2)
-modresps <- getmodresps(params)
-
-par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2)     # add the tick labels
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
-title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
-title(ylab="Relative amplitude at 1Hz", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
-title(main='S cones 2F',cex.main=2)
-
-for (cond in 1:3){
-  lines(contrastsfinedB,modresps[cond,], col=colpal[cond], lwd=3, cex=0.5)
-  points(contrastsdB,abs(cleanmeansP2[cond,])/abs(cleanmeansP2[2,5]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
-}  
-  lines(contrastsfinedB,modresps[4,], col=colpal[6], lwd=3, cex=0.5)
-  points(contrastsdB,abs(cleanmeansP2[6,])/abs(cleanmeansP2[2,5]), pch = 25, col='black', bg=colpal[6], cex=1.6, lwd=3)   # draw the data points themselves
-
-text(17,0.95,'(i)',adj=0.5,cex=2.5)
-
-plotlims <- c(-24,12,0,0.6) 
-ticklocsx <- seq(-24,12,12)    
-ticklocsy <- seq(0,0.6,0.1)    
-ticklabelsx <- c('1/16','1/4','1','4')        
-ticklabelsy <- ticklocsy    # set labels for y ticks
-
-par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2)    
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
-
-title(xlab="w", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
-title(ylab="Probability", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
-title(main='Suppression 2F',cex.main=2)
-
-a <- density(20*log10(pupilweightpopLum2),from=-48,to=12)   
-polygon(c(-48,a$x,12), c(0,a$y,0), col=addalpha(colpalmod[1],0.5),border=NA)
-
-a <- density(20*log10(pupilweightpopMel2),from=-48,to=12)   
-polygon(c(-48,a$x,12), c(0,a$y,0), col=addalpha(colpalmod[2],0.5),border=NA)
-
-a <- density(20*log10(pupilweightpopLM2),from=-48,to=12)   
-polygon(c(-48,a$x,12), c(0,a$y,0), col=addalpha(colpalmod[3],0.5),border=NA)
-
-a <- density(20*log10(pupilweightpopS2),from=-48,to=12)   
-polygon(c(-48,a$x,12), c(0,a$y,0), col=addalpha(colpalmod[4],0.5),border=NA)
-
-prior <- dnorm(10^((-48:12)/20),1,0.5)
-prior <- 0.5*prior/max(prior)
-lines(-48:12,prior)
-
-lines(20*log10(c(mean(pupilWLum2),mean(pupilWLum2))),c(0,0.6),lwd=3,col=colpalmod[1])
-lines(20*log10(c(mean(pupilWMel2),mean(pupilWMel2))),c(0,0.6),lwd=3,col=colpalmod[2])
-lines(20*log10(c(mean(pupilWLM2),mean(pupilWLM2))),c(0,0.6),lwd=3,col=colpalmod[3])
-lines(20*log10(c(mean(pupilWS2),mean(pupilWS2))),c(0,0.6),lwd=3,col=colpalmod[4])
-
-legend(-24,0.6,c('Prior','Lum 2F', 'Mel 2F', 'LM 2F', 'S 2F'),col=c('black',colpalmod[1:4]),lwd=c(1,3,3,3,3),lty=1, cex=1.5, box.lwd=2, bg='white')
-
-text(10,0.58,'(j)',adj=0.5,cex=2.5)
-
-dev.off()
-
-}
-
 ```
@@
 
-coneab <- read.csv('local/coneabsorptions.csv',header=FALSE)
-spectra <- read.csv('local/spectra.csv',header=FALSE)
+coneab <- read.csv('resources/coneabsorptions.csv',header=FALSE)
+spectra <- read.csv('resources/spectra.csv',header=FALSE)
 
@@
 
-  schematic <- readTIFF('local/schematic.tiff')
+  schematic <- readTIFF('resources/schematic.tiff')
   aspratio <- 15/12  # this is the aspect ratio of the output pdf
@@
 
-lspec <- read.csv('local/STLAB_1_oo_irrad_spectra.csv',header=FALSE)
-rspec <- read.csv('local/STLAB_2_oo_irrad_spectra.csv',header=FALSE)
+lspec <- read.csv('resources/STLAB_1_oo_irrad_spectra.csv',header=FALSE)
+rspec <- read.csv('resources/STLAB_2_oo_irrad_spectra.csv',header=FALSE)
 
@@
 
-plotlims <- c(-24,24,-24,24) 
-ticklocsx <- seq(-24,24,12)    
-ticklocsy <- seq(-24,24,12)      
-ticklabelsx <- c('1/16','1/4','1','4','16')        
-ticklabelsy <- ticklabelsx    # set labels for y ticks
+allfacilitation <- matrix(0,nrow=2,ncol=4)
+allsuppression <- matrix(0,nrow=2,ncol=4)
+
+allfacilitation[1,1] <- mean(modrespsLum[2,]/modrespsLum[1,])
+allsuppression[1,1] <- mean(modrespsLum[1,]/modrespsLum[4,])
+allfacilitation[1,2] <- mean(modrespsLM[2,]/modrespsLM[1,])
+allsuppression[1,2] <- mean(modrespsLM[1,]/modrespsLM[4,])
+allfacilitation[1,3] <- mean(modrespsS[2,]/modrespsS[1,])
+allsuppression[1,3] <- mean(modrespsS[1,]/modrespsS[4,])
+allfacilitation[1,4] <- mean(modrespsMel[2,]/modrespsMel[1,])
+allsuppression[1,4] <- mean(modrespsMel[1,]/modrespsMel[4,])
+
+allfacilitation[2,1] <- mean(modrespsLum2[2,]/modrespsLum2[1,])
+allsuppression[2,1] <- mean(modrespsLum2[1,]/modrespsLum2[4,])
+allfacilitation[2,2] <- mean(modrespsLM2[2,]/modrespsLM2[1,])
+allsuppression[2,2] <- mean(modrespsLM2[1,]/modrespsLM2[4,])
+allfacilitation[2,3] <- mean(modrespsS2[2,]/modrespsS2[1,])
+allsuppression[2,3] <- mean(modrespsS2[1,]/modrespsS2[4,])
+allfacilitation[2,4] <- mean(modrespsMel2[2,]/modrespsMel2[1,])
+allsuppression[2,4] <- mean(modrespsMel2[1,]/modrespsMel2[4,])
+
+plotlims <- c(1,2,1,2) 
+ticklocsx <- seq(1,2,0.2)    
+ticklocsy <- seq(1,2,0.2)      
+ticklabelsx <- ticklocsx        
+ticklabelsy <- ticklocsy    # set labels for y ticks
 
@@
 
-points(allbin[1:4,5],alldich[1:4,5],pch=21)
+points(allfacilitation[1,1],allsuppression[1,1],pch=21,col=stimcolours[1],bg=stimcolours[2],cex=2,lwd=3)
+points(allfacilitation[1,2],allsuppression[1,2],pch=21,col=stimcolours[3],bg=stimcolours[4],cex=2,lwd=3)
+points(allfacilitation[1,3],allsuppression[1,3],pch=21,col=stimcolours[6],bg=stimcolours[5],cex=2,lwd=3)
+points(allfacilitation[1,4],allsuppression[1,4],pch=21,col=stimcolours[7],bg=stimcolours[8],cex=2,lwd=3)
+
+points(allfacilitation[2,1],allsuppression[2,1],pch=22,col=stimcolours[1],bg=stimcolours[2],cex=2,lwd=3)
+points(allfacilitation[2,2],allsuppression[2,2],pch=22,col=stimcolours[3],bg=stimcolours[4],cex=2,lwd=3)
+points(allfacilitation[2,3],allsuppression[2,3],pch=22,col=stimcolours[6],bg=stimcolours[5],cex=2,lwd=3)
+points(allfacilitation[2,4],allsuppression[2,4],pch=22,col=stimcolours[7],bg=stimcolours[8],cex=2,lwd=3)
 
@@
 title(ylab="Dichoptic suppression", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
-
-points(allbin[5:8,5],alldich[5:8,5],pch=21)
 
@@
 The anatomical pathway from the retina to the subcortical nuclei controlling the pupillary light response (PLR) is well established: it includes the Pretectal Olivary nucleus (PON), the Superior Cervical ganglion and the Edinger-Westphal nucleus, which project to the iris sphincter muscles that directly control the pupil size [@McDougal2008; @McDougal2015; @Wang2015].
-Evidence of a binocular component to the PLR is shown by the existence of a consensual response of the pupil [the stimulation of one eye will cause constriction of the other eye, @Wyatt1981].
+Evidence of a binocular component to the PLR is shown by the existence of a consensual response of the pupil [the stimulation of one eye will cause constriction of the other eye; @Wyatt1981].
 The anatomical segregation of the subcortical pathway from the rest of the brain means that this binocular combination of signals must occur independently of the cortical processes of binocular integration required for visual perception.
@@
 The strongest dichoptic masking is found in the first harmonic L-M condition, where we also observed the binocular suppression effect.
-We summarise this relationship by calculating an index for each effect, and show that the binocular facilitation effect is negatively correlated with the dichoptic masking effect (see Figure \@ref(fig:suppressionfig)).
 
@@
 Next, we fitted all 8 data sets using a Bayesian hierarchical implementation of a simple binocular combination model [@Meese2006; @Segala2023].
-Our primary interest was to compare posterior distributions of the weight of interocular suppression, which are showin in Figure \@ref(fig:suppressionfig).
+Our primary objective was to compare posterior distributions of the weight of interocular suppression, which are shown in Figure \@ref(fig:suppressionfig).
 Consistent with our earlier observations, at the first harmonic the strongest suppressive weight corresponds to the L-M condition, and the weakest suppression corresponds to the luminance condition [also consistent with @Segala2023].
@@
 Further details of fitted parameters, and model behaviour in other empirical conditions are provided in the Supplementary Materials.
+We used the model fits to summarise the relationship between binocular facilitation and interocular suppression by calculating an index for each effect, and show that the facilitation effect is negatively correlated with the dichoptic masking effect (see Figure \@ref(fig:suppressionfig)).
 
@@
 Panel (b) shows the pupil response at the second harmonic frequency during binocular stimulation.
-In panel (a) the luminance amplitudes have been scaled down by a factor of 10 to be compared with the other conditions.", fig.align="center", echo=FALSE}
+In panel (a) the luminance amplitudes have been scaled down by a factor of 10 to enable comparison with the other conditions.", fig.align="center", echo=FALSE}
 
@@
 The background spectra were defined by setting all channels to half maximum output for the brighter of the two devices (STLab 1, left eye) and then using the STLab 1/STLab 2 calibration ratio to find the equivalent settings for the companion device (STLab 2, right eye).
-The background spectrum illuminance was approximately 74 lux, or 62 cd/m$^2$.
+The background spectrum illuminance was approximately 74 lux, or 68.5 cd/m$^2$.
 The spectral power distributions and $\alpha$-opic irradiances of the background spectra for both eyes are shown in Figure \@ref(fig:spectraplots)c-d.

### 2024-04-28 manuscript.tex
Synchronising

@@
 The anatomical pathway from the retina to the subcortical nuclei controlling the pupillary light response (PLR) is well established: it includes the Pretectal Olivary nucleus (PON), the Superior Cervical ganglion and the Edinger-Westphal nucleus, which project to the iris sphincter muscles that directly control the pupil size (\protect\hyperlink{ref-McDougal2015}{McDougal and Gamlin, 2015}, \protect\hyperlink{ref-McDougal2008}{2008}; \protect\hyperlink{ref-Wang2015}{Wang and Munoz, 2015}).
-Evidence of a binocular component to the PLR is shown by the existence of a consensual response of the pupil (the stimulation of one eye will cause constriction of the other eye, \protect\hyperlink{ref-Wyatt1981}{Wyatt and Musselman, 1981}).
+Evidence of a binocular component to the PLR is shown by the existence of a consensual response of the pupil {[}the stimulation of one eye will cause constriction of the other eye; Wyatt and Musselman (\protect\hyperlink{ref-Wyatt1981}{1981}){]}.
 The anatomical segregation of the subcortical pathway from the rest of the brain means that this binocular combination of signals must occur independently of the cortical processes of binocular integration required for visual perception.
@@
 Panel (b) shows the outputs of each LED primary at maximum intensity, and panels (c) and (d) show the overall spectral power distributions and the alpha-opic irradiances of the background spectra used for both eyes.
-The subsequent rows show the power differences (e-h), and alpha-opic irradiances (i-l) relative to the background, averaged pupil diameter waveform (m-p) and Fourier spectra (q-t) for binocular stimulation.
+The subsequent rows show the power differences (e-h), and photoreceptor contrasts (i-l) relative to the background, averaged pupil diameter waveforms (m-p) and Fourier spectra (q-t) for binocular stimulation.
 Column headings indicate the pathway stimulated, and shaded regions in panels m-t indicate bootstrapped 95\% confidence intervals.}\label{fig:spectraplots}
@@
 The strongest dichoptic masking is found in the first harmonic L-M condition, where we also observed the binocular suppression effect.
-We summarise this relationship by calculating an index for each effect, and show that the binocular facilitation effect is negatively correlated with the dichoptic masking effect (see Figure \ref{fig:suppressionfig}).
 
@@
 Next, we fitted all 8 data sets using a Bayesian hierarchical implementation of a simple binocular combination model (\protect\hyperlink{ref-Meese2006}{Meese et al., 2006}; \protect\hyperlink{ref-Segala2023}{Segala et al., 2023}).
-Our primary interest was to compare posterior distributions of the weight of interocular suppression, which are showin in Figure \ref{fig:suppressionfig}.
+Our primary objective was to compare posterior distributions of the weight of interocular suppression, which are shown in Figure \ref{fig:suppressionfig}.
 Consistent with our earlier observations, at the first harmonic the strongest suppressive weight corresponds to the L-M condition, and the weakest suppression corresponds to the luminance condition (also consistent with \protect\hyperlink{ref-Segala2023}{Segala et al., 2023}).
@@
 Further details of fitted parameters, and model behaviour in other empirical conditions are provided in the Supplementary Materials.
+We used the model fits to summarise the relationship between binocular facilitation and interocular suppression by calculating an index for each effect, and show that the facilitation effect is negatively correlated with the dichoptic masking effect (see Figure \ref{fig:suppressionfig}).
 
@@
 Panel (b) shows the pupil response at the second harmonic frequency during binocular stimulation.
-In panel (a) the luminance amplitudes have been scaled down by a factor of 10 to be compared with the other conditions.}\label{fig:phaseplots}
+In panel (a) the luminance amplitudes have been scaled down by a factor of 10 to enable comparison with the other conditions.}\label{fig:phaseplots}
 \end{figure}
@@
 The background spectra were defined by setting all channels to half maximum output for the brighter of the two devices (STLab 1, left eye) and then using the STLab 1/STLab 2 calibration ratio to find the equivalent settings for the companion device (STLab 2, right eye).
-The background spectrum illuminance was approximately 74 lux, or 62 cd/m\(^2\).
+The background spectrum illuminance was approximately 74 lux, or 68.5 cd/m\(^2\).
 The spectral power distributions and \(\alpha\)-opic irradiances of the background spectra for both eyes are shown in Figure \ref{fig:spectraplots}c-d.

### 2024-04-28 checkforoutliers.R

@@ -1,0 +1,601 @@
+
+processdata <- 2
+
+library(FourierStats)
+# cut off for data inclusion (Mahalanobis distance for complex data)
+SDthresh <<- 99
+nbootstraps <<- 1000
+
+localdir <- 'local/'    # all files are stored in the project directory /local/ which git is told to ignore
+if (!file.exists(localdir)){dir.create(localdir)}   # create a local directory to store data and outputs
+rawdir <- 'local/rawdata/'
+if (!file.exists(rawdir)){dir.create(rawdir)}   # create a local directory to store raw data
+figdir <- 'Figures/'
+if (!file.exists(figdir)){dir.create(figdir)}   # create a local directory to store figures
+datadir <- 'local/processeddata/'
+if (!file.exists(datadir)){dir.create(datadir)}   # create a local directory to store processed data
+
+# files from P301-P324 are for S-cone stimulation
+# files from P501-P524 are for melanopsin stimulation
+# files from P601-P624 are for luminance stimulation
+# files from P701-P724 are for (L-M) cone stimulation
+
+# load in individual participant data and average, save group data
+if (processdata > 1){
+  
+  prefixlist <- c('P6','P7','P3','P5')
+  exptnames <- c('AveragedataLumA.RData','AveragedataLMA.RData','AveragedataSA.RData','AveragedataMelA.RData')
+  
+  includedvalues <- array(0,dim=c(4,24,6,5))
+  includedvalues2 <- array(0,dim=c(4,24,6,5))
+  
+  for (expt in 1:4){
+    d <- dir(datadir,pattern=prefixlist[expt], full.names = TRUE)
+    
+    tempmasksP <- array(0,dim=c(length(d),6,5))
+    tempmeansP <- tempmasksP
+    tempmeansP2 <- tempmasksP
+    tempmasksP2 <- tempmasksP
+    tempspectraP <- array(0,dim=c(length(d),300))
+    tempwavesP <- array(0,dim=c(length(d),1680))
+    
+    for (s in 1:length(d)){
+      
+      load(d[s])
[…]

### 2024-04-28 extraplottingchunks.R

@@ -1,0 +1,1183 @@
+```{r luminance plot, include=FALSE, results='hide'}
+
+load(file=paste0(datadir,'AveragedataLum.RData'))
+
+# generate plot showing the group pupillometry data for the luminance condition
+if (processdata > 0){
+
+allPLumratios <- abs(cleanmeansP[2,])/abs(cleanmeansP[1,])
+allPLum2ratios <- abs(cleanmeansP2[2,])/abs(cleanmeansP2[1,])
+
+# plot figure
+plotlims <- c(15,40,0,3)
+ticklocsx <- contrastsdB
+ticklabelsx <-c(6,12,24,48,96)
+ticklocsy <- seq(0,3,0.5)    # locations of tick marks on y axis
+ticklabelsy <- ticklocsy
+
+postscript("SumLum.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
+
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)
+title(ylab="Bin:Mon ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+lines(contrastsdB,allPLumratios, col=colpal[1], lwd=3, cex=0.5)
+lines(contrastsdB,allPLum2ratios, col=colpal[2], lwd=3, cex=0.5)
+points(contrastsdB,allPLumratios, pch = 21, col='black', bg=colpal[1], cex=1.6, lwd=3)
+points(contrastsdB,allPLum2ratios, pch = 22, col='black', bg=colpal[2], cex=1.6, lwd=3)
+
+legend(contrastsdB[4],3,c('Lum 1F','Lum 2F'), pch=21:24, pt.bg=colpal[1:2],box.lwd=2,pt.cex=1.6,pt.lwd=3)
+text(17,2.8,'(c)',adj=0.5,cex=2.5)
+
+dev.off()
+
[…]

### 2024-05-07 manuscript.Rmd
Revised modelling and data presentation

@@
 author: |
- | Federico G. Segala$^1$, Joel T. Martin$^1$, Annie Y. Morsi$^1$, Alex R. Wade$^{1,2}$ & Daniel H. Baker$^{1,2}$
+ | Federico G. Segala$^1$, Joel T. Martin$^{1,2}$, Annie Y. Morsi$^1$, Alex R. Wade$^{1,3}$ & Daniel H. Baker$^{1,3}$
 output:
@@
 
-processdata <- 3  # this flag determines the amount of processing, with 4 levels:
+processdata <- 1  # this flag determines the amount of processing, with 4 levels:
 # 0 - do no processing, generate the pdf using existing versions of all figures
@@
 SDthresh <<- 3
-nbootstraps <<- 1000
+nbootstraps <<- 10000
 
@@
 # settings for sampler 
-numSavedSteps <- 10000    # total number of MCMC steps
+numSavedSteps <- 100000    # total number of MCMC steps
 adaptSteps <- 1000  # Number of steps to "tune" the samplers
@@
 nChains <- 16
-ncores <- 8  # because of multi-threading, this is usually double the true number of physical cores, so we halve the number as Stan can only use physical cores
+ncores <- 8
 options(mc.cores=ncores)
@@
 
-$^2$York Biomedical Research Institute, University of York, Heslington, York, United Kingdom.
+$^2$School of Philosophy, Psychology and Language Sciences, University of Edinburgh, Edinburgh, United Kingdom.
+
+$^3$York Biomedical Research Institute, University of York, Heslington, York, United Kingdom.
 
@@
   includedvalues2 <- array(0,dim=c(4,24,6,5))
+  includedmasks <- array(0,dim=c(4,24,6,5))
+  includedmasks2 <- array(0,dim=c(4,24,6,5))
 
@@
         i <- which(D<SDthresh)
+        includedmasks[expt,i,cond,level] <- 1
         mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
@@
         i <- which(D<SDthresh)
-        includedvalues2[expt,i,cond,level] <- 1
+        includedmasks2[expt,i,cond,level] <- 1
         mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
@@
 
-  save(file=paste0(datadir,'included.RData'),list=c('includedvalues','includedvalues2'))
+  save(file=paste0(datadir,'included.RData'),list=c('includedvalues','includedvalues2','includedmasks','includedmasks2'))
 
@@
     real x[Ntotal] ;
-    real<lower=0> w[Ntotal] ;
     int<lower=1> c[Ntotal] ;
@@
     wtmu ~ normal( 1 , 0.5 ) ;
-    kmu ~ normal( 0.2 , 0.05 ) ;
+    kmu ~ normal( 0.002 , 0.001 ) ;
     pmu ~ normal( 0.4 , 0.2 ) ;
@@
 
-    if (c[i]==1)  // monocular condition
+    if (c[i]==1)  // monocular condition F1
        y[i] ~ student_t( 
@@
                 k[s[i]] + (Rmax[s[i]]*(pow(x[i],p[s[i]]+q[s[i]]))/(Z[s[i]] + (pow(x[i],q[s[i]])))) ,
-                w[i]*sigma ) ;
-
-     else if (c[i]==2)  // binocular condition 
+                sigma ) ;
+
+     else if (c[i]==2)  // binocular condition F1
        y[i] ~ student_t( 
@@
                 k[s[i]] + (Rmax[s[i]]*((pow(x[i],p[s[i]]+q[s[i]]))/(Z[s[i]] + (pow(x[i],q[s[i]])) + wt[s[i]]*(pow(x[i],q[s[i]]))) + (pow(x[i],p[s[i]]+q[s[i]]))/(Z[s[i]] + (pow(x[i],q[s[i]])) + wt[s[i]]*(pow(x[i],q[s[i]]))))),
-                w[i]*sigma ) ;
-
-     else if (c[i]==3)  // dichoptic condition
+                sigma ) ;
+
+     else if (c[i]==3)  // dichoptic condition F1
        y[i] ~ student_t( 
@@
                 k[s[i]] + (Rmax[s[i]]*((pow(x[i],p[s[i]]+q[s[i]]))/(Z[s[i]] + (pow(x[i],q[s[i]])) + wt[s[i]]*(pow(48,q[s[i]]))) + (pow(48,p[s[i]]+q[s[i]]))/(Z[s[i]] + (pow(48,q[s[i]])) + wt[s[i]]*(pow(x[i],q[s[i]]))))),
-                w[i]*sigma ) ;
-
-     else if (c[i]==4)  // binocular cross condition 
+                sigma ) ;
+
+     else if (c[i]==4)  // binocular cross condition F1
        y[i] ~ student_t( 
@@
                 k[s[i]] + (Rmax[s[i]]*(pow(x[i],p[s[i]]+q[s[i]]))/(Z[s[i]] + (pow(x[i],q[s[i]])) + wt[s[i]]*(pow(x[i],q[s[i]])))) ,
-                w[i]*sigma ) ;
-
-     else if (c[i]==5)  // dichoptic cross condition
+                sigma ) ;
+
+     else if (c[i]==5)  // dichoptic cross condition F1
        y[i] ~ student_t( 
@@
                 k[s[i]] + (Rmax[s[i]]*(pow(x[i],p[s[i]]+q[s[i]]))/(Z[s[i]] + (pow(x[i],q[s[i]])) + wt[s[i]]*(pow(48,q[s[i]])))) ,
-                w[i]*sigma ) ;       
+                sigma ) ;
+
+     else if (c[i]==6)  // monocular condition F2
+       y[i] ~ student_t( 
+                nu ,
+                k[s[i]] + (Rmax[s[i]]*(pow(x[i],p[s[i]]+q[s[i]]))/(Z[s[i]] + (pow(x[i],q[s[i]])))) ,
+                sigma ) ;
+
+     else if (c[i]==7)  // binocular cross condition F2
+       y[i] ~ student_t( 
+                nu ,
+                k[s[i]] + (Rmax[s[i]]*(pow(x[i],p[s[i]]+q[s[i]]))/(Z[s[i]] + (pow(x[i],q[s[i]])) + wt[s[i]]*(pow(x[i],q[s[i]])))) ,
+                sigma ) ;
+
+     else if (c[i]==8)  // dichoptic cross condition F2
+       y[i] ~ student_t( 
+                nu ,
+                k[s[i]] + (Rmax[s[i]]*(pow(48,p[s[i]]+q[s[i]]))/(Z[s[i]] + (pow(48,q[s[i]])) + wt[s[i]]*(pow(x[i],q[s[i]])))) ,
+                sigma ) ;
+
     }
@@
 
-      allmasksP[s,,] <- cleanmasksP  #/cleanmasksP[2,5]
-      allmeansP[s,,] <- cleanmeansP  #/cleanmeansP[2,5]
-      allmasksP2[s,,] <- cleanmasksP2  #/cleanmasksP2[2,5]
-      allmeansP2[s,,] <- cleanmeansP2  #/cleanmeansP2[2,5]
-
-    }
-
-    # 1st harmonic
+      allmasksP[s,,] <- cleanmasksP
+      allmeansP[s,,] <- cleanmeansP
+      allmasksP2[s,,] <- cleanmasksP2
+      allmeansP2[s,,] <- cleanmeansP2
+
+    }
+
+    # 1st harmonic F1
     condlist <- c(1,2,3,5,6)
@@
     s <- NULL
-    w <- NULL
     i <- 0
@@
                 s[i] <- subj
-                w[i] <- 1
-              }
-            }
-          }
-        }
-      }
-    }
-
-    pupildatalist = list(x = x, y = y, s = s, w = w, c = c, Nsubj = max(s), Ntotal = length(y))
+              }
+            }
+          }
+        }
+      }
+    }
+    # 1st harmonic F2
+    condlist <- c(4,5,6)
+    for (subj in 1:dim(allmasksP)[1]){
+      for (cond in 1:length(condlist)){
+        for (cont in 1:length(contlist)){
+          dp <- abs(allmasksP[subj,condlist[cond],cont])
+          if (includedmasks[expt,subj,condlist[cond],cont]==1){
+            if (is.na(dp)==0){
+              if (is.infinite(dp)==0){
+                i <- i + 1
+                x[i] <- contlist[cont]
+                y[i] <- dp
+                c[i] <- cond+5
+                s[i] <- subj
+              }
+            }
+          }
+        }
+      }
+    }
+
+    pupildatalist = list(x = x, y = y, s = s, c = c, Nsubj = max(s), Ntotal = length(y))
 
@@
                 s[i] <- subj
-              w[i] <- 1
-            }
-          }
-          }
-          }
-      }
-    }
-
-    pupildatalist = list(x = x, y = y, s = s, w = w, c = c, Nsubj = max(s), Ntotal = length(y))
+              }
+            }
+          }
+        }
+      }
+    }
+    # 2nd harmonic F2
+    condlist <- c(4,5,6)
+    for (subj in 1:dim(allmasksP)[1]){
+      for (cond in 1:length(condlist)){
+        for (cont in 1:length(contlist)){
+          dp <- abs(allmasksP2[subj,condlist[cond],cont])
+          if (includedmasks2[expt,subj,condlist[cond],cont]==1){
+            if (is.na(dp)==0){
+              if (is.infinite(dp)==0){
+                i <- i + 1
+                x[i] <- contlist[cont]
+                y[i] <- dp
+                c[i] <- cond+5
+                s[i] <- subj
+              }
+            }
+          }
+        }
+      }
+    }
+
+    pupildatalist = list(x = x, y = y, s = s, c = c, Nsubj = max(s), Ntotal = length(y))
 
@@
 
-# create figure containing modelling results
+# get predictions of the model based on earlier fits
 
@@
 
-  nchains <- dim(pupilsamples)[2]
-  pupilweightpopLum <- NULL
-  pupilZpopLum <- NULL
-  pupilKpopLum <- NULL
-  pupilPpopLum <- NULL
-  pupilQpopLum <- NULL
-  pupilRpopLum <- NULL
-
-  for (n in 1:nchains){
-    pupilweightpopLum <- c(pupilweightpopLum,pupilsamples@sim$samples[[n]]$wtmu)
-    pupilZpopLum <- c(pupilZpopLum,pupilsamples@sim$samples[[n]]$Zmu)
-    pupilKpopLum <- c(pupilKpopLum,pupilsamples@sim$samples[[n]]$kmu)
-    pupilPpopLum <- c(pupilPpopLum,pupilsamples@sim$samples[[n]]$pmu)
-    pupilQpopLum <- c(pupilQpopLum,pupilsamples@sim$samples[[n]]$qmu)
-    pupilRpopLum <- c(pupilRpopLum,pupilsamples@sim$samples[[n]]$Rmaxmu)
-  }
-
-  pupilWLum <- 10^(map_estimate(log10(pupilweightpopLum)))
-  pupilZLum <- 10^(map_estimate(log10(pupilZpopLum)))
-  pupilKLum <- 10^(map_estimate(log10(pupilKpopLum)))/sqrt(24)
-  pupilPLum <- 10^(map_estimate(log10(pupilPpopLum+pupilQpopLum)))
-  pupilQLum <- 10^(map_estimate(log10(pupilQpopLum)))
-  pupilRmaxLum <- 10^(map_estimate(log10(pupilRpopLum)))
+  draws <- extract(pupilsamples)
+
+  pupilweightpopLum <- draws$wtmu
+  pupilZpopLum <- draws$Zmu
+  pupilKpopLum <- draws$kmu
+  pupilPpopLum <- draws$pmu
+  pupilQpopLum <- draws$qmu
+  pupilRpopLum <- draws$Rmaxmu
+
+  pupilWLum <- 10^as.numeric(map_estimate(log10(pupilweightpopLum)))
+  pupilZLum <- 10^as.numeric(map_estimate(log10(pupilZpopLum)))
+  pupilKLum <- 10^as.numeric(map_estimate(log10(pupilKpopLum)))/sqrt(24)
+  pupilPLum <- 10^as.numeric(map_estimate(log10(pupilPpopLum+pupilQpopLum)))
+  pupilQLum <- 10^as.numeric(map_estimate(log10(pupilQpopLum)))
+  pupilRmaxLum <- 10^as.numeric(map_estimate(log10(pupilRpopLum)))
 
@@
 
-  nchains <- dim(pupilsamples)[2]
-  pupilweightpopMel <- NULL
-  pupilZpopMel <- NULL
-  pupilKpopMel <- NULL
-  pupilPpopMel <- NULL
-  pupilQpopMel <- NULL
-  pupilRpopMel <- NULL
-
-  for (n in 1:nchains){
-    pupilweightpopMel <- c(pupilweightpopMel,pupilsamples@sim$samples[[n]]$wtmu)
-    pupilZpopMel <- c(pupilZpopMel,pupilsamples@sim$samples[[n]]$Zmu)
-    pupilKpopMel <- c(pupilKpopMel,pupilsamples@sim$samples[[n]]$kmu)
-    pupilPpopMel <- c(pupilPpopMel,pupilsamples@sim$samples[[n]]$pmu)
-    pupilQpopMel <- c(pupilQpopMel,pupilsamples@sim$samples[[n]]$qmu)
-    pupilRpopMel <- c(pupilRpopMel,pupilsamples@sim$samples[[n]]$Rmaxmu)
-  }
-
-  pupilWMel <- 10^(map_estimate(log10(pupilweightpopMel)))
-  pupilZMel <- 10^(map_estimate(log10(pupilZpopMel)))
-  pupilKMel <- 10^(map_estimate(log10(pupilKpopMel)))/sqrt(24)
-  pupilPMel <- 10^(map_estimate(log10(pupilPpopMel+pupilQpopMel)))
-  pupilQMel <- 10^(map_estimate(log10(pupilQpopMel)))
-  pupilRmaxMel <- 10^(map_estimate(log10(pupilRpopMel)))
+  draws <- extract(pupilsamples)
+
+  pupilweightpopMel <- draws$wtmu
+  pupilZpopMel <- draws$Zmu
+  pupilKpopMel <- draws$kmu
+  pupilPpopMel <- draws$pmu
+  pupilQpopMel <- draws$qmu
+  pupilRpopMel <- draws$Rmaxmu
+
+  pupilWMel <- 10^as.numeric(map_estimate(log10(pupilweightpopMel)))
+  pupilZMel <- 10^as.numeric(map_estimate(log10(pupilZpopMel)))
+  pupilKMel <- 10^as.numeric(map_estimate(log10(pupilKpopMel)))/sqrt(24)
+  pupilPMel <- 10^as.numeric(map_estimate(log10(pupilPpopMel+pupilQpopMel)))
+  pupilQMel <- 10^as.numeric(map_estimate(log10(pupilQpopMel)))
+  pupilRmaxMel <- 10^as.numeric(map_estimate(log10(pupilRpopMel)))
 
@@
 
-  nchains <- dim(pupilsamples)[2]
-  pupilweightpopLM <- NULL
-  pupilZpopLM <- NULL
-  pupilKpopLM <- NULL
-  pupilPpopLM <- NULL
-  pupilQpopLM <- NULL
-  pupilRpopLM <- NULL
-
-  for (n in 1:nchains){
-    pupilweightpopLM <- c(pupilweightpopLM,pupilsamples@sim$samples[[n]]$wtmu)
-    pupilZpopLM <- c(pupilZpopLM,pupilsamples@sim$samples[[n]]$Zmu)
-    pupilKpopLM <- c(pupilKpopLM,pupilsamples@sim$samples[[n]]$kmu)
-    pupilPpopLM <- c(pupilPpopLM,pupilsamples@sim$samples[[n]]$pmu)
-    pupilQpopLM <- c(pupilQpopLM,pupilsamples@sim$samples[[n]]$qmu)
-    pupilRpopLM <- c(pupilRpopLM,pupilsamples@sim$samples[[n]]$Rmaxmu)
-  }
-
-  pupilWLM <- 10^(map_estimate(log10(pupilweightpopLM)))
-  pupilZLM <- 10^(map_estimate(log10(pupilZpopLM)))
-  pupilKLM <- 10^(map_estimate(log10(pupilKpopLM)))/sqrt(24)
-  pupilPLM <- 10^(map_estimate(log10(pupilPpopLM+pupilQpopLM)))
-  pupilQLM <- 10^(map_estimate(log10(pupilQpopLM)))
-  pupilRmaxLM <- 10^(map_estimate(log10(pupilRpopLM)))
+  draws <- extract(pupilsamples)
+
+  pupilweightpopLM <- draws$wtmu
+  pupilZpopLM <- draws$Zmu
+  pupilKpopLM <- draws$kmu
+  pupilPpopLM <- draws$pmu
+  pupilQpopLM <- draws$qmu
+  pupilRpopLM <- draws$Rmaxmu
+
+  pupilWLM <- 10^as.numeric(map_estimate(log10(pupilweightpopLM)))
+  pupilZLM <- 10^as.numeric(map_estimate(log10(pupilZpopLM)))
+  pupilKLM <- 10^as.numeric(map_estimate(log10(pupilKpopLM)))/sqrt(24)
+  pupilPLM <- 10^as.numeric(map_estimate(log10(pupilPpopLM+pupilQpopLM)))
+  pupilQLM <- 10^as.numeric(map_estimate(log10(pupilQpopLM)))
+  pupilRmaxLM <- 10^as.numeric(map_estimate(log10(pupilRpopLM)))
 
@@
 
-  nchains <- dim(pupilsamples)[2]
-  pupilweightpopS <- NULL
-  pupilZpopS <- NULL
-  pupilKpopS <- NULL
-  pupilPpopS <- NULL
-  pupilQpopS <- NULL
-  pupilRpopS <- NULL
-
-  for (n in 1:nchains){
-    pupilweightpopS <- c(pupilweightpopS,pupilsamples@sim$samples[[n]]$wtmu)
-    pupilZpopS <- c(pupilZpopS,pupilsamples@sim$samples[[n]]$Zmu)
-    pupilKpopS <- c(pupilKpopS,pupilsamples@sim$samples[[n]]$kmu)
-    pupilPpopS <- c(pupilPpopS,pupilsamples@sim$samples[[n]]$pmu)
-    pupilQpopS <- c(pupilQpopS,pupilsamples@sim$samples[[n]]$qmu)
-    pupilRpopS <- c(pupilRpopS,pupilsamples@sim$samples[[n]]$Rmaxmu)
-  }
-
-  pupilWS <- 10^(map_estimate(log10(pupilweightpopS)))
-  pupilZS <- 10^(map_estimate(log10(pupilZpopS)))
-  pupilKS <- 10^(map_estimate(log10(pupilKpopS)))/sqrt(24)
-  pupilPS <- 10^(map_estimate(log10(pupilPpopS+pupilQpopS)))
-  pupilQS <- 10^(map_estimate(log10(pupilQpopS)))
-  pupilRmaxS <- 10^(map_estimate(log10(pupilRpopS)))
+  draws <- extract(pupilsamples)
+
+  pupilweightpopS <- draws$wtmu
+  pupilZpopS <- draws$Zmu
+  pupilKpopS <- draws$kmu
+  pupilPpopS <- draws$pmu
+  pupilQpopS <- draws$qmu
+  pupilRpopS <- draws$Rmaxmu
+
+  pupilWS <- 10^as.numeric(map_estimate(log10(pupilweightpopS)))
+  pupilZS <- 10^as.numeric(map_estimate(log10(pupilZpopS)))
+  pupilKS <- 10^as.numeric(map_estimate(log10(pupilKpopS)))/sqrt(24)
+  pupilPS <- 10^as.numeric(map_estimate(log10(pupilPpopS+pupilQpopS)))
+  pupilQS <- 10^as.numeric(map_estimate(log10(pupilQpopS)))
+  pupilRmaxS <- 10^as.numeric(map_estimate(log10(pupilRpopS)))
 
@@
 
-  nchains <- dim(pupilsamples2)[2]
-  pupilweightpopLum2 <- NULL
-  pupilZpopLum2 <- NULL
-  pupilKpopLum2 <- NULL
-  pupilPpopLum2 <- NULL
-  pupilQpopLum2 <- NULL
-  pupilRpopLum2 <- NULL
-
-  for (n in 1:nchains){
-    pupilweightpopLum2 <- c(pupilweightpopLum2,pupilsamples2@sim$samples[[n]]$wtmu)
-    pupilZpopLum2 <- c(pupilZpopLum2,pupilsamples2@sim$samples[[n]]$Zmu)
-    pupilKpopLum2 <- c(pupilKpopLum2,pupilsamples2@sim$samples[[n]]$kmu)
-    pupilPpopLum2 <- c(pupilPpopLum2,pupilsamples2@sim$samples[[n]]$pmu)
-    pupilQpopLum2 <- c(pupilQpopLum2,pupilsamples2@sim$samples[[n]]$qmu)
-    pupilRpopLum2 <- c(pupilRpopLum2,pupilsamples2@sim$samples[[n]]$Rmaxmu)
-  }
-
-  pupilWLum2 <- 10^(map_estimate(log10(pupilweightpopLum2)))
-  pupilZLum2 <- 10^(map_estimate(log10(pupilZpopLum2)))
-  pupilKLum2 <- 10^(map_estimate(log10(pupilKpopLum2)))/sqrt(24)
-  pupilPLum2 <- 10^(map_estimate(log10(pupilPpopLum2+pupilQpopLum2)))
-  pupilQLum2 <- 10^(map_estimate(log10(pupilQpopLum2)))
-  pupilRmaxLum2 <- 10^(map_estimate(log10(pupilRpopLum2)))
+  draws <- extract(pupilsamples2)
+
+  pupilweightpopLum2 <- draws$wtmu
+  pupilZpopLum2 <- draws$Zmu
+  pupilKpopLum2 <- draws$kmu
+  pupilPpopLum2 <- draws$pmu
+  pupilQpopLum2 <- draws$qmu
+  pupilRpopLum2 <- draws$Rmaxmu
+
+  pupilWLum2 <- 10^as.numeric(map_estimate(log10(pupilweightpopLum2)))
+  pupilZLum2 <- 10^as.numeric(map_estimate(log10(pupilZpopLum2)))
+  pupilKLum2 <- 10^as.numeric(map_estimate(log10(pupilKpopLum2)))/sqrt(24)
+  pupilPLum2 <- 10^as.numeric(map_estimate(log10(pupilPpopLum2+pupilQpopLum2)))
+  pupilQLum2 <- 10^as.numeric(map_estimate(log10(pupilQpopLum2)))
+  pupilRmaxLum2 <- 10^as.numeric(map_estimate(log10(pupilRpopLum2)))
 
@@
 
-  nchains <- dim(pupilsamples2)[2]
-  pupilweightpopMel2 <- NULL
-  pupilZpopMel2 <- NULL
-  pupilKpopMel2 <- NULL
-  pupilPpopMel2 <- NULL
-  pupilQpopMel2 <- NULL
-  pupilRpopMel2 <- NULL
-
-  for (n in 1:nchains){
-    pupilweightpopMel2 <- c(pupilweightpopMel2,pupilsamples2@sim$samples[[n]]$wtmu)
-    pupilZpopMel2 <- c(pupilZpopMel2,pupilsamples2@sim$samples[[n]]$Zmu)
-    pupilKpopMel2 <- c(pupilKpopMel2,pupilsamples2@sim$samples[[n]]$kmu)
-    pupilPpopMel2 <- c(pupilPpopMel2,pupilsamples2@sim$samples[[n]]$pmu)
-    pupilQpopMel2 <- c(pupilQpopMel2,pupilsamples2@sim$samples[[n]]$qmu)
-    pupilRpopMel2 <- c(pupilRpopMel2,pupilsamples2@sim$samples[[n]]$Rmaxmu)
-  }
-
-  pupilWMel2 <- 10^(map_estimate(log10(pupilweightpopMel2)))
-  pupilZMel2 <- 10^(map_estimate(log10(pupilZpopMel2)))
-  pupilKMel2 <- 10^(map_estimate(log10(pupilKpopMel2)))/sqrt(24)
-  pupilPMel2 <- 10^(map_estimate(log10(pupilPpopMel2+pupilQpopMel2)))
-  pupilQMel2 <- 10^(map_estimate(log10(pupilQpopMel2)))
-  pupilRmaxMel2 <- 10^(map_estimate(log10(pupilRpopMel2)))
+  draws <- extract(pupilsamples2)
+
+  pupilweightpopMel2 <- draws$wtmu
+  pupilZpopMel2 <- draws$Zmu
+  pupilKpopMel2 <- draws$kmu
+  pupilPpopMel2 <- draws$pmu
+  pupilQpopMel2 <- draws$qmu
+  pupilRpopMel2 <- draws$Rmaxmu
+
+  pupilWMel2 <- 10^as.numeric(map_estimate(log10(pupilweightpopMel2)))
+  pupilZMel2 <- 10^as.numeric(map_estimate(log10(pupilZpopMel2)))
+  pupilKMel2 <- 10^as.numeric(map_estimate(log10(pupilKpopMel2)))/sqrt(24)
+  pupilPMel2 <- 10^as.numeric(map_estimate(log10(pupilPpopMel2+pupilQpopMel2)))
+  pupilQMel2 <- 10^as.numeric(map_estimate(log10(pupilQpopMel2)))
+  pupilRmaxMel2 <- 10^as.numeric(map_estimate(log10(pupilRpopMel2)))
 
@@
 
-  nchains <- dim(pupilsamples2)[2]
-  pupilweightpopLM2 <- NULL
-  pupilZpopLM2 <- NULL
-  pupilKpopLM2 <- NULL
-  pupilPpopLM2 <- NULL
-  pupilQpopLM2 <- NULL
-  pupilRpopLM2 <- NULL
-
-  for (n in 1:nchains){
-    pupilweightpopLM2 <- c(pupilweightpopLM2,pupilsamples2@sim$samples[[n]]$wtmu)
-    pupilZpopLM2 <- c(pupilZpopLM2,pupilsamples2@sim$samples[[n]]$Zmu)
-    pupilKpopLM2 <- c(pupilKpopLM2,pupilsamples2@sim$samples[[n]]$kmu)
-    pupilPpopLM2 <- c(pupilPpopLM2,pupilsamples2@sim$samples[[n]]$pmu)
-    pupilQpopLM2 <- c(pupilQpopLM2,pupilsamples2@sim$samples[[n]]$qmu)
-    pupilRpopLM2 <- c(pupilRpopLM2,pupilsamples2@sim$samples[[n]]$Rmaxmu)
-  }
-
-  pupilWLM2 <- 10^(map_estimate(log10(pupilweightpopLM2)))
-  pupilZLM2 <- 10^(map_estimate(log10(pupilZpopLM2)))
-  pupilKLM2 <- 10^(map_estimate(log10(pupilKpopLM2)))/sqrt(24)
-  pupilPLM2 <- 10^(map_estimate(log10(pupilPpopLM2+pupilQpopLM2)))
-  pupilQLM2 <- 10^(map_estimate(log10(pupilQpopLM2)))
-  pupilRmaxLM2 <- 10^(map_estimate(log10(pupilRpopLM2)))
+  draws <- extract(pupilsamples2)
+
+  pupilweightpopLM2 <- draws$wtmu
+  pupilZpopLM2 <- draws$Zmu
+  pupilKpopLM2 <- draws$kmu
+  pupilPpopLM2 <- draws$pmu
+  pupilQpopLM2 <- draws$qmu
+  pupilRpopLM2 <- draws$Rmaxmu
+
+  pupilWLM2 <- 10^as.numeric(map_estimate(log10(pupilweightpopLM2)))
+  pupilZLM2 <- 10^as.numeric(map_estimate(log10(pupilZpopLM2)))
+  pupilKLM2 <- 10^as.numeric(map_estimate(log10(pupilKpopLM2)))/sqrt(24)
+  pupilPLM2 <- 10^as.numeric(map_estimate(log10(pupilPpopLM2+pupilQpopLM2)))
+  pupilQLM2 <- 10^as.numeric(map_estimate(log10(pupilQpopLM2)))
+  pupilRmaxLM2 <- 10^as.numeric(map_estimate(log10(pupilRpopLM2)))
 
@@
 
-  nchains <- dim(pupilsamples2)[2]
-  pupilweightpopS2 <- NULL
-  pupilZpopS2 <- NULL
-  pupilKpopS2 <- NULL
-  pupilPpopS2 <- NULL
-  pupilQpopS2 <- NULL
-  pupilRpopS2 <- NULL
-
-  for (n in 1:nchains){
-    pupilweightpopS2 <- c(pupilweightpopS2,pupilsamples2@sim$samples[[n]]$wtmu)
-    pupilZpopS2 <- c(pupilZpopS2,pupilsamples2@sim$samples[[n]]$Zmu)
-    pupilKpopS2 <- c(pupilKpopS2,pupilsamples2@sim$samples[[n]]$kmu)
-    pupilPpopS2 <- c(pupilPpopS2,pupilsamples2@sim$samples[[n]]$pmu)
-    pupilQpopS2 <- c(pupilQpopS2,pupilsamples2@sim$samples[[n]]$qmu)
-    pupilRpopS2 <- c(pupilRpopS2,pupilsamples2@sim$samples[[n]]$Rmaxmu)
-  }
-
-  pupilWS2 <- 10^(map_estimate(log10(pupilweightpopS2)))
-  pupilZS2 <- 10^(map_estimate(log10(pupilZpopS2)))
-  pupilKS2 <- 10^(map_estimate(log10(pupilKpopS2)))/sqrt(24)
-  pupilPS2 <- 10^(map_estimate(log10(pupilPpopS2+pupilQpopS2)))
-  pupilQS2 <- 10^(map_estimate(log10(pupilQpopS2)))
-  pupilRmaxS2 <- 10^(map_estimate(log10(pupilRpopS2)))
+  draws <- extract(pupilsamples2)
+
+  pupilweightpopS2 <- draws$wtmu
+  pupilZpopS2 <- draws$Zmu
+  pupilKpopS2 <- draws$kmu
+  pupilPpopS2 <- draws$pmu
+  pupilQpopS2 <- draws$qmu
+  pupilRpopS2 <- draws$Rmaxmu
+
+  pupilWS2 <- 10^as.numeric(map_estimate(log10(pupilweightpopS2)))
+  pupilZS2 <- 10^as.numeric(map_estimate(log10(pupilZpopS2)))
+  pupilKS2 <- 10^as.numeric(map_estimate(log10(pupilKpopS2)))/sqrt(24)
+  pupilPS2 <- 10^as.numeric(map_estimate(log10(pupilPpopS2+pupilQpopS2)))
+  pupilQS2 <- 10^as.numeric(map_estimate(log10(pupilQpopS2)))
+  pupilRmaxS2 <- 10^as.numeric(map_estimate(log10(pupilRpopS2)))
 
@@
 
-modresps <- matrix(0,nrow=4,ncol=length(contrastsfine))
+modresps <- matrix(0,nrow=5,ncol=length(contrastsfine))
 modresps[1,] <- params[1]*(contrastsfine^params[2])/(params[3] + contrastsfine^params[6]) + params[5]
@@
 modresps[4,] <- params[1]*dichresp2 + params[5]
+
+dichresp3 <- ((48^params[2])/(params[3] + 48^params[6] + params[4]*contrastsfine^params[6]))
+modresps[5,] <- params[1]*dichresp3 + params[5]
 
@@
 
-```{r plotCRFs, include=FALSE, results='hide'}
-
-# create plots of spectra, cone absorption, waveforms and Fourier spectra
+```{r plot1Fdata, include=FALSE, results='hide'}
+
 if (processdata > 0){
@@
 contrastsfinedB <- 2:40
+
+pdf(paste0(figdir,"FirstHarmonic.pdf"), bg="transparent", height = 8, width = 24)
+
+layout(matrix(c(1,2,5,5,6,7,3,4,5,5,8,9),2,6,byrow=TRUE)) 
+par(mar=c(3,6,2,1))
 
@@
 
-  pdf(paste0(figdir,"CRFs.pdf"), bg="transparent", height = 6, width = 14)
-  par(mfcol=c(2,4), mar=c(3,6,2,2))
-
 load(file=paste0(datadir,'AveragedataLum.RData'))
@@
 text(17,0.14,'(a)',adj=0.5,cex=2.5)
-
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims2[1:2], ylim=plotlims2[3:4])   
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy2, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
-mtext(text = ticklabelsy2, side = 2, at=ticklocsy2, line=0.2, las=1) 
-title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)    # titles for axes
-title(ylab="Amplitude at 1Hz (mm)", col.lab=rgb(0,0,0), line=3.5, cex.lab=1.5)
-for (cond in 1:3){
-  lines(contrastsfinedB,modrespsLum2[condlist2[cond],], col=colpal[condlist[cond]], lwd=3, cex=0.5)
-  # lines(contrastsdB,abs(cleanmeansP2[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)
-  arrows(contrastsdB,abs(cleanmeansP2[condlist[cond],]),contrastsdB,cleanmeansP2CI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
-  arrows(contrastsdB,abs(cleanmeansP2[condlist[cond],]),contrastsdB,cleanmeansP2CI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
-  points(contrastsdB,abs(cleanmeansP2[condlist[cond],]), pch = 20+cond, col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
-}  
-text(17,0.014,'(e)',adj=0.5,cex=2.5)
 
@@
 
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims2[1:2], ylim=plotlims2[3:4])   
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy2, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
-mtext(text = ticklabelsy2, side = 2, at=ticklocsy2, line=0.2, las=1) 
-title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)    # titles for axes
-title(ylab="Amplitude at 1Hz (mm)", col.lab=rgb(0,0,0), line=3.5, cex.lab=1.5)
-for (cond in 1:3){
-  lines(contrastsfinedB,modrespsLM2[condlist2[cond],], col=colpal[condlist[cond]], lwd=3, cex=0.5)
-  # lines(contrastsdB,abs(cleanmeansP2[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)
-  arrows(contrastsdB,abs(cleanmeansP2[condlist[cond],]),contrastsdB,cleanmeansP2CI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
-  arrows(contrastsdB,abs(cleanmeansP2[condlist[cond],]),contrastsdB,cleanmeansP2CI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
-  points(contrastsdB,abs(cleanmeansP2[condlist[cond],]), pch = 20+cond, col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
-}  
-text(17,0.014,'(f)',adj=0.5,cex=2.5)
-
 load(file=paste0(datadir,'AveragedataS.RData'))
@@
 
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims2[1:2], ylim=plotlims2[3:4])   
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy2, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
-mtext(text = ticklabelsy2, side = 2, at=ticklocsy2, line=0.2, las=1) 
-title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)    # titles for axes
-title(ylab="Amplitude at 1Hz (mm)", col.lab=rgb(0,0,0), line=3.5, cex.lab=1.5)
-for (cond in 1:3){
-  lines(contrastsfinedB,modrespsS2[condlist2[cond],], col=colpal[condlist[cond]], lwd=3, cex=0.5)
-  # lines(contrastsdB,abs(cleanmeansP2[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)
-  arrows(contrastsdB,abs(cleanmeansP2[condlist[cond],]),contrastsdB,cleanmeansP2CI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
-  arrows(contrastsdB,abs(cleanmeansP2[condlist[cond],]),contrastsdB,cleanmeansP2CI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
-  points(contrastsdB,abs(cleanmeansP2[condlist[cond],]), pch = 20+cond, col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
-}  
-text(17,0.014,'(g)',adj=0.5,cex=2.5)
-
 load(file=paste0(datadir,'AveragedataMel.RData'))
@@
 
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims2[1:2], ylim=plotlims2[3:4])   
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy2, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
-mtext(text = ticklabelsy2, side = 2, at=ticklocsy2, line=0.2, las=1) 
-title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)    # titles for axes
-title(ylab="Amplitude at 1Hz (mm)", col.lab=rgb(0,0,0), line=3.5, cex.lab=1.5)
-for (cond in 1:3){
-  lines(contrastsfinedB,modrespsMel2[condlist2[cond],], col=colpal[condlist[cond]], lwd=3, cex=0.5)
-  # lines(contrastsdB,abs(cleanmeansP2[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)
-  arrows(contrastsdB,abs(cleanmeansP2[condlist[cond],]),contrastsdB,cleanmeansP2CI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
-  arrows(contrastsdB,abs(cleanmeansP2[condlist[cond],]),contrastsdB,cleanmeansP2CI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
-  points(contrastsdB,abs(cleanmeansP2[condlist[cond],]), pch = 20+cond, col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
-}  
-text(17,0.014,'(h)',adj=0.5,cex=2.5)
-
-dev.off()
-
-}
-
-```
-
-```{r plotsuppression, include=FALSE, results='hide'}
-
-if (processdata > 0){
-
-pdf(paste(figdir,"suppressionfig.pdf",sep=''), bg="transparent", height = 10, width = 10)
-
-par(mfrow=c(2,2))
-
-allbin <- matrix(0,nrow=8,ncol=5)
-alldich <- matrix(0,nrow=8,ncol=5)
-justbin <- matrix(0,nrow=8,ncol=5)
-justdich <- matrix(0,nrow=8,ncol=5)
-
-load(file=paste0(datadir,'AveragedataLum.RData'))
-allbin[1,] <- abs(cleanmeansP[2,])/abs(cleanmeansP[1,])
-allbin[5,] <- abs(cleanmeansP2[2,])/abs(cleanmeansP2[1,])
-alldich[1,] <- abs(cleanmeansP[1,])/abs(cleanmeansP[6,])
-alldich[5,] <- abs(cleanmeansP2[1,])/abs(cleanmeansP2[6,])
-justbin[1,] <- abs(cleanmeansP[2,])
-justbin[5,] <- abs(cleanmeansP2[2,])
-justdich[1,] <- abs(cleanmeansP[6,])
-justdich[5,] <- abs(cleanmeansP2[6,])
-
-load(file=paste0(datadir,'AveragedataLM.RData'))
-allbin[2,] <- abs(cleanmeansP[2,])/abs(cleanmeansP[1,])
-allbin[6,] <- abs(cleanmeansP2[2,])/abs(cleanmeansP2[1,])
-alldich[2,] <- abs(cleanmeansP[1,])/abs(cleanmeansP[6,])
-alldich[6,] <- abs(cleanmeansP2[1,])/abs(cleanmeansP2[6,])
-justbin[2,] <- abs(cleanmeansP[2,])
-justbin[6,] <- abs(cleanmeansP2[2,])
-justdich[2,] <- abs(cleanmeansP[6,])
-justdich[6,] <- abs(cleanmeansP2[6,])
-
-load(file=paste0(datadir,'AveragedataS.RData'))
-allbin[3,] <- abs(cleanmeansP[2,])/abs(cleanmeansP[1,])
-allbin[7,] <- abs(cleanmeansP2[2,])/abs(cleanmeansP2[1,])
-alldich[3,] <- abs(cleanmeansP[1,])/abs(cleanmeansP[6,])
-alldich[7,] <- abs(cleanmeansP2[1,])/abs(cleanmeansP2[6,])
-justbin[3,] <- abs(cleanmeansP[2,])
-justbin[7,] <- abs(cleanmeansP2[2,])
-justdich[3,] <- abs(cleanmeansP[6,])
-justdich[7,] <- abs(cleanmeansP2[6,])
-
-load(file=paste0(datadir,'AveragedataMel.RData'))
-allbin[4,] <- abs(cleanmeansP[2,])/abs(cleanmeansP[1,])
-allbin[8,] <- abs(cleanmeansP2[2,])/abs(cleanmeansP2[1,])
-alldich[4,] <- abs(cleanmeansP[1,])/abs(cleanmeansP[6,])
-alldich[8,] <- abs(cleanmeansP2[1,])/abs(cleanmeansP2[6,])
-justbin[4,] <- abs(cleanmeansP[2,])
-justbin[8,] <- abs(cleanmeansP2[2,])
-justdich[4,] <- abs(cleanmeansP[6,])
-justdich[8,] <- abs(cleanmeansP2[6,])
-
-allbin <- 20*log10(allbin)
-alldich <- 20*log10(alldich)
-
-allfacilitation <- matrix(0,nrow=2,ncol=4)
-allsuppression <- matrix(0,nrow=2,ncol=4)
-
-allfacilitation[1,1] <- mean(modrespsLum[2,]/modrespsLum[1,])
-allsuppression[1,1] <- mean(modrespsLum[1,]/modrespsLum[4,])
-allfacilitation[1,2] <- mean(modrespsLM[2,]/modrespsLM[1,])
-allsuppression[1,2] <- mean(modrespsLM[1,]/modrespsLM[4,])
-allfacilitation[1,3] <- mean(modrespsS[2,]/modrespsS[1,])
-allsuppression[1,3] <- mean(modrespsS[1,]/modrespsS[4,])
-allfacilitation[1,4] <- mean(modrespsMel[2,]/modrespsMel[1,])
-allsuppression[1,4] <- mean(modrespsMel[1,]/modrespsMel[4,])
-
-allfacilitation[2,1] <- mean(modrespsLum2[2,]/modrespsLum2[1,])
-allsuppression[2,1] <- mean(modrespsLum2[1,]/modrespsLum2[4,])
-allfacilitation[2,2] <- mean(modrespsLM2[2,]/modrespsLM2[1,])
-allsuppression[2,2] <- mean(modrespsLM2[1,]/modrespsLM2[4,])
-allfacilitation[2,3] <- mean(modrespsS2[2,]/modrespsS2[1,])
-allsuppression[2,3] <- mean(modrespsS2[1,]/modrespsS2[4,])
-allfacilitation[2,4] <- mean(modrespsMel2[2,]/modrespsMel2[1,])
-allsuppression[2,4] <- mean(modrespsMel2[1,]/modrespsMel2[4,])
-
-plotlims <- c(1,2,1,2) 
-ticklocsx <- seq(1,2,0.2)    
-ticklocsy <- seq(1,2,0.2)      
-ticklabelsx <- ticklocsx        
-ticklabelsy <- ticklocsy    # set labels for y ticks
-
-par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2)    
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
-
-title(xlab="Binocular facilitation", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
-title(ylab="Dichoptic suppression", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
-
-points(allfacilitation[1,1],allsuppression[1,1],pch=21,col=stimcolours[1],bg=stimcolours[2],cex=2,lwd=3)
-points(allfacilitation[1,2],allsuppression[1,2],pch=21,col=stimcolours[3],bg=stimcolours[4],cex=2,lwd=3)
-points(allfacilitation[1,3],allsuppression[1,3],pch=21,col=stimcolours[6],bg=stimcolours[5],cex=2,lwd=3)
-points(allfacilitation[1,4],allsuppression[1,4],pch=21,col=stimcolours[7],bg=stimcolours[8],cex=2,lwd=3)
-
-points(allfacilitation[2,1],allsuppression[2,1],pch=22,col=stimcolours[1],bg=stimcolours[2],cex=2,lwd=3)
-points(allfacilitation[2,2],allsuppression[2,2],pch=22,col=stimcolours[3],bg=stimcolours[4],cex=2,lwd=3)
-points(allfacilitation[2,3],allsuppression[2,3],pch=22,col=stimcolours[6],bg=stimcolours[5],cex=2,lwd=3)
-points(allfacilitation[2,4],allsuppression[2,4],pch=22,col=stimcolours[7],bg=stimcolours[8],cex=2,lwd=3)
-
-par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2)    
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
-
-title(xlab="Binocular facilitation", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
-title(ylab="Dichoptic suppression", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
+par(mar=c(8,12,8,4))
 
@@
 a <- density(20*log10(pupilweightpopLum),from=-48,to=12)   
-polygon(c(-48,a$x,12), c(0,a$y,0), col=addalpha(colpalmod[1],0.5),border=NA)
+polygon(c(-48,a$x,12), c(0,a$y,0), col=addalpha(stimcolours[1],0.5),border=NA)
+
+a<- density(20*log10(pupilweightpopLM),from=-48,to=12)   
+polygon(c(-48,a$x,12), c(0,a$y,0), col=addalpha(stimcolours[4],0.5),border=NA)
+
+a <- density(20*log10(pupilweightpopS),from=-48,to=12)   
+polygon(c(-48,a$x,12), c(0,a$y,0), col=addalpha(stimcolours[6],0.5),border=NA)
 
 a <- density(20*log10(pupilweightpopMel),from=-48,to=12)   
-polygon(c(-48,a$x,12), c(0,a$y,0), col=addalpha(colpalmod[2],0.5),border=NA)
-
-a<- density(20*log10(pupilweightpopLM),from=-48,to=12)   
-polygon(c(-48,a$x,12), c(0,a$y,0), col=addalpha(colpalmod[3],0.5),border=NA)
-
-a <- density(20*log10(pupilweightpopS),from=-48,to=12)   
-polygon(c(-48,a$x,12), c(0,a$y,0), col=addalpha(colpalmod[4],0.5),border=NA)
+polygon(c(-48,a$x,12), c(0,a$y,0), col=addalpha(stimcolours[7],0.5),border=NA)
 
@@
 prior <- 0.5*prior/max(prior)
-lines(-48:12,prior)
-
-lines(20*log10(c(mean(pupilWLum),mean(pupilWLum))),c(0,0.6),lwd=3,col=colpalmod[1])
-lines(20*log10(c(mean(pupilWMel),mean(pupilWMel))),c(0,0.6),lwd=3,col=colpalmod[2])
-lines(20*log10(c(mean(pupilWLM),mean(pupilWLM))),c(0,0.6),lwd=3,col=colpalmod[3])
-lines(20*log10(c(mean(pupilWS),mean(pupilWS))),c(0,0.6),lwd=3,col=colpalmod[4])
-
-legend(-24,0.6,c('Prior','Lum 1F', 'Mel 1F', 'LM 1F', 'S 1F'),col=c('black',colpalmod[1:4]),lwd=c(1,3,3,3,3),lty=1, cex=1.5, box.lwd=2, bg='white')
-
-text(10,0.58,'(c)',adj=0.5,cex=2.5)
+lines(-48:12,prior,lwd=2)
+
+lines(20*log10(c(mean(pupilWLum),mean(pupilWLum))),c(0,0.6),lwd=6,col=stimcolours[1])
+lines(20*log10(c(mean(pupilWLM),mean(pupilWLM))),c(0,0.6),lwd=6,col=stimcolours[4])
+lines(20*log10(c(mean(pupilWS),mean(pupilWS))),c(0,0.6),lwd=6,col=stimcolours[6])
+lines(20*log10(c(mean(pupilWMel),mean(pupilWMel))),c(0,0.6),lwd=6,col=stimcolours[7])
+
+legend(-24,0.6,c('Prior','Lum 1F', 'L-M 1F', 'S 1F', 'Mel 1F'), col=c('black',stimcolours[c(1,4,6,7)]),lwd=c(2,6,6,6,6),lty=1, cex=1.8, box.lwd=2, bg='white')
+
+text(10,0.58,'(e)',adj=0.5,cex=2.5)
+
+par(mar=c(3,6,2,1))
+
+condlist <- c(4,5,6)
+condlist2 <- c(1,4,5)
+plotlims <- c(15,40,0,0.15)
+plotlims2 <- c(15,40,0,0.015) 
+ticklocsx <- contrastsdB    # locations of tick marks on x axis
+ticklocsy <- seq(0,0.15,0.05)
+ticklocsy2 <- seq(0,0.015,0.005)    # locations of tick marks on y axis
+ticklabelsx <-c(6,12,24,48,96)        # set labels for x ticks
+ticklabelsy <- ticklocsy
+ticklabelsy2 <- ticklocsy2     # set labels for y ticks
+
+load(file=paste0(datadir,'AveragedataLum.RData'))
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)    # titles for axes
+title(ylab="Amplitude at 0.4Hz (mm)", col.lab=rgb(0,0,0), line=3, cex.lab=1.5)
+title(main='Luminance',cex.main=2)
+for (cond in 1:3){
+  lines(contrastsfinedB,modrespsLum[condlist2[cond],], col=colpal[condlist[cond]], lwd=3, cex=0.5)
+  # lines(contrastsfinedB,abs(cleanmeansP[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)
+  arrows(contrastsdB,abs(cleanmasksP[condlist[cond],]),contrastsdB,cleanmasksPCI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  arrows(contrastsdB,abs(cleanmasksP[condlist[cond],]),contrastsdB,cleanmasksPCI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  points(contrastsdB,abs(cleanmasksP[condlist[cond],]), pch = 20+cond, col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
+}  
+legend(15,0.125,c('Monocular','Binocular cross','Dichoptic cross'),pch=21:23,pt.bg=colpal[condlist],pt.lwd=3,pt.cex=1.6,box.lwd=2,cex=1.2)
+text(17,0.14,'(f)',adj=0.5,cex=2.5)
+
+load(file=paste0(datadir,'AveragedataLM.RData'))
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims2[1:2], ylim=plotlims2[3:4])   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy2, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
+mtext(text = ticklabelsy2, side = 2, at=ticklocsy2, line=0.2, las=1) 
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)    # titles for axes
+title(ylab="Amplitude at 0.4Hz (mm)", col.lab=rgb(0,0,0), line=3.5, cex.lab=1.5)
+title(main='L-M cone',cex.main=2)
+for (cond in 1:3){
+  lines(contrastsfinedB,modrespsLM[condlist2[cond],], col=colpal[condlist[cond]], lwd=3, cex=0.5)
+  # lines(contrastsdB,abs(cleanmeansP[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)
+  arrows(contrastsdB,abs(cleanmasksP[condlist[cond],]),contrastsdB,cleanmasksPCI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  arrows(contrastsdB,abs(cleanmasksP[condlist[cond],]),contrastsdB,cleanmasksPCI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  points(contrastsdB,abs(cleanmasksP[condlist[cond],]), pch = 20+cond, col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
+}  
+text(17,0.014,'(g)',adj=0.5,cex=2.5)
+
+load(file=paste0(datadir,'AveragedataS.RData'))
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims2[1:2], ylim=plotlims2[3:4])   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy2, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
+mtext(text = ticklabelsy2, side = 2, at=ticklocsy2, line=0.2, las=1) 
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)    # titles for axes
+title(ylab="Amplitude at 0.4Hz (mm)", col.lab=rgb(0,0,0), line=3.5, cex.lab=1.5)
+title(main='S cone',cex.main=2)
+for (cond in 1:3){
+  lines(contrastsfinedB,modrespsS[condlist2[cond],], col=colpal[condlist[cond]], lwd=3, cex=0.5)
+  # lines(contrastsdB,abs(cleanmeansP[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)
+  arrows(contrastsdB,abs(cleanmasksP[condlist[cond],]),contrastsdB,cleanmasksPCI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  arrows(contrastsdB,abs(cleanmasksP[condlist[cond],]),contrastsdB,cleanmasksPCI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  points(contrastsdB,abs(cleanmasksP[condlist[cond],]), pch = 20+cond, col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
+}  
+text(17,0.014,'(h)',adj=0.5,cex=2.5)
+
+load(file=paste0(datadir,'AveragedataMel.RData'))
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims2[1:2], ylim=plotlims2[3:4])   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy2, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
+mtext(text = ticklabelsy2, side = 2, at=ticklocsy2, line=0.2, las=1) 
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)    # titles for axes
+title(ylab="Amplitude at 0.4Hz (mm)", col.lab=rgb(0,0,0), line=3.5, cex.lab=1.5)
+title(main='Melanopsin',cex.main=2)
+for (cond in 1:3){
+  lines(contrastsfinedB,modrespsMel[condlist2[cond],], col=colpal[condlist[cond]], lwd=3, cex=0.5)
+  # lines(contrastsdB,abs(cleanmeansP[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)
+  arrows(contrastsdB,abs(cleanmasksP[condlist[cond],]),contrastsdB,cleanmasksPCI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  arrows(contrastsdB,abs(cleanmasksP[condlist[cond],]),contrastsdB,cleanmasksPCI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  points(contrastsdB,abs(cleanmasksP[condlist[cond],]), pch = 20+cond, col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
+}  
+text(17,0.014,'(i)',adj=0.5,cex=2.5)
+
+dev.off()
+
+}
+
+```
+
+```{r plot2Fdata, include=FALSE, results='hide'}
+
+if (processdata > 0){
+
+contrastsfinedB <- 2:40
+
+pdf(paste0(figdir,"SecondHarmonic.pdf"), bg="transparent", height = 8, width = 24)
+
+layout(matrix(c(1,2,5,5,6,7,3,4,5,5,8,9),2,6,byrow=TRUE)) 
+par(mar=c(3,6,2,1))
+
+condlist <- c(1,2,6)
+condlist2 <- c(1,2,4)
+plotlims <- c(15,40,0,0.15)
+plotlims2 <- c(15,40,0,0.015) 
+ticklocsx <- contrastsdB    # locations of tick marks on x axis
+ticklocsy <- seq(0,0.15,0.05)
+ticklocsy2 <- seq(0,0.015,0.005)    # locations of tick marks on y axis
+ticklabelsx <-c(6,12,24,48,96)        # set labels for x ticks
+ticklabelsy <- ticklocsy
+ticklabelsy2 <- ticklocsy2     # set labels for y ticks
+
+load(file=paste0(datadir,'AveragedataLum.RData'))
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims2[1:2], ylim=plotlims2[3:4])   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy2, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
+mtext(text = ticklabelsy2, side = 2, at=ticklocsy2, line=0.2, las=1) 
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)    # titles for axes
+title(ylab="Amplitude at 1Hz (mm)", col.lab=rgb(0,0,0), line=3.5, cex.lab=1.5)
+title(main='Luminance',cex.main=2)
+for (cond in 1:3){
+  lines(contrastsfinedB,modrespsLum2[condlist2[cond],], col=colpal[condlist[cond]], lwd=3, cex=0.5)
+  # lines(contrastsfinedB,abs(cleanmeansP[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)
+  arrows(contrastsdB,abs(cleanmeansP2[condlist[cond],]),contrastsdB,cleanmeansP2CI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  arrows(contrastsdB,abs(cleanmeansP2[condlist[cond],]),contrastsdB,cleanmeansP2CI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  points(contrastsdB,abs(cleanmeansP2[condlist[cond],]), pch = 20+cond, col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
+}  
+legend(15,0.0125,c('Monocular','Binocular','Dichoptic cross'),pch=21:23,pt.bg=colpal[condlist],pt.lwd=3,pt.cex=1.6,box.lwd=2,cex=1.2)
+text(17,0.014,'(a)',adj=0.5,cex=2.5)
+
+load(file=paste0(datadir,'AveragedataLM.RData'))
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims2[1:2], ylim=plotlims2[3:4])   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy2, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
+mtext(text = ticklabelsy2, side = 2, at=ticklocsy2, line=0.2, las=1) 
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)    # titles for axes
+title(ylab="Amplitude at 1Hz (mm)", col.lab=rgb(0,0,0), line=3.5, cex.lab=1.5)
+title(main='L-M cone',cex.main=2)
+for (cond in 1:3){
+  lines(contrastsfinedB,modrespsLM2[condlist2[cond],], col=colpal[condlist[cond]], lwd=3, cex=0.5)
+  # lines(contrastsdB,abs(cleanmeansP[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)
+  arrows(contrastsdB,abs(cleanmeansP2[condlist[cond],]),contrastsdB,cleanmeansP2CI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  arrows(contrastsdB,abs(cleanmeansP2[condlist[cond],]),contrastsdB,cleanmeansP2CI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  points(contrastsdB,abs(cleanmeansP2[condlist[cond],]), pch = 20+cond, col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
+}  
+text(17,0.014,'(b)',adj=0.5,cex=2.5)
+
+load(file=paste0(datadir,'AveragedataS.RData'))
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims2[1:2], ylim=plotlims2[3:4])   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy2, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
+mtext(text = ticklabelsy2, side = 2, at=ticklocsy2, line=0.2, las=1) 
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)    # titles for axes
+title(ylab="Amplitude at 1Hz (mm)", col.lab=rgb(0,0,0), line=3.5, cex.lab=1.5)
+title(main='S cone',cex.main=2)
+for (cond in 1:3){
+  lines(contrastsfinedB,modrespsS2[condlist2[cond],], col=colpal[condlist[cond]], lwd=3, cex=0.5)
+  # lines(contrastsdB,abs(cleanmeansP[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)
+  arrows(contrastsdB,abs(cleanmeansP2[condlist[cond],]),contrastsdB,cleanmeansP2CI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  arrows(contrastsdB,abs(cleanmeansP2[condlist[cond],]),contrastsdB,cleanmeansP2CI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  points(contrastsdB,abs(cleanmeansP2[condlist[cond],]), pch = 20+cond, col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
+}  
+text(17,0.014,'(c)',adj=0.5,cex=2.5)
+
+load(file=paste0(datadir,'AveragedataMel.RData'))
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims2[1:2], ylim=plotlims2[3:4])   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy2, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
+mtext(text = ticklabelsy2, side = 2, at=ticklocsy2, line=0.2, las=1) 
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)    # titles for axes
+title(ylab="Amplitude at 1Hz (mm)", col.lab=rgb(0,0,0), line=3.5, cex.lab=1.5)
+title(main='Melanopsin',cex.main=2)
+for (cond in 1:3){
+  lines(contrastsfinedB,modrespsMel2[condlist2[cond],], col=colpal[condlist[cond]], lwd=3, cex=0.5)
+  # lines(contrastsdB,abs(cleanmeansP[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)
+  arrows(contrastsdB,abs(cleanmeansP2[condlist[cond],]),contrastsdB,cleanmeansP2CI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  arrows(contrastsdB,abs(cleanmeansP2[condlist[cond],]),contrastsdB,cleanmeansP2CI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  points(contrastsdB,abs(cleanmeansP2[condlist[cond],]), pch = 20+cond, col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
+}  
+text(17,0.014,'(d)',adj=0.5,cex=2.5)
+
+par(mar=c(8,12,8,4))
 
@@
 a <- density(20*log10(pupilweightpopLum2),from=-48,to=12)   
-polygon(c(-48,a$x,12), c(0,a$y,0), col=addalpha(colpalmod[1],0.5),border=NA)
+polygon(c(-48,a$x,12), c(0,a$y,0), col=addalpha(stimcolours[1],0.5),border=NA)
+
+a<- density(20*log10(pupilweightpopLM2),from=-48,to=12)   
+polygon(c(-48,a$x,12), c(0,a$y,0), col=addalpha(stimcolours[4],0.5),border=NA)
+
+a <- density(20*log10(pupilweightpopS2),from=-48,to=12)   
+polygon(c(-48,a$x,12), c(0,a$y,0), col=addalpha(stimcolours[6],0.5),border=NA)
 
 a <- density(20*log10(pupilweightpopMel2),from=-48,to=12)   
-polygon(c(-48,a$x,12), c(0,a$y,0), col=addalpha(colpalmod[2],0.5),border=NA)
-
-a <- density(20*log10(pupilweightpopLM2),from=-48,to=12)   
-polygon(c(-48,a$x,12), c(0,a$y,0), col=addalpha(colpalmod[3],0.5),border=NA)
-
-a <- density(20*log10(pupilweightpopS2),from=-48,to=12)   
-polygon(c(-48,a$x,12), c(0,a$y,0), col=addalpha(colpalmod[4],0.5),border=NA)
+polygon(c(-48,a$x,12), c(0,a$y,0), col=addalpha(stimcolours[7],0.5),border=NA)
 
@@
 prior <- 0.5*prior/max(prior)
-lines(-48:12,prior)
-
-lines(20*log10(c(mean(pupilWLum2),mean(pupilWLum2))),c(0,0.6),lwd=3,col=colpalmod[1])
-lines(20*log10(c(mean(pupilWMel2),mean(pupilWMel2))),c(0,0.6),lwd=3,col=colpalmod[2])
-lines(20*log10(c(mean(pupilWLM2),mean(pupilWLM2))),c(0,0.6),lwd=3,col=colpalmod[3])
-lines(20*log10(c(mean(pupilWS2),mean(pupilWS2))),c(0,0.6),lwd=3,col=colpalmod[4])
-
-legend(-24,0.6,c('Prior','Lum 2F', 'Mel 2F', 'LM 2F', 'S 2F'),col=c('black',colpalmod[1:4]),lwd=c(1,3,3,3,3),lty=1, cex=1.5, box.lwd=2, bg='white')
-
-text(10,0.58,'(d)',adj=0.5,cex=2.5)
+lines(-48:12,prior,lwd=2)
+
+lines(20*log10(c(mean(pupilWLum2),mean(pupilWLum2))),c(0,0.6),lwd=6,col=stimcolours[1])
+lines(20*log10(c(mean(pupilWLM2),mean(pupilWLM2))),c(0,0.6),lwd=6,col=stimcolours[4])
+lines(20*log10(c(mean(pupilWS2),mean(pupilWS2))),c(0,0.6),lwd=6,col=stimcolours[6])
+lines(20*log10(c(mean(pupilWMel2),mean(pupilWMel2))),c(0,0.6),lwd=6,col=stimcolours[7])
+
+legend(-24,0.6,c('Prior','Lum 2F', 'L-M 2F', 'S 2F', 'Mel 2F'), col=c('black',stimcolours[c(1,4,6,7)]),lwd=c(2,6,6,6,6),lty=1, cex=1.8, box.lwd=2, bg='white')
+
+text(10,0.58,'(e)',adj=0.5,cex=2.5)
+
+par(mar=c(3,6,2,1))
+
+condlist <- c(4,5,6)
+condlist2 <- c(1,4,5)
+plotlims <- c(15,40,0,0.15)
+plotlims2 <- c(15,40,0,0.015) 
+ticklocsx <- contrastsdB    # locations of tick marks on x axis
+ticklocsy <- seq(0,0.15,0.05)
+ticklocsy2 <- seq(0,0.015,0.005)    # locations of tick marks on y axis
+ticklabelsx <-c(6,12,24,48,96)        # set labels for x ticks
+ticklabelsy <- ticklocsy
+ticklabelsy2 <- ticklocsy2     # set labels for y ticks
+
+load(file=paste0(datadir,'AveragedataLum.RData'))
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims2[1:2], ylim=plotlims2[3:4])   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy2, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
+mtext(text = ticklabelsy2, side = 2, at=ticklocsy2, line=0.2, las=1) 
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)    # titles for axes
+title(ylab="Amplitude at 0.8Hz (mm)", col.lab=rgb(0,0,0), line=3.5, cex.lab=1.5)
+title(main='Luminance',cex.main=2)
+for (cond in 1:3){
+  lines(contrastsfinedB,modrespsLum2[condlist2[cond],], col=colpal[condlist[cond]], lwd=3, cex=0.5)
+  # lines(contrastsfinedB,abs(cleanmeansP[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)
+  arrows(contrastsdB,abs(cleanmasksP2[condlist[cond],]),contrastsdB,cleanmasksP2CI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  arrows(contrastsdB,abs(cleanmasksP2[condlist[cond],]),contrastsdB,cleanmasksP2CI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  points(contrastsdB,abs(cleanmasksP2[condlist[cond],]), pch = 20+cond, col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
+}  
+legend(15,0.0125,c('Monocular','Binocular cross','Dichoptic cross'),pch=21:23,pt.bg=colpal[condlist],pt.lwd=3,pt.cex=1.6,box.lwd=2,cex=1.2)
+text(17,0.014,'(f)',adj=0.5,cex=2.5)
+
+load(file=paste0(datadir,'AveragedataLM.RData'))
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims2[1:2], ylim=plotlims2[3:4])   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy2, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
+mtext(text = ticklabelsy2, side = 2, at=ticklocsy2, line=0.2, las=1) 
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)    # titles for axes
+title(ylab="Amplitude at 0.8Hz (mm)", col.lab=rgb(0,0,0), line=3.5, cex.lab=1.5)
+title(main='L-M cone',cex.main=2)
+for (cond in 1:3){
+  lines(contrastsfinedB,modrespsLM2[condlist2[cond],], col=colpal[condlist[cond]], lwd=3, cex=0.5)
+  # lines(contrastsdB,abs(cleanmeansP[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)
+  arrows(contrastsdB,abs(cleanmasksP2[condlist[cond],]),contrastsdB,cleanmasksP2CI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  arrows(contrastsdB,abs(cleanmasksP2[condlist[cond],]),contrastsdB,cleanmasksP2CI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  points(contrastsdB,abs(cleanmasksP2[condlist[cond],]), pch = 20+cond, col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
+}  
+text(17,0.014,'(g)',adj=0.5,cex=2.5)
+
+load(file=paste0(datadir,'AveragedataS.RData'))
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims2[1:2], ylim=plotlims2[3:4])   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy2, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
+mtext(text = ticklabelsy2, side = 2, at=ticklocsy2, line=0.2, las=1) 
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)    # titles for axes
+title(ylab="Amplitude at 0.8Hz (mm)", col.lab=rgb(0,0,0), line=3.5, cex.lab=1.5)
+title(main='S cone',cex.main=2)
+for (cond in 1:3){
+  lines(contrastsfinedB,modrespsS2[condlist2[cond],], col=colpal[condlist[cond]], lwd=3, cex=0.5)
+  # lines(contrastsdB,abs(cleanmeansP[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)
+  arrows(contrastsdB,abs(cleanmasksP2[condlist[cond],]),contrastsdB,cleanmasksP2CI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  arrows(contrastsdB,abs(cleanmasksP2[condlist[cond],]),contrastsdB,cleanmasksP2CI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  points(contrastsdB,abs(cleanmasksP2[condlist[cond],]), pch = 20+cond, col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
+}  
+text(17,0.014,'(h)',adj=0.5,cex=2.5)
+
+load(file=paste0(datadir,'AveragedataMel.RData'))
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims2[1:2], ylim=plotlims2[3:4])   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy2, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
+mtext(text = ticklabelsy2, side = 2, at=ticklocsy2, line=0.2, las=1) 
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)    # titles for axes
+title(ylab="Amplitude at 0.8Hz (mm)", col.lab=rgb(0,0,0), line=3.5, cex.lab=1.5)
+title(main='Melanopsin',cex.main=2)
+for (cond in 1:3){
+  lines(contrastsfinedB,modrespsMel2[condlist2[cond],], col=colpal[condlist[cond]], lwd=3, cex=0.5)
+  # lines(contrastsdB,abs(cleanmeansP[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)
+  arrows(contrastsdB,abs(cleanmasksP2[condlist[cond],]),contrastsdB,cleanmasksP2CI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  arrows(contrastsdB,abs(cleanmasksP2[condlist[cond],]),contrastsdB,cleanmasksP2CI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  points(contrastsdB,abs(cleanmasksP2[condlist[cond],]), pch = 20+cond, col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
+}  
+text(17,0.014,'(i)',adj=0.5,cex=2.5)
 
@@
 The anatomical pathway from the retina to the subcortical nuclei controlling the pupillary light response (PLR) is well established: it includes the Pretectal Olivary nucleus (PON), the Superior Cervical ganglion and the Edinger-Westphal nucleus, which project to the iris sphincter muscles that directly control the pupil size [@McDougal2008; @McDougal2015; @Wang2015].
-Evidence of a binocular component to the PLR is shown by the existence of a consensual response of the pupil [the stimulation of one eye will cause constriction of the other eye; @Wyatt1981].
+Evidence of a binocular component to the PLR is shown by the existence of a consensual response of the pupil [the stimulation of one eye will cause constriction of the other eye\; @Wyatt1981].
 The anatomical segregation of the subcortical pathway from the rest of the brain means that this binocular combination of signals must occur independently of the cortical processes of binocular integration required for visual perception.
@@
 
-Different classes of retinal photoreceptors, including cones, rods and the recently discovered melanopsin-containing intrinsically photosensitive retinal ganglion cells (ipRGCs), are directly involved in controlling and maintaining the size of the pupils [@Barrionuevo2014; @Barrionuevo2018; @Dacey2005; @Murray2018; @Spitschan2014; @Spitschan2019; @Woelders2018].
+Different classes of retinal photoreceptors, including cones, rods and melanopsin-containing intrinsically photosensitive retinal ganglion cells (ipRGCs), are directly involved in controlling and maintaining the size of the pupils [@Barrionuevo2014; @Barrionuevo2018; @Dacey2005; @Murray2018; @Spitschan2014; @Spitschan2019; @Woelders2018].
 The cones have been shown to drive the initial rapid constriction of the pupils [@Mathot2018], while the slower and longer activation of the ipRGCs shows their role in maintaining the constriction over a prolonged period of time and in regulating the post-illumination pupillary response [@Markwell2010; @McDougal2010].
@@
 Silent substitution exploits the fact that each photoreceptor class has a distinct spectral tuning that overlaps with the others.
-Using a multiprimary system, in which the primaries have different spectra, it is possible to target one class of photoreceptors while maintaining the others at a constant activity level, effectively silencing them [@Shapiro1996; @Spitschan2018, this paper also offers a clear explanation of how to implement silent substitution].
+Using a multiprimary system, in which the primaries (i.e.
+LEDs) have different spectra, it is possible to target one class of photoreceptors while maintaining the others at a constant activity level, effectively silencing them [@Shapiro1996; @Spitschan2018, this paper also offers a clear explanation of how to implement silent substitution].
 Studies using silent substitution have shown that the pupils behave differently depending on which photoreceptor or pathway is being stimulated.
 For example, pupil responses have been shown to be out of phase when the S cones are stimulated, relative to when the ipRGCs or the L+M cones are stimulated [@Spitschan2014; @Cao2015].
-Additionally, when L and M cones are stimulated individually, there appears to be a paradoxical pupil response: increments in L cone stimulation cause a constriction of the pupil, while increments in M cone stimulation lead to a dilation of the pupil [@Woelders2018; @Murray2018].
+Additionally, when L and M cones are stimulated individually, there appears to be a paradoxical pupil response: increments in L cone stimulation cause a constriction of the pupil, while increments in M cone stimulation lead to a dilation of the pupil [@Woelders2018; @Murray2018], perhaps due to activity in the L-M opponent pathway.
 
 Binocular combination has been extensively studied in visual perception, where it is mediated by neurons in primary visual cortex [@Hubel1962; @Moradi2009].
-For pattern vision, binocular summation occurs at threshold, such that less contrast is required to detect a target shown to both eyes than for a target shown to only one eye [@Baker2018; @Campbell1965; @Legge1984].
+For pattern vision, binocular summation occurs at threshold, such that a lower contrast is required to detect a target shown to both eyes than a target shown to only one eye [@Baker2018; @Campbell1965; @Legge1984].
 At higher contrasts, a process of 'ocularity invariance' is observed, in which the response to monocularly- and binocularly-presented patterns is equal [@Baker2007; @Ding2006; @Meese2006; @Moradi2009].
@@
 Here we take a different approach, using a custom binocular multiprimary system (see Figure \@ref(fig:spectraplots)a,b) that can modulate each (undilated) eye independently, and a binocular eye tracker to measure the diameter of both pupils.
-We measure the amplitude of pupil modulation (using Fourier analysis) in response to sinusoidal stimulation at 0.5Hz, for stimuli directed at the luminnce pathway, L-M cone pathway, S-cone pathway, and melanopsin pathway.
-Our key comparisons are between monocular and binocular stimulation, and between monocular stimulation and a dichoptic masking condition in which the non-target eye is stimulated by a high contrast mask signal at a different frequency (0.4Hz).
-The results are interpreted using a contemporary model of binocular vision [@Meese2006] implemented within a hierarchical Bayesian framework
+We measure the amplitude of pupil modulation (using Fourier analysis) in response to sinusoidal stimulation at 0.5Hz, for stimuli directed at the luminance pathway, L-M cone pathway, S-cone pathway, and melanopsin pathway (see Figure \@ref(fig:spectraplots)e-l).
+Our key comparisons are between monocular and binocular stimulation, and between monocular stimulation and a dichoptic masking condition in which the two eyes are stimulated at different frequencies (0.5 and 0.4Hz).
+The results are interpreted using a contemporary model of binocular vision [@Meese2006] implemented within a hierarchical Bayesian framework.
 
@@
 We also observed a second harmonic response (at 1Hz) for all conditions, which was weaker than the first harmonic for luminance and melanopsin stimulation, but stronger for L-M and S-cone stimulation.
-The additional component is also apparent in the pupil waveforms shown in Figure \@ref(fig:spectraplots)n-p.
+The second harmonic is also apparent in the pupil waveforms shown in Figure \@ref(fig:spectraplots)n-p.
 Our main analysis therefore focuses on the amplitude of the pupil modulations at both the first and second harmonic frequencies across different stimulus conditions.
@@
 
-Figure \@ref(fig:CRFplots) shows contrast response functions across stimulation conditions for responses at the first harmonic (panels a-d) and the second harmonic (panels e-h) frequencies.
-In each plot, the response to monocular stimulation is given by the red circles and typically increases monotonically as a function of stimulus (temporal) contrast (main effects of stimulus contrast are significant for all data sets, see Supplementary Materials).
-Relative to monocular stimulation, binocular stimulation typically led to higher response amplitudes, indicating a binocular facilitation effect (main effects of condition are significant for all data sets, see Supplementary Materials).
-This is strongest for the luminance and S-cone conditions at the first harmonic (Figure \@ref(fig:CRFplots)a,c) and the L-M cone and Melanopsin conditions at the second harmonic (Figure \@ref(fig:CRFplots)f,h).
-One striking exception to this pattern is in the L-M cone condition at the first harmonic (Figure \@ref(fig:CRFplots)b): this condition produced a binocular suppression effect, where the response to binocular stimulation is weaker than the response to monocular stimulation (blue squares below red circles).
+Figure \@ref(fig:FirstHarmonicPlots)a-d shows contrast response functions across stimulation conditions for responses at the first harmonic of the main stimulation frequency (0.5Hz).
+In each plot, the response to monocular stimulation is given by the red circles and typically increases monotonically as a function of stimulus (temporal) contrast.
+Relative to monocular stimulation, binocular stimulation led to higher response amplitudes, indicating a binocular facilitation effect, for the luminance and S-cone conditions (Figure \@ref(fig:FirstHarmonicPlots)a,c), and to some extent for the melanopsin condition (Figure \@ref(fig:FirstHarmonicPlots)d).
+However, the L-M cone condition (Figure \@ref(fig:FirstHarmonicPlots)b) produced a binocular suppression effect, where the response to binocular stimulation was weaker than the response to monocular stimulation (blue squares below red circles).
 These results indicate that the magnitude of binocular facilitation differs across photoreceptor pathway, suggesting heterogeneity in the underlying neural computation.
 
-```{r CRFplots, fig.cap="Contrast response functions for monocular (red circles), binocular (blue squares) and dichoptic (yellow diamonds) conditions, for stimulation of different pathways (columns) at the first and second harmonic frequencies (rows).
-Error bars indicate bootstrapped 95\\% confidence intervals", fig.align="center", echo=FALSE}
-
-knitr::include_graphics(paste0(figdir,'CRFs.pdf'))
+```{r FirstHarmonicPlots, fig.cap="Contrast response functions for pupil modualations in response to flicker at 0.5Hz (panels a-d), and 0.4Hz (panels f-i), and posterior parameter distributions for the weight of interocular suppression (panel e).
+Within each panel (except panel e), data points are the coherently averaged amplitudes for each condition, and error bars indicate bootstrapped 95\\% confidence intervals.
+Curves show model fits using the maximum a posteriori (MAP) parameter values (see Table 1).
+In panel (e), vertical lines show the MAP estimates, and the thin black curve indicates the prior (note the logarithmic x-axis).", fig.align="center", echo=FALSE}
+
+knitr::include_graphics(paste0(figdir,'FirstHarmonic.pdf'))
 
@@
 In contemporary models of binocular signal combination, the amount of binocular facilitation is determined by the magnitude of interocular suppression, with strong suppression reducing facilitation [@Kingdom2015].
-We can estimate the strength of interocular suppression by measuring how much monocular responses are reduced when a high contrast dichoptic mask is shown to the other eye.
-In our paradigm, this mask flickered at a lower frequency (0.4Hz) so that the two stimulus components remain distinct in the Fourier spectrum [e.g.
+We can estimate the strength of interocular suppression by measuring how much monocular responses are reduced when a dichoptic 'mask' is shown to the other eye.
+In our paradigm, the two components flickered at different frequencies (0.5 and 0.4Hz) so that their responses remained distinct in the Fourier spectrum [e.g.
 @Busse2009].
-The yellow diamond symbols in Figure \@ref(fig:CRFplots) show the target responses in this condition, and in most cases are weaker than the monocular responses (red circles).
-The strongest dichoptic masking is found in the first harmonic L-M condition, where we also observed the binocular suppression effect.
-
-```{r suppressionfig, fig.cap="P.", fig.align="center", echo=FALSE}
-
-knitr::include_graphics(paste0(figdir,'suppressionfig.pdf'))
+The yellow diamond symbols in Figure \@ref(fig:FirstHarmonicPlots)a-d show the target responses in this condition, and in most cases were weaker than the monocular responses (red circles).
+The strongest dichoptic masking is found in the L-M condition, where we also observed the binocular suppression effect.
+Suppression can also be estimated from the responses at 0.4Hz (Figure \@ref(fig:FirstHarmonicPlots)f-i).
+The reduced amplitude in the binocular cross condition (purple squares) relative to the 0.4Hz monocular condition (grey circles), and the progressive decline in amplitude of the dichoptic cross response (yellow diamonds) also differ across photoreceptor conditions, showing similar differences to those observed at 0.5Hz.
+
+To quantify the extent of suppression for each photoreceptor pathway, we fitted each data set using a Bayesian hierarchical implementation of a simple binocular combination model [@Meese2006; @Segala2023].
+Our primary objective was to compare posterior distributions of the weight of interocular suppression, which are shown in Figure \@ref(fig:FirstHarmonicPlots)e.
+Consistent with our earlier observations, the strongest suppressive weight corresponds to the L-M and Melanopsin conditions, and the weakest suppression corresponds to the luminance and S-cone conditions, with virtually no overlap between the posterior distributions for weak and strong suppression.
+The model fits were of good quality, as shown by the curves in Figure \@ref(fig:FirstHarmonicPlots)a-d,f-i.
+The fitted model parameters are given in Table \@ref(tab:paramtable).
+
+```{r paramtable, echo=FALSE}
+
+condnames <- c('Luminance 1F','L-M 1F','S 1F','Melanopsin 1F','Luminance 2F','L-M 2F','S 2F','Melanopsin 2F')
+zlist <- c(pupilZLum, pupilZLM, pupilZS, pupilZMel, pupilZLum2, pupilZLM2, pupilZS2, pupilZMel2)
+klist <- c(pupilKLum, pupilKLM, pupilKS, pupilKMel, pupilKLum2, pupilKLM2, pupilKS2, pupilKMel2)
+wlist <- c(pupilWLum, pupilWLM, pupilWS, pupilWMel, pupilWLum2, pupilWLM2, pupilWS2, pupilWMel2)
+plist <- c(pupilPLum, pupilPLM, pupilPS, pupilPMel, pupilPLum2, pupilPLM2, pupilPS2, pupilPMel2)
+qlist <- c(pupilQLum, pupilQLM, pupilQS, pupilQMel, pupilQLum2, pupilQLM2, pupilQS2, pupilQMel2)
+Rlist <- c(pupilRmaxLum, pupilRmaxLM, pupilRmaxS, pupilRmaxMel, pupilRmaxLum2, pupilRmaxLM2, pupilRmaxS2, pupilRmaxMel2)
+tabledata <- data.frame(condnames,round(zlist,digits=2),round(klist,digits=5),round(wlist,digits=2),round(plist,digits=2),round(qlist,digits=2),round(Rlist,digits=4))
+
+colnames(tabledata) <- c('Experiment','Z','k','w','p','q','Rmax')
+kable(tabledata, align='lcccccc',booktabs=TRUE,linesep='',caption = 'Summary of maximum a posteriori (MAP) parameter estimates for each data set.') %>%
+kableExtra::kable_styling(latex_options = "HOLD_position") %>% row_spec(4,hline_after=TRUE)
 
@@
 
-Next, we fitted all 8 data sets using a Bayesian hierarchical implementation of a simple binocular combination model [@Meese2006; @Segala2023].
-Our primary objective was to compare posterior distributions of the weight of interocular suppression, which are shown in Figure \@ref(fig:suppressionfig).
-Consistent with our earlier observations, at the first harmonic the strongest suppressive weight corresponds to the L-M condition, and the weakest suppression corresponds to the luminance condition [also consistent with @Segala2023].
-The model fits were of good quality, as shown by the curves in Figure \@ref(fig:CRFplots).
-Further details of fitted parameters, and model behaviour in other empirical conditions are provided in the Supplementary Materials.
-We used the model fits to summarise the relationship between binocular facilitation and interocular suppression by calculating an index for each effect, and show that the facilitation effect is negatively correlated with the dichoptic masking effect (see Figure \@ref(fig:suppressionfig)).
+At the second harmonic frequencies, the levels of suppression were more uniform across different photoreceptor pathways (see Figure \@ref(fig:SecondHarmonicPlots)).
+In general, suppression estimates were near or above 1 (see lower rows of Table \@ref(tab:paramtable)), with substantial overlap between the posterior distributions (Figure \@ref(fig:SecondHarmonicPlots)e).
+The contrast response functions also looked more uniform, and generally involved less binocular facilitation and more interocular suppression than were seen at the first harmonics.
+The L-M condition now featured the weakest suppressive weight, and the strongest binocular facilitation, which was the opposite pattern seen at the first harmonic.
+
+```{r SecondHarmonicPlots, fig.cap="Responses at the second harmonic frequencies (1Hz and 0.8Hz), in the same format as Figure 2.", fig.align="center", echo=FALSE}
+
+knitr::include_graphics(paste0(figdir,'SecondHarmonic.pdf'))
+
+```
 
@@
 At the first harmonic, melanopsin and S-cone signals differed in phase by more than 90 degrees, though they were not fully in antiphase.
-The luminance and L-M responses were more closely in antiphase to each other, however this is likely due to our choice to modulate L+M- in the first half-cycle (corresponding to a luminance increase in the luminance condition), and L-M+ in the second half-cycle (corresponding to a luminance decrease in the luminance condition).
-Had we reversed this phase arrangement, we would likely have seen a close phase correspondence between the L-M and luminance conditions.
+The luminance and L-M responses were approximately in antiphase to each other, however this is likely due to our choice to modulate L+M- in the first half-cycle (corresponding to a luminance increase in the luminance condition), and L-M+ in the second half-cycle (corresponding to a luminance decrease in the luminance condition).
+Had we reversed this phase arrangement, we would likely have seen a close phase correspondence between the L-M and luminance conditions (another way to think about this is that L-cone decreases and M-cone increases are processed like luminance increases).
 Phase differences between the luminance, S-cone and melanopsin conditions are likely attributable to different lags in phototransduction at the earliest stage (i.e.
@@
 We found that, at the first harmonic frequency, the L-M pathway had a bigger suppression weight than the other pathways, while, at the second harmonic frequency, the S-(L+M) pathway had a bigger suppression weight.
-Finally, we looked at the pupil phases and observed different behaviours for the different pathways at the first and second harmonic frequencies.
-While the patterns differed between the first and second harmonics, within the same harmonic, whether the stimuli were presented monocularly or binocularly, the patterns were similar.
-
-Our four experiments produced results that we were expecting based on our previous pupillometry findings [@Segala2023]: the signals between the 2 pupils are combined non-linearly regardless of which photoreceptor pathway is being stimulated and whether the fovea or the periphery of the retina is being stimulated.
+Finally, we looked at the pupil phases and observed different lag times for the different pathways at the first and second harmonic frequencies.
+
+Our four experiments produced results that we were expecting based on our previous pupillometry findings [@Segala2023]: the signals from the two retinae are combined non-linearly regardless of which photoreceptor pathway is being stimulated and whether the fovea or the periphery of the retina is being stimulated.
 We also observed responses at both the first and the second harmonic frequencies, which were expected based on previous literature [@Spitschan2014; @Stark1957; @Verdon1988].
@@
 It is true that we had already observed second harmonic responses when stimulating the periphery of the retina with achromatic luminance modulations flickering at 2 Hz (see Figure \@ref(fig:appendixfig1)b), but the peak was very small when compared to the first harmonic peak, which is similar to what we observed in the luminance experiment here.
-On the other hand, in the melanopsin and L-M pathway experiments, the first and second harmonics are similar in amplitudes, and in the S-(L+M) pathway experiment, the peak of the second harmonic is even bigger than the peak of the first harmonic.
+On the other hand, in the melanopsin and L-M pathway experiments, the first and second harmonics are similar in amplitude, and in the S-(L+M) pathway experiment, the peak of the second harmonic is even bigger than the peak of the first harmonic.
 One reason for why this might be happening may be because the driving signal is stronger when using a lower flicker frequency [indeed, pupillometry is more responsive to slow flicker frequencies of less than 1 Hz, @Spitschan2014] and when stimulating the periphery of the retina (we have a very clear waveform for the luminance experiment in Figure \@ref(fig:pupildataLum)b).
@@
 
-Twenty-four participants were recruited for each of the four experiments for a total of ninety-six (68 females) adult participants, whose ages ranged from 18 to 41.
-All participants had normal or corrected to normal binocular vision and normal colour vision, and gave written informed consent.
+Twenty-four participants were recruited for each of the four experiments for a total of ninety-six adult participants (28 male, 68 female), whose ages ranged from 18 to 41.
+All participants had normal or corrected to normal vision, no known abnormalities of binocular or colour vision, and gave written informed consent.
 Our procedures were approved by the Ethics Committee of the Department of Psychology at the University of York (identification number 184).
@@
 
-To present synchronised stimulus modulations independently to each eye, two light engines, each with 10 independently addressable LED colour channels (SpectraTuneLAB: LEDMOTIVE Technologies, LLC, Barcelona, Spain), were integrated into a customised viewing system.
+To present synchronised stimulus modulations independently to each eye, two light engines (SpectraTuneLAB: LEDMOTIVE Technologies, LLC, Barcelona, Spain), each with 10 independently addressable LED colour channels, were integrated into a customised viewing system.
 The light engines were operated via a Python interface to their REST API [@Martin2022], which supports synchronous launch and playback of spectral sequences prepared in advance and stored in JSON format.
-When preparing the spectral sequences, the age of participants was recorded to account for the yellowing of the lenses.
+When preparing the spectral sequences, the age of participants was used to account for the yellowing of the lenses.
 We calculated silent substitution solutions using the _PySilSub_ toolbox [@Martin2023], using linear algebra.
@@
 Initial pilot experiments indicated that this frequency was too high to elicit measurable responses when stimulating individual photoreceptor pathways.
-For all experiments, we therefore used a primary flicker frequency of 0.5Hz, as previous literature showed that it was slow enough to elicit a pupil response from all photoreceptor classes [@Spitschan2014].
-We also focussed on only recording pupillometry data as this frequency would be well below the minimum threshold to elicit steady-state EEG responses [@Norcia2015].
+For all experiments, we therefore used a primary flicker frequency of 0.5Hz, as previous literature showed that this was slow enough to elicit a pupil response from all photoreceptor classes [@Spitschan2014].
+We also focussed on only recording pupillometry data as this frequency would be too slow to elicit steady-state EEG responses [@Norcia2015].
 
@@
 Before the start of each experiment, participants adjusted the objective planes of the lenses with the help of the experimenter until the stimulus was in focus and they perceived the two pieces of blackout material as one fused disc.
-Pupil responses to binocular temporal contrast modulations were examined in a factorial design that combined six ocular conditions and five temporal contrast levels (6, 12, 24, 48 and 96%) of the available dynamic range.
+Pupil responses to binocular temporal contrast modulations were examined in a factorial design that combined six ocular conditions and five temporal contrast levels: 6, 12, 24, 48 and 96% of the available dynamic range.
 This design, similar to that used in our previous studies [@Segala2023; @Baker2017; @Baker2020], was applied in four separate experiments, each with a different mode of photoreceptor stimulation.
@@
 In the remaining three conditions (the cross-frequency conditions) one eye’s disc flickered at 0.4 Hz, and the other eye’s disc flickered at 0.5 Hz.
-We also tested monocular responses at 0.4 Hz, as well as binocular (one eye sees each frequency at the target contrast) and dichoptic (target stimulus flickering at 0.5 Hz, mask contrast of 48% at 0.4 Hz in the other eye) arrangements.
+This included monocular responses at 0.4 Hz, as well as binocular (one eye sees each frequency at the target contrast) and dichoptic (target stimulus flickering at 0.5 Hz, mask contrast of 48% at 0.4 Hz in the other eye) arrangements.
 We counterbalanced presentation of the target stimulus across the left and right eyes.
@@
 The participants sat as close as possible to the VR headset, leaving enough space for the eye-tracker to record the eyes.
-The experiment was carried out in a single session of around 45-60 minutes, divided into three blocks of 15-17 minutes each.
+Each experiment was carried out in a single session of around 45-60 minutes, divided into three blocks of 15-17 minutes each.
 In each block, there were a total of 60 trials lasting 15 seconds each (12s of stimulus presentation, followed by 3s of interstimulus interval).
 The participants were given no task other than look at the black fixation dot while trying to minimise their blinking during the presentation period.
-For all experiments other than the luminance condition, participants adapted to the mean luminance for two minutes before stimulation began.
+For all experiments other than the luminance condition, participants adapted to the unmodulated background luminance for two minutes before stimulation began.
 
@@
 
-To describe our data, we chose the same model described in our previous study [@Segala2023].
-The model has the same general form as the first stage of the contrast gain control model proposed by @Meese2006 and omits the second stage.
+To describe our data, we used the same model described in our previous study [@Segala2023].
+The model has the same general form as the first stage of the contrast gain control model proposed by @Meese2006, but omits the second stage.
 For the previous model that we used [@Segala2023], the exponent of the numerator and denominator had fixed values of 2 and (implicitly) 1.
 Here, we allow these parameters (called _p_ and _q_) to be free, in order to permit different shapes of contrast response function, e.g.
-saturating or super-saturating.
+accelerating or saturating.
 The responses of the left eye and right eye channels are as follows:
@@
 \begin{equation}
-\label{eq:respLchap4}
-Resp_L = \frac{L^p}{Z + L^q + wR^q},
+\label{eq:respL}
+resp_L = \frac{L^p}{Z + L^q + \omega R^q},
 \end{equation}
@@
 \begin{equation}
-\label{eq:respRchap4}
-Resp_R = \frac{R^p}{Z + R^q + wL^q},
+\label{eq:respR}
+resp_R = \frac{R^p}{Z + R^q + \omega L^q},
 \end{equation}
 
-\noindent where _L_ and _R_ are the contrast signals from the left and right eyes, _p_ and _q_ are exponents, _Z_ is a saturation constant that shifts the contrast-response function laterally, and _w_ is the weight of suppression from the other eye.
+\noindent where _L_ and _R_ are the contrast signals from the left and right eyes, _p_ and _q_ are exponents, _Z_ is a saturation constant that shifts the contrast-response function laterally, and $\omega$ is the weight of suppression from the other eye.
 
@@
 \begin{equation}
-\label{eq:respBchap4}
-Resp_B = R_{max}(Resp_L + Resp_R) + k,
+\label{eq:respB}
+resp_B = R_{max}(resp_L + resp_R) + k,
 \end{equation}
@@
 
-We performed model fitting on the normalised amplitudes to account for amplitude differences between the experiments.
 The models were fit using a hierarchical Bayesian framework implemented in Stan [@Carpenter2017].
 The data for each photoreceptor type and response frequency was fit separately, for a total of 8 model fits.
-The prior
+The prior for the $\omega$ parameter was Gaussian, with a mean of 1 and standard deviation of 0.5.
+Priors for the other free parameters were also Gaussian, with mean values based on previous work [@Segala2023].
+We calculated over `r numSavedSteps*thinSteps` posterior samples, and retained `r 100*1/thinSteps`% for plotting.
 
@@
 <div id='refs'> </div>
-
-# Supplementary Materials
-
-```{r paramtable1F, echo=FALSE}
-
-condnames <- c('Luminance 1F', 'Melanopsin 1F', 'L-M 1F', 'S 1F')
-zlist <- c(pupilZLum, pupilZMel, pupilZLM, pupilZS)
-klist <- c(pupilKLum, pupilKMel, pupilKLM, pupilKS)
-wlist <- c(pupilWLum, pupilWMel, pupilWLM, pupilWS)
-plist <- c(pupilPLum, pupilPMel, pupilPLM, pupilPS)
-qlist <- c(pupilQLum, pupilQMel, pupilQLM, pupilQS)
-Rlist <- c(round(c(pupilRmaxLum, pupilRmaxMel, pupilRmaxLM, pupilRmaxS),5))
-tabledata <- data.frame(condnames,round(zlist,digits=2),round(klist,digits=2),round(wlist,digits=2),round(plist,digits=2),round(qlist,digits=2),Rlist)
-
-colnames(tabledata) <- c('Experiment','Z','k','w','p','q','Rmax')
-kable(tabledata, align='lcccccc',caption = 'Summary of median parameter values at the first harmonic frequency.')
-
-```
-
-```{r paramtable2F, echo=FALSE}
-
-condnames <- c('Luminance 2F', 'Melanopsin 2F', 'L-M 2F', 'S 2F')
-zlist <- c(pupilZLum2, pupilZMel2, pupilZLM2, pupilZS2)
-klist <- c(pupilKLum2, pupilKMel2, pupilKLM2, pupilKS2)
-wlist <- c(pupilWLum2, pupilWMel2, pupilWLM2, pupilWS2)
-plist <- c(pupilPLum2, pupilPMel2, pupilPLM2, pupilPS2)
-qlist <- c(pupilQLum2, pupilQMel2, pupilQLM2, pupilQS2)
-Rlist <- c(round(c(pupilRmaxLum2, pupilRmaxMel2, pupilRmaxLM2, pupilRmaxS2),5))
-tabledata <- data.frame(condnames,round(zlist,digits=2),round(klist,digits=2),round(wlist,digits=2),round(plist,digits=2),round(qlist,digits=2),Rlist)
-
-colnames(tabledata) <- c('Experiment','Z','k','w','p','q','Rmax')
-kable(tabledata, align='lcccccc',caption = 'Summary of median parameter values at the second harmonic frequency.')
-
-```

### 2024-05-07 manuscript.tex
Revised modelling and data presentation

@@
 \title{Binocular combination in the autonomic nervous system}
-\author{Federico G. Segala\(^1\), Joel T. Martin\(^1\), Annie Y. Morsi\(^1\), Alex R. Wade\(^{1,2}\) \& Daniel H. Baker\(^{1,2}\)}
+\author{Federico G. Segala\(^1\), Joel T. Martin\(^{1,2}\), Annie Y. Morsi\(^1\), Alex R. Wade\(^{1,3}\) \& Daniel H. Baker\(^{1,3}\)}
 \date{}
@@
 
-\(^2\)York Biomedical Research Institute, University of York, Heslington, York, United Kingdom.
+\(^2\)School of Philosophy, Psychology and Language Sciences, University of Edinburgh, Edinburgh, United Kingdom.
+
+\(^3\)York Biomedical Research Institute, University of York, Heslington, York, United Kingdom.
 
@@
 The anatomical pathway from the retina to the subcortical nuclei controlling the pupillary light response (PLR) is well established: it includes the Pretectal Olivary nucleus (PON), the Superior Cervical ganglion and the Edinger-Westphal nucleus, which project to the iris sphincter muscles that directly control the pupil size (\protect\hyperlink{ref-McDougal2015}{McDougal and Gamlin, 2015}, \protect\hyperlink{ref-McDougal2008}{2008}; \protect\hyperlink{ref-Wang2015}{Wang and Munoz, 2015}).
-Evidence of a binocular component to the PLR is shown by the existence of a consensual response of the pupil {[}the stimulation of one eye will cause constriction of the other eye; Wyatt and Musselman (\protect\hyperlink{ref-Wyatt1981}{1981}){]}.
+Evidence of a binocular component to the PLR is shown by the existence of a consensual response of the pupil (the stimulation of one eye will cause constriction of the other eye; \protect\hyperlink{ref-Wyatt1981}{Wyatt and Musselman, 1981}).
 The anatomical segregation of the subcortical pathway from the rest of the brain means that this binocular combination of signals must occur independently of the cortical processes of binocular integration required for visual perception.
@@
 
-Different classes of retinal photoreceptors, including cones, rods and the recently discovered melanopsin-containing intrinsically photosensitive retinal ganglion cells (ipRGCs), are directly involved in controlling and maintaining the size of the pupils (\protect\hyperlink{ref-Barrionuevo2018}{Barrionuevo et al., 2018}; \protect\hyperlink{ref-Barrionuevo2014}{Barrionuevo et al., 2014}; \protect\hyperlink{ref-Dacey2005}{Dacey et al., 2005}; \protect\hyperlink{ref-Murray2018}{Murray et al., 2018}; \protect\hyperlink{ref-Spitschan2019}{Spitschan, 2019}; \protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}; \protect\hyperlink{ref-Woelders2018}{Woelders et al., 2018}).
+Different classes of retinal photoreceptors, including cones, rods and melanopsin-containing intrinsically photosensitive retinal ganglion cells (ipRGCs), are directly involved in controlling and maintaining the size of the pupils (\protect\hyperlink{ref-Barrionuevo2018}{Barrionuevo et al., 2018}; \protect\hyperlink{ref-Barrionuevo2014}{Barrionuevo et al., 2014}; \protect\hyperlink{ref-Dacey2005}{Dacey et al., 2005}; \protect\hyperlink{ref-Murray2018}{Murray et al., 2018}; \protect\hyperlink{ref-Spitschan2019}{Spitschan, 2019}; \protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}; \protect\hyperlink{ref-Woelders2018}{Woelders et al., 2018}).
 The cones have been shown to drive the initial rapid constriction of the pupils (\protect\hyperlink{ref-Mathot2018}{Mathôt, 2018}), while the slower and longer activation of the ipRGCs shows their role in maintaining the constriction over a prolonged period of time and in regulating the post-illumination pupillary response (\protect\hyperlink{ref-Markwell2010}{Markwell et al., 2010}; \protect\hyperlink{ref-McDougal2010}{McDougal and Gamlin, 2010}).
@@
 Silent substitution exploits the fact that each photoreceptor class has a distinct spectral tuning that overlaps with the others.
-Using a multiprimary system, in which the primaries have different spectra, it is possible to target one class of photoreceptors while maintaining the others at a constant activity level, effectively silencing them (\protect\hyperlink{ref-Shapiro1996}{Shapiro et al., 1996}; \protect\hyperlink{ref-Spitschan2018}{Spitschan and Woelders, 2018}, this paper also offers a clear explanation of how to implement silent substitution).
+Using a multiprimary system, in which the primaries (i.e.~LEDs) have different spectra, it is possible to target one class of photoreceptors while maintaining the others at a constant activity level, effectively silencing them (\protect\hyperlink{ref-Shapiro1996}{Shapiro et al., 1996}; \protect\hyperlink{ref-Spitschan2018}{Spitschan and Woelders, 2018}, this paper also offers a clear explanation of how to implement silent substitution).
 Studies using silent substitution have shown that the pupils behave differently depending on which photoreceptor or pathway is being stimulated.
 For example, pupil responses have been shown to be out of phase when the S cones are stimulated, relative to when the ipRGCs or the L+M cones are stimulated (\protect\hyperlink{ref-Cao2015}{Cao et al., 2015}; \protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}).
-Additionally, when L and M cones are stimulated individually, there appears to be a paradoxical pupil response: increments in L cone stimulation cause a constriction of the pupil, while increments in M cone stimulation lead to a dilation of the pupil (\protect\hyperlink{ref-Murray2018}{Murray et al., 2018}; \protect\hyperlink{ref-Woelders2018}{Woelders et al., 2018}).
+Additionally, when L and M cones are stimulated individually, there appears to be a paradoxical pupil response: increments in L cone stimulation cause a constriction of the pupil, while increments in M cone stimulation lead to a dilation of the pupil (\protect\hyperlink{ref-Murray2018}{Murray et al., 2018}; \protect\hyperlink{ref-Woelders2018}{Woelders et al., 2018}), perhaps due to activity in the L-M opponent pathway.
 
 Binocular combination has been extensively studied in visual perception, where it is mediated by neurons in primary visual cortex (\protect\hyperlink{ref-Hubel1962}{Hubel and Wiesel, 1962}; \protect\hyperlink{ref-Moradi2009}{Moradi and Heeger, 2009}).
-For pattern vision, binocular summation occurs at threshold, such that less contrast is required to detect a target shown to both eyes than for a target shown to only one eye (\protect\hyperlink{ref-Baker2018}{Baker et al., 2018}; \protect\hyperlink{ref-Campbell1965}{Campbell and Green, 1965}; \protect\hyperlink{ref-Legge1984}{Legge, 1984}).
+For pattern vision, binocular summation occurs at threshold, such that a lower contrast is required to detect a target shown to both eyes than a target shown to only one eye (\protect\hyperlink{ref-Baker2018}{Baker et al., 2018}; \protect\hyperlink{ref-Campbell1965}{Campbell and Green, 1965}; \protect\hyperlink{ref-Legge1984}{Legge, 1984}).
 At higher contrasts, a process of `ocularity invariance' is observed, in which the response to monocularly- and binocularly-presented patterns is equal (\protect\hyperlink{ref-Baker2007}{Baker et al., 2007}; \protect\hyperlink{ref-Ding2006}{Ding and Sperling, 2006}; \protect\hyperlink{ref-Meese2006}{Meese et al., 2006}; \protect\hyperlink{ref-Moradi2009}{Moradi and Heeger, 2009}).
@@
 Here we take a different approach, using a custom binocular multiprimary system (see Figure \ref{fig:spectraplots}a,b) that can modulate each (undilated) eye independently, and a binocular eye tracker to measure the diameter of both pupils.
-We measure the amplitude of pupil modulation (using Fourier analysis) in response to sinusoidal stimulation at 0.5Hz, for stimuli directed at the luminnce pathway, L-M cone pathway, S-cone pathway, and melanopsin pathway.
-Our key comparisons are between monocular and binocular stimulation, and between monocular stimulation and a dichoptic masking condition in which the non-target eye is stimulated by a high contrast mask signal at a different frequency (0.4Hz).
-The results are interpreted using a contemporary model of binocular vision (\protect\hyperlink{ref-Meese2006}{Meese et al., 2006}) implemented within a hierarchical Bayesian framework
+We measure the amplitude of pupil modulation (using Fourier analysis) in response to sinusoidal stimulation at 0.5Hz, for stimuli directed at the luminance pathway, L-M cone pathway, S-cone pathway, and melanopsin pathway (see Figure \ref{fig:spectraplots}e-l).
+Our key comparisons are between monocular and binocular stimulation, and between monocular stimulation and a dichoptic masking condition in which the two eyes are stimulated at different frequencies (0.5 and 0.4Hz).
+The results are interpreted using a contemporary model of binocular vision (\protect\hyperlink{ref-Meese2006}{Meese et al., 2006}) implemented within a hierarchical Bayesian framework.
 
@@
 We also observed a second harmonic response (at 1Hz) for all conditions, which was weaker than the first harmonic for luminance and melanopsin stimulation, but stronger for L-M and S-cone stimulation.
-The additional component is also apparent in the pupil waveforms shown in Figure \ref{fig:spectraplots}n-p.~Our main analysis therefore focuses on the amplitude of the pupil modulations at both the first and second harmonic frequencies across different stimulus conditions.
+The second harmonic is also apparent in the pupil waveforms shown in Figure \ref{fig:spectraplots}n-p.~Our main analysis therefore focuses on the amplitude of the pupil modulations at both the first and second harmonic frequencies across different stimulus conditions.
 
@@
 
-Figure \ref{fig:CRFplots} shows contrast response functions across stimulation conditions for responses at the first harmonic (panels a-d) and the second harmonic (panels e-h) frequencies.
-In each plot, the response to monocular stimulation is given by the red circles and typically increases monotonically as a function of stimulus (temporal) contrast (main effects of stimulus contrast are significant for all data sets, see Supplementary Materials).
-Relative to monocular stimulation, binocular stimulation typically led to higher response amplitudes, indicating a binocular facilitation effect (main effects of condition are significant for all data sets, see Supplementary Materials).
-This is strongest for the luminance and S-cone conditions at the first harmonic (Figure \ref{fig:CRFplots}a,c) and the L-M cone and Melanopsin conditions at the second harmonic (Figure \ref{fig:CRFplots}f,h).
-One striking exception to this pattern is in the L-M cone condition at the first harmonic (Figure \ref{fig:CRFplots}b): this condition produced a binocular suppression effect, where the response to binocular stimulation is weaker than the response to monocular stimulation (blue squares below red circles).
+Figure \ref{fig:FirstHarmonicPlots}a-d shows contrast response functions across stimulation conditions for responses at the first harmonic of the main stimulation frequency (0.5Hz).
+In each plot, the response to monocular stimulation is given by the red circles and typically increases monotonically as a function of stimulus (temporal) contrast.
+Relative to monocular stimulation, binocular stimulation led to higher response amplitudes, indicating a binocular facilitation effect, for the luminance and S-cone conditions (Figure \ref{fig:FirstHarmonicPlots}a,c), and to some extent for the melanopsin condition (Figure \ref{fig:FirstHarmonicPlots}d).
+However, the L-M cone condition (Figure \ref{fig:FirstHarmonicPlots}b) produced a binocular suppression effect, where the response to binocular stimulation was weaker than the response to monocular stimulation (blue squares below red circles).
 These results indicate that the magnitude of binocular facilitation differs across photoreceptor pathway, suggesting heterogeneity in the underlying neural computation.
@@
 
-{\centering \includegraphics{Figures/CRFs}
+{\centering \includegraphics{Figures/FirstHarmonic}
 
@@
 
-\caption{Contrast response functions for monocular (red circles), binocular (blue squares) and dichoptic (yellow diamonds) conditions, for stimulation of different pathways (columns) at the first and second harmonic frequencies (rows).
-Error bars indicate bootstrapped 95\% confidence intervals}\label{fig:CRFplots}
+\caption{Contrast response functions for pupil modualations in response to flicker at 0.5Hz (panels a-d), and 0.4Hz (panels f-i), and posterior parameter distributions for the weight of interocular suppression (panel e).
+Within each panel (except panel e), data points are the coherently averaged amplitudes for each condition, and error bars indicate bootstrapped 95\% confidence intervals.
+Curves show model fits using the maximum a posteriori (MAP) parameter values (see Table 1).
+In panel (e), vertical lines show the MAP estimates, and the thin black curve indicates the prior (note the logarithmic x-axis).}\label{fig:FirstHarmonicPlots}
 \end{figure}
@@
 In contemporary models of binocular signal combination, the amount of binocular facilitation is determined by the magnitude of interocular suppression, with strong suppression reducing facilitation (\protect\hyperlink{ref-Kingdom2015}{Kingdom and Libenson, 2015}).
-We can estimate the strength of interocular suppression by measuring how much monocular responses are reduced when a high contrast dichoptic mask is shown to the other eye.
-In our paradigm, this mask flickered at a lower frequency (0.4Hz) so that the two stimulus components remain distinct in the Fourier spectrum (e.g.
+We can estimate the strength of interocular suppression by measuring how much monocular responses are reduced when a dichoptic `mask' is shown to the other eye.
+In our paradigm, the two components flickered at different frequencies (0.5 and 0.4Hz) so that their responses remained distinct in the Fourier spectrum (e.g.
 \protect\hyperlink{ref-Busse2009}{Busse et al., 2009}).
-The yellow diamond symbols in Figure \ref{fig:CRFplots} show the target responses in this condition, and in most cases are weaker than the monocular responses (red circles).
-The strongest dichoptic masking is found in the first harmonic L-M condition, where we also observed the binocular suppression effect.
+The yellow diamond symbols in Figure \ref{fig:FirstHarmonicPlots}a-d show the target responses in this condition, and in most cases were weaker than the monocular responses (red circles).
+The strongest dichoptic masking is found in the L-M condition, where we also observed the binocular suppression effect.
+Suppression can also be estimated from the responses at 0.4Hz (Figure \ref{fig:FirstHarmonicPlots}f-i).
+The reduced amplitude in the binocular cross condition (purple squares) relative to the 0.4Hz monocular condition (grey circles), and the progressive decline in amplitude of the dichoptic cross response (yellow diamonds) also differ across photoreceptor conditions, showing similar differences to those observed at 0.5Hz.
+
+To quantify the extent of suppression for each photoreceptor pathway, we fitted each data set using a Bayesian hierarchical implementation of a simple binocular combination model (\protect\hyperlink{ref-Meese2006}{Meese et al., 2006}; \protect\hyperlink{ref-Segala2023}{Segala et al., 2023}).
+Our primary objective was to compare posterior distributions of the weight of interocular suppression, which are shown in Figure \ref{fig:FirstHarmonicPlots}e.
+Consistent with our earlier observations, the strongest suppressive weight corresponds to the L-M and Melanopsin conditions, and the weakest suppression corresponds to the luminance and S-cone conditions, with virtually no overlap between the posterior distributions for weak and strong suppression.
+The model fits were of good quality, as shown by the curves in Figure \ref{fig:FirstHarmonicPlots}a-d,f-i.
+The fitted model parameters are given in Table \ref{tab:paramtable}.
+
+\begin{table}[H]
+
+\caption{\label{tab:paramtable}Summary of maximum a posteriori (MAP) parameter estimates for each data set.}
+\centering
+\begin{tabular}[t]{lcccccc}
+\toprule
+Experiment & Z & k & w & p & q & Rmax\\
+\midrule
+Luminance 1F & 95.77 & 0.00083 & 0.37 & 1.32 & 1.24 & 0.0905\\
+L-M 1F & 49.82 & 0.00109 & 1.71 & 1.50 & 1.21 & 0.0032\\
+S 1F & 63.00 & 0.00121 & 0.39 & 1.94 & 1.79 & 0.0042\\
+Melanopsin 1F & 79.61 & 0.00094 & 1.71 & 1.29 & 0.76 & 0.0025\\
+\midrule
+Luminance 2F & 48.81 & 0.00089 & 1.24 & 1.15 & 0.88 & 0.0039\\
+L-M 2F & 66.00 & 0.00075 & 0.95 & 1.10 & 0.82 & 0.0050\\
+S 2F & 75.94 & 0.00097 & 2.22 & 1.41 & 0.83 & 0.0018\\
+Melanopsin 2F & 67.94 & 0.00101 & 1.37 & 0.90 & 0.49 & 0.0035\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+At the second harmonic frequencies, the levels of suppression were more uniform across different photoreceptor pathways (see Figure \ref{fig:SecondHarmonicPlots}).
+In general, suppression estimates were near or above 1 (see lower rows of Table \ref{tab:paramtable}), with substantial overlap between the posterior distributions (Figure \ref{fig:SecondHarmonicPlots}e).
+The contrast response functions also looked more uniform, and generally involved less binocular facilitation and more interocular suppression than were seen at the first harmonics.
+The L-M condition now featured the weakest suppressive weight, and the strongest binocular facilitation, which was the opposite pattern seen at the first harmonic.
 
@@
 
-{\centering \includegraphics{Figures/suppressionfig}
+{\centering \includegraphics{Figures/SecondHarmonic}
 
@@
 
-\caption{P.}\label{fig:suppressionfig}
+\caption{Responses at the second harmonic frequencies (1Hz and 0.8Hz), in the same format as Figure 2.}\label{fig:SecondHarmonicPlots}
 \end{figure}
-
-Next, we fitted all 8 data sets using a Bayesian hierarchical implementation of a simple binocular combination model (\protect\hyperlink{ref-Meese2006}{Meese et al., 2006}; \protect\hyperlink{ref-Segala2023}{Segala et al., 2023}).
-Our primary objective was to compare posterior distributions of the weight of interocular suppression, which are shown in Figure \ref{fig:suppressionfig}.
-Consistent with our earlier observations, at the first harmonic the strongest suppressive weight corresponds to the L-M condition, and the weakest suppression corresponds to the luminance condition (also consistent with \protect\hyperlink{ref-Segala2023}{Segala et al., 2023}).
-The model fits were of good quality, as shown by the curves in Figure \ref{fig:CRFplots}.
-Further details of fitted parameters, and model behaviour in other empirical conditions are provided in the Supplementary Materials.
-We used the model fits to summarise the relationship between binocular facilitation and interocular suppression by calculating an index for each effect, and show that the facilitation effect is negatively correlated with the dichoptic masking effect (see Figure \ref{fig:suppressionfig}).
 
@@
 At the first harmonic, melanopsin and S-cone signals differed in phase by more than 90 degrees, though they were not fully in antiphase.
-The luminance and L-M responses were more closely in antiphase to each other, however this is likely due to our choice to modulate L+M- in the first half-cycle (corresponding to a luminance increase in the luminance condition), and L-M+ in the second half-cycle (corresponding to a luminance decrease in the luminance condition).
-Had we reversed this phase arrangement, we would likely have seen a close phase correspondence between the L-M and luminance conditions.
+The luminance and L-M responses were approximately in antiphase to each other, however this is likely due to our choice to modulate L+M- in the first half-cycle (corresponding to a luminance increase in the luminance condition), and L-M+ in the second half-cycle (corresponding to a luminance decrease in the luminance condition).
+Had we reversed this phase arrangement, we would likely have seen a close phase correspondence between the L-M and luminance conditions (another way to think about this is that L-cone decreases and M-cone increases are processed like luminance increases).
 Phase differences between the luminance, S-cone and melanopsin conditions are likely attributable to different lags in phototransduction at the earliest stage (i.e.~in the retina).
@@
 We found that, at the first harmonic frequency, the L-M pathway had a bigger suppression weight than the other pathways, while, at the second harmonic frequency, the S-(L+M) pathway had a bigger suppression weight.
-Finally, we looked at the pupil phases and observed different behaviours for the different pathways at the first and second harmonic frequencies.
-While the patterns differed between the first and second harmonics, within the same harmonic, whether the stimuli were presented monocularly or binocularly, the patterns were similar.
+Finally, we looked at the pupil phases and observed different lag times for the different pathways at the first and second harmonic frequencies.
 
-Our four experiments produced results that we were expecting based on our previous pupillometry findings (\protect\hyperlink{ref-Segala2023}{Segala et al., 2023}): the signals between the 2 pupils are combined non-linearly regardless of which photoreceptor pathway is being stimulated and whether the fovea or the periphery of the retina is being stimulated.
+Our four experiments produced results that we were expecting based on our previous pupillometry findings (\protect\hyperlink{ref-Segala2023}{Segala et al., 2023}): the signals from the two retinae are combined non-linearly regardless of which photoreceptor pathway is being stimulated and whether the fovea or the periphery of the retina is being stimulated.
 We also observed responses at both the first and the second harmonic frequencies, which were expected based on previous literature (\protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}; \protect\hyperlink{ref-Stark1957}{Stark and Sherman, 1957}; \protect\hyperlink{ref-Verdon1988}{Verdon and Howarth, 1988}).
@@
 It is true that we had already observed second harmonic responses when stimulating the periphery of the retina with achromatic luminance modulations flickering at 2 Hz (see Figure \ref{fig:appendixfig1}b), but the peak was very small when compared to the first harmonic peak, which is similar to what we observed in the luminance experiment here.
-On the other hand, in the melanopsin and L-M pathway experiments, the first and second harmonics are similar in amplitudes, and in the S-(L+M) pathway experiment, the peak of the second harmonic is even bigger than the peak of the first harmonic.
+On the other hand, in the melanopsin and L-M pathway experiments, the first and second harmonics are similar in amplitude, and in the S-(L+M) pathway experiment, the peak of the second harmonic is even bigger than the peak of the first harmonic.
 One reason for why this might be happening may be because the driving signal is stronger when using a lower flicker frequency (indeed, pupillometry is more responsive to slow flicker frequencies of less than 1 Hz, \protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}) and when stimulating the periphery of the retina (we have a very clear waveform for the luminance experiment in Figure \ref{fig:pupildataLum}b).
@@
 
-To present synchronised stimulus modulations independently to each eye, two light engines, each with 10 independently addressable LED colour channels (SpectraTuneLAB: LEDMOTIVE Technologies, LLC, Barcelona, Spain), were integrated into a customised viewing system.
+To present synchronised stimulus modulations independently to each eye, two light engines (SpectraTuneLAB: LEDMOTIVE Technologies, LLC, Barcelona, Spain), each with 10 independently addressable LED colour channels, were integrated into a customised viewing system.
 The light engines were operated via a Python interface to their REST API (\protect\hyperlink{ref-Martin2022}{Martin et al., 2022}), which supports synchronous launch and playback of spectral sequences prepared in advance and stored in JSON format.
-When preparing the spectral sequences, the age of participants was recorded to account for the yellowing of the lenses.
+When preparing the spectral sequences, the age of participants was used to account for the yellowing of the lenses.
 We calculated silent substitution solutions using the \emph{PySilSub} toolbox (\protect\hyperlink{ref-Martin2023}{Martin et al., 2023}), using linear algebra.
@@
 Initial pilot experiments indicated that this frequency was too high to elicit measurable responses when stimulating individual photoreceptor pathways.
-For all experiments, we therefore used a primary flicker frequency of 0.5Hz, as previous literature showed that it was slow enough to elicit a pupil response from all photoreceptor classes (\protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}).
-We also focussed on only recording pupillometry data as this frequency would be well below the minimum threshold to elicit steady-state EEG responses (\protect\hyperlink{ref-Norcia2015}{Norcia et al., 2015}).
+For all experiments, we therefore used a primary flicker frequency of 0.5Hz, as previous literature showed that this was slow enough to elicit a pupil response from all photoreceptor classes (\protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}).
+We also focussed on only recording pupillometry data as this frequency would be too slow to elicit steady-state EEG responses (\protect\hyperlink{ref-Norcia2015}{Norcia et al., 2015}).
 
@@
 Before the start of each experiment, participants adjusted the objective planes of the lenses with the help of the experimenter until the stimulus was in focus and they perceived the two pieces of blackout material as one fused disc.
-Pupil responses to binocular temporal contrast modulations were examined in a factorial design that combined six ocular conditions and five temporal contrast levels (6, 12, 24, 48 and 96\%) of the available dynamic range.
+Pupil responses to binocular temporal contrast modulations were examined in a factorial design that combined six ocular conditions and five temporal contrast levels: 6, 12, 24, 48 and 96\% of the available dynamic range.
 This design, similar to that used in our previous studies (\protect\hyperlink{ref-Baker2020}{Baker et al., 2020}; \protect\hyperlink{ref-Baker2017}{Baker and Wade, 2017}; \protect\hyperlink{ref-Segala2023}{Segala et al., 2023}), was applied in four separate experiments, each with a different mode of photoreceptor stimulation.
@@
 In the remaining three conditions (the cross-frequency conditions) one eye's disc flickered at 0.4 Hz, and the other eye's disc flickered at 0.5 Hz.
-We also tested monocular responses at 0.4 Hz, as well as binocular (one eye sees each frequency at the target contrast) and dichoptic (target stimulus flickering at 0.5 Hz, mask contrast of 48\% at 0.4 Hz in the other eye) arrangements.
+This included monocular responses at 0.4 Hz, as well as binocular (one eye sees each frequency at the target contrast) and dichoptic (target stimulus flickering at 0.5 Hz, mask contrast of 48\% at 0.4 Hz in the other eye) arrangements.
 We counterbalanced presentation of the target stimulus across the left and right eyes.
@@
 
-For all experiments, we used a bootstrapping procedure with 1000 iterations to estimate standard errors across participants.
+For all experiments, we used a bootstrapping procedure with \ensuremath{10^{4}} iterations to estimate standard errors across participants.
 All analysis and figure construction was conducted using a single R-script, available online, making this study fully computationally reproducible: \url{https://osf.io/gdvt4/}.
@@
 
-To describe our data, we chose the same model described in our previous study (\protect\hyperlink{ref-Segala2023}{Segala et al., 2023}).
+To describe our data, we used the same model described in our previous study (\protect\hyperlink{ref-Segala2023}{Segala et al., 2023}).
 The model has the same general form as the first stage of the contrast gain control model proposed by Meese et al.
-(\protect\hyperlink{ref-Meese2006}{2006}) and omits the second stage.
+(\protect\hyperlink{ref-Meese2006}{2006}), but omits the second stage.
 For the previous model that we used (\protect\hyperlink{ref-Segala2023}{Segala et al., 2023}), the exponent of the numerator and denominator had fixed values of 2 and (implicitly) 1.
-Here, we allow these parameters (called \emph{p} and \emph{q}) to be free, in order to permit different shapes of contrast response function, e.g.~saturating or super-saturating.
+Here, we allow these parameters (called \emph{p} and \emph{q}) to be free, in order to permit different shapes of contrast response function, e.g.~accelerating or saturating.
 The responses of the left eye and right eye channels are as follows:
@@
 \begin{equation}
-\label{eq:respRchap4}
-Resp_R = \frac{R^p}{Z + R^q + wL^q},
+\label{eq:respR}
+resp_R = \frac{R^p}{Z + R^q + \omega L^q},
 \end{equation}
 
-\noindent where \emph{L} and \emph{R} are the contrast signals from the left and right eyes, \emph{p} and \emph{q} are exponents, \emph{Z} is a saturation constant that shifts the contrast-response function laterally, and \emph{w} is the weight of suppression from the other eye.
+\noindent where \emph{L} and \emph{R} are the contrast signals from the left and right eyes, \emph{p} and \emph{q} are exponents, \emph{Z} is a saturation constant that shifts the contrast-response function laterally, and \(\omega\) is the weight of suppression from the other eye.
 
@@
 
-We performed model fitting on the normalised amplitudes to account for amplitude differences between the experiments.
 The models were fit using a hierarchical Bayesian framework implemented in Stan (\protect\hyperlink{ref-Carpenter2017}{Carpenter et al., 2017}).
 The data for each photoreceptor type and response frequency was fit separately, for a total of 8 model fits.
-The prior
+The prior for the \(\omega\) parameter was Gaussian, with a mean of 1 and standard deviation of 0.5.
+Priors for the other free parameters were also Gaussian, with mean values based on previous work (\protect\hyperlink{ref-Segala2023}{Segala et al., 2023}).
+We calculated over \ensuremath{10^{6}} posterior samples, and retained 10\% for plotting.
 
@@
 
-\hypertarget{supplementary-materials}{%
-\section{Supplementary Materials}\label{supplementary-materials}}
-
-\begin{table}
-
-\caption{\label{tab:paramtable1F}Summary of median parameter values at the first harmonic frequency.}
-\centering
-\begin{tabular}[t]{l|c|c|c|c|c|c}
-\hline
-Experiment & Z & k & w & p & q & Rmax\\
-\hline
-Luminance 1F & 96.61 & 0 & 0.37 & 1.34 & 1.28 & 0.08258\\
-\hline
-Melanopsin 1F & 72.80 & 0 & 1.62 & 1.18 & 0.64 & 0.00259\\
-\hline
-L-M 1F & 62.89 & 0 & 1.52 & 1.54 & 1.28 & 0.00287\\
-\hline
-S 1F & 61.56 & 0 & 1.40 & 0.41 & 1.08 & 0.04916\\
-\hline
-\end{tabular}
-\end{table}
-
-\begin{table}
-
-\caption{\label{tab:paramtable2F}Summary of median parameter values at the second harmonic frequency.}
-\centering
-\begin{tabular}[t]{l|c|c|c|c|c|c}
-\hline
-Experiment & Z & k & w & p & q & Rmax\\
-\hline
-Luminance 2F & 63.38 & 0 & 1.17 & 1.17 & 0.94 & 0.00652\\
-\hline
-Melanopsin 2F & 68.76 & 0 & 1.40 & 0.88 & 0.50 & 0.00368\\
-\hline
-L-M 2F & 74.12 & 0 & 0.85 & 1.19 & 0.85 & 0.00472\\
-\hline
-S 2F & 77.31 & 0 & 1.91 & 1.36 & 0.77 & 0.00211\\
-\hline
-\end{tabular}
-\end{table}
-
 \end{document}

### 2024-05-07 checkforoutliers.R

@@ -1,601 +1,0 @@
-
-processdata <- 2
-
-library(FourierStats)
-# cut off for data inclusion (Mahalanobis distance for complex data)
-SDthresh <<- 99
-nbootstraps <<- 1000
-
-localdir <- 'local/'    # all files are stored in the project directory /local/ which git is told to ignore
-if (!file.exists(localdir)){dir.create(localdir)}   # create a local directory to store data and outputs
-rawdir <- 'local/rawdata/'
-if (!file.exists(rawdir)){dir.create(rawdir)}   # create a local directory to store raw data
-figdir <- 'Figures/'
-if (!file.exists(figdir)){dir.create(figdir)}   # create a local directory to store figures
-datadir <- 'local/processeddata/'
-if (!file.exists(datadir)){dir.create(datadir)}   # create a local directory to store processed data
-
-# files from P301-P324 are for S-cone stimulation
-# files from P501-P524 are for melanopsin stimulation
-# files from P601-P624 are for luminance stimulation
-# files from P701-P724 are for (L-M) cone stimulation
-
-# load in individual participant data and average, save group data
-if (processdata > 1){
-  
-  prefixlist <- c('P6','P7','P3','P5')
-  exptnames <- c('AveragedataLumA.RData','AveragedataLMA.RData','AveragedataSA.RData','AveragedataMelA.RData')
-  
-  includedvalues <- array(0,dim=c(4,24,6,5))
-  includedvalues2 <- array(0,dim=c(4,24,6,5))
-  
-  for (expt in 1:4){
-    d <- dir(datadir,pattern=prefixlist[expt], full.names = TRUE)
-    
-    tempmasksP <- array(0,dim=c(length(d),6,5))
-    tempmeansP <- tempmasksP
-    tempmeansP2 <- tempmasksP
-    tempmasksP2 <- tempmasksP
-    tempspectraP <- array(0,dim=c(length(d),300))
-    tempwavesP <- array(0,dim=c(length(d),1680))
-    
-    for (s in 1:length(d)){
-      
-      load(d[s])
[…]

### 2024-05-07 extraplottingchunks.R

@@ -1,1183 +1,0 @@
-```{r luminance plot, include=FALSE, results='hide'}
-
-load(file=paste0(datadir,'AveragedataLum.RData'))
-
-# generate plot showing the group pupillometry data for the luminance condition
-if (processdata > 0){
-
-allPLumratios <- abs(cleanmeansP[2,])/abs(cleanmeansP[1,])
-allPLum2ratios <- abs(cleanmeansP2[2,])/abs(cleanmeansP2[1,])
-
-# plot figure
-plotlims <- c(15,40,0,3)
-ticklocsx <- contrastsdB
-ticklabelsx <-c(6,12,24,48,96)
-ticklocsy <- seq(0,3,0.5)    # locations of tick marks on y axis
-ticklabelsy <- ticklocsy
-
-postscript("SumLum.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
-
-par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx)
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
-title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)
-title(ylab="Bin:Mon ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-
-lines(contrastsdB,allPLumratios, col=colpal[1], lwd=3, cex=0.5)
-lines(contrastsdB,allPLum2ratios, col=colpal[2], lwd=3, cex=0.5)
-points(contrastsdB,allPLumratios, pch = 21, col='black', bg=colpal[1], cex=1.6, lwd=3)
-points(contrastsdB,allPLum2ratios, pch = 22, col='black', bg=colpal[2], cex=1.6, lwd=3)
-
-legend(contrastsdB[4],3,c('Lum 1F','Lum 2F'), pch=21:24, pt.bg=colpal[1:2],box.lwd=2,pt.cex=1.6,pt.lwd=3)
-text(17,2.8,'(c)',adj=0.5,cex=2.5)
-
-dev.off()
-
[…]

### 2024-05-08 manuscript.Rmd
Edits to discussion

@@
 
-processdata <- 1  # this flag determines the amount of processing, with 4 levels:
+processdata <- 0  # this flag determines the amount of processing, with 4 levels:
 # 0 - do no processing, generate the pdf using existing versions of all figures
@@
 
-condnames <- c('Luminance 1F','L-M 1F','S 1F','Melanopsin 1F','Luminance 2F','L-M 2F','S 2F','Melanopsin 2F')
+condnames <- c('Luminance 1F','L-M cone 1F','S cone 1F','Melanopsin 1F','Luminance 2F','L-M cone 2F','S cone 2F','Melanopsin 2F')
 zlist <- c(pupilZLum, pupilZLM, pupilZS, pupilZMel, pupilZLum2, pupilZLM2, pupilZS2, pupilZMel2)
@@
 
-We used pupillometry and silent substitution to measure monocular and binocular responses of the pupils to flickering stimuli when stimulating specific photoreceptor pathways.
-In our luminance experiment, we found that peripheral stimulation of the retina can elicit a pupillary response and we were also able to record a response at the second harmonic, which was not seen when we stimulated the fovea [@Segala2023].
-In all four experiments, we were able to record contrast response functions at both the first and the second harmonics.
+We used binocular pupillometry and silent substitution to measure monocular and binocular responses of the pupils to flickering stimuli when stimulating specific photoreceptor pathways.
+In all four experiments, we were able to record contrast response functions at both the first and the second harmonic frequencies.
 All experiments showed that binocular combination in the autonomic nervous system happens in a non-linear manner, with evidence of different magnitudes of interocular suppression depending on the photoreceptor pathway.
 This pattern of results was confirmed by a computational model, which allowed us to compare the weight of interocular suppression for each pathway.
-We found that, at the first harmonic frequency, the L-M pathway had a bigger suppression weight than the other pathways, while, at the second harmonic frequency, the S-(L+M) pathway had a bigger suppression weight.
-Finally, we looked at the pupil phases and observed different lag times for the different pathways at the first and second harmonic frequencies.
-
-Our four experiments produced results that we were expecting based on our previous pupillometry findings [@Segala2023]: the signals from the two retinae are combined non-linearly regardless of which photoreceptor pathway is being stimulated and whether the fovea or the periphery of the retina is being stimulated.
-We also observed responses at both the first and the second harmonic frequencies, which were expected based on previous literature [@Spitschan2014; @Stark1957; @Verdon1988].
-There was, however, one aspect of our results that we were surprised to observe: the amplitude of this second harmonic response in the different photoreceptor pathways.
-It is true that we had already observed second harmonic responses when stimulating the periphery of the retina with achromatic luminance modulations flickering at 2 Hz (see Figure \@ref(fig:appendixfig1)b), but the peak was very small when compared to the first harmonic peak, which is similar to what we observed in the luminance experiment here.
-On the other hand, in the melanopsin and L-M pathway experiments, the first and second harmonics are similar in amplitude, and in the S-(L+M) pathway experiment, the peak of the second harmonic is even bigger than the peak of the first harmonic.
-One reason for why this might be happening may be because the driving signal is stronger when using a lower flicker frequency [indeed, pupillometry is more responsive to slow flicker frequencies of less than 1 Hz, @Spitschan2014] and when stimulating the periphery of the retina (we have a very clear waveform for the luminance experiment in Figure \@ref(fig:pupildataLum)b).
-However, this explanation is not entirely satisfactory: we observed a second harmonic when stimulating the periphery using a higher flicker frequency and the pupil waveforms from the other three experiments are not as clear as the one from the luminance experiment.
-The presence of a second harmonic might indicate the existence of non-linearities that are not observable in the fovea: indeed, steady-state visual responses can contain activity beyond the first harmonic and these harmonics reflect non-linearities (e.g.
-squaring, exponentiation, rectification) in the visual response [@Norcia2015].
-Additionally, it can be the case that, when these non-linearities are strong, then the higher harmonics can have equal or even higher peaks than the first harmonic.
-Here, we did observe strong non-linearities in our photoreceptor pathways, as reflected by the interocular suppression weights that were output by our computational model.
-For the S-(L+M) pathway specifically, it seems that the higher peak of the second harmonic is a behaviour intrinsic to S cones, as this was observed previously [@Spitschan2014].
-
-The pupil phases shown in Figure \@ref(fig:phaseplots) give us more information about the pathways controlling the pupil response.
-The first thing that we  notice is that the luminance and L-M pathway responses are in anti-phase.
-It is important to note that, for our L-M pathway stimulation, the stimulus flickered between magenta (first half of the cycle) and cyan (second half of the cycle), which means that the pupil was dilating during the magenta stimulation and then constricting during the cyan presentation.
-This seems to suggest that increments in magenta would correspond to decrements in brightness and increments in cyan would correspond to increments in brightness.
-It is possible that, if we had reversed the presentation cycle for the L-M pathway, the pupil response would have been in phase with the luminance responses.
-It has been recently shown that L-cone and melanopsin stimulation induce an opponent pupillary response to M- and S-cone stimulation [@Murray2018; @Woelders2018].
-Our melanopsin and S-(L+M) results show a similar behaviour both for monocular and binocular responses.
-The L-M pathways results are desynchronised approximately in quadrature phase from the melanopsin and S-(L+M) results.
-These results also seem to align with what was previously found: combining L and M responses should display results that are between the opponency shown by the isolated cone stimulation.
-Additionally, this could explain the very strong suppression that binocular (L-M) stimulation displays compared to the monocular stimulation: if L and M produce pupil responses that are in anti-phase with each other, then combining the two together should elicit smaller responses.
-Finally, since the results from our experiments are not in phase, it would suggest that the photoreceptors control the pupil diameter through different pathways.
+We found that at the first harmonic frequency the L-M and melanopsin pathways involved strong suppression, whereas the luminance and S-cone pathways involved weaker suppression.
+Suppression was strong in all four pathways at the second harmonic frequency.
+Finally, the phase of the pupil response revealed different lag times for the different pathways at the first and second harmonic frequencies.
+
+This is the first study to investigate binocular interactions in the melanopsin pathway directly.
+A previous meta-analysis [@Spitschan2019] indicated that there may be a substantial binocular facilitation effect in the circadian pathway, as indexed by melatonin suppression (melatonin is a hormone released by the pineal gland; its production is suppressed by exposure to bright light, particularly when the melanopsin-containing ipRGCs are stimulated).
+In brief, monocular stimulation of the ipRGCs requires up to ten times the signal strength to produce an equivalent effect to binocular stimulation.
+This superadditive effect implies an absence of interocular suppression, and perhaps the presence of either a highly compressive nonlinearity, or an AND-style neural operation.
+Our findings here are very different - we do not see substantial binocular facilitation effects in response to melanopsin modulation, and our data indicate that interocular suppression is very strong.
+Moreover, by measuring the full contrast response function, we can rule out compressive nonlinearities, because the functions accelerate at both the first and second harmonic frequencies.
+The explanation for this difference could be due to different anatomical pathways.
+Binocular combination in the circadian system likely takes place in the suprachiasmatic nucleus, whereas in the pupil constriction circuit the Edinger-Westphal nucleus is the most likely site of binocular integration [@Mathot2018].
+Presumably these anatomical differences, and the practical constraints of the two systems, lead to differences in response.
+
+Our recent psychophysical work [@Baker2024] has looked at binocular interactions in the L-M and S-cone pathways, and compared these to the luminance pathway.
+Using a contrast discrimination paradigm with spatial modulations of luminance and colour, @Baker2024 found equally strong interocular suppression in all three pathways.
+This is rather different from our pupillometry results here, which demonstrate weaker suppression in the luminance and S-cone pathways than in the L-M pathway (see Figure \@ref(fig:FirstHarmonicPlots)).
+However, the current experiments involve temporal modulations, which are quite distinct from the spatial modulations used in @Baker2024.
+Our other recent work [@Segala2023] has shown that temporal luminance modulations involve much weaker interocular suppression in the cortical response than do spatial luminance modulations [@Baker2017].
+These different normalization processes might reflect different priorities for spatial and temporal vision.
+Spatial vision aims to fuse images to provide binocular single vision, and benefits from 'ocularity invariance' [@Baker2007], in which visual appearance is constant when viewed with one eye or two.
+Temporal vision is critical for motion perception, which can involve alternative binocular computations, such as calculating velocity differences between the eyes [@Kaestner2019].
+Of course the present measurements were of pupil size, which may be subject to different anatomical and functional constraints from those in the cortex.
+Future research should aim to extend our current findings to perception using psychophysical approaches.
 
@@
 We have demonstrated that binocular combination of temporal flickering light in the autonomic nervous system depends on the photoreceptor pathway.
-We were able to elicit pupil responses by stimulating only the periphery of the retina and we were able to record contrast response functions for all photoreceptor pathways.
-While all pathways showed non-linear combination, they showed a variation in how the signals are combined, particularly in the weight of interocular suppression.
+We were able to elicit pupil responses by stimulating the periphery of the retina and we were able to record contrast response functions for all photoreceptor pathways.
+While all pathways showed non-linear combination, they varied in how the signals are combined, particularly in the weight of interocular suppression.
+This was strong ($\omega \ge 1$) for L-M and melanopsin signals at the first harmonic, and all pathways at the second harmonic.
+Suppression was weaker ($\omega < 1$) in the luminance pathway (consistent with previous work), and also for S-cone directed modulations.
 

### 2024-05-08 manuscript.tex
Edits to discussion

@@
 
-Different classes of retinal photoreceptors, including cones, rods and melanopsin-containing intrinsically photosensitive retinal ganglion cells (ipRGCs), are directly involved in controlling and maintaining the size of the pupils (\protect\hyperlink{ref-Barrionuevo2018}{Barrionuevo et al., 2018}; \protect\hyperlink{ref-Barrionuevo2014}{Barrionuevo et al., 2014}; \protect\hyperlink{ref-Dacey2005}{Dacey et al., 2005}; \protect\hyperlink{ref-Murray2018}{Murray et al., 2018}; \protect\hyperlink{ref-Spitschan2019}{Spitschan, 2019}; \protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}; \protect\hyperlink{ref-Woelders2018}{Woelders et al., 2018}).
+Different classes of retinal photoreceptors, including cones, rods and melanopsin-containing intrinsically photosensitive retinal ganglion cells (ipRGCs), are directly involved in controlling and maintaining the size of the pupils (\protect\hyperlink{ref-Barrionuevo2018}{Barrionuevo et al., 2018}; \protect\hyperlink{ref-Barrionuevo2014}{Barrionuevo et al., 2014}; \protect\hyperlink{ref-Dacey2005}{Dacey et al., 2005}; \protect\hyperlink{ref-Murray2018}{Murray et al., 2018}; \protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}; \protect\hyperlink{ref-Spitschan2019}{Spitschan and Cajochen, 2019}; \protect\hyperlink{ref-Woelders2018}{Woelders et al., 2018}).
 The cones have been shown to drive the initial rapid constriction of the pupils (\protect\hyperlink{ref-Mathot2018}{Mathôt, 2018}), while the slower and longer activation of the ipRGCs shows their role in maintaining the constriction over a prolonged period of time and in regulating the post-illumination pupillary response (\protect\hyperlink{ref-Markwell2010}{Markwell et al., 2010}; \protect\hyperlink{ref-McDougal2010}{McDougal and Gamlin, 2010}).
@@
 Luminance 1F & 95.77 & 0.00083 & 0.37 & 1.32 & 1.24 & 0.0905\\
-L-M 1F & 49.82 & 0.00109 & 1.71 & 1.50 & 1.21 & 0.0032\\
-S 1F & 63.00 & 0.00121 & 0.39 & 1.94 & 1.79 & 0.0042\\
+L-M cone 1F & 49.82 & 0.00109 & 1.71 & 1.50 & 1.21 & 0.0032\\
+S cone 1F & 63.00 & 0.00121 & 0.39 & 1.94 & 1.79 & 0.0042\\
 Melanopsin 1F & 79.61 & 0.00094 & 1.71 & 1.29 & 0.76 & 0.0025\\
@@
 Luminance 2F & 48.81 & 0.00089 & 1.24 & 1.15 & 0.88 & 0.0039\\
-L-M 2F & 66.00 & 0.00075 & 0.95 & 1.10 & 0.82 & 0.0050\\
-S 2F & 75.94 & 0.00097 & 2.22 & 1.41 & 0.83 & 0.0018\\
+L-M cone 2F & 66.00 & 0.00075 & 0.95 & 1.10 & 0.82 & 0.0050\\
+S cone 2F & 75.94 & 0.00097 & 2.22 & 1.41 & 0.83 & 0.0018\\
 Melanopsin 2F & 67.94 & 0.00101 & 1.37 & 0.90 & 0.49 & 0.0035\\
@@
 
-We used pupillometry and silent substitution to measure monocular and binocular responses of the pupils to flickering stimuli when stimulating specific photoreceptor pathways.
-In our luminance experiment, we found that peripheral stimulation of the retina can elicit a pupillary response and we were also able to record a response at the second harmonic, which was not seen when we stimulated the fovea (\protect\hyperlink{ref-Segala2023}{Segala et al., 2023}).
-In all four experiments, we were able to record contrast response functions at both the first and the second harmonics.
+We used binocular pupillometry and silent substitution to measure monocular and binocular responses of the pupils to flickering stimuli when stimulating specific photoreceptor pathways.
+In all four experiments, we were able to record contrast response functions at both the first and the second harmonic frequencies.
 All experiments showed that binocular combination in the autonomic nervous system happens in a non-linear manner, with evidence of different magnitudes of interocular suppression depending on the photoreceptor pathway.
 This pattern of results was confirmed by a computational model, which allowed us to compare the weight of interocular suppression for each pathway.
-We found that, at the first harmonic frequency, the L-M pathway had a bigger suppression weight than the other pathways, while, at the second harmonic frequency, the S-(L+M) pathway had a bigger suppression weight.
-Finally, we looked at the pupil phases and observed different lag times for the different pathways at the first and second harmonic frequencies.
+We found that at the first harmonic frequency the L-M and melanopsin pathways involved strong suppression, whereas the luminance and S-cone pathways involved weaker suppression.
+Suppression was strong in all four pathways at the second harmonic frequency.
+Finally, the phase of the pupil response revealed different lag times for the different pathways at the first and second harmonic frequencies.
 
-Our four experiments produced results that we were expecting based on our previous pupillometry findings (\protect\hyperlink{ref-Segala2023}{Segala et al., 2023}): the signals from the two retinae are combined non-linearly regardless of which photoreceptor pathway is being stimulated and whether the fovea or the periphery of the retina is being stimulated.
-We also observed responses at both the first and the second harmonic frequencies, which were expected based on previous literature (\protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}; \protect\hyperlink{ref-Stark1957}{Stark and Sherman, 1957}; \protect\hyperlink{ref-Verdon1988}{Verdon and Howarth, 1988}).
-There was, however, one aspect of our results that we were surprised to observe: the amplitude of this second harmonic response in the different photoreceptor pathways.
-It is true that we had already observed second harmonic responses when stimulating the periphery of the retina with achromatic luminance modulations flickering at 2 Hz (see Figure \ref{fig:appendixfig1}b), but the peak was very small when compared to the first harmonic peak, which is similar to what we observed in the luminance experiment here.
-On the other hand, in the melanopsin and L-M pathway experiments, the first and second harmonics are similar in amplitude, and in the S-(L+M) pathway experiment, the peak of the second harmonic is even bigger than the peak of the first harmonic.
-One reason for why this might be happening may be because the driving signal is stronger when using a lower flicker frequency (indeed, pupillometry is more responsive to slow flicker frequencies of less than 1 Hz, \protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}) and when stimulating the periphery of the retina (we have a very clear waveform for the luminance experiment in Figure \ref{fig:pupildataLum}b).
-However, this explanation is not entirely satisfactory: we observed a second harmonic when stimulating the periphery using a higher flicker frequency and the pupil waveforms from the other three experiments are not as clear as the one from the luminance experiment.
-The presence of a second harmonic might indicate the existence of non-linearities that are not observable in the fovea: indeed, steady-state visual responses can contain activity beyond the first harmonic and these harmonics reflect non-linearities (e.g.~squaring, exponentiation, rectification) in the visual response (\protect\hyperlink{ref-Norcia2015}{Norcia et al., 2015}).
-Additionally, it can be the case that, when these non-linearities are strong, then the higher harmonics can have equal or even higher peaks than the first harmonic.
-Here, we did observe strong non-linearities in our photoreceptor pathways, as reflected by the interocular suppression weights that were output by our computational model.
-For the S-(L+M) pathway specifically, it seems that the higher peak of the second harmonic is a behaviour intrinsic to S cones, as this was observed previously (\protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}).
+This is the first study to investigate binocular interactions in the melanopsin pathway directly.
+A previous meta-analysis (\protect\hyperlink{ref-Spitschan2019}{Spitschan and Cajochen, 2019}) indicated that there may be a substantial binocular facilitation effect in the circadian pathway, as indexed by melatonin suppression (melatonin is a hormone released by the pineal gland; its production is suppressed by exposure to bright light, particularly when the melanopsin-containing ipRGCs are stimulated).
+In brief, monocular stimulation of the ipRGCs requires up to ten times the signal strength to produce an equivalent effect to binocular stimulation.
+This superadditive effect implies an absence of interocular suppression, and perhaps the presence of either a highly compressive nonlinearity, or an AND-style neural operation.
+Our findings here are very different - we do not see substantial binocular facilitation effects in response to melanopsin modulation, and our data indicate that interocular suppression is very strong.
+Moreover, by measuring the full contrast response function, we can rule out compressive nonlinearities, because the functions accelerate at both the first and second harmonic frequencies.
+The explanation for this difference could be due to different anatomical pathways.
+Binocular combination in the circadian system likely takes place in the suprachiasmatic nucleus, whereas in the pupil constriction circuit the Edinger-Westphal nucleus is the most likely site of binocular integration (\protect\hyperlink{ref-Mathot2018}{Mathôt, 2018}).
+Presumably these anatomical differences, and the practical constraints of the two systems, lead to differences in response.
 
-The pupil phases shown in Figure \ref{fig:phaseplots} give us more information about the pathways controlling the pupil response.
-The first thing that we notice is that the luminance and L-M pathway responses are in anti-phase.
-It is important to note that, for our L-M pathway stimulation, the stimulus flickered between magenta (first half of the cycle) and cyan (second half of the cycle), which means that the pupil was dilating during the magenta stimulation and then constricting during the cyan presentation.
-This seems to suggest that increments in magenta would correspond to decrements in brightness and increments in cyan would correspond to increments in brightness.
-It is possible that, if we had reversed the presentation cycle for the L-M pathway, the pupil response would have been in phase with the luminance responses.
-It has been recently shown that L-cone and melanopsin stimulation induce an opponent pupillary response to M- and S-cone stimulation (\protect\hyperlink{ref-Murray2018}{Murray et al., 2018}; \protect\hyperlink{ref-Woelders2018}{Woelders et al., 2018}).
-Our melanopsin and S-(L+M) results show a similar behaviour both for monocular and binocular responses.
-The L-M pathways results are desynchronised approximately in quadrature phase from the melanopsin and S-(L+M) results.
-These results also seem to align with what was previously found: combining L and M responses should display results that are between the opponency shown by the isolated cone stimulation.
-Additionally, this could explain the very strong suppression that binocular (L-M) stimulation displays compared to the monocular stimulation: if L and M produce pupil responses that are in anti-phase with each other, then combining the two together should elicit smaller responses.
-Finally, since the results from our experiments are not in phase, it would suggest that the photoreceptors control the pupil diameter through different pathways.
+Our recent psychophysical work (\protect\hyperlink{ref-Baker2024}{Baker et al., 2024}) has looked at binocular interactions in the L-M and S-cone pathways, and compared these to the luminance pathway.
+Using a contrast discrimination paradigm with spatial modulations of luminance and colour, Baker et al.
+(\protect\hyperlink{ref-Baker2024}{2024}) found equally strong interocular suppression in all three pathways.
+This is rather different from our pupillometry results here, which demonstrate weaker suppression in the luminance and S-cone pathways than in the L-M pathway (see Figure \ref{fig:FirstHarmonicPlots}).
+However, the current experiments involve temporal modulations, which are quite distinct from the spatial modulations used in Baker et al.
+(\protect\hyperlink{ref-Baker2024}{2024}).
+Our other recent work (\protect\hyperlink{ref-Segala2023}{Segala et al., 2023}) has shown that temporal luminance modulations involve much weaker interocular suppression in the cortical response than do spatial luminance modulations (\protect\hyperlink{ref-Baker2017}{Baker and Wade, 2017}).
+These different normalization processes might reflect different priorities for spatial and temporal vision.
+Spatial vision aims to fuse images to provide binocular single vision, and benefits from `ocularity invariance' (\protect\hyperlink{ref-Baker2007}{Baker et al., 2007}), in which visual appearance is constant when viewed with one eye or two.
+Temporal vision is critical for motion perception, which can involve alternative binocular computations, such as calculating velocity differences between the eyes (\protect\hyperlink{ref-Kaestner2019}{Kaestner et al., 2019}).
+Of course the present measurements were of pupil size, which may be subject to different anatomical and functional constraints from those in the cortex.
+Future research should aim to extend our current findings to perception using psychophysical approaches.
 
@@
 We have demonstrated that binocular combination of temporal flickering light in the autonomic nervous system depends on the photoreceptor pathway.
-We were able to elicit pupil responses by stimulating only the periphery of the retina and we were able to record contrast response functions for all photoreceptor pathways.
-While all pathways showed non-linear combination, they showed a variation in how the signals are combined, particularly in the weight of interocular suppression.
+We were able to elicit pupil responses by stimulating the periphery of the retina and we were able to record contrast response functions for all photoreceptor pathways.
+While all pathways showed non-linear combination, they varied in how the signals are combined, particularly in the weight of interocular suppression.
+This was strong (\(\omega \ge 1\)) for L-M and melanopsin signals at the first harmonic, and all pathways at the second harmonic.
+Suppression was weaker (\(\omega < 1\)) in the luminance pathway (consistent with previous work), and also for S-cone directed modulations.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Baker2024}{}}%
+Baker DH, Hansford KJ, Segala FG, Morsi AY, Huxley RJ, Martin JT, Rockman M, Wade AR.
+2024.
+Binocular integration of chromatic and luminance signals.
+\emph{Journal of Vision} \textbf{Under review}.
+doi:\href{https://doi.org/10.31234/osf.io/atsfh}{10.31234/osf.io/atsfh}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Baker2018}{}}%
@@
 2018.
-\href{https://www.frontiersin.org/articles/10.3389/fneur.2018.01140}{Non-linearities in the {Rod} and {Cone} {Photoreceptor} {Inputs} to the {Afferent} {Pupil} {Light} {Response}}.
+Non-linearities in the {Rod} and {Cone} {Photoreceptor} {Inputs} to the {Afferent} {Pupil} {Light} {Response}.
 \emph{Frontiers in Neurology} \textbf{9}.
+doi:\href{https://doi.org/10.3389/fneur.2018.01140}{10.3389/fneur.2018.01140}
 
@@
 doi:\href{https://doi.org/10.1113/jphysiol.1962.sp006837}{10.1113/jphysiol.1962.sp006837}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Kaestner2019}{}}%
+Kaestner M, Maloney RT, Wailes-Newson KH, Bloj M, Harris JM, Morland AB, Wade AR.
+2019.
+Asymmetries between achromatic and chromatic extraction of 3D motion signals.
+\emph{Proc Natl Acad Sci U S A} \textbf{116}:13631--13640.
+doi:\href{https://doi.org/10.1073/pnas.1817202116}{10.1073/pnas.1817202116}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Spitschan2019}{}}%
-Spitschan M. 2019. Photoreceptor inputs to pupil control. \emph{Journal of Vision} \textbf{19}:5. doi:\href{https://doi.org/10.1167/19.9.5}{10.1167/19.9.5}
+Spitschan M, Cajochen C. 2019. Binocular facilitation in light-mediated melatonin suppression? \emph{J Pineal Res} \textbf{67}:e12602. doi:\href{https://doi.org/10.1111/jpi.12602}{10.1111/jpi.12602}
 
@@
 2018.
-\href{https://www.frontiersin.org/articles/10.3389/fneur.2018.00941}{The {Method} of {Silent} {Substitution} for {Examining} {Melanopsin} {Contributions} to {Pupil} {Control}}.
+The {Method} of {Silent} {Substitution} for {Examining} {Melanopsin} {Contributions} to {Pupil} {Control}.
 \emph{Frontiers in Neurology} \textbf{9}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Stark1957}{}}%
-Stark L, Sherman PM.
-1957.
-A servoanalytic study of consensual pupil reflex to light.
-\emph{Journal of Neurophysiology} \textbf{20}:17--26.
-doi:\href{https://doi.org/10.1152/jn.1957.20.1.17}{10.1152/jn.1957.20.1.17}
+doi:\href{https://doi.org/10.3389/fneur.2018.00941}{10.3389/fneur.2018.00941}
 
@@
 doi:\href{https://doi.org/10.1016/s0042-6989(00)00021-3}{10.1016/s0042-6989(00)00021-3}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Verdon1988}{}}%
-Verdon W, Howarth PA.
-1988.
-The pupil's response to short wavelength cone stimulation.
-\emph{Vision research} \textbf{28}:1119--1128.
-doi:\href{https://doi.org/10.1016/0042-6989(88)90138-1}{10.1016/0042-6989(88)90138-1}
 

### 2024-05-09 manuscript.Rmd
Updated authors and added automatisation of downloads from OSF (individual data download doesn't seem to work).

@@
 author: |
- | Federico G. Segala$^1$, Joel T. Martin$^{1,2}$, Annie Y. Morsi$^1$, Alex R. Wade$^{1,3}$ & Daniel H. Baker$^{1,3}$
+ | Federico G. Segala$^1$, Aurelio Bruno$^{1,2}$, Joel T. Martin$^{1,3}$, Annie Y. Morsi$^1$, Alex R. Wade$^{1,4}$
+ | & Daniel H. Baker$^{1,4}$
 output:
@@
 
-$^2$School of Philosophy, Psychology and Language Sciences, University of Edinburgh, Edinburgh, United Kingdom.
-
-$^3$York Biomedical Research Institute, University of York, Heslington, York, United Kingdom.
+$^2$School of Psychology and Vision Sciences, Leicester, United Kingdom.
+
+$^3$School of Philosophy, Psychology and Language Sciences, University of Edinburgh, Edinburgh, United Kingdom.
+
+$^4$York Biomedical Research Institute, University of York, Heslington, York, United Kingdom.
 
@@
 if (processdata > 2){
+  # for (participant in 1:24) {
+  # 
+  #     # if there is no directory for this participant's data
+  #     if (!file.exists(paste0(rawdir,'P',600+participant,'_S1_annotations.csv'))){
+  #       
+  #        # if the tar file of this participant's data doesn't exist
+  #        if (!file.exists(paste0(rawdir,'P',600+participant,'.zip'))){
+  #          # download it from OSF
+  #          if (!exists('osffiles')){
+  #          osfnode <- '6u7db'
+  #          osfproject <- osf_retrieve_node(osfnode)
+  #         osffiles <- osf_ls_files(osfproject,n_max=300)}
+  #         fid <- which(osffiles$name==paste0('P',600+participant,'.zip'))
+  #         osf_download(osffiles[fid,],rawdir,progress=TRUE)
+  #        }
+  #        
+  #        # then unzip the zip file
+  #        unzip(paste0(rawdir,'P',600+participant,'.zip'), exdir=rawdir, overwrite=TRUE)
+  #        
+  #        # and delete the tar file to save storage space
+  #        file.remove(paste0(rawdir,'P',600+participant,'.zip'))
+  #     }
+  #   
+  #   # if there is no directory for this participant's data
+  #     if (!file.exists(paste0(rawdir,'P',500+participant,'_S1_annotations.csv'))){
+  #       
+  #        # if the tar file of this participant's data doesn't exist
+  #        if (!file.exists(paste0(rawdir,'P',500+participant,'.zip'))){
+  #          # download it from OSF
+  #          if (!exists('osffiles')){
+  #          osfnode <- 'xkgd9'
+  #          osfproject <- osf_retrieve_node(osfnode)
+  #         osffiles <- osf_ls_files(osfproject,n_max=300)}
+  #         fid <- which(osffiles$name==paste0('P',500+participant,'.zip'))
+  #         osf_download(osffiles[fid,],rawdir,progress=TRUE)
+  #        }
+  #        
+  #        # then unzip the zip file
+  #        unzip(paste0(rawdir,'P',500+participant,'.zip'), exdir=rawdir, overwrite=TRUE)
+  #        
+  #        # and delete the tar file to save storage space
+  #        file.remove(paste0(rawdir,'P',500+participant,'.zip'))
+  #     }
+  #   
+  #   # if there is no directory for this participant's data
+  #     if (!file.exists(paste0(rawdir,'P',700+participant,'_S1_annotations.csv'))){
+  #       
+  #        # if the tar file of this participant's data doesn't exist
+  #        if (!file.exists(paste0(rawdir,'P',700+participant,'.zip'))){
+  #          # download it from OSF
+  #          if (!exists('osffiles')){
+  #          osfnode <- 'pexyk'
+  #          osfproject <- osf_retrieve_node(osfnode)
+  #         osffiles <- osf_ls_files(osfproject,n_max=300)}
+  #         fid <- which(osffiles$name==paste0('P',700+participant,'.zip'))
+  #         osf_download(osffiles[fid,],rawdir,progress=TRUE)
+  #        }
+  #        
+  #        # then unzip the zip file
+  #        unzip(paste0(rawdir,'P',700+participant,'.zip'), exdir=rawdir, overwrite=TRUE)
+  #        
+  #        # and delete the tar file to save storage space
+  #        file.remove(paste0(rawdir,'P',700+participant,'.zip'))
+  #     }
+  #   
+  #   # if there is no directory for this participant's data
+  #     if (!file.exists(paste0(rawdir,'P',300+participant,'_S1_annotations.csv'))){
+  #       
+  #        # if the tar file of this participant's data doesn't exist
+  #        if (!file.exists(paste0(rawdir,'P',300+participant,'.zip'))){
+  #          # download it from OSF
+  #          if (!exists('osffiles')){
+  #          osfnode <- 'k9mdq'
+  #          osfproject <- osf_retrieve_node(osfnode)
+  #         osffiles <- osf_ls_files(osfproject,n_max=300)}
+  #         fid <- which(osffiles$name==paste0('P',300+participant,'.zip'))
+  #         osf_download(osffiles[fid,],rawdir,progress=TRUE)
+  #        }
+  #        
+  #        # then unzip the zip file
+  #        unzip(paste0(rawdir,'P',300+participant,'.zip'), exdir=rawdir, overwrite=TRUE)
+  #        
+  #        # and delete the tar file to save storage space
+  #        file.remove(paste0(rawdir,'P',300+participant,'.zip'))
+  #     }
+  # }
 
@@
 if (processdata > 1){
+
+  # if there is no directory for this participant's data
+      if (!file.exists(paste0(datadir,pattern='_summary.RData'))){
+
+         # if the tar file of this participant's data doesn't exist
+         if (!file.exists(paste0(datadir,'IndividualSummary.zip'))){
+           # download it from OSF
+           if (!exists('osffiles')){
+           osfnode <- '9ebtd'
+           osfproject <- osf_retrieve_node(osfnode)
+          osffiles <- osf_ls_files(osfproject,n_max=300)}
+          fid <- which(osffiles$name==paste0('IndividualSummary.zip'))
+          osf_download(osffiles[fid,],datadir,progress=TRUE)
+         }
+
+         # then unzip the zip file
+         unzip(paste0(datadir,'IndividualSummary.zip'), exdir=datadir, overwrite=TRUE)
+
+         # and delete the tar file to save storage space
+         file.remove(paste0(datadir,'IndividualSummary.zip'))
+         file.remove(paste0(datadir,'__MACOSX'))
+      }
 
@@
 
+if (!file.exists(paste0(datadir,'modeloutputLum.RData'))){
+  if (!exists('osffiles')){
+    osfnode <- '9ebtd'
+    osfproject <- osf_retrieve_node(osfnode)
+    osffiles <- osf_ls_files(osfproject,n_max=300)
+  }
+  fid <- which(osffiles$name==paste0('modeloutputLum.RData'))
+  osf_download(osffiles[fid,],datadir,progress=TRUE)
+}
+
+if (!file.exists(paste0(datadir,'modeloutputLM.RData'))){
+  if (!exists('osffiles')){
+    osfnode <- '9ebtd'
+    osfproject <- osf_retrieve_node(osfnode)
+    osffiles <- osf_ls_files(osfproject,n_max=300)
+  }
+  fid <- which(osffiles$name==paste0('modeloutputLM.RData'))
+  osf_download(osffiles[fid,],datadir,progress=TRUE)
+}
+
+if (!file.exists(paste0(datadir,'modeloutputMel.RData'))){
+  if (!exists('osffiles')){
+    osfnode <- '9ebtd'
+    osfproject <- osf_retrieve_node(osfnode)
+    osffiles <- osf_ls_files(osfproject,n_max=300)
+  }
+  fid <- which(osffiles$name==paste0('modeloutputMel.RData'))
+  osf_download(osffiles[fid,],datadir,progress=TRUE)
+}
+
+if (!file.exists(paste0(datadir,'modeloutputS.RData'))){
+  if (!exists('osffiles')){
+    osfnode <- '9ebtd'
+    osfproject <- osf_retrieve_node(osfnode)
+    osffiles <- osf_ls_files(osfproject,n_max=300)
+  }
+  fid <- which(osffiles$name==paste0('modeloutputS.RData'))
+  osf_download(osffiles[fid,],datadir,progress=TRUE)
+}
+
 # get predictions of the model based on earlier fits
@@
 if (processdata > 0){
+
+if (!file.exists(paste0(datadir,'AveragedataLum.RData'))){
+  if (!exists('osffiles')){
+    osfnode <- '9ebtd'
+    osfproject <- osf_retrieve_node(osfnode)
+    osffiles <- osf_ls_files(osfproject,n_max=300)
+  }
+  fid <- which(osffiles$name==paste0('AveragedataLum.RData'))
+  osf_download(osffiles[fid,],datadir,progress=TRUE)
+}
+
+if (!file.exists(paste0(datadir,'AveragedataLM.RData'))){
+  if (!exists('osffiles')){
+    osfnode <- '9ebtd'
+    osfproject <- osf_retrieve_node(osfnode)
+    osffiles <- osf_ls_files(osfproject,n_max=300)
+  }
+  fid <- which(osffiles$name==paste0('AveragedataLM.RData'))
+  osf_download(osffiles[fid,],datadir,progress=TRUE)
+}
+
+if (!file.exists(paste0(datadir,'AveragedataMel.RData'))){
+  if (!exists('osffiles')){
+    osfnode <- '9ebtd'
+    osfproject <- osf_retrieve_node(osfnode)
+    osffiles <- osf_ls_files(osfproject,n_max=300)
+  }
+  fid <- which(osffiles$name==paste0('AveragedataMel.RData'))
+  osf_download(osffiles[fid,],datadir,progress=TRUE)
+}
+
+if (!file.exists(paste0(datadir,'AveragedataS.RData'))){
+  if (!exists('osffiles')){
+    osfnode <- '9ebtd'
+    osfproject <- osf_retrieve_node(osfnode)
+    osffiles <- osf_ls_files(osfproject,n_max=300)
+  }
+  fid <- which(osffiles$name==paste0('AveragedataS.RData'))
+  osf_download(osffiles[fid,],datadir,progress=TRUE)
+}
 

### 2024-05-09 manuscript.tex
Retrying the previous commit

@@
 \setcounter{secnumdepth}{5}
+% definitions for citeproc citations
+\NewDocumentCommand\citeproctext{}{}
+\NewDocumentCommand\citeproc{mm}{%
+  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
+\makeatletter
+ % allow citations to break across lines
+ \let\@cite@ofmt\@firstofone
+ % avoid brackets around text for \cite:
+ \def\@biblabel#1{}
+ \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
+\makeatother
 \newlength{\cslhangindent}
@@
 \setlength{\csllabelwidth}{3em}
-\newlength{\cslentryspacingunit} % times entry-spacing
-\setlength{\cslentryspacingunit}{\parskip}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
+\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
+ {\begin{list}{}{%
+  \setlength{\itemindent}{0pt}
+  \setlength{\leftmargin}{0pt}
+  \setlength{\parsep}{0pt}
   % turn on hanging indent if param 1 is 1
   \ifodd #1
-  \let\oldpar\par
-  \def\par{\hangindent=\cslhangindent\oldpar}
+   \setlength{\leftmargin}{\cslhangindent}
+   \setlength{\itemindent}{-1\cslhangindent}
   \fi
   % set entry spacing
-  \setlength{\parskip}{#2\cslentryspacingunit}
- }%
- {}
+  \setlength{\itemsep}{#2\baselineskip}}}
+ {\end{list}}
 \usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
@@
 \fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\usepackage{bookmark}
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
@@
 \title{Binocular combination in the autonomic nervous system}
-\author{Federico G. Segala\(^1\), Joel T. Martin\(^{1,2}\), Annie Y. Morsi\(^1\), Alex R. Wade\(^{1,3}\) \& Daniel H. Baker\(^{1,3}\)}
+\author{Federico G. Segala\(^1\), Aurelio Bruno\(^{1,2}\), Joel T. Martin\(^{1,3}\), Annie Y. Morsi\(^1\), Alex R. Wade\(^{1,4}\)\\
+\& Daniel H. Baker\(^{1,4}\)}
 \date{}
@@
 
-\(^2\)School of Philosophy, Psychology and Language Sciences, University of Edinburgh, Edinburgh, United Kingdom.
+\(^2\)School of Psychology and Vision Sciences, Leicester, United Kingdom.
 
-\(^3\)York Biomedical Research Institute, University of York, Heslington, York, United Kingdom.
+\(^3\)School of Philosophy, Psychology and Language Sciences, University of Edinburgh, Edinburgh, United Kingdom.
+
+\(^4\)York Biomedical Research Institute, University of York, Heslington, York, United Kingdom.
 
@@
 
-\hypertarget{abstract-250-words}{%
-\section{Abstract (250 words)}\label{abstract-250-words}}
+\section{Abstract (250 words)}\label{abstract-250-words}
 
@@
 
-\hypertarget{significance-statement-120-words}{%
-\section{Significance statement (120 words)}\label{significance-statement-120-words}}
+\section{Significance statement (120 words)}\label{significance-statement-120-words}
 
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
+\section{Introduction}\label{introduction}
 
-The autonomic nervous system regulates many involuntary bodily processes, including the constriction and dilation of the pupils in response to light (\protect\hyperlink{ref-McDougal2015}{McDougal and Gamlin, 2015}).
-The anatomical pathway from the retina to the subcortical nuclei controlling the pupillary light response (PLR) is well established: it includes the Pretectal Olivary nucleus (PON), the Superior Cervical ganglion and the Edinger-Westphal nucleus, which project to the iris sphincter muscles that directly control the pupil size (\protect\hyperlink{ref-McDougal2015}{McDougal and Gamlin, 2015}, \protect\hyperlink{ref-McDougal2008}{2008}; \protect\hyperlink{ref-Wang2015}{Wang and Munoz, 2015}).
-Evidence of a binocular component to the PLR is shown by the existence of a consensual response of the pupil (the stimulation of one eye will cause constriction of the other eye; \protect\hyperlink{ref-Wyatt1981}{Wyatt and Musselman, 1981}).
+The autonomic nervous system regulates many involuntary bodily processes, including the constriction and dilation of the pupils in response to light (\citeproc{ref-McDougal2015}{McDougal and Gamlin, 2015}).
+The anatomical pathway from the retina to the subcortical nuclei controlling the pupillary light response (PLR) is well established: it includes the Pretectal Olivary nucleus (PON), the Superior Cervical ganglion and the Edinger-Westphal nucleus, which project to the iris sphincter muscles that directly control the pupil size (\citeproc{ref-McDougal2015}{McDougal and Gamlin, 2015}, \citeproc{ref-McDougal2008}{2008}; \citeproc{ref-Wang2015}{Wang and Munoz, 2015}).
+Evidence of a binocular component to the PLR is shown by the existence of a consensual response of the pupil (the stimulation of one eye will cause constriction of the other eye; \citeproc{ref-Wyatt1981}{Wyatt and Musselman, 1981}).
 The anatomical segregation of the subcortical pathway from the rest of the brain means that this binocular combination of signals must occur independently of the cortical processes of binocular integration required for visual perception.
-Our recent work (\protect\hyperlink{ref-Segala2023}{Segala et al., 2023}) has shown that the algorithm underlying binocular combination of light in the pupil pathway differs from that in the cortex.
+Our recent work (\citeproc{ref-Segala2023}{Segala et al., 2023}) has shown that the algorithm underlying binocular combination of light in the pupil pathway differs from that in the cortex.
 Here we extend this paradigm to compare binocular combination in different photoreceptor pathways that feed into the autonomic nervous system.
 
-Different classes of retinal photoreceptors, including cones, rods and melanopsin-containing intrinsically photosensitive retinal ganglion cells (ipRGCs), are directly involved in controlling and maintaining the size of the pupils (\protect\hyperlink{ref-Barrionuevo2018}{Barrionuevo et al., 2018}; \protect\hyperlink{ref-Barrionuevo2014}{Barrionuevo et al., 2014}; \protect\hyperlink{ref-Dacey2005}{Dacey et al., 2005}; \protect\hyperlink{ref-Murray2018}{Murray et al., 2018}; \protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}; \protect\hyperlink{ref-Spitschan2019}{Spitschan and Cajochen, 2019}; \protect\hyperlink{ref-Woelders2018}{Woelders et al., 2018}).
-The cones have been shown to drive the initial rapid constriction of the pupils (\protect\hyperlink{ref-Mathot2018}{Mathôt, 2018}), while the slower and longer activation of the ipRGCs shows their role in maintaining the constriction over a prolonged period of time and in regulating the post-illumination pupillary response (\protect\hyperlink{ref-Markwell2010}{Markwell et al., 2010}; \protect\hyperlink{ref-McDougal2010}{McDougal and Gamlin, 2010}).
-The ipRGCs are a unique photoreceptor class that has been discovered recently (\protect\hyperlink{ref-Provencio2000}{Provencio et al., 2000}).
-They express the photopigment melanopsin, and are involved in the regulation of the circadian rhythm (\protect\hyperlink{ref-Panda2002}{Panda et al., 2002}; \protect\hyperlink{ref-Provencio2000}{Provencio et al., 2000}; \protect\hyperlink{ref-Ruby2002}{Ruby et al., 2002}), forming a major input to the PON (\protect\hyperlink{ref-Dacey2003}{Dacey et al., 2003}).
+Different classes of retinal photoreceptors, including cones, rods and melanopsin-containing intrinsically photosensitive retinal ganglion cells (ipRGCs), are directly involved in controlling and maintaining the size of the pupils (\citeproc{ref-Barrionuevo2018}{Barrionuevo et al., 2018}; \citeproc{ref-Barrionuevo2014}{Barrionuevo et al., 2014}; \citeproc{ref-Dacey2005}{Dacey et al., 2005}; \citeproc{ref-Murray2018}{Murray et al., 2018}; \citeproc{ref-Spitschan2014}{Spitschan et al., 2014}; \citeproc{ref-Spitschan2019}{Spitschan and Cajochen, 2019}; \citeproc{ref-Woelders2018}{Woelders et al., 2018}).
+The cones have been shown to drive the initial rapid constriction of the pupils (\citeproc{ref-Mathot2018}{Mathôt, 2018}), while the slower and longer activation of the ipRGCs shows their role in maintaining the constriction over a prolonged period of time and in regulating the post-illumination pupillary response (\citeproc{ref-Markwell2010}{Markwell et al., 2010}; \citeproc{ref-McDougal2010}{McDougal and Gamlin, 2010}).
+The ipRGCs are a unique photoreceptor class that has been discovered recently (\citeproc{ref-Provencio2000}{Provencio et al., 2000}).
+They express the photopigment melanopsin, and are involved in the regulation of the circadian rhythm (\citeproc{ref-Panda2002}{Panda et al., 2002}; \citeproc{ref-Provencio2000}{Provencio et al., 2000}; \citeproc{ref-Ruby2002}{Ruby et al., 2002}), forming a major input to the PON (\citeproc{ref-Dacey2003}{Dacey et al., 2003}).
 The first direct evidence of the involvement of the ipRGCs in the PLR was shown in rats by Lucas et al.
-(\protect\hyperlink{ref-Lucas2003}{2003}) who genetically deleted the melanopsin gene from rats, resulting in the loss of the intrinsic photosensitivity of the cells and a reduced pupil constriction.
-This same behaviour was later also observed in primates and humans (\protect\hyperlink{ref-Gamlin2007}{Gamlin et al., 2007}), where it was demonstrated that the PLR continues during light presentation even when cone and rod signalling is blocked, indicating the primary role of the ipRGCs in maintaining pupil constriction over a prolonged time.
+(\citeproc{ref-Lucas2003}{2003}) who genetically deleted the melanopsin gene from rats, resulting in the loss of the intrinsic photosensitivity of the cells and a reduced pupil constriction.
+This same behaviour was later also observed in primates and humans (\citeproc{ref-Gamlin2007}{Gamlin et al., 2007}), where it was demonstrated that the PLR continues during light presentation even when cone and rod signalling is blocked, indicating the primary role of the ipRGCs in maintaining pupil constriction over a prolonged time.
 
-A technique known as silent substitution (\protect\hyperlink{ref-Estevez1982}{Estévez and Spekreijse, 1982}) can be used to selectively stimulate specific photoreceptor classes.
+A technique known as silent substitution (\citeproc{ref-Estevez1982}{Estévez and Spekreijse, 1982}) can be used to selectively stimulate specific photoreceptor classes.
 Silent substitution exploits the fact that each photoreceptor class has a distinct spectral tuning that overlaps with the others.
-Using a multiprimary system, in which the primaries (i.e.~LEDs) have different spectra, it is possible to target one class of photoreceptors while maintaining the others at a constant activity level, effectively silencing them (\protect\hyperlink{ref-Shapiro1996}{Shapiro et al., 1996}; \protect\hyperlink{ref-Spitschan2018}{Spitschan and Woelders, 2018}, this paper also offers a clear explanation of how to implement silent substitution).
+Using a multiprimary system, in which the primaries (i.e.~LEDs) have different spectra, it is possible to target one class of photoreceptors while maintaining the others at a constant activity level, effectively silencing them (\citeproc{ref-Shapiro1996}{Shapiro et al., 1996}; \citeproc{ref-Spitschan2018}{Spitschan and Woelders, 2018}, this paper also offers a clear explanation of how to implement silent substitution).
 Studies using silent substitution have shown that the pupils behave differently depending on which photoreceptor or pathway is being stimulated.
-For example, pupil responses have been shown to be out of phase when the S cones are stimulated, relative to when the ipRGCs or the L+M cones are stimulated (\protect\hyperlink{ref-Cao2015}{Cao et al., 2015}; \protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}).
-Additionally, when L and M cones are stimulated individually, there appears to be a paradoxical pupil response: increments in L cone stimulation cause a constriction of the pupil, while increments in M cone stimulation lead to a dilation of the pupil (\protect\hyperlink{ref-Murray2018}{Murray et al., 2018}; \protect\hyperlink{ref-Woelders2018}{Woelders et al., 2018}), perhaps due to activity in the L-M opponent pathway.
+For example, pupil responses have been shown to be out of phase when the S cones are stimulated, relative to when the ipRGCs or the L+M cones are stimulated (\citeproc{ref-Cao2015}{Cao et al., 2015}; \citeproc{ref-Spitschan2014}{Spitschan et al., 2014}).
+Additionally, when L and M cones are stimulated individually, there appears to be a paradoxical pupil response: increments in L cone stimulation cause a constriction of the pupil, while increments in M cone stimulation lead to a dilation of the pupil (\citeproc{ref-Murray2018}{Murray et al., 2018}; \citeproc{ref-Woelders2018}{Woelders et al., 2018}), perhaps due to activity in the L-M opponent pathway.
 
-Binocular combination has been extensively studied in visual perception, where it is mediated by neurons in primary visual cortex (\protect\hyperlink{ref-Hubel1962}{Hubel and Wiesel, 1962}; \protect\hyperlink{ref-Moradi2009}{Moradi and Heeger, 2009}).
-For pattern vision, binocular summation occurs at threshold, such that a lower contrast is required to detect a target shown to both eyes than a target shown to only one eye (\protect\hyperlink{ref-Baker2018}{Baker et al., 2018}; \protect\hyperlink{ref-Campbell1965}{Campbell and Green, 1965}; \protect\hyperlink{ref-Legge1984}{Legge, 1984}).
-At higher contrasts, a process of `ocularity invariance' is observed, in which the response to monocularly- and binocularly-presented patterns is equal (\protect\hyperlink{ref-Baker2007}{Baker et al., 2007}; \protect\hyperlink{ref-Ding2006}{Ding and Sperling, 2006}; \protect\hyperlink{ref-Meese2006}{Meese et al., 2006}; \protect\hyperlink{ref-Moradi2009}{Moradi and Heeger, 2009}).
+Binocular combination has been extensively studied in visual perception, where it is mediated by neurons in primary visual cortex (\citeproc{ref-Hubel1962}{Hubel and Wiesel, 1962}; \citeproc{ref-Moradi2009}{Moradi and Heeger, 2009}).
+For pattern vision, binocular summation occurs at threshold, such that a lower contrast is required to detect a target shown to both eyes than a target shown to only one eye (\citeproc{ref-Baker2018}{Baker et al., 2018}; \citeproc{ref-Campbell1965}{Campbell and Green, 1965}; \citeproc{ref-Legge1984}{Legge, 1984}).
+At higher contrasts, a process of `ocularity invariance' is observed, in which the response to monocularly- and binocularly-presented patterns is equal (\citeproc{ref-Baker2007}{Baker et al., 2007}; \citeproc{ref-Ding2006}{Ding and Sperling, 2006}; \citeproc{ref-Meese2006}{Meese et al., 2006}; \citeproc{ref-Moradi2009}{Moradi and Heeger, 2009}).
 This is thought to be due to a process of interocular suppression that compensates for the additional excitatory drive caused by stimulating two eyes.
-Our recent work (\protect\hyperlink{ref-Segala2023}{Segala et al., 2023}) has shown that cortical signal combination for luminance flicker is substantially more linear than for spatial patterns, whereas there is evidence of interocular suppression in the pupil pathway.
+Our recent work (\citeproc{ref-Segala2023}{Segala et al., 2023}) has shown that cortical signal combination for luminance flicker is substantially more linear than for spatial patterns, whereas there is evidence of interocular suppression in the pupil pathway.
 
@@
 If the stimulated eye is pharmacologically dilated to control pupil size, the response from the unstimulated eye (known as the consensual response) can be recorded (e.g.
-\protect\hyperlink{ref-McDougal2010}{McDougal and Gamlin, 2010}; \protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}).
+\citeproc{ref-McDougal2010}{McDougal and Gamlin, 2010}; \citeproc{ref-Spitschan2014}{Spitschan et al., 2014}).
 While this approach controls the total amount of light incident at the retina, it does not permit investigation of binocular combination for specific photoreceptor pathways.
@@
 Our key comparisons are between monocular and binocular stimulation, and between monocular stimulation and a dichoptic masking condition in which the two eyes are stimulated at different frequencies (0.5 and 0.4Hz).
-The results are interpreted using a contemporary model of binocular vision (\protect\hyperlink{ref-Meese2006}{Meese et al., 2006}) implemented within a hierarchical Bayesian framework.
+The results are interpreted using a contemporary model of binocular vision (\citeproc{ref-Meese2006}{Meese et al., 2006}) implemented within a hierarchical Bayesian framework.
 
-\hypertarget{results}{%
-\section{Results}\label{results}}
+\section{Results}\label{results}
 
@@
 
-In contemporary models of binocular signal combination, the amount of binocular facilitation is determined by the magnitude of interocular suppression, with strong suppression reducing facilitation (\protect\hyperlink{ref-Kingdom2015}{Kingdom and Libenson, 2015}).
+In contemporary models of binocular signal combination, the amount of binocular facilitation is determined by the magnitude of interocular suppression, with strong suppression reducing facilitation (\citeproc{ref-Kingdom2015}{Kingdom and Libenson, 2015}).
 We can estimate the strength of interocular suppression by measuring how much monocular responses are reduced when a dichoptic `mask' is shown to the other eye.
 In our paradigm, the two components flickered at different frequencies (0.5 and 0.4Hz) so that their responses remained distinct in the Fourier spectrum (e.g.
-\protect\hyperlink{ref-Busse2009}{Busse et al., 2009}).
+\citeproc{ref-Busse2009}{Busse et al., 2009}).
 The yellow diamond symbols in Figure \ref{fig:FirstHarmonicPlots}a-d show the target responses in this condition, and in most cases were weaker than the monocular responses (red circles).
@@
 
-To quantify the extent of suppression for each photoreceptor pathway, we fitted each data set using a Bayesian hierarchical implementation of a simple binocular combination model (\protect\hyperlink{ref-Meese2006}{Meese et al., 2006}; \protect\hyperlink{ref-Segala2023}{Segala et al., 2023}).
+To quantify the extent of suppression for each photoreceptor pathway, we fitted each data set using a Bayesian hierarchical implementation of a simple binocular combination model (\citeproc{ref-Meese2006}{Meese et al., 2006}; \citeproc{ref-Segala2023}{Segala et al., 2023}).
 Our primary objective was to compare posterior distributions of the weight of interocular suppression, which are shown in Figure \ref{fig:FirstHarmonicPlots}e.
@@
 
-Finally, we inspected the response phase of our four stimulation conditions, given previous reports that these differ across pathways (\protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}), and may be in antiphase for melanopsin and S-cone signals.
+Finally, we inspected the response phase of our four stimulation conditions, given previous reports that these differ across pathways (\citeproc{ref-Spitschan2014}{Spitschan et al., 2014}), and may be in antiphase for melanopsin and S-cone signals.
 Figure \ref{fig:phaseplots} shows the phase angles for the first (a) and second (b) harmonic frequencies for binocular stimulation (monocular stimulation produced very similar results).
@@
 
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
+\section{Discussion}\label{discussion}
 
@@
 This is the first study to investigate binocular interactions in the melanopsin pathway directly.
-A previous meta-analysis (\protect\hyperlink{ref-Spitschan2019}{Spitschan and Cajochen, 2019}) indicated that there may be a substantial binocular facilitation effect in the circadian pathway, as indexed by melatonin suppression (melatonin is a hormone released by the pineal gland; its production is suppressed by exposure to bright light, particularly when the melanopsin-containing ipRGCs are stimulated).
+A previous meta-analysis (\citeproc{ref-Spitschan2019}{Spitschan and Cajochen, 2019}) indicated that there may be a substantial binocular facilitation effect in the circadian pathway, as indexed by melatonin suppression (melatonin is a hormone released by the pineal gland; its production is suppressed by exposure to bright light, particularly when the melanopsin-containing ipRGCs are stimulated).
 In brief, monocular stimulation of the ipRGCs requires up to ten times the signal strength to produce an equivalent effect to binocular stimulation.
@@
 The explanation for this difference could be due to different anatomical pathways.
-Binocular combination in the circadian system likely takes place in the suprachiasmatic nucleus, whereas in the pupil constriction circuit the Edinger-Westphal nucleus is the most likely site of binocular integration (\protect\hyperlink{ref-Mathot2018}{Mathôt, 2018}).
+Binocular combination in the circadian system likely takes place in the suprachiasmatic nucleus, whereas in the pupil constriction circuit the Edinger-Westphal nucleus is the most likely site of binocular integration (\citeproc{ref-Mathot2018}{Mathôt, 2018}).
 Presumably these anatomical differences, and the practical constraints of the two systems, lead to differences in response.
 
-Our recent psychophysical work (\protect\hyperlink{ref-Baker2024}{Baker et al., 2024}) has looked at binocular interactions in the L-M and S-cone pathways, and compared these to the luminance pathway.
+Our recent psychophysical work (\citeproc{ref-Baker2024}{Baker et al., 2024}) has looked at binocular interactions in the L-M and S-cone pathways, and compared these to the luminance pathway.
 Using a contrast discrimination paradigm with spatial modulations of luminance and colour, Baker et al.
-(\protect\hyperlink{ref-Baker2024}{2024}) found equally strong interocular suppression in all three pathways.
+(\citeproc{ref-Baker2024}{2024}) found equally strong interocular suppression in all three pathways.
 This is rather different from our pupillometry results here, which demonstrate weaker suppression in the luminance and S-cone pathways than in the L-M pathway (see Figure \ref{fig:FirstHarmonicPlots}).
 However, the current experiments involve temporal modulations, which are quite distinct from the spatial modulations used in Baker et al.
-(\protect\hyperlink{ref-Baker2024}{2024}).
-Our other recent work (\protect\hyperlink{ref-Segala2023}{Segala et al., 2023}) has shown that temporal luminance modulations involve much weaker interocular suppression in the cortical response than do spatial luminance modulations (\protect\hyperlink{ref-Baker2017}{Baker and Wade, 2017}).
+(\citeproc{ref-Baker2024}{2024}).
+Our other recent work (\citeproc{ref-Segala2023}{Segala et al., 2023}) has shown that temporal luminance modulations involve much weaker interocular suppression in the cortical response than do spatial luminance modulations (\citeproc{ref-Baker2017}{Baker and Wade, 2017}).
 These different normalization processes might reflect different priorities for spatial and temporal vision.
-Spatial vision aims to fuse images to provide binocular single vision, and benefits from `ocularity invariance' (\protect\hyperlink{ref-Baker2007}{Baker et al., 2007}), in which visual appearance is constant when viewed with one eye or two.
-Temporal vision is critical for motion perception, which can involve alternative binocular computations, such as calculating velocity differences between the eyes (\protect\hyperlink{ref-Kaestner2019}{Kaestner et al., 2019}).
+Spatial vision aims to fuse images to provide binocular single vision, and benefits from `ocularity invariance' (\citeproc{ref-Baker2007}{Baker et al., 2007}), in which visual appearance is constant when viewed with one eye or two.
+Temporal vision is critical for motion perception, which can involve alternative binocular computations, such as calculating velocity differences between the eyes (\citeproc{ref-Kaestner2019}{Kaestner et al., 2019}).
 Of course the present measurements were of pupil size, which may be subject to different anatomical and functional constraints from those in the cortex.
@@
 
-\hypertarget{conclusions}{%
-\section{Conclusions}\label{conclusions}}
+\section{Conclusions}\label{conclusions}
 
@@
 
-\hypertarget{materials-and-methods}{%
-\section{Materials and methods}\label{materials-and-methods}}
+\section{Materials and methods}\label{materials-and-methods}
 
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
+\subsection{Participants}\label{participants}
 
@@
 
-\hypertarget{apparatus-stimuli}{%
-\subsection{Apparatus \& stimuli}\label{apparatus-stimuli}}
+\subsection{Apparatus \& stimuli}\label{apparatus-stimuli}
 
 To present synchronised stimulus modulations independently to each eye, two light engines (SpectraTuneLAB: LEDMOTIVE Technologies, LLC, Barcelona, Spain), each with 10 independently addressable LED colour channels, were integrated into a customised viewing system.
-The light engines were operated via a Python interface to their REST API (\protect\hyperlink{ref-Martin2022}{Martin et al., 2022}), which supports synchronous launch and playback of spectral sequences prepared in advance and stored in JSON format.
+The light engines were operated via a Python interface to their REST API (\citeproc{ref-Martin2022}{Martin et al., 2022}), which supports synchronous launch and playback of spectral sequences prepared in advance and stored in JSON format.
 When preparing the spectral sequences, the age of participants was used to account for the yellowing of the lenses.
-We calculated silent substitution solutions using the \emph{PySilSub} toolbox (\protect\hyperlink{ref-Martin2023}{Martin et al., 2023}), using linear algebra.
+We calculated silent substitution solutions using the \emph{PySilSub} toolbox (\citeproc{ref-Martin2023}{Martin et al., 2023}), using linear algebra.
 The outputs of the two light engines (see Figure \ref{fig:spectraplots}b,c) were calibrated using an Ocean Optics Jaz spectroradiometer, which was wavelength-calibrated to an Argon lamp and intensity calibrated using a NIST-traceable light source.
-We used the Stockman and Sharpe (\protect\hyperlink{ref-Stockman2000}{2000}) 10-degree cone fundamentals, and estimates of melanopsin absorbance spectra from CIE S 026 (discussed in \protect\hyperlink{ref-Martin2023}{Martin et al., 2023}) to calculate \(\alpha\)-opic irradiance.
+We used the Stockman and Sharpe (\citeproc{ref-Stockman2000}{2000}) 10-degree cone fundamentals, and estimates of melanopsin absorbance spectra from CIE S 026 (discussed in \citeproc{ref-Martin2023}{Martin et al., 2023}) to calculate \(\alpha\)-opic irradiance.
 
@@
 The diffuser discs were positioned in the objective planes of the lenses of a modified VR headset (SHINECON SC-G01, Dongguan Shinecon Industrial Co.~Ltd., Guangdong, China), which was used by the participants to view the stimuli.
-The stimuli were two discs of flickering light with a diameter of approximately 30 degrees, which were fused together into a cyclopean percept resembling a donut-shaped ring of light, similar to that used in other studies (e.g., \protect\hyperlink{ref-Barrionuevo2016}{Barrionuevo and Cao, 2016}; \protect\hyperlink{ref-Murray2018}{Murray et al., 2018}; \protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}; \protect\hyperlink{ref-Zele2018}{Zele et al., 2018}).
+The stimuli were two discs of flickering light with a diameter of approximately 30 degrees, which were fused together into a cyclopean percept resembling a donut-shaped ring of light, similar to that used in other studies (e.g., \citeproc{ref-Barrionuevo2016}{Barrionuevo and Cao, 2016}; \citeproc{ref-Murray2018}{Murray et al., 2018}; \citeproc{ref-Spitschan2014}{Spitschan et al., 2014}; \citeproc{ref-Zele2018}{Zele et al., 2018}).
 The VR headset modifications allowed for small adjustments to account for individual differences in interpupillary distance and focal length.
-The use of this set up allowed us to modulate the stimuli in three different ocular configurations, similar to the ones we used in our previous study (\protect\hyperlink{ref-Segala2023}{Segala et al., 2023}): monocular, binocular and dichoptic.
+The use of this set up allowed us to modulate the stimuli in three different ocular configurations, similar to the ones we used in our previous study (\citeproc{ref-Segala2023}{Segala et al., 2023}): monocular, binocular and dichoptic.
 In the monocular configuration, the unstimulated eye still saw a non-flickering disc of mean luminance.
 A schematic of the stimulation system is shown in Figure \ref{fig:spectraplots}a.
-Pupillometry data were collected using a binocular Pupil Core eye-tracker headset (Pupil Labs GmbH, Berlin, Germany, \protect\hyperlink{ref-Kassner2014}{Kassner et al., 2014}) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
+Pupillometry data were collected using a binocular Pupil Core eye-tracker headset (Pupil Labs GmbH, Berlin, Germany, \citeproc{ref-Kassner2014}{Kassner et al., 2014}) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
 
-Our previous study (\protect\hyperlink{ref-Segala2023}{Segala et al., 2023}) used a temporal frequency of 2Hz for foveal luminance flicker, and recorded EEG data simultaneously with pupillometry.
+Our previous study (\citeproc{ref-Segala2023}{Segala et al., 2023}) used a temporal frequency of 2Hz for foveal luminance flicker, and recorded EEG data simultaneously with pupillometry.
 Initial pilot experiments indicated that this frequency was too high to elicit measurable responses when stimulating individual photoreceptor pathways.
-For all experiments, we therefore used a primary flicker frequency of 0.5Hz, as previous literature showed that this was slow enough to elicit a pupil response from all photoreceptor classes (\protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}).
-We also focussed on only recording pupillometry data as this frequency would be too slow to elicit steady-state EEG responses (\protect\hyperlink{ref-Norcia2015}{Norcia et al., 2015}).
+For all experiments, we therefore used a primary flicker frequency of 0.5Hz, as previous literature showed that this was slow enough to elicit a pupil response from all photoreceptor classes (\citeproc{ref-Spitschan2014}{Spitschan et al., 2014}).
+We also focussed on only recording pupillometry data as this frequency would be too slow to elicit steady-state EEG responses (\citeproc{ref-Norcia2015}{Norcia et al., 2015}).
 
@@
 
-\hypertarget{procedure}{%
-\subsection{Procedure}\label{procedure}}
+\subsection{Procedure}\label{procedure}
 
@@
 Pupil responses to binocular temporal contrast modulations were examined in a factorial design that combined six ocular conditions and five temporal contrast levels: 6, 12, 24, 48 and 96\% of the available dynamic range.
-This design, similar to that used in our previous studies (\protect\hyperlink{ref-Baker2020}{Baker et al., 2020}; \protect\hyperlink{ref-Baker2017}{Baker and Wade, 2017}; \protect\hyperlink{ref-Segala2023}{Segala et al., 2023}), was applied in four separate experiments, each with a different mode of photoreceptor stimulation.
+This design, similar to that used in our previous studies (\citeproc{ref-Baker2020}{Baker et al., 2020}; \citeproc{ref-Baker2017}{Baker and Wade, 2017}; \citeproc{ref-Segala2023}{Segala et al., 2023}), was applied in four separate experiments, each with a different mode of photoreceptor stimulation.
 In the first three conditions, the discs flickered at 0.5 Hz, in either a monocular, binocular or dichoptic arrangement.
@@
 Using a trackball, participants adjusted the angle in cone space to find their subjective isoluminant point, which resulted in changing the flickering intensity of the stimulus until the amplitude of the flicker appeared to be minimised.
-The result was used to modify the requested contrasts during stimulus preparation so as to account for individual differences affecting perceived illuminance, principally the L:M cone ratio (\protect\hyperlink{ref-Carroll2002}{Carroll et al., 2002}; \protect\hyperlink{ref-Hofer2005}{Hofer et al., 2005}).
+The result was used to modify the requested contrasts during stimulus preparation so as to account for individual differences affecting perceived illuminance, principally the L:M cone ratio (\citeproc{ref-Carroll2002}{Carroll et al., 2002}; \citeproc{ref-Hofer2005}{Hofer et al., 2005}).
 
-\hypertarget{data-analysis}{%
-\subsection{Data analysis}\label{data-analysis}}
+\subsection{Data analysis}\label{data-analysis}
 
-The pupillometry data were analysed using the same method we used in our previous study (\protect\hyperlink{ref-Segala2023}{Segala et al., 2023}).
-The data were converted from mp4 videos to a csv text file using the Pupil Player software (\protect\hyperlink{ref-Kassner2014}{Kassner et al., 2014}), which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
+The pupillometry data were analysed using the same method we used in our previous study (\citeproc{ref-Segala2023}{Segala et al., 2023}).
+The data were converted from mp4 videos to a csv text file using the Pupil Player software (\citeproc{ref-Kassner2014}{Kassner et al., 2014}), which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
 The individual data were then loaded into R for analysis, where a ten-second waveform for each trial in each eye was extracted (excluding the first two seconds after stimulus onset).
@@
 Finally, data were averaged across all participants to obtain the group results.
-We used coherent averaging and at each stage we excluded data points with a Mahalanobis distance exceeding \(D\) = 3 from the complex-valued mean (\protect\hyperlink{ref-Baker2021}{Baker, 2021}).
+We used coherent averaging and at each stage we excluded data points with a Mahalanobis distance exceeding \(D\) = 3 from the complex-valued mean (\citeproc{ref-Baker2021}{Baker, 2021}).
 For monocular stimulation, we confirmed that the consensual response was equivalent to the response in the stimulated eye.
@@
 
-\hypertarget{computational-model-and-parameter-estimation}{%
-\subsection{Computational model and parameter estimation}\label{computational-model-and-parameter-estimation}}
+\subsection{Computational model and parameter estimation}\label{computational-model-and-parameter-estimation}
 
-To describe our data, we used the same model described in our previous study (\protect\hyperlink{ref-Segala2023}{Segala et al., 2023}).
+To describe our data, we used the same model described in our previous study (\citeproc{ref-Segala2023}{Segala et al., 2023}).
 The model has the same general form as the first stage of the contrast gain control model proposed by Meese et al.
-(\protect\hyperlink{ref-Meese2006}{2006}), but omits the second stage.
-For the previous model that we used (\protect\hyperlink{ref-Segala2023}{Segala et al., 2023}), the exponent of the numerator and denominator had fixed values of 2 and (implicitly) 1.
+(\citeproc{ref-Meese2006}{2006}), but omits the second stage.
+For the previous model that we used (\citeproc{ref-Segala2023}{Segala et al., 2023}), the exponent of the numerator and denominator had fixed values of 2 and (implicitly) 1.
 Here, we allow these parameters (called \emph{p} and \emph{q}) to be free, in order to permit different shapes of contrast response function, e.g.~accelerating or saturating.
@@
 
-The models were fit using a hierarchical Bayesian framework implemented in Stan (\protect\hyperlink{ref-Carpenter2017}{Carpenter et al., 2017}).
+The models were fit using a hierarchical Bayesian framework implemented in Stan (\citeproc{ref-Carpenter2017}{Carpenter et al., 2017}).
 The data for each photoreceptor type and response frequency was fit separately, for a total of 8 model fits.
 The prior for the \(\omega\) parameter was Gaussian, with a mean of 1 and standard deviation of 0.5.
-Priors for the other free parameters were also Gaussian, with mean values based on previous work (\protect\hyperlink{ref-Segala2023}{Segala et al., 2023}).
+Priors for the other free parameters were also Gaussian, with mean values based on previous work (\citeproc{ref-Segala2023}{Segala et al., 2023}).
 We calculated over \ensuremath{10^{6}} posterior samples, and retained 10\% for plotting.
 
-\hypertarget{acknowledgements-and-funding-sources}{%
-\section{Acknowledgements and funding sources}\label{acknowledgements-and-funding-sources}}
+\section{Acknowledgements and funding sources}\label{acknowledgements-and-funding-sources}
 
@@
 
-\hypertarget{references}{%
-\section{References}\label{references}}
+\section{References}\label{references}
 
-\hypertarget{refs}{}
+\phantomsection\label{refs}
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-Baker2021}{}}%
+\bibitem[\citeproctext]{ref-Baker2021}
 Baker DH.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Baker2024}{}}%
+\bibitem[\citeproctext]{ref-Baker2024}
 Baker DH, Hansford KJ, Segala FG, Morsi AY, Huxley RJ, Martin JT, Rockman M, Wade AR.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Baker2018}{}}%
+\bibitem[\citeproctext]{ref-Baker2018}
 Baker DH, Lygo FA, Meese TS, Georgeson MA.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Baker2007}{}}%
+\bibitem[\citeproctext]{ref-Baker2007}
 Baker DH, Meese TS, Georgeson MA.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Baker2020}{}}%
+\bibitem[\citeproctext]{ref-Baker2020}
 Baker DH, Vilidaite G, McClarnon E, Valkova E, Bruno A, Millman RE.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Baker2017}{}}%
+\bibitem[\citeproctext]{ref-Baker2017}
 Baker DH, Wade AR.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Barrionuevo2016}{}}%
+\bibitem[\citeproctext]{ref-Barrionuevo2016}
 Barrionuevo PA, Cao D.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Barrionuevo2018}{}}%
+\bibitem[\citeproctext]{ref-Barrionuevo2018}
 Barrionuevo PA, McAnany JJ, Zele AJ, Cao D.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Barrionuevo2014}{}}%
+\bibitem[\citeproctext]{ref-Barrionuevo2014}
 Barrionuevo PA, Nicandro N, McAnany JJ, Zele AJ, Gamlin P, Cao D.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Busse2009}{}}%
+\bibitem[\citeproctext]{ref-Busse2009}
 Busse L, Wade AR, Carandini M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Campbell1965}{}}%
+\bibitem[\citeproctext]{ref-Campbell1965}
 Campbell FW, Green DG. 1965. Monocular versus binocular visual acuity. \emph{Nature} \textbf{208}:191--2. doi:\href{https://doi.org/10.1038/208191a0}{10.1038/208191a0}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Cao2015}{}}%
+\bibitem[\citeproctext]{ref-Cao2015}
 Cao D, Nicandro N, Barrionuevo PA.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Carpenter2017}{}}%
+\bibitem[\citeproctext]{ref-Carpenter2017}
 Carpenter B, Gelman A, Hoffman MD, Lee D, Goodrich B, Betancourt M, Brubaker MA, Guo J, Li P, Riddell A.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Carroll2002}{}}%
+\bibitem[\citeproctext]{ref-Carroll2002}
 Carroll J, Neitz J, Neitz M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Dacey2005}{}}%
+\bibitem[\citeproctext]{ref-Dacey2005}
 Dacey DM, Liao H-W, Peterson BB, Robinson FR, Smith VC, Pokorny J, Yau K-W, Gamlin PD.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Dacey2003}{}}%
+\bibitem[\citeproctext]{ref-Dacey2003}
 Dacey DM, Peterson BB, Robinson FR, Gamlin PD.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Ding2006}{}}%
+\bibitem[\citeproctext]{ref-Ding2006}
 Ding J, Sperling G.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Estevez1982}{}}%
+\bibitem[\citeproctext]{ref-Estevez1982}
 Estévez O, Spekreijse H.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Gamlin2007}{}}%
+\bibitem[\citeproctext]{ref-Gamlin2007}
 Gamlin PDR, McDougal DH, Pokorny J, Smith VC, Yau K-W, Dacey DM.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Hofer2005}{}}%
+\bibitem[\citeproctext]{ref-Hofer2005}
 Hofer H, Carroll J, Neitz J, Neitz M, Williams DR.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Hubel1962}{}}%
+\bibitem[\citeproctext]{ref-Hubel1962}
 Hubel DH, Wiesel TN.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Kaestner2019}{}}%
+\bibitem[\citeproctext]{ref-Kaestner2019}
 Kaestner M, Maloney RT, Wailes-Newson KH, Bloj M, Harris JM, Morland AB, Wade AR.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Kassner2014}{}}%
+\bibitem[\citeproctext]{ref-Kassner2014}
 Kassner M, Patera W, Bulling A.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Kingdom2015}{}}%
+\bibitem[\citeproctext]{ref-Kingdom2015}
 Kingdom FAA, Libenson L.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Legge1984}{}}%
+\bibitem[\citeproctext]{ref-Legge1984}
 Legge GE. 1984. Binocular contrast summation--II. Quadratic summation. \emph{Vision Res} \textbf{24}:385--94. doi:\href{https://doi.org/10.1016/0042-6989(84)90064-6}{10.1016/0042-6989(84)90064-6}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Lucas2003}{}}%
+\bibitem[\citeproctext]{ref-Lucas2003}
 Lucas RJ, Hattar S, Takao M, Berson DM, Foster RG, Yau K-W.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Markwell2010}{}}%
+\bibitem[\citeproctext]{ref-Markwell2010}
 Markwell EL, Feigl B, Zele AJ.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Martin2023}{}}%
+\bibitem[\citeproctext]{ref-Martin2023}
 Martin JT, Boynton GM, Baker DH, Wade AR, Spitschan M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Martin2022}{}}%
+\bibitem[\citeproctext]{ref-Martin2022}
 Martin JT, Pinto J, Bulte D, Spitschan M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Mathot2018}{}}%
+\bibitem[\citeproctext]{ref-Mathot2018}
 Mathôt S. 2018. Pupillometry: Psychology, physiology, and function. \emph{J Cogn} \textbf{1}:16. doi:\href{https://doi.org/10.5334/joc.18}{10.5334/joc.18}
 
-\leavevmode\vadjust pre{\hypertarget{ref-McDougal2015}{}}%
+\bibitem[\citeproctext]{ref-McDougal2015}
 McDougal DH, Gamlin PD. 2015. Autonomic control of the eye. \emph{Comprehensive Physiology} \textbf{5}:439--473. doi:\href{https://doi.org/10.1002/cphy.c140014}{10.1002/cphy.c140014}
 
-\leavevmode\vadjust pre{\hypertarget{ref-McDougal2010}{}}%
+\bibitem[\citeproctext]{ref-McDougal2010}
 McDougal DH, Gamlin PD.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-McDougal2008}{}}%
+\bibitem[\citeproctext]{ref-McDougal2008}
 McDougal DH, Gamlin PD. 2008. Pupillary control pathways.The Senses: A Comprehensive Reference. Elsevier. pp. 521--536.
 
-\leavevmode\vadjust pre{\hypertarget{ref-Meese2006}{}}%
+\bibitem[\citeproctext]{ref-Meese2006}
 Meese TS, Georgeson MA, Baker DH. 2006. Binocular contrast vision at and above threshold. \emph{Journal of Vision} \textbf{6}:1224--43. doi:\href{https://doi.org/10.1167/6.11.7}{10.1167/6.11.7}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Moradi2009}{}}%
+\bibitem[\citeproctext]{ref-Moradi2009}
 Moradi F, Heeger DJ. 2009. Inter-ocular contrast normalization in human visual cortex. \emph{J Vis} \textbf{9}:13.1--22. doi:\href{https://doi.org/10.1167/9.3.13}{10.1167/9.3.13}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Murray2018}{}}%
+\bibitem[\citeproctext]{ref-Murray2018}
 Murray IJ, Kremers J, McKeefry D, Parry NRA.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Norcia2015}{}}%
+\bibitem[\citeproctext]{ref-Norcia2015}
 Norcia AM, Appelbaum LG, Ales JM, Cottereau BR, Rossion B.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Panda2002}{}}%
+\bibitem[\citeproctext]{ref-Panda2002}
 Panda S, Sato TK, Castrucci AM, Rollag MD, DeGrip WJ, Hogenesch JB, Provencio I, Kay SA.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Provencio2000}{}}%
+\bibitem[\citeproctext]{ref-Provencio2000}
 Provencio I, Rodriguez IR, Jiang G, Hayes WP, Moreira EF, Rollag MD.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Ruby2002}{}}%
+\bibitem[\citeproctext]{ref-Ruby2002}
 Ruby NF, Brennan TJ, Xie X, Cao V, Franken P, Heller HC, O'Hara BF.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Segala2023}{}}%
+\bibitem[\citeproctext]{ref-Segala2023}
 Segala FG, Bruno A, Martin JT, Aung MT, Wade AR, Baker DH.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Shapiro1996}{}}%
+\bibitem[\citeproctext]{ref-Shapiro1996}
 Shapiro AG, Pokorny J, Smith VC.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Spitschan2019}{}}%
+\bibitem[\citeproctext]{ref-Spitschan2019}
 Spitschan M, Cajochen C. 2019. Binocular facilitation in light-mediated melatonin suppression? \emph{J Pineal Res} \textbf{67}:e12602. doi:\href{https://doi.org/10.1111/jpi.12602}{10.1111/jpi.12602}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Spitschan2014}{}}%
+\bibitem[\citeproctext]{ref-Spitschan2014}
 Spitschan M, Jain S, Brainard DH, Aguirre GK.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Spitschan2018}{}}%
+\bibitem[\citeproctext]{ref-Spitschan2018}
 Spitschan M, Woelders T.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Stockman2000}{}}%
+\bibitem[\citeproctext]{ref-Stockman2000}
 Stockman A, Sharpe LT.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Wang2015}{}}%
+\bibitem[\citeproctext]{ref-Wang2015}
 Wang C-A, Munoz DP.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Woelders2018}{}}%
+\bibitem[\citeproctext]{ref-Woelders2018}
 Woelders T, Leenheers T, Gordijn MCM, Hut RA, Beersma DGM, Wams EJ.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Wyatt1981}{}}%
+\bibitem[\citeproctext]{ref-Wyatt1981}
 Wyatt HJ, Musselman JF.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Zele2018}{}}%
+\bibitem[\citeproctext]{ref-Zele2018}
 Zele AJ, Feigl B, Adhikari P, Maynard ML, Cao D.

### 2024-05-09 manuscript.Rmd
Retrying the previous commit
Changed OSF downloads and reoriented two figures

--- 2024-05-08 manuscript.Rmd
@@
 
-processdata <- 0  # this flag determines the amount of processing, with 4 levels:
+processdata <- 1 # this flag determines the amount of processing, with 4 levels:
 # 0 - do no processing, generate the pdf using existing versions of all figures
@@
 
-localdir <- 'local/'    # all files are stored in the project directory /local/ which git is told to ignore
-if (!file.exists(localdir)){dir.create(localdir)}   # create a local directory to store data and outputs
+# all files are stored in the project directory /local/ which git is told to ignore
+# create a local directory to store data and outputs
+localdir <- 'local/'
+if (!file.exists(localdir)){dir.create(localdir)}
+
+# create a local directory to store raw data
 rawdir <- 'local/rawdata/'
-if (!file.exists(rawdir)){dir.create(rawdir)}   # create a local directory to store raw data
+if (!file.exists(rawdir)){dir.create(rawdir)}
+
+# create a local directory to store processed data
+datadir <- 'local/processeddata/'
+if (!file.exists(datadir)){dir.create(datadir)}
+
+# create a local directory to store figures
 figdir <- 'Figures/'
-if (!file.exists(figdir)){dir.create(figdir)}   # create a local directory to store figures
-datadir <- 'local/processeddata/'
-if (!file.exists(datadir)){dir.create(datadir)}   # create a local directory to store processed data
+if (!file.exists(figdir)){dir.create(figdir)}
 
@@
 
-# if (processdata==2){
-# # if we're going to need the pre-processed files, extract from zip file
-#   if (!file.exists(paste0(datadir,'P101summary.RData'))){
-#    if (file.exists('resources/allprocessed.zip')){file.copy('resources/allprocessed.zip',localdir)}
-#    if (!file.exists('resources/allprocessed.zip')){ 
-#           osfnode <- '2qu6y'
-#           osfproject <- osf_retrieve_node(osfnode)
-#           osffiles <- osf_ls_files(osfproject,n_max=300)
-#           fid <- which(osffiles$name=='allprocessed.zip')
-#           osf_download(osffiles[fid,],localdir,progress=TRUE)
-#    }
-#           unzip(paste0(localdir,'allprocessed.zip'),exdir=localdir)
-#           d <- dir(paste0(localdir,'allprocessed'),full.names=TRUE)
-#           file.copy(d,datadir)
-#   }
-# }
+if (processdata==2){
+# if we're going to need the pre-processed files, extract from zip file
+  if (!file.exists(paste0(datadir,'P301_summary.RData'))){
+   if (!file.exists(paste0(localdir,'IndividualSummary.zip'))){
+          osfnode <- '9ebtd'
+          osfproject <- osf_retrieve_node(osfnode)
+          osffiles <- osf_ls_files(osfproject,n_max=300)
+          fid <- which(osffiles$name=='IndividualSummary.zip')
+          osf_download(osffiles[fid,],localdir,progress=TRUE)
+   }
+          unzip(paste0(localdir,'IndividualSummary.zip'),exdir=datadir)
+  }
+}
+
+if (processdata<2){
+  # if we're using the pre-processed data, check it's present and download if not
+exptnames <- c('AveragedataLum.RData','AveragedataLM.RData','AveragedataS.RData','AveragedataMel.RData','included.RData')
+for (f in 1:length(exptnames)){
+if (!file.exists(paste0(datadir,exptnames[f]))){
+  if (!exists('osffiles')){
+    osfnode <- '9ebtd'
+    osfproject <- osf_retrieve_node(osfnode)
+    osffiles <- osf_ls_files(osfproject,n_max=300)
+  }
+  fid <- which(osffiles$name==exptnames[f])
+  osf_download(osffiles[fid,],datadir,progress=TRUE)
+}}}
+
+if (domodelling==0){
+# if we're not doing the modelling, check if the model outputs are present and download if not
+  exptnames <- c('modeloutputLum.RData','modeloutputLM.RData','modeloutputS.RData','modeloutputMel.RData')
+
+for (f in 1:length(exptnames)){
+if (!file.exists(paste0(datadir,exptnames[f]))){
+  if (!exists('osffiles')){
+    osfnode <- '9ebtd'
+    osfproject <- osf_retrieve_node(osfnode)
+    osffiles <- osf_ls_files(osfproject,n_max=300)
+  }
+  fid <- which(osffiles$name==exptnames[f])
+  osf_download(osffiles[fid,],datadir,progress=TRUE)
+}
+}
+}
 
@@
 
-pdf(paste0(figdir,"FirstHarmonic.pdf"), bg="transparent", height = 8, width = 24)
-
-layout(matrix(c(1,2,5,5,6,7,3,4,5,5,8,9),2,6,byrow=TRUE)) 
+pdf(paste0(figdir,"FirstHarmonic.pdf"), bg="transparent", height = 24, width = 8)
+
+layout(matrix(c(1,2,3,4,5,5,5,5,6,7,8,9),6,2,byrow=TRUE)) 
 par(mar=c(3,6,2,1))
@@
 axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2)    
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
-
-title(xlab="w", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
-title(ylab="Probability", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
-title(main='Suppressive weight 1F',cex.main=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=1, cex=1.5)    
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1, cex=1.5)
+
+title(xlab=expression(omega), col.lab=rgb(0,0,0), line=4, cex.lab=6)    
+title(ylab="Probability", col.lab=rgb(0,0,0), line=3, cex.lab=3)
+title(main='Suppressive weight 1F',cex.main=3)
 
@@
 
-pdf(paste0(figdir,"SecondHarmonic.pdf"), bg="transparent", height = 8, width = 24)
-
-layout(matrix(c(1,2,5,5,6,7,3,4,5,5,8,9),2,6,byrow=TRUE)) 
+pdf(paste0(figdir,"SecondHarmonic.pdf"), bg="transparent", height = 24, width = 8)
+
+layout(matrix(c(1,2,3,4,5,5,5,5,6,7,8,9),6,2,byrow=TRUE)) 
 par(mar=c(3,6,2,1))
@@
 axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2)    
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
-
-title(xlab="w", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
-title(ylab="Probability", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
-title(main='Suppressive weight 2F',cex.main=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=1, cex=1.5)    
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1, cex=1.5)
+
+title(xlab=expression(omega), col.lab=rgb(0,0,0), line=4, cex.lab=6)    
+title(ylab="Probability", col.lab=rgb(0,0,0), line=3, cex.lab=3)
+title(main='Suppressive weight 2F',cex.main=3)
 
@@
 Curves show model fits using the maximum a posteriori (MAP) parameter values (see Table 1).
-In panel (e), vertical lines show the MAP estimates, and the thin black curve indicates the prior (note the logarithmic x-axis).", fig.align="center", echo=FALSE}
+In panel (e), vertical lines show the MAP estimates, and the thin black curve indicates the prior (note the logarithmic x-axis).", fig.align="center", out.width="40%", echo=FALSE}
 
@@
 
-```{r SecondHarmonicPlots, fig.cap="Responses at the second harmonic frequencies (1Hz and 0.8Hz), in the same format as Figure 2.", fig.align="center", echo=FALSE}
+```{r SecondHarmonicPlots, fig.cap="Responses at the second harmonic frequencies (1Hz and 0.8Hz), in the same format as Figure 2.", fig.align="center", out.width="40%", echo=FALSE}
 

### 2024-05-09 manuscript.tex
Changed OSF downloads and reoriented two figures

--- 2024-05-08 manuscript.tex
@@
 
-{\centering \includegraphics{Figures/FirstHarmonic}
+{\centering \includegraphics[width=0.4\linewidth]{Figures/FirstHarmonic}
 
@@
 
-{\centering \includegraphics{Figures/SecondHarmonic}
+{\centering \includegraphics[width=0.4\linewidth]{Figures/SecondHarmonic}
 

### 2024-05-09 manuscript.Rmd
Modified titles of x axes

@@
 
-processdata <- 1 # this flag determines the amount of processing, with 4 levels:
+processdata <- 0 # this flag determines the amount of processing, with 4 levels:
 # 0 - do no processing, generate the pdf using existing versions of all figures
@@
 mtext(text = ticklabelsy2, side = 2, at=ticklocsy2, line=0.2, las=1) 
-title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)    # titles for axes
+title(xlab="Target contrast (% of max)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)    # titles for axes
 title(ylab="Amplitude at 0.5Hz (mm)", col.lab=rgb(0,0,0), line=3.5, cex.lab=1.5)
@@
 mtext(text = ticklabelsy2, side = 2, at=ticklocsy2, line=0.2, las=1) 
-title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)    # titles for axes
+title(xlab="Target contrast (% of max)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)    # titles for axes
 title(ylab="Amplitude at 0.4Hz (mm)", col.lab=rgb(0,0,0), line=3.5, cex.lab=1.5)
@@
 mtext(text = ticklabelsy2, side = 2, at=ticklocsy2, line=0.2, las=1) 
-title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)    # titles for axes
+title(xlab="Target contrast (% of max)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)    # titles for axes
 title(ylab="Amplitude at 1Hz (mm)", col.lab=rgb(0,0,0), line=3.5, cex.lab=1.5)
@@
 mtext(text = ticklabelsy2, side = 2, at=ticklocsy2, line=0.2, las=1) 
-title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)    # titles for axes
+title(xlab="Target contrast (% of max)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)    # titles for axes
 title(ylab="Amplitude at 0.8Hz (mm)", col.lab=rgb(0,0,0), line=3.5, cex.lab=1.5)

### 2024-05-09 manuscript.tex
Modified titles of x axes

@@
 \PassOptionsToPackage{hyphens}{url}
-\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
+\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
 %
@@
 ]{article}
-\usepackage{amsmath,amssymb}
-\usepackage{iftex}
-\ifPDFTeX
+\usepackage{lmodern}
+\usepackage{amssymb,amsmath}
+\usepackage{ifxetex,ifluatex}
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
   \usepackage[T1]{fontenc}
@@
 \else % if luatex or xetex
-  \usepackage{unicode-math} % this also loads fontspec
+  \usepackage{unicode-math}
   \defaultfontfeatures{Scale=MatchLowercase}
   \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
-\fi
-\usepackage{lmodern}
-\ifPDFTeX\else
-  % xetex/luatex font selection
 \fi
@@
 \usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\hypersetup{
+  pdftitle={Binocular combination in the autonomic nervous system},
+  colorlinks=true,
+  linkcolor=black,
+  filecolor=Maroon,
+  citecolor=Blue,
+  urlcolor=Blue,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
 \usepackage[margin=1in]{geometry}
-\usepackage{longtable,booktabs,array}
-\usepackage{calc} % for calculating minipage widths
+\usepackage{longtable,booktabs}
 % Correct order of tables after \paragraph or \subparagraph
@@
 \makesavenoteenv{longtable}
-\usepackage{graphicx}
+\usepackage{graphicx,grffile}
 \makeatletter
@@
 \setcounter{secnumdepth}{5}
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newlength{\cslentryspacingunit} % times entry-spacing
-\setlength{\cslentryspacingunit}{\parskip}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1
-  \let\oldpar\par
-  \def\par{\hangindent=\cslhangindent\oldpar}
-  \fi
-  % set entry spacing
-  \setlength{\parskip}{#2\cslentryspacingunit}
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 \usepackage{caption}
@@
 \usepackage{xcolor}
-\ifLuaTeX
-  \usepackage{selnolig}  % disable illegal ligatures
-\fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same}
-\hypersetup{
-  pdftitle={Binocular combination in the autonomic nervous system},
-  colorlinks=true,
-  linkcolor={black},
-  filecolor={Maroon},
-  citecolor={Blue},
-  urlcolor={Blue},
-  pdfcreator={LaTeX via pandoc}}
 
@@
 
-The autonomic nervous system regulates many involuntary bodily processes, including the constriction and dilation of the pupils in response to light (\protect\hyperlink{ref-McDougal2015}{McDougal and Gamlin, 2015}).
-The anatomical pathway from the retina to the subcortical nuclei controlling the pupillary light response (PLR) is well established: it includes the Pretectal Olivary nucleus (PON), the Superior Cervical ganglion and the Edinger-Westphal nucleus, which project to the iris sphincter muscles that directly control the pupil size (\protect\hyperlink{ref-McDougal2015}{McDougal and Gamlin, 2015}, \protect\hyperlink{ref-McDougal2008}{2008}; \protect\hyperlink{ref-Wang2015}{Wang and Munoz, 2015}).
-Evidence of a binocular component to the PLR is shown by the existence of a consensual response of the pupil (the stimulation of one eye will cause constriction of the other eye; \protect\hyperlink{ref-Wyatt1981}{Wyatt and Musselman, 1981}).
+The autonomic nervous system regulates many involuntary bodily processes, including the constriction and dilation of the pupils in response to light (McDougal and Gamlin, \protect\hyperlink{ref-McDougal2015}{2015}).
+The anatomical pathway from the retina to the subcortical nuclei controlling the pupillary light response (PLR) is well established: it includes the Pretectal Olivary nucleus (PON), the Superior Cervical ganglion and the Edinger-Westphal nucleus, which project to the iris sphincter muscles that directly control the pupil size (McDougal and Gamlin, \protect\hyperlink{ref-McDougal2015}{2015}, \protect\hyperlink{ref-McDougal2008}{2008}; Wang and Munoz, \protect\hyperlink{ref-Wang2015}{2015}).
+Evidence of a binocular component to the PLR is shown by the existence of a consensual response of the pupil (the stimulation of one eye will cause constriction of the other eye; Wyatt and Musselman, \protect\hyperlink{ref-Wyatt1981}{1981}).
 The anatomical segregation of the subcortical pathway from the rest of the brain means that this binocular combination of signals must occur independently of the cortical processes of binocular integration required for visual perception.
-Our recent work (\protect\hyperlink{ref-Segala2023}{Segala et al., 2023}) has shown that the algorithm underlying binocular combination of light in the pupil pathway differs from that in the cortex.
+Our recent work (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}) has shown that the algorithm underlying binocular combination of light in the pupil pathway differs from that in the cortex.
 Here we extend this paradigm to compare binocular combination in different photoreceptor pathways that feed into the autonomic nervous system.
 
-Different classes of retinal photoreceptors, including cones, rods and melanopsin-containing intrinsically photosensitive retinal ganglion cells (ipRGCs), are directly involved in controlling and maintaining the size of the pupils (\protect\hyperlink{ref-Barrionuevo2018}{Barrionuevo et al., 2018}; \protect\hyperlink{ref-Barrionuevo2014}{Barrionuevo et al., 2014}; \protect\hyperlink{ref-Dacey2005}{Dacey et al., 2005}; \protect\hyperlink{ref-Murray2018}{Murray et al., 2018}; \protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}; \protect\hyperlink{ref-Spitschan2019}{Spitschan and Cajochen, 2019}; \protect\hyperlink{ref-Woelders2018}{Woelders et al., 2018}).
-The cones have been shown to drive the initial rapid constriction of the pupils (\protect\hyperlink{ref-Mathot2018}{Mathôt, 2018}), while the slower and longer activation of the ipRGCs shows their role in maintaining the constriction over a prolonged period of time and in regulating the post-illumination pupillary response (\protect\hyperlink{ref-Markwell2010}{Markwell et al., 2010}; \protect\hyperlink{ref-McDougal2010}{McDougal and Gamlin, 2010}).
-The ipRGCs are a unique photoreceptor class that has been discovered recently (\protect\hyperlink{ref-Provencio2000}{Provencio et al., 2000}).
-They express the photopigment melanopsin, and are involved in the regulation of the circadian rhythm (\protect\hyperlink{ref-Panda2002}{Panda et al., 2002}; \protect\hyperlink{ref-Provencio2000}{Provencio et al., 2000}; \protect\hyperlink{ref-Ruby2002}{Ruby et al., 2002}), forming a major input to the PON (\protect\hyperlink{ref-Dacey2003}{Dacey et al., 2003}).
+Different classes of retinal photoreceptors, including cones, rods and melanopsin-containing intrinsically photosensitive retinal ganglion cells (ipRGCs), are directly involved in controlling and maintaining the size of the pupils (Barrionuevo et al., \protect\hyperlink{ref-Barrionuevo2018}{2018}, \protect\hyperlink{ref-Barrionuevo2014}{2014}; Dacey et al., \protect\hyperlink{ref-Dacey2005}{2005}; Murray et al., \protect\hyperlink{ref-Murray2018}{2018}; Spitschan and Cajochen, \protect\hyperlink{ref-Spitschan2019}{2019}; Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}; Woelders et al., \protect\hyperlink{ref-Woelders2018}{2018}).
+The cones have been shown to drive the initial rapid constriction of the pupils (Mathôt, \protect\hyperlink{ref-Mathot2018}{2018}), while the slower and longer activation of the ipRGCs shows their role in maintaining the constriction over a prolonged period of time and in regulating the post-illumination pupillary response (Markwell et al., \protect\hyperlink{ref-Markwell2010}{2010}; McDougal and Gamlin, \protect\hyperlink{ref-McDougal2010}{2010}).
+The ipRGCs are a unique photoreceptor class that has been discovered recently (Provencio et al., \protect\hyperlink{ref-Provencio2000}{2000}).
+They express the photopigment melanopsin, and are involved in the regulation of the circadian rhythm (Panda et al., \protect\hyperlink{ref-Panda2002}{2002}; Provencio et al., \protect\hyperlink{ref-Provencio2000}{2000}; Ruby et al., \protect\hyperlink{ref-Ruby2002}{2002}), forming a major input to the PON (Dacey et al., \protect\hyperlink{ref-Dacey2003}{2003}).
 The first direct evidence of the involvement of the ipRGCs in the PLR was shown in rats by Lucas et al.
 (\protect\hyperlink{ref-Lucas2003}{2003}) who genetically deleted the melanopsin gene from rats, resulting in the loss of the intrinsic photosensitivity of the cells and a reduced pupil constriction.
-This same behaviour was later also observed in primates and humans (\protect\hyperlink{ref-Gamlin2007}{Gamlin et al., 2007}), where it was demonstrated that the PLR continues during light presentation even when cone and rod signalling is blocked, indicating the primary role of the ipRGCs in maintaining pupil constriction over a prolonged time.
+This same behaviour was later also observed in primates and humans (Gamlin et al., \protect\hyperlink{ref-Gamlin2007}{2007}), where it was demonstrated that the PLR continues during light presentation even when cone and rod signalling is blocked, indicating the primary role of the ipRGCs in maintaining pupil constriction over a prolonged time.
 
-A technique known as silent substitution (\protect\hyperlink{ref-Estevez1982}{Estévez and Spekreijse, 1982}) can be used to selectively stimulate specific photoreceptor classes.
+A technique known as silent substitution (Estévez and Spekreijse, \protect\hyperlink{ref-Estevez1982}{1982}) can be used to selectively stimulate specific photoreceptor classes.
 Silent substitution exploits the fact that each photoreceptor class has a distinct spectral tuning that overlaps with the others.
-Using a multiprimary system, in which the primaries (i.e.~LEDs) have different spectra, it is possible to target one class of photoreceptors while maintaining the others at a constant activity level, effectively silencing them (\protect\hyperlink{ref-Shapiro1996}{Shapiro et al., 1996}; \protect\hyperlink{ref-Spitschan2018}{Spitschan and Woelders, 2018}, this paper also offers a clear explanation of how to implement silent substitution).
+Using a multiprimary system, in which the primaries (i.e.~LEDs) have different spectra, it is possible to target one class of photoreceptors while maintaining the others at a constant activity level, effectively silencing them (Shapiro et al., \protect\hyperlink{ref-Shapiro1996}{1996}; Spitschan and Woelders, \protect\hyperlink{ref-Spitschan2018}{2018}, this paper also offers a clear explanation of how to implement silent substitution).
 Studies using silent substitution have shown that the pupils behave differently depending on which photoreceptor or pathway is being stimulated.
-For example, pupil responses have been shown to be out of phase when the S cones are stimulated, relative to when the ipRGCs or the L+M cones are stimulated (\protect\hyperlink{ref-Cao2015}{Cao et al., 2015}; \protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}).
-Additionally, when L and M cones are stimulated individually, there appears to be a paradoxical pupil response: increments in L cone stimulation cause a constriction of the pupil, while increments in M cone stimulation lead to a dilation of the pupil (\protect\hyperlink{ref-Murray2018}{Murray et al., 2018}; \protect\hyperlink{ref-Woelders2018}{Woelders et al., 2018}), perhaps due to activity in the L-M opponent pathway.
+For example, pupil responses have been shown to be out of phase when the S cones are stimulated, relative to when the ipRGCs or the L+M cones are stimulated (Cao et al., \protect\hyperlink{ref-Cao2015}{2015}; Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}).
+Additionally, when L and M cones are stimulated individually, there appears to be a paradoxical pupil response: increments in L cone stimulation cause a constriction of the pupil, while increments in M cone stimulation lead to a dilation of the pupil (Murray et al., \protect\hyperlink{ref-Murray2018}{2018}; Woelders et al., \protect\hyperlink{ref-Woelders2018}{2018}), perhaps due to activity in the L-M opponent pathway.
 
-Binocular combination has been extensively studied in visual perception, where it is mediated by neurons in primary visual cortex (\protect\hyperlink{ref-Hubel1962}{Hubel and Wiesel, 1962}; \protect\hyperlink{ref-Moradi2009}{Moradi and Heeger, 2009}).
-For pattern vision, binocular summation occurs at threshold, such that a lower contrast is required to detect a target shown to both eyes than a target shown to only one eye (\protect\hyperlink{ref-Baker2018}{Baker et al., 2018}; \protect\hyperlink{ref-Campbell1965}{Campbell and Green, 1965}; \protect\hyperlink{ref-Legge1984}{Legge, 1984}).
-At higher contrasts, a process of `ocularity invariance' is observed, in which the response to monocularly- and binocularly-presented patterns is equal (\protect\hyperlink{ref-Baker2007}{Baker et al., 2007}; \protect\hyperlink{ref-Ding2006}{Ding and Sperling, 2006}; \protect\hyperlink{ref-Meese2006}{Meese et al., 2006}; \protect\hyperlink{ref-Moradi2009}{Moradi and Heeger, 2009}).
+Binocular combination has been extensively studied in visual perception, where it is mediated by neurons in primary visual cortex (Hubel and Wiesel, \protect\hyperlink{ref-Hubel1962}{1962}; Moradi and Heeger, \protect\hyperlink{ref-Moradi2009}{2009}).
+For pattern vision, binocular summation occurs at threshold, such that a lower contrast is required to detect a target shown to both eyes than a target shown to only one eye (Baker et al., \protect\hyperlink{ref-Baker2018}{2018}; Campbell and Green, \protect\hyperlink{ref-Campbell1965}{1965}; Legge, \protect\hyperlink{ref-Legge1984}{1984}).
+At higher contrasts, a process of `ocularity invariance' is observed, in which the response to monocularly- and binocularly-presented patterns is equal (Baker et al., \protect\hyperlink{ref-Baker2007}{2007}; Ding and Sperling, \protect\hyperlink{ref-Ding2006}{2006}; Meese et al., \protect\hyperlink{ref-Meese2006}{2006}; Moradi and Heeger, \protect\hyperlink{ref-Moradi2009}{2009}).
 This is thought to be due to a process of interocular suppression that compensates for the additional excitatory drive caused by stimulating two eyes.
-Our recent work (\protect\hyperlink{ref-Segala2023}{Segala et al., 2023}) has shown that cortical signal combination for luminance flicker is substantially more linear than for spatial patterns, whereas there is evidence of interocular suppression in the pupil pathway.
+Our recent work (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}) has shown that cortical signal combination for luminance flicker is substantially more linear than for spatial patterns, whereas there is evidence of interocular suppression in the pupil pathway.
 
 Most studies that use silent substitution to investigate the PLR stimulate only one eye.
-If the stimulated eye is pharmacologically dilated to control pupil size, the response from the unstimulated eye (known as the consensual response) can be recorded (e.g.
-\protect\hyperlink{ref-McDougal2010}{McDougal and Gamlin, 2010}; \protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}).
+If the stimulated eye is pharmacologically dilated to control pupil size, the response from the unstimulated eye (known as the consensual response) can be recorded (e.g.~McDougal and Gamlin, \protect\hyperlink{ref-McDougal2010}{2010}; Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}).
 While this approach controls the total amount of light incident at the retina, it does not permit investigation of binocular combination for specific photoreceptor pathways.
@@
 Our key comparisons are between monocular and binocular stimulation, and between monocular stimulation and a dichoptic masking condition in which the two eyes are stimulated at different frequencies (0.5 and 0.4Hz).
-The results are interpreted using a contemporary model of binocular vision (\protect\hyperlink{ref-Meese2006}{Meese et al., 2006}) implemented within a hierarchical Bayesian framework.
+The results are interpreted using a contemporary model of binocular vision (Meese et al., \protect\hyperlink{ref-Meese2006}{2006}) implemented within a hierarchical Bayesian framework.
 
@@
 
-In contemporary models of binocular signal combination, the amount of binocular facilitation is determined by the magnitude of interocular suppression, with strong suppression reducing facilitation (\protect\hyperlink{ref-Kingdom2015}{Kingdom and Libenson, 2015}).
+In contemporary models of binocular signal combination, the amount of binocular facilitation is determined by the magnitude of interocular suppression, with strong suppression reducing facilitation (Kingdom and Libenson, \protect\hyperlink{ref-Kingdom2015}{2015}).
 We can estimate the strength of interocular suppression by measuring how much monocular responses are reduced when a dichoptic `mask' is shown to the other eye.
-In our paradigm, the two components flickered at different frequencies (0.5 and 0.4Hz) so that their responses remained distinct in the Fourier spectrum (e.g.
-\protect\hyperlink{ref-Busse2009}{Busse et al., 2009}).
+In our paradigm, the two components flickered at different frequencies (0.5 and 0.4Hz) so that their responses remained distinct in the Fourier spectrum (e.g.~Busse et al., \protect\hyperlink{ref-Busse2009}{2009}).
 The yellow diamond symbols in Figure \ref{fig:FirstHarmonicPlots}a-d show the target responses in this condition, and in most cases were weaker than the monocular responses (red circles).
@@
 
-To quantify the extent of suppression for each photoreceptor pathway, we fitted each data set using a Bayesian hierarchical implementation of a simple binocular combination model (\protect\hyperlink{ref-Meese2006}{Meese et al., 2006}; \protect\hyperlink{ref-Segala2023}{Segala et al., 2023}).
+To quantify the extent of suppression for each photoreceptor pathway, we fitted each data set using a Bayesian hierarchical implementation of a simple binocular combination model (Meese et al., \protect\hyperlink{ref-Meese2006}{2006}; Segala et al., \protect\hyperlink{ref-Segala2023}{2023}).
 Our primary objective was to compare posterior distributions of the weight of interocular suppression, which are shown in Figure \ref{fig:FirstHarmonicPlots}e.
@@
 
-Finally, we inspected the response phase of our four stimulation conditions, given previous reports that these differ across pathways (\protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}), and may be in antiphase for melanopsin and S-cone signals.
+Finally, we inspected the response phase of our four stimulation conditions, given previous reports that these differ across pathways (Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}), and may be in antiphase for melanopsin and S-cone signals.
 Figure \ref{fig:phaseplots} shows the phase angles for the first (a) and second (b) harmonic frequencies for binocular stimulation (monocular stimulation produced very similar results).
@@
 This is the first study to investigate binocular interactions in the melanopsin pathway directly.
-A previous meta-analysis (\protect\hyperlink{ref-Spitschan2019}{Spitschan and Cajochen, 2019}) indicated that there may be a substantial binocular facilitation effect in the circadian pathway, as indexed by melatonin suppression (melatonin is a hormone released by the pineal gland; its production is suppressed by exposure to bright light, particularly when the melanopsin-containing ipRGCs are stimulated).
+A previous meta-analysis (Spitschan and Cajochen, \protect\hyperlink{ref-Spitschan2019}{2019}) indicated that there may be a substantial binocular facilitation effect in the circadian pathway, as indexed by melatonin suppression (melatonin is a hormone released by the pineal gland; its production is suppressed by exposure to bright light, particularly when the melanopsin-containing ipRGCs are stimulated).
 In brief, monocular stimulation of the ipRGCs requires up to ten times the signal strength to produce an equivalent effect to binocular stimulation.
@@
 The explanation for this difference could be due to different anatomical pathways.
-Binocular combination in the circadian system likely takes place in the suprachiasmatic nucleus, whereas in the pupil constriction circuit the Edinger-Westphal nucleus is the most likely site of binocular integration (\protect\hyperlink{ref-Mathot2018}{Mathôt, 2018}).
+Binocular combination in the circadian system likely takes place in the suprachiasmatic nucleus, whereas in the pupil constriction circuit the Edinger-Westphal nucleus is the most likely site of binocular integration (Mathôt, \protect\hyperlink{ref-Mathot2018}{2018}).
 Presumably these anatomical differences, and the practical constraints of the two systems, lead to differences in response.
 
-Our recent psychophysical work (\protect\hyperlink{ref-Baker2024}{Baker et al., 2024}) has looked at binocular interactions in the L-M and S-cone pathways, and compared these to the luminance pathway.
+Our recent psychophysical work (Baker et al., \protect\hyperlink{ref-Baker2024}{2024}) has looked at binocular interactions in the L-M and S-cone pathways, and compared these to the luminance pathway.
 Using a contrast discrimination paradigm with spatial modulations of luminance and colour, Baker et al.
@@
 (\protect\hyperlink{ref-Baker2024}{2024}).
-Our other recent work (\protect\hyperlink{ref-Segala2023}{Segala et al., 2023}) has shown that temporal luminance modulations involve much weaker interocular suppression in the cortical response than do spatial luminance modulations (\protect\hyperlink{ref-Baker2017}{Baker and Wade, 2017}).
+Our other recent work (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}) has shown that temporal luminance modulations involve much weaker interocular suppression in the cortical response than do spatial luminance modulations (Baker and Wade, \protect\hyperlink{ref-Baker2017}{2017}).
 These different normalization processes might reflect different priorities for spatial and temporal vision.
-Spatial vision aims to fuse images to provide binocular single vision, and benefits from `ocularity invariance' (\protect\hyperlink{ref-Baker2007}{Baker et al., 2007}), in which visual appearance is constant when viewed with one eye or two.
-Temporal vision is critical for motion perception, which can involve alternative binocular computations, such as calculating velocity differences between the eyes (\protect\hyperlink{ref-Kaestner2019}{Kaestner et al., 2019}).
+Spatial vision aims to fuse images to provide binocular single vision, and benefits from `ocularity invariance' (Baker et al., \protect\hyperlink{ref-Baker2007}{2007}), in which visual appearance is constant when viewed with one eye or two.
+Temporal vision is critical for motion perception, which can involve alternative binocular computations, such as calculating velocity differences between the eyes (Kaestner et al., \protect\hyperlink{ref-Kaestner2019}{2019}).
 Of course the present measurements were of pupil size, which may be subject to different anatomical and functional constraints from those in the cortex.
@@
 To present synchronised stimulus modulations independently to each eye, two light engines (SpectraTuneLAB: LEDMOTIVE Technologies, LLC, Barcelona, Spain), each with 10 independently addressable LED colour channels, were integrated into a customised viewing system.
-The light engines were operated via a Python interface to their REST API (\protect\hyperlink{ref-Martin2022}{Martin et al., 2022}), which supports synchronous launch and playback of spectral sequences prepared in advance and stored in JSON format.
+The light engines were operated via a Python interface to their REST API (Martin et al., \protect\hyperlink{ref-Martin2022}{2022}), which supports synchronous launch and playback of spectral sequences prepared in advance and stored in JSON format.
 When preparing the spectral sequences, the age of participants was used to account for the yellowing of the lenses.
-We calculated silent substitution solutions using the \emph{PySilSub} toolbox (\protect\hyperlink{ref-Martin2023}{Martin et al., 2023}), using linear algebra.
+We calculated silent substitution solutions using the \emph{PySilSub} toolbox (Martin et al., \protect\hyperlink{ref-Martin2023}{2023}), using linear algebra.
 The outputs of the two light engines (see Figure \ref{fig:spectraplots}b,c) were calibrated using an Ocean Optics Jaz spectroradiometer, which was wavelength-calibrated to an Argon lamp and intensity calibrated using a NIST-traceable light source.
-We used the Stockman and Sharpe (\protect\hyperlink{ref-Stockman2000}{2000}) 10-degree cone fundamentals, and estimates of melanopsin absorbance spectra from CIE S 026 (discussed in \protect\hyperlink{ref-Martin2023}{Martin et al., 2023}) to calculate \(\alpha\)-opic irradiance.
+We used the Stockman and Sharpe (\protect\hyperlink{ref-Stockman2000}{2000}) 10-degree cone fundamentals, and estimates of melanopsin absorbance spectra from CIE S 026 (discussed in Martin et al., \protect\hyperlink{ref-Martin2023}{2023}) to calculate \(\alpha\)-opic irradiance.
 
@@
 The diffuser discs were positioned in the objective planes of the lenses of a modified VR headset (SHINECON SC-G01, Dongguan Shinecon Industrial Co.~Ltd., Guangdong, China), which was used by the participants to view the stimuli.
-The stimuli were two discs of flickering light with a diameter of approximately 30 degrees, which were fused together into a cyclopean percept resembling a donut-shaped ring of light, similar to that used in other studies (e.g., \protect\hyperlink{ref-Barrionuevo2016}{Barrionuevo and Cao, 2016}; \protect\hyperlink{ref-Murray2018}{Murray et al., 2018}; \protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}; \protect\hyperlink{ref-Zele2018}{Zele et al., 2018}).
+The stimuli were two discs of flickering light with a diameter of approximately 30 degrees, which were fused together into a cyclopean percept resembling a donut-shaped ring of light, similar to that used in other studies (e.g., Barrionuevo and Cao, \protect\hyperlink{ref-Barrionuevo2016}{2016}; Murray et al., \protect\hyperlink{ref-Murray2018}{2018}; Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}; Zele et al., \protect\hyperlink{ref-Zele2018}{2018}).
 The VR headset modifications allowed for small adjustments to account for individual differences in interpupillary distance and focal length.
-The use of this set up allowed us to modulate the stimuli in three different ocular configurations, similar to the ones we used in our previous study (\protect\hyperlink{ref-Segala2023}{Segala et al., 2023}): monocular, binocular and dichoptic.
+The use of this set up allowed us to modulate the stimuli in three different ocular configurations, similar to the ones we used in our previous study (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}): monocular, binocular and dichoptic.
 In the monocular configuration, the unstimulated eye still saw a non-flickering disc of mean luminance.
 A schematic of the stimulation system is shown in Figure \ref{fig:spectraplots}a.
-Pupillometry data were collected using a binocular Pupil Core eye-tracker headset (Pupil Labs GmbH, Berlin, Germany, \protect\hyperlink{ref-Kassner2014}{Kassner et al., 2014}) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
+Pupillometry data were collected using a binocular Pupil Core eye-tracker headset (Pupil Labs GmbH, Berlin, Germany, Kassner et al., \protect\hyperlink{ref-Kassner2014}{2014}) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
 
-Our previous study (\protect\hyperlink{ref-Segala2023}{Segala et al., 2023}) used a temporal frequency of 2Hz for foveal luminance flicker, and recorded EEG data simultaneously with pupillometry.
+Our previous study (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}) used a temporal frequency of 2Hz for foveal luminance flicker, and recorded EEG data simultaneously with pupillometry.
 Initial pilot experiments indicated that this frequency was too high to elicit measurable responses when stimulating individual photoreceptor pathways.
-For all experiments, we therefore used a primary flicker frequency of 0.5Hz, as previous literature showed that this was slow enough to elicit a pupil response from all photoreceptor classes (\protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}).
-We also focussed on only recording pupillometry data as this frequency would be too slow to elicit steady-state EEG responses (\protect\hyperlink{ref-Norcia2015}{Norcia et al., 2015}).
+For all experiments, we therefore used a primary flicker frequency of 0.5Hz, as previous literature showed that this was slow enough to elicit a pupil response from all photoreceptor classes (Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}).
+We also focussed on only recording pupillometry data as this frequency would be too slow to elicit steady-state EEG responses (Norcia et al., \protect\hyperlink{ref-Norcia2015}{2015}).
 
@@
 Pupil responses to binocular temporal contrast modulations were examined in a factorial design that combined six ocular conditions and five temporal contrast levels: 6, 12, 24, 48 and 96\% of the available dynamic range.
-This design, similar to that used in our previous studies (\protect\hyperlink{ref-Baker2020}{Baker et al., 2020}; \protect\hyperlink{ref-Baker2017}{Baker and Wade, 2017}; \protect\hyperlink{ref-Segala2023}{Segala et al., 2023}), was applied in four separate experiments, each with a different mode of photoreceptor stimulation.
+This design, similar to that used in our previous studies (Baker et al., \protect\hyperlink{ref-Baker2020}{2020}; Baker and Wade, \protect\hyperlink{ref-Baker2017}{2017}; Segala et al., \protect\hyperlink{ref-Segala2023}{2023}), was applied in four separate experiments, each with a different mode of photoreceptor stimulation.
 In the first three conditions, the discs flickered at 0.5 Hz, in either a monocular, binocular or dichoptic arrangement.
@@
 Using a trackball, participants adjusted the angle in cone space to find their subjective isoluminant point, which resulted in changing the flickering intensity of the stimulus until the amplitude of the flicker appeared to be minimised.
-The result was used to modify the requested contrasts during stimulus preparation so as to account for individual differences affecting perceived illuminance, principally the L:M cone ratio (\protect\hyperlink{ref-Carroll2002}{Carroll et al., 2002}; \protect\hyperlink{ref-Hofer2005}{Hofer et al., 2005}).
+The result was used to modify the requested contrasts during stimulus preparation so as to account for individual differences affecting perceived illuminance, principally the L:M cone ratio (Carroll et al., \protect\hyperlink{ref-Carroll2002}{2002}; Hofer et al., \protect\hyperlink{ref-Hofer2005}{2005}).
 
@@
 
-The pupillometry data were analysed using the same method we used in our previous study (\protect\hyperlink{ref-Segala2023}{Segala et al., 2023}).
-The data were converted from mp4 videos to a csv text file using the Pupil Player software (\protect\hyperlink{ref-Kassner2014}{Kassner et al., 2014}), which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
+The pupillometry data were analysed using the same method we used in our previous study (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}).
+The data were converted from mp4 videos to a csv text file using the Pupil Player software (Kassner et al., \protect\hyperlink{ref-Kassner2014}{2014}), which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
 The individual data were then loaded into R for analysis, where a ten-second waveform for each trial in each eye was extracted (excluding the first two seconds after stimulus onset).
@@
 Finally, data were averaged across all participants to obtain the group results.
-We used coherent averaging and at each stage we excluded data points with a Mahalanobis distance exceeding \(D\) = 3 from the complex-valued mean (\protect\hyperlink{ref-Baker2021}{Baker, 2021}).
+We used coherent averaging and at each stage we excluded data points with a Mahalanobis distance exceeding \(D\) = 3 from the complex-valued mean (Baker, \protect\hyperlink{ref-Baker2021}{2021}).
 For monocular stimulation, we confirmed that the consensual response was equivalent to the response in the stimulated eye.
@@
 
-To describe our data, we used the same model described in our previous study (\protect\hyperlink{ref-Segala2023}{Segala et al., 2023}).
+To describe our data, we used the same model described in our previous study (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}).
 The model has the same general form as the first stage of the contrast gain control model proposed by Meese et al.
 (\protect\hyperlink{ref-Meese2006}{2006}), but omits the second stage.
-For the previous model that we used (\protect\hyperlink{ref-Segala2023}{Segala et al., 2023}), the exponent of the numerator and denominator had fixed values of 2 and (implicitly) 1.
+For the previous model that we used (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}), the exponent of the numerator and denominator had fixed values of 2 and (implicitly) 1.
 Here, we allow these parameters (called \emph{p} and \emph{q}) to be free, in order to permit different shapes of contrast response function, e.g.~accelerating or saturating.
@@
 
-The models were fit using a hierarchical Bayesian framework implemented in Stan (\protect\hyperlink{ref-Carpenter2017}{Carpenter et al., 2017}).
+The models were fit using a hierarchical Bayesian framework implemented in Stan (Carpenter et al., \protect\hyperlink{ref-Carpenter2017}{2017}).
 The data for each photoreceptor type and response frequency was fit separately, for a total of 8 model fits.
 The prior for the \(\omega\) parameter was Gaussian, with a mean of 1 and standard deviation of 0.5.
-Priors for the other free parameters were also Gaussian, with mean values based on previous work (\protect\hyperlink{ref-Segala2023}{Segala et al., 2023}).
+Priors for the other free parameters were also Gaussian, with mean values based on previous work (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}).
 We calculated over \ensuremath{10^{6}} posterior samples, and retained 10\% for plotting.
@@
 \hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-Baker2021}{}}%
+\leavevmode\hypertarget{ref-Baker2021}{}%
 Baker DH.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Baker2024}{}}%
+\leavevmode\hypertarget{ref-Baker2024}{}%
 Baker DH, Hansford KJ, Segala FG, Morsi AY, Huxley RJ, Martin JT, Rockman M, Wade AR.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Baker2018}{}}%
+\leavevmode\hypertarget{ref-Baker2018}{}%
 Baker DH, Lygo FA, Meese TS, Georgeson MA.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Baker2007}{}}%
+\leavevmode\hypertarget{ref-Baker2007}{}%
 Baker DH, Meese TS, Georgeson MA.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Baker2020}{}}%
+\leavevmode\hypertarget{ref-Baker2020}{}%
 Baker DH, Vilidaite G, McClarnon E, Valkova E, Bruno A, Millman RE.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Baker2017}{}}%
+\leavevmode\hypertarget{ref-Baker2017}{}%
 Baker DH, Wade AR.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Barrionuevo2016}{}}%
+\leavevmode\hypertarget{ref-Barrionuevo2016}{}%
 Barrionuevo PA, Cao D.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Barrionuevo2018}{}}%
+\leavevmode\hypertarget{ref-Barrionuevo2018}{}%
 Barrionuevo PA, McAnany JJ, Zele AJ, Cao D.
 2018.
-Non-linearities in the {Rod} and {Cone} {Photoreceptor} {Inputs} to the {Afferent} {Pupil} {Light} {Response}.
+Non-linearities in the Rod and Cone Photoreceptor Inputs to the Afferent Pupil Light Response.
 \emph{Frontiers in Neurology} \textbf{9}.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Barrionuevo2014}{}}%
+\leavevmode\hypertarget{ref-Barrionuevo2014}{}%
 Barrionuevo PA, Nicandro N, McAnany JJ, Zele AJ, Gamlin P, Cao D.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Busse2009}{}}%
+\leavevmode\hypertarget{ref-Busse2009}{}%
 Busse L, Wade AR, Carandini M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Campbell1965}{}}%
+\leavevmode\hypertarget{ref-Campbell1965}{}%
 Campbell FW, Green DG. 1965. Monocular versus binocular visual acuity. \emph{Nature} \textbf{208}:191--2. doi:\href{https://doi.org/10.1038/208191a0}{10.1038/208191a0}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Cao2015}{}}%
+\leavevmode\hypertarget{ref-Cao2015}{}%
 Cao D, Nicandro N, Barrionuevo PA.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Carpenter2017}{}}%
+\leavevmode\hypertarget{ref-Carpenter2017}{}%
 Carpenter B, Gelman A, Hoffman MD, Lee D, Goodrich B, Betancourt M, Brubaker MA, Guo J, Li P, Riddell A.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Carroll2002}{}}%
-Carroll J, Neitz J, Neitz M.
-2002.
-Estimates of {L}:{M} cone ratio from {ERG} flicker photometry and genetics.
-\emph{Journal of Vision} \textbf{2}:1.
-doi:\href{https://doi.org/10.1167/2.8.1}{10.1167/2.8.1}
+\leavevmode\hypertarget{ref-Carroll2002}{}%
+Carroll J, Neitz J, Neitz M. 2002. Estimates of L:M cone ratio from ERG flicker photometry and genetics. \emph{Journal of Vision} \textbf{2}:1. doi:\href{https://doi.org/10.1167/2.8.1}{10.1167/2.8.1}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Dacey2005}{}}%
+\leavevmode\hypertarget{ref-Dacey2005}{}%
 Dacey DM, Liao H-W, Peterson BB, Robinson FR, Smith VC, Pokorny J, Yau K-W, Gamlin PD.
 2005.
-Melanopsin-expressing ganglion cells in primate retina signal colour and irradiance and project to the {LGN}.
+Melanopsin-expressing ganglion cells in primate retina signal colour and irradiance and project to the LGN.
 \emph{Nature} \textbf{433}:749--754.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Dacey2003}{}}%
+\leavevmode\hypertarget{ref-Dacey2003}{}%
 Dacey DM, Peterson BB, Robinson FR, Gamlin PD.
 2003.
-Fireworks in the primate retina: In vitro photodynamics reveals diverse LGN-projecting ganglion cell types.
+Fireworks in the primate retina: In vitro photodynamics reveals diverse lgn-projecting ganglion cell types.
 \emph{Neuron} \textbf{37}:15--27.
-doi:\url{https://doi.org/10.1016/S0896-6273(02)01143-1}
+doi:\href{https://doi.org/https://doi.org/10.1016/S0896-6273(02)01143-1}{https://doi.org/10.1016/S0896-6273(02)01143-1}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Ding2006}{}}%
+\leavevmode\hypertarget{ref-Ding2006}{}%
 Ding J, Sperling G.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Estevez1982}{}}%
+\leavevmode\hypertarget{ref-Estevez1982}{}%
 Estévez O, Spekreijse H.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Gamlin2007}{}}%
+\leavevmode\hypertarget{ref-Gamlin2007}{}%
 Gamlin PDR, McDougal DH, Pokorny J, Smith VC, Yau K-W, Dacey DM.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Hofer2005}{}}%
+\leavevmode\hypertarget{ref-Hofer2005}{}%
 Hofer H, Carroll J, Neitz J, Neitz M, Williams DR.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Hubel1962}{}}%
+\leavevmode\hypertarget{ref-Hubel1962}{}%
 Hubel DH, Wiesel TN.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Kaestner2019}{}}%
+\leavevmode\hypertarget{ref-Kaestner2019}{}%
 Kaestner M, Maloney RT, Wailes-Newson KH, Bloj M, Harris JM, Morland AB, Wade AR.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Kassner2014}{}}%
+\leavevmode\hypertarget{ref-Kassner2014}{}%
 Kassner M, Patera W, Bulling A.
 2014.
-Pupil: An open source platform for pervasive eye tracking and mobile gaze-based interaction.Proceedings of the 2014 {ACM} International Joint Conference on Pervasive and Ubiquitous Computing: Adjunct Publication.
-{ACM}.
+Pupil: An open source platform for pervasive eye tracking and mobile gaze-based interaction.Proceedings of the 2014 ACM International Joint Conference on Pervasive and Ubiquitous Computing: Adjunct Publication.
+ACM.
 doi:\href{https://doi.org/10.1145/2638728.2641695}{10.1145/2638728.2641695}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Kingdom2015}{}}%
+\leavevmode\hypertarget{ref-Kingdom2015}{}%
 Kingdom FAA, Libenson L.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Legge1984}{}}%
-Legge GE. 1984. Binocular contrast summation--II. Quadratic summation. \emph{Vision Res} \textbf{24}:385--94. doi:\href{https://doi.org/10.1016/0042-6989(84)90064-6}{10.1016/0042-6989(84)90064-6}
+\leavevmode\hypertarget{ref-Legge1984}{}%
+Legge GE. 1984. Binocular contrast summation--ii. Quadratic summation. \emph{Vision Res} \textbf{24}:385--94. doi:\href{https://doi.org/10.1016/0042-6989(84)90064-6}{10.1016/0042-6989(84)90064-6}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Lucas2003}{}}%
+\leavevmode\hypertarget{ref-Lucas2003}{}%
 Lucas RJ, Hattar S, Takao M, Berson DM, Foster RG, Yau K-W.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Markwell2010}{}}%
+\leavevmode\hypertarget{ref-Markwell2010}{}%
 Markwell EL, Feigl B, Zele AJ.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Martin2023}{}}%
+\leavevmode\hypertarget{ref-Martin2023}{}%
 Martin JT, Boynton GM, Baker DH, Wade AR, Spitschan M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Martin2022}{}}%
+\leavevmode\hypertarget{ref-Martin2022}{}%
 Martin JT, Pinto J, Bulte D, Spitschan M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Mathot2018}{}}%
+\leavevmode\hypertarget{ref-Mathot2018}{}%
 Mathôt S. 2018. Pupillometry: Psychology, physiology, and function. \emph{J Cogn} \textbf{1}:16. doi:\href{https://doi.org/10.5334/joc.18}{10.5334/joc.18}
 
-\leavevmode\vadjust pre{\hypertarget{ref-McDougal2015}{}}%
+\leavevmode\hypertarget{ref-McDougal2015}{}%
 McDougal DH, Gamlin PD. 2015. Autonomic control of the eye. \emph{Comprehensive Physiology} \textbf{5}:439--473. doi:\href{https://doi.org/10.1002/cphy.c140014}{10.1002/cphy.c140014}
 
-\leavevmode\vadjust pre{\hypertarget{ref-McDougal2010}{}}%
+\leavevmode\hypertarget{ref-McDougal2010}{}%
 McDougal DH, Gamlin PD.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-McDougal2008}{}}%
+\leavevmode\hypertarget{ref-McDougal2008}{}%
 McDougal DH, Gamlin PD. 2008. Pupillary control pathways.The Senses: A Comprehensive Reference. Elsevier. pp. 521--536.
 
-\leavevmode\vadjust pre{\hypertarget{ref-Meese2006}{}}%
+\leavevmode\hypertarget{ref-Meese2006}{}%
 Meese TS, Georgeson MA, Baker DH. 2006. Binocular contrast vision at and above threshold. \emph{Journal of Vision} \textbf{6}:1224--43. doi:\href{https://doi.org/10.1167/6.11.7}{10.1167/6.11.7}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Moradi2009}{}}%
+\leavevmode\hypertarget{ref-Moradi2009}{}%
 Moradi F, Heeger DJ. 2009. Inter-ocular contrast normalization in human visual cortex. \emph{J Vis} \textbf{9}:13.1--22. doi:\href{https://doi.org/10.1167/9.3.13}{10.1167/9.3.13}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Murray2018}{}}%
+\leavevmode\hypertarget{ref-Murray2018}{}%
 Murray IJ, Kremers J, McKeefry D, Parry NRA.
 2018.
-Paradoxical pupil responses to isolated {M}-cone increments.
+Paradoxical pupil responses to isolated M-cone increments.
 \emph{Journal of the Optical Society of America A} \textbf{35}:B66--B71.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Norcia2015}{}}%
+\leavevmode\hypertarget{ref-Norcia2015}{}%
 Norcia AM, Appelbaum LG, Ales JM, Cottereau BR, Rossion B.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Panda2002}{}}%
+\leavevmode\hypertarget{ref-Panda2002}{}%
 Panda S, Sato TK, Castrucci AM, Rollag MD, DeGrip WJ, Hogenesch JB, Provencio I, Kay SA.
 2002.
-Melanopsin (Opn4) requirement for normal light-induced circadian phase shifting.
+Melanopsin (opn4) requirement for normal light-induced circadian phase shifting.
 \emph{Science} \textbf{298}:2213--2216.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Provencio2000}{}}%
+\leavevmode\hypertarget{ref-Provencio2000}{}%
 Provencio I, Rodriguez IR, Jiang G, Hayes WP, Moreira EF, Rollag MD.
 2000.
-A {Novel} {Human} {Opsin} in the {Inner} {Retina}.
+A Novel Human Opsin in the Inner Retina.
 \emph{Journal of Neuroscience} \textbf{20}:600--605.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Ruby2002}{}}%
+\leavevmode\hypertarget{ref-Ruby2002}{}%
 Ruby NF, Brennan TJ, Xie X, Cao V, Franken P, Heller HC, O'Hara BF.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Segala2023}{}}%
+\leavevmode\hypertarget{ref-Segala2023}{}%
 Segala FG, Bruno A, Martin JT, Aung MT, Wade AR, Baker DH.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Shapiro1996}{}}%
+\leavevmode\hypertarget{ref-Shapiro1996}{}%
 Shapiro AG, Pokorny J, Smith VC.
 1996.
-Cone{\textendash}rod receptor spaces with illustrations that use {CRT} phosphor and light-emitting-diode spectra.
+Conerod receptor spaces with illustrations that use CRT phosphor and light-emitting-diode spectra.
 \emph{Journal of the Optical Society of America A} \textbf{13}:2319.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Spitschan2019}{}}%
+\leavevmode\hypertarget{ref-Spitschan2019}{}%
 Spitschan M, Cajochen C. 2019. Binocular facilitation in light-mediated melatonin suppression? \emph{J Pineal Res} \textbf{67}:e12602. doi:\href{https://doi.org/10.1111/jpi.12602}{10.1111/jpi.12602}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Spitschan2014}{}}%
+\leavevmode\hypertarget{ref-Spitschan2014}{}%
 Spitschan M, Jain S, Brainard DH, Aguirre GK.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Spitschan2018}{}}%
+\leavevmode\hypertarget{ref-Spitschan2018}{}%
 Spitschan M, Woelders T.
 2018.
-The {Method} of {Silent} {Substitution} for {Examining} {Melanopsin} {Contributions} to {Pupil} {Control}.
+The Method of Silent Substitution for Examining Melanopsin Contributions to Pupil Control.
 \emph{Frontiers in Neurology} \textbf{9}.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Stockman2000}{}}%
+\leavevmode\hypertarget{ref-Stockman2000}{}%
 Stockman A, Sharpe LT.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Wang2015}{}}%
+\leavevmode\hypertarget{ref-Wang2015}{}%
 Wang C-A, Munoz DP.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Woelders2018}{}}%
+\leavevmode\hypertarget{ref-Woelders2018}{}%
 Woelders T, Leenheers T, Gordijn MCM, Hut RA, Beersma DGM, Wams EJ.
 2018.
-Melanopsin- and {L}-cone--induced pupil constriction is inhibited by {S}- and {M}-cones in humans.
+Melanopsin- and L-cone--induced pupil constriction is inhibited by S- and M-cones in humans.
 \emph{Proceedings of the National Academy of Sciences} \textbf{115}:792--797.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Wyatt1981}{}}%
+\leavevmode\hypertarget{ref-Wyatt1981}{}%
 Wyatt HJ, Musselman JF.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Zele2018}{}}%
+\leavevmode\hypertarget{ref-Zele2018}{}%
 Zele AJ, Feigl B, Adhikari P, Maynard ML, Cao D.
@@
 
-\end{CSLReferences}
-
 \end{document}

### 2024-05-22 manuscript.Rmd
Changed Annie's name
Added autobuild, experiment code, switched refs to pnas style

@@
 author: |
- | Federico G. Segala$^1$, Aurelio Bruno$^{1,2}$, Joel T. Martin$^{1,3}$, Annie Y. Morsi$^1$, Alex R. Wade$^{1,4}$
+ | Federico G. Segala$^1$, Aurelio Bruno$^{1,2}$, Joel T. Martin$^{1,3}$, Anisa Y. Morsi$^1$, Alex R. Wade$^{1,4}$
  | & Daniel H. Baker$^{1,4}$
@@
 linkcolor: black
-csl: elife.csl
+csl: pnas.csl
 header-includes:
-- \usepackage{caption}
+  \usepackage{caption}
+  \usepackage{lineno} \linenumbers
 ---
@@
 # check which packages are installed, install the missing ones, and activate
-packagelist <- c('knitr','remotes','tictoc','R.matlab','bookdown','grImport','png','tiff','pals','ez','gtools','signal','boot','quickpsy','rstan','bayestestR','rstatix','coda','parallel','utils','osfr','ggplot2','grid','gridExtra','cowplot','ggsignif','osfr') # list of CRAN packages
+packagelist <- c('knitr','remotes','tictoc','R.matlab','bookdown','grImport','png','tiff','pals','ez','gtools','signal','boot','rstan','bayestestR','rstatix','coda','parallel','utils','osfr','grid','gridExtra','cowplot','ggsignif') # list of CRAN packages
 
@@
 
-$^2$School of Psychology and Vision Sciences, Leicester, United Kingdom.
+$^2$School of Psychology and Vision Sciences, University of Leicester, Leicester, United Kingdom.
 
@@
 
-plotlims <- c(380,800,0,0.2)
-ticklocsx <- seq(400,800,100)    # locations of tick marks on x axis
-ticklocsy <- seq(0,0.2,0.1)    # locations of tick marks on y axis
-ticklabelsx <- ticklocsx        # set labels for x ticks
-ticklabelsy <- ticklocsy    # set labels for y ticks
-
 plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
@@
 
-plotlims <- c(0.5,5.5,0,15)
-ticklocsx <- 1:5    # locations of tick marks on x axis
+plotlims <- c(0.5,4.5,0,15)
+ticklocsx <- 1:4    # locations of tick marks on x axis
 ticklocsy <- seq(0,15,5)    # locations of tick marks on y axis
-ticklabelsx <- c('sc','mc','lc','rh','mel')        # set labels for x ticks
+ticklabelsx <- c('sc','mc','lc','mel')        # set labels for x ticks
 ticklabelsy <- ticklocsy    # set labels for y ticks
@@
 
-for (b in 1:5){
+coneab <- coneab[c(1:3,5),]   # don't plot rod predictions
+for (b in 1:4){
   polygon(c(b-0.3,b,b,b-0.3),c(0,0,coneab[b,2],coneab[b,2]),col=colpal[2],border=NA)
@@
 
-plotlims <- c(380,800,-0.2,0.2)
-ticklocsx <- seq(400,800,100)    # locations of tick marks on x axis
-ticklocsy <- seq(-0.2,0.2,0.1)    # locations of tick marks on y axis
-ticklabelsx <- ticklocsx        # set labels for x ticks
-ticklabelsy <- ticklocsy    # set labels for y ticks
-
 plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
@@
 
-plotlims <- c(0.5,5.5,-100,100)
-ticklocsx <- 1:5    # locations of tick marks on x axis
+pcontrast <- pcontrast[c(1,2,3,5),]   # don't plot rods
+
+plotlims <- c(0.5,4.5,-100,100)
+ticklocsx <- 1:4    # locations of tick marks on x axis
 ticklocsy <- seq(-100,100,50)    # locations of tick marks on y axis
-ticklabelsx <- c('sc','mc','lc','rh','mel')        # set labels for x ticks
+ticklabelsx <- c('sc','mc','lc','mel')        # set labels for x ticks
 ticklabelsy <- ticklocsy    # set labels for y ticks
@@
 
-for (b in 1:5){
+for (b in 1:4){
   polygon(c(b-0.3,b+0.3,b+0.3,b-0.3),c(0,0,pcontrast[b,4],pcontrast[b,4]),col=stimcolours[1],border='black',lwd=2)
@@
 
-lines(c(0.5,5.5),c(0,0),lwd=2)
-
-text(4.55,80,'(i)',pos=4,cex=2)
-
-plotlims <- c(0.5,5.5,-20,20)
-ticklocsx <- 1:5    # locations of tick marks on x axis
+lines(c(0.5,4.5),c(0,0),lwd=2)
+
+text(3.65,80,'(i)',pos=4,cex=2)
+
+plotlims <- c(0.5,4.5,-20,20)
+ticklocsx <- 1:4    # locations of tick marks on x axis
 ticklocsy <- seq(-20,20,10)    # locations of tick marks on y axis
-ticklabelsx <- c('sc','mc','lc','rh','mel')        # set labels for x ticks
 ticklabelsy <- ticklocsy    # set labels for y ticks
@@
 
-for (b in 1:5){
+for (b in 1:4){
   polygon(c(b-0.3,b+0.3,b+0.3,b-0.3),c(0,0,pcontrast[b,6],pcontrast[b,6]),col=stimcolours[3],border='black',lwd=2)
@@
 
-lines(c(0.5,5.5),c(0,0),lwd=2)
-
-text(4.6,18,'(j)',pos=4,cex=2)
-
-plotlims <- c(0.5,5.5,-50,50)
-ticklocsx <- 1:5    # locations of tick marks on x axis
+lines(c(0.5,4.5),c(0,0),lwd=2)
+
+text(3.6,18,'(j)',pos=4,cex=2)
+
+plotlims <- c(0.5,4.5,-50,50)
+ticklocsx <- 1:4    # locations of tick marks on x axis
 ticklocsy <- seq(-50,50,25)    # locations of tick marks on y axis
-ticklabelsx <- c('sc','mc','lc','rh','mel')        # set labels for x ticks
 ticklabelsy <- ticklocsy    # set labels for y ticks
@@
 
-for (b in 1:5){
+for (b in 1:4){
   polygon(c(b-0.3,b+0.3,b+0.3,b-0.3),c(0,0,pcontrast[b,8],pcontrast[b,8]),col=stimcolours[5],border='black',lwd=2)
@@
 
-lines(c(0.5,5.5),c(0,0),lwd=2)
-
-text(4.6,45,'(k)',pos=4,cex=2)
-
-plotlims <- c(0.5,5.5,-20,20)
-ticklocsx <- 1:5    # locations of tick marks on x axis
-ticklocsy <- seq(-20,20,20)    # locations of tick marks on y axis
-ticklabelsx <- c('sc','mc','lc','rh','mel')        # set labels for x ticks
+lines(c(0.5,4.5),c(0,0),lwd=2)
+
+text(3.6,45,'(k)',pos=4,cex=2)
+
+plotlims <- c(0.5,4.5,-20,20)
+ticklocsx <- 1:4    # locations of tick marks on x axis
+ticklocsy <- seq(-20,20,10)    # locations of tick marks on y axis
 ticklabelsy <- ticklocsy    # set labels for y ticks
@@
 
-for (b in 1:5){
+for (b in 1:4){
   polygon(c(b-0.3,b+0.3,b+0.3,b-0.3),c(0,0,pcontrast[b,10],pcontrast[b,10]),col=stimcolours[7],border='black',lwd=2)
@@
 
-lines(c(0.5,5.5),c(0,0),lwd=2)
+lines(c(0.5,4.5),c(0,0),lwd=2)
 
@@
 if (plotcontrasts==0){
-plotlims <- c(0.5,5.5,-15,15)
-ticklocsx <- 1:5    # locations of tick marks on x axis
+plotlims <- c(0.5,4.5,-15,15)
+ticklocsx <- 1:4    # locations of tick marks on x axis
 ticklocsy <- seq(-15,15,5)    # locations of tick marks on y axis
-ticklabelsx <- c('sc','mc','lc','rh','mel')        # set labels for x ticks
+ticklabelsx <- c('sc','mc','lc','mel')        # set labels for x ticks
 ticklabelsy <- ticklocsy    # set labels for y ticks
@@
 
-for (b in 1:5){
+for (b in 1:4){
   polygon(c(b-0.3,b+0.3,b+0.3,b-0.3),c(0,0,coneab[b,4],coneab[b,4]),col=stimcolours[1],border='black',lwd=2)
@@
 
-lines(c(0.5,5.5),c(0,0),lwd=2)
-
-text(4.5,14,'(i)',pos=4,cex=2)
-
-plotlims <- c(0.5,5.5,-4,4)
-ticklocsx <- 1:5    # locations of tick marks on x axis
+lines(c(0.5,4.5),c(0,0),lwd=2)
+
+text(3.5,14,'(i)',pos=4,cex=2)
+
+plotlims <- c(0.5,4.5,-4,4)
+ticklocsx <- 1:4    # locations of tick marks on x axis
 ticklocsy <- seq(-4,4,2)    # locations of tick marks on y axis
-ticklabelsx <- c('sc','mc','lc','rh','mel')        # set labels for x ticks
 ticklabelsy <- ticklocsy    # set labels for y ticks
@@
 
-for (b in 1:5){
+for (b in 1:4){
   polygon(c(b-0.3,b+0.3,b+0.3,b-0.3),c(0,0,coneab[b,6],coneab[b,6]),col=stimcolours[3],border='black',lwd=2)
@@
 
-lines(c(0.5,5.5),c(0,0),lwd=2)
-
-text(4.5,3.6,'(j)',pos=4,cex=2)
-
-plotlims <- c(0.5,5.5,-4,4)
-ticklocsx <- 1:5    # locations of tick marks on x axis
-ticklocsy <- seq(-4,4,2)    # locations of tick marks on y axis
-ticklabelsx <- c('sc','mc','lc','rh','mel')        # set labels for x ticks
-ticklabelsy <- ticklocsy    # set labels for y ticks
+lines(c(0.5,4.5),c(0,0),lwd=2)
+
+text(3.5,3.6,'(j)',pos=4,cex=2)
 
@@
 
-for (b in 1:5){
+for (b in 1:4){
   polygon(c(b-0.3,b+0.3,b+0.3,b-0.3),c(0,0,coneab[b,8],coneab[b,8]),col=stimcolours[5],border='black',lwd=2)
@@
 
-lines(c(0.5,5.5),c(0,0),lwd=2)
-
-text(4.5,3.6,'(k)',pos=4,cex=2)
-
-plotlims <- c(0.5,5.5,-4,4)
-ticklocsx <- 1:5    # locations of tick marks on x axis
-ticklocsy <- seq(-4,4,2)    # locations of tick marks on y axis
-ticklabelsx <- c('sc','mc','lc','rh','mel')        # set labels for x ticks
-ticklabelsy <- ticklocsy    # set labels for y ticks
+lines(c(0.5,4.5),c(0,0),lwd=2)
+
+text(3.5,3.6,'(k)',pos=4,cex=2)
 
@@
 
-for (b in 1:5){
+for (b in 1:4){
   polygon(c(b-0.3,b+0.3,b+0.3,b-0.3),c(0,0,coneab[b,10],coneab[b,10]),col=stimcolours[7],border='black',lwd=2)
@@
 
-lines(c(0.5,5.5),c(0,0),lwd=2)
-
-text(4.5,3.6,'(l)',pos=4,cex=2)
+lines(c(0.5,4.5),c(0,0),lwd=2)
+
+text(3.5,3.6,'(l)',pos=4,cex=2)
 }
@@
 The diameter of the pupil fluctuates in response to levels of ambient light and is regulated by the autonomic nervous system.
-Increasing light in one eye causes both pupils to constrict, implying the system must combine signals across the two eyes, a process of binocular integration occuring independently of visual cortex.
+Increasing light in one eye causes both pupils to constrict, implying the system must combine signals across the two eyes -- a process of binocular integration occuring independently of visual cortex.
 Distinct classes of retinal photoreceptor are involved in controlling and maintaining pupil diameter, with cones and rods driving the initial constriction and intrinsically photosensitive retinal ganglion cells maintaining diameter over prolonged time periods.
-Here, we used silent substitution to investigate binocular combination while targeting different photoreceptor pathways with sinusoidally modulated inputs.
+Here, we investigate binocular combination by targeting different photoreceptor pathways using the silent substitution method to modulate the input spectra.
 We find different patterns of binocular response in each pathway, and across the first and second harmonic frequencies.
@@
 Notably, the L-M pathway involved binocular inhibition, whereby responses to binocular stimulation were weaker than for monocular stimulation.
-The second harmonic involved greater binocular facilitation in all pathways, and we show that binocular facilitation is negatively correlated with the magnitude of dichoptic masking.
+The second harmonic involved strong interocular suppression in all pathways, but with some evidence of binocular facilitation.
 Our results are consistent with a computational model of binocular signal combination (implemented in a Bayesian hierarchical framework), in which the weight of interocular suppression differs across pathways.
@@
 They express the photopigment melanopsin, and are involved in the regulation of the circadian rhythm [@Provencio2000; @Panda2002; @Ruby2002], forming a major input to the PON [@Dacey2003].
-The first direct evidence of the involvement of the ipRGCs in the PLR was shown in rats by @Lucas2003 who genetically deleted the melanopsin gene from rats, resulting in the loss of the intrinsic photosensitivity of the cells and a reduced pupil constriction.
+The first direct evidence of the involvement of the ipRGCs in the PLR was shown in melanopsin knockout rats by @Lucas2003, resulting in the loss of the intrinsic photosensitivity of the cells and a reduced pupil constriction.
 This same behaviour was later also observed in primates and humans [@Gamlin2007], where it was demonstrated that the PLR continues during light presentation even when cone and rod signalling is blocked, indicating the primary role of the ipRGCs in maintaining pupil constriction over a prolonged time.
@@
 Suppression can also be estimated from the responses at 0.4Hz (Figure \@ref(fig:FirstHarmonicPlots)f-i).
-The reduced amplitude in the binocular cross condition (purple squares) relative to the 0.4Hz monocular condition (grey circles), and the progressive decline in amplitude of the dichoptic cross response (yellow diamonds) also differ across photoreceptor conditions, showing similar differences to those observed at 0.5Hz.
-
-To quantify the extent of suppression for each photoreceptor pathway, we fitted each data set using a Bayesian hierarchical implementation of a simple binocular combination model [@Meese2006; @Segala2023].
+The reduced amplitude in the binocular cross condition (where the two eyes received different temporal frequencies; purple squares) relative to the 0.4Hz monocular condition (grey circles), and the progressive decline in amplitude of the dichoptic cross response (yellow diamonds) also differ across photoreceptor conditions, showing similar differences to those observed at 0.5Hz.
+
+To estimate the extent of interocular suppression for each photoreceptor pathway, we fitted each data set using a Bayesian hierarchical implementation of a simple binocular combination model [@Meese2006; @Segala2023].
 Our primary objective was to compare posterior distributions of the weight of interocular suppression, which are shown in Figure \@ref(fig:FirstHarmonicPlots)e.
@@
 At the first harmonic, melanopsin and S-cone signals differed in phase by more than 90 degrees, though they were not fully in antiphase.
-The luminance and L-M responses were approximately in antiphase to each other, however this is likely due to our choice to modulate L+M- in the first half-cycle (corresponding to a luminance increase in the luminance condition), and L-M+ in the second half-cycle (corresponding to a luminance decrease in the luminance condition).
+The luminance and L-M responses were approximately in antiphase to each other, however this is likely due to our choice to modulate L+M- in the first half-cycle of the sine wave (corresponding to a luminance increase in the luminance condition), and L-M+ in the second half-cycle (corresponding to a luminance decrease in the luminance condition).
 Had we reversed this phase arrangement, we would likely have seen a close phase correspondence between the L-M and luminance conditions (another way to think about this is that L-cone decreases and M-cone increases are processed like luminance increases).
@@
 Panel (b) shows the pupil response at the second harmonic frequency during binocular stimulation.
+The five data points for each pathway correspond to the five contrast levels displayed.
 In panel (a) the luminance amplitudes have been scaled down by a factor of 10 to enable comparison with the other conditions.", fig.align="center", echo=FALSE}
@@
 Ltd., Guangdong, China), which was used by the participants to view the stimuli.
-The stimuli were two discs of flickering light with a diameter of approximately 30 degrees, which were fused together into a cyclopean percept resembling a donut-shaped ring of light, similar to that used in other studies [e.g., @Barrionuevo2016; @Murray2018; @Spitschan2014; @Zele2018].
+The stimuli were two discs of flickering light with a diameter of approximately 30 degrees, which were fused together into a cyclopean percept resembling a donut-shaped ring of light, similar to that used in other studies [e.g., @Barrionuevo2016; @Murray2018; @Spitschan2014; @Spitschan2015; @Zele2018].
 The VR headset modifications allowed for small adjustments to account for individual differences in interpupillary distance and focal length.
@@
 Splatter on nominally silenced photoreceptors was very small (see Figure \@ref(fig:spectraplots)j-l), well below the levels that would be expected to generate measureable pupil modulations.
+We also estimated activation of penumbral L and M cones [@Spitschan2015; @Barrionuevo2016; @Zele2019], which was minimal ($\le 1.5%$ contrast; less than splatter on the open-field cones) for melanopsin-directed stimuli.
+We note that the temporal frequency of our modulation (0.5Hz) is well below the range where penumbral cone activation can elicit visible percepts, and that such percepts fade after around 1 second [@Spitschan2015], and do not typically affect pupil responses [@Spitschan2014].
 

### 2024-05-22 manuscript.tex
Changed Annie's name
Added autobuild, experiment code, switched refs to pnas style

--- 2024-05-09 manuscript.tex
@@
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
-\usepackage{caption}
+\usepackage{caption} \usepackage{lineno} \linenumbers
 \usepackage{booktabs}
@@
 \title{Binocular combination in the autonomic nervous system}
-\author{Federico G. Segala\(^1\), Aurelio Bruno\(^{1,2}\), Joel T. Martin\(^{1,3}\), Annie Y. Morsi\(^1\), Alex R. Wade\(^{1,4}\)\\
+\author{Federico G. Segala\(^1\), Aurelio Bruno\(^{1,2}\), Joel T. Martin\(^{1,3}\), Anisa Y. Morsi\(^1\), Alex R. Wade\(^{1,4}\)\\
 \& Daniel H. Baker\(^{1,4}\)}
@@
 
-\(^2\)School of Psychology and Vision Sciences, Leicester, United Kingdom.
+\(^2\)School of Psychology and Vision Sciences, University of Leicester, Leicester, United Kingdom.
 
@@
 
-The autonomic nervous system regulates many involuntary bodily processes, including the constriction and dilation of the pupils in response to light (\protect\hyperlink{ref-McDougal2015}{McDougal and Gamlin, 2015}).
-The anatomical pathway from the retina to the subcortical nuclei controlling the pupillary light response (PLR) is well established: it includes the Pretectal Olivary nucleus (PON), the Superior Cervical ganglion and the Edinger-Westphal nucleus, which project to the iris sphincter muscles that directly control the pupil size (\protect\hyperlink{ref-McDougal2015}{McDougal and Gamlin, 2015}, \protect\hyperlink{ref-McDougal2008}{2008}; \protect\hyperlink{ref-Wang2015}{Wang and Munoz, 2015}).
-Evidence of a binocular component to the PLR is shown by the existence of a consensual response of the pupil (the stimulation of one eye will cause constriction of the other eye; \protect\hyperlink{ref-Wyatt1981}{Wyatt and Musselman, 1981}).
+The autonomic nervous system regulates many involuntary bodily processes, including the constriction and dilation of the pupils in response to light (\protect\hyperlink{ref-McDougal2015}{1}).
+The anatomical pathway from the retina to the subcortical nuclei controlling the pupillary light response (PLR) is well established: it includes the Pretectal Olivary nucleus (PON), the Superior Cervical ganglion and the Edinger-Westphal nucleus, which project to the iris sphincter muscles that directly control the pupil size (\protect\hyperlink{ref-McDougal2015}{1}--\protect\hyperlink{ref-Wang2015}{3}).
+Evidence of a binocular component to the PLR is shown by the existence of a consensual response of the pupil (the stimulation of one eye will cause constriction of the other eye; \protect\hyperlink{ref-Wyatt1981}{4}).
 The anatomical segregation of the subcortical pathway from the rest of the brain means that this binocular combination of signals must occur independently of the cortical processes of binocular integration required for visual perception.
-Our recent work (\protect\hyperlink{ref-Segala2023}{Segala et al., 2023}) has shown that the algorithm underlying binocular combination of light in the pupil pathway differs from that in the cortex.
+Our recent work (\protect\hyperlink{ref-Segala2023}{5}) has shown that the algorithm underlying binocular combination of light in the pupil pathway differs from that in the cortex.
 Here we extend this paradigm to compare binocular combination in different photoreceptor pathways that feed into the autonomic nervous system.
 
-Different classes of retinal photoreceptors, including cones, rods and melanopsin-containing intrinsically photosensitive retinal ganglion cells (ipRGCs), are directly involved in controlling and maintaining the size of the pupils (\protect\hyperlink{ref-Barrionuevo2018}{Barrionuevo et al., 2018}; \protect\hyperlink{ref-Barrionuevo2014}{Barrionuevo et al., 2014}; \protect\hyperlink{ref-Dacey2005}{Dacey et al., 2005}; \protect\hyperlink{ref-Murray2018}{Murray et al., 2018}; \protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}; \protect\hyperlink{ref-Spitschan2019}{Spitschan and Cajochen, 2019}; \protect\hyperlink{ref-Woelders2018}{Woelders et al., 2018}).
-The cones have been shown to drive the initial rapid constriction of the pupils (\protect\hyperlink{ref-Mathot2018}{Mathôt, 2018}), while the slower and longer activation of the ipRGCs shows their role in maintaining the constriction over a prolonged period of time and in regulating the post-illumination pupillary response (\protect\hyperlink{ref-Markwell2010}{Markwell et al., 2010}; \protect\hyperlink{ref-McDougal2010}{McDougal and Gamlin, 2010}).
-The ipRGCs are a unique photoreceptor class that has been discovered recently (\protect\hyperlink{ref-Provencio2000}{Provencio et al., 2000}).
-They express the photopigment melanopsin, and are involved in the regulation of the circadian rhythm (\protect\hyperlink{ref-Panda2002}{Panda et al., 2002}; \protect\hyperlink{ref-Provencio2000}{Provencio et al., 2000}; \protect\hyperlink{ref-Ruby2002}{Ruby et al., 2002}), forming a major input to the PON (\protect\hyperlink{ref-Dacey2003}{Dacey et al., 2003}).
-The first direct evidence of the involvement of the ipRGCs in the PLR was shown in rats by Lucas et al.
-(\protect\hyperlink{ref-Lucas2003}{2003}) who genetically deleted the melanopsin gene from rats, resulting in the loss of the intrinsic photosensitivity of the cells and a reduced pupil constriction.
-This same behaviour was later also observed in primates and humans (\protect\hyperlink{ref-Gamlin2007}{Gamlin et al., 2007}), where it was demonstrated that the PLR continues during light presentation even when cone and rod signalling is blocked, indicating the primary role of the ipRGCs in maintaining pupil constriction over a prolonged time.
+Different classes of retinal photoreceptors, including cones, rods and melanopsin-containing intrinsically photosensitive retinal ganglion cells (ipRGCs), are directly involved in controlling and maintaining the size of the pupils (\protect\hyperlink{ref-Barrionuevo2014}{6}--\protect\hyperlink{ref-Woelders2018}{12}).
+The cones have been shown to drive the initial rapid constriction of the pupils (\protect\hyperlink{ref-Mathot2018}{13}), while the slower and longer activation of the ipRGCs shows their role in maintaining the constriction over a prolonged period of time and in regulating the post-illumination pupillary response (\protect\hyperlink{ref-Markwell2010}{14}, \protect\hyperlink{ref-McDougal2010}{15}).
+The ipRGCs are a unique photoreceptor class that has been discovered recently (\protect\hyperlink{ref-Provencio2000}{16}).
+They express the photopigment melanopsin, and are involved in the regulation of the circadian rhythm (\protect\hyperlink{ref-Provencio2000}{16}--\protect\hyperlink{ref-Ruby2002}{18}), forming a major input to the PON (\protect\hyperlink{ref-Dacey2003}{19}).
+The first direct evidence of the involvement of the ipRGCs in the PLR was shown in melanopsin knockout rats by (\protect\hyperlink{ref-Lucas2003}{20}), resulting in the loss of the intrinsic photosensitivity of the cells and a reduced pupil constriction.
+This same behaviour was later also observed in primates and humans (\protect\hyperlink{ref-Gamlin2007}{21}), where it was demonstrated that the PLR continues during light presentation even when cone and rod signalling is blocked, indicating the primary role of the ipRGCs in maintaining pupil constriction over a prolonged time.
 
-A technique known as silent substitution (\protect\hyperlink{ref-Estevez1982}{Estévez and Spekreijse, 1982}) can be used to selectively stimulate specific photoreceptor classes.
+A technique known as silent substitution (\protect\hyperlink{ref-Estevez1982}{22}) can be used to selectively stimulate specific photoreceptor classes.
 Silent substitution exploits the fact that each photoreceptor class has a distinct spectral tuning that overlaps with the others.
-Using a multiprimary system, in which the primaries (i.e.~LEDs) have different spectra, it is possible to target one class of photoreceptors while maintaining the others at a constant activity level, effectively silencing them (\protect\hyperlink{ref-Shapiro1996}{Shapiro et al., 1996}; \protect\hyperlink{ref-Spitschan2018}{Spitschan and Woelders, 2018}, this paper also offers a clear explanation of how to implement silent substitution).
+Using a multiprimary system, in which the primaries (i.e.~LEDs) have different spectra, it is possible to target one class of photoreceptors while maintaining the others at a constant activity level, effectively silencing them (\protect\hyperlink{ref-Shapiro1996}{23}, \protect\hyperlink{ref-Spitschan2018}{24}, this paper also offers a clear explanation of how to implement silent substitution).
 Studies using silent substitution have shown that the pupils behave differently depending on which photoreceptor or pathway is being stimulated.
-For example, pupil responses have been shown to be out of phase when the S cones are stimulated, relative to when the ipRGCs or the L+M cones are stimulated (\protect\hyperlink{ref-Cao2015}{Cao et al., 2015}; \protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}).
-Additionally, when L and M cones are stimulated individually, there appears to be a paradoxical pupil response: increments in L cone stimulation cause a constriction of the pupil, while increments in M cone stimulation lead to a dilation of the pupil (\protect\hyperlink{ref-Murray2018}{Murray et al., 2018}; \protect\hyperlink{ref-Woelders2018}{Woelders et al., 2018}), perhaps due to activity in the L-M opponent pathway.
+For example, pupil responses have been shown to be out of phase when the S cones are stimulated, relative to when the ipRGCs or the L+M cones are stimulated (\protect\hyperlink{ref-Spitschan2014}{10}, \protect\hyperlink{ref-Cao2015}{25}).
+Additionally, when L and M cones are stimulated individually, there appears to be a paradoxical pupil response: increments in L cone stimulation cause a constriction of the pupil, while increments in M cone stimulation lead to a dilation of the pupil (\protect\hyperlink{ref-Murray2018}{9}, \protect\hyperlink{ref-Woelders2018}{12}), perhaps due to activity in the L-M opponent pathway.
 
-Binocular combination has been extensively studied in visual perception, where it is mediated by neurons in primary visual cortex (\protect\hyperlink{ref-Hubel1962}{Hubel and Wiesel, 1962}; \protect\hyperlink{ref-Moradi2009}{Moradi and Heeger, 2009}).
-For pattern vision, binocular summation occurs at threshold, such that a lower contrast is required to detect a target shown to both eyes than a target shown to only one eye (\protect\hyperlink{ref-Baker2018}{Baker et al., 2018}; \protect\hyperlink{ref-Campbell1965}{Campbell and Green, 1965}; \protect\hyperlink{ref-Legge1984}{Legge, 1984}).
-At higher contrasts, a process of `ocularity invariance' is observed, in which the response to monocularly- and binocularly-presented patterns is equal (\protect\hyperlink{ref-Baker2007}{Baker et al., 2007}; \protect\hyperlink{ref-Ding2006}{Ding and Sperling, 2006}; \protect\hyperlink{ref-Meese2006}{Meese et al., 2006}; \protect\hyperlink{ref-Moradi2009}{Moradi and Heeger, 2009}).
+Binocular combination has been extensively studied in visual perception, where it is mediated by neurons in primary visual cortex (\protect\hyperlink{ref-Hubel1962}{26}, \protect\hyperlink{ref-Moradi2009}{27}).
+For pattern vision, binocular summation occurs at threshold, such that a lower contrast is required to detect a target shown to both eyes than a target shown to only one eye (\protect\hyperlink{ref-Baker2018}{28}--\protect\hyperlink{ref-Legge1984}{30}).
+At higher contrasts, a process of `ocularity invariance' is observed, in which the response to monocularly- and binocularly-presented patterns is equal (\protect\hyperlink{ref-Moradi2009}{27}, \protect\hyperlink{ref-Baker2007}{31}--\protect\hyperlink{ref-Meese2006}{33}).
 This is thought to be due to a process of interocular suppression that compensates for the additional excitatory drive caused by stimulating two eyes.
-Our recent work (\protect\hyperlink{ref-Segala2023}{Segala et al., 2023}) has shown that cortical signal combination for luminance flicker is substantially more linear than for spatial patterns, whereas there is evidence of interocular suppression in the pupil pathway.
+Our recent work (\protect\hyperlink{ref-Segala2023}{5}) has shown that cortical signal combination for luminance flicker is substantially more linear than for spatial patterns, whereas there is evidence of interocular suppression in the pupil pathway.
 
 Most studies that use silent substitution to investigate the PLR stimulate only one eye.
-If the stimulated eye is pharmacologically dilated to control pupil size, the response from the unstimulated eye (known as the consensual response) can be recorded (e.g.
-\protect\hyperlink{ref-McDougal2010}{McDougal and Gamlin, 2010}; \protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}).
+If the stimulated eye is pharmacologically dilated to control pupil size, the response from the unstimulated eye (known as the consensual response) can be recorded (\protect\hyperlink{ref-Spitschan2014}{10}, e.g.
+\protect\hyperlink{ref-McDougal2010}{15}).
 While this approach controls the total amount of light incident at the retina, it does not permit investigation of binocular combination for specific photoreceptor pathways.
@@
 Our key comparisons are between monocular and binocular stimulation, and between monocular stimulation and a dichoptic masking condition in which the two eyes are stimulated at different frequencies (0.5 and 0.4Hz).
-The results are interpreted using a contemporary model of binocular vision (\protect\hyperlink{ref-Meese2006}{Meese et al., 2006}) implemented within a hierarchical Bayesian framework.
+The results are interpreted using a contemporary model of binocular vision (\protect\hyperlink{ref-Meese2006}{33}) implemented within a hierarchical Bayesian framework.
 
@@
 
-In contemporary models of binocular signal combination, the amount of binocular facilitation is determined by the magnitude of interocular suppression, with strong suppression reducing facilitation (\protect\hyperlink{ref-Kingdom2015}{Kingdom and Libenson, 2015}).
+In contemporary models of binocular signal combination, the amount of binocular facilitation is determined by the magnitude of interocular suppression, with strong suppression reducing facilitation (\protect\hyperlink{ref-Kingdom2015}{34}).
 We can estimate the strength of interocular suppression by measuring how much monocular responses are reduced when a dichoptic `mask' is shown to the other eye.
 In our paradigm, the two components flickered at different frequencies (0.5 and 0.4Hz) so that their responses remained distinct in the Fourier spectrum (e.g.
-\protect\hyperlink{ref-Busse2009}{Busse et al., 2009}).
+\protect\hyperlink{ref-Busse2009}{35}).
 The yellow diamond symbols in Figure \ref{fig:FirstHarmonicPlots}a-d show the target responses in this condition, and in most cases were weaker than the monocular responses (red circles).
@@
 Suppression can also be estimated from the responses at 0.4Hz (Figure \ref{fig:FirstHarmonicPlots}f-i).
-The reduced amplitude in the binocular cross condition (purple squares) relative to the 0.4Hz monocular condition (grey circles), and the progressive decline in amplitude of the dichoptic cross response (yellow diamonds) also differ across photoreceptor conditions, showing similar differences to those observed at 0.5Hz.
+The reduced amplitude in the binocular cross condition (where the two eyes received different temporal frequencies; purple squares) relative to the 0.4Hz monocular condition (grey circles), and the progressive decline in amplitude of the dichoptic cross response (yellow diamonds) also differ across photoreceptor conditions, showing similar differences to those observed at 0.5Hz.
 
-To quantify the extent of suppression for each photoreceptor pathway, we fitted each data set using a Bayesian hierarchical implementation of a simple binocular combination model (\protect\hyperlink{ref-Meese2006}{Meese et al., 2006}; \protect\hyperlink{ref-Segala2023}{Segala et al., 2023}).
+To estimate the extent of interocular suppression for each photoreceptor pathway, we fitted each data set using a Bayesian hierarchical implementation of a simple binocular combination model (\protect\hyperlink{ref-Segala2023}{5}, \protect\hyperlink{ref-Meese2006}{33}).
 Our primary objective was to compare posterior distributions of the weight of interocular suppression, which are shown in Figure \ref{fig:FirstHarmonicPlots}e.
@@
 
-Finally, we inspected the response phase of our four stimulation conditions, given previous reports that these differ across pathways (\protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}), and may be in antiphase for melanopsin and S-cone signals.
+Finally, we inspected the response phase of our four stimulation conditions, given previous reports that these differ across pathways (\protect\hyperlink{ref-Spitschan2014}{10}), and may be in antiphase for melanopsin and S-cone signals.
 Figure \ref{fig:phaseplots} shows the phase angles for the first (a) and second (b) harmonic frequencies for binocular stimulation (monocular stimulation produced very similar results).
 At the first harmonic, melanopsin and S-cone signals differed in phase by more than 90 degrees, though they were not fully in antiphase.
-The luminance and L-M responses were approximately in antiphase to each other, however this is likely due to our choice to modulate L+M- in the first half-cycle (corresponding to a luminance increase in the luminance condition), and L-M+ in the second half-cycle (corresponding to a luminance decrease in the luminance condition).
+The luminance and L-M responses were approximately in antiphase to each other, however this is likely due to our choice to modulate L+M- in the first half-cycle of the sine wave (corresponding to a luminance increase in the luminance condition), and L-M+ in the second half-cycle (corresponding to a luminance decrease in the luminance condition).
 Had we reversed this phase arrangement, we would likely have seen a close phase correspondence between the L-M and luminance conditions (another way to think about this is that L-cone decreases and M-cone increases are processed like luminance increases).
@@
 Panel (b) shows the pupil response at the second harmonic frequency during binocular stimulation.
+The five data points for each pathway correspond to the five contrast levels displayed.
 In panel (a) the luminance amplitudes have been scaled down by a factor of 10 to enable comparison with the other conditions.}\label{fig:phaseplots}
@@
 This is the first study to investigate binocular interactions in the melanopsin pathway directly.
-A previous meta-analysis (\protect\hyperlink{ref-Spitschan2019}{Spitschan and Cajochen, 2019}) indicated that there may be a substantial binocular facilitation effect in the circadian pathway, as indexed by melatonin suppression (melatonin is a hormone released by the pineal gland; its production is suppressed by exposure to bright light, particularly when the melanopsin-containing ipRGCs are stimulated).
+A previous meta-analysis (\protect\hyperlink{ref-Spitschan2019}{11}) indicated that there may be a substantial binocular facilitation effect in the circadian pathway, as indexed by melatonin suppression (melatonin is a hormone released by the pineal gland; its production is suppressed by exposure to bright light, particularly when the melanopsin-containing ipRGCs are stimulated).
 In brief, monocular stimulation of the ipRGCs requires up to ten times the signal strength to produce an equivalent effect to binocular stimulation.
@@
 The explanation for this difference could be due to different anatomical pathways.
-Binocular combination in the circadian system likely takes place in the suprachiasmatic nucleus, whereas in the pupil constriction circuit the Edinger-Westphal nucleus is the most likely site of binocular integration (\protect\hyperlink{ref-Mathot2018}{Mathôt, 2018}).
+Binocular combination in the circadian system likely takes place in the suprachiasmatic nucleus, whereas in the pupil constriction circuit the Edinger-Westphal nucleus is the most likely site of binocular integration (\protect\hyperlink{ref-Mathot2018}{13}).
 Presumably these anatomical differences, and the practical constraints of the two systems, lead to differences in response.
 
-Our recent psychophysical work (\protect\hyperlink{ref-Baker2024}{Baker et al., 2024}) has looked at binocular interactions in the L-M and S-cone pathways, and compared these to the luminance pathway.
-Using a contrast discrimination paradigm with spatial modulations of luminance and colour, Baker et al.
-(\protect\hyperlink{ref-Baker2024}{2024}) found equally strong interocular suppression in all three pathways.
+Our recent psychophysical work (\protect\hyperlink{ref-Baker2024}{36}) has looked at binocular interactions in the L-M and S-cone pathways, and compared these to the luminance pathway.
+Using a contrast discrimination paradigm with spatial modulations of luminance and colour, (\protect\hyperlink{ref-Baker2024}{36}) found equally strong interocular suppression in all three pathways.
 This is rather different from our pupillometry results here, which demonstrate weaker suppression in the luminance and S-cone pathways than in the L-M pathway (see Figure \ref{fig:FirstHarmonicPlots}).
-However, the current experiments involve temporal modulations, which are quite distinct from the spatial modulations used in Baker et al.
-(\protect\hyperlink{ref-Baker2024}{2024}).
-Our other recent work (\protect\hyperlink{ref-Segala2023}{Segala et al., 2023}) has shown that temporal luminance modulations involve much weaker interocular suppression in the cortical response than do spatial luminance modulations (\protect\hyperlink{ref-Baker2017}{Baker and Wade, 2017}).
+However, the current experiments involve temporal modulations, which are quite distinct from the spatial modulations used in (\protect\hyperlink{ref-Baker2024}{36}).
+Our other recent work (\protect\hyperlink{ref-Segala2023}{5}) has shown that temporal luminance modulations involve much weaker interocular suppression in the cortical response than do spatial luminance modulations (\protect\hyperlink{ref-Baker2017}{37}).
 These different normalization processes might reflect different priorities for spatial and temporal vision.
-Spatial vision aims to fuse images to provide binocular single vision, and benefits from `ocularity invariance' (\protect\hyperlink{ref-Baker2007}{Baker et al., 2007}), in which visual appearance is constant when viewed with one eye or two.
-Temporal vision is critical for motion perception, which can involve alternative binocular computations, such as calculating velocity differences between the eyes (\protect\hyperlink{ref-Kaestner2019}{Kaestner et al., 2019}).
+Spatial vision aims to fuse images to provide binocular single vision, and benefits from `ocularity invariance' (\protect\hyperlink{ref-Baker2007}{31}), in which visual appearance is constant when viewed with one eye or two.
+Temporal vision is critical for motion perception, which can involve alternative binocular computations, such as calculating velocity differences between the eyes (\protect\hyperlink{ref-Kaestner2019}{38}).
 Of course the present measurements were of pupil size, which may be subject to different anatomical and functional constraints from those in the cortex.
@@
 To present synchronised stimulus modulations independently to each eye, two light engines (SpectraTuneLAB: LEDMOTIVE Technologies, LLC, Barcelona, Spain), each with 10 independently addressable LED colour channels, were integrated into a customised viewing system.
-The light engines were operated via a Python interface to their REST API (\protect\hyperlink{ref-Martin2022}{Martin et al., 2022}), which supports synchronous launch and playback of spectral sequences prepared in advance and stored in JSON format.
+The light engines were operated via a Python interface to their REST API (\protect\hyperlink{ref-Martin2022}{39}), which supports synchronous launch and playback of spectral sequences prepared in advance and stored in JSON format.
 When preparing the spectral sequences, the age of participants was used to account for the yellowing of the lenses.
-We calculated silent substitution solutions using the \emph{PySilSub} toolbox (\protect\hyperlink{ref-Martin2023}{Martin et al., 2023}), using linear algebra.
+We calculated silent substitution solutions using the \emph{PySilSub} toolbox (\protect\hyperlink{ref-Martin2023}{40}), using linear algebra.
 The outputs of the two light engines (see Figure \ref{fig:spectraplots}b,c) were calibrated using an Ocean Optics Jaz spectroradiometer, which was wavelength-calibrated to an Argon lamp and intensity calibrated using a NIST-traceable light source.
-We used the Stockman and Sharpe (\protect\hyperlink{ref-Stockman2000}{2000}) 10-degree cone fundamentals, and estimates of melanopsin absorbance spectra from CIE S 026 (discussed in \protect\hyperlink{ref-Martin2023}{Martin et al., 2023}) to calculate \(\alpha\)-opic irradiance.
+We used the (\protect\hyperlink{ref-Stockman2000}{41}) 10-degree cone fundamentals, and estimates of melanopsin absorbance spectra from CIE S 026 (discussed in \protect\hyperlink{ref-Martin2023}{40}) to calculate \(\alpha\)-opic irradiance.
 
@@
 The diffuser discs were positioned in the objective planes of the lenses of a modified VR headset (SHINECON SC-G01, Dongguan Shinecon Industrial Co.~Ltd., Guangdong, China), which was used by the participants to view the stimuli.
-The stimuli were two discs of flickering light with a diameter of approximately 30 degrees, which were fused together into a cyclopean percept resembling a donut-shaped ring of light, similar to that used in other studies (e.g., \protect\hyperlink{ref-Barrionuevo2016}{Barrionuevo and Cao, 2016}; \protect\hyperlink{ref-Murray2018}{Murray et al., 2018}; \protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}; \protect\hyperlink{ref-Zele2018}{Zele et al., 2018}).
+The stimuli were two discs of flickering light with a diameter of approximately 30 degrees, which were fused together into a cyclopean percept resembling a donut-shaped ring of light, similar to that used in other studies (\protect\hyperlink{ref-Murray2018}{9}, \protect\hyperlink{ref-Spitschan2014}{10}, e.g., \protect\hyperlink{ref-Barrionuevo2016}{42}, \protect\hyperlink{ref-Spitschan2015}{43}, \protect\hyperlink{ref-Zele2018}{44}).
 The VR headset modifications allowed for small adjustments to account for individual differences in interpupillary distance and focal length.
-The use of this set up allowed us to modulate the stimuli in three different ocular configurations, similar to the ones we used in our previous study (\protect\hyperlink{ref-Segala2023}{Segala et al., 2023}): monocular, binocular and dichoptic.
+The use of this set up allowed us to modulate the stimuli in three different ocular configurations, similar to the ones we used in our previous study (\protect\hyperlink{ref-Segala2023}{5}): monocular, binocular and dichoptic.
 In the monocular configuration, the unstimulated eye still saw a non-flickering disc of mean luminance.
 A schematic of the stimulation system is shown in Figure \ref{fig:spectraplots}a.
-Pupillometry data were collected using a binocular Pupil Core eye-tracker headset (Pupil Labs GmbH, Berlin, Germany, \protect\hyperlink{ref-Kassner2014}{Kassner et al., 2014}) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
+Pupillometry data were collected using a binocular Pupil Core eye-tracker headset (Pupil Labs GmbH, Berlin, Germany, \protect\hyperlink{ref-Kassner2014}{45}) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
 
-Our previous study (\protect\hyperlink{ref-Segala2023}{Segala et al., 2023}) used a temporal frequency of 2Hz for foveal luminance flicker, and recorded EEG data simultaneously with pupillometry.
+Our previous study (\protect\hyperlink{ref-Segala2023}{5}) used a temporal frequency of 2Hz for foveal luminance flicker, and recorded EEG data simultaneously with pupillometry.
 Initial pilot experiments indicated that this frequency was too high to elicit measurable responses when stimulating individual photoreceptor pathways.
-For all experiments, we therefore used a primary flicker frequency of 0.5Hz, as previous literature showed that this was slow enough to elicit a pupil response from all photoreceptor classes (\protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}).
-We also focussed on only recording pupillometry data as this frequency would be too slow to elicit steady-state EEG responses (\protect\hyperlink{ref-Norcia2015}{Norcia et al., 2015}).
+For all experiments, we therefore used a primary flicker frequency of 0.5Hz, as previous literature showed that this was slow enough to elicit a pupil response from all photoreceptor classes (\protect\hyperlink{ref-Spitschan2014}{10}).
+We also focussed on only recording pupillometry data as this frequency would be too slow to elicit steady-state EEG responses (\protect\hyperlink{ref-Norcia2015}{46}).
 
@@
 Splatter on nominally silenced photoreceptors was very small (see Figure \ref{fig:spectraplots}j-l), well below the levels that would be expected to generate measureable pupil modulations.
+We also estimated activation of penumbral L and M cones (\protect\hyperlink{ref-Barrionuevo2016}{42}, \protect\hyperlink{ref-Spitschan2015}{43}, \protect\hyperlink{ref-Zele2019}{47}), which was minimal (\(\le 1.5%
+\) contrast; less than splatter on the open-field cones) for melanopsin-directed stimuli.
+We note that the temporal frequency of our modulation (0.5Hz) is well below the range where penumbral cone activation can elicit visible percepts, and that such percepts fade after around 1 second (\protect\hyperlink{ref-Spitschan2015}{43}), and do not typically affect pupil responses (\protect\hyperlink{ref-Spitschan2014}{10}).
 
@@
 Pupil responses to binocular temporal contrast modulations were examined in a factorial design that combined six ocular conditions and five temporal contrast levels: 6, 12, 24, 48 and 96\% of the available dynamic range.
-This design, similar to that used in our previous studies (\protect\hyperlink{ref-Baker2020}{Baker et al., 2020}; \protect\hyperlink{ref-Baker2017}{Baker and Wade, 2017}; \protect\hyperlink{ref-Segala2023}{Segala et al., 2023}), was applied in four separate experiments, each with a different mode of photoreceptor stimulation.
+This design, similar to that used in our previous studies (\protect\hyperlink{ref-Segala2023}{5}, \protect\hyperlink{ref-Baker2017}{37}, \protect\hyperlink{ref-Baker2020}{48}), was applied in four separate experiments, each with a different mode of photoreceptor stimulation.
 In the first three conditions, the discs flickered at 0.5 Hz, in either a monocular, binocular or dichoptic arrangement.
@@
 Using a trackball, participants adjusted the angle in cone space to find their subjective isoluminant point, which resulted in changing the flickering intensity of the stimulus until the amplitude of the flicker appeared to be minimised.
-The result was used to modify the requested contrasts during stimulus preparation so as to account for individual differences affecting perceived illuminance, principally the L:M cone ratio (\protect\hyperlink{ref-Carroll2002}{Carroll et al., 2002}; \protect\hyperlink{ref-Hofer2005}{Hofer et al., 2005}).
+The result was used to modify the requested contrasts during stimulus preparation so as to account for individual differences affecting perceived illuminance, principally the L:M cone ratio (\protect\hyperlink{ref-Carroll2002}{49}, \protect\hyperlink{ref-Hofer2005}{50}).
 
@@
 
-The pupillometry data were analysed using the same method we used in our previous study (\protect\hyperlink{ref-Segala2023}{Segala et al., 2023}).
-The data were converted from mp4 videos to a csv text file using the Pupil Player software (\protect\hyperlink{ref-Kassner2014}{Kassner et al., 2014}), which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
+The pupillometry data were analysed using the same method we used in our previous study (\protect\hyperlink{ref-Segala2023}{5}).
+The data were converted from mp4 videos to a csv text file using the Pupil Player software (\protect\hyperlink{ref-Kassner2014}{45}), which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
 The individual data were then loaded into R for analysis, where a ten-second waveform for each trial in each eye was extracted (excluding the first two seconds after stimulus onset).
@@
 Finally, data were averaged across all participants to obtain the group results.
-We used coherent averaging and at each stage we excluded data points with a Mahalanobis distance exceeding \(D\) = 3 from the complex-valued mean (\protect\hyperlink{ref-Baker2021}{Baker, 2021}).
+We used coherent averaging and at each stage we excluded data points with a Mahalanobis distance exceeding \(D\) = 3 from the complex-valued mean (\protect\hyperlink{ref-Baker2021}{51}).
 For monocular stimulation, we confirmed that the consensual response was equivalent to the response in the stimulated eye.
@@
 
-To describe our data, we used the same model described in our previous study (\protect\hyperlink{ref-Segala2023}{Segala et al., 2023}).
-The model has the same general form as the first stage of the contrast gain control model proposed by Meese et al.
-(\protect\hyperlink{ref-Meese2006}{2006}), but omits the second stage.
-For the previous model that we used (\protect\hyperlink{ref-Segala2023}{Segala et al., 2023}), the exponent of the numerator and denominator had fixed values of 2 and (implicitly) 1.
+To describe our data, we used the same model described in our previous study (\protect\hyperlink{ref-Segala2023}{5}).
+The model has the same general form as the first stage of the contrast gain control model proposed by (\protect\hyperlink{ref-Meese2006}{33}), but omits the second stage.
+For the previous model that we used (\protect\hyperlink{ref-Segala2023}{5}), the exponent of the numerator and denominator had fixed values of 2 and (implicitly) 1.
 Here, we allow these parameters (called \emph{p} and \emph{q}) to be free, in order to permit different shapes of contrast response function, e.g.~accelerating or saturating.
@@
 
-The models were fit using a hierarchical Bayesian framework implemented in Stan (\protect\hyperlink{ref-Carpenter2017}{Carpenter et al., 2017}).
+The models were fit using a hierarchical Bayesian framework implemented in Stan (\protect\hyperlink{ref-Carpenter2017}{52}).
 The data for each photoreceptor type and response frequency was fit separately, for a total of 8 model fits.
 The prior for the \(\omega\) parameter was Gaussian, with a mean of 1 and standard deviation of 0.5.
-Priors for the other free parameters were also Gaussian, with mean values based on previous work (\protect\hyperlink{ref-Segala2023}{Segala et al., 2023}).
+Priors for the other free parameters were also Gaussian, with mean values based on previous work (\protect\hyperlink{ref-Segala2023}{5}).
 We calculated over \ensuremath{10^{6}} posterior samples, and retained 10\% for plotting.
@@
 \hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-Baker2021}{}}%
-Baker DH.
-2021.
-Statistical analysis of periodic data in neuroscience.
-\emph{Neurons, Behavior, Data analysis, and Theory} \textbf{5}.
-doi:\href{https://doi.org/10.51628/001c.27680}{10.51628/001c.27680}
+\begin{CSLReferences}{0}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-McDougal2015}{}}%
+\CSLLeftMargin{1. }%
+\CSLRightInline{D. H. McDougal, P. D. Gamlin, \href{https://doi.org/10.1002/cphy.c140014}{Autonomic control of the eye}. \emph{Comprehensive Physiology} \textbf{5}, 439--473 (2015).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-McDougal2008}{}}%
+\CSLLeftMargin{2. }%
+\CSLRightInline{D. H. McDougal, P. D. Gamlin, {``Pupillary control pathways.''} in \emph{The Senses: A Comprehensive Reference}, (Elsevier, 2008), pp. 521--536.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Wang2015}{}}%
+\CSLLeftMargin{3. }%
+\CSLRightInline{C.-A.
+Wang, D.
+P.
+Munoz, \href{https://doi.org/10.1016/j.conb.2015.03.018}{A circuit for pupil orienting responses: Implications for cognitive modulation of pupil size}.
+\emph{Curr Opin Neurobiol} \textbf{33}, 134--40 (2015).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Wyatt1981}{}}%
+\CSLLeftMargin{4. }%
+\CSLRightInline{H.
+J.
+Wyatt, J.
+F.
+Musselman, \href{https://doi.org/10.1016/0042-6989(81)90097-3}{Pupillary light reflex in humans: Evidence for an unbalanced pathway from nasal retina, and for signal cancellation in brainstem}.
+\emph{Vision Res} \textbf{21}, 513--25 (1981).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Segala2023}{}}%
+\CSLLeftMargin{5. }%
+\CSLRightInline{F.
+G.
+Segala, \emph{et al.}, \href{https://doi.org/10.7554/elife.87048}{Different rules for binocular combination of luminance flicker in cortical and subcortical pathways}.
+\emph{eLife} \textbf{12} (2023).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Barrionuevo2014}{}}%
+\CSLLeftMargin{6. }%
+\CSLRightInline{P.
+A.
+Barrionuevo, \emph{et al.}, \href{https://doi.org/10.1167/iovs.13-13252}{Assessing rod, cone, and melanopsin contributions to human pupil flicker responses}.
+\emph{Investigative Ophthalmology \& Visual Science} \textbf{55}, 719--27 (2014).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Barrionuevo2018}{}}%
+\CSLLeftMargin{7. }%
+\CSLRightInline{P.
+A.
+Barrionuevo, J.
+J.
+McAnany, A.
+J.
+Zele, D.
+Cao, \href{https://doi.org/10.3389/fneur.2018.01140}{Non-linearities in the {Rod} and {Cone} {Photoreceptor} {Inputs} to the {Afferent} {Pupil} {Light} {Response}}.
+\emph{Frontiers in Neurology} \textbf{9} (2018).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Dacey2005}{}}%
+\CSLLeftMargin{8. }%
+\CSLRightInline{D.
+M.
+Dacey, \emph{et al.}, \href{https://doi.org/10.1038/nature03387}{Melanopsin-expressing ganglion cells in primate retina signal colour and irradiance and project to the {LGN}}.
+\emph{Nature} \textbf{433}, 749--754 (2005).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Murray2018}{}}%
+\CSLLeftMargin{9. }%
+\CSLRightInline{I.
+J.
+Murray, J.
+Kremers, D.
+McKeefry, N.
+R.
+A.
+Parry, \href{https://doi.org/10.1364/JOSAA.35.000B66}{Paradoxical pupil responses to isolated {M}-cone increments}.
+\emph{Journal of the Optical Society of America A} \textbf{35}, B66--B71 (2018).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Spitschan2014}{}}%
+\CSLLeftMargin{10. }%
+\CSLRightInline{M.
+Spitschan, S.
+Jain, D.
+H.
+Brainard, G.
+K.
+Aguirre, \href{https://doi.org/10.1073/pnas.1400942111}{Opponent melanopsin and s-cone signals in the human pupillary light response}.
+\emph{Proceedings of the National Academy of Sciences} \textbf{111}, 15568--15572 (2014).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Spitschan2019}{}}%
+\CSLLeftMargin{11. }%
+\CSLRightInline{M. Spitschan, C. Cajochen, \href{https://doi.org/10.1111/jpi.12602}{Binocular facilitation in light-mediated melatonin suppression?} \emph{J Pineal Res} \textbf{67}, e12602 (2019).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Woelders2018}{}}%
+\CSLLeftMargin{12. }%
+\CSLRightInline{T.
+Woelders, \emph{et al.}, \href{https://doi.org/10.1073/pnas.1716281115}{Melanopsin- and {L}-cone--induced pupil constriction is inhibited by {S}- and {M}-cones in humans}.
+\emph{Proceedings of the National Academy of Sciences} \textbf{115}, 792--797 (2018).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Mathot2018}{}}%
+\CSLLeftMargin{13. }%
+\CSLRightInline{S. Mathôt, \href{https://doi.org/10.5334/joc.18}{Pupillometry: Psychology, physiology, and function}. \emph{J Cogn} \textbf{1}, 16 (2018).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Markwell2010}{}}%
+\CSLLeftMargin{14. }%
+\CSLRightInline{E.
+L.
+Markwell, B.
+Feigl, A.
+J.
+Zele, \href{https://doi.org/10.1111/j.1444-0938.2010.00479.x}{Intrinsically photosensitive melanopsin retinal ganglion cell contributions to the pupillary light reflex and circadian rhythm}.
+\emph{Clinical and Experimental Optometry} \textbf{93}, 137--149 (2010).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-McDougal2010}{}}%
+\CSLLeftMargin{15. }%
+\CSLRightInline{D.
+H.
+McDougal, P.
+D.
+Gamlin, \href{https://doi.org/10.1016/j.visres.2009.10.012}{The influence of intrinsically-photosensitive retinal ganglion cells on the spectral sensitivity and response dynamics of the human pupillary light reflex}.
+\emph{Vision Research} \textbf{50}, 72--87 (2010).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Provencio2000}{}}%
+\CSLLeftMargin{16. }%
+\CSLRightInline{I.
+Provencio, \emph{et al.}, \href{https://doi.org/10.1523/JNEUROSCI.20-02-00600.2000}{A {Novel} {Human} {Opsin} in the {Inner} {Retina}}.
+\emph{Journal of Neuroscience} \textbf{20}, 600--605 (2000).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Panda2002}{}}%
+\CSLLeftMargin{17. }%
+\CSLRightInline{S.
+Panda, \emph{et al.}, \href{https://doi.org/10.1126/science.1076848}{Melanopsin (Opn4) requirement for normal light-induced circadian phase shifting}.
+\emph{Science} \textbf{298}, 2213--2216 (2002).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Ruby2002}{}}%
+\CSLLeftMargin{18. }%
+\CSLRightInline{N. F. Ruby, \emph{et al.}, \href{https://doi.org/10.1126/science.1076701}{Role of melanopsin in circadian responses to light}. \emph{Science} \textbf{298}, 2211--2213 (2002).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Dacey2003}{}}%
+\CSLLeftMargin{19. }%
+\CSLRightInline{D.
+M.
+Dacey, B.
+B.
+Peterson, F.
+R.
+Robinson, P.
+D.
+Gamlin, \href{https://doi.org/10.1016/S0896-6273(02)01143-1}{Fireworks in the primate retina: In vitro photodynamics reveals diverse LGN-projecting ganglion cell types}.
+\emph{Neuron} \textbf{37}, 15--27 (2003).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Lucas2003}{}}%
+\CSLLeftMargin{20. }%
+\CSLRightInline{R.
+J.
+Lucas, \emph{et al.}, \href{https://doi.org/10.1126/science.1077293}{Diminished pupillary light reflex at high irradiances in melanopsin-knockout mice}.
+\emph{Science} \textbf{299}, 245--247 (2003).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Gamlin2007}{}}%
+\CSLLeftMargin{21. }%
+\CSLRightInline{P.
+D.
+R.
+Gamlin, \emph{et al.}, \href{https://doi.org/10.1016/j.visres.2006.12.015}{Human and macaque pupil responses driven by melanopsin-containing retinal ganglion cells}.
+\emph{Vision Research} \textbf{47}, 946--954 (2007).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Estevez1982}{}}%
+\CSLLeftMargin{22. }%
+\CSLRightInline{O.
+Estévez, H.
+Spekreijse, \href{https://doi.org/10.1016/0042-6989(82)90104-3}{The "silent substitution" method in visual research}.
+\emph{Vision Research} \textbf{22}, 681--691 (1982).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Shapiro1996}{}}%
+\CSLLeftMargin{23. }%
+\CSLRightInline{A.
+G.
+Shapiro, J.
+Pokorny, V.
+C.
+Smith, \href{https://doi.org/10.1364/josaa.13.002319}{Cone{\textendash}rod receptor spaces with illustrations that use {CRT} phosphor and light-emitting-diode spectra}.
+\emph{Journal of the Optical Society of America A} \textbf{13}, 2319 (1996).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Spitschan2018}{}}%
+\CSLLeftMargin{24. }%
+\CSLRightInline{M.
+Spitschan, T.
+Woelders, \href{https://doi.org/10.3389/fneur.2018.00941}{The {Method} of {Silent} {Substitution} for {Examining} {Melanopsin} {Contributions} to {Pupil} {Control}}.
+\emph{Frontiers in Neurology} \textbf{9} (2018).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Cao2015}{}}%
+\CSLLeftMargin{25. }%
+\CSLRightInline{D.
+Cao, N.
+Nicandro, P.
+A.
+Barrionuevo, \href{https://doi.org/10.1167/15.1.27}{A five-primary photostimulator suitable for studying intrinsically photosensitive retinal ganglion cell functions in humans}.
+\emph{Journal of Vision} \textbf{15}, 27 (2015).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Hubel1962}{}}%
+\CSLLeftMargin{26. }%
+\CSLRightInline{D.
+H.
+Hubel, T.
+N.
+Wiesel, \href{https://doi.org/10.1113/jphysiol.1962.sp006837}{Receptive fields, binocular interaction and functional architecture in the cat's visual cortex}.
+\emph{J Physiol} \textbf{160}, 106--54 (1962).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Moradi2009}{}}%
+\CSLLeftMargin{27. }%
+\CSLRightInline{F. Moradi, D. J. Heeger, \href{https://doi.org/10.1167/9.3.13}{Inter-ocular contrast normalization in human visual cortex}. \emph{J Vis} \textbf{9}, 13.1--22 (2009).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Baker2018}{}}%
+\CSLLeftMargin{28. }%
+\CSLRightInline{D.
+H.
+Baker, F.
+A.
+Lygo, T.
+S.
+Meese, M.
+A.
+Georgeson, \href{https://doi.org/10.1037/bul0000163}{Binocular summation revisited: Beyond \(\sqrt{2}\)}.
+\emph{Psychol Bull} \textbf{144}, 1186--1199 (2018).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Campbell1965}{}}%
+\CSLLeftMargin{29. }%
+\CSLRightInline{F. W. Campbell, D. G. Green, \href{https://doi.org/10.1038/208191a0}{Monocular versus binocular visual acuity}. \emph{Nature} \textbf{208}, 191--2 (1965).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Legge1984}{}}%
+\CSLLeftMargin{30. }%
+\CSLRightInline{G. E. Legge, \href{https://doi.org/10.1016/0042-6989(84)90064-6}{Binocular contrast summation--II. Quadratic summation}. \emph{Vision Res} \textbf{24}, 385--94 (1984).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Baker2007}{}}%
+\CSLLeftMargin{31. }%
+\CSLRightInline{D.
+H.
+Baker, T.
+S.
+Meese, M.
+A.
+Georgeson, \href{https://doi.org/10.1163/156856807781503622}{Binocular interaction: Contrast matching and contrast discrimination are predicted by the same model}.
+\emph{Spat Vis} \textbf{20}, 397--413 (2007).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Ding2006}{}}%
+\CSLLeftMargin{32. }%
+\CSLRightInline{J. Ding, G. Sperling, \href{https://doi.org/10.1073/pnas.0509629103}{A gain-control theory of binocular combination}. \emph{Proc Natl Acad Sci U S A} \textbf{103}, 1141--6 (2006).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Meese2006}{}}%
+\CSLLeftMargin{33. }%
+\CSLRightInline{T.
+S.
+Meese, M.
+A.
+Georgeson, D.
+H.
+Baker, \href{https://doi.org/10.1167/6.11.7}{Binocular contrast vision at and above threshold}.
+\emph{Journal of Vision} \textbf{6}, 1224--43 (2006).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Kingdom2015}{}}%
+\CSLLeftMargin{34. }%
+\CSLRightInline{F.
+A.
+A.
+Kingdom, L.
+Libenson, \href{https://doi.org/10.1167/15.5.2}{Dichoptic color saturation mixture: Binocular luminance contrast promotes perceptual averaging}.
+\emph{J Vis} \textbf{15}, 2 (2015).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Busse2009}{}}%
+\CSLLeftMargin{35. }%
+\CSLRightInline{L.
+Busse, A.
+R.
+Wade, M.
+Carandini, \href{https://doi.org/10.1016/j.neuron.2009.11.004}{Representation of concurrent stimuli by population activity in visual cortex}.
+\emph{Neuron} \textbf{64}, 931--42 (2009).}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Baker2024}{}}%
-Baker DH, Hansford KJ, Segala FG, Morsi AY, Huxley RJ, Martin JT, Rockman M, Wade AR.
-2024.
-Binocular integration of chromatic and luminance signals.
-\emph{Journal of Vision} \textbf{Under review}.
-doi:\href{https://doi.org/10.31234/osf.io/atsfh}{10.31234/osf.io/atsfh}
+\CSLLeftMargin{36. }%
+\CSLRightInline{D.
+H.
+Baker, \emph{et al.}, \href{https://doi.org/10.31234/osf.io/atsfh}{Binocular integration of chromatic and luminance signals}.
+\emph{Journal of Vision} \textbf{Under review} (2024).}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Baker2018}{}}%
-Baker DH, Lygo FA, Meese TS, Georgeson MA.
-2018.
-Binocular summation revisited: Beyond \(\sqrt{2}\).
-\emph{Psychol Bull} \textbf{144}:1186--1199.
-doi:\href{https://doi.org/10.1037/bul0000163}{10.1037/bul0000163}
+\leavevmode\vadjust pre{\hypertarget{ref-Baker2017}{}}%
+\CSLLeftMargin{37. }%
+\CSLRightInline{D.
+H.
+Baker, A.
+R.
+Wade, \href{https://doi.org/10.1093/cercor/bhw395}{Evidence for an optimal algorithm underlying signal combination in human visual cortex}.
+\emph{Cereb Cortex} \textbf{27}, 254--264 (2017).}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Baker2007}{}}%
-Baker DH, Meese TS, Georgeson MA.
-2007.
-Binocular interaction: Contrast matching and contrast discrimination are predicted by the same model.
-\emph{Spat Vis} \textbf{20}:397--413.
-doi:\href{https://doi.org/10.1163/156856807781503622}{10.1163/156856807781503622}
+\leavevmode\vadjust pre{\hypertarget{ref-Kaestner2019}{}}%
+\CSLLeftMargin{38. }%
+\CSLRightInline{M.
+Kaestner, \emph{et al.}, \href{https://doi.org/10.1073/pnas.1817202116}{Asymmetries between achromatic and chromatic extraction of 3D motion signals}.
+\emph{Proc Natl Acad Sci U S A} \textbf{116}, 13631--13640 (2019).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Martin2022}{}}%
+\CSLLeftMargin{39. }%
+\CSLRightInline{J.
+T.
+Martin, J.
+Pinto, D.
+Bulte, M.
+Spitschan, \href{https://doi.org/10.3758/s13428-021-01759-3}{PyPlr: A versatile, integrated system of hardware and software for researching the human pupillary light reflex}.
+\emph{Behavior Research Methods} \textbf{54}, 2720--2739 (2022).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Martin2023}{}}%
+\CSLLeftMargin{40. }%
+\CSLRightInline{J.
+T.
+Martin, G.
+M.
+Boynton, D.
+H.
+Baker, A.
+R.
+Wade, M.
+Spitschan, \href{https://doi.org/10.1167/jov.23.7.10}{PySilSub: An open-source python toolbox for implementing the method of silent substitution in vision and nonvisual photoreception research}.
+\emph{Journal of Vision} \textbf{23}, 10 (2023).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Stockman2000}{}}%
+\CSLLeftMargin{41. }%
+\CSLRightInline{A.
+Stockman, L.
+T.
+Sharpe, \href{https://doi.org/10.1016/s0042-6989(00)00021-3}{The spectral sensitivities of the middle- and long-wavelength-sensitive cones derived from measurements in observers of known genotype}.
+\emph{Vision Res} \textbf{40}, 1711--37 (2000).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Barrionuevo2016}{}}%
+\CSLLeftMargin{42. }%
+\CSLRightInline{P.
+A.
+Barrionuevo, D.
+Cao, \href{https://doi.org/10.1167/16.11.29}{Luminance and chromatic signals interact differently with melanopsin activation to control the pupil light response}.
+\emph{Journal of Vision} \textbf{16(11)}, 29 (2016).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Spitschan2015}{}}%
+\CSLLeftMargin{43. }%
+\CSLRightInline{M.
+Spitschan, G.
+K.
+Aguirre, D.
+H.
+Brainard, \href{https://doi.org/10.1371/journal.pone.0124328}{Selective stimulation of penumbral cones reveals perception in the shadow of retinal blood vessels}.
+\emph{PLoS One} \textbf{10}, e0124328 (2015).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Zele2018}{}}%
+\CSLLeftMargin{44. }%
+\CSLRightInline{A.
+J.
+Zele, B.
+Feigl, P.
+Adhikari, M.
+L.
+Maynard, D.
+Cao, \href{https://doi.org/10.1038/s41598-018-22197-w}{Melanopsin photoreception contributes to human visual detection, temporal and colour processing}.
+\emph{Scientific Reports} \textbf{8} (2018).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Kassner2014}{}}%
+\CSLLeftMargin{45. }%
+\CSLRightInline{M.
+Kassner, W.
+Patera, A.
+Bulling, Pupil: An open source platform for pervasive eye tracking and mobile gaze-based interaction.
+in \emph{Proceedings of the 2014 {ACM} International Joint Conference on Pervasive and Ubiquitous Computing: Adjunct Publication}, ({ACM}, 2014) https:/doi.org/\href{https://doi.org/10.1145/2638728.2641695}{10.1145/2638728.2641695}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Norcia2015}{}}%
+\CSLLeftMargin{46. }%
+\CSLRightInline{A.
+M.
+Norcia, L.
+G.
+Appelbaum, J.
+M.
+Ales, B.
+R.
+Cottereau, B.
+Rossion, \href{https://doi.org/10.1167/15.6.4}{The steady-state visual evoked potential in vision research: A review}.
+\emph{Journal of Vision} \textbf{15(6)}, 4 (2015).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Zele2019}{}}%
+\CSLLeftMargin{47. }%
+\CSLRightInline{A.
+J.
+Zele, P.
+Adhikari, D.
+Cao, B.
+Feigl, \href{https://doi.org/10.1016/j.visres.2019.04.009}{Melanopsin driven enhancement of cone-mediated visual processing}.
+\emph{Vision Res} \textbf{160}, 72--81 (2019).}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Baker2020}{}}%
-Baker DH, Vilidaite G, McClarnon E, Valkova E, Bruno A, Millman RE.
-2020.
-Binaural summation of amplitude modulation involves weak interaural suppression.
-\emph{Sci Rep} \textbf{10}:3560.
-doi:\href{https://doi.org/10.1038/s41598-020-60602-5}{10.1038/s41598-020-60602-5}
+\CSLLeftMargin{48. }%
+\CSLRightInline{D.
+H.
+Baker, \emph{et al.}, \href{https://doi.org/10.1038/s41598-020-60602-5}{Binaural summation of amplitude modulation involves weak interaural suppression}.
+\emph{Sci Rep} \textbf{10}, 3560 (2020).}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Baker2017}{}}%
-Baker DH, Wade AR.
-2017.
-Evidence for an optimal algorithm underlying signal combination in human visual cortex.
-\emph{Cereb Cortex} \textbf{27}:254--264.
-doi:\href{https://doi.org/10.1093/cercor/bhw395}{10.1093/cercor/bhw395}
+\leavevmode\vadjust pre{\hypertarget{ref-Carroll2002}{}}%
+\CSLLeftMargin{49. }%
+\CSLRightInline{J.
+Carroll, J.
+Neitz, M.
+Neitz, \href{https://doi.org/10.1167/2.8.1}{Estimates of {L}:{M} cone ratio from {ERG} flicker photometry and genetics}.
+\emph{Journal of Vision} \textbf{2}, 1 (2002).}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Barrionuevo2016}{}}%
-Barrionuevo PA, Cao D.
-2016.
-Luminance and chromatic signals interact differently with melanopsin activation to control the pupil light response.
-\emph{Journal of Vision} \textbf{16(11)}:29.
-doi:\href{https://doi.org/10.1167/16.11.29}{10.1167/16.11.29}
+\leavevmode\vadjust pre{\hypertarget{ref-Hofer2005}{}}%
+\CSLLeftMargin{50. }%
+\CSLRightInline{H.
+Hofer, J.
+Carroll, J.
+Neitz, M.
+Neitz, D.
+R.
+Williams, \href{https://doi.org/10.1523/jneurosci.2414-05.2005}{Organization of the human trichromatic cone mosaic}.
+\emph{The Journal of Neuroscience} \textbf{25}, 9669--9679 (2005).}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Barrionuevo2018}{}}%
-Barrionuevo PA, McAnany JJ, Zele AJ, Cao D.
-2018.
-Non-linearities in the {Rod} and {Cone} {Photoreceptor} {Inputs} to the {Afferent} {Pupil} {Light} {Response}.
-\emph{Frontiers in Neurology} \textbf{9}.
-doi:\href{https://doi.org/10.3389/fneur.2018.01140}{10.3389/fneur.2018.01140}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Barrionuevo2014}{}}%
-Barrionuevo PA, Nicandro N, McAnany JJ, Zele AJ, Gamlin P, Cao D.
-2014.
-Assessing rod, cone, and melanopsin contributions to human pupil flicker responses.
-\emph{Investigative Ophthalmology \& Visual Science} \textbf{55}:719--27.
-doi:\href{https://doi.org/10.1167/iovs.13-13252}{10.1167/iovs.13-13252}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Busse2009}{}}%
-Busse L, Wade AR, Carandini M.
-2009.
-Representation of concurrent stimuli by population activity in visual cortex.
-\emph{Neuron} \textbf{64}:931--42.
-doi:\href{https://doi.org/10.1016/j.neuron.2009.11.004}{10.1016/j.neuron.2009.11.004}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Campbell1965}{}}%
-Campbell FW, Green DG. 1965. Monocular versus binocular visual acuity. \emph{Nature} \textbf{208}:191--2. doi:\href{https://doi.org/10.1038/208191a0}{10.1038/208191a0}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Cao2015}{}}%
-Cao D, Nicandro N, Barrionuevo PA.
-2015.
-A five-primary photostimulator suitable for studying intrinsically photosensitive retinal ganglion cell functions in humans.
-\emph{Journal of Vision} \textbf{15}:27.
-doi:\href{https://doi.org/10.1167/15.1.27}{10.1167/15.1.27}
+\leavevmode\vadjust pre{\hypertarget{ref-Baker2021}{}}%
+\CSLLeftMargin{51. }%
+\CSLRightInline{D. H. Baker, \href{https://doi.org/10.51628/001c.27680}{Statistical analysis of periodic data in neuroscience}. \emph{Neurons, Behavior, Data analysis, and Theory} \textbf{5} (2021).}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Carpenter2017}{}}%
-Carpenter B, Gelman A, Hoffman MD, Lee D, Goodrich B, Betancourt M, Brubaker MA, Guo J, Li P, Riddell A.
-2017.
-Stan: A probabilistic programming language.
-\emph{J Stat Softw} \textbf{76}.
-doi:\href{https://doi.org/10.18637/jss.v076.i01}{10.18637/jss.v076.i01}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Carroll2002}{}}%
-Carroll J, Neitz J, Neitz M.
-2002.
-Estimates of {L}:{M} cone ratio from {ERG} flicker photometry and genetics.
-\emph{Journal of Vision} \textbf{2}:1.
-doi:\href{https://doi.org/10.1167/2.8.1}{10.1167/2.8.1}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Dacey2005}{}}%
-Dacey DM, Liao H-W, Peterson BB, Robinson FR, Smith VC, Pokorny J, Yau K-W, Gamlin PD.
-2005.
-Melanopsin-expressing ganglion cells in primate retina signal colour and irradiance and project to the {LGN}.
-\emph{Nature} \textbf{433}:749--754.
-doi:\href{https://doi.org/10.1038/nature03387}{10.1038/nature03387}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Dacey2003}{}}%
-Dacey DM, Peterson BB, Robinson FR, Gamlin PD.
-2003.
-Fireworks in the primate retina: In vitro photodynamics reveals diverse LGN-projecting ganglion cell types.
-\emph{Neuron} \textbf{37}:15--27.
-doi:\url{https://doi.org/10.1016/S0896-6273(02)01143-1}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Ding2006}{}}%
-Ding J, Sperling G.
-2006.
-A gain-control theory of binocular combination.
-\emph{Proc Natl Acad Sci U S A} \textbf{103}:1141--6.
-doi:\href{https://doi.org/10.1073/pnas.0509629103}{10.1073/pnas.0509629103}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Estevez1982}{}}%
-Estévez O, Spekreijse H.
-1982.
-The "silent substitution" method in visual research.
-\emph{Vision Research} \textbf{22}:681--691.
-doi:\href{https://doi.org/10.1016/0042-6989(82)90104-3}{10.1016/0042-6989(82)90104-3}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Gamlin2007}{}}%
-Gamlin PDR, McDougal DH, Pokorny J, Smith VC, Yau K-W, Dacey DM.
-2007.
-Human and macaque pupil responses driven by melanopsin-containing retinal ganglion cells.
-\emph{Vision Research} \textbf{47}:946--954.
-doi:\href{https://doi.org/10.1016/j.visres.2006.12.015}{10.1016/j.visres.2006.12.015}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Hofer2005}{}}%
-Hofer H, Carroll J, Neitz J, Neitz M, Williams DR.
-2005.
-Organization of the human trichromatic cone mosaic.
-\emph{The Journal of Neuroscience} \textbf{25}:9669--9679.
-doi:\href{https://doi.org/10.1523/jneurosci.2414-05.2005}{10.1523/jneurosci.2414-05.2005}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Hubel1962}{}}%
-Hubel DH, Wiesel TN.
-1962.
-Receptive fields, binocular interaction and functional architecture in the cat's visual cortex.
-\emph{J Physiol} \textbf{160}:106--54.
-doi:\href{https://doi.org/10.1113/jphysiol.1962.sp006837}{10.1113/jphysiol.1962.sp006837}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Kaestner2019}{}}%
-Kaestner M, Maloney RT, Wailes-Newson KH, Bloj M, Harris JM, Morland AB, Wade AR.
-2019.
-Asymmetries between achromatic and chromatic extraction of 3D motion signals.
-\emph{Proc Natl Acad Sci U S A} \textbf{116}:13631--13640.
-doi:\href{https://doi.org/10.1073/pnas.1817202116}{10.1073/pnas.1817202116}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Kassner2014}{}}%
-Kassner M, Patera W, Bulling A.
-2014.
-Pupil: An open source platform for pervasive eye tracking and mobile gaze-based interaction.Proceedings of the 2014 {ACM} International Joint Conference on Pervasive and Ubiquitous Computing: Adjunct Publication.
-{ACM}.
-doi:\href{https://doi.org/10.1145/2638728.2641695}{10.1145/2638728.2641695}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Kingdom2015}{}}%
-Kingdom FAA, Libenson L.
-2015.
-Dichoptic color saturation mixture: Binocular luminance contrast promotes perceptual averaging.
-\emph{J Vis} \textbf{15}:2.
-doi:\href{https://doi.org/10.1167/15.5.2}{10.1167/15.5.2}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Legge1984}{}}%
-Legge GE. 1984. Binocular contrast summation--II. Quadratic summation. \emph{Vision Res} \textbf{24}:385--94. doi:\href{https://doi.org/10.1016/0042-6989(84)90064-6}{10.1016/0042-6989(84)90064-6}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Lucas2003}{}}%
-Lucas RJ, Hattar S, Takao M, Berson DM, Foster RG, Yau K-W.
-2003.
-Diminished pupillary light reflex at high irradiances in melanopsin-knockout mice.
-\emph{Science} \textbf{299}:245--247.
-doi:\href{https://doi.org/10.1126/science.1077293}{10.1126/science.1077293}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Markwell2010}{}}%
-Markwell EL, Feigl B, Zele AJ.
-2010.
-Intrinsically photosensitive melanopsin retinal ganglion cell contributions to the pupillary light reflex and circadian rhythm.
-\emph{Clinical and Experimental Optometry} \textbf{93}:137--149.
-doi:\href{https://doi.org/10.1111/j.1444-0938.2010.00479.x}{10.1111/j.1444-0938.2010.00479.x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Martin2023}{}}%
-Martin JT, Boynton GM, Baker DH, Wade AR, Spitschan M.
-2023.
-PySilSub: An open-source python toolbox for implementing the method of silent substitution in vision and nonvisual photoreception research.
-\emph{Journal of Vision} \textbf{23}:10.
-doi:\href{https://doi.org/10.1167/jov.23.7.10}{10.1167/jov.23.7.10}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Martin2022}{}}%
-Martin JT, Pinto J, Bulte D, Spitschan M.
-2022.
-PyPlr: A versatile, integrated system of hardware and software for researching the human pupillary light reflex.
-\emph{Behavior Research Methods} \textbf{54}:2720--2739.
-doi:\href{https://doi.org/10.3758/s13428-021-01759-3}{10.3758/s13428-021-01759-3}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Mathot2018}{}}%
-Mathôt S. 2018. Pupillometry: Psychology, physiology, and function. \emph{J Cogn} \textbf{1}:16. doi:\href{https://doi.org/10.5334/joc.18}{10.5334/joc.18}
-
-\leavevmode\vadjust pre{\hypertarget{ref-McDougal2015}{}}%
-McDougal DH, Gamlin PD. 2015. Autonomic control of the eye. \emph{Comprehensive Physiology} \textbf{5}:439--473. doi:\href{https://doi.org/10.1002/cphy.c140014}{10.1002/cphy.c140014}
-
-\leavevmode\vadjust pre{\hypertarget{ref-McDougal2010}{}}%
-McDougal DH, Gamlin PD.
-2010.
-The influence of intrinsically-photosensitive retinal ganglion cells on the spectral sensitivity and response dynamics of the human pupillary light reflex.
-\emph{Vision Research} \textbf{50}:72--87.
-doi:\href{https://doi.org/10.1016/j.visres.2009.10.012}{10.1016/j.visres.2009.10.012}
-
-\leavevmode\vadjust pre{\hypertarget{ref-McDougal2008}{}}%
-McDougal DH, Gamlin PD. 2008. Pupillary control pathways.The Senses: A Comprehensive Reference. Elsevier. pp. 521--536.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Meese2006}{}}%
-Meese TS, Georgeson MA, Baker DH. 2006. Binocular contrast vision at and above threshold. \emph{Journal of Vision} \textbf{6}:1224--43. doi:\href{https://doi.org/10.1167/6.11.7}{10.1167/6.11.7}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Moradi2009}{}}%
-Moradi F, Heeger DJ. 2009. Inter-ocular contrast normalization in human visual cortex. \emph{J Vis} \textbf{9}:13.1--22. doi:\href{https://doi.org/10.1167/9.3.13}{10.1167/9.3.13}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Murray2018}{}}%
-Murray IJ, Kremers J, McKeefry D, Parry NRA.
-2018.
-Paradoxical pupil responses to isolated {M}-cone increments.
-\emph{Journal of the Optical Society of America A} \textbf{35}:B66--B71.
-doi:\href{https://doi.org/10.1364/JOSAA.35.000B66}{10.1364/JOSAA.35.000B66}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Norcia2015}{}}%
-Norcia AM, Appelbaum LG, Ales JM, Cottereau BR, Rossion B.
-2015.
-The steady-state visual evoked potential in vision research: A review.
-\emph{Journal of Vision} \textbf{15(6)}:4.
-doi:\href{https://doi.org/10.1167/15.6.4}{10.1167/15.6.4}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Panda2002}{}}%
-Panda S, Sato TK, Castrucci AM, Rollag MD, DeGrip WJ, Hogenesch JB, Provencio I, Kay SA.
-2002.
-Melanopsin (Opn4) requirement for normal light-induced circadian phase shifting.
-\emph{Science} \textbf{298}:2213--2216.
-doi:\href{https://doi.org/10.1126/science.1076848}{10.1126/science.1076848}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Provencio2000}{}}%
-Provencio I, Rodriguez IR, Jiang G, Hayes WP, Moreira EF, Rollag MD.
-2000.
-A {Novel} {Human} {Opsin} in the {Inner} {Retina}.
-\emph{Journal of Neuroscience} \textbf{20}:600--605.
-doi:\href{https://doi.org/10.1523/JNEUROSCI.20-02-00600.2000}{10.1523/JNEUROSCI.20-02-00600.2000}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Ruby2002}{}}%
-Ruby NF, Brennan TJ, Xie X, Cao V, Franken P, Heller HC, O'Hara BF.
-2002.
-Role of melanopsin in circadian responses to light.
-\emph{Science} \textbf{298}:2211--2213.
-doi:\href{https://doi.org/10.1126/science.1076701}{10.1126/science.1076701}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Segala2023}{}}%
-Segala FG, Bruno A, Martin JT, Aung MT, Wade AR, Baker DH.
-2023.
-Different rules for binocular combination of luminance flicker in cortical and subcortical pathways.
-\emph{eLife} \textbf{12}.
-doi:\href{https://doi.org/10.7554/elife.87048}{10.7554/elife.87048}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Shapiro1996}{}}%
-Shapiro AG, Pokorny J, Smith VC.
-1996.
-Cone{\textendash}rod receptor spaces with illustrations that use {CRT} phosphor and light-emitting-diode spectra.
-\emph{Journal of the Optical Society of America A} \textbf{13}:2319.
-doi:\href{https://doi.org/10.1364/josaa.13.002319}{10.1364/josaa.13.002319}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Spitschan2019}{}}%
-Spitschan M, Cajochen C. 2019. Binocular facilitation in light-mediated melatonin suppression? \emph{J Pineal Res} \textbf{67}:e12602. doi:\href{https://doi.org/10.1111/jpi.12602}{10.1111/jpi.12602}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Spitschan2014}{}}%
-Spitschan M, Jain S, Brainard DH, Aguirre GK.
-2014.
-Opponent melanopsin and s-cone signals in the human pupillary light response.
-\emph{Proceedings of the National Academy of Sciences} \textbf{111}:15568--15572.
-doi:\href{https://doi.org/10.1073/pnas.1400942111}{10.1073/pnas.1400942111}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Spitschan2018}{}}%
-Spitschan M, Woelders T.
-2018.
-The {Method} of {Silent} {Substitution} for {Examining} {Melanopsin} {Contributions} to {Pupil} {Control}.
-\emph{Frontiers in Neurology} \textbf{9}.
-doi:\href{https://doi.org/10.3389/fneur.2018.00941}{10.3389/fneur.2018.00941}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Stockman2000}{}}%
-Stockman A, Sharpe LT.
-2000.
-The spectral sensitivities of the middle- and long-wavelength-sensitive cones derived from measurements in observers of known genotype.
-\emph{Vision Res} \textbf{40}:1711--37.
-doi:\href{https://doi.org/10.1016/s0042-6989(00)00021-3}{10.1016/s0042-6989(00)00021-3}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Wang2015}{}}%
-Wang C-A, Munoz DP.
-2015.
-A circuit for pupil orienting responses: Implications for cognitive modulation of pupil size.
-\emph{Curr Opin Neurobiol} \textbf{33}:134--40.
-doi:\href{https://doi.org/10.1016/j.conb.2015.03.018}{10.1016/j.conb.2015.03.018}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Woelders2018}{}}%
-Woelders T, Leenheers T, Gordijn MCM, Hut RA, Beersma DGM, Wams EJ.
-2018.
-Melanopsin- and {L}-cone--induced pupil constriction is inhibited by {S}- and {M}-cones in humans.
-\emph{Proceedings of the National Academy of Sciences} \textbf{115}:792--797.
-doi:\href{https://doi.org/10.1073/pnas.1716281115}{10.1073/pnas.1716281115}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Wyatt1981}{}}%
-Wyatt HJ, Musselman JF.
-1981.
-Pupillary light reflex in humans: Evidence for an unbalanced pathway from nasal retina, and for signal cancellation in brainstem.
-\emph{Vision Res} \textbf{21}:513--25.
-doi:\href{https://doi.org/10.1016/0042-6989(81)90097-3}{10.1016/0042-6989(81)90097-3}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Zele2018}{}}%
-Zele AJ, Feigl B, Adhikari P, Maynard ML, Cao D.
-2018.
-Melanopsin photoreception contributes to human visual detection, temporal and colour processing.
-\emph{Scientific Reports} \textbf{8}.
-doi:\href{https://doi.org/10.1038/s41598-018-22197-w}{10.1038/s41598-018-22197-w}
+\CSLLeftMargin{52. }%
+\CSLRightInline{B. Carpenter, \emph{et al.}, \href{https://doi.org/10.18637/jss.v076.i01}{Stan: A probabilistic programming language}. \emph{J Stat Softw} \textbf{76} (2017).}
 

### 2024-05-22 ExperimentCode/analyisis.py

@@ -1,0 +1,66 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Fri Aug 19 13:06:03 2022
+
+@author: bbsrc
+"""
+import os
+import os.path as op
+import pandas as pd
+import numpy as np
+import matplotlib.pyplot as plt
+from scipy.signal import butter, filtfilt
+
+from pyplr import utils, preproc
+
+DATA_DIR ='/home/bbsrc/Desktop/Experiments/MonBinPupil/S-cone/results/jtm/000/exports/000/'
+
+annotations = pd.read_csv(op.join(DATA_DIR, 'annotations.csv'))
+pupil = pd.read_csv(op.join(DATA_DIR, 'pupil_positions.csv'))
+left = pupil.loc[pupil.eye_id==0]
+right = pupil.loc[pupil.eye_id==1]
+
+for eye in [left, right]:
+    eye.loc[eye.confidence<.1, 'diameter_3d'] = np.nan  
+    eye.diameter_3d = eye.diameter_3d.interpolate()
+    eye = preproc.butterworth_series(eye, ['diameter_3d'], 3, 4/(120/2))
+
+events = annotations[annotations.label=='pre_scene']
+events = events.set_index('timestamp')
+left = left.set_index('pupil_timestamp')
+right = right.set_index('pupil_timestamp')
+
+borrow_attributes = [
+'label', 'duration', 'condition_code',
+'contrastL', 'contrastR', 'frequencyL', 
+'frequencyR','ocular_condition']
+
+
+left_trials = utils.extract(
+    left, events, offset=0, duration = 1440, borrow_attributes=borrow_attributes
+    )
+
+right_trials = utils.extract(
+    right, events, offset=0, duration = 1440, borrow_attributes=borrow_attributes
+    )
+
+t = np.linspace(0, 12, 1440) 
+for ids, df in right_trials.groupby('event'):
+    plt.plot(t, df.diameter_3d)
+
+
+# Plot
+fig, ax = plt.subplots(1, 1, figsize=(12, 4))
+
+newL = (
+       left_trials.groupby(
+           ['contrastL', 'frequencyL', 'onset'])
+       ['diameter_3d'].mean().unstack().T
+)
+    
+newR = (
+       right_trials.groupby(
+           ['contrastR', 'frequencyR', 'onset'])
+       ['diameter_3d'].mean().unstack().T
+       )

### 2024-05-22 ExperimentCode/change_data_source.py

@@ -1,0 +1,26 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Fri Mar  3 07:56:21 2023
+
+@author: bbsrc
+
+Load in the old datasource file and change the parameters.
+"""
+
+import pandas as pd
+
+ds = pd.read_csv('../MonBin/datasource.csv')
+
+
+ds['frequencyL'] = ds['frequencyL'].replace(1.6, .4)
+ds['frequencyL'] = ds['frequencyL'].replace(2.0, .5)
+ds['frequencyR'] = ds['frequencyR'].replace(1.6, .4)
+ds['frequencyR'] = ds['frequencyR'].replace(2.0, .5)
+
+ds['videoL'] = ds['videoL'].str.replace('_f1.6', '_f0.4')
+ds['videoL'] = ds['videoL'].str.replace('_f2.0', '_f0.5')
+ds['videoR'] = ds['videoR'].str.replace('_f1.6', '_f0.4')
+ds['videoR'] = ds['videoR'].str.replace('_f2.0', '_f0.5')
+
+ds.to_csv('./datasource.csv')

### 2024-05-22 ExperimentCode/make_conditions.py

@@ -1,0 +1,30 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Jun 13 15:14:08 2022
+
+@author: bbsrc
+"""
+
+from itertools import product 
+
+import pandas as pd
+
+
+
+ocular_conditions = ['MonL', 'MonR', 'Bin', 'DichL', 'DichR', 
+                     'MonXL', 'MonXR', 'BinX', 'DichXL', 'DichXR']
+contrasts = [.06, .12, .24, .48, .96]
+conditions = product(ocular_conditions, contrasts)
+conditions = [(i+1, *con) 
+              for i, con in enumerate(product(ocular_conditions, contrasts))]
+# Double up on Bin conditions
+conditions = conditions + [c for c in conditions if 'Bin' in c]
+conditions = sorted(conditions)
+conditions = pd.DataFrame(conditions, columns=[
+    'condition_code',
+    'condition',
+    'contrast'
+    ]
+    )
+

### 2024-05-22 ExperimentCode/make_luminance_stims.py

@@ -1,0 +1,263 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Sat Jun 11 16:37:42 2022
+
+@author: jtm545
+
+Script to make the stimuli for the MonBin1 experiment. 
+
+"""
+
+import os
+import os.path as op
+from itertools import product
+from pprint import pprint
+import pickle
+from datetime import datetime
+
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+
+
+from pyplr import stlabhelp
+from pysilsub.problems import SilentSubstitutionProblem as SSP
+from pysilsub.CIE import get_CIE_1924_photopic_vl
+
+LUMENS_PER_WATT = 683
+
+
+# %% ~~~ PLOT STYLE ~~~
+
+plt.style.use('seaborn')
+plt.rcParams['font.size'] = 14
+plt.rcParams['font.family'] = 'Helvetica'
+
+# %% ~~~ CONSTANTS ~~~
+
+MINTENSITY = 0
+MAXTENSITY = 4095
+BACKGROUND = MAXTENSITY/2
+Fs = 100  # STLAB switching time
+VL = get_CIE_1924_photopic_vl()
+
+# %% ~~~ MAKE FOLDERS FOR OUTPUT ~~~
+
+STIM_FOLDER = './Luminance/stims/'
+if not op.exists(STIM_FOLDER):
+    os.mkdir(STIM_FOLDER)
+
+STLAB_1_STIM_FOLDER = op.join(STIM_FOLDER, 'STLAB_1/')
+if not op.exists(STLAB_1_STIM_FOLDER):
+    os.mkdir(STLAB_1_STIM_FOLDER)
+    
+STLAB_2_STIM_FOLDER = op.join(STIM_FOLDER, 'STLAB_2/')
+if not op.exists(STLAB_2_STIM_FOLDER):
+    os.mkdir(STLAB_2_STIM_FOLDER)
+    
+CALIBRATION_FOLDER = './calibration/'
+if not op.exists(CALIBRATION_FOLDER):
+    os.mkdir(CALIBRATION_FOLDER)
+
+GAMMA_FOLDER = op.join(CALIBRATION_FOLDER, 'gamma/')
+if not op.exists(GAMMA_FOLDER):
+    os.mkdir(op.join(GAMMA_FOLDER))
+
+#%% ~~~ CALIBRATION ~~~ #
+
+# Load predictive models for each device.
[…]

### 2024-05-22 ExperimentCode/make_stimuli.py

@@ -1,0 +1,307 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Sat Jun 11 16:37:42 2022
+
+@author: jtm545
+
+Script to make the stimuli for the MonBinPupil experiment. 
+"""
+import os
+import os.path as op
+from itertools import product
+from pprint import pprint
+from datetime import datetime
+import pickle
+
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+
+from pyplr import stlabhelp
+from pysilsub.problems import SilentSubstitutionProblem as SSP
+from pysilsub.observers import ColorimetricObserver as ICO
+
+# %% ~~~ PLOT STYLE ~~~
+
+plt.style.use('seaborn')
+plt.rcParams['font.size'] = 14
+plt.rcParams['font.family'] = 'Helvetica'
+
+# %% Functions
+
+
+def check_exists(folder: str) -> str:
+    if not op.exists(folder):
+        os.makedirs(folder)
+    return folder
+
+
+# %% ~~~ EXPERIMENTS ~~~
+# These appear to be the maximum achieveable contrasts
+SCONE = {
+    'ignore': ['rh'],
+    'target': ['sc'],
+    'silence': ['mc', 'lc', 'mel'],
+    'max_contrast': .45
+}
+
+MCONE = {
+    'ignore': ['rh'],
+    'target': ['mc'],
+    'silence': ['sc', 'lc', 'mel'],
+    'max_contrast': .13
+}
+
+LCONE = {
+    'ignore': ['rh'],
+    'target': ['lc'],
+    'silence': ['sc', 'mc', 'mel'],
+    'max_contrast': .15
+}
+
+MELANOPSIN = {
+    'ignore': ['rh'],
+    'target': ['mel'],
+    'silence': ['sc', 'mc', 'lc'],
+    'max_contrast': .22
+}
+
+LMINUSM = {
+    'ignore': ['rh'],
+    'target': ['mc', 'lc'],
+    'silence': ['sc', 'mel'],
+    'max_contrast': .1
+}
+
+
+EXPERIMENTS = {
+    'S-cone': SCONE,
+    'M-cone': MCONE,
+    'L-cone': LCONE,
+    'Melanopsin': MELANOPSIN,
+    'L-M': LMINUSM
+}
+
+
+
+# %% ~~~ CONSTANTS ~~~
+
+
[…]

### 2024-05-22 ExperimentCode/make_stimuli_luminance_2.py

@@ -1,0 +1,208 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Sat Jun 11 16:37:42 2022
+
+@author: jtm545
+
+Script to make the stimuli for the MonBin1 experiment. 
+"""
+
+import os
+import os.path as op
+from itertools import product
+
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+
+from pyplr import stlabhelp
+from pysilsub.devices import StimulationDevice
+from pysilsub.binocular import BinocularStimulationDevice
+from pysilsub.CIE import get_CIE_1924_photopic_vl, get_CIES026_action_spectra
+
+
+# Make stims folder if it doesn't exist
+if not op.exists('./Luminance'):
+    os.mkdir('./Luminance')
+    os.mkdir('./Luminance/STLAB_1')
+    os.mkdir('./Luminance/STLAB_2')
+    print('> Created stims folder: "./Luminance"')
+
+# Constants
+MINTENSITY = 0
+MAXTENSITY = 4095
+BACKGROUND = MAXTENSITY/2
+Fs = 100
+vl = get_CIE_1924_photopic_vl()
+lms = get_CIES026_action_spectra()
+
+# Predictive models for each device
+S1 = StimulationDevice.from_json('./calibration/STLAB_1_York.json')
+S2 = StimulationDevice.from_json('./calibration/STLAB_2_York.json')
+
+# Binocular helper to optimise settings 
+Sbin = BinocularStimulationDevice(S1, S2)
+Sbin.anchor = 'left'
+Sbin.optim = 'right'
+
+# Gamma correct the anchored device
+S1.do_gamma(fit='polynomial')
+S1.gamma[ S1.gamma<0] = 0
+S1.plot_gamma(show_corrected=True)
+S2.do_gamma(fit='polynomial')
+S2.gamma[S2.gamma<0] = 0
+S2.plot_gamma(show_corrected=True)
+
+# Bounds for primaries
+bounds = [(0., 1.,) for primary in range(10)]
+
+
+# Plot for stimuli
+plt.style.use('seaborn')
+fig, axs = plt.subplots(2, 3, figsize=(12, 6))
+
+# Stimulus parameters
+frequencies = [.4, .5]
+contrasts = [.06, .12, .24, .48, .96]
+#contrasts = [.96]
+seconds = 12
+
[…]

### 2024-05-22 ExperimentCode/monbin.py

@@ -1,0 +1,391 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Script to run monocular and binocular targeted photoreceptor experiments.
+
+
+@author: jtm
+"""
+import os
+import os.path as op
+import shutil
+import glob
+from time import sleep
+import pickle
+
+import pandas as pd
+import parallel
+from pyplr.pupil import PupilCore
+from pyplr.stlabscene import SpectraTuneLabScene
+from pyplr.protocol import timer
+
+import make_stimuli
+
+
+#-------------------------------#
+#    Experiment configuration   #
+#-------------------------------#
+# Experiments to choose from
+EXPERIMENTS_TO_RUN = dict(
+    enumerate(['S-cone', 'M-cone', 'L-cone', 'Melanopsin', 'L-M', 'Luminance']))
+
+# Experiment pauses at end of trial if this file exists
+PAUSEFILE = op.join(op.expanduser('~'), 'PAUSEFILE')
+
+# Timing parameters in s
+ADAPTATION_PERIOD = 2*60
+INCLUDE_ADAPTATION_PERIOD = True
+STIMULUS_DURATION = 12
+
+# Experiment parameters
+DOUBLE_TRIALS = False
+
+# Set to 1. to run all 60 trials
+FRAC_TRIALS = 1.0
+
+# inter-trial interval
+ITI = 3
+
+# Hardware flags
+USE_STLAB = True
+USE_PUPIL_CORE = True
+USE_EEG = False
+
+#-------------------------------#
+# Functions
+
+
+class OverwriteError(Exception):
+    pass
+
+
+def choose_experiment():
+    print('Which experiment to run?\n')
+    print(*EXPERIMENTS_TO_RUN.items(), sep='\n')
+    experiment = ''
+    while experiment not in EXPERIMENTS_TO_RUN.keys():
+        experiment = int(input('\n> Enter the number: '))
+        if experiment not in EXPERIMENTS_TO_RUN.keys():
+            print('Enter a valid experiment...')
+    return EXPERIMENTS_TO_RUN[experiment]
+
+#-------------------------------#
+
+
+def main():
+    try:
+        print('\n')
+        print(f"{'='*80 : ^80}")
+        print(f"{'MonBin Photoreceptors': ^80}")
+        print(f"{'='*80 : ^80}")
+        print('\n')
+        sleep(.1)
+
+        # Ask experimenter to choose the experiment
+        experiment = choose_experiment()
+
+        # Ask for subject ID and block number
[…]

### 2024-05-22 ExperimentCode/psychonulltest_mouse.py

@@ -1,0 +1,263 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Apr 17 11:14:04 2023
+
+@author: bbsrc
+
+This script implements a psychophysical nulling procedure for STLAB.
+
+"""
+
+from pysilsub.observers import ColorimetricObserver
+from pysilsub.problems import SilentSubstitutionProblem
+from pyplr import stlabscene
+from pyplr import stlabhelp
+from pynput import mouse  
+import matplotlib.pyplot as plt
+import pandas as pd
+import numpy as np
+import pickle
+import glob
+import os
+#sys.path.append("/home/j/jtm545/MonBinMRI/Code/PyPlr")
+#sys.path.append("/home/j/jtm545/MonBinMRI/Code/PySilSub")
+
+
+# Upper and lower limites, -90 to 0 or 30
+# Random starting point within range on each trial
+# Right click to start trial
+# Background spectrum between trials
+# Optimal flicker... ?
+# Display diagram after protocol
+# Include standard settings in case of bad data
+
+# Configuration
+TARGET = ['mc', 'lc']
+SILENCE = ['sc', 'mel']
+IGNORE = ['rh']
+
+
+
+# Use global variables. This is bad practice because it makes code hard to test 
+# and diag4nose, but in this case they make sense (to me).
+global FLICKER_FREQUENCY, TARGET_CONTRAST, RESPONSES, LOWER_LIMIT, UPPER_LIMIT, ALPHA, TRIALNUM
+FLICKER_FREQUENCY = 15  # Hz
+TARGET_CONTRAST = [0.0, 0.0]
+RESPONSES = []
+LOWER_LIMIT, UPPER_LIMIT = -np.pi/2., np.pi/5  # -90 to 36 degrees
+TRIALNUM = 0
+
+OBSERVER_AGE = 41
+MAXTENSITY = 4095
+STLAB_1, STLAB_2 = 1021, 1022
+STLAB_BROADCAST = 1023
+
+
+
+def new_alpha():
+    """New random alpha value between -90 and 36 degrees."""
+    return np.random.uniform(-np.pi/2., np.pi/5)
+
+ALPHA = new_alpha()
+
+# Time step for making video files
+time_step = int((
+    int(FLICKER_FREQUENCY*1000)
+    if FLICKER_FREQUENCY < 1.
+    else int((1 / FLICKER_FREQUENCY) * 1000)
+)/2)
+
[…]

### 2024-05-22 manuscript.Rmd
Test level 1 of processdata

@@
 author: |
- | Federico G. Segala$^1$, Aurelio Bruno$^{1,2}$, Joel T. Martin$^{1,3}$, Anisa Y. Morsi$^1$, Alex R. Wade$^{1,4}$
- | & Daniel H. Baker$^{1,4}$
+ | Federico G. Segala$^1$, Aurelio Bruno$^{1,2}$, Joel T. Martin$^{1,3}$, $
+ | Anisa Y. Morsi$^1$, Alex R. Wade$^{1,4} & Daniel H. Baker$^{1,4}$
 output:
@@
 
-processdata <- 0 # this flag determines the amount of processing, with 4 levels:
+processdata <- 1 # this flag determines the amount of processing, with 4 levels:
 # 0 - do no processing, generate the pdf using existing versions of all figures

### 2024-05-22 manuscript.Rmd
Testing processdata level 2
Processdata 2

--- 2024-05-22 manuscript.Rmd
@@
 author: |
- | Federico G. Segala$^1$, Aurelio Bruno$^{1,2}$, Joel T. Martin$^{1,3}$, Anisa Y. Morsi$^1$, Alex R. Wade$^{1,4}$
- | & Daniel H. Baker$^{1,4}$
+ | Federico G. Segala$^1$, Aurelio Bruno$^{1,2}$, Joel T. Martin$^{1,3}$,
+ | Anisa Y. Morsi$^1$, Alex R. Wade$^{1,4}$ & Daniel H. Baker$^{1,4}$
 output:
@@
 
-processdata <- 0 # this flag determines the amount of processing, with 4 levels:
+processdata <- 2 # this flag determines the amount of processing, with 4 levels:
 # 0 - do no processing, generate the pdf using existing versions of all figures

### 2024-05-22 manuscript.Rmd
Test Stan modelling with reduced number of iterations

--- 2024-05-22 manuscript.Rmd
@@
 
-domodelling <- 0    # if set to 1, run the Stan models (takes ~24 hours)
+domodelling <- 1    # if set to 1, run the Stan models (takes ~24 hours)
 
@@
 # settings for sampler 
-numSavedSteps <- 100000    # total number of MCMC steps
-adaptSteps <- 1000  # Number of steps to "tune" the samplers
-burnInSteps <- 2000 
-thinSteps <- 10
-nChains <- 16
-ncores <- 8
+numSavedSteps <- 100000/100    # total number of MCMC steps
+adaptSteps <- 1000/10  # Number of steps to "tune" the samplers
+burnInSteps <- 2000/10
+thinSteps <- 10/10
+nChains <- 16/4
+ncores <- 8/8
 options(mc.cores=ncores)

### 2024-05-22 manuscript.Rmd
Fixed to download individual data files for modelling

@@
 
-if (processdata==2){
+if (processdata==2 || domodelling==1){
 # if we're going to need the pre-processed files, extract from zip file

### 2024-05-22 manuscript.Rmd
Revert to standard settings

@@
 
-domodelling <- 1    # if set to 1, run the Stan models (takes ~24 hours)
+domodelling <- 0    # if set to 1, run the Stan models (takes ~24 hours)
 
@@
 # settings for sampler 
-numSavedSteps <- 100000/100    # total number of MCMC steps
-adaptSteps <- 1000/10  # Number of steps to "tune" the samplers
-burnInSteps <- 2000/10
-thinSteps <- 10/10
-nChains <- 16/4
-ncores <- 8/8
+numSavedSteps <- 100000    # total number of MCMC steps
+adaptSteps <- 1000  # Number of steps to "tune" the samplers
+burnInSteps <- 2000
+thinSteps <- 10
+nChains <- 16
+ncores <- 8
 options(mc.cores=ncores)

### 2024-06-04 manuscript.Rmd
Corrected typo in abstract

@@
 The diameter of the pupil fluctuates in response to levels of ambient light and is regulated by the autonomic nervous system.
-Increasing light in one eye causes both pupils to constrict, implying the system must combine signals across the two eyes -- a process of binocular integration occuring independently of visual cortex.
+Increasing light in one eye causes both pupils to constrict, implying the system must combine signals across the two eyes -- a process of binocular integration occurring independently of visual cortex.
 Distinct classes of retinal photoreceptor are involved in controlling and maintaining pupil diameter, with cones and rods driving the initial constriction and intrinsically photosensitive retinal ganglion cells maintaining diameter over prolonged time periods.

### 2024-06-04 manuscript.tex
Corrected typo in abstract

@@
 \setcounter{secnumdepth}{5}
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newlength{\cslentryspacingunit} % times entry-spacing
-\setlength{\cslentryspacingunit}{\parskip}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1
-  \let\oldpar\par
-  \def\par{\hangindent=\cslhangindent\oldpar}
-  \fi
-  % set entry spacing
-  \setlength{\parskip}{#2\cslentryspacingunit}
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 \usepackage{caption} \usepackage{lineno} \linenumbers
@@
 \usepackage{xcolor}
-\ifLuaTeX
-  \usepackage{selnolig}  % disable illegal ligatures
-\fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same}
-\hypersetup{
-  pdftitle={Binocular combination in the autonomic nervous system},
-  colorlinks=true,
-  linkcolor={black},
-  filecolor={Maroon},
-  citecolor={Blue},
-  urlcolor={Blue},
-  pdfcreator={LaTeX via pandoc}}
 
 \title{Binocular combination in the autonomic nervous system}
-\author{Federico G. Segala\(^1\), Aurelio Bruno\(^{1,2}\), Joel T. Martin\(^{1,3}\), Anisa Y. Morsi\(^1\), Alex R. Wade\(^{1,4}\)\\
-\& Daniel H. Baker\(^{1,4}\)}
+\author{Federico G. Segala\(^1\), Aurelio Bruno\(^{1,2}\), Joel T. Martin\(^{1,3}\),\\
+Anisa Y. Morsi\(^1\), Alex R. Wade\(^{1,4}\) \& Daniel H. Baker\(^{1,4}\)}
 \date{}
@@
 
-\hypertarget{significance-statement-120-words}{%
-\section{Significance statement (120 words)}\label{significance-statement-120-words}}
-
 \hypertarget{introduction}{%
@@
 The anatomical pathway from the retina to the subcortical nuclei controlling the pupillary light response (PLR) is well established: it includes the Pretectal Olivary nucleus (PON), the Superior Cervical ganglion and the Edinger-Westphal nucleus, which project to the iris sphincter muscles that directly control the pupil size (\protect\hyperlink{ref-McDougal2015}{1}--\protect\hyperlink{ref-Wang2015}{3}).
-Evidence of a binocular component to the PLR is shown by the existence of a consensual response of the pupil (the stimulation of one eye will cause constriction of the other eye; \protect\hyperlink{ref-Wyatt1981}{4}).
+Evidence of a binocular component to the PLR is shown by the existence of a consensual response of the pupil (\protect\hyperlink{ref-Wyatt1981}{4}).
 The anatomical segregation of the subcortical pathway from the rest of the brain means that this binocular combination of signals must occur independently of the cortical processes of binocular integration required for visual perception.
@@
 Silent substitution exploits the fact that each photoreceptor class has a distinct spectral tuning that overlaps with the others.
-Using a multiprimary system, in which the primaries (i.e.~LEDs) have different spectra, it is possible to target one class of photoreceptors while maintaining the others at a constant activity level, effectively silencing them (\protect\hyperlink{ref-Shapiro1996}{23}, \protect\hyperlink{ref-Spitschan2018}{24}, this paper also offers a clear explanation of how to implement silent substitution).
+Using a multiprimary system, in which the primaries (i.e.~LEDs) have different spectra, it is possible to target one class of photoreceptors while maintaining the others at a constant activity level, effectively silencing them (\protect\hyperlink{ref-Shapiro1996}{23}, \protect\hyperlink{ref-Spitschan2018}{24}).
 Studies using silent substitution have shown that the pupils behave differently depending on which photoreceptor or pathway is being stimulated.
@@
 Most studies that use silent substitution to investigate the PLR stimulate only one eye.
-If the stimulated eye is pharmacologically dilated to control pupil size, the response from the unstimulated eye (known as the consensual response) can be recorded (\protect\hyperlink{ref-Spitschan2014}{10}, e.g.
-\protect\hyperlink{ref-McDougal2010}{15}).
+If the stimulated eye is pharmacologically dilated to control pupil size, the response from the unstimulated eye (known as the consensual response) can be recorded (\protect\hyperlink{ref-Spitschan2014}{10}, \protect\hyperlink{ref-McDougal2010}{15}).
 While this approach controls the total amount of light incident at the retina, it does not permit investigation of binocular combination for specific photoreceptor pathways.
@@
 We can estimate the strength of interocular suppression by measuring how much monocular responses are reduced when a dichoptic `mask' is shown to the other eye.
-In our paradigm, the two components flickered at different frequencies (0.5 and 0.4Hz) so that their responses remained distinct in the Fourier spectrum (e.g.
-\protect\hyperlink{ref-Busse2009}{35}).
+In our paradigm, the two components flickered at different frequencies (0.5 and 0.4Hz) so that their responses remained distinct in the Fourier spectrum (\protect\hyperlink{ref-Busse2009}{35}).
 The yellow diamond symbols in Figure \ref{fig:FirstHarmonicPlots}a-d show the target responses in this condition, and in most cases were weaker than the monocular responses (red circles).
@@
 The outputs of the two light engines (see Figure \ref{fig:spectraplots}b,c) were calibrated using an Ocean Optics Jaz spectroradiometer, which was wavelength-calibrated to an Argon lamp and intensity calibrated using a NIST-traceable light source.
-We used the (\protect\hyperlink{ref-Stockman2000}{41}) 10-degree cone fundamentals, and estimates of melanopsin absorbance spectra from CIE S 026 (discussed in \protect\hyperlink{ref-Martin2023}{40}) to calculate \(\alpha\)-opic irradiance.
+We used the (\protect\hyperlink{ref-Stockman2000}{41}) 10-degree cone fundamentals, and estimates of melanopsin absorbance spectra from CIE S 026 (\protect\hyperlink{ref-Martin2023}{40}) to calculate \(\alpha\)-opic irradiance.
 
@@
 The diffuser discs were positioned in the objective planes of the lenses of a modified VR headset (SHINECON SC-G01, Dongguan Shinecon Industrial Co.~Ltd., Guangdong, China), which was used by the participants to view the stimuli.
-The stimuli were two discs of flickering light with a diameter of approximately 30 degrees, which were fused together into a cyclopean percept resembling a donut-shaped ring of light, similar to that used in other studies (\protect\hyperlink{ref-Murray2018}{9}, \protect\hyperlink{ref-Spitschan2014}{10}, e.g., \protect\hyperlink{ref-Barrionuevo2016}{42}, \protect\hyperlink{ref-Spitschan2015}{43}, \protect\hyperlink{ref-Zele2018}{44}).
+The stimuli were two discs of flickering light with a diameter of approximately 30 degrees, which were fused together into a cyclopean percept resembling a donut-shaped ring of light, similar to that used in other studies (\protect\hyperlink{ref-Murray2018}{9}, \protect\hyperlink{ref-Spitschan2014}{10}, \protect\hyperlink{ref-Barrionuevo2016}{42}--\protect\hyperlink{ref-Zele2018}{44}).
 The VR headset modifications allowed for small adjustments to account for individual differences in interpupillary distance and focal length.
@@
 A schematic of the stimulation system is shown in Figure \ref{fig:spectraplots}a.
-Pupillometry data were collected using a binocular Pupil Core eye-tracker headset (Pupil Labs GmbH, Berlin, Germany, \protect\hyperlink{ref-Kassner2014}{45}) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
+Pupillometry data were collected using a binocular Pupil Core eye-tracker headset (\protect\hyperlink{ref-Kassner2014}{45}) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
 
@@
 \hypertarget{refs}{}
-\begin{CSLReferences}{0}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-McDougal2015}{}}%
-\CSLLeftMargin{1. }%
-\CSLRightInline{D. H. McDougal, P. D. Gamlin, \href{https://doi.org/10.1002/cphy.c140014}{Autonomic control of the eye}. \emph{Comprehensive Physiology} \textbf{5}, 439--473 (2015).}
+\leavevmode\hypertarget{ref-McDougal2015}{}%
+1. D. H. McDougal, P. D. Gamlin, Autonomic control of the eye. \emph{Comprehensive Physiology} \textbf{5}, 439--473 (2015).
 
-\leavevmode\vadjust pre{\hypertarget{ref-McDougal2008}{}}%
-\CSLLeftMargin{2. }%
-\CSLRightInline{D. H. McDougal, P. D. Gamlin, {``Pupillary control pathways.''} in \emph{The Senses: A Comprehensive Reference}, (Elsevier, 2008), pp. 521--536.}
+\leavevmode\hypertarget{ref-McDougal2008}{}%
+2. D. H. McDougal, P. D. Gamlin, ``Pupillary control pathways.'' in \emph{The Senses: A Comprehensive Reference}, (Elsevier, 2008), pp. 521--536.
 
-\leavevmode\vadjust pre{\hypertarget{ref-Wang2015}{}}%
-\CSLLeftMargin{3. }%
-\CSLRightInline{C.-A.
-Wang, D.
-P.
-Munoz, \href{https://doi.org/10.1016/j.conb.2015.03.018}{A circuit for pupil orienting responses: Implications for cognitive modulation of pupil size}.
-\emph{Curr Opin Neurobiol} \textbf{33}, 134--40 (2015).}
+\leavevmode\hypertarget{ref-Wang2015}{}%
+3. C.-A. Wang, D. P. Munoz, A circuit for pupil orienting responses: Implications for cognitive modulation of pupil size. \emph{Curr Opin Neurobiol} \textbf{33}, 134--40 (2015).
 
-\leavevmode\vadjust pre{\hypertarget{ref-Wyatt1981}{}}%
-\CSLLeftMargin{4. }%
-\CSLRightInline{H.
+\leavevmode\hypertarget{ref-Wyatt1981}{}%
+4.
+H.
 J.
@@
 F.
-Musselman, \href{https://doi.org/10.1016/0042-6989(81)90097-3}{Pupillary light reflex in humans: Evidence for an unbalanced pathway from nasal retina, and for signal cancellation in brainstem}.
-\emph{Vision Res} \textbf{21}, 513--25 (1981).}
+Musselman, Pupillary light reflex in humans: Evidence for an unbalanced pathway from nasal retina, and for signal cancellation in brainstem.
+\emph{Vision Res} \textbf{21}, 513--25 (1981).
 
-\leavevmode\vadjust pre{\hypertarget{ref-Segala2023}{}}%
-\CSLLeftMargin{5. }%
-\CSLRightInline{F.
-G.
-Segala, \emph{et al.}, \href{https://doi.org/10.7554/elife.87048}{Different rules for binocular combination of luminance flicker in cortical and subcortical pathways}.
-\emph{eLife} \textbf{12} (2023).}
+\leavevmode\hypertarget{ref-Segala2023}{}%
+5. F. G. Segala\emph{et al.}, Different rules for binocular combination of luminance flicker in cortical and subcortical pathways. \emph{eLife} \textbf{12} (2023).
 
-\leavevmode\vadjust pre{\hypertarget{ref-Barrionuevo2014}{}}%
-\CSLLeftMargin{6. }%
-\CSLRightInline{P.
-A.
-Barrionuevo, \emph{et al.}, \href{https://doi.org/10.1167/iovs.13-13252}{Assessing rod, cone, and melanopsin contributions to human pupil flicker responses}.
-\emph{Investigative Ophthalmology \& Visual Science} \textbf{55}, 719--27 (2014).}
+\leavevmode\hypertarget{ref-Barrionuevo2014}{}%
+6. P. A. Barrionuevo\emph{et al.}, Assessing rod, cone, and melanopsin contributions to human pupil flicker responses. \emph{Investigative Ophthalmology \& Visual Science} \textbf{55}, 719--27 (2014).
 
-\leavevmode\vadjust pre{\hypertarget{ref-Barrionuevo2018}{}}%
-\CSLLeftMargin{7. }%
-\CSLRightInline{P.
-A.
-Barrionuevo, J.
-J.
-McAnany, A.
-J.
-Zele, D.
-Cao, \href{https://doi.org/10.3389/fneur.2018.01140}{Non-linearities in the {Rod} and {Cone} {Photoreceptor} {Inputs} to the {Afferent} {Pupil} {Light} {Response}}.
-\emph{Frontiers in Neurology} \textbf{9} (2018).}
+\leavevmode\hypertarget{ref-Barrionuevo2018}{}%
+7. P. A. Barrionuevo, J. J. McAnany, A. J. Zele, D. Cao, Non-linearities in the Rod and Cone Photoreceptor Inputs to the Afferent Pupil Light Response. \emph{Frontiers in Neurology} \textbf{9} (2018).
 
-\leavevmode\vadjust pre{\hypertarget{ref-Dacey2005}{}}%
-\CSLLeftMargin{8. }%
-\CSLRightInline{D.
+\leavevmode\hypertarget{ref-Dacey2005}{}%
+8. D. M. Dacey\emph{et al.}, Melanopsin-expressing ganglion cells in primate retina signal colour and irradiance and project to the LGN. \emph{Nature} \textbf{433}, 749--754 (2005).
+
+\leavevmode\hypertarget{ref-Murray2018}{}%
+9. I. J. Murray, J. Kremers, D. McKeefry, N. R. A. Parry, Paradoxical pupil responses to isolated M-cone increments. \emph{Journal of the Optical Society of America A} \textbf{35}, B66--B71 (2018).
+
+\leavevmode\hypertarget{ref-Spitschan2014}{}%
+10.
 M.
-Dacey, \emph{et al.}, \href{https://doi.org/10.1038/nature03387}{Melanopsin-expressing ganglion cells in primate retina signal colour and irradiance and project to the {LGN}}.
-\emph{Nature} \textbf{433}, 749--754 (2005).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Murray2018}{}}%
-\CSLLeftMargin{9. }%
-\CSLRightInline{I.
-J.
-Murray, J.
-Kremers, D.
-McKeefry, N.
-R.
-A.
-Parry, \href{https://doi.org/10.1364/JOSAA.35.000B66}{Paradoxical pupil responses to isolated {M}-cone increments}.
-\emph{Journal of the Optical Society of America A} \textbf{35}, B66--B71 (2018).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Spitschan2014}{}}%
-\CSLLeftMargin{10. }%
-\CSLRightInline{M.
 Spitschan, S.
@@
 K.
-Aguirre, \href{https://doi.org/10.1073/pnas.1400942111}{Opponent melanopsin and s-cone signals in the human pupillary light response}.
-\emph{Proceedings of the National Academy of Sciences} \textbf{111}, 15568--15572 (2014).}
+Aguirre, Opponent melanopsin and s-cone signals in the human pupillary light response.
+\emph{Proceedings of the National Academy of Sciences} \textbf{111}, 15568--15572 (2014).
 
-\leavevmode\vadjust pre{\hypertarget{ref-Spitschan2019}{}}%
-\CSLLeftMargin{11. }%
-\CSLRightInline{M. Spitschan, C. Cajochen, \href{https://doi.org/10.1111/jpi.12602}{Binocular facilitation in light-mediated melatonin suppression?} \emph{J Pineal Res} \textbf{67}, e12602 (2019).}
+\leavevmode\hypertarget{ref-Spitschan2019}{}%
+11. M. Spitschan, C. Cajochen, Binocular facilitation in light-mediated melatonin suppression? \emph{J Pineal Res} \textbf{67}, e12602 (2019).
 
-\leavevmode\vadjust pre{\hypertarget{ref-Woelders2018}{}}%
-\CSLLeftMargin{12. }%
-\CSLRightInline{T.
-Woelders, \emph{et al.}, \href{https://doi.org/10.1073/pnas.1716281115}{Melanopsin- and {L}-cone--induced pupil constriction is inhibited by {S}- and {M}-cones in humans}.
-\emph{Proceedings of the National Academy of Sciences} \textbf{115}, 792--797 (2018).}
+\leavevmode\hypertarget{ref-Woelders2018}{}%
+12.
+T.
+Woelders\emph{et al.}, Melanopsin- and L-cone--induced pupil constriction is inhibited by S- and M-cones in humans.
+\emph{Proceedings of the National Academy of Sciences} \textbf{115}, 792--797 (2018).
 
-\leavevmode\vadjust pre{\hypertarget{ref-Mathot2018}{}}%
-\CSLLeftMargin{13. }%
-\CSLRightInline{S. Mathôt, \href{https://doi.org/10.5334/joc.18}{Pupillometry: Psychology, physiology, and function}. \emph{J Cogn} \textbf{1}, 16 (2018).}
+\leavevmode\hypertarget{ref-Mathot2018}{}%
+13. S. Mathôt, Pupillometry: Psychology, physiology, and function. \emph{J Cogn} \textbf{1}, 16 (2018).
 
-\leavevmode\vadjust pre{\hypertarget{ref-Markwell2010}{}}%
-\CSLLeftMargin{14. }%
-\CSLRightInline{E.
+\leavevmode\hypertarget{ref-Markwell2010}{}%
+14.
+E.
 L.
@@
 J.
-Zele, \href{https://doi.org/10.1111/j.1444-0938.2010.00479.x}{Intrinsically photosensitive melanopsin retinal ganglion cell contributions to the pupillary light reflex and circadian rhythm}.
-\emph{Clinical and Experimental Optometry} \textbf{93}, 137--149 (2010).}
+Zele, Intrinsically photosensitive melanopsin retinal ganglion cell contributions to the pupillary light reflex and circadian rhythm.
+\emph{Clinical and Experimental Optometry} \textbf{93}, 137--149 (2010).
 
-\leavevmode\vadjust pre{\hypertarget{ref-McDougal2010}{}}%
-\CSLLeftMargin{15. }%
-\CSLRightInline{D.
+\leavevmode\hypertarget{ref-McDougal2010}{}%
+15.
+D.
 H.
@@
 D.
-Gamlin, \href{https://doi.org/10.1016/j.visres.2009.10.012}{The influence of intrinsically-photosensitive retinal ganglion cells on the spectral sensitivity and response dynamics of the human pupillary light reflex}.
-\emph{Vision Research} \textbf{50}, 72--87 (2010).}
+Gamlin, The influence of intrinsically-photosensitive retinal ganglion cells on the spectral sensitivity and response dynamics of the human pupillary light reflex.
+\emph{Vision Research} \textbf{50}, 72--87 (2010).
 
-\leavevmode\vadjust pre{\hypertarget{ref-Provencio2000}{}}%
-\CSLLeftMargin{16. }%
-\CSLRightInline{I.
-Provencio, \emph{et al.}, \href{https://doi.org/10.1523/JNEUROSCI.20-02-00600.2000}{A {Novel} {Human} {Opsin} in the {Inner} {Retina}}.
-\emph{Journal of Neuroscience} \textbf{20}, 600--605 (2000).}
+\leavevmode\hypertarget{ref-Provencio2000}{}%
+16. I. Provencio\emph{et al.}, A Novel Human Opsin in the Inner Retina. \emph{Journal of Neuroscience} \textbf{20}, 600--605 (2000).
 
-\leavevmode\vadjust pre{\hypertarget{ref-Panda2002}{}}%
-\CSLLeftMargin{17. }%
-\CSLRightInline{S.
-Panda, \emph{et al.}, \href{https://doi.org/10.1126/science.1076848}{Melanopsin (Opn4) requirement for normal light-induced circadian phase shifting}.
-\emph{Science} \textbf{298}, 2213--2216 (2002).}
+\leavevmode\hypertarget{ref-Panda2002}{}%
+17. S. Panda\emph{et al.}, Melanopsin (opn4) requirement for normal light-induced circadian phase shifting. \emph{Science} \textbf{298}, 2213--2216 (2002).
 
-\leavevmode\vadjust pre{\hypertarget{ref-Ruby2002}{}}%
-\CSLLeftMargin{18. }%
-\CSLRightInline{N. F. Ruby, \emph{et al.}, \href{https://doi.org/10.1126/science.1076701}{Role of melanopsin in circadian responses to light}. \emph{Science} \textbf{298}, 2211--2213 (2002).}
+\leavevmode\hypertarget{ref-Ruby2002}{}%
+18. N. F. Ruby\emph{et al.}, Role of melanopsin in circadian responses to light. \emph{Science} \textbf{298}, 2211--2213 (2002).
 
-\leavevmode\vadjust pre{\hypertarget{ref-Dacey2003}{}}%
-\CSLLeftMargin{19. }%
-\CSLRightInline{D.
+\leavevmode\hypertarget{ref-Dacey2003}{}%
+19.
+D.
 M.
@@
 D.
-Gamlin, \href{https://doi.org/10.1016/S0896-6273(02)01143-1}{Fireworks in the primate retina: In vitro photodynamics reveals diverse LGN-projecting ganglion cell types}.
-\emph{Neuron} \textbf{37}, 15--27 (2003).}
+Gamlin, Fireworks in the primate retina: In vitro photodynamics reveals diverse lgn-projecting ganglion cell types.
+\emph{Neuron} \textbf{37}, 15--27 (2003).
 
-\leavevmode\vadjust pre{\hypertarget{ref-Lucas2003}{}}%
-\CSLLeftMargin{20. }%
-\CSLRightInline{R.
-J.
-Lucas, \emph{et al.}, \href{https://doi.org/10.1126/science.1077293}{Diminished pupillary light reflex at high irradiances in melanopsin-knockout mice}.
-\emph{Science} \textbf{299}, 245--247 (2003).}
+\leavevmode\hypertarget{ref-Lucas2003}{}%
+20. R. J. Lucas\emph{et al.}, Diminished pupillary light reflex at high irradiances in melanopsin-knockout mice. \emph{Science} \textbf{299}, 245--247 (2003).
 
-\leavevmode\vadjust pre{\hypertarget{ref-Gamlin2007}{}}%
-\CSLLeftMargin{21. }%
-\CSLRightInline{P.
-D.
-R.
-Gamlin, \emph{et al.}, \href{https://doi.org/10.1016/j.visres.2006.12.015}{Human and macaque pupil responses driven by melanopsin-containing retinal ganglion cells}.
-\emph{Vision Research} \textbf{47}, 946--954 (2007).}
+\leavevmode\hypertarget{ref-Gamlin2007}{}%
+21. P. D. R. Gamlin\emph{et al.}, Human and macaque pupil responses driven by melanopsin-containing retinal ganglion cells. \emph{Vision Research} \textbf{47}, 946--954 (2007).
 
-\leavevmode\vadjust pre{\hypertarget{ref-Estevez1982}{}}%
-\CSLLeftMargin{22. }%
-\CSLRightInline{O.
-Estévez, H.
-Spekreijse, \href{https://doi.org/10.1016/0042-6989(82)90104-3}{The "silent substitution" method in visual research}.
-\emph{Vision Research} \textbf{22}, 681--691 (1982).}
+\leavevmode\hypertarget{ref-Estevez1982}{}%
+22. O. Estévez, H. Spekreijse, The "silent substitution" method in visual research. \emph{Vision Research} \textbf{22}, 681--691 (1982).
 
-\leavevmode\vadjust pre{\hypertarget{ref-Shapiro1996}{}}%
-\CSLLeftMargin{23. }%
-\CSLRightInline{A.
+\leavevmode\hypertarget{ref-Shapiro1996}{}%
+23.
+A.
 G.
@@
 C.
-Smith, \href{https://doi.org/10.1364/josaa.13.002319}{Cone{\textendash}rod receptor spaces with illustrations that use {CRT} phosphor and light-emitting-diode spectra}.
-\emph{Journal of the Optical Society of America A} \textbf{13}, 2319 (1996).}
+Smith, Conerod receptor spaces with illustrations that use CRT phosphor and light-emitting-diode spectra.
+\emph{Journal of the Optical Society of America A} \textbf{13}, 2319 (1996).
 
-\leavevmode\vadjust pre{\hypertarget{ref-Spitschan2018}{}}%
-\CSLLeftMargin{24. }%
-\CSLRightInline{M.
-Spitschan, T.
-Woelders, \href{https://doi.org/10.3389/fneur.2018.00941}{The {Method} of {Silent} {Substitution} for {Examining} {Melanopsin} {Contributions} to {Pupil} {Control}}.
-\emph{Frontiers in Neurology} \textbf{9} (2018).}
+\leavevmode\hypertarget{ref-Spitschan2018}{}%
+24. M. Spitschan, T. Woelders, The Method of Silent Substitution for Examining Melanopsin Contributions to Pupil Control. \emph{Frontiers in Neurology} \textbf{9} (2018).
 
-\leavevmode\vadjust pre{\hypertarget{ref-Cao2015}{}}%
-\CSLLeftMargin{25. }%
-\CSLRightInline{D.
+\leavevmode\hypertarget{ref-Cao2015}{}%
+25.
+D.
 Cao, N.
@@
 A.
-Barrionuevo, \href{https://doi.org/10.1167/15.1.27}{A five-primary photostimulator suitable for studying intrinsically photosensitive retinal ganglion cell functions in humans}.
-\emph{Journal of Vision} \textbf{15}, 27 (2015).}
+Barrionuevo, A five-primary photostimulator suitable for studying intrinsically photosensitive retinal ganglion cell functions in humans.
+\emph{Journal of Vision} \textbf{15}, 27 (2015).
 
-\leavevmode\vadjust pre{\hypertarget{ref-Hubel1962}{}}%
-\CSLLeftMargin{26. }%
-\CSLRightInline{D.
-H.
-Hubel, T.
-N.
-Wiesel, \href{https://doi.org/10.1113/jphysiol.1962.sp006837}{Receptive fields, binocular interaction and functional architecture in the cat's visual cortex}.
-\emph{J Physiol} \textbf{160}, 106--54 (1962).}
+\leavevmode\hypertarget{ref-Hubel1962}{}%
+26. D. H. Hubel, T. N. Wiesel, Receptive fields, binocular interaction and functional architecture in the cat's visual cortex. \emph{J Physiol} \textbf{160}, 106--54 (1962).
 
-\leavevmode\vadjust pre{\hypertarget{ref-Moradi2009}{}}%
-\CSLLeftMargin{27. }%
-\CSLRightInline{F. Moradi, D. J. Heeger, \href{https://doi.org/10.1167/9.3.13}{Inter-ocular contrast normalization in human visual cortex}. \emph{J Vis} \textbf{9}, 13.1--22 (2009).}
+\leavevmode\hypertarget{ref-Moradi2009}{}%
+27. F. Moradi, D. J. Heeger, Inter-ocular contrast normalization in human visual cortex. \emph{J Vis} \textbf{9}, 13.1--22 (2009).
 
-\leavevmode\vadjust pre{\hypertarget{ref-Baker2018}{}}%
-\CSLLeftMargin{28. }%
-\CSLRightInline{D.
-H.
-Baker, F.
-A.
-Lygo, T.
-S.
-Meese, M.
-A.
-Georgeson, \href{https://doi.org/10.1037/bul0000163}{Binocular summation revisited: Beyond \(\sqrt{2}\)}.
-\emph{Psychol Bull} \textbf{144}, 1186--1199 (2018).}
+\leavevmode\hypertarget{ref-Baker2018}{}%
+28. D. H. Baker, F. A. Lygo, T. S. Meese, M. A. Georgeson, Binocular summation revisited: Beyond \(\sqrt{2}\). \emph{Psychol Bull} \textbf{144}, 1186--1199 (2018).
 
-\leavevmode\vadjust pre{\hypertarget{ref-Campbell1965}{}}%
-\CSLLeftMargin{29. }%
-\CSLRightInline{F. W. Campbell, D. G. Green, \href{https://doi.org/10.1038/208191a0}{Monocular versus binocular visual acuity}. \emph{Nature} \textbf{208}, 191--2 (1965).}
+\leavevmode\hypertarget{ref-Campbell1965}{}%
+29. F. W. Campbell, D. G. Green, Monocular versus binocular visual acuity. \emph{Nature} \textbf{208}, 191--2 (1965).
 
-\leavevmode\vadjust pre{\hypertarget{ref-Legge1984}{}}%
-\CSLLeftMargin{30. }%
-\CSLRightInline{G. E. Legge, \href{https://doi.org/10.1016/0042-6989(84)90064-6}{Binocular contrast summation--II. Quadratic summation}. \emph{Vision Res} \textbf{24}, 385--94 (1984).}
+\leavevmode\hypertarget{ref-Legge1984}{}%
+30. G. E. Legge, Binocular contrast summation--ii. Quadratic summation. \emph{Vision Res} \textbf{24}, 385--94 (1984).
 
-\leavevmode\vadjust pre{\hypertarget{ref-Baker2007}{}}%
-\CSLLeftMargin{31. }%
-\CSLRightInline{D.
-H.
-Baker, T.
-S.
-Meese, M.
-A.
-Georgeson, \href{https://doi.org/10.1163/156856807781503622}{Binocular interaction: Contrast matching and contrast discrimination are predicted by the same model}.
-\emph{Spat Vis} \textbf{20}, 397--413 (2007).}
+\leavevmode\hypertarget{ref-Baker2007}{}%
+31. D. H. Baker, T. S. Meese, M. A. Georgeson, Binocular interaction: Contrast matching and contrast discrimination are predicted by the same model. \emph{Spat Vis} \textbf{20}, 397--413 (2007).
 
-\leavevmode\vadjust pre{\hypertarget{ref-Ding2006}{}}%
-\CSLLeftMargin{32. }%
-\CSLRightInline{J. Ding, G. Sperling, \href{https://doi.org/10.1073/pnas.0509629103}{A gain-control theory of binocular combination}. \emph{Proc Natl Acad Sci U S A} \textbf{103}, 1141--6 (2006).}
+\leavevmode\hypertarget{ref-Ding2006}{}%
+32. J. Ding, G. Sperling, A gain-control theory of binocular combination. \emph{Proc Natl Acad Sci U S A} \textbf{103}, 1141--6 (2006).
 
-\leavevmode\vadjust pre{\hypertarget{ref-Meese2006}{}}%
-\CSLLeftMargin{33. }%
-\CSLRightInline{T.
-S.
-Meese, M.
-A.
-Georgeson, D.
-H.
-Baker, \href{https://doi.org/10.1167/6.11.7}{Binocular contrast vision at and above threshold}.
-\emph{Journal of Vision} \textbf{6}, 1224--43 (2006).}
+\leavevmode\hypertarget{ref-Meese2006}{}%
+33. T. S. Meese, M. A. Georgeson, D. H. Baker, Binocular contrast vision at and above threshold. \emph{Journal of Vision} \textbf{6}, 1224--43 (2006).
 
-\leavevmode\vadjust pre{\hypertarget{ref-Kingdom2015}{}}%
-\CSLLeftMargin{34. }%
-\CSLRightInline{F.
-A.
-A.
-Kingdom, L.
-Libenson, \href{https://doi.org/10.1167/15.5.2}{Dichoptic color saturation mixture: Binocular luminance contrast promotes perceptual averaging}.
-\emph{J Vis} \textbf{15}, 2 (2015).}
+\leavevmode\hypertarget{ref-Kingdom2015}{}%
+34. F. A. A. Kingdom, L. Libenson, Dichoptic color saturation mixture: Binocular luminance contrast promotes perceptual averaging. \emph{J Vis} \textbf{15}, 2 (2015).
 
-\leavevmode\vadjust pre{\hypertarget{ref-Busse2009}{}}%
-\CSLLeftMargin{35. }%
-\CSLRightInline{L.
-Busse, A.
-R.
-Wade, M.
-Carandini, \href{https://doi.org/10.1016/j.neuron.2009.11.004}{Representation of concurrent stimuli by population activity in visual cortex}.
-\emph{Neuron} \textbf{64}, 931--42 (2009).}
+\leavevmode\hypertarget{ref-Busse2009}{}%
+35. L. Busse, A. R. Wade, M. Carandini, Representation of concurrent stimuli by population activity in visual cortex. \emph{Neuron} \textbf{64}, 931--42 (2009).
 
-\leavevmode\vadjust pre{\hypertarget{ref-Baker2024}{}}%
-\CSLLeftMargin{36. }%
-\CSLRightInline{D.
-H.
-Baker, \emph{et al.}, \href{https://doi.org/10.31234/osf.io/atsfh}{Binocular integration of chromatic and luminance signals}.
-\emph{Journal of Vision} \textbf{Under review} (2024).}
+\leavevmode\hypertarget{ref-Baker2024}{}%
+36. D. H. Baker\emph{et al.}, Binocular integration of chromatic and luminance signals. \emph{Journal of Vision} \textbf{Under review} (2024).
 
-\leavevmode\vadjust pre{\hypertarget{ref-Baker2017}{}}%
-\CSLLeftMargin{37. }%
-\CSLRightInline{D.
-H.
-Baker, A.
-R.
-Wade, \href{https://doi.org/10.1093/cercor/bhw395}{Evidence for an optimal algorithm underlying signal combination in human visual cortex}.
-\emph{Cereb Cortex} \textbf{27}, 254--264 (2017).}
+\leavevmode\hypertarget{ref-Baker2017}{}%
+37. D. H. Baker, A. R. Wade, Evidence for an optimal algorithm underlying signal combination in human visual cortex. \emph{Cereb Cortex} \textbf{27}, 254--264 (2017).
 
-\leavevmode\vadjust pre{\hypertarget{ref-Kaestner2019}{}}%
-\CSLLeftMargin{38. }%
-\CSLRightInline{M.
-Kaestner, \emph{et al.}, \href{https://doi.org/10.1073/pnas.1817202116}{Asymmetries between achromatic and chromatic extraction of 3D motion signals}.
-\emph{Proc Natl Acad Sci U S A} \textbf{116}, 13631--13640 (2019).}
+\leavevmode\hypertarget{ref-Kaestner2019}{}%
+38. M. Kaestner\emph{et al.}, Asymmetries between achromatic and chromatic extraction of 3D motion signals. \emph{Proc Natl Acad Sci U S A} \textbf{116}, 13631--13640 (2019).
 
-\leavevmode\vadjust pre{\hypertarget{ref-Martin2022}{}}%
-\CSLLeftMargin{39. }%
-\CSLRightInline{J.
+\leavevmode\hypertarget{ref-Martin2022}{}%
+39.
+J.
 T.
@@
 Bulte, M.
-Spitschan, \href{https://doi.org/10.3758/s13428-021-01759-3}{PyPlr: A versatile, integrated system of hardware and software for researching the human pupillary light reflex}.
-\emph{Behavior Research Methods} \textbf{54}, 2720--2739 (2022).}
+Spitschan, PyPlr: A versatile, integrated system of hardware and software for researching the human pupillary light reflex.
+\emph{Behavior Research Methods} \textbf{54}, 2720--2739 (2022).
 
-\leavevmode\vadjust pre{\hypertarget{ref-Martin2023}{}}%
-\CSLLeftMargin{40. }%
-\CSLRightInline{J.
+\leavevmode\hypertarget{ref-Martin2023}{}%
+40.
+J.
 T.
@@
 Wade, M.
-Spitschan, \href{https://doi.org/10.1167/jov.23.7.10}{PySilSub: An open-source python toolbox for implementing the method of silent substitution in vision and nonvisual photoreception research}.
-\emph{Journal of Vision} \textbf{23}, 10 (2023).}
+Spitschan, PySilSub: An open-source python toolbox for implementing the method of silent substitution in vision and nonvisual photoreception research.
+\emph{Journal of Vision} \textbf{23}, 10 (2023).
 
-\leavevmode\vadjust pre{\hypertarget{ref-Stockman2000}{}}%
-\CSLLeftMargin{41. }%
-\CSLRightInline{A.
+\leavevmode\hypertarget{ref-Stockman2000}{}%
+41.
+A.
 Stockman, L.
 T.
-Sharpe, \href{https://doi.org/10.1016/s0042-6989(00)00021-3}{The spectral sensitivities of the middle- and long-wavelength-sensitive cones derived from measurements in observers of known genotype}.
-\emph{Vision Res} \textbf{40}, 1711--37 (2000).}
+Sharpe, The spectral sensitivities of the middle- and long-wavelength-sensitive cones derived from measurements in observers of known genotype.
+\emph{Vision Res} \textbf{40}, 1711--37 (2000).
 
-\leavevmode\vadjust pre{\hypertarget{ref-Barrionuevo2016}{}}%
-\CSLLeftMargin{42. }%
-\CSLRightInline{P.
+\leavevmode\hypertarget{ref-Barrionuevo2016}{}%
+42. P. A. Barrionuevo, D. Cao, Luminance and chromatic signals interact differently with melanopsin activation to control the pupil light response. \emph{Journal of Vision} \textbf{16(11)}, 29 (2016).
+
+\leavevmode\hypertarget{ref-Spitschan2015}{}%
+43. M. Spitschan, G. K. Aguirre, D. H. Brainard, Selective stimulation of penumbral cones reveals perception in the shadow of retinal blood vessels. \emph{PLoS One} \textbf{10}, e0124328 (2015).
+
+\leavevmode\hypertarget{ref-Zele2018}{}%
+44.
 A.
-Barrionuevo, D.
-Cao, \href{https://doi.org/10.1167/16.11.29}{Luminance and chromatic signals interact differently with melanopsin activation to control the pupil light response}.
-\emph{Journal of Vision} \textbf{16(11)}, 29 (2016).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Spitschan2015}{}}%
-\CSLLeftMargin{43. }%
-\CSLRightInline{M.
-Spitschan, G.
-K.
-Aguirre, D.
-H.
-Brainard, \href{https://doi.org/10.1371/journal.pone.0124328}{Selective stimulation of penumbral cones reveals perception in the shadow of retinal blood vessels}.
-\emph{PLoS One} \textbf{10}, e0124328 (2015).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Zele2018}{}}%
-\CSLLeftMargin{44. }%
-\CSLRightInline{A.
 J.
@@
 Maynard, D.
-Cao, \href{https://doi.org/10.1038/s41598-018-22197-w}{Melanopsin photoreception contributes to human visual detection, temporal and colour processing}.
-\emph{Scientific Reports} \textbf{8} (2018).}
+Cao, Melanopsin photoreception contributes to human visual detection, temporal and colour processing.
+\emph{Scientific Reports} \textbf{8} (2018).
 
-\leavevmode\vadjust pre{\hypertarget{ref-Kassner2014}{}}%
-\CSLLeftMargin{45. }%
-\CSLRightInline{M.
+\leavevmode\hypertarget{ref-Kassner2014}{}%
+45.
+M.
 Kassner, W.
@@
 Bulling, Pupil: An open source platform for pervasive eye tracking and mobile gaze-based interaction.
-in \emph{Proceedings of the 2014 {ACM} International Joint Conference on Pervasive and Ubiquitous Computing: Adjunct Publication}, ({ACM}, 2014) https:/doi.org/\href{https://doi.org/10.1145/2638728.2641695}{10.1145/2638728.2641695}.}
+in \emph{Proceedings of the 2014 ACM International Joint Conference on Pervasive and Ubiquitous Computing: Adjunct Publication}, (ACM, 2014) \url{https:/doi.org/10.1145/2638728.2641695}.
 
-\leavevmode\vadjust pre{\hypertarget{ref-Norcia2015}{}}%
-\CSLLeftMargin{46. }%
-\CSLRightInline{A.
-M.
-Norcia, L.
-G.
-Appelbaum, J.
-M.
-Ales, B.
-R.
-Cottereau, B.
-Rossion, \href{https://doi.org/10.1167/15.6.4}{The steady-state visual evoked potential in vision research: A review}.
-\emph{Journal of Vision} \textbf{15(6)}, 4 (2015).}
+\leavevmode\hypertarget{ref-Norcia2015}{}%
+46. A. M. Norcia, L. G. Appelbaum, J. M. Ales, B. R. Cottereau, B. Rossion, The steady-state visual evoked potential in vision research: A review. \emph{Journal of Vision} \textbf{15(6)}, 4 (2015).
 
-\leavevmode\vadjust pre{\hypertarget{ref-Zele2019}{}}%
-\CSLLeftMargin{47. }%
-\CSLRightInline{A.
-J.
-Zele, P.
-Adhikari, D.
-Cao, B.
-Feigl, \href{https://doi.org/10.1016/j.visres.2019.04.009}{Melanopsin driven enhancement of cone-mediated visual processing}.
-\emph{Vision Res} \textbf{160}, 72--81 (2019).}
+\leavevmode\hypertarget{ref-Zele2019}{}%
+47. A. J. Zele, P. Adhikari, D. Cao, B. Feigl, Melanopsin driven enhancement of cone-mediated visual processing. \emph{Vision Res} \textbf{160}, 72--81 (2019).
 
-\leavevmode\vadjust pre{\hypertarget{ref-Baker2020}{}}%
-\CSLLeftMargin{48. }%
-\CSLRightInline{D.
-H.
-Baker, \emph{et al.}, \href{https://doi.org/10.1038/s41598-020-60602-5}{Binaural summation of amplitude modulation involves weak interaural suppression}.
-\emph{Sci Rep} \textbf{10}, 3560 (2020).}
+\leavevmode\hypertarget{ref-Baker2020}{}%
+48. D. H. Baker\emph{et al.}, Binaural summation of amplitude modulation involves weak interaural suppression. \emph{Sci Rep} \textbf{10}, 3560 (2020).
 
-\leavevmode\vadjust pre{\hypertarget{ref-Carroll2002}{}}%
-\CSLLeftMargin{49. }%
-\CSLRightInline{J.
-Carroll, J.
-Neitz, M.
-Neitz, \href{https://doi.org/10.1167/2.8.1}{Estimates of {L}:{M} cone ratio from {ERG} flicker photometry and genetics}.
-\emph{Journal of Vision} \textbf{2}, 1 (2002).}
+\leavevmode\hypertarget{ref-Carroll2002}{}%
+49. J. Carroll, J. Neitz, M. Neitz, Estimates of L:M cone ratio from ERG flicker photometry and genetics. \emph{Journal of Vision} \textbf{2}, 1 (2002).
 
-\leavevmode\vadjust pre{\hypertarget{ref-Hofer2005}{}}%
-\CSLLeftMargin{50. }%
-\CSLRightInline{H.
-Hofer, J.
-Carroll, J.
-Neitz, M.
-Neitz, D.
-R.
-Williams, \href{https://doi.org/10.1523/jneurosci.2414-05.2005}{Organization of the human trichromatic cone mosaic}.
-\emph{The Journal of Neuroscience} \textbf{25}, 9669--9679 (2005).}
+\leavevmode\hypertarget{ref-Hofer2005}{}%
+50. H. Hofer, J. Carroll, J. Neitz, M. Neitz, D. R. Williams, Organization of the human trichromatic cone mosaic. \emph{The Journal of Neuroscience} \textbf{25}, 9669--9679 (2005).
 
-\leavevmode\vadjust pre{\hypertarget{ref-Baker2021}{}}%
-\CSLLeftMargin{51. }%
-\CSLRightInline{D. H. Baker, \href{https://doi.org/10.51628/001c.27680}{Statistical analysis of periodic data in neuroscience}. \emph{Neurons, Behavior, Data analysis, and Theory} \textbf{5} (2021).}
+\leavevmode\hypertarget{ref-Baker2021}{}%
+51. D. H. Baker, Statistical analysis of periodic data in neuroscience. \emph{Neurons, Behavior, Data analysis, and Theory} \textbf{5} (2021).
 
-\leavevmode\vadjust pre{\hypertarget{ref-Carpenter2017}{}}%
-\CSLLeftMargin{52. }%
-\CSLRightInline{B. Carpenter, \emph{et al.}, \href{https://doi.org/10.18637/jss.v076.i01}{Stan: A probabilistic programming language}. \emph{J Stat Softw} \textbf{76} (2017).}
-
-\end{CSLReferences}
+\leavevmode\hypertarget{ref-Carpenter2017}{}%
+52. B. Carpenter\emph{et al.}, Stan: A probabilistic programming language. \emph{J Stat Softw} \textbf{76} (2017).
 

### 2024-06-06 manuscript.Rmd
Added significance statement and started doing some formatting changes to the title page.

@@
 
-$^1$Department of Psychology, University of York, Heslington, York, United Kingdom.
-
-$^2$School of Psychology and Vision Sciences, University of Leicester, Leicester, United Kingdom.
-
-$^3$School of Philosophy, Psychology and Language Sciences, University of Edinburgh, Edinburgh, United Kingdom.
-
-$^4$York Biomedical Research Institute, University of York, Heslington, York, United Kingdom.
+$^1$Department of Psychology, University of York, Heslington, York, YO10 5DD, United Kingdom.
+
+$^2$School of Psychology and Vision Sciences, University of Leicester, Leicester, LE1 7RH, United Kingdom.
+
+$^3$School of Philosophy, Psychology and Language Sciences, University of Edinburgh, Edinburgh, EH8 9AD, United Kingdom.
+
+$^4$York Biomedical Research Institute, University of York, Heslington, York, YO10 5NG, United Kingdom.
 
@@
 
+The diameter of the pupil depends on the level of ambient light and is controlled by distinct retinal photoreceptor classes (cones, rods and intrinsically photosensitive retinal ganglion cells).
+The computational processes behind binocular integration within the subcortical pathways controlling pupil dimension have been investigated and have been shown to occur independently of visual cortex.
+We investigated binocular combination within the different photoreceptor pathways using silent substitution.
+We found different patterns of binocular combination in each pathway and also differences in the phase of the pupil response.
+The results are consistent with a computational model of binocular signal combination, where the weight of interocular suppression differs across pathways, and demonstrate the algorithm governing binocular combination in the autonomic nervous system.
+
 # Introduction
@@
 
-```{r phaseplots, fig.cap="Pupil phase plots at the first and second harmonic frequencies for the luminance, melanopsin, L-M pathway and the S-(L+M) pathway conditions Panel (a) shows the pupil response at the first harmonic frequency during binocular stimulation.
+```{r phaseplots, fig.cap="Pupil phase plots at the first and second harmonic frequencies for the luminance, melanopsin, L-M pathway and the S-(L+M) pathway conditions.
+Panel (a) shows the pupil response at the first harmonic frequency during binocular stimulation.
 Panel (b) shows the pupil response at the second harmonic frequency during binocular stimulation.

### 2024-06-06 manuscript.tex
Added significance statement and started doing some formatting changes to the title page.

@@
 
-\(^1\)Department of Psychology, University of York, Heslington, York, United Kingdom.
+\(^1\)Department of Psychology, University of York, Heslington, York, YO10 5DD, United Kingdom.
 
-\(^2\)School of Psychology and Vision Sciences, University of Leicester, Leicester, United Kingdom.
+\(^2\)School of Psychology and Vision Sciences, University of Leicester, Leicester, LE1 7RH, United Kingdom.
 
-\(^3\)School of Philosophy, Psychology and Language Sciences, University of Edinburgh, Edinburgh, United Kingdom.
+\(^3\)School of Philosophy, Psychology and Language Sciences, University of Edinburgh, Edinburgh, EH8 9AD, United Kingdom.
 
-\(^4\)York Biomedical Research Institute, University of York, Heslington, York, United Kingdom.
+\(^4\)York Biomedical Research Institute, University of York, Heslington, York, YO10 5NG, United Kingdom.
 
@@
 This work demonstrates for the first time the algorithm governing binocular combination in the autonomic nervous system.
+
+\hypertarget{significance-statement-120-words}{%
+\section{Significance statement (120 words)}\label{significance-statement-120-words}}
+
+The diameter of the pupil depends on the level of ambient light and is controlled by distinct retinal photoreceptor classes (cones, rods and intrinsically photosensitive retinal ganglion cells).
+The computational processes behind binocular integration within the subcortical pathways controlling pupil dimension have been investigated and have been shown to occur independently of visual cortex.
+We investigated binocular combination within the different photoreceptor pathways using silent substitution.
+We found different patterns of binocular combination in each pathway and also differences in the phase of the pupil response.
+The results are consistent with a computational model of binocular signal combination, where the weight of interocular suppression differs across pathways, and demonstrate the algorithm governing binocular combination in the autonomic nervous system.
 
@@
 
-\caption{Pupil phase plots at the first and second harmonic frequencies for the luminance, melanopsin, L-M pathway and the S-(L+M) pathway conditions Panel (a) shows the pupil response at the first harmonic frequency during binocular stimulation.
+\caption{Pupil phase plots at the first and second harmonic frequencies for the luminance, melanopsin, L-M pathway and the S-(L+M) pathway conditions.
+Panel (a) shows the pupil response at the first harmonic frequency during binocular stimulation.
 Panel (b) shows the pupil response at the second harmonic frequency during binocular stimulation.

### 2024-06-07 manuscript.Rmd
Edited significance statement

@@
 
-The diameter of the pupil depends on the level of ambient light and is controlled by distinct retinal photoreceptor classes (cones, rods and intrinsically photosensitive retinal ganglion cells).
-The computational processes behind binocular integration within the subcortical pathways controlling pupil dimension have been investigated and have been shown to occur independently of visual cortex.
-We investigated binocular combination within the different photoreceptor pathways using silent substitution.
-We found different patterns of binocular combination in each pathway and also differences in the phase of the pupil response.
-The results are consistent with a computational model of binocular signal combination, where the weight of interocular suppression differs across pathways, and demonstrate the algorithm governing binocular combination in the autonomic nervous system.
+Pupil diameters are determined by a network of subcortical nuclei that must combine incoming light levels across the two eyes, independently of cortical visual areas.
+We investigated the algorithmic properties of this binocular combination process for the first time.
+Using silent subsitution, we targeted different post-retinal pathways (luminance, L-M cones, S-cones, and melanopsin) with flickering stimuli generated by a novel binocular multi-primary system.
+We found different patterns of binocular combination across pathways, and also differences in the phase of the pupil response.
+The results were well described by a computational model of binocular signal combination, in which the weight of suppression between the eyes differed across pathways.
+This elucidates the algorithm governing binocular combination in the autonomic nervous system.
 

### 2024-06-07 manuscript.Rmd
Removed word limit reminders
Added preprint server information, classification and keywords

@@
 Address for correspondence: Federico G. Segala, [federico.segala\@york.ac.uk](federico.segala@york.ac.uk)
+
+Preprint server: a preprint has been deposited on BioRxiv (https://doi.org/10.1101/2024.06.04.597314) with a no reuse/adaptation without permission license
+
+Classification: Biological Sciences - Psychological and Cognitive Sciences
+
+Keywords: Pupil diameter, Pupillometry, Silent substitution, Melanopsin, Binocular combination, Computational modelling
 
@@
 
-# Abstract (250 words)
+# Abstract
 
@@
 
-# Significance statement (120 words)
+# Significance statement
 

### 2024-06-07 manuscript.tex
Added preprint server information, classification and keywords

@@
 
-\hypertarget{abstract-250-words}{%
-\section{Abstract (250 words)}\label{abstract-250-words}}
+Preprint server: a preprint has been deposited on BioRxiv (\url{https://doi.org/10.1101/2024.06.04.597314}) with a no reuse/adaptation without permission license
+
+Classification: Biological Sciences - Psychological and Cognitive Sciences
+
+Keywords: Pupil diameter, Pupillometry, Silent substitution, Melanopsin, Binocular combination, Computational modelling
+
+\hypertarget{abstract}{%
+\section{Abstract}\label{abstract}}
 
@@
 
-\hypertarget{significance-statement-120-words}{%
-\section{Significance statement (120 words)}\label{significance-statement-120-words}}
+\hypertarget{significance-statement}{%
+\section{Significance statement}\label{significance-statement}}
 
-The diameter of the pupil depends on the level of ambient light and is controlled by distinct retinal photoreceptor classes (cones, rods and intrinsically photosensitive retinal ganglion cells).
-The computational processes behind binocular integration within the subcortical pathways controlling pupil dimension have been investigated and have been shown to occur independently of visual cortex.
-We investigated binocular combination within the different photoreceptor pathways using silent substitution.
-We found different patterns of binocular combination in each pathway and also differences in the phase of the pupil response.
-The results are consistent with a computational model of binocular signal combination, where the weight of interocular suppression differs across pathways, and demonstrate the algorithm governing binocular combination in the autonomic nervous system.
+Pupil diameters are determined by a network of subcortical nuclei that must combine incoming light levels across the two eyes, independently of cortical visual areas.
+We investigated the algorithmic properties of this binocular combination process for the first time.
+Using silent subsitution, we targeted different post-retinal pathways (luminance, L-M cones, S-cones, and melanopsin) with flickering stimuli generated by a novel binocular multi-primary system.
+We found different patterns of binocular combination across pathways, and also differences in the phase of the pupil response.
+The results were well described by a computational model of binocular signal combination, in which the weight of suppression between the eyes differed across pathways.
+This elucidates the algorithm governing binocular combination in the autonomic nervous system.
 

### 2024-07-03 manuscript.Rmd
Small edits
edits

--- 2024-06-07 manuscript.Rmd
@@
 author: |
- | Federico G. Segala$^1$, Aurelio Bruno$^{1,2}$, Joel T. Martin$^{1,3}$,
+ | Federico G. Segala$^1$*, Aurelio Bruno$^{1,2}$, Joel T. Martin$^{1,3}$,
  | Anisa Y. Morsi$^1$, Alex R. Wade$^{1,4}$ & Daniel H. Baker$^{1,4}$
@@
 linkcolor: black
-csl: pnas.csl
+csl: nature-communications.csl
 header-includes:
   \usepackage{caption}
-  \usepackage{lineno} \linenumbers
 ---
@@
 
-Address for correspondence: Federico G. Segala, [federico.segala\@york.ac.uk](federico.segala@york.ac.uk)
+*Corresponding author
 
@@
 
-# Significance statement (120 words)
-
-Pupil diameters are determined by a network of subcortical nuclei that must combine incoming light levels across the two eyes, independently of cortical visual areas.
-We investigated the algorithmic properties of this binocular combination process for the first time.
-Using silent subsitution, we targeted different post-retinal pathways (luminance, L-M cones, S-cones, and melanopsin) with flickering stimuli generated by a novel binocular multi-primary system.
-We found different patterns of binocular combination across pathways, and also differences in the phase of the pupil response.
-The results were well described by a computational model of binocular signal combination, in which the weight of suppression between the eyes differed across pathways.
-This elucidates the algorithm governing binocular combination in the autonomic nervous system.
-
 # Introduction
@@
 The anatomical pathway from the retina to the subcortical nuclei controlling the pupillary light response (PLR) is well established: it includes the Pretectal Olivary nucleus (PON), the Superior Cervical ganglion and the Edinger-Westphal nucleus, which project to the iris sphincter muscles that directly control the pupil size [@McDougal2008; @McDougal2015; @Wang2015].
-Evidence of a binocular component to the PLR is shown by the existence of a consensual response of the pupil [the stimulation of one eye will cause constriction of the other eye\; @Wyatt1981].
+Evidence of a binocular component to the PLR is shown by the existence of a consensual response of the pupil (the stimulation of one eye will cause constriction of the other eye)[@Wyatt1981].
 The anatomical segregation of the subcortical pathway from the rest of the brain means that this binocular combination of signals must occur independently of the cortical processes of binocular integration required for visual perception.
@@
 They express the photopigment melanopsin, and are involved in the regulation of the circadian rhythm [@Provencio2000; @Panda2002; @Ruby2002], forming a major input to the PON [@Dacey2003].
-The first direct evidence of the involvement of the ipRGCs in the PLR was shown in melanopsin knockout rats by @Lucas2003, resulting in the loss of the intrinsic photosensitivity of the cells and a reduced pupil constriction.
+The first direct evidence of the involvement of the ipRGCs in the PLR was shown in melanopsin knockout rats by Lucas et al.
+[@Lucas2003], resulting in the loss of the intrinsic photosensitivity of the cells and a reduced pupil constriction.
 This same behaviour was later also observed in primates and humans [@Gamlin2007], where it was demonstrated that the PLR continues during light presentation even when cone and rod signalling is blocked, indicating the primary role of the ipRGCs in maintaining pupil constriction over a prolonged time.
@@
 Our recent psychophysical work [@Baker2024] has looked at binocular interactions in the L-M and S-cone pathways, and compared these to the luminance pathway.
-Using a contrast discrimination paradigm with spatial modulations of luminance and colour, @Baker2024 found equally strong interocular suppression in all three pathways.
+Using a contrast discrimination paradigm with spatial modulations of luminance and colour, we found equally strong interocular suppression in all three pathways.
 This is rather different from our pupillometry results here, which demonstrate weaker suppression in the luminance and S-cone pathways than in the L-M pathway (see Figure \@ref(fig:FirstHarmonicPlots)).
-However, the current experiments involve temporal modulations, which are quite distinct from the spatial modulations used in @Baker2024.
+However, the current experiments involve temporal modulations, which are quite distinct from the spatial modulations used in our previous work [@Baker2024].
 Our other recent work [@Segala2023] has shown that temporal luminance modulations involve much weaker interocular suppression in the cortical response than do spatial luminance modulations [@Baker2017].
@@
 
-# Materials and methods
+# Methods
 
@@
 The outputs of the two light engines (see Figure \@ref(fig:spectraplots)b,c) were calibrated using an Ocean Optics Jaz spectroradiometer, which was wavelength-calibrated to an Argon lamp and intensity calibrated using a NIST-traceable light source.
-We used the @Stockman2000 10-degree cone fundamentals, and estimates of melanopsin absorbance spectra from CIE S 026 [discussed in @Martin2023] to calculate $\alpha$-opic irradiance.
+We used the Stockman and Sharpe 10-degree cone fundamentals [@Stockman2000], and estimates of melanopsin absorbance spectra from CIE S 026 [discussed in @Martin2023] to calculate $\alpha$-opic irradiance.
 
@@
 A schematic of the stimulation system is shown in Figure \@ref(fig:spectraplots)a.
-Pupillometry data were collected using a binocular Pupil Core eye-tracker headset [Pupil Labs GmbH, Berlin, Germany, @Kassner2014] running at 120 Hz, and the signals were recorded with the Pupil Capture software.
+Pupillometry data were collected using a binocular Pupil Core eye-tracker headset (Pupil Labs GmbH, Berlin, Germany) [@Kassner2014] running at 120 Hz, and the signals were recorded with the Pupil Capture software.
 
@@
 To describe our data, we used the same model described in our previous study [@Segala2023].
-The model has the same general form as the first stage of the contrast gain control model proposed by @Meese2006, but omits the second stage.
+The model has the same general form as the first stage of the contrast gain control model proposed by Meese, Georgeson and Baker [@Meese2006], but omits the second stage.
 For the previous model that we used [@Segala2023], the exponent of the numerator and denominator had fixed values of 2 and (implicitly) 1.
@@
 
-# Acknowledgements and funding sources
+# References
+
+<div id="refs"></div>
+
+# Acknowledgements
 
@@
 
-# References
-
-<div id='refs'> </div>
+# Author contributions
+
+D.H.B.
+and A.R.W.
+conceived the project D.H.B, A.R.W., and A.B.
+supervised the project.
+F.G.S., J.T.M., A.R.W., and D.H.B.
+designed the experiments.
+F.G.S., J.T.M., and A.Y.M.
+performed the experiments and collected the data.
+F.G.S and D.H.B.
+analysed the data and implemented the computational model.
+F.G.S.
+and D.H.B.
+wrote the manuscript with input from all authors.
+A.B., J.T.M., A.Y.M., and A.R.W.
+provided feedback on the manuscript.
+
+# Competing interests
+
+The authors declare no competing interests.
+
+# Materials and Correspondence
+
+Correspondence and material requests should be addressed to [Federico G. Segala](federico.segala@york.ac.uk).

### 2024-07-03 manuscript.tex
Small edits
Add files via upload

--- 2024-06-06 manuscript.tex
@@
 \setcounter{secnumdepth}{5}
-\usepackage{caption} \usepackage{lineno} \linenumbers
+\usepackage{caption}
 \usepackage{booktabs}
@@
 \title{Binocular combination in the autonomic nervous system}
-\author{Federico G. Segala\(^1\), Aurelio Bruno\(^{1,2}\), Joel T. Martin\(^{1,3}\),\\
+\author{Federico G. Segala\(^1\)*, Aurelio Bruno\(^{1,2}\), Joel T. Martin\(^{1,3}\),\\
 Anisa Y. Morsi\(^1\), Alex R. Wade\(^{1,4}\) \& Daniel H. Baker\(^{1,4}\)}
@@
 
-Address for correspondence: Federico G. Segala, \url{federico.segala@york.ac.uk}
+*Corresponding author
 
-\hypertarget{abstract-250-words}{%
-\section{Abstract (250 words)}\label{abstract-250-words}}
+\hypertarget{abstract}{%
+\section{Abstract}\label{abstract}}
 
@@
 
-\hypertarget{significance-statement-120-words}{%
-\section{Significance statement (120 words)}\label{significance-statement-120-words}}
-
-The diameter of the pupil depends on the level of ambient light and is controlled by distinct retinal photoreceptor classes (cones, rods and intrinsically photosensitive retinal ganglion cells).
-The computational processes behind binocular integration within the subcortical pathways controlling pupil dimension have been investigated and have been shown to occur independently of visual cortex.
-We investigated binocular combination within the different photoreceptor pathways using silent substitution.
-We found different patterns of binocular combination in each pathway and also differences in the phase of the pupil response.
-The results are consistent with a computational model of binocular signal combination, where the weight of interocular suppression differs across pathways, and demonstrate the algorithm governing binocular combination in the autonomic nervous system.
-
 \hypertarget{introduction}{%
@@
 
-The autonomic nervous system regulates many involuntary bodily processes, including the constriction and dilation of the pupils in response to light (\protect\hyperlink{ref-McDougal2015}{1}).
-The anatomical pathway from the retina to the subcortical nuclei controlling the pupillary light response (PLR) is well established: it includes the Pretectal Olivary nucleus (PON), the Superior Cervical ganglion and the Edinger-Westphal nucleus, which project to the iris sphincter muscles that directly control the pupil size (\protect\hyperlink{ref-McDougal2015}{1}--\protect\hyperlink{ref-Wang2015}{3}).
-Evidence of a binocular component to the PLR is shown by the existence of a consensual response of the pupil (\protect\hyperlink{ref-Wyatt1981}{4}).
+The autonomic nervous system regulates many involuntary bodily processes, including the constriction and dilation of the pupils in response to light.\textsuperscript{\protect\hyperlink{ref-McDougal2015}{1}} The anatomical pathway from the retina to the subcortical nuclei controlling the pupillary light response (PLR) is well established: it includes the Pretectal Olivary nucleus (PON), the Superior Cervical ganglion and the Edinger-Westphal nucleus, which project to the iris sphincter muscles that directly control the pupil size.\textsuperscript{\protect\hyperlink{ref-McDougal2015}{1}--\protect\hyperlink{ref-Wang2015}{3}} Evidence of a binocular component to the PLR is shown by the existence of a consensual response of the pupil (the stimulation of one eye will cause constriction of the other eye)\textsuperscript{\protect\hyperlink{ref-Wyatt1981}{4}}.
 The anatomical segregation of the subcortical pathway from the rest of the brain means that this binocular combination of signals must occur independently of the cortical processes of binocular integration required for visual perception.
-Our recent work (\protect\hyperlink{ref-Segala2023}{5}) has shown that the algorithm underlying binocular combination of light in the pupil pathway differs from that in the cortex.
+Our recent work\textsuperscript{\protect\hyperlink{ref-Segala2023}{5}} has shown that the algorithm underlying binocular combination of light in the pupil pathway differs from that in the cortex.
 Here we extend this paradigm to compare binocular combination in different photoreceptor pathways that feed into the autonomic nervous system.
 
-Different classes of retinal photoreceptors, including cones, rods and melanopsin-containing intrinsically photosensitive retinal ganglion cells (ipRGCs), are directly involved in controlling and maintaining the size of the pupils (\protect\hyperlink{ref-Barrionuevo2014}{6}--\protect\hyperlink{ref-Woelders2018}{12}).
-The cones have been shown to drive the initial rapid constriction of the pupils (\protect\hyperlink{ref-Mathot2018}{13}), while the slower and longer activation of the ipRGCs shows their role in maintaining the constriction over a prolonged period of time and in regulating the post-illumination pupillary response (\protect\hyperlink{ref-Markwell2010}{14}, \protect\hyperlink{ref-McDougal2010}{15}).
-The ipRGCs are a unique photoreceptor class that has been discovered recently (\protect\hyperlink{ref-Provencio2000}{16}).
-They express the photopigment melanopsin, and are involved in the regulation of the circadian rhythm (\protect\hyperlink{ref-Provencio2000}{16}--\protect\hyperlink{ref-Ruby2002}{18}), forming a major input to the PON (\protect\hyperlink{ref-Dacey2003}{19}).
-The first direct evidence of the involvement of the ipRGCs in the PLR was shown in melanopsin knockout rats by (\protect\hyperlink{ref-Lucas2003}{20}), resulting in the loss of the intrinsic photosensitivity of the cells and a reduced pupil constriction.
-This same behaviour was later also observed in primates and humans (\protect\hyperlink{ref-Gamlin2007}{21}), where it was demonstrated that the PLR continues during light presentation even when cone and rod signalling is blocked, indicating the primary role of the ipRGCs in maintaining pupil constriction over a prolonged time.
+Different classes of retinal photoreceptors, including cones, rods and melanopsin-containing intrinsically photosensitive retinal ganglion cells (ipRGCs), are directly involved in controlling and maintaining the size of the pupils.\textsuperscript{\protect\hyperlink{ref-Barrionuevo2014}{6}--\protect\hyperlink{ref-Woelders2018}{12}} The cones have been shown to drive the initial rapid constriction of the pupils,\textsuperscript{\protect\hyperlink{ref-Mathot2018}{13}} while the slower and longer activation of the ipRGCs shows their role in maintaining the constriction over a prolonged period of time and in regulating the post-illumination pupillary response.\textsuperscript{\protect\hyperlink{ref-Markwell2010}{14},\protect\hyperlink{ref-McDougal2010}{15}} The ipRGCs are a unique photoreceptor class that has been discovered recently.\textsuperscript{\protect\hyperlink{ref-Provencio2000}{16}} They express the photopigment melanopsin, and are involved in the regulation of the circadian rhythm,\textsuperscript{\protect\hyperlink{ref-Provencio2000}{16}--\protect\hyperlink{ref-Ruby2002}{18}} forming a major input to the PON.\textsuperscript{\protect\hyperlink{ref-Dacey2003}{19}} The first direct evidence of the involvement of the ipRGCs in the PLR was shown in melanopsin knockout rats by Lucas et al.~\textsuperscript{\protect\hyperlink{ref-Lucas2003}{20}}, resulting in the loss of the intrinsic photosensitivity of the cells and a reduced pupil constriction.
+This same behaviour was later also observed in primates and humans,\textsuperscript{\protect\hyperlink{ref-Gamlin2007}{21}} where it was demonstrated that the PLR continues during light presentation even when cone and rod signalling is blocked, indicating the primary role of the ipRGCs in maintaining pupil constriction over a prolonged time.
 
-A technique known as silent substitution (\protect\hyperlink{ref-Estevez1982}{22}) can be used to selectively stimulate specific photoreceptor classes.
+A technique known as silent substitution\textsuperscript{\protect\hyperlink{ref-Estevez1982}{22}} can be used to selectively stimulate specific photoreceptor classes.
 Silent substitution exploits the fact that each photoreceptor class has a distinct spectral tuning that overlaps with the others.
-Using a multiprimary system, in which the primaries (i.e.~LEDs) have different spectra, it is possible to target one class of photoreceptors while maintaining the others at a constant activity level, effectively silencing them (\protect\hyperlink{ref-Shapiro1996}{23}, \protect\hyperlink{ref-Spitschan2018}{24}).
-Studies using silent substitution have shown that the pupils behave differently depending on which photoreceptor or pathway is being stimulated.
-For example, pupil responses have been shown to be out of phase when the S cones are stimulated, relative to when the ipRGCs or the L+M cones are stimulated (\protect\hyperlink{ref-Spitschan2014}{10}, \protect\hyperlink{ref-Cao2015}{25}).
-Additionally, when L and M cones are stimulated individually, there appears to be a paradoxical pupil response: increments in L cone stimulation cause a constriction of the pupil, while increments in M cone stimulation lead to a dilation of the pupil (\protect\hyperlink{ref-Murray2018}{9}, \protect\hyperlink{ref-Woelders2018}{12}), perhaps due to activity in the L-M opponent pathway.
+Using a multiprimary system, in which the primaries (i.e.~LEDs) have different spectra, it is possible to target one class of photoreceptors while maintaining the others at a constant activity level, effectively silencing them.\textsuperscript{\protect\hyperlink{ref-Shapiro1996}{23},\protect\hyperlink{ref-Spitschan2018}{24}} Studies using silent substitution have shown that the pupils behave differently depending on which photoreceptor or pathway is being stimulated.
+For example, pupil responses have been shown to be out of phase when the S cones are stimulated, relative to when the ipRGCs or the L+M cones are stimulated.\textsuperscript{\protect\hyperlink{ref-Spitschan2014}{10},\protect\hyperlink{ref-Cao2015}{25}} Additionally, when L and M cones are stimulated individually, there appears to be a paradoxical pupil response: increments in L cone stimulation cause a constriction of the pupil, while increments in M cone stimulation lead to a dilation of the pupil,\textsuperscript{\protect\hyperlink{ref-Murray2018}{9},\protect\hyperlink{ref-Woelders2018}{12}} perhaps due to activity in the L-M opponent pathway.
 
-Binocular combination has been extensively studied in visual perception, where it is mediated by neurons in primary visual cortex (\protect\hyperlink{ref-Hubel1962}{26}, \protect\hyperlink{ref-Moradi2009}{27}).
-For pattern vision, binocular summation occurs at threshold, such that a lower contrast is required to detect a target shown to both eyes than a target shown to only one eye (\protect\hyperlink{ref-Baker2018}{28}--\protect\hyperlink{ref-Legge1984}{30}).
-At higher contrasts, a process of `ocularity invariance' is observed, in which the response to monocularly- and binocularly-presented patterns is equal (\protect\hyperlink{ref-Moradi2009}{27}, \protect\hyperlink{ref-Baker2007}{31}--\protect\hyperlink{ref-Meese2006}{33}).
-This is thought to be due to a process of interocular suppression that compensates for the additional excitatory drive caused by stimulating two eyes.
-Our recent work (\protect\hyperlink{ref-Segala2023}{5}) has shown that cortical signal combination for luminance flicker is substantially more linear than for spatial patterns, whereas there is evidence of interocular suppression in the pupil pathway.
+Binocular combination has been extensively studied in visual perception, where it is mediated by neurons in primary visual cortex.\textsuperscript{\protect\hyperlink{ref-Hubel1962}{26},\protect\hyperlink{ref-Moradi2009}{27}} For pattern vision, binocular summation occurs at threshold, such that a lower contrast is required to detect a target shown to both eyes than a target shown to only one eye.\textsuperscript{\protect\hyperlink{ref-Baker2018}{28}--\protect\hyperlink{ref-Legge1984}{30}} At higher contrasts, a process of `ocularity invariance' is observed, in which the response to monocularly- and binocularly-presented patterns is equal.\textsuperscript{\protect\hyperlink{ref-Moradi2009}{27},\protect\hyperlink{ref-Baker2007}{31}--\protect\hyperlink{ref-Meese2006}{33}} This is thought to be due to a process of interocular suppression that compensates for the additional excitatory drive caused by stimulating two eyes.
+Our recent work\textsuperscript{\protect\hyperlink{ref-Segala2023}{5}} has shown that cortical signal combination for luminance flicker is substantially more linear than for spatial patterns, whereas there is evidence of interocular suppression in the pupil pathway.
 
 Most studies that use silent substitution to investigate the PLR stimulate only one eye.
-If the stimulated eye is pharmacologically dilated to control pupil size, the response from the unstimulated eye (known as the consensual response) can be recorded (\protect\hyperlink{ref-Spitschan2014}{10}, \protect\hyperlink{ref-McDougal2010}{15}).
-While this approach controls the total amount of light incident at the retina, it does not permit investigation of binocular combination for specific photoreceptor pathways.
+If the stimulated eye is pharmacologically dilated to control pupil size, the response from the unstimulated eye (known as the consensual response) can be recorded.\textsuperscript{\protect\hyperlink{ref-Spitschan2014}{10},\protect\hyperlink{ref-McDougal2010}{15}} While this approach controls the total amount of light incident at the retina, it does not permit investigation of binocular combination for specific photoreceptor pathways.
 Here we take a different approach, using a custom binocular multiprimary system (see Figure \ref{fig:spectraplots}a,b) that can modulate each (undilated) eye independently, and a binocular eye tracker to measure the diameter of both pupils.
@@
 Our key comparisons are between monocular and binocular stimulation, and between monocular stimulation and a dichoptic masking condition in which the two eyes are stimulated at different frequencies (0.5 and 0.4Hz).
-The results are interpreted using a contemporary model of binocular vision (\protect\hyperlink{ref-Meese2006}{33}) implemented within a hierarchical Bayesian framework.
+The results are interpreted using a contemporary model of binocular vision\textsuperscript{\protect\hyperlink{ref-Meese2006}{33}} implemented within a hierarchical Bayesian framework.
 
@@
 
-In contemporary models of binocular signal combination, the amount of binocular facilitation is determined by the magnitude of interocular suppression, with strong suppression reducing facilitation (\protect\hyperlink{ref-Kingdom2015}{34}).
-We can estimate the strength of interocular suppression by measuring how much monocular responses are reduced when a dichoptic `mask' is shown to the other eye.
-In our paradigm, the two components flickered at different frequencies (0.5 and 0.4Hz) so that their responses remained distinct in the Fourier spectrum (\protect\hyperlink{ref-Busse2009}{35}).
-The yellow diamond symbols in Figure \ref{fig:FirstHarmonicPlots}a-d show the target responses in this condition, and in most cases were weaker than the monocular responses (red circles).
+In contemporary models of binocular signal combination, the amount of binocular facilitation is determined by the magnitude of interocular suppression, with strong suppression reducing facilitation.\textsuperscript{\protect\hyperlink{ref-Kingdom2015}{34}} We can estimate the strength of interocular suppression by measuring how much monocular responses are reduced when a dichoptic `mask' is shown to the other eye.
+In our paradigm, the two components flickered at different frequencies (0.5 and 0.4Hz) so that their responses remained distinct in the Fourier spectrum.\textsuperscript{\protect\hyperlink{ref-Busse2009}{35}} The yellow diamond symbols in Figure \ref{fig:FirstHarmonicPlots}a-d show the target responses in this condition, and in most cases were weaker than the monocular responses (red circles).
 The strongest dichoptic masking is found in the L-M condition, where we also observed the binocular suppression effect.
@@
 
-To estimate the extent of interocular suppression for each photoreceptor pathway, we fitted each data set using a Bayesian hierarchical implementation of a simple binocular combination model (\protect\hyperlink{ref-Segala2023}{5}, \protect\hyperlink{ref-Meese2006}{33}).
-Our primary objective was to compare posterior distributions of the weight of interocular suppression, which are shown in Figure \ref{fig:FirstHarmonicPlots}e.
+To estimate the extent of interocular suppression for each photoreceptor pathway, we fitted each data set using a Bayesian hierarchical implementation of a simple binocular combination model.\textsuperscript{\protect\hyperlink{ref-Segala2023}{5},\protect\hyperlink{ref-Meese2006}{33}} Our primary objective was to compare posterior distributions of the weight of interocular suppression, which are shown in Figure \ref{fig:FirstHarmonicPlots}e.
 Consistent with our earlier observations, the strongest suppressive weight corresponds to the L-M and Melanopsin conditions, and the weakest suppression corresponds to the luminance and S-cone conditions, with virtually no overlap between the posterior distributions for weak and strong suppression.
@@
 
-Finally, we inspected the response phase of our four stimulation conditions, given previous reports that these differ across pathways (\protect\hyperlink{ref-Spitschan2014}{10}), and may be in antiphase for melanopsin and S-cone signals.
+Finally, we inspected the response phase of our four stimulation conditions, given previous reports that these differ across pathways,\textsuperscript{\protect\hyperlink{ref-Spitschan2014}{10}} and may be in antiphase for melanopsin and S-cone signals.
 Figure \ref{fig:phaseplots} shows the phase angles for the first (a) and second (b) harmonic frequencies for binocular stimulation (monocular stimulation produced very similar results).
@@
 This is the first study to investigate binocular interactions in the melanopsin pathway directly.
-A previous meta-analysis (\protect\hyperlink{ref-Spitschan2019}{11}) indicated that there may be a substantial binocular facilitation effect in the circadian pathway, as indexed by melatonin suppression (melatonin is a hormone released by the pineal gland; its production is suppressed by exposure to bright light, particularly when the melanopsin-containing ipRGCs are stimulated).
+A previous meta-analysis\textsuperscript{\protect\hyperlink{ref-Spitschan2019}{11}} indicated that there may be a substantial binocular facilitation effect in the circadian pathway, as indexed by melatonin suppression (melatonin is a hormone released by the pineal gland; its production is suppressed by exposure to bright light, particularly when the melanopsin-containing ipRGCs are stimulated).
 In brief, monocular stimulation of the ipRGCs requires up to ten times the signal strength to produce an equivalent effect to binocular stimulation.
@@
 The explanation for this difference could be due to different anatomical pathways.
-Binocular combination in the circadian system likely takes place in the suprachiasmatic nucleus, whereas in the pupil constriction circuit the Edinger-Westphal nucleus is the most likely site of binocular integration (\protect\hyperlink{ref-Mathot2018}{13}).
-Presumably these anatomical differences, and the practical constraints of the two systems, lead to differences in response.
+Binocular combination in the circadian system likely takes place in the suprachiasmatic nucleus, whereas in the pupil constriction circuit the Edinger-Westphal nucleus is the most likely site of binocular integration.\textsuperscript{\protect\hyperlink{ref-Mathot2018}{13}} Presumably these anatomical differences, and the practical constraints of the two systems, lead to differences in response.
 
-Our recent psychophysical work (\protect\hyperlink{ref-Baker2024}{36}) has looked at binocular interactions in the L-M and S-cone pathways, and compared these to the luminance pathway.
-Using a contrast discrimination paradigm with spatial modulations of luminance and colour, (\protect\hyperlink{ref-Baker2024}{36}) found equally strong interocular suppression in all three pathways.
+Our recent psychophysical work\textsuperscript{\protect\hyperlink{ref-Baker2024}{36}} has looked at binocular interactions in the L-M and S-cone pathways, and compared these to the luminance pathway.
+Using a contrast discrimination paradigm with spatial modulations of luminance and colour, we found equally strong interocular suppression in all three pathways.
 This is rather different from our pupillometry results here, which demonstrate weaker suppression in the luminance and S-cone pathways than in the L-M pathway (see Figure \ref{fig:FirstHarmonicPlots}).
-However, the current experiments involve temporal modulations, which are quite distinct from the spatial modulations used in (\protect\hyperlink{ref-Baker2024}{36}).
-Our other recent work (\protect\hyperlink{ref-Segala2023}{5}) has shown that temporal luminance modulations involve much weaker interocular suppression in the cortical response than do spatial luminance modulations (\protect\hyperlink{ref-Baker2017}{37}).
-These different normalization processes might reflect different priorities for spatial and temporal vision.
-Spatial vision aims to fuse images to provide binocular single vision, and benefits from `ocularity invariance' (\protect\hyperlink{ref-Baker2007}{31}), in which visual appearance is constant when viewed with one eye or two.
-Temporal vision is critical for motion perception, which can involve alternative binocular computations, such as calculating velocity differences between the eyes (\protect\hyperlink{ref-Kaestner2019}{38}).
-Of course the present measurements were of pupil size, which may be subject to different anatomical and functional constraints from those in the cortex.
+However, the current experiments involve temporal modulations, which are quite distinct from the spatial modulations used in our previous work.\textsuperscript{\protect\hyperlink{ref-Baker2024}{36}} Our other recent work\textsuperscript{\protect\hyperlink{ref-Segala2023}{5}} has shown that temporal luminance modulations involve much weaker interocular suppression in the cortical response than do spatial luminance modulations.\textsuperscript{\protect\hyperlink{ref-Baker2017}{37}} These different normalization processes might reflect different priorities for spatial and temporal vision.
+Spatial vision aims to fuse images to provide binocular single vision, and benefits from `ocularity invariance',\textsuperscript{\protect\hyperlink{ref-Baker2007}{31}} in which visual appearance is constant when viewed with one eye or two.
+Temporal vision is critical for motion perception, which can involve alternative binocular computations, such as calculating velocity differences between the eyes.\textsuperscript{\protect\hyperlink{ref-Kaestner2019}{38}} Of course the present measurements were of pupil size, which may be subject to different anatomical and functional constraints from those in the cortex.
 Future research should aim to extend our current findings to perception using psychophysical approaches.
@@
 
-\hypertarget{materials-and-methods}{%
-\section{Materials and methods}\label{materials-and-methods}}
+\hypertarget{methods}{%
+\section{Methods}\label{methods}}
 
@@
 To present synchronised stimulus modulations independently to each eye, two light engines (SpectraTuneLAB: LEDMOTIVE Technologies, LLC, Barcelona, Spain), each with 10 independently addressable LED colour channels, were integrated into a customised viewing system.
-The light engines were operated via a Python interface to their REST API (\protect\hyperlink{ref-Martin2022}{39}), which supports synchronous launch and playback of spectral sequences prepared in advance and stored in JSON format.
+The light engines were operated via a Python interface to their REST API,\textsuperscript{\protect\hyperlink{ref-Martin2022}{39}} which supports synchronous launch and playback of spectral sequences prepared in advance and stored in JSON format.
 When preparing the spectral sequences, the age of participants was used to account for the yellowing of the lenses.
-We calculated silent substitution solutions using the \emph{PySilSub} toolbox (\protect\hyperlink{ref-Martin2023}{40}), using linear algebra.
+We calculated silent substitution solutions using the \emph{PySilSub} toolbox,\textsuperscript{\protect\hyperlink{ref-Martin2023}{40}} using linear algebra.
 The outputs of the two light engines (see Figure \ref{fig:spectraplots}b,c) were calibrated using an Ocean Optics Jaz spectroradiometer, which was wavelength-calibrated to an Argon lamp and intensity calibrated using a NIST-traceable light source.
-We used the (\protect\hyperlink{ref-Stockman2000}{41}) 10-degree cone fundamentals, and estimates of melanopsin absorbance spectra from CIE S 026 (\protect\hyperlink{ref-Martin2023}{40}) to calculate \(\alpha\)-opic irradiance.
+We used the Stockman and Sharpe 10-degree cone fundamentals,\textsuperscript{\protect\hyperlink{ref-Stockman2000}{41}} and estimates of melanopsin absorbance spectra from CIE S 026\textsuperscript{\protect\hyperlink{ref-Martin2023}{40}} to calculate \(\alpha\)-opic irradiance.
 
@@
 The diffuser discs were positioned in the objective planes of the lenses of a modified VR headset (SHINECON SC-G01, Dongguan Shinecon Industrial Co.~Ltd., Guangdong, China), which was used by the participants to view the stimuli.
-The stimuli were two discs of flickering light with a diameter of approximately 30 degrees, which were fused together into a cyclopean percept resembling a donut-shaped ring of light, similar to that used in other studies (\protect\hyperlink{ref-Murray2018}{9}, \protect\hyperlink{ref-Spitschan2014}{10}, \protect\hyperlink{ref-Barrionuevo2016}{42}--\protect\hyperlink{ref-Zele2018}{44}).
-The VR headset modifications allowed for small adjustments to account for individual differences in interpupillary distance and focal length.
-The use of this set up allowed us to modulate the stimuli in three different ocular configurations, similar to the ones we used in our previous study (\protect\hyperlink{ref-Segala2023}{5}): monocular, binocular and dichoptic.
+The stimuli were two discs of flickering light with a diameter of approximately 30 degrees, which were fused together into a cyclopean percept resembling a donut-shaped ring of light, similar to that used in other studies.\textsuperscript{\protect\hyperlink{ref-Murray2018}{9},\protect\hyperlink{ref-Spitschan2014}{10},\protect\hyperlink{ref-Barrionuevo2016}{42}--\protect\hyperlink{ref-Zele2018}{44}} The VR headset modifications allowed for small adjustments to account for individual differences in interpupillary distance and focal length.
+The use of this set up allowed us to modulate the stimuli in three different ocular configurations, similar to the ones we used in our previous study:\textsuperscript{\protect\hyperlink{ref-Segala2023}{5}} monocular, binocular and dichoptic.
 In the monocular configuration, the unstimulated eye still saw a non-flickering disc of mean luminance.
 A schematic of the stimulation system is shown in Figure \ref{fig:spectraplots}a.
-Pupillometry data were collected using a binocular Pupil Core eye-tracker headset (\protect\hyperlink{ref-Kassner2014}{45}) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
+Pupillometry data were collected using a binocular Pupil Core eye-tracker headset (Pupil Labs GmbH, Berlin, Germany)\textsuperscript{\protect\hyperlink{ref-Kassner2014}{45}} running at 120 Hz, and the signals were recorded with the Pupil Capture software.
 
-Our previous study (\protect\hyperlink{ref-Segala2023}{5}) used a temporal frequency of 2Hz for foveal luminance flicker, and recorded EEG data simultaneously with pupillometry.
+Our previous study\textsuperscript{\protect\hyperlink{ref-Segala2023}{5}} used a temporal frequency of 2Hz for foveal luminance flicker, and recorded EEG data simultaneously with pupillometry.
 Initial pilot experiments indicated that this frequency was too high to elicit measurable responses when stimulating individual photoreceptor pathways.
-For all experiments, we therefore used a primary flicker frequency of 0.5Hz, as previous literature showed that this was slow enough to elicit a pupil response from all photoreceptor classes (\protect\hyperlink{ref-Spitschan2014}{10}).
-We also focussed on only recording pupillometry data as this frequency would be too slow to elicit steady-state EEG responses (\protect\hyperlink{ref-Norcia2015}{46}).
+For all experiments, we therefore used a primary flicker frequency of 0.5Hz, as previous literature showed that this was slow enough to elicit a pupil response from all photoreceptor classes.\textsuperscript{\protect\hyperlink{ref-Spitschan2014}{10}} We also focussed on only recording pupillometry data as this frequency would be too slow to elicit steady-state EEG responses.\textsuperscript{\protect\hyperlink{ref-Norcia2015}{46}}
 
@@
 Splatter on nominally silenced photoreceptors was very small (see Figure \ref{fig:spectraplots}j-l), well below the levels that would be expected to generate measureable pupil modulations.
-We also estimated activation of penumbral L and M cones (\protect\hyperlink{ref-Barrionuevo2016}{42}, \protect\hyperlink{ref-Spitschan2015}{43}, \protect\hyperlink{ref-Zele2019}{47}), which was minimal (\(\le 1.5%
+We also estimated activation of penumbral L and M cones,\textsuperscript{\protect\hyperlink{ref-Barrionuevo2016}{42},\protect\hyperlink{ref-Spitschan2015}{43},\protect\hyperlink{ref-Zele2019}{47}} which was minimal (\(\le 1.5%
 \) contrast; less than splatter on the open-field cones) for melanopsin-directed stimuli.
-We note that the temporal frequency of our modulation (0.5Hz) is well below the range where penumbral cone activation can elicit visible percepts, and that such percepts fade after around 1 second (\protect\hyperlink{ref-Spitschan2015}{43}), and do not typically affect pupil responses (\protect\hyperlink{ref-Spitschan2014}{10}).
+We note that the temporal frequency of our modulation (0.5Hz) is well below the range where penumbral cone activation can elicit visible percepts, and that such percepts fade after around 1 second,\textsuperscript{\protect\hyperlink{ref-Spitschan2015}{43}} and do not typically affect pupil responses.\textsuperscript{\protect\hyperlink{ref-Spitschan2014}{10}}
 
@@
 Pupil responses to binocular temporal contrast modulations were examined in a factorial design that combined six ocular conditions and five temporal contrast levels: 6, 12, 24, 48 and 96\% of the available dynamic range.
-This design, similar to that used in our previous studies (\protect\hyperlink{ref-Segala2023}{5}, \protect\hyperlink{ref-Baker2017}{37}, \protect\hyperlink{ref-Baker2020}{48}), was applied in four separate experiments, each with a different mode of photoreceptor stimulation.
+This design, similar to that used in our previous studies,\textsuperscript{\protect\hyperlink{ref-Segala2023}{5},\protect\hyperlink{ref-Baker2017}{37},\protect\hyperlink{ref-Baker2020}{48}} was applied in four separate experiments, each with a different mode of photoreceptor stimulation.
 In the first three conditions, the discs flickered at 0.5 Hz, in either a monocular, binocular or dichoptic arrangement.
@@
 Using a trackball, participants adjusted the angle in cone space to find their subjective isoluminant point, which resulted in changing the flickering intensity of the stimulus until the amplitude of the flicker appeared to be minimised.
-The result was used to modify the requested contrasts during stimulus preparation so as to account for individual differences affecting perceived illuminance, principally the L:M cone ratio (\protect\hyperlink{ref-Carroll2002}{49}, \protect\hyperlink{ref-Hofer2005}{50}).
+The result was used to modify the requested contrasts during stimulus preparation so as to account for individual differences affecting perceived illuminance, principally the L:M cone ratio.\textsuperscript{\protect\hyperlink{ref-Carroll2002}{49},\protect\hyperlink{ref-Hofer2005}{50}}
 
@@
 
-The pupillometry data were analysed using the same method we used in our previous study (\protect\hyperlink{ref-Segala2023}{5}).
-The data were converted from mp4 videos to a csv text file using the Pupil Player software (\protect\hyperlink{ref-Kassner2014}{45}), which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
+The pupillometry data were analysed using the same method we used in our previous study.\textsuperscript{\protect\hyperlink{ref-Segala2023}{5}} The data were converted from mp4 videos to a csv text file using the Pupil Player software,\textsuperscript{\protect\hyperlink{ref-Kassner2014}{45}} which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
 The individual data were then loaded into R for analysis, where a ten-second waveform for each trial in each eye was extracted (excluding the first two seconds after stimulus onset).
@@
 Finally, data were averaged across all participants to obtain the group results.
-We used coherent averaging and at each stage we excluded data points with a Mahalanobis distance exceeding \(D\) = 3 from the complex-valued mean (\protect\hyperlink{ref-Baker2021}{51}).
-For monocular stimulation, we confirmed that the consensual response was equivalent to the response in the stimulated eye.
+We used coherent averaging and at each stage we excluded data points with a Mahalanobis distance exceeding \(D\) = 3 from the complex-valued mean.\textsuperscript{\protect\hyperlink{ref-Baker2021}{51}} For monocular stimulation, we confirmed that the consensual response was equivalent to the response in the stimulated eye.
 
@@
 
-To describe our data, we used the same model described in our previous study (\protect\hyperlink{ref-Segala2023}{5}).
-The model has the same general form as the first stage of the contrast gain control model proposed by (\protect\hyperlink{ref-Meese2006}{33}), but omits the second stage.
-For the previous model that we used (\protect\hyperlink{ref-Segala2023}{5}), the exponent of the numerator and denominator had fixed values of 2 and (implicitly) 1.
+To describe our data, we used the same model described in our previous study.\textsuperscript{\protect\hyperlink{ref-Segala2023}{5}} The model has the same general form as the first stage of the contrast gain control model proposed by Meese, Georgeson and Baker,\textsuperscript{\protect\hyperlink{ref-Meese2006}{33}} but omits the second stage.
+For the previous model that we used,\textsuperscript{\protect\hyperlink{ref-Segala2023}{5}} the exponent of the numerator and denominator had fixed values of 2 and (implicitly) 1.
 Here, we allow these parameters (called \emph{p} and \emph{q}) to be free, in order to permit different shapes of contrast response function, e.g.~accelerating or saturating.
@@
 
-The models were fit using a hierarchical Bayesian framework implemented in Stan (\protect\hyperlink{ref-Carpenter2017}{52}).
-The data for each photoreceptor type and response frequency was fit separately, for a total of 8 model fits.
+The models were fit using a hierarchical Bayesian framework implemented in Stan.\textsuperscript{\protect\hyperlink{ref-Carpenter2017}{52}} The data for each photoreceptor type and response frequency was fit separately, for a total of 8 model fits.
 The prior for the \(\omega\) parameter was Gaussian, with a mean of 1 and standard deviation of 0.5.
-Priors for the other free parameters were also Gaussian, with mean values based on previous work (\protect\hyperlink{ref-Segala2023}{5}).
-We calculated over \ensuremath{10^{6}} posterior samples, and retained 10\% for plotting.
-
-\hypertarget{acknowledgements-and-funding-sources}{%
-\section{Acknowledgements and funding sources}\label{acknowledgements-and-funding-sources}}
-
-Supported by Biotechnology and Biological Sciences Research Council grant BB/V007580/1 awarded to DHB and ARW.
+Priors for the other free parameters were also Gaussian, with mean values based on previous work.\textsuperscript{\protect\hyperlink{ref-Segala2023}{5}} We calculated over \ensuremath{10^{6}} posterior samples, and retained 10\% for plotting.
 
@@
 \leavevmode\hypertarget{ref-McDougal2015}{}%
-1. D. H. McDougal, P. D. Gamlin, Autonomic control of the eye. \emph{Comprehensive Physiology} \textbf{5}, 439--473 (2015).
+1. McDougal, D. H. \& Gamlin, P. D. Autonomic control of the eye. \emph{Comprehensive Physiology} \textbf{5}, 439--473 (2015).
 
 \leavevmode\hypertarget{ref-McDougal2008}{}%
-2. D. H. McDougal, P. D. Gamlin, ``Pupillary control pathways.'' in \emph{The Senses: A Comprehensive Reference}, (Elsevier, 2008), pp. 521--536.
+2. McDougal, D. H. \& Gamlin, P. D. Pupillary control pathways. in \emph{The senses: A comprehensive reference} 521--536 (Elsevier, 2008).
 
 \leavevmode\hypertarget{ref-Wang2015}{}%
-3. C.-A. Wang, D. P. Munoz, A circuit for pupil orienting responses: Implications for cognitive modulation of pupil size. \emph{Curr Opin Neurobiol} \textbf{33}, 134--40 (2015).
+3. Wang, C.-A. \& Munoz, D. P. A circuit for pupil orienting responses: Implications for cognitive modulation of pupil size. \emph{Curr Opin Neurobiol} \textbf{33}, 134--40 (2015).
 
@@
 4.
-H.
+Wyatt, H.
 J.
-Wyatt, J.
+\& Musselman, J.
 F.
-Musselman, Pupillary light reflex in humans: Evidence for an unbalanced pathway from nasal retina, and for signal cancellation in brainstem.
+Pupillary light reflex in humans: Evidence for an unbalanced pathway from nasal retina, and for signal cancellation in brainstem.
 \emph{Vision Res} \textbf{21}, 513--25 (1981).
@@
 \leavevmode\hypertarget{ref-Segala2023}{}%
-5. F. G. Segala\emph{et al.}, Different rules for binocular combination of luminance flicker in cortical and subcortical pathways. \emph{eLife} \textbf{12} (2023).
+5. Segala, F. G. \emph{et al.} Different rules for binocular combination of luminance flicker in cortical and subcortical pathways. \emph{eLife} \textbf{12}, (2023).
 
 \leavevmode\hypertarget{ref-Barrionuevo2014}{}%
-6. P. A. Barrionuevo\emph{et al.}, Assessing rod, cone, and melanopsin contributions to human pupil flicker responses. \emph{Investigative Ophthalmology \& Visual Science} \textbf{55}, 719--27 (2014).
+6.
+Barrionuevo, P.
+A.
+\emph{et al.} Assessing rod, cone, and melanopsin contributions to human pupil flicker responses.
+\emph{Investigative Ophthalmology \& Visual Science} \textbf{55}, 719--27 (2014).
 
 \leavevmode\hypertarget{ref-Barrionuevo2018}{}%
-7. P. A. Barrionuevo, J. J. McAnany, A. J. Zele, D. Cao, Non-linearities in the Rod and Cone Photoreceptor Inputs to the Afferent Pupil Light Response. \emph{Frontiers in Neurology} \textbf{9} (2018).
+7.
+Barrionuevo, P.
+A., McAnany, J.
+J., Zele, A.
+J.
+\& Cao, D.
+Non-linearities in the Rod and Cone Photoreceptor Inputs to the Afferent Pupil Light Response.
+\emph{Frontiers in Neurology} \textbf{9}, (2018).
 
 \leavevmode\hypertarget{ref-Dacey2005}{}%
-8. D. M. Dacey\emph{et al.}, Melanopsin-expressing ganglion cells in primate retina signal colour and irradiance and project to the LGN. \emph{Nature} \textbf{433}, 749--754 (2005).
+8. Dacey, D. M. \emph{et al.} Melanopsin-expressing ganglion cells in primate retina signal colour and irradiance and project to the LGN. \emph{Nature} \textbf{433}, 749--754 (2005).
 
 \leavevmode\hypertarget{ref-Murray2018}{}%
-9. I. J. Murray, J. Kremers, D. McKeefry, N. R. A. Parry, Paradoxical pupil responses to isolated M-cone increments. \emph{Journal of the Optical Society of America A} \textbf{35}, B66--B71 (2018).
+9.
+Murray, I.
+J., Kremers, J., McKeefry, D.
+\& Parry, N.
+R.
+A.
+Paradoxical pupil responses to isolated M-cone increments.
+\emph{Journal of the Optical Society of America A} \textbf{35}, B66--B71 (2018).
 
@@
 10.
-M.
-Spitschan, S.
-Jain, D.
+Spitschan, M., Jain, S., Brainard, D.
 H.
-Brainard, G.
+\& Aguirre, G.
 K.
-Aguirre, Opponent melanopsin and s-cone signals in the human pupillary light response.
+Opponent melanopsin and s-cone signals in the human pupillary light response.
 \emph{Proceedings of the National Academy of Sciences} \textbf{111}, 15568--15572 (2014).
@@
 \leavevmode\hypertarget{ref-Spitschan2019}{}%
-11. M. Spitschan, C. Cajochen, Binocular facilitation in light-mediated melatonin suppression? \emph{J Pineal Res} \textbf{67}, e12602 (2019).
+11. Spitschan, M. \& Cajochen, C. Binocular facilitation in light-mediated melatonin suppression? \emph{J Pineal Res} \textbf{67}, e12602 (2019).
 
@@
 12.
-T.
-Woelders\emph{et al.}, Melanopsin- and L-cone--induced pupil constriction is inhibited by S- and M-cones in humans.
+Woelders, T.
+\emph{et al.} Melanopsin- and L-cone--induced pupil constriction is inhibited by S- and M-cones in humans.
 \emph{Proceedings of the National Academy of Sciences} \textbf{115}, 792--797 (2018).
@@
 \leavevmode\hypertarget{ref-Mathot2018}{}%
-13. S. Mathôt, Pupillometry: Psychology, physiology, and function. \emph{J Cogn} \textbf{1}, 16 (2018).
+13. Mathôt, S. Pupillometry: Psychology, physiology, and function. \emph{J Cogn} \textbf{1}, 16 (2018).
 
@@
 14.
-E.
-L.
-Markwell, B.
-Feigl, A.
+Markwell, E.
+L., Feigl, B.
+\& Zele, A.
 J.
-Zele, Intrinsically photosensitive melanopsin retinal ganglion cell contributions to the pupillary light reflex and circadian rhythm.
+Intrinsically photosensitive melanopsin retinal ganglion cell contributions to the pupillary light reflex and circadian rhythm.
 \emph{Clinical and Experimental Optometry} \textbf{93}, 137--149 (2010).
@@
 15.
+McDougal, D.
+H.
+\& Gamlin, P.
 D.
-H.
-McDougal, P.
-D.
-Gamlin, The influence of intrinsically-photosensitive retinal ganglion cells on the spectral sensitivity and response dynamics of the human pupillary light reflex.
+The influence of intrinsically-photosensitive retinal ganglion cells on the spectral sensitivity and response dynamics of the human pupillary light reflex.
 \emph{Vision Research} \textbf{50}, 72--87 (2010).
@@
 \leavevmode\hypertarget{ref-Provencio2000}{}%
-16. I. Provencio\emph{et al.}, A Novel Human Opsin in the Inner Retina. \emph{Journal of Neuroscience} \textbf{20}, 600--605 (2000).
+16. Provencio, I. \emph{et al.} A Novel Human Opsin in the Inner Retina. \emph{Journal of Neuroscience} \textbf{20}, 600--605 (2000).
 
 \leavevmode\hypertarget{ref-Panda2002}{}%
-17. S. Panda\emph{et al.}, Melanopsin (opn4) requirement for normal light-induced circadian phase shifting. \emph{Science} \textbf{298}, 2213--2216 (2002).
+17. Panda, S. \emph{et al.} Melanopsin (opn4) requirement for normal light-induced circadian phase shifting. \emph{Science} \textbf{298}, 2213--2216 (2002).
 
 \leavevmode\hypertarget{ref-Ruby2002}{}%
-18. N. F. Ruby\emph{et al.}, Role of melanopsin in circadian responses to light. \emph{Science} \textbf{298}, 2211--2213 (2002).
+18. Ruby, N. F. \emph{et al.} Role of melanopsin in circadian responses to light. \emph{Science} \textbf{298}, 2211--2213 (2002).
 
@@
 19.
+Dacey, D.
+M., Peterson, B.
+B., Robinson, F.
+R.
+\& Gamlin, P.
 D.
-M.
-Dacey, B.
-B.
-Peterson, F.
-R.
-Robinson, P.
-D.
-Gamlin, Fireworks in the primate retina: In vitro photodynamics reveals diverse lgn-projecting ganglion cell types.
+Fireworks in the primate retina: In vitro photodynamics reveals diverse lgn-projecting ganglion cell types.
 \emph{Neuron} \textbf{37}, 15--27 (2003).
@@
 \leavevmode\hypertarget{ref-Lucas2003}{}%
-20. R. J. Lucas\emph{et al.}, Diminished pupillary light reflex at high irradiances in melanopsin-knockout mice. \emph{Science} \textbf{299}, 245--247 (2003).
+20. Lucas, R. J. \emph{et al.} Diminished pupillary light reflex at high irradiances in melanopsin-knockout mice. \emph{Science} \textbf{299}, 245--247 (2003).
 
 \leavevmode\hypertarget{ref-Gamlin2007}{}%
-21. P. D. R. Gamlin\emph{et al.}, Human and macaque pupil responses driven by melanopsin-containing retinal ganglion cells. \emph{Vision Research} \textbf{47}, 946--954 (2007).
+21. Gamlin, P. D. R. \emph{et al.} Human and macaque pupil responses driven by melanopsin-containing retinal ganglion cells. \emph{Vision Research} \textbf{47}, 946--954 (2007).
 
 \leavevmode\hypertarget{ref-Estevez1982}{}%
-22. O. Estévez, H. Spekreijse, The "silent substitution" method in visual research. \emph{Vision Research} \textbf{22}, 681--691 (1982).
+22. Estévez, O. \& Spekreijse, H. The "silent substitution" method in visual research. \emph{Vision Research} \textbf{22}, 681--691 (1982).
 
@@
 23.
-A.
-G.
-Shapiro, J.
-Pokorny, V.
+Shapiro, A.
+G., Pokorny, J.
+\& Smith, V.
 C.
-Smith, Conerod receptor spaces with illustrations that use CRT phosphor and light-emitting-diode spectra.
+Conerod receptor spaces with illustrations that use CRT phosphor and light-emitting-diode spectra.
 \emph{Journal of the Optical Society of America A} \textbf{13}, 2319 (1996).
@@
 \leavevmode\hypertarget{ref-Spitschan2018}{}%
-24. M. Spitschan, T. Woelders, The Method of Silent Substitution for Examining Melanopsin Contributions to Pupil Control. \emph{Frontiers in Neurology} \textbf{9} (2018).
+24. Spitschan, M. \& Woelders, T. The Method of Silent Substitution for Examining Melanopsin Contributions to Pupil Control. \emph{Frontiers in Neurology} \textbf{9}, (2018).
 
@@
 25.
-D.
-Cao, N.
-Nicandro, P.
+Cao, D., Nicandro, N.
+\& Barrionuevo, P.
 A.
-Barrionuevo, A five-primary photostimulator suitable for studying intrinsically photosensitive retinal ganglion cell functions in humans.
+A five-primary photostimulator suitable for studying intrinsically photosensitive retinal ganglion cell functions in humans.
 \emph{Journal of Vision} \textbf{15}, 27 (2015).
@@
 \leavevmode\hypertarget{ref-Hubel1962}{}%
-26. D. H. Hubel, T. N. Wiesel, Receptive fields, binocular interaction and functional architecture in the cat's visual cortex. \emph{J Physiol} \textbf{160}, 106--54 (1962).
+26. Hubel, D. H. \& Wiesel, T. N. Receptive fields, binocular interaction and functional architecture in the cat's visual cortex. \emph{J Physiol} \textbf{160}, 106--54 (1962).
 
 \leavevmode\hypertarget{ref-Moradi2009}{}%
-27. F. Moradi, D. J. Heeger, Inter-ocular contrast normalization in human visual cortex. \emph{J Vis} \textbf{9}, 13.1--22 (2009).
+27. Moradi, F. \& Heeger, D. J. Inter-ocular contrast normalization in human visual cortex. \emph{J Vis} \textbf{9}, 13.1--22 (2009).
 
 \leavevmode\hypertarget{ref-Baker2018}{}%
-28. D. H. Baker, F. A. Lygo, T. S. Meese, M. A. Georgeson, Binocular summation revisited: Beyond \(\sqrt{2}\). \emph{Psychol Bull} \textbf{144}, 1186--1199 (2018).
+28. Baker, D. H., Lygo, F. A., Meese, T. S. \& Georgeson, M. A. Binocular summation revisited: Beyond \(\sqrt{2}\). \emph{Psychol Bull} \textbf{144}, 1186--1199 (2018).
 
 \leavevmode\hypertarget{ref-Campbell1965}{}%
-29. F. W. Campbell, D. G. Green, Monocular versus binocular visual acuity. \emph{Nature} \textbf{208}, 191--2 (1965).
+29. Campbell, F. W. \& Green, D. G. Monocular versus binocular visual acuity. \emph{Nature} \textbf{208}, 191--2 (1965).
 
 \leavevmode\hypertarget{ref-Legge1984}{}%
-30. G. E. Legge, Binocular contrast summation--ii. Quadratic summation. \emph{Vision Res} \textbf{24}, 385--94 (1984).
+30. Legge, G. E. Binocular contrast summation--ii. Quadratic summation. \emph{Vision Res} \textbf{24}, 385--94 (1984).
 
 \leavevmode\hypertarget{ref-Baker2007}{}%
-31. D. H. Baker, T. S. Meese, M. A. Georgeson, Binocular interaction: Contrast matching and contrast discrimination are predicted by the same model. \emph{Spat Vis} \textbf{20}, 397--413 (2007).
+31. Baker, D. H., Meese, T. S. \& Georgeson, M. A. Binocular interaction: Contrast matching and contrast discrimination are predicted by the same model. \emph{Spat Vis} \textbf{20}, 397--413 (2007).
 
 \leavevmode\hypertarget{ref-Ding2006}{}%
-32. J. Ding, G. Sperling, A gain-control theory of binocular combination. \emph{Proc Natl Acad Sci U S A} \textbf{103}, 1141--6 (2006).
+32. Ding, J. \& Sperling, G. A gain-control theory of binocular combination. \emph{Proc Natl Acad Sci U S A} \textbf{103}, 1141--6 (2006).
 
 \leavevmode\hypertarget{ref-Meese2006}{}%
-33. T. S. Meese, M. A. Georgeson, D. H. Baker, Binocular contrast vision at and above threshold. \emph{Journal of Vision} \textbf{6}, 1224--43 (2006).
+33. Meese, T. S., Georgeson, M. A. \& Baker, D. H. Binocular contrast vision at and above threshold. \emph{Journal of Vision} \textbf{6}, 1224--43 (2006).
 
 \leavevmode\hypertarget{ref-Kingdom2015}{}%
-34. F. A. A. Kingdom, L. Libenson, Dichoptic color saturation mixture: Binocular luminance contrast promotes perceptual averaging. \emph{J Vis} \textbf{15}, 2 (2015).
+34. Kingdom, F. A. A. \& Libenson, L. Dichoptic color saturation mixture: Binocular luminance contrast promotes perceptual averaging. \emph{J Vis} \textbf{15}, 2 (2015).
 
 \leavevmode\hypertarget{ref-Busse2009}{}%
-35. L. Busse, A. R. Wade, M. Carandini, Representation of concurrent stimuli by population activity in visual cortex. \emph{Neuron} \textbf{64}, 931--42 (2009).
+35. Busse, L., Wade, A. R. \& Carandini, M. Representation of concurrent stimuli by population activity in visual cortex. \emph{Neuron} \textbf{64}, 931--42 (2009).
 
 \leavevmode\hypertarget{ref-Baker2024}{}%
-36. D. H. Baker\emph{et al.}, Binocular integration of chromatic and luminance signals. \emph{Journal of Vision} \textbf{Under review} (2024).
+36. Baker, D. H. \emph{et al.} Binocular integration of chromatic and luminance signals. \emph{Journal of Vision} \textbf{Under review}, (2024).
 
 \leavevmode\hypertarget{ref-Baker2017}{}%
-37. D. H. Baker, A. R. Wade, Evidence for an optimal algorithm underlying signal combination in human visual cortex. \emph{Cereb Cortex} \textbf{27}, 254--264 (2017).
+37. Baker, D. H. \& Wade, A. R. Evidence for an optimal algorithm underlying signal combination in human visual cortex. \emph{Cereb Cortex} \textbf{27}, 254--264 (2017).
 
 \leavevmode\hypertarget{ref-Kaestner2019}{}%
-38. M. Kaestner\emph{et al.}, Asymmetries between achromatic and chromatic extraction of 3D motion signals. \emph{Proc Natl Acad Sci U S A} \textbf{116}, 13631--13640 (2019).
+38. Kaestner, M. \emph{et al.} Asymmetries between achromatic and chromatic extraction of 3D motion signals. \emph{Proc Natl Acad Sci U S A} \textbf{116}, 13631--13640 (2019).
 
@@
 39.
-J.
-T.
 Martin, J.
-Pinto, D.
-Bulte, M.
-Spitschan, PyPlr: A versatile, integrated system of hardware and software for researching the human pupillary light reflex.
+T., Pinto, J., Bulte, D.
+\& Spitschan, M.
+PyPlr: A versatile, integrated system of hardware and software for researching the human pupillary light reflex.
 \emph{Behavior Research Methods} \textbf{54}, 2720--2739 (2022).
@@
 40.
-J.
-T.
-Martin, G.
-M.
-Boynton, D.
-H.
-Baker, A.
+Martin, J.
+T., Boynton, G.
+M., Baker, D.
+H., Wade, A.
 R.
-Wade, M.
-Spitschan, PySilSub: An open-source python toolbox for implementing the method of silent substitution in vision and nonvisual photoreception research.
+\& Spitschan, M.
+PySilSub: An open-source python toolbox for implementing the method of silent substitution in vision and nonvisual photoreception research.
 \emph{Journal of Vision} \textbf{23}, 10 (2023).
@@
 41.
-A.
-Stockman, L.
+Stockman, A.
+\& Sharpe, L.
 T.
-Sharpe, The spectral sensitivities of the middle- and long-wavelength-sensitive cones derived from measurements in observers of known genotype.
+The spectral sensitivities of the middle- and long-wavelength-sensitive cones derived from measurements in observers of known genotype.
 \emph{Vision Res} \textbf{40}, 1711--37 (2000).
@@
 \leavevmode\hypertarget{ref-Barrionuevo2016}{}%
-42. P. A. Barrionuevo, D. Cao, Luminance and chromatic signals interact differently with melanopsin activation to control the pupil light response. \emph{Journal of Vision} \textbf{16(11)}, 29 (2016).
+42.
+Barrionuevo, P.
+A.
+\& Cao, D.
+Luminance and chromatic signals interact differently with melanopsin activation to control the pupil light response.
+\emph{Journal of Vision} \textbf{16(11)}, 29 (2016).
 
 \leavevmode\hypertarget{ref-Spitschan2015}{}%
-43. M. Spitschan, G. K. Aguirre, D. H. Brainard, Selective stimulation of penumbral cones reveals perception in the shadow of retinal blood vessels. \emph{PLoS One} \textbf{10}, e0124328 (2015).
+43. Spitschan, M., Aguirre, G. K. \& Brainard, D. H. Selective stimulation of penumbral cones reveals perception in the shadow of retinal blood vessels. \emph{PLoS One} \textbf{10}, e0124328 (2015).
 
@@
 44.
-A.
-J.
-Zele, B.
-Feigl, P.
-Adhikari, M.
+Zele, A.
+J., Feigl, B., Adhikari, P., Maynard, M.
 L.
-Maynard, D.
-Cao, Melanopsin photoreception contributes to human visual detection, temporal and colour processing.
-\emph{Scientific Reports} \textbf{8} (2018).
+\& Cao, D.
+Melanopsin photoreception contributes to human visual detection, temporal and colour processing.
+\emph{Scientific Reports} \textbf{8}, (2018).
 
@@
 45.
-M.
-Kassner, W.
-Patera, A.
-Bulling, Pupil: An open source platform for pervasive eye tracking and mobile gaze-based interaction.
-in \emph{Proceedings of the 2014 ACM International Joint Conference on Pervasive and Ubiquitous Computing: Adjunct Publication}, (ACM, 2014) \url{https:/doi.org/10.1145/2638728.2641695}.
+Kassner, M., Patera, W.
+\& Bulling, A.
+Pupil: An open source platform for pervasive eye tracking and mobile gaze-based interaction.
+in \emph{Proceedings of the 2014 ACM international joint conference on pervasive and ubiquitous computing: Adjunct publication} (ACM, 2014).
+doi:\href{https://doi.org/10.1145/2638728.2641695}{10.1145/2638728.2641695}.
 
 \leavevmode\hypertarget{ref-Norcia2015}{}%
-46. A. M. Norcia, L. G. Appelbaum, J. M. Ales, B. R. Cottereau, B. Rossion, The steady-state visual evoked potential in vision research: A review. \emph{Journal of Vision} \textbf{15(6)}, 4 (2015).
+46.
+Norcia, A.
+M., Appelbaum, L.
+G., Ales, J.
+M., Cottereau, B.
+R.
+\& Rossion, B.
+The steady-state visual evoked potential in vision research: A review.
+\emph{Journal of Vision} \textbf{15(6)}, 4 (2015).
 
 \leavevmode\hypertarget{ref-Zele2019}{}%
-47. A. J. Zele, P. Adhikari, D. Cao, B. Feigl, Melanopsin driven enhancement of cone-mediated visual processing. \emph{Vision Res} \textbf{160}, 72--81 (2019).
+47. Zele, A. J., Adhikari, P., Cao, D. \& Feigl, B. Melanopsin driven enhancement of cone-mediated visual processing. \emph{Vision Res} \textbf{160}, 72--81 (2019).
 
 \leavevmode\hypertarget{ref-Baker2020}{}%
-48. D. H. Baker\emph{et al.}, Binaural summation of amplitude modulation involves weak interaural suppression. \emph{Sci Rep} \textbf{10}, 3560 (2020).
+48. Baker, D. H. \emph{et al.} Binaural summation of amplitude modulation involves weak interaural suppression. \emph{Sci Rep} \textbf{10}, 3560 (2020).
 
 \leavevmode\hypertarget{ref-Carroll2002}{}%
-49. J. Carroll, J. Neitz, M. Neitz, Estimates of L:M cone ratio from ERG flicker photometry and genetics. \emph{Journal of Vision} \textbf{2}, 1 (2002).
+49. Carroll, J., Neitz, J. \& Neitz, M. Estimates of L:M cone ratio from ERG flicker photometry and genetics. \emph{Journal of Vision} \textbf{2}, 1 (2002).
 
 \leavevmode\hypertarget{ref-Hofer2005}{}%
-50. H. Hofer, J. Carroll, J. Neitz, M. Neitz, D. R. Williams, Organization of the human trichromatic cone mosaic. \emph{The Journal of Neuroscience} \textbf{25}, 9669--9679 (2005).
+50. Hofer, H., Carroll, J., Neitz, J., Neitz, M. \& Williams, D. R. Organization of the human trichromatic cone mosaic. \emph{The Journal of Neuroscience} \textbf{25}, 9669--9679 (2005).
 
 \leavevmode\hypertarget{ref-Baker2021}{}%
-51. D. H. Baker, Statistical analysis of periodic data in neuroscience. \emph{Neurons, Behavior, Data analysis, and Theory} \textbf{5} (2021).
+51. Baker, D. H. Statistical analysis of periodic data in neuroscience. \emph{Neurons, Behavior, Data analysis, and Theory} \textbf{5}, (2021).
 
 \leavevmode\hypertarget{ref-Carpenter2017}{}%
-52. B. Carpenter\emph{et al.}, Stan: A probabilistic programming language. \emph{J Stat Softw} \textbf{76} (2017).
+52. Carpenter, B. \emph{et al.} Stan: A probabilistic programming language. \emph{J Stat Softw} \textbf{76}, (2017).
+
+\hypertarget{acknowledgements}{%
+\section{Acknowledgements}\label{acknowledgements}}
+
+Supported by Biotechnology and Biological Sciences Research Council grant BB/V007580/1 awarded to DHB and ARW.
+
+\hypertarget{author-contributions}{%
+\section{Author contributions}\label{author-contributions}}
+
+D.H.B.
+and A.R.W.
+conceived the project D.H.B, A.R.W., and A.B.
+supervised the project.
+F.G.S., J.T.M., A.R.W., and D.H.B.
+designed the experiments.
+F.G.S., J.T.M., and A.Y.M.
+performed the experiments and collected the data.
+F.G.S and D.H.B.
+analysed the data and implemented the computational model.
+F.G.S.
+and D.H.B.
+wrote the manuscript with input from all authors.
+A.B., J.T.M., A.Y.M., and A.R.W.
+provided feedback on the manuscript.
+
+\hypertarget{competing-interests}{%
+\section{Competing interests}\label{competing-interests}}
+
+The authors declare no competing interests.
+
+\hypertarget{materials-and-correspondence}{%
+\section{Materials and Correspondence}\label{materials-and-correspondence}}
+
+Correspondence and material requests should be addressed to \href{federico.segala@york.ac.uk}{Federico G. Segala}.
 

### 2024-07-09 manuscript.Rmd
Condensed abstract, added line numbers

@@
   \usepackage{caption}
+  \usepackage{lineno} \linenumbers
 ---
@@
 
-The diameter of the pupil fluctuates in response to levels of ambient light and is regulated by the autonomic nervous system.
-Increasing light in one eye causes both pupils to constrict, implying the system must combine signals across the two eyes -- a process of binocular integration occurring independently of visual cortex.
-Distinct classes of retinal photoreceptor are involved in controlling and maintaining pupil diameter, with cones and rods driving the initial constriction and intrinsically photosensitive retinal ganglion cells maintaining diameter over prolonged time periods.
-Here, we investigate binocular combination by targeting different photoreceptor pathways using the silent substitution method to modulate the input spectra.
-We find different patterns of binocular response in each pathway, and across the first and second harmonic frequencies.
-At the first harmonic, luminance and S-cone responses showed strong binocular facilitation, and weak interocular suppression.
+Pupil diameters are regulated by the autonomic nervous system, which combines light signals across the eyes independently of the visual cortex.
+Distinct classes of retinal photoreceptor are involved in this process, with cones and rods driving the initial constriction and intrinsically photosensitive retinal ganglion cells maintaining diameter over prolonged time periods.
+We investigated binocular combination by targeting different photoreceptor pathways using a novel binocular multiprimary system to modulate the input spectra via silent substitution.
+At the first harmonic of the modulation frequency, luminance and S-cone responses showed strong binocular facilitation, and weak interocular suppression.
 Melanopsin responses were invariant to the number of eyes stimulated.

### 2024-07-09 manuscript.tex
Condensed abstract, added line numbers

--- 2024-06-06 manuscript.tex
@@
 \PassOptionsToPackage{hyphens}{url}
-\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
+\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
 %
@@
 ]{article}
-\usepackage{lmodern}
-\usepackage{amssymb,amsmath}
-\usepackage{ifxetex,ifluatex}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+\usepackage{amsmath,amssymb}
+\usepackage{iftex}
+\ifPDFTeX
   \usepackage[T1]{fontenc}
@@
 \else % if luatex or xetex
-  \usepackage{unicode-math}
+  \usepackage{unicode-math} % this also loads fontspec
   \defaultfontfeatures{Scale=MatchLowercase}
   \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+\usepackage{lmodern}
+\ifPDFTeX\else
+  % xetex/luatex font selection
 \fi
@@
 \usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdftitle={Binocular combination in the autonomic nervous system},
-  colorlinks=true,
-  linkcolor=black,
-  filecolor=Maroon,
-  citecolor=Blue,
-  urlcolor=Blue,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
 \usepackage[margin=1in]{geometry}
-\usepackage{longtable,booktabs}
+\usepackage{longtable,booktabs,array}
+\usepackage{calc} % for calculating minipage widths
 % Correct order of tables after \paragraph or \subparagraph
@@
 \makesavenoteenv{longtable}
-\usepackage{graphicx,grffile}
+\usepackage{graphicx}
 \makeatletter
@@
 \setcounter{secnumdepth}{5}
+% definitions for citeproc citations
+\NewDocumentCommand\citeproctext{}{}
+\NewDocumentCommand\citeproc{mm}{%
+  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
+\makeatletter
+ % allow citations to break across lines
+ \let\@cite@ofmt\@firstofone
+ % avoid brackets around text for \cite:
+ \def\@biblabel#1{}
+ \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
+\makeatother
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
+ {\begin{list}{}{%
+  \setlength{\itemindent}{0pt}
+  \setlength{\leftmargin}{0pt}
+  \setlength{\parsep}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+   \setlength{\leftmargin}{\cslhangindent}
+   \setlength{\itemindent}{-1\cslhangindent}
+  \fi
+  % set entry spacing
+  \setlength{\itemsep}{#2\baselineskip}}}
+ {\end{list}}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 \usepackage{caption} \usepackage{lineno} \linenumbers
@@
 \usepackage{xcolor}
+\ifLuaTeX
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
+\usepackage{bookmark}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same}
+\hypersetup{
+  pdftitle={Binocular combination in the autonomic nervous system},
+  colorlinks=true,
+  linkcolor={black},
+  filecolor={Maroon},
+  citecolor={Blue},
+  urlcolor={Blue},
+  pdfcreator={LaTeX via pandoc}}
 
 \title{Binocular combination in the autonomic nervous system}
-\author{Federico G. Segala\(^1\), Aurelio Bruno\(^{1,2}\), Joel T. Martin\(^{1,3}\),\\
+\author{Federico G. Segala\(^1\)*, Aurelio Bruno\(^{1,2}\), Joel T. Martin\(^{1,3}\),\\
 Anisa Y. Morsi\(^1\), Alex R. Wade\(^{1,4}\) \& Daniel H. Baker\(^{1,4}\)}
@@
 
-Address for correspondence: Federico G. Segala, \url{federico.segala@york.ac.uk}
+*Corresponding author
 
-\hypertarget{abstract-250-words}{%
-\section{Abstract (250 words)}\label{abstract-250-words}}
+\section{Abstract}\label{abstract}
 
-The diameter of the pupil fluctuates in response to levels of ambient light and is regulated by the autonomic nervous system.
-Increasing light in one eye causes both pupils to constrict, implying the system must combine signals across the two eyes -- a process of binocular integration occurring independently of visual cortex.
-Distinct classes of retinal photoreceptor are involved in controlling and maintaining pupil diameter, with cones and rods driving the initial constriction and intrinsically photosensitive retinal ganglion cells maintaining diameter over prolonged time periods.
-Here, we investigate binocular combination by targeting different photoreceptor pathways using the silent substitution method to modulate the input spectra.
-We find different patterns of binocular response in each pathway, and across the first and second harmonic frequencies.
-At the first harmonic, luminance and S-cone responses showed strong binocular facilitation, and weak interocular suppression.
+Pupil diameters are regulated by the autonomic nervous system, which combines light signals across the eyes independently of the visual cortex.
+Distinct classes of retinal photoreceptor are involved in this process, with cones and rods driving the initial constriction and intrinsically photosensitive retinal ganglion cells maintaining diameter over prolonged time periods.
+We investigated binocular combination by targeting different photoreceptor pathways using a novel binocular multiprimary system to modulate the input spectra via silent substitution.
+At the first harmonic of the modulation frequency, luminance and S-cone responses showed strong binocular facilitation, and weak interocular suppression.
 Melanopsin responses were invariant to the number of eyes stimulated.
@@
 
-\hypertarget{significance-statement-120-words}{%
-\section{Significance statement (120 words)}\label{significance-statement-120-words}}
+\section{Introduction}\label{introduction}
 
-The diameter of the pupil depends on the level of ambient light and is controlled by distinct retinal photoreceptor classes (cones, rods and intrinsically photosensitive retinal ganglion cells).
-The computational processes behind binocular integration within the subcortical pathways controlling pupil dimension have been investigated and have been shown to occur independently of visual cortex.
-We investigated binocular combination within the different photoreceptor pathways using silent substitution.
-We found different patterns of binocular combination in each pathway and also differences in the phase of the pupil response.
-The results are consistent with a computational model of binocular signal combination, where the weight of interocular suppression differs across pathways, and demonstrate the algorithm governing binocular combination in the autonomic nervous system.
-
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
-
-The autonomic nervous system regulates many involuntary bodily processes, including the constriction and dilation of the pupils in response to light (\protect\hyperlink{ref-McDougal2015}{1}).
-The anatomical pathway from the retina to the subcortical nuclei controlling the pupillary light response (PLR) is well established: it includes the Pretectal Olivary nucleus (PON), the Superior Cervical ganglion and the Edinger-Westphal nucleus, which project to the iris sphincter muscles that directly control the pupil size (\protect\hyperlink{ref-McDougal2015}{1}--\protect\hyperlink{ref-Wang2015}{3}).
-Evidence of a binocular component to the PLR is shown by the existence of a consensual response of the pupil (\protect\hyperlink{ref-Wyatt1981}{4}).
+The autonomic nervous system regulates many involuntary bodily processes, including the constriction and dilation of the pupils in response to light\textsuperscript{\citeproc{ref-McDougal2015}{1}}.
+The anatomical pathway from the retina to the subcortical nuclei controlling the pupillary light response (PLR) is well established: it includes the Pretectal Olivary nucleus (PON), the Superior Cervical ganglion and the Edinger-Westphal nucleus, which project to the iris sphincter muscles that directly control the pupil size\textsuperscript{\citeproc{ref-McDougal2015}{1}--\citeproc{ref-Wang2015}{3}}.
+Evidence of a binocular component to the PLR is shown by the existence of a consensual response of the pupil (the stimulation of one eye will cause constriction of the other eye)\textsuperscript{\citeproc{ref-Wyatt1981}{4}}.
 The anatomical segregation of the subcortical pathway from the rest of the brain means that this binocular combination of signals must occur independently of the cortical processes of binocular integration required for visual perception.
-Our recent work (\protect\hyperlink{ref-Segala2023}{5}) has shown that the algorithm underlying binocular combination of light in the pupil pathway differs from that in the cortex.
+Our recent work\textsuperscript{\citeproc{ref-Segala2023}{5}} has shown that the algorithm underlying binocular combination of light in the pupil pathway differs from that in the cortex.
 Here we extend this paradigm to compare binocular combination in different photoreceptor pathways that feed into the autonomic nervous system.
 
-Different classes of retinal photoreceptors, including cones, rods and melanopsin-containing intrinsically photosensitive retinal ganglion cells (ipRGCs), are directly involved in controlling and maintaining the size of the pupils (\protect\hyperlink{ref-Barrionuevo2014}{6}--\protect\hyperlink{ref-Woelders2018}{12}).
-The cones have been shown to drive the initial rapid constriction of the pupils (\protect\hyperlink{ref-Mathot2018}{13}), while the slower and longer activation of the ipRGCs shows their role in maintaining the constriction over a prolonged period of time and in regulating the post-illumination pupillary response (\protect\hyperlink{ref-Markwell2010}{14}, \protect\hyperlink{ref-McDougal2010}{15}).
-The ipRGCs are a unique photoreceptor class that has been discovered recently (\protect\hyperlink{ref-Provencio2000}{16}).
-They express the photopigment melanopsin, and are involved in the regulation of the circadian rhythm (\protect\hyperlink{ref-Provencio2000}{16}--\protect\hyperlink{ref-Ruby2002}{18}), forming a major input to the PON (\protect\hyperlink{ref-Dacey2003}{19}).
-The first direct evidence of the involvement of the ipRGCs in the PLR was shown in melanopsin knockout rats by (\protect\hyperlink{ref-Lucas2003}{20}), resulting in the loss of the intrinsic photosensitivity of the cells and a reduced pupil constriction.
-This same behaviour was later also observed in primates and humans (\protect\hyperlink{ref-Gamlin2007}{21}), where it was demonstrated that the PLR continues during light presentation even when cone and rod signalling is blocked, indicating the primary role of the ipRGCs in maintaining pupil constriction over a prolonged time.
+Different classes of retinal photoreceptors, including cones, rods and melanopsin-containing intrinsically photosensitive retinal ganglion cells (ipRGCs), are directly involved in controlling and maintaining the size of the pupils\textsuperscript{\citeproc{ref-Barrionuevo2014}{6}--\citeproc{ref-Woelders2018}{12}}.
+The cones have been shown to drive the initial rapid constriction of the pupils\textsuperscript{\citeproc{ref-Mathot2018}{13}}, while the slower and longer activation of the ipRGCs shows their role in maintaining the constriction over a prolonged period of time and in regulating the post-illumination pupillary response\textsuperscript{\citeproc{ref-Markwell2010}{14},\citeproc{ref-McDougal2010}{15}}.
+The ipRGCs are a unique photoreceptor class that has been discovered recently\textsuperscript{\citeproc{ref-Provencio2000}{16}}.
+They express the photopigment melanopsin, and are involved in the regulation of the circadian rhythm\textsuperscript{\citeproc{ref-Provencio2000}{16}--\citeproc{ref-Ruby2002}{18}}, forming a major input to the PON\textsuperscript{\citeproc{ref-Dacey2003}{19}}.
+The first direct evidence of the involvement of the ipRGCs in the PLR was shown in melanopsin knockout rats by Lucas et al.\textsuperscript{\citeproc{ref-Lucas2003}{20}}, resulting in the loss of the intrinsic photosensitivity of the cells and a reduced pupil constriction.
+This same behaviour was later also observed in primates and humans\textsuperscript{\citeproc{ref-Gamlin2007}{21}}, where it was demonstrated that the PLR continues during light presentation even when cone and rod signalling is blocked, indicating the primary role of the ipRGCs in maintaining pupil constriction over a prolonged time.
 
-A technique known as silent substitution (\protect\hyperlink{ref-Estevez1982}{22}) can be used to selectively stimulate specific photoreceptor classes.
+A technique known as silent substitution\textsuperscript{\citeproc{ref-Estevez1982}{22}} can be used to selectively stimulate specific photoreceptor classes.
 Silent substitution exploits the fact that each photoreceptor class has a distinct spectral tuning that overlaps with the others.
-Using a multiprimary system, in which the primaries (i.e.~LEDs) have different spectra, it is possible to target one class of photoreceptors while maintaining the others at a constant activity level, effectively silencing them (\protect\hyperlink{ref-Shapiro1996}{23}, \protect\hyperlink{ref-Spitschan2018}{24}).
+Using a multiprimary system, in which the primaries (i.e.~LEDs) have different spectra, it is possible to target one class of photoreceptors while maintaining the others at a constant activity level, effectively silencing them\textsuperscript{\citeproc{ref-Shapiro1996}{23},\citeproc{ref-Spitschan2018}{24}, this paper also offers a clear explanation of how to implement silent substitution}.
 Studies using silent substitution have shown that the pupils behave differently depending on which photoreceptor or pathway is being stimulated.
-For example, pupil responses have been shown to be out of phase when the S cones are stimulated, relative to when the ipRGCs or the L+M cones are stimulated (\protect\hyperlink{ref-Spitschan2014}{10}, \protect\hyperlink{ref-Cao2015}{25}).
-Additionally, when L and M cones are stimulated individually, there appears to be a paradoxical pupil response: increments in L cone stimulation cause a constriction of the pupil, while increments in M cone stimulation lead to a dilation of the pupil (\protect\hyperlink{ref-Murray2018}{9}, \protect\hyperlink{ref-Woelders2018}{12}), perhaps due to activity in the L-M opponent pathway.
+For example, pupil responses have been shown to be out of phase when the S cones are stimulated, relative to when the ipRGCs or the L+M cones are stimulated\textsuperscript{\citeproc{ref-Spitschan2014}{10},\citeproc{ref-Cao2015}{25}}.
+Additionally, when L and M cones are stimulated individually, there appears to be a paradoxical pupil response: increments in L cone stimulation cause a constriction of the pupil, while increments in M cone stimulation lead to a dilation of the pupil\textsuperscript{\citeproc{ref-Murray2018}{9},\citeproc{ref-Woelders2018}{12}}, perhaps due to activity in the L-M opponent pathway.
 
-Binocular combination has been extensively studied in visual perception, where it is mediated by neurons in primary visual cortex (\protect\hyperlink{ref-Hubel1962}{26}, \protect\hyperlink{ref-Moradi2009}{27}).
-For pattern vision, binocular summation occurs at threshold, such that a lower contrast is required to detect a target shown to both eyes than a target shown to only one eye (\protect\hyperlink{ref-Baker2018}{28}--\protect\hyperlink{ref-Legge1984}{30}).
-At higher contrasts, a process of `ocularity invariance' is observed, in which the response to monocularly- and binocularly-presented patterns is equal (\protect\hyperlink{ref-Moradi2009}{27}, \protect\hyperlink{ref-Baker2007}{31}--\protect\hyperlink{ref-Meese2006}{33}).
+Binocular combination has been extensively studied in visual perception, where it is mediated by neurons in primary visual cortex\textsuperscript{\citeproc{ref-Hubel1962}{26},\citeproc{ref-Moradi2009}{27}}.
+For pattern vision, binocular summation occurs at threshold, such that a lower contrast is required to detect a target shown to both eyes than a target shown to only one eye\textsuperscript{\citeproc{ref-Baker2018}{28}--\citeproc{ref-Legge1984}{30}}.
+At higher contrasts, a process of `ocularity invariance' is observed, in which the response to monocularly- and binocularly-presented patterns is equal\textsuperscript{\citeproc{ref-Moradi2009}{27},\citeproc{ref-Baker2007}{31}--\citeproc{ref-Meese2006}{33}}.
 This is thought to be due to a process of interocular suppression that compensates for the additional excitatory drive caused by stimulating two eyes.
-Our recent work (\protect\hyperlink{ref-Segala2023}{5}) has shown that cortical signal combination for luminance flicker is substantially more linear than for spatial patterns, whereas there is evidence of interocular suppression in the pupil pathway.
+Our recent work\textsuperscript{\citeproc{ref-Segala2023}{5}} has shown that cortical signal combination for luminance flicker is substantially more linear than for spatial patterns, whereas there is evidence of interocular suppression in the pupil pathway.
 
 Most studies that use silent substitution to investigate the PLR stimulate only one eye.
-If the stimulated eye is pharmacologically dilated to control pupil size, the response from the unstimulated eye (known as the consensual response) can be recorded (\protect\hyperlink{ref-Spitschan2014}{10}, \protect\hyperlink{ref-McDougal2010}{15}).
+If the stimulated eye is pharmacologically dilated to control pupil size, the response from the unstimulated eye (known as the consensual response) can be recorded\textsuperscript{\citeproc{ref-Spitschan2014}{10},e.g.
+\citeproc{ref-McDougal2010}{15}}.
 While this approach controls the total amount of light incident at the retina, it does not permit investigation of binocular combination for specific photoreceptor pathways.
@@
 Our key comparisons are between monocular and binocular stimulation, and between monocular stimulation and a dichoptic masking condition in which the two eyes are stimulated at different frequencies (0.5 and 0.4Hz).
-The results are interpreted using a contemporary model of binocular vision (\protect\hyperlink{ref-Meese2006}{33}) implemented within a hierarchical Bayesian framework.
+The results are interpreted using a contemporary model of binocular vision\textsuperscript{\citeproc{ref-Meese2006}{33}} implemented within a hierarchical Bayesian framework.
 
-\hypertarget{results}{%
-\section{Results}\label{results}}
+\section{Results}\label{results}
 
@@
 
-In contemporary models of binocular signal combination, the amount of binocular facilitation is determined by the magnitude of interocular suppression, with strong suppression reducing facilitation (\protect\hyperlink{ref-Kingdom2015}{34}).
+In contemporary models of binocular signal combination, the amount of binocular facilitation is determined by the magnitude of interocular suppression, with strong suppression reducing facilitation\textsuperscript{\citeproc{ref-Kingdom2015}{34}}.
 We can estimate the strength of interocular suppression by measuring how much monocular responses are reduced when a dichoptic `mask' is shown to the other eye.
-In our paradigm, the two components flickered at different frequencies (0.5 and 0.4Hz) so that their responses remained distinct in the Fourier spectrum (\protect\hyperlink{ref-Busse2009}{35}).
+In our paradigm, the two components flickered at different frequencies (0.5 and 0.4Hz) so that their responses remained distinct in the Fourier spectrum\textsuperscript{e.g.
+\citeproc{ref-Busse2009}{35}}.
 The yellow diamond symbols in Figure \ref{fig:FirstHarmonicPlots}a-d show the target responses in this condition, and in most cases were weaker than the monocular responses (red circles).
@@
 
-To estimate the extent of interocular suppression for each photoreceptor pathway, we fitted each data set using a Bayesian hierarchical implementation of a simple binocular combination model (\protect\hyperlink{ref-Segala2023}{5}, \protect\hyperlink{ref-Meese2006}{33}).
+To estimate the extent of interocular suppression for each photoreceptor pathway, we fitted each data set using a Bayesian hierarchical implementation of a simple binocular combination model\textsuperscript{\citeproc{ref-Segala2023}{5},\citeproc{ref-Meese2006}{33}}.
 Our primary objective was to compare posterior distributions of the weight of interocular suppression, which are shown in Figure \ref{fig:FirstHarmonicPlots}e.
@@
 
-Finally, we inspected the response phase of our four stimulation conditions, given previous reports that these differ across pathways (\protect\hyperlink{ref-Spitschan2014}{10}), and may be in antiphase for melanopsin and S-cone signals.
+Finally, we inspected the response phase of our four stimulation conditions, given previous reports that these differ across pathways\textsuperscript{\citeproc{ref-Spitschan2014}{10}}, and may be in antiphase for melanopsin and S-cone signals.
 Figure \ref{fig:phaseplots} shows the phase angles for the first (a) and second (b) harmonic frequencies for binocular stimulation (monocular stimulation produced very similar results).
@@
 This is the first study to investigate binocular interactions in the melanopsin pathway directly.
-A previous meta-analysis (\protect\hyperlink{ref-Spitschan2019}{11}) indicated that there may be a substantial binocular facilitation effect in the circadian pathway, as indexed by melatonin suppression (melatonin is a hormone released by the pineal gland; its production is suppressed by exposure to bright light, particularly when the melanopsin-containing ipRGCs are stimulated).
+A previous meta-analysis\textsuperscript{\citeproc{ref-Spitschan2019}{11}} indicated that there may be a substantial binocular facilitation effect in the circadian pathway, as indexed by melatonin suppression (melatonin is a hormone released by the pineal gland; its production is suppressed by exposure to bright light, particularly when the melanopsin-containing ipRGCs are stimulated).
 In brief, monocular stimulation of the ipRGCs requires up to ten times the signal strength to produce an equivalent effect to binocular stimulation.
@@
 The explanation for this difference could be due to different anatomical pathways.
-Binocular combination in the circadian system likely takes place in the suprachiasmatic nucleus, whereas in the pupil constriction circuit the Edinger-Westphal nucleus is the most likely site of binocular integration (\protect\hyperlink{ref-Mathot2018}{13}).
+Binocular combination in the circadian system likely takes place in the suprachiasmatic nucleus, whereas in the pupil constriction circuit the Edinger-Westphal nucleus is the most likely site of binocular integration\textsuperscript{\citeproc{ref-Mathot2018}{13}}.
 Presumably these anatomical differences, and the practical constraints of the two systems, lead to differences in response.
 
-Our recent psychophysical work (\protect\hyperlink{ref-Baker2024}{36}) has looked at binocular interactions in the L-M and S-cone pathways, and compared these to the luminance pathway.
-Using a contrast discrimination paradigm with spatial modulations of luminance and colour, (\protect\hyperlink{ref-Baker2024}{36}) found equally strong interocular suppression in all three pathways.
+Our recent psychophysical work\textsuperscript{\citeproc{ref-Baker2024}{36}} has looked at binocular interactions in the L-M and S-cone pathways, and compared these to the luminance pathway.
+Using a contrast discrimination paradigm with spatial modulations of luminance and colour, we found equally strong interocular suppression in all three pathways.
 This is rather different from our pupillometry results here, which demonstrate weaker suppression in the luminance and S-cone pathways than in the L-M pathway (see Figure \ref{fig:FirstHarmonicPlots}).
-However, the current experiments involve temporal modulations, which are quite distinct from the spatial modulations used in (\protect\hyperlink{ref-Baker2024}{36}).
-Our other recent work (\protect\hyperlink{ref-Segala2023}{5}) has shown that temporal luminance modulations involve much weaker interocular suppression in the cortical response than do spatial luminance modulations (\protect\hyperlink{ref-Baker2017}{37}).
+However, the current experiments involve temporal modulations, which are quite distinct from the spatial modulations used in our previous work\textsuperscript{\citeproc{ref-Baker2024}{36}}.
+Our other recent work\textsuperscript{\citeproc{ref-Segala2023}{5}} has shown that temporal luminance modulations involve much weaker interocular suppression in the cortical response than do spatial luminance modulations\textsuperscript{\citeproc{ref-Baker2017}{37}}.
 These different normalization processes might reflect different priorities for spatial and temporal vision.
-Spatial vision aims to fuse images to provide binocular single vision, and benefits from `ocularity invariance' (\protect\hyperlink{ref-Baker2007}{31}), in which visual appearance is constant when viewed with one eye or two.
-Temporal vision is critical for motion perception, which can involve alternative binocular computations, such as calculating velocity differences between the eyes (\protect\hyperlink{ref-Kaestner2019}{38}).
+Spatial vision aims to fuse images to provide binocular single vision, and benefits from `ocularity invariance'\textsuperscript{\citeproc{ref-Baker2007}{31}}, in which visual appearance is constant when viewed with one eye or two.
+Temporal vision is critical for motion perception, which can involve alternative binocular computations, such as calculating velocity differences between the eyes\textsuperscript{\citeproc{ref-Kaestner2019}{38}}.
 Of course the present measurements were of pupil size, which may be subject to different anatomical and functional constraints from those in the cortex.
@@
 
-\hypertarget{materials-and-methods}{%
-\section{Materials and methods}\label{materials-and-methods}}
+\section{Methods}\label{methods}
 
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
+\subsection{Participants}\label{participants}
 
@@
 
-\hypertarget{apparatus-stimuli}{%
-\subsection{Apparatus \& stimuli}\label{apparatus-stimuli}}
+\subsection{Apparatus \& stimuli}\label{apparatus-stimuli}
 
 To present synchronised stimulus modulations independently to each eye, two light engines (SpectraTuneLAB: LEDMOTIVE Technologies, LLC, Barcelona, Spain), each with 10 independently addressable LED colour channels, were integrated into a customised viewing system.
-The light engines were operated via a Python interface to their REST API (\protect\hyperlink{ref-Martin2022}{39}), which supports synchronous launch and playback of spectral sequences prepared in advance and stored in JSON format.
+The light engines were operated via a Python interface to their REST API\textsuperscript{\citeproc{ref-Martin2022}{39}}, which supports synchronous launch and playback of spectral sequences prepared in advance and stored in JSON format.
 When preparing the spectral sequences, the age of participants was used to account for the yellowing of the lenses.
-We calculated silent substitution solutions using the \emph{PySilSub} toolbox (\protect\hyperlink{ref-Martin2023}{40}), using linear algebra.
+We calculated silent substitution solutions using the \emph{PySilSub} toolbox\textsuperscript{\citeproc{ref-Martin2023}{40}}, using linear algebra.
 The outputs of the two light engines (see Figure \ref{fig:spectraplots}b,c) were calibrated using an Ocean Optics Jaz spectroradiometer, which was wavelength-calibrated to an Argon lamp and intensity calibrated using a NIST-traceable light source.
-We used the (\protect\hyperlink{ref-Stockman2000}{41}) 10-degree cone fundamentals, and estimates of melanopsin absorbance spectra from CIE S 026 (\protect\hyperlink{ref-Martin2023}{40}) to calculate \(\alpha\)-opic irradiance.
+We used the Stockman and Sharpe 10-degree cone fundamentals\textsuperscript{\citeproc{ref-Stockman2000}{41}}, and estimates of melanopsin absorbance spectra from CIE S 026\textsuperscript{discussed in \citeproc{ref-Martin2023}{40}} to calculate \(\alpha\)-opic irradiance.
 
@@
 The diffuser discs were positioned in the objective planes of the lenses of a modified VR headset (SHINECON SC-G01, Dongguan Shinecon Industrial Co.~Ltd., Guangdong, China), which was used by the participants to view the stimuli.
-The stimuli were two discs of flickering light with a diameter of approximately 30 degrees, which were fused together into a cyclopean percept resembling a donut-shaped ring of light, similar to that used in other studies (\protect\hyperlink{ref-Murray2018}{9}, \protect\hyperlink{ref-Spitschan2014}{10}, \protect\hyperlink{ref-Barrionuevo2016}{42}--\protect\hyperlink{ref-Zele2018}{44}).
+The stimuli were two discs of flickering light with a diameter of approximately 30 degrees, which were fused together into a cyclopean percept resembling a donut-shaped ring of light, similar to that used in other studies\textsuperscript{\citeproc{ref-Murray2018}{9},\citeproc{ref-Spitschan2014}{10},e.g., \citeproc{ref-Barrionuevo2016}{42},\citeproc{ref-Spitschan2015}{43},\citeproc{ref-Zele2018}{44}}.
 The VR headset modifications allowed for small adjustments to account for individual differences in interpupillary distance and focal length.
-The use of this set up allowed us to modulate the stimuli in three different ocular configurations, similar to the ones we used in our previous study (\protect\hyperlink{ref-Segala2023}{5}): monocular, binocular and dichoptic.
+The use of this set up allowed us to modulate the stimuli in three different ocular configurations, similar to the ones we used in our previous study\textsuperscript{\citeproc{ref-Segala2023}{5}}: monocular, binocular and dichoptic.
 In the monocular configuration, the unstimulated eye still saw a non-flickering disc of mean luminance.
 A schematic of the stimulation system is shown in Figure \ref{fig:spectraplots}a.
-Pupillometry data were collected using a binocular Pupil Core eye-tracker headset (\protect\hyperlink{ref-Kassner2014}{45}) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
+Pupillometry data were collected using a binocular Pupil Core eye-tracker headset (Pupil Labs GmbH, Berlin, Germany)\textsuperscript{\citeproc{ref-Kassner2014}{45}} running at 120 Hz, and the signals were recorded with the Pupil Capture software.
 
-Our previous study (\protect\hyperlink{ref-Segala2023}{5}) used a temporal frequency of 2Hz for foveal luminance flicker, and recorded EEG data simultaneously with pupillometry.
+Our previous study\textsuperscript{\citeproc{ref-Segala2023}{5}} used a temporal frequency of 2Hz for foveal luminance flicker, and recorded EEG data simultaneously with pupillometry.
 Initial pilot experiments indicated that this frequency was too high to elicit measurable responses when stimulating individual photoreceptor pathways.
-For all experiments, we therefore used a primary flicker frequency of 0.5Hz, as previous literature showed that this was slow enough to elicit a pupil response from all photoreceptor classes (\protect\hyperlink{ref-Spitschan2014}{10}).
-We also focussed on only recording pupillometry data as this frequency would be too slow to elicit steady-state EEG responses (\protect\hyperlink{ref-Norcia2015}{46}).
+For all experiments, we therefore used a primary flicker frequency of 0.5Hz, as previous literature showed that this was slow enough to elicit a pupil response from all photoreceptor classes\textsuperscript{\citeproc{ref-Spitschan2014}{10}}.
+We also focussed on only recording pupillometry data as this frequency would be too slow to elicit steady-state EEG responses\textsuperscript{\citeproc{ref-Norcia2015}{46}}.
 
@@
 Splatter on nominally silenced photoreceptors was very small (see Figure \ref{fig:spectraplots}j-l), well below the levels that would be expected to generate measureable pupil modulations.
-We also estimated activation of penumbral L and M cones (\protect\hyperlink{ref-Barrionuevo2016}{42}, \protect\hyperlink{ref-Spitschan2015}{43}, \protect\hyperlink{ref-Zele2019}{47}), which was minimal (\(\le 1.5%
+We also estimated activation of penumbral L and M cones\textsuperscript{\citeproc{ref-Barrionuevo2016}{42},\citeproc{ref-Spitschan2015}{43},\citeproc{ref-Zele2019}{47}}, which was minimal (\(\le 1.5%
 \) contrast; less than splatter on the open-field cones) for melanopsin-directed stimuli.
-We note that the temporal frequency of our modulation (0.5Hz) is well below the range where penumbral cone activation can elicit visible percepts, and that such percepts fade after around 1 second (\protect\hyperlink{ref-Spitschan2015}{43}), and do not typically affect pupil responses (\protect\hyperlink{ref-Spitschan2014}{10}).
+We note that the temporal frequency of our modulation (0.5Hz) is well below the range where penumbral cone activation can elicit visible percepts, and that such percepts fade after around 1 second\textsuperscript{\citeproc{ref-Spitschan2015}{43}}, and do not typically affect pupil responses\textsuperscript{\citeproc{ref-Spitschan2014}{10}}.
 
-\hypertarget{procedure}{%
-\subsection{Procedure}\label{procedure}}
+\subsection{Procedure}\label{procedure}
 
@@
 Pupil responses to binocular temporal contrast modulations were examined in a factorial design that combined six ocular conditions and five temporal contrast levels: 6, 12, 24, 48 and 96\% of the available dynamic range.
-This design, similar to that used in our previous studies (\protect\hyperlink{ref-Segala2023}{5}, \protect\hyperlink{ref-Baker2017}{37}, \protect\hyperlink{ref-Baker2020}{48}), was applied in four separate experiments, each with a different mode of photoreceptor stimulation.
+This design, similar to that used in our previous studies\textsuperscript{\citeproc{ref-Segala2023}{5},\citeproc{ref-Baker2017}{37},\citeproc{ref-Baker2020}{48}}, was applied in four separate experiments, each with a different mode of photoreceptor stimulation.
 In the first three conditions, the discs flickered at 0.5 Hz, in either a monocular, binocular or dichoptic arrangement.
@@
 Using a trackball, participants adjusted the angle in cone space to find their subjective isoluminant point, which resulted in changing the flickering intensity of the stimulus until the amplitude of the flicker appeared to be minimised.
-The result was used to modify the requested contrasts during stimulus preparation so as to account for individual differences affecting perceived illuminance, principally the L:M cone ratio (\protect\hyperlink{ref-Carroll2002}{49}, \protect\hyperlink{ref-Hofer2005}{50}).
+The result was used to modify the requested contrasts during stimulus preparation so as to account for individual differences affecting perceived illuminance, principally the L:M cone ratio\textsuperscript{\citeproc{ref-Carroll2002}{49},\citeproc{ref-Hofer2005}{50}}.
 
-\hypertarget{data-analysis}{%
-\subsection{Data analysis}\label{data-analysis}}
+\subsection{Data analysis}\label{data-analysis}
 
-The pupillometry data were analysed using the same method we used in our previous study (\protect\hyperlink{ref-Segala2023}{5}).
-The data were converted from mp4 videos to a csv text file using the Pupil Player software (\protect\hyperlink{ref-Kassner2014}{45}), which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
+The pupillometry data were analysed using the same method we used in our previous study\textsuperscript{\citeproc{ref-Segala2023}{5}}.
+The data were converted from mp4 videos to a csv text file using the Pupil Player software\textsuperscript{\citeproc{ref-Kassner2014}{45}}, which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
 The individual data were then loaded into R for analysis, where a ten-second waveform for each trial in each eye was extracted (excluding the first two seconds after stimulus onset).
@@
 Finally, data were averaged across all participants to obtain the group results.
-We used coherent averaging and at each stage we excluded data points with a Mahalanobis distance exceeding \(D\) = 3 from the complex-valued mean (\protect\hyperlink{ref-Baker2021}{51}).
+We used coherent averaging and at each stage we excluded data points with a Mahalanobis distance exceeding \(D\) = 3 from the complex-valued mean\textsuperscript{\citeproc{ref-Baker2021}{51}}.
 For monocular stimulation, we confirmed that the consensual response was equivalent to the response in the stimulated eye.
@@
 
-\hypertarget{computational-model-and-parameter-estimation}{%
-\subsection{Computational model and parameter estimation}\label{computational-model-and-parameter-estimation}}
+\subsection{Computational model and parameter estimation}\label{computational-model-and-parameter-estimation}
 
-To describe our data, we used the same model described in our previous study (\protect\hyperlink{ref-Segala2023}{5}).
-The model has the same general form as the first stage of the contrast gain control model proposed by (\protect\hyperlink{ref-Meese2006}{33}), but omits the second stage.
-For the previous model that we used (\protect\hyperlink{ref-Segala2023}{5}), the exponent of the numerator and denominator had fixed values of 2 and (implicitly) 1.
+To describe our data, we used the same model described in our previous study\textsuperscript{\citeproc{ref-Segala2023}{5}}.
+The model has the same general form as the first stage of the contrast gain control model proposed by Meese, Georgeson and Baker\textsuperscript{\citeproc{ref-Meese2006}{33}}, but omits the second stage.
+For the previous model that we used\textsuperscript{\citeproc{ref-Segala2023}{5}}, the exponent of the numerator and denominator had fixed values of 2 and (implicitly) 1.
 Here, we allow these parameters (called \emph{p} and \emph{q}) to be free, in order to permit different shapes of contrast response function, e.g.~accelerating or saturating.
@@
 
-The models were fit using a hierarchical Bayesian framework implemented in Stan (\protect\hyperlink{ref-Carpenter2017}{52}).
+The models were fit using a hierarchical Bayesian framework implemented in Stan\textsuperscript{\citeproc{ref-Carpenter2017}{52}}.
 The data for each photoreceptor type and response frequency was fit separately, for a total of 8 model fits.
 The prior for the \(\omega\) parameter was Gaussian, with a mean of 1 and standard deviation of 0.5.
-Priors for the other free parameters were also Gaussian, with mean values based on previous work (\protect\hyperlink{ref-Segala2023}{5}).
+Priors for the other free parameters were also Gaussian, with mean values based on previous work\textsuperscript{\citeproc{ref-Segala2023}{5}}.
 We calculated over \ensuremath{10^{6}} posterior samples, and retained 10\% for plotting.
 
-\hypertarget{acknowledgements-and-funding-sources}{%
-\section{Acknowledgements and funding sources}\label{acknowledgements-and-funding-sources}}
+\section{References}\label{references}
+
+\phantomsection\label{refs}
+\begin{CSLReferences}{0}{0}
+\bibitem[\citeproctext]{ref-McDougal2015}
+\CSLLeftMargin{1. }%
+\CSLRightInline{McDougal, D. H. \& Gamlin, P. D. \href{https://doi.org/10.1002/cphy.c140014}{Autonomic control of the eye}. \emph{Comprehensive Physiology} \textbf{5}, 439--473 (2015).}
+
+\bibitem[\citeproctext]{ref-McDougal2008}
+\CSLLeftMargin{2. }%
+\CSLRightInline{McDougal, D. H. \& Gamlin, P. D. Pupillary control pathways. in \emph{The senses: A comprehensive reference} 521--536 (Elsevier, 2008).}
+
+\bibitem[\citeproctext]{ref-Wang2015}
+\CSLLeftMargin{3. }%
+\CSLRightInline{Wang, C.-A.
+\& Munoz, D.
+P.
+\href{https://doi.org/10.1016/j.conb.2015.03.018}{A circuit for pupil orienting responses: Implications for cognitive modulation of pupil size}.
+\emph{Curr Opin Neurobiol} \textbf{33}, 134--40 (2015).}
+
+\bibitem[\citeproctext]{ref-Wyatt1981}
+\CSLLeftMargin{4. }%
+\CSLRightInline{Wyatt, H.
+J.
+\& Musselman, J.
+F.
+\href{https://doi.org/10.1016/0042-6989(81)90097-3}{Pupillary light reflex in humans: Evidence for an unbalanced pathway from nasal retina, and for signal cancellation in brainstem}.
+\emph{Vision Res} \textbf{21}, 513--25 (1981).}
+
+\bibitem[\citeproctext]{ref-Segala2023}
+\CSLLeftMargin{5. }%
+\CSLRightInline{Segala, F.
+G.
+\emph{et al.} \href{https://doi.org/10.7554/elife.87048}{Different rules for binocular combination of luminance flicker in cortical and subcortical pathways}.
+\emph{eLife} \textbf{12}, (2023).}
+
+\bibitem[\citeproctext]{ref-Barrionuevo2014}
+\CSLLeftMargin{6. }%
+\CSLRightInline{Barrionuevo, P.
+A.
+\emph{et al.} \href{https://doi.org/10.1167/iovs.13-13252}{Assessing rod, cone, and melanopsin contributions to human pupil flicker responses}.
+\emph{Investigative Ophthalmology \& Visual Science} \textbf{55}, 719--27 (2014).}
+
+\bibitem[\citeproctext]{ref-Barrionuevo2018}
+\CSLLeftMargin{7. }%
+\CSLRightInline{Barrionuevo, P.
+A., McAnany, J.
+J., Zele, A.
+J.
+\& Cao, D.
+\href{https://doi.org/10.3389/fneur.2018.01140}{Non-linearities in the {Rod} and {Cone} {Photoreceptor} {Inputs} to the {Afferent} {Pupil} {Light} {Response}}.
+\emph{Frontiers in Neurology} \textbf{9}, (2018).}
+
+\bibitem[\citeproctext]{ref-Dacey2005}
+\CSLLeftMargin{8. }%
+\CSLRightInline{Dacey, D.
+M.
+\emph{et al.} \href{https://doi.org/10.1038/nature03387}{Melanopsin-expressing ganglion cells in primate retina signal colour and irradiance and project to the {LGN}}.
+\emph{Nature} \textbf{433}, 749--754 (2005).}
+
+\bibitem[\citeproctext]{ref-Murray2018}
+\CSLLeftMargin{9. }%
+\CSLRightInline{Murray, I.
+J., Kremers, J., McKeefry, D.
+\& Parry, N.
+R.
+A.
+\href{https://doi.org/10.1364/JOSAA.35.000B66}{Paradoxical pupil responses to isolated {M}-cone increments}.
+\emph{Journal of the Optical Society of America A} \textbf{35}, B66--B71 (2018).}
+
+\bibitem[\citeproctext]{ref-Spitschan2014}
+\CSLLeftMargin{10. }%
+\CSLRightInline{Spitschan, M., Jain, S., Brainard, D.
+H.
+\& Aguirre, G.
+K.
+\href{https://doi.org/10.1073/pnas.1400942111}{Opponent melanopsin and s-cone signals in the human pupillary light response}.
+\emph{Proceedings of the National Academy of Sciences} \textbf{111}, 15568--15572 (2014).}
+
+\bibitem[\citeproctext]{ref-Spitschan2019}
+\CSLLeftMargin{11. }%
+\CSLRightInline{Spitschan, M. \& Cajochen, C. \href{https://doi.org/10.1111/jpi.12602}{Binocular facilitation in light-mediated melatonin suppression?} \emph{J Pineal Res} \textbf{67}, e12602 (2019).}
+
+\bibitem[\citeproctext]{ref-Woelders2018}
+\CSLLeftMargin{12. }%
+\CSLRightInline{Woelders, T.
+\emph{et al.} \href{https://doi.org/10.1073/pnas.1716281115}{Melanopsin- and {L}-cone--induced pupil constriction is inhibited by {S}- and {M}-cones in humans}.
+\emph{Proceedings of the National Academy of Sciences} \textbf{115}, 792--797 (2018).}
+
+\bibitem[\citeproctext]{ref-Mathot2018}
+\CSLLeftMargin{13. }%
+\CSLRightInline{Mathôt, S. \href{https://doi.org/10.5334/joc.18}{Pupillometry: Psychology, physiology, and function}. \emph{J Cogn} \textbf{1}, 16 (2018).}
+
+\bibitem[\citeproctext]{ref-Markwell2010}
+\CSLLeftMargin{14. }%
+\CSLRightInline{Markwell, E.
+L., Feigl, B.
+\& Zele, A.
+J.
+\href{https://doi.org/10.1111/j.1444-0938.2010.00479.x}{Intrinsically photosensitive melanopsin retinal ganglion cell contributions to the pupillary light reflex and circadian rhythm}.
+\emph{Clinical and Experimental Optometry} \textbf{93}, 137--149 (2010).}
+
+\bibitem[\citeproctext]{ref-McDougal2010}
+\CSLLeftMargin{15. }%
+\CSLRightInline{McDougal, D.
+H.
+\& Gamlin, P.
+D.
+\href{https://doi.org/10.1016/j.visres.2009.10.012}{The influence of intrinsically-photosensitive retinal ganglion cells on the spectral sensitivity and response dynamics of the human pupillary light reflex}.
+\emph{Vision Research} \textbf{50}, 72--87 (2010).}
+
+\bibitem[\citeproctext]{ref-Provencio2000}
+\CSLLeftMargin{16. }%
+\CSLRightInline{Provencio, I.
+\emph{et al.} \href{https://doi.org/10.1523/JNEUROSCI.20-02-00600.2000}{A {Novel} {Human} {Opsin} in the {Inner} {Retina}}.
+\emph{Journal of Neuroscience} \textbf{20}, 600--605 (2000).}
+
+\bibitem[\citeproctext]{ref-Panda2002}
+\CSLLeftMargin{17. }%
+\CSLRightInline{Panda, S.
+\emph{et al.} \href{https://doi.org/10.1126/science.1076848}{Melanopsin (Opn4) requirement for normal light-induced circadian phase shifting}.
+\emph{Science} \textbf{298}, 2213--2216 (2002).}
+
+\bibitem[\citeproctext]{ref-Ruby2002}
+\CSLLeftMargin{18. }%
+\CSLRightInline{Ruby, N. F. \emph{et al.} \href{https://doi.org/10.1126/science.1076701}{Role of melanopsin in circadian responses to light}. \emph{Science} \textbf{298}, 2211--2213 (2002).}
+
+\bibitem[\citeproctext]{ref-Dacey2003}
+\CSLLeftMargin{19. }%
+\CSLRightInline{Dacey, D.
+M., Peterson, B.
+B., Robinson, F.
+R.
+\& Gamlin, P.
+D.
+\href{https://doi.org/10.1016/S0896-6273(02)01143-1}{Fireworks in the primate retina: In vitro photodynamics reveals diverse LGN-projecting ganglion cell types}.
+\emph{Neuron} \textbf{37}, 15--27 (2003).}
+
+\bibitem[\citeproctext]{ref-Lucas2003}
+\CSLLeftMargin{20. }%
+\CSLRightInline{Lucas, R.
+J.
+\emph{et al.} \href{https://doi.org/10.1126/science.1077293}{Diminished pupillary light reflex at high irradiances in melanopsin-knockout mice}.
+\emph{Science} \textbf{299}, 245--247 (2003).}
+
+\bibitem[\citeproctext]{ref-Gamlin2007}
+\CSLLeftMargin{21. }%
+\CSLRightInline{Gamlin, P.
+D.
+R.
+\emph{et al.} \href{https://doi.org/10.1016/j.visres.2006.12.015}{Human and macaque pupil responses driven by melanopsin-containing retinal ganglion cells}.
+\emph{Vision Research} \textbf{47}, 946--954 (2007).}
+
+\bibitem[\citeproctext]{ref-Estevez1982}
+\CSLLeftMargin{22. }%
+\CSLRightInline{Estévez, O.
+\& Spekreijse, H.
+\href{https://doi.org/10.1016/0042-6989(82)90104-3}{The "silent substitution" method in visual research}.
+\emph{Vision Research} \textbf{22}, 681--691 (1982).}
+
+\bibitem[\citeproctext]{ref-Shapiro1996}
+\CSLLeftMargin{23. }%
+\CSLRightInline{Shapiro, A.
+G., Pokorny, J.
+\& Smith, V.
+C.
+\href{https://doi.org/10.1364/josaa.13.002319}{Cone{\textendash}rod receptor spaces with illustrations that use {CRT} phosphor and light-emitting-diode spectra}.
+\emph{Journal of the Optical Society of America A} \textbf{13}, 2319 (1996).}
+
+\bibitem[\citeproctext]{ref-Spitschan2018}
+\CSLLeftMargin{24. }%
+\CSLRightInline{Spitschan, M.
+\& Woelders, T.
+\href{https://doi.org/10.3389/fneur.2018.00941}{The {Method} of {Silent} {Substitution} for {Examining} {Melanopsin} {Contributions} to {Pupil} {Control}}.
+\emph{Frontiers in Neurology} \textbf{9}, (2018).}
+
+\bibitem[\citeproctext]{ref-Cao2015}
+\CSLLeftMargin{25. }%
+\CSLRightInline{Cao, D., Nicandro, N.
+\& Barrionuevo, P.
+A.
+\href{https://doi.org/10.1167/15.1.27}{A five-primary photostimulator suitable for studying intrinsically photosensitive retinal ganglion cell functions in humans}.
+\emph{Journal of Vision} \textbf{15}, 27 (2015).}
+
+\bibitem[\citeproctext]{ref-Hubel1962}
+\CSLLeftMargin{26. }%
+\CSLRightInline{Hubel, D.
+H.
+\& Wiesel, T.
+N.
+\href{https://doi.org/10.1113/jphysiol.1962.sp006837}{Receptive fields, binocular interaction and functional architecture in the cat's visual cortex}.
+\emph{J Physiol} \textbf{160}, 106--54 (1962).}
+
+\bibitem[\citeproctext]{ref-Moradi2009}
+\CSLLeftMargin{27. }%
+\CSLRightInline{Moradi, F. \& Heeger, D. J. \href{https://doi.org/10.1167/9.3.13}{Inter-ocular contrast normalization in human visual cortex}. \emph{J Vis} \textbf{9}, 13.1--22 (2009).}
+
+\bibitem[\citeproctext]{ref-Baker2018}
+\CSLLeftMargin{28. }%
+\CSLRightInline{Baker, D.
+H., Lygo, F.
+A., Meese, T.
+S.
+\& Georgeson, M.
+A.
+\href{https://doi.org/10.1037/bul0000163}{Binocular summation revisited: Beyond \(\sqrt{2}\)}.
+\emph{Psychol Bull} \textbf{144}, 1186--1199 (2018).}
+
+\bibitem[\citeproctext]{ref-Campbell1965}
+\CSLLeftMargin{29. }%
+\CSLRightInline{Campbell, F. W. \& Green, D. G. \href{https://doi.org/10.1038/208191a0}{Monocular versus binocular visual acuity}. \emph{Nature} \textbf{208}, 191--2 (1965).}
+
+\bibitem[\citeproctext]{ref-Legge1984}
+\CSLLeftMargin{30. }%
+\CSLRightInline{Legge, G. E. \href{https://doi.org/10.1016/0042-6989(84)90064-6}{Binocular contrast summation--II. Quadratic summation}. \emph{Vision Res} \textbf{24}, 385--94 (1984).}
+
+\bibitem[\citeproctext]{ref-Baker2007}
+\CSLLeftMargin{31. }%
+\CSLRightInline{Baker, D.
+H., Meese, T.
+S.
+\& Georgeson, M.
+A.
+\href{https://doi.org/10.1163/156856807781503622}{Binocular interaction: Contrast matching and contrast discrimination are predicted by the same model}.
+\emph{Spat Vis} \textbf{20}, 397--413 (2007).}
+
+\bibitem[\citeproctext]{ref-Ding2006}
+\CSLLeftMargin{32. }%
+\CSLRightInline{Ding, J. \& Sperling, G. \href{https://doi.org/10.1073/pnas.0509629103}{A gain-control theory of binocular combination}. \emph{Proc Natl Acad Sci U S A} \textbf{103}, 1141--6 (2006).}
+
+\bibitem[\citeproctext]{ref-Meese2006}
+\CSLLeftMargin{33. }%
+\CSLRightInline{Meese, T.
+S., Georgeson, M.
+A.
+\& Baker, D.
+H.
+\href{https://doi.org/10.1167/6.11.7}{Binocular contrast vision at and above threshold}.
+\emph{Journal of Vision} \textbf{6}, 1224--43 (2006).}
+
+\bibitem[\citeproctext]{ref-Kingdom2015}
+\CSLLeftMargin{34. }%
+\CSLRightInline{Kingdom, F.
+A.
+A.
+\& Libenson, L.
+\href{https://doi.org/10.1167/15.5.2}{Dichoptic color saturation mixture: Binocular luminance contrast promotes perceptual averaging}.
+\emph{J Vis} \textbf{15}, 2 (2015).}
+
+\bibitem[\citeproctext]{ref-Busse2009}
+\CSLLeftMargin{35. }%
+\CSLRightInline{Busse, L., Wade, A.
+R.
+\& Carandini, M.
+\href{https://doi.org/10.1016/j.neuron.2009.11.004}{Representation of concurrent stimuli by population activity in visual cortex}.
+\emph{Neuron} \textbf{64}, 931--42 (2009).}
+
+\bibitem[\citeproctext]{ref-Baker2024}
+\CSLLeftMargin{36. }%
+\CSLRightInline{Baker, D.
+H.
+\emph{et al.} \href{https://doi.org/10.31234/osf.io/atsfh}{Binocular integration of chromatic and luminance signals}.
+\emph{Journal of Vision} \textbf{Under review}, (2024).}
+
+\bibitem[\citeproctext]{ref-Baker2017}
+\CSLLeftMargin{37. }%
+\CSLRightInline{Baker, D.
+H.
+\& Wade, A.
+R.
+\href{https://doi.org/10.1093/cercor/bhw395}{Evidence for an optimal algorithm underlying signal combination in human visual cortex}.
+\emph{Cereb Cortex} \textbf{27}, 254--264 (2017).}
+
+\bibitem[\citeproctext]{ref-Kaestner2019}
+\CSLLeftMargin{38. }%
+\CSLRightInline{Kaestner, M.
+\emph{et al.} \href{https://doi.org/10.1073/pnas.1817202116}{Asymmetries between achromatic and chromatic extraction of 3D motion signals}.
+\emph{Proc Natl Acad Sci U S A} \textbf{116}, 13631--13640 (2019).}
+
+\bibitem[\citeproctext]{ref-Martin2022}
+\CSLLeftMargin{39. }%
+\CSLRightInline{Martin, J.
+T., Pinto, J., Bulte, D.
+\& Spitschan, M.
+\href{https://doi.org/10.3758/s13428-021-01759-3}{PyPlr: A versatile, integrated system of hardware and software for researching the human pupillary light reflex}.
+\emph{Behavior Research Methods} \textbf{54}, 2720--2739 (2022).}
+
+\bibitem[\citeproctext]{ref-Martin2023}
+\CSLLeftMargin{40. }%
+\CSLRightInline{Martin, J.
+T., Boynton, G.
+M., Baker, D.
+H., Wade, A.
+R.
+\& Spitschan, M.
+\href{https://doi.org/10.1167/jov.23.7.10}{PySilSub: An open-source python toolbox for implementing the method of silent substitution in vision and nonvisual photoreception research}.
+\emph{Journal of Vision} \textbf{23}, 10 (2023).}
+
+\bibitem[\citeproctext]{ref-Stockman2000}
+\CSLLeftMargin{41. }%
+\CSLRightInline{Stockman, A.
+\& Sharpe, L.
+T.
+\href{https://doi.org/10.1016/s0042-6989(00)00021-3}{The spectral sensitivities of the middle- and long-wavelength-sensitive cones derived from measurements in observers of known genotype}.
+\emph{Vision Res} \textbf{40}, 1711--37 (2000).}
+
+\bibitem[\citeproctext]{ref-Barrionuevo2016}
+\CSLLeftMargin{42. }%
+\CSLRightInline{Barrionuevo, P.
+A.
+\& Cao, D.
+\href{https://doi.org/10.1167/16.11.29}{Luminance and chromatic signals interact differently with melanopsin activation to control the pupil light response}.
+\emph{Journal of Vision} \textbf{16(11)}, 29 (2016).}
+
+\bibitem[\citeproctext]{ref-Spitschan2015}
+\CSLLeftMargin{43. }%
+\CSLRightInline{Spitschan, M., Aguirre, G.
+K.
+\& Brainard, D.
+H.
+\href{https://doi.org/10.1371/journal.pone.0124328}{Selective stimulation of penumbral cones reveals perception in the shadow of retinal blood vessels}.
+\emph{PLoS One} \textbf{10}, e0124328 (2015).}
+
+\bibitem[\citeproctext]{ref-Zele2018}
+\CSLLeftMargin{44. }%
+\CSLRightInline{Zele, A.
+J., Feigl, B., Adhikari, P., Maynard, M.
+L.
+\& Cao, D.
+\href{https://doi.org/10.1038/s41598-018-22197-w}{Melanopsin photoreception contributes to human visual detection, temporal and colour processing}.
+\emph{Scientific Reports} \textbf{8}, (2018).}
+
+\bibitem[\citeproctext]{ref-Kassner2014}
+\CSLLeftMargin{45. }%
+\CSLRightInline{Kassner, M., Patera, W.
+\& Bulling, A.
+Pupil: An open source platform for pervasive eye tracking and mobile gaze-based interaction.
+in \emph{Proceedings of the 2014 {ACM} international joint conference on pervasive and ubiquitous computing: Adjunct publication} ({ACM}, 2014).
+doi:\href{https://doi.org/10.1145/2638728.2641695}{10.1145/2638728.2641695}.}
+
+\bibitem[\citeproctext]{ref-Norcia2015}
+\CSLLeftMargin{46. }%
+\CSLRightInline{Norcia, A.
+M., Appelbaum, L.
+G., Ales, J.
+M., Cottereau, B.
+R.
+\& Rossion, B.
+\href{https://doi.org/10.1167/15.6.4}{The steady-state visual evoked potential in vision research: A review}.
+\emph{Journal of Vision} \textbf{15(6)}, 4 (2015).}
+
+\bibitem[\citeproctext]{ref-Zele2019}
+\CSLLeftMargin{47. }%
+\CSLRightInline{Zele, A.
+J., Adhikari, P., Cao, D.
+\& Feigl, B.
+\href{https://doi.org/10.1016/j.visres.2019.04.009}{Melanopsin driven enhancement of cone-mediated visual processing}.
+\emph{Vision Res} \textbf{160}, 72--81 (2019).}
+
+\bibitem[\citeproctext]{ref-Baker2020}
+\CSLLeftMargin{48. }%
+\CSLRightInline{Baker, D.
+H.
+\emph{et al.} \href{https://doi.org/10.1038/s41598-020-60602-5}{Binaural summation of amplitude modulation involves weak interaural suppression}.
+\emph{Sci Rep} \textbf{10}, 3560 (2020).}
+
+\bibitem[\citeproctext]{ref-Carroll2002}
+\CSLLeftMargin{49. }%
+\CSLRightInline{Carroll, J., Neitz, J.
+\& Neitz, M.
+\href{https://doi.org/10.1167/2.8.1}{Estimates of {L}:{M} cone ratio from {ERG} flicker photometry and genetics}.
+\emph{Journal of Vision} \textbf{2}, 1 (2002).}
+
+\bibitem[\citeproctext]{ref-Hofer2005}
+\CSLLeftMargin{50. }%
+\CSLRightInline{Hofer, H., Carroll, J., Neitz, J., Neitz, M.
+\& Williams, D.
+R.
+\href{https://doi.org/10.1523/jneurosci.2414-05.2005}{Organization of the human trichromatic cone mosaic}.
+\emph{The Journal of Neuroscience} \textbf{25}, 9669--9679 (2005).}
+
+\bibitem[\citeproctext]{ref-Baker2021}
+\CSLLeftMargin{51. }%
+\CSLRightInline{Baker, D. H. \href{https://doi.org/10.51628/001c.27680}{Statistical analysis of periodic data in neuroscience}. \emph{Neurons, Behavior, Data analysis, and Theory} \textbf{5}, (2021).}
+
+\bibitem[\citeproctext]{ref-Carpenter2017}
+\CSLLeftMargin{52. }%
+\CSLRightInline{Carpenter, B. \emph{et al.} \href{https://doi.org/10.18637/jss.v076.i01}{Stan: A probabilistic programming language}. \emph{J Stat Softw} \textbf{76}, (2017).}
+
+\end{CSLReferences}
+
+\section{Acknowledgements}\label{acknowledgements}
 
@@
 
-\hypertarget{references}{%
-\section{References}\label{references}}
+\section{Author contributions}\label{author-contributions}
 
-\hypertarget{refs}{}
-\leavevmode\hypertarget{ref-McDougal2015}{}%
-1. D. H. McDougal, P. D. Gamlin, Autonomic control of the eye. \emph{Comprehensive Physiology} \textbf{5}, 439--473 (2015).
+D.H.B.
+and A.R.W.
+conceived the project D.H.B, A.R.W., and A.B.
+supervised the project.
+F.G.S., J.T.M., A.R.W., and D.H.B.
+designed the experiments.
+F.G.S., J.T.M., and A.Y.M.
+performed the experiments and collected the data.
+F.G.S and D.H.B.
+analysed the data and implemented the computational model.
+F.G.S.
+and D.H.B.
+wrote the manuscript with input from all authors.
+A.B., J.T.M., A.Y.M., and A.R.W.
+provided feedback on the manuscript.
 
-\leavevmode\hypertarget{ref-McDougal2008}{}%
-2. D. H. McDougal, P. D. Gamlin, ``Pupillary control pathways.'' in \emph{The Senses: A Comprehensive Reference}, (Elsevier, 2008), pp. 521--536.
+\section{Competing interests}\label{competing-interests}
 
-\leavevmode\hypertarget{ref-Wang2015}{}%
-3. C.-A. Wang, D. P. Munoz, A circuit for pupil orienting responses: Implications for cognitive modulation of pupil size. \emph{Curr Opin Neurobiol} \textbf{33}, 134--40 (2015).
+The authors declare no competing interests.
 
-\leavevmode\hypertarget{ref-Wyatt1981}{}%
-4.
-H.
-J.
-Wyatt, J.
-F.
-Musselman, Pupillary light reflex in humans: Evidence for an unbalanced pathway from nasal retina, and for signal cancellation in brainstem.
-\emph{Vision Res} \textbf{21}, 513--25 (1981).
+\section{Materials and Correspondence}\label{materials-and-correspondence}
 
-\leavevmode\hypertarget{ref-Segala2023}{}%
-5. F. G. Segala\emph{et al.}, Different rules for binocular combination of luminance flicker in cortical and subcortical pathways. \emph{eLife} \textbf{12} (2023).
-
-\leavevmode\hypertarget{ref-Barrionuevo2014}{}%
-6. P. A. Barrionuevo\emph{et al.}, Assessing rod, cone, and melanopsin contributions to human pupil flicker responses. \emph{Investigative Ophthalmology \& Visual Science} \textbf{55}, 719--27 (2014).
-
-\leavevmode\hypertarget{ref-Barrionuevo2018}{}%
-7. P. A. Barrionuevo, J. J. McAnany, A. J. Zele, D. Cao, Non-linearities in the Rod and Cone Photoreceptor Inputs to the Afferent Pupil Light Response. \emph{Frontiers in Neurology} \textbf{9} (2018).
-
-\leavevmode\hypertarget{ref-Dacey2005}{}%
-8. D. M. Dacey\emph{et al.}, Melanopsin-expressing ganglion cells in primate retina signal colour and irradiance and project to the LGN. \emph{Nature} \textbf{433}, 749--754 (2005).
-
-\leavevmode\hypertarget{ref-Murray2018}{}%
-9. I. J. Murray, J. Kremers, D. McKeefry, N. R. A. Parry, Paradoxical pupil responses to isolated M-cone increments. \emph{Journal of the Optical Society of America A} \textbf{35}, B66--B71 (2018).
-
-\leavevmode\hypertarget{ref-Spitschan2014}{}%
-10.
-M.
-Spitschan, S.
-Jain, D.
-H.
-Brainard, G.
-K.
-Aguirre, Opponent melanopsin and s-cone signals in the human pupillary light response.
-\emph{Proceedings of the National Academy of Sciences} \textbf{111}, 15568--15572 (2014).
-
-\leavevmode\hypertarget{ref-Spitschan2019}{}%
-11. M. Spitschan, C. Cajochen, Binocular facilitation in light-mediated melatonin suppression? \emph{J Pineal Res} \textbf{67}, e12602 (2019).
-
-\leavevmode\hypertarget{ref-Woelders2018}{}%
-12.
-T.
-Woelders\emph{et al.}, Melanopsin- and L-cone--induced pupil constriction is inhibited by S- and M-cones in humans.
-\emph{Proceedings of the National Academy of Sciences} \textbf{115}, 792--797 (2018).
-
-\leavevmode\hypertarget{ref-Mathot2018}{}%
-13. S. Mathôt, Pupillometry: Psychology, physiology, and function. \emph{J Cogn} \textbf{1}, 16 (2018).
-
-\leavevmode\hypertarget{ref-Markwell2010}{}%
-14.
-E.
-L.
-Markwell, B.
-Feigl, A.
-J.
-Zele, Intrinsically photosensitive melanopsin retinal ganglion cell contributions to the pupillary light reflex and circadian rhythm.
-\emph{Clinical and Experimental Optometry} \textbf{93}, 137--149 (2010).
-
-\leavevmode\hypertarget{ref-McDougal2010}{}%
-15.
-D.
-H.
-McDougal, P.
-D.
-Gamlin, The influence of intrinsically-photosensitive retinal ganglion cells on the spectral sensitivity and response dynamics of the human pupillary light reflex.
-\emph{Vision Research} \textbf{50}, 72--87 (2010).
-
-\leavevmode\hypertarget{ref-Provencio2000}{}%
-16. I. Provencio\emph{et al.}, A Novel Human Opsin in the Inner Retina. \emph{Journal of Neuroscience} \textbf{20}, 600--605 (2000).
-
-\leavevmode\hypertarget{ref-Panda2002}{}%
-17. S. Panda\emph{et al.}, Melanopsin (opn4) requirement for normal light-induced circadian phase shifting. \emph{Science} \textbf{298}, 2213--2216 (2002).
-
-\leavevmode\hypertarget{ref-Ruby2002}{}%
-18. N. F. Ruby\emph{et al.}, Role of melanopsin in circadian responses to light. \emph{Science} \textbf{298}, 2211--2213 (2002).
-
-\leavevmode\hypertarget{ref-Dacey2003}{}%
-19.
-D.
-M.
-Dacey, B.
-B.
-Peterson, F.
-R.
-Robinson, P.
-D.
-Gamlin, Fireworks in the primate retina: In vitro photodynamics reveals diverse lgn-projecting ganglion cell types.
-\emph{Neuron} \textbf{37}, 15--27 (2003).
-
-\leavevmode\hypertarget{ref-Lucas2003}{}%
-20. R. J. Lucas\emph{et al.}, Diminished pupillary light reflex at high irradiances in melanopsin-knockout mice. \emph{Science} \textbf{299}, 245--247 (2003).
-
-\leavevmode\hypertarget{ref-Gamlin2007}{}%
-21. P. D. R. Gamlin\emph{et al.}, Human and macaque pupil responses driven by melanopsin-containing retinal ganglion cells. \emph{Vision Research} \textbf{47}, 946--954 (2007).
-
-\leavevmode\hypertarget{ref-Estevez1982}{}%
-22. O. Estévez, H. Spekreijse, The "silent substitution" method in visual research. \emph{Vision Research} \textbf{22}, 681--691 (1982).
-
-\leavevmode\hypertarget{ref-Shapiro1996}{}%
-23.
-A.
-G.
-Shapiro, J.
-Pokorny, V.
-C.
-Smith, Conerod receptor spaces with illustrations that use CRT phosphor and light-emitting-diode spectra.
-\emph{Journal of the Optical Society of America A} \textbf{13}, 2319 (1996).
-
-\leavevmode\hypertarget{ref-Spitschan2018}{}%
-24. M. Spitschan, T. Woelders, The Method of Silent Substitution for Examining Melanopsin Contributions to Pupil Control. \emph{Frontiers in Neurology} \textbf{9} (2018).
-
-\leavevmode\hypertarget{ref-Cao2015}{}%
-25.
-D.
-Cao, N.
-Nicandro, P.
-A.
-Barrionuevo, A five-primary photostimulator suitable for studying intrinsically photosensitive retinal ganglion cell functions in humans.
-\emph{Journal of Vision} \textbf{15}, 27 (2015).
-
-\leavevmode\hypertarget{ref-Hubel1962}{}%
-26. D. H. Hubel, T. N. Wiesel, Receptive fields, binocular interaction and functional architecture in the cat's visual cortex. \emph{J Physiol} \textbf{160}, 106--54 (1962).
-
-\leavevmode\hypertarget{ref-Moradi2009}{}%
-27. F. Moradi, D. J. Heeger, Inter-ocular contrast normalization in human visual cortex. \emph{J Vis} \textbf{9}, 13.1--22 (2009).
-
-\leavevmode\hypertarget{ref-Baker2018}{}%
-28. D. H. Baker, F. A. Lygo, T. S. Meese, M. A. Georgeson, Binocular summation revisited: Beyond \(\sqrt{2}\). \emph{Psychol Bull} \textbf{144}, 1186--1199 (2018).
-
-\leavevmode\hypertarget{ref-Campbell1965}{}%
-29. F. W. Campbell, D. G. Green, Monocular versus binocular visual acuity. \emph{Nature} \textbf{208}, 191--2 (1965).
-
-\leavevmode\hypertarget{ref-Legge1984}{}%
-30. G. E. Legge, Binocular contrast summation--ii. Quadratic summation. \emph{Vision Res} \textbf{24}, 385--94 (1984).
-
-\leavevmode\hypertarget{ref-Baker2007}{}%
-31. D. H. Baker, T. S. Meese, M. A. Georgeson, Binocular interaction: Contrast matching and contrast discrimination are predicted by the same model. \emph{Spat Vis} \textbf{20}, 397--413 (2007).
-
-\leavevmode\hypertarget{ref-Ding2006}{}%
-32. J. Ding, G. Sperling, A gain-control theory of binocular combination. \emph{Proc Natl Acad Sci U S A} \textbf{103}, 1141--6 (2006).
-
-\leavevmode\hypertarget{ref-Meese2006}{}%
-33. T. S. Meese, M. A. Georgeson, D. H. Baker, Binocular contrast vision at and above threshold. \emph{Journal of Vision} \textbf{6}, 1224--43 (2006).
-
-\leavevmode\hypertarget{ref-Kingdom2015}{}%
-34. F. A. A. Kingdom, L. Libenson, Dichoptic color saturation mixture: Binocular luminance contrast promotes perceptual averaging. \emph{J Vis} \textbf{15}, 2 (2015).
-
-\leavevmode\hypertarget{ref-Busse2009}{}%
-35. L. Busse, A. R. Wade, M. Carandini, Representation of concurrent stimuli by population activity in visual cortex. \emph{Neuron} \textbf{64}, 931--42 (2009).
-
-\leavevmode\hypertarget{ref-Baker2024}{}%
-36. D. H. Baker\emph{et al.}, Binocular integration of chromatic and luminance signals. \emph{Journal of Vision} \textbf{Under review} (2024).
-
-\leavevmode\hypertarget{ref-Baker2017}{}%
-37. D. H. Baker, A. R. Wade, Evidence for an optimal algorithm underlying signal combination in human visual cortex. \emph{Cereb Cortex} \textbf{27}, 254--264 (2017).
-
-\leavevmode\hypertarget{ref-Kaestner2019}{}%
-38. M. Kaestner\emph{et al.}, Asymmetries between achromatic and chromatic extraction of 3D motion signals. \emph{Proc Natl Acad Sci U S A} \textbf{116}, 13631--13640 (2019).
-
-\leavevmode\hypertarget{ref-Martin2022}{}%
-39.
-J.
-T.
-Martin, J.
-Pinto, D.
-Bulte, M.
-Spitschan, PyPlr: A versatile, integrated system of hardware and software for researching the human pupillary light reflex.
-\emph{Behavior Research Methods} \textbf{54}, 2720--2739 (2022).
-
-\leavevmode\hypertarget{ref-Martin2023}{}%
-40.
-J.
-T.
-Martin, G.
-M.
-Boynton, D.
-H.
-Baker, A.
-R.
-Wade, M.
-Spitschan, PySilSub: An open-source python toolbox for implementing the method of silent substitution in vision and nonvisual photoreception research.
-\emph{Journal of Vision} \textbf{23}, 10 (2023).
-
-\leavevmode\hypertarget{ref-Stockman2000}{}%
-41.
-A.
-Stockman, L.
-T.
-Sharpe, The spectral sensitivities of the middle- and long-wavelength-sensitive cones derived from measurements in observers of known genotype.
-\emph{Vision Res} \textbf{40}, 1711--37 (2000).
-
-\leavevmode\hypertarget{ref-Barrionuevo2016}{}%
-42. P. A. Barrionuevo, D. Cao, Luminance and chromatic signals interact differently with melanopsin activation to control the pupil light response. \emph{Journal of Vision} \textbf{16(11)}, 29 (2016).
-
-\leavevmode\hypertarget{ref-Spitschan2015}{}%
-43. M. Spitschan, G. K. Aguirre, D. H. Brainard, Selective stimulation of penumbral cones reveals perception in the shadow of retinal blood vessels. \emph{PLoS One} \textbf{10}, e0124328 (2015).
-
-\leavevmode\hypertarget{ref-Zele2018}{}%
-44.
-A.
-J.
-Zele, B.
-Feigl, P.
-Adhikari, M.
-L.
-Maynard, D.
-Cao, Melanopsin photoreception contributes to human visual detection, temporal and colour processing.
-\emph{Scientific Reports} \textbf{8} (2018).
-
-\leavevmode\hypertarget{ref-Kassner2014}{}%
-45.
-M.
-Kassner, W.
-Patera, A.
-Bulling, Pupil: An open source platform for pervasive eye tracking and mobile gaze-based interaction.
-in \emph{Proceedings of the 2014 ACM International Joint Conference on Pervasive and Ubiquitous Computing: Adjunct Publication}, (ACM, 2014) \url{https:/doi.org/10.1145/2638728.2641695}.
-
-\leavevmode\hypertarget{ref-Norcia2015}{}%
-46. A. M. Norcia, L. G. Appelbaum, J. M. Ales, B. R. Cottereau, B. Rossion, The steady-state visual evoked potential in vision research: A review. \emph{Journal of Vision} \textbf{15(6)}, 4 (2015).
-
-\leavevmode\hypertarget{ref-Zele2019}{}%
-47. A. J. Zele, P. Adhikari, D. Cao, B. Feigl, Melanopsin driven enhancement of cone-mediated visual processing. \emph{Vision Res} \textbf{160}, 72--81 (2019).
-
-\leavevmode\hypertarget{ref-Baker2020}{}%
-48. D. H. Baker\emph{et al.}, Binaural summation of amplitude modulation involves weak interaural suppression. \emph{Sci Rep} \textbf{10}, 3560 (2020).
-
-\leavevmode\hypertarget{ref-Carroll2002}{}%
-49. J. Carroll, J. Neitz, M. Neitz, Estimates of L:M cone ratio from ERG flicker photometry and genetics. \emph{Journal of Vision} \textbf{2}, 1 (2002).
-
-\leavevmode\hypertarget{ref-Hofer2005}{}%
-50. H. Hofer, J. Carroll, J. Neitz, M. Neitz, D. R. Williams, Organization of the human trichromatic cone mosaic. \emph{The Journal of Neuroscience} \textbf{25}, 9669--9679 (2005).
-
-\leavevmode\hypertarget{ref-Baker2021}{}%
-51. D. H. Baker, Statistical analysis of periodic data in neuroscience. \emph{Neurons, Behavior, Data analysis, and Theory} \textbf{5} (2021).
-
-\leavevmode\hypertarget{ref-Carpenter2017}{}%
-52. B. Carpenter\emph{et al.}, Stan: A probabilistic programming language. \emph{J Stat Softw} \textbf{76} (2017).
+Correspondence and material requests should be addressed to \href{federico.segala@york.ac.uk}{Federico G. Segala}.
 

### 2024-07-16 manuscript.Rmd
Edits

--- 2024-06-07 manuscript.Rmd
@@
 linkcolor: black
-csl: pnas.csl
+csl: the-journal-of-neuroscience.csl
 header-includes:
   \usepackage{caption}
-  \usepackage{lineno} \linenumbers
+  \usepackage{setspace}\doublespacing
+  # \usepackage{lineno} \linenumbers
 ---
@@
 
-Address for correspondence: Federico G. Segala, [federico.segala\@york.ac.uk](federico.segala@york.ac.uk)
-
-Preprint server: a preprint has been deposited on BioRxiv (https://doi.org/10.1101/2024.06.04.597314) with a no reuse/adaptation without permission license
-
-Classification: Biological Sciences - Psychological and Cognitive Sciences
-
-Keywords: Pupil diameter, Pupillometry, Silent substitution, Melanopsin, Binocular combination, Computational modelling
+Corresponding author: Federico G. Segala, [federico.segala@york.ac.uk](federico.segala@york.ac.uk).
+
+Number of pages: 21
+
+Number of figures: 4
+
+Number of tables: 1
+
+Number of words for abstract: 187
+
+Number of words for introduction: 1005
+
+Number of words for discussion: 600
+
+Conflict of interest: The authors declare no competing financial interests.
+
+Acknowledgements: Supported by Biotechnology and Biological Sciences Research Council grant BB/V007580/1 awarded to DHB and ARW.
+
+\pagebreak
 
@@
 The results are interpreted using a contemporary model of binocular vision [@Meese2006] implemented within a hierarchical Bayesian framework.
-
-# Results
-
-Figure \@ref(fig:spectraplots)m-p shows averaged waveforms of pupil diameter in response to binocular stimulation.
-For luminance stimuli (Figure \@ref(fig:spectraplots)m) a strong modulation is apparent at the stimulation frequency (0.5Hz), which is also clear in the Fourier amplitude spectrum (Figure \@ref(fig:spectraplots)q).
-For binocular stimulation of the L-M pathway, S-cone pathway and melanopsin pathway, pupil modulations were less than 10\% of the amplitude of the luminance modulation (note the change in y-axis scale for the Fourier spectra), but still apparent at 0.5Hz in the Fourier spectra (Figure \@ref(fig:spectraplots)n-p).
-We also observed a second harmonic response (at 1Hz) for all conditions, which was weaker than the first harmonic for luminance and melanopsin stimulation, but stronger for L-M and S-cone stimulation.
-The second harmonic is also apparent in the pupil waveforms shown in Figure \@ref(fig:spectraplots)n-p.
-Our main analysis therefore focuses on the amplitude of the pupil modulations at both the first and second harmonic frequencies across different stimulus conditions.
-
-```{r spectraplots, fig.cap="Summary of the spectral power distributions and alpha-opic irradiances for the background and each condition, as well as averaged pupil diameters and Fourier spectra.
-Panel (a) shows a schematic of the binocular stimulation system for presenting spectrally tuned modulations independently to each eye.
-The VR headset was attached to a clamp stand that the experimenters could use to adjust the height and align the headset with the eyes of the participant.
-The participant's head was supported by a chin rest to keep it in position throughout the experiment.
-Panel (b) shows the outputs of each LED primary at maximum intensity, and panels (c) and (d) show the overall spectral power distributions and the alpha-opic irradiances of the background spectra used for both eyes.
-The subsequent rows show the power differences (e-h), and photoreceptor contrasts (i-l) relative to the background, averaged pupil diameter waveforms (m-p) and Fourier spectra (q-t) for binocular stimulation.
-Column headings indicate the pathway stimulated, and shaded regions in panels m-t indicate bootstrapped 95\\% confidence intervals.", fig.align="center", out.width = '80%', echo=FALSE}
-
-knitr::include_graphics(paste0(figdir,'methodsfig.pdf'))
-
-```
-
-Figure \@ref(fig:FirstHarmonicPlots)a-d shows contrast response functions across stimulation conditions for responses at the first harmonic of the main stimulation frequency (0.5Hz).
-In each plot, the response to monocular stimulation is given by the red circles and typically increases monotonically as a function of stimulus (temporal) contrast.
-Relative to monocular stimulation, binocular stimulation led to higher response amplitudes, indicating a binocular facilitation effect, for the luminance and S-cone conditions (Figure \@ref(fig:FirstHarmonicPlots)a,c), and to some extent for the melanopsin condition (Figure \@ref(fig:FirstHarmonicPlots)d).
-However, the L-M cone condition (Figure \@ref(fig:FirstHarmonicPlots)b) produced a binocular suppression effect, where the response to binocular stimulation was weaker than the response to monocular stimulation (blue squares below red circles).
-These results indicate that the magnitude of binocular facilitation differs across photoreceptor pathway, suggesting heterogeneity in the underlying neural computation.
-
-```{r FirstHarmonicPlots, fig.cap="Contrast response functions for pupil modualations in response to flicker at 0.5Hz (panels a-d), and 0.4Hz (panels f-i), and posterior parameter distributions for the weight of interocular suppression (panel e).
-Within each panel (except panel e), data points are the coherently averaged amplitudes for each condition, and error bars indicate bootstrapped 95\\% confidence intervals.
-Curves show model fits using the maximum a posteriori (MAP) parameter values (see Table 1).
-In panel (e), vertical lines show the MAP estimates, and the thin black curve indicates the prior (note the logarithmic x-axis).", fig.align="center", out.width="40%", echo=FALSE}
-
-knitr::include_graphics(paste0(figdir,'FirstHarmonic.pdf'))
-
-```
-
-In contemporary models of binocular signal combination, the amount of binocular facilitation is determined by the magnitude of interocular suppression, with strong suppression reducing facilitation [@Kingdom2015].
-We can estimate the strength of interocular suppression by measuring how much monocular responses are reduced when a dichoptic 'mask' is shown to the other eye.
-In our paradigm, the two components flickered at different frequencies (0.5 and 0.4Hz) so that their responses remained distinct in the Fourier spectrum [e.g.
-@Busse2009].
-The yellow diamond symbols in Figure \@ref(fig:FirstHarmonicPlots)a-d show the target responses in this condition, and in most cases were weaker than the monocular responses (red circles).
-The strongest dichoptic masking is found in the L-M condition, where we also observed the binocular suppression effect.
-Suppression can also be estimated from the responses at 0.4Hz (Figure \@ref(fig:FirstHarmonicPlots)f-i).
-The reduced amplitude in the binocular cross condition (where the two eyes received different temporal frequencies; purple squares) relative to the 0.4Hz monocular condition (grey circles), and the progressive decline in amplitude of the dichoptic cross response (yellow diamonds) also differ across photoreceptor conditions, showing similar differences to those observed at 0.5Hz.
-
-To estimate the extent of interocular suppression for each photoreceptor pathway, we fitted each data set using a Bayesian hierarchical implementation of a simple binocular combination model [@Meese2006; @Segala2023].
-Our primary objective was to compare posterior distributions of the weight of interocular suppression, which are shown in Figure \@ref(fig:FirstHarmonicPlots)e.
-Consistent with our earlier observations, the strongest suppressive weight corresponds to the L-M and Melanopsin conditions, and the weakest suppression corresponds to the luminance and S-cone conditions, with virtually no overlap between the posterior distributions for weak and strong suppression.
-The model fits were of good quality, as shown by the curves in Figure \@ref(fig:FirstHarmonicPlots)a-d,f-i.
-The fitted model parameters are given in Table \@ref(tab:paramtable).
-
-```{r paramtable, echo=FALSE}
-
-condnames <- c('Luminance 1F','L-M cone 1F','S cone 1F','Melanopsin 1F','Luminance 2F','L-M cone 2F','S cone 2F','Melanopsin 2F')
-zlist <- c(pupilZLum, pupilZLM, pupilZS, pupilZMel, pupilZLum2, pupilZLM2, pupilZS2, pupilZMel2)
-klist <- c(pupilKLum, pupilKLM, pupilKS, pupilKMel, pupilKLum2, pupilKLM2, pupilKS2, pupilKMel2)
-wlist <- c(pupilWLum, pupilWLM, pupilWS, pupilWMel, pupilWLum2, pupilWLM2, pupilWS2, pupilWMel2)
-plist <- c(pupilPLum, pupilPLM, pupilPS, pupilPMel, pupilPLum2, pupilPLM2, pupilPS2, pupilPMel2)
-qlist <- c(pupilQLum, pupilQLM, pupilQS, pupilQMel, pupilQLum2, pupilQLM2, pupilQS2, pupilQMel2)
-Rlist <- c(pupilRmaxLum, pupilRmaxLM, pupilRmaxS, pupilRmaxMel, pupilRmaxLum2, pupilRmaxLM2, pupilRmaxS2, pupilRmaxMel2)
-tabledata <- data.frame(condnames,round(zlist,digits=2),round(klist,digits=5),round(wlist,digits=2),round(plist,digits=2),round(qlist,digits=2),round(Rlist,digits=4))
-
-colnames(tabledata) <- c('Experiment','Z','k','w','p','q','Rmax')
-kable(tabledata, align='lcccccc',booktabs=TRUE,linesep='',caption = 'Summary of maximum a posteriori (MAP) parameter estimates for each data set.') %>%
-kableExtra::kable_styling(latex_options = "HOLD_position") %>% row_spec(4,hline_after=TRUE)
-
-```
-
-At the second harmonic frequencies, the levels of suppression were more uniform across different photoreceptor pathways (see Figure \@ref(fig:SecondHarmonicPlots)).
-In general, suppression estimates were near or above 1 (see lower rows of Table \@ref(tab:paramtable)), with substantial overlap between the posterior distributions (Figure \@ref(fig:SecondHarmonicPlots)e).
-The contrast response functions also looked more uniform, and generally involved less binocular facilitation and more interocular suppression than were seen at the first harmonics.
-The L-M condition now featured the weakest suppressive weight, and the strongest binocular facilitation, which was the opposite pattern seen at the first harmonic.
-
-```{r SecondHarmonicPlots, fig.cap="Responses at the second harmonic frequencies (1Hz and 0.8Hz), in the same format as Figure 2.", fig.align="center", out.width="40%", echo=FALSE}
-
-knitr::include_graphics(paste0(figdir,'SecondHarmonic.pdf'))
-
-```
-
-Finally, we inspected the response phase of our four stimulation conditions, given previous reports that these differ across pathways [@Spitschan2014], and may be in antiphase for melanopsin and S-cone signals.
-Figure \@ref(fig:phaseplots) shows the phase angles for the first (a) and second (b) harmonic frequencies for binocular stimulation (monocular stimulation produced very similar results).
-At the first harmonic, melanopsin and S-cone signals differed in phase by more than 90 degrees, though they were not fully in antiphase.
-The luminance and L-M responses were approximately in antiphase to each other, however this is likely due to our choice to modulate L+M- in the first half-cycle of the sine wave (corresponding to a luminance increase in the luminance condition), and L-M+ in the second half-cycle (corresponding to a luminance decrease in the luminance condition).
-Had we reversed this phase arrangement, we would likely have seen a close phase correspondence between the L-M and luminance conditions (another way to think about this is that L-cone decreases and M-cone increases are processed like luminance increases).
-Phase differences between the luminance, S-cone and melanopsin conditions are likely attributable to different lags in phototransduction at the earliest stage (i.e.
-in the retina).
-At the second harmonic frequency (Figure \@ref(fig:phaseplots)b), the luminance condition was again out of phase with the other three, and was approximately in quadrature phase with the L-M condition, and in antiphase with both the S-cone and melanopsin conditions (which were in phase with each other).
-
-```{r phaseplots, fig.cap="Pupil phase plots at the first and second harmonic frequencies for the luminance, melanopsin, L-M pathway and the S-(L+M) pathway conditions.
-Panel (a) shows the pupil response at the first harmonic frequency during binocular stimulation.
-Panel (b) shows the pupil response at the second harmonic frequency during binocular stimulation.
-The five data points for each pathway correspond to the five contrast levels displayed.
-In panel (a) the luminance amplitudes have been scaled down by a factor of 10 to enable comparison with the other conditions.", fig.align="center", echo=FALSE}
-
-knitr::include_graphics(paste0(figdir,'phaseplots.pdf'))
-
-```
-
-# Discussion
-
-We used binocular pupillometry and silent substitution to measure monocular and binocular responses of the pupils to flickering stimuli when stimulating specific photoreceptor pathways.
-In all four experiments, we were able to record contrast response functions at both the first and the second harmonic frequencies.
-All experiments showed that binocular combination in the autonomic nervous system happens in a non-linear manner, with evidence of different magnitudes of interocular suppression depending on the photoreceptor pathway.
-This pattern of results was confirmed by a computational model, which allowed us to compare the weight of interocular suppression for each pathway.
-We found that at the first harmonic frequency the L-M and melanopsin pathways involved strong suppression, whereas the luminance and S-cone pathways involved weaker suppression.
-Suppression was strong in all four pathways at the second harmonic frequency.
-Finally, the phase of the pupil response revealed different lag times for the different pathways at the first and second harmonic frequencies.
-
-This is the first study to investigate binocular interactions in the melanopsin pathway directly.
-A previous meta-analysis [@Spitschan2019] indicated that there may be a substantial binocular facilitation effect in the circadian pathway, as indexed by melatonin suppression (melatonin is a hormone released by the pineal gland; its production is suppressed by exposure to bright light, particularly when the melanopsin-containing ipRGCs are stimulated).
-In brief, monocular stimulation of the ipRGCs requires up to ten times the signal strength to produce an equivalent effect to binocular stimulation.
-This superadditive effect implies an absence of interocular suppression, and perhaps the presence of either a highly compressive nonlinearity, or an AND-style neural operation.
-Our findings here are very different - we do not see substantial binocular facilitation effects in response to melanopsin modulation, and our data indicate that interocular suppression is very strong.
-Moreover, by measuring the full contrast response function, we can rule out compressive nonlinearities, because the functions accelerate at both the first and second harmonic frequencies.
-The explanation for this difference could be due to different anatomical pathways.
-Binocular combination in the circadian system likely takes place in the suprachiasmatic nucleus, whereas in the pupil constriction circuit the Edinger-Westphal nucleus is the most likely site of binocular integration [@Mathot2018].
-Presumably these anatomical differences, and the practical constraints of the two systems, lead to differences in response.
-
-Our recent psychophysical work [@Baker2024] has looked at binocular interactions in the L-M and S-cone pathways, and compared these to the luminance pathway.
-Using a contrast discrimination paradigm with spatial modulations of luminance and colour, @Baker2024 found equally strong interocular suppression in all three pathways.
-This is rather different from our pupillometry results here, which demonstrate weaker suppression in the luminance and S-cone pathways than in the L-M pathway (see Figure \@ref(fig:FirstHarmonicPlots)).
-However, the current experiments involve temporal modulations, which are quite distinct from the spatial modulations used in @Baker2024.
-Our other recent work [@Segala2023] has shown that temporal luminance modulations involve much weaker interocular suppression in the cortical response than do spatial luminance modulations [@Baker2017].
-These different normalization processes might reflect different priorities for spatial and temporal vision.
-Spatial vision aims to fuse images to provide binocular single vision, and benefits from 'ocularity invariance' [@Baker2007], in which visual appearance is constant when viewed with one eye or two.
-Temporal vision is critical for motion perception, which can involve alternative binocular computations, such as calculating velocity differences between the eyes [@Kaestner2019].
-Of course the present measurements were of pupil size, which may be subject to different anatomical and functional constraints from those in the cortex.
-Future research should aim to extend our current findings to perception using psychophysical approaches.
-
-# Conclusions
-
-We have demonstrated that binocular combination of temporal flickering light in the autonomic nervous system depends on the photoreceptor pathway.
-We were able to elicit pupil responses by stimulating the periphery of the retina and we were able to record contrast response functions for all photoreceptor pathways.
-While all pathways showed non-linear combination, they varied in how the signals are combined, particularly in the weight of interocular suppression.
-This was strong ($\omega \ge 1$) for L-M and melanopsin signals at the first harmonic, and all pathways at the second harmonic.
-Suppression was weaker ($\omega < 1$) in the luminance pathway (consistent with previous work), and also for S-cone directed modulations.
 
@@
 
-# Acknowledgements and funding sources
-
-Supported by Biotechnology and Biological Sciences Research Council grant BB/V007580/1 awarded to DHB and ARW.
+# Results
+
+Figure \@ref(fig:spectraplots)m-p shows averaged waveforms of pupil diameter in response to binocular stimulation.
+For luminance stimuli (Figure \@ref(fig:spectraplots)m) a strong modulation is apparent at the stimulation frequency (0.5Hz), which is also clear in the Fourier amplitude spectrum (Figure \@ref(fig:spectraplots)q).
+For binocular stimulation of the L-M pathway, S-cone pathway and melanopsin pathway, pupil modulations were less than 10\% of the amplitude of the luminance modulation (note the change in y-axis scale for the Fourier spectra), but still apparent at 0.5Hz in the Fourier spectra (Figure \@ref(fig:spectraplots)n-p).
+We also observed a second harmonic response (at 1Hz) for all conditions, which was weaker than the first harmonic for luminance and melanopsin stimulation, but stronger for L-M and S-cone stimulation.
+The second harmonic is also apparent in the pupil waveforms shown in Figure \@ref(fig:spectraplots)n-p.
+Our main analysis therefore focuses on the amplitude of the pupil modulations at both the first and second harmonic frequencies across different stimulus conditions.
+
+```{r spectraplots, fig.cap="Summary of the spectral power distributions and alpha-opic irradiances for the background and each condition, as well as averaged pupil diameters and Fourier spectra.
+Panel (a) shows a schematic of the binocular stimulation system for presenting spectrally tuned modulations independently to each eye.
+The VR headset was attached to a clamp stand that the experimenters could use to adjust the height and align the headset with the eyes of the participant.
+The participant's head was supported by a chin rest to keep it in position throughout the experiment.
+Panel (b) shows the outputs of each LED primary at maximum intensity, and panels (c) and (d) show the overall spectral power distributions and the alpha-opic irradiances of the background spectra used for both eyes.
+The subsequent rows show the power differences (e-h), and photoreceptor contrasts (i-l) relative to the background, averaged pupil diameter waveforms (m-p) and Fourier spectra (q-t) for binocular stimulation.
+Column headings indicate the pathway stimulated, and shaded regions in panels m-t indicate bootstrapped 95\\% confidence intervals.", fig.align="center", out.width = '80%', echo=FALSE}
+
+knitr::include_graphics(paste0(figdir,'methodsfig.pdf'))
+
+```
+
+Figure \@ref(fig:FirstHarmonicPlots)a-d shows contrast response functions across stimulation conditions for responses at the first harmonic of the main stimulation frequency (0.5Hz).
+In each plot, the response to monocular stimulation is given by the red circles and typically increases monotonically as a function of stimulus (temporal) contrast.
+Relative to monocular stimulation, binocular stimulation led to higher response amplitudes, indicating a binocular facilitation effect, for the luminance and S-cone conditions (Figure \@ref(fig:FirstHarmonicPlots)a,c), and to some extent for the melanopsin condition (Figure \@ref(fig:FirstHarmonicPlots)d).
+However, the L-M cone condition (Figure \@ref(fig:FirstHarmonicPlots)b) produced a binocular suppression effect, where the response to binocular stimulation was weaker than the response to monocular stimulation (blue squares below red circles).
+These results indicate that the magnitude of binocular facilitation differs across photoreceptor pathway, suggesting heterogeneity in the underlying neural computation.
+
+```{r FirstHarmonicPlots, fig.cap="Contrast response functions for pupil modualations in response to flicker at 0.5Hz (panels a-d), and 0.4Hz (panels f-i), and posterior parameter distributions for the weight of interocular suppression (panel e).
+Within each panel (except panel e), data points are the coherently averaged amplitudes for each condition, and error bars indicate bootstrapped 95\\% confidence intervals.
+Curves show model fits using the maximum a posteriori (MAP) parameter values (see Table 1).
+In panel (e), vertical lines show the MAP estimates, and the thin black curve indicates the prior (note the logarithmic x-axis).", fig.align="center", out.width="40%", echo=FALSE}
+
+knitr::include_graphics(paste0(figdir,'FirstHarmonic.pdf'))
+
+```
+
+In contemporary models of binocular signal combination, the amount of binocular facilitation is determined by the magnitude of interocular suppression, with strong suppression reducing facilitation [@Kingdom2015].
+We can estimate the strength of interocular suppression by measuring how much monocular responses are reduced when a dichoptic 'mask' is shown to the other eye.
+In our paradigm, the two components flickered at different frequencies (0.5 and 0.4Hz) so that their responses remained distinct in the Fourier spectrum [e.g.
+@Busse2009].
+The yellow diamond symbols in Figure \@ref(fig:FirstHarmonicPlots)a-d show the target responses in this condition, and in most cases were weaker than the monocular responses (red circles).
+The strongest dichoptic masking is found in the L-M condition, where we also observed the binocular suppression effect.
+Suppression can also be estimated from the responses at 0.4Hz (Figure \@ref(fig:FirstHarmonicPlots)f-i).
+The reduced amplitude in the binocular cross condition (where the two eyes received different temporal frequencies; purple squares) relative to the 0.4Hz monocular condition (grey circles), and the progressive decline in amplitude of the dichoptic cross response (yellow diamonds) also differ across photoreceptor conditions, showing similar differences to those observed at 0.5Hz.
+
+To estimate the extent of interocular suppression for each photoreceptor pathway, we fitted each data set using a Bayesian hierarchical implementation of a simple binocular combination model [@Meese2006; @Segala2023].
+Our primary objective was to compare posterior distributions of the weight of interocular suppression, which are shown in Figure \@ref(fig:FirstHarmonicPlots)e.
+Consistent with our earlier observations, the strongest suppressive weight corresponds to the L-M and Melanopsin conditions, and the weakest suppression corresponds to the luminance and S-cone conditions, with virtually no overlap between the posterior distributions for weak and strong suppression.
+The model fits were of good quality, as shown by the curves in Figure \@ref(fig:FirstHarmonicPlots)a-d,f-i.
+The fitted model parameters are given in Table \@ref(tab:paramtable).
+
+```{r paramtable, echo=FALSE}
+
+condnames <- c('Luminance 1F','L-M cone 1F','S cone 1F','Melanopsin 1F','Luminance 2F','L-M cone 2F','S cone 2F','Melanopsin 2F')
+zlist <- c(pupilZLum, pupilZLM, pupilZS, pupilZMel, pupilZLum2, pupilZLM2, pupilZS2, pupilZMel2)
+klist <- c(pupilKLum, pupilKLM, pupilKS, pupilKMel, pupilKLum2, pupilKLM2, pupilKS2, pupilKMel2)
+wlist <- c(pupilWLum, pupilWLM, pupilWS, pupilWMel, pupilWLum2, pupilWLM2, pupilWS2, pupilWMel2)
+plist <- c(pupilPLum, pupilPLM, pupilPS, pupilPMel, pupilPLum2, pupilPLM2, pupilPS2, pupilPMel2)
+qlist <- c(pupilQLum, pupilQLM, pupilQS, pupilQMel, pupilQLum2, pupilQLM2, pupilQS2, pupilQMel2)
+Rlist <- c(pupilRmaxLum, pupilRmaxLM, pupilRmaxS, pupilRmaxMel, pupilRmaxLum2, pupilRmaxLM2, pupilRmaxS2, pupilRmaxMel2)
+tabledata <- data.frame(condnames,round(zlist,digits=2),round(klist,digits=5),round(wlist,digits=2),round(plist,digits=2),round(qlist,digits=2),round(Rlist,digits=4))
+
+colnames(tabledata) <- c('Experiment','Z','k','w','p','q','Rmax')
+kable(tabledata, align='lcccccc',booktabs=TRUE,linesep='',caption = 'Summary of maximum a posteriori (MAP) parameter estimates for each data set.') %>%
+kableExtra::kable_styling(latex_options = "HOLD_position") %>% row_spec(4,hline_after=TRUE)
+
+```
+
+At the second harmonic frequencies, the levels of suppression were more uniform across different photoreceptor pathways (see Figure \@ref(fig:SecondHarmonicPlots)).
+In general, suppression estimates were near or above 1 (see lower rows of Table \@ref(tab:paramtable)), with substantial overlap between the posterior distributions (Figure \@ref(fig:SecondHarmonicPlots)e).
+The contrast response functions also looked more uniform, and generally involved less binocular facilitation and more interocular suppression than were seen at the first harmonics.
+The L-M condition now featured the weakest suppressive weight, and the strongest binocular facilitation, which was the opposite pattern seen at the first harmonic.
+
+```{r SecondHarmonicPlots, fig.cap="Responses at the second harmonic frequencies (1Hz and 0.8Hz), in the same format as Figure 2.", fig.align="center", out.width="40%", echo=FALSE}
+
+knitr::include_graphics(paste0(figdir,'SecondHarmonic.pdf'))
+
+```
+
+Finally, we inspected the response phase of our four stimulation conditions, given previous reports that these differ across pathways [@Spitschan2014], and may be in antiphase for melanopsin and S-cone signals.
+Figure \@ref(fig:phaseplots) shows the phase angles for the first (a) and second (b) harmonic frequencies for binocular stimulation (monocular stimulation produced very similar results).
+At the first harmonic, melanopsin and S-cone signals differed in phase by more than 90 degrees, though they were not fully in antiphase.
+The luminance and L-M responses were approximately in antiphase to each other, however this is likely due to our choice to modulate L+M- in the first half-cycle of the sine wave (corresponding to a luminance increase in the luminance condition), and L-M+ in the second half-cycle (corresponding to a luminance decrease in the luminance condition).
+Had we reversed this phase arrangement, we would likely have seen a close phase correspondence between the L-M and luminance conditions (another way to think about this is that L-cone decreases and M-cone increases are processed like luminance increases).
+Phase differences between the luminance, S-cone and melanopsin conditions are likely attributable to different lags in phototransduction at the earliest stage (i.e.
+in the retina).
+At the second harmonic frequency (Figure \@ref(fig:phaseplots)b), the luminance condition was again out of phase with the other three, and was approximately in quadrature phase with the L-M condition, and in antiphase with both the S-cone and melanopsin conditions (which were in phase with each other).
+
+```{r phaseplots, fig.cap="Pupil phase plots at the first and second harmonic frequencies for the luminance, melanopsin, L-M pathway and the S-(L+M) pathway conditions.
+Panel (a) shows the pupil response at the first harmonic frequency during binocular stimulation.
+Panel (b) shows the pupil response at the second harmonic frequency during binocular stimulation.
+The five data points for each pathway correspond to the five contrast levels displayed.
+In panel (a) the luminance amplitudes have been scaled down by a factor of 10 to enable comparison with the other conditions.", fig.align="center", echo=FALSE}
+
+knitr::include_graphics(paste0(figdir,'phaseplots.pdf'))
+
+```
+
+# Discussion
+
+We used binocular pupillometry and silent substitution to measure monocular and binocular responses of the pupils to flickering stimuli when stimulating specific photoreceptor pathways.
+In all four experiments, we were able to record contrast response functions at both the first and the second harmonic frequencies.
+All experiments showed that binocular combination in the autonomic nervous system happens in a non-linear manner, with evidence of different magnitudes of interocular suppression depending on the photoreceptor pathway.
+This pattern of results was confirmed by a computational model, which allowed us to compare the weight of interocular suppression for each pathway.
+We found that at the first harmonic frequency the L-M and melanopsin pathways involved strong suppression, whereas the luminance and S-cone pathways involved weaker suppression.
+Suppression was strong in all four pathways at the second harmonic frequency.
+Finally, the phase of the pupil response revealed different lag times for the different pathways at the first and second harmonic frequencies.
+
+This is the first study to investigate binocular interactions in the melanopsin pathway directly.
+A previous meta-analysis [@Spitschan2019] indicated that there may be a substantial binocular facilitation effect in the circadian pathway, as indexed by melatonin suppression (melatonin is a hormone released by the pineal gland; its production is suppressed by exposure to bright light, particularly when the melanopsin-containing ipRGCs are stimulated).
+In brief, monocular stimulation of the ipRGCs requires up to ten times the signal strength to produce an equivalent effect to binocular stimulation.
+This superadditive effect implies an absence of interocular suppression, and perhaps the presence of either a highly compressive nonlinearity, or an AND-style neural operation.
+Our findings here are very different - we do not see substantial binocular facilitation effects in response to melanopsin modulation, and our data indicate that interocular suppression is very strong.
+Moreover, by measuring the full contrast response function, we can rule out compressive nonlinearities, because the functions accelerate at both the first and second harmonic frequencies.
+The explanation for this difference could be due to different anatomical pathways.
+Binocular combination in the circadian system likely takes place in the suprachiasmatic nucleus, whereas in the pupil constriction circuit the Edinger-Westphal nucleus is the most likely site of binocular integration [@Mathot2018].
+Presumably these anatomical differences, and the practical constraints of the two systems, lead to differences in response.
+
+Our recent psychophysical work [@Baker2024] has looked at binocular interactions in the L-M and S-cone pathways, and compared these to the luminance pathway.
+Using a contrast discrimination paradigm with spatial modulations of luminance and colour, @Baker2024 found equally strong interocular suppression in all three pathways.
+This is rather different from our pupillometry results here, which demonstrate weaker suppression in the luminance and S-cone pathways than in the L-M pathway (see Figure \@ref(fig:FirstHarmonicPlots)).
+However, the current experiments involve temporal modulations, which are quite distinct from the spatial modulations used in @Baker2024.
+Our other recent work [@Segala2023] has shown that temporal luminance modulations involve much weaker interocular suppression in the cortical response than do spatial luminance modulations [@Baker2017].
+These different normalization processes might reflect different priorities for spatial and temporal vision.
+Spatial vision aims to fuse images to provide binocular single vision, and benefits from 'ocularity invariance' [@Baker2007], in which visual appearance is constant when viewed with one eye or two.
+Temporal vision is critical for motion perception, which can involve alternative binocular computations, such as calculating velocity differences between the eyes [@Kaestner2019].
+Of course the present measurements were of pupil size, which may be subject to different anatomical and functional constraints from those in the cortex.
+Future research should aim to extend our current findings to perception using psychophysical approaches.
+
+# Conclusions
+
+We have demonstrated that binocular combination of temporal flickering light in the autonomic nervous system depends on the photoreceptor pathway.
+We were able to elicit pupil responses by stimulating the periphery of the retina and we were able to record contrast response functions for all photoreceptor pathways.
+While all pathways showed non-linear combination, they varied in how the signals are combined, particularly in the weight of interocular suppression.
+This was strong ($\omega \ge 1$) for L-M and melanopsin signals at the first harmonic, and all pathways at the second harmonic.
+Suppression was weaker ($\omega < 1$) in the luminance pathway (consistent with previous work), and also for S-cone directed modulations.
 

### 2024-07-16 manuscript.tex
Edits

--- 2024-06-07 manuscript.tex
@@
 \setcounter{secnumdepth}{5}
-\usepackage{caption} \usepackage{lineno} \linenumbers
+\usepackage{caption} \usepackage{setspace}\doublespacing
 \usepackage{booktabs}
@@
 
-Address for correspondence: Federico G. Segala, \url{federico.segala@york.ac.uk}
+Corresponding author: Federico G. Segala, \url{federico.segala@york.ac.uk}.
 
-Preprint server: a preprint has been deposited on BioRxiv (\url{https://doi.org/10.1101/2024.06.04.597314}) with a no reuse/adaptation without permission license
+Number of pages: 21
 
-Classification: Biological Sciences - Psychological and Cognitive Sciences
+Number of figures: 4
 
-Keywords: Pupil diameter, Pupillometry, Silent substitution, Melanopsin, Binocular combination, Computational modelling
+Number of tables: 1
+
+Number of words for abstract: 199
+
+Number of words for introduction: 896
+
+Number of words for discussion: 600
+
+Conflict of interest: The authors declare no competing financial interests.
+
+Acknowledgements: Supported by Biotechnology and Biological Sciences Research Council grant BB/V007580/1 awarded to DHB and ARW.
+
+\pagebreak
 
@@
 
-The autonomic nervous system regulates many involuntary bodily processes, including the constriction and dilation of the pupils in response to light (\protect\hyperlink{ref-McDougal2015}{1}).
-The anatomical pathway from the retina to the subcortical nuclei controlling the pupillary light response (PLR) is well established: it includes the Pretectal Olivary nucleus (PON), the Superior Cervical ganglion and the Edinger-Westphal nucleus, which project to the iris sphincter muscles that directly control the pupil size (\protect\hyperlink{ref-McDougal2015}{1}--\protect\hyperlink{ref-Wang2015}{3}).
-Evidence of a binocular component to the PLR is shown by the existence of a consensual response of the pupil (\protect\hyperlink{ref-Wyatt1981}{4}).
+The autonomic nervous system regulates many involuntary bodily processes, including the constriction and dilation of the pupils in response to light (McDougal and Gamlin, \protect\hyperlink{ref-McDougal2015}{2015}).
+The anatomical pathway from the retina to the subcortical nuclei controlling the pupillary light response (PLR) is well established: it includes the Pretectal Olivary nucleus (PON), the Superior Cervical ganglion and the Edinger-Westphal nucleus, which project to the iris sphincter muscles that directly control the pupil size (McDougal and Gamlin, \protect\hyperlink{ref-McDougal2008}{2008}, \protect\hyperlink{ref-McDougal2015}{2015}; Wang and Munoz, \protect\hyperlink{ref-Wang2015}{2015}).
+Evidence of a binocular component to the PLR is shown by the existence of a consensual response of the pupil (the stimulation of one eye will cause constriction of the other eye; Wyatt and Musselman, \protect\hyperlink{ref-Wyatt1981}{1981}).
 The anatomical segregation of the subcortical pathway from the rest of the brain means that this binocular combination of signals must occur independently of the cortical processes of binocular integration required for visual perception.
-Our recent work (\protect\hyperlink{ref-Segala2023}{5}) has shown that the algorithm underlying binocular combination of light in the pupil pathway differs from that in the cortex.
+Our recent work (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}) has shown that the algorithm underlying binocular combination of light in the pupil pathway differs from that in the cortex.
 Here we extend this paradigm to compare binocular combination in different photoreceptor pathways that feed into the autonomic nervous system.
 
-Different classes of retinal photoreceptors, including cones, rods and melanopsin-containing intrinsically photosensitive retinal ganglion cells (ipRGCs), are directly involved in controlling and maintaining the size of the pupils (\protect\hyperlink{ref-Barrionuevo2014}{6}--\protect\hyperlink{ref-Woelders2018}{12}).
-The cones have been shown to drive the initial rapid constriction of the pupils (\protect\hyperlink{ref-Mathot2018}{13}), while the slower and longer activation of the ipRGCs shows their role in maintaining the constriction over a prolonged period of time and in regulating the post-illumination pupillary response (\protect\hyperlink{ref-Markwell2010}{14}, \protect\hyperlink{ref-McDougal2010}{15}).
-The ipRGCs are a unique photoreceptor class that has been discovered recently (\protect\hyperlink{ref-Provencio2000}{16}).
-They express the photopigment melanopsin, and are involved in the regulation of the circadian rhythm (\protect\hyperlink{ref-Provencio2000}{16}--\protect\hyperlink{ref-Ruby2002}{18}), forming a major input to the PON (\protect\hyperlink{ref-Dacey2003}{19}).
-The first direct evidence of the involvement of the ipRGCs in the PLR was shown in melanopsin knockout rats by (\protect\hyperlink{ref-Lucas2003}{20}), resulting in the loss of the intrinsic photosensitivity of the cells and a reduced pupil constriction.
-This same behaviour was later also observed in primates and humans (\protect\hyperlink{ref-Gamlin2007}{21}), where it was demonstrated that the PLR continues during light presentation even when cone and rod signalling is blocked, indicating the primary role of the ipRGCs in maintaining pupil constriction over a prolonged time.
+Different classes of retinal photoreceptors, including cones, rods and melanopsin-containing intrinsically photosensitive retinal ganglion cells (ipRGCs), are directly involved in controlling and maintaining the size of the pupils (Dacey et al., \protect\hyperlink{ref-Dacey2005}{2005}; Barrionuevo et al., \protect\hyperlink{ref-Barrionuevo2014}{2014}, \protect\hyperlink{ref-Barrionuevo2018}{2018}; Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}; Murray et al., \protect\hyperlink{ref-Murray2018}{2018}; Woelders et al., \protect\hyperlink{ref-Woelders2018}{2018}; Spitschan and Cajochen, \protect\hyperlink{ref-Spitschan2019}{2019}).
+The cones have been shown to drive the initial rapid constriction of the pupils (Mathôt, \protect\hyperlink{ref-Mathot2018}{2018}), while the slower and longer activation of the ipRGCs shows their role in maintaining the constriction over a prolonged period of time and in regulating the post-illumination pupillary response (Markwell et al., \protect\hyperlink{ref-Markwell2010}{2010}; McDougal and Gamlin, \protect\hyperlink{ref-McDougal2010}{2010}).
+The ipRGCs are a unique photoreceptor class that has been discovered recently (Provencio et al., \protect\hyperlink{ref-Provencio2000}{2000}).
+They express the photopigment melanopsin, and are involved in the regulation of the circadian rhythm (Provencio et al., \protect\hyperlink{ref-Provencio2000}{2000}; Panda et al., \protect\hyperlink{ref-Panda2002}{2002}; Ruby et al., \protect\hyperlink{ref-Ruby2002}{2002}), forming a major input to the PON (Dacey et al., \protect\hyperlink{ref-Dacey2003}{2003}).
+The first direct evidence of the involvement of the ipRGCs in the PLR was shown in melanopsin knockout rats by Lucas et al.
+(\protect\hyperlink{ref-Lucas2003}{2003}), resulting in the loss of the intrinsic photosensitivity of the cells and a reduced pupil constriction.
+This same behaviour was later also observed in primates and humans (Gamlin et al., \protect\hyperlink{ref-Gamlin2007}{2007}), where it was demonstrated that the PLR continues during light presentation even when cone and rod signalling is blocked, indicating the primary role of the ipRGCs in maintaining pupil constriction over a prolonged time.
 
-A technique known as silent substitution (\protect\hyperlink{ref-Estevez1982}{22}) can be used to selectively stimulate specific photoreceptor classes.
+A technique known as silent substitution (Estévez and Spekreijse, \protect\hyperlink{ref-Estevez1982}{1982}) can be used to selectively stimulate specific photoreceptor classes.
 Silent substitution exploits the fact that each photoreceptor class has a distinct spectral tuning that overlaps with the others.
-Using a multiprimary system, in which the primaries (i.e.~LEDs) have different spectra, it is possible to target one class of photoreceptors while maintaining the others at a constant activity level, effectively silencing them (\protect\hyperlink{ref-Shapiro1996}{23}, \protect\hyperlink{ref-Spitschan2018}{24}).
+Using a multiprimary system, in which the primaries (i.e.~LEDs) have different spectra, it is possible to target one class of photoreceptors while maintaining the others at a constant activity level, effectively silencing them (Shapiro et al., \protect\hyperlink{ref-Shapiro1996}{1996}; Spitschan and Woelders, \protect\hyperlink{ref-Spitschan2018}{2018}, this paper also offers a clear explanation of how to implement silent substitution).
 Studies using silent substitution have shown that the pupils behave differently depending on which photoreceptor or pathway is being stimulated.
-For example, pupil responses have been shown to be out of phase when the S cones are stimulated, relative to when the ipRGCs or the L+M cones are stimulated (\protect\hyperlink{ref-Spitschan2014}{10}, \protect\hyperlink{ref-Cao2015}{25}).
-Additionally, when L and M cones are stimulated individually, there appears to be a paradoxical pupil response: increments in L cone stimulation cause a constriction of the pupil, while increments in M cone stimulation lead to a dilation of the pupil (\protect\hyperlink{ref-Murray2018}{9}, \protect\hyperlink{ref-Woelders2018}{12}), perhaps due to activity in the L-M opponent pathway.
+For example, pupil responses have been shown to be out of phase when the S cones are stimulated, relative to when the ipRGCs or the L+M cones are stimulated (Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}; Cao et al., \protect\hyperlink{ref-Cao2015}{2015}).
+Additionally, when L and M cones are stimulated individually, there appears to be a paradoxical pupil response: increments in L cone stimulation cause a constriction of the pupil, while increments in M cone stimulation lead to a dilation of the pupil (Murray et al., \protect\hyperlink{ref-Murray2018}{2018}; Woelders et al., \protect\hyperlink{ref-Woelders2018}{2018}), perhaps due to activity in the L-M opponent pathway.
 
-Binocular combination has been extensively studied in visual perception, where it is mediated by neurons in primary visual cortex (\protect\hyperlink{ref-Hubel1962}{26}, \protect\hyperlink{ref-Moradi2009}{27}).
-For pattern vision, binocular summation occurs at threshold, such that a lower contrast is required to detect a target shown to both eyes than a target shown to only one eye (\protect\hyperlink{ref-Baker2018}{28}--\protect\hyperlink{ref-Legge1984}{30}).
-At higher contrasts, a process of `ocularity invariance' is observed, in which the response to monocularly- and binocularly-presented patterns is equal (\protect\hyperlink{ref-Moradi2009}{27}, \protect\hyperlink{ref-Baker2007}{31}--\protect\hyperlink{ref-Meese2006}{33}).
+Binocular combination has been extensively studied in visual perception, where it is mediated by neurons in primary visual cortex (Hubel and Wiesel, \protect\hyperlink{ref-Hubel1962}{1962}; Moradi and Heeger, \protect\hyperlink{ref-Moradi2009}{2009}).
+For pattern vision, binocular summation occurs at threshold, such that a lower contrast is required to detect a target shown to both eyes than a target shown to only one eye (Campbell and Green, \protect\hyperlink{ref-Campbell1965}{1965}; Legge, \protect\hyperlink{ref-Legge1984}{1984}; Baker et al., \protect\hyperlink{ref-Baker2018}{2018}).
+At higher contrasts, a process of `ocularity invariance' is observed, in which the response to monocularly- and binocularly-presented patterns is equal (Ding and Sperling, \protect\hyperlink{ref-Ding2006}{2006}; Meese et al., \protect\hyperlink{ref-Meese2006}{2006}; Baker et al., \protect\hyperlink{ref-Baker2007}{2007}; Moradi and Heeger, \protect\hyperlink{ref-Moradi2009}{2009}).
 This is thought to be due to a process of interocular suppression that compensates for the additional excitatory drive caused by stimulating two eyes.
-Our recent work (\protect\hyperlink{ref-Segala2023}{5}) has shown that cortical signal combination for luminance flicker is substantially more linear than for spatial patterns, whereas there is evidence of interocular suppression in the pupil pathway.
+Our recent work (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}) has shown that cortical signal combination for luminance flicker is substantially more linear than for spatial patterns, whereas there is evidence of interocular suppression in the pupil pathway.
 
 Most studies that use silent substitution to investigate the PLR stimulate only one eye.
-If the stimulated eye is pharmacologically dilated to control pupil size, the response from the unstimulated eye (known as the consensual response) can be recorded (\protect\hyperlink{ref-Spitschan2014}{10}, \protect\hyperlink{ref-McDougal2010}{15}).
+If the stimulated eye is pharmacologically dilated to control pupil size, the response from the unstimulated eye (known as the consensual response) can be recorded (e.g.~McDougal and Gamlin, \protect\hyperlink{ref-McDougal2010}{2010}; Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}).
 While this approach controls the total amount of light incident at the retina, it does not permit investigation of binocular combination for specific photoreceptor pathways.
@@
 Our key comparisons are between monocular and binocular stimulation, and between monocular stimulation and a dichoptic masking condition in which the two eyes are stimulated at different frequencies (0.5 and 0.4Hz).
-The results are interpreted using a contemporary model of binocular vision (\protect\hyperlink{ref-Meese2006}{33}) implemented within a hierarchical Bayesian framework.
+The results are interpreted using a contemporary model of binocular vision (Meese et al., \protect\hyperlink{ref-Meese2006}{2006}) implemented within a hierarchical Bayesian framework.
+
+\hypertarget{materials-and-methods}{%
+\section{Materials and methods}\label{materials-and-methods}}
+
+\hypertarget{participants}{%
+\subsection{Participants}\label{participants}}
+
+Twenty-four participants were recruited for each of the four experiments for a total of ninety-six adult participants (28 male, 68 female), whose ages ranged from 18 to 41.
+All participants had normal or corrected to normal vision, no known abnormalities of binocular or colour vision, and gave written informed consent.
+Our procedures were approved by the Ethics Committee of the Department of Psychology at the University of York (identification number 184).
+
+\hypertarget{apparatus-stimuli}{%
+\subsection{Apparatus \& stimuli}\label{apparatus-stimuli}}
+
+To present synchronised stimulus modulations independently to each eye, two light engines (SpectraTuneLAB: LEDMOTIVE Technologies, LLC, Barcelona, Spain), each with 10 independently addressable LED colour channels, were integrated into a customised viewing system.
+The light engines were operated via a Python interface to their REST API (Martin et al., \protect\hyperlink{ref-Martin2022}{2022}), which supports synchronous launch and playback of spectral sequences prepared in advance and stored in JSON format.
+When preparing the spectral sequences, the age of participants was used to account for the yellowing of the lenses.
+We calculated silent substitution solutions using the \emph{PySilSub} toolbox (Martin et al., \protect\hyperlink{ref-Martin2023}{2023}), using linear algebra.
+The outputs of the two light engines (see Figure \ref{fig:spectraplots}b,c) were calibrated using an Ocean Optics Jaz spectroradiometer, which was wavelength-calibrated to an Argon lamp and intensity calibrated using a NIST-traceable light source.
+We used the Stockman and Sharpe (\protect\hyperlink{ref-Stockman2000}{2000}) 10-degree cone fundamentals, and estimates of melanopsin absorbance spectra from CIE S 026 (discussed in Martin et al., \protect\hyperlink{ref-Martin2023}{2023}) to calculate \(\alpha\)-opic irradiance.
+
+The output from the light engines was directed through liquid light guides (LLG3-8H: Thorlabs Ltd, Cambridgeshire, UK) and diffused onto semi-opaque and highly diffusive white glass discs with a diameter of 50 mm for even illumination (34-473: Edmund Optics, York, UK).
+The light guide gaskets were butt-coupled to the light engine diffusers with threaded adapters (SM1A9, AD3LLG: Thorlabs Ltd, Cambridgeshire, UK) and the exiting ends of the light guides were mated with 51 mm depth optical cylinders (SM2L20: Thorlabs Ltd, Cambridgeshire, UK) via appropriately threaded adapters (AD3LLG, SM2A6: Thorlabs Ltd, Cambridgeshire, UK).
+The stimulus diffuser discs were retained at the front end of the optical cylinders approximately 51 mm from the light source, at which distance the output beam was sufficiently dispersed to afford even illumination of the diffuser when viewed from the front.
+To guarantee safe illumination levels, a circular neutral-density filter with the same diameter of the white glass discs (50 mm) and an optical density of 0.6 log units was placed in the optical path between the light source and the diffusers.
+A small circular piece of blackout material with a diameter of approximately 8 degrees (10 mm) was positioned centrally on the front of each diffuser disc to aid as a fusion lock, as a fixation point, and to occlude the fovea.
+
+The diffuser discs were positioned in the objective planes of the lenses of a modified VR headset (SHINECON SC-G01, Dongguan Shinecon Industrial Co.~Ltd., Guangdong, China), which was used by the participants to view the stimuli.
+The stimuli were two discs of flickering light with a diameter of approximately 30 degrees, which were fused together into a cyclopean percept resembling a donut-shaped ring of light, similar to that used in other studies (e.g., Barrionuevo and Cao, \protect\hyperlink{ref-Barrionuevo2016}{2016}; Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}, \protect\hyperlink{ref-Spitschan2015}{2015}; Murray et al., \protect\hyperlink{ref-Murray2018}{2018}; Zele et al., \protect\hyperlink{ref-Zele2018}{2018}).
+The VR headset modifications allowed for small adjustments to account for individual differences in interpupillary distance and focal length.
+The use of this set up allowed us to modulate the stimuli in three different ocular configurations, similar to the ones we used in our previous study (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}): monocular, binocular and dichoptic.
+In the monocular configuration, the unstimulated eye still saw a non-flickering disc of mean luminance.
+A schematic of the stimulation system is shown in Figure \ref{fig:spectraplots}a.
+Pupillometry data were collected using a binocular Pupil Core eye-tracker headset (Pupil Labs GmbH, Berlin, Germany, Kassner et al., \protect\hyperlink{ref-Kassner2014}{2014}) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
+
+Our previous study (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}) used a temporal frequency of 2Hz for foveal luminance flicker, and recorded EEG data simultaneously with pupillometry.
+Initial pilot experiments indicated that this frequency was too high to elicit measurable responses when stimulating individual photoreceptor pathways.
+For all experiments, we therefore used a primary flicker frequency of 0.5Hz, as previous literature showed that this was slow enough to elicit a pupil response from all photoreceptor classes (Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}).
+We also focussed on only recording pupillometry data as this frequency would be too slow to elicit steady-state EEG responses (Norcia et al., \protect\hyperlink{ref-Norcia2015}{2015}).
+
+For all experiments, sinusoidal temporal modulations were presented against the same background spectrum (matched between the eyes), which was used to achieve silent substitution in the three photoreceptor modulation experiments.
+The background spectra were defined by setting all channels to half maximum output for the brighter of the two devices (STLab 1, left eye) and then using the STLab 1/STLab 2 calibration ratio to find the equivalent settings for the companion device (STLab 2, right eye).
+The background spectrum illuminance was approximately 74 lux, or 68.5 cd/m\(^2\).
+The spectral power distributions and \(\alpha\)-opic irradiances of the background spectra for both eyes are shown in Figure \ref{fig:spectraplots}c-d.
+
+In the luminance experiment, the stimulus intensity was increased and decreased relative to the background, which we expected to modulate all photoreceptor classes (see Figure \ref{fig:spectraplots}e,i).
+In the L-M cone modulation experiment, we used silent substution to increase the L-cone activity, and simultaneously decrease the M-cone activity, during the first half-cycle of the sine wave.
+In the second half-cycle the polarity of the modulation reversed (see Figure \ref{fig:spectraplots}f,j).
+The maximum available L-M contrast was approximately 10\%.
+In the S-cone modulation experiment, we increased and decreased S-cone-directed signals, whilst keeping activity in the other photoreceptors constant (see Figure \ref{fig:spectraplots}g,k).
+Our system allowed a maximum contrast of 45\%.
+Finally, in the melanopsin experiment, we modulated the activity of the melanopsin-containing intrinsically photoreceptive retinal ganglion cells, whilst keeping cone activity constant (see Figure \ref{fig:spectraplots}h,l).
+The maximum available melanopsin contrast was 22\%.
+We assume that the activity of rods was constant at the high background luminance intensity used here, and so did not attempt to silence rod activity in any condition, as this would have greatly reduced the available dynamic range.
+Splatter on nominally silenced photoreceptors was very small (see Figure \ref{fig:spectraplots}j-l), well below the levels that would be expected to generate measureable pupil modulations.
+We also estimated activation of penumbral L and M cones (Spitschan et al., \protect\hyperlink{ref-Spitschan2015}{2015}; Barrionuevo and Cao, \protect\hyperlink{ref-Barrionuevo2016}{2016}; Zele et al., \protect\hyperlink{ref-Zele2019}{2019}), which was minimal (\(\le 1.5%
+\) contrast; less than splatter on the open-field cones) for melanopsin-directed stimuli.
+We note that the temporal frequency of our modulation (0.5Hz) is well below the range where penumbral cone activation can elicit visible percepts, and that such percepts fade after around 1 second (Spitschan et al., \protect\hyperlink{ref-Spitschan2015}{2015}), and do not typically affect pupil responses (Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}).
+
+\hypertarget{procedure}{%
+\subsection{Procedure}\label{procedure}}
+
+Before the start of each experiment, participants adjusted the objective planes of the lenses with the help of the experimenter until the stimulus was in focus and they perceived the two pieces of blackout material as one fused disc.
+Pupil responses to binocular temporal contrast modulations were examined in a factorial design that combined six ocular conditions and five temporal contrast levels: 6, 12, 24, 48 and 96\% of the available dynamic range.
+This design, similar to that used in our previous studies (Baker and Wade, \protect\hyperlink{ref-Baker2017}{2017}; Baker et al., \protect\hyperlink{ref-Baker2020}{2020}; Segala et al., \protect\hyperlink{ref-Segala2023}{2023}), was applied in four separate experiments, each with a different mode of photoreceptor stimulation.
+In the first three conditions, the discs flickered at 0.5 Hz, in either a monocular, binocular or dichoptic arrangement.
+In the dichoptic condition the non-target eye saw a flickering fixed contrast of 48\% of the available dynamic range.
+In the remaining three conditions (the cross-frequency conditions) one eye's disc flickered at 0.4 Hz, and the other eye's disc flickered at 0.5 Hz.
+This included monocular responses at 0.4 Hz, as well as binocular (one eye sees each frequency at the target contrast) and dichoptic (target stimulus flickering at 0.5 Hz, mask contrast of 48\% at 0.4 Hz in the other eye) arrangements.
+We counterbalanced presentation of the target stimulus across the left and right eyes.
+
+The experiments were conducted in a windowless room, in which the only source of light was the modified VR headset.
+The participants sat as close as possible to the VR headset, leaving enough space for the eye-tracker to record the eyes.
+Each experiment was carried out in a single session of around 45-60 minutes, divided into three blocks of 15-17 minutes each.
+In each block, there were a total of 60 trials lasting 15 seconds each (12s of stimulus presentation, followed by 3s of interstimulus interval).
+The participants were given no task other than look at the black fixation dot while trying to minimise their blinking during the presentation period.
+For all experiments other than the luminance condition, participants adapted to the unmodulated background luminance for two minutes before stimulation began.
+
+Before the start of the L-M experiment, participants completed a luminance nulling perceptual calibration procedure in L-M cone space on an Iiyama \(\textrm{VisionMaster}^{\textrm{TM}}\) Pro 510 display (800 x 600 pixels, 60 Hz refresh rate).
+During the task, participants were presented with a disc flickering within the L-M cone space (between magenta and cyan).
+Using a trackball, participants adjusted the angle in cone space to find their subjective isoluminant point, which resulted in changing the flickering intensity of the stimulus until the amplitude of the flicker appeared to be minimised.
+The result was used to modify the requested contrasts during stimulus preparation so as to account for individual differences affecting perceived illuminance, principally the L:M cone ratio (Carroll et al., \protect\hyperlink{ref-Carroll2002}{2002}; Hofer et al., \protect\hyperlink{ref-Hofer2005}{2005}).
+
+\hypertarget{data-analysis}{%
+\subsection{Data analysis}\label{data-analysis}}
+
+The pupillometry data were analysed using the same method we used in our previous study (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}).
+The data were converted from mp4 videos to a csv text file using the Pupil Player software (Kassner et al., \protect\hyperlink{ref-Kassner2014}{2014}), which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
+The individual data were then loaded into R for analysis, where a ten-second waveform for each trial in each eye was extracted (excluding the first two seconds after stimulus onset).
+We interpolated across any dropped or missing frames to ensure regular and continuous sampling over time.
+The Fourier transform was calculated for each waveform, and all repetitions of each condition were pooled across eye and then averaged.
+Finally, data were averaged across all participants to obtain the group results.
+We used coherent averaging and at each stage we excluded data points with a Mahalanobis distance exceeding \(D\) = 3 from the complex-valued mean (Baker, \protect\hyperlink{ref-Baker2021}{2021}).
+For monocular stimulation, we confirmed that the consensual response was equivalent to the response in the stimulated eye.
+
+For all experiments, we used a bootstrapping procedure with \ensuremath{10^{4}} iterations to estimate standard errors across participants.
+All analysis and figure construction was conducted using a single R-script, available online, making this study fully computationally reproducible: \url{https://osf.io/gdvt4/}.
+
+\hypertarget{computational-model-and-parameter-estimation}{%
+\subsection{Computational model and parameter estimation}\label{computational-model-and-parameter-estimation}}
+
+To describe our data, we used the same model described in our previous study (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}).
+The model has the same general form as the first stage of the contrast gain control model proposed by Meese et al.
+(\protect\hyperlink{ref-Meese2006}{2006}), but omits the second stage.
+For the previous model that we used (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}), the exponent of the numerator and denominator had fixed values of 2 and (implicitly) 1.
+Here, we allow these parameters (called \emph{p} and \emph{q}) to be free, in order to permit different shapes of contrast response function, e.g.~accelerating or saturating.
+The responses of the left eye and right eye channels are as follows:
+
+\begin{equation}
+\label{eq:respL}
+resp_L = \frac{L^p}{Z + L^q + \omega R^q},
+\end{equation}
+
+\begin{equation}
+\label{eq:respR}
+resp_R = \frac{R^p}{Z + R^q + \omega L^q},
+\end{equation}
+
+\noindent where \emph{L} and \emph{R} are the contrast signals from the left and right eyes, \emph{p} and \emph{q} are exponents, \emph{Z} is a saturation constant that shifts the contrast-response function laterally, and \(\omega\) is the weight of suppression from the other eye.
+
+The responses from the two eyes are then summed binocularly:
+
+\begin{equation}
+\label{eq:respB}
+resp_B = R_{max}(resp_L + resp_R) + k,
+\end{equation}
+
+\noindent where \emph{k} is a noise parameter, and \(R_{max}\) scales the overall response amplitude.
+
+The models were fit using a hierarchical Bayesian framework implemented in Stan (Carpenter et al., \protect\hyperlink{ref-Carpenter2017}{2017}).
+The data for each photoreceptor type and response frequency was fit separately, for a total of 8 model fits.
+The prior for the \(\omega\) parameter was Gaussian, with a mean of 1 and standard deviation of 0.5.
+Priors for the other free parameters were also Gaussian, with mean values based on previous work (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}).
+We calculated over \ensuremath{10^{6}} posterior samples, and retained 10\% for plotting.
 
@@
 
-In contemporary models of binocular signal combination, the amount of binocular facilitation is determined by the magnitude of interocular suppression, with strong suppression reducing facilitation (\protect\hyperlink{ref-Kingdom2015}{34}).
+In contemporary models of binocular signal combination, the amount of binocular facilitation is determined by the magnitude of interocular suppression, with strong suppression reducing facilitation (Kingdom and Libenson, \protect\hyperlink{ref-Kingdom2015}{2015}).
 We can estimate the strength of interocular suppression by measuring how much monocular responses are reduced when a dichoptic `mask' is shown to the other eye.
-In our paradigm, the two components flickered at different frequencies (0.5 and 0.4Hz) so that their responses remained distinct in the Fourier spectrum (\protect\hyperlink{ref-Busse2009}{35}).
+In our paradigm, the two components flickered at different frequencies (0.5 and 0.4Hz) so that their responses remained distinct in the Fourier spectrum (e.g.~Busse et al., \protect\hyperlink{ref-Busse2009}{2009}).
 The yellow diamond symbols in Figure \ref{fig:FirstHarmonicPlots}a-d show the target responses in this condition, and in most cases were weaker than the monocular responses (red circles).
@@
 
-To estimate the extent of interocular suppression for each photoreceptor pathway, we fitted each data set using a Bayesian hierarchical implementation of a simple binocular combination model (\protect\hyperlink{ref-Segala2023}{5}, \protect\hyperlink{ref-Meese2006}{33}).
+To estimate the extent of interocular suppression for each photoreceptor pathway, we fitted each data set using a Bayesian hierarchical implementation of a simple binocular combination model (Meese et al., \protect\hyperlink{ref-Meese2006}{2006}; Segala et al., \protect\hyperlink{ref-Segala2023}{2023}).
 Our primary objective was to compare posterior distributions of the weight of interocular suppression, which are shown in Figure \ref{fig:FirstHarmonicPlots}e.
@@
 
-Finally, we inspected the response phase of our four stimulation conditions, given previous reports that these differ across pathways (\protect\hyperlink{ref-Spitschan2014}{10}), and may be in antiphase for melanopsin and S-cone signals.
+Finally, we inspected the response phase of our four stimulation conditions, given previous reports that these differ across pathways (Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}), and may be in antiphase for melanopsin and S-cone signals.
 Figure \ref{fig:phaseplots} shows the phase angles for the first (a) and second (b) harmonic frequencies for binocular stimulation (monocular stimulation produced very similar results).
@@
 This is the first study to investigate binocular interactions in the melanopsin pathway directly.
-A previous meta-analysis (\protect\hyperlink{ref-Spitschan2019}{11}) indicated that there may be a substantial binocular facilitation effect in the circadian pathway, as indexed by melatonin suppression (melatonin is a hormone released by the pineal gland; its production is suppressed by exposure to bright light, particularly when the melanopsin-containing ipRGCs are stimulated).
+A previous meta-analysis (Spitschan and Cajochen, \protect\hyperlink{ref-Spitschan2019}{2019}) indicated that there may be a substantial binocular facilitation effect in the circadian pathway, as indexed by melatonin suppression (melatonin is a hormone released by the pineal gland; its production is suppressed by exposure to bright light, particularly when the melanopsin-containing ipRGCs are stimulated).
 In brief, monocular stimulation of the ipRGCs requires up to ten times the signal strength to produce an equivalent effect to binocular stimulation.
@@
 The explanation for this difference could be due to different anatomical pathways.
-Binocular combination in the circadian system likely takes place in the suprachiasmatic nucleus, whereas in the pupil constriction circuit the Edinger-Westphal nucleus is the most likely site of binocular integration (\protect\hyperlink{ref-Mathot2018}{13}).
+Binocular combination in the circadian system likely takes place in the suprachiasmatic nucleus, whereas in the pupil constriction circuit the Edinger-Westphal nucleus is the most likely site of binocular integration (Mathôt, \protect\hyperlink{ref-Mathot2018}{2018}).
 Presumably these anatomical differences, and the practical constraints of the two systems, lead to differences in response.
 
-Our recent psychophysical work (\protect\hyperlink{ref-Baker2024}{36}) has looked at binocular interactions in the L-M and S-cone pathways, and compared these to the luminance pathway.
-Using a contrast discrimination paradigm with spatial modulations of luminance and colour, (\protect\hyperlink{ref-Baker2024}{36}) found equally strong interocular suppression in all three pathways.
+Our recent psychophysical work (Baker et al., \protect\hyperlink{ref-Baker2024}{2024}) has looked at binocular interactions in the L-M and S-cone pathways, and compared these to the luminance pathway.
+Using a contrast discrimination paradigm with spatial modulations of luminance and colour, Baker et al.
+(\protect\hyperlink{ref-Baker2024}{2024}) found equally strong interocular suppression in all three pathways.
 This is rather different from our pupillometry results here, which demonstrate weaker suppression in the luminance and S-cone pathways than in the L-M pathway (see Figure \ref{fig:FirstHarmonicPlots}).
-However, the current experiments involve temporal modulations, which are quite distinct from the spatial modulations used in (\protect\hyperlink{ref-Baker2024}{36}).
-Our other recent work (\protect\hyperlink{ref-Segala2023}{5}) has shown that temporal luminance modulations involve much weaker interocular suppression in the cortical response than do spatial luminance modulations (\protect\hyperlink{ref-Baker2017}{37}).
+However, the current experiments involve temporal modulations, which are quite distinct from the spatial modulations used in Baker et al.
+(\protect\hyperlink{ref-Baker2024}{2024}).
+Our other recent work (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}) has shown that temporal luminance modulations involve much weaker interocular suppression in the cortical response than do spatial luminance modulations (Baker and Wade, \protect\hyperlink{ref-Baker2017}{2017}).
 These different normalization processes might reflect different priorities for spatial and temporal vision.
-Spatial vision aims to fuse images to provide binocular single vision, and benefits from `ocularity invariance' (\protect\hyperlink{ref-Baker2007}{31}), in which visual appearance is constant when viewed with one eye or two.
-Temporal vision is critical for motion perception, which can involve alternative binocular computations, such as calculating velocity differences between the eyes (\protect\hyperlink{ref-Kaestner2019}{38}).
+Spatial vision aims to fuse images to provide binocular single vision, and benefits from `ocularity invariance' (Baker et al., \protect\hyperlink{ref-Baker2007}{2007}), in which visual appearance is constant when viewed with one eye or two.
+Temporal vision is critical for motion perception, which can involve alternative binocular computations, such as calculating velocity differences between the eyes (Kaestner et al., \protect\hyperlink{ref-Kaestner2019}{2019}).
 Of course the present measurements were of pupil size, which may be subject to different anatomical and functional constraints from those in the cortex.
@@
 
-\hypertarget{materials-and-methods}{%
-\section{Materials and methods}\label{materials-and-methods}}
-
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
-
-Twenty-four participants were recruited for each of the four experiments for a total of ninety-six adult participants (28 male, 68 female), whose ages ranged from 18 to 41.
-All participants had normal or corrected to normal vision, no known abnormalities of binocular or colour vision, and gave written informed consent.
-Our procedures were approved by the Ethics Committee of the Department of Psychology at the University of York (identification number 184).
-
-\hypertarget{apparatus-stimuli}{%
-\subsection{Apparatus \& stimuli}\label{apparatus-stimuli}}
-
-To present synchronised stimulus modulations independently to each eye, two light engines (SpectraTuneLAB: LEDMOTIVE Technologies, LLC, Barcelona, Spain), each with 10 independently addressable LED colour channels, were integrated into a customised viewing system.
-The light engines were operated via a Python interface to their REST API (\protect\hyperlink{ref-Martin2022}{39}), which supports synchronous launch and playback of spectral sequences prepared in advance and stored in JSON format.
-When preparing the spectral sequences, the age of participants was used to account for the yellowing of the lenses.
-We calculated silent substitution solutions using the \emph{PySilSub} toolbox (\protect\hyperlink{ref-Martin2023}{40}), using linear algebra.
-The outputs of the two light engines (see Figure \ref{fig:spectraplots}b,c) were calibrated using an Ocean Optics Jaz spectroradiometer, which was wavelength-calibrated to an Argon lamp and intensity calibrated using a NIST-traceable light source.
-We used the (\protect\hyperlink{ref-Stockman2000}{41}) 10-degree cone fundamentals, and estimates of melanopsin absorbance spectra from CIE S 026 (\protect\hyperlink{ref-Martin2023}{40}) to calculate \(\alpha\)-opic irradiance.
-
-The output from the light engines was directed through liquid light guides (LLG3-8H: Thorlabs Ltd, Cambridgeshire, UK) and diffused onto semi-opaque and highly diffusive white glass discs with a diameter of 50 mm for even illumination (34-473: Edmund Optics, York, UK).
-The light guide gaskets were butt-coupled to the light engine diffusers with threaded adapters (SM1A9, AD3LLG: Thorlabs Ltd, Cambridgeshire, UK) and the exiting ends of the light guides were mated with 51 mm depth optical cylinders (SM2L20: Thorlabs Ltd, Cambridgeshire, UK) via appropriately threaded adapters (AD3LLG, SM2A6: Thorlabs Ltd, Cambridgeshire, UK).
-The stimulus diffuser discs were retained at the front end of the optical cylinders approximately 51 mm from the light source, at which distance the output beam was sufficiently dispersed to afford even illumination of the diffuser when viewed from the front.
-To guarantee safe illumination levels, a circular neutral-density filter with the same diameter of the white glass discs (50 mm) and an optical density of 0.6 log units was placed in the optical path between the light source and the diffusers.
-A small circular piece of blackout material with a diameter of approximately 8 degrees (10 mm) was positioned centrally on the front of each diffuser disc to aid as a fusion lock, as a fixation point, and to occlude the fovea.
-
-The diffuser discs were positioned in the objective planes of the lenses of a modified VR headset (SHINECON SC-G01, Dongguan Shinecon Industrial Co.~Ltd., Guangdong, China), which was used by the participants to view the stimuli.
-The stimuli were two discs of flickering light with a diameter of approximately 30 degrees, which were fused together into a cyclopean percept resembling a donut-shaped ring of light, similar to that used in other studies (\protect\hyperlink{ref-Murray2018}{9}, \protect\hyperlink{ref-Spitschan2014}{10}, \protect\hyperlink{ref-Barrionuevo2016}{42}--\protect\hyperlink{ref-Zele2018}{44}).
-The VR headset modifications allowed for small adjustments to account for individual differences in interpupillary distance and focal length.
-The use of this set up allowed us to modulate the stimuli in three different ocular configurations, similar to the ones we used in our previous study (\protect\hyperlink{ref-Segala2023}{5}): monocular, binocular and dichoptic.
-In the monocular configuration, the unstimulated eye still saw a non-flickering disc of mean luminance.
-A schematic of the stimulation system is shown in Figure \ref{fig:spectraplots}a.
-Pupillometry data were collected using a binocular Pupil Core eye-tracker headset (\protect\hyperlink{ref-Kassner2014}{45}) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
-
-Our previous study (\protect\hyperlink{ref-Segala2023}{5}) used a temporal frequency of 2Hz for foveal luminance flicker, and recorded EEG data simultaneously with pupillometry.
-Initial pilot experiments indicated that this frequency was too high to elicit measurable responses when stimulating individual photoreceptor pathways.
-For all experiments, we therefore used a primary flicker frequency of 0.5Hz, as previous literature showed that this was slow enough to elicit a pupil response from all photoreceptor classes (\protect\hyperlink{ref-Spitschan2014}{10}).
-We also focussed on only recording pupillometry data as this frequency would be too slow to elicit steady-state EEG responses (\protect\hyperlink{ref-Norcia2015}{46}).
-
-For all experiments, sinusoidal temporal modulations were presented against the same background spectrum (matched between the eyes), which was used to achieve silent substitution in the three photoreceptor modulation experiments.
-The background spectra were defined by setting all channels to half maximum output for the brighter of the two devices (STLab 1, left eye) and then using the STLab 1/STLab 2 calibration ratio to find the equivalent settings for the companion device (STLab 2, right eye).
-The background spectrum illuminance was approximately 74 lux, or 68.5 cd/m\(^2\).
-The spectral power distributions and \(\alpha\)-opic irradiances of the background spectra for both eyes are shown in Figure \ref{fig:spectraplots}c-d.
-
-In the luminance experiment, the stimulus intensity was increased and decreased relative to the background, which we expected to modulate all photoreceptor classes (see Figure \ref{fig:spectraplots}e,i).
-In the L-M cone modulation experiment, we used silent substution to increase the L-cone activity, and simultaneously decrease the M-cone activity, during the first half-cycle of the sine wave.
-In the second half-cycle the polarity of the modulation reversed (see Figure \ref{fig:spectraplots}f,j).
-The maximum available L-M contrast was approximately 10\%.
-In the S-cone modulation experiment, we increased and decreased S-cone-directed signals, whilst keeping activity in the other photoreceptors constant (see Figure \ref{fig:spectraplots}g,k).
-Our system allowed a maximum contrast of 45\%.
-Finally, in the melanopsin experiment, we modulated the activity of the melanopsin-containing intrinsically photoreceptive retinal ganglion cells, whilst keeping cone activity constant (see Figure \ref{fig:spectraplots}h,l).
-The maximum available melanopsin contrast was 22\%.
-We assume that the activity of rods was constant at the high background luminance intensity used here, and so did not attempt to silence rod activity in any condition, as this would have greatly reduced the available dynamic range.
-Splatter on nominally silenced photoreceptors was very small (see Figure \ref{fig:spectraplots}j-l), well below the levels that would be expected to generate measureable pupil modulations.
-We also estimated activation of penumbral L and M cones (\protect\hyperlink{ref-Barrionuevo2016}{42}, \protect\hyperlink{ref-Spitschan2015}{43}, \protect\hyperlink{ref-Zele2019}{47}), which was minimal (\(\le 1.5%
-\) contrast; less than splatter on the open-field cones) for melanopsin-directed stimuli.
-We note that the temporal frequency of our modulation (0.5Hz) is well below the range where penumbral cone activation can elicit visible percepts, and that such percepts fade after around 1 second (\protect\hyperlink{ref-Spitschan2015}{43}), and do not typically affect pupil responses (\protect\hyperlink{ref-Spitschan2014}{10}).
-
-\hypertarget{procedure}{%
-\subsection{Procedure}\label{procedure}}
-
-Before the start of each experiment, participants adjusted the objective planes of the lenses with the help of the experimenter until the stimulus was in focus and they perceived the two pieces of blackout material as one fused disc.
-Pupil responses to binocular temporal contrast modulations were examined in a factorial design that combined six ocular conditions and five temporal contrast levels: 6, 12, 24, 48 and 96\% of the available dynamic range.
-This design, similar to that used in our previous studies (\protect\hyperlink{ref-Segala2023}{5}, \protect\hyperlink{ref-Baker2017}{37}, \protect\hyperlink{ref-Baker2020}{48}), was applied in four separate experiments, each with a different mode of photoreceptor stimulation.
-In the first three conditions, the discs flickered at 0.5 Hz, in either a monocular, binocular or dichoptic arrangement.
-In the dichoptic condition the non-target eye saw a flickering fixed contrast of 48\% of the available dynamic range.
-In the remaining three conditions (the cross-frequency conditions) one eye's disc flickered at 0.4 Hz, and the other eye's disc flickered at 0.5 Hz.
-This included monocular responses at 0.4 Hz, as well as binocular (one eye sees each frequency at the target contrast) and dichoptic (target stimulus flickering at 0.5 Hz, mask contrast of 48\% at 0.4 Hz in the other eye) arrangements.
-We counterbalanced presentation of the target stimulus across the left and right eyes.
-
-The experiments were conducted in a windowless room, in which the only source of light was the modified VR headset.
-The participants sat as close as possible to the VR headset, leaving enough space for the eye-tracker to record the eyes.
-Each experiment was carried out in a single session of around 45-60 minutes, divided into three blocks of 15-17 minutes each.
-In each block, there were a total of 60 trials lasting 15 seconds each (12s of stimulus presentation, followed by 3s of interstimulus interval).
-The participants were given no task other than look at the black fixation dot while trying to minimise their blinking during the presentation period.
-For all experiments other than the luminance condition, participants adapted to the unmodulated background luminance for two minutes before stimulation began.
-
-Before the start of the L-M experiment, participants completed a luminance nulling perceptual calibration procedure in L-M cone space on an Iiyama \(\textrm{VisionMaster}^{\textrm{TM}}\) Pro 510 display (800 x 600 pixels, 60 Hz refresh rate).
-During the task, participants were presented with a disc flickering within the L-M cone space (between magenta and cyan).
-Using a trackball, participants adjusted the angle in cone space to find their subjective isoluminant point, which resulted in changing the flickering intensity of the stimulus until the amplitude of the flicker appeared to be minimised.
-The result was used to modify the requested contrasts during stimulus preparation so as to account for individual differences affecting perceived illuminance, principally the L:M cone ratio (\protect\hyperlink{ref-Carroll2002}{49}, \protect\hyperlink{ref-Hofer2005}{50}).
-
-\hypertarget{data-analysis}{%
-\subsection{Data analysis}\label{data-analysis}}
-
-The pupillometry data were analysed using the same method we used in our previous study (\protect\hyperlink{ref-Segala2023}{5}).
-The data were converted from mp4 videos to a csv text file using the Pupil Player software (\protect\hyperlink{ref-Kassner2014}{45}), which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
-The individual data were then loaded into R for analysis, where a ten-second waveform for each trial in each eye was extracted (excluding the first two seconds after stimulus onset).
-We interpolated across any dropped or missing frames to ensure regular and continuous sampling over time.
-The Fourier transform was calculated for each waveform, and all repetitions of each condition were pooled across eye and then averaged.
-Finally, data were averaged across all participants to obtain the group results.
-We used coherent averaging and at each stage we excluded data points with a Mahalanobis distance exceeding \(D\) = 3 from the complex-valued mean (\protect\hyperlink{ref-Baker2021}{51}).
-For monocular stimulation, we confirmed that the consensual response was equivalent to the response in the stimulated eye.
-
-For all experiments, we used a bootstrapping procedure with \ensuremath{10^{4}} iterations to estimate standard errors across participants.
-All analysis and figure construction was conducted using a single R-script, available online, making this study fully computationally reproducible: \url{https://osf.io/gdvt4/}.
-
-\hypertarget{computational-model-and-parameter-estimation}{%
-\subsection{Computational model and parameter estimation}\label{computational-model-and-parameter-estimation}}
-
-To describe our data, we used the same model described in our previous study (\protect\hyperlink{ref-Segala2023}{5}).
-The model has the same general form as the first stage of the contrast gain control model proposed by (\protect\hyperlink{ref-Meese2006}{33}), but omits the second stage.
-For the previous model that we used (\protect\hyperlink{ref-Segala2023}{5}), the exponent of the numerator and denominator had fixed values of 2 and (implicitly) 1.
-Here, we allow these parameters (called \emph{p} and \emph{q}) to be free, in order to permit different shapes of contrast response function, e.g.~accelerating or saturating.
-The responses of the left eye and right eye channels are as follows:
-
-\begin{equation}
-\label{eq:respL}
-resp_L = \frac{L^p}{Z + L^q + \omega R^q},
-\end{equation}
-
-\begin{equation}
-\label{eq:respR}
-resp_R = \frac{R^p}{Z + R^q + \omega L^q},
-\end{equation}
-
-\noindent where \emph{L} and \emph{R} are the contrast signals from the left and right eyes, \emph{p} and \emph{q} are exponents, \emph{Z} is a saturation constant that shifts the contrast-response function laterally, and \(\omega\) is the weight of suppression from the other eye.
-
-The responses from the two eyes are then summed binocularly:
-
-\begin{equation}
-\label{eq:respB}
-resp_B = R_{max}(resp_L + resp_R) + k,
-\end{equation}
-
-\noindent where \emph{k} is a noise parameter, and \(R_{max}\) scales the overall response amplitude.
-
-The models were fit using a hierarchical Bayesian framework implemented in Stan (\protect\hyperlink{ref-Carpenter2017}{52}).
-The data for each photoreceptor type and response frequency was fit separately, for a total of 8 model fits.
-The prior for the \(\omega\) parameter was Gaussian, with a mean of 1 and standard deviation of 0.5.
-Priors for the other free parameters were also Gaussian, with mean values based on previous work (\protect\hyperlink{ref-Segala2023}{5}).
-We calculated over \ensuremath{10^{6}} posterior samples, and retained 10\% for plotting.
-
-\hypertarget{acknowledgements-and-funding-sources}{%
-\section{Acknowledgements and funding sources}\label{acknowledgements-and-funding-sources}}
-
-Supported by Biotechnology and Biological Sciences Research Council grant BB/V007580/1 awarded to DHB and ARW.
-
 \hypertarget{references}{%
@@
 \hypertarget{refs}{}
-\leavevmode\hypertarget{ref-McDougal2015}{}%
-1. D. H. McDougal, P. D. Gamlin, Autonomic control of the eye. \emph{Comprehensive Physiology} \textbf{5}, 439--473 (2015).
+\leavevmode\hypertarget{ref-Baker2021}{}%
+Baker DH (2021) Statistical analysis of periodic data in neuroscience. Neurons, Behavior, Data analysis, and Theory 5 Available at: \url{https://doi.org/10.51628\%2F001c.27680}.
+
+\leavevmode\hypertarget{ref-Baker2024}{}%
+Baker DH, Hansford KJ, Segala FG, Morsi AY, Huxley RJ, Martin JT, Rockman M, Wade AR (2024) Binocular integration of chromatic and luminance signals. Journal of Vision Under review.
+
+\leavevmode\hypertarget{ref-Baker2018}{}%
+Baker DH, Lygo FA, Meese TS, Georgeson MA (2018) Binocular summation revisited: Beyond \(\sqrt{2}\). Psychol Bull 144:1186--1199.
+
+\leavevmode\hypertarget{ref-Baker2007}{}%
+Baker DH, Meese TS, Georgeson MA (2007) Binocular interaction: Contrast matching and contrast discrimination are predicted by the same model. Spat Vis 20:397--413.
+
+\leavevmode\hypertarget{ref-Baker2020}{}%
+Baker DH, Vilidaite G, McClarnon E, Valkova E, Bruno A, Millman RE (2020) Binaural summation of amplitude modulation involves weak interaural suppression. Sci Rep 10:3560.
+
+\leavevmode\hypertarget{ref-Baker2017}{}%
+Baker DH, Wade AR (2017) Evidence for an optimal algorithm underlying signal combination in human visual cortex. Cereb Cortex 27:254--264.
+
+\leavevmode\hypertarget{ref-Barrionuevo2016}{}%
+Barrionuevo PA, Cao D (2016) Luminance and chromatic signals interact differently with melanopsin activation to control the pupil light response. Journal of Vision 16(11):29.
+
+\leavevmode\hypertarget{ref-Barrionuevo2018}{}%
+Barrionuevo PA, McAnany JJ, Zele AJ, Cao D (2018) Non-linearities in the Rod and Cone Photoreceptor Inputs to the Afferent Pupil Light Response. Frontiers in Neurology 9.
+
+\leavevmode\hypertarget{ref-Barrionuevo2014}{}%
+Barrionuevo PA, Nicandro N, McAnany JJ, Zele AJ, Gamlin P, Cao D (2014) Assessing rod, cone, and melanopsin contributions to human pupil flicker responses.
+Investigative Ophthalmology \& Visual Science 55:719--727.
+
+\leavevmode\hypertarget{ref-Busse2009}{}%
+Busse L, Wade AR, Carandini M (2009) Representation of concurrent stimuli by population activity in visual cortex. Neuron 64:931--942.
+
+\leavevmode\hypertarget{ref-Campbell1965}{}%
+Campbell FW, Green DG (1965) Monocular versus binocular visual acuity. Nature 208:191--192.
+
+\leavevmode\hypertarget{ref-Cao2015}{}%
+Cao D, Nicandro N, Barrionuevo PA (2015) A five-primary photostimulator suitable for studying intrinsically photosensitive retinal ganglion cell functions in humans.
+Journal of Vision 15:27 Available at: \url{https://doi.org/10.1167/15.1.27} {[}Accessed July 18, 2023{]}.
+
+\leavevmode\hypertarget{ref-Carpenter2017}{}%
+Carpenter B, Gelman A, Hoffman MD, Lee D, Goodrich B, Betancourt M, Brubaker MA, Guo J, Li P, Riddell A (2017) Stan: A probabilistic programming language. J Stat Softw 76.
+
+\leavevmode\hypertarget{ref-Carroll2002}{}%
+Carroll J, Neitz J, Neitz M (2002) Estimates of L:M cone ratio from ERG flicker photometry and genetics.
+Journal of Vision 2:1 Available at: \url{https://doi.org/10.1167/2.8.1} {[}Accessed June 5, 2023{]}.
+
+\leavevmode\hypertarget{ref-Dacey2005}{}%
+Dacey DM, Liao H-W, Peterson BB, Robinson FR, Smith VC, Pokorny J, Yau K-W, Gamlin PD (2005) Melanopsin-expressing ganglion cells in primate retina signal colour and irradiance and project to the LGN.
+Nature 433:749--754 Available at: \url{https://www.nature.com/articles/nature03387} {[}Accessed July 18, 2023{]}.
+
+\leavevmode\hypertarget{ref-Dacey2003}{}%
+Dacey DM, Peterson BB, Robinson FR, Gamlin PD (2003) Fireworks in the primate retina: In vitro photodynamics reveals diverse lgn-projecting ganglion cell types.
+Neuron 37:15--27 Available at: \url{https://www.sciencedirect.com/science/article/pii/S0896627302011431}.
+
+\leavevmode\hypertarget{ref-Ding2006}{}%
+Ding J, Sperling G (2006) A gain-control theory of binocular combination. Proc Natl Acad Sci U S A 103:1141--1146.
+
+\leavevmode\hypertarget{ref-Estevez1982}{}%
+Estévez O, Spekreijse H (1982) The "silent substitution" method in visual research.
+Vision Research 22:681--691 Available at: \url{https://www.sciencedirect.com/science/article/pii/0042698982901043} {[}Accessed July 18, 2023{]}.
+
+\leavevmode\hypertarget{ref-Gamlin2007}{}%
+Gamlin PDR, McDougal DH, Pokorny J, Smith VC, Yau K-W, Dacey DM (2007) Human and macaque pupil responses driven by melanopsin-containing retinal ganglion cells.
+Vision Research 47:946--954 Available at: \url{https://www.sciencedirect.com/science/article/pii/S0042698906005682} {[}Accessed July 18, 2023{]}.
+
+\leavevmode\hypertarget{ref-Hofer2005}{}%
+Hofer H, Carroll J, Neitz J, Neitz M, Williams DR (2005) Organization of the human trichromatic cone mosaic.
+The Journal of Neuroscience 25:9669--9679 Available at: \url{https://doi.org/10.1523\%2Fjneurosci.2414-05.2005}.
+
+\leavevmode\hypertarget{ref-Hubel1962}{}%
+Hubel DH, Wiesel TN (1962) Receptive fields, binocular interaction and functional architecture in the cat's visual cortex. J Physiol 160:106--154.
+
+\leavevmode\hypertarget{ref-Kaestner2019}{}%
+Kaestner M, Maloney RT, Wailes-Newson KH, Bloj M, Harris JM, Morland AB, Wade AR (2019) Asymmetries between achromatic and chromatic extraction of 3D motion signals.
+Proc Natl Acad Sci U S A 116:13631--13640.
+
+\leavevmode\hypertarget{ref-Kassner2014}{}%
+Kassner M, Patera W, Bulling A (2014) Pupil: An open source platform for pervasive eye tracking and mobile gaze-based interaction.
+In: Proceedings of the 2014 ACM international joint conference on pervasive and ubiquitous computing: Adjunct publication.
+ACM.
+Available at: \url{https://doi.org/10.1145\%2F2638728.2641695}.
+
+\leavevmode\hypertarget{ref-Kingdom2015}{}%
+Kingdom FAA, Libenson L (2015) Dichoptic color saturation mixture: Binocular luminance contrast promotes perceptual averaging. J Vis 15:2.
+
+\leavevmode\hypertarget{ref-Legge1984}{}%
+Legge GE (1984) Binocular contrast summation--ii. Quadratic summation. Vision Res 24:385--394.
+
+\leavevmode\hypertarget{ref-Lucas2003}{}%
+Lucas RJ, Hattar S, Takao M, Berson DM, Foster RG, Yau K-W (2003) Diminished pupillary light reflex at high irradiances in melanopsin-knockout mice.
+Science 299:245--247 Available at: \url{https://doi.org/10.1126\%2Fscience.1077293}.
+
+\leavevmode\hypertarget{ref-Markwell2010}{}%
+Markwell EL, Feigl B, Zele AJ (2010) Intrinsically photosensitive melanopsin retinal ganglion cell contributions to the pupillary light reflex and circadian rhythm.
+Clinical and Experimental Optometry 93:137--149 Available at: \url{https://doi.org/10.1111\%2Fj.1444-0938.2010.00479.x}.
+
+\leavevmode\hypertarget{ref-Martin2023}{}%
+Martin JT, Boynton GM, Baker DH, Wade AR, Spitschan M (2023) PySilSub: An open-source python toolbox for implementing the method of silent substitution in vision and nonvisual photoreception research.
+Journal of Vision 23:10 Available at: \url{https://doi.org/10.1167\%2Fjov.23.7.10}.
+
+\leavevmode\hypertarget{ref-Martin2022}{}%
+Martin JT, Pinto J, Bulte D, Spitschan M (2022) PyPlr: A versatile, integrated system of hardware and software for researching the human pupillary light reflex.
+Behavior Research Methods 54:2720--2739.
+
+\leavevmode\hypertarget{ref-Mathot2018}{}%
+Mathôt S (2018) Pupillometry: Psychology, physiology, and function. J Cogn 1:16.
 
 \leavevmode\hypertarget{ref-McDougal2008}{}%
-2. D. H. McDougal, P. D. Gamlin, ``Pupillary control pathways.'' in \emph{The Senses: A Comprehensive Reference}, (Elsevier, 2008), pp. 521--536.
+McDougal DH, Gamlin PD (2008) Pupillary control pathways. In: The senses: A comprehensive reference, pp 521--536. Elsevier.
+
+\leavevmode\hypertarget{ref-McDougal2010}{}%
+McDougal DH, Gamlin PD (2010) The influence of intrinsically-photosensitive retinal ganglion cells on the spectral sensitivity and response dynamics of the human pupillary light reflex.
+Vision Research 50:72--87 Available at: \url{https://www.sciencedirect.com/science/article/pii/S0042698909004763} {[}Accessed July 18, 2023{]}.
+
+\leavevmode\hypertarget{ref-McDougal2015}{}%
+McDougal DH, Gamlin PD (2015) Autonomic control of the eye. Comprehensive Physiology 5:439--473.
+
+\leavevmode\hypertarget{ref-Meese2006}{}%
+Meese TS, Georgeson MA, Baker DH (2006) Binocular contrast vision at and above threshold. Journal of Vision 6:1224--1243.
+
+\leavevmode\hypertarget{ref-Moradi2009}{}%
+Moradi F, Heeger DJ (2009) Inter-ocular contrast normalization in human visual cortex. J Vis 9:13.1--22.
+
+\leavevmode\hypertarget{ref-Murray2018}{}%
+Murray IJ, Kremers J, McKeefry D, Parry NRA (2018) Paradoxical pupil responses to isolated M-cone increments.
+Journal of the Optical Society of America A 35:B66--B71 Available at: \url{https://opg.optica.org/josaa/abstract.cfm?uri=josaa-35-4-B66} {[}Accessed July 18, 2023{]}.
+
+\leavevmode\hypertarget{ref-Norcia2015}{}%
+Norcia AM, Appelbaum LG, Ales JM, Cottereau BR, Rossion B (2015) The steady-state visual evoked potential in vision research: A review. Journal of Vision 15(6):4.
+
+\leavevmode\hypertarget{ref-Panda2002}{}%
+Panda S, Sato TK, Castrucci AM, Rollag MD, DeGrip WJ, Hogenesch JB, Provencio I, Kay SA (2002) Melanopsin (opn4) requirement for normal light-induced circadian phase shifting.
+Science 298:2213--2216 Available at: \url{https://doi.org/10.1126\%2Fscience.1076848}.
+
+\leavevmode\hypertarget{ref-Provencio2000}{}%
+Provencio I, Rodriguez IR, Jiang G, Hayes WP, Moreira EF, Rollag MD (2000) A Novel Human Opsin in the Inner Retina.
+Journal of Neuroscience 20:600--605 Available at: \url{https://www.jneurosci.org/content/20/2/600} {[}Accessed July 18, 2023{]}.
+
+\leavevmode\hypertarget{ref-Ruby2002}{}%
+Ruby NF, Brennan TJ, Xie X, Cao V, Franken P, Heller HC, O'Hara BF (2002) Role of melanopsin in circadian responses to light.
+Science 298:2211--2213 Available at: \url{https://doi.org/10.1126\%2Fscience.1076701}.
+
+\leavevmode\hypertarget{ref-Segala2023}{}%
+Segala FG, Bruno A, Martin JT, Aung MT, Wade AR, Baker DH (2023) Different rules for binocular combination of luminance flicker in cortical and subcortical pathways.
+eLife 12 Available at: \url{https://doi.org/10.7554\%2Felife.87048}.
+
+\leavevmode\hypertarget{ref-Shapiro1996}{}%
+Shapiro AG, Pokorny J, Smith VC (1996) Conerod receptor spaces with illustrations that use CRT phosphor and light-emitting-diode spectra.
+Journal of the Optical Society of America A 13:2319 Available at: \url{https://doi.org/10.1364\%2Fjosaa.13.002319}.
+
+\leavevmode\hypertarget{ref-Spitschan2015}{}%
+Spitschan M, Aguirre GK, Brainard DH (2015) Selective stimulation of penumbral cones reveals perception in the shadow of retinal blood vessels. PLoS One 10:e0124328.
+
+\leavevmode\hypertarget{ref-Spitschan2019}{}%
+Spitschan M, Cajochen C (2019) Binocular facilitation in light-mediated melatonin suppression? J Pineal Res 67:e12602.
+
+\leavevmode\hypertarget{ref-Spitschan2014}{}%
+Spitschan M, Jain S, Brainard DH, Aguirre GK (2014) Opponent melanopsin and s-cone signals in the human pupillary light response.
+Proceedings of the National Academy of Sciences 111:15568--15572 Available at: \url{https://doi.org/10.1073\%2Fpnas.1400942111}.
+
+\leavevmode\hypertarget{ref-Spitschan2018}{}%
+Spitschan M, Woelders T (2018) The Method of Silent Substitution for Examining Melanopsin Contributions to Pupil Control. Frontiers in Neurology 9.
+
+\leavevmode\hypertarget{ref-Stockman2000}{}%
+Stockman A, Sharpe LT (2000) The spectral sensitivities of the middle- and long-wavelength-sensitive cones derived from measurements in observers of known genotype. Vision Res 40:1711--1737.
 
 \leavevmode\hypertarget{ref-Wang2015}{}%
-3. C.-A. Wang, D. P. Munoz, A circuit for pupil orienting responses: Implications for cognitive modulation of pupil size. \emph{Curr Opin Neurobiol} \textbf{33}, 134--40 (2015).
+Wang C-A, Munoz DP (2015) A circuit for pupil orienting responses: Implications for cognitive modulation of pupil size. Curr Opin Neurobiol 33:134--140.
+
+\leavevmode\hypertarget{ref-Woelders2018}{}%
+Woelders T, Leenheers T, Gordijn MCM, Hut RA, Beersma DGM, Wams EJ (2018) Melanopsin- and L-cone--induced pupil constriction is inhibited by S- and M-cones in humans.
+Proceedings of the National Academy of Sciences 115:792--797 Available at: \url{https://www.pnas.org/doi/full/10.1073/pnas.1716281115} {[}Accessed July 18, 2023{]}.
 
 \leavevmode\hypertarget{ref-Wyatt1981}{}%
-4.
-H.
-J.
-Wyatt, J.
-F.
-Musselman, Pupillary light reflex in humans: Evidence for an unbalanced pathway from nasal retina, and for signal cancellation in brainstem.
-\emph{Vision Res} \textbf{21}, 513--25 (1981).
+Wyatt HJ, Musselman JF (1981) Pupillary light reflex in humans: Evidence for an unbalanced pathway from nasal retina, and for signal cancellation in brainstem. Vision Res 21:513--525.
 
-\leavevmode\hypertarget{ref-Segala2023}{}%
-5. F. G. Segala\emph{et al.}, Different rules for binocular combination of luminance flicker in cortical and subcortical pathways. \emph{eLife} \textbf{12} (2023).
-
-\leavevmode\hypertarget{ref-Barrionuevo2014}{}%
-6. P. A. Barrionuevo\emph{et al.}, Assessing rod, cone, and melanopsin contributions to human pupil flicker responses. \emph{Investigative Ophthalmology \& Visual Science} \textbf{55}, 719--27 (2014).
-
-\leavevmode\hypertarget{ref-Barrionuevo2018}{}%
-7. P. A. Barrionuevo, J. J. McAnany, A. J. Zele, D. Cao, Non-linearities in the Rod and Cone Photoreceptor Inputs to the Afferent Pupil Light Response. \emph{Frontiers in Neurology} \textbf{9} (2018).
-
-\leavevmode\hypertarget{ref-Dacey2005}{}%
-8. D. M. Dacey\emph{et al.}, Melanopsin-expressing ganglion cells in primate retina signal colour and irradiance and project to the LGN. \emph{Nature} \textbf{433}, 749--754 (2005).
-
-\leavevmode\hypertarget{ref-Murray2018}{}%
-9. I. J. Murray, J. Kremers, D. McKeefry, N. R. A. Parry, Paradoxical pupil responses to isolated M-cone increments. \emph{Journal of the Optical Society of America A} \textbf{35}, B66--B71 (2018).
-
-\leavevmode\hypertarget{ref-Spitschan2014}{}%
-10.
-M.
-Spitschan, S.
-Jain, D.
-H.
-Brainard, G.
-K.
-Aguirre, Opponent melanopsin and s-cone signals in the human pupillary light response.
-\emph{Proceedings of the National Academy of Sciences} \textbf{111}, 15568--15572 (2014).
-
-\leavevmode\hypertarget{ref-Spitschan2019}{}%
-11. M. Spitschan, C. Cajochen, Binocular facilitation in light-mediated melatonin suppression? \emph{J Pineal Res} \textbf{67}, e12602 (2019).
-
-\leavevmode\hypertarget{ref-Woelders2018}{}%
-12.
-T.
-Woelders\emph{et al.}, Melanopsin- and L-cone--induced pupil constriction is inhibited by S- and M-cones in humans.
-\emph{Proceedings of the National Academy of Sciences} \textbf{115}, 792--797 (2018).
-
-\leavevmode\hypertarget{ref-Mathot2018}{}%
-13. S. Mathôt, Pupillometry: Psychology, physiology, and function. \emph{J Cogn} \textbf{1}, 16 (2018).
-
-\leavevmode\hypertarget{ref-Markwell2010}{}%
-14.
-E.
-L.
-Markwell, B.
-Feigl, A.
-J.
-Zele, Intrinsically photosensitive melanopsin retinal ganglion cell contributions to the pupillary light reflex and circadian rhythm.
-\emph{Clinical and Experimental Optometry} \textbf{93}, 137--149 (2010).
-
-\leavevmode\hypertarget{ref-McDougal2010}{}%
-15.
-D.
-H.
-McDougal, P.
-D.
-Gamlin, The influence of intrinsically-photosensitive retinal ganglion cells on the spectral sensitivity and response dynamics of the human pupillary light reflex.
-\emph{Vision Research} \textbf{50}, 72--87 (2010).
-
-\leavevmode\hypertarget{ref-Provencio2000}{}%
-16. I. Provencio\emph{et al.}, A Novel Human Opsin in the Inner Retina. \emph{Journal of Neuroscience} \textbf{20}, 600--605 (2000).
-
-\leavevmode\hypertarget{ref-Panda2002}{}%
-17. S. Panda\emph{et al.}, Melanopsin (opn4) requirement for normal light-induced circadian phase shifting. \emph{Science} \textbf{298}, 2213--2216 (2002).
-
-\leavevmode\hypertarget{ref-Ruby2002}{}%
-18. N. F. Ruby\emph{et al.}, Role of melanopsin in circadian responses to light. \emph{Science} \textbf{298}, 2211--2213 (2002).
-
-\leavevmode\hypertarget{ref-Dacey2003}{}%
-19.
-D.
-M.
-Dacey, B.
-B.
-Peterson, F.
-R.
-Robinson, P.
-D.
-Gamlin, Fireworks in the primate retina: In vitro photodynamics reveals diverse lgn-projecting ganglion cell types.
-\emph{Neuron} \textbf{37}, 15--27 (2003).
-
-\leavevmode\hypertarget{ref-Lucas2003}{}%
-20. R. J. Lucas\emph{et al.}, Diminished pupillary light reflex at high irradiances in melanopsin-knockout mice. \emph{Science} \textbf{299}, 245--247 (2003).
-
-\leavevmode\hypertarget{ref-Gamlin2007}{}%
-21. P. D. R. Gamlin\emph{et al.}, Human and macaque pupil responses driven by melanopsin-containing retinal ganglion cells. \emph{Vision Research} \textbf{47}, 946--954 (2007).
-
-\leavevmode\hypertarget{ref-Estevez1982}{}%
-22. O. Estévez, H. Spekreijse, The "silent substitution" method in visual research. \emph{Vision Research} \textbf{22}, 681--691 (1982).
-
-\leavevmode\hypertarget{ref-Shapiro1996}{}%
-23.
-A.
-G.
-Shapiro, J.
-Pokorny, V.
-C.
-Smith, Conerod receptor spaces with illustrations that use CRT phosphor and light-emitting-diode spectra.
-\emph{Journal of the Optical Society of America A} \textbf{13}, 2319 (1996).
-
-\leavevmode\hypertarget{ref-Spitschan2018}{}%
-24. M. Spitschan, T. Woelders, The Method of Silent Substitution for Examining Melanopsin Contributions to Pupil Control. \emph{Frontiers in Neurology} \textbf{9} (2018).
-
-\leavevmode\hypertarget{ref-Cao2015}{}%
-25.
-D.
-Cao, N.
-Nicandro, P.
-A.
-Barrionuevo, A five-primary photostimulator suitable for studying intrinsically photosensitive retinal ganglion cell functions in humans.
-\emph{Journal of Vision} \textbf{15}, 27 (2015).
-
-\leavevmode\hypertarget{ref-Hubel1962}{}%
-26. D. H. Hubel, T. N. Wiesel, Receptive fields, binocular interaction and functional architecture in the cat's visual cortex. \emph{J Physiol} \textbf{160}, 106--54 (1962).
-
-\leavevmode\hypertarget{ref-Moradi2009}{}%
-27. F. Moradi, D. J. Heeger, Inter-ocular contrast normalization in human visual cortex. \emph{J Vis} \textbf{9}, 13.1--22 (2009).
-
-\leavevmode\hypertarget{ref-Baker2018}{}%
-28. D. H. Baker, F. A. Lygo, T. S. Meese, M. A. Georgeson, Binocular summation revisited: Beyond \(\sqrt{2}\). \emph{Psychol Bull} \textbf{144}, 1186--1199 (2018).
-
-\leavevmode\hypertarget{ref-Campbell1965}{}%
-29. F. W. Campbell, D. G. Green, Monocular versus binocular visual acuity. \emph{Nature} \textbf{208}, 191--2 (1965).
-
-\leavevmode\hypertarget{ref-Legge1984}{}%
-30. G. E. Legge, Binocular contrast summation--ii. Quadratic summation. \emph{Vision Res} \textbf{24}, 385--94 (1984).
-
-\leavevmode\hypertarget{ref-Baker2007}{}%
-31. D. H. Baker, T. S. Meese, M. A. Georgeson, Binocular interaction: Contrast matching and contrast discrimination are predicted by the same model. \emph{Spat Vis} \textbf{20}, 397--413 (2007).
-
-\leavevmode\hypertarget{ref-Ding2006}{}%
-32. J. Ding, G. Sperling, A gain-control theory of binocular combination. \emph{Proc Natl Acad Sci U S A} \textbf{103}, 1141--6 (2006).
-
-\leavevmode\hypertarget{ref-Meese2006}{}%
-33. T. S. Meese, M. A. Georgeson, D. H. Baker, Binocular contrast vision at and above threshold. \emph{Journal of Vision} \textbf{6}, 1224--43 (2006).
-
-\leavevmode\hypertarget{ref-Kingdom2015}{}%
-34. F. A. A. Kingdom, L. Libenson, Dichoptic color saturation mixture: Binocular luminance contrast promotes perceptual averaging. \emph{J Vis} \textbf{15}, 2 (2015).
-
-\leavevmode\hypertarget{ref-Busse2009}{}%
-35. L. Busse, A. R. Wade, M. Carandini, Representation of concurrent stimuli by population activity in visual cortex. \emph{Neuron} \textbf{64}, 931--42 (2009).
-
-\leavevmode\hypertarget{ref-Baker2024}{}%
-36. D. H. Baker\emph{et al.}, Binocular integration of chromatic and luminance signals. \emph{Journal of Vision} \textbf{Under review} (2024).
-
-\leavevmode\hypertarget{ref-Baker2017}{}%
-37. D. H. Baker, A. R. Wade, Evidence for an optimal algorithm underlying signal combination in human visual cortex. \emph{Cereb Cortex} \textbf{27}, 254--264 (2017).
-
-\leavevmode\hypertarget{ref-Kaestner2019}{}%
-38. M. Kaestner\emph{et al.}, Asymmetries between achromatic and chromatic extraction of 3D motion signals. \emph{Proc Natl Acad Sci U S A} \textbf{116}, 13631--13640 (2019).
-
-\leavevmode\hypertarget{ref-Martin2022}{}%
-39.
-J.
-T.
-Martin, J.
-Pinto, D.
-Bulte, M.
-Spitschan, PyPlr: A versatile, integrated system of hardware and software for researching the human pupillary light reflex.
-\emph{Behavior Research Methods} \textbf{54}, 2720--2739 (2022).
-
-\leavevmode\hypertarget{ref-Martin2023}{}%
-40.
-J.
-T.
-Martin, G.
-M.
-Boynton, D.
-H.
-Baker, A.
-R.
-Wade, M.
-Spitschan, PySilSub: An open-source python toolbox for implementing the method of silent substitution in vision and nonvisual photoreception research.
-\emph{Journal of Vision} \textbf{23}, 10 (2023).
-
-\leavevmode\hypertarget{ref-Stockman2000}{}%
-41.
-A.
-Stockman, L.
-T.
-Sharpe, The spectral sensitivities of the middle- and long-wavelength-sensitive cones derived from measurements in observers of known genotype.
-\emph{Vision Res} \textbf{40}, 1711--37 (2000).
-
-\leavevmode\hypertarget{ref-Barrionuevo2016}{}%
-42. P. A. Barrionuevo, D. Cao, Luminance and chromatic signals interact differently with melanopsin activation to control the pupil light response. \emph{Journal of Vision} \textbf{16(11)}, 29 (2016).
-
-\leavevmode\hypertarget{ref-Spitschan2015}{}%
-43. M. Spitschan, G. K. Aguirre, D. H. Brainard, Selective stimulation of penumbral cones reveals perception in the shadow of retinal blood vessels. \emph{PLoS One} \textbf{10}, e0124328 (2015).
+\leavevmode\hypertarget{ref-Zele2019}{}%
+Zele AJ, Adhikari P, Cao D, Feigl B (2019) Melanopsin driven enhancement of cone-mediated visual processing. Vision Res 160:72--81.
 
 \leavevmode\hypertarget{ref-Zele2018}{}%
-44.
-A.
-J.
-Zele, B.
-Feigl, P.
-Adhikari, M.
-L.
-Maynard, D.
-Cao, Melanopsin photoreception contributes to human visual detection, temporal and colour processing.
-\emph{Scientific Reports} \textbf{8} (2018).
-
-\leavevmode\hypertarget{ref-Kassner2014}{}%
-45.
-M.
-Kassner, W.
-Patera, A.
-Bulling, Pupil: An open source platform for pervasive eye tracking and mobile gaze-based interaction.
-in \emph{Proceedings of the 2014 ACM International Joint Conference on Pervasive and Ubiquitous Computing: Adjunct Publication}, (ACM, 2014) \url{https:/doi.org/10.1145/2638728.2641695}.
-
-\leavevmode\hypertarget{ref-Norcia2015}{}%
-46. A. M. Norcia, L. G. Appelbaum, J. M. Ales, B. R. Cottereau, B. Rossion, The steady-state visual evoked potential in vision research: A review. \emph{Journal of Vision} \textbf{15(6)}, 4 (2015).
-
-\leavevmode\hypertarget{ref-Zele2019}{}%
-47. A. J. Zele, P. Adhikari, D. Cao, B. Feigl, Melanopsin driven enhancement of cone-mediated visual processing. \emph{Vision Res} \textbf{160}, 72--81 (2019).
-
-\leavevmode\hypertarget{ref-Baker2020}{}%
-48. D. H. Baker\emph{et al.}, Binaural summation of amplitude modulation involves weak interaural suppression. \emph{Sci Rep} \textbf{10}, 3560 (2020).
-
-\leavevmode\hypertarget{ref-Carroll2002}{}%
-49. J. Carroll, J. Neitz, M. Neitz, Estimates of L:M cone ratio from ERG flicker photometry and genetics. \emph{Journal of Vision} \textbf{2}, 1 (2002).
-
-\leavevmode\hypertarget{ref-Hofer2005}{}%
-50. H. Hofer, J. Carroll, J. Neitz, M. Neitz, D. R. Williams, Organization of the human trichromatic cone mosaic. \emph{The Journal of Neuroscience} \textbf{25}, 9669--9679 (2005).
-
-\leavevmode\hypertarget{ref-Baker2021}{}%
-51. D. H. Baker, Statistical analysis of periodic data in neuroscience. \emph{Neurons, Behavior, Data analysis, and Theory} \textbf{5} (2021).
-
-\leavevmode\hypertarget{ref-Carpenter2017}{}%
-52. B. Carpenter\emph{et al.}, Stan: A probabilistic programming language. \emph{J Stat Softw} \textbf{76} (2017).
+Zele AJ, Feigl B, Adhikari P, Maynard ML, Cao D (2018) Melanopsin photoreception contributes to human visual detection, temporal and colour processing.
+Scientific Reports 8 Available at: \url{https://doi.org/10.1038\%2Fs41598-018-22197-w}.
 

### 2024-07-16 manuscript.Rmd
Shortened introduction to fit JoN restrictions

@@
 
-Number of words for abstract: 187
-
-Number of words for introduction: 1005
-
-Number of words for discussion: 600
+Number of words for abstract: 187/250
+
+Number of words for introduction: 634/650
+
+Number of words for discussion: 600/1500
 
@@
 The autonomic nervous system regulates many involuntary bodily processes, including the constriction and dilation of the pupils in response to light [@McDougal2015].
-The anatomical pathway from the retina to the subcortical nuclei controlling the pupillary light response (PLR) is well established: it includes the Pretectal Olivary nucleus (PON), the Superior Cervical ganglion and the Edinger-Westphal nucleus, which project to the iris sphincter muscles that directly control the pupil size [@McDougal2008; @McDougal2015; @Wang2015].
-Evidence of a binocular component to the PLR is shown by the existence of a consensual response of the pupil [the stimulation of one eye will cause constriction of the other eye\; @Wyatt1981].
+The anatomical pathway from the retina to the subcortical nuclei controlling the pupillary light response (PLR) is well established: it includes the Pretectal Olivary nucleus (PON), the Superior Cervical ganglion and the Edinger-Westphal nucleus, which project to the iris sphincter muscles that directly control the pupil size [@McDougal2015].
+Evidence of a binocular component to the PLR is shown by the consensual response of the pupil [stimulation of one eye will cause constriction of the other eye\; @Wyatt1981].
 The anatomical segregation of the subcortical pathway from the rest of the brain means that this binocular combination of signals must occur independently of the cortical processes of binocular integration required for visual perception.
@@
 
-Different classes of retinal photoreceptors, including cones, rods and melanopsin-containing intrinsically photosensitive retinal ganglion cells (ipRGCs), are directly involved in controlling and maintaining the size of the pupils [@Barrionuevo2014; @Barrionuevo2018; @Dacey2005; @Murray2018; @Spitschan2014; @Spitschan2019; @Woelders2018].
-The cones have been shown to drive the initial rapid constriction of the pupils [@Mathot2018], while the slower and longer activation of the ipRGCs shows their role in maintaining the constriction over a prolonged period of time and in regulating the post-illumination pupillary response [@Markwell2010; @McDougal2010].
-The ipRGCs are a unique photoreceptor class that has been discovered recently [@Provencio2000].
-They express the photopigment melanopsin, and are involved in the regulation of the circadian rhythm [@Provencio2000; @Panda2002; @Ruby2002], forming a major input to the PON [@Dacey2003].
+Different classes of retinal photoreceptors, including cones, rods and melanopsin-containing intrinsically photosensitive retinal ganglion cells (ipRGCs), are directly involved in controlling and maintaining the size of the pupils [e.g.
+@McDougal2010; @Barrionuevo2016; @Murray2018; @Spitschan2014; @Woelders2018].
+Cones drive the initial rapid constriction of the pupils [@Mathot2018], while the slower and longer activation of the ipRGCs maintains constriction over a prolonged period of time and regulates the post-illumination pupillary response [@Markwell2010; @McDougal2010].
+The ipRGCs are a recently discovered photoreceptor class [@Provencio2000] that express the photopigment melanopsin, and are involved in the regulation of the circadian rhythm [@Panda2002; @Ruby2002], forming a major input to the PON [@Dacey2003].
 The first direct evidence of the involvement of the ipRGCs in the PLR was shown in melanopsin knockout rats by @Lucas2003, resulting in the loss of the intrinsic photosensitivity of the cells and a reduced pupil constriction.
-This same behaviour was later also observed in primates and humans [@Gamlin2007], where it was demonstrated that the PLR continues during light presentation even when cone and rod signalling is blocked, indicating the primary role of the ipRGCs in maintaining pupil constriction over a prolonged time.
-
-A technique known as silent substitution [@Estevez1982] can be used to selectively stimulate specific photoreceptor classes.
+Similar behaviour was later observed in primates and humans [@Gamlin2007] using silent substitution (see Methods), where it was demonstrated that the PLR continues during light presentation even when cone and rod signalling is blocked, indicating the primary role of the ipRGCs in maintaining pupil constriction over a prolonged time.
+
+Binocular combination has been extensively studied in visual perception, where it is mediated by neurons in primary visual cortex [@Hubel1962].
+For pattern vision, binocular summation occurs at threshold, such that a lower contrast is required to detect a target shown to both eyes than a target shown to one eye [@Baker2018; @Campbell1965].
+At higher contrasts, a process of 'ocularity invariance' is observed, in which the response to monocularly- and binocularly-presented patterns is equal [@Baker2007; @Moradi2009].
+This is explained by a process of interocular suppression that cancels out the additional excitatory drive caused by stimulating two eyes.
+Our recent work [@Segala2023] showed that cortical signal combination for luminance flicker is substantially more linear than for spatial patterns, whereas there is evidence of interocular suppression in the pupil pathway.
+Here we measure the amplitude of pupil modulations in response to flickering stimuli directed at the luminance, L-M cone, S-cone, and melanopsin pathways (see Figure \@ref(fig:spectraplots)e-l).
+Our key comparisons are between monocular and binocular stimulation, and in a dichoptic masking condition where the two eyes are stimulated at different frequencies.
+The results are interpreted using a contemporary model of binocular vision [@Meese2006] implemented within a hierarchical Bayesian framework.
+
+# Materials and methods
+
+## Participants
+
+Twenty-four participants were recruited for each of the four experiments for a total of ninety-six adult participants (28 male, 68 female), whose ages ranged from 18 to 41.
+All participants had normal or corrected to normal vision, no known abnormalities of binocular or colour vision, and gave written informed consent.
+Our procedures were approved by the Ethics Committee of the Department of Psychology at the University of York (identification number 184).
+
+## Apparatus & stimuli
+
+To present synchronised stimulus modulations independently to each eye, two light engines (SpectraTuneLAB: LEDMOTIVE Technologies, LLC, Barcelona, Spain), each with 10 independently addressable LED colour channels, were integrated into a customised binocular viewing system.
+The light engines were operated via a Python interface to their REST API [@Martin2022], which supports synchronous launch and playback of spectral sequences prepared in advance and stored in JSON format.
+When preparing the spectral sequences, the age of participants was used to account for the yellowing of the lenses.
+We used the silent substitution technique [@Estevez1982] to selectively stimulate specific photoreceptor classes.
 Silent substitution exploits the fact that each photoreceptor class has a distinct spectral tuning that overlaps with the others.
@@
 LEDs) have different spectra, it is possible to target one class of photoreceptors while maintaining the others at a constant activity level, effectively silencing them [@Shapiro1996; @Spitschan2018, this paper also offers a clear explanation of how to implement silent substitution].
-Studies using silent substitution have shown that the pupils behave differently depending on which photoreceptor or pathway is being stimulated.
-For example, pupil responses have been shown to be out of phase when the S cones are stimulated, relative to when the ipRGCs or the L+M cones are stimulated [@Spitschan2014; @Cao2015].
-Additionally, when L and M cones are stimulated individually, there appears to be a paradoxical pupil response: increments in L cone stimulation cause a constriction of the pupil, while increments in M cone stimulation lead to a dilation of the pupil [@Woelders2018; @Murray2018], perhaps due to activity in the L-M opponent pathway.
-
-Binocular combination has been extensively studied in visual perception, where it is mediated by neurons in primary visual cortex [@Hubel1962; @Moradi2009].
-For pattern vision, binocular summation occurs at threshold, such that a lower contrast is required to detect a target shown to both eyes than a target shown to only one eye [@Baker2018; @Campbell1965; @Legge1984].
-At higher contrasts, a process of 'ocularity invariance' is observed, in which the response to monocularly- and binocularly-presented patterns is equal [@Baker2007; @Ding2006; @Meese2006; @Moradi2009].
-This is thought to be due to a process of interocular suppression that compensates for the additional excitatory drive caused by stimulating two eyes.
-Our recent work [@Segala2023] has shown that cortical signal combination for luminance flicker is substantially more linear than for spatial patterns, whereas there is evidence of interocular suppression in the pupil pathway.
-
-Most studies that use silent substitution to investigate the PLR stimulate only one eye.
-If the stimulated eye is pharmacologically dilated to control pupil size, the response from the unstimulated eye (known as the consensual response) can be recorded [e.g.
-@McDougal2010; @Spitschan2014].
-While this approach controls the total amount of light incident at the retina, it does not permit investigation of binocular combination for specific photoreceptor pathways.
-Here we take a different approach, using a custom binocular multiprimary system (see Figure \@ref(fig:spectraplots)a,b) that can modulate each (undilated) eye independently, and a binocular eye tracker to measure the diameter of both pupils.
-We measure the amplitude of pupil modulation (using Fourier analysis) in response to sinusoidal stimulation at 0.5Hz, for stimuli directed at the luminance pathway, L-M cone pathway, S-cone pathway, and melanopsin pathway (see Figure \@ref(fig:spectraplots)e-l).
-Our key comparisons are between monocular and binocular stimulation, and between monocular stimulation and a dichoptic masking condition in which the two eyes are stimulated at different frequencies (0.5 and 0.4Hz).
-The results are interpreted using a contemporary model of binocular vision [@Meese2006] implemented within a hierarchical Bayesian framework.
-
-# Materials and methods
-
-## Participants
-
-Twenty-four participants were recruited for each of the four experiments for a total of ninety-six adult participants (28 male, 68 female), whose ages ranged from 18 to 41.
-All participants had normal or corrected to normal vision, no known abnormalities of binocular or colour vision, and gave written informed consent.
-Our procedures were approved by the Ethics Committee of the Department of Psychology at the University of York (identification number 184).
-
-## Apparatus & stimuli
-
-To present synchronised stimulus modulations independently to each eye, two light engines (SpectraTuneLAB: LEDMOTIVE Technologies, LLC, Barcelona, Spain), each with 10 independently addressable LED colour channels, were integrated into a customised viewing system.
-The light engines were operated via a Python interface to their REST API [@Martin2022], which supports synchronous launch and playback of spectral sequences prepared in advance and stored in JSON format.
-When preparing the spectral sequences, the age of participants was used to account for the yellowing of the lenses.
 We calculated silent substitution solutions using the _PySilSub_ toolbox [@Martin2023], using linear algebra.

### 2024-07-16 manuscript.tex
Shortened introduction to fit JoN restrictions

@@
 \setcounter{secnumdepth}{5}
+% definitions for citeproc citations
+\NewDocumentCommand\citeproctext{}{}
+\NewDocumentCommand\citeproc{mm}{%
+  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
+\makeatletter
+ % allow citations to break across lines
+ \let\@cite@ofmt\@firstofone
+ % avoid brackets around text for \cite:
+ \def\@biblabel#1{}
+ \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
+\makeatother
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
+ {\begin{list}{}{%
+  \setlength{\itemindent}{0pt}
+  \setlength{\leftmargin}{0pt}
+  \setlength{\parsep}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+   \setlength{\leftmargin}{\cslhangindent}
+   \setlength{\itemindent}{-1\cslhangindent}
+  \fi
+  % set entry spacing
+  \setlength{\itemsep}{#2\baselineskip}}}
+ {\end{list}}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 \usepackage{caption} \usepackage{setspace}\doublespacing
@@
 \usepackage{xcolor}
+\ifLuaTeX
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
+\usepackage{bookmark}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same}
+\hypersetup{
+  pdftitle={Binocular combination in the autonomic nervous system},
+  colorlinks=true,
+  linkcolor={black},
+  filecolor={Maroon},
+  citecolor={Blue},
+  urlcolor={Blue},
+  pdfcreator={LaTeX via pandoc}}
 
@@
 
-Number of words for abstract: 199
+Number of words for abstract: 187/250
 
-Number of words for introduction: 896
+Number of words for introduction: 685/650
 
-Number of words for discussion: 600
+Number of words for discussion: 600/1500
 
@@
 
-\hypertarget{abstract}{%
-\section{Abstract}\label{abstract}}
+\section{Abstract}\label{abstract}
 
@@
 
-\hypertarget{significance-statement}{%
-\section{Significance statement}\label{significance-statement}}
+\section{Significance statement}\label{significance-statement}
 
@@
 
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
+\section{Introduction}\label{introduction}
 
-The autonomic nervous system regulates many involuntary bodily processes, including the constriction and dilation of the pupils in response to light (McDougal and Gamlin, \protect\hyperlink{ref-McDougal2015}{2015}).
-The anatomical pathway from the retina to the subcortical nuclei controlling the pupillary light response (PLR) is well established: it includes the Pretectal Olivary nucleus (PON), the Superior Cervical ganglion and the Edinger-Westphal nucleus, which project to the iris sphincter muscles that directly control the pupil size (McDougal and Gamlin, \protect\hyperlink{ref-McDougal2008}{2008}, \protect\hyperlink{ref-McDougal2015}{2015}; Wang and Munoz, \protect\hyperlink{ref-Wang2015}{2015}).
-Evidence of a binocular component to the PLR is shown by the existence of a consensual response of the pupil (the stimulation of one eye will cause constriction of the other eye; Wyatt and Musselman, \protect\hyperlink{ref-Wyatt1981}{1981}).
+The autonomic nervous system regulates many involuntary bodily processes, including the constriction and dilation of the pupils in response to light (\citeproc{ref-McDougal2015}{McDougal and Gamlin, 2015}).
+The anatomical pathway from the retina to the subcortical nuclei controlling the pupillary light response (PLR) is well established: it includes the Pretectal Olivary nucleus (PON), the Superior Cervical ganglion and the Edinger-Westphal nucleus, which project to the iris sphincter muscles that directly control the pupil size (\citeproc{ref-McDougal2015}{McDougal and Gamlin, 2015}).
+Evidence of a binocular component to the PLR is shown by the consensual response of the pupil (stimulation of one eye will cause constriction of the other eye; \citeproc{ref-Wyatt1981}{Wyatt and Musselman, 1981}).
 The anatomical segregation of the subcortical pathway from the rest of the brain means that this binocular combination of signals must occur independently of the cortical processes of binocular integration required for visual perception.
-Our recent work (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}) has shown that the algorithm underlying binocular combination of light in the pupil pathway differs from that in the cortex.
+Our recent work (\citeproc{ref-Segala2023}{Segala et al., 2023}) has shown that the algorithm underlying binocular combination of light in the pupil pathway differs from that in the cortex.
 Here we extend this paradigm to compare binocular combination in different photoreceptor pathways that feed into the autonomic nervous system.
 
-Different classes of retinal photoreceptors, including cones, rods and melanopsin-containing intrinsically photosensitive retinal ganglion cells (ipRGCs), are directly involved in controlling and maintaining the size of the pupils (Dacey et al., \protect\hyperlink{ref-Dacey2005}{2005}; Barrionuevo et al., \protect\hyperlink{ref-Barrionuevo2014}{2014}, \protect\hyperlink{ref-Barrionuevo2018}{2018}; Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}; Murray et al., \protect\hyperlink{ref-Murray2018}{2018}; Woelders et al., \protect\hyperlink{ref-Woelders2018}{2018}; Spitschan and Cajochen, \protect\hyperlink{ref-Spitschan2019}{2019}).
-The cones have been shown to drive the initial rapid constriction of the pupils (Mathôt, \protect\hyperlink{ref-Mathot2018}{2018}), while the slower and longer activation of the ipRGCs shows their role in maintaining the constriction over a prolonged period of time and in regulating the post-illumination pupillary response (Markwell et al., \protect\hyperlink{ref-Markwell2010}{2010}; McDougal and Gamlin, \protect\hyperlink{ref-McDougal2010}{2010}).
-The ipRGCs are a unique photoreceptor class that has been discovered recently (Provencio et al., \protect\hyperlink{ref-Provencio2000}{2000}).
-They express the photopigment melanopsin, and are involved in the regulation of the circadian rhythm (Provencio et al., \protect\hyperlink{ref-Provencio2000}{2000}; Panda et al., \protect\hyperlink{ref-Panda2002}{2002}; Ruby et al., \protect\hyperlink{ref-Ruby2002}{2002}), forming a major input to the PON (Dacey et al., \protect\hyperlink{ref-Dacey2003}{2003}).
+Different classes of retinal photoreceptors, including cones, rods and melanopsin-containing intrinsically photosensitive retinal ganglion cells (ipRGCs), are directly involved in controlling and maintaining the size of the pupils (e.g.
+\citeproc{ref-McDougal2010}{McDougal and Gamlin, 2010}; \citeproc{ref-Spitschan2014}{Spitschan et al., 2014}; \citeproc{ref-Barrionuevo2016}{Barrionuevo and Cao, 2016}; \citeproc{ref-Murray2018}{Murray et al., 2018}; \citeproc{ref-Woelders2018}{Woelders et al., 2018}).
+Cones drive the initial rapid constriction of the pupils (\citeproc{ref-Mathot2018}{Mathôt, 2018}), while the slower and longer activation of the ipRGCs maintains constriction over a prolonged period of time and regulates the post-illumination pupillary response (\citeproc{ref-Markwell2010}{Markwell et al., 2010}; \citeproc{ref-McDougal2010}{McDougal and Gamlin, 2010}).
+The ipRGCs are a recently discovered photoreceptor class (\citeproc{ref-Provencio2000}{Provencio et al., 2000}) that express the photopigment melanopsin, and are involved in the regulation of the circadian rhythm (\citeproc{ref-Panda2002}{Panda et al., 2002}; \citeproc{ref-Ruby2002}{Ruby et al., 2002}), forming a major input to the PON (\citeproc{ref-Dacey2003}{Dacey et al., 2003}).
 The first direct evidence of the involvement of the ipRGCs in the PLR was shown in melanopsin knockout rats by Lucas et al.
-(\protect\hyperlink{ref-Lucas2003}{2003}), resulting in the loss of the intrinsic photosensitivity of the cells and a reduced pupil constriction.
-This same behaviour was later also observed in primates and humans (Gamlin et al., \protect\hyperlink{ref-Gamlin2007}{2007}), where it was demonstrated that the PLR continues during light presentation even when cone and rod signalling is blocked, indicating the primary role of the ipRGCs in maintaining pupil constriction over a prolonged time.
+(\citeproc{ref-Lucas2003}{2003}), resulting in the loss of the intrinsic photosensitivity of the cells and a reduced pupil constriction.
+Similar behaviour was later observed in primates and humans (\citeproc{ref-Gamlin2007}{Gamlin et al., 2007}) using silent substitution (see Methods), where it was demonstrated that the PLR continues during light presentation even when cone and rod signalling is blocked, indicating the primary role of the ipRGCs in maintaining pupil constriction over a prolonged time.
 
-A technique known as silent substitution (Estévez and Spekreijse, \protect\hyperlink{ref-Estevez1982}{1982}) can be used to selectively stimulate specific photoreceptor classes.
-Silent substitution exploits the fact that each photoreceptor class has a distinct spectral tuning that overlaps with the others.
-Using a multiprimary system, in which the primaries (i.e.~LEDs) have different spectra, it is possible to target one class of photoreceptors while maintaining the others at a constant activity level, effectively silencing them (Shapiro et al., \protect\hyperlink{ref-Shapiro1996}{1996}; Spitschan and Woelders, \protect\hyperlink{ref-Spitschan2018}{2018}, this paper also offers a clear explanation of how to implement silent substitution).
-Studies using silent substitution have shown that the pupils behave differently depending on which photoreceptor or pathway is being stimulated.
-For example, pupil responses have been shown to be out of phase when the S cones are stimulated, relative to when the ipRGCs or the L+M cones are stimulated (Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}; Cao et al., \protect\hyperlink{ref-Cao2015}{2015}).
-Additionally, when L and M cones are stimulated individually, there appears to be a paradoxical pupil response: increments in L cone stimulation cause a constriction of the pupil, while increments in M cone stimulation lead to a dilation of the pupil (Murray et al., \protect\hyperlink{ref-Murray2018}{2018}; Woelders et al., \protect\hyperlink{ref-Woelders2018}{2018}), perhaps due to activity in the L-M opponent pathway.
+Binocular combination has been extensively studied in visual perception, where it is mediated by neurons in primary visual cortex (\citeproc{ref-Hubel1962}{Hubel and Wiesel, 1962}).
+For pattern vision, binocular summation occurs at threshold, such that a lower contrast is required to detect a target shown to both eyes than a target shown to one eye (\citeproc{ref-Campbell1965}{Campbell and Green, 1965}; \citeproc{ref-Baker2018}{Baker et al., 2018}).
+At higher contrasts, a process of `ocularity invariance' is observed, in which the response to monocularly- and binocularly-presented patterns is equal (\citeproc{ref-Baker2007}{Baker et al., 2007}; \citeproc{ref-Moradi2009}{Moradi and Heeger, 2009}).
+This is explained by a process of interocular suppression that cancels out the additional excitatory drive caused by stimulating two eyes.
+Our recent work (\citeproc{ref-Segala2023}{Segala et al., 2023}) showed that cortical signal combination for luminance flicker is substantially more linear than for spatial patterns, whereas there is evidence of interocular suppression in the pupil pathway.
+Here we measure the amplitude of pupil modulations in response to flickering stimuli directed at the luminance, L-M cone, S-cone, and melanopsin pathways (see Figure \ref{fig:spectraplots}e-l).
+Our key comparisons are between monocular and binocular stimulation, and in a dichoptic masking condition where the two eyes are stimulated at different frequencies.
+The results are interpreted using a contemporary model of binocular vision (\citeproc{ref-Meese2006}{Meese et al., 2006}) implemented within a hierarchical Bayesian framework.
 
-Binocular combination has been extensively studied in visual perception, where it is mediated by neurons in primary visual cortex (Hubel and Wiesel, \protect\hyperlink{ref-Hubel1962}{1962}; Moradi and Heeger, \protect\hyperlink{ref-Moradi2009}{2009}).
-For pattern vision, binocular summation occurs at threshold, such that a lower contrast is required to detect a target shown to both eyes than a target shown to only one eye (Campbell and Green, \protect\hyperlink{ref-Campbell1965}{1965}; Legge, \protect\hyperlink{ref-Legge1984}{1984}; Baker et al., \protect\hyperlink{ref-Baker2018}{2018}).
-At higher contrasts, a process of `ocularity invariance' is observed, in which the response to monocularly- and binocularly-presented patterns is equal (Ding and Sperling, \protect\hyperlink{ref-Ding2006}{2006}; Meese et al., \protect\hyperlink{ref-Meese2006}{2006}; Baker et al., \protect\hyperlink{ref-Baker2007}{2007}; Moradi and Heeger, \protect\hyperlink{ref-Moradi2009}{2009}).
-This is thought to be due to a process of interocular suppression that compensates for the additional excitatory drive caused by stimulating two eyes.
-Our recent work (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}) has shown that cortical signal combination for luminance flicker is substantially more linear than for spatial patterns, whereas there is evidence of interocular suppression in the pupil pathway.
+\section{Materials and methods}\label{materials-and-methods}
 
-Most studies that use silent substitution to investigate the PLR stimulate only one eye.
-If the stimulated eye is pharmacologically dilated to control pupil size, the response from the unstimulated eye (known as the consensual response) can be recorded (e.g.~McDougal and Gamlin, \protect\hyperlink{ref-McDougal2010}{2010}; Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}).
-While this approach controls the total amount of light incident at the retina, it does not permit investigation of binocular combination for specific photoreceptor pathways.
-Here we take a different approach, using a custom binocular multiprimary system (see Figure \ref{fig:spectraplots}a,b) that can modulate each (undilated) eye independently, and a binocular eye tracker to measure the diameter of both pupils.
-We measure the amplitude of pupil modulation (using Fourier analysis) in response to sinusoidal stimulation at 0.5Hz, for stimuli directed at the luminance pathway, L-M cone pathway, S-cone pathway, and melanopsin pathway (see Figure \ref{fig:spectraplots}e-l).
-Our key comparisons are between monocular and binocular stimulation, and between monocular stimulation and a dichoptic masking condition in which the two eyes are stimulated at different frequencies (0.5 and 0.4Hz).
-The results are interpreted using a contemporary model of binocular vision (Meese et al., \protect\hyperlink{ref-Meese2006}{2006}) implemented within a hierarchical Bayesian framework.
-
-\hypertarget{materials-and-methods}{%
-\section{Materials and methods}\label{materials-and-methods}}
-
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
+\subsection{Participants}\label{participants}
 
@@
 
-\hypertarget{apparatus-stimuli}{%
-\subsection{Apparatus \& stimuli}\label{apparatus-stimuli}}
+\subsection{Apparatus \& stimuli}\label{apparatus-stimuli}
 
-To present synchronised stimulus modulations independently to each eye, two light engines (SpectraTuneLAB: LEDMOTIVE Technologies, LLC, Barcelona, Spain), each with 10 independently addressable LED colour channels, were integrated into a customised viewing system.
-The light engines were operated via a Python interface to their REST API (Martin et al., \protect\hyperlink{ref-Martin2022}{2022}), which supports synchronous launch and playback of spectral sequences prepared in advance and stored in JSON format.
+To present synchronised stimulus modulations independently to each eye, two light engines (SpectraTuneLAB: LEDMOTIVE Technologies, LLC, Barcelona, Spain), each with 10 independently addressable LED colour channels, were integrated into a customised binocular viewing system.
+The light engines were operated via a Python interface to their REST API (\citeproc{ref-Martin2022}{Martin et al., 2022}), which supports synchronous launch and playback of spectral sequences prepared in advance and stored in JSON format.
 When preparing the spectral sequences, the age of participants was used to account for the yellowing of the lenses.
-We calculated silent substitution solutions using the \emph{PySilSub} toolbox (Martin et al., \protect\hyperlink{ref-Martin2023}{2023}), using linear algebra.
+We used the silent substitution technique (\citeproc{ref-Estevez1982}{Estévez and Spekreijse, 1982}) to selectively stimulate specific photoreceptor classes.
+Silent substitution exploits the fact that each photoreceptor class has a distinct spectral tuning that overlaps with the others.
+Using a multiprimary system, in which the primaries (i.e.~LEDs) have different spectra, it is possible to target one class of photoreceptors while maintaining the others at a constant activity level, effectively silencing them (\citeproc{ref-Shapiro1996}{Shapiro et al., 1996}; \citeproc{ref-Spitschan2018}{Spitschan and Woelders, 2018}, this paper also offers a clear explanation of how to implement silent substitution).
+We calculated silent substitution solutions using the \emph{PySilSub} toolbox (\citeproc{ref-Martin2023}{Martin et al., 2023}), using linear algebra.
 The outputs of the two light engines (see Figure \ref{fig:spectraplots}b,c) were calibrated using an Ocean Optics Jaz spectroradiometer, which was wavelength-calibrated to an Argon lamp and intensity calibrated using a NIST-traceable light source.
-We used the Stockman and Sharpe (\protect\hyperlink{ref-Stockman2000}{2000}) 10-degree cone fundamentals, and estimates of melanopsin absorbance spectra from CIE S 026 (discussed in Martin et al., \protect\hyperlink{ref-Martin2023}{2023}) to calculate \(\alpha\)-opic irradiance.
+We used the Stockman and Sharpe (\citeproc{ref-Stockman2000}{2000}) 10-degree cone fundamentals, and estimates of melanopsin absorbance spectra from CIE S 026 (discussed in \citeproc{ref-Martin2023}{Martin et al., 2023}) to calculate \(\alpha\)-opic irradiance.
 
@@
 The diffuser discs were positioned in the objective planes of the lenses of a modified VR headset (SHINECON SC-G01, Dongguan Shinecon Industrial Co.~Ltd., Guangdong, China), which was used by the participants to view the stimuli.
-The stimuli were two discs of flickering light with a diameter of approximately 30 degrees, which were fused together into a cyclopean percept resembling a donut-shaped ring of light, similar to that used in other studies (e.g., Barrionuevo and Cao, \protect\hyperlink{ref-Barrionuevo2016}{2016}; Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}, \protect\hyperlink{ref-Spitschan2015}{2015}; Murray et al., \protect\hyperlink{ref-Murray2018}{2018}; Zele et al., \protect\hyperlink{ref-Zele2018}{2018}).
+The stimuli were two discs of flickering light with a diameter of approximately 30 degrees, which were fused together into a cyclopean percept resembling a donut-shaped ring of light, similar to that used in other studies (\citeproc{ref-Spitschan2014}{Spitschan et al., 2014}, \citeproc{ref-Spitschan2015}{2015}; e.g., \citeproc{ref-Barrionuevo2016}{Barrionuevo and Cao, 2016}; \citeproc{ref-Murray2018}{Murray et al., 2018}; \citeproc{ref-Zele2018}{Zele et al., 2018}).
 The VR headset modifications allowed for small adjustments to account for individual differences in interpupillary distance and focal length.
-The use of this set up allowed us to modulate the stimuli in three different ocular configurations, similar to the ones we used in our previous study (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}): monocular, binocular and dichoptic.
+The use of this set up allowed us to modulate the stimuli in three different ocular configurations, similar to the ones we used in our previous study (\citeproc{ref-Segala2023}{Segala et al., 2023}): monocular, binocular and dichoptic.
 In the monocular configuration, the unstimulated eye still saw a non-flickering disc of mean luminance.
 A schematic of the stimulation system is shown in Figure \ref{fig:spectraplots}a.
-Pupillometry data were collected using a binocular Pupil Core eye-tracker headset (Pupil Labs GmbH, Berlin, Germany, Kassner et al., \protect\hyperlink{ref-Kassner2014}{2014}) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
+Pupillometry data were collected using a binocular Pupil Core eye-tracker headset (Pupil Labs GmbH, Berlin, Germany, \citeproc{ref-Kassner2014}{Kassner et al., 2014}) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
 
-Our previous study (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}) used a temporal frequency of 2Hz for foveal luminance flicker, and recorded EEG data simultaneously with pupillometry.
+Our previous study (\citeproc{ref-Segala2023}{Segala et al., 2023}) used a temporal frequency of 2Hz for foveal luminance flicker, and recorded EEG data simultaneously with pupillometry.
 Initial pilot experiments indicated that this frequency was too high to elicit measurable responses when stimulating individual photoreceptor pathways.
-For all experiments, we therefore used a primary flicker frequency of 0.5Hz, as previous literature showed that this was slow enough to elicit a pupil response from all photoreceptor classes (Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}).
-We also focussed on only recording pupillometry data as this frequency would be too slow to elicit steady-state EEG responses (Norcia et al., \protect\hyperlink{ref-Norcia2015}{2015}).
+For all experiments, we therefore used a primary flicker frequency of 0.5Hz, as previous literature showed that this was slow enough to elicit a pupil response from all photoreceptor classes (\citeproc{ref-Spitschan2014}{Spitschan et al., 2014}).
+We also focussed on only recording pupillometry data as this frequency would be too slow to elicit steady-state EEG responses (\citeproc{ref-Norcia2015}{Norcia et al., 2015}).
 
@@
 Splatter on nominally silenced photoreceptors was very small (see Figure \ref{fig:spectraplots}j-l), well below the levels that would be expected to generate measureable pupil modulations.
-We also estimated activation of penumbral L and M cones (Spitschan et al., \protect\hyperlink{ref-Spitschan2015}{2015}; Barrionuevo and Cao, \protect\hyperlink{ref-Barrionuevo2016}{2016}; Zele et al., \protect\hyperlink{ref-Zele2019}{2019}), which was minimal (\(\le 1.5%
+We also estimated activation of penumbral L and M cones (\citeproc{ref-Spitschan2015}{Spitschan et al., 2015}; \citeproc{ref-Barrionuevo2016}{Barrionuevo and Cao, 2016}; \citeproc{ref-Zele2019}{Zele et al., 2019}), which was minimal (\(\le 1.5%
 \) contrast; less than splatter on the open-field cones) for melanopsin-directed stimuli.
-We note that the temporal frequency of our modulation (0.5Hz) is well below the range where penumbral cone activation can elicit visible percepts, and that such percepts fade after around 1 second (Spitschan et al., \protect\hyperlink{ref-Spitschan2015}{2015}), and do not typically affect pupil responses (Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}).
+We note that the temporal frequency of our modulation (0.5Hz) is well below the range where penumbral cone activation can elicit visible percepts, and that such percepts fade after around 1 second (\citeproc{ref-Spitschan2015}{Spitschan et al., 2015}), and do not typically affect pupil responses (\citeproc{ref-Spitschan2014}{Spitschan et al., 2014}).
 
-\hypertarget{procedure}{%
-\subsection{Procedure}\label{procedure}}
+\subsection{Procedure}\label{procedure}
 
@@
 Pupil responses to binocular temporal contrast modulations were examined in a factorial design that combined six ocular conditions and five temporal contrast levels: 6, 12, 24, 48 and 96\% of the available dynamic range.
-This design, similar to that used in our previous studies (Baker and Wade, \protect\hyperlink{ref-Baker2017}{2017}; Baker et al., \protect\hyperlink{ref-Baker2020}{2020}; Segala et al., \protect\hyperlink{ref-Segala2023}{2023}), was applied in four separate experiments, each with a different mode of photoreceptor stimulation.
+This design, similar to that used in our previous studies (\citeproc{ref-Baker2017}{Baker and Wade, 2017}; \citeproc{ref-Baker2020}{Baker et al., 2020}; \citeproc{ref-Segala2023}{Segala et al., 2023}), was applied in four separate experiments, each with a different mode of photoreceptor stimulation.
 In the first three conditions, the discs flickered at 0.5 Hz, in either a monocular, binocular or dichoptic arrangement.
@@
 Using a trackball, participants adjusted the angle in cone space to find their subjective isoluminant point, which resulted in changing the flickering intensity of the stimulus until the amplitude of the flicker appeared to be minimised.
-The result was used to modify the requested contrasts during stimulus preparation so as to account for individual differences affecting perceived illuminance, principally the L:M cone ratio (Carroll et al., \protect\hyperlink{ref-Carroll2002}{2002}; Hofer et al., \protect\hyperlink{ref-Hofer2005}{2005}).
+The result was used to modify the requested contrasts during stimulus preparation so as to account for individual differences affecting perceived illuminance, principally the L:M cone ratio (\citeproc{ref-Carroll2002}{Carroll et al., 2002}; \citeproc{ref-Hofer2005}{Hofer et al., 2005}).
 
-\hypertarget{data-analysis}{%
-\subsection{Data analysis}\label{data-analysis}}
+\subsection{Data analysis}\label{data-analysis}
 
-The pupillometry data were analysed using the same method we used in our previous study (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}).
-The data were converted from mp4 videos to a csv text file using the Pupil Player software (Kassner et al., \protect\hyperlink{ref-Kassner2014}{2014}), which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
+The pupillometry data were analysed using the same method we used in our previous study (\citeproc{ref-Segala2023}{Segala et al., 2023}).
+The data were converted from mp4 videos to a csv text file using the Pupil Player software (\citeproc{ref-Kassner2014}{Kassner et al., 2014}), which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
 The individual data were then loaded into R for analysis, where a ten-second waveform for each trial in each eye was extracted (excluding the first two seconds after stimulus onset).
@@
 Finally, data were averaged across all participants to obtain the group results.
-We used coherent averaging and at each stage we excluded data points with a Mahalanobis distance exceeding \(D\) = 3 from the complex-valued mean (Baker, \protect\hyperlink{ref-Baker2021}{2021}).
+We used coherent averaging and at each stage we excluded data points with a Mahalanobis distance exceeding \(D\) = 3 from the complex-valued mean (\citeproc{ref-Baker2021}{Baker, 2021}).
 For monocular stimulation, we confirmed that the consensual response was equivalent to the response in the stimulated eye.
@@
 
-\hypertarget{computational-model-and-parameter-estimation}{%
-\subsection{Computational model and parameter estimation}\label{computational-model-and-parameter-estimation}}
+\subsection{Computational model and parameter estimation}\label{computational-model-and-parameter-estimation}
 
-To describe our data, we used the same model described in our previous study (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}).
+To describe our data, we used the same model described in our previous study (\citeproc{ref-Segala2023}{Segala et al., 2023}).
 The model has the same general form as the first stage of the contrast gain control model proposed by Meese et al.
-(\protect\hyperlink{ref-Meese2006}{2006}), but omits the second stage.
-For the previous model that we used (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}), the exponent of the numerator and denominator had fixed values of 2 and (implicitly) 1.
+(\citeproc{ref-Meese2006}{2006}), but omits the second stage.
+For the previous model that we used (\citeproc{ref-Segala2023}{Segala et al., 2023}), the exponent of the numerator and denominator had fixed values of 2 and (implicitly) 1.
 Here, we allow these parameters (called \emph{p} and \emph{q}) to be free, in order to permit different shapes of contrast response function, e.g.~accelerating or saturating.
@@
 
-The models were fit using a hierarchical Bayesian framework implemented in Stan (Carpenter et al., \protect\hyperlink{ref-Carpenter2017}{2017}).
+The models were fit using a hierarchical Bayesian framework implemented in Stan (\citeproc{ref-Carpenter2017}{Carpenter et al., 2017}).
 The data for each photoreceptor type and response frequency was fit separately, for a total of 8 model fits.
 The prior for the \(\omega\) parameter was Gaussian, with a mean of 1 and standard deviation of 0.5.
-Priors for the other free parameters were also Gaussian, with mean values based on previous work (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}).
+Priors for the other free parameters were also Gaussian, with mean values based on previous work (\citeproc{ref-Segala2023}{Segala et al., 2023}).
 We calculated over \ensuremath{10^{6}} posterior samples, and retained 10\% for plotting.
 
-\hypertarget{results}{%
-\section{Results}\label{results}}
+\section{Results}\label{results}
 
@@
 
-In contemporary models of binocular signal combination, the amount of binocular facilitation is determined by the magnitude of interocular suppression, with strong suppression reducing facilitation (Kingdom and Libenson, \protect\hyperlink{ref-Kingdom2015}{2015}).
+In contemporary models of binocular signal combination, the amount of binocular facilitation is determined by the magnitude of interocular suppression, with strong suppression reducing facilitation (\citeproc{ref-Kingdom2015}{Kingdom and Libenson, 2015}).
 We can estimate the strength of interocular suppression by measuring how much monocular responses are reduced when a dichoptic `mask' is shown to the other eye.
-In our paradigm, the two components flickered at different frequencies (0.5 and 0.4Hz) so that their responses remained distinct in the Fourier spectrum (e.g.~Busse et al., \protect\hyperlink{ref-Busse2009}{2009}).
+In our paradigm, the two components flickered at different frequencies (0.5 and 0.4Hz) so that their responses remained distinct in the Fourier spectrum (e.g.
+\citeproc{ref-Busse2009}{Busse et al., 2009}).
 The yellow diamond symbols in Figure \ref{fig:FirstHarmonicPlots}a-d show the target responses in this condition, and in most cases were weaker than the monocular responses (red circles).
@@
 
-To estimate the extent of interocular suppression for each photoreceptor pathway, we fitted each data set using a Bayesian hierarchical implementation of a simple binocular combination model (Meese et al., \protect\hyperlink{ref-Meese2006}{2006}; Segala et al., \protect\hyperlink{ref-Segala2023}{2023}).
+To estimate the extent of interocular suppression for each photoreceptor pathway, we fitted each data set using a Bayesian hierarchical implementation of a simple binocular combination model (\citeproc{ref-Meese2006}{Meese et al., 2006}; \citeproc{ref-Segala2023}{Segala et al., 2023}).
 Our primary objective was to compare posterior distributions of the weight of interocular suppression, which are shown in Figure \ref{fig:FirstHarmonicPlots}e.
@@
 
-Finally, we inspected the response phase of our four stimulation conditions, given previous reports that these differ across pathways (Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}), and may be in antiphase for melanopsin and S-cone signals.
+Finally, we inspected the response phase of our four stimulation conditions, given previous reports that these differ across pathways (\citeproc{ref-Spitschan2014}{Spitschan et al., 2014}), and may be in antiphase for melanopsin and S-cone signals.
 Figure \ref{fig:phaseplots} shows the phase angles for the first (a) and second (b) harmonic frequencies for binocular stimulation (monocular stimulation produced very similar results).
@@
 This is the first study to investigate binocular interactions in the melanopsin pathway directly.
-A previous meta-analysis (Spitschan and Cajochen, \protect\hyperlink{ref-Spitschan2019}{2019}) indicated that there may be a substantial binocular facilitation effect in the circadian pathway, as indexed by melatonin suppression (melatonin is a hormone released by the pineal gland; its production is suppressed by exposure to bright light, particularly when the melanopsin-containing ipRGCs are stimulated).
+A previous meta-analysis (\citeproc{ref-Spitschan2019}{Spitschan and Cajochen, 2019}) indicated that there may be a substantial binocular facilitation effect in the circadian pathway, as indexed by melatonin suppression (melatonin is a hormone released by the pineal gland; its production is suppressed by exposure to bright light, particularly when the melanopsin-containing ipRGCs are stimulated).
 In brief, monocular stimulation of the ipRGCs requires up to ten times the signal strength to produce an equivalent effect to binocular stimulation.
@@
 The explanation for this difference could be due to different anatomical pathways.
-Binocular combination in the circadian system likely takes place in the suprachiasmatic nucleus, whereas in the pupil constriction circuit the Edinger-Westphal nucleus is the most likely site of binocular integration (Mathôt, \protect\hyperlink{ref-Mathot2018}{2018}).
+Binocular combination in the circadian system likely takes place in the suprachiasmatic nucleus, whereas in the pupil constriction circuit the Edinger-Westphal nucleus is the most likely site of binocular integration (\citeproc{ref-Mathot2018}{Mathôt, 2018}).
 Presumably these anatomical differences, and the practical constraints of the two systems, lead to differences in response.
 
-Our recent psychophysical work (Baker et al., \protect\hyperlink{ref-Baker2024}{2024}) has looked at binocular interactions in the L-M and S-cone pathways, and compared these to the luminance pathway.
+Our recent psychophysical work (\citeproc{ref-Baker2024}{Baker et al., 2024}) has looked at binocular interactions in the L-M and S-cone pathways, and compared these to the luminance pathway.
 Using a contrast discrimination paradigm with spatial modulations of luminance and colour, Baker et al.
-(\protect\hyperlink{ref-Baker2024}{2024}) found equally strong interocular suppression in all three pathways.
+(\citeproc{ref-Baker2024}{2024}) found equally strong interocular suppression in all three pathways.
 This is rather different from our pupillometry results here, which demonstrate weaker suppression in the luminance and S-cone pathways than in the L-M pathway (see Figure \ref{fig:FirstHarmonicPlots}).
 However, the current experiments involve temporal modulations, which are quite distinct from the spatial modulations used in Baker et al.
-(\protect\hyperlink{ref-Baker2024}{2024}).
-Our other recent work (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}) has shown that temporal luminance modulations involve much weaker interocular suppression in the cortical response than do spatial luminance modulations (Baker and Wade, \protect\hyperlink{ref-Baker2017}{2017}).
+(\citeproc{ref-Baker2024}{2024}).
+Our other recent work (\citeproc{ref-Segala2023}{Segala et al., 2023}) has shown that temporal luminance modulations involve much weaker interocular suppression in the cortical response than do spatial luminance modulations (\citeproc{ref-Baker2017}{Baker and Wade, 2017}).
 These different normalization processes might reflect different priorities for spatial and temporal vision.
-Spatial vision aims to fuse images to provide binocular single vision, and benefits from `ocularity invariance' (Baker et al., \protect\hyperlink{ref-Baker2007}{2007}), in which visual appearance is constant when viewed with one eye or two.
-Temporal vision is critical for motion perception, which can involve alternative binocular computations, such as calculating velocity differences between the eyes (Kaestner et al., \protect\hyperlink{ref-Kaestner2019}{2019}).
+Spatial vision aims to fuse images to provide binocular single vision, and benefits from `ocularity invariance' (\citeproc{ref-Baker2007}{Baker et al., 2007}), in which visual appearance is constant when viewed with one eye or two.
+Temporal vision is critical for motion perception, which can involve alternative binocular computations, such as calculating velocity differences between the eyes (\citeproc{ref-Kaestner2019}{Kaestner et al., 2019}).
 Of course the present measurements were of pupil size, which may be subject to different anatomical and functional constraints from those in the cortex.
@@
 
-\hypertarget{references}{%
-\section{References}\label{references}}
+\section{References}\label{references}
 
-\hypertarget{refs}{}
-\leavevmode\hypertarget{ref-Baker2021}{}%
+\phantomsection\label{refs}
+\begin{CSLReferences}{1}{1}
+\bibitem[\citeproctext]{ref-Baker2021}
 Baker DH (2021) Statistical analysis of periodic data in neuroscience. Neurons, Behavior, Data analysis, and Theory 5 Available at: \url{https://doi.org/10.51628\%2F001c.27680}.
 
-\leavevmode\hypertarget{ref-Baker2024}{}%
-Baker DH, Hansford KJ, Segala FG, Morsi AY, Huxley RJ, Martin JT, Rockman M, Wade AR (2024) Binocular integration of chromatic and luminance signals. Journal of Vision Under review.
+\bibitem[\citeproctext]{ref-Baker2024}
+Baker DH, Hansford KJ, Segala FG, Morsi AY, Huxley RJ, Martin JT, Rockman M, Wade AR (2024) \href{https://doi.org/10.31234/osf.io/atsfh}{Binocular integration of chromatic and luminance signals}.
+Journal of Vision Under review.
 
-\leavevmode\hypertarget{ref-Baker2018}{}%
-Baker DH, Lygo FA, Meese TS, Georgeson MA (2018) Binocular summation revisited: Beyond \(\sqrt{2}\). Psychol Bull 144:1186--1199.
+\bibitem[\citeproctext]{ref-Baker2018}
+Baker DH, Lygo FA, Meese TS, Georgeson MA (2018) \href{https://doi.org/10.1037/bul0000163}{Binocular summation revisited: Beyond \(\sqrt{2}\)}. Psychol Bull 144:1186--1199.
 
-\leavevmode\hypertarget{ref-Baker2007}{}%
-Baker DH, Meese TS, Georgeson MA (2007) Binocular interaction: Contrast matching and contrast discrimination are predicted by the same model. Spat Vis 20:397--413.
+\bibitem[\citeproctext]{ref-Baker2007}
+Baker DH, Meese TS, Georgeson MA (2007) \href{https://doi.org/10.1163/156856807781503622}{Binocular interaction: Contrast matching and contrast discrimination are predicted by the same model}.
+Spat Vis 20:397--413.
 
-\leavevmode\hypertarget{ref-Baker2020}{}%
-Baker DH, Vilidaite G, McClarnon E, Valkova E, Bruno A, Millman RE (2020) Binaural summation of amplitude modulation involves weak interaural suppression. Sci Rep 10:3560.
+\bibitem[\citeproctext]{ref-Baker2020}
+Baker DH, Vilidaite G, McClarnon E, Valkova E, Bruno A, Millman RE (2020) \href{https://doi.org/10.1038/s41598-020-60602-5}{Binaural summation of amplitude modulation involves weak interaural suppression}.
+Sci Rep 10:3560.
 
-\leavevmode\hypertarget{ref-Baker2017}{}%
-Baker DH, Wade AR (2017) Evidence for an optimal algorithm underlying signal combination in human visual cortex. Cereb Cortex 27:254--264.
+\bibitem[\citeproctext]{ref-Baker2017}
+Baker DH, Wade AR (2017) \href{https://doi.org/10.1093/cercor/bhw395}{Evidence for an optimal algorithm underlying signal combination in human visual cortex}. Cereb Cortex 27:254--264.
 
-\leavevmode\hypertarget{ref-Barrionuevo2016}{}%
-Barrionuevo PA, Cao D (2016) Luminance and chromatic signals interact differently with melanopsin activation to control the pupil light response. Journal of Vision 16(11):29.
+\bibitem[\citeproctext]{ref-Barrionuevo2016}
+Barrionuevo PA, Cao D (2016) \href{https://doi.org/10.1167/16.11.29}{Luminance and chromatic signals interact differently with melanopsin activation to control the pupil light response}.
+Journal of Vision 16(11):29.
 
-\leavevmode\hypertarget{ref-Barrionuevo2018}{}%
-Barrionuevo PA, McAnany JJ, Zele AJ, Cao D (2018) Non-linearities in the Rod and Cone Photoreceptor Inputs to the Afferent Pupil Light Response. Frontiers in Neurology 9.
+\bibitem[\citeproctext]{ref-Busse2009}
+Busse L, Wade AR, Carandini M (2009) \href{https://doi.org/10.1016/j.neuron.2009.11.004}{Representation of concurrent stimuli by population activity in visual cortex}. Neuron 64:931--942.
 
-\leavevmode\hypertarget{ref-Barrionuevo2014}{}%
-Barrionuevo PA, Nicandro N, McAnany JJ, Zele AJ, Gamlin P, Cao D (2014) Assessing rod, cone, and melanopsin contributions to human pupil flicker responses.
-Investigative Ophthalmology \& Visual Science 55:719--727.
+\bibitem[\citeproctext]{ref-Campbell1965}
+Campbell FW, Green DG (1965) \href{https://doi.org/10.1038/208191a0}{Monocular versus binocular visual acuity}. Nature 208:191--192.
 
-\leavevmode\hypertarget{ref-Busse2009}{}%
-Busse L, Wade AR, Carandini M (2009) Representation of concurrent stimuli by population activity in visual cortex. Neuron 64:931--942.
+\bibitem[\citeproctext]{ref-Carpenter2017}
+Carpenter B, Gelman A, Hoffman MD, Lee D, Goodrich B, Betancourt M, Brubaker MA, Guo J, Li P, Riddell A (2017) \href{https://doi.org/10.18637/jss.v076.i01}{Stan: A probabilistic programming language}.
+J Stat Softw 76.
 
-\leavevmode\hypertarget{ref-Campbell1965}{}%
-Campbell FW, Green DG (1965) Monocular versus binocular visual acuity. Nature 208:191--192.
-
-\leavevmode\hypertarget{ref-Cao2015}{}%
-Cao D, Nicandro N, Barrionuevo PA (2015) A five-primary photostimulator suitable for studying intrinsically photosensitive retinal ganglion cell functions in humans.
-Journal of Vision 15:27 Available at: \url{https://doi.org/10.1167/15.1.27} {[}Accessed July 18, 2023{]}.
-
-\leavevmode\hypertarget{ref-Carpenter2017}{}%
-Carpenter B, Gelman A, Hoffman MD, Lee D, Goodrich B, Betancourt M, Brubaker MA, Guo J, Li P, Riddell A (2017) Stan: A probabilistic programming language. J Stat Softw 76.
-
-\leavevmode\hypertarget{ref-Carroll2002}{}%
-Carroll J, Neitz J, Neitz M (2002) Estimates of L:M cone ratio from ERG flicker photometry and genetics.
+\bibitem[\citeproctext]{ref-Carroll2002}
+Carroll J, Neitz J, Neitz M (2002) Estimates of {L}:{M} cone ratio from {ERG} flicker photometry and genetics.
 Journal of Vision 2:1 Available at: \url{https://doi.org/10.1167/2.8.1} {[}Accessed June 5, 2023{]}.
 
-\leavevmode\hypertarget{ref-Dacey2005}{}%
-Dacey DM, Liao H-W, Peterson BB, Robinson FR, Smith VC, Pokorny J, Yau K-W, Gamlin PD (2005) Melanopsin-expressing ganglion cells in primate retina signal colour and irradiance and project to the LGN.
-Nature 433:749--754 Available at: \url{https://www.nature.com/articles/nature03387} {[}Accessed July 18, 2023{]}.
-
-\leavevmode\hypertarget{ref-Dacey2003}{}%
-Dacey DM, Peterson BB, Robinson FR, Gamlin PD (2003) Fireworks in the primate retina: In vitro photodynamics reveals diverse lgn-projecting ganglion cell types.
+\bibitem[\citeproctext]{ref-Dacey2003}
+Dacey DM, Peterson BB, Robinson FR, Gamlin PD (2003) Fireworks in the primate retina: In vitro photodynamics reveals diverse LGN-projecting ganglion cell types.
 Neuron 37:15--27 Available at: \url{https://www.sciencedirect.com/science/article/pii/S0896627302011431}.
 
-\leavevmode\hypertarget{ref-Ding2006}{}%
-Ding J, Sperling G (2006) A gain-control theory of binocular combination. Proc Natl Acad Sci U S A 103:1141--1146.
-
-\leavevmode\hypertarget{ref-Estevez1982}{}%
+\bibitem[\citeproctext]{ref-Estevez1982}
 Estévez O, Spekreijse H (1982) The "silent substitution" method in visual research.
@@
 
-\leavevmode\hypertarget{ref-Gamlin2007}{}%
+\bibitem[\citeproctext]{ref-Gamlin2007}
 Gamlin PDR, McDougal DH, Pokorny J, Smith VC, Yau K-W, Dacey DM (2007) Human and macaque pupil responses driven by melanopsin-containing retinal ganglion cells.
@@
 
-\leavevmode\hypertarget{ref-Hofer2005}{}%
+\bibitem[\citeproctext]{ref-Hofer2005}
 Hofer H, Carroll J, Neitz J, Neitz M, Williams DR (2005) Organization of the human trichromatic cone mosaic.
@@
 
-\leavevmode\hypertarget{ref-Hubel1962}{}%
-Hubel DH, Wiesel TN (1962) Receptive fields, binocular interaction and functional architecture in the cat's visual cortex. J Physiol 160:106--154.
+\bibitem[\citeproctext]{ref-Hubel1962}
+Hubel DH, Wiesel TN (1962) \href{https://doi.org/10.1113/jphysiol.1962.sp006837}{Receptive fields, binocular interaction and functional architecture in the cat's visual cortex}.
+J Physiol 160:106--154.
 
-\leavevmode\hypertarget{ref-Kaestner2019}{}%
-Kaestner M, Maloney RT, Wailes-Newson KH, Bloj M, Harris JM, Morland AB, Wade AR (2019) Asymmetries between achromatic and chromatic extraction of 3D motion signals.
+\bibitem[\citeproctext]{ref-Kaestner2019}
+Kaestner M, Maloney RT, Wailes-Newson KH, Bloj M, Harris JM, Morland AB, Wade AR (2019) \href{https://doi.org/10.1073/pnas.1817202116}{Asymmetries between achromatic and chromatic extraction of 3D motion signals}.
 Proc Natl Acad Sci U S A 116:13631--13640.
 
-\leavevmode\hypertarget{ref-Kassner2014}{}%
+\bibitem[\citeproctext]{ref-Kassner2014}
 Kassner M, Patera W, Bulling A (2014) Pupil: An open source platform for pervasive eye tracking and mobile gaze-based interaction.
-In: Proceedings of the 2014 ACM international joint conference on pervasive and ubiquitous computing: Adjunct publication.
-ACM.
+In: Proceedings of the 2014 {ACM} international joint conference on pervasive and ubiquitous computing: Adjunct publication.
+{ACM}.
 Available at: \url{https://doi.org/10.1145\%2F2638728.2641695}.
 
-\leavevmode\hypertarget{ref-Kingdom2015}{}%
-Kingdom FAA, Libenson L (2015) Dichoptic color saturation mixture: Binocular luminance contrast promotes perceptual averaging. J Vis 15:2.
+\bibitem[\citeproctext]{ref-Kingdom2015}
+Kingdom FAA, Libenson L (2015) \href{https://doi.org/10.1167/15.5.2}{Dichoptic color saturation mixture: Binocular luminance contrast promotes perceptual averaging}. J Vis 15:2.
 
-\leavevmode\hypertarget{ref-Legge1984}{}%
-Legge GE (1984) Binocular contrast summation--ii. Quadratic summation. Vision Res 24:385--394.
-
-\leavevmode\hypertarget{ref-Lucas2003}{}%
+\bibitem[\citeproctext]{ref-Lucas2003}
 Lucas RJ, Hattar S, Takao M, Berson DM, Foster RG, Yau K-W (2003) Diminished pupillary light reflex at high irradiances in melanopsin-knockout mice.
@@
 
-\leavevmode\hypertarget{ref-Markwell2010}{}%
+\bibitem[\citeproctext]{ref-Markwell2010}
 Markwell EL, Feigl B, Zele AJ (2010) Intrinsically photosensitive melanopsin retinal ganglion cell contributions to the pupillary light reflex and circadian rhythm.
@@
 
-\leavevmode\hypertarget{ref-Martin2023}{}%
+\bibitem[\citeproctext]{ref-Martin2023}
 Martin JT, Boynton GM, Baker DH, Wade AR, Spitschan M (2023) PySilSub: An open-source python toolbox for implementing the method of silent substitution in vision and nonvisual photoreception research.
@@
 
-\leavevmode\hypertarget{ref-Martin2022}{}%
-Martin JT, Pinto J, Bulte D, Spitschan M (2022) PyPlr: A versatile, integrated system of hardware and software for researching the human pupillary light reflex.
+\bibitem[\citeproctext]{ref-Martin2022}
+Martin JT, Pinto J, Bulte D, Spitschan M (2022) \href{https://doi.org/10.3758/s13428-021-01759-3}{PyPlr: A versatile, integrated system of hardware and software for researching the human pupillary light reflex}.
 Behavior Research Methods 54:2720--2739.
 
-\leavevmode\hypertarget{ref-Mathot2018}{}%
-Mathôt S (2018) Pupillometry: Psychology, physiology, and function. J Cogn 1:16.
+\bibitem[\citeproctext]{ref-Mathot2018}
+Mathôt S (2018) \href{https://doi.org/10.5334/joc.18}{Pupillometry: Psychology, physiology, and function}. J Cogn 1:16.
 
-\leavevmode\hypertarget{ref-McDougal2008}{}%
-McDougal DH, Gamlin PD (2008) Pupillary control pathways. In: The senses: A comprehensive reference, pp 521--536. Elsevier.
-
-\leavevmode\hypertarget{ref-McDougal2010}{}%
+\bibitem[\citeproctext]{ref-McDougal2010}
 McDougal DH, Gamlin PD (2010) The influence of intrinsically-photosensitive retinal ganglion cells on the spectral sensitivity and response dynamics of the human pupillary light reflex.
@@
 
-\leavevmode\hypertarget{ref-McDougal2015}{}%
-McDougal DH, Gamlin PD (2015) Autonomic control of the eye. Comprehensive Physiology 5:439--473.
+\bibitem[\citeproctext]{ref-McDougal2015}
+McDougal DH, Gamlin PD (2015) \href{https://doi.org/10.1002/cphy.c140014}{Autonomic control of the eye}. Comprehensive Physiology 5:439--473.
 
-\leavevmode\hypertarget{ref-Meese2006}{}%
-Meese TS, Georgeson MA, Baker DH (2006) Binocular contrast vision at and above threshold. Journal of Vision 6:1224--1243.
+\bibitem[\citeproctext]{ref-Meese2006}
+Meese TS, Georgeson MA, Baker DH (2006) \href{https://doi.org/10.1167/6.11.7}{Binocular contrast vision at and above threshold}. Journal of Vision 6:1224--1243.
 
-\leavevmode\hypertarget{ref-Moradi2009}{}%
-Moradi F, Heeger DJ (2009) Inter-ocular contrast normalization in human visual cortex. J Vis 9:13.1--22.
+\bibitem[\citeproctext]{ref-Moradi2009}
+Moradi F, Heeger DJ (2009) \href{https://doi.org/10.1167/9.3.13}{Inter-ocular contrast normalization in human visual cortex}. J Vis 9:13.1--22.
 
-\leavevmode\hypertarget{ref-Murray2018}{}%
-Murray IJ, Kremers J, McKeefry D, Parry NRA (2018) Paradoxical pupil responses to isolated M-cone increments.
+\bibitem[\citeproctext]{ref-Murray2018}
+Murray IJ, Kremers J, McKeefry D, Parry NRA (2018) Paradoxical pupil responses to isolated {M}-cone increments.
 Journal of the Optical Society of America A 35:B66--B71 Available at: \url{https://opg.optica.org/josaa/abstract.cfm?uri=josaa-35-4-B66} {[}Accessed July 18, 2023{]}.
 
-\leavevmode\hypertarget{ref-Norcia2015}{}%
-Norcia AM, Appelbaum LG, Ales JM, Cottereau BR, Rossion B (2015) The steady-state visual evoked potential in vision research: A review. Journal of Vision 15(6):4.
+\bibitem[\citeproctext]{ref-Norcia2015}
+Norcia AM, Appelbaum LG, Ales JM, Cottereau BR, Rossion B (2015) \href{https://doi.org/10.1167/15.6.4}{The steady-state visual evoked potential in vision research: A review}.
+Journal of Vision 15(6):4.
 
-\leavevmode\hypertarget{ref-Panda2002}{}%
-Panda S, Sato TK, Castrucci AM, Rollag MD, DeGrip WJ, Hogenesch JB, Provencio I, Kay SA (2002) Melanopsin (opn4) requirement for normal light-induced circadian phase shifting.
+\bibitem[\citeproctext]{ref-Panda2002}
+Panda S, Sato TK, Castrucci AM, Rollag MD, DeGrip WJ, Hogenesch JB, Provencio I, Kay SA (2002) Melanopsin (Opn4) requirement for normal light-induced circadian phase shifting.
 Science 298:2213--2216 Available at: \url{https://doi.org/10.1126\%2Fscience.1076848}.
 
-\leavevmode\hypertarget{ref-Provencio2000}{}%
-Provencio I, Rodriguez IR, Jiang G, Hayes WP, Moreira EF, Rollag MD (2000) A Novel Human Opsin in the Inner Retina.
+\bibitem[\citeproctext]{ref-Provencio2000}
+Provencio I, Rodriguez IR, Jiang G, Hayes WP, Moreira EF, Rollag MD (2000) A {Novel} {Human} {Opsin} in the {Inner} {Retina}.
 Journal of Neuroscience 20:600--605 Available at: \url{https://www.jneurosci.org/content/20/2/600} {[}Accessed July 18, 2023{]}.
 
-\leavevmode\hypertarget{ref-Ruby2002}{}%
+\bibitem[\citeproctext]{ref-Ruby2002}
 Ruby NF, Brennan TJ, Xie X, Cao V, Franken P, Heller HC, O'Hara BF (2002) Role of melanopsin in circadian responses to light.
@@
 
-\leavevmode\hypertarget{ref-Segala2023}{}%
+\bibitem[\citeproctext]{ref-Segala2023}
 Segala FG, Bruno A, Martin JT, Aung MT, Wade AR, Baker DH (2023) Different rules for binocular combination of luminance flicker in cortical and subcortical pathways.
@@
 
-\leavevmode\hypertarget{ref-Shapiro1996}{}%
-Shapiro AG, Pokorny J, Smith VC (1996) Conerod receptor spaces with illustrations that use CRT phosphor and light-emitting-diode spectra.
+\bibitem[\citeproctext]{ref-Shapiro1996}
+Shapiro AG, Pokorny J, Smith VC (1996) Cone{\textendash}rod receptor spaces with illustrations that use {CRT} phosphor and light-emitting-diode spectra.
 Journal of the Optical Society of America A 13:2319 Available at: \url{https://doi.org/10.1364\%2Fjosaa.13.002319}.
 
-\leavevmode\hypertarget{ref-Spitschan2015}{}%
-Spitschan M, Aguirre GK, Brainard DH (2015) Selective stimulation of penumbral cones reveals perception in the shadow of retinal blood vessels. PLoS One 10:e0124328.
+\bibitem[\citeproctext]{ref-Spitschan2015}
+Spitschan M, Aguirre GK, Brainard DH (2015) \href{https://doi.org/10.1371/journal.pone.0124328}{Selective stimulation of penumbral cones reveals perception in the shadow of retinal blood vessels}.
+PLoS One 10:e0124328.
 
-\leavevmode\hypertarget{ref-Spitschan2019}{}%
-Spitschan M, Cajochen C (2019) Binocular facilitation in light-mediated melatonin suppression? J Pineal Res 67:e12602.
+\bibitem[\citeproctext]{ref-Spitschan2019}
+Spitschan M, Cajochen C (2019) \href{https://doi.org/10.1111/jpi.12602}{Binocular facilitation in light-mediated melatonin suppression?} J Pineal Res 67:e12602.
 
-\leavevmode\hypertarget{ref-Spitschan2014}{}%
+\bibitem[\citeproctext]{ref-Spitschan2014}
 Spitschan M, Jain S, Brainard DH, Aguirre GK (2014) Opponent melanopsin and s-cone signals in the human pupillary light response.
@@
 
-\leavevmode\hypertarget{ref-Spitschan2018}{}%
-Spitschan M, Woelders T (2018) The Method of Silent Substitution for Examining Melanopsin Contributions to Pupil Control. Frontiers in Neurology 9.
+\bibitem[\citeproctext]{ref-Spitschan2018}
+Spitschan M, Woelders T (2018) \href{https://doi.org/10.3389/fneur.2018.00941}{The {Method} of {Silent} {Substitution} for {Examining} {Melanopsin} {Contributions} to {Pupil} {Control}}.
+Frontiers in Neurology 9.
 
-\leavevmode\hypertarget{ref-Stockman2000}{}%
-Stockman A, Sharpe LT (2000) The spectral sensitivities of the middle- and long-wavelength-sensitive cones derived from measurements in observers of known genotype. Vision Res 40:1711--1737.
+\bibitem[\citeproctext]{ref-Stockman2000}
+Stockman A, Sharpe LT (2000) \href{https://doi.org/10.1016/s0042-6989(00)00021-3}{The spectral sensitivities of the middle- and long-wavelength-sensitive cones derived from measurements in observers of known genotype}.
+Vision Res 40:1711--1737.
 
-\leavevmode\hypertarget{ref-Wang2015}{}%
-Wang C-A, Munoz DP (2015) A circuit for pupil orienting responses: Implications for cognitive modulation of pupil size. Curr Opin Neurobiol 33:134--140.
-
-\leavevmode\hypertarget{ref-Woelders2018}{}%
-Woelders T, Leenheers T, Gordijn MCM, Hut RA, Beersma DGM, Wams EJ (2018) Melanopsin- and L-cone--induced pupil constriction is inhibited by S- and M-cones in humans.
+\bibitem[\citeproctext]{ref-Woelders2018}
+Woelders T, Leenheers T, Gordijn MCM, Hut RA, Beersma DGM, Wams EJ (2018) Melanopsin- and {L}-cone--induced pupil constriction is inhibited by {S}- and {M}-cones in humans.
 Proceedings of the National Academy of Sciences 115:792--797 Available at: \url{https://www.pnas.org/doi/full/10.1073/pnas.1716281115} {[}Accessed July 18, 2023{]}.
 
-\leavevmode\hypertarget{ref-Wyatt1981}{}%
-Wyatt HJ, Musselman JF (1981) Pupillary light reflex in humans: Evidence for an unbalanced pathway from nasal retina, and for signal cancellation in brainstem. Vision Res 21:513--525.
+\bibitem[\citeproctext]{ref-Wyatt1981}
+Wyatt HJ, Musselman JF (1981) \href{https://doi.org/10.1016/0042-6989(81)90097-3}{Pupillary light reflex in humans: Evidence for an unbalanced pathway from nasal retina, and for signal cancellation in brainstem}.
+Vision Res 21:513--525.
 
-\leavevmode\hypertarget{ref-Zele2019}{}%
-Zele AJ, Adhikari P, Cao D, Feigl B (2019) Melanopsin driven enhancement of cone-mediated visual processing. Vision Res 160:72--81.
+\bibitem[\citeproctext]{ref-Zele2019}
+Zele AJ, Adhikari P, Cao D, Feigl B (2019) \href{https://doi.org/10.1016/j.visres.2019.04.009}{Melanopsin driven enhancement of cone-mediated visual processing}. Vision Res 160:72--81.
 
-\leavevmode\hypertarget{ref-Zele2018}{}%
+\bibitem[\citeproctext]{ref-Zele2018}
 Zele AJ, Feigl B, Adhikari P, Maynard ML, Cao D (2018) Melanopsin photoreception contributes to human visual detection, temporal and colour processing.
@@
 
+\end{CSLReferences}
+
 \end{document}

### 2024-08-05 manuscript.tex
Added back line numbers

--- 2024-07-16 manuscript.tex
@@
 \setcounter{secnumdepth}{5}
-\usepackage{caption} \usepackage{setspace}\doublespacing
+\usepackage{caption} \usepackage{setspace}\doublespacing \usepackage{lineno} \linenumbers
 \usepackage{booktabs}
@@
 
-Number of words for abstract: 199
+Number of words for abstract: 187/250
 
-Number of words for introduction: 896
+Number of words for introduction: 634/650
 
-Number of words for discussion: 600
+Number of words for discussion: 600/1500
 
@@
 The autonomic nervous system regulates many involuntary bodily processes, including the constriction and dilation of the pupils in response to light (McDougal and Gamlin, \protect\hyperlink{ref-McDougal2015}{2015}).
-The anatomical pathway from the retina to the subcortical nuclei controlling the pupillary light response (PLR) is well established: it includes the Pretectal Olivary nucleus (PON), the Superior Cervical ganglion and the Edinger-Westphal nucleus, which project to the iris sphincter muscles that directly control the pupil size (McDougal and Gamlin, \protect\hyperlink{ref-McDougal2008}{2008}, \protect\hyperlink{ref-McDougal2015}{2015}; Wang and Munoz, \protect\hyperlink{ref-Wang2015}{2015}).
-Evidence of a binocular component to the PLR is shown by the existence of a consensual response of the pupil (the stimulation of one eye will cause constriction of the other eye; Wyatt and Musselman, \protect\hyperlink{ref-Wyatt1981}{1981}).
+The anatomical pathway from the retina to the subcortical nuclei controlling the pupillary light response (PLR) is well established: it includes the Pretectal Olivary nucleus (PON), the Superior Cervical ganglion and the Edinger-Westphal nucleus, which project to the iris sphincter muscles that directly control the pupil size (McDougal and Gamlin, \protect\hyperlink{ref-McDougal2015}{2015}).
+Evidence of a binocular component to the PLR is shown by the consensual response of the pupil (stimulation of one eye will cause constriction of the other eye; Wyatt and Musselman, \protect\hyperlink{ref-Wyatt1981}{1981}).
 The anatomical segregation of the subcortical pathway from the rest of the brain means that this binocular combination of signals must occur independently of the cortical processes of binocular integration required for visual perception.
@@
 
-Different classes of retinal photoreceptors, including cones, rods and melanopsin-containing intrinsically photosensitive retinal ganglion cells (ipRGCs), are directly involved in controlling and maintaining the size of the pupils (Dacey et al., \protect\hyperlink{ref-Dacey2005}{2005}; Barrionuevo et al., \protect\hyperlink{ref-Barrionuevo2014}{2014}, \protect\hyperlink{ref-Barrionuevo2018}{2018}; Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}; Murray et al., \protect\hyperlink{ref-Murray2018}{2018}; Woelders et al., \protect\hyperlink{ref-Woelders2018}{2018}; Spitschan and Cajochen, \protect\hyperlink{ref-Spitschan2019}{2019}).
-The cones have been shown to drive the initial rapid constriction of the pupils (Mathôt, \protect\hyperlink{ref-Mathot2018}{2018}), while the slower and longer activation of the ipRGCs shows their role in maintaining the constriction over a prolonged period of time and in regulating the post-illumination pupillary response (Markwell et al., \protect\hyperlink{ref-Markwell2010}{2010}; McDougal and Gamlin, \protect\hyperlink{ref-McDougal2010}{2010}).
-The ipRGCs are a unique photoreceptor class that has been discovered recently (Provencio et al., \protect\hyperlink{ref-Provencio2000}{2000}).
-They express the photopigment melanopsin, and are involved in the regulation of the circadian rhythm (Provencio et al., \protect\hyperlink{ref-Provencio2000}{2000}; Panda et al., \protect\hyperlink{ref-Panda2002}{2002}; Ruby et al., \protect\hyperlink{ref-Ruby2002}{2002}), forming a major input to the PON (Dacey et al., \protect\hyperlink{ref-Dacey2003}{2003}).
+Different classes of retinal photoreceptors, including cones, rods and melanopsin-containing intrinsically photosensitive retinal ganglion cells (ipRGCs), are directly involved in controlling and maintaining the size of the pupils (e.g.~McDougal and Gamlin, \protect\hyperlink{ref-McDougal2010}{2010}; Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}; Barrionuevo and Cao, \protect\hyperlink{ref-Barrionuevo2016}{2016}; Murray et al., \protect\hyperlink{ref-Murray2018}{2018}; Woelders et al., \protect\hyperlink{ref-Woelders2018}{2018}).
+Cones drive the initial rapid constriction of the pupils (Mathôt, \protect\hyperlink{ref-Mathot2018}{2018}), while the slower and longer activation of the ipRGCs maintains constriction over a prolonged period of time and regulates the post-illumination pupillary response (Markwell et al., \protect\hyperlink{ref-Markwell2010}{2010}; McDougal and Gamlin, \protect\hyperlink{ref-McDougal2010}{2010}).
+The ipRGCs are a recently discovered photoreceptor class (Provencio et al., \protect\hyperlink{ref-Provencio2000}{2000}) that express the photopigment melanopsin, and are involved in the regulation of the circadian rhythm (Panda et al., \protect\hyperlink{ref-Panda2002}{2002}; Ruby et al., \protect\hyperlink{ref-Ruby2002}{2002}), forming a major input to the PON (Dacey et al., \protect\hyperlink{ref-Dacey2003}{2003}).
 The first direct evidence of the involvement of the ipRGCs in the PLR was shown in melanopsin knockout rats by Lucas et al.
 (\protect\hyperlink{ref-Lucas2003}{2003}), resulting in the loss of the intrinsic photosensitivity of the cells and a reduced pupil constriction.
-This same behaviour was later also observed in primates and humans (Gamlin et al., \protect\hyperlink{ref-Gamlin2007}{2007}), where it was demonstrated that the PLR continues during light presentation even when cone and rod signalling is blocked, indicating the primary role of the ipRGCs in maintaining pupil constriction over a prolonged time.
+Similar behaviour was later observed in primates and humans (Gamlin et al., \protect\hyperlink{ref-Gamlin2007}{2007}) using silent substitution (see Methods), where it was demonstrated that the PLR continues during light presentation even when cone and rod signalling is blocked, indicating the primary role of the ipRGCs in maintaining pupil constriction over a prolonged time.
 
-A technique known as silent substitution (Estévez and Spekreijse, \protect\hyperlink{ref-Estevez1982}{1982}) can be used to selectively stimulate specific photoreceptor classes.
-Silent substitution exploits the fact that each photoreceptor class has a distinct spectral tuning that overlaps with the others.
-Using a multiprimary system, in which the primaries (i.e.~LEDs) have different spectra, it is possible to target one class of photoreceptors while maintaining the others at a constant activity level, effectively silencing them (Shapiro et al., \protect\hyperlink{ref-Shapiro1996}{1996}; Spitschan and Woelders, \protect\hyperlink{ref-Spitschan2018}{2018}, this paper also offers a clear explanation of how to implement silent substitution).
-Studies using silent substitution have shown that the pupils behave differently depending on which photoreceptor or pathway is being stimulated.
-For example, pupil responses have been shown to be out of phase when the S cones are stimulated, relative to when the ipRGCs or the L+M cones are stimulated (Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}; Cao et al., \protect\hyperlink{ref-Cao2015}{2015}).
-Additionally, when L and M cones are stimulated individually, there appears to be a paradoxical pupil response: increments in L cone stimulation cause a constriction of the pupil, while increments in M cone stimulation lead to a dilation of the pupil (Murray et al., \protect\hyperlink{ref-Murray2018}{2018}; Woelders et al., \protect\hyperlink{ref-Woelders2018}{2018}), perhaps due to activity in the L-M opponent pathway.
-
-Binocular combination has been extensively studied in visual perception, where it is mediated by neurons in primary visual cortex (Hubel and Wiesel, \protect\hyperlink{ref-Hubel1962}{1962}; Moradi and Heeger, \protect\hyperlink{ref-Moradi2009}{2009}).
-For pattern vision, binocular summation occurs at threshold, such that a lower contrast is required to detect a target shown to both eyes than a target shown to only one eye (Campbell and Green, \protect\hyperlink{ref-Campbell1965}{1965}; Legge, \protect\hyperlink{ref-Legge1984}{1984}; Baker et al., \protect\hyperlink{ref-Baker2018}{2018}).
-At higher contrasts, a process of `ocularity invariance' is observed, in which the response to monocularly- and binocularly-presented patterns is equal (Ding and Sperling, \protect\hyperlink{ref-Ding2006}{2006}; Meese et al., \protect\hyperlink{ref-Meese2006}{2006}; Baker et al., \protect\hyperlink{ref-Baker2007}{2007}; Moradi and Heeger, \protect\hyperlink{ref-Moradi2009}{2009}).
-This is thought to be due to a process of interocular suppression that compensates for the additional excitatory drive caused by stimulating two eyes.
-Our recent work (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}) has shown that cortical signal combination for luminance flicker is substantially more linear than for spatial patterns, whereas there is evidence of interocular suppression in the pupil pathway.
-
-Most studies that use silent substitution to investigate the PLR stimulate only one eye.
-If the stimulated eye is pharmacologically dilated to control pupil size, the response from the unstimulated eye (known as the consensual response) can be recorded (e.g.~McDougal and Gamlin, \protect\hyperlink{ref-McDougal2010}{2010}; Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}).
-While this approach controls the total amount of light incident at the retina, it does not permit investigation of binocular combination for specific photoreceptor pathways.
-Here we take a different approach, using a custom binocular multiprimary system (see Figure \ref{fig:spectraplots}a,b) that can modulate each (undilated) eye independently, and a binocular eye tracker to measure the diameter of both pupils.
-We measure the amplitude of pupil modulation (using Fourier analysis) in response to sinusoidal stimulation at 0.5Hz, for stimuli directed at the luminance pathway, L-M cone pathway, S-cone pathway, and melanopsin pathway (see Figure \ref{fig:spectraplots}e-l).
-Our key comparisons are between monocular and binocular stimulation, and between monocular stimulation and a dichoptic masking condition in which the two eyes are stimulated at different frequencies (0.5 and 0.4Hz).
+Binocular combination has been extensively studied in visual perception, where it is mediated by neurons in primary visual cortex (Hubel and Wiesel, \protect\hyperlink{ref-Hubel1962}{1962}).
+For pattern vision, binocular summation occurs at threshold, such that a lower contrast is required to detect a target shown to both eyes than a target shown to one eye (Campbell and Green, \protect\hyperlink{ref-Campbell1965}{1965}; Baker et al., \protect\hyperlink{ref-Baker2018}{2018}).
+At higher contrasts, a process of `ocularity invariance' is observed, in which the response to monocularly- and binocularly-presented patterns is equal (Baker et al., \protect\hyperlink{ref-Baker2007}{2007}; Moradi and Heeger, \protect\hyperlink{ref-Moradi2009}{2009}).
+This is explained by a process of interocular suppression that cancels out the additional excitatory drive caused by stimulating two eyes.
+Our recent work (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}) showed that cortical signal combination for luminance flicker is substantially more linear than for spatial patterns, whereas there is evidence of interocular suppression in the pupil pathway.
+Here we measure the amplitude of pupil modulations in response to flickering stimuli directed at the luminance, L-M cone, S-cone, and melanopsin pathways (see Figure \ref{fig:spectraplots}e-l).
+Our key comparisons are between monocular and binocular stimulation, and in a dichoptic masking condition where the two eyes are stimulated at different frequencies.
 The results are interpreted using a contemporary model of binocular vision (Meese et al., \protect\hyperlink{ref-Meese2006}{2006}) implemented within a hierarchical Bayesian framework.
@@
 
-To present synchronised stimulus modulations independently to each eye, two light engines (SpectraTuneLAB: LEDMOTIVE Technologies, LLC, Barcelona, Spain), each with 10 independently addressable LED colour channels, were integrated into a customised viewing system.
+To present synchronised stimulus modulations independently to each eye, two light engines (SpectraTuneLAB: LEDMOTIVE Technologies, LLC, Barcelona, Spain), each with 10 independently addressable LED colour channels, were integrated into a customised binocular viewing system.
 The light engines were operated via a Python interface to their REST API (Martin et al., \protect\hyperlink{ref-Martin2022}{2022}), which supports synchronous launch and playback of spectral sequences prepared in advance and stored in JSON format.
 When preparing the spectral sequences, the age of participants was used to account for the yellowing of the lenses.
+We used the silent substitution technique (Estévez and Spekreijse, \protect\hyperlink{ref-Estevez1982}{1982}) to selectively stimulate specific photoreceptor classes.
+Silent substitution exploits the fact that each photoreceptor class has a distinct spectral tuning that overlaps with the others.
+Using a multiprimary system, in which the primaries (i.e.~LEDs) have different spectra, it is possible to target one class of photoreceptors while maintaining the others at a constant activity level, effectively silencing them (Shapiro et al., \protect\hyperlink{ref-Shapiro1996}{1996}; Spitschan and Woelders, \protect\hyperlink{ref-Spitschan2018}{2018}, this paper also offers a clear explanation of how to implement silent substitution).
 We calculated silent substitution solutions using the \emph{PySilSub} toolbox (Martin et al., \protect\hyperlink{ref-Martin2023}{2023}), using linear algebra.
@@
 
-\leavevmode\hypertarget{ref-Barrionuevo2018}{}%
-Barrionuevo PA, McAnany JJ, Zele AJ, Cao D (2018) Non-linearities in the Rod and Cone Photoreceptor Inputs to the Afferent Pupil Light Response. Frontiers in Neurology 9.
-
-\leavevmode\hypertarget{ref-Barrionuevo2014}{}%
-Barrionuevo PA, Nicandro N, McAnany JJ, Zele AJ, Gamlin P, Cao D (2014) Assessing rod, cone, and melanopsin contributions to human pupil flicker responses.
-Investigative Ophthalmology \& Visual Science 55:719--727.
-
 \leavevmode\hypertarget{ref-Busse2009}{}%
@@
 Campbell FW, Green DG (1965) Monocular versus binocular visual acuity. Nature 208:191--192.
-
-\leavevmode\hypertarget{ref-Cao2015}{}%
-Cao D, Nicandro N, Barrionuevo PA (2015) A five-primary photostimulator suitable for studying intrinsically photosensitive retinal ganglion cell functions in humans.
-Journal of Vision 15:27 Available at: \url{https://doi.org/10.1167/15.1.27} {[}Accessed July 18, 2023{]}.
 
@@
 
-\leavevmode\hypertarget{ref-Dacey2005}{}%
-Dacey DM, Liao H-W, Peterson BB, Robinson FR, Smith VC, Pokorny J, Yau K-W, Gamlin PD (2005) Melanopsin-expressing ganglion cells in primate retina signal colour and irradiance and project to the LGN.
-Nature 433:749--754 Available at: \url{https://www.nature.com/articles/nature03387} {[}Accessed July 18, 2023{]}.
-
 \leavevmode\hypertarget{ref-Dacey2003}{}%
@@
 Neuron 37:15--27 Available at: \url{https://www.sciencedirect.com/science/article/pii/S0896627302011431}.
-
-\leavevmode\hypertarget{ref-Ding2006}{}%
-Ding J, Sperling G (2006) A gain-control theory of binocular combination. Proc Natl Acad Sci U S A 103:1141--1146.
 
@@
 
-\leavevmode\hypertarget{ref-Legge1984}{}%
-Legge GE (1984) Binocular contrast summation--ii. Quadratic summation. Vision Res 24:385--394.
-
 \leavevmode\hypertarget{ref-Lucas2003}{}%
@@
 Mathôt S (2018) Pupillometry: Psychology, physiology, and function. J Cogn 1:16.
-
-\leavevmode\hypertarget{ref-McDougal2008}{}%
-McDougal DH, Gamlin PD (2008) Pupillary control pathways. In: The senses: A comprehensive reference, pp 521--536. Elsevier.
 
@@
 
-\leavevmode\hypertarget{ref-Wang2015}{}%
-Wang C-A, Munoz DP (2015) A circuit for pupil orienting responses: Implications for cognitive modulation of pupil size. Curr Opin Neurobiol 33:134--140.
-
 \leavevmode\hypertarget{ref-Woelders2018}{}%

### 2024-11-28 manuscript.Rmd
Added back line numbers
Modifeid manuscript

@@
   \usepackage{setspace}\doublespacing
-  # \usepackage{lineno} \linenumbers
+  \usepackage{lineno} \linenumbers
+  \newcommand{\beginsupplement}{\setcounter{table}{0}
+  \renewcommand{\thetable}{S\arabic{table}}
+  \setcounter{figure}{0}
+  \renewcommand{\thefigure}{S\arabic{figure}}}
 ---
@@
 
-pdf(paste0(figdir,"methodsfig.pdf"), bg="transparent", height = 13, width = 12)
+pdf(paste0(figdir,"methodsfigrods.pdf"), bg="transparent", height = 13, width = 12)
 
@@
 
-plotlims <- c(0.5,4.5,0,15)
-ticklocsx <- 1:4    # locations of tick marks on x axis
+plotlims <- c(0.5,5.5,0,15)
+ticklocsx <- 1:5    # locations of tick marks on x axis
 ticklocsy <- seq(0,15,5)    # locations of tick marks on y axis
-ticklabelsx <- c('sc','mc','lc','mel')        # set labels for x ticks
+ticklabelsx <- c('sc','mc','lc','rods','mel')        # set labels for x ticks
 ticklabelsy <- ticklocsy    # set labels for y ticks
@@
 
-coneab <- coneab[c(1:3,5),]   # don't plot rod predictions
-for (b in 1:4){
+# coneab <- coneab[c(1:3,5),]   # don't plot rod predictions
+for (b in 1:5){
   polygon(c(b-0.3,b,b,b-0.3),c(0,0,coneab[b,2],coneab[b,2]),col=colpal[2],border=NA)
@@
 
-text(4.5,14,'(d)',pos=4,cex=2)
+text(5.5,14,'(d)',pos=4,cex=2)
 
@@
 title(ylab="Difference power", col.lab=rgb(0,0,0), line=2.8, cex.lab=1.5)
-title(main='Luminance',cex.main=2)
+title(main='Light flux',cex.main=2)
 
@@
 
-pcontrast <- pcontrast[c(1,2,3,5),]   # don't plot rods
-
-plotlims <- c(0.5,4.5,-100,100)
-ticklocsx <- 1:4    # locations of tick marks on x axis
+# pcontrast <- pcontrast[c(1,2,3,5),]   # don't plot rods
+
+plotlims <- c(0.5,5.5,-100,100)
+ticklocsx <- 1:5    # locations of tick marks on x axis
 ticklocsy <- seq(-100,100,50)    # locations of tick marks on y axis
-ticklabelsx <- c('sc','mc','lc','mel')        # set labels for x ticks
+ticklabelsx <- c('sc','mc','lc','rods','mel')        # set labels for x ticks
 ticklabelsy <- ticklocsy    # set labels for y ticks
@@
 
-for (b in 1:4){
+for (b in 1:5){
   polygon(c(b-0.3,b+0.3,b+0.3,b-0.3),c(0,0,pcontrast[b,4],pcontrast[b,4]),col=stimcolours[1],border='black',lwd=2)
@@
 
-lines(c(0.5,4.5),c(0,0),lwd=2)
-
-text(3.65,80,'(i)',pos=4,cex=2)
-
-plotlims <- c(0.5,4.5,-20,20)
-ticklocsx <- 1:4    # locations of tick marks on x axis
+lines(c(0.5,5.5),c(0,0),lwd=2)
+
+text(4.65,80,'(i)',pos=4,cex=2)
+
+plotlims <- c(0.5,5.5,-20,20)
+ticklocsx <- 1:5    # locations of tick marks on x axis
 ticklocsy <- seq(-20,20,10)    # locations of tick marks on y axis
@@
 
-for (b in 1:4){
+for (b in 1:5){
   polygon(c(b-0.3,b+0.3,b+0.3,b-0.3),c(0,0,pcontrast[b,6],pcontrast[b,6]),col=stimcolours[3],border='black',lwd=2)
@@
 
-lines(c(0.5,4.5),c(0,0),lwd=2)
-
-text(3.6,18,'(j)',pos=4,cex=2)
-
-plotlims <- c(0.5,4.5,-50,50)
-ticklocsx <- 1:4    # locations of tick marks on x axis
+lines(c(0.5,5.5),c(0,0),lwd=2)
+
+text(4.6,18,'(j)',pos=4,cex=2)
+
+plotlims <- c(0.5,5.5,-50,50)
+ticklocsx <- 1:5    # locations of tick marks on x axis
 ticklocsy <- seq(-50,50,25)    # locations of tick marks on y axis
@@
 
-for (b in 1:4){
+for (b in 1:5){
   polygon(c(b-0.3,b+0.3,b+0.3,b-0.3),c(0,0,pcontrast[b,8],pcontrast[b,8]),col=stimcolours[5],border='black',lwd=2)
@@
 
-lines(c(0.5,4.5),c(0,0),lwd=2)
-
-text(3.6,45,'(k)',pos=4,cex=2)
-
-plotlims <- c(0.5,4.5,-20,20)
-ticklocsx <- 1:4    # locations of tick marks on x axis
+lines(c(0.5,5.5),c(0,0),lwd=2)
+
+text(4.6,45,'(k)',pos=4,cex=2)
+
+plotlims <- c(0.5,5.5,-20,20)
+ticklocsx <- 1:5    # locations of tick marks on x axis
 ticklocsy <- seq(-20,20,10)    # locations of tick marks on y axis
@@
 
-for (b in 1:4){
+for (b in 1:5){
   polygon(c(b-0.3,b+0.3,b+0.3,b-0.3),c(0,0,pcontrast[b,10],pcontrast[b,10]),col=stimcolours[7],border='black',lwd=2)
@@
 
-lines(c(0.5,4.5),c(0,0),lwd=2)
+lines(c(0.5,5.5),c(0,0),lwd=2)
 
@@
 layout(matrix(c(1,2,3,4,5,5,5,5,6,7,8,9),6,2,byrow=TRUE))
+
 par(mar=c(3,6,2,1))
@@
 title(ylab="Amplitude at 0.5Hz (mm)", col.lab=rgb(0,0,0), line=3, cex.lab=1.5)
-title(main='Luminance',cex.main=2)
+title(main='Light flux',cex.main=2)
 for (cond in 1:3){
@@
 
-legend(-24,0.6,c('Prior','Lum 1F', 'L-M 1F', 'S 1F', 'Mel 1F'), col=c('black',stimcolours[c(1,4,6,7)]),lwd=c(2,6,6,6,6),lty=1, cex=1.8, box.lwd=2, bg='white')
+legend(-24,0.6,c('Prior','LF 1F', 'L-M 1F', 'S 1F', 'Mel 1F'), col=c('black',stimcolours[c(1,4,6,7)]),lwd=c(2,6,6,6,6),lty=1, cex=1.8, box.lwd=2, bg='white')
 
@@
 title(ylab="Amplitude at 0.4Hz (mm)", col.lab=rgb(0,0,0), line=3, cex.lab=1.5)
-title(main='Luminance',cex.main=2)
+title(main='Light flux',cex.main=2)
 for (cond in 1:3){
@@
 title(ylab="Amplitude at 1Hz (mm)", col.lab=rgb(0,0,0), line=3.5, cex.lab=1.5)
-title(main='Luminance',cex.main=2)
+title(main='Light flux',cex.main=2)
 for (cond in 1:3){
@@
 
-legend(-24,0.6,c('Prior','Lum 2F', 'L-M 2F', 'S 2F', 'Mel 2F'), col=c('black',stimcolours[c(1,4,6,7)]),lwd=c(2,6,6,6,6),lty=1, cex=1.8, box.lwd=2, bg='white')
+legend(-24,0.6,c('Prior','LF 2F', 'L-M 2F', 'S 2F', 'Mel 2F'), col=c('black',stimcolours[c(1,4,6,7)]),lwd=c(2,6,6,6,6),lty=1, cex=1.8, box.lwd=2, bg='white')
 
@@
 title(ylab="Amplitude at 0.8Hz (mm)", col.lab=rgb(0,0,0), line=3.5, cex.lab=1.5)
-title(main='Luminance',cex.main=2)
+title(main='Light flux',cex.main=2)
 for (cond in 1:3){
@@
 
-legend(-0.019,0.0155,c('Luminance','L-M','S','Melanopsin'),lty=1,col=stimcolours[c(1,3,6,7)],lwd=3,pch=21,pt.cex=2,pt.bg=stimcolours[c(2,4,5,8)],cex=1.1,box.lwd=3,bg='white')
+legend(-0.019,0.0155,c('Light flux','L-M','S','Melanopsin'),lty=1,col=stimcolours[c(1,3,6,7)],lwd=3,pch=21,pt.cex=2,pt.bg=stimcolours[c(2,4,5,8)],cex=1.1,box.lwd=3,bg='white')
 
@@
 We investigated binocular combination by targeting different photoreceptor pathways using a novel binocular multiprimary system to modulate the input spectra via silent substitution.
-At the first harmonic of the modulation frequency, luminance and S-cone responses showed strong binocular facilitation, and weak interocular suppression.
+At the first harmonic of the modulation frequency, light flux and S-cone responses showed strong binocular facilitation, and weak interocular suppression.
 Melanopsin responses were invariant to the number of eyes stimulated.
@@
 We investigated the algorithmic properties of this binocular combination process for the first time.
-Using silent subsitution, we targeted different post-retinal pathways (luminance, L-M cones, S-cones, and melanopsin) with flickering stimuli generated by a novel binocular multi-primary system.
+Using silent subsitution, we targeted different post-retinal pathways (light flux, L-M cones, S-cones, and melanopsin) with flickering stimuli generated by a novel binocular multi-primary system.
 We found different patterns of binocular combination across pathways, and also differences in the phase of the pupil response.
@@
 Our recent work [@Segala2023] showed that cortical signal combination for luminance flicker is substantially more linear than for spatial patterns, whereas there is evidence of interocular suppression in the pupil pathway.
-Here we measure the amplitude of pupil modulations in response to flickering stimuli directed at the luminance, L-M cone, S-cone, and melanopsin pathways (see Figure \@ref(fig:spectraplots)e-l).
+Here we measure the amplitude of pupil modulations in response to flickering stimuli directed at the light flux, L-M cone, S-cone, and melanopsin pathways (see Figure \@ref(fig:spectraplots)e-l).
 Our key comparisons are between monocular and binocular stimulation, and in a dichoptic masking condition where the two eyes are stimulated at different frequencies.
@@
 
-To present synchronised stimulus modulations independently to each eye, two light engines (SpectraTuneLAB: LEDMOTIVE Technologies, LLC, Barcelona, Spain), each with 10 independently addressable LED colour channels, were integrated into a customised binocular viewing system.
+To present synchronised stimulus modulations independently to each eye, two light engines (SpectraTuneLAB, which are thermally stable across time with active cooling according to the manufacturers: LEDMOTIVE Technologies, LLC, Barcelona, Spain), each with 10 independently addressable LED colour channels, were integrated into a customised binocular viewing system.
 The light engines were operated via a Python interface to their REST API [@Martin2022], which supports synchronous launch and playback of spectral sequences prepared in advance and stored in JSON format.
+A special command was commissioned from LEDMOTIVE to allow two different stimulus files to be launched simultaneously from the two devices.
+The synchronisation of the spectra from the two devices was tested and showed that they were synchronised to within approximately 3ms.
+
 When preparing the spectral sequences, the age of participants was used to account for the yellowing of the lenses.
@@
 The use of this set up allowed us to modulate the stimuli in three different ocular configurations, similar to the ones we used in our previous study [@Segala2023]: monocular, binocular and dichoptic.
-In the monocular configuration, the unstimulated eye still saw a non-flickering disc of mean luminance.
+In the monocular configuration, the unstimulated eye still saw a non-flickering disc of mean light flux.
 A schematic of the stimulation system is shown in Figure \@ref(fig:spectraplots)a.
@@
 
-In the luminance experiment, the stimulus intensity was increased and decreased relative to the background, which we expected to modulate all photoreceptor classes (see Figure \@ref(fig:spectraplots)e,i).
-In the L-M cone modulation experiment, we used silent substution to increase the L-cone activity, and simultaneously decrease the M-cone activity, during the first half-cycle of the sine wave.
+Silent substitution stimuli were prepared and calibrated for each participant with custom Python software [@Martin2023] and Python scripts.
+Estimates of photoreceptor spectral sensitivities for each participant were constructed from the known photopigment absorbance spectra [@Stockman2000], taking account of the peak axial density of the respective photopigments, as well as lens [@Pokorny1987; @Stockman1999; @Stockman2000] and macular pigment density [@Bone1988; @Stockman1999], in accordance with the field size and age-dependant CIEPO06 observer model [@CIE2006].
+The melanopic and rhodopic action spectra of the 32-year-old standard observer were taken from CIE S 026 [@CIE2018] and then adjusted for age-related lens transmittance with a spectral correction function, in line with the standard.
+Macular pigment correction was not applied to the rhodopic and melanopic action spectra because rods are not present at the fovea and ipRGCs sit above the retinal pigment layer [@Trieschmann2007].
+
+In the light flux experiment, the stimulus intensity was increased and decreased relative to the background, which we expected to modulate all photoreceptor classes (see Figure \@ref(fig:spectraplots)e,i).
+In the L-M cone modulation experiment, we used silent substitution to increase the L-cone activity, and simultaneously decrease the M-cone activity, during the first half-cycle of the sine wave.
 In the second half-cycle the polarity of the modulation reversed (see Figure \@ref(fig:spectraplots)f,j).
@@
 We assume that the activity of rods was constant at the high background luminance intensity used here, and so did not attempt to silence rod activity in any condition, as this would have greatly reduced the available dynamic range.
-Splatter on nominally silenced photoreceptors was very small (see Figure \@ref(fig:spectraplots)j-l), well below the levels that would be expected to generate measureable pupil modulations.
+Splatter on nominally silenced photoreceptors was very small (see Figure \@ref(fig:spectraplots)j-l), well below the levels that would be expected to generate measurable pupil modulations, although we can observe that the rods may not be saturated in the L-M and melanopsin-directed stimuli (Figure \@ref(fig:spectraplots)j and \@ref(fig:spectraplots)l) and could intrude in these two experiments.
 We also estimated activation of penumbral L and M cones [@Spitschan2015; @Barrionuevo2016; @Zele2019], which was minimal ($\le 1.5%$ contrast; less than splatter on the open-field cones) for melanopsin-directed stimuli.
@@
 The participants were given no task other than look at the black fixation dot while trying to minimise their blinking during the presentation period.
-For all experiments other than the luminance condition, participants adapted to the unmodulated background luminance for two minutes before stimulation began.
+For all experiments other than the light flux condition, participants adapted to the unmodulated background luminance for two minutes before stimulation began.
 
@@
 Figure \@ref(fig:spectraplots)m-p shows averaged waveforms of pupil diameter in response to binocular stimulation.
-For luminance stimuli (Figure \@ref(fig:spectraplots)m) a strong modulation is apparent at the stimulation frequency (0.5Hz), which is also clear in the Fourier amplitude spectrum (Figure \@ref(fig:spectraplots)q).
-For binocular stimulation of the L-M pathway, S-cone pathway and melanopsin pathway, pupil modulations were less than 10\% of the amplitude of the luminance modulation (note the change in y-axis scale for the Fourier spectra), but still apparent at 0.5Hz in the Fourier spectra (Figure \@ref(fig:spectraplots)n-p).
-We also observed a second harmonic response (at 1Hz) for all conditions, which was weaker than the first harmonic for luminance and melanopsin stimulation, but stronger for L-M and S-cone stimulation.
+For light flux stimuli (Figure \@ref(fig:spectraplots)m) a strong modulation is apparent at the stimulation frequency (0.5Hz), which is also clear in the Fourier amplitude spectrum (Figure \@ref(fig:spectraplots)q).
+For binocular stimulation of the L-M pathway, S-cone pathway and melanopsin pathway, pupil modulations were less than 10\% of the amplitude of the light flux modulation (note the change in y-axis scale for the Fourier spectra), but still apparent at 0.5Hz in the Fourier spectra (Figure \@ref(fig:spectraplots)n-p).
+We also observed a second harmonic response (at 1Hz) for all conditions, which was weaker than the first harmonic for light flux and melanopsin stimulation, but stronger for L-M and S-cone stimulation.
 The second harmonic is also apparent in the pupil waveforms shown in Figure \@ref(fig:spectraplots)n-p.
@@
 
-knitr::include_graphics(paste0(figdir,'methodsfig.pdf'))
+knitr::include_graphics(paste0(figdir,'methodsfigrods.pdf'))
 
@@
 In each plot, the response to monocular stimulation is given by the red circles and typically increases monotonically as a function of stimulus (temporal) contrast.
-Relative to monocular stimulation, binocular stimulation led to higher response amplitudes, indicating a binocular facilitation effect, for the luminance and S-cone conditions (Figure \@ref(fig:FirstHarmonicPlots)a,c), and to some extent for the melanopsin condition (Figure \@ref(fig:FirstHarmonicPlots)d).
+Relative to monocular stimulation, binocular stimulation led to higher response amplitudes, indicating a binocular facilitation effect, for the light flux and S-cone conditions (Figure \@ref(fig:FirstHarmonicPlots)a,c), and to some extent for the melanopsin condition (Figure \@ref(fig:FirstHarmonicPlots)d).
 However, the L-M cone condition (Figure \@ref(fig:FirstHarmonicPlots)b) produced a binocular suppression effect, where the response to binocular stimulation was weaker than the response to monocular stimulation (blue squares below red circles).
@@
 Our primary objective was to compare posterior distributions of the weight of interocular suppression, which are shown in Figure \@ref(fig:FirstHarmonicPlots)e.
-Consistent with our earlier observations, the strongest suppressive weight corresponds to the L-M and Melanopsin conditions, and the weakest suppression corresponds to the luminance and S-cone conditions, with virtually no overlap between the posterior distributions for weak and strong suppression.
+Consistent with our earlier observations, the strongest suppressive weight corresponds to the L-M and Melanopsin conditions, and the weakest suppression corresponds to the light flux and S-cone conditions, with virtually no overlap between the posterior distributions for weak and strong suppression.
 The model fits were of good quality, as shown by the curves in Figure \@ref(fig:FirstHarmonicPlots)a-d,f-i.
@@
 
-condnames <- c('Luminance 1F','L-M cone 1F','S cone 1F','Melanopsin 1F','Luminance 2F','L-M cone 2F','S cone 2F','Melanopsin 2F')
+condnames <- c('Light flux 1F','L-M cone 1F','S cone 1F','Melanopsin 1F','Light flux 2F','L-M cone 2F','S cone 2F','Melanopsin 2F')
 zlist <- c(pupilZLum, pupilZLM, pupilZS, pupilZMel, pupilZLum2, pupilZLM2, pupilZS2, pupilZMel2)
@@
 At the first harmonic, melanopsin and S-cone signals differed in phase by more than 90 degrees, though they were not fully in antiphase.
-The luminance and L-M responses were approximately in antiphase to each other, however this is likely due to our choice to modulate L+M- in the first half-cycle of the sine wave (corresponding to a luminance increase in the luminance condition), and L-M+ in the second half-cycle (corresponding to a luminance decrease in the luminance condition).
-Had we reversed this phase arrangement, we would likely have seen a close phase correspondence between the L-M and luminance conditions (another way to think about this is that L-cone decreases and M-cone increases are processed like luminance increases).
-Phase differences between the luminance, S-cone and melanopsin conditions are likely attributable to different lags in phototransduction at the earliest stage (i.e.
+The light flux and L-M responses were approximately in antiphase to each other, however this is likely due to our choice to modulate L+M- in the first half-cycle of the sine wave (corresponding to a luminance increase in the light flux condition), and L-M+ in the second half-cycle (corresponding to a luminance decrease in the light flux condition).
+Had we reversed this phase arrangement, we would likely have seen a close phase correspondence between the L-M and light flux conditions (another way to think about this is that L-cone decreases and M-cone increases are processed like luminance increases).
+Phase differences between the light flux, S-cone and melanopsin conditions are likely attributable to different lags in phototransduction at the earliest stage (i.e.
 in the retina).
-At the second harmonic frequency (Figure \@ref(fig:phaseplots)b), the luminance condition was again out of phase with the other three, and was approximately in quadrature phase with the L-M condition, and in antiphase with both the S-cone and melanopsin conditions (which were in phase with each other).
-
-```{r phaseplots, fig.cap="Pupil phase plots at the first and second harmonic frequencies for the luminance, melanopsin, L-M pathway and the S-(L+M) pathway conditions.
+At the second harmonic frequency (Figure \@ref(fig:phaseplots)b), the light flux condition was again out of phase with the other three, and was approximately in quadrature phase with the L-M condition, and in antiphase with both the S-cone and melanopsin conditions (which were in phase with each other).
+
+```{r phaseplots, fig.cap="Pupil phase plots at the first and second harmonic frequencies for the light flux, melanopsin, L-M pathway and the S-(L+M) pathway conditions.
 Panel (a) shows the pupil response at the first harmonic frequency during binocular stimulation.
@@
 The five data points for each pathway correspond to the five contrast levels displayed.
-In panel (a) the luminance amplitudes have been scaled down by a factor of 10 to enable comparison with the other conditions.", fig.align="center", echo=FALSE}
+In panel (a) the light flux amplitudes have been scaled down by a factor of 10 to enable comparison with the other conditions.", fig.align="center", echo=FALSE}
 
@@
 This pattern of results was confirmed by a computational model, which allowed us to compare the weight of interocular suppression for each pathway.
-We found that at the first harmonic frequency the L-M and melanopsin pathways involved strong suppression, whereas the luminance and S-cone pathways involved weaker suppression.
+We found that at the first harmonic frequency the L-M and melanopsin pathways involved strong suppression, whereas the light flux and S-cone pathways involved weaker suppression.
 Suppression was strong in all four pathways at the second harmonic frequency.
@@
 
-Our recent psychophysical work [@Baker2024] has looked at binocular interactions in the L-M and S-cone pathways, and compared these to the luminance pathway.
-Using a contrast discrimination paradigm with spatial modulations of luminance and colour, @Baker2024 found equally strong interocular suppression in all three pathways.
-This is rather different from our pupillometry results here, which demonstrate weaker suppression in the luminance and S-cone pathways than in the L-M pathway (see Figure \@ref(fig:FirstHarmonicPlots)).
+Our recent psychophysical work [@Baker2024] has looked at binocular interactions in the L-M and S-cone pathways, and compared these to the light flux pathway.
+Using a contrast discrimination paradigm with spatial modulations of light flux and colour, @Baker2024 found equally strong interocular suppression in all three pathways.
+This is rather different from our pupillometry results here, which demonstrate weaker suppression in the light flux and S-cone pathways than in the L-M pathway (see Figure \@ref(fig:FirstHarmonicPlots)).
 However, the current experiments involve temporal modulations, which are quite distinct from the spatial modulations used in @Baker2024.
@@
 This was strong ($\omega \ge 1$) for L-M and melanopsin signals at the first harmonic, and all pathways at the second harmonic.
-Suppression was weaker ($\omega < 1$) in the luminance pathway (consistent with previous work), and also for S-cone directed modulations.
+Suppression was weaker ($\omega < 1$) in the light flux pathway (consistent with previous work), and also for S-cone directed modulations.
 
@@
 <div id='refs'> </div>
+
+# Supplementary material
+
+\beginsupplement
+
+```{r primarylinearity, fig.cap="Linearity of primaries for each device.
+The calibration measures were summed (i.e., total unweighted irradiance), and the input-output relationship summarised by a 7th order polynomial reverse curve fit.
+By applying the coefficients of the regression, it is possible to achieve a linear output in the primaries.", fig.align="center", echo=FALSE}
+
+knitr::include_graphics(paste0(figdir,'SuppFig1.pdf'))
+
+```

### 2025-01-01 manuscript.Rmd
Minor edits and updated one reference

@@
 For pattern vision, binocular summation occurs at threshold, such that a lower contrast is required to detect a target shown to both eyes than a target shown to one eye [@Baker2018; @Campbell1965].
-At higher contrasts, a process of 'ocularity invariance' is observed, in which the response to monocularly- and binocularly-presented patterns is equal [@Baker2007; @Moradi2009].
+At higher contrasts, the phenomenon of 'ocularity invariance' is observed, in which the response to monocularly- and binocularly-presented patterns is equal [@Baker2007; @Moradi2009].
 This is explained by a process of interocular suppression that cancels out the additional excitatory drive caused by stimulating two eyes.
 Our recent work [@Segala2023] showed that cortical signal combination for luminance flicker is substantially more linear than for spatial patterns, whereas there is evidence of interocular suppression in the pupil pathway.
-Here we measure the amplitude of pupil modulations in response to flickering stimuli directed at the light flux, L-M cone, S-cone, and melanopsin pathways (see Figure \@ref(fig:spectraplots)e-l).
+Here we measure the amplitude of pupil modulations in response to flickering stimuli presented as light flux, or directed towards the L-M cone, S-cone, and melanopsin pathways (see Figure \@ref(fig:spectraplots)e-l).
 Our key comparisons are between monocular and binocular stimulation, and in a dichoptic masking condition where the two eyes are stimulated at different frequencies.
@@
 The outputs of the two light engines (see Figure \@ref(fig:spectraplots)b,c) were calibrated using an Ocean Optics Jaz spectroradiometer, which was wavelength-calibrated to an Argon lamp and intensity calibrated using a NIST-traceable light source.
+Each primary was also linearized using a polynomial fit (see Figure \@ref(fig:primarylinearity) for details).
 We used the @Stockman2000 10-degree cone fundamentals, and estimates of melanopsin absorbance spectra from CIE S 026 [discussed in @Martin2023] to calculate $\alpha$-opic irradiance.
@@
 
-To describe our data, we used the same model described in our previous study [@Segala2023].
+To quantitatively summarise our data, we used the same model described in our previous study [@Segala2023].
 The model has the same general form as the first stage of the contrast gain control model proposed by @Meese2006, but omits the second stage.
@@
 At the second harmonic frequency (Figure \@ref(fig:phaseplots)b), the light flux condition was again out of phase with the other three, and was approximately in quadrature phase with the L-M condition, and in antiphase with both the S-cone and melanopsin conditions (which were in phase with each other).
-
-```{r phaseplots, fig.cap="Pupil phase plots at the first and second harmonic frequencies for the light flux, melanopsin, L-M pathway and the S-(L+M) pathway conditions.
+We note that the marked phase differences between conditions make the possibility that our results are dominated by rod activity relatively unlikely (e.g.
+in the L-M and melanopsin conditions, which have very different phase profiles).
+
+```{r phaseplots, fig.cap="Pupil phase plots at the first and second harmonic frequencies for the light flux, melanopsin, L-M pathway and the S-cone pathway conditions.
 Panel (a) shows the pupil response at the first harmonic frequency during binocular stimulation.
@@
 
-We have demonstrated that binocular combination of temporal flickering light in the autonomic nervous system depends on the photoreceptor pathway.
+We have demonstrated that binocular combination of temporal flickering light in the autonomic nervous system depends on the photoreceptor pathway stimulated.
 We were able to elicit pupil responses by stimulating the periphery of the retina and we were able to record contrast response functions for all photoreceptor pathways.

### 2025-01-01 manuscript.tex
Minor edits and updated one reference

--- 2024-07-16 manuscript.tex
@@
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
-\usepackage{caption} \usepackage{setspace}\doublespacing
+\usepackage{caption} \usepackage{setspace}\doublespacing \usepackage{lineno} \linenumbers \newcommand{\beginsupplement}{\setcounter{table}{0} \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
 \usepackage{booktabs}
@@
 
-Number of words for introduction: 685/650
+Number of words for introduction: 634/650
 
@@
 For pattern vision, binocular summation occurs at threshold, such that a lower contrast is required to detect a target shown to both eyes than a target shown to one eye (\citeproc{ref-Campbell1965}{Campbell and Green, 1965}; \citeproc{ref-Baker2018}{Baker et al., 2018}).
-At higher contrasts, a process of `ocularity invariance' is observed, in which the response to monocularly- and binocularly-presented patterns is equal (\citeproc{ref-Baker2007}{Baker et al., 2007}; \citeproc{ref-Moradi2009}{Moradi and Heeger, 2009}).
+At higher contrasts, the phenomenon of `ocularity invariance' is observed, in which the response to monocularly- and binocularly-presented patterns is equal (\citeproc{ref-Baker2007}{Baker et al., 2007}; \citeproc{ref-Moradi2009}{Moradi and Heeger, 2009}).
 This is explained by a process of interocular suppression that cancels out the additional excitatory drive caused by stimulating two eyes.
 Our recent work (\citeproc{ref-Segala2023}{Segala et al., 2023}) showed that cortical signal combination for luminance flicker is substantially more linear than for spatial patterns, whereas there is evidence of interocular suppression in the pupil pathway.
-Here we measure the amplitude of pupil modulations in response to flickering stimuli directed at the luminance, L-M cone, S-cone, and melanopsin pathways (see Figure \ref{fig:spectraplots}e-l).
+Here we measure the amplitude of pupil modulations in response to flickering stimuli presented as light flux, or directed towards the L-M cone, S-cone, and melanopsin pathways (see Figure \ref{fig:spectraplots}e-l).
 Our key comparisons are between monocular and binocular stimulation, and in a dichoptic masking condition where the two eyes are stimulated at different frequencies.
@@
 
-To present synchronised stimulus modulations independently to each eye, two light engines (SpectraTuneLAB: LEDMOTIVE Technologies, LLC, Barcelona, Spain), each with 10 independently addressable LED colour channels, were integrated into a customised binocular viewing system.
+To present synchronised stimulus modulations independently to each eye, two light engines (SpectraTuneLAB, which are thermally stable across time with active cooling according to the manufacturers: LEDMOTIVE Technologies, LLC, Barcelona, Spain), each with 10 independently addressable LED colour channels, were integrated into a customised binocular viewing system.
 The light engines were operated via a Python interface to their REST API (\citeproc{ref-Martin2022}{Martin et al., 2022}), which supports synchronous launch and playback of spectral sequences prepared in advance and stored in JSON format.
+A special command was commissioned from LEDMOTIVE to allow two different stimulus files to be launched simultaneously from the two devices.
+The synchronisation of the spectra from the two devices was tested and showed that they were synchronised to within approximately 3ms.
+
 When preparing the spectral sequences, the age of participants was used to account for the yellowing of the lenses.
@@
 The outputs of the two light engines (see Figure \ref{fig:spectraplots}b,c) were calibrated using an Ocean Optics Jaz spectroradiometer, which was wavelength-calibrated to an Argon lamp and intensity calibrated using a NIST-traceable light source.
+Each primary was also linearized using a polynomial fit (see Figure \ref{fig:primarylinearity} for details).
 We used the Stockman and Sharpe (\citeproc{ref-Stockman2000}{2000}) 10-degree cone fundamentals, and estimates of melanopsin absorbance spectra from CIE S 026 (discussed in \citeproc{ref-Martin2023}{Martin et al., 2023}) to calculate \(\alpha\)-opic irradiance.
@@
 The use of this set up allowed us to modulate the stimuli in three different ocular configurations, similar to the ones we used in our previous study (\citeproc{ref-Segala2023}{Segala et al., 2023}): monocular, binocular and dichoptic.
-In the monocular configuration, the unstimulated eye still saw a non-flickering disc of mean luminance.
+In the monocular configuration, the unstimulated eye still saw a non-flickering disc of mean light flux.
 A schematic of the stimulation system is shown in Figure \ref{fig:spectraplots}a.
@@
 
-In the luminance experiment, the stimulus intensity was increased and decreased relative to the background, which we expected to modulate all photoreceptor classes (see Figure \ref{fig:spectraplots}e,i).
-In the L-M cone modulation experiment, we used silent substution to increase the L-cone activity, and simultaneously decrease the M-cone activity, during the first half-cycle of the sine wave.
+Silent substitution stimuli were prepared and calibrated for each participant with custom Python software (\citeproc{ref-Martin2023}{Martin et al., 2023}) and Python scripts.
+Estimates of photoreceptor spectral sensitivities for each participant were constructed from the known photopigment absorbance spectra (\citeproc{ref-Stockman2000}{Stockman and Sharpe, 2000}), taking account of the peak axial density of the respective photopigments, as well as lens (\citeproc{ref-Pokorny1987}{Pokorny et al., 1987}; \citeproc{ref-Stockman1999}{Stockman et al., 1999}; \citeproc{ref-Stockman2000}{Stockman and Sharpe, 2000}) and macular pigment density (\citeproc{ref-Bone1988}{Bone et al., 1988}; \citeproc{ref-Stockman1999}{Stockman et al., 1999}), in accordance with the field size and age-dependant CIEPO06 observer model (\citeproc{ref-CIE2006}{CIE, 2006}).
+The melanopic and rhodopic action spectra of the 32-year-old standard observer were taken from CIE S 026 (\citeproc{ref-CIE2018}{CIE, 2018}) and then adjusted for age-related lens transmittance with a spectral correction function, in line with the standard.
+Macular pigment correction was not applied to the rhodopic and melanopic action spectra because rods are not present at the fovea and ipRGCs sit above the retinal pigment layer (\citeproc{ref-Trieschmann2007}{Trieschmann et al., 2007}).
+
+In the light flux experiment, the stimulus intensity was increased and decreased relative to the background, which we expected to modulate all photoreceptor classes (see Figure \ref{fig:spectraplots}e,i).
+In the L-M cone modulation experiment, we used silent substitution to increase the L-cone activity, and simultaneously decrease the M-cone activity, during the first half-cycle of the sine wave.
 In the second half-cycle the polarity of the modulation reversed (see Figure \ref{fig:spectraplots}f,j).
@@
 We assume that the activity of rods was constant at the high background luminance intensity used here, and so did not attempt to silence rod activity in any condition, as this would have greatly reduced the available dynamic range.
-Splatter on nominally silenced photoreceptors was very small (see Figure \ref{fig:spectraplots}j-l), well below the levels that would be expected to generate measureable pupil modulations.
+Splatter on nominally silenced photoreceptors was very small (see Figure \ref{fig:spectraplots}j-l), well below the levels that would be expected to generate measurable pupil modulations, although we can observe that the rods may not be saturated in the L-M and melanopsin-directed stimuli (Figure \ref{fig:spectraplots}j and \ref{fig:spectraplots}l) and could intrude in these two experiments.
 We also estimated activation of penumbral L and M cones (\citeproc{ref-Spitschan2015}{Spitschan et al., 2015}; \citeproc{ref-Barrionuevo2016}{Barrionuevo and Cao, 2016}; \citeproc{ref-Zele2019}{Zele et al., 2019}), which was minimal (\(\le 1.5%
@@
 
-To describe our data, we used the same model described in our previous study (\citeproc{ref-Segala2023}{Segala et al., 2023}).
+To quantitatively summarise our data, we used the same model described in our previous study (\citeproc{ref-Segala2023}{Segala et al., 2023}).
 The model has the same general form as the first stage of the contrast gain control model proposed by Meese et al.
@@
 Figure \ref{fig:spectraplots}m-p shows averaged waveforms of pupil diameter in response to binocular stimulation.
-For luminance stimuli (Figure \ref{fig:spectraplots}m) a strong modulation is apparent at the stimulation frequency (0.5Hz), which is also clear in the Fourier amplitude spectrum (Figure \ref{fig:spectraplots}q).
-For binocular stimulation of the L-M pathway, S-cone pathway and melanopsin pathway, pupil modulations were less than 10\% of the amplitude of the luminance modulation (note the change in y-axis scale for the Fourier spectra), but still apparent at 0.5Hz in the Fourier spectra (Figure \ref{fig:spectraplots}n-p).
-We also observed a second harmonic response (at 1Hz) for all conditions, which was weaker than the first harmonic for luminance and melanopsin stimulation, but stronger for L-M and S-cone stimulation.
+For light flux stimuli (Figure \ref{fig:spectraplots}m) a strong modulation is apparent at the stimulation frequency (0.5Hz), which is also clear in the Fourier amplitude spectrum (Figure \ref{fig:spectraplots}q).
+For binocular stimulation of the L-M pathway, S-cone pathway and melanopsin pathway, pupil modulations were less than 10\% of the amplitude of the light flux modulation (note the change in y-axis scale for the Fourier spectra), but still apparent at 0.5Hz in the Fourier spectra (Figure \ref{fig:spectraplots}n-p).
+We also observed a second harmonic response (at 1Hz) for all conditions, which was weaker than the first harmonic for light flux and melanopsin stimulation, but stronger for L-M and S-cone stimulation.
 The second harmonic is also apparent in the pupil waveforms shown in Figure \ref{fig:spectraplots}n-p.~Our main analysis therefore focuses on the amplitude of the pupil modulations at both the first and second harmonic frequencies across different stimulus conditions.
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{Figures/methodsfig}
+{\centering \includegraphics[width=0.8\linewidth]{Figures/methodsfigrods}
 
@@
 In each plot, the response to monocular stimulation is given by the red circles and typically increases monotonically as a function of stimulus (temporal) contrast.
-Relative to monocular stimulation, binocular stimulation led to higher response amplitudes, indicating a binocular facilitation effect, for the luminance and S-cone conditions (Figure \ref{fig:FirstHarmonicPlots}a,c), and to some extent for the melanopsin condition (Figure \ref{fig:FirstHarmonicPlots}d).
+Relative to monocular stimulation, binocular stimulation led to higher response amplitudes, indicating a binocular facilitation effect, for the light flux and S-cone conditions (Figure \ref{fig:FirstHarmonicPlots}a,c), and to some extent for the melanopsin condition (Figure \ref{fig:FirstHarmonicPlots}d).
 However, the L-M cone condition (Figure \ref{fig:FirstHarmonicPlots}b) produced a binocular suppression effect, where the response to binocular stimulation was weaker than the response to monocular stimulation (blue squares below red circles).
@@
 Our primary objective was to compare posterior distributions of the weight of interocular suppression, which are shown in Figure \ref{fig:FirstHarmonicPlots}e.
-Consistent with our earlier observations, the strongest suppressive weight corresponds to the L-M and Melanopsin conditions, and the weakest suppression corresponds to the luminance and S-cone conditions, with virtually no overlap between the posterior distributions for weak and strong suppression.
+Consistent with our earlier observations, the strongest suppressive weight corresponds to the L-M and Melanopsin conditions, and the weakest suppression corresponds to the light flux and S-cone conditions, with virtually no overlap between the posterior distributions for weak and strong suppression.
 The model fits were of good quality, as shown by the curves in Figure \ref{fig:FirstHarmonicPlots}a-d,f-i.
@@
 \midrule
-Luminance 1F & 95.77 & 0.00083 & 0.37 & 1.32 & 1.24 & 0.0905\\
+Light flux 1F & 95.77 & 0.00083 & 0.37 & 1.32 & 1.24 & 0.0905\\
 L-M cone 1F & 49.82 & 0.00109 & 1.71 & 1.50 & 1.21 & 0.0032\\
@@
 \midrule
-Luminance 2F & 48.81 & 0.00089 & 1.24 & 1.15 & 0.88 & 0.0039\\
+Light flux 2F & 48.81 & 0.00089 & 1.24 & 1.15 & 0.88 & 0.0039\\
 L-M cone 2F & 66.00 & 0.00075 & 0.95 & 1.10 & 0.82 & 0.0050\\
@@
 At the first harmonic, melanopsin and S-cone signals differed in phase by more than 90 degrees, though they were not fully in antiphase.
-The luminance and L-M responses were approximately in antiphase to each other, however this is likely due to our choice to modulate L+M- in the first half-cycle of the sine wave (corresponding to a luminance increase in the luminance condition), and L-M+ in the second half-cycle (corresponding to a luminance decrease in the luminance condition).
-Had we reversed this phase arrangement, we would likely have seen a close phase correspondence between the L-M and luminance conditions (another way to think about this is that L-cone decreases and M-cone increases are processed like luminance increases).
-Phase differences between the luminance, S-cone and melanopsin conditions are likely attributable to different lags in phototransduction at the earliest stage (i.e.~in the retina).
-At the second harmonic frequency (Figure \ref{fig:phaseplots}b), the luminance condition was again out of phase with the other three, and was approximately in quadrature phase with the L-M condition, and in antiphase with both the S-cone and melanopsin conditions (which were in phase with each other).
+The light flux and L-M responses were approximately in antiphase to each other, however this is likely due to our choice to modulate L+M- in the first half-cycle of the sine wave (corresponding to a luminance increase in the light flux condition), and L-M+ in the second half-cycle (corresponding to a luminance decrease in the light flux condition).
+Had we reversed this phase arrangement, we would likely have seen a close phase correspondence between the L-M and light flux conditions (another way to think about this is that L-cone decreases and M-cone increases are processed like luminance increases).
+Phase differences between the light flux, S-cone and melanopsin conditions are likely attributable to different lags in phototransduction at the earliest stage (i.e.~in the retina).
+At the second harmonic frequency (Figure \ref{fig:phaseplots}b), the light flux condition was again out of phase with the other three, and was approximately in quadrature phase with the L-M condition, and in antiphase with both the S-cone and melanopsin conditions (which were in phase with each other).
+We note that the marked phase differences between conditions make the possibility that our results are dominated by rod activity relatively unlikely (e.g.~in the L-M and melanopsin conditions, which have very different phase profiles).
 
@@
 
-\caption{Pupil phase plots at the first and second harmonic frequencies for the luminance, melanopsin, L-M pathway and the S-(L+M) pathway conditions.
+\caption{Pupil phase plots at the first and second harmonic frequencies for the light flux, melanopsin, L-M pathway and the S-cone pathway conditions.
 Panel (a) shows the pupil response at the first harmonic frequency during binocular stimulation.
@@
 The five data points for each pathway correspond to the five contrast levels displayed.
-In panel (a) the luminance amplitudes have been scaled down by a factor of 10 to enable comparison with the other conditions.}\label{fig:phaseplots}
+In panel (a) the light flux amplitudes have been scaled down by a factor of 10 to enable comparison with the other conditions.}\label{fig:phaseplots}
 \end{figure}
@@
 
-Our recent psychophysical work (\citeproc{ref-Baker2024}{Baker et al., 2024}) has looked at binocular interactions in the L-M and S-cone pathways, and compared these to the luminance pathway.
-Using a contrast discrimination paradigm with spatial modulations of luminance and colour, Baker et al.
+Our recent psychophysical work (\citeproc{ref-Baker2024}{Baker et al., 2024}) has looked at binocular interactions in the L-M and S-cone pathways, and compared these to the light flux pathway.
+Using a contrast discrimination paradigm with spatial modulations of light flux and colour, Baker et al.
 (\citeproc{ref-Baker2024}{2024}) found equally strong interocular suppression in all three pathways.
-This is rather different from our pupillometry results here, which demonstrate weaker suppression in the luminance and S-cone pathways than in the L-M pathway (see Figure \ref{fig:FirstHarmonicPlots}).
+This is rather different from our pupillometry results here, which demonstrate weaker suppression in the light flux and S-cone pathways than in the L-M pathway (see Figure \ref{fig:FirstHarmonicPlots}).
 However, the current experiments involve temporal modulations, which are quite distinct from the spatial modulations used in Baker et al.
@@
 This was strong (\(\omega \ge 1\)) for L-M and melanopsin signals at the first harmonic, and all pathways at the second harmonic.
-Suppression was weaker (\(\omega < 1\)) in the luminance pathway (consistent with previous work), and also for S-cone directed modulations.
+Suppression was weaker (\(\omega < 1\)) in the light flux pathway (consistent with previous work), and also for S-cone directed modulations.
 
@@
 \bibitem[\citeproctext]{ref-Baker2024}
-Baker DH, Hansford KJ, Segala FG, Morsi AY, Huxley RJ, Martin JT, Rockman M, Wade AR (2024) \href{https://doi.org/10.31234/osf.io/atsfh}{Binocular integration of chromatic and luminance signals}.
-Journal of Vision Under review.
+Baker DH, Hansford KJ, Segala FG, Morsi AY, Huxley RJ, Martin JT, Rockman M, Wade AR (2024) \href{https://doi.org/10.1167/jov.24.12.7}{Binocular integration of chromatic and luminance signals}.
+J Vis 24(12):7.
 
@@
 
+\bibitem[\citeproctext]{ref-Bone1988}
+Bone RA, Landrum JT, Fernandez L, Tarsis SL (1988) Analysis of the macular pigment by {HPLC}: Retinal distribution and age study. Investigative Ophthalmology \& Visual Science 29:843--849.
+
 \bibitem[\citeproctext]{ref-Busse2009}
@@
 Journal of Vision 2:1 Available at: \url{https://doi.org/10.1167/2.8.1} {[}Accessed June 5, 2023{]}.
+
+\bibitem[\citeproctext]{ref-CIE2006}
+CIE (2006) Fundamental chromaticity diagram with physiological axes. CIE Central Bureau. Available at: \url{https://cie.co.at/publications/fundamental-chromaticity-diagram-physiological-axes-part-1}.
+
+\bibitem[\citeproctext]{ref-CIE2018}
+CIE (2018) CIE system for metrology of optical radiation for ipRGC-influenced responses to light. CIE Central Bureau. Available at: \url{https://doi.org/10.25039/S026.2018}.
 
@@
 
+\bibitem[\citeproctext]{ref-Pokorny1987}
+Pokorny J, Smith VC, Lutze M (1987) Aging of the human lens. Applied Optics 26:1437 Available at: \url{http://dx.doi.org/10.1364/AO.26.001437}.
+
 \bibitem[\citeproctext]{ref-Provencio2000}
@@
 
+\bibitem[\citeproctext]{ref-Stockman1999}
+Stockman A, Sharpe LT, Fach C (1999) The spectral sensitivity of the human short-wavelength sensitive cones derived from thresholds and color matches.
+Vision Research 39:2901--2927 Available at: \url{https://www.sciencedirect.com/science/article/pii/S0042698998002259}.
+
+\bibitem[\citeproctext]{ref-Trieschmann2007}
+Trieschmann M, Kuijk FJGM van, Alexander R, Hermans P, Luthert P, Bird AC, Pauleikhoff D (2007) Macular pigment in the human retina: Histological evaluation of localization and distribution.
+Eye 22:132--137 Available at: \url{http://dx.doi.org/10.1038/sj.eye.6702780}.
+
 \bibitem[\citeproctext]{ref-Woelders2018}
@@
 
+\section{Supplementary material}\label{supplementary-material}
+
+\setcounter{table}{0} \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}
+
+\begin{figure}
+
+{\centering \includegraphics{Figures/SuppFig1}
+
+}
+
+\caption{Linearity of primaries for each device.
+The calibration measures were summed (i.e., total unweighted irradiance), and the input-output relationship summarised by a 7th order polynomial reverse curve fit.
+By applying the coefficients of the regression, it is possible to achieve a linear output in the primaries.}\label{fig:primarylinearity}
+\end{figure}
+
 \end{document}

### 2025-01-14 manuscript.Rmd
Added high resolution supplementary figure

@@
 
-Number of pages: 21
-
-Number of figures: 4
-
-Number of tables: 1
-
-Number of words for abstract: 187/250
-
-Number of words for introduction: 634/650
-
-Number of words for discussion: 600/1500
-
-Conflict of interest: The authors declare no competing financial interests.
-
-Acknowledgements: Supported by Biotechnology and Biological Sciences Research Council grant BB/V007580/1 awarded to DHB and ARW.
-
-\pagebreak
-
 ```{r individualanalyses, include=FALSE, results='hide'}
@@
 
+# Acknowledgements
+
+Supported by Biotechnology and Biological Sciences Research Council grant BB/V007580/1 awarded to DHB and ARW.
+
+# Declaration of interests
+
+The authors declare no competing interests.
+
 # References
@@
 <div id='refs'> </div>
+
+\pagebreak
 
@@
 
-knitr::include_graphics(paste0(figdir,'SuppFig1.pdf'))
+knitr::include_graphics(paste0(figdir,'gamma_figure.pdf'))
 

### 2025-01-14 manuscript.tex
Added high resolution supplementary figure

--- 2024-08-05 manuscript.tex
@@
 \setcounter{secnumdepth}{5}
-\usepackage{caption} \usepackage{setspace}\doublespacing \usepackage{lineno} \linenumbers
+\usepackage{caption} \usepackage{setspace}\doublespacing \usepackage{lineno} \linenumbers \newcommand{\beginsupplement}{\setcounter{table}{0} \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
 \usepackage{booktabs}
@@
 
-Number of pages: 21
-
-Number of figures: 4
-
-Number of tables: 1
-
-Number of words for abstract: 187/250
-
-Number of words for introduction: 634/650
-
-Number of words for discussion: 600/1500
-
-Conflict of interest: The authors declare no competing financial interests.
-
-Acknowledgements: Supported by Biotechnology and Biological Sciences Research Council grant BB/V007580/1 awarded to DHB and ARW.
-
-\pagebreak
-
 \hypertarget{abstract}{%
@@
 For pattern vision, binocular summation occurs at threshold, such that a lower contrast is required to detect a target shown to both eyes than a target shown to one eye (Campbell and Green, \protect\hyperlink{ref-Campbell1965}{1965}; Baker et al., \protect\hyperlink{ref-Baker2018}{2018}).
-At higher contrasts, a process of `ocularity invariance' is observed, in which the response to monocularly- and binocularly-presented patterns is equal (Baker et al., \protect\hyperlink{ref-Baker2007}{2007}; Moradi and Heeger, \protect\hyperlink{ref-Moradi2009}{2009}).
+At higher contrasts, the phenomenon of `ocularity invariance' is observed, in which the response to monocularly- and binocularly-presented patterns is equal (Baker et al., \protect\hyperlink{ref-Baker2007}{2007}; Moradi and Heeger, \protect\hyperlink{ref-Moradi2009}{2009}).
 This is explained by a process of interocular suppression that cancels out the additional excitatory drive caused by stimulating two eyes.
 Our recent work (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}) showed that cortical signal combination for luminance flicker is substantially more linear than for spatial patterns, whereas there is evidence of interocular suppression in the pupil pathway.
-Here we measure the amplitude of pupil modulations in response to flickering stimuli directed at the luminance, L-M cone, S-cone, and melanopsin pathways (see Figure \ref{fig:spectraplots}e-l).
+Here we measure the amplitude of pupil modulations in response to flickering stimuli presented as light flux, or directed towards the L-M cone, S-cone, and melanopsin pathways (see Figure \ref{fig:spectraplots}e-l).
 Our key comparisons are between monocular and binocular stimulation, and in a dichoptic masking condition where the two eyes are stimulated at different frequencies.
@@
 
-To present synchronised stimulus modulations independently to each eye, two light engines (SpectraTuneLAB: LEDMOTIVE Technologies, LLC, Barcelona, Spain), each with 10 independently addressable LED colour channels, were integrated into a customised binocular viewing system.
+To present synchronised stimulus modulations independently to each eye, two light engines (SpectraTuneLAB, which are thermally stable across time with active cooling according to the manufacturers: LEDMOTIVE Technologies, LLC, Barcelona, Spain), each with 10 independently addressable LED colour channels, were integrated into a customised binocular viewing system.
 The light engines were operated via a Python interface to their REST API (Martin et al., \protect\hyperlink{ref-Martin2022}{2022}), which supports synchronous launch and playback of spectral sequences prepared in advance and stored in JSON format.
+A special command was commissioned from LEDMOTIVE to allow two different stimulus files to be launched simultaneously from the two devices.
+The synchronisation of the spectra from the two devices was tested and showed that they were synchronised to within approximately 3ms.
+
 When preparing the spectral sequences, the age of participants was used to account for the yellowing of the lenses.
@@
 The outputs of the two light engines (see Figure \ref{fig:spectraplots}b,c) were calibrated using an Ocean Optics Jaz spectroradiometer, which was wavelength-calibrated to an Argon lamp and intensity calibrated using a NIST-traceable light source.
+Each primary was also linearized using a polynomial fit (see Figure \ref{fig:primarylinearity} for details).
 We used the Stockman and Sharpe (\protect\hyperlink{ref-Stockman2000}{2000}) 10-degree cone fundamentals, and estimates of melanopsin absorbance spectra from CIE S 026 (discussed in Martin et al., \protect\hyperlink{ref-Martin2023}{2023}) to calculate \(\alpha\)-opic irradiance.
@@
 The use of this set up allowed us to modulate the stimuli in three different ocular configurations, similar to the ones we used in our previous study (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}): monocular, binocular and dichoptic.
-In the monocular configuration, the unstimulated eye still saw a non-flickering disc of mean luminance.
+In the monocular configuration, the unstimulated eye still saw a non-flickering disc of mean light flux.
 A schematic of the stimulation system is shown in Figure \ref{fig:spectraplots}a.
@@
 
-In the luminance experiment, the stimulus intensity was increased and decreased relative to the background, which we expected to modulate all photoreceptor classes (see Figure \ref{fig:spectraplots}e,i).
-In the L-M cone modulation experiment, we used silent substution to increase the L-cone activity, and simultaneously decrease the M-cone activity, during the first half-cycle of the sine wave.
+Silent substitution stimuli were prepared and calibrated for each participant with custom Python software (Martin et al., \protect\hyperlink{ref-Martin2023}{2023}) and Python scripts.
+Estimates of photoreceptor spectral sensitivities for each participant were constructed from the known photopigment absorbance spectra (Stockman and Sharpe, \protect\hyperlink{ref-Stockman2000}{2000}), taking account of the peak axial density of the respective photopigments, as well as lens (Pokorny et al., \protect\hyperlink{ref-Pokorny1987}{1987}; Stockman et al., \protect\hyperlink{ref-Stockman1999}{1999}; Stockman and Sharpe, \protect\hyperlink{ref-Stockman2000}{2000}) and macular pigment density (Bone et al., \protect\hyperlink{ref-Bone1988}{1988}; Stockman et al., \protect\hyperlink{ref-Stockman1999}{1999}), in accordance with the field size and age-dependant CIEPO06 observer model (CIE, \protect\hyperlink{ref-CIE2006}{2006}).
+The melanopic and rhodopic action spectra of the 32-year-old standard observer were taken from CIE S 026 (CIE, \protect\hyperlink{ref-CIE2018}{2018}) and then adjusted for age-related lens transmittance with a spectral correction function, in line with the standard.
+Macular pigment correction was not applied to the rhodopic and melanopic action spectra because rods are not present at the fovea and ipRGCs sit above the retinal pigment layer (Trieschmann et al., \protect\hyperlink{ref-Trieschmann2007}{2007}).
+
+In the light flux experiment, the stimulus intensity was increased and decreased relative to the background, which we expected to modulate all photoreceptor classes (see Figure \ref{fig:spectraplots}e,i).
+In the L-M cone modulation experiment, we used silent substitution to increase the L-cone activity, and simultaneously decrease the M-cone activity, during the first half-cycle of the sine wave.
 In the second half-cycle the polarity of the modulation reversed (see Figure \ref{fig:spectraplots}f,j).
@@
 We assume that the activity of rods was constant at the high background luminance intensity used here, and so did not attempt to silence rod activity in any condition, as this would have greatly reduced the available dynamic range.
-Splatter on nominally silenced photoreceptors was very small (see Figure \ref{fig:spectraplots}j-l), well below the levels that would be expected to generate measureable pupil modulations.
+Splatter on nominally silenced photoreceptors was very small (see Figure \ref{fig:spectraplots}j-l), well below the levels that would be expected to generate measurable pupil modulations, although we can observe that the rods may not be saturated in the L-M and melanopsin-directed stimuli (Figure \ref{fig:spectraplots}j and \ref{fig:spectraplots}l) and could intrude in these two experiments.
 We also estimated activation of penumbral L and M cones (Spitschan et al., \protect\hyperlink{ref-Spitschan2015}{2015}; Barrionuevo and Cao, \protect\hyperlink{ref-Barrionuevo2016}{2016}; Zele et al., \protect\hyperlink{ref-Zele2019}{2019}), which was minimal (\(\le 1.5%
@@
 
-To describe our data, we used the same model described in our previous study (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}).
+To quantitatively summarise our data, we used the same model described in our previous study (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}).
 The model has the same general form as the first stage of the contrast gain control model proposed by Meese et al.
@@
 
-Our recent psychophysical work (Baker et al., \protect\hyperlink{ref-Baker2024}{2024}) has looked at binocular interactions in the L-M and S-cone pathways, and compared these to the luminance pathway.
-Using a contrast discrimination paradigm with spatial modulations of luminance and colour, Baker et al.
+Our recent psychophysical work (Baker et al., \protect\hyperlink{ref-Baker2024}{2024}) has looked at binocular interactions in the L-M and S-cone pathways, and compared these to the light flux pathway.
+Using a contrast discrimination paradigm with spatial modulations of light flux and colour, Baker et al.
 (\protect\hyperlink{ref-Baker2024}{2024}) found equally strong interocular suppression in all three pathways.
-This is rather different from our pupillometry results here, which demonstrate weaker suppression in the luminance and S-cone pathways than in the L-M pathway (see Figure \ref{fig:FirstHarmonicPlots}).
+This is rather different from our pupillometry results here, which demonstrate weaker suppression in the light flux and S-cone pathways than in the L-M pathway (see Figure \ref{fig:FirstHarmonicPlots}).
 However, the current experiments involve temporal modulations, which are quite distinct from the spatial modulations used in Baker et al.
@@
 This was strong (\(\omega \ge 1\)) for L-M and melanopsin signals at the first harmonic, and all pathways at the second harmonic.
-Suppression was weaker (\(\omega < 1\)) in the luminance pathway (consistent with previous work), and also for S-cone directed modulations.
+Suppression was weaker (\(\omega < 1\)) in the light flux pathway (consistent with previous work), and also for S-cone directed modulations.
+
+\hypertarget{acknowledgements}{%
+\section{Acknowledgements}\label{acknowledgements}}
+
+Supported by Biotechnology and Biological Sciences Research Council grant BB/V007580/1 awarded to DHB and ARW.
+
+\hypertarget{declaration-of-interests}{%
+\section{Declaration of interests}\label{declaration-of-interests}}
+
+The authors declare no competing interests.
 
@@
 \leavevmode\hypertarget{ref-Baker2024}{}%
-Baker DH, Hansford KJ, Segala FG, Morsi AY, Huxley RJ, Martin JT, Rockman M, Wade AR (2024) Binocular integration of chromatic and luminance signals. Journal of Vision Under review.
+Baker DH, Hansford KJ, Segala FG, Morsi AY, Huxley RJ, Martin JT, Rockman M, Wade AR (2024) Binocular integration of chromatic and luminance signals. J Vis 24(12):7.
 
@@
 
+\leavevmode\hypertarget{ref-Bone1988}{}%
+Bone RA, Landrum JT, Fernandez L, Tarsis SL (1988) Analysis of the macular pigment by HPLC: Retinal distribution and age study. Investigative Ophthalmology \& Visual Science 29:843--849.
+
 \leavevmode\hypertarget{ref-Busse2009}{}%
@@
 Journal of Vision 2:1 Available at: \url{https://doi.org/10.1167/2.8.1} {[}Accessed June 5, 2023{]}.
+
+\leavevmode\hypertarget{ref-CIE2006}{}%
+CIE (2006) Fundamental chromaticity diagram with physiological axes. CIE Central Bureau. Available at: \url{https://cie.co.at/publications/fundamental-chromaticity-diagram-physiological-axes-part-1}.
+
+\leavevmode\hypertarget{ref-CIE2018}{}%
+CIE (2018) CIE system for metrology of optical radiation for ipRGC-influenced responses to light. CIE Central Bureau. Available at: \url{https://doi.org/10.25039/S026.2018}.
 
@@
 
+\leavevmode\hypertarget{ref-Pokorny1987}{}%
+Pokorny J, Smith VC, Lutze M (1987) Aging of the human lens. Applied Optics 26:1437 Available at: \url{http://dx.doi.org/10.1364/AO.26.001437}.
+
 \leavevmode\hypertarget{ref-Provencio2000}{}%
@@
 
+\leavevmode\hypertarget{ref-Stockman1999}{}%
+Stockman A, Sharpe LT, Fach C (1999) The spectral sensitivity of the human short-wavelength sensitive cones derived from thresholds and color matches.
+Vision Research 39:2901--2927 Available at: \url{https://www.sciencedirect.com/science/article/pii/S0042698998002259}.
+
+\leavevmode\hypertarget{ref-Trieschmann2007}{}%
+Trieschmann M, Kuijk FJGM van, Alexander R, Hermans P, Luthert P, Bird AC, Pauleikhoff D (2007) Macular pigment in the human retina: Histological evaluation of localization and distribution.
+Eye 22:132--137 Available at: \url{http://dx.doi.org/10.1038/sj.eye.6702780}.
+
 \leavevmode\hypertarget{ref-Woelders2018}{}%
@@
 
+\pagebreak
+
+\hypertarget{supplementary-material}{%
+\section{Supplementary material}\label{supplementary-material}}
+
+\setcounter{table}{0} \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}
+
+\begin{figure}
+
+{\centering \includegraphics{Figures/gamma_figure}
+
+}
+
+\caption{Linearity of primaries for each device.
+The calibration measures were summed (i.e., total unweighted irradiance), and the input-output relationship summarised by a 7th order polynomial reverse curve fit.
+By applying the coefficients of the regression, it is possible to achieve a linear output in the primaries.}\label{fig:primarylinearity}
+\end{figure}
+
 \end{document}

### 2025-02-06 manuscript.Rmd
Removed significance statement and modified figure 1 so that (d) now shows.

@@
 
-pdf(paste0(figdir,"methodsfigrods.pdf"), bg="transparent", height = 13, width = 12)
+pdf(paste0(figdir,"methodsfigrods1.pdf"), bg="transparent", height = 13, width = 12)
 
@@
 
-text(5.5,14,'(d)',pos=4,cex=2)
+text(4.5,14,'(d)',pos=4,cex=2)
 
@@
 
-# Significance statement
-
-Pupil diameters are determined by a network of subcortical nuclei that must combine incoming light levels across the two eyes, independently of cortical visual areas.
-We investigated the algorithmic properties of this binocular combination process for the first time.
-Using silent subsitution, we targeted different post-retinal pathways (light flux, L-M cones, S-cones, and melanopsin) with flickering stimuli generated by a novel binocular multi-primary system.
-We found different patterns of binocular combination across pathways, and also differences in the phase of the pupil response.
-The results were well described by a computational model of binocular signal combination, in which the weight of suppression between the eyes differed across pathways.
-This elucidates the algorithm governing binocular combination in the autonomic nervous system.
-
 # Introduction

### 2025-02-06 manuscript.tex
Removed significance statement and modified figure 1 so that (d) now shows.

@@
 This work demonstrates for the first time the algorithm governing binocular combination in the autonomic nervous system.
-
-\hypertarget{significance-statement}{%
-\section{Significance statement}\label{significance-statement}}
-
-Pupil diameters are determined by a network of subcortical nuclei that must combine incoming light levels across the two eyes, independently of cortical visual areas.
-We investigated the algorithmic properties of this binocular combination process for the first time.
-Using silent subsitution, we targeted different post-retinal pathways (light flux, L-M cones, S-cones, and melanopsin) with flickering stimuli generated by a novel binocular multi-primary system.
-We found different patterns of binocular combination across pathways, and also differences in the phase of the pupil response.
-The results were well described by a computational model of binocular signal combination, in which the weight of suppression between the eyes differed across pathways.
-This elucidates the algorithm governing binocular combination in the autonomic nervous system.
 

### 2025-02-10 manuscript.Rmd
Small change to add reference to thesis

@@
 linkcolor: black
-csl: the-journal-of-neuroscience.csl
+csl: elife.csl
 header-includes:
@@
 The results are interpreted using a contemporary model of binocular vision [@Meese2006] implemented within a hierarchical Bayesian framework.
+These results previously formed part of a doctoral thesis by the first author [@SegalaThesis2023].
 

### 2025-02-10 manuscript.tex
Small change to add reference to thesis

@@
 
-Different classes of retinal photoreceptors, including cones, rods and melanopsin-containing intrinsically photosensitive retinal ganglion cells (ipRGCs), are directly involved in controlling and maintaining the size of the pupils (e.g.~McDougal and Gamlin, \protect\hyperlink{ref-McDougal2010}{2010}; Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}; Barrionuevo and Cao, \protect\hyperlink{ref-Barrionuevo2016}{2016}; Murray et al., \protect\hyperlink{ref-Murray2018}{2018}; Woelders et al., \protect\hyperlink{ref-Woelders2018}{2018}).
+Different classes of retinal photoreceptors, including cones, rods and melanopsin-containing intrinsically photosensitive retinal ganglion cells (ipRGCs), are directly involved in controlling and maintaining the size of the pupils (e.g.~McDougal and Gamlin, \protect\hyperlink{ref-McDougal2010}{2010}; Barrionuevo and Cao, \protect\hyperlink{ref-Barrionuevo2016}{2016}; Murray et al., \protect\hyperlink{ref-Murray2018}{2018}; Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}; Woelders et al., \protect\hyperlink{ref-Woelders2018}{2018}).
 Cones drive the initial rapid constriction of the pupils (Mathôt, \protect\hyperlink{ref-Mathot2018}{2018}), while the slower and longer activation of the ipRGCs maintains constriction over a prolonged period of time and regulates the post-illumination pupillary response (Markwell et al., \protect\hyperlink{ref-Markwell2010}{2010}; McDougal and Gamlin, \protect\hyperlink{ref-McDougal2010}{2010}).
@@
 Binocular combination has been extensively studied in visual perception, where it is mediated by neurons in primary visual cortex (Hubel and Wiesel, \protect\hyperlink{ref-Hubel1962}{1962}).
-For pattern vision, binocular summation occurs at threshold, such that a lower contrast is required to detect a target shown to both eyes than a target shown to one eye (Campbell and Green, \protect\hyperlink{ref-Campbell1965}{1965}; Baker et al., \protect\hyperlink{ref-Baker2018}{2018}).
+For pattern vision, binocular summation occurs at threshold, such that a lower contrast is required to detect a target shown to both eyes than a target shown to one eye (Baker et al., \protect\hyperlink{ref-Baker2018}{2018}; Campbell and Green, \protect\hyperlink{ref-Campbell1965}{1965}).
 At higher contrasts, the phenomenon of `ocularity invariance' is observed, in which the response to monocularly- and binocularly-presented patterns is equal (Baker et al., \protect\hyperlink{ref-Baker2007}{2007}; Moradi and Heeger, \protect\hyperlink{ref-Moradi2009}{2009}).
@@
 The results are interpreted using a contemporary model of binocular vision (Meese et al., \protect\hyperlink{ref-Meese2006}{2006}) implemented within a hierarchical Bayesian framework.
+These results previously formed part of a doctoral thesis by the first author (Segala, \protect\hyperlink{ref-SegalaThesis2023}{2023}).
 
@@
 The diffuser discs were positioned in the objective planes of the lenses of a modified VR headset (SHINECON SC-G01, Dongguan Shinecon Industrial Co.~Ltd., Guangdong, China), which was used by the participants to view the stimuli.
-The stimuli were two discs of flickering light with a diameter of approximately 30 degrees, which were fused together into a cyclopean percept resembling a donut-shaped ring of light, similar to that used in other studies (e.g., Barrionuevo and Cao, \protect\hyperlink{ref-Barrionuevo2016}{2016}; Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}, \protect\hyperlink{ref-Spitschan2015}{2015}; Murray et al., \protect\hyperlink{ref-Murray2018}{2018}; Zele et al., \protect\hyperlink{ref-Zele2018}{2018}).
+The stimuli were two discs of flickering light with a diameter of approximately 30 degrees, which were fused together into a cyclopean percept resembling a donut-shaped ring of light, similar to that used in other studies (e.g., Barrionuevo and Cao, \protect\hyperlink{ref-Barrionuevo2016}{2016}; Murray et al., \protect\hyperlink{ref-Murray2018}{2018}; Spitschan et al., \protect\hyperlink{ref-Spitschan2015}{2015}, \protect\hyperlink{ref-Spitschan2014}{2014}; Zele et al., \protect\hyperlink{ref-Zele2018}{2018}).
 The VR headset modifications allowed for small adjustments to account for individual differences in interpupillary distance and focal length.
@@
 Silent substitution stimuli were prepared and calibrated for each participant with custom Python software (Martin et al., \protect\hyperlink{ref-Martin2023}{2023}) and Python scripts.
-Estimates of photoreceptor spectral sensitivities for each participant were constructed from the known photopigment absorbance spectra (Stockman and Sharpe, \protect\hyperlink{ref-Stockman2000}{2000}), taking account of the peak axial density of the respective photopigments, as well as lens (Pokorny et al., \protect\hyperlink{ref-Pokorny1987}{1987}; Stockman et al., \protect\hyperlink{ref-Stockman1999}{1999}; Stockman and Sharpe, \protect\hyperlink{ref-Stockman2000}{2000}) and macular pigment density (Bone et al., \protect\hyperlink{ref-Bone1988}{1988}; Stockman et al., \protect\hyperlink{ref-Stockman1999}{1999}), in accordance with the field size and age-dependant CIEPO06 observer model (CIE, \protect\hyperlink{ref-CIE2006}{2006}).
+Estimates of photoreceptor spectral sensitivities for each participant were constructed from the known photopigment absorbance spectra (Stockman and Sharpe, \protect\hyperlink{ref-Stockman2000}{2000}), taking account of the peak axial density of the respective photopigments, as well as lens (Pokorny et al., \protect\hyperlink{ref-Pokorny1987}{1987}; Stockman and Sharpe, \protect\hyperlink{ref-Stockman2000}{2000}; Stockman et al., \protect\hyperlink{ref-Stockman1999}{1999}) and macular pigment density (Bone et al., \protect\hyperlink{ref-Bone1988}{1988}; Stockman et al., \protect\hyperlink{ref-Stockman1999}{1999}), in accordance with the field size and age-dependant CIEPO06 observer model (CIE, \protect\hyperlink{ref-CIE2006}{2006}).
 The melanopic and rhodopic action spectra of the 32-year-old standard observer were taken from CIE S 026 (CIE, \protect\hyperlink{ref-CIE2018}{2018}) and then adjusted for age-related lens transmittance with a spectral correction function, in line with the standard.
@@
 Splatter on nominally silenced photoreceptors was very small (see Figure \ref{fig:spectraplots}j-l), well below the levels that would be expected to generate measurable pupil modulations, although we can observe that the rods may not be saturated in the L-M and melanopsin-directed stimuli (Figure \ref{fig:spectraplots}j and \ref{fig:spectraplots}l) and could intrude in these two experiments.
-We also estimated activation of penumbral L and M cones (Spitschan et al., \protect\hyperlink{ref-Spitschan2015}{2015}; Barrionuevo and Cao, \protect\hyperlink{ref-Barrionuevo2016}{2016}; Zele et al., \protect\hyperlink{ref-Zele2019}{2019}), which was minimal (\(\le 1.5%
+We also estimated activation of penumbral L and M cones (Barrionuevo and Cao, \protect\hyperlink{ref-Barrionuevo2016}{2016}; Spitschan et al., \protect\hyperlink{ref-Spitschan2015}{2015}; Zele et al., \protect\hyperlink{ref-Zele2019}{2019}), which was minimal (\(\le 1.5%
 \) contrast; less than splatter on the open-field cones) for melanopsin-directed stimuli.
@@
 Pupil responses to binocular temporal contrast modulations were examined in a factorial design that combined six ocular conditions and five temporal contrast levels: 6, 12, 24, 48 and 96\% of the available dynamic range.
-This design, similar to that used in our previous studies (Baker and Wade, \protect\hyperlink{ref-Baker2017}{2017}; Baker et al., \protect\hyperlink{ref-Baker2020}{2020}; Segala et al., \protect\hyperlink{ref-Segala2023}{2023}), was applied in four separate experiments, each with a different mode of photoreceptor stimulation.
+This design, similar to that used in our previous studies (Baker et al., \protect\hyperlink{ref-Baker2020}{2020}; Baker and Wade, \protect\hyperlink{ref-Baker2017}{2017}; Segala et al., \protect\hyperlink{ref-Segala2023}{2023}), was applied in four separate experiments, each with a different mode of photoreceptor stimulation.
 In the first three conditions, the discs flickered at 0.5 Hz, in either a monocular, binocular or dichoptic arrangement.
@@
 \leavevmode\hypertarget{ref-Baker2021}{}%
-Baker DH (2021) Statistical analysis of periodic data in neuroscience. Neurons, Behavior, Data analysis, and Theory 5 Available at: \url{https://doi.org/10.51628\%2F001c.27680}.
+Baker DH.
+2021.
+Statistical analysis of periodic data in neuroscience.
+\emph{Neurons, Behavior, Data analysis, and Theory} \textbf{5}.
+doi:\href{https://doi.org/10.51628/001c.27680}{10.51628/001c.27680}
 
 \leavevmode\hypertarget{ref-Baker2024}{}%
-Baker DH, Hansford KJ, Segala FG, Morsi AY, Huxley RJ, Martin JT, Rockman M, Wade AR (2024) Binocular integration of chromatic and luminance signals. J Vis 24(12):7.
+Baker DH, Hansford KJ, Segala FG, Morsi AY, Huxley RJ, Martin JT, Rockman M, Wade AR.
+2024.
+Binocular integration of chromatic and luminance signals.
+\emph{J Vis} \textbf{24(12)}:7.
+doi:\href{https://doi.org/10.1167/jov.24.12.7}{10.1167/jov.24.12.7}
 
 \leavevmode\hypertarget{ref-Baker2018}{}%
-Baker DH, Lygo FA, Meese TS, Georgeson MA (2018) Binocular summation revisited: Beyond \(\sqrt{2}\). Psychol Bull 144:1186--1199.
+Baker DH, Lygo FA, Meese TS, Georgeson MA.
+2018.
+Binocular summation revisited: Beyond \(\sqrt{2}\).
+\emph{Psychol Bull} \textbf{144}:1186--1199.
+doi:\href{https://doi.org/10.1037/bul0000163}{10.1037/bul0000163}
 
 \leavevmode\hypertarget{ref-Baker2007}{}%
-Baker DH, Meese TS, Georgeson MA (2007) Binocular interaction: Contrast matching and contrast discrimination are predicted by the same model. Spat Vis 20:397--413.
+Baker DH, Meese TS, Georgeson MA.
+2007.
+Binocular interaction: Contrast matching and contrast discrimination are predicted by the same model.
+\emph{Spat Vis} \textbf{20}:397--413.
+doi:\href{https://doi.org/10.1163/156856807781503622}{10.1163/156856807781503622}
 
 \leavevmode\hypertarget{ref-Baker2020}{}%
-Baker DH, Vilidaite G, McClarnon E, Valkova E, Bruno A, Millman RE (2020) Binaural summation of amplitude modulation involves weak interaural suppression. Sci Rep 10:3560.
+Baker DH, Vilidaite G, McClarnon E, Valkova E, Bruno A, Millman RE.
+2020.
+Binaural summation of amplitude modulation involves weak interaural suppression.
+\emph{Sci Rep} \textbf{10}:3560.
+doi:\href{https://doi.org/10.1038/s41598-020-60602-5}{10.1038/s41598-020-60602-5}
 
 \leavevmode\hypertarget{ref-Baker2017}{}%
-Baker DH, Wade AR (2017) Evidence for an optimal algorithm underlying signal combination in human visual cortex. Cereb Cortex 27:254--264.
+Baker DH, Wade AR.
+2017.
+Evidence for an optimal algorithm underlying signal combination in human visual cortex.
+\emph{Cereb Cortex} \textbf{27}:254--264.
+doi:\href{https://doi.org/10.1093/cercor/bhw395}{10.1093/cercor/bhw395}
 
 \leavevmode\hypertarget{ref-Barrionuevo2016}{}%
-Barrionuevo PA, Cao D (2016) Luminance and chromatic signals interact differently with melanopsin activation to control the pupil light response. Journal of Vision 16(11):29.
+Barrionuevo PA, Cao D.
+2016.
+Luminance and chromatic signals interact differently with melanopsin activation to control the pupil light response.
+\emph{Journal of Vision} \textbf{16(11)}:29.
+doi:\href{https://doi.org/10.1167/16.11.29}{10.1167/16.11.29}
 
 \leavevmode\hypertarget{ref-Bone1988}{}%
-Bone RA, Landrum JT, Fernandez L, Tarsis SL (1988) Analysis of the macular pigment by HPLC: Retinal distribution and age study. Investigative Ophthalmology \& Visual Science 29:843--849.
+Bone RA, Landrum JT, Fernandez L, Tarsis SL.
+1988.
+Analysis of the macular pigment by HPLC: Retinal distribution and age study.
+\emph{Investigative Ophthalmology \& Visual Science} \textbf{29}:843--849.
 
 \leavevmode\hypertarget{ref-Busse2009}{}%
-Busse L, Wade AR, Carandini M (2009) Representation of concurrent stimuli by population activity in visual cortex. Neuron 64:931--942.
+Busse L, Wade AR, Carandini M.
+2009.
+Representation of concurrent stimuli by population activity in visual cortex.
+\emph{Neuron} \textbf{64}:931--42.
+doi:\href{https://doi.org/10.1016/j.neuron.2009.11.004}{10.1016/j.neuron.2009.11.004}
 
 \leavevmode\hypertarget{ref-Campbell1965}{}%
-Campbell FW, Green DG (1965) Monocular versus binocular visual acuity. Nature 208:191--192.
+Campbell FW, Green DG. 1965. Monocular versus binocular visual acuity. \emph{Nature} \textbf{208}:191--2. doi:\href{https://doi.org/10.1038/208191a0}{10.1038/208191a0}
 
 \leavevmode\hypertarget{ref-Carpenter2017}{}%
-Carpenter B, Gelman A, Hoffman MD, Lee D, Goodrich B, Betancourt M, Brubaker MA, Guo J, Li P, Riddell A (2017) Stan: A probabilistic programming language. J Stat Softw 76.
+Carpenter B, Gelman A, Hoffman MD, Lee D, Goodrich B, Betancourt M, Brubaker MA, Guo J, Li P, Riddell A.
+2017.
+Stan: A probabilistic programming language.
+\emph{J Stat Softw} \textbf{76}.
+doi:\href{https://doi.org/10.18637/jss.v076.i01}{10.18637/jss.v076.i01}
 
 \leavevmode\hypertarget{ref-Carroll2002}{}%
-Carroll J, Neitz J, Neitz M (2002) Estimates of L:M cone ratio from ERG flicker photometry and genetics.
-Journal of Vision 2:1 Available at: \url{https://doi.org/10.1167/2.8.1} {[}Accessed June 5, 2023{]}.
+Carroll J, Neitz J, Neitz M. 2002. Estimates of L:M cone ratio from ERG flicker photometry and genetics. \emph{Journal of Vision} \textbf{2}:1. doi:\href{https://doi.org/10.1167/2.8.1}{10.1167/2.8.1}
+
+\leavevmode\hypertarget{ref-CIE2018}{}%
+CIE. 2018. CIE system for metrology of optical radiation for ipRGC-influenced responses to light. CIE Central Bureau. doi:\href{https://doi.org/10.25039/S026.2018}{10.25039/S026.2018}
 
 \leavevmode\hypertarget{ref-CIE2006}{}%
-CIE (2006) Fundamental chromaticity diagram with physiological axes. CIE Central Bureau. Available at: \url{https://cie.co.at/publications/fundamental-chromaticity-diagram-physiological-axes-part-1}.
-
-\leavevmode\hypertarget{ref-CIE2018}{}%
-CIE (2018) CIE system for metrology of optical radiation for ipRGC-influenced responses to light. CIE Central Bureau. Available at: \url{https://doi.org/10.25039/S026.2018}.
+CIE. 2006. Fundamental chromaticity diagram with physiological axes. CIE Central Bureau.
 
 \leavevmode\hypertarget{ref-Dacey2003}{}%
-Dacey DM, Peterson BB, Robinson FR, Gamlin PD (2003) Fireworks in the primate retina: In vitro photodynamics reveals diverse lgn-projecting ganglion cell types.
-Neuron 37:15--27 Available at: \url{https://www.sciencedirect.com/science/article/pii/S0896627302011431}.
+Dacey DM, Peterson BB, Robinson FR, Gamlin PD.
+2003.
+Fireworks in the primate retina: In vitro photodynamics reveals diverse lgn-projecting ganglion cell types.
+\emph{Neuron} \textbf{37}:15--27.
+doi:\href{https://doi.org/https://doi.org/10.1016/S0896-6273(02)01143-1}{https://doi.org/10.1016/S0896-6273(02)01143-1}
 
 \leavevmode\hypertarget{ref-Estevez1982}{}%
-Estévez O, Spekreijse H (1982) The "silent substitution" method in visual research.
-Vision Research 22:681--691 Available at: \url{https://www.sciencedirect.com/science/article/pii/0042698982901043} {[}Accessed July 18, 2023{]}.
+Estévez O, Spekreijse H.
+1982.
+The "silent substitution" method in visual research.
+\emph{Vision Research} \textbf{22}:681--691.
+doi:\href{https://doi.org/10.1016/0042-6989(82)90104-3}{10.1016/0042-6989(82)90104-3}
 
 \leavevmode\hypertarget{ref-Gamlin2007}{}%
-Gamlin PDR, McDougal DH, Pokorny J, Smith VC, Yau K-W, Dacey DM (2007) Human and macaque pupil responses driven by melanopsin-containing retinal ganglion cells.
-Vision Research 47:946--954 Available at: \url{https://www.sciencedirect.com/science/article/pii/S0042698906005682} {[}Accessed July 18, 2023{]}.
+Gamlin PDR, McDougal DH, Pokorny J, Smith VC, Yau K-W, Dacey DM.
+2007.
+Human and macaque pupil responses driven by melanopsin-containing retinal ganglion cells.
+\emph{Vision Research} \textbf{47}:946--954.
+doi:\href{https://doi.org/10.1016/j.visres.2006.12.015}{10.1016/j.visres.2006.12.015}
 
 \leavevmode\hypertarget{ref-Hofer2005}{}%
-Hofer H, Carroll J, Neitz J, Neitz M, Williams DR (2005) Organization of the human trichromatic cone mosaic.
-The Journal of Neuroscience 25:9669--9679 Available at: \url{https://doi.org/10.1523\%2Fjneurosci.2414-05.2005}.
+Hofer H, Carroll J, Neitz J, Neitz M, Williams DR.
+2005.
+Organization of the human trichromatic cone mosaic.
+\emph{The Journal of Neuroscience} \textbf{25}:9669--9679.
+doi:\href{https://doi.org/10.1523/jneurosci.2414-05.2005}{10.1523/jneurosci.2414-05.2005}
 
 \leavevmode\hypertarget{ref-Hubel1962}{}%
-Hubel DH, Wiesel TN (1962) Receptive fields, binocular interaction and functional architecture in the cat's visual cortex. J Physiol 160:106--154.
+Hubel DH, Wiesel TN.
+1962.
+Receptive fields, binocular interaction and functional architecture in the cat's visual cortex.
+\emph{J Physiol} \textbf{160}:106--54.
+doi:\href{https://doi.org/10.1113/jphysiol.1962.sp006837}{10.1113/jphysiol.1962.sp006837}
 
 \leavevmode\hypertarget{ref-Kaestner2019}{}%
-Kaestner M, Maloney RT, Wailes-Newson KH, Bloj M, Harris JM, Morland AB, Wade AR (2019) Asymmetries between achromatic and chromatic extraction of 3D motion signals.
-Proc Natl Acad Sci U S A 116:13631--13640.
+Kaestner M, Maloney RT, Wailes-Newson KH, Bloj M, Harris JM, Morland AB, Wade AR.
+2019.
+Asymmetries between achromatic and chromatic extraction of 3D motion signals.
+\emph{Proc Natl Acad Sci U S A} \textbf{116}:13631--13640.
+doi:\href{https://doi.org/10.1073/pnas.1817202116}{10.1073/pnas.1817202116}
 
 \leavevmode\hypertarget{ref-Kassner2014}{}%
-Kassner M, Patera W, Bulling A (2014) Pupil: An open source platform for pervasive eye tracking and mobile gaze-based interaction.
-In: Proceedings of the 2014 ACM international joint conference on pervasive and ubiquitous computing: Adjunct publication.
+Kassner M, Patera W, Bulling A.
+2014.
+Pupil: An open source platform for pervasive eye tracking and mobile gaze-based interaction.Proceedings of the 2014 ACM International Joint Conference on Pervasive and Ubiquitous Computing: Adjunct Publication.
 ACM.
-Available at: \url{https://doi.org/10.1145\%2F2638728.2641695}.
+doi:\href{https://doi.org/10.1145/2638728.2641695}{10.1145/2638728.2641695}
 
 \leavevmode\hypertarget{ref-Kingdom2015}{}%
-Kingdom FAA, Libenson L (2015) Dichoptic color saturation mixture: Binocular luminance contrast promotes perceptual averaging. J Vis 15:2.
+Kingdom FAA, Libenson L.
+2015.
+Dichoptic color saturation mixture: Binocular luminance contrast promotes perceptual averaging.
+\emph{J Vis} \textbf{15}:2.
+doi:\href{https://doi.org/10.1167/15.5.2}{10.1167/15.5.2}
 
 \leavevmode\hypertarget{ref-Lucas2003}{}%
-Lucas RJ, Hattar S, Takao M, Berson DM, Foster RG, Yau K-W (2003) Diminished pupillary light reflex at high irradiances in melanopsin-knockout mice.
-Science 299:245--247 Available at: \url{https://doi.org/10.1126\%2Fscience.1077293}.
+Lucas RJ, Hattar S, Takao M, Berson DM, Foster RG, Yau K-W.
+2003.
+Diminished pupillary light reflex at high irradiances in melanopsin-knockout mice.
+\emph{Science} \textbf{299}:245--247.
+doi:\href{https://doi.org/10.1126/science.1077293}{10.1126/science.1077293}
 
 \leavevmode\hypertarget{ref-Markwell2010}{}%
-Markwell EL, Feigl B, Zele AJ (2010) Intrinsically photosensitive melanopsin retinal ganglion cell contributions to the pupillary light reflex and circadian rhythm.
-Clinical and Experimental Optometry 93:137--149 Available at: \url{https://doi.org/10.1111\%2Fj.1444-0938.2010.00479.x}.
+Markwell EL, Feigl B, Zele AJ.
+2010.
+Intrinsically photosensitive melanopsin retinal ganglion cell contributions to the pupillary light reflex and circadian rhythm.
+\emph{Clinical and Experimental Optometry} \textbf{93}:137--149.
+doi:\href{https://doi.org/10.1111/j.1444-0938.2010.00479.x}{10.1111/j.1444-0938.2010.00479.x}
 
 \leavevmode\hypertarget{ref-Martin2023}{}%
-Martin JT, Boynton GM, Baker DH, Wade AR, Spitschan M (2023) PySilSub: An open-source python toolbox for implementing the method of silent substitution in vision and nonvisual photoreception research.
-Journal of Vision 23:10 Available at: \url{https://doi.org/10.1167\%2Fjov.23.7.10}.
+Martin JT, Boynton GM, Baker DH, Wade AR, Spitschan M.
+2023.
+PySilSub: An open-source python toolbox for implementing the method of silent substitution in vision and nonvisual photoreception research.
+\emph{Journal of Vision} \textbf{23}:10.
+doi:\href{https://doi.org/10.1167/jov.23.7.10}{10.1167/jov.23.7.10}
 
 \leavevmode\hypertarget{ref-Martin2022}{}%
-Martin JT, Pinto J, Bulte D, Spitschan M (2022) PyPlr: A versatile, integrated system of hardware and software for researching the human pupillary light reflex.
-Behavior Research Methods 54:2720--2739.
+Martin JT, Pinto J, Bulte D, Spitschan M.
+2022.
+PyPlr: A versatile, integrated system of hardware and software for researching the human pupillary light reflex.
+\emph{Behavior Research Methods} \textbf{54}:2720--2739.
+doi:\href{https://doi.org/10.3758/s13428-021-01759-3}{10.3758/s13428-021-01759-3}
 
 \leavevmode\hypertarget{ref-Mathot2018}{}%
-Mathôt S (2018) Pupillometry: Psychology, physiology, and function. J Cogn 1:16.
+Mathôt S. 2018. Pupillometry: Psychology, physiology, and function. \emph{J Cogn} \textbf{1}:16. doi:\href{https://doi.org/10.5334/joc.18}{10.5334/joc.18}
+
+\leavevmode\hypertarget{ref-McDougal2015}{}%
+McDougal DH, Gamlin PD. 2015. Autonomic control of the eye. \emph{Comprehensive Physiology} \textbf{5}:439--473. doi:\href{https://doi.org/10.1002/cphy.c140014}{10.1002/cphy.c140014}
 
 \leavevmode\hypertarget{ref-McDougal2010}{}%
-McDougal DH, Gamlin PD (2010) The influence of intrinsically-photosensitive retinal ganglion cells on the spectral sensitivity and response dynamics of the human pupillary light reflex.
-Vision Research 50:72--87 Available at: \url{https://www.sciencedirect.com/science/article/pii/S0042698909004763} {[}Accessed July 18, 2023{]}.
-
-\leavevmode\hypertarget{ref-McDougal2015}{}%
-McDougal DH, Gamlin PD (2015) Autonomic control of the eye. Comprehensive Physiology 5:439--473.
+McDougal DH, Gamlin PD.
+2010.
+The influence of intrinsically-photosensitive retinal ganglion cells on the spectral sensitivity and response dynamics of the human pupillary light reflex.
+\emph{Vision Research} \textbf{50}:72--87.
+doi:\href{https://doi.org/10.1016/j.visres.2009.10.012}{10.1016/j.visres.2009.10.012}
 
 \leavevmode\hypertarget{ref-Meese2006}{}%
-Meese TS, Georgeson MA, Baker DH (2006) Binocular contrast vision at and above threshold. Journal of Vision 6:1224--1243.
+Meese TS, Georgeson MA, Baker DH. 2006. Binocular contrast vision at and above threshold. \emph{Journal of Vision} \textbf{6}:1224--43. doi:\href{https://doi.org/10.1167/6.11.7}{10.1167/6.11.7}
 
 \leavevmode\hypertarget{ref-Moradi2009}{}%
-Moradi F, Heeger DJ (2009) Inter-ocular contrast normalization in human visual cortex. J Vis 9:13.1--22.
+Moradi F, Heeger DJ. 2009. Inter-ocular contrast normalization in human visual cortex. \emph{J Vis} \textbf{9}:13.1--22. doi:\href{https://doi.org/10.1167/9.3.13}{10.1167/9.3.13}
 
 \leavevmode\hypertarget{ref-Murray2018}{}%
-Murray IJ, Kremers J, McKeefry D, Parry NRA (2018) Paradoxical pupil responses to isolated M-cone increments.
-Journal of the Optical Society of America A 35:B66--B71 Available at: \url{https://opg.optica.org/josaa/abstract.cfm?uri=josaa-35-4-B66} {[}Accessed July 18, 2023{]}.
+Murray IJ, Kremers J, McKeefry D, Parry NRA.
+2018.
+Paradoxical pupil responses to isolated M-cone increments.
+\emph{Journal of the Optical Society of America A} \textbf{35}:B66--B71.
+doi:\href{https://doi.org/10.1364/JOSAA.35.000B66}{10.1364/JOSAA.35.000B66}
 
 \leavevmode\hypertarget{ref-Norcia2015}{}%
-Norcia AM, Appelbaum LG, Ales JM, Cottereau BR, Rossion B (2015) The steady-state visual evoked potential in vision research: A review. Journal of Vision 15(6):4.
+Norcia AM, Appelbaum LG, Ales JM, Cottereau BR, Rossion B.
+2015.
+The steady-state visual evoked potential in vision research: A review.
+\emph{Journal of Vision} \textbf{15(6)}:4.
+doi:\href{https://doi.org/10.1167/15.6.4}{10.1167/15.6.4}
 
 \leavevmode\hypertarget{ref-Panda2002}{}%
-Panda S, Sato TK, Castrucci AM, Rollag MD, DeGrip WJ, Hogenesch JB, Provencio I, Kay SA (2002) Melanopsin (opn4) requirement for normal light-induced circadian phase shifting.
-Science 298:2213--2216 Available at: \url{https://doi.org/10.1126\%2Fscience.1076848}.
+Panda S, Sato TK, Castrucci AM, Rollag MD, DeGrip WJ, Hogenesch JB, Provencio I, Kay SA.
+2002.
+Melanopsin (opn4) requirement for normal light-induced circadian phase shifting.
+\emph{Science} \textbf{298}:2213--2216.
+doi:\href{https://doi.org/10.1126/science.1076848}{10.1126/science.1076848}
 
 \leavevmode\hypertarget{ref-Pokorny1987}{}%
-Pokorny J, Smith VC, Lutze M (1987) Aging of the human lens. Applied Optics 26:1437 Available at: \url{http://dx.doi.org/10.1364/AO.26.001437}.
+Pokorny J, Smith VC, Lutze M. 1987. Aging of the human lens. \emph{Applied Optics} \textbf{26}:1437. doi:\href{https://doi.org/10.1364/ao.26.001437}{10.1364/ao.26.001437}
 
 \leavevmode\hypertarget{ref-Provencio2000}{}%
-Provencio I, Rodriguez IR, Jiang G, Hayes WP, Moreira EF, Rollag MD (2000) A Novel Human Opsin in the Inner Retina.
-Journal of Neuroscience 20:600--605 Available at: \url{https://www.jneurosci.org/content/20/2/600} {[}Accessed July 18, 2023{]}.
+Provencio I, Rodriguez IR, Jiang G, Hayes WP, Moreira EF, Rollag MD.
+2000.
+A Novel Human Opsin in the Inner Retina.
+\emph{Journal of Neuroscience} \textbf{20}:600--605.
+doi:\href{https://doi.org/10.1523/JNEUROSCI.20-02-00600.2000}{10.1523/JNEUROSCI.20-02-00600.2000}
 
 \leavevmode\hypertarget{ref-Ruby2002}{}%
-Ruby NF, Brennan TJ, Xie X, Cao V, Franken P, Heller HC, O'Hara BF (2002) Role of melanopsin in circadian responses to light.
-Science 298:2211--2213 Available at: \url{https://doi.org/10.1126\%2Fscience.1076701}.
+Ruby NF, Brennan TJ, Xie X, Cao V, Franken P, Heller HC, O'Hara BF.
+2002.
+Role of melanopsin in circadian responses to light.
+\emph{Science} \textbf{298}:2211--2213.
+doi:\href{https://doi.org/10.1126/science.1076701}{10.1126/science.1076701}
+
+\leavevmode\hypertarget{ref-SegalaThesis2023}{}%
+Segala FG.
+2023.
+Binocular combination of light in canonical and non-canonical pathways (phd).
+University of York.
+doi:\href{https://doi.org/https://etheses.whiterose.ac.uk/id/oai_id/oai:etheses.whiterose.ac.uk:34419}{https://etheses.whiterose.ac.uk/id/oai\_id/oai:etheses.whiterose.ac.uk:34419}
 
 \leavevmode\hypertarget{ref-Segala2023}{}%
-Segala FG, Bruno A, Martin JT, Aung MT, Wade AR, Baker DH (2023) Different rules for binocular combination of luminance flicker in cortical and subcortical pathways.
-eLife 12 Available at: \url{https://doi.org/10.7554\%2Felife.87048}.
+Segala FG, Bruno A, Martin JT, Aung MT, Wade AR, Baker DH.
+2023.
+Different rules for binocular combination of luminance flicker in cortical and subcortical pathways.
+\emph{eLife} \textbf{12}.
+doi:\href{https://doi.org/10.7554/elife.87048}{10.7554/elife.87048}
 
 \leavevmode\hypertarget{ref-Shapiro1996}{}%
-Shapiro AG, Pokorny J, Smith VC (1996) Conerod receptor spaces with illustrations that use CRT phosphor and light-emitting-diode spectra.
-Journal of the Optical Society of America A 13:2319 Available at: \url{https://doi.org/10.1364\%2Fjosaa.13.002319}.
+Shapiro AG, Pokorny J, Smith VC.
+1996.
+Conerod receptor spaces with illustrations that use CRT phosphor and light-emitting-diode spectra.
+\emph{Journal of the Optical Society of America A} \textbf{13}:2319.
+doi:\href{https://doi.org/10.1364/josaa.13.002319}{10.1364/josaa.13.002319}
 
 \leavevmode\hypertarget{ref-Spitschan2015}{}%
-Spitschan M, Aguirre GK, Brainard DH (2015) Selective stimulation of penumbral cones reveals perception in the shadow of retinal blood vessels. PLoS One 10:e0124328.
+Spitschan M, Aguirre GK, Brainard DH.
+2015.
+Selective stimulation of penumbral cones reveals perception in the shadow of retinal blood vessels.
+\emph{PLoS One} \textbf{10}:e0124328.
+doi:\href{https://doi.org/10.1371/journal.pone.0124328}{10.1371/journal.pone.0124328}
 
 \leavevmode\hypertarget{ref-Spitschan2019}{}%
-Spitschan M, Cajochen C (2019) Binocular facilitation in light-mediated melatonin suppression? J Pineal Res 67:e12602.
+Spitschan M, Cajochen C. 2019. Binocular facilitation in light-mediated melatonin suppression? \emph{J Pineal Res} \textbf{67}:e12602. doi:\href{https://doi.org/10.1111/jpi.12602}{10.1111/jpi.12602}
 
 \leavevmode\hypertarget{ref-Spitschan2014}{}%
-Spitschan M, Jain S, Brainard DH, Aguirre GK (2014) Opponent melanopsin and s-cone signals in the human pupillary light response.
-Proceedings of the National Academy of Sciences 111:15568--15572 Available at: \url{https://doi.org/10.1073\%2Fpnas.1400942111}.
+Spitschan M, Jain S, Brainard DH, Aguirre GK.
+2014.
+Opponent melanopsin and s-cone signals in the human pupillary light response.
+\emph{Proceedings of the National Academy of Sciences} \textbf{111}:15568--15572.
+doi:\href{https://doi.org/10.1073/pnas.1400942111}{10.1073/pnas.1400942111}
 
 \leavevmode\hypertarget{ref-Spitschan2018}{}%
-Spitschan M, Woelders T (2018) The Method of Silent Substitution for Examining Melanopsin Contributions to Pupil Control. Frontiers in Neurology 9.
+Spitschan M, Woelders T.
+2018.
+The Method of Silent Substitution for Examining Melanopsin Contributions to Pupil Control.
+\emph{Frontiers in Neurology} \textbf{9}.
+doi:\href{https://doi.org/10.3389/fneur.2018.00941}{10.3389/fneur.2018.00941}
 
 \leavevmode\hypertarget{ref-Stockman2000}{}%
-Stockman A, Sharpe LT (2000) The spectral sensitivities of the middle- and long-wavelength-sensitive cones derived from measurements in observers of known genotype. Vision Res 40:1711--1737.
+Stockman A, Sharpe LT.
+2000.
+The spectral sensitivities of the middle- and long-wavelength-sensitive cones derived from measurements in observers of known genotype.
+\emph{Vision Res} \textbf{40}:1711--37.
+doi:\href{https://doi.org/10.1016/s0042-6989(00)00021-3}{10.1016/s0042-6989(00)00021-3}
 
 \leavevmode\hypertarget{ref-Stockman1999}{}%
-Stockman A, Sharpe LT, Fach C (1999) The spectral sensitivity of the human short-wavelength sensitive cones derived from thresholds and color matches.
-Vision Research 39:2901--2927 Available at: \url{https://www.sciencedirect.com/science/article/pii/S0042698998002259}.
+Stockman A, Sharpe LT, Fach C.
+1999.
+The spectral sensitivity of the human short-wavelength sensitive cones derived from thresholds and color matches.
+\emph{Vision Research} \textbf{39}:2901--2927.
+doi:\href{https://doi.org/https://doi.org/10.1016/S0042-6989(98)00225-9}{https://doi.org/10.1016/S0042-6989(98)00225-9}
 
 \leavevmode\hypertarget{ref-Trieschmann2007}{}%
-Trieschmann M, Kuijk FJGM van, Alexander R, Hermans P, Luthert P, Bird AC, Pauleikhoff D (2007) Macular pigment in the human retina: Histological evaluation of localization and distribution.
-Eye 22:132--137 Available at: \url{http://dx.doi.org/10.1038/sj.eye.6702780}.
+Trieschmann M, Kuijk FJGM van, Alexander R, Hermans P, Luthert P, Bird AC, Pauleikhoff D.
+2007.
+Macular pigment in the human retina: Histological evaluation of localization and distribution.
+\emph{Eye} \textbf{22}:132--137.
+doi:\href{https://doi.org/10.1038/sj.eye.6702780}{10.1038/sj.eye.6702780}
 
 \leavevmode\hypertarget{ref-Woelders2018}{}%
-Woelders T, Leenheers T, Gordijn MCM, Hut RA, Beersma DGM, Wams EJ (2018) Melanopsin- and L-cone--induced pupil constriction is inhibited by S- and M-cones in humans.
-Proceedings of the National Academy of Sciences 115:792--797 Available at: \url{https://www.pnas.org/doi/full/10.1073/pnas.1716281115} {[}Accessed July 18, 2023{]}.
+Woelders T, Leenheers T, Gordijn MCM, Hut RA, Beersma DGM, Wams EJ.
+2018.
+Melanopsin- and L-cone--induced pupil constriction is inhibited by S- and M-cones in humans.
+\emph{Proceedings of the National Academy of Sciences} \textbf{115}:792--797.
+doi:\href{https://doi.org/10.1073/pnas.1716281115}{10.1073/pnas.1716281115}
 
 \leavevmode\hypertarget{ref-Wyatt1981}{}%
-Wyatt HJ, Musselman JF (1981) Pupillary light reflex in humans: Evidence for an unbalanced pathway from nasal retina, and for signal cancellation in brainstem. Vision Res 21:513--525.
+Wyatt HJ, Musselman JF.
+1981.
+Pupillary light reflex in humans: Evidence for an unbalanced pathway from nasal retina, and for signal cancellation in brainstem.
+\emph{Vision Res} \textbf{21}:513--25.
+doi:\href{https://doi.org/10.1016/0042-6989(81)90097-3}{10.1016/0042-6989(81)90097-3}
 
 \leavevmode\hypertarget{ref-Zele2019}{}%
-Zele AJ, Adhikari P, Cao D, Feigl B (2019) Melanopsin driven enhancement of cone-mediated visual processing. Vision Res 160:72--81.
+Zele AJ, Adhikari P, Cao D, Feigl B.
+2019.
+Melanopsin driven enhancement of cone-mediated visual processing.
+\emph{Vision Res} \textbf{160}:72--81.
+doi:\href{https://doi.org/10.1016/j.visres.2019.04.009}{10.1016/j.visres.2019.04.009}
 
 \leavevmode\hypertarget{ref-Zele2018}{}%
-Zele AJ, Feigl B, Adhikari P, Maynard ML, Cao D (2018) Melanopsin photoreception contributes to human visual detection, temporal and colour processing.
-Scientific Reports 8 Available at: \url{https://doi.org/10.1038\%2Fs41598-018-22197-w}.
+Zele AJ, Feigl B, Adhikari P, Maynard ML, Cao D.
+2018.
+Melanopsin photoreception contributes to human visual detection, temporal and colour processing.
+\emph{Scientific Reports} \textbf{8}.
+doi:\href{https://doi.org/10.1038/s41598-018-22197-w}{10.1038/s41598-018-22197-w}
 

### 2025-02-24 manuscript.Rmd
Modified reference style

--- 2025-02-06 manuscript.Rmd
@@
 title: 'Binocular combination in the autonomic nervous system'
-author: |
- | Federico G. Segala$^1$, Aurelio Bruno$^{1,2}$, Joel T. Martin$^{1,3}$,
- | Anisa Y. Morsi$^1$, Alex R. Wade$^{1,4}$ & Daniel H. Baker$^{1,4}$
 output:
@@
 linkcolor: black
-csl: the-journal-of-neuroscience.csl
+csl: proceedings-of-the-royal-society-b.csl
 header-includes:
   \usepackage{caption}
-  \usepackage{setspace}\doublespacing
   \usepackage{lineno} \linenumbers
@@
 ```
-
-$^1$Department of Psychology, University of York, Heslington, York, YO10 5DD, United Kingdom.
-
-$^2$School of Psychology and Vision Sciences, University of Leicester, Leicester, LE1 7RH, United Kingdom.
-
-$^3$School of Philosophy, Psychology and Language Sciences, University of Edinburgh, Edinburgh, EH8 9AD, United Kingdom.
-
-$^4$York Biomedical Research Institute, University of York, Heslington, York, YO10 5NG, United Kingdom.
-
-Corresponding author: Federico G. Segala, [federico.segala@york.ac.uk](federico.segala@york.ac.uk).
 
@@
 The anatomical pathway from the retina to the subcortical nuclei controlling the pupillary light response (PLR) is well established: it includes the Pretectal Olivary nucleus (PON), the Superior Cervical ganglion and the Edinger-Westphal nucleus, which project to the iris sphincter muscles that directly control the pupil size [@McDougal2015].
-Evidence of a binocular component to the PLR is shown by the consensual response of the pupil [stimulation of one eye will cause constriction of the other eye\; @Wyatt1981].
+Evidence of a binocular component to the PLR is shown by the consensual response of the pupil (stimulation of one eye will cause constriction of the other eye @Wyatt1981).
 The anatomical segregation of the subcortical pathway from the rest of the brain means that this binocular combination of signals must occur independently of the cortical processes of binocular integration required for visual perception.
-Our recent work [@Segala2023] has shown that the algorithm underlying binocular combination of light in the pupil pathway differs from that in the cortex.
+Recent work [@Segala2023] has shown that the algorithm underlying binocular combination of light in the pupil pathway differs from that in the cortex.
 Here we extend this paradigm to compare binocular combination in different photoreceptor pathways that feed into the autonomic nervous system.
@@
 The ipRGCs are a recently discovered photoreceptor class [@Provencio2000] that express the photopigment melanopsin, and are involved in the regulation of the circadian rhythm [@Panda2002; @Ruby2002], forming a major input to the PON [@Dacey2003].
-The first direct evidence of the involvement of the ipRGCs in the PLR was shown in melanopsin knockout rats by @Lucas2003, resulting in the loss of the intrinsic photosensitivity of the cells and a reduced pupil constriction.
+The first direct evidence of the involvement of the ipRGCs in the PLR was shown in melanopsin knockout rats [@Lucas2003], resulting in the loss of the intrinsic photosensitivity of the cells and a reduced pupil constriction.
 Similar behaviour was later observed in primates and humans [@Gamlin2007] using silent substitution (see Methods), where it was demonstrated that the PLR continues during light presentation even when cone and rod signalling is blocked, indicating the primary role of the ipRGCs in maintaining pupil constriction over a prolonged time.
@@
 This is explained by a process of interocular suppression that cancels out the additional excitatory drive caused by stimulating two eyes.
-Our recent work [@Segala2023] showed that cortical signal combination for luminance flicker is substantially more linear than for spatial patterns, whereas there is evidence of interocular suppression in the pupil pathway.
+Recent work [@Segala2023] showed that cortical signal combination for luminance flicker is substantially more linear than for spatial patterns, whereas there is evidence of interocular suppression in the pupil pathway.
 Here we measure the amplitude of pupil modulations in response to flickering stimuli presented as light flux, or directed towards the L-M cone, S-cone, and melanopsin pathways (see Figure \@ref(fig:spectraplots)e-l).
@@
 All participants had normal or corrected to normal vision, no known abnormalities of binocular or colour vision, and gave written informed consent.
-Our procedures were approved by the Ethics Committee of the Department of Psychology at the University of York (identification number 184).
+Our procedures were approved by the Ethics Committee of the Department of Psychology at the XXX (identification number 184).
 
@@
 Each primary was also linearized using a polynomial fit (see Figure \@ref(fig:primarylinearity) for details).
-We used the @Stockman2000 10-degree cone fundamentals, and estimates of melanopsin absorbance spectra from CIE S 026 [discussed in @Martin2023] to calculate $\alpha$-opic irradiance.
+We used the 10-degree cone fundamentals [@Stockman2000], and estimates of melanopsin absorbance spectra from CIE S 026 [discussed in @Martin2023] to calculate $\alpha$-opic irradiance.
 
@@
 The VR headset modifications allowed for small adjustments to account for individual differences in interpupillary distance and focal length.
-The use of this set up allowed us to modulate the stimuli in three different ocular configurations, similar to the ones we used in our previous study [@Segala2023]: monocular, binocular and dichoptic.
+The use of this set up allowed us to modulate the stimuli in three different ocular configurations, similar to the ones used in a previous study [@Segala2023]: monocular, binocular and dichoptic.
 In the monocular configuration, the unstimulated eye still saw a non-flickering disc of mean light flux.
 A schematic of the stimulation system is shown in Figure \@ref(fig:spectraplots)a.
-Pupillometry data were collected using a binocular Pupil Core eye-tracker headset [Pupil Labs GmbH, Berlin, Germany, @Kassner2014] running at 120 Hz, and the signals were recorded with the Pupil Capture software.
-
-Our previous study [@Segala2023] used a temporal frequency of 2Hz for foveal luminance flicker, and recorded EEG data simultaneously with pupillometry.
+Pupillometry data were collected using a binocular Pupil Core eye-tracker headset (Pupil Labs GmbH, Berlin, Germany @Kassner2014) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
+
+A previous study [@Segala2023] used a temporal frequency of 2Hz for foveal luminance flicker, and recorded EEG data simultaneously with pupillometry.
 Initial pilot experiments indicated that this frequency was too high to elicit measurable responses when stimulating individual photoreceptor pathways.
@@
 Pupil responses to binocular temporal contrast modulations were examined in a factorial design that combined six ocular conditions and five temporal contrast levels: 6, 12, 24, 48 and 96% of the available dynamic range.
-This design, similar to that used in our previous studies [@Segala2023; @Baker2017; @Baker2020], was applied in four separate experiments, each with a different mode of photoreceptor stimulation.
+This design, similar to that used in previous studies [@Segala2023; @Baker2017; @Baker2020], was applied in four separate experiments, each with a different mode of photoreceptor stimulation.
 In the first three conditions, the discs flickered at 0.5 Hz, in either a monocular, binocular or dichoptic arrangement.
@@
 
-The pupillometry data were analysed using the same method we used in our previous study [@Segala2023].
+The pupillometry data were analysed using the same method used in a previous study [@Segala2023].
 The data were converted from mp4 videos to a csv text file using the Pupil Player software [@Kassner2014], which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
@@
 
-To quantitatively summarise our data, we used the same model described in our previous study [@Segala2023].
-The model has the same general form as the first stage of the contrast gain control model proposed by @Meese2006, but omits the second stage.
-For the previous model that we used [@Segala2023], the exponent of the numerator and denominator had fixed values of 2 and (implicitly) 1.
+To quantitatively summarise our data, we used the same model described in a previous study [@Segala2023].
+The model has the same general form as the first stage of the contrast gain control model proposed by Meese and colleagues [@Meese2006], but omits the second stage.
+For the previous model that was used by Segala and colleagues [@Segala2023], the exponent of the numerator and denominator had fixed values of 2 and (implicitly) 1.
 Here, we allow these parameters (called _p_ and _q_) to be free, in order to permit different shapes of contrast response function, e.g.
@@
 
-Our recent psychophysical work [@Baker2024] has looked at binocular interactions in the L-M and S-cone pathways, and compared these to the light flux pathway.
-Using a contrast discrimination paradigm with spatial modulations of light flux and colour, @Baker2024 found equally strong interocular suppression in all three pathways.
+A recent psychophysical work [@Baker2024] has looked at binocular interactions in the L-M and S-cone pathways, and compared these to the light flux pathway.
+Using a contrast discrimination paradigm with spatial modulations of light flux and colour, the study [@Baker2024] found equally strong interocular suppression in all three pathways.
 This is rather different from our pupillometry results here, which demonstrate weaker suppression in the light flux and S-cone pathways than in the L-M pathway (see Figure \@ref(fig:FirstHarmonicPlots)).
-However, the current experiments involve temporal modulations, which are quite distinct from the spatial modulations used in @Baker2024.
-Our other recent work [@Segala2023] has shown that temporal luminance modulations involve much weaker interocular suppression in the cortical response than do spatial luminance modulations [@Baker2017].
+However, the current experiments involve temporal modulations, which are quite distinct from the spatial modulations used in the study by Baker and colleagues [@Baker2024].
+Other recent work [@Segala2023] has shown that temporal luminance modulations involve much weaker interocular suppression in the cortical response than do spatial luminance modulations [@Baker2017].
 These different normalization processes might reflect different priorities for spatial and temporal vision.
@@
 
-# Acknowledgements
-
-Supported by Biotechnology and Biological Sciences Research Council grant BB/V007580/1 awarded to DHB and ARW.
-
-# Declaration of interests
-
-The authors declare no competing interests.
-
 # References

### 2025-02-24 manuscript.tex
Modified reference style

--- 2025-02-06 manuscript.tex
@@
 \setcounter{secnumdepth}{5}
-\usepackage{caption} \usepackage{setspace}\doublespacing \usepackage{lineno} \linenumbers \newcommand{\beginsupplement}{\setcounter{table}{0} \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
+\usepackage{caption} \usepackage{lineno} \linenumbers \newcommand{\beginsupplement}{\setcounter{table}{0} \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
 \usepackage{booktabs}
@@
 \title{Binocular combination in the autonomic nervous system}
-\author{Federico G. Segala\(^1\), Aurelio Bruno\(^{1,2}\), Joel T. Martin\(^{1,3}\),\\
-Anisa Y. Morsi\(^1\), Alex R. Wade\(^{1,4}\) \& Daniel H. Baker\(^{1,4}\)}
-\date{}
+\author{}
+\date{\vspace{-2.5em}}
 
@@
 \maketitle
-
-\(^1\)Department of Psychology, University of York, Heslington, York, YO10 5DD, United Kingdom.
-
-\(^2\)School of Psychology and Vision Sciences, University of Leicester, Leicester, LE1 7RH, United Kingdom.
-
-\(^3\)School of Philosophy, Psychology and Language Sciences, University of Edinburgh, Edinburgh, EH8 9AD, United Kingdom.
-
-\(^4\)York Biomedical Research Institute, University of York, Heslington, York, YO10 5NG, United Kingdom.
-
-Corresponding author: Federico G. Segala, \url{federico.segala@york.ac.uk}.
 
@@
 
-The autonomic nervous system regulates many involuntary bodily processes, including the constriction and dilation of the pupils in response to light (McDougal and Gamlin, \protect\hyperlink{ref-McDougal2015}{2015}).
-The anatomical pathway from the retina to the subcortical nuclei controlling the pupillary light response (PLR) is well established: it includes the Pretectal Olivary nucleus (PON), the Superior Cervical ganglion and the Edinger-Westphal nucleus, which project to the iris sphincter muscles that directly control the pupil size (McDougal and Gamlin, \protect\hyperlink{ref-McDougal2015}{2015}).
-Evidence of a binocular component to the PLR is shown by the consensual response of the pupil (stimulation of one eye will cause constriction of the other eye; Wyatt and Musselman, \protect\hyperlink{ref-Wyatt1981}{1981}).
+The autonomic nervous system regulates many involuntary bodily processes, including the constriction and dilation of the pupils in response to light {[}\protect\hyperlink{ref-McDougal2015}{1}{]}.
+The anatomical pathway from the retina to the subcortical nuclei controlling the pupillary light response (PLR) is well established: it includes the Pretectal Olivary nucleus (PON), the Superior Cervical ganglion and the Edinger-Westphal nucleus, which project to the iris sphincter muscles that directly control the pupil size {[}\protect\hyperlink{ref-McDougal2015}{1}{]}.
+Evidence of a binocular component to the PLR is shown by the consensual response of the pupil (stimulation of one eye will cause constriction of the other eye {[}\protect\hyperlink{ref-Wyatt1981}{2}{]}).
 The anatomical segregation of the subcortical pathway from the rest of the brain means that this binocular combination of signals must occur independently of the cortical processes of binocular integration required for visual perception.
-Our recent work (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}) has shown that the algorithm underlying binocular combination of light in the pupil pathway differs from that in the cortex.
+Recent work {[}\protect\hyperlink{ref-Segala2023}{3}{]} has shown that the algorithm underlying binocular combination of light in the pupil pathway differs from that in the cortex.
 Here we extend this paradigm to compare binocular combination in different photoreceptor pathways that feed into the autonomic nervous system.
 
-Different classes of retinal photoreceptors, including cones, rods and melanopsin-containing intrinsically photosensitive retinal ganglion cells (ipRGCs), are directly involved in controlling and maintaining the size of the pupils (e.g.~McDougal and Gamlin, \protect\hyperlink{ref-McDougal2010}{2010}; Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}; Barrionuevo and Cao, \protect\hyperlink{ref-Barrionuevo2016}{2016}; Murray et al., \protect\hyperlink{ref-Murray2018}{2018}; Woelders et al., \protect\hyperlink{ref-Woelders2018}{2018}).
-Cones drive the initial rapid constriction of the pupils (Mathôt, \protect\hyperlink{ref-Mathot2018}{2018}), while the slower and longer activation of the ipRGCs maintains constriction over a prolonged period of time and regulates the post-illumination pupillary response (Markwell et al., \protect\hyperlink{ref-Markwell2010}{2010}; McDougal and Gamlin, \protect\hyperlink{ref-McDougal2010}{2010}).
-The ipRGCs are a recently discovered photoreceptor class (Provencio et al., \protect\hyperlink{ref-Provencio2000}{2000}) that express the photopigment melanopsin, and are involved in the regulation of the circadian rhythm (Panda et al., \protect\hyperlink{ref-Panda2002}{2002}; Ruby et al., \protect\hyperlink{ref-Ruby2002}{2002}), forming a major input to the PON (Dacey et al., \protect\hyperlink{ref-Dacey2003}{2003}).
-The first direct evidence of the involvement of the ipRGCs in the PLR was shown in melanopsin knockout rats by Lucas et al.
-(\protect\hyperlink{ref-Lucas2003}{2003}), resulting in the loss of the intrinsic photosensitivity of the cells and a reduced pupil constriction.
-Similar behaviour was later observed in primates and humans (Gamlin et al., \protect\hyperlink{ref-Gamlin2007}{2007}) using silent substitution (see Methods), where it was demonstrated that the PLR continues during light presentation even when cone and rod signalling is blocked, indicating the primary role of the ipRGCs in maintaining pupil constriction over a prolonged time.
+Different classes of retinal photoreceptors, including cones, rods and melanopsin-containing intrinsically photosensitive retinal ganglion cells (ipRGCs), are directly involved in controlling and maintaining the size of the pupils {[}\protect\hyperlink{ref-McDougal2010}{4}--\protect\hyperlink{ref-Woelders2018}{8}{]}.
+Cones drive the initial rapid constriction of the pupils {[}\protect\hyperlink{ref-Mathot2018}{9}{]}, while the slower and longer activation of the ipRGCs maintains constriction over a prolonged period of time and regulates the post-illumination pupillary response {[}\protect\hyperlink{ref-McDougal2010}{4},\protect\hyperlink{ref-Markwell2010}{10}{]}.
+The ipRGCs are a recently discovered photoreceptor class {[}\protect\hyperlink{ref-Provencio2000}{11}{]} that express the photopigment melanopsin, and are involved in the regulation of the circadian rhythm {[}\protect\hyperlink{ref-Panda2002}{12},\protect\hyperlink{ref-Ruby2002}{13}{]}, forming a major input to the PON {[}\protect\hyperlink{ref-Dacey2003}{14}{]}.
+The first direct evidence of the involvement of the ipRGCs in the PLR was shown in melanopsin knockout rats {[}\protect\hyperlink{ref-Lucas2003}{15}{]}, resulting in the loss of the intrinsic photosensitivity of the cells and a reduced pupil constriction.
+Similar behaviour was later observed in primates and humans {[}\protect\hyperlink{ref-Gamlin2007}{16}{]} using silent substitution (see Methods), where it was demonstrated that the PLR continues during light presentation even when cone and rod signalling is blocked, indicating the primary role of the ipRGCs in maintaining pupil constriction over a prolonged time.
 
-Binocular combination has been extensively studied in visual perception, where it is mediated by neurons in primary visual cortex (Hubel and Wiesel, \protect\hyperlink{ref-Hubel1962}{1962}).
-For pattern vision, binocular summation occurs at threshold, such that a lower contrast is required to detect a target shown to both eyes than a target shown to one eye (Campbell and Green, \protect\hyperlink{ref-Campbell1965}{1965}; Baker et al., \protect\hyperlink{ref-Baker2018}{2018}).
-At higher contrasts, the phenomenon of `ocularity invariance' is observed, in which the response to monocularly- and binocularly-presented patterns is equal (Baker et al., \protect\hyperlink{ref-Baker2007}{2007}; Moradi and Heeger, \protect\hyperlink{ref-Moradi2009}{2009}).
+Binocular combination has been extensively studied in visual perception, where it is mediated by neurons in primary visual cortex {[}\protect\hyperlink{ref-Hubel1962}{17}{]}.
+For pattern vision, binocular summation occurs at threshold, such that a lower contrast is required to detect a target shown to both eyes than a target shown to one eye {[}\protect\hyperlink{ref-Baker2018}{18},\protect\hyperlink{ref-Campbell1965}{19}{]}.
+At higher contrasts, the phenomenon of `ocularity invariance' is observed, in which the response to monocularly- and binocularly-presented patterns is equal {[}\protect\hyperlink{ref-Baker2007}{20},\protect\hyperlink{ref-Moradi2009}{21}{]}.
 This is explained by a process of interocular suppression that cancels out the additional excitatory drive caused by stimulating two eyes.
-Our recent work (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}) showed that cortical signal combination for luminance flicker is substantially more linear than for spatial patterns, whereas there is evidence of interocular suppression in the pupil pathway.
+Recent work {[}\protect\hyperlink{ref-Segala2023}{3}{]} showed that cortical signal combination for luminance flicker is substantially more linear than for spatial patterns, whereas there is evidence of interocular suppression in the pupil pathway.
 Here we measure the amplitude of pupil modulations in response to flickering stimuli presented as light flux, or directed towards the L-M cone, S-cone, and melanopsin pathways (see Figure \ref{fig:spectraplots}e-l).
 Our key comparisons are between monocular and binocular stimulation, and in a dichoptic masking condition where the two eyes are stimulated at different frequencies.
-The results are interpreted using a contemporary model of binocular vision (Meese et al., \protect\hyperlink{ref-Meese2006}{2006}) implemented within a hierarchical Bayesian framework.
+The results are interpreted using a contemporary model of binocular vision {[}\protect\hyperlink{ref-Meese2006}{22}{]} implemented within a hierarchical Bayesian framework.
 
@@
 To present synchronised stimulus modulations independently to each eye, two light engines (SpectraTuneLAB, which are thermally stable across time with active cooling according to the manufacturers: LEDMOTIVE Technologies, LLC, Barcelona, Spain), each with 10 independently addressable LED colour channels, were integrated into a customised binocular viewing system.
-The light engines were operated via a Python interface to their REST API (Martin et al., \protect\hyperlink{ref-Martin2022}{2022}), which supports synchronous launch and playback of spectral sequences prepared in advance and stored in JSON format.
+The light engines were operated via a Python interface to their REST API {[}\protect\hyperlink{ref-Martin2022}{23}{]}, which supports synchronous launch and playback of spectral sequences prepared in advance and stored in JSON format.
 A special command was commissioned from LEDMOTIVE to allow two different stimulus files to be launched simultaneously from the two devices.
@@
 When preparing the spectral sequences, the age of participants was used to account for the yellowing of the lenses.
-We used the silent substitution technique (Estévez and Spekreijse, \protect\hyperlink{ref-Estevez1982}{1982}) to selectively stimulate specific photoreceptor classes.
+We used the silent substitution technique {[}\protect\hyperlink{ref-Estevez1982}{24}{]} to selectively stimulate specific photoreceptor classes.
 Silent substitution exploits the fact that each photoreceptor class has a distinct spectral tuning that overlaps with the others.
-Using a multiprimary system, in which the primaries (i.e.~LEDs) have different spectra, it is possible to target one class of photoreceptors while maintaining the others at a constant activity level, effectively silencing them (Shapiro et al., \protect\hyperlink{ref-Shapiro1996}{1996}; Spitschan and Woelders, \protect\hyperlink{ref-Spitschan2018}{2018}, this paper also offers a clear explanation of how to implement silent substitution).
-We calculated silent substitution solutions using the \emph{PySilSub} toolbox (Martin et al., \protect\hyperlink{ref-Martin2023}{2023}), using linear algebra.
+Using a multiprimary system, in which the primaries (i.e.~LEDs) have different spectra, it is possible to target one class of photoreceptors while maintaining the others at a constant activity level, effectively silencing them {[}\protect\hyperlink{ref-Shapiro1996}{25},\protect\hyperlink{ref-Spitschan2018}{26}{]}.
+We calculated silent substitution solutions using the \emph{PySilSub} toolbox {[}\protect\hyperlink{ref-Martin2023}{27}{]}, using linear algebra.
 The outputs of the two light engines (see Figure \ref{fig:spectraplots}b,c) were calibrated using an Ocean Optics Jaz spectroradiometer, which was wavelength-calibrated to an Argon lamp and intensity calibrated using a NIST-traceable light source.
 Each primary was also linearized using a polynomial fit (see Figure \ref{fig:primarylinearity} for details).
-We used the Stockman and Sharpe (\protect\hyperlink{ref-Stockman2000}{2000}) 10-degree cone fundamentals, and estimates of melanopsin absorbance spectra from CIE S 026 (discussed in Martin et al., \protect\hyperlink{ref-Martin2023}{2023}) to calculate \(\alpha\)-opic irradiance.
+We used the 10-degree cone fundamentals {[}\protect\hyperlink{ref-Stockman2000}{28}{]}, and estimates of melanopsin absorbance spectra from CIE S 026 {[}\protect\hyperlink{ref-Martin2023}{27}{]} to calculate \(\alpha\)-opic irradiance.
 
@@
 The diffuser discs were positioned in the objective planes of the lenses of a modified VR headset (SHINECON SC-G01, Dongguan Shinecon Industrial Co.~Ltd., Guangdong, China), which was used by the participants to view the stimuli.
-The stimuli were two discs of flickering light with a diameter of approximately 30 degrees, which were fused together into a cyclopean percept resembling a donut-shaped ring of light, similar to that used in other studies (e.g., Barrionuevo and Cao, \protect\hyperlink{ref-Barrionuevo2016}{2016}; Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}, \protect\hyperlink{ref-Spitschan2015}{2015}; Murray et al., \protect\hyperlink{ref-Murray2018}{2018}; Zele et al., \protect\hyperlink{ref-Zele2018}{2018}).
+The stimuli were two discs of flickering light with a diameter of approximately 30 degrees, which were fused together into a cyclopean percept resembling a donut-shaped ring of light, similar to that used in other studies {[}\protect\hyperlink{ref-Barrionuevo2016}{5}--\protect\hyperlink{ref-Spitschan2014}{7},\protect\hyperlink{ref-Spitschan2015}{29},\protect\hyperlink{ref-Zele2018}{30}{]}.
 The VR headset modifications allowed for small adjustments to account for individual differences in interpupillary distance and focal length.
-The use of this set up allowed us to modulate the stimuli in three different ocular configurations, similar to the ones we used in our previous study (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}): monocular, binocular and dichoptic.
+The use of this set up allowed us to modulate the stimuli in three different ocular configurations, similar to the ones used in a previous study {[}\protect\hyperlink{ref-Segala2023}{3}{]}: monocular, binocular and dichoptic.
 In the monocular configuration, the unstimulated eye still saw a non-flickering disc of mean light flux.
 A schematic of the stimulation system is shown in Figure \ref{fig:spectraplots}a.
-Pupillometry data were collected using a binocular Pupil Core eye-tracker headset (Pupil Labs GmbH, Berlin, Germany, Kassner et al., \protect\hyperlink{ref-Kassner2014}{2014}) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
+Pupillometry data were collected using a binocular Pupil Core eye-tracker headset (Pupil Labs GmbH, Berlin, Germany {[}\protect\hyperlink{ref-Kassner2014}{31}{]}) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
 
-Our previous study (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}) used a temporal frequency of 2Hz for foveal luminance flicker, and recorded EEG data simultaneously with pupillometry.
+A previous study {[}\protect\hyperlink{ref-Segala2023}{3}{]} used a temporal frequency of 2Hz for foveal luminance flicker, and recorded EEG data simultaneously with pupillometry.
 Initial pilot experiments indicated that this frequency was too high to elicit measurable responses when stimulating individual photoreceptor pathways.
-For all experiments, we therefore used a primary flicker frequency of 0.5Hz, as previous literature showed that this was slow enough to elicit a pupil response from all photoreceptor classes (Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}).
-We also focussed on only recording pupillometry data as this frequency would be too slow to elicit steady-state EEG responses (Norcia et al., \protect\hyperlink{ref-Norcia2015}{2015}).
+For all experiments, we therefore used a primary flicker frequency of 0.5Hz, as previous literature showed that this was slow enough to elicit a pupil response from all photoreceptor classes {[}\protect\hyperlink{ref-Spitschan2014}{7}{]}.
+We also focussed on only recording pupillometry data as this frequency would be too slow to elicit steady-state EEG responses {[}\protect\hyperlink{ref-Norcia2015}{32}{]}.
 
@@
 
-Silent substitution stimuli were prepared and calibrated for each participant with custom Python software (Martin et al., \protect\hyperlink{ref-Martin2023}{2023}) and Python scripts.
-Estimates of photoreceptor spectral sensitivities for each participant were constructed from the known photopigment absorbance spectra (Stockman and Sharpe, \protect\hyperlink{ref-Stockman2000}{2000}), taking account of the peak axial density of the respective photopigments, as well as lens (Pokorny et al., \protect\hyperlink{ref-Pokorny1987}{1987}; Stockman et al., \protect\hyperlink{ref-Stockman1999}{1999}; Stockman and Sharpe, \protect\hyperlink{ref-Stockman2000}{2000}) and macular pigment density (Bone et al., \protect\hyperlink{ref-Bone1988}{1988}; Stockman et al., \protect\hyperlink{ref-Stockman1999}{1999}), in accordance with the field size and age-dependant CIEPO06 observer model (CIE, \protect\hyperlink{ref-CIE2006}{2006}).
-The melanopic and rhodopic action spectra of the 32-year-old standard observer were taken from CIE S 026 (CIE, \protect\hyperlink{ref-CIE2018}{2018}) and then adjusted for age-related lens transmittance with a spectral correction function, in line with the standard.
-Macular pigment correction was not applied to the rhodopic and melanopic action spectra because rods are not present at the fovea and ipRGCs sit above the retinal pigment layer (Trieschmann et al., \protect\hyperlink{ref-Trieschmann2007}{2007}).
+Silent substitution stimuli were prepared and calibrated for each participant with custom Python software {[}\protect\hyperlink{ref-Martin2023}{27}{]} and Python scripts.
+Estimates of photoreceptor spectral sensitivities for each participant were constructed from the known photopigment absorbance spectra {[}\protect\hyperlink{ref-Stockman2000}{28}{]}, taking account of the peak axial density of the respective photopigments, as well as lens {[}\protect\hyperlink{ref-Stockman2000}{28},\protect\hyperlink{ref-Pokorny1987}{33},\protect\hyperlink{ref-Stockman1999}{34}{]} and macular pigment density {[}\protect\hyperlink{ref-Stockman1999}{34},\protect\hyperlink{ref-Bone1988}{35}{]}, in accordance with the field size and age-dependant CIEPO06 observer model {[}\protect\hyperlink{ref-CIE2006}{36}{]}.
+The melanopic and rhodopic action spectra of the 32-year-old standard observer were taken from CIE S 026 {[}\protect\hyperlink{ref-CIE2018}{37}{]} and then adjusted for age-related lens transmittance with a spectral correction function, in line with the standard.
+Macular pigment correction was not applied to the rhodopic and melanopic action spectra because rods are not present at the fovea and ipRGCs sit above the retinal pigment layer {[}\protect\hyperlink{ref-Trieschmann2007}{38}{]}.
 
@@
 Splatter on nominally silenced photoreceptors was very small (see Figure \ref{fig:spectraplots}j-l), well below the levels that would be expected to generate measurable pupil modulations, although we can observe that the rods may not be saturated in the L-M and melanopsin-directed stimuli (Figure \ref{fig:spectraplots}j and \ref{fig:spectraplots}l) and could intrude in these two experiments.
-We also estimated activation of penumbral L and M cones (Spitschan et al., \protect\hyperlink{ref-Spitschan2015}{2015}; Barrionuevo and Cao, \protect\hyperlink{ref-Barrionuevo2016}{2016}; Zele et al., \protect\hyperlink{ref-Zele2019}{2019}), which was minimal (\(\le 1.5%
+We also estimated activation of penumbral L and M cones {[}\protect\hyperlink{ref-Barrionuevo2016}{5},\protect\hyperlink{ref-Spitschan2015}{29},\protect\hyperlink{ref-Zele2019}{39}{]}, which was minimal (\(\le 1.5%
 \) contrast; less than splatter on the open-field cones) for melanopsin-directed stimuli.
-We note that the temporal frequency of our modulation (0.5Hz) is well below the range where penumbral cone activation can elicit visible percepts, and that such percepts fade after around 1 second (Spitschan et al., \protect\hyperlink{ref-Spitschan2015}{2015}), and do not typically affect pupil responses (Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}).
+We note that the temporal frequency of our modulation (0.5Hz) is well below the range where penumbral cone activation can elicit visible percepts, and that such percepts fade after around 1 second {[}\protect\hyperlink{ref-Spitschan2015}{29}{]}, and do not typically affect pupil responses {[}\protect\hyperlink{ref-Spitschan2014}{7}{]}.
 
@@
 Pupil responses to binocular temporal contrast modulations were examined in a factorial design that combined six ocular conditions and five temporal contrast levels: 6, 12, 24, 48 and 96\% of the available dynamic range.
-This design, similar to that used in our previous studies (Baker and Wade, \protect\hyperlink{ref-Baker2017}{2017}; Baker et al., \protect\hyperlink{ref-Baker2020}{2020}; Segala et al., \protect\hyperlink{ref-Segala2023}{2023}), was applied in four separate experiments, each with a different mode of photoreceptor stimulation.
+This design, similar to that used in previous studies {[}\protect\hyperlink{ref-Segala2023}{3},\protect\hyperlink{ref-Baker2017}{40},\protect\hyperlink{ref-Baker2020}{41}{]}, was applied in four separate experiments, each with a different mode of photoreceptor stimulation.
 In the first three conditions, the discs flickered at 0.5 Hz, in either a monocular, binocular or dichoptic arrangement.
@@
 Using a trackball, participants adjusted the angle in cone space to find their subjective isoluminant point, which resulted in changing the flickering intensity of the stimulus until the amplitude of the flicker appeared to be minimised.
-The result was used to modify the requested contrasts during stimulus preparation so as to account for individual differences affecting perceived illuminance, principally the L:M cone ratio (Carroll et al., \protect\hyperlink{ref-Carroll2002}{2002}; Hofer et al., \protect\hyperlink{ref-Hofer2005}{2005}).
+The result was used to modify the requested contrasts during stimulus preparation so as to account for individual differences affecting perceived illuminance, principally the L:M cone ratio {[}\protect\hyperlink{ref-Carroll2002}{42},\protect\hyperlink{ref-Hofer2005}{43}{]}.
 
@@
 
-The pupillometry data were analysed using the same method we used in our previous study (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}).
-The data were converted from mp4 videos to a csv text file using the Pupil Player software (Kassner et al., \protect\hyperlink{ref-Kassner2014}{2014}), which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
+The pupillometry data were analysed using the same method used in a previous study {[}\protect\hyperlink{ref-Segala2023}{3}{]}.
+The data were converted from mp4 videos to a csv text file using the Pupil Player software {[}\protect\hyperlink{ref-Kassner2014}{31}{]}, which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
 The individual data were then loaded into R for analysis, where a ten-second waveform for each trial in each eye was extracted (excluding the first two seconds after stimulus onset).
@@
 Finally, data were averaged across all participants to obtain the group results.
-We used coherent averaging and at each stage we excluded data points with a Mahalanobis distance exceeding \(D\) = 3 from the complex-valued mean (Baker, \protect\hyperlink{ref-Baker2021}{2021}).
+We used coherent averaging and at each stage we excluded data points with a Mahalanobis distance exceeding \(D\) = 3 from the complex-valued mean {[}\protect\hyperlink{ref-Baker2021}{44}{]}.
 For monocular stimulation, we confirmed that the consensual response was equivalent to the response in the stimulated eye.
@@
 
-To quantitatively summarise our data, we used the same model described in our previous study (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}).
-The model has the same general form as the first stage of the contrast gain control model proposed by Meese et al.
-(\protect\hyperlink{ref-Meese2006}{2006}), but omits the second stage.
-For the previous model that we used (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}), the exponent of the numerator and denominator had fixed values of 2 and (implicitly) 1.
+To quantitatively summarise our data, we used the same model described in a previous study {[}\protect\hyperlink{ref-Segala2023}{3}{]}.
+The model has the same general form as the first stage of the contrast gain control model proposed by Meese and colleagues {[}\protect\hyperlink{ref-Meese2006}{22}{]}, but omits the second stage.
+For the previous model that was used by Segala and colleagues {[}\protect\hyperlink{ref-Segala2023}{3}{]}, the exponent of the numerator and denominator had fixed values of 2 and (implicitly) 1.
 Here, we allow these parameters (called \emph{p} and \emph{q}) to be free, in order to permit different shapes of contrast response function, e.g.~accelerating or saturating.
@@
 
-The models were fit using a hierarchical Bayesian framework implemented in Stan (Carpenter et al., \protect\hyperlink{ref-Carpenter2017}{2017}).
+The models were fit using a hierarchical Bayesian framework implemented in Stan {[}\protect\hyperlink{ref-Carpenter2017}{45}{]}.
 The data for each photoreceptor type and response frequency was fit separately, for a total of 8 model fits.
 The prior for the \(\omega\) parameter was Gaussian, with a mean of 1 and standard deviation of 0.5.
-Priors for the other free parameters were also Gaussian, with mean values based on previous work (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}).
+Priors for the other free parameters were also Gaussian, with mean values based on previous work {[}\protect\hyperlink{ref-Segala2023}{3}{]}.
 We calculated over \ensuremath{10^{6}} posterior samples, and retained 10\% for plotting.
@@
 
-In contemporary models of binocular signal combination, the amount of binocular facilitation is determined by the magnitude of interocular suppression, with strong suppression reducing facilitation (Kingdom and Libenson, \protect\hyperlink{ref-Kingdom2015}{2015}).
+In contemporary models of binocular signal combination, the amount of binocular facilitation is determined by the magnitude of interocular suppression, with strong suppression reducing facilitation {[}\protect\hyperlink{ref-Kingdom2015}{46}{]}.
 We can estimate the strength of interocular suppression by measuring how much monocular responses are reduced when a dichoptic `mask' is shown to the other eye.
-In our paradigm, the two components flickered at different frequencies (0.5 and 0.4Hz) so that their responses remained distinct in the Fourier spectrum (e.g.~Busse et al., \protect\hyperlink{ref-Busse2009}{2009}).
+In our paradigm, the two components flickered at different frequencies (0.5 and 0.4Hz) so that their responses remained distinct in the Fourier spectrum {[}\protect\hyperlink{ref-Busse2009}{47}{]}.
 The yellow diamond symbols in Figure \ref{fig:FirstHarmonicPlots}a-d show the target responses in this condition, and in most cases were weaker than the monocular responses (red circles).
@@
 
-To estimate the extent of interocular suppression for each photoreceptor pathway, we fitted each data set using a Bayesian hierarchical implementation of a simple binocular combination model (Meese et al., \protect\hyperlink{ref-Meese2006}{2006}; Segala et al., \protect\hyperlink{ref-Segala2023}{2023}).
+To estimate the extent of interocular suppression for each photoreceptor pathway, we fitted each data set using a Bayesian hierarchical implementation of a simple binocular combination model {[}\protect\hyperlink{ref-Segala2023}{3},\protect\hyperlink{ref-Meese2006}{22}{]}.
 Our primary objective was to compare posterior distributions of the weight of interocular suppression, which are shown in Figure \ref{fig:FirstHarmonicPlots}e.
@@
 
-Finally, we inspected the response phase of our four stimulation conditions, given previous reports that these differ across pathways (Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}), and may be in antiphase for melanopsin and S-cone signals.
+Finally, we inspected the response phase of our four stimulation conditions, given previous reports that these differ across pathways {[}\protect\hyperlink{ref-Spitschan2014}{7}{]}, and may be in antiphase for melanopsin and S-cone signals.
 Figure \ref{fig:phaseplots} shows the phase angles for the first (a) and second (b) harmonic frequencies for binocular stimulation (monocular stimulation produced very similar results).
@@
 This is the first study to investigate binocular interactions in the melanopsin pathway directly.
-A previous meta-analysis (Spitschan and Cajochen, \protect\hyperlink{ref-Spitschan2019}{2019}) indicated that there may be a substantial binocular facilitation effect in the circadian pathway, as indexed by melatonin suppression (melatonin is a hormone released by the pineal gland; its production is suppressed by exposure to bright light, particularly when the melanopsin-containing ipRGCs are stimulated).
+A previous meta-analysis {[}\protect\hyperlink{ref-Spitschan2019}{48}{]} indicated that there may be a substantial binocular facilitation effect in the circadian pathway, as indexed by melatonin suppression (melatonin is a hormone released by the pineal gland; its production is suppressed by exposure to bright light, particularly when the melanopsin-containing ipRGCs are stimulated).
 In brief, monocular stimulation of the ipRGCs requires up to ten times the signal strength to produce an equivalent effect to binocular stimulation.
@@
 The explanation for this difference could be due to different anatomical pathways.
-Binocular combination in the circadian system likely takes place in the suprachiasmatic nucleus, whereas in the pupil constriction circuit the Edinger-Westphal nucleus is the most likely site of binocular integration (Mathôt, \protect\hyperlink{ref-Mathot2018}{2018}).
+Binocular combination in the circadian system likely takes place in the suprachiasmatic nucleus, whereas in the pupil constriction circuit the Edinger-Westphal nucleus is the most likely site of binocular integration {[}\protect\hyperlink{ref-Mathot2018}{9}{]}.
 Presumably these anatomical differences, and the practical constraints of the two systems, lead to differences in response.
 
-Our recent psychophysical work (Baker et al., \protect\hyperlink{ref-Baker2024}{2024}) has looked at binocular interactions in the L-M and S-cone pathways, and compared these to the light flux pathway.
-Using a contrast discrimination paradigm with spatial modulations of light flux and colour, Baker et al.
-(\protect\hyperlink{ref-Baker2024}{2024}) found equally strong interocular suppression in all three pathways.
+A recent psychophysical work {[}\protect\hyperlink{ref-Baker2024}{49}{]} has looked at binocular interactions in the L-M and S-cone pathways, and compared these to the light flux pathway.
+Using a contrast discrimination paradigm with spatial modulations of light flux and colour, the study {[}\protect\hyperlink{ref-Baker2024}{49}{]} found equally strong interocular suppression in all three pathways.
 This is rather different from our pupillometry results here, which demonstrate weaker suppression in the light flux and S-cone pathways than in the L-M pathway (see Figure \ref{fig:FirstHarmonicPlots}).
-However, the current experiments involve temporal modulations, which are quite distinct from the spatial modulations used in Baker et al.
-(\protect\hyperlink{ref-Baker2024}{2024}).
-Our other recent work (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}) has shown that temporal luminance modulations involve much weaker interocular suppression in the cortical response than do spatial luminance modulations (Baker and Wade, \protect\hyperlink{ref-Baker2017}{2017}).
+However, the current experiments involve temporal modulations, which are quite distinct from the spatial modulations used in the study by Baker and colleagues {[}\protect\hyperlink{ref-Baker2024}{49}{]}.
+Other recent work {[}\protect\hyperlink{ref-Segala2023}{3}{]} has shown that temporal luminance modulations involve much weaker interocular suppression in the cortical response than do spatial luminance modulations {[}\protect\hyperlink{ref-Baker2017}{40}{]}.
 These different normalization processes might reflect different priorities for spatial and temporal vision.
-Spatial vision aims to fuse images to provide binocular single vision, and benefits from `ocularity invariance' (Baker et al., \protect\hyperlink{ref-Baker2007}{2007}), in which visual appearance is constant when viewed with one eye or two.
-Temporal vision is critical for motion perception, which can involve alternative binocular computations, such as calculating velocity differences between the eyes (Kaestner et al., \protect\hyperlink{ref-Kaestner2019}{2019}).
+Spatial vision aims to fuse images to provide binocular single vision, and benefits from `ocularity invariance' {[}\protect\hyperlink{ref-Baker2007}{20}{]}, in which visual appearance is constant when viewed with one eye or two.
+Temporal vision is critical for motion perception, which can involve alternative binocular computations, such as calculating velocity differences between the eyes {[}\protect\hyperlink{ref-Kaestner2019}{50}{]}.
 Of course the present measurements were of pupil size, which may be subject to different anatomical and functional constraints from those in the cortex.
@@
 
-\hypertarget{acknowledgements}{%
-\section{Acknowledgements}\label{acknowledgements}}
-
-Supported by Biotechnology and Biological Sciences Research Council grant BB/V007580/1 awarded to DHB and ARW.
-
-\hypertarget{declaration-of-interests}{%
-\section{Declaration of interests}\label{declaration-of-interests}}
-
-The authors declare no competing interests.
-
 \hypertarget{references}{%
@@
 \hypertarget{refs}{}
+\leavevmode\hypertarget{ref-McDougal2015}{}%
+1. McDougal DH, Gamlin PD. 2015 Autonomic control of the eye. \emph{Comprehensive Physiology} \textbf{5}, 439--473. (doi:\href{https://doi.org/10.1002/cphy.c140014}{10.1002/cphy.c140014})
+
+\leavevmode\hypertarget{ref-Wyatt1981}{}%
+2.
+Wyatt HJ, Musselman JF.
+1981 Pupillary light reflex in humans: Evidence for an unbalanced pathway from nasal retina, and for signal cancellation in brainstem.
+\emph{Vision Res} \textbf{21}, 513--25.
+(doi:\href{https://doi.org/10.1016/0042-6989(81)90097-3}{10.1016/0042-6989(81)90097-3})
+
+\leavevmode\hypertarget{ref-Segala2023}{}%
+3.
+Segala FG, Bruno A, Martin JT, Aung MT, Wade AR, Baker DH.
+2023 Different rules for binocular combination of luminance flicker in cortical and subcortical pathways.
+\emph{eLife} \textbf{12}.
+(doi:\href{https://doi.org/10.7554/elife.87048}{10.7554/elife.87048})
+
+\leavevmode\hypertarget{ref-McDougal2010}{}%
+4.
+McDougal DH, Gamlin PD.
+2010 The influence of intrinsically-photosensitive retinal ganglion cells on the spectral sensitivity and response dynamics of the human pupillary light reflex.
+\emph{Vision Research} \textbf{50}, 72--87.
+(doi:\href{https://doi.org/10.1016/j.visres.2009.10.012}{10.1016/j.visres.2009.10.012})
+
+\leavevmode\hypertarget{ref-Barrionuevo2016}{}%
+5.
+Barrionuevo PA, Cao D.
+2016 Luminance and chromatic signals interact differently with melanopsin activation to control the pupil light response.
+\emph{Journal of Vision} \textbf{16(11)}, 29.
+(doi:\href{https://doi.org/10.1167/16.11.29}{10.1167/16.11.29})
+
+\leavevmode\hypertarget{ref-Murray2018}{}%
+6.
+Murray IJ, Kremers J, McKeefry D, Parry NRA.
+2018 Paradoxical pupil responses to isolated M-cone increments.
+\emph{Journal of the Optical Society of America A} \textbf{35}, B66--B71.
+(doi:\href{https://doi.org/10.1364/JOSAA.35.000B66}{10.1364/JOSAA.35.000B66})
+
+\leavevmode\hypertarget{ref-Spitschan2014}{}%
+7.
+Spitschan M, Jain S, Brainard DH, Aguirre GK.
+2014 Opponent melanopsin and s-cone signals in the human pupillary light response.
+\emph{Proceedings of the National Academy of Sciences} \textbf{111}, 15568--15572.
+(doi:\href{https://doi.org/10.1073/pnas.1400942111}{10.1073/pnas.1400942111})
+
+\leavevmode\hypertarget{ref-Woelders2018}{}%
+8.
+Woelders T, Leenheers T, Gordijn MCM, Hut RA, Beersma DGM, Wams EJ.
+2018 Melanopsin- and L-cone--induced pupil constriction is inhibited by S- and M-cones in humans.
+\emph{Proceedings of the National Academy of Sciences} \textbf{115}, 792--797.
+(doi:\href{https://doi.org/10.1073/pnas.1716281115}{10.1073/pnas.1716281115})
+
+\leavevmode\hypertarget{ref-Mathot2018}{}%
+9. Mathôt S. 2018 Pupillometry: Psychology, physiology, and function. \emph{J Cogn} \textbf{1}, 16. (doi:\href{https://doi.org/10.5334/joc.18}{10.5334/joc.18})
+
+\leavevmode\hypertarget{ref-Markwell2010}{}%
+10.
+Markwell EL, Feigl B, Zele AJ.
+2010 Intrinsically photosensitive melanopsin retinal ganglion cell contributions to the pupillary light reflex and circadian rhythm.
+\emph{Clinical and Experimental Optometry} \textbf{93}, 137--149.
+(doi:\href{https://doi.org/10.1111/j.1444-0938.2010.00479.x}{10.1111/j.1444-0938.2010.00479.x})
+
+\leavevmode\hypertarget{ref-Provencio2000}{}%
+11.
+Provencio I, Rodriguez IR, Jiang G, Hayes WP, Moreira EF, Rollag MD.
+2000 A Novel Human Opsin in the Inner Retina.
+\emph{Journal of Neuroscience} \textbf{20}, 600--605.
+(doi:\href{https://doi.org/10.1523/JNEUROSCI.20-02-00600.2000}{10.1523/JNEUROSCI.20-02-00600.2000})
+
+\leavevmode\hypertarget{ref-Panda2002}{}%
+12.
+Panda S, Sato TK, Castrucci AM, Rollag MD, DeGrip WJ, Hogenesch JB, Provencio I, Kay SA.
+2002 Melanopsin (opn4) requirement for normal light-induced circadian phase shifting.
+\emph{Science} \textbf{298}, 2213--2216.
+(doi:\href{https://doi.org/10.1126/science.1076848}{10.1126/science.1076848})
+
+\leavevmode\hypertarget{ref-Ruby2002}{}%
+13.
+Ruby NF, Brennan TJ, Xie X, Cao V, Franken P, Heller HC, O'Hara BF.
+2002 Role of melanopsin in circadian responses to light.
+\emph{Science} \textbf{298}, 2211--2213.
+(doi:\href{https://doi.org/10.1126/science.1076701}{10.1126/science.1076701})
+
+\leavevmode\hypertarget{ref-Dacey2003}{}%
+14.
+Dacey DM, Peterson BB, Robinson FR, Gamlin PD.
+2003 Fireworks in the primate retina: In vitro photodynamics reveals diverse lgn-projecting ganglion cell types.
+\emph{Neuron} \textbf{37}, 15--27.
+(doi:\href{https://doi.org/https://doi.org/10.1016/S0896-6273(02)01143-1}{https://doi.org/10.1016/S0896-6273(02)01143-1})
+
+\leavevmode\hypertarget{ref-Lucas2003}{}%
+15.
+Lucas RJ, Hattar S, Takao M, Berson DM, Foster RG, Yau K-W.
+2003 Diminished pupillary light reflex at high irradiances in melanopsin-knockout mice.
+\emph{Science} \textbf{299}, 245--247.
+(doi:\href{https://doi.org/10.1126/science.1077293}{10.1126/science.1077293})
+
+\leavevmode\hypertarget{ref-Gamlin2007}{}%
+16.
+Gamlin PDR, McDougal DH, Pokorny J, Smith VC, Yau K-W, Dacey DM.
+2007 Human and macaque pupil responses driven by melanopsin-containing retinal ganglion cells.
+\emph{Vision Research} \textbf{47}, 946--954.
+(doi:\href{https://doi.org/10.1016/j.visres.2006.12.015}{10.1016/j.visres.2006.12.015})
+
+\leavevmode\hypertarget{ref-Hubel1962}{}%
+17.
+Hubel DH, Wiesel TN.
+1962 Receptive fields, binocular interaction and functional architecture in the cat's visual cortex.
+\emph{J Physiol} \textbf{160}, 106--54.
+(doi:\href{https://doi.org/10.1113/jphysiol.1962.sp006837}{10.1113/jphysiol.1962.sp006837})
+
+\leavevmode\hypertarget{ref-Baker2018}{}%
+18.
+Baker DH, Lygo FA, Meese TS, Georgeson MA.
+2018 Binocular summation revisited: Beyond \(\sqrt{2}\).
+\emph{Psychol Bull} \textbf{144}, 1186--1199.
+(doi:\href{https://doi.org/10.1037/bul0000163}{10.1037/bul0000163})
+
+\leavevmode\hypertarget{ref-Campbell1965}{}%
+19. Campbell FW, Green DG. 1965 Monocular versus binocular visual acuity. \emph{Nature} \textbf{208}, 191--2. (doi:\href{https://doi.org/10.1038/208191a0}{10.1038/208191a0})
+
+\leavevmode\hypertarget{ref-Baker2007}{}%
+20.
+Baker DH, Meese TS, Georgeson MA.
+2007 Binocular interaction: Contrast matching and contrast discrimination are predicted by the same model.
+\emph{Spat Vis} \textbf{20}, 397--413.
+(doi:\href{https://doi.org/10.1163/156856807781503622}{10.1163/156856807781503622})
+
+\leavevmode\hypertarget{ref-Moradi2009}{}%
+21. Moradi F, Heeger DJ. 2009 Inter-ocular contrast normalization in human visual cortex. \emph{J Vis} \textbf{9}, 13.1--22. (doi:\href{https://doi.org/10.1167/9.3.13}{10.1167/9.3.13})
+
+\leavevmode\hypertarget{ref-Meese2006}{}%
+22. Meese TS, Georgeson MA, Baker DH. 2006 Binocular contrast vision at and above threshold. \emph{Journal of Vision} \textbf{6}, 1224--43. (doi:\href{https://doi.org/10.1167/6.11.7}{10.1167/6.11.7})
+
+\leavevmode\hypertarget{ref-Martin2022}{}%
+23.
+Martin JT, Pinto J, Bulte D, Spitschan M.
+2022 PyPlr: A versatile, integrated system of hardware and software for researching the human pupillary light reflex.
+\emph{Behavior Research Methods} \textbf{54}, 2720--2739.
+(doi:\href{https://doi.org/10.3758/s13428-021-01759-3}{10.3758/s13428-021-01759-3})
+
+\leavevmode\hypertarget{ref-Estevez1982}{}%
+24.
+Estévez O, Spekreijse H.
+1982 The "silent substitution" method in visual research.
+\emph{Vision Research} \textbf{22}, 681--691.
+(doi:\href{https://doi.org/10.1016/0042-6989(82)90104-3}{10.1016/0042-6989(82)90104-3})
+
+\leavevmode\hypertarget{ref-Shapiro1996}{}%
+25.
+Shapiro AG, Pokorny J, Smith VC.
+1996 Conerod receptor spaces with illustrations that use CRT phosphor and light-emitting-diode spectra.
+\emph{Journal of the Optical Society of America A} \textbf{13}, 2319.
+(doi:\href{https://doi.org/10.1364/josaa.13.002319}{10.1364/josaa.13.002319})
+
+\leavevmode\hypertarget{ref-Spitschan2018}{}%
+26.
+Spitschan M, Woelders T.
+2018 The Method of Silent Substitution for Examining Melanopsin Contributions to Pupil Control.
+\emph{Frontiers in Neurology} \textbf{9}.
+(doi:\href{https://doi.org/10.3389/fneur.2018.00941}{10.3389/fneur.2018.00941})
+
+\leavevmode\hypertarget{ref-Martin2023}{}%
+27.
+Martin JT, Boynton GM, Baker DH, Wade AR, Spitschan M.
+2023 PySilSub: An open-source python toolbox for implementing the method of silent substitution in vision and nonvisual photoreception research.
+\emph{Journal of Vision} \textbf{23}, 10.
+(doi:\href{https://doi.org/10.1167/jov.23.7.10}{10.1167/jov.23.7.10})
+
+\leavevmode\hypertarget{ref-Stockman2000}{}%
+28.
+Stockman A, Sharpe LT.
+2000 The spectral sensitivities of the middle- and long-wavelength-sensitive cones derived from measurements in observers of known genotype.
+\emph{Vision Res} \textbf{40}, 1711--37.
+(doi:\href{https://doi.org/10.1016/s0042-6989(00)00021-3}{10.1016/s0042-6989(00)00021-3})
+
+\leavevmode\hypertarget{ref-Spitschan2015}{}%
+29.
+Spitschan M, Aguirre GK, Brainard DH.
+2015 Selective stimulation of penumbral cones reveals perception in the shadow of retinal blood vessels.
+\emph{PLoS One} \textbf{10}, e0124328.
+(doi:\href{https://doi.org/10.1371/journal.pone.0124328}{10.1371/journal.pone.0124328})
+
+\leavevmode\hypertarget{ref-Zele2018}{}%
+30.
+Zele AJ, Feigl B, Adhikari P, Maynard ML, Cao D.
+2018 Melanopsin photoreception contributes to human visual detection, temporal and colour processing.
+\emph{Scientific Reports} \textbf{8}.
+(doi:\href{https://doi.org/10.1038/s41598-018-22197-w}{10.1038/s41598-018-22197-w})
+
+\leavevmode\hypertarget{ref-Kassner2014}{}%
+31.
+Kassner M, Patera W, Bulling A.
+2014 Pupil: An open source platform for pervasive eye tracking and mobile gaze-based interaction.
+In \emph{Proceedings of the 2014 ACM international joint conference on pervasive and ubiquitous computing: Adjunct publication}, ACM.
+(doi:\href{https://doi.org/10.1145/2638728.2641695}{10.1145/2638728.2641695})
+
+\leavevmode\hypertarget{ref-Norcia2015}{}%
+32.
+Norcia AM, Appelbaum LG, Ales JM, Cottereau BR, Rossion B.
+2015 The steady-state visual evoked potential in vision research: A review.
+\emph{Journal of Vision} \textbf{15(6)}, 4.
+(doi:\href{https://doi.org/10.1167/15.6.4}{10.1167/15.6.4})
+
+\leavevmode\hypertarget{ref-Pokorny1987}{}%
+33. Pokorny J, Smith VC, Lutze M. 1987 Aging of the human lens. \emph{Applied Optics} \textbf{26}, 1437. (doi:\href{https://doi.org/10.1364/ao.26.001437}{10.1364/ao.26.001437})
+
+\leavevmode\hypertarget{ref-Stockman1999}{}%
+34.
+Stockman A, Sharpe LT, Fach C.
+1999 The spectral sensitivity of the human short-wavelength sensitive cones derived from thresholds and color matches.
+\emph{Vision Research} \textbf{39}, 2901--2927.
+(doi:\href{https://doi.org/https://doi.org/10.1016/S0042-6989(98)00225-9}{https://doi.org/10.1016/S0042-6989(98)00225-9})
+
+\leavevmode\hypertarget{ref-Bone1988}{}%
+35.
+Bone RA, Landrum JT, Fernandez L, Tarsis SL.
+1988 Analysis of the macular pigment by HPLC: Retinal distribution and age study.
+\emph{Investigative Ophthalmology \& Visual Science} \textbf{29}, 843--849.
+
+\leavevmode\hypertarget{ref-CIE2006}{}%
+36. CIE. 2006 Fundamental chromaticity diagram with physiological axes.
+
+\leavevmode\hypertarget{ref-CIE2018}{}%
+37. CIE. 2018 CIE system for metrology of optical radiation for ipRGC-influenced responses to light. (doi:\href{https://doi.org/10.25039/S026.2018}{10.25039/S026.2018})
+
+\leavevmode\hypertarget{ref-Trieschmann2007}{}%
+38.
+Trieschmann M, Kuijk FJGM van, Alexander R, Hermans P, Luthert P, Bird AC, Pauleikhoff D.
+2007 Macular pigment in the human retina: Histological evaluation of localization and distribution.
+\emph{Eye} \textbf{22}, 132--137.
+(doi:\href{https://doi.org/10.1038/sj.eye.6702780}{10.1038/sj.eye.6702780})
+
+\leavevmode\hypertarget{ref-Zele2019}{}%
+39.
+Zele AJ, Adhikari P, Cao D, Feigl B.
+2019 Melanopsin driven enhancement of cone-mediated visual processing.
+\emph{Vision Res} \textbf{160}, 72--81.
+(doi:\href{https://doi.org/10.1016/j.visres.2019.04.009}{10.1016/j.visres.2019.04.009})
+
+\leavevmode\hypertarget{ref-Baker2017}{}%
+40.
+Baker DH, Wade AR.
+2017 Evidence for an optimal algorithm underlying signal combination in human visual cortex.
+\emph{Cereb Cortex} \textbf{27}, 254--264.
+(doi:\href{https://doi.org/10.1093/cercor/bhw395}{10.1093/cercor/bhw395})
+
+\leavevmode\hypertarget{ref-Baker2020}{}%
+41.
+Baker DH, Vilidaite G, McClarnon E, Valkova E, Bruno A, Millman RE.
+2020 Binaural summation of amplitude modulation involves weak interaural suppression.
+\emph{Sci Rep} \textbf{10}, 3560.
+(doi:\href{https://doi.org/10.1038/s41598-020-60602-5}{10.1038/s41598-020-60602-5})
+
+\leavevmode\hypertarget{ref-Carroll2002}{}%
+42.
+Carroll J, Neitz J, Neitz M.
+2002 Estimates of L:M cone ratio from ERG flicker photometry and genetics.
+\emph{Journal of Vision} \textbf{2}, 1.
+(doi:\href{https://doi.org/10.1167/2.8.1}{10.1167/2.8.1})
+
+\leavevmode\hypertarget{ref-Hofer2005}{}%
+43.
+Hofer H, Carroll J, Neitz J, Neitz M, Williams DR.
+2005 Organization of the human trichromatic cone mosaic.
+\emph{The Journal of Neuroscience} \textbf{25}, 9669--9679.
+(doi:\href{https://doi.org/10.1523/jneurosci.2414-05.2005}{10.1523/jneurosci.2414-05.2005})
+
 \leavevmode\hypertarget{ref-Baker2021}{}%
-Baker DH (2021) Statistical analysis of periodic data in neuroscience. Neurons, Behavior, Data analysis, and Theory 5 Available at: \url{https://doi.org/10.51628\%2F001c.27680}.
+44.
+Baker DH.
+2021 Statistical analysis of periodic data in neuroscience.
+\emph{Neurons, Behavior, Data analysis, and Theory} \textbf{5}.
+(doi:\href{https://doi.org/10.51628/001c.27680}{10.51628/001c.27680})
+
+\leavevmode\hypertarget{ref-Carpenter2017}{}%
+45. Carpenter B \emph{et al.} 2017 Stan: A probabilistic programming language. \emph{J Stat Softw} \textbf{76}. (doi:\href{https://doi.org/10.18637/jss.v076.i01}{10.18637/jss.v076.i01})
+
+\leavevmode\hypertarget{ref-Kingdom2015}{}%
+46.
+Kingdom FAA, Libenson L.
+2015 Dichoptic color saturation mixture: Binocular luminance contrast promotes perceptual averaging.
+\emph{J Vis} \textbf{15}, 2.
+(doi:\href{https://doi.org/10.1167/15.5.2}{10.1167/15.5.2})
+
+\leavevmode\hypertarget{ref-Busse2009}{}%
+47.
+Busse L, Wade AR, Carandini M.
+2009 Representation of concurrent stimuli by population activity in visual cortex.
+\emph{Neuron} \textbf{64}, 931--42.
+(doi:\href{https://doi.org/10.1016/j.neuron.2009.11.004}{10.1016/j.neuron.2009.11.004})
+
+\leavevmode\hypertarget{ref-Spitschan2019}{}%
+48.
+Spitschan M, Cajochen C.
+2019 Binocular facilitation in light-mediated melatonin suppression?
+\emph{J Pineal Res} \textbf{67}, e12602.
+(doi:\href{https://doi.org/10.1111/jpi.12602}{10.1111/jpi.12602})
 
 \leavevmode\hypertarget{ref-Baker2024}{}%
-Baker DH, Hansford KJ, Segala FG, Morsi AY, Huxley RJ, Martin JT, Rockman M, Wade AR (2024) Binocular integration of chromatic and luminance signals. J Vis 24(12):7.
-
-\leavevmode\hypertarget{ref-Baker2018}{}%
-Baker DH, Lygo FA, Meese TS, Georgeson MA (2018) Binocular summation revisited: Beyond \(\sqrt{2}\). Psychol Bull 144:1186--1199.
-
-\leavevmode\hypertarget{ref-Baker2007}{}%
-Baker DH, Meese TS, Georgeson MA (2007) Binocular interaction: Contrast matching and contrast discrimination are predicted by the same model. Spat Vis 20:397--413.
-
-\leavevmode\hypertarget{ref-Baker2020}{}%
-Baker DH, Vilidaite G, McClarnon E, Valkova E, Bruno A, Millman RE (2020) Binaural summation of amplitude modulation involves weak interaural suppression. Sci Rep 10:3560.
-
-\leavevmode\hypertarget{ref-Baker2017}{}%
-Baker DH, Wade AR (2017) Evidence for an optimal algorithm underlying signal combination in human visual cortex. Cereb Cortex 27:254--264.
-
-\leavevmode\hypertarget{ref-Barrionuevo2016}{}%
-Barrionuevo PA, Cao D (2016) Luminance and chromatic signals interact differently with melanopsin activation to control the pupil light response. Journal of Vision 16(11):29.
-
-\leavevmode\hypertarget{ref-Bone1988}{}%
-Bone RA, Landrum JT, Fernandez L, Tarsis SL (1988) Analysis of the macular pigment by HPLC: Retinal distribution and age study. Investigative Ophthalmology \& Visual Science 29:843--849.
-
-\leavevmode\hypertarget{ref-Busse2009}{}%
-Busse L, Wade AR, Carandini M (2009) Representation of concurrent stimuli by population activity in visual cortex. Neuron 64:931--942.
-
-\leavevmode\hypertarget{ref-Campbell1965}{}%
-Campbell FW, Green DG (1965) Monocular versus binocular visual acuity. Nature 208:191--192.
-
-\leavevmode\hypertarget{ref-Carpenter2017}{}%
-Carpenter B, Gelman A, Hoffman MD, Lee D, Goodrich B, Betancourt M, Brubaker MA, Guo J, Li P, Riddell A (2017) Stan: A probabilistic programming language. J Stat Softw 76.
-
-\leavevmode\hypertarget{ref-Carroll2002}{}%
-Carroll J, Neitz J, Neitz M (2002) Estimates of L:M cone ratio from ERG flicker photometry and genetics.
-Journal of Vision 2:1 Available at: \url{https://doi.org/10.1167/2.8.1} {[}Accessed June 5, 2023{]}.
-
-\leavevmode\hypertarget{ref-CIE2006}{}%
-CIE (2006) Fundamental chromaticity diagram with physiological axes. CIE Central Bureau. Available at: \url{https://cie.co.at/publications/fundamental-chromaticity-diagram-physiological-axes-part-1}.
-
-\leavevmode\hypertarget{ref-CIE2018}{}%
-CIE (2018) CIE system for metrology of optical radiation for ipRGC-influenced responses to light. CIE Central Bureau. Available at: \url{https://doi.org/10.25039/S026.2018}.
-
-\leavevmode\hypertarget{ref-Dacey2003}{}%
-Dacey DM, Peterson BB, Robinson FR, Gamlin PD (2003) Fireworks in the primate retina: In vitro photodynamics reveals diverse lgn-projecting ganglion cell types.
-Neuron 37:15--27 Available at: \url{https://www.sciencedirect.com/science/article/pii/S0896627302011431}.
-
-\leavevmode\hypertarget{ref-Estevez1982}{}%
-Estévez O, Spekreijse H (1982) The "silent substitution" method in visual research.
-Vision Research 22:681--691 Available at: \url{https://www.sciencedirect.com/science/article/pii/0042698982901043} {[}Accessed July 18, 2023{]}.
-
-\leavevmode\hypertarget{ref-Gamlin2007}{}%
-Gamlin PDR, McDougal DH, Pokorny J, Smith VC, Yau K-W, Dacey DM (2007) Human and macaque pupil responses driven by melanopsin-containing retinal ganglion cells.
-Vision Research 47:946--954 Available at: \url{https://www.sciencedirect.com/science/article/pii/S0042698906005682} {[}Accessed July 18, 2023{]}.
-
-\leavevmode\hypertarget{ref-Hofer2005}{}%
-Hofer H, Carroll J, Neitz J, Neitz M, Williams DR (2005) Organization of the human trichromatic cone mosaic.
-The Journal of Neuroscience 25:9669--9679 Available at: \url{https://doi.org/10.1523\%2Fjneurosci.2414-05.2005}.
-
-\leavevmode\hypertarget{ref-Hubel1962}{}%
-Hubel DH, Wiesel TN (1962) Receptive fields, binocular interaction and functional architecture in the cat's visual cortex. J Physiol 160:106--154.
+49.
+Baker DH, Hansford KJ, Segala FG, Morsi AY, Huxley RJ, Martin JT, Rockman M, Wade AR.
+2024 Binocular integration of chromatic and luminance signals.
+\emph{J Vis} \textbf{24(12)}, 7.
+(doi:\href{https://doi.org/10.1167/jov.24.12.7}{10.1167/jov.24.12.7})
 
 \leavevmode\hypertarget{ref-Kaestner2019}{}%
-Kaestner M, Maloney RT, Wailes-Newson KH, Bloj M, Harris JM, Morland AB, Wade AR (2019) Asymmetries between achromatic and chromatic extraction of 3D motion signals.
-Proc Natl Acad Sci U S A 116:13631--13640.
-
-\leavevmode\hypertarget{ref-Kassner2014}{}%
-Kassner M, Patera W, Bulling A (2014) Pupil: An open source platform for pervasive eye tracking and mobile gaze-based interaction.
-In: Proceedings of the 2014 ACM international joint conference on pervasive and ubiquitous computing: Adjunct publication.
-ACM.
-Available at: \url{https://doi.org/10.1145\%2F2638728.2641695}.
-
-\leavevmode\hypertarget{ref-Kingdom2015}{}%
-Kingdom FAA, Libenson L (2015) Dichoptic color saturation mixture: Binocular luminance contrast promotes perceptual averaging. J Vis 15:2.
-
-\leavevmode\hypertarget{ref-Lucas2003}{}%
-Lucas RJ, Hattar S, Takao M, Berson DM, Foster RG, Yau K-W (2003) Diminished pupillary light reflex at high irradiances in melanopsin-knockout mice.
-Science 299:245--247 Available at: \url{https://doi.org/10.1126\%2Fscience.1077293}.
-
-\leavevmode\hypertarget{ref-Markwell2010}{}%
-Markwell EL, Feigl B, Zele AJ (2010) Intrinsically photosensitive melanopsin retinal ganglion cell contributions to the pupillary light reflex and circadian rhythm.
-Clinical and Experimental Optometry 93:137--149 Available at: \url{https://doi.org/10.1111\%2Fj.1444-0938.2010.00479.x}.
-
-\leavevmode\hypertarget{ref-Martin2023}{}%
-Martin JT, Boynton GM, Baker DH, Wade AR, Spitschan M (2023) PySilSub: An open-source python toolbox for implementing the method of silent substitution in vision and nonvisual photoreception research.
-Journal of Vision 23:10 Available at: \url{https://doi.org/10.1167\%2Fjov.23.7.10}.
-
-\leavevmode\hypertarget{ref-Martin2022}{}%
-Martin JT, Pinto J, Bulte D, Spitschan M (2022) PyPlr: A versatile, integrated system of hardware and software for researching the human pupillary light reflex.
-Behavior Research Methods 54:2720--2739.
-
-\leavevmode\hypertarget{ref-Mathot2018}{}%
-Mathôt S (2018) Pupillometry: Psychology, physiology, and function. J Cogn 1:16.
-
-\leavevmode\hypertarget{ref-McDougal2010}{}%
-McDougal DH, Gamlin PD (2010) The influence of intrinsically-photosensitive retinal ganglion cells on the spectral sensitivity and response dynamics of the human pupillary light reflex.
-Vision Research 50:72--87 Available at: \url{https://www.sciencedirect.com/science/article/pii/S0042698909004763} {[}Accessed July 18, 2023{]}.
-
-\leavevmode\hypertarget{ref-McDougal2015}{}%
-McDougal DH, Gamlin PD (2015) Autonomic control of the eye. Comprehensive Physiology 5:439--473.
-
-\leavevmode\hypertarget{ref-Meese2006}{}%
-Meese TS, Georgeson MA, Baker DH (2006) Binocular contrast vision at and above threshold. Journal of Vision 6:1224--1243.
-
-\leavevmode\hypertarget{ref-Moradi2009}{}%
-Moradi F, Heeger DJ (2009) Inter-ocular contrast normalization in human visual cortex. J Vis 9:13.1--22.
-
-\leavevmode\hypertarget{ref-Murray2018}{}%
-Murray IJ, Kremers J, McKeefry D, Parry NRA (2018) Paradoxical pupil responses to isolated M-cone increments.
-Journal of the Optical Society of America A 35:B66--B71 Available at: \url{https://opg.optica.org/josaa/abstract.cfm?uri=josaa-35-4-B66} {[}Accessed July 18, 2023{]}.
-
-\leavevmode\hypertarget{ref-Norcia2015}{}%
-Norcia AM, Appelbaum LG, Ales JM, Cottereau BR, Rossion B (2015) The steady-state visual evoked potential in vision research: A review. Journal of Vision 15(6):4.
-
-\leavevmode\hypertarget{ref-Panda2002}{}%
-Panda S, Sato TK, Castrucci AM, Rollag MD, DeGrip WJ, Hogenesch JB, Provencio I, Kay SA (2002) Melanopsin (opn4) requirement for normal light-induced circadian phase shifting.
-Science 298:2213--2216 Available at: \url{https://doi.org/10.1126\%2Fscience.1076848}.
-
-\leavevmode\hypertarget{ref-Pokorny1987}{}%
-Pokorny J, Smith VC, Lutze M (1987) Aging of the human lens. Applied Optics 26:1437 Available at: \url{http://dx.doi.org/10.1364/AO.26.001437}.
-
-\leavevmode\hypertarget{ref-Provencio2000}{}%
-Provencio I, Rodriguez IR, Jiang G, Hayes WP, Moreira EF, Rollag MD (2000) A Novel Human Opsin in the Inner Retina.
-Journal of Neuroscience 20:600--605 Available at: \url{https://www.jneurosci.org/content/20/2/600} {[}Accessed July 18, 2023{]}.
-
-\leavevmode\hypertarget{ref-Ruby2002}{}%
-Ruby NF, Brennan TJ, Xie X, Cao V, Franken P, Heller HC, O'Hara BF (2002) Role of melanopsin in circadian responses to light.
-Science 298:2211--2213 Available at: \url{https://doi.org/10.1126\%2Fscience.1076701}.
-
-\leavevmode\hypertarget{ref-Segala2023}{}%
-Segala FG, Bruno A, Martin JT, Aung MT, Wade AR, Baker DH (2023) Different rules for binocular combination of luminance flicker in cortical and subcortical pathways.
-eLife 12 Available at: \url{https://doi.org/10.7554\%2Felife.87048}.
-
-\leavevmode\hypertarget{ref-Shapiro1996}{}%
-Shapiro AG, Pokorny J, Smith VC (1996) Conerod receptor spaces with illustrations that use CRT phosphor and light-emitting-diode spectra.
-Journal of the Optical Society of America A 13:2319 Available at: \url{https://doi.org/10.1364\%2Fjosaa.13.002319}.
-
-\leavevmode\hypertarget{ref-Spitschan2015}{}%
-Spitschan M, Aguirre GK, Brainard DH (2015) Selective stimulation of penumbral cones reveals perception in the shadow of retinal blood vessels. PLoS One 10:e0124328.
-
-\leavevmode\hypertarget{ref-Spitschan2019}{}%
-Spitschan M, Cajochen C (2019) Binocular facilitation in light-mediated melatonin suppression? J Pineal Res 67:e12602.
-
-\leavevmode\hypertarget{ref-Spitschan2014}{}%
-Spitschan M, Jain S, Brainard DH, Aguirre GK (2014) Opponent melanopsin and s-cone signals in the human pupillary light response.
-Proceedings of the National Academy of Sciences 111:15568--15572 Available at: \url{https://doi.org/10.1073\%2Fpnas.1400942111}.
-
-\leavevmode\hypertarget{ref-Spitschan2018}{}%
-Spitschan M, Woelders T (2018) The Method of Silent Substitution for Examining Melanopsin Contributions to Pupil Control. Frontiers in Neurology 9.
-
-\leavevmode\hypertarget{ref-Stockman2000}{}%
-Stockman A, Sharpe LT (2000) The spectral sensitivities of the middle- and long-wavelength-sensitive cones derived from measurements in observers of known genotype. Vision Res 40:1711--1737.
-
-\leavevmode\hypertarget{ref-Stockman1999}{}%
-Stockman A, Sharpe LT, Fach C (1999) The spectral sensitivity of the human short-wavelength sensitive cones derived from thresholds and color matches.
-Vision Research 39:2901--2927 Available at: \url{https://www.sciencedirect.com/science/article/pii/S0042698998002259}.
-
-\leavevmode\hypertarget{ref-Trieschmann2007}{}%
-Trieschmann M, Kuijk FJGM van, Alexander R, Hermans P, Luthert P, Bird AC, Pauleikhoff D (2007) Macular pigment in the human retina: Histological evaluation of localization and distribution.
-Eye 22:132--137 Available at: \url{http://dx.doi.org/10.1038/sj.eye.6702780}.
-
-\leavevmode\hypertarget{ref-Woelders2018}{}%
-Woelders T, Leenheers T, Gordijn MCM, Hut RA, Beersma DGM, Wams EJ (2018) Melanopsin- and L-cone--induced pupil constriction is inhibited by S- and M-cones in humans.
-Proceedings of the National Academy of Sciences 115:792--797 Available at: \url{https://www.pnas.org/doi/full/10.1073/pnas.1716281115} {[}Accessed July 18, 2023{]}.
-
-\leavevmode\hypertarget{ref-Wyatt1981}{}%
-Wyatt HJ, Musselman JF (1981) Pupillary light reflex in humans: Evidence for an unbalanced pathway from nasal retina, and for signal cancellation in brainstem. Vision Res 21:513--525.
-
-\leavevmode\hypertarget{ref-Zele2019}{}%
-Zele AJ, Adhikari P, Cao D, Feigl B (2019) Melanopsin driven enhancement of cone-mediated visual processing. Vision Res 160:72--81.
-
-\leavevmode\hypertarget{ref-Zele2018}{}%
-Zele AJ, Feigl B, Adhikari P, Maynard ML, Cao D (2018) Melanopsin photoreception contributes to human visual detection, temporal and colour processing.
-Scientific Reports 8 Available at: \url{https://doi.org/10.1038\%2Fs41598-018-22197-w}.
+50.
+Kaestner M, Maloney RT, Wailes-Newson KH, Bloj M, Harris JM, Morland AB, Wade AR.
+2019 Asymmetries between achromatic and chromatic extraction of 3D motion signals.
+\emph{Proc Natl Acad Sci U S A} \textbf{116}, 13631--13640.
+(doi:\href{https://doi.org/10.1073/pnas.1817202116}{10.1073/pnas.1817202116})
 

### 2025-02-25 manuscript.Rmd
Add files via upload

@@
 All participants had normal or corrected to normal vision, no known abnormalities of binocular or colour vision, and gave written informed consent.
-Our procedures were approved by the Ethics Committee of the Department of Psychology at the XXX (identification number 184).
+Our procedures were approved by the Ethics Committee of the REDACTED FOR DOUBLE ANONYMOUS PEER REVIEW (identification number 184).
 
@@
 For all experiments, we used a bootstrapping procedure with `r nbootstraps` iterations to estimate standard errors across participants.
-All analysis and figure construction was conducted using a single R-script, available online, making this study fully computationally reproducible: https://osf.io/gdvt4/.
+All analysis and figure construction was conducted using a single R-script, available online, making this study fully computationally reproducible: REDACTED FOR DOUBLE ANONYMOUS PEER REVIEW.
 

### 2025-02-25 manuscript.tex
Add files via upload

@@
 For all experiments, we used a bootstrapping procedure with \ensuremath{10^{4}} iterations to estimate standard errors across participants.
-All analysis and figure construction was conducted using a single R-script, available online, making this study fully computationally reproducible: \url{https://osf.io/gdvt4/}.
+All analysis and figure construction was conducted using a single R-script, available online, making this study fully computationally reproducible: REDACTED FOR DOUBLE ANONYMOUS PEER REVIEW.
 

### 2025-02-28 manuscript.Rmd
Changes

--- 2025-02-10 manuscript.Rmd
@@
 linkcolor: black
-csl: elife.csl
+csl: investigative-ophthalmology-and-visual-science.csl
 header-includes:
@@
 The anatomical pathway from the retina to the subcortical nuclei controlling the pupillary light response (PLR) is well established: it includes the Pretectal Olivary nucleus (PON), the Superior Cervical ganglion and the Edinger-Westphal nucleus, which project to the iris sphincter muscles that directly control the pupil size [@McDougal2015].
-Evidence of a binocular component to the PLR is shown by the consensual response of the pupil [stimulation of one eye will cause constriction of the other eye\; @Wyatt1981].
+Evidence of a binocular component to the PLR is shown by the consensual response of the pupil (stimulation of one eye will cause constriction of the other eye) [@Wyatt1981].
 The anatomical segregation of the subcortical pathway from the rest of the brain means that this binocular combination of signals must occur independently of the cortical processes of binocular integration required for visual perception.
@@
 The results are interpreted using a contemporary model of binocular vision [@Meese2006] implemented within a hierarchical Bayesian framework.
-These results previously formed part of a doctoral thesis by the first author [@SegalaThesis2023].
 
@@
 Each primary was also linearized using a polynomial fit (see Figure \@ref(fig:primarylinearity) for details).
-We used the @Stockman2000 10-degree cone fundamentals, and estimates of melanopsin absorbance spectra from CIE S 026 [discussed in @Martin2023] to calculate $\alpha$-opic irradiance.
+We used the 10-degree cone fundamentals [@Stockman2000], and estimates of melanopsin absorbance spectra from CIE S 026 (discussed in a previous paper [@Martin2023]) to calculate $\alpha$-opic irradiance.
 
@@
 A schematic of the stimulation system is shown in Figure \@ref(fig:spectraplots)a.
-Pupillometry data were collected using a binocular Pupil Core eye-tracker headset [Pupil Labs GmbH, Berlin, Germany, @Kassner2014] running at 120 Hz, and the signals were recorded with the Pupil Capture software.
+Pupillometry data were collected using a binocular Pupil Core eye-tracker headset (Pupil Labs GmbH, Berlin, Germany [@Kassner2014]) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
 
@@
 To quantitatively summarise our data, we used the same model described in our previous study [@Segala2023].
-The model has the same general form as the first stage of the contrast gain control model proposed by @Meese2006, but omits the second stage.
+The model has the same general form as the first stage of the contrast gain control model proposed by Meese and colleagues [@Meese2006], but omits the second stage.
 For the previous model that we used [@Segala2023], the exponent of the numerator and denominator had fixed values of 2 and (implicitly) 1.
@@
 Our recent psychophysical work [@Baker2024] has looked at binocular interactions in the L-M and S-cone pathways, and compared these to the light flux pathway.
-Using a contrast discrimination paradigm with spatial modulations of light flux and colour, @Baker2024 found equally strong interocular suppression in all three pathways.
+Using a contrast discrimination paradigm with spatial modulations of light flux and colour, we found equally strong interocular suppression in all three pathways [@Baker2024].
 This is rather different from our pupillometry results here, which demonstrate weaker suppression in the light flux and S-cone pathways than in the L-M pathway (see Figure \@ref(fig:FirstHarmonicPlots)).
-However, the current experiments involve temporal modulations, which are quite distinct from the spatial modulations used in @Baker2024.
+However, the current experiments involve temporal modulations, which are quite distinct from the spatial modulations used in our previous work [@Baker2024].
 Our other recent work [@Segala2023] has shown that temporal luminance modulations involve much weaker interocular suppression in the cortical response than do spatial luminance modulations [@Baker2017].

### 2025-02-28 manuscript.tex
Changes

--- 2025-02-10 manuscript.tex
@@
 
-The autonomic nervous system regulates many involuntary bodily processes, including the constriction and dilation of the pupils in response to light (McDougal and Gamlin, \protect\hyperlink{ref-McDougal2015}{2015}).
-The anatomical pathway from the retina to the subcortical nuclei controlling the pupillary light response (PLR) is well established: it includes the Pretectal Olivary nucleus (PON), the Superior Cervical ganglion and the Edinger-Westphal nucleus, which project to the iris sphincter muscles that directly control the pupil size (McDougal and Gamlin, \protect\hyperlink{ref-McDougal2015}{2015}).
-Evidence of a binocular component to the PLR is shown by the consensual response of the pupil (stimulation of one eye will cause constriction of the other eye; Wyatt and Musselman, \protect\hyperlink{ref-Wyatt1981}{1981}).
-The anatomical segregation of the subcortical pathway from the rest of the brain means that this binocular combination of signals must occur independently of the cortical processes of binocular integration required for visual perception.
-Our recent work (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}) has shown that the algorithm underlying binocular combination of light in the pupil pathway differs from that in the cortex.
+The autonomic nervous system regulates many involuntary bodily processes, including the constriction and dilation of the pupils in response to light.\textsuperscript{\protect\hyperlink{ref-McDougal2015}{1}} The anatomical pathway from the retina to the subcortical nuclei controlling the pupillary light response (PLR) is well established: it includes the Pretectal Olivary nucleus (PON), the Superior Cervical ganglion and the Edinger-Westphal nucleus, which project to the iris sphincter muscles that directly control the pupil size.\textsuperscript{\protect\hyperlink{ref-McDougal2015}{1}} Evidence of a binocular component to the PLR is shown by the consensual response of the pupil (stimulation of one eye will cause constriction of the other eye).\textsuperscript{\protect\hyperlink{ref-Wyatt1981}{2}} The anatomical segregation of the subcortical pathway from the rest of the brain means that this binocular combination of signals must occur independently of the cortical processes of binocular integration required for visual perception.
+Our recent work\textsuperscript{\protect\hyperlink{ref-Segala2023}{3}} has shown that the algorithm underlying binocular combination of light in the pupil pathway differs from that in the cortex.
 Here we extend this paradigm to compare binocular combination in different photoreceptor pathways that feed into the autonomic nervous system.
 
-Different classes of retinal photoreceptors, including cones, rods and melanopsin-containing intrinsically photosensitive retinal ganglion cells (ipRGCs), are directly involved in controlling and maintaining the size of the pupils (e.g.~McDougal and Gamlin, \protect\hyperlink{ref-McDougal2010}{2010}; Barrionuevo and Cao, \protect\hyperlink{ref-Barrionuevo2016}{2016}; Murray et al., \protect\hyperlink{ref-Murray2018}{2018}; Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}; Woelders et al., \protect\hyperlink{ref-Woelders2018}{2018}).
-Cones drive the initial rapid constriction of the pupils (Mathôt, \protect\hyperlink{ref-Mathot2018}{2018}), while the slower and longer activation of the ipRGCs maintains constriction over a prolonged period of time and regulates the post-illumination pupillary response (Markwell et al., \protect\hyperlink{ref-Markwell2010}{2010}; McDougal and Gamlin, \protect\hyperlink{ref-McDougal2010}{2010}).
-The ipRGCs are a recently discovered photoreceptor class (Provencio et al., \protect\hyperlink{ref-Provencio2000}{2000}) that express the photopigment melanopsin, and are involved in the regulation of the circadian rhythm (Panda et al., \protect\hyperlink{ref-Panda2002}{2002}; Ruby et al., \protect\hyperlink{ref-Ruby2002}{2002}), forming a major input to the PON (Dacey et al., \protect\hyperlink{ref-Dacey2003}{2003}).
-The first direct evidence of the involvement of the ipRGCs in the PLR was shown in melanopsin knockout rats by Lucas et al.
-(\protect\hyperlink{ref-Lucas2003}{2003}), resulting in the loss of the intrinsic photosensitivity of the cells and a reduced pupil constriction.
-Similar behaviour was later observed in primates and humans (Gamlin et al., \protect\hyperlink{ref-Gamlin2007}{2007}) using silent substitution (see Methods), where it was demonstrated that the PLR continues during light presentation even when cone and rod signalling is blocked, indicating the primary role of the ipRGCs in maintaining pupil constriction over a prolonged time.
+Different classes of retinal photoreceptors, including cones, rods and melanopsin-containing intrinsically photosensitive retinal ganglion cells (ipRGCs), are directly involved in controlling and maintaining the size of the pupils.\textsuperscript{\protect\hyperlink{ref-McDougal2010}{4}--\protect\hyperlink{ref-Woelders2018}{8}} Cones drive the initial rapid constriction of the pupils,\textsuperscript{\protect\hyperlink{ref-Mathot2018}{9}} while the slower and longer activation of the ipRGCs maintains constriction over a prolonged period of time and regulates the post-illumination pupillary response.\textsuperscript{\protect\hyperlink{ref-McDougal2010}{4},\protect\hyperlink{ref-Markwell2010}{10}} The ipRGCs are a recently discovered photoreceptor class\textsuperscript{\protect\hyperlink{ref-Provencio2000}{11}} that express the photopigment melanopsin, and are involved in the regulation of the circadian rhythm,\textsuperscript{\protect\hyperlink{ref-Panda2002}{12},\protect\hyperlink{ref-Ruby2002}{13}} forming a major input to the PON.\textsuperscript{\protect\hyperlink{ref-Dacey2003}{14}} The first direct evidence of the involvement of the ipRGCs in the PLR was shown in melanopsin knockout rats,\textsuperscript{\protect\hyperlink{ref-Lucas2003}{15}} resulting in the loss of the intrinsic photosensitivity of the cells and a reduced pupil constriction.
+Similar behaviour was later observed in primates and humans\textsuperscript{\protect\hyperlink{ref-Gamlin2007}{16}} using silent substitution (see Methods), where it was demonstrated that the PLR continues during light presentation even when cone and rod signalling is blocked, indicating the primary role of the ipRGCs in maintaining pupil constriction over a prolonged time.
 
-Binocular combination has been extensively studied in visual perception, where it is mediated by neurons in primary visual cortex (Hubel and Wiesel, \protect\hyperlink{ref-Hubel1962}{1962}).
-For pattern vision, binocular summation occurs at threshold, such that a lower contrast is required to detect a target shown to both eyes than a target shown to one eye (Baker et al., \protect\hyperlink{ref-Baker2018}{2018}; Campbell and Green, \protect\hyperlink{ref-Campbell1965}{1965}).
-At higher contrasts, the phenomenon of `ocularity invariance' is observed, in which the response to monocularly- and binocularly-presented patterns is equal (Baker et al., \protect\hyperlink{ref-Baker2007}{2007}; Moradi and Heeger, \protect\hyperlink{ref-Moradi2009}{2009}).
-This is explained by a process of interocular suppression that cancels out the additional excitatory drive caused by stimulating two eyes.
-Our recent work (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}) showed that cortical signal combination for luminance flicker is substantially more linear than for spatial patterns, whereas there is evidence of interocular suppression in the pupil pathway.
+Binocular combination has been extensively studied in visual perception, where it is mediated by neurons in primary visual cortex.\textsuperscript{\protect\hyperlink{ref-Hubel1962}{17}} For pattern vision, binocular summation occurs at threshold, such that a lower contrast is required to detect a target shown to both eyes than a target shown to one eye.\textsuperscript{\protect\hyperlink{ref-Baker2018}{18},\protect\hyperlink{ref-Campbell1965}{19}} At higher contrasts, the phenomenon of `ocularity invariance' is observed, in which the response to monocularly- and binocularly-presented patterns is equal.\textsuperscript{\protect\hyperlink{ref-Baker2007}{20},\protect\hyperlink{ref-Moradi2009}{21}} This is explained by a process of interocular suppression that cancels out the additional excitatory drive caused by stimulating two eyes.
+Our recent work\textsuperscript{\protect\hyperlink{ref-Segala2023}{3}} showed that cortical signal combination for luminance flicker is substantially more linear than for spatial patterns, whereas there is evidence of interocular suppression in the pupil pathway.
 Here we measure the amplitude of pupil modulations in response to flickering stimuli presented as light flux, or directed towards the L-M cone, S-cone, and melanopsin pathways (see Figure \ref{fig:spectraplots}e-l).
 Our key comparisons are between monocular and binocular stimulation, and in a dichoptic masking condition where the two eyes are stimulated at different frequencies.
-The results are interpreted using a contemporary model of binocular vision (Meese et al., \protect\hyperlink{ref-Meese2006}{2006}) implemented within a hierarchical Bayesian framework.
-These results previously formed part of a doctoral thesis by the first author (Segala, \protect\hyperlink{ref-SegalaThesis2023}{2023}).
+The results are interpreted using a contemporary model of binocular vision\textsuperscript{\protect\hyperlink{ref-Meese2006}{22}} implemented within a hierarchical Bayesian framework.
 
@@
 To present synchronised stimulus modulations independently to each eye, two light engines (SpectraTuneLAB, which are thermally stable across time with active cooling according to the manufacturers: LEDMOTIVE Technologies, LLC, Barcelona, Spain), each with 10 independently addressable LED colour channels, were integrated into a customised binocular viewing system.
-The light engines were operated via a Python interface to their REST API (Martin et al., \protect\hyperlink{ref-Martin2022}{2022}), which supports synchronous launch and playback of spectral sequences prepared in advance and stored in JSON format.
+The light engines were operated via a Python interface to their REST API,\textsuperscript{\protect\hyperlink{ref-Martin2022}{23}} which supports synchronous launch and playback of spectral sequences prepared in advance and stored in JSON format.
 A special command was commissioned from LEDMOTIVE to allow two different stimulus files to be launched simultaneously from the two devices.
@@
 When preparing the spectral sequences, the age of participants was used to account for the yellowing of the lenses.
-We used the silent substitution technique (Estévez and Spekreijse, \protect\hyperlink{ref-Estevez1982}{1982}) to selectively stimulate specific photoreceptor classes.
+We used the silent substitution technique\textsuperscript{\protect\hyperlink{ref-Estevez1982}{24}} to selectively stimulate specific photoreceptor classes.
 Silent substitution exploits the fact that each photoreceptor class has a distinct spectral tuning that overlaps with the others.
-Using a multiprimary system, in which the primaries (i.e.~LEDs) have different spectra, it is possible to target one class of photoreceptors while maintaining the others at a constant activity level, effectively silencing them (Shapiro et al., \protect\hyperlink{ref-Shapiro1996}{1996}; Spitschan and Woelders, \protect\hyperlink{ref-Spitschan2018}{2018}, this paper also offers a clear explanation of how to implement silent substitution).
-We calculated silent substitution solutions using the \emph{PySilSub} toolbox (Martin et al., \protect\hyperlink{ref-Martin2023}{2023}), using linear algebra.
+Using a multiprimary system, in which the primaries (i.e.~LEDs) have different spectra, it is possible to target one class of photoreceptors while maintaining the others at a constant activity level, effectively silencing them.\textsuperscript{\protect\hyperlink{ref-Shapiro1996}{25},\protect\hyperlink{ref-Spitschan2018}{26}} We calculated silent substitution solutions using the \emph{PySilSub} toolbox,\textsuperscript{\protect\hyperlink{ref-Martin2023}{27}} using linear algebra.
 The outputs of the two light engines (see Figure \ref{fig:spectraplots}b,c) were calibrated using an Ocean Optics Jaz spectroradiometer, which was wavelength-calibrated to an Argon lamp and intensity calibrated using a NIST-traceable light source.
 Each primary was also linearized using a polynomial fit (see Figure \ref{fig:primarylinearity} for details).
-We used the Stockman and Sharpe (\protect\hyperlink{ref-Stockman2000}{2000}) 10-degree cone fundamentals, and estimates of melanopsin absorbance spectra from CIE S 026 (discussed in Martin et al., \protect\hyperlink{ref-Martin2023}{2023}) to calculate \(\alpha\)-opic irradiance.
+We used the 10-degree cone fundamentals,\textsuperscript{\protect\hyperlink{ref-Stockman2000}{28}} and estimates of melanopsin absorbance spectra from CIE S 026 (discussed in a previous paper\textsuperscript{\protect\hyperlink{ref-Martin2023}{27}}) to calculate \(\alpha\)-opic irradiance.
 
@@
 The diffuser discs were positioned in the objective planes of the lenses of a modified VR headset (SHINECON SC-G01, Dongguan Shinecon Industrial Co.~Ltd., Guangdong, China), which was used by the participants to view the stimuli.
-The stimuli were two discs of flickering light with a diameter of approximately 30 degrees, which were fused together into a cyclopean percept resembling a donut-shaped ring of light, similar to that used in other studies (e.g., Barrionuevo and Cao, \protect\hyperlink{ref-Barrionuevo2016}{2016}; Murray et al., \protect\hyperlink{ref-Murray2018}{2018}; Spitschan et al., \protect\hyperlink{ref-Spitschan2015}{2015}, \protect\hyperlink{ref-Spitschan2014}{2014}; Zele et al., \protect\hyperlink{ref-Zele2018}{2018}).
-The VR headset modifications allowed for small adjustments to account for individual differences in interpupillary distance and focal length.
-The use of this set up allowed us to modulate the stimuli in three different ocular configurations, similar to the ones we used in our previous study (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}): monocular, binocular and dichoptic.
+The stimuli were two discs of flickering light with a diameter of approximately 30 degrees, which were fused together into a cyclopean percept resembling a donut-shaped ring of light, similar to that used in other studies.\textsuperscript{\protect\hyperlink{ref-Barrionuevo2016}{5}--\protect\hyperlink{ref-Spitschan2014}{7},\protect\hyperlink{ref-Spitschan2015}{29},\protect\hyperlink{ref-Zele2018}{30}} The VR headset modifications allowed for small adjustments to account for individual differences in interpupillary distance and focal length.
+The use of this set up allowed us to modulate the stimuli in three different ocular configurations, similar to the ones we used in our previous study:\textsuperscript{\protect\hyperlink{ref-Segala2023}{3}} monocular, binocular and dichoptic.
 In the monocular configuration, the unstimulated eye still saw a non-flickering disc of mean light flux.
 A schematic of the stimulation system is shown in Figure \ref{fig:spectraplots}a.
-Pupillometry data were collected using a binocular Pupil Core eye-tracker headset (Pupil Labs GmbH, Berlin, Germany, Kassner et al., \protect\hyperlink{ref-Kassner2014}{2014}) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
+Pupillometry data were collected using a binocular Pupil Core eye-tracker headset (Pupil Labs GmbH, Berlin, Germany\textsuperscript{\protect\hyperlink{ref-Kassner2014}{31}}) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
 
-Our previous study (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}) used a temporal frequency of 2Hz for foveal luminance flicker, and recorded EEG data simultaneously with pupillometry.
+Our previous study\textsuperscript{\protect\hyperlink{ref-Segala2023}{3}} used a temporal frequency of 2Hz for foveal luminance flicker, and recorded EEG data simultaneously with pupillometry.
 Initial pilot experiments indicated that this frequency was too high to elicit measurable responses when stimulating individual photoreceptor pathways.
-For all experiments, we therefore used a primary flicker frequency of 0.5Hz, as previous literature showed that this was slow enough to elicit a pupil response from all photoreceptor classes (Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}).
-We also focussed on only recording pupillometry data as this frequency would be too slow to elicit steady-state EEG responses (Norcia et al., \protect\hyperlink{ref-Norcia2015}{2015}).
+For all experiments, we therefore used a primary flicker frequency of 0.5Hz, as previous literature showed that this was slow enough to elicit a pupil response from all photoreceptor classes.\textsuperscript{\protect\hyperlink{ref-Spitschan2014}{7}} We also focussed on only recording pupillometry data as this frequency would be too slow to elicit steady-state EEG responses.\textsuperscript{\protect\hyperlink{ref-Norcia2015}{32}}
 
@@
 
-Silent substitution stimuli were prepared and calibrated for each participant with custom Python software (Martin et al., \protect\hyperlink{ref-Martin2023}{2023}) and Python scripts.
-Estimates of photoreceptor spectral sensitivities for each participant were constructed from the known photopigment absorbance spectra (Stockman and Sharpe, \protect\hyperlink{ref-Stockman2000}{2000}), taking account of the peak axial density of the respective photopigments, as well as lens (Pokorny et al., \protect\hyperlink{ref-Pokorny1987}{1987}; Stockman and Sharpe, \protect\hyperlink{ref-Stockman2000}{2000}; Stockman et al., \protect\hyperlink{ref-Stockman1999}{1999}) and macular pigment density (Bone et al., \protect\hyperlink{ref-Bone1988}{1988}; Stockman et al., \protect\hyperlink{ref-Stockman1999}{1999}), in accordance with the field size and age-dependant CIEPO06 observer model (CIE, \protect\hyperlink{ref-CIE2006}{2006}).
-The melanopic and rhodopic action spectra of the 32-year-old standard observer were taken from CIE S 026 (CIE, \protect\hyperlink{ref-CIE2018}{2018}) and then adjusted for age-related lens transmittance with a spectral correction function, in line with the standard.
-Macular pigment correction was not applied to the rhodopic and melanopic action spectra because rods are not present at the fovea and ipRGCs sit above the retinal pigment layer (Trieschmann et al., \protect\hyperlink{ref-Trieschmann2007}{2007}).
+Silent substitution stimuli were prepared and calibrated for each participant with custom Python software\textsuperscript{\protect\hyperlink{ref-Martin2023}{27}} and Python scripts.
+Estimates of photoreceptor spectral sensitivities for each participant were constructed from the known photopigment absorbance spectra,\textsuperscript{\protect\hyperlink{ref-Stockman2000}{28}} taking account of the peak axial density of the respective photopigments, as well as lens\textsuperscript{\protect\hyperlink{ref-Stockman2000}{28},\protect\hyperlink{ref-Pokorny1987}{33},\protect\hyperlink{ref-Stockman1999}{34}} and macular pigment density,\textsuperscript{\protect\hyperlink{ref-Stockman1999}{34},\protect\hyperlink{ref-Bone1988}{35}} in accordance with the field size and age-dependant CIEPO06 observer model.\textsuperscript{\protect\hyperlink{ref-CIE2006}{36}} The melanopic and rhodopic action spectra of the 32-year-old standard observer were taken from CIE S 026\textsuperscript{\protect\hyperlink{ref-CIE2018}{37}} and then adjusted for age-related lens transmittance with a spectral correction function, in line with the standard.
+Macular pigment correction was not applied to the rhodopic and melanopic action spectra because rods are not present at the fovea and ipRGCs sit above the retinal pigment layer.\textsuperscript{\protect\hyperlink{ref-Trieschmann2007}{38}}
 
@@
 Splatter on nominally silenced photoreceptors was very small (see Figure \ref{fig:spectraplots}j-l), well below the levels that would be expected to generate measurable pupil modulations, although we can observe that the rods may not be saturated in the L-M and melanopsin-directed stimuli (Figure \ref{fig:spectraplots}j and \ref{fig:spectraplots}l) and could intrude in these two experiments.
-We also estimated activation of penumbral L and M cones (Barrionuevo and Cao, \protect\hyperlink{ref-Barrionuevo2016}{2016}; Spitschan et al., \protect\hyperlink{ref-Spitschan2015}{2015}; Zele et al., \protect\hyperlink{ref-Zele2019}{2019}), which was minimal (\(\le 1.5%
+We also estimated activation of penumbral L and M cones,\textsuperscript{\protect\hyperlink{ref-Barrionuevo2016}{5},\protect\hyperlink{ref-Spitschan2015}{29},\protect\hyperlink{ref-Zele2019}{39}} which was minimal (\(\le 1.5%
 \) contrast; less than splatter on the open-field cones) for melanopsin-directed stimuli.
-We note that the temporal frequency of our modulation (0.5Hz) is well below the range where penumbral cone activation can elicit visible percepts, and that such percepts fade after around 1 second (Spitschan et al., \protect\hyperlink{ref-Spitschan2015}{2015}), and do not typically affect pupil responses (Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}).
+We note that the temporal frequency of our modulation (0.5Hz) is well below the range where penumbral cone activation can elicit visible percepts, and that such percepts fade after around 1 second,\textsuperscript{\protect\hyperlink{ref-Spitschan2015}{29}} and do not typically affect pupil responses.\textsuperscript{\protect\hyperlink{ref-Spitschan2014}{7}}
 
@@
 Pupil responses to binocular temporal contrast modulations were examined in a factorial design that combined six ocular conditions and five temporal contrast levels: 6, 12, 24, 48 and 96\% of the available dynamic range.
-This design, similar to that used in our previous studies (Baker et al., \protect\hyperlink{ref-Baker2020}{2020}; Baker and Wade, \protect\hyperlink{ref-Baker2017}{2017}; Segala et al., \protect\hyperlink{ref-Segala2023}{2023}), was applied in four separate experiments, each with a different mode of photoreceptor stimulation.
+This design, similar to that used in our previous studies,\textsuperscript{\protect\hyperlink{ref-Segala2023}{3},\protect\hyperlink{ref-Baker2017}{40},\protect\hyperlink{ref-Baker2020}{41}} was applied in four separate experiments, each with a different mode of photoreceptor stimulation.
 In the first three conditions, the discs flickered at 0.5 Hz, in either a monocular, binocular or dichoptic arrangement.
@@
 Using a trackball, participants adjusted the angle in cone space to find their subjective isoluminant point, which resulted in changing the flickering intensity of the stimulus until the amplitude of the flicker appeared to be minimised.
-The result was used to modify the requested contrasts during stimulus preparation so as to account for individual differences affecting perceived illuminance, principally the L:M cone ratio (Carroll et al., \protect\hyperlink{ref-Carroll2002}{2002}; Hofer et al., \protect\hyperlink{ref-Hofer2005}{2005}).
+The result was used to modify the requested contrasts during stimulus preparation so as to account for individual differences affecting perceived illuminance, principally the L:M cone ratio.\textsuperscript{\protect\hyperlink{ref-Carroll2002}{42},\protect\hyperlink{ref-Hofer2005}{43}}
 
@@
 
-The pupillometry data were analysed using the same method we used in our previous study (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}).
-The data were converted from mp4 videos to a csv text file using the Pupil Player software (Kassner et al., \protect\hyperlink{ref-Kassner2014}{2014}), which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
+The pupillometry data were analysed using the same method we used in our previous study.\textsuperscript{\protect\hyperlink{ref-Segala2023}{3}} The data were converted from mp4 videos to a csv text file using the Pupil Player software,\textsuperscript{\protect\hyperlink{ref-Kassner2014}{31}} which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
 The individual data were then loaded into R for analysis, where a ten-second waveform for each trial in each eye was extracted (excluding the first two seconds after stimulus onset).
@@
 Finally, data were averaged across all participants to obtain the group results.
-We used coherent averaging and at each stage we excluded data points with a Mahalanobis distance exceeding \(D\) = 3 from the complex-valued mean (Baker, \protect\hyperlink{ref-Baker2021}{2021}).
-For monocular stimulation, we confirmed that the consensual response was equivalent to the response in the stimulated eye.
+We used coherent averaging and at each stage we excluded data points with a Mahalanobis distance exceeding \(D\) = 3 from the complex-valued mean.\textsuperscript{\protect\hyperlink{ref-Baker2021}{44}} For monocular stimulation, we confirmed that the consensual response was equivalent to the response in the stimulated eye.
 
@@
 
-To quantitatively summarise our data, we used the same model described in our previous study (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}).
-The model has the same general form as the first stage of the contrast gain control model proposed by Meese et al.
-(\protect\hyperlink{ref-Meese2006}{2006}), but omits the second stage.
-For the previous model that we used (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}), the exponent of the numerator and denominator had fixed values of 2 and (implicitly) 1.
+To quantitatively summarise our data, we used the same model described in our previous study.\textsuperscript{\protect\hyperlink{ref-Segala2023}{3}} The model has the same general form as the first stage of the contrast gain control model proposed by Meese and colleagues,\textsuperscript{\protect\hyperlink{ref-Meese2006}{22}} but omits the second stage.
+For the previous model that we used,\textsuperscript{\protect\hyperlink{ref-Segala2023}{3}} the exponent of the numerator and denominator had fixed values of 2 and (implicitly) 1.
 Here, we allow these parameters (called \emph{p} and \emph{q}) to be free, in order to permit different shapes of contrast response function, e.g.~accelerating or saturating.
@@
 
-The models were fit using a hierarchical Bayesian framework implemented in Stan (Carpenter et al., \protect\hyperlink{ref-Carpenter2017}{2017}).
-The data for each photoreceptor type and response frequency was fit separately, for a total of 8 model fits.
+The models were fit using a hierarchical Bayesian framework implemented in Stan.\textsuperscript{\protect\hyperlink{ref-Carpenter2017}{45}} The data for each photoreceptor type and response frequency was fit separately, for a total of 8 model fits.
 The prior for the \(\omega\) parameter was Gaussian, with a mean of 1 and standard deviation of 0.5.
-Priors for the other free parameters were also Gaussian, with mean values based on previous work (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}).
-We calculated over \ensuremath{10^{6}} posterior samples, and retained 10\% for plotting.
+Priors for the other free parameters were also Gaussian, with mean values based on previous work.\textsuperscript{\protect\hyperlink{ref-Segala2023}{3}} We calculated over \ensuremath{10^{6}} posterior samples, and retained 10\% for plotting.
 
@@
 
-In contemporary models of binocular signal combination, the amount of binocular facilitation is determined by the magnitude of interocular suppression, with strong suppression reducing facilitation (Kingdom and Libenson, \protect\hyperlink{ref-Kingdom2015}{2015}).
-We can estimate the strength of interocular suppression by measuring how much monocular responses are reduced when a dichoptic `mask' is shown to the other eye.
-In our paradigm, the two components flickered at different frequencies (0.5 and 0.4Hz) so that their responses remained distinct in the Fourier spectrum (e.g.~Busse et al., \protect\hyperlink{ref-Busse2009}{2009}).
-The yellow diamond symbols in Figure \ref{fig:FirstHarmonicPlots}a-d show the target responses in this condition, and in most cases were weaker than the monocular responses (red circles).
+In contemporary models of binocular signal combination, the amount of binocular facilitation is determined by the magnitude of interocular suppression, with strong suppression reducing facilitation.\textsuperscript{\protect\hyperlink{ref-Kingdom2015}{46}} We can estimate the strength of interocular suppression by measuring how much monocular responses are reduced when a dichoptic `mask' is shown to the other eye.
+In our paradigm, the two components flickered at different frequencies (0.5 and 0.4Hz) so that their responses remained distinct in the Fourier spectrum.\textsuperscript{\protect\hyperlink{ref-Busse2009}{47}} The yellow diamond symbols in Figure \ref{fig:FirstHarmonicPlots}a-d show the target responses in this condition, and in most cases were weaker than the monocular responses (red circles).
 The strongest dichoptic masking is found in the L-M condition, where we also observed the binocular suppression effect.
@@
 
-To estimate the extent of interocular suppression for each photoreceptor pathway, we fitted each data set using a Bayesian hierarchical implementation of a simple binocular combination model (Meese et al., \protect\hyperlink{ref-Meese2006}{2006}; Segala et al., \protect\hyperlink{ref-Segala2023}{2023}).
-Our primary objective was to compare posterior distributions of the weight of interocular suppression, which are shown in Figure \ref{fig:FirstHarmonicPlots}e.
+To estimate the extent of interocular suppression for each photoreceptor pathway, we fitted each data set using a Bayesian hierarchical implementation of a simple binocular combination model.\textsuperscript{\protect\hyperlink{ref-Segala2023}{3},\protect\hyperlink{ref-Meese2006}{22}} Our primary objective was to compare posterior distributions of the weight of interocular suppression, which are shown in Figure \ref{fig:FirstHarmonicPlots}e.
 Consistent with our earlier observations, the strongest suppressive weight corresponds to the L-M and Melanopsin conditions, and the weakest suppression corresponds to the light flux and S-cone conditions, with virtually no overlap between the posterior distributions for weak and strong suppression.
@@
 
-Finally, we inspected the response phase of our four stimulation conditions, given previous reports that these differ across pathways (Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}), and may be in antiphase for melanopsin and S-cone signals.
+Finally, we inspected the response phase of our four stimulation conditions, given previous reports that these differ across pathways,\textsuperscript{\protect\hyperlink{ref-Spitschan2014}{7}} and may be in antiphase for melanopsin and S-cone signals.
 Figure \ref{fig:phaseplots} shows the phase angles for the first (a) and second (b) harmonic frequencies for binocular stimulation (monocular stimulation produced very similar results).
@@
 This is the first study to investigate binocular interactions in the melanopsin pathway directly.
-A previous meta-analysis (Spitschan and Cajochen, \protect\hyperlink{ref-Spitschan2019}{2019}) indicated that there may be a substantial binocular facilitation effect in the circadian pathway, as indexed by melatonin suppression (melatonin is a hormone released by the pineal gland; its production is suppressed by exposure to bright light, particularly when the melanopsin-containing ipRGCs are stimulated).
+A previous meta-analysis\textsuperscript{\protect\hyperlink{ref-Spitschan2019}{48}} indicated that there may be a substantial binocular facilitation effect in the circadian pathway, as indexed by melatonin suppression (melatonin is a hormone released by the pineal gland; its production is suppressed by exposure to bright light, particularly when the melanopsin-containing ipRGCs are stimulated).
 In brief, monocular stimulation of the ipRGCs requires up to ten times the signal strength to produce an equivalent effect to binocular stimulation.
@@
 The explanation for this difference could be due to different anatomical pathways.
-Binocular combination in the circadian system likely takes place in the suprachiasmatic nucleus, whereas in the pupil constriction circuit the Edinger-Westphal nucleus is the most likely site of binocular integration (Mathôt, \protect\hyperlink{ref-Mathot2018}{2018}).
-Presumably these anatomical differences, and the practical constraints of the two systems, lead to differences in response.
+Binocular combination in the circadian system likely takes place in the suprachiasmatic nucleus, whereas in the pupil constriction circuit the Edinger-Westphal nucleus is the most likely site of binocular integration.\textsuperscript{\protect\hyperlink{ref-Mathot2018}{9}} Presumably these anatomical differences, and the practical constraints of the two systems, lead to differences in response.
 
-Our recent psychophysical work (Baker et al., \protect\hyperlink{ref-Baker2024}{2024}) has looked at binocular interactions in the L-M and S-cone pathways, and compared these to the light flux pathway.
-Using a contrast discrimination paradigm with spatial modulations of light flux and colour, Baker et al.
-(\protect\hyperlink{ref-Baker2024}{2024}) found equally strong interocular suppression in all three pathways.
-This is rather different from our pupillometry results here, which demonstrate weaker suppression in the light flux and S-cone pathways than in the L-M pathway (see Figure \ref{fig:FirstHarmonicPlots}).
-However, the current experiments involve temporal modulations, which are quite distinct from the spatial modulations used in Baker et al.
-(\protect\hyperlink{ref-Baker2024}{2024}).
-Our other recent work (Segala et al., \protect\hyperlink{ref-Segala2023}{2023}) has shown that temporal luminance modulations involve much weaker interocular suppression in the cortical response than do spatial luminance modulations (Baker and Wade, \protect\hyperlink{ref-Baker2017}{2017}).
-These different normalization processes might reflect different priorities for spatial and temporal vision.
-Spatial vision aims to fuse images to provide binocular single vision, and benefits from `ocularity invariance' (Baker et al., \protect\hyperlink{ref-Baker2007}{2007}), in which visual appearance is constant when viewed with one eye or two.
-Temporal vision is critical for motion perception, which can involve alternative binocular computations, such as calculating velocity differences between the eyes (Kaestner et al., \protect\hyperlink{ref-Kaestner2019}{2019}).
-Of course the present measurements were of pupil size, which may be subject to different anatomical and functional constraints from those in the cortex.
+Our recent psychophysical work\textsuperscript{\protect\hyperlink{ref-Baker2024}{49}} has looked at binocular interactions in the L-M and S-cone pathways, and compared these to the light flux pathway.
+Using a contrast discrimination paradigm with spatial modulations of light flux and colour, we found equally strong interocular suppression in all three pathways.\textsuperscript{\protect\hyperlink{ref-Baker2024}{49}} This is rather different from our pupillometry results here, which demonstrate weaker suppression in the light flux and S-cone pathways than in the L-M pathway (see Figure \ref{fig:FirstHarmonicPlots}).
+However, the current experiments involve temporal modulations, which are quite distinct from the spatial modulations used in our previous work.\textsuperscript{\protect\hyperlink{ref-Baker2024}{49}} Our other recent work\textsuperscript{\protect\hyperlink{ref-Segala2023}{3}} has shown that temporal luminance modulations involve much weaker interocular suppression in the cortical response than do spatial luminance modulations.\textsuperscript{\protect\hyperlink{ref-Baker2017}{40}} These different normalization processes might reflect different priorities for spatial and temporal vision.
+Spatial vision aims to fuse images to provide binocular single vision, and benefits from `ocularity invariance,'\textsuperscript{\protect\hyperlink{ref-Baker2007}{20}} in which visual appearance is constant when viewed with one eye or two.
+Temporal vision is critical for motion perception, which can involve alternative binocular computations, such as calculating velocity differences between the eyes.\textsuperscript{\protect\hyperlink{ref-Kaestner2019}{50}} Of course the present measurements were of pupil size, which may be subject to different anatomical and functional constraints from those in the cortex.
 Future research should aim to extend our current findings to perception using psychophysical approaches.
@@
 \hypertarget{refs}{}
+\leavevmode\hypertarget{ref-McDougal2015}{}%
+1. McDougal DH, Gamlin PD. Autonomic control of the eye. \emph{Comprehensive Physiology}. 2015;5(1):439-473. doi:\href{https://doi.org/10.1002/cphy.c140014}{10.1002/cphy.c140014}
+
+\leavevmode\hypertarget{ref-Wyatt1981}{}%
+2.
+Wyatt HJ, Musselman JF.
+Pupillary light reflex in humans: Evidence for an unbalanced pathway from nasal retina, and for signal cancellation in brainstem.
+\emph{Vision Res}.
+1981;21(4):513-525.
+doi:\href{https://doi.org/10.1016/0042-6989(81)90097-3}{10.1016/0042-6989(81)90097-3}
+
+\leavevmode\hypertarget{ref-Segala2023}{}%
+3.
+Segala FG, Bruno A, Martin JT, Aung MT, Wade AR, Baker DH.
+Different rules for binocular combination of luminance flicker in cortical and subcortical pathways.
+\emph{eLife}.
+2023;12.
+doi:\href{https://doi.org/10.7554/elife.87048}{10.7554/elife.87048}
+
+\leavevmode\hypertarget{ref-McDougal2010}{}%
+4.
+McDougal DH, Gamlin PD.
+The influence of intrinsically-photosensitive retinal ganglion cells on the spectral sensitivity and response dynamics of the human pupillary light reflex.
+\emph{Vision Research}.
+2010;50(1):72-87.
+doi:\href{https://doi.org/10.1016/j.visres.2009.10.012}{10.1016/j.visres.2009.10.012}
+
+\leavevmode\hypertarget{ref-Barrionuevo2016}{}%
+5.
+Barrionuevo PA, Cao D.
+Luminance and chromatic signals interact differently with melanopsin activation to control the pupil light response.
+\emph{Journal of Vision}.
+2016;16(11):29.
+doi:\href{https://doi.org/10.1167/16.11.29}{10.1167/16.11.29}
+
+\leavevmode\hypertarget{ref-Murray2018}{}%
+6.
+Murray IJ, Kremers J, McKeefry D, Parry NRA.
+Paradoxical pupil responses to isolated M-cone increments.
+\emph{Journal of the Optical Society of America A}.
+2018;35(4):B66-B71.
+doi:\href{https://doi.org/10.1364/JOSAA.35.000B66}{10.1364/JOSAA.35.000B66}
+
+\leavevmode\hypertarget{ref-Spitschan2014}{}%
+7.
+Spitschan M, Jain S, Brainard DH, Aguirre GK.
+Opponent melanopsin and s-cone signals in the human pupillary light response.
+\emph{Proceedings of the National Academy of Sciences}.
+2014;111(43):15568-15572.
+doi:\href{https://doi.org/10.1073/pnas.1400942111}{10.1073/pnas.1400942111}
+
+\leavevmode\hypertarget{ref-Woelders2018}{}%
+8.
+Woelders T, Leenheers T, Gordijn MCM, Hut RA, Beersma DGM, Wams EJ.
+Melanopsin- and L-cone--induced pupil constriction is inhibited by S- and M-cones in humans.
+\emph{Proceedings of the National Academy of Sciences}.
+2018;115(4):792-797.
+doi:\href{https://doi.org/10.1073/pnas.1716281115}{10.1073/pnas.1716281115}
+
+\leavevmode\hypertarget{ref-Mathot2018}{}%
+9. Mathôt S. Pupillometry: Psychology, physiology, and function. \emph{J Cogn}. 2018;1(1):16. doi:\href{https://doi.org/10.5334/joc.18}{10.5334/joc.18}
+
+\leavevmode\hypertarget{ref-Markwell2010}{}%
+10.
+Markwell EL, Feigl B, Zele AJ.
+Intrinsically photosensitive melanopsin retinal ganglion cell contributions to the pupillary light reflex and circadian rhythm.
+\emph{Clinical and Experimental Optometry}.
+2010;93(3):137-149.
+doi:\href{https://doi.org/10.1111/j.1444-0938.2010.00479.x}{10.1111/j.1444-0938.2010.00479.x}
+
+\leavevmode\hypertarget{ref-Provencio2000}{}%
+11.
+Provencio I, Rodriguez IR, Jiang G, Hayes WP, Moreira EF, Rollag MD.
+A Novel Human Opsin in the Inner Retina.
+\emph{Journal of Neuroscience}.
+2000;20(2):600-605.
+doi:\href{https://doi.org/10.1523/JNEUROSCI.20-02-00600.2000}{10.1523/JNEUROSCI.20-02-00600.2000}
+
+\leavevmode\hypertarget{ref-Panda2002}{}%
+12.
+Panda S, Sato TK, Castrucci AM, et al.
+Melanopsin (opn4) requirement for normal light-induced circadian phase shifting.
+\emph{Science}.
+2002;298(5601):2213-2216.
+doi:\href{https://doi.org/10.1126/science.1076848}{10.1126/science.1076848}
+
+\leavevmode\hypertarget{ref-Ruby2002}{}%
+13.
+Ruby NF, Brennan TJ, Xie X, et al.
+Role of melanopsin in circadian responses to light.
+\emph{Science}.
+2002;298(5601):2211-2213.
+doi:\href{https://doi.org/10.1126/science.1076701}{10.1126/science.1076701}
+
+\leavevmode\hypertarget{ref-Dacey2003}{}%
+14.
+Dacey DM, Peterson BB, Robinson FR, Gamlin PD.
+Fireworks in the primate retina: In vitro photodynamics reveals diverse lgn-projecting ganglion cell types.
+\emph{Neuron}.
+2003;37(1):15-27.
+doi:\href{https://doi.org/https://doi.org/10.1016/S0896-6273(02)01143-1}{https://doi.org/10.1016/S0896-6273(02)01143-1}
+
+\leavevmode\hypertarget{ref-Lucas2003}{}%
+15.
+Lucas RJ, Hattar S, Takao M, Berson DM, Foster RG, Yau KW.
+Diminished pupillary light reflex at high irradiances in melanopsin-knockout mice.
+\emph{Science}.
+2003;299(5604):245-247.
+doi:\href{https://doi.org/10.1126/science.1077293}{10.1126/science.1077293}
+
+\leavevmode\hypertarget{ref-Gamlin2007}{}%
+16.
+Gamlin PDR, McDougal DH, Pokorny J, Smith VC, Yau KW, Dacey DM.
+Human and macaque pupil responses driven by melanopsin-containing retinal ganglion cells.
+\emph{Vision Research}.
+2007;47(7):946-954.
+doi:\href{https://doi.org/10.1016/j.visres.2006.12.015}{10.1016/j.visres.2006.12.015}
+
+\leavevmode\hypertarget{ref-Hubel1962}{}%
+17.
+Hubel DH, Wiesel TN.
+Receptive fields, binocular interaction and functional architecture in the cat's visual cortex.
+\emph{J Physiol}.
+1962;160(1):106-154.
+doi:\href{https://doi.org/10.1113/jphysiol.1962.sp006837}{10.1113/jphysiol.1962.sp006837}
+
+\leavevmode\hypertarget{ref-Baker2018}{}%
+18.
+Baker DH, Lygo FA, Meese TS, Georgeson MA.
+Binocular summation revisited: Beyond \(\sqrt{2}\).
+\emph{Psychol Bull}.
+2018;144(11):1186-1199.
+doi:\href{https://doi.org/10.1037/bul0000163}{10.1037/bul0000163}
+
+\leavevmode\hypertarget{ref-Campbell1965}{}%
+19. Campbell FW, Green DG. Monocular versus binocular visual acuity. \emph{Nature}. 1965;208(5006):191-192. doi:\href{https://doi.org/10.1038/208191a0}{10.1038/208191a0}
+
+\leavevmode\hypertarget{ref-Baker2007}{}%
+20.
+Baker DH, Meese TS, Georgeson MA.
+Binocular interaction: Contrast matching and contrast discrimination are predicted by the same model.
+\emph{Spat Vis}.
+2007;20(5):397-413.
+doi:\href{https://doi.org/10.1163/156856807781503622}{10.1163/156856807781503622}
+
+\leavevmode\hypertarget{ref-Moradi2009}{}%
+21. Moradi F, Heeger DJ. Inter-ocular contrast normalization in human visual cortex. \emph{J Vis}. 2009;9(3):13.1-22. doi:\href{https://doi.org/10.1167/9.3.13}{10.1167/9.3.13}
+
+\leavevmode\hypertarget{ref-Meese2006}{}%
+22. Meese TS, Georgeson MA, Baker DH. Binocular contrast vision at and above threshold. \emph{Journal of Vision}. 2006;6(11):1224-1243. doi:\href{https://doi.org/10.1167/6.11.7}{10.1167/6.11.7}
+
+\leavevmode\hypertarget{ref-Martin2022}{}%
+23.
+Martin JT, Pinto J, Bulte D, Spitschan M.
+PyPlr: A versatile, integrated system of hardware and software for researching the human pupillary light reflex.
+\emph{Behavior Research Methods}.
+2022;54(6):2720-2739.
+doi:\href{https://doi.org/10.3758/s13428-021-01759-3}{10.3758/s13428-021-01759-3}
+
+\leavevmode\hypertarget{ref-Estevez1982}{}%
+24.
+Estévez O, Spekreijse H.
+The "silent substitution" method in visual research.
+\emph{Vision Research}.
+1982;22(6):681-691.
+doi:\href{https://doi.org/10.1016/0042-6989(82)90104-3}{10.1016/0042-6989(82)90104-3}
+
+\leavevmode\hypertarget{ref-Shapiro1996}{}%
+25.
+Shapiro AG, Pokorny J, Smith VC.
+Conerod receptor spaces with illustrations that use CRT phosphor and light-emitting-diode spectra.
+\emph{Journal of the Optical Society of America A}.
+1996;13(12):2319.
+doi:\href{https://doi.org/10.1364/josaa.13.002319}{10.1364/josaa.13.002319}
+
+\leavevmode\hypertarget{ref-Spitschan2018}{}%
+26.
+Spitschan M, Woelders T.
+The Method of Silent Substitution for Examining Melanopsin Contributions to Pupil Control.
+\emph{Frontiers in Neurology}.
+2018;9.
+doi:\href{https://doi.org/10.3389/fneur.2018.00941}{10.3389/fneur.2018.00941}
+
+\leavevmode\hypertarget{ref-Martin2023}{}%
+27.
+Martin JT, Boynton GM, Baker DH, Wade AR, Spitschan M.
+PySilSub: An open-source python toolbox for implementing the method of silent substitution in vision and nonvisual photoreception research.
+\emph{Journal of Vision}.
+2023;23(7):10.
+doi:\href{https://doi.org/10.1167/jov.23.7.10}{10.1167/jov.23.7.10}
+
+\leavevmode\hypertarget{ref-Stockman2000}{}%
+28.
+Stockman A, Sharpe LT.
+The spectral sensitivities of the middle- and long-wavelength-sensitive cones derived from measurements in observers of known genotype.
+\emph{Vision Res}.
+2000;40(13):1711-1737.
+doi:\href{https://doi.org/10.1016/s0042-6989(00)00021-3}{10.1016/s0042-6989(00)00021-3}
+
+\leavevmode\hypertarget{ref-Spitschan2015}{}%
+29.
+Spitschan M, Aguirre GK, Brainard DH.
+Selective stimulation of penumbral cones reveals perception in the shadow of retinal blood vessels.
+\emph{PLoS One}.
+2015;10(4):e0124328.
+doi:\href{https://doi.org/10.1371/journal.pone.0124328}{10.1371/journal.pone.0124328}
+
+\leavevmode\hypertarget{ref-Zele2018}{}%
+30.
+Zele AJ, Feigl B, Adhikari P, Maynard ML, Cao D.
+Melanopsin photoreception contributes to human visual detection, temporal and colour processing.
+\emph{Scientific Reports}.
+2018;8(1).
+doi:\href{https://doi.org/10.1038/s41598-018-22197-w}{10.1038/s41598-018-22197-w}
+
+\leavevmode\hypertarget{ref-Kassner2014}{}%
+31.
+Kassner M, Patera W, Bulling A.
+Pupil: An open source platform for pervasive eye tracking and mobile gaze-based interaction.
+In: \emph{Proceedings of the 2014 ACM International Joint Conference on Pervasive and Ubiquitous Computing: Adjunct Publication}.
+ACM; 2014.
+doi:\href{https://doi.org/10.1145/2638728.2641695}{10.1145/2638728.2641695}
+
+\leavevmode\hypertarget{ref-Norcia2015}{}%
+32.
+Norcia AM, Appelbaum LG, Ales JM, Cottereau BR, Rossion B.
+The steady-state visual evoked potential in vision research: A review.
+\emph{Journal of Vision}.
+2015;15(6):4.
+doi:\href{https://doi.org/10.1167/15.6.4}{10.1167/15.6.4}
+
+\leavevmode\hypertarget{ref-Pokorny1987}{}%
+33. Pokorny J, Smith VC, Lutze M. Aging of the human lens. \emph{Applied Optics}. 1987;26(8):1437. doi:\href{https://doi.org/10.1364/ao.26.001437}{10.1364/ao.26.001437}
+
+\leavevmode\hypertarget{ref-Stockman1999}{}%
+34.
+Stockman A, Sharpe LT, Fach C.
+The spectral sensitivity of the human short-wavelength sensitive cones derived from thresholds and color matches.
+\emph{Vision Research}.
+1999;39(17):2901-2927.
+doi:\href{https://doi.org/https://doi.org/10.1016/S0042-6989(98)00225-9}{https://doi.org/10.1016/S0042-6989(98)00225-9}
+
+\leavevmode\hypertarget{ref-Bone1988}{}%
+35. Bone RA, Landrum JT, Fernandez L, Tarsis SL. Analysis of the macular pigment by HPLC: Retinal distribution and age study. \emph{Investigative Ophthalmology \& Visual Science}. 1988;29(6):843-849.
+
+\leavevmode\hypertarget{ref-CIE2006}{}%
+36. CIE. \emph{Fundamental Chromaticity Diagram with Physiological Axes}. CIE Central Bureau; 2006. \url{https://cie.co.at/publications/fundamental-chromaticity-diagram-physiological-axes-part-1}
+
+\leavevmode\hypertarget{ref-CIE2018}{}%
+37. CIE. \emph{CIE System for Metrology of Optical Radiation for ipRGC-Influenced Responses to Light}. CIE Central Bureau; 2018. doi:\href{https://doi.org/10.25039/S026.2018}{10.25039/S026.2018}
+
+\leavevmode\hypertarget{ref-Trieschmann2007}{}%
+38.
+Trieschmann M, Kuijk FJGM van, Alexander R, et al.
+Macular pigment in the human retina: Histological evaluation of localization and distribution.
+\emph{Eye}.
+2007;22(1):132-137.
+doi:\href{https://doi.org/10.1038/sj.eye.6702780}{10.1038/sj.eye.6702780}
+
+\leavevmode\hypertarget{ref-Zele2019}{}%
+39.
+Zele AJ, Adhikari P, Cao D, Feigl B.
+Melanopsin driven enhancement of cone-mediated visual processing.
+\emph{Vision Res}.
+2019;160:72-81.
+doi:\href{https://doi.org/10.1016/j.visres.2019.04.009}{10.1016/j.visres.2019.04.009}
+
+\leavevmode\hypertarget{ref-Baker2017}{}%
+40.
+Baker DH, Wade AR.
+Evidence for an optimal algorithm underlying signal combination in human visual cortex.
+\emph{Cereb Cortex}.
+2017;27(1):254-264.
+doi:\href{https://doi.org/10.1093/cercor/bhw395}{10.1093/cercor/bhw395}
+
+\leavevmode\hypertarget{ref-Baker2020}{}%
+41.
+Baker DH, Vilidaite G, McClarnon E, Valkova E, Bruno A, Millman RE.
+Binaural summation of amplitude modulation involves weak interaural suppression.
+\emph{Sci Rep}.
+2020;10(1):3560.
+doi:\href{https://doi.org/10.1038/s41598-020-60602-5}{10.1038/s41598-020-60602-5}
+
+\leavevmode\hypertarget{ref-Carroll2002}{}%
+42. Carroll J, Neitz J, Neitz M. Estimates of L:M cone ratio from ERG flicker photometry and genetics. \emph{Journal of Vision}. 2002;2(8):1. doi:\href{https://doi.org/10.1167/2.8.1}{10.1167/2.8.1}
+
+\leavevmode\hypertarget{ref-Hofer2005}{}%
+43.
+Hofer H, Carroll J, Neitz J, Neitz M, Williams DR.
+Organization of the human trichromatic cone mosaic.
+\emph{The Journal of Neuroscience}.
+2005;25(42):9669-9679.
+doi:\href{https://doi.org/10.1523/jneurosci.2414-05.2005}{10.1523/jneurosci.2414-05.2005}
+
 \leavevmode\hypertarget{ref-Baker2021}{}%
-Baker DH.
-2021.
-Statistical analysis of periodic data in neuroscience.
-\emph{Neurons, Behavior, Data analysis, and Theory} \textbf{5}.
-doi:\href{https://doi.org/10.51628/001c.27680}{10.51628/001c.27680}
+44. Baker DH. Statistical analysis of periodic data in neuroscience. \emph{Neurons, Behavior, Data analysis, and Theory}. 2021;5(3). doi:\href{https://doi.org/10.51628/001c.27680}{10.51628/001c.27680}
+
+\leavevmode\hypertarget{ref-Carpenter2017}{}%
+45. Carpenter B, Gelman A, Hoffman MD, et al. Stan: A probabilistic programming language. \emph{J Stat Softw}. 2017;76. doi:\href{https://doi.org/10.18637/jss.v076.i01}{10.18637/jss.v076.i01}
+
+\leavevmode\hypertarget{ref-Kingdom2015}{}%
+46.
+Kingdom FAA, Libenson L.
+Dichoptic color saturation mixture: Binocular luminance contrast promotes perceptual averaging.
+\emph{J Vis}.
+2015;15(5):2.
+doi:\href{https://doi.org/10.1167/15.5.2}{10.1167/15.5.2}
+
+\leavevmode\hypertarget{ref-Busse2009}{}%
+47.
+Busse L, Wade AR, Carandini M.
+Representation of concurrent stimuli by population activity in visual cortex.
+\emph{Neuron}.
+2009;64(6):931-942.
+doi:\href{https://doi.org/10.1016/j.neuron.2009.11.004}{10.1016/j.neuron.2009.11.004}
+
+\leavevmode\hypertarget{ref-Spitschan2019}{}%
+48. Spitschan M, Cajochen C. Binocular facilitation in light-mediated melatonin suppression? \emph{J Pineal Res}. 2019;67(4):e12602. doi:\href{https://doi.org/10.1111/jpi.12602}{10.1111/jpi.12602}
 
 \leavevmode\hypertarget{ref-Baker2024}{}%
-Baker DH, Hansford KJ, Segala FG, Morsi AY, Huxley RJ, Martin JT, Rockman M, Wade AR.
-2024.
-Binocular integration of chromatic and luminance signals.
-\emph{J Vis} \textbf{24(12)}:7.
-doi:\href{https://doi.org/10.1167/jov.24.12.7}{10.1167/jov.24.12.7}
-
-\leavevmode\hypertarget{ref-Baker2018}{}%
-Baker DH, Lygo FA, Meese TS, Georgeson MA.
-2018.
-Binocular summation revisited: Beyond \(\sqrt{2}\).
-\emph{Psychol Bull} \textbf{144}:1186--1199.
-doi:\href{https://doi.org/10.1037/bul0000163}{10.1037/bul0000163}
-
-\leavevmode\hypertarget{ref-Baker2007}{}%
-Baker DH, Meese TS, Georgeson MA.
-2007.
-Binocular interaction: Contrast matching and contrast discrimination are predicted by the same model.
-\emph{Spat Vis} \textbf{20}:397--413.
-doi:\href{https://doi.org/10.1163/156856807781503622}{10.1163/156856807781503622}
-
-\leavevmode\hypertarget{ref-Baker2020}{}%
-Baker DH, Vilidaite G, McClarnon E, Valkova E, Bruno A, Millman RE.
-2020.
-Binaural summation of amplitude modulation involves weak interaural suppression.
-\emph{Sci Rep} \textbf{10}:3560.
-doi:\href{https://doi.org/10.1038/s41598-020-60602-5}{10.1038/s41598-020-60602-5}
-
-\leavevmode\hypertarget{ref-Baker2017}{}%
-Baker DH, Wade AR.
-2017.
-Evidence for an optimal algorithm underlying signal combination in human visual cortex.
-\emph{Cereb Cortex} \textbf{27}:254--264.
-doi:\href{https://doi.org/10.1093/cercor/bhw395}{10.1093/cercor/bhw395}
-
-\leavevmode\hypertarget{ref-Barrionuevo2016}{}%
-Barrionuevo PA, Cao D.
-2016.
-Luminance and chromatic signals interact differently with melanopsin activation to control the pupil light response.
-\emph{Journal of Vision} \textbf{16(11)}:29.
-doi:\href{https://doi.org/10.1167/16.11.29}{10.1167/16.11.29}
-
-\leavevmode\hypertarget{ref-Bone1988}{}%
-Bone RA, Landrum JT, Fernandez L, Tarsis SL.
-1988.
-Analysis of the macular pigment by HPLC: Retinal distribution and age study.
-\emph{Investigative Ophthalmology \& Visual Science} \textbf{29}:843--849.
-
-\leavevmode\hypertarget{ref-Busse2009}{}%
-Busse L, Wade AR, Carandini M.
-2009.
-Representation of concurrent stimuli by population activity in visual cortex.
-\emph{Neuron} \textbf{64}:931--42.
-doi:\href{https://doi.org/10.1016/j.neuron.2009.11.004}{10.1016/j.neuron.2009.11.004}
-
-\leavevmode\hypertarget{ref-Campbell1965}{}%
-Campbell FW, Green DG. 1965. Monocular versus binocular visual acuity. \emph{Nature} \textbf{208}:191--2. doi:\href{https://doi.org/10.1038/208191a0}{10.1038/208191a0}
-
-\leavevmode\hypertarget{ref-Carpenter2017}{}%
-Carpenter B, Gelman A, Hoffman MD, Lee D, Goodrich B, Betancourt M, Brubaker MA, Guo J, Li P, Riddell A.
-2017.
-Stan: A probabilistic programming language.
-\emph{J Stat Softw} \textbf{76}.
-doi:\href{https://doi.org/10.18637/jss.v076.i01}{10.18637/jss.v076.i01}
-
-\leavevmode\hypertarget{ref-Carroll2002}{}%
-Carroll J, Neitz J, Neitz M. 2002. Estimates of L:M cone ratio from ERG flicker photometry and genetics. \emph{Journal of Vision} \textbf{2}:1. doi:\href{https://doi.org/10.1167/2.8.1}{10.1167/2.8.1}
-
-\leavevmode\hypertarget{ref-CIE2018}{}%
-CIE. 2018. CIE system for metrology of optical radiation for ipRGC-influenced responses to light. CIE Central Bureau. doi:\href{https://doi.org/10.25039/S026.2018}{10.25039/S026.2018}
-
-\leavevmode\hypertarget{ref-CIE2006}{}%
-CIE. 2006. Fundamental chromaticity diagram with physiological axes. CIE Central Bureau.
-
-\leavevmode\hypertarget{ref-Dacey2003}{}%
-Dacey DM, Peterson BB, Robinson FR, Gamlin PD.
-2003.
-Fireworks in the primate retina: In vitro photodynamics reveals diverse lgn-projecting ganglion cell types.
-\emph{Neuron} \textbf{37}:15--27.
-doi:\href{https://doi.org/https://doi.org/10.1016/S0896-6273(02)01143-1}{https://doi.org/10.1016/S0896-6273(02)01143-1}
-
-\leavevmode\hypertarget{ref-Estevez1982}{}%
-Estévez O, Spekreijse H.
-1982.
-The "silent substitution" method in visual research.
-\emph{Vision Research} \textbf{22}:681--691.
-doi:\href{https://doi.org/10.1016/0042-6989(82)90104-3}{10.1016/0042-6989(82)90104-3}
-
-\leavevmode\hypertarget{ref-Gamlin2007}{}%
-Gamlin PDR, McDougal DH, Pokorny J, Smith VC, Yau K-W, Dacey DM.
-2007.
-Human and macaque pupil responses driven by melanopsin-containing retinal ganglion cells.
-\emph{Vision Research} \textbf{47}:946--954.
-doi:\href{https://doi.org/10.1016/j.visres.2006.12.015}{10.1016/j.visres.2006.12.015}
-
-\leavevmode\hypertarget{ref-Hofer2005}{}%
-Hofer H, Carroll J, Neitz J, Neitz M, Williams DR.
-2005.
-Organization of the human trichromatic cone mosaic.
-\emph{The Journal of Neuroscience} \textbf{25}:9669--9679.
-doi:\href{https://doi.org/10.1523/jneurosci.2414-05.2005}{10.1523/jneurosci.2414-05.2005}
-
-\leavevmode\hypertarget{ref-Hubel1962}{}%
-Hubel DH, Wiesel TN.
-1962.
-Receptive fields, binocular interaction and functional architecture in the cat's visual cortex.
-\emph{J Physiol} \textbf{160}:106--54.
-doi:\href{https://doi.org/10.1113/jphysiol.1962.sp006837}{10.1113/jphysiol.1962.sp006837}
+49. Baker DH, Hansford KJ, Segala FG, et al. Binocular integration of chromatic and luminance signals. \emph{J Vis}. 2024;24(12):7. doi:\href{https://doi.org/10.1167/jov.24.12.7}{10.1167/jov.24.12.7}
 
 \leavevmode\hypertarget{ref-Kaestner2019}{}%
-Kaestner M, Maloney RT, Wailes-Newson KH, Bloj M, Harris JM, Morland AB, Wade AR.
-2019.
+50.
+Kaestner M, Maloney RT, Wailes-Newson KH, et al.
 Asymmetries between achromatic and chromatic extraction of 3D motion signals.
-\emph{Proc Natl Acad Sci U S A} \textbf{116}:13631--13640.
+\emph{Proc Natl Acad Sci U S A}.
+2019;116(27):13631-13640.
 doi:\href{https://doi.org/10.1073/pnas.1817202116}{10.1073/pnas.1817202116}
-
-\leavevmode\hypertarget{ref-Kassner2014}{}%
-Kassner M, Patera W, Bulling A.
-2014.
-Pupil: An open source platform for pervasive eye tracking and mobile gaze-based interaction.Proceedings of the 2014 ACM International Joint Conference on Pervasive and Ubiquitous Computing: Adjunct Publication.
-ACM.
-doi:\href{https://doi.org/10.1145/2638728.2641695}{10.1145/2638728.2641695}
-
-\leavevmode\hypertarget{ref-Kingdom2015}{}%
-Kingdom FAA, Libenson L.
-2015.
-Dichoptic color saturation mixture: Binocular luminance contrast promotes perceptual averaging.
-\emph{J Vis} \textbf{15}:2.
-doi:\href{https://doi.org/10.1167/15.5.2}{10.1167/15.5.2}
-
-\leavevmode\hypertarget{ref-Lucas2003}{}%
-Lucas RJ, Hattar S, Takao M, Berson DM, Foster RG, Yau K-W.
-2003.
-Diminished pupillary light reflex at high irradiances in melanopsin-knockout mice.
-\emph{Science} \textbf{299}:245--247.
-doi:\href{https://doi.org/10.1126/science.1077293}{10.1126/science.1077293}
-
-\leavevmode\hypertarget{ref-Markwell2010}{}%
-Markwell EL, Feigl B, Zele AJ.
-2010.
-Intrinsically photosensitive melanopsin retinal ganglion cell contributions to the pupillary light reflex and circadian rhythm.
-\emph{Clinical and Experimental Optometry} \textbf{93}:137--149.
-doi:\href{https://doi.org/10.1111/j.1444-0938.2010.00479.x}{10.1111/j.1444-0938.2010.00479.x}
-
-\leavevmode\hypertarget{ref-Martin2023}{}%
-Martin JT, Boynton GM, Baker DH, Wade AR, Spitschan M.
-2023.
-PySilSub: An open-source python toolbox for implementing the method of silent substitution in vision and nonvisual photoreception research.
-\emph{Journal of Vision} \textbf{23}:10.
-doi:\href{https://doi.org/10.1167/jov.23.7.10}{10.1167/jov.23.7.10}
-
-\leavevmode\hypertarget{ref-Martin2022}{}%
-Martin JT, Pinto J, Bulte D, Spitschan M.
-2022.
-PyPlr: A versatile, integrated system of hardware and software for researching the human pupillary light reflex.
-\emph{Behavior Research Methods} \textbf{54}:2720--2739.
-doi:\href{https://doi.org/10.3758/s13428-021-01759-3}{10.3758/s13428-021-01759-3}
-
-\leavevmode\hypertarget{ref-Mathot2018}{}%
-Mathôt S. 2018. Pupillometry: Psychology, physiology, and function. \emph{J Cogn} \textbf{1}:16. doi:\href{https://doi.org/10.5334/joc.18}{10.5334/joc.18}
-
-\leavevmode\hypertarget{ref-McDougal2015}{}%
-McDougal DH, Gamlin PD. 2015. Autonomic control of the eye. \emph{Comprehensive Physiology} \textbf{5}:439--473. doi:\href{https://doi.org/10.1002/cphy.c140014}{10.1002/cphy.c140014}
-
-\leavevmode\hypertarget{ref-McDougal2010}{}%
-McDougal DH, Gamlin PD.
-2010.
-The influence of intrinsically-photosensitive retinal ganglion cells on the spectral sensitivity and response dynamics of the human pupillary light reflex.
-\emph{Vision Research} \textbf{50}:72--87.
-doi:\href{https://doi.org/10.1016/j.visres.2009.10.012}{10.1016/j.visres.2009.10.012}
-
-\leavevmode\hypertarget{ref-Meese2006}{}%
-Meese TS, Georgeson MA, Baker DH. 2006. Binocular contrast vision at and above threshold. \emph{Journal of Vision} \textbf{6}:1224--43. doi:\href{https://doi.org/10.1167/6.11.7}{10.1167/6.11.7}
-
-\leavevmode\hypertarget{ref-Moradi2009}{}%
-Moradi F, Heeger DJ. 2009. Inter-ocular contrast normalization in human visual cortex. \emph{J Vis} \textbf{9}:13.1--22. doi:\href{https://doi.org/10.1167/9.3.13}{10.1167/9.3.13}
-
-\leavevmode\hypertarget{ref-Murray2018}{}%
-Murray IJ, Kremers J, McKeefry D, Parry NRA.
-2018.
-Paradoxical pupil responses to isolated M-cone increments.
-\emph{Journal of the Optical Society of America A} \textbf{35}:B66--B71.
-doi:\href{https://doi.org/10.1364/JOSAA.35.000B66}{10.1364/JOSAA.35.000B66}
-
-\leavevmode\hypertarget{ref-Norcia2015}{}%
-Norcia AM, Appelbaum LG, Ales JM, Cottereau BR, Rossion B.
-2015.
-The steady-state visual evoked potential in vision research: A review.
-\emph{Journal of Vision} \textbf{15(6)}:4.
-doi:\href{https://doi.org/10.1167/15.6.4}{10.1167/15.6.4}
-
-\leavevmode\hypertarget{ref-Panda2002}{}%
-Panda S, Sato TK, Castrucci AM, Rollag MD, DeGrip WJ, Hogenesch JB, Provencio I, Kay SA.
-2002.
-Melanopsin (opn4) requirement for normal light-induced circadian phase shifting.
-\emph{Science} \textbf{298}:2213--2216.
-doi:\href{https://doi.org/10.1126/science.1076848}{10.1126/science.1076848}
-
-\leavevmode\hypertarget{ref-Pokorny1987}{}%
-Pokorny J, Smith VC, Lutze M. 1987. Aging of the human lens. \emph{Applied Optics} \textbf{26}:1437. doi:\href{https://doi.org/10.1364/ao.26.001437}{10.1364/ao.26.001437}
-
-\leavevmode\hypertarget{ref-Provencio2000}{}%
-Provencio I, Rodriguez IR, Jiang G, Hayes WP, Moreira EF, Rollag MD.
-2000.
-A Novel Human Opsin in the Inner Retina.
-\emph{Journal of Neuroscience} \textbf{20}:600--605.
-doi:\href{https://doi.org/10.1523/JNEUROSCI.20-02-00600.2000}{10.1523/JNEUROSCI.20-02-00600.2000}
-
-\leavevmode\hypertarget{ref-Ruby2002}{}%
-Ruby NF, Brennan TJ, Xie X, Cao V, Franken P, Heller HC, O'Hara BF.
-2002.
-Role of melanopsin in circadian responses to light.
-\emph{Science} \textbf{298}:2211--2213.
-doi:\href{https://doi.org/10.1126/science.1076701}{10.1126/science.1076701}
-
-\leavevmode\hypertarget{ref-SegalaThesis2023}{}%
-Segala FG.
-2023.
-Binocular combination of light in canonical and non-canonical pathways (phd).
-University of York.
-doi:\href{https://doi.org/https://etheses.whiterose.ac.uk/id/oai_id/oai:etheses.whiterose.ac.uk:34419}{https://etheses.whiterose.ac.uk/id/oai\_id/oai:etheses.whiterose.ac.uk:34419}
-
-\leavevmode\hypertarget{ref-Segala2023}{}%
-Segala FG, Bruno A, Martin JT, Aung MT, Wade AR, Baker DH.
-2023.
-Different rules for binocular combination of luminance flicker in cortical and subcortical pathways.
-\emph{eLife} \textbf{12}.
-doi:\href{https://doi.org/10.7554/elife.87048}{10.7554/elife.87048}
-
-\leavevmode\hypertarget{ref-Shapiro1996}{}%
-Shapiro AG, Pokorny J, Smith VC.
-1996.
-Conerod receptor spaces with illustrations that use CRT phosphor and light-emitting-diode spectra.
-\emph{Journal of the Optical Society of America A} \textbf{13}:2319.
-doi:\href{https://doi.org/10.1364/josaa.13.002319}{10.1364/josaa.13.002319}
-
-\leavevmode\hypertarget{ref-Spitschan2015}{}%
-Spitschan M, Aguirre GK, Brainard DH.
-2015.
-Selective stimulation of penumbral cones reveals perception in the shadow of retinal blood vessels.
-\emph{PLoS One} \textbf{10}:e0124328.
-doi:\href{https://doi.org/10.1371/journal.pone.0124328}{10.1371/journal.pone.0124328}
-
-\leavevmode\hypertarget{ref-Spitschan2019}{}%
-Spitschan M, Cajochen C. 2019. Binocular facilitation in light-mediated melatonin suppression? \emph{J Pineal Res} \textbf{67}:e12602. doi:\href{https://doi.org/10.1111/jpi.12602}{10.1111/jpi.12602}
-
-\leavevmode\hypertarget{ref-Spitschan2014}{}%
-Spitschan M, Jain S, Brainard DH, Aguirre GK.
-2014.
-Opponent melanopsin and s-cone signals in the human pupillary light response.
-\emph{Proceedings of the National Academy of Sciences} \textbf{111}:15568--15572.
-doi:\href{https://doi.org/10.1073/pnas.1400942111}{10.1073/pnas.1400942111}
-
-\leavevmode\hypertarget{ref-Spitschan2018}{}%
-Spitschan M, Woelders T.
-2018.
-The Method of Silent Substitution for Examining Melanopsin Contributions to Pupil Control.
-\emph{Frontiers in Neurology} \textbf{9}.
-doi:\href{https://doi.org/10.3389/fneur.2018.00941}{10.3389/fneur.2018.00941}
-
-\leavevmode\hypertarget{ref-Stockman2000}{}%
-Stockman A, Sharpe LT.
-2000.
-The spectral sensitivities of the middle- and long-wavelength-sensitive cones derived from measurements in observers of known genotype.
-\emph{Vision Res} \textbf{40}:1711--37.
-doi:\href{https://doi.org/10.1016/s0042-6989(00)00021-3}{10.1016/s0042-6989(00)00021-3}
-
-\leavevmode\hypertarget{ref-Stockman1999}{}%
-Stockman A, Sharpe LT, Fach C.
-1999.
-The spectral sensitivity of the human short-wavelength sensitive cones derived from thresholds and color matches.
-\emph{Vision Research} \textbf{39}:2901--2927.
-doi:\href{https://doi.org/https://doi.org/10.1016/S0042-6989(98)00225-9}{https://doi.org/10.1016/S0042-6989(98)00225-9}
-
-\leavevmode\hypertarget{ref-Trieschmann2007}{}%
-Trieschmann M, Kuijk FJGM van, Alexander R, Hermans P, Luthert P, Bird AC, Pauleikhoff D.
-2007.
-Macular pigment in the human retina: Histological evaluation of localization and distribution.
-\emph{Eye} \textbf{22}:132--137.
-doi:\href{https://doi.org/10.1038/sj.eye.6702780}{10.1038/sj.eye.6702780}
-
-\leavevmode\hypertarget{ref-Woelders2018}{}%
-Woelders T, Leenheers T, Gordijn MCM, Hut RA, Beersma DGM, Wams EJ.
-2018.
-Melanopsin- and L-cone--induced pupil constriction is inhibited by S- and M-cones in humans.
-\emph{Proceedings of the National Academy of Sciences} \textbf{115}:792--797.
-doi:\href{https://doi.org/10.1073/pnas.1716281115}{10.1073/pnas.1716281115}
-
-\leavevmode\hypertarget{ref-Wyatt1981}{}%
-Wyatt HJ, Musselman JF.
-1981.
-Pupillary light reflex in humans: Evidence for an unbalanced pathway from nasal retina, and for signal cancellation in brainstem.
-\emph{Vision Res} \textbf{21}:513--25.
-doi:\href{https://doi.org/10.1016/0042-6989(81)90097-3}{10.1016/0042-6989(81)90097-3}
-
-\leavevmode\hypertarget{ref-Zele2019}{}%
-Zele AJ, Adhikari P, Cao D, Feigl B.
-2019.
-Melanopsin driven enhancement of cone-mediated visual processing.
-\emph{Vision Res} \textbf{160}:72--81.
-doi:\href{https://doi.org/10.1016/j.visres.2019.04.009}{10.1016/j.visres.2019.04.009}
-
-\leavevmode\hypertarget{ref-Zele2018}{}%
-Zele AJ, Feigl B, Adhikari P, Maynard ML, Cao D.
-2018.
-Melanopsin photoreception contributes to human visual detection, temporal and colour processing.
-\emph{Scientific Reports} \textbf{8}.
-doi:\href{https://doi.org/10.1038/s41598-018-22197-w}{10.1038/s41598-018-22197-w}
 

### 2025-02-28 manuscript.Rmd
Abstract formatting

@@
 
-Pupil diameters are regulated by the autonomic nervous system, which combines light signals across the eyes independently of the visual cortex.
+**Purpose:** Pupil diameters are regulated by the autonomic nervous system, which combines light signals across the eyes independently of the visual cortex.
 Distinct classes of retinal photoreceptor are involved in this process, with cones and rods driving the initial constriction and intrinsically photosensitive retinal ganglion cells maintaining diameter over prolonged time periods.
-We investigated binocular combination by targeting different photoreceptor pathways using a novel binocular multiprimary system to modulate the input spectra via silent substitution.
-At the first harmonic of the modulation frequency, light flux and S-cone responses showed strong binocular facilitation, and weak interocular suppression.
+
+**Methods:** We investigated binocular combination by targeting different photoreceptor pathways using a novel binocular multiprimary system to modulate the input spectra via silent substitution.
+
+**Results:** At the first harmonic of the modulation frequency, light flux and S-cone responses showed strong binocular facilitation, and weak interocular suppression.
 Melanopsin responses were invariant to the number of eyes stimulated.
@@
 We also find pathway differences in response phase, consistent with different lag times for phototransduction.
-This work demonstrates for the first time the algorithm governing binocular combination in the autonomic nervous system.
+
+**Conclusions:** This work demonstrates for the first time the algorithm governing binocular combination in the autonomic nervous system.
 

### 2025-02-28 manuscript.tex
Abstract formatting

@@
 
-Pupil diameters are regulated by the autonomic nervous system, which combines light signals across the eyes independently of the visual cortex.
+\textbf{Purpose:} Pupil diameters are regulated by the autonomic nervous system, which combines light signals across the eyes independently of the visual cortex.
 Distinct classes of retinal photoreceptor are involved in this process, with cones and rods driving the initial constriction and intrinsically photosensitive retinal ganglion cells maintaining diameter over prolonged time periods.
-We investigated binocular combination by targeting different photoreceptor pathways using a novel binocular multiprimary system to modulate the input spectra via silent substitution.
-At the first harmonic of the modulation frequency, light flux and S-cone responses showed strong binocular facilitation, and weak interocular suppression.
+
+\textbf{Methods:} We investigated binocular combination by targeting different photoreceptor pathways using a novel binocular multiprimary system to modulate the input spectra via silent substitution.
+
+\textbf{Results:} At the first harmonic of the modulation frequency, light flux and S-cone responses showed strong binocular facilitation, and weak interocular suppression.
 Melanopsin responses were invariant to the number of eyes stimulated.
@@
 We also find pathway differences in response phase, consistent with different lag times for phototransduction.
-This work demonstrates for the first time the algorithm governing binocular combination in the autonomic nervous system.
+
+\textbf{Conclusions:} This work demonstrates for the first time the algorithm governing binocular combination in the autonomic nervous system.
 

### 2025-03-04 manuscript.Rmd
Changes to abstract and title page

@@
 
-Corresponding author: Federico G. Segala, [federico.segala@york.ac.uk](federico.segala@york.ac.uk).
+**Corresponding author**:
+
+Federico G. Segala
+
+Department of Psychology
+
+University of York
+
+Heslington
+
+York, YO10 5DD, United Kingdom
+
+[federico.segala@york.ac.uk](federico.segala@york.ac.uk).
+
+**Word count**: 4500
+
+**Number of Figures**: 5   **Number of Tables**: 1  **Number of Supplementary Files**: 0
+
+**Funding**: Supported by Biotechnology and Biological Sciences Research Council grant BB/V007580/1 awarded to DHB and ARW.
+
+**Commercial Relationships Disclosure**: F.G. Segala, None; A. Bruno, None; J.T. Martin, None; A.Y. Morsi, None; A.R. Wade, None; D.H. Baker, None
+
+**Running Head**: Binocular combination in autonomic nervous system
+
+\pagebreak
 
@@
 
-**Conclusions:** This work demonstrates for the first time the algorithm governing binocular combination in the autonomic nervous system.
+**Conclusions:** This work demonstrates for the first time the algorithm governing binocular combination of temporal flickering light in the autonomic nervous system, which depends on the photoreceptor pathway stimulated.
 
@@
 The outputs of the two light engines (see Figure \@ref(fig:spectraplots)b,c) were calibrated using an Ocean Optics Jaz spectroradiometer, which was wavelength-calibrated to an Argon lamp and intensity calibrated using a NIST-traceable light source.
-Each primary was also linearized using a polynomial fit (see Figure \@ref(fig:primarylinearity) for details).
+Each primary was also linearised using a polynomial fit (see Figure \@ref(fig:primarylinearity) for details).
 We used the 10-degree cone fundamentals [@Stockman2000], and estimates of melanopsin absorbance spectra from CIE S 026 (discussed in a previous paper [@Martin2023]) to calculate $\alpha$-opic irradiance.

### 2025-03-04 manuscript.tex
Changes to abstract and title page

@@
 
-Corresponding author: Federico G. Segala, \url{federico.segala@york.ac.uk}.
+\textbf{Corresponding author}:
+
+Federico G. Segala
+
+Department of Psychology
+
+University of York
+
+Heslington
+
+York, YO10 5DD, United Kingdom
+
+\url{federico.segala@york.ac.uk}.
+
+\textbf{Word count}: 4500
+
+\textbf{Number of Figures}: 5 \textbf{Number of Tables}: 1 \textbf{Number of Supplementary Files}: 0
+
+\textbf{Funding}: Supported by Biotechnology and Biological Sciences Research Council grant BB/V007580/1 awarded to DHB and ARW.
+
+\textbf{Commercial Relationships Disclosure}: F.G. Segala, None; A. Bruno, None; J.T. Martin, None; A.Y. Morsi, None; A.R. Wade, None; D.H. Baker, None
+
+\textbf{Running Head}: Binocular combination in autonomic nervous system
+
+\pagebreak
 
@@
 
-\textbf{Conclusions:} This work demonstrates for the first time the algorithm governing binocular combination in the autonomic nervous system.
+\textbf{Conclusions:} This work demonstrates for the first time the algorithm governing binocular combination of temporal flickering light in the autonomic nervous system, which depends on the photoreceptor pathway stimulated.
 
@@
 The outputs of the two light engines (see Figure \ref{fig:spectraplots}b,c) were calibrated using an Ocean Optics Jaz spectroradiometer, which was wavelength-calibrated to an Argon lamp and intensity calibrated using a NIST-traceable light source.
-Each primary was also linearized using a polynomial fit (see Figure \ref{fig:primarylinearity} for details).
+Each primary was also linearised using a polynomial fit (see Figure \ref{fig:primarylinearity} for details).
 We used the 10-degree cone fundamentals,\textsuperscript{\protect\hyperlink{ref-Stockman2000}{28}} and estimates of melanopsin absorbance spectra from CIE S 026 (discussed in a previous paper\textsuperscript{\protect\hyperlink{ref-Martin2023}{27}}) to calculate \(\alpha\)-opic irradiance.

### 2025-09-15 manuscript.Rmd
Changes

@@
 
-pdf(paste0(figdir,"methodsfigrods1.pdf"), bg="transparent", height = 13, width = 12)
+pdf(paste0(figdir,"methodsfigrods.pdf"), bg="transparent", height = 13, width = 12)
 
@@
 
+prefixlist <- c('P6','P7','P3','P5')
+
+  d <- dir(datadir,pattern=prefixlist[1], full.names = TRUE)
+
   load(file=paste0(datadir,'AveragedataLum.RData'))
@@
 filtL <- signal::filter(filt,meanwavesPCI[2,])
-polygon(times[c(1:length(times),length(times):1)],c(filtL,filtU[length(filtU):1]),col=addalpha(colpal[2],0.3),border=NA)
+polygon(times[c(1:length(times),length(times):1)],c(filtL,filtU[length(filtU):1]),col=addalpha(colpal[2],0.4),border=NA)
 lines(times, filtwaveP, col=colpal[2], lwd=1.5)
@@
 
+for (part in 1:24) {
+  load(file=paste0(d[part]))
+  filt <- butter(3,0.083)
+  filtwaveP <- signal::filter(filt, meanwavesP)
+  lines(times, filtwaveP, col=addalpha(colpal[2],0.7), lwd=0.2)
+}
+
 text(-1,0.4,'(m)',pos=4,cex=2)
@@
   load(file=paste0(datadir,'AveragedataLM.RData'))
+d <- dir(datadir,pattern=prefixlist[2], full.names = TRUE)
 
@@
 
+for (part in 1:24) {
+  load(file=paste0(d[part]))
+  filt <- butter(3,0.083)
+  filtwaveP <- signal::filter(filt, meanwavesP)
+  lines(times, filtwaveP, col=addalpha(colpal[2],0.7), lwd=0.2)
+}
+
 text(-1,0.4,'(n)',pos=4,cex=2)
@@
   load(file=paste0(datadir,'AveragedataS.RData'))
+  d <- dir(datadir,pattern=prefixlist[3], full.names = TRUE)
 
@@
 
+for (part in 1:24) {
+  load(file=paste0(d[part]))
+  filt <- butter(3,0.083)
+  filtwaveP <- signal::filter(filt, meanwavesP)
+  lines(times, filtwaveP, col=addalpha(colpal[2],0.7), lwd=0.2)
+}
+
 text(-1,0.4,'(o)',pos=4,cex=2)
@@
 load(file=paste0(datadir,'AveragedataMel.RData'))
+d <- dir(datadir,pattern=prefixlist[4], full.names = TRUE)
 
@@
 filtL <- signal::filter(filt,meanwavesPCI[2,])
-polygon(times[c(1:length(times),length(times):1)],c(filtL,filtU[length(filtU):1]),col=addalpha(colpal[2],0.3),border=NA)
+polygon(times[c(1:length(times),length(times):1)],c(filtL,filtU[length(filtU):1]),col=addalpha(colpal[2],0.4),border=NA)
 lines(times, filtwaveP, col=colpal[2], lwd=1.5)
 lines(times, (sinewave/10)-0.9, col='black', lwd=2)
+
+for (part in 1:24) {
+  load(file=paste0(d[part]))
+  filt <- butter(3,0.083)
+  filtwaveP <- signal::filter(filt, meanwavesP)
+  lines(times, filtwaveP, col=addalpha(colpal[2],0.7), lwd=0.2)
+}
 
@@
 ```
+
+```{r individualpupiltraces, include=FALSE, results='hide'}
+
+# create plots of spectra, cone absorption, waveforms and Fourier spectra
+if (processdata > 0){
+
+pdf(paste0(figdir,"indpupiltrace.pdf"), bg="transparent", height = 13, width = 12)
+
+layout(matrix(1:4, 2, 2, byrow = TRUE))
+par(mar=c(3.5,2.5,1,1))
+
+prefixlist <- c('P6','P7','P3','P5')
+
+  d <- dir(datadir,pattern=prefixlist[1], full.names = TRUE)
+
+plotlims <- c(-1,13,-1,0.5)
+ticklocsx <- c(-1,seq(0,12,2),13)    # locations of tick marks on x axis
+ticklocsy <- seq(-1,0.5,0.5)    # locations of tick marks on y axis
+ticklabelsx <- c('',seq(0,12,2),'')        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(ylab="Diameter change (mm)", col.lab=rgb(0,0,0), line=2.8, cex.lab=1.5)
+
+lines(times, (sinewave/10)-0.9, col='black', lwd=2)
+
+for (part in 1:24) {
+  load(file=paste0(d[part]))
+  filt <- butter(3,0.083)
+  filtwaveP <- signal::filter(filt, meanwavesP)
+  lines(times, filtwaveP, col=colpal[2], lwd=1)
+}
+
+text(-1,0.4,'(a)',pos=4,cex=2)
+
+d <- dir(datadir,pattern=prefixlist[2], full.names = TRUE)
+
+plotlims <- c(-1,13,-1,0.5)
+ticklocsx <- c(-1,seq(0,12,2),13)    # locations of tick marks on x axis
+ticklocsy <- seq(-1,0.5,0.5)    # locations of tick marks on y axis
+ticklabelsx <- c('',seq(0,12,2),'')        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(ylab="Diameter change (mm)", col.lab=rgb(0,0,0), line=2.8, cex.lab=1.5)
+
+lines(times, (sinewave/10)-0.9, col='black', lwd=2)
+
+for (part in 1:24) {
+  load(file=paste0(d[part]))
+  filt <- butter(3,0.083)
+  filtwaveP <- signal::filter(filt, meanwavesP)
+  lines(times, filtwaveP, col=colpal[2], lwd=1)
+}
+
+text(-1,0.4,'(b)',pos=4,cex=2)
+
+  d <- dir(datadir,pattern=prefixlist[3], full.names = TRUE)
+
+plotlims <- c(-1,13,-1,0.5)
+ticklocsx <- c(-1,seq(0,12,2),13)    # locations of tick marks on x axis
+ticklocsy <- seq(-1,0.5,0.5)    # locations of tick marks on y axis
+ticklabelsx <- c('',seq(0,12,2),'')        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(ylab="Diameter change (mm)", col.lab=rgb(0,0,0), line=2.8, cex.lab=1.5)
+
+lines(times, (sinewave/10)-0.9, col='black', lwd=2)
+
+for (part in 1:24) {
+  load(file=paste0(d[part]))
+  filt <- butter(3,0.083)
+  filtwaveP <- signal::filter(filt, meanwavesP)
+  lines(times, filtwaveP, col=colpal[2], lwd=1)
+}
+
+text(-1,0.4,'(c)',pos=4,cex=2)
+
+d <- dir(datadir,pattern=prefixlist[4], full.names = TRUE)
+
+plotlims <- c(-1,13,-1,0.5)
+ticklocsx <- c(-1,seq(0,12,2),13)    # locations of tick marks on x axis
+ticklocsy <- seq(-1,0.5,0.5)    # locations of tick marks on y axis
+ticklabelsx <- c('',seq(0,12,2),'')        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(ylab="Diameter change (mm)", col.lab=rgb(0,0,0), line=2.8, cex.lab=1.5)
+
+lines(times, (sinewave/10)-0.9, col='black', lwd=2)
+
+for (part in 1:24) {
+  load(file=paste0(d[part]))
+  filt <- butter(3,0.083)
+  filtwaveP <- signal::filter(filt, meanwavesP)
+  lines(times, filtwaveP, col=colpal[2], lwd=1)
+}
+
+text(-1,0.4,'(d)',pos=4,cex=2)
+
+dev.off()
+
+}
+
+```

### 2025-10-09 manuscript.Rmd
Changes

@@
 linkcolor: black
-csl: investigative-ophthalmology-and-visual-science.csl
+csl: plos-computational-biology.csl
 header-includes:
@@
 
-**Corresponding author**:
-
-Federico G. Segala
-
-Department of Psychology
-
-University of York
-
-Heslington
-
-York, YO10 5DD, United Kingdom
-
-[federico.segala@york.ac.uk](federico.segala@york.ac.uk).
-
-**Word count**: 4500
-
-**Number of Figures**: 5   **Number of Tables**: 1  **Number of Supplementary Files**: 0
-
-**Funding**: Supported by Biotechnology and Biological Sciences Research Council grant BB/V007580/1 awarded to DHB and ARW.
-
-**Commercial Relationships Disclosure**: F.G. Segala, None; A. Bruno, None; J.T. Martin, None; A.Y. Morsi, None; A.R. Wade, None; D.H. Baker, None
-
-**Running Head**: Binocular combination in autonomic nervous system
+*Corresponding author
+
+E-mail:[federico.segala@york.ac.uk](federico.segala@york.ac.uk) (FGS)
 
@@
 
-**Purpose:** Pupil diameters are regulated by the autonomic nervous system, which combines light signals across the eyes independently of the visual cortex.
+Pupil diameters are regulated by the autonomic nervous system, which combines light signals across the eyes independently of the visual cortex.
 Distinct classes of retinal photoreceptor are involved in this process, with cones and rods driving the initial constriction and intrinsically photosensitive retinal ganglion cells maintaining diameter over prolonged time periods.
-
-**Methods:** We investigated binocular combination by targeting different photoreceptor pathways using a novel binocular multiprimary system to modulate the input spectra via silent substitution.
-
-**Results:** At the first harmonic of the modulation frequency, light flux and S-cone responses showed strong binocular facilitation, and weak interocular suppression.
+We investigated binocular combination by targeting different photoreceptor pathways using a novel binocular multiprimary system to modulate the input spectra via silent substitution.
+At the first harmonic of the modulation frequency, luminance and S-cone responses showed strong binocular facilitation, and weak interocular suppression.
 Melanopsin responses were invariant to the number of eyes stimulated.
@@
 We also find pathway differences in response phase, consistent with different lag times for phototransduction.
-
-**Conclusions:** This work demonstrates for the first time the algorithm governing binocular combination of temporal flickering light in the autonomic nervous system, which depends on the photoreceptor pathway stimulated.
+This work demonstrates for the first time the algorithm governing binocular combination in the autonomic nervous system.
+
+# Author Summary
+
+Our pupils constantly adjust in size to control how much light enters the eye: in brighter conditions the pupils will reduce in size, and in dimmer conditions they will increase in size.
+This process, known as the pupillary light response, is usually taken for granted but is crucial for vision, and is controlled automatically by the body’s nervous system.
+Different types of light-sensing cells in the retina, the photoreceptor cells, contribute to this response: some respond quickly to changes in light, while others maintain responses over longer periods.
+In our study, we explored how signals from the two eyes are combined to regulate pupil size.
+Using a new type of visual stimulation that allowed us to selectively target specific classes of photoreceptor cells, we found that the way the two eyes’ signals are combined depends on which class of photoreceptor cells is involved.
+For example, some photoreceptor classes showed cooperation between the eyes, while others showed competition.
+By revealing these distinct patterns of signal combination, our work provides new insight into how light information is integrated in the pupils.
 
@@
 The results are interpreted using a contemporary model of binocular vision [@Meese2006] implemented within a hierarchical Bayesian framework.
+
+# Results
+
+Figure \@ref(fig:spectraplots)m-p shows averaged waveforms of pupil diameter in response to binocular stimulation.
+For light flux stimuli (Figure \@ref(fig:spectraplots)m) a strong modulation is apparent at the stimulation frequency (0.5Hz), which is also clear in the Fourier amplitude spectrum (Figure \@ref(fig:spectraplots)q).
+For binocular stimulation of the L-M pathway, S-cone pathway and melanopsin pathway, pupil modulations were less than 10\% of the amplitude of the light flux modulation (note the change in y-axis scale for the Fourier spectra), but still apparent at 0.5Hz in the Fourier spectra (Figure \@ref(fig:spectraplots)n-p).
+We also observed a second harmonic response (at 1Hz) for all conditions, which was weaker than the first harmonic for light flux and melanopsin stimulation, but stronger for L-M and S-cone stimulation.
+The second harmonic is also apparent in the pupil waveforms shown in Figure \@ref(fig:spectraplots)n-p.
+Our main analysis therefore focuses on the amplitude of the pupil modulations at both the first and second harmonic frequencies across different stimulus conditions.
+
+```{r spectraplots, fig.cap="Summary of the spectral power distributions and alpha-opic irradiances for the background and each condition, as well as averaged pupil diameters and Fourier spectra.
+Panel (a) shows a schematic of the binocular stimulation system for presenting spectrally tuned modulations independently to each eye.
+The VR headset was attached to a clamp stand that the experimenters could use to adjust the height and align the headset with the eyes of the participant.
+The participant's head was supported by a chin rest to keep it in position throughout the experiment.
+Panel (b) shows the outputs of each LED primary at maximum intensity, and panels (c) and (d) show the overall spectral power distributions and the alpha-opic irradiances of the background spectra used for both eyes.
+The subsequent rows show the power differences (e-h), and photoreceptor contrasts (i-l) relative to the background, averaged pupil diameter waveforms (m-p) and Fourier spectra (q-t) for binocular stimulation.
+Column headings indicate the pathway stimulated, and shaded regions in panels m-t indicate bootstrapped 95\\% confidence intervals.", fig.align="center", out.width = '80%', echo=FALSE}
+
+knitr::include_graphics(paste0(figdir,'methodsfigrods.pdf'))
+
+```
+
+Figure \@ref(fig:FirstHarmonicPlots)a-d shows contrast response functions across stimulation conditions for responses at the first harmonic of the main stimulation frequency (0.5Hz).
+In each plot, the response to monocular stimulation is given by the red circles and typically increases monotonically as a function of stimulus (temporal) contrast.
+Relative to monocular stimulation, binocular stimulation led to higher response amplitudes, indicating a binocular facilitation effect, for the light flux and S-cone conditions (Figure \@ref(fig:FirstHarmonicPlots)a,c), and to some extent for the melanopsin condition (Figure \@ref(fig:FirstHarmonicPlots)d).
+However, the L-M cone condition (Figure \@ref(fig:FirstHarmonicPlots)b) produced a binocular suppression effect, where the response to binocular stimulation was weaker than the response to monocular stimulation (blue squares below red circles).
+These results indicate that the magnitude of binocular facilitation differs across photoreceptor pathway, suggesting heterogeneity in the underlying neural computation.
+
+```{r FirstHarmonicPlots, fig.cap="Contrast response functions for pupil modualations in response to flicker at 0.5Hz (panels a-d), and 0.4Hz (panels f-i), and posterior parameter distributions for the weight of interocular suppression (panel e).
+Within each panel (except panel e), data points are the coherently averaged amplitudes for each condition, and error bars indicate bootstrapped 95\\% confidence intervals.
+Curves show model fits using the maximum a posteriori (MAP) parameter values (see Table 1).
+In panel (e), vertical lines show the MAP estimates, and the thin black curve indicates the prior (note the logarithmic x-axis).", fig.align="center", out.width="40%", echo=FALSE}
+
+knitr::include_graphics(paste0(figdir,'FirstHarmonic.pdf'))
+
+```
+
+In contemporary models of binocular signal combination, the amount of binocular facilitation is determined by the magnitude of interocular suppression, with strong suppression reducing facilitation [@Kingdom2015].
+We can estimate the strength of interocular suppression by measuring how much monocular responses are reduced when a dichoptic 'mask' is shown to the other eye.
+In our paradigm, the two components flickered at different frequencies (0.5 and 0.4Hz) so that their responses remained distinct in the Fourier spectrum [e.g.
+@Busse2009].
+The yellow diamond symbols in Figure \@ref(fig:FirstHarmonicPlots)a-d show the target responses in this condition, and in most cases were weaker than the monocular responses (red circles).
+The strongest dichoptic masking is found in the L-M condition, where we also observed the binocular suppression effect.
+Suppression can also be estimated from the responses at 0.4Hz (Figure \@ref(fig:FirstHarmonicPlots)f-i).
+The reduced amplitude in the binocular cross condition (where the two eyes received different temporal frequencies; purple squares) relative to the 0.4Hz monocular condition (grey circles), and the progressive decline in amplitude of the dichoptic cross response (yellow diamonds) also differ across photoreceptor conditions, showing similar differences to those observed at 0.5Hz.
+
+To estimate the extent of interocular suppression for each photoreceptor pathway, we fitted each data set using a Bayesian hierarchical implementation of a simple binocular combination model [@Meese2006; @Segala2023].
+Our primary objective was to compare posterior distributions of the weight of interocular suppression, which are shown in Figure \@ref(fig:FirstHarmonicPlots)e.
+Consistent with our earlier observations, the strongest suppressive weight corresponds to the L-M and Melanopsin conditions, and the weakest suppression corresponds to the light flux and S-cone conditions, with virtually no overlap between the posterior distributions for weak and strong suppression.
+The model fits were of good quality, as shown by the curves in Figure \@ref(fig:FirstHarmonicPlots)a-d,f-i.
+The fitted model parameters are given in Table \@ref(tab:paramtable).
+
+```{r paramtable, echo=FALSE}
+
+condnames <- c('Light flux 1F','L-M cone 1F','S cone 1F','Melanopsin 1F','Light flux 2F','L-M cone 2F','S cone 2F','Melanopsin 2F')
+zlist <- c(pupilZLum, pupilZLM, pupilZS, pupilZMel, pupilZLum2, pupilZLM2, pupilZS2, pupilZMel2)
+klist <- c(pupilKLum, pupilKLM, pupilKS, pupilKMel, pupilKLum2, pupilKLM2, pupilKS2, pupilKMel2)
+wlist <- c(pupilWLum, pupilWLM, pupilWS, pupilWMel, pupilWLum2, pupilWLM2, pupilWS2, pupilWMel2)
+plist <- c(pupilPLum, pupilPLM, pupilPS, pupilPMel, pupilPLum2, pupilPLM2, pupilPS2, pupilPMel2)
+qlist <- c(pupilQLum, pupilQLM, pupilQS, pupilQMel, pupilQLum2, pupilQLM2, pupilQS2, pupilQMel2)
+Rlist <- c(pupilRmaxLum, pupilRmaxLM, pupilRmaxS, pupilRmaxMel, pupilRmaxLum2, pupilRmaxLM2, pupilRmaxS2, pupilRmaxMel2)
+tabledata <- data.frame(condnames,round(zlist,digits=2),round(klist,digits=5),round(wlist,digits=2),round(plist,digits=2),round(qlist,digits=2),round(Rlist,digits=4))
+
+colnames(tabledata) <- c('Experiment','Z','k','w','p','q','Rmax')
+kable(tabledata, align='lcccccc',booktabs=TRUE,linesep='',caption = 'Summary of maximum a posteriori (MAP) parameter estimates for each data set.') %>%
+kableExtra::kable_styling(latex_options = "HOLD_position") %>% row_spec(4,hline_after=TRUE)
+
+```
+
+```{r SecondHarmonicPlots, fig.cap="Responses at the second harmonic frequencies (1Hz and 0.8Hz), in the same format as Figure 2.", fig.align="center", out.width="40%", echo=FALSE}
+
+knitr::include_graphics(paste0(figdir,'SecondHarmonic.pdf'))
+
+```
+
+At the second harmonic frequencies, the levels of suppression were more uniform across different photoreceptor pathways (see Figure \@ref(fig:SecondHarmonicPlots)).
+In general, suppression estimates were near or above 1 (see lower rows of Table \@ref(tab:paramtable)), with substantial overlap between the posterior distributions (Figure \@ref(fig:SecondHarmonicPlots)e).
+The contrast response functions also looked more uniform, and generally involved less binocular facilitation and more interocular suppression than were seen at the first harmonics.
+The L-M condition now featured the weakest suppressive weight, and the strongest binocular facilitation, which was the opposite pattern seen at the first harmonic.
+
+```{r phaseplots, fig.cap="Pupil phase plots at the first and second harmonic frequencies for the light flux, melanopsin, L-M pathway and the S-cone pathway conditions.
+Panel (a) shows the pupil response at the first harmonic frequency during binocular stimulation.
+Panel (b) shows the pupil response at the second harmonic frequency during binocular stimulation.
+The five data points for each pathway correspond to the five contrast levels displayed.
+In panel (a) the light flux amplitudes have been scaled down by a factor of 10 to enable comparison with the other conditions.", fig.align="center", echo=FALSE}
+
+knitr::include_graphics(paste0(figdir,'phaseplots.pdf'))
+
+```
+
+Finally, we inspected the response phase of our four stimulation conditions, given previous reports that these differ across pathways [@Spitschan2014], and may be in antiphase for melanopsin and S-cone signals.
+Figure \@ref(fig:phaseplots) shows the phase angles for the first (a) and second (b) harmonic frequencies for binocular stimulation (monocular stimulation produced very similar results).
+At the first harmonic, melanopsin and S-cone signals differed in phase by more than 90 degrees, though they were not fully in antiphase.
+The light flux and L-M responses were approximately in antiphase to each other, however this is likely due to our choice to modulate L+M- in the first half-cycle of the sine wave (corresponding to a luminance increase in the light flux condition), and L-M+ in the second half-cycle (corresponding to a luminance decrease in the light flux condition).
+Had we reversed this phase arrangement, we would likely have seen a close phase correspondence between the L-M and light flux conditions (another way to think about this is that L-cone decreases and M-cone increases are processed like luminance increases).
+Phase differences between the light flux, S-cone and melanopsin conditions are likely attributable to different lags in phototransduction at the earliest stage (i.e.
+in the retina).
+At the second harmonic frequency (Figure \@ref(fig:phaseplots)b), the light flux condition was again out of phase with the other three, and was approximately in quadrature phase with the L-M condition, and in antiphase with both the S-cone and melanopsin conditions (which were in phase with each other).
+We note that the marked phase differences between conditions make the possibility that our results are dominated by rod activity relatively unlikely (e.g.
+in the L-M and melanopsin conditions, which have very different phase profiles).
+
+# Discussion
+
+We used binocular pupillometry and silent substitution to measure monocular and binocular responses of the pupils to flickering stimuli when stimulating specific photoreceptor pathways.
+In all four experiments, we were able to record contrast response functions at both the first and the second harmonic frequencies.
+All experiments showed that binocular combination in the autonomic nervous system happens in a non-linear manner, with evidence of different magnitudes of interocular suppression depending on the photoreceptor pathway.
+This pattern of results was confirmed by a computational model, which allowed us to compare the weight of interocular suppression for each pathway.
+We found that at the first harmonic frequency the L-M and melanopsin pathways involved strong suppression, whereas the light flux and S-cone pathways involved weaker suppression.
+Suppression was strong in all four pathways at the second harmonic frequency.
+Finally, the phase of the pupil response revealed different lag times for the different pathways at the first and second harmonic frequencies.
+
+This is the first study to investigate binocular interactions in the melanopsin pathway directly.
+A previous meta-analysis [@Spitschan2019] indicated that there may be a substantial binocular facilitation effect in the circadian pathway, as indexed by melatonin suppression (melatonin is a hormone released by the pineal gland; its production is suppressed by exposure to bright light, particularly when the melanopsin-containing ipRGCs are stimulated).
+In brief, monocular stimulation of the ipRGCs requires up to ten times the signal strength to produce an equivalent effect to binocular stimulation.
+This superadditive effect implies an absence of interocular suppression, and perhaps the presence of either a highly compressive nonlinearity, or an AND-style neural operation.
+Our findings here are very different - we do not see substantial binocular facilitation effects in response to melanopsin modulation, and our data indicate that interocular suppression is very strong.
+Moreover, by measuring the full contrast response function, we can rule out compressive nonlinearities, because the functions accelerate at both the first and second harmonic frequencies.
+The explanation for this difference could be due to different anatomical pathways.
+Binocular combination in the circadian system likely takes place in the suprachiasmatic nucleus, whereas in the pupil constriction circuit the Edinger-Westphal nucleus is the most likely site of binocular integration [@Mathot2018].
+Presumably these anatomical differences, and the practical constraints of the two systems, lead to differences in response.
+
+Our recent psychophysical work [@Baker2024] has looked at binocular interactions in the L-M and S-cone pathways, and compared these to the light flux pathway.
+Using a contrast discrimination paradigm with spatial modulations of light flux and colour, we found equally strong interocular suppression in all three pathways [@Baker2024].
+This is rather different from our pupillometry results here, which demonstrate weaker suppression in the light flux and S-cone pathways than in the L-M pathway (see Figure \@ref(fig:FirstHarmonicPlots)).
+However, the current experiments involve temporal modulations, which are quite distinct from the spatial modulations used in our previous work [@Baker2024].
+Our other recent work [@Segala2023] has shown that temporal luminance modulations involve much weaker interocular suppression in the cortical response than do spatial luminance modulations [@Baker2017].
+These different normalization processes might reflect different priorities for spatial and temporal vision.
+Spatial vision aims to fuse images to provide binocular single vision, and benefits from 'ocularity invariance' [@Baker2007], in which visual appearance is constant when viewed with one eye or two.
+Temporal vision is critical for motion perception, which can involve alternative binocular computations, such as calculating velocity differences between the eyes [@Kaestner2019].
+Of course the present measurements were of pupil size, which may be subject to different anatomical and functional constraints from those in the cortex.
+Future research should aim to extend our current findings to perception using psychophysical approaches.
+
+# Conclusions
+
+We have demonstrated that binocular combination of temporal flickering light in the autonomic nervous system depends on the photoreceptor pathway stimulated.
+We were able to elicit pupil responses by stimulating the periphery of the retina and we were able to record contrast response functions for all photoreceptor pathways.
+While all pathways showed non-linear combination, they varied in how the signals are combined, particularly in the weight of interocular suppression.
+This was strong ($\omega \ge 1$) for L-M and melanopsin signals at the first harmonic, and all pathways at the second harmonic.
+Suppression was weaker ($\omega < 1$) in the light flux pathway (consistent with previous work), and also for S-cone directed modulations.
 
@@
 
-# Results
-
-Figure \@ref(fig:spectraplots)m-p shows averaged waveforms of pupil diameter in response to binocular stimulation.
-For light flux stimuli (Figure \@ref(fig:spectraplots)m) a strong modulation is apparent at the stimulation frequency (0.5Hz), which is also clear in the Fourier amplitude spectrum (Figure \@ref(fig:spectraplots)q).
-For binocular stimulation of the L-M pathway, S-cone pathway and melanopsin pathway, pupil modulations were less than 10\% of the amplitude of the light flux modulation (note the change in y-axis scale for the Fourier spectra), but still apparent at 0.5Hz in the Fourier spectra (Figure \@ref(fig:spectraplots)n-p).
-We also observed a second harmonic response (at 1Hz) for all conditions, which was weaker than the first harmonic for light flux and melanopsin stimulation, but stronger for L-M and S-cone stimulation.
-The second harmonic is also apparent in the pupil waveforms shown in Figure \@ref(fig:spectraplots)n-p.
-Our main analysis therefore focuses on the amplitude of the pupil modulations at both the first and second harmonic frequencies across different stimulus conditions.
-
-```{r spectraplots, fig.cap="Summary of the spectral power distributions and alpha-opic irradiances for the background and each condition, as well as averaged pupil diameters and Fourier spectra.
-Panel (a) shows a schematic of the binocular stimulation system for presenting spectrally tuned modulations independently to each eye.
-The VR headset was attached to a clamp stand that the experimenters could use to adjust the height and align the headset with the eyes of the participant.
-The participant's head was supported by a chin rest to keep it in position throughout the experiment.
-Panel (b) shows the outputs of each LED primary at maximum intensity, and panels (c) and (d) show the overall spectral power distributions and the alpha-opic irradiances of the background spectra used for both eyes.
-The subsequent rows show the power differences (e-h), and photoreceptor contrasts (i-l) relative to the background, averaged pupil diameter waveforms (m-p) and Fourier spectra (q-t) for binocular stimulation.
-Column headings indicate the pathway stimulated, and shaded regions in panels m-t indicate bootstrapped 95\\% confidence intervals.", fig.align="center", out.width = '80%', echo=FALSE}
-
-knitr::include_graphics(paste0(figdir,'methodsfigrods.pdf'))
-
-```
-
-Figure \@ref(fig:FirstHarmonicPlots)a-d shows contrast response functions across stimulation conditions for responses at the first harmonic of the main stimulation frequency (0.5Hz).
-In each plot, the response to monocular stimulation is given by the red circles and typically increases monotonically as a function of stimulus (temporal) contrast.
-Relative to monocular stimulation, binocular stimulation led to higher response amplitudes, indicating a binocular facilitation effect, for the light flux and S-cone conditions (Figure \@ref(fig:FirstHarmonicPlots)a,c), and to some extent for the melanopsin condition (Figure \@ref(fig:FirstHarmonicPlots)d).
-However, the L-M cone condition (Figure \@ref(fig:FirstHarmonicPlots)b) produced a binocular suppression effect, where the response to binocular stimulation was weaker than the response to monocular stimulation (blue squares below red circles).
-These results indicate that the magnitude of binocular facilitation differs across photoreceptor pathway, suggesting heterogeneity in the underlying neural computation.
-
-```{r FirstHarmonicPlots, fig.cap="Contrast response functions for pupil modualations in response to flicker at 0.5Hz (panels a-d), and 0.4Hz (panels f-i), and posterior parameter distributions for the weight of interocular suppression (panel e).
-Within each panel (except panel e), data points are the coherently averaged amplitudes for each condition, and error bars indicate bootstrapped 95\\% confidence intervals.
-Curves show model fits using the maximum a posteriori (MAP) parameter values (see Table 1).
-In panel (e), vertical lines show the MAP estimates, and the thin black curve indicates the prior (note the logarithmic x-axis).", fig.align="center", out.width="40%", echo=FALSE}
-
-knitr::include_graphics(paste0(figdir,'FirstHarmonic.pdf'))
-
-```
-
-In contemporary models of binocular signal combination, the amount of binocular facilitation is determined by the magnitude of interocular suppression, with strong suppression reducing facilitation [@Kingdom2015].
-We can estimate the strength of interocular suppression by measuring how much monocular responses are reduced when a dichoptic 'mask' is shown to the other eye.
-In our paradigm, the two components flickered at different frequencies (0.5 and 0.4Hz) so that their responses remained distinct in the Fourier spectrum [e.g.
-@Busse2009].
-The yellow diamond symbols in Figure \@ref(fig:FirstHarmonicPlots)a-d show the target responses in this condition, and in most cases were weaker than the monocular responses (red circles).
-The strongest dichoptic masking is found in the L-M condition, where we also observed the binocular suppression effect.
-Suppression can also be estimated from the responses at 0.4Hz (Figure \@ref(fig:FirstHarmonicPlots)f-i).
-The reduced amplitude in the binocular cross condition (where the two eyes received different temporal frequencies; purple squares) relative to the 0.4Hz monocular condition (grey circles), and the progressive decline in amplitude of the dichoptic cross response (yellow diamonds) also differ across photoreceptor conditions, showing similar differences to those observed at 0.5Hz.
-
-To estimate the extent of interocular suppression for each photoreceptor pathway, we fitted each data set using a Bayesian hierarchical implementation of a simple binocular combination model [@Meese2006; @Segala2023].
-Our primary objective was to compare posterior distributions of the weight of interocular suppression, which are shown in Figure \@ref(fig:FirstHarmonicPlots)e.
-Consistent with our earlier observations, the strongest suppressive weight corresponds to the L-M and Melanopsin conditions, and the weakest suppression corresponds to the light flux and S-cone conditions, with virtually no overlap between the posterior distributions for weak and strong suppression.
-The model fits were of good quality, as shown by the curves in Figure \@ref(fig:FirstHarmonicPlots)a-d,f-i.
-The fitted model parameters are given in Table \@ref(tab:paramtable).
-
-```{r paramtable, echo=FALSE}
-
-condnames <- c('Light flux 1F','L-M cone 1F','S cone 1F','Melanopsin 1F','Light flux 2F','L-M cone 2F','S cone 2F','Melanopsin 2F')
-zlist <- c(pupilZLum, pupilZLM, pupilZS, pupilZMel, pupilZLum2, pupilZLM2, pupilZS2, pupilZMel2)
-klist <- c(pupilKLum, pupilKLM, pupilKS, pupilKMel, pupilKLum2, pupilKLM2, pupilKS2, pupilKMel2)
-wlist <- c(pupilWLum, pupilWLM, pupilWS, pupilWMel, pupilWLum2, pupilWLM2, pupilWS2, pupilWMel2)
-plist <- c(pupilPLum, pupilPLM, pupilPS, pupilPMel, pupilPLum2, pupilPLM2, pupilPS2, pupilPMel2)
-qlist <- c(pupilQLum, pupilQLM, pupilQS, pupilQMel, pupilQLum2, pupilQLM2, pupilQS2, pupilQMel2)
-Rlist <- c(pupilRmaxLum, pupilRmaxLM, pupilRmaxS, pupilRmaxMel, pupilRmaxLum2, pupilRmaxLM2, pupilRmaxS2, pupilRmaxMel2)
-tabledata <- data.frame(condnames,round(zlist,digits=2),round(klist,digits=5),round(wlist,digits=2),round(plist,digits=2),round(qlist,digits=2),round(Rlist,digits=4))
-
-colnames(tabledata) <- c('Experiment','Z','k','w','p','q','Rmax')
-kable(tabledata, align='lcccccc',booktabs=TRUE,linesep='',caption = 'Summary of maximum a posteriori (MAP) parameter estimates for each data set.') %>%
-kableExtra::kable_styling(latex_options = "HOLD_position") %>% row_spec(4,hline_after=TRUE)
-
-```
-
-At the second harmonic frequencies, the levels of suppression were more uniform across different photoreceptor pathways (see Figure \@ref(fig:SecondHarmonicPlots)).
-In general, suppression estimates were near or above 1 (see lower rows of Table \@ref(tab:paramtable)), with substantial overlap between the posterior distributions (Figure \@ref(fig:SecondHarmonicPlots)e).
-The contrast response functions also looked more uniform, and generally involved less binocular facilitation and more interocular suppression than were seen at the first harmonics.
-The L-M condition now featured the weakest suppressive weight, and the strongest binocular facilitation, which was the opposite pattern seen at the first harmonic.
-
-```{r SecondHarmonicPlots, fig.cap="Responses at the second harmonic frequencies (1Hz and 0.8Hz), in the same format as Figure 2.", fig.align="center", out.width="40%", echo=FALSE}
-
-knitr::include_graphics(paste0(figdir,'SecondHarmonic.pdf'))
-
-```
-
-Finally, we inspected the response phase of our four stimulation conditions, given previous reports that these differ across pathways [@Spitschan2014], and may be in antiphase for melanopsin and S-cone signals.
-Figure \@ref(fig:phaseplots) shows the phase angles for the first (a) and second (b) harmonic frequencies for binocular stimulation (monocular stimulation produced very similar results).
-At the first harmonic, melanopsin and S-cone signals differed in phase by more than 90 degrees, though they were not fully in antiphase.
-The light flux and L-M responses were approximately in antiphase to each other, however this is likely due to our choice to modulate L+M- in the first half-cycle of the sine wave (corresponding to a luminance increase in the light flux condition), and L-M+ in the second half-cycle (corresponding to a luminance decrease in the light flux condition).
-Had we reversed this phase arrangement, we would likely have seen a close phase correspondence between the L-M and light flux conditions (another way to think about this is that L-cone decreases and M-cone increases are processed like luminance increases).
-Phase differences between the light flux, S-cone and melanopsin conditions are likely attributable to different lags in phototransduction at the earliest stage (i.e.
-in the retina).
-At the second harmonic frequency (Figure \@ref(fig:phaseplots)b), the light flux condition was again out of phase with the other three, and was approximately in quadrature phase with the L-M condition, and in antiphase with both the S-cone and melanopsin conditions (which were in phase with each other).
-We note that the marked phase differences between conditions make the possibility that our results are dominated by rod activity relatively unlikely (e.g.
-in the L-M and melanopsin conditions, which have very different phase profiles).
-
-```{r phaseplots, fig.cap="Pupil phase plots at the first and second harmonic frequencies for the light flux, melanopsin, L-M pathway and the S-cone pathway conditions.
-Panel (a) shows the pupil response at the first harmonic frequency during binocular stimulation.
-Panel (b) shows the pupil response at the second harmonic frequency during binocular stimulation.
-The five data points for each pathway correspond to the five contrast levels displayed.
-In panel (a) the light flux amplitudes have been scaled down by a factor of 10 to enable comparison with the other conditions.", fig.align="center", echo=FALSE}
-
-knitr::include_graphics(paste0(figdir,'phaseplots.pdf'))
-
-```
-
-# Discussion
-
-We used binocular pupillometry and silent substitution to measure monocular and binocular responses of the pupils to flickering stimuli when stimulating specific photoreceptor pathways.
-In all four experiments, we were able to record contrast response functions at both the first and the second harmonic frequencies.
-All experiments showed that binocular combination in the autonomic nervous system happens in a non-linear manner, with evidence of different magnitudes of interocular suppression depending on the photoreceptor pathway.
-This pattern of results was confirmed by a computational model, which allowed us to compare the weight of interocular suppression for each pathway.
-We found that at the first harmonic frequency the L-M and melanopsin pathways involved strong suppression, whereas the light flux and S-cone pathways involved weaker suppression.
-Suppression was strong in all four pathways at the second harmonic frequency.
-Finally, the phase of the pupil response revealed different lag times for the different pathways at the first and second harmonic frequencies.
-
-This is the first study to investigate binocular interactions in the melanopsin pathway directly.
-A previous meta-analysis [@Spitschan2019] indicated that there may be a substantial binocular facilitation effect in the circadian pathway, as indexed by melatonin suppression (melatonin is a hormone released by the pineal gland; its production is suppressed by exposure to bright light, particularly when the melanopsin-containing ipRGCs are stimulated).
-In brief, monocular stimulation of the ipRGCs requires up to ten times the signal strength to produce an equivalent effect to binocular stimulation.
-This superadditive effect implies an absence of interocular suppression, and perhaps the presence of either a highly compressive nonlinearity, or an AND-style neural operation.
-Our findings here are very different - we do not see substantial binocular facilitation effects in response to melanopsin modulation, and our data indicate that interocular suppression is very strong.
-Moreover, by measuring the full contrast response function, we can rule out compressive nonlinearities, because the functions accelerate at both the first and second harmonic frequencies.
-The explanation for this difference could be due to different anatomical pathways.
-Binocular combination in the circadian system likely takes place in the suprachiasmatic nucleus, whereas in the pupil constriction circuit the Edinger-Westphal nucleus is the most likely site of binocular integration [@Mathot2018].
-Presumably these anatomical differences, and the practical constraints of the two systems, lead to differences in response.
-
-Our recent psychophysical work [@Baker2024] has looked at binocular interactions in the L-M and S-cone pathways, and compared these to the light flux pathway.
-Using a contrast discrimination paradigm with spatial modulations of light flux and colour, we found equally strong interocular suppression in all three pathways [@Baker2024].
-This is rather different from our pupillometry results here, which demonstrate weaker suppression in the light flux and S-cone pathways than in the L-M pathway (see Figure \@ref(fig:FirstHarmonicPlots)).
-However, the current experiments involve temporal modulations, which are quite distinct from the spatial modulations used in our previous work [@Baker2024].
-Our other recent work [@Segala2023] has shown that temporal luminance modulations involve much weaker interocular suppression in the cortical response than do spatial luminance modulations [@Baker2017].
-These different normalization processes might reflect different priorities for spatial and temporal vision.
-Spatial vision aims to fuse images to provide binocular single vision, and benefits from 'ocularity invariance' [@Baker2007], in which visual appearance is constant when viewed with one eye or two.
-Temporal vision is critical for motion perception, which can involve alternative binocular computations, such as calculating velocity differences between the eyes [@Kaestner2019].
-Of course the present measurements were of pupil size, which may be subject to different anatomical and functional constraints from those in the cortex.
-Future research should aim to extend our current findings to perception using psychophysical approaches.
-
-# Conclusions
-
-We have demonstrated that binocular combination of temporal flickering light in the autonomic nervous system depends on the photoreceptor pathway stimulated.
-We were able to elicit pupil responses by stimulating the periphery of the retina and we were able to record contrast response functions for all photoreceptor pathways.
-While all pathways showed non-linear combination, they varied in how the signals are combined, particularly in the weight of interocular suppression.
-This was strong ($\omega \ge 1$) for L-M and melanopsin signals at the first harmonic, and all pathways at the second harmonic.
-Suppression was weaker ($\omega < 1$) in the light flux pathway (consistent with previous work), and also for S-cone directed modulations.
-
 # References

### 2025-10-09 manuscript.tex
Changes

--- 2025-02-28 manuscript.tex
@@
 
-Corresponding author: Federico G. Segala, \url{federico.segala@york.ac.uk}.
+*Corresponding author
+
+E-mail:\url{federico.segala@york.ac.uk} (FGS)
+
+\pagebreak
 
@@
 We investigated binocular combination by targeting different photoreceptor pathways using a novel binocular multiprimary system to modulate the input spectra via silent substitution.
-At the first harmonic of the modulation frequency, light flux and S-cone responses showed strong binocular facilitation, and weak interocular suppression.
+At the first harmonic of the modulation frequency, luminance and S-cone responses showed strong binocular facilitation, and weak interocular suppression.
 Melanopsin responses were invariant to the number of eyes stimulated.
@@
 
+\hypertarget{author-summary}{%
+\section{Author Summary}\label{author-summary}}
+
+Our pupils constantly adjust in size to control how much light enters the eye: in brighter conditions the pupils will reduce in size, and in dimmer conditions they will increase in size.
+This process, known as the pupillary light response, is usually taken for granted but is crucial for vision, and is controlled automatically by the body's nervous system.
+Different types of light-sensing cells in the retina, the photoreceptor cells, contribute to this response: some respond quickly to changes in light, while others maintain responses over longer periods.
+In our study, we explored how signals from the two eyes are combined to regulate pupil size.
+Using a new type of visual stimulation that allowed us to selectively target specific classes of photoreceptor cells, we found that the way the two eyes' signals are combined depends on which class of photoreceptor cells is involved.
+For example, some photoreceptor classes showed cooperation between the eyes, while others showed competition.
+By revealing these distinct patterns of signal combination, our work provides new insight into how light information is integrated in the pupils.
+
 \hypertarget{introduction}{%
@@
 
-The autonomic nervous system regulates many involuntary bodily processes, including the constriction and dilation of the pupils in response to light.\textsuperscript{\protect\hyperlink{ref-McDougal2015}{1}} The anatomical pathway from the retina to the subcortical nuclei controlling the pupillary light response (PLR) is well established: it includes the Pretectal Olivary nucleus (PON), the Superior Cervical ganglion and the Edinger-Westphal nucleus, which project to the iris sphincter muscles that directly control the pupil size.\textsuperscript{\protect\hyperlink{ref-McDougal2015}{1}} Evidence of a binocular component to the PLR is shown by the consensual response of the pupil (stimulation of one eye will cause constriction of the other eye).\textsuperscript{\protect\hyperlink{ref-Wyatt1981}{2}} The anatomical segregation of the subcortical pathway from the rest of the brain means that this binocular combination of signals must occur independently of the cortical processes of binocular integration required for visual perception.
-Our recent work\textsuperscript{\protect\hyperlink{ref-Segala2023}{3}} has shown that the algorithm underlying binocular combination of light in the pupil pathway differs from that in the cortex.
+The autonomic nervous system regulates many involuntary bodily processes, including the constriction and dilation of the pupils in response to light {[}\protect\hyperlink{ref-McDougal2015}{1}{]}.
+The anatomical pathway from the retina to the subcortical nuclei controlling the pupillary light response (PLR) is well established: it includes the Pretectal Olivary nucleus (PON), the Superior Cervical ganglion and the Edinger-Westphal nucleus, which project to the iris sphincter muscles that directly control the pupil size {[}\protect\hyperlink{ref-McDougal2015}{1}{]}.
+Evidence of a binocular component to the PLR is shown by the consensual response of the pupil (stimulation of one eye will cause constriction of the other eye) {[}\protect\hyperlink{ref-Wyatt1981}{2}{]}.
+The anatomical segregation of the subcortical pathway from the rest of the brain means that this binocular combination of signals must occur independently of the cortical processes of binocular integration required for visual perception.
+Our recent work {[}\protect\hyperlink{ref-Segala2023}{3}{]} has shown that the algorithm underlying binocular combination of light in the pupil pathway differs from that in the cortex.
 Here we extend this paradigm to compare binocular combination in different photoreceptor pathways that feed into the autonomic nervous system.
 
-Different classes of retinal photoreceptors, including cones, rods and melanopsin-containing intrinsically photosensitive retinal ganglion cells (ipRGCs), are directly involved in controlling and maintaining the size of the pupils.\textsuperscript{\protect\hyperlink{ref-McDougal2010}{4}--\protect\hyperlink{ref-Woelders2018}{8}} Cones drive the initial rapid constriction of the pupils,\textsuperscript{\protect\hyperlink{ref-Mathot2018}{9}} while the slower and longer activation of the ipRGCs maintains constriction over a prolonged period of time and regulates the post-illumination pupillary response.\textsuperscript{\protect\hyperlink{ref-McDougal2010}{4},\protect\hyperlink{ref-Markwell2010}{10}} The ipRGCs are a recently discovered photoreceptor class\textsuperscript{\protect\hyperlink{ref-Provencio2000}{11}} that express the photopigment melanopsin, and are involved in the regulation of the circadian rhythm,\textsuperscript{\protect\hyperlink{ref-Panda2002}{12},\protect\hyperlink{ref-Ruby2002}{13}} forming a major input to the PON.\textsuperscript{\protect\hyperlink{ref-Dacey2003}{14}} The first direct evidence of the involvement of the ipRGCs in the PLR was shown in melanopsin knockout rats,\textsuperscript{\protect\hyperlink{ref-Lucas2003}{15}} resulting in the loss of the intrinsic photosensitivity of the cells and a reduced pupil constriction.
-Similar behaviour was later observed in primates and humans\textsuperscript{\protect\hyperlink{ref-Gamlin2007}{16}} using silent substitution (see Methods), where it was demonstrated that the PLR continues during light presentation even when cone and rod signalling is blocked, indicating the primary role of the ipRGCs in maintaining pupil constriction over a prolonged time.
+Different classes of retinal photoreceptors, including cones, rods and melanopsin-containing intrinsically photosensitive retinal ganglion cells (ipRGCs), are directly involved in controlling and maintaining the size of the pupils {[}\protect\hyperlink{ref-McDougal2010}{4}--\protect\hyperlink{ref-Woelders2018}{8}{]}.
+Cones drive the initial rapid constriction of the pupils {[}\protect\hyperlink{ref-Mathot2018}{9}{]}, while the slower and longer activation of the ipRGCs maintains constriction over a prolonged period of time and regulates the post-illumination pupillary response {[}\protect\hyperlink{ref-McDougal2010}{4},\protect\hyperlink{ref-Markwell2010}{10}{]}.
+The ipRGCs are a recently discovered photoreceptor class {[}\protect\hyperlink{ref-Provencio2000}{11}{]} that express the photopigment melanopsin, and are involved in the regulation of the circadian rhythm {[}\protect\hyperlink{ref-Panda2002}{12},\protect\hyperlink{ref-Ruby2002}{13}{]}, forming a major input to the PON {[}\protect\hyperlink{ref-Dacey2003}{14}{]}.
+The first direct evidence of the involvement of the ipRGCs in the PLR was shown in melanopsin knockout rats {[}\protect\hyperlink{ref-Lucas2003}{15}{]}, resulting in the loss of the intrinsic photosensitivity of the cells and a reduced pupil constriction.
+Similar behaviour was later observed in primates and humans {[}\protect\hyperlink{ref-Gamlin2007}{16}{]} using silent substitution (see Methods), where it was demonstrated that the PLR continues during light presentation even when cone and rod signalling is blocked, indicating the primary role of the ipRGCs in maintaining pupil constriction over a prolonged time.
 
-Binocular combination has been extensively studied in visual perception, where it is mediated by neurons in primary visual cortex.\textsuperscript{\protect\hyperlink{ref-Hubel1962}{17}} For pattern vision, binocular summation occurs at threshold, such that a lower contrast is required to detect a target shown to both eyes than a target shown to one eye.\textsuperscript{\protect\hyperlink{ref-Baker2018}{18},\protect\hyperlink{ref-Campbell1965}{19}} At higher contrasts, the phenomenon of `ocularity invariance' is observed, in which the response to monocularly- and binocularly-presented patterns is equal.\textsuperscript{\protect\hyperlink{ref-Baker2007}{20},\protect\hyperlink{ref-Moradi2009}{21}} This is explained by a process of interocular suppression that cancels out the additional excitatory drive caused by stimulating two eyes.
-Our recent work\textsuperscript{\protect\hyperlink{ref-Segala2023}{3}} showed that cortical signal combination for luminance flicker is substantially more linear than for spatial patterns, whereas there is evidence of interocular suppression in the pupil pathway.
+Binocular combination has been extensively studied in visual perception, where it is mediated by neurons in primary visual cortex {[}\protect\hyperlink{ref-Hubel1962}{17}{]}.
+For pattern vision, binocular summation occurs at threshold, such that a lower contrast is required to detect a target shown to both eyes than a target shown to one eye {[}\protect\hyperlink{ref-Baker2018}{18},\protect\hyperlink{ref-Campbell1965}{19}{]}.
+At higher contrasts, the phenomenon of `ocularity invariance' is observed, in which the response to monocularly- and binocularly-presented patterns is equal {[}\protect\hyperlink{ref-Baker2007}{20},\protect\hyperlink{ref-Moradi2009}{21}{]}.
+This is explained by a process of interocular suppression that cancels out the additional excitatory drive caused by stimulating two eyes.
+Our recent work {[}\protect\hyperlink{ref-Segala2023}{3}{]} showed that cortical signal combination for luminance flicker is substantially more linear than for spatial patterns, whereas there is evidence of interocular suppression in the pupil pathway.
 Here we measure the amplitude of pupil modulations in response to flickering stimuli presented as light flux, or directed towards the L-M cone, S-cone, and melanopsin pathways (see Figure \ref{fig:spectraplots}e-l).
 Our key comparisons are between monocular and binocular stimulation, and in a dichoptic masking condition where the two eyes are stimulated at different frequencies.
-The results are interpreted using a contemporary model of binocular vision\textsuperscript{\protect\hyperlink{ref-Meese2006}{22}} implemented within a hierarchical Bayesian framework.
-
-\hypertarget{materials-and-methods}{%
-\section{Materials and methods}\label{materials-and-methods}}
-
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
-
-Twenty-four participants were recruited for each of the four experiments for a total of ninety-six adult participants (28 male, 68 female), whose ages ranged from 18 to 41.
-All participants had normal or corrected to normal vision, no known abnormalities of binocular or colour vision, and gave written informed consent.
-Our procedures were approved by the Ethics Committee of the Department of Psychology at the University of York (identification number 184).
-
-\hypertarget{apparatus-stimuli}{%
-\subsection{Apparatus \& stimuli}\label{apparatus-stimuli}}
-
-To present synchronised stimulus modulations independently to each eye, two light engines (SpectraTuneLAB, which are thermally stable across time with active cooling according to the manufacturers: LEDMOTIVE Technologies, LLC, Barcelona, Spain), each with 10 independently addressable LED colour channels, were integrated into a customised binocular viewing system.
-The light engines were operated via a Python interface to their REST API,\textsuperscript{\protect\hyperlink{ref-Martin2022}{23}} which supports synchronous launch and playback of spectral sequences prepared in advance and stored in JSON format.
-A special command was commissioned from LEDMOTIVE to allow two different stimulus files to be launched simultaneously from the two devices.
-The synchronisation of the spectra from the two devices was tested and showed that they were synchronised to within approximately 3ms.
-
-When preparing the spectral sequences, the age of participants was used to account for the yellowing of the lenses.
-We used the silent substitution technique\textsuperscript{\protect\hyperlink{ref-Estevez1982}{24}} to selectively stimulate specific photoreceptor classes.
-Silent substitution exploits the fact that each photoreceptor class has a distinct spectral tuning that overlaps with the others.
-Using a multiprimary system, in which the primaries (i.e.~LEDs) have different spectra, it is possible to target one class of photoreceptors while maintaining the others at a constant activity level, effectively silencing them.\textsuperscript{\protect\hyperlink{ref-Shapiro1996}{25},\protect\hyperlink{ref-Spitschan2018}{26}} We calculated silent substitution solutions using the \emph{PySilSub} toolbox,\textsuperscript{\protect\hyperlink{ref-Martin2023}{27}} using linear algebra.
-The outputs of the two light engines (see Figure \ref{fig:spectraplots}b,c) were calibrated using an Ocean Optics Jaz spectroradiometer, which was wavelength-calibrated to an Argon lamp and intensity calibrated using a NIST-traceable light source.
-Each primary was also linearized using a polynomial fit (see Figure \ref{fig:primarylinearity} for details).
-We used the 10-degree cone fundamentals,\textsuperscript{\protect\hyperlink{ref-Stockman2000}{28}} and estimates of melanopsin absorbance spectra from CIE S 026 (discussed in a previous paper\textsuperscript{\protect\hyperlink{ref-Martin2023}{27}}) to calculate \(\alpha\)-opic irradiance.
-
-The output from the light engines was directed through liquid light guides (LLG3-8H: Thorlabs Ltd, Cambridgeshire, UK) and diffused onto semi-opaque and highly diffusive white glass discs with a diameter of 50 mm for even illumination (34-473: Edmund Optics, York, UK).
-The light guide gaskets were butt-coupled to the light engine diffusers with threaded adapters (SM1A9, AD3LLG: Thorlabs Ltd, Cambridgeshire, UK) and the exiting ends of the light guides were mated with 51 mm depth optical cylinders (SM2L20: Thorlabs Ltd, Cambridgeshire, UK) via appropriately threaded adapters (AD3LLG, SM2A6: Thorlabs Ltd, Cambridgeshire, UK).
-The stimulus diffuser discs were retained at the front end of the optical cylinders approximately 51 mm from the light source, at which distance the output beam was sufficiently dispersed to afford even illumination of the diffuser when viewed from the front.
-To guarantee safe illumination levels, a circular neutral-density filter with the same diameter of the white glass discs (50 mm) and an optical density of 0.6 log units was placed in the optical path between the light source and the diffusers.
-A small circular piece of blackout material with a diameter of approximately 8 degrees (10 mm) was positioned centrally on the front of each diffuser disc to aid as a fusion lock, as a fixation point, and to occlude the fovea.
-
-The diffuser discs were positioned in the objective planes of the lenses of a modified VR headset (SHINECON SC-G01, Dongguan Shinecon Industrial Co.~Ltd., Guangdong, China), which was used by the participants to view the stimuli.
-The stimuli were two discs of flickering light with a diameter of approximately 30 degrees, which were fused together into a cyclopean percept resembling a donut-shaped ring of light, similar to that used in other studies.\textsuperscript{\protect\hyperlink{ref-Barrionuevo2016}{5}--\protect\hyperlink{ref-Spitschan2014}{7},\protect\hyperlink{ref-Spitschan2015}{29},\protect\hyperlink{ref-Zele2018}{30}} The VR headset modifications allowed for small adjustments to account for individual differences in interpupillary distance and focal length.
-The use of this set up allowed us to modulate the stimuli in three different ocular configurations, similar to the ones we used in our previous study:\textsuperscript{\protect\hyperlink{ref-Segala2023}{3}} monocular, binocular and dichoptic.
-In the monocular configuration, the unstimulated eye still saw a non-flickering disc of mean light flux.
-A schematic of the stimulation system is shown in Figure \ref{fig:spectraplots}a.
-Pupillometry data were collected using a binocular Pupil Core eye-tracker headset (Pupil Labs GmbH, Berlin, Germany\textsuperscript{\protect\hyperlink{ref-Kassner2014}{31}}) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
-
-Our previous study\textsuperscript{\protect\hyperlink{ref-Segala2023}{3}} used a temporal frequency of 2Hz for foveal luminance flicker, and recorded EEG data simultaneously with pupillometry.
-Initial pilot experiments indicated that this frequency was too high to elicit measurable responses when stimulating individual photoreceptor pathways.
-For all experiments, we therefore used a primary flicker frequency of 0.5Hz, as previous literature showed that this was slow enough to elicit a pupil response from all photoreceptor classes.\textsuperscript{\protect\hyperlink{ref-Spitschan2014}{7}} We also focussed on only recording pupillometry data as this frequency would be too slow to elicit steady-state EEG responses.\textsuperscript{\protect\hyperlink{ref-Norcia2015}{32}}
-
-For all experiments, sinusoidal temporal modulations were presented against the same background spectrum (matched between the eyes), which was used to achieve silent substitution in the three photoreceptor modulation experiments.
-The background spectra were defined by setting all channels to half maximum output for the brighter of the two devices (STLab 1, left eye) and then using the STLab 1/STLab 2 calibration ratio to find the equivalent settings for the companion device (STLab 2, right eye).
-The background spectrum illuminance was approximately 74 lux, or 68.5 cd/m\(^2\).
-The spectral power distributions and \(\alpha\)-opic irradiances of the background spectra for both eyes are shown in Figure \ref{fig:spectraplots}c-d.
-
-Silent substitution stimuli were prepared and calibrated for each participant with custom Python software\textsuperscript{\protect\hyperlink{ref-Martin2023}{27}} and Python scripts.
-Estimates of photoreceptor spectral sensitivities for each participant were constructed from the known photopigment absorbance spectra,\textsuperscript{\protect\hyperlink{ref-Stockman2000}{28}} taking account of the peak axial density of the respective photopigments, as well as lens\textsuperscript{\protect\hyperlink{ref-Stockman2000}{28},\protect\hyperlink{ref-Pokorny1987}{33},\protect\hyperlink{ref-Stockman1999}{34}} and macular pigment density,\textsuperscript{\protect\hyperlink{ref-Stockman1999}{34},\protect\hyperlink{ref-Bone1988}{35}} in accordance with the field size and age-dependant CIEPO06 observer model.\textsuperscript{\protect\hyperlink{ref-CIE2006}{36}} The melanopic and rhodopic action spectra of the 32-year-old standard observer were taken from CIE S 026\textsuperscript{\protect\hyperlink{ref-CIE2018}{37}} and then adjusted for age-related lens transmittance with a spectral correction function, in line with the standard.
-Macular pigment correction was not applied to the rhodopic and melanopic action spectra because rods are not present at the fovea and ipRGCs sit above the retinal pigment layer.\textsuperscript{\protect\hyperlink{ref-Trieschmann2007}{38}}
-
-In the light flux experiment, the stimulus intensity was increased and decreased relative to the background, which we expected to modulate all photoreceptor classes (see Figure \ref{fig:spectraplots}e,i).
-In the L-M cone modulation experiment, we used silent substitution to increase the L-cone activity, and simultaneously decrease the M-cone activity, during the first half-cycle of the sine wave.
-In the second half-cycle the polarity of the modulation reversed (see Figure \ref{fig:spectraplots}f,j).
-The maximum available L-M contrast was approximately 10\%.
-In the S-cone modulation experiment, we increased and decreased S-cone-directed signals, whilst keeping activity in the other photoreceptors constant (see Figure \ref{fig:spectraplots}g,k).
-Our system allowed a maximum contrast of 45\%.
-Finally, in the melanopsin experiment, we modulated the activity of the melanopsin-containing intrinsically photoreceptive retinal ganglion cells, whilst keeping cone activity constant (see Figure \ref{fig:spectraplots}h,l).
-The maximum available melanopsin contrast was 22\%.
-We assume that the activity of rods was constant at the high background luminance intensity used here, and so did not attempt to silence rod activity in any condition, as this would have greatly reduced the available dynamic range.
-Splatter on nominally silenced photoreceptors was very small (see Figure \ref{fig:spectraplots}j-l), well below the levels that would be expected to generate measurable pupil modulations, although we can observe that the rods may not be saturated in the L-M and melanopsin-directed stimuli (Figure \ref{fig:spectraplots}j and \ref{fig:spectraplots}l) and could intrude in these two experiments.
-We also estimated activation of penumbral L and M cones,\textsuperscript{\protect\hyperlink{ref-Barrionuevo2016}{5},\protect\hyperlink{ref-Spitschan2015}{29},\protect\hyperlink{ref-Zele2019}{39}} which was minimal (\(\le 1.5%
-\) contrast; less than splatter on the open-field cones) for melanopsin-directed stimuli.
-We note that the temporal frequency of our modulation (0.5Hz) is well below the range where penumbral cone activation can elicit visible percepts, and that such percepts fade after around 1 second,\textsuperscript{\protect\hyperlink{ref-Spitschan2015}{29}} and do not typically affect pupil responses.\textsuperscript{\protect\hyperlink{ref-Spitschan2014}{7}}
-
-\hypertarget{procedure}{%
-\subsection{Procedure}\label{procedure}}
-
-Before the start of each experiment, participants adjusted the objective planes of the lenses with the help of the experimenter until the stimulus was in focus and they perceived the two pieces of blackout material as one fused disc.
-Pupil responses to binocular temporal contrast modulations were examined in a factorial design that combined six ocular conditions and five temporal contrast levels: 6, 12, 24, 48 and 96\% of the available dynamic range.
-This design, similar to that used in our previous studies,\textsuperscript{\protect\hyperlink{ref-Segala2023}{3},\protect\hyperlink{ref-Baker2017}{40},\protect\hyperlink{ref-Baker2020}{41}} was applied in four separate experiments, each with a different mode of photoreceptor stimulation.
-In the first three conditions, the discs flickered at 0.5 Hz, in either a monocular, binocular or dichoptic arrangement.
-In the dichoptic condition the non-target eye saw a flickering fixed contrast of 48\% of the available dynamic range.
-In the remaining three conditions (the cross-frequency conditions) one eye's disc flickered at 0.4 Hz, and the other eye's disc flickered at 0.5 Hz.
-This included monocular responses at 0.4 Hz, as well as binocular (one eye sees each frequency at the target contrast) and dichoptic (target stimulus flickering at 0.5 Hz, mask contrast of 48\% at 0.4 Hz in the other eye) arrangements.
-We counterbalanced presentation of the target stimulus across the left and right eyes.
-
-The experiments were conducted in a windowless room, in which the only source of light was the modified VR headset.
-The participants sat as close as possible to the VR headset, leaving enough space for the eye-tracker to record the eyes.
-Each experiment was carried out in a single session of around 45-60 minutes, divided into three blocks of 15-17 minutes each.
-In each block, there were a total of 60 trials lasting 15 seconds each (12s of stimulus presentation, followed by 3s of interstimulus interval).
-The participants were given no task other than look at the black fixation dot while trying to minimise their blinking during the presentation period.
-For all experiments other than the light flux condition, participants adapted to the unmodulated background luminance for two minutes before stimulation began.
-
-Before the start of the L-M experiment, participants completed a luminance nulling perceptual calibration procedure in L-M cone space on an Iiyama \(\textrm{VisionMaster}^{\textrm{TM}}\) Pro 510 display (800 x 600 pixels, 60 Hz refresh rate).
-During the task, participants were presented with a disc flickering within the L-M cone space (between magenta and cyan).
-Using a trackball, participants adjusted the angle in cone space to find their subjective isoluminant point, which resulted in changing the flickering intensity of the stimulus until the amplitude of the flicker appeared to be minimised.
-The result was used to modify the requested contrasts during stimulus preparation so as to account for individual differences affecting perceived illuminance, principally the L:M cone ratio.\textsuperscript{\protect\hyperlink{ref-Carroll2002}{42},\protect\hyperlink{ref-Hofer2005}{43}}
-
-\hypertarget{data-analysis}{%
-\subsection{Data analysis}\label{data-analysis}}
-
-The pupillometry data were analysed using the same method we used in our previous study.\textsuperscript{\protect\hyperlink{ref-Segala2023}{3}} The data were converted from mp4 videos to a csv text file using the Pupil Player software,\textsuperscript{\protect\hyperlink{ref-Kassner2014}{31}} which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
-The individual data were then loaded into R for analysis, where a ten-second waveform for each trial in each eye was extracted (excluding the first two seconds after stimulus onset).
-We interpolated across any dropped or missing frames to ensure regular and continuous sampling over time.
-The Fourier transform was calculated for each waveform, and all repetitions of each condition were pooled across eye and then averaged.
-Finally, data were averaged across all participants to obtain the group results.
-We used coherent averaging and at each stage we excluded data points with a Mahalanobis distance exceeding \(D\) = 3 from the complex-valued mean.\textsuperscript{\protect\hyperlink{ref-Baker2021}{44}} For monocular stimulation, we confirmed that the consensual response was equivalent to the response in the stimulated eye.
-
-For all experiments, we used a bootstrapping procedure with \ensuremath{10^{4}} iterations to estimate standard errors across participants.
-All analysis and figure construction was conducted using a single R-script, available online, making this study fully computationally reproducible: \url{https://osf.io/gdvt4/}.
-
-\hypertarget{computational-model-and-parameter-estimation}{%
-\subsection{Computational model and parameter estimation}\label{computational-model-and-parameter-estimation}}
-
-To quantitatively summarise our data, we used the same model described in our previous study.\textsuperscript{\protect\hyperlink{ref-Segala2023}{3}} The model has the same general form as the first stage of the contrast gain control model proposed by Meese and colleagues,\textsuperscript{\protect\hyperlink{ref-Meese2006}{22}} but omits the second stage.
-For the previous model that we used,\textsuperscript{\protect\hyperlink{ref-Segala2023}{3}} the exponent of the numerator and denominator had fixed values of 2 and (implicitly) 1.
-Here, we allow these parameters (called \emph{p} and \emph{q}) to be free, in order to permit different shapes of contrast response function, e.g.~accelerating or saturating.
-The responses of the left eye and right eye channels are as follows:
-
-\begin{equation}
-\label{eq:respL}
-resp_L = \frac{L^p}{Z + L^q + \omega R^q},
-\end{equation}
-
-\begin{equation}
-\label{eq:respR}
-resp_R = \frac{R^p}{Z + R^q + \omega L^q},
-\end{equation}
-
-\noindent where \emph{L} and \emph{R} are the contrast signals from the left and right eyes, \emph{p} and \emph{q} are exponents, \emph{Z} is a saturation constant that shifts the contrast-response function laterally, and \(\omega\) is the weight of suppression from the other eye.
-
-The responses from the two eyes are then summed binocularly:
-
-\begin{equation}
-\label{eq:respB}
-resp_B = R_{max}(resp_L + resp_R) + k,
-\end{equation}
-
-\noindent where \emph{k} is a noise parameter, and \(R_{max}\) scales the overall response amplitude.
-
-The models were fit using a hierarchical Bayesian framework implemented in Stan.\textsuperscript{\protect\hyperlink{ref-Carpenter2017}{45}} The data for each photoreceptor type and response frequency was fit separately, for a total of 8 model fits.
-The prior for the \(\omega\) parameter was Gaussian, with a mean of 1 and standard deviation of 0.5.
-Priors for the other free parameters were also Gaussian, with mean values based on previous work.\textsuperscript{\protect\hyperlink{ref-Segala2023}{3}} We calculated over \ensuremath{10^{6}} posterior samples, and retained 10\% for plotting.
+The results are interpreted using a contemporary model of binocular vision {[}\protect\hyperlink{ref-Meese2006}{22}{]} implemented within a hierarchical Bayesian framework.
 
@@
 
-In contemporary models of binocular signal combination, the amount of binocular facilitation is determined by the magnitude of interocular suppression, with strong suppression reducing facilitation.\textsuperscript{\protect\hyperlink{ref-Kingdom2015}{46}} We can estimate the strength of interocular suppression by measuring how much monocular responses are reduced when a dichoptic `mask' is shown to the other eye.
-In our paradigm, the two components flickered at different frequencies (0.5 and 0.4Hz) so that their responses remained distinct in the Fourier spectrum.\textsuperscript{\protect\hyperlink{ref-Busse2009}{47}} The yellow diamond symbols in Figure \ref{fig:FirstHarmonicPlots}a-d show the target responses in this condition, and in most cases were weaker than the monocular responses (red circles).
+In contemporary models of binocular signal combination, the amount of binocular facilitation is determined by the magnitude of interocular suppression, with strong suppression reducing facilitation {[}\protect\hyperlink{ref-Kingdom2015}{23}{]}.
+We can estimate the strength of interocular suppression by measuring how much monocular responses are reduced when a dichoptic `mask' is shown to the other eye.
+In our paradigm, the two components flickered at different frequencies (0.5 and 0.4Hz) so that their responses remained distinct in the Fourier spectrum {[}\protect\hyperlink{ref-Busse2009}{24}{]}.
+The yellow diamond symbols in Figure \ref{fig:FirstHarmonicPlots}a-d show the target responses in this condition, and in most cases were weaker than the monocular responses (red circles).
 The strongest dichoptic masking is found in the L-M condition, where we also observed the binocular suppression effect.
@@
 
-To estimate the extent of interocular suppression for each photoreceptor pathway, we fitted each data set using a Bayesian hierarchical implementation of a simple binocular combination model.\textsuperscript{\protect\hyperlink{ref-Segala2023}{3},\protect\hyperlink{ref-Meese2006}{22}} Our primary objective was to compare posterior distributions of the weight of interocular suppression, which are shown in Figure \ref{fig:FirstHarmonicPlots}e.
+To estimate the extent of interocular suppression for each photoreceptor pathway, we fitted each data set using a Bayesian hierarchical implementation of a simple binocular combination model {[}\protect\hyperlink{ref-Segala2023}{3},\protect\hyperlink{ref-Meese2006}{22}{]}.
+Our primary objective was to compare posterior distributions of the weight of interocular suppression, which are shown in Figure \ref{fig:FirstHarmonicPlots}e.
 Consistent with our earlier observations, the strongest suppressive weight corresponds to the L-M and Melanopsin conditions, and the weakest suppression corresponds to the light flux and S-cone conditions, with virtually no overlap between the posterior distributions for weak and strong suppression.
@@
 
-At the second harmonic frequencies, the levels of suppression were more uniform across different photoreceptor pathways (see Figure \ref{fig:SecondHarmonicPlots}).
-In general, suppression estimates were near or above 1 (see lower rows of Table \ref{tab:paramtable}), with substantial overlap between the posterior distributions (Figure \ref{fig:SecondHarmonicPlots}e).
-The contrast response functions also looked more uniform, and generally involved less binocular facilitation and more interocular suppression than were seen at the first harmonics.
-The L-M condition now featured the weakest suppressive weight, and the strongest binocular facilitation, which was the opposite pattern seen at the first harmonic.
-
 \begin{figure}
@@
 
-Finally, we inspected the response phase of our four stimulation conditions, given previous reports that these differ across pathways,\textsuperscript{\protect\hyperlink{ref-Spitschan2014}{7}} and may be in antiphase for melanopsin and S-cone signals.
-Figure \ref{fig:phaseplots} shows the phase angles for the first (a) and second (b) harmonic frequencies for binocular stimulation (monocular stimulation produced very similar results).
-At the first harmonic, melanopsin and S-cone signals differed in phase by more than 90 degrees, though they were not fully in antiphase.
-The light flux and L-M responses were approximately in antiphase to each other, however this is likely due to our choice to modulate L+M- in the first half-cycle of the sine wave (corresponding to a luminance increase in the light flux condition), and L-M+ in the second half-cycle (corresponding to a luminance decrease in the light flux condition).
-Had we reversed this phase arrangement, we would likely have seen a close phase correspondence between the L-M and light flux conditions (another way to think about this is that L-cone decreases and M-cone increases are processed like luminance increases).
-Phase differences between the light flux, S-cone and melanopsin conditions are likely attributable to different lags in phototransduction at the earliest stage (i.e.~in the retina).
-At the second harmonic frequency (Figure \ref{fig:phaseplots}b), the light flux condition was again out of phase with the other three, and was approximately in quadrature phase with the L-M condition, and in antiphase with both the S-cone and melanopsin conditions (which were in phase with each other).
-We note that the marked phase differences between conditions make the possibility that our results are dominated by rod activity relatively unlikely (e.g.~in the L-M and melanopsin conditions, which have very different phase profiles).
+At the second harmonic frequencies, the levels of suppression were more uniform across different photoreceptor pathways (see Figure \ref{fig:SecondHarmonicPlots}).
+In general, suppression estimates were near or above 1 (see lower rows of Table \ref{tab:paramtable}), with substantial overlap between the posterior distributions (Figure \ref{fig:SecondHarmonicPlots}e).
+The contrast response functions also looked more uniform, and generally involved less binocular facilitation and more interocular suppression than were seen at the first harmonics.
+The L-M condition now featured the weakest suppressive weight, and the strongest binocular facilitation, which was the opposite pattern seen at the first harmonic.
 
@@
 
+Finally, we inspected the response phase of our four stimulation conditions, given previous reports that these differ across pathways {[}\protect\hyperlink{ref-Spitschan2014}{7}{]}, and may be in antiphase for melanopsin and S-cone signals.
+Figure \ref{fig:phaseplots} shows the phase angles for the first (a) and second (b) harmonic frequencies for binocular stimulation (monocular stimulation produced very similar results).
+At the first harmonic, melanopsin and S-cone signals differed in phase by more than 90 degrees, though they were not fully in antiphase.
+The light flux and L-M responses were approximately in antiphase to each other, however this is likely due to our choice to modulate L+M- in the first half-cycle of the sine wave (corresponding to a luminance increase in the light flux condition), and L-M+ in the second half-cycle (corresponding to a luminance decrease in the light flux condition).
+Had we reversed this phase arrangement, we would likely have seen a close phase correspondence between the L-M and light flux conditions (another way to think about this is that L-cone decreases and M-cone increases are processed like luminance increases).
+Phase differences between the light flux, S-cone and melanopsin conditions are likely attributable to different lags in phototransduction at the earliest stage (i.e.~in the retina).
+At the second harmonic frequency (Figure \ref{fig:phaseplots}b), the light flux condition was again out of phase with the other three, and was approximately in quadrature phase with the L-M condition, and in antiphase with both the S-cone and melanopsin conditions (which were in phase with each other).
+We note that the marked phase differences between conditions make the possibility that our results are dominated by rod activity relatively unlikely (e.g.~in the L-M and melanopsin conditions, which have very different phase profiles).
+
 \hypertarget{discussion}{%
@@
 This is the first study to investigate binocular interactions in the melanopsin pathway directly.
-A previous meta-analysis\textsuperscript{\protect\hyperlink{ref-Spitschan2019}{48}} indicated that there may be a substantial binocular facilitation effect in the circadian pathway, as indexed by melatonin suppression (melatonin is a hormone released by the pineal gland; its production is suppressed by exposure to bright light, particularly when the melanopsin-containing ipRGCs are stimulated).
+A previous meta-analysis {[}\protect\hyperlink{ref-Spitschan2019}{25}{]} indicated that there may be a substantial binocular facilitation effect in the circadian pathway, as indexed by melatonin suppression (melatonin is a hormone released by the pineal gland; its production is suppressed by exposure to bright light, particularly when the melanopsin-containing ipRGCs are stimulated).
 In brief, monocular stimulation of the ipRGCs requires up to ten times the signal strength to produce an equivalent effect to binocular stimulation.
@@
 The explanation for this difference could be due to different anatomical pathways.
-Binocular combination in the circadian system likely takes place in the suprachiasmatic nucleus, whereas in the pupil constriction circuit the Edinger-Westphal nucleus is the most likely site of binocular integration.\textsuperscript{\protect\hyperlink{ref-Mathot2018}{9}} Presumably these anatomical differences, and the practical constraints of the two systems, lead to differences in response.
+Binocular combination in the circadian system likely takes place in the suprachiasmatic nucleus, whereas in the pupil constriction circuit the Edinger-Westphal nucleus is the most likely site of binocular integration {[}\protect\hyperlink{ref-Mathot2018}{9}{]}.
+Presumably these anatomical differences, and the practical constraints of the two systems, lead to differences in response.
 
-Our recent psychophysical work\textsuperscript{\protect\hyperlink{ref-Baker2024}{49}} has looked at binocular interactions in the L-M and S-cone pathways, and compared these to the light flux pathway.
-Using a contrast discrimination paradigm with spatial modulations of light flux and colour, we found equally strong interocular suppression in all three pathways.\textsuperscript{\protect\hyperlink{ref-Baker2024}{49}} This is rather different from our pupillometry results here, which demonstrate weaker suppression in the light flux and S-cone pathways than in the L-M pathway (see Figure \ref{fig:FirstHarmonicPlots}).
-However, the current experiments involve temporal modulations, which are quite distinct from the spatial modulations used in our previous work.\textsuperscript{\protect\hyperlink{ref-Baker2024}{49}} Our other recent work\textsuperscript{\protect\hyperlink{ref-Segala2023}{3}} has shown that temporal luminance modulations involve much weaker interocular suppression in the cortical response than do spatial luminance modulations.\textsuperscript{\protect\hyperlink{ref-Baker2017}{40}} These different normalization processes might reflect different priorities for spatial and temporal vision.
-Spatial vision aims to fuse images to provide binocular single vision, and benefits from `ocularity invariance,'\textsuperscript{\protect\hyperlink{ref-Baker2007}{20}} in which visual appearance is constant when viewed with one eye or two.
-Temporal vision is critical for motion perception, which can involve alternative binocular computations, such as calculating velocity differences between the eyes.\textsuperscript{\protect\hyperlink{ref-Kaestner2019}{50}} Of course the present measurements were of pupil size, which may be subject to different anatomical and functional constraints from those in the cortex.
+Our recent psychophysical work {[}\protect\hyperlink{ref-Baker2024}{26}{]} has looked at binocular interactions in the L-M and S-cone pathways, and compared these to the light flux pathway.
+Using a contrast discrimination paradigm with spatial modulations of light flux and colour, we found equally strong interocular suppression in all three pathways {[}\protect\hyperlink{ref-Baker2024}{26}{]}.
+This is rather different from our pupillometry results here, which demonstrate weaker suppression in the light flux and S-cone pathways than in the L-M pathway (see Figure \ref{fig:FirstHarmonicPlots}).
+However, the current experiments involve temporal modulations, which are quite distinct from the spatial modulations used in our previous work {[}\protect\hyperlink{ref-Baker2024}{26}{]}.
+Our other recent work {[}\protect\hyperlink{ref-Segala2023}{3}{]} has shown that temporal luminance modulations involve much weaker interocular suppression in the cortical response than do spatial luminance modulations {[}\protect\hyperlink{ref-Baker2017}{27}{]}.
+These different normalization processes might reflect different priorities for spatial and temporal vision.
+Spatial vision aims to fuse images to provide binocular single vision, and benefits from `ocularity invariance' {[}\protect\hyperlink{ref-Baker2007}{20}{]}, in which visual appearance is constant when viewed with one eye or two.
+Temporal vision is critical for motion perception, which can involve alternative binocular computations, such as calculating velocity differences between the eyes {[}\protect\hyperlink{ref-Kaestner2019}{28}{]}.
+Of course the present measurements were of pupil size, which may be subject to different anatomical and functional constraints from those in the cortex.
 Future research should aim to extend our current findings to perception using psychophysical approaches.
@@
 
+\hypertarget{materials-and-methods}{%
+\section{Materials and methods}\label{materials-and-methods}}
+
+\hypertarget{participants}{%
+\subsection{Participants}\label{participants}}
+
+Twenty-four participants were recruited for each of the four experiments for a total of ninety-six adult participants (28 male, 68 female), whose ages ranged from 18 to 41.
+All participants had normal or corrected to normal vision, no known abnormalities of binocular or colour vision, and gave written informed consent.
+Our procedures were approved by the Ethics Committee of the Department of Psychology at the University of York (identification number 184).
+
+\hypertarget{apparatus-stimuli}{%
+\subsection{Apparatus \& stimuli}\label{apparatus-stimuli}}
+
+To present synchronised stimulus modulations independently to each eye, two light engines (SpectraTuneLAB, which are thermally stable across time with active cooling according to the manufacturers: LEDMOTIVE Technologies, LLC, Barcelona, Spain), each with 10 independently addressable LED colour channels, were integrated into a customised binocular viewing system.
+The light engines were operated via a Python interface to their REST API {[}\protect\hyperlink{ref-Martin2022}{29}{]}, which supports synchronous launch and playback of spectral sequences prepared in advance and stored in JSON format.
+A special command was commissioned from LEDMOTIVE to allow two different stimulus files to be launched simultaneously from the two devices.
+The synchronisation of the spectra from the two devices was tested and showed that they were synchronised to within approximately 3ms.
+
+When preparing the spectral sequences, the age of participants was used to account for the yellowing of the lenses.
+We used the silent substitution technique {[}\protect\hyperlink{ref-Estevez1982}{30}{]} to selectively stimulate specific photoreceptor classes.
+Silent substitution exploits the fact that each photoreceptor class has a distinct spectral tuning that overlaps with the others.
+Using a multiprimary system, in which the primaries (i.e.~LEDs) have different spectra, it is possible to target one class of photoreceptors while maintaining the others at a constant activity level, effectively silencing them {[}\protect\hyperlink{ref-Shapiro1996}{31},\protect\hyperlink{ref-Spitschan2018}{32}{]}.
+We calculated silent substitution solutions using the \emph{PySilSub} toolbox {[}\protect\hyperlink{ref-Martin2023}{33}{]}, using linear algebra.
+The outputs of the two light engines (see Figure \ref{fig:spectraplots}b,c) were calibrated using an Ocean Optics Jaz spectroradiometer, which was wavelength-calibrated to an Argon lamp and intensity calibrated using a NIST-traceable light source.
+Each primary was also linearised using a polynomial fit (see Figure \ref{fig:primarylinearity} for details).
+We used the 10-degree cone fundamentals {[}\protect\hyperlink{ref-Stockman2000}{34}{]}, and estimates of melanopsin absorbance spectra from CIE S 026 (discussed in a previous paper {[}\protect\hyperlink{ref-Martin2023}{33}{]}) to calculate \(\alpha\)-opic irradiance.
+
+The output from the light engines was directed through liquid light guides (LLG3-8H: Thorlabs Ltd, Cambridgeshire, UK) and diffused onto semi-opaque and highly diffusive white glass discs with a diameter of 50 mm for even illumination (34-473: Edmund Optics, York, UK).
+The light guide gaskets were butt-coupled to the light engine diffusers with threaded adapters (SM1A9, AD3LLG: Thorlabs Ltd, Cambridgeshire, UK) and the exiting ends of the light guides were mated with 51 mm depth optical cylinders (SM2L20: Thorlabs Ltd, Cambridgeshire, UK) via appropriately threaded adapters (AD3LLG, SM2A6: Thorlabs Ltd, Cambridgeshire, UK).
+The stimulus diffuser discs were retained at the front end of the optical cylinders approximately 51 mm from the light source, at which distance the output beam was sufficiently dispersed to afford even illumination of the diffuser when viewed from the front.
+To guarantee safe illumination levels, a circular neutral-density filter with the same diameter of the white glass discs (50 mm) and an optical density of 0.6 log units was placed in the optical path between the light source and the diffusers.
+A small circular piece of blackout material with a diameter of approximately 8 degrees (10 mm) was positioned centrally on the front of each diffuser disc to aid as a fusion lock, as a fixation point, and to occlude the fovea.
+
+The diffuser discs were positioned in the objective planes of the lenses of a modified VR headset (SHINECON SC-G01, Dongguan Shinecon Industrial Co.~Ltd., Guangdong, China), which was used by the participants to view the stimuli.
+The stimuli were two discs of flickering light with a diameter of approximately 30 degrees, which were fused together into a cyclopean percept resembling a donut-shaped ring of light, similar to that used in other studies {[}\protect\hyperlink{ref-Barrionuevo2016}{5}--\protect\hyperlink{ref-Spitschan2014}{7},\protect\hyperlink{ref-Spitschan2015}{35},\protect\hyperlink{ref-Zele2018}{36}{]}.
+The VR headset modifications allowed for small adjustments to account for individual differences in interpupillary distance and focal length.
+The use of this set up allowed us to modulate the stimuli in three different ocular configurations, similar to the ones we used in our previous study {[}\protect\hyperlink{ref-Segala2023}{3}{]}: monocular, binocular and dichoptic.
+In the monocular configuration, the unstimulated eye still saw a non-flickering disc of mean light flux.
+A schematic of the stimulation system is shown in Figure \ref{fig:spectraplots}a.
+Pupillometry data were collected using a binocular Pupil Core eye-tracker headset (Pupil Labs GmbH, Berlin, Germany {[}\protect\hyperlink{ref-Kassner2014}{37}{]}) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
+
+Our previous study {[}\protect\hyperlink{ref-Segala2023}{3}{]} used a temporal frequency of 2Hz for foveal luminance flicker, and recorded EEG data simultaneously with pupillometry.
+Initial pilot experiments indicated that this frequency was too high to elicit measurable responses when stimulating individual photoreceptor pathways.
+For all experiments, we therefore used a primary flicker frequency of 0.5Hz, as previous literature showed that this was slow enough to elicit a pupil response from all photoreceptor classes {[}\protect\hyperlink{ref-Spitschan2014}{7}{]}.
+We also focussed on only recording pupillometry data as this frequency would be too slow to elicit steady-state EEG responses {[}\protect\hyperlink{ref-Norcia2015}{38}{]}.
+
+For all experiments, sinusoidal temporal modulations were presented against the same background spectrum (matched between the eyes), which was used to achieve silent substitution in the three photoreceptor modulation experiments.
+The background spectra were defined by setting all channels to half maximum output for the brighter of the two devices (STLab 1, left eye) and then using the STLab 1/STLab 2 calibration ratio to find the equivalent settings for the companion device (STLab 2, right eye).
+The background spectrum illuminance was approximately 74 lux, or 68.5 cd/m\(^2\).
+The spectral power distributions and \(\alpha\)-opic irradiances of the background spectra for both eyes are shown in Figure \ref{fig:spectraplots}c-d.
+
+Silent substitution stimuli were prepared and calibrated for each participant with custom Python software {[}\protect\hyperlink{ref-Martin2023}{33}{]} and Python scripts.
+Estimates of photoreceptor spectral sensitivities for each participant were constructed from the known photopigment absorbance spectra {[}\protect\hyperlink{ref-Stockman2000}{34}{]}, taking account of the peak axial density of the respective photopigments, as well as lens {[}\protect\hyperlink{ref-Stockman2000}{34},\protect\hyperlink{ref-Pokorny1987}{39},\protect\hyperlink{ref-Stockman1999}{40}{]} and macular pigment density {[}\protect\hyperlink{ref-Stockman1999}{40},\protect\hyperlink{ref-Bone1988}{41}{]}, in accordance with the field size and age-dependant CIEPO06 observer model {[}\protect\hyperlink{ref-CIE2006}{42}{]}.
+The melanopic and rhodopic action spectra of the 32-year-old standard observer were taken from CIE S 026 {[}\protect\hyperlink{ref-CIE2018}{43}{]} and then adjusted for age-related lens transmittance with a spectral correction function, in line with the standard.
+Macular pigment correction was not applied to the rhodopic and melanopic action spectra because rods are not present at the fovea and ipRGCs sit above the retinal pigment layer {[}\protect\hyperlink{ref-Trieschmann2007}{44}{]}.
+
+In the light flux experiment, the stimulus intensity was increased and decreased relative to the background, which we expected to modulate all photoreceptor classes (see Figure \ref{fig:spectraplots}e,i).
+In the L-M cone modulation experiment, we used silent substitution to increase the L-cone activity, and simultaneously decrease the M-cone activity, during the first half-cycle of the sine wave.
+In the second half-cycle the polarity of the modulation reversed (see Figure \ref{fig:spectraplots}f,j).
+The maximum available L-M contrast was approximately 10\%.
+In the S-cone modulation experiment, we increased and decreased S-cone-directed signals, whilst keeping activity in the other photoreceptors constant (see Figure \ref{fig:spectraplots}g,k).
+Our system allowed a maximum contrast of 45\%.
+Finally, in the melanopsin experiment, we modulated the activity of the melanopsin-containing intrinsically photoreceptive retinal ganglion cells, whilst keeping cone activity constant (see Figure \ref{fig:spectraplots}h,l).
+The maximum available melanopsin contrast was 22\%.
+We assume that the activity of rods was constant at the high background luminance intensity used here, and so did not attempt to silence rod activity in any condition, as this would have greatly reduced the available dynamic range.
+Splatter on nominally silenced photoreceptors was very small (see Figure \ref{fig:spectraplots}j-l), well below the levels that would be expected to generate measurable pupil modulations, although we can observe that the rods may not be saturated in the L-M and melanopsin-directed stimuli (Figure \ref{fig:spectraplots}j and \ref{fig:spectraplots}l) and could intrude in these two experiments.
+We also estimated activation of penumbral L and M cones {[}\protect\hyperlink{ref-Barrionuevo2016}{5},\protect\hyperlink{ref-Spitschan2015}{35},\protect\hyperlink{ref-Zele2019}{45}{]}, which was minimal (\(\le 1.5%
+\) contrast; less than splatter on the open-field cones) for melanopsin-directed stimuli.
+We note that the temporal frequency of our modulation (0.5Hz) is well below the range where penumbral cone activation can elicit visible percepts, and that such percepts fade after around 1 second {[}\protect\hyperlink{ref-Spitschan2015}{35}{]}, and do not typically affect pupil responses {[}\protect\hyperlink{ref-Spitschan2014}{7}{]}.
+
+\hypertarget{procedure}{%
+\subsection{Procedure}\label{procedure}}
+
+Before the start of each experiment, participants adjusted the objective planes of the lenses with the help of the experimenter until the stimulus was in focus and they perceived the two pieces of blackout material as one fused disc.
+Pupil responses to binocular temporal contrast modulations were examined in a factorial design that combined six ocular conditions and five temporal contrast levels: 6, 12, 24, 48 and 96\% of the available dynamic range.
+This design, similar to that used in our previous studies {[}\protect\hyperlink{ref-Segala2023}{3},\protect\hyperlink{ref-Baker2017}{27},\protect\hyperlink{ref-Baker2020}{46}{]}, was applied in four separate experiments, each with a different mode of photoreceptor stimulation.
+In the first three conditions, the discs flickered at 0.5 Hz, in either a monocular, binocular or dichoptic arrangement.
+In the dichoptic condition the non-target eye saw a flickering fixed contrast of 48\% of the available dynamic range.
+In the remaining three conditions (the cross-frequency conditions) one eye's disc flickered at 0.4 Hz, and the other eye's disc flickered at 0.5 Hz.
+This included monocular responses at 0.4 Hz, as well as binocular (one eye sees each frequency at the target contrast) and dichoptic (target stimulus flickering at 0.5 Hz, mask contrast of 48\% at 0.4 Hz in the other eye) arrangements.
+We counterbalanced presentation of the target stimulus across the left and right eyes.
+
+The experiments were conducted in a windowless room, in which the only source of light was the modified VR headset.
+The participants sat as close as possible to the VR headset, leaving enough space for the eye-tracker to record the eyes.
+Each experiment was carried out in a single session of around 45-60 minutes, divided into three blocks of 15-17 minutes each.
+In each block, there were a total of 60 trials lasting 15 seconds each (12s of stimulus presentation, followed by 3s of interstimulus interval).
+The participants were given no task other than look at the black fixation dot while trying to minimise their blinking during the presentation period.
+For all experiments other than the light flux condition, participants adapted to the unmodulated background luminance for two minutes before stimulation began.
+
+Before the start of the L-M experiment, participants completed a luminance nulling perceptual calibration procedure in L-M cone space on an Iiyama \(\textrm{VisionMaster}^{\textrm{TM}}\) Pro 510 display (800 x 600 pixels, 60 Hz refresh rate).
+During the task, participants were presented with a disc flickering within the L-M cone space (between magenta and cyan).
+Using a trackball, participants adjusted the angle in cone space to find their subjective isoluminant point, which resulted in changing the flickering intensity of the stimulus until the amplitude of the flicker appeared to be minimised.
+The result was used to modify the requested contrasts during stimulus preparation so as to account for individual differences affecting perceived illuminance, principally the L:M cone ratio {[}\protect\hyperlink{ref-Carroll2002}{47},\protect\hyperlink{ref-Hofer2005}{48}{]}.
+
+\hypertarget{data-analysis}{%
+\subsection{Data analysis}\label{data-analysis}}
+
+The pupillometry data were analysed using the same method we used in our previous study {[}\protect\hyperlink{ref-Segala2023}{3}{]}.
+The data were converted from mp4 videos to a csv text file using the Pupil Player software {[}\protect\hyperlink{ref-Kassner2014}{37}{]}, which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
+The individual data were then loaded into R for analysis, where a ten-second waveform for each trial in each eye was extracted (excluding the first two seconds after stimulus onset).
+We interpolated across any dropped or missing frames to ensure regular and continuous sampling over time.
+The Fourier transform was calculated for each waveform, and all repetitions of each condition were pooled across eye and then averaged.
+Finally, data were averaged across all participants to obtain the group results.
+We used coherent averaging and at each stage we excluded data points with a Mahalanobis distance exceeding \(D\) = 3 from the complex-valued mean {[}\protect\hyperlink{ref-Baker2021}{49}{]}.
+For monocular stimulation, we confirmed that the consensual response was equivalent to the response in the stimulated eye.
+
+For all experiments, we used a bootstrapping procedure with \ensuremath{10^{4}} iterations to estimate standard errors across participants.
+All analysis and figure construction was conducted using a single R-script, available online, making this study fully computationally reproducible: \url{https://osf.io/gdvt4/}.
+
+\hypertarget{computational-model-and-parameter-estimation}{%
+\subsection{Computational model and parameter estimation}\label{computational-model-and-parameter-estimation}}
+
+To quantitatively summarise our data, we used the same model described in our previous study {[}\protect\hyperlink{ref-Segala2023}{3}{]}.
+The model has the same general form as the first stage of the contrast gain control model proposed by Meese and colleagues {[}\protect\hyperlink{ref-Meese2006}{22}{]}, but omits the second stage.
+For the previous model that we used {[}\protect\hyperlink{ref-Segala2023}{3}{]}, the exponent of the numerator and denominator had fixed values of 2 and (implicitly) 1.
+Here, we allow these parameters (called \emph{p} and \emph{q}) to be free, in order to permit different shapes of contrast response function, e.g.~accelerating or saturating.
+The responses of the left eye and right eye channels are as follows:
+
+\begin{equation}
+\label{eq:respL}
+resp_L = \frac{L^p}{Z + L^q + \omega R^q},
+\end{equation}
+
+\begin{equation}
+\label{eq:respR}
+resp_R = \frac{R^p}{Z + R^q + \omega L^q},
+\end{equation}
+
+\noindent where \emph{L} and \emph{R} are the contrast signals from the left and right eyes, \emph{p} and \emph{q} are exponents, \emph{Z} is a saturation constant that shifts the contrast-response function laterally, and \(\omega\) is the weight of suppression from the other eye.
+
+The responses from the two eyes are then summed binocularly:
+
+\begin{equation}
+\label{eq:respB}
+resp_B = R_{max}(resp_L + resp_R) + k,
+\end{equation}
+
+\noindent where \emph{k} is a noise parameter, and \(R_{max}\) scales the overall response amplitude.
+
+The models were fit using a hierarchical Bayesian framework implemented in Stan {[}\protect\hyperlink{ref-Carpenter2017}{50}{]}.
+The data for each photoreceptor type and response frequency was fit separately, for a total of 8 model fits.
+The prior for the \(\omega\) parameter was Gaussian, with a mean of 1 and standard deviation of 0.5.
+Priors for the other free parameters were also Gaussian, with mean values based on previous work {[}\protect\hyperlink{ref-Segala2023}{3}{]}.
+We calculated over \ensuremath{10^{6}} posterior samples, and retained 10\% for plotting.
+
 \hypertarget{references}{%
@@
 \leavevmode\hypertarget{ref-McDougal2015}{}%
-1. McDougal DH, Gamlin PD. Autonomic control of the eye. \emph{Comprehensive Physiology}. 2015;5(1):439-473. doi:\href{https://doi.org/10.1002/cphy.c140014}{10.1002/cphy.c140014}
+1. McDougal DH, Gamlin PD. Autonomic control of the eye. Comprehensive Physiology. 2015;5: 439--473. doi:\href{https://doi.org/10.1002/cphy.c140014}{10.1002/cphy.c140014}
 
@@
 Pupillary light reflex in humans: Evidence for an unbalanced pathway from nasal retina, and for signal cancellation in brainstem.
-\emph{Vision Res}.
-1981;21(4):513-525.
+Vision Res.
+1981;21: 513--25.
 doi:\href{https://doi.org/10.1016/0042-6989(81)90097-3}{10.1016/0042-6989(81)90097-3}
@@
 Different rules for binocular combination of luminance flicker in cortical and subcortical pathways.
-\emph{eLife}.
+eLife.
 2023;12.
@@
 The influence of intrinsically-photosensitive retinal ganglion cells on the spectral sensitivity and response dynamics of the human pupillary light reflex.
-\emph{Vision Research}.
-2010;50(1):72-87.
+Vision Research.
+2010;50: 72--87.
 doi:\href{https://doi.org/10.1016/j.visres.2009.10.012}{10.1016/j.visres.2009.10.012}
@@
 Luminance and chromatic signals interact differently with melanopsin activation to control the pupil light response.
-\emph{Journal of Vision}.
-2016;16(11):29.
+Journal of Vision.
+2016;16(11): 29.
 doi:\href{https://doi.org/10.1167/16.11.29}{10.1167/16.11.29}
@@
 Paradoxical pupil responses to isolated M-cone increments.
-\emph{Journal of the Optical Society of America A}.
-2018;35(4):B66-B71.
+Journal of the Optical Society of America A.
+2018;35: B66--B71.
 doi:\href{https://doi.org/10.1364/JOSAA.35.000B66}{10.1364/JOSAA.35.000B66}
@@
 Opponent melanopsin and s-cone signals in the human pupillary light response.
-\emph{Proceedings of the National Academy of Sciences}.
-2014;111(43):15568-15572.
+Proceedings of the National Academy of Sciences.
+2014;111: 15568--15572.
 doi:\href{https://doi.org/10.1073/pnas.1400942111}{10.1073/pnas.1400942111}
@@
 Melanopsin- and L-cone--induced pupil constriction is inhibited by S- and M-cones in humans.
-\emph{Proceedings of the National Academy of Sciences}.
-2018;115(4):792-797.
+Proceedings of the National Academy of Sciences.
+2018;115: 792--797.
 doi:\href{https://doi.org/10.1073/pnas.1716281115}{10.1073/pnas.1716281115}
@@
 \leavevmode\hypertarget{ref-Mathot2018}{}%
-9. Mathôt S. Pupillometry: Psychology, physiology, and function. \emph{J Cogn}. 2018;1(1):16. doi:\href{https://doi.org/10.5334/joc.18}{10.5334/joc.18}
+9. Mathôt S. Pupillometry: Psychology, physiology, and function. J Cogn. 2018;1: 16. doi:\href{https://doi.org/10.5334/joc.18}{10.5334/joc.18}
 
@@
 Intrinsically photosensitive melanopsin retinal ganglion cell contributions to the pupillary light reflex and circadian rhythm.
-\emph{Clinical and Experimental Optometry}.
-2010;93(3):137-149.
+Clinical and Experimental Optometry.
+2010;93: 137--149.
 doi:\href{https://doi.org/10.1111/j.1444-0938.2010.00479.x}{10.1111/j.1444-0938.2010.00479.x}
@@
 A Novel Human Opsin in the Inner Retina.
-\emph{Journal of Neuroscience}.
-2000;20(2):600-605.
+Journal of Neuroscience.
+2000;20: 600--605.
 doi:\href{https://doi.org/10.1523/JNEUROSCI.20-02-00600.2000}{10.1523/JNEUROSCI.20-02-00600.2000}
@@
 12.
-Panda S, Sato TK, Castrucci AM, et al.
+Panda S, Sato TK, Castrucci AM, Rollag MD, DeGrip WJ, Hogenesch JB, et al.
 Melanopsin (opn4) requirement for normal light-induced circadian phase shifting.
-\emph{Science}.
-2002;298(5601):2213-2216.
+Science.
+2002;298: 2213--2216.
 doi:\href{https://doi.org/10.1126/science.1076848}{10.1126/science.1076848}
@@
 13.
-Ruby NF, Brennan TJ, Xie X, et al.
+Ruby NF, Brennan TJ, Xie X, Cao V, Franken P, Heller HC, et al.
 Role of melanopsin in circadian responses to light.
-\emph{Science}.
-2002;298(5601):2211-2213.
+Science.
+2002;298: 2211--2213.
 doi:\href{https://doi.org/10.1126/science.1076701}{10.1126/science.1076701}
@@
 Fireworks in the primate retina: In vitro photodynamics reveals diverse lgn-projecting ganglion cell types.
-\emph{Neuron}.
-2003;37(1):15-27.
+Neuron.
+2003;37: 15--27.
 doi:\href{https://doi.org/https://doi.org/10.1016/S0896-6273(02)01143-1}{https://doi.org/10.1016/S0896-6273(02)01143-1}
@@
 15.
-Lucas RJ, Hattar S, Takao M, Berson DM, Foster RG, Yau KW.
+Lucas RJ, Hattar S, Takao M, Berson DM, Foster RG, Yau K-W.
 Diminished pupillary light reflex at high irradiances in melanopsin-knockout mice.
-\emph{Science}.
-2003;299(5604):245-247.
+Science.
+2003;299: 245--247.
 doi:\href{https://doi.org/10.1126/science.1077293}{10.1126/science.1077293}
@@
 16.
-Gamlin PDR, McDougal DH, Pokorny J, Smith VC, Yau KW, Dacey DM.
+Gamlin PDR, McDougal DH, Pokorny J, Smith VC, Yau K-W, Dacey DM.
 Human and macaque pupil responses driven by melanopsin-containing retinal ganglion cells.
-\emph{Vision Research}.
-2007;47(7):946-954.
+Vision Research.
+2007;47: 946--954.
 doi:\href{https://doi.org/10.1016/j.visres.2006.12.015}{10.1016/j.visres.2006.12.015}
@@
 Receptive fields, binocular interaction and functional architecture in the cat's visual cortex.
-\emph{J Physiol}.
-1962;160(1):106-154.
+J Physiol.
+1962;160: 106--54.
 doi:\href{https://doi.org/10.1113/jphysiol.1962.sp006837}{10.1113/jphysiol.1962.sp006837}
@@
 \leavevmode\hypertarget{ref-Baker2018}{}%
-18.
-Baker DH, Lygo FA, Meese TS, Georgeson MA.
-Binocular summation revisited: Beyond \(\sqrt{2}\).
-\emph{Psychol Bull}.
-2018;144(11):1186-1199.
-doi:\href{https://doi.org/10.1037/bul0000163}{10.1037/bul0000163}
+18. Baker DH, Lygo FA, Meese TS, Georgeson MA. Binocular summation revisited: Beyond \(\sqrt{2}\). Psychol Bull. 2018;144: 1186--1199. doi:\href{https://doi.org/10.1037/bul0000163}{10.1037/bul0000163}
 
 \leavevmode\hypertarget{ref-Campbell1965}{}%
-19. Campbell FW, Green DG. Monocular versus binocular visual acuity. \emph{Nature}. 1965;208(5006):191-192. doi:\href{https://doi.org/10.1038/208191a0}{10.1038/208191a0}
+19. Campbell FW, Green DG. Monocular versus binocular visual acuity. Nature. 1965;208: 191--2. doi:\href{https://doi.org/10.1038/208191a0}{10.1038/208191a0}
 
@@
 Binocular interaction: Contrast matching and contrast discrimination are predicted by the same model.
-\emph{Spat Vis}.
-2007;20(5):397-413.
+Spat Vis.
+2007;20: 397--413.
 doi:\href{https://doi.org/10.1163/156856807781503622}{10.1163/156856807781503622}
@@
 \leavevmode\hypertarget{ref-Moradi2009}{}%
-21. Moradi F, Heeger DJ. Inter-ocular contrast normalization in human visual cortex. \emph{J Vis}. 2009;9(3):13.1-22. doi:\href{https://doi.org/10.1167/9.3.13}{10.1167/9.3.13}
+21. Moradi F, Heeger DJ. Inter-ocular contrast normalization in human visual cortex. J Vis. 2009;9: 13.1--22. doi:\href{https://doi.org/10.1167/9.3.13}{10.1167/9.3.13}
 
 \leavevmode\hypertarget{ref-Meese2006}{}%
-22. Meese TS, Georgeson MA, Baker DH. Binocular contrast vision at and above threshold. \emph{Journal of Vision}. 2006;6(11):1224-1243. doi:\href{https://doi.org/10.1167/6.11.7}{10.1167/6.11.7}
+22. Meese TS, Georgeson MA, Baker DH. Binocular contrast vision at and above threshold. Journal of Vision. 2006;6: 1224--43. doi:\href{https://doi.org/10.1167/6.11.7}{10.1167/6.11.7}
+
+\leavevmode\hypertarget{ref-Kingdom2015}{}%
+23.
+Kingdom FAA, Libenson L.
+Dichoptic color saturation mixture: Binocular luminance contrast promotes perceptual averaging.
+J Vis.
+2015;15: 2.
+doi:\href{https://doi.org/10.1167/15.5.2}{10.1167/15.5.2}
+
+\leavevmode\hypertarget{ref-Busse2009}{}%
+24.
+Busse L, Wade AR, Carandini M.
+Representation of concurrent stimuli by population activity in visual cortex.
+Neuron.
+2009;64: 931--42.
+doi:\href{https://doi.org/10.1016/j.neuron.2009.11.004}{10.1016/j.neuron.2009.11.004}
+
+\leavevmode\hypertarget{ref-Spitschan2019}{}%
+25. Spitschan M, Cajochen C. Binocular facilitation in light-mediated melatonin suppression? J Pineal Res. 2019;67: e12602. doi:\href{https://doi.org/10.1111/jpi.12602}{10.1111/jpi.12602}
+
+\leavevmode\hypertarget{ref-Baker2024}{}%
+26.
+Baker DH, Hansford KJ, Segala FG, Morsi AY, Huxley RJ, Martin JT, et al.
+Binocular integration of chromatic and luminance signals.
+J Vis.
+2024;24(12): 7.
+doi:\href{https://doi.org/10.1167/jov.24.12.7}{10.1167/jov.24.12.7}
+
+\leavevmode\hypertarget{ref-Baker2017}{}%
+27.
+Baker DH, Wade AR.
+Evidence for an optimal algorithm underlying signal combination in human visual cortex.
+Cereb Cortex.
+2017;27: 254--264.
+doi:\href{https://doi.org/10.1093/cercor/bhw395}{10.1093/cercor/bhw395}
+
+\leavevmode\hypertarget{ref-Kaestner2019}{}%
+28.
+Kaestner M, Maloney RT, Wailes-Newson KH, Bloj M, Harris JM, Morland AB, et al.
+Asymmetries between achromatic and chromatic extraction of 3D motion signals.
+Proc Natl Acad Sci U S A.
+2019;116: 13631--13640.
+doi:\href{https://doi.org/10.1073/pnas.1817202116}{10.1073/pnas.1817202116}
 
 \leavevmode\hypertarget{ref-Martin2022}{}%
-23.
+29.
 Martin JT, Pinto J, Bulte D, Spitschan M.
 PyPlr: A versatile, integrated system of hardware and software for researching the human pupillary light reflex.
-\emph{Behavior Research Methods}.
-2022;54(6):2720-2739.
+Behavior Research Methods.
+2022;54: 2720--2739.
 doi:\href{https://doi.org/10.3758/s13428-021-01759-3}{10.3758/s13428-021-01759-3}
@@
 \leavevmode\hypertarget{ref-Estevez1982}{}%
-24.
+30.
 Estévez O, Spekreijse H.
 The "silent substitution" method in visual research.
-\emph{Vision Research}.
-1982;22(6):681-691.
+Vision Research.
+1982;22: 681--691.
 doi:\href{https://doi.org/10.1016/0042-6989(82)90104-3}{10.1016/0042-6989(82)90104-3}
@@
 \leavevmode\hypertarget{ref-Shapiro1996}{}%
-25.
+31.
 Shapiro AG, Pokorny J, Smith VC.
 Conerod receptor spaces with illustrations that use CRT phosphor and light-emitting-diode spectra.
-\emph{Journal of the Optical Society of America A}.
-1996;13(12):2319.
+Journal of the Optical Society of America A.
+1996;13: 2319.
 doi:\href{https://doi.org/10.1364/josaa.13.002319}{10.1364/josaa.13.002319}
@@
 \leavevmode\hypertarget{ref-Spitschan2018}{}%
-26.
+32.
 Spitschan M, Woelders T.
 The Method of Silent Substitution for Examining Melanopsin Contributions to Pupil Control.
-\emph{Frontiers in Neurology}.
+Frontiers in Neurology.
 2018;9.
@@
 \leavevmode\hypertarget{ref-Martin2023}{}%
-27.
+33.
 Martin JT, Boynton GM, Baker DH, Wade AR, Spitschan M.
 PySilSub: An open-source python toolbox for implementing the method of silent substitution in vision and nonvisual photoreception research.
-\emph{Journal of Vision}.
-2023;23(7):10.
+Journal of Vision.
+2023;23: 10.
 doi:\href{https://doi.org/10.1167/jov.23.7.10}{10.1167/jov.23.7.10}
@@
 \leavevmode\hypertarget{ref-Stockman2000}{}%
-28.
+34.
 Stockman A, Sharpe LT.
 The spectral sensitivities of the middle- and long-wavelength-sensitive cones derived from measurements in observers of known genotype.
-\emph{Vision Res}.
-2000;40(13):1711-1737.
+Vision Res.
+2000;40: 1711--37.
 doi:\href{https://doi.org/10.1016/s0042-6989(00)00021-3}{10.1016/s0042-6989(00)00021-3}
@@
 \leavevmode\hypertarget{ref-Spitschan2015}{}%
-29.
+35.
 Spitschan M, Aguirre GK, Brainard DH.
 Selective stimulation of penumbral cones reveals perception in the shadow of retinal blood vessels.
-\emph{PLoS One}.
-2015;10(4):e0124328.
+PLoS One.
+2015;10: e0124328.
 doi:\href{https://doi.org/10.1371/journal.pone.0124328}{10.1371/journal.pone.0124328}
@@
 \leavevmode\hypertarget{ref-Zele2018}{}%
-30.
+36.
 Zele AJ, Feigl B, Adhikari P, Maynard ML, Cao D.
 Melanopsin photoreception contributes to human visual detection, temporal and colour processing.
-\emph{Scientific Reports}.
-2018;8(1).
+Scientific Reports.
+2018;8.
 doi:\href{https://doi.org/10.1038/s41598-018-22197-w}{10.1038/s41598-018-22197-w}
@@
 \leavevmode\hypertarget{ref-Kassner2014}{}%
-31.
+37.
 Kassner M, Patera W, Bulling A.
 Pupil: An open source platform for pervasive eye tracking and mobile gaze-based interaction.
-In: \emph{Proceedings of the 2014 ACM International Joint Conference on Pervasive and Ubiquitous Computing: Adjunct Publication}.
+Proceedings of the 2014 ACM international joint conference on pervasive and ubiquitous computing: Adjunct publication.
 ACM; 2014.
@@
 \leavevmode\hypertarget{ref-Norcia2015}{}%
-32.
+38.
 Norcia AM, Appelbaum LG, Ales JM, Cottereau BR, Rossion B.
 The steady-state visual evoked potential in vision research: A review.
-\emph{Journal of Vision}.
-2015;15(6):4.
+Journal of Vision.
+2015;15(6): 4.
 doi:\href{https://doi.org/10.1167/15.6.4}{10.1167/15.6.4}
@@
 \leavevmode\hypertarget{ref-Pokorny1987}{}%
-33. Pokorny J, Smith VC, Lutze M. Aging of the human lens. \emph{Applied Optics}. 1987;26(8):1437. doi:\href{https://doi.org/10.1364/ao.26.001437}{10.1364/ao.26.001437}
+39. Pokorny J, Smith VC, Lutze M. Aging of the human lens. Applied Optics. 1987;26: 1437. doi:\href{https://doi.org/10.1364/ao.26.001437}{10.1364/ao.26.001437}
 
 \leavevmode\hypertarget{ref-Stockman1999}{}%
-34.
+40.
 Stockman A, Sharpe LT, Fach C.
 The spectral sensitivity of the human short-wavelength sensitive cones derived from thresholds and color matches.
-\emph{Vision Research}.
-1999;39(17):2901-2927.
+Vision Research.
+1999;39: 2901--2927.
 doi:\href{https://doi.org/https://doi.org/10.1016/S0042-6989(98)00225-9}{https://doi.org/10.1016/S0042-6989(98)00225-9}
@@
 \leavevmode\hypertarget{ref-Bone1988}{}%
-35. Bone RA, Landrum JT, Fernandez L, Tarsis SL. Analysis of the macular pigment by HPLC: Retinal distribution and age study. \emph{Investigative Ophthalmology \& Visual Science}. 1988;29(6):843-849.
+41. Bone RA, Landrum JT, Fernandez L, Tarsis SL. Analysis of the macular pigment by HPLC: Retinal distribution and age study. Investigative Ophthalmology \& Visual Science. 1988;29: 843--849.
 
 \leavevmode\hypertarget{ref-CIE2006}{}%
-36. CIE. \emph{Fundamental Chromaticity Diagram with Physiological Axes}. CIE Central Bureau; 2006. \url{https://cie.co.at/publications/fundamental-chromaticity-diagram-physiological-axes-part-1}
+42. CIE. Fundamental chromaticity diagram with physiological axes. CIE Central Bureau; 2006. Available: \url{https://cie.co.at/publications/fundamental-chromaticity-diagram-physiological-axes-part-1}
 
 \leavevmode\hypertarget{ref-CIE2018}{}%
-37. CIE. \emph{CIE System for Metrology of Optical Radiation for ipRGC-Influenced Responses to Light}. CIE Central Bureau; 2018. doi:\href{https://doi.org/10.25039/S026.2018}{10.25039/S026.2018}
+43. CIE. CIE system for metrology of optical radiation for ipRGC-influenced responses to light. CIE Central Bureau; 2018. doi:\href{https://doi.org/10.25039/S026.2018}{10.25039/S026.2018}
 
 \leavevmode\hypertarget{ref-Trieschmann2007}{}%
-38.
-Trieschmann M, Kuijk FJGM van, Alexander R, et al.
+44.
+Trieschmann M, Kuijk FJGM van, Alexander R, Hermans P, Luthert P, Bird AC, et al.
 Macular pigment in the human retina: Histological evaluation of localization and distribution.
-\emph{Eye}.
-2007;22(1):132-137.
+Eye.
+2007;22: 132--137.
 doi:\href{https://doi.org/10.1038/sj.eye.6702780}{10.1038/sj.eye.6702780}
@@
 \leavevmode\hypertarget{ref-Zele2019}{}%
-39.
+45.
 Zele AJ, Adhikari P, Cao D, Feigl B.
 Melanopsin driven enhancement of cone-mediated visual processing.
-\emph{Vision Res}.
-2019;160:72-81.
+Vision Res.
+2019;160: 72--81.
 doi:\href{https://doi.org/10.1016/j.visres.2019.04.009}{10.1016/j.visres.2019.04.009}
 
-\leavevmode\hypertarget{ref-Baker2017}{}%
-40.
-Baker DH, Wade AR.
-Evidence for an optimal algorithm underlying signal combination in human visual cortex.
-\emph{Cereb Cortex}.
-2017;27(1):254-264.
-doi:\href{https://doi.org/10.1093/cercor/bhw395}{10.1093/cercor/bhw395}
-
 \leavevmode\hypertarget{ref-Baker2020}{}%
-41.
+46.
 Baker DH, Vilidaite G, McClarnon E, Valkova E, Bruno A, Millman RE.
 Binaural summation of amplitude modulation involves weak interaural suppression.
-\emph{Sci Rep}.
-2020;10(1):3560.
+Sci Rep.
+2020;10: 3560.
 doi:\href{https://doi.org/10.1038/s41598-020-60602-5}{10.1038/s41598-020-60602-5}
@@
 \leavevmode\hypertarget{ref-Carroll2002}{}%
-42. Carroll J, Neitz J, Neitz M. Estimates of L:M cone ratio from ERG flicker photometry and genetics. \emph{Journal of Vision}. 2002;2(8):1. doi:\href{https://doi.org/10.1167/2.8.1}{10.1167/2.8.1}
+47. Carroll J, Neitz J, Neitz M. Estimates of L:M cone ratio from ERG flicker photometry and genetics. Journal of Vision. 2002;2: 1. doi:\href{https://doi.org/10.1167/2.8.1}{10.1167/2.8.1}
 
 \leavevmode\hypertarget{ref-Hofer2005}{}%
-43.
+48.
 Hofer H, Carroll J, Neitz J, Neitz M, Williams DR.
 Organization of the human trichromatic cone mosaic.
-\emph{The Journal of Neuroscience}.
-2005;25(42):9669-9679.
+The Journal of Neuroscience.
+2005;25: 9669--9679.
 doi:\href{https://doi.org/10.1523/jneurosci.2414-05.2005}{10.1523/jneurosci.2414-05.2005}
@@
 \leavevmode\hypertarget{ref-Baker2021}{}%
-44. Baker DH. Statistical analysis of periodic data in neuroscience. \emph{Neurons, Behavior, Data analysis, and Theory}. 2021;5(3). doi:\href{https://doi.org/10.51628/001c.27680}{10.51628/001c.27680}
+49. Baker DH. Statistical analysis of periodic data in neuroscience. Neurons, Behavior, Data analysis, and Theory. 2021;5. doi:\href{https://doi.org/10.51628/001c.27680}{10.51628/001c.27680}
 
 \leavevmode\hypertarget{ref-Carpenter2017}{}%
-45. Carpenter B, Gelman A, Hoffman MD, et al. Stan: A probabilistic programming language. \emph{J Stat Softw}. 2017;76. doi:\href{https://doi.org/10.18637/jss.v076.i01}{10.18637/jss.v076.i01}
-
-\leavevmode\hypertarget{ref-Kingdom2015}{}%
-46.
-Kingdom FAA, Libenson L.
-Dichoptic color saturation mixture: Binocular luminance contrast promotes perceptual averaging.
-\emph{J Vis}.
-2015;15(5):2.
-doi:\href{https://doi.org/10.1167/15.5.2}{10.1167/15.5.2}
-
-\leavevmode\hypertarget{ref-Busse2009}{}%
-47.
-Busse L, Wade AR, Carandini M.
-Representation of concurrent stimuli by population activity in visual cortex.
-\emph{Neuron}.
-2009;64(6):931-942.
-doi:\href{https://doi.org/10.1016/j.neuron.2009.11.004}{10.1016/j.neuron.2009.11.004}
-
-\leavevmode\hypertarget{ref-Spitschan2019}{}%
-48. Spitschan M, Cajochen C. Binocular facilitation in light-mediated melatonin suppression? \emph{J Pineal Res}. 2019;67(4):e12602. doi:\href{https://doi.org/10.1111/jpi.12602}{10.1111/jpi.12602}
-
-\leavevmode\hypertarget{ref-Baker2024}{}%
-49. Baker DH, Hansford KJ, Segala FG, et al. Binocular integration of chromatic and luminance signals. \emph{J Vis}. 2024;24(12):7. doi:\href{https://doi.org/10.1167/jov.24.12.7}{10.1167/jov.24.12.7}
-
-\leavevmode\hypertarget{ref-Kaestner2019}{}%
 50.
-Kaestner M, Maloney RT, Wailes-Newson KH, et al.
-Asymmetries between achromatic and chromatic extraction of 3D motion signals.
-\emph{Proc Natl Acad Sci U S A}.
-2019;116(27):13631-13640.
-doi:\href{https://doi.org/10.1073/pnas.1817202116}{10.1073/pnas.1817202116}
+Carpenter B, Gelman A, Hoffman MD, Lee D, Goodrich B, Betancourt M, et al.
+Stan: A probabilistic programming language.
+J Stat Softw.
+2017;76.
+doi:\href{https://doi.org/10.18637/jss.v076.i01}{10.18637/jss.v076.i01}
 

### 2025-10-16 manuscript.Rmd
Update author summary

@@
 Our pupils constantly adjust in size to control how much light enters the eye: in brighter conditions the pupils will reduce in size, and in dimmer conditions they will increase in size.
-This process, known as the pupillary light response, is usually taken for granted but is crucial for vision, and is controlled automatically by the body’s nervous system.
-Different types of light-sensing cells in the retina, the photoreceptor cells, contribute to this response: some respond quickly to changes in light, while others maintain responses over longer periods.
+This process, known as the pupillary light reflex, is usually taken for granted but is crucial for vision, and is controlled automatically by the body’s nervous system.
+Different types of light-sensing cells in the retina contribute to this response: some respond quickly to changes in light, while others maintain responses over longer periods.
 In our study, we explored how signals from the two eyes are combined to regulate pupil size.
-Using a new type of visual stimulation that allowed us to selectively target specific classes of photoreceptor cells, we found that the way the two eyes’ signals are combined depends on which class of photoreceptor cells is involved.
-For example, some photoreceptor classes showed cooperation between the eyes, while others showed competition.
-By revealing these distinct patterns of signal combination, our work provides new insight into how light information is integrated in the pupils.
+Using a novel binocular light stimulator that allowed us to selectively target specific classes of photoreceptive cells separately in each eye, we found that the way the two eyes’ signals are combined depends on which cell types are involved.
+For example, some cell classes showed cooperation between the eyes, while others showed competition.
+By revealing these distinct patterns of signal combination, our work provides new insight into how light information is integrated to regulate the pupils.
+A computational model built to summarize the results allows for comparisons within and between different sensory systems.
 

### 2025-10-16 manuscript.tex
Update author summary

@@
 Our pupils constantly adjust in size to control how much light enters the eye: in brighter conditions the pupils will reduce in size, and in dimmer conditions they will increase in size.
-This process, known as the pupillary light response, is usually taken for granted but is crucial for vision, and is controlled automatically by the body's nervous system.
-Different types of light-sensing cells in the retina, the photoreceptor cells, contribute to this response: some respond quickly to changes in light, while others maintain responses over longer periods.
+This process, known as the pupillary light reflex, is usually taken for granted but is crucial for vision, and is controlled automatically by the body's nervous system.
+Different types of light-sensing cells in the retina contribute to this response: some respond quickly to changes in light, while others maintain responses over longer periods.
 In our study, we explored how signals from the two eyes are combined to regulate pupil size.
-Using a new type of visual stimulation that allowed us to selectively target specific classes of photoreceptor cells, we found that the way the two eyes' signals are combined depends on which class of photoreceptor cells is involved.
-For example, some photoreceptor classes showed cooperation between the eyes, while others showed competition.
-By revealing these distinct patterns of signal combination, our work provides new insight into how light information is integrated in the pupils.
+Using a novel binocular light stimulator that allowed us to selectively target specific classes of photoreceptive cells separately in each eye, we found that the way the two eyes' signals are combined depends on which cell types are involved.
+For example, some cell classes showed cooperation between the eyes, while others showed competition.
+By revealing these distinct patterns of signal combination, our work provides new insight into how light information is integrated to regulate the pupils.
+A computational model built to summarize the results allows for comparisons within and between different sensory systems.
 

### 2025-12-18 manuscript.Rmd
Edits

--- 2025-10-09 manuscript.Rmd
@@
 linkcolor: black
-csl: plos-computational-biology.csl
+csl: plos-one.csl
 header-includes:
@@
 
-# Author Summary
-
-Our pupils constantly adjust in size to control how much light enters the eye: in brighter conditions the pupils will reduce in size, and in dimmer conditions they will increase in size.
-This process, known as the pupillary light response, is usually taken for granted but is crucial for vision, and is controlled automatically by the body’s nervous system.
-Different types of light-sensing cells in the retina, the photoreceptor cells, contribute to this response: some respond quickly to changes in light, while others maintain responses over longer periods.
-In our study, we explored how signals from the two eyes are combined to regulate pupil size.
-Using a new type of visual stimulation that allowed us to selectively target specific classes of photoreceptor cells, we found that the way the two eyes’ signals are combined depends on which class of photoreceptor cells is involved.
-For example, some photoreceptor classes showed cooperation between the eyes, while others showed competition.
-By revealing these distinct patterns of signal combination, our work provides new insight into how light information is integrated in the pupils.
-
 # Introduction
@@
 
-# Results
-
-Figure \@ref(fig:spectraplots)m-p shows averaged waveforms of pupil diameter in response to binocular stimulation.
-For light flux stimuli (Figure \@ref(fig:spectraplots)m) a strong modulation is apparent at the stimulation frequency (0.5Hz), which is also clear in the Fourier amplitude spectrum (Figure \@ref(fig:spectraplots)q).
-For binocular stimulation of the L-M pathway, S-cone pathway and melanopsin pathway, pupil modulations were less than 10\% of the amplitude of the light flux modulation (note the change in y-axis scale for the Fourier spectra), but still apparent at 0.5Hz in the Fourier spectra (Figure \@ref(fig:spectraplots)n-p).
-We also observed a second harmonic response (at 1Hz) for all conditions, which was weaker than the first harmonic for light flux and melanopsin stimulation, but stronger for L-M and S-cone stimulation.
-The second harmonic is also apparent in the pupil waveforms shown in Figure \@ref(fig:spectraplots)n-p.
-Our main analysis therefore focuses on the amplitude of the pupil modulations at both the first and second harmonic frequencies across different stimulus conditions.
-
-```{r spectraplots, fig.cap="Summary of the spectral power distributions and alpha-opic irradiances for the background and each condition, as well as averaged pupil diameters and Fourier spectra.
-Panel (a) shows a schematic of the binocular stimulation system for presenting spectrally tuned modulations independently to each eye.
-The VR headset was attached to a clamp stand that the experimenters could use to adjust the height and align the headset with the eyes of the participant.
-The participant's head was supported by a chin rest to keep it in position throughout the experiment.
-Panel (b) shows the outputs of each LED primary at maximum intensity, and panels (c) and (d) show the overall spectral power distributions and the alpha-opic irradiances of the background spectra used for both eyes.
-The subsequent rows show the power differences (e-h), and photoreceptor contrasts (i-l) relative to the background, averaged pupil diameter waveforms (m-p) and Fourier spectra (q-t) for binocular stimulation.
-Column headings indicate the pathway stimulated, and shaded regions in panels m-t indicate bootstrapped 95\\% confidence intervals.", fig.align="center", out.width = '80%', echo=FALSE}
-
-knitr::include_graphics(paste0(figdir,'methodsfigrods.pdf'))
-
-```
-
-Figure \@ref(fig:FirstHarmonicPlots)a-d shows contrast response functions across stimulation conditions for responses at the first harmonic of the main stimulation frequency (0.5Hz).
-In each plot, the response to monocular stimulation is given by the red circles and typically increases monotonically as a function of stimulus (temporal) contrast.
-Relative to monocular stimulation, binocular stimulation led to higher response amplitudes, indicating a binocular facilitation effect, for the light flux and S-cone conditions (Figure \@ref(fig:FirstHarmonicPlots)a,c), and to some extent for the melanopsin condition (Figure \@ref(fig:FirstHarmonicPlots)d).
-However, the L-M cone condition (Figure \@ref(fig:FirstHarmonicPlots)b) produced a binocular suppression effect, where the response to binocular stimulation was weaker than the response to monocular stimulation (blue squares below red circles).
-These results indicate that the magnitude of binocular facilitation differs across photoreceptor pathway, suggesting heterogeneity in the underlying neural computation.
-
-```{r FirstHarmonicPlots, fig.cap="Contrast response functions for pupil modualations in response to flicker at 0.5Hz (panels a-d), and 0.4Hz (panels f-i), and posterior parameter distributions for the weight of interocular suppression (panel e).
-Within each panel (except panel e), data points are the coherently averaged amplitudes for each condition, and error bars indicate bootstrapped 95\\% confidence intervals.
-Curves show model fits using the maximum a posteriori (MAP) parameter values (see Table 1).
-In panel (e), vertical lines show the MAP estimates, and the thin black curve indicates the prior (note the logarithmic x-axis).", fig.align="center", out.width="40%", echo=FALSE}
-
-knitr::include_graphics(paste0(figdir,'FirstHarmonic.pdf'))
-
-```
-
-In contemporary models of binocular signal combination, the amount of binocular facilitation is determined by the magnitude of interocular suppression, with strong suppression reducing facilitation [@Kingdom2015].
-We can estimate the strength of interocular suppression by measuring how much monocular responses are reduced when a dichoptic 'mask' is shown to the other eye.
-In our paradigm, the two components flickered at different frequencies (0.5 and 0.4Hz) so that their responses remained distinct in the Fourier spectrum [e.g.
-@Busse2009].
-The yellow diamond symbols in Figure \@ref(fig:FirstHarmonicPlots)a-d show the target responses in this condition, and in most cases were weaker than the monocular responses (red circles).
-The strongest dichoptic masking is found in the L-M condition, where we also observed the binocular suppression effect.
-Suppression can also be estimated from the responses at 0.4Hz (Figure \@ref(fig:FirstHarmonicPlots)f-i).
-The reduced amplitude in the binocular cross condition (where the two eyes received different temporal frequencies; purple squares) relative to the 0.4Hz monocular condition (grey circles), and the progressive decline in amplitude of the dichoptic cross response (yellow diamonds) also differ across photoreceptor conditions, showing similar differences to those observed at 0.5Hz.
-
-To estimate the extent of interocular suppression for each photoreceptor pathway, we fitted each data set using a Bayesian hierarchical implementation of a simple binocular combination model [@Meese2006; @Segala2023].
-Our primary objective was to compare posterior distributions of the weight of interocular suppression, which are shown in Figure \@ref(fig:FirstHarmonicPlots)e.
-Consistent with our earlier observations, the strongest suppressive weight corresponds to the L-M and Melanopsin conditions, and the weakest suppression corresponds to the light flux and S-cone conditions, with virtually no overlap between the posterior distributions for weak and strong suppression.
-The model fits were of good quality, as shown by the curves in Figure \@ref(fig:FirstHarmonicPlots)a-d,f-i.
-The fitted model parameters are given in Table \@ref(tab:paramtable).
-
-```{r paramtable, echo=FALSE}
-
-condnames <- c('Light flux 1F','L-M cone 1F','S cone 1F','Melanopsin 1F','Light flux 2F','L-M cone 2F','S cone 2F','Melanopsin 2F')
-zlist <- c(pupilZLum, pupilZLM, pupilZS, pupilZMel, pupilZLum2, pupilZLM2, pupilZS2, pupilZMel2)
-klist <- c(pupilKLum, pupilKLM, pupilKS, pupilKMel, pupilKLum2, pupilKLM2, pupilKS2, pupilKMel2)
-wlist <- c(pupilWLum, pupilWLM, pupilWS, pupilWMel, pupilWLum2, pupilWLM2, pupilWS2, pupilWMel2)
-plist <- c(pupilPLum, pupilPLM, pupilPS, pupilPMel, pupilPLum2, pupilPLM2, pupilPS2, pupilPMel2)
-qlist <- c(pupilQLum, pupilQLM, pupilQS, pupilQMel, pupilQLum2, pupilQLM2, pupilQS2, pupilQMel2)
-Rlist <- c(pupilRmaxLum, pupilRmaxLM, pupilRmaxS, pupilRmaxMel, pupilRmaxLum2, pupilRmaxLM2, pupilRmaxS2, pupilRmaxMel2)
-tabledata <- data.frame(condnames,round(zlist,digits=2),round(klist,digits=5),round(wlist,digits=2),round(plist,digits=2),round(qlist,digits=2),round(Rlist,digits=4))
-
-colnames(tabledata) <- c('Experiment','Z','k','w','p','q','Rmax')
-kable(tabledata, align='lcccccc',booktabs=TRUE,linesep='',caption = 'Summary of maximum a posteriori (MAP) parameter estimates for each data set.') %>%
-kableExtra::kable_styling(latex_options = "HOLD_position") %>% row_spec(4,hline_after=TRUE)
-
-```
-
-```{r SecondHarmonicPlots, fig.cap="Responses at the second harmonic frequencies (1Hz and 0.8Hz), in the same format as Figure 2.", fig.align="center", out.width="40%", echo=FALSE}
-
-knitr::include_graphics(paste0(figdir,'SecondHarmonic.pdf'))
-
-```
-
-At the second harmonic frequencies, the levels of suppression were more uniform across different photoreceptor pathways (see Figure \@ref(fig:SecondHarmonicPlots)).
-In general, suppression estimates were near or above 1 (see lower rows of Table \@ref(tab:paramtable)), with substantial overlap between the posterior distributions (Figure \@ref(fig:SecondHarmonicPlots)e).
-The contrast response functions also looked more uniform, and generally involved less binocular facilitation and more interocular suppression than were seen at the first harmonics.
-The L-M condition now featured the weakest suppressive weight, and the strongest binocular facilitation, which was the opposite pattern seen at the first harmonic.
-
-```{r phaseplots, fig.cap="Pupil phase plots at the first and second harmonic frequencies for the light flux, melanopsin, L-M pathway and the S-cone pathway conditions.
-Panel (a) shows the pupil response at the first harmonic frequency during binocular stimulation.
-Panel (b) shows the pupil response at the second harmonic frequency during binocular stimulation.
-The five data points for each pathway correspond to the five contrast levels displayed.
-In panel (a) the light flux amplitudes have been scaled down by a factor of 10 to enable comparison with the other conditions.", fig.align="center", echo=FALSE}
-
-knitr::include_graphics(paste0(figdir,'phaseplots.pdf'))
-
-```
-
-Finally, we inspected the response phase of our four stimulation conditions, given previous reports that these differ across pathways [@Spitschan2014], and may be in antiphase for melanopsin and S-cone signals.
-Figure \@ref(fig:phaseplots) shows the phase angles for the first (a) and second (b) harmonic frequencies for binocular stimulation (monocular stimulation produced very similar results).
-At the first harmonic, melanopsin and S-cone signals differed in phase by more than 90 degrees, though they were not fully in antiphase.
-The light flux and L-M responses were approximately in antiphase to each other, however this is likely due to our choice to modulate L+M- in the first half-cycle of the sine wave (corresponding to a luminance increase in the light flux condition), and L-M+ in the second half-cycle (corresponding to a luminance decrease in the light flux condition).
-Had we reversed this phase arrangement, we would likely have seen a close phase correspondence between the L-M and light flux conditions (another way to think about this is that L-cone decreases and M-cone increases are processed like luminance increases).
-Phase differences between the light flux, S-cone and melanopsin conditions are likely attributable to different lags in phototransduction at the earliest stage (i.e.
-in the retina).
-At the second harmonic frequency (Figure \@ref(fig:phaseplots)b), the light flux condition was again out of phase with the other three, and was approximately in quadrature phase with the L-M condition, and in antiphase with both the S-cone and melanopsin conditions (which were in phase with each other).
-We note that the marked phase differences between conditions make the possibility that our results are dominated by rod activity relatively unlikely (e.g.
-in the L-M and melanopsin conditions, which have very different phase profiles).
-
-# Discussion
-
-We used binocular pupillometry and silent substitution to measure monocular and binocular responses of the pupils to flickering stimuli when stimulating specific photoreceptor pathways.
-In all four experiments, we were able to record contrast response functions at both the first and the second harmonic frequencies.
-All experiments showed that binocular combination in the autonomic nervous system happens in a non-linear manner, with evidence of different magnitudes of interocular suppression depending on the photoreceptor pathway.
-This pattern of results was confirmed by a computational model, which allowed us to compare the weight of interocular suppression for each pathway.
-We found that at the first harmonic frequency the L-M and melanopsin pathways involved strong suppression, whereas the light flux and S-cone pathways involved weaker suppression.
-Suppression was strong in all four pathways at the second harmonic frequency.
-Finally, the phase of the pupil response revealed different lag times for the different pathways at the first and second harmonic frequencies.
-
-This is the first study to investigate binocular interactions in the melanopsin pathway directly.
-A previous meta-analysis [@Spitschan2019] indicated that there may be a substantial binocular facilitation effect in the circadian pathway, as indexed by melatonin suppression (melatonin is a hormone released by the pineal gland; its production is suppressed by exposure to bright light, particularly when the melanopsin-containing ipRGCs are stimulated).
-In brief, monocular stimulation of the ipRGCs requires up to ten times the signal strength to produce an equivalent effect to binocular stimulation.
-This superadditive effect implies an absence of interocular suppression, and perhaps the presence of either a highly compressive nonlinearity, or an AND-style neural operation.
-Our findings here are very different - we do not see substantial binocular facilitation effects in response to melanopsin modulation, and our data indicate that interocular suppression is very strong.
-Moreover, by measuring the full contrast response function, we can rule out compressive nonlinearities, because the functions accelerate at both the first and second harmonic frequencies.
-The explanation for this difference could be due to different anatomical pathways.
-Binocular combination in the circadian system likely takes place in the suprachiasmatic nucleus, whereas in the pupil constriction circuit the Edinger-Westphal nucleus is the most likely site of binocular integration [@Mathot2018].
-Presumably these anatomical differences, and the practical constraints of the two systems, lead to differences in response.
-
-Our recent psychophysical work [@Baker2024] has looked at binocular interactions in the L-M and S-cone pathways, and compared these to the light flux pathway.
-Using a contrast discrimination paradigm with spatial modulations of light flux and colour, we found equally strong interocular suppression in all three pathways [@Baker2024].
-This is rather different from our pupillometry results here, which demonstrate weaker suppression in the light flux and S-cone pathways than in the L-M pathway (see Figure \@ref(fig:FirstHarmonicPlots)).
-However, the current experiments involve temporal modulations, which are quite distinct from the spatial modulations used in our previous work [@Baker2024].
-Our other recent work [@Segala2023] has shown that temporal luminance modulations involve much weaker interocular suppression in the cortical response than do spatial luminance modulations [@Baker2017].
-These different normalization processes might reflect different priorities for spatial and temporal vision.
-Spatial vision aims to fuse images to provide binocular single vision, and benefits from 'ocularity invariance' [@Baker2007], in which visual appearance is constant when viewed with one eye or two.
-Temporal vision is critical for motion perception, which can involve alternative binocular computations, such as calculating velocity differences between the eyes [@Kaestner2019].
-Of course the present measurements were of pupil size, which may be subject to different anatomical and functional constraints from those in the cortex.
-Future research should aim to extend our current findings to perception using psychophysical approaches.
-
-# Conclusions
-
-We have demonstrated that binocular combination of temporal flickering light in the autonomic nervous system depends on the photoreceptor pathway stimulated.
-We were able to elicit pupil responses by stimulating the periphery of the retina and we were able to record contrast response functions for all photoreceptor pathways.
-While all pathways showed non-linear combination, they varied in how the signals are combined, particularly in the weight of interocular suppression.
-This was strong ($\omega \ge 1$) for L-M and melanopsin signals at the first harmonic, and all pathways at the second harmonic.
-Suppression was weaker ($\omega < 1$) in the light flux pathway (consistent with previous work), and also for S-cone directed modulations.
-
 # Materials and methods
@@
 Our procedures were approved by the Ethics Committee of the Department of Psychology at the University of York (identification number 184).
+Participant recruitment began on 3 March 2023 and concluded on 8 Decemeber 2023.
 
@@
 We used the 10-degree cone fundamentals [@Stockman2000], and estimates of melanopsin absorbance spectra from CIE S 026 (discussed in a previous paper [@Martin2023]) to calculate $\alpha$-opic irradiance.
+
+```{r spectraplots, fig.cap="Summary of the spectral power distributions and alpha-opic irradiances for the background and each condition, as well as averaged pupil diameters and Fourier spectra.
+Panel (a) shows a schematic of the binocular stimulation system for presenting spectrally tuned modulations independently to each eye.
+The VR headset was attached to a clamp stand that the experimenters could use to adjust the height and align the headset with the eyes of the participant.
+The participant's head was supported by a chin rest to keep it in position throughout the experiment.
+Panel (b) shows the outputs of each LED primary at maximum intensity, and panels (c) and (d) show the overall spectral power distributions and the alpha-opic irradiances of the background spectra used for both eyes.
+The subsequent rows show the power differences (e-h), and photoreceptor contrasts (i-l) relative to the background, averaged pupil diameter waveforms (m-p) and Fourier spectra (q-t) for binocular stimulation.
+Column headings indicate the pathway stimulated, and shaded regions in panels m-t indicate bootstrapped 95\\% confidence intervals.", fig.align="center", out.width = '80%', echo=FALSE}
+
+knitr::include_graphics(paste0(figdir,'methodsfigrods.pdf'))
+
+```
 
@@
 
+# Results
+
+Figure \@ref(fig:spectraplots)m-p shows averaged waveforms of pupil diameter in response to binocular stimulation.
+For light flux stimuli (Figure \@ref(fig:spectraplots)m) a strong modulation is apparent at the stimulation frequency (0.5Hz), which is also clear in the Fourier amplitude spectrum (Figure \@ref(fig:spectraplots)q).
+For binocular stimulation of the L-M pathway, S-cone pathway and melanopsin pathway, pupil modulations were less than 10\% of the amplitude of the light flux modulation (note the change in y-axis scale for the Fourier spectra), but still apparent at 0.5Hz in the Fourier spectra (Figure \@ref(fig:spectraplots)n-p).
+We also observed a second harmonic response (at 1Hz) for all conditions, which was weaker than the first harmonic for light flux and melanopsin stimulation, but stronger for L-M and S-cone stimulation.
+The second harmonic is also apparent in the pupil waveforms shown in Figure \@ref(fig:spectraplots)n-p.
+Our main analysis therefore focuses on the amplitude of the pupil modulations at both the first and second harmonic frequencies across different stimulus conditions.
+
+Figure \@ref(fig:FirstHarmonicPlots)a-d shows contrast response functions across stimulation conditions for responses at the first harmonic of the main stimulation frequency (0.5Hz).
+In each plot, the response to monocular stimulation is given by the red circles and typically increases monotonically as a function of stimulus (temporal) contrast.
+Relative to monocular stimulation, binocular stimulation led to higher response amplitudes, indicating a binocular facilitation effect, for the light flux and S-cone conditions (Figure \@ref(fig:FirstHarmonicPlots)a,c), and to some extent for the melanopsin condition (Figure \@ref(fig:FirstHarmonicPlots)d).
+However, the L-M cone condition (Figure \@ref(fig:FirstHarmonicPlots)b) produced a binocular suppression effect, where the response to binocular stimulation was weaker than the response to monocular stimulation (blue squares below red circles).
+These results indicate that the magnitude of binocular facilitation differs across photoreceptor pathway, suggesting heterogeneity in the underlying neural computation.
+
+```{r FirstHarmonicPlots, fig.cap="Contrast response functions for pupil modualations in response to flicker at 0.5Hz (panels a-d), and 0.4Hz (panels f-i), and posterior parameter distributions for the weight of interocular suppression (panel e).
+Within each panel (except panel e), data points are the coherently averaged amplitudes for each condition, and error bars indicate bootstrapped 95\\% confidence intervals.
+Curves show model fits using the maximum a posteriori (MAP) parameter values (see Table 1).
+In panel (e), vertical lines show the MAP estimates, and the thin black curve indicates the prior (note the logarithmic x-axis).", fig.align="center", out.width="40%", echo=FALSE}
+
+knitr::include_graphics(paste0(figdir,'FirstHarmonic.pdf'))
+
+```
+
+In contemporary models of binocular signal combination, the amount of binocular facilitation is determined by the magnitude of interocular suppression, with strong suppression reducing facilitation [@Kingdom2015].
+We can estimate the strength of interocular suppression by measuring how much monocular responses are reduced when a dichoptic 'mask' is shown to the other eye.
+In our paradigm, the two components flickered at different frequencies (0.5 and 0.4Hz) so that their responses remained distinct in the Fourier spectrum [e.g.
+@Busse2009].
+The yellow diamond symbols in Figure \@ref(fig:FirstHarmonicPlots)a-d show the target responses in this condition, and in most cases were weaker than the monocular responses (red circles).
+The strongest dichoptic masking is found in the L-M condition, where we also observed the binocular suppression effect.
+Suppression can also be estimated from the responses at 0.4Hz (Figure \@ref(fig:FirstHarmonicPlots)f-i).
+The reduced amplitude in the binocular cross condition (where the two eyes received different temporal frequencies; purple squares) relative to the 0.4Hz monocular condition (grey circles), and the progressive decline in amplitude of the dichoptic cross response (yellow diamonds) also differ across photoreceptor conditions, showing similar differences to those observed at 0.5Hz.
+
+To estimate the extent of interocular suppression for each photoreceptor pathway, we fitted each data set using a Bayesian hierarchical implementation of a simple binocular combination model [@Meese2006; @Segala2023].
+Our primary objective was to compare posterior distributions of the weight of interocular suppression, which are shown in Figure \@ref(fig:FirstHarmonicPlots)e.
+Consistent with our earlier observations, the strongest suppressive weight corresponds to the L-M and Melanopsin conditions, and the weakest suppression corresponds to the light flux and S-cone conditions, with virtually no overlap between the posterior distributions for weak and strong suppression.
+The model fits were of good quality, as shown by the curves in Figure \@ref(fig:FirstHarmonicPlots)a-d,f-i.
+The fitted model parameters are given in Table \@ref(tab:paramtable).
+
+```{r paramtable, echo=FALSE}
+
+condnames <- c('Light flux 1F','L-M cone 1F','S cone 1F','Melanopsin 1F','Light flux 2F','L-M cone 2F','S cone 2F','Melanopsin 2F')
+zlist <- c(pupilZLum, pupilZLM, pupilZS, pupilZMel, pupilZLum2, pupilZLM2, pupilZS2, pupilZMel2)
+klist <- c(pupilKLum, pupilKLM, pupilKS, pupilKMel, pupilKLum2, pupilKLM2, pupilKS2, pupilKMel2)
+wlist <- c(pupilWLum, pupilWLM, pupilWS, pupilWMel, pupilWLum2, pupilWLM2, pupilWS2, pupilWMel2)
+plist <- c(pupilPLum, pupilPLM, pupilPS, pupilPMel, pupilPLum2, pupilPLM2, pupilPS2, pupilPMel2)
+qlist <- c(pupilQLum, pupilQLM, pupilQS, pupilQMel, pupilQLum2, pupilQLM2, pupilQS2, pupilQMel2)
+Rlist <- c(pupilRmaxLum, pupilRmaxLM, pupilRmaxS, pupilRmaxMel, pupilRmaxLum2, pupilRmaxLM2, pupilRmaxS2, pupilRmaxMel2)
+tabledata <- data.frame(condnames,round(zlist,digits=2),round(klist,digits=5),round(wlist,digits=2),round(plist,digits=2),round(qlist,digits=2),round(Rlist,digits=4))
+
+colnames(tabledata) <- c('Experiment','Z','k','w','p','q','Rmax')
+kable(tabledata, align='lcccccc',booktabs=TRUE,linesep='',caption = 'Summary of maximum a posteriori (MAP) parameter estimates for each data set.') %>%
+kableExtra::kable_styling(latex_options = "HOLD_position") %>% row_spec(4,hline_after=TRUE)
+
+```
+
+At the second harmonic frequencies, the levels of suppression were more uniform across different photoreceptor pathways (see Figure \@ref(fig:SecondHarmonicPlots)).
+In general, suppression estimates were near or above 1 (see lower rows of Table \@ref(tab:paramtable)), with substantial overlap between the posterior distributions (Figure \@ref(fig:SecondHarmonicPlots)e).
+The contrast response functions also looked more uniform, and generally involved less binocular facilitation and more interocular suppression than were seen at the first harmonics.
+The L-M condition now featured the weakest suppressive weight, and the strongest binocular facilitation, which was the opposite pattern seen at the first harmonic.
+
+```{r SecondHarmonicPlots, fig.cap="Responses at the second harmonic frequencies (1Hz and 0.8Hz), in the same format as Figure 2.", fig.align="center", out.width="40%", echo=FALSE}
+
+knitr::include_graphics(paste0(figdir,'SecondHarmonic.pdf'))
+
+```
+
+Finally, we inspected the response phase of our four stimulation conditions, given previous reports that these differ across pathways [@Spitschan2014], and may be in antiphase for melanopsin and S-cone signals.
+Figure \@ref(fig:phaseplots) shows the phase angles for the first (a) and second (b) harmonic frequencies for binocular stimulation (monocular stimulation produced very similar results).
+At the first harmonic, melanopsin and S-cone signals differed in phase by more than 90 degrees, though they were not fully in antiphase.
+The light flux and L-M responses were approximately in antiphase to each other, however this is likely due to our choice to modulate L+M- in the first half-cycle of the sine wave (corresponding to a luminance increase in the light flux condition), and L-M+ in the second half-cycle (corresponding to a luminance decrease in the light flux condition).
+Had we reversed this phase arrangement, we would likely have seen a close phase correspondence between the L-M and light flux conditions (another way to think about this is that L-cone decreases and M-cone increases are processed like luminance increases).
+Phase differences between the light flux, S-cone and melanopsin conditions are likely attributable to different lags in phototransduction at the earliest stage (i.e.
+in the retina).
+At the second harmonic frequency (Figure \@ref(fig:phaseplots)b), the light flux condition was again out of phase with the other three, and was approximately in quadrature phase with the L-M condition, and in antiphase with both the S-cone and melanopsin conditions (which were in phase with each other).
+We note that the marked phase differences between conditions make the possibility that our results are dominated by rod activity relatively unlikely (e.g.
+in the L-M and melanopsin conditions, which have very different phase profiles).
+
+```{r phaseplots, fig.cap="Pupil phase plots at the first and second harmonic frequencies for the light flux, melanopsin, L-M pathway and the S-cone pathway conditions.
+Panel (a) shows the pupil response at the first harmonic frequency during binocular stimulation.
+Panel (b) shows the pupil response at the second harmonic frequency during binocular stimulation.
+The five data points for each pathway correspond to the five contrast levels displayed.
+In panel (a) the light flux amplitudes have been scaled down by a factor of 10 to enable comparison with the other conditions.", fig.align="center", echo=FALSE}
+
+knitr::include_graphics(paste0(figdir,'phaseplots.pdf'))
+
+```
+
+# Discussion
+
+We used binocular pupillometry and silent substitution to measure monocular and binocular responses of the pupils to flickering stimuli when stimulating specific photoreceptor pathways.
+In all four experiments, we were able to record contrast response functions at both the first and the second harmonic frequencies.
+All experiments showed that binocular combination in the autonomic nervous system happens in a non-linear manner, with evidence of different magnitudes of interocular suppression depending on the photoreceptor pathway.
+This pattern of results was confirmed by a computational model, which allowed us to compare the weight of interocular suppression for each pathway.
+We found that at the first harmonic frequency the L-M and melanopsin pathways involved strong suppression, whereas the light flux and S-cone pathways involved weaker suppression.
+Suppression was strong in all four pathways at the second harmonic frequency.
+Finally, the phase of the pupil response revealed different lag times for the different pathways at the first and second harmonic frequencies.
+
+This is the first study to investigate binocular interactions in the melanopsin pathway directly.
+A previous meta-analysis [@Spitschan2019] indicated that there may be a substantial binocular facilitation effect in the circadian pathway, as indexed by melatonin suppression (melatonin is a hormone released by the pineal gland; its production is suppressed by exposure to bright light, particularly when the melanopsin-containing ipRGCs are stimulated).
+In brief, monocular stimulation of the ipRGCs requires up to ten times the signal strength to produce an equivalent effect to binocular stimulation.
+This superadditive effect implies an absence of interocular suppression, and perhaps the presence of either a highly compressive nonlinearity, or an AND-style neural operation.
+Our findings here are very different - we do not see substantial binocular facilitation effects in response to melanopsin modulation, and our data indicate that interocular suppression is very strong.
+Moreover, by measuring the full contrast response function, we can rule out compressive nonlinearities, because the functions accelerate at both the first and second harmonic frequencies.
+The explanation for this difference could be due to different anatomical pathways.
+Binocular combination in the circadian system likely takes place in the suprachiasmatic nucleus, whereas in the pupil constriction circuit the Edinger-Westphal nucleus is the most likely site of binocular integration [@Mathot2018].
+Presumably these anatomical differences, and the practical constraints of the two systems, lead to differences in response.
+
+Our recent psychophysical work [@Baker2024] has looked at binocular interactions in the L-M and S-cone pathways, and compared these to the light flux pathway.
+Using a contrast discrimination paradigm with spatial modulations of light flux and colour, we found equally strong interocular suppression in all three pathways [@Baker2024].
+This is rather different from our pupillometry results here, which demonstrate weaker suppression in the light flux and S-cone pathways than in the L-M pathway (see Figure \@ref(fig:FirstHarmonicPlots)).
+However, the current experiments involve temporal modulations, which are quite distinct from the spatial modulations used in our previous work [@Baker2024].
+Our other recent work [@Segala2023] has shown that temporal luminance modulations involve much weaker interocular suppression in the cortical response than do spatial luminance modulations [@Baker2017].
+These different normalization processes might reflect different priorities for spatial and temporal vision.
+Spatial vision aims to fuse images to provide binocular single vision, and benefits from 'ocularity invariance' [@Baker2007], in which visual appearance is constant when viewed with one eye or two.
+Temporal vision is critical for motion perception, which can involve alternative binocular computations, such as calculating velocity differences between the eyes [@Kaestner2019].
+Of course the present measurements were of pupil size, which may be subject to different anatomical and functional constraints from those in the cortex.
+Future research should aim to extend our current findings to perception using psychophysical approaches.
+
+# Conclusions
+
+We have demonstrated that binocular combination of temporal flickering light in the autonomic nervous system depends on the photoreceptor pathway stimulated.
+We were able to elicit pupil responses by stimulating the periphery of the retina and we were able to record contrast response functions for all photoreceptor pathways.
+While all pathways showed non-linear combination, they varied in how the signals are combined, particularly in the weight of interocular suppression.
+This was strong ($\omega \ge 1$) for L-M and melanopsin signals at the first harmonic, and all pathways at the second harmonic.
+Suppression was weaker ($\omega < 1$) in the light flux pathway (consistent with previous work), and also for S-cone directed modulations.
+
 # References

### 2025-12-18 manuscript.tex
Edits

--- 2025-10-09 manuscript.tex
@@
 
-\hypertarget{author-summary}{%
-\section{Author Summary}\label{author-summary}}
-
-Our pupils constantly adjust in size to control how much light enters the eye: in brighter conditions the pupils will reduce in size, and in dimmer conditions they will increase in size.
-This process, known as the pupillary light response, is usually taken for granted but is crucial for vision, and is controlled automatically by the body's nervous system.
-Different types of light-sensing cells in the retina, the photoreceptor cells, contribute to this response: some respond quickly to changes in light, while others maintain responses over longer periods.
-In our study, we explored how signals from the two eyes are combined to regulate pupil size.
-Using a new type of visual stimulation that allowed us to selectively target specific classes of photoreceptor cells, we found that the way the two eyes' signals are combined depends on which class of photoreceptor cells is involved.
-For example, some photoreceptor classes showed cooperation between the eyes, while others showed competition.
-By revealing these distinct patterns of signal combination, our work provides new insight into how light information is integrated in the pupils.
-
 \hypertarget{introduction}{%
@@
 
-\hypertarget{results}{%
-\section{Results}\label{results}}
+\hypertarget{materials-and-methods}{%
+\section{Materials and methods}\label{materials-and-methods}}
 
-Figure \ref{fig:spectraplots}m-p shows averaged waveforms of pupil diameter in response to binocular stimulation.
-For light flux stimuli (Figure \ref{fig:spectraplots}m) a strong modulation is apparent at the stimulation frequency (0.5Hz), which is also clear in the Fourier amplitude spectrum (Figure \ref{fig:spectraplots}q).
-For binocular stimulation of the L-M pathway, S-cone pathway and melanopsin pathway, pupil modulations were less than 10\% of the amplitude of the light flux modulation (note the change in y-axis scale for the Fourier spectra), but still apparent at 0.5Hz in the Fourier spectra (Figure \ref{fig:spectraplots}n-p).
-We also observed a second harmonic response (at 1Hz) for all conditions, which was weaker than the first harmonic for light flux and melanopsin stimulation, but stronger for L-M and S-cone stimulation.
-The second harmonic is also apparent in the pupil waveforms shown in Figure \ref{fig:spectraplots}n-p.~Our main analysis therefore focuses on the amplitude of the pupil modulations at both the first and second harmonic frequencies across different stimulus conditions.
+\hypertarget{participants}{%
+\subsection{Participants}\label{participants}}
+
+Twenty-four participants were recruited for each of the four experiments for a total of ninety-six adult participants (28 male, 68 female), whose ages ranged from 18 to 41.
+All participants had normal or corrected to normal vision, no known abnormalities of binocular or colour vision, and gave written informed consent.
+Our procedures were approved by the Ethics Committee of the Department of Psychology at the University of York (identification number 184).
+Participant recruitment began on 3 March 2023 and concluded on 8 Decemeber 2023.
+
+\hypertarget{apparatus-stimuli}{%
+\subsection{Apparatus \& stimuli}\label{apparatus-stimuli}}
+
+To present synchronised stimulus modulations independently to each eye, two light engines (SpectraTuneLAB, which are thermally stable across time with active cooling according to the manufacturers: LEDMOTIVE Technologies, LLC, Barcelona, Spain), each with 10 independently addressable LED colour channels, were integrated into a customised binocular viewing system.
+The light engines were operated via a Python interface to their REST API {[}\protect\hyperlink{ref-Martin2022}{23}{]}, which supports synchronous launch and playback of spectral sequences prepared in advance and stored in JSON format.
+A special command was commissioned from LEDMOTIVE to allow two different stimulus files to be launched simultaneously from the two devices.
+The synchronisation of the spectra from the two devices was tested and showed that they were synchronised to within approximately 3ms.
+
+When preparing the spectral sequences, the age of participants was used to account for the yellowing of the lenses.
+We used the silent substitution technique {[}\protect\hyperlink{ref-Estevez1982}{24}{]} to selectively stimulate specific photoreceptor classes.
+Silent substitution exploits the fact that each photoreceptor class has a distinct spectral tuning that overlaps with the others.
+Using a multiprimary system, in which the primaries (i.e.~LEDs) have different spectra, it is possible to target one class of photoreceptors while maintaining the others at a constant activity level, effectively silencing them {[}\protect\hyperlink{ref-Shapiro1996}{25},\protect\hyperlink{ref-Spitschan2018}{26}{]}.
+We calculated silent substitution solutions using the \emph{PySilSub} toolbox {[}\protect\hyperlink{ref-Martin2023}{27}{]}, using linear algebra.
+The outputs of the two light engines (see Figure \ref{fig:spectraplots}b,c) were calibrated using an Ocean Optics Jaz spectroradiometer, which was wavelength-calibrated to an Argon lamp and intensity calibrated using a NIST-traceable light source.
+Each primary was also linearised using a polynomial fit (see Figure \ref{fig:primarylinearity} for details).
+We used the 10-degree cone fundamentals {[}\protect\hyperlink{ref-Stockman2000}{28}{]}, and estimates of melanopsin absorbance spectra from CIE S 026 (discussed in a previous paper {[}\protect\hyperlink{ref-Martin2023}{27}{]}) to calculate \(\alpha\)-opic irradiance.
 
@@
 
-Figure \ref{fig:FirstHarmonicPlots}a-d shows contrast response functions across stimulation conditions for responses at the first harmonic of the main stimulation frequency (0.5Hz).
-In each plot, the response to monocular stimulation is given by the red circles and typically increases monotonically as a function of stimulus (temporal) contrast.
-Relative to monocular stimulation, binocular stimulation led to higher response amplitudes, indicating a binocular facilitation effect, for the light flux and S-cone conditions (Figure \ref{fig:FirstHarmonicPlots}a,c), and to some extent for the melanopsin condition (Figure \ref{fig:FirstHarmonicPlots}d).
-However, the L-M cone condition (Figure \ref{fig:FirstHarmonicPlots}b) produced a binocular suppression effect, where the response to binocular stimulation was weaker than the response to monocular stimulation (blue squares below red circles).
-These results indicate that the magnitude of binocular facilitation differs across photoreceptor pathway, suggesting heterogeneity in the underlying neural computation.
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.4\linewidth]{Figures/FirstHarmonic}
-
-}
-
-\caption{Contrast response functions for pupil modualations in response to flicker at 0.5Hz (panels a-d), and 0.4Hz (panels f-i), and posterior parameter distributions for the weight of interocular suppression (panel e).
-Within each panel (except panel e), data points are the coherently averaged amplitudes for each condition, and error bars indicate bootstrapped 95\% confidence intervals.
-Curves show model fits using the maximum a posteriori (MAP) parameter values (see Table 1).
-In panel (e), vertical lines show the MAP estimates, and the thin black curve indicates the prior (note the logarithmic x-axis).}\label{fig:FirstHarmonicPlots}
-\end{figure}
-
-In contemporary models of binocular signal combination, the amount of binocular facilitation is determined by the magnitude of interocular suppression, with strong suppression reducing facilitation {[}\protect\hyperlink{ref-Kingdom2015}{23}{]}.
-We can estimate the strength of interocular suppression by measuring how much monocular responses are reduced when a dichoptic `mask' is shown to the other eye.
-In our paradigm, the two components flickered at different frequencies (0.5 and 0.4Hz) so that their responses remained distinct in the Fourier spectrum {[}\protect\hyperlink{ref-Busse2009}{24}{]}.
-The yellow diamond symbols in Figure \ref{fig:FirstHarmonicPlots}a-d show the target responses in this condition, and in most cases were weaker than the monocular responses (red circles).
-The strongest dichoptic masking is found in the L-M condition, where we also observed the binocular suppression effect.
-Suppression can also be estimated from the responses at 0.4Hz (Figure \ref{fig:FirstHarmonicPlots}f-i).
-The reduced amplitude in the binocular cross condition (where the two eyes received different temporal frequencies; purple squares) relative to the 0.4Hz monocular condition (grey circles), and the progressive decline in amplitude of the dichoptic cross response (yellow diamonds) also differ across photoreceptor conditions, showing similar differences to those observed at 0.5Hz.
-
-To estimate the extent of interocular suppression for each photoreceptor pathway, we fitted each data set using a Bayesian hierarchical implementation of a simple binocular combination model {[}\protect\hyperlink{ref-Segala2023}{3},\protect\hyperlink{ref-Meese2006}{22}{]}.
-Our primary objective was to compare posterior distributions of the weight of interocular suppression, which are shown in Figure \ref{fig:FirstHarmonicPlots}e.
-Consistent with our earlier observations, the strongest suppressive weight corresponds to the L-M and Melanopsin conditions, and the weakest suppression corresponds to the light flux and S-cone conditions, with virtually no overlap between the posterior distributions for weak and strong suppression.
-The model fits were of good quality, as shown by the curves in Figure \ref{fig:FirstHarmonicPlots}a-d,f-i.
-The fitted model parameters are given in Table \ref{tab:paramtable}.
-
-\begin{table}[H]
-
-\caption{\label{tab:paramtable}Summary of maximum a posteriori (MAP) parameter estimates for each data set.}
-\centering
-\begin{tabular}[t]{lcccccc}
-\toprule
-Experiment & Z & k & w & p & q & Rmax\\
-\midrule
-Light flux 1F & 95.77 & 0.00083 & 0.37 & 1.32 & 1.24 & 0.0905\\
-L-M cone 1F & 49.82 & 0.00109 & 1.71 & 1.50 & 1.21 & 0.0032\\
-S cone 1F & 63.00 & 0.00121 & 0.39 & 1.94 & 1.79 & 0.0042\\
-Melanopsin 1F & 79.61 & 0.00094 & 1.71 & 1.29 & 0.76 & 0.0025\\
-\midrule
-Light flux 2F & 48.81 & 0.00089 & 1.24 & 1.15 & 0.88 & 0.0039\\
-L-M cone 2F & 66.00 & 0.00075 & 0.95 & 1.10 & 0.82 & 0.0050\\
-S cone 2F & 75.94 & 0.00097 & 2.22 & 1.41 & 0.83 & 0.0018\\
-Melanopsin 2F & 67.94 & 0.00101 & 1.37 & 0.90 & 0.49 & 0.0035\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.4\linewidth]{Figures/SecondHarmonic}
-
-}
-
-\caption{Responses at the second harmonic frequencies (1Hz and 0.8Hz), in the same format as Figure 2.}\label{fig:SecondHarmonicPlots}
-\end{figure}
-
-At the second harmonic frequencies, the levels of suppression were more uniform across different photoreceptor pathways (see Figure \ref{fig:SecondHarmonicPlots}).
-In general, suppression estimates were near or above 1 (see lower rows of Table \ref{tab:paramtable}), with substantial overlap between the posterior distributions (Figure \ref{fig:SecondHarmonicPlots}e).
-The contrast response functions also looked more uniform, and generally involved less binocular facilitation and more interocular suppression than were seen at the first harmonics.
-The L-M condition now featured the weakest suppressive weight, and the strongest binocular facilitation, which was the opposite pattern seen at the first harmonic.
-
-\begin{figure}
-
-{\centering \includegraphics{Figures/phaseplots}
-
-}
-
-\caption{Pupil phase plots at the first and second harmonic frequencies for the light flux, melanopsin, L-M pathway and the S-cone pathway conditions.
-Panel (a) shows the pupil response at the first harmonic frequency during binocular stimulation.
-Panel (b) shows the pupil response at the second harmonic frequency during binocular stimulation.
-The five data points for each pathway correspond to the five contrast levels displayed.
-In panel (a) the light flux amplitudes have been scaled down by a factor of 10 to enable comparison with the other conditions.}\label{fig:phaseplots}
-\end{figure}
-
-Finally, we inspected the response phase of our four stimulation conditions, given previous reports that these differ across pathways {[}\protect\hyperlink{ref-Spitschan2014}{7}{]}, and may be in antiphase for melanopsin and S-cone signals.
-Figure \ref{fig:phaseplots} shows the phase angles for the first (a) and second (b) harmonic frequencies for binocular stimulation (monocular stimulation produced very similar results).
-At the first harmonic, melanopsin and S-cone signals differed in phase by more than 90 degrees, though they were not fully in antiphase.
-The light flux and L-M responses were approximately in antiphase to each other, however this is likely due to our choice to modulate L+M- in the first half-cycle of the sine wave (corresponding to a luminance increase in the light flux condition), and L-M+ in the second half-cycle (corresponding to a luminance decrease in the light flux condition).
-Had we reversed this phase arrangement, we would likely have seen a close phase correspondence between the L-M and light flux conditions (another way to think about this is that L-cone decreases and M-cone increases are processed like luminance increases).
-Phase differences between the light flux, S-cone and melanopsin conditions are likely attributable to different lags in phototransduction at the earliest stage (i.e.~in the retina).
-At the second harmonic frequency (Figure \ref{fig:phaseplots}b), the light flux condition was again out of phase with the other three, and was approximately in quadrature phase with the L-M condition, and in antiphase with both the S-cone and melanopsin conditions (which were in phase with each other).
-We note that the marked phase differences between conditions make the possibility that our results are dominated by rod activity relatively unlikely (e.g.~in the L-M and melanopsin conditions, which have very different phase profiles).
-
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
-
-We used binocular pupillometry and silent substitution to measure monocular and binocular responses of the pupils to flickering stimuli when stimulating specific photoreceptor pathways.
-In all four experiments, we were able to record contrast response functions at both the first and the second harmonic frequencies.
-All experiments showed that binocular combination in the autonomic nervous system happens in a non-linear manner, with evidence of different magnitudes of interocular suppression depending on the photoreceptor pathway.
-This pattern of results was confirmed by a computational model, which allowed us to compare the weight of interocular suppression for each pathway.
-We found that at the first harmonic frequency the L-M and melanopsin pathways involved strong suppression, whereas the light flux and S-cone pathways involved weaker suppression.
-Suppression was strong in all four pathways at the second harmonic frequency.
-Finally, the phase of the pupil response revealed different lag times for the different pathways at the first and second harmonic frequencies.
-
-This is the first study to investigate binocular interactions in the melanopsin pathway directly.
-A previous meta-analysis {[}\protect\hyperlink{ref-Spitschan2019}{25}{]} indicated that there may be a substantial binocular facilitation effect in the circadian pathway, as indexed by melatonin suppression (melatonin is a hormone released by the pineal gland; its production is suppressed by exposure to bright light, particularly when the melanopsin-containing ipRGCs are stimulated).
-In brief, monocular stimulation of the ipRGCs requires up to ten times the signal strength to produce an equivalent effect to binocular stimulation.
-This superadditive effect implies an absence of interocular suppression, and perhaps the presence of either a highly compressive nonlinearity, or an AND-style neural operation.
-Our findings here are very different - we do not see substantial binocular facilitation effects in response to melanopsin modulation, and our data indicate that interocular suppression is very strong.
-Moreover, by measuring the full contrast response function, we can rule out compressive nonlinearities, because the functions accelerate at both the first and second harmonic frequencies.
-The explanation for this difference could be due to different anatomical pathways.
-Binocular combination in the circadian system likely takes place in the suprachiasmatic nucleus, whereas in the pupil constriction circuit the Edinger-Westphal nucleus is the most likely site of binocular integration {[}\protect\hyperlink{ref-Mathot2018}{9}{]}.
-Presumably these anatomical differences, and the practical constraints of the two systems, lead to differences in response.
-
-Our recent psychophysical work {[}\protect\hyperlink{ref-Baker2024}{26}{]} has looked at binocular interactions in the L-M and S-cone pathways, and compared these to the light flux pathway.
-Using a contrast discrimination paradigm with spatial modulations of light flux and colour, we found equally strong interocular suppression in all three pathways {[}\protect\hyperlink{ref-Baker2024}{26}{]}.
-This is rather different from our pupillometry results here, which demonstrate weaker suppression in the light flux and S-cone pathways than in the L-M pathway (see Figure \ref{fig:FirstHarmonicPlots}).
-However, the current experiments involve temporal modulations, which are quite distinct from the spatial modulations used in our previous work {[}\protect\hyperlink{ref-Baker2024}{26}{]}.
-Our other recent work {[}\protect\hyperlink{ref-Segala2023}{3}{]} has shown that temporal luminance modulations involve much weaker interocular suppression in the cortical response than do spatial luminance modulations {[}\protect\hyperlink{ref-Baker2017}{27}{]}.
-These different normalization processes might reflect different priorities for spatial and temporal vision.
-Spatial vision aims to fuse images to provide binocular single vision, and benefits from `ocularity invariance' {[}\protect\hyperlink{ref-Baker2007}{20}{]}, in which visual appearance is constant when viewed with one eye or two.
-Temporal vision is critical for motion perception, which can involve alternative binocular computations, such as calculating velocity differences between the eyes {[}\protect\hyperlink{ref-Kaestner2019}{28}{]}.
-Of course the present measurements were of pupil size, which may be subject to different anatomical and functional constraints from those in the cortex.
-Future research should aim to extend our current findings to perception using psychophysical approaches.
-
-\hypertarget{conclusions}{%
-\section{Conclusions}\label{conclusions}}
-
-We have demonstrated that binocular combination of temporal flickering light in the autonomic nervous system depends on the photoreceptor pathway stimulated.
-We were able to elicit pupil responses by stimulating the periphery of the retina and we were able to record contrast response functions for all photoreceptor pathways.
-While all pathways showed non-linear combination, they varied in how the signals are combined, particularly in the weight of interocular suppression.
-This was strong (\(\omega \ge 1\)) for L-M and melanopsin signals at the first harmonic, and all pathways at the second harmonic.
-Suppression was weaker (\(\omega < 1\)) in the light flux pathway (consistent with previous work), and also for S-cone directed modulations.
-
-\hypertarget{materials-and-methods}{%
-\section{Materials and methods}\label{materials-and-methods}}
-
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
-
-Twenty-four participants were recruited for each of the four experiments for a total of ninety-six adult participants (28 male, 68 female), whose ages ranged from 18 to 41.
-All participants had normal or corrected to normal vision, no known abnormalities of binocular or colour vision, and gave written informed consent.
-Our procedures were approved by the Ethics Committee of the Department of Psychology at the University of York (identification number 184).
-
-\hypertarget{apparatus-stimuli}{%
-\subsection{Apparatus \& stimuli}\label{apparatus-stimuli}}
-
-To present synchronised stimulus modulations independently to each eye, two light engines (SpectraTuneLAB, which are thermally stable across time with active cooling according to the manufacturers: LEDMOTIVE Technologies, LLC, Barcelona, Spain), each with 10 independently addressable LED colour channels, were integrated into a customised binocular viewing system.
-The light engines were operated via a Python interface to their REST API {[}\protect\hyperlink{ref-Martin2022}{29}{]}, which supports synchronous launch and playback of spectral sequences prepared in advance and stored in JSON format.
-A special command was commissioned from LEDMOTIVE to allow two different stimulus files to be launched simultaneously from the two devices.
-The synchronisation of the spectra from the two devices was tested and showed that they were synchronised to within approximately 3ms.
-
-When preparing the spectral sequences, the age of participants was used to account for the yellowing of the lenses.
-We used the silent substitution technique {[}\protect\hyperlink{ref-Estevez1982}{30}{]} to selectively stimulate specific photoreceptor classes.
-Silent substitution exploits the fact that each photoreceptor class has a distinct spectral tuning that overlaps with the others.
-Using a multiprimary system, in which the primaries (i.e.~LEDs) have different spectra, it is possible to target one class of photoreceptors while maintaining the others at a constant activity level, effectively silencing them {[}\protect\hyperlink{ref-Shapiro1996}{31},\protect\hyperlink{ref-Spitschan2018}{32}{]}.
-We calculated silent substitution solutions using the \emph{PySilSub} toolbox {[}\protect\hyperlink{ref-Martin2023}{33}{]}, using linear algebra.
-The outputs of the two light engines (see Figure \ref{fig:spectraplots}b,c) were calibrated using an Ocean Optics Jaz spectroradiometer, which was wavelength-calibrated to an Argon lamp and intensity calibrated using a NIST-traceable light source.
-Each primary was also linearised using a polynomial fit (see Figure \ref{fig:primarylinearity} for details).
-We used the 10-degree cone fundamentals {[}\protect\hyperlink{ref-Stockman2000}{34}{]}, and estimates of melanopsin absorbance spectra from CIE S 026 (discussed in a previous paper {[}\protect\hyperlink{ref-Martin2023}{33}{]}) to calculate \(\alpha\)-opic irradiance.
-
 The output from the light engines was directed through liquid light guides (LLG3-8H: Thorlabs Ltd, Cambridgeshire, UK) and diffused onto semi-opaque and highly diffusive white glass discs with a diameter of 50 mm for even illumination (34-473: Edmund Optics, York, UK).
@@
 The diffuser discs were positioned in the objective planes of the lenses of a modified VR headset (SHINECON SC-G01, Dongguan Shinecon Industrial Co.~Ltd., Guangdong, China), which was used by the participants to view the stimuli.
-The stimuli were two discs of flickering light with a diameter of approximately 30 degrees, which were fused together into a cyclopean percept resembling a donut-shaped ring of light, similar to that used in other studies {[}\protect\hyperlink{ref-Barrionuevo2016}{5}--\protect\hyperlink{ref-Spitschan2014}{7},\protect\hyperlink{ref-Spitschan2015}{35},\protect\hyperlink{ref-Zele2018}{36}{]}.
+The stimuli were two discs of flickering light with a diameter of approximately 30 degrees, which were fused together into a cyclopean percept resembling a donut-shaped ring of light, similar to that used in other studies {[}\protect\hyperlink{ref-Barrionuevo2016}{5}--\protect\hyperlink{ref-Spitschan2014}{7},\protect\hyperlink{ref-Spitschan2015}{29},\protect\hyperlink{ref-Zele2018}{30}{]}.
 The VR headset modifications allowed for small adjustments to account for individual differences in interpupillary distance and focal length.
@@
 A schematic of the stimulation system is shown in Figure \ref{fig:spectraplots}a.
-Pupillometry data were collected using a binocular Pupil Core eye-tracker headset (Pupil Labs GmbH, Berlin, Germany {[}\protect\hyperlink{ref-Kassner2014}{37}{]}) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
+Pupillometry data were collected using a binocular Pupil Core eye-tracker headset (Pupil Labs GmbH, Berlin, Germany {[}\protect\hyperlink{ref-Kassner2014}{31}{]}) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
 
@@
 For all experiments, we therefore used a primary flicker frequency of 0.5Hz, as previous literature showed that this was slow enough to elicit a pupil response from all photoreceptor classes {[}\protect\hyperlink{ref-Spitschan2014}{7}{]}.
-We also focussed on only recording pupillometry data as this frequency would be too slow to elicit steady-state EEG responses {[}\protect\hyperlink{ref-Norcia2015}{38}{]}.
+We also focussed on only recording pupillometry data as this frequency would be too slow to elicit steady-state EEG responses {[}\protect\hyperlink{ref-Norcia2015}{32}{]}.
 
@@
 
-Silent substitution stimuli were prepared and calibrated for each participant with custom Python software {[}\protect\hyperlink{ref-Martin2023}{33}{]} and Python scripts.
-Estimates of photoreceptor spectral sensitivities for each participant were constructed from the known photopigment absorbance spectra {[}\protect\hyperlink{ref-Stockman2000}{34}{]}, taking account of the peak axial density of the respective photopigments, as well as lens {[}\protect\hyperlink{ref-Stockman2000}{34},\protect\hyperlink{ref-Pokorny1987}{39},\protect\hyperlink{ref-Stockman1999}{40}{]} and macular pigment density {[}\protect\hyperlink{ref-Stockman1999}{40},\protect\hyperlink{ref-Bone1988}{41}{]}, in accordance with the field size and age-dependant CIEPO06 observer model {[}\protect\hyperlink{ref-CIE2006}{42}{]}.
-The melanopic and rhodopic action spectra of the 32-year-old standard observer were taken from CIE S 026 {[}\protect\hyperlink{ref-CIE2018}{43}{]} and then adjusted for age-related lens transmittance with a spectral correction function, in line with the standard.
-Macular pigment correction was not applied to the rhodopic and melanopic action spectra because rods are not present at the fovea and ipRGCs sit above the retinal pigment layer {[}\protect\hyperlink{ref-Trieschmann2007}{44}{]}.
+Silent substitution stimuli were prepared and calibrated for each participant with custom Python software {[}\protect\hyperlink{ref-Martin2023}{27}{]} and Python scripts.
+Estimates of photoreceptor spectral sensitivities for each participant were constructed from the known photopigment absorbance spectra {[}\protect\hyperlink{ref-Stockman2000}{28}{]}, taking account of the peak axial density of the respective photopigments, as well as lens {[}\protect\hyperlink{ref-Stockman2000}{28},\protect\hyperlink{ref-Pokorny1987}{33},\protect\hyperlink{ref-Stockman1999}{34}{]} and macular pigment density {[}\protect\hyperlink{ref-Stockman1999}{34},\protect\hyperlink{ref-Bone1988}{35}{]}, in accordance with the field size and age-dependant CIEPO06 observer model {[}\protect\hyperlink{ref-CIE2006}{36}{]}.
+The melanopic and rhodopic action spectra of the 32-year-old standard observer were taken from CIE S 026 {[}\protect\hyperlink{ref-CIE2018}{37}{]} and then adjusted for age-related lens transmittance with a spectral correction function, in line with the standard.
+Macular pigment correction was not applied to the rhodopic and melanopic action spectra because rods are not present at the fovea and ipRGCs sit above the retinal pigment layer {[}\protect\hyperlink{ref-Trieschmann2007}{38}{]}.
 
@@
 Splatter on nominally silenced photoreceptors was very small (see Figure \ref{fig:spectraplots}j-l), well below the levels that would be expected to generate measurable pupil modulations, although we can observe that the rods may not be saturated in the L-M and melanopsin-directed stimuli (Figure \ref{fig:spectraplots}j and \ref{fig:spectraplots}l) and could intrude in these two experiments.
-We also estimated activation of penumbral L and M cones {[}\protect\hyperlink{ref-Barrionuevo2016}{5},\protect\hyperlink{ref-Spitschan2015}{35},\protect\hyperlink{ref-Zele2019}{45}{]}, which was minimal (\(\le 1.5%
+We also estimated activation of penumbral L and M cones {[}\protect\hyperlink{ref-Barrionuevo2016}{5},\protect\hyperlink{ref-Spitschan2015}{29},\protect\hyperlink{ref-Zele2019}{39}{]}, which was minimal (\(\le 1.5%
 \) contrast; less than splatter on the open-field cones) for melanopsin-directed stimuli.
-We note that the temporal frequency of our modulation (0.5Hz) is well below the range where penumbral cone activation can elicit visible percepts, and that such percepts fade after around 1 second {[}\protect\hyperlink{ref-Spitschan2015}{35}{]}, and do not typically affect pupil responses {[}\protect\hyperlink{ref-Spitschan2014}{7}{]}.
+We note that the temporal frequency of our modulation (0.5Hz) is well below the range where penumbral cone activation can elicit visible percepts, and that such percepts fade after around 1 second {[}\protect\hyperlink{ref-Spitschan2015}{29}{]}, and do not typically affect pupil responses {[}\protect\hyperlink{ref-Spitschan2014}{7}{]}.
 
@@
 Pupil responses to binocular temporal contrast modulations were examined in a factorial design that combined six ocular conditions and five temporal contrast levels: 6, 12, 24, 48 and 96\% of the available dynamic range.
-This design, similar to that used in our previous studies {[}\protect\hyperlink{ref-Segala2023}{3},\protect\hyperlink{ref-Baker2017}{27},\protect\hyperlink{ref-Baker2020}{46}{]}, was applied in four separate experiments, each with a different mode of photoreceptor stimulation.
+This design, similar to that used in our previous studies {[}\protect\hyperlink{ref-Segala2023}{3},\protect\hyperlink{ref-Baker2017}{40},\protect\hyperlink{ref-Baker2020}{41}{]}, was applied in four separate experiments, each with a different mode of photoreceptor stimulation.
 In the first three conditions, the discs flickered at 0.5 Hz, in either a monocular, binocular or dichoptic arrangement.
@@
 Using a trackball, participants adjusted the angle in cone space to find their subjective isoluminant point, which resulted in changing the flickering intensity of the stimulus until the amplitude of the flicker appeared to be minimised.
-The result was used to modify the requested contrasts during stimulus preparation so as to account for individual differences affecting perceived illuminance, principally the L:M cone ratio {[}\protect\hyperlink{ref-Carroll2002}{47},\protect\hyperlink{ref-Hofer2005}{48}{]}.
+The result was used to modify the requested contrasts during stimulus preparation so as to account for individual differences affecting perceived illuminance, principally the L:M cone ratio {[}\protect\hyperlink{ref-Carroll2002}{42},\protect\hyperlink{ref-Hofer2005}{43}{]}.
 
@@
 The pupillometry data were analysed using the same method we used in our previous study {[}\protect\hyperlink{ref-Segala2023}{3}{]}.
-The data were converted from mp4 videos to a csv text file using the Pupil Player software {[}\protect\hyperlink{ref-Kassner2014}{37}{]}, which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
+The data were converted from mp4 videos to a csv text file using the Pupil Player software {[}\protect\hyperlink{ref-Kassner2014}{31}{]}, which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
 The individual data were then loaded into R for analysis, where a ten-second waveform for each trial in each eye was extracted (excluding the first two seconds after stimulus onset).
@@
 Finally, data were averaged across all participants to obtain the group results.
-We used coherent averaging and at each stage we excluded data points with a Mahalanobis distance exceeding \(D\) = 3 from the complex-valued mean {[}\protect\hyperlink{ref-Baker2021}{49}{]}.
+We used coherent averaging and at each stage we excluded data points with a Mahalanobis distance exceeding \(D\) = 3 from the complex-valued mean {[}\protect\hyperlink{ref-Baker2021}{44}{]}.
 For monocular stimulation, we confirmed that the consensual response was equivalent to the response in the stimulated eye.
@@
 
-The models were fit using a hierarchical Bayesian framework implemented in Stan {[}\protect\hyperlink{ref-Carpenter2017}{50}{]}.
+The models were fit using a hierarchical Bayesian framework implemented in Stan {[}\protect\hyperlink{ref-Carpenter2017}{45}{]}.
 The data for each photoreceptor type and response frequency was fit separately, for a total of 8 model fits.
@@
 We calculated over \ensuremath{10^{6}} posterior samples, and retained 10\% for plotting.
+
+\hypertarget{results}{%
+\section{Results}\label{results}}
+
+Figure \ref{fig:spectraplots}m-p shows averaged waveforms of pupil diameter in response to binocular stimulation.
+For light flux stimuli (Figure \ref{fig:spectraplots}m) a strong modulation is apparent at the stimulation frequency (0.5Hz), which is also clear in the Fourier amplitude spectrum (Figure \ref{fig:spectraplots}q).
+For binocular stimulation of the L-M pathway, S-cone pathway and melanopsin pathway, pupil modulations were less than 10\% of the amplitude of the light flux modulation (note the change in y-axis scale for the Fourier spectra), but still apparent at 0.5Hz in the Fourier spectra (Figure \ref{fig:spectraplots}n-p).
+We also observed a second harmonic response (at 1Hz) for all conditions, which was weaker than the first harmonic for light flux and melanopsin stimulation, but stronger for L-M and S-cone stimulation.
+The second harmonic is also apparent in the pupil waveforms shown in Figure \ref{fig:spectraplots}n-p.~Our main analysis therefore focuses on the amplitude of the pupil modulations at both the first and second harmonic frequencies across different stimulus conditions.
+
+Figure \ref{fig:FirstHarmonicPlots}a-d shows contrast response functions across stimulation conditions for responses at the first harmonic of the main stimulation frequency (0.5Hz).
+In each plot, the response to monocular stimulation is given by the red circles and typically increases monotonically as a function of stimulus (temporal) contrast.
+Relative to monocular stimulation, binocular stimulation led to higher response amplitudes, indicating a binocular facilitation effect, for the light flux and S-cone conditions (Figure \ref{fig:FirstHarmonicPlots}a,c), and to some extent for the melanopsin condition (Figure \ref{fig:FirstHarmonicPlots}d).
+However, the L-M cone condition (Figure \ref{fig:FirstHarmonicPlots}b) produced a binocular suppression effect, where the response to binocular stimulation was weaker than the response to monocular stimulation (blue squares below red circles).
+These results indicate that the magnitude of binocular facilitation differs across photoreceptor pathway, suggesting heterogeneity in the underlying neural computation.
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.4\linewidth]{Figures/FirstHarmonic}
+
+}
+
+\caption{Contrast response functions for pupil modualations in response to flicker at 0.5Hz (panels a-d), and 0.4Hz (panels f-i), and posterior parameter distributions for the weight of interocular suppression (panel e).
+Within each panel (except panel e), data points are the coherently averaged amplitudes for each condition, and error bars indicate bootstrapped 95\% confidence intervals.
+Curves show model fits using the maximum a posteriori (MAP) parameter values (see Table 1).
+In panel (e), vertical lines show the MAP estimates, and the thin black curve indicates the prior (note the logarithmic x-axis).}\label{fig:FirstHarmonicPlots}
+\end{figure}
+
+In contemporary models of binocular signal combination, the amount of binocular facilitation is determined by the magnitude of interocular suppression, with strong suppression reducing facilitation {[}\protect\hyperlink{ref-Kingdom2015}{46}{]}.
+We can estimate the strength of interocular suppression by measuring how much monocular responses are reduced when a dichoptic `mask' is shown to the other eye.
+In our paradigm, the two components flickered at different frequencies (0.5 and 0.4Hz) so that their responses remained distinct in the Fourier spectrum {[}\protect\hyperlink{ref-Busse2009}{47}{]}.
+The yellow diamond symbols in Figure \ref{fig:FirstHarmonicPlots}a-d show the target responses in this condition, and in most cases were weaker than the monocular responses (red circles).
+The strongest dichoptic masking is found in the L-M condition, where we also observed the binocular suppression effect.
+Suppression can also be estimated from the responses at 0.4Hz (Figure \ref{fig:FirstHarmonicPlots}f-i).
+The reduced amplitude in the binocular cross condition (where the two eyes received different temporal frequencies; purple squares) relative to the 0.4Hz monocular condition (grey circles), and the progressive decline in amplitude of the dichoptic cross response (yellow diamonds) also differ across photoreceptor conditions, showing similar differences to those observed at 0.5Hz.
+
+To estimate the extent of interocular suppression for each photoreceptor pathway, we fitted each data set using a Bayesian hierarchical implementation of a simple binocular combination model {[}\protect\hyperlink{ref-Segala2023}{3},\protect\hyperlink{ref-Meese2006}{22}{]}.
+Our primary objective was to compare posterior distributions of the weight of interocular suppression, which are shown in Figure \ref{fig:FirstHarmonicPlots}e.
+Consistent with our earlier observations, the strongest suppressive weight corresponds to the L-M and Melanopsin conditions, and the weakest suppression corresponds to the light flux and S-cone conditions, with virtually no overlap between the posterior distributions for weak and strong suppression.
+The model fits were of good quality, as shown by the curves in Figure \ref{fig:FirstHarmonicPlots}a-d,f-i.
+The fitted model parameters are given in Table \ref{tab:paramtable}.
+
+\begin{table}[H]
+
+\caption{\label{tab:paramtable}Summary of maximum a posteriori (MAP) parameter estimates for each data set.}
+\centering
+\begin{tabular}[t]{lcccccc}
+\toprule
+Experiment & Z & k & w & p & q & Rmax\\
+\midrule
+Light flux 1F & 95.77 & 0.00083 & 0.37 & 1.32 & 1.24 & 0.0905\\
+L-M cone 1F & 49.82 & 0.00109 & 1.71 & 1.50 & 1.21 & 0.0032\\
+S cone 1F & 63.00 & 0.00121 & 0.39 & 1.94 & 1.79 & 0.0042\\
+Melanopsin 1F & 79.61 & 0.00094 & 1.71 & 1.29 & 0.76 & 0.0025\\
+\midrule
+Light flux 2F & 48.81 & 0.00089 & 1.24 & 1.15 & 0.88 & 0.0039\\
+L-M cone 2F & 66.00 & 0.00075 & 0.95 & 1.10 & 0.82 & 0.0050\\
+S cone 2F & 75.94 & 0.00097 & 2.22 & 1.41 & 0.83 & 0.0018\\
+Melanopsin 2F & 67.94 & 0.00101 & 1.37 & 0.90 & 0.49 & 0.0035\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+At the second harmonic frequencies, the levels of suppression were more uniform across different photoreceptor pathways (see Figure \ref{fig:SecondHarmonicPlots}).
+In general, suppression estimates were near or above 1 (see lower rows of Table \ref{tab:paramtable}), with substantial overlap between the posterior distributions (Figure \ref{fig:SecondHarmonicPlots}e).
+The contrast response functions also looked more uniform, and generally involved less binocular facilitation and more interocular suppression than were seen at the first harmonics.
+The L-M condition now featured the weakest suppressive weight, and the strongest binocular facilitation, which was the opposite pattern seen at the first harmonic.
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.4\linewidth]{Figures/SecondHarmonic}
+
+}
+
+\caption{Responses at the second harmonic frequencies (1Hz and 0.8Hz), in the same format as Figure 2.}\label{fig:SecondHarmonicPlots}
+\end{figure}
+
+Finally, we inspected the response phase of our four stimulation conditions, given previous reports that these differ across pathways {[}\protect\hyperlink{ref-Spitschan2014}{7}{]}, and may be in antiphase for melanopsin and S-cone signals.
+Figure \ref{fig:phaseplots} shows the phase angles for the first (a) and second (b) harmonic frequencies for binocular stimulation (monocular stimulation produced very similar results).
+At the first harmonic, melanopsin and S-cone signals differed in phase by more than 90 degrees, though they were not fully in antiphase.
+The light flux and L-M responses were approximately in antiphase to each other, however this is likely due to our choice to modulate L+M- in the first half-cycle of the sine wave (corresponding to a luminance increase in the light flux condition), and L-M+ in the second half-cycle (corresponding to a luminance decrease in the light flux condition).
+Had we reversed this phase arrangement, we would likely have seen a close phase correspondence between the L-M and light flux conditions (another way to think about this is that L-cone decreases and M-cone increases are processed like luminance increases).
+Phase differences between the light flux, S-cone and melanopsin conditions are likely attributable to different lags in phototransduction at the earliest stage (i.e.~in the retina).
+At the second harmonic frequency (Figure \ref{fig:phaseplots}b), the light flux condition was again out of phase with the other three, and was approximately in quadrature phase with the L-M condition, and in antiphase with both the S-cone and melanopsin conditions (which were in phase with each other).
+We note that the marked phase differences between conditions make the possibility that our results are dominated by rod activity relatively unlikely (e.g.~in the L-M and melanopsin conditions, which have very different phase profiles).
+
+\begin{figure}
+
+{\centering \includegraphics{Figures/phaseplots}
+
+}
+
+\caption{Pupil phase plots at the first and second harmonic frequencies for the light flux, melanopsin, L-M pathway and the S-cone pathway conditions.
+Panel (a) shows the pupil response at the first harmonic frequency during binocular stimulation.
+Panel (b) shows the pupil response at the second harmonic frequency during binocular stimulation.
+The five data points for each pathway correspond to the five contrast levels displayed.
+In panel (a) the light flux amplitudes have been scaled down by a factor of 10 to enable comparison with the other conditions.}\label{fig:phaseplots}
+\end{figure}
+
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
+
+We used binocular pupillometry and silent substitution to measure monocular and binocular responses of the pupils to flickering stimuli when stimulating specific photoreceptor pathways.
+In all four experiments, we were able to record contrast response functions at both the first and the second harmonic frequencies.
+All experiments showed that binocular combination in the autonomic nervous system happens in a non-linear manner, with evidence of different magnitudes of interocular suppression depending on the photoreceptor pathway.
+This pattern of results was confirmed by a computational model, which allowed us to compare the weight of interocular suppression for each pathway.
+We found that at the first harmonic frequency the L-M and melanopsin pathways involved strong suppression, whereas the light flux and S-cone pathways involved weaker suppression.
+Suppression was strong in all four pathways at the second harmonic frequency.
+Finally, the phase of the pupil response revealed different lag times for the different pathways at the first and second harmonic frequencies.
+
+This is the first study to investigate binocular interactions in the melanopsin pathway directly.
+A previous meta-analysis {[}\protect\hyperlink{ref-Spitschan2019}{48}{]} indicated that there may be a substantial binocular facilitation effect in the circadian pathway, as indexed by melatonin suppression (melatonin is a hormone released by the pineal gland; its production is suppressed by exposure to bright light, particularly when the melanopsin-containing ipRGCs are stimulated).
+In brief, monocular stimulation of the ipRGCs requires up to ten times the signal strength to produce an equivalent effect to binocular stimulation.
+This superadditive effect implies an absence of interocular suppression, and perhaps the presence of either a highly compressive nonlinearity, or an AND-style neural operation.
+Our findings here are very different - we do not see substantial binocular facilitation effects in response to melanopsin modulation, and our data indicate that interocular suppression is very strong.
+Moreover, by measuring the full contrast response function, we can rule out compressive nonlinearities, because the functions accelerate at both the first and second harmonic frequencies.
+The explanation for this difference could be due to different anatomical pathways.
+Binocular combination in the circadian system likely takes place in the suprachiasmatic nucleus, whereas in the pupil constriction circuit the Edinger-Westphal nucleus is the most likely site of binocular integration {[}\protect\hyperlink{ref-Mathot2018}{9}{]}.
+Presumably these anatomical differences, and the practical constraints of the two systems, lead to differences in response.
+
+Our recent psychophysical work {[}\protect\hyperlink{ref-Baker2024}{49}{]} has looked at binocular interactions in the L-M and S-cone pathways, and compared these to the light flux pathway.
+Using a contrast discrimination paradigm with spatial modulations of light flux and colour, we found equally strong interocular suppression in all three pathways {[}\protect\hyperlink{ref-Baker2024}{49}{]}.
+This is rather different from our pupillometry results here, which demonstrate weaker suppression in the light flux and S-cone pathways than in the L-M pathway (see Figure \ref{fig:FirstHarmonicPlots}).
+However, the current experiments involve temporal modulations, which are quite distinct from the spatial modulations used in our previous work {[}\protect\hyperlink{ref-Baker2024}{49}{]}.
+Our other recent work {[}\protect\hyperlink{ref-Segala2023}{3}{]} has shown that temporal luminance modulations involve much weaker interocular suppression in the cortical response than do spatial luminance modulations {[}\protect\hyperlink{ref-Baker2017}{40}{]}.
+These different normalization processes might reflect different priorities for spatial and temporal vision.
+Spatial vision aims to fuse images to provide binocular single vision, and benefits from `ocularity invariance' {[}\protect\hyperlink{ref-Baker2007}{20}{]}, in which visual appearance is constant when viewed with one eye or two.
+Temporal vision is critical for motion perception, which can involve alternative binocular computations, such as calculating velocity differences between the eyes {[}\protect\hyperlink{ref-Kaestner2019}{50}{]}.
+Of course the present measurements were of pupil size, which may be subject to different anatomical and functional constraints from those in the cortex.
+Future research should aim to extend our current findings to perception using psychophysical approaches.
+
+\hypertarget{conclusions}{%
+\section{Conclusions}\label{conclusions}}
+
+We have demonstrated that binocular combination of temporal flickering light in the autonomic nervous system depends on the photoreceptor pathway stimulated.
+We were able to elicit pupil responses by stimulating the periphery of the retina and we were able to record contrast response functions for all photoreceptor pathways.
+While all pathways showed non-linear combination, they varied in how the signals are combined, particularly in the weight of interocular suppression.
+This was strong (\(\omega \ge 1\)) for L-M and melanopsin signals at the first harmonic, and all pathways at the second harmonic.
+Suppression was weaker (\(\omega < 1\)) in the light flux pathway (consistent with previous work), and also for S-cone directed modulations.
 
@@
 
+\leavevmode\hypertarget{ref-Martin2022}{}%
+23.
+Martin JT, Pinto J, Bulte D, Spitschan M.
+PyPlr: A versatile, integrated system of hardware and software for researching the human pupillary light reflex.
+Behavior Research Methods.
+2022;54: 2720--2739.
+doi:\href{https://doi.org/10.3758/s13428-021-01759-3}{10.3758/s13428-021-01759-3}
+
+\leavevmode\hypertarget{ref-Estevez1982}{}%
+24.
+Estévez O, Spekreijse H.
+The "silent substitution" method in visual research.
+Vision Research.
+1982;22: 681--691.
+doi:\href{https://doi.org/10.1016/0042-6989(82)90104-3}{10.1016/0042-6989(82)90104-3}
+
+\leavevmode\hypertarget{ref-Shapiro1996}{}%
+25.
+Shapiro AG, Pokorny J, Smith VC.
+Conerod receptor spaces with illustrations that use CRT phosphor and light-emitting-diode spectra.
+Journal of the Optical Society of America A.
+1996;13: 2319.
+doi:\href{https://doi.org/10.1364/josaa.13.002319}{10.1364/josaa.13.002319}
+
+\leavevmode\hypertarget{ref-Spitschan2018}{}%
+26.
+Spitschan M, Woelders T.
+The Method of Silent Substitution for Examining Melanopsin Contributions to Pupil Control.
+Frontiers in Neurology.
+2018;9.
+doi:\href{https://doi.org/10.3389/fneur.2018.00941}{10.3389/fneur.2018.00941}
+
+\leavevmode\hypertarget{ref-Martin2023}{}%
+27.
+Martin JT, Boynton GM, Baker DH, Wade AR, Spitschan M.
+PySilSub: An open-source python toolbox for implementing the method of silent substitution in vision and nonvisual photoreception research.
+Journal of Vision.
+2023;23: 10.
+doi:\href{https://doi.org/10.1167/jov.23.7.10}{10.1167/jov.23.7.10}
+
+\leavevmode\hypertarget{ref-Stockman2000}{}%
+28.
+Stockman A, Sharpe LT.
+The spectral sensitivities of the middle- and long-wavelength-sensitive cones derived from measurements in observers of known genotype.
+Vision Res.
+2000;40: 1711--37.
+doi:\href{https://doi.org/10.1016/s0042-6989(00)00021-3}{10.1016/s0042-6989(00)00021-3}
+
+\leavevmode\hypertarget{ref-Spitschan2015}{}%
+29.
+Spitschan M, Aguirre GK, Brainard DH.
+Selective stimulation of penumbral cones reveals perception in the shadow of retinal blood vessels.
+PLoS One.
+2015;10: e0124328.
+doi:\href{https://doi.org/10.1371/journal.pone.0124328}{10.1371/journal.pone.0124328}
+
+\leavevmode\hypertarget{ref-Zele2018}{}%
+30.
+Zele AJ, Feigl B, Adhikari P, Maynard ML, Cao D.
+Melanopsin photoreception contributes to human visual detection, temporal and colour processing.
+Scientific Reports.
+2018;8.
+doi:\href{https://doi.org/10.1038/s41598-018-22197-w}{10.1038/s41598-018-22197-w}
+
+\leavevmode\hypertarget{ref-Kassner2014}{}%
+31.
+Kassner M, Patera W, Bulling A.
+Pupil: An open source platform for pervasive eye tracking and mobile gaze-based interaction.
+Proceedings of the 2014 ACM international joint conference on pervasive and ubiquitous computing: Adjunct publication.
+ACM; 2014.
+doi:\href{https://doi.org/10.1145/2638728.2641695}{10.1145/2638728.2641695}
+
+\leavevmode\hypertarget{ref-Norcia2015}{}%
+32.
+Norcia AM, Appelbaum LG, Ales JM, Cottereau BR, Rossion B.
+The steady-state visual evoked potential in vision research: A review.
+Journal of Vision.
+2015;15(6): 4.
+doi:\href{https://doi.org/10.1167/15.6.4}{10.1167/15.6.4}
+
+\leavevmode\hypertarget{ref-Pokorny1987}{}%
+33. Pokorny J, Smith VC, Lutze M. Aging of the human lens. Applied Optics. 1987;26: 1437. doi:\href{https://doi.org/10.1364/ao.26.001437}{10.1364/ao.26.001437}
+
+\leavevmode\hypertarget{ref-Stockman1999}{}%
+34.
+Stockman A, Sharpe LT, Fach C.
+The spectral sensitivity of the human short-wavelength sensitive cones derived from thresholds and color matches.
+Vision Research.
+1999;39: 2901--2927.
+doi:\href{https://doi.org/https://doi.org/10.1016/S0042-6989(98)00225-9}{https://doi.org/10.1016/S0042-6989(98)00225-9}
+
+\leavevmode\hypertarget{ref-Bone1988}{}%
+35. Bone RA, Landrum JT, Fernandez L, Tarsis SL. Analysis of the macular pigment by HPLC: Retinal distribution and age study. Investigative Ophthalmology \& Visual Science. 1988;29: 843--849.
+
+\leavevmode\hypertarget{ref-CIE2006}{}%
+36. CIE. Fundamental chromaticity diagram with physiological axes. CIE Central Bureau; 2006. Available: \url{https://cie.co.at/publications/fundamental-chromaticity-diagram-physiological-axes-part-1}
+
+\leavevmode\hypertarget{ref-CIE2018}{}%
+37. CIE. CIE system for metrology of optical radiation for ipRGC-influenced responses to light. CIE Central Bureau; 2018. doi:\href{https://doi.org/10.25039/S026.2018}{10.25039/S026.2018}
+
+\leavevmode\hypertarget{ref-Trieschmann2007}{}%
+38.
+Trieschmann M, Kuijk FJGM van, Alexander R, Hermans P, Luthert P, Bird AC, et al.
+Macular pigment in the human retina: Histological evaluation of localization and distribution.
+Eye.
+2007;22: 132--137.
+doi:\href{https://doi.org/10.1038/sj.eye.6702780}{10.1038/sj.eye.6702780}
+
+\leavevmode\hypertarget{ref-Zele2019}{}%
+39.
+Zele AJ, Adhikari P, Cao D, Feigl B.
+Melanopsin driven enhancement of cone-mediated visual processing.
+Vision Res.
+2019;160: 72--81.
+doi:\href{https://doi.org/10.1016/j.visres.2019.04.009}{10.1016/j.visres.2019.04.009}
+
+\leavevmode\hypertarget{ref-Baker2017}{}%
+40.
+Baker DH, Wade AR.
+Evidence for an optimal algorithm underlying signal combination in human visual cortex.
+Cereb Cortex.
+2017;27: 254--264.
+doi:\href{https://doi.org/10.1093/cercor/bhw395}{10.1093/cercor/bhw395}
+
+\leavevmode\hypertarget{ref-Baker2020}{}%
+41.
+Baker DH, Vilidaite G, McClarnon E, Valkova E, Bruno A, Millman RE.
+Binaural summation of amplitude modulation involves weak interaural suppression.
+Sci Rep.
+2020;10: 3560.
+doi:\href{https://doi.org/10.1038/s41598-020-60602-5}{10.1038/s41598-020-60602-5}
+
+\leavevmode\hypertarget{ref-Carroll2002}{}%
+42. Carroll J, Neitz J, Neitz M. Estimates of L:M cone ratio from ERG flicker photometry and genetics. Journal of Vision. 2002;2: 1. doi:\href{https://doi.org/10.1167/2.8.1}{10.1167/2.8.1}
+
+\leavevmode\hypertarget{ref-Hofer2005}{}%
+43.
+Hofer H, Carroll J, Neitz J, Neitz M, Williams DR.
+Organization of the human trichromatic cone mosaic.
+The Journal of Neuroscience.
+2005;25: 9669--9679.
+doi:\href{https://doi.org/10.1523/jneurosci.2414-05.2005}{10.1523/jneurosci.2414-05.2005}
+
+\leavevmode\hypertarget{ref-Baker2021}{}%
+44. Baker DH. Statistical analysis of periodic data in neuroscience. Neurons, Behavior, Data analysis, and Theory. 2021;5. doi:\href{https://doi.org/10.51628/001c.27680}{10.51628/001c.27680}
+
+\leavevmode\hypertarget{ref-Carpenter2017}{}%
+45.
+Carpenter B, Gelman A, Hoffman MD, Lee D, Goodrich B, Betancourt M, et al.
+Stan: A probabilistic programming language.
+J Stat Softw.
+2017;76.
+doi:\href{https://doi.org/10.18637/jss.v076.i01}{10.18637/jss.v076.i01}
+
 \leavevmode\hypertarget{ref-Kingdom2015}{}%
-23.
+46.
 Kingdom FAA, Libenson L.
@@
 \leavevmode\hypertarget{ref-Busse2009}{}%
-24.
+47.
 Busse L, Wade AR, Carandini M.
@@
 \leavevmode\hypertarget{ref-Spitschan2019}{}%
-25. Spitschan M, Cajochen C. Binocular facilitation in light-mediated melatonin suppression? J Pineal Res. 2019;67: e12602. doi:\href{https://doi.org/10.1111/jpi.12602}{10.1111/jpi.12602}
+48. Spitschan M, Cajochen C. Binocular facilitation in light-mediated melatonin suppression? J Pineal Res. 2019;67: e12602. doi:\href{https://doi.org/10.1111/jpi.12602}{10.1111/jpi.12602}
 
 \leavevmode\hypertarget{ref-Baker2024}{}%
-26.
+49.
 Baker DH, Hansford KJ, Segala FG, Morsi AY, Huxley RJ, Martin JT, et al.
@@
 
-\leavevmode\hypertarget{ref-Baker2017}{}%
-27.
-Baker DH, Wade AR.
-Evidence for an optimal algorithm underlying signal combination in human visual cortex.
-Cereb Cortex.
-2017;27: 254--264.
-doi:\href{https://doi.org/10.1093/cercor/bhw395}{10.1093/cercor/bhw395}
-
 \leavevmode\hypertarget{ref-Kaestner2019}{}%
-28.
+50.
 Kaestner M, Maloney RT, Wailes-Newson KH, Bloj M, Harris JM, Morland AB, et al.
@@
 doi:\href{https://doi.org/10.1073/pnas.1817202116}{10.1073/pnas.1817202116}
-
-\leavevmode\hypertarget{ref-Martin2022}{}%
-29.
-Martin JT, Pinto J, Bulte D, Spitschan M.
-PyPlr: A versatile, integrated system of hardware and software for researching the human pupillary light reflex.
-Behavior Research Methods.
-2022;54: 2720--2739.
-doi:\href{https://doi.org/10.3758/s13428-021-01759-3}{10.3758/s13428-021-01759-3}
-
-\leavevmode\hypertarget{ref-Estevez1982}{}%
-30.
-Estévez O, Spekreijse H.
-The "silent substitution" method in visual research.
-Vision Research.
-1982;22: 681--691.
-doi:\href{https://doi.org/10.1016/0042-6989(82)90104-3}{10.1016/0042-6989(82)90104-3}
-
-\leavevmode\hypertarget{ref-Shapiro1996}{}%
-31.
-Shapiro AG, Pokorny J, Smith VC.
-Conerod receptor spaces with illustrations that use CRT phosphor and light-emitting-diode spectra.
-Journal of the Optical Society of America A.
-1996;13: 2319.
-doi:\href{https://doi.org/10.1364/josaa.13.002319}{10.1364/josaa.13.002319}
-
-\leavevmode\hypertarget{ref-Spitschan2018}{}%
-32.
-Spitschan M, Woelders T.
-The Method of Silent Substitution for Examining Melanopsin Contributions to Pupil Control.
-Frontiers in Neurology.
-2018;9.
-doi:\href{https://doi.org/10.3389/fneur.2018.00941}{10.3389/fneur.2018.00941}
-
-\leavevmode\hypertarget{ref-Martin2023}{}%
-33.
-Martin JT, Boynton GM, Baker DH, Wade AR, Spitschan M.
-PySilSub: An open-source python toolbox for implementing the method of silent substitution in vision and nonvisual photoreception research.
-Journal of Vision.
-2023;23: 10.
-doi:\href{https://doi.org/10.1167/jov.23.7.10}{10.1167/jov.23.7.10}
-
-\leavevmode\hypertarget{ref-Stockman2000}{}%
-34.
-Stockman A, Sharpe LT.
-The spectral sensitivities of the middle- and long-wavelength-sensitive cones derived from measurements in observers of known genotype.
-Vision Res.
-2000;40: 1711--37.
-doi:\href{https://doi.org/10.1016/s0042-6989(00)00021-3}{10.1016/s0042-6989(00)00021-3}
-
-\leavevmode\hypertarget{ref-Spitschan2015}{}%
-35.
-Spitschan M, Aguirre GK, Brainard DH.
-Selective stimulation of penumbral cones reveals perception in the shadow of retinal blood vessels.
-PLoS One.
-2015;10: e0124328.
-doi:\href{https://doi.org/10.1371/journal.pone.0124328}{10.1371/journal.pone.0124328}
-
-\leavevmode\hypertarget{ref-Zele2018}{}%
-36.
-Zele AJ, Feigl B, Adhikari P, Maynard ML, Cao D.
-Melanopsin photoreception contributes to human visual detection, temporal and colour processing.
-Scientific Reports.
-2018;8.
-doi:\href{https://doi.org/10.1038/s41598-018-22197-w}{10.1038/s41598-018-22197-w}
-
-\leavevmode\hypertarget{ref-Kassner2014}{}%
-37.
-Kassner M, Patera W, Bulling A.
-Pupil: An open source platform for pervasive eye tracking and mobile gaze-based interaction.
-Proceedings of the 2014 ACM international joint conference on pervasive and ubiquitous computing: Adjunct publication.
-ACM; 2014.
-doi:\href{https://doi.org/10.1145/2638728.2641695}{10.1145/2638728.2641695}
-
-\leavevmode\hypertarget{ref-Norcia2015}{}%
-38.
-Norcia AM, Appelbaum LG, Ales JM, Cottereau BR, Rossion B.
-The steady-state visual evoked potential in vision research: A review.
-Journal of Vision.
-2015;15(6): 4.
-doi:\href{https://doi.org/10.1167/15.6.4}{10.1167/15.6.4}
-
-\leavevmode\hypertarget{ref-Pokorny1987}{}%
-39. Pokorny J, Smith VC, Lutze M. Aging of the human lens. Applied Optics. 1987;26: 1437. doi:\href{https://doi.org/10.1364/ao.26.001437}{10.1364/ao.26.001437}
-
-\leavevmode\hypertarget{ref-Stockman1999}{}%
-40.
-Stockman A, Sharpe LT, Fach C.
-The spectral sensitivity of the human short-wavelength sensitive cones derived from thresholds and color matches.
-Vision Research.
-1999;39: 2901--2927.
-doi:\href{https://doi.org/https://doi.org/10.1016/S0042-6989(98)00225-9}{https://doi.org/10.1016/S0042-6989(98)00225-9}
-
-\leavevmode\hypertarget{ref-Bone1988}{}%
-41. Bone RA, Landrum JT, Fernandez L, Tarsis SL. Analysis of the macular pigment by HPLC: Retinal distribution and age study. Investigative Ophthalmology \& Visual Science. 1988;29: 843--849.
-
-\leavevmode\hypertarget{ref-CIE2006}{}%
-42. CIE. Fundamental chromaticity diagram with physiological axes. CIE Central Bureau; 2006. Available: \url{https://cie.co.at/publications/fundamental-chromaticity-diagram-physiological-axes-part-1}
-
-\leavevmode\hypertarget{ref-CIE2018}{}%
-43. CIE. CIE system for metrology of optical radiation for ipRGC-influenced responses to light. CIE Central Bureau; 2018. doi:\href{https://doi.org/10.25039/S026.2018}{10.25039/S026.2018}
-
-\leavevmode\hypertarget{ref-Trieschmann2007}{}%
-44.
-Trieschmann M, Kuijk FJGM van, Alexander R, Hermans P, Luthert P, Bird AC, et al.
-Macular pigment in the human retina: Histological evaluation of localization and distribution.
-Eye.
-2007;22: 132--137.
-doi:\href{https://doi.org/10.1038/sj.eye.6702780}{10.1038/sj.eye.6702780}
-
-\leavevmode\hypertarget{ref-Zele2019}{}%
-45.
-Zele AJ, Adhikari P, Cao D, Feigl B.
-Melanopsin driven enhancement of cone-mediated visual processing.
-Vision Res.
-2019;160: 72--81.
-doi:\href{https://doi.org/10.1016/j.visres.2019.04.009}{10.1016/j.visres.2019.04.009}
-
-\leavevmode\hypertarget{ref-Baker2020}{}%
-46.
-Baker DH, Vilidaite G, McClarnon E, Valkova E, Bruno A, Millman RE.
-Binaural summation of amplitude modulation involves weak interaural suppression.
-Sci Rep.
-2020;10: 3560.
-doi:\href{https://doi.org/10.1038/s41598-020-60602-5}{10.1038/s41598-020-60602-5}
-
-\leavevmode\hypertarget{ref-Carroll2002}{}%
-47. Carroll J, Neitz J, Neitz M. Estimates of L:M cone ratio from ERG flicker photometry and genetics. Journal of Vision. 2002;2: 1. doi:\href{https://doi.org/10.1167/2.8.1}{10.1167/2.8.1}
-
-\leavevmode\hypertarget{ref-Hofer2005}{}%
-48.
-Hofer H, Carroll J, Neitz J, Neitz M, Williams DR.
-Organization of the human trichromatic cone mosaic.
-The Journal of Neuroscience.
-2005;25: 9669--9679.
-doi:\href{https://doi.org/10.1523/jneurosci.2414-05.2005}{10.1523/jneurosci.2414-05.2005}
-
-\leavevmode\hypertarget{ref-Baker2021}{}%
-49. Baker DH. Statistical analysis of periodic data in neuroscience. Neurons, Behavior, Data analysis, and Theory. 2021;5. doi:\href{https://doi.org/10.51628/001c.27680}{10.51628/001c.27680}
-
-\leavevmode\hypertarget{ref-Carpenter2017}{}%
-50.
-Carpenter B, Gelman A, Hoffman MD, Lee D, Goodrich B, Betancourt M, et al.
-Stan: A probabilistic programming language.
-J Stat Softw.
-2017;76.
-doi:\href{https://doi.org/10.18637/jss.v076.i01}{10.18637/jss.v076.i01}
 
